### 2014-08-29 docs/CarbonInvestments.tex
Initial import into new clean archive
Previous archive was getting large and has been archived for posterity.

\documentclass[10pt]{book} %,openbib

\usepackage[utf8x]{inputenc}
\usepackage{amsmath, amsfonts, mathrsfs, textcomp,amssymb,natbib,bbm,natbib}
\usepackage{multicol}
\usepackage{graphicx}

\title{Reproductive Allocation Calculations}
\author{K. Abramowicz, E. Wenk, D. Falster}
\date{\today}

\graphicspath{../output/docs}

\setlength{\textwidth}{151mm}\topmargin 7mm \textheight 210mm
\headheight 0mm \headsep 10mm \footskip 15mm \textwidth 151mm
\oddsidemargin 6.3mm \evensidemargin 6.3mm \marginparwidth 20mm

\begin{document}
\maketitle
\chapter{Software description}
\section{Purpose of software}
The goal of the code is to:
\begin{itemize}
\item Estimate reproductive investment from census data
\item Estimate growth investment
\item Determin Reproductive Allocation schedules for 14 species.
\end{itemize}
\section{Structure of Software}
\begin{center}
\includegraphics[width=0.75\linewidth]{Flow1.png}\\
\includegraphics[width=0.75\linewidth]{Flow2.png}\\
\includegraphics[width=0.75\linewidth]{Flow3.png}
\end{center}

\section{Listing of files}
\begin{itemize}
\item Data Files
\begin{itemize}
\item \texttt{flower\_parts.csv} File containing measurements of weight, length, and dimensions for given species. The file is used to obtain the average weights of plant parts based on the count, length and dimension measurements of individual species at given times.
\item \texttt{reproduction.csv} File containing information about counts, lengths and dimensions (not weights) for individuals at different censuses.
\item \texttt{2013\_Kuringgai\_harvest.csv} File containing information sbout diameters and weight for the sampled trees.
\item \texttt{Flowering\_cat\_lookup\_table.csv} File containing table describing the allowed parts of plants and the way they are measured.
\item \texttt{MultiplierTable.csv} File containing table describing the multiplicity of possible seed per plan part.
\end{itemize}
\item{R-functions' files}
\begin{itemize}
\item \texttt{WeightFunctions.R} - converts counts, lengths and dimensions to weights
\item \texttt{WeightCalculationAtCansus.R} - calculates weight of tree parts
\item \texttt{RemoveDumplicates.R} - merges multiple entries for the same tree parts
\item \texttt{DeriveMissingParts.R} - For particular species no measurements are provided/possible and they are being imputed with the values calculated by the script above.
\item \texttt{WeightCalculationsForTree.R} - calculates of weight dynamics for a tree along censuses
\item \texttt{InvestmentCalculations.R} - determines of investments of the plant along all censuses given a weight tree structure object
\item \texttt{InvestmentInAPartType.R} - calculates the investment in creation of a given type element at given census
\item \texttt{InvestmentInIndividualPart} - calculates the investment in creation of an \textbf{individual} of a given type at given census
\end{itemize}
\item{R-scripts}
\begin{itemize}
\item \texttt{AvWeightForParts.R} - calculates the average weights for the parts included in the {flower\_parts.csv} file for a given species.
\item \texttt{AvCountsPerMM.R} - calculates the average density of counts per mm for a given species. Saves results in AvCountsPerMM.csv
\item \texttt{RegressionCoefficients.R} - Script determining the regression coefficients that are use to obtain weights of elements from their dimensions.
\item \texttt{GraphRepresentation.R} - Script containing the structure for each specie which describes part names, their progression, and carbon flow.
\item \texttt{OrderedListsOfParts.R} - Script containing the ordered part names. Used for construction of this document.
\item \texttt{RedoDocument.R} - Short script calling all functions which produce tables and plots used in this document.
\item \texttt{CalculateMassAndDiameter.R} -script calculating and saving masses and diameters for the individual plants (using data in \texttt{2013\_Kuringgai\_harvest.csv})
\item \texttt{RA\_Calculations.R} - script reading reproductive investment, growth investment and calculating total investment and RA.
\end{itemize}
\item{Plotting functions}
\begin{itemize}
\item \texttt{Plot\_RAs} Function that plots and saves in a pdf RA for all the species on one plot.
\item \texttt{PlotIndividual\_RA} Function that for each species creates a 3 panel plot with reproductive investment, growth investment and RA.
\end{itemize}
\item Libraries used
\begin{itemize}
\item \texttt{igraph} used for representing and manipulating plant graphs.
\item \texttt{stringr} used for some string manipulations.
\item \texttt{colorspace} used for defining HCL colours for plotting RAs.
\end{itemize}
\end{itemize}

\newpage
%
%
% Individual functions
%
%
\section{Individual Functions Description}
\subsection*{WeightFromCount (in WeightFunctions.R)}
Given the count, species type and plant part the function returns a vector that contains the weight of each plant part. \\
Input parameters:
\begin{itemize}
\item \texttt{count}  integer describing number of observed plant parts
\item \texttt{species} character string defining the name of the species (as used in \texttt{flower\_part.csv}) file
\item \texttt{part} character sting corresponding to the name of the plant part
\end{itemize}
Output parameters:
\begin{itemize}
\item \texttt{w}  vector of length \texttt{count} with weight of the plant part at each position.
\end{itemize}

\subsection*{WeightFromLength (in WeightFunctions.R)}
Given the length of a body par, species type and plant part the function returns a vector that contains the weight of each plant part. The function uses the species specific relationship to estimate the count corresponding to the observed length. \\
Input parameters:
\begin{itemize}
\item \texttt{length}  double describing the length of observed plant parts
\item \texttt{species} character string defining the name of the species (as used in \texttt{flower\_part.csv}) file
\item \texttt{part} character sting corresponding to the name of the plant part
\end{itemize}
Output parameters:
\begin{itemize}
\item \texttt{w}  vector with weight of the plant part at each position. The size of the vector is estimated using allometric relationship.
\end{itemize}

\subsection*{WeightCalculationsAtCensus}
Given the census data from the measurement Excel spreadsheet the function creates a list which contains information about all existing parts, their counts, and weights.
\\
Input parameters:
\begin{itemize}
\item \texttt{C}  Data from a given census about an individual tree
\end{itemize}
Output parameters:
\begin{itemize}
\item \texttt{C\_list}   A list which elements are list that contain fields: \texttt{type} -part name, \texttt{m.type} - measurement type (count, length), \texttt{count} - number of such parts, \texttt{weight} - vector of weight for each part.
\end{itemize}

\subsection*{RemoveDuplicates}
Checks the list describing tree at a given census and merges multiple fields for the same tree part.
\\
Input parameters:
\begin{itemize}
\item \texttt{C}  List with the structure of output of \texttt{MeasurmentsToWeight} function.
\end{itemize}
Output parameters:
\begin{itemize}
\item \texttt{C\_new}  The same list with the fields for the same tree part merged. If there were two measurement types used for a given part the \texttt{m.type} is changed to \texttt{mixed}.
\end{itemize}

\subsection*{WeightCalculationsForTree}
Given the information about particular individual tree the functions returns a list representing the growth development of the tree.
\\
Input parameters:
\begin{itemize}
\item \texttt{Tree}  Rows of data.frame in  \texttt{reproduction.csv} corresponding to  an individual tree from all censuses
\end{itemize}
Output parameters:
\begin{itemize}
\item \texttt{TreeList}  A list which in the first element contains the tree id. The remaining 18 elements are 3 element lists with fields \texttt{pre.existing}, \texttt{new} and \texttt{total} describing the structure of the tree at each census. Each of the 3 lists is in the format corresponding to the result of \texttt{MeasurmentsToWeight} function.
\end{itemize}

\subsection*{AdjustForMultiplicity (in MultiplicityAdjustment.R)}
Function \texttt{AdjustForMultiplicity} together with its help functions (\texttt{AdjustForMultiplicity\_Census,AdjustForMultiplicity\_List}) that given Tree Structure adjust counts and weights to take into account number of seeds per fruit/flower etc.
Input parameters:
\begin{itemize}
\item \texttt{Tree}  Tree structure with weights and individual ID of a plant (result of WeightCalculationsForTree)
\end{itemize}
Input parameters:
\begin{itemize}
\item \texttt{Tree}  Tree structure with weights and individual ID of a plant (result of WeightCalculationsForTree), where counts are multiplied by multipliers and weights are divided.
\end{itemize}

\subsection*{InvestmentInIndividualPart}
Given element name, its weight, allowed progression and the list of possible existing predecessors the function returns the investment  that was made to grow the element from its previous form to the existing one.
Input parameters:
\begin{itemize}
\item \texttt{Element}  Name of element
\item \texttt{TreeList\_Pred}  Tree structure (similar to the result of WeightCalculcations function) with possible predecessors. Its length determine the time point at which we are now.
\item \texttt{Progression} Character vector defining the possible previous stages of the Element.
\item \texttt{El\_weight} Weight of the element.

\end{itemize}
Output parameter is a list containing 6 elements
\begin{itemize}
\item \texttt{TreeList\_Pred}  Updated list of possible predecessors with the used predecessor removed.
\item \texttt{Invest} Calculated investment (using the path from element to it's predecessor, incorporating the carbon flow in case of division)
\item \texttt{from} Selected predecessor's name
\item \texttt{to} The same as  \texttt{Element}
\item \texttt{Census} Information at which census the transition to Element has been observed.
\item \texttt{Count} 1.
\end{itemize}

\noindent \textbf{Function description:}
\begin{itemize}
\item Given the element, possible predecessor and history of development of the tree, the function performs a back search in history looking for matching Predecessor.
\item After finding Predecessor the investment is calculated. The investment is defined as the difference between the Element mass and the proportion of the mass of Predecessor. If the path from Predecessor to the Element does not have any accessory tissue the proportion will be 1. Otherwise the side allocation of the carbon to the accessory tissue is taken into consideration.
\item The predecessor is removed from the list of possible predecessors and the list is returned for further calculations.
\end{itemize}

\subsection*{InvestmentInAPartType}
Given part name, tree structure, allowed progression and the tree structure of possible existing predecessors the function returns the investment that was made to grow the plant part of a given type. It also calculates the investment in all newly created elements of a given type.
Input parameters:
\begin{itemize}
\item \texttt{TreeList}  Tree structure (like the result of WeightCalculcations function) containing information about the plant. The length of the list determine current time point.
\item \texttt{TreeList\_Pred}  Tree structure (like the result of WeightCalculcations function) with possible predecessors.
\item \texttt{Element}  Name of element
\item \texttt{Progression} Character vector defining the possible previous stages of the Element.
\end{itemize}
Output parameter is a list containing 2 elements
\begin{itemize}
\item \texttt{TreeList\_Pred}  Updated list of possible predecessors with the used predecessors removed.
\item \texttt{Invest} Data structure containing information about investment in creation/progression of all elements of a given type at a given time.
\end{itemize}

\noindent \textbf{Function description:}
\begin{itemize}
\item Function determines the census by calculating length of TreeList\_Pred.
\item First we check if there are new elements of given type at this time point. If yes, the investment in them is calculated as their weight.
\item The function checks if there are pre.existing elements of that type. If yes, it checks how many they are and use function CalculateIndividualInvestment to find the investment made in them attaining the stat.
\item \textit{OBS!} Exception is made if at the first census we have a part that is pre.existing. It's mass is not to be counted as new since it was created outside the monitoring period, however, the information about it needs to be included as in later censuses it might develop resulting in carbon investment.
\end{itemize}

\subsection*{InvestmentCalculations}
Given a tree structure along all censuses the history of investment is calculated.
Input parameters:
\begin{itemize}
\item \texttt{TreeList}  Tree structure (the result of WeightCalculcations function) containing information about the plant.
\end{itemize}
Output parameter:
\begin{itemize}
\item \texttt{Inv} Data frame containing information about investment in creation/progression of specific parts along all censuses.
\item \texttt{Lost} Data frame containing information about lost parts.
\item \texttt{Error} Data frame containing information about possible errors (missing predecessors to preexisting species).
\end{itemize}

\noindent \textbf{Function description:}
\begin{itemize}
\item First the structure of the specie is determined and number of main paths is determined. Then for each of the main paths:
\begin{itemize}
\item We determine the main progression line, and go backwards census by census along all elements in the main progression lines calculating the investment.
If the line includes "x-or" parts (mostly aborted fruits,flowers) calculation  along this lines is made as well.
\item After calculating main and "x-or" lines the list of possible predecessors is reset to all values and separate carbon investment is performed for each of the auxiliary tissue type.
\end{itemize}
\end{itemize}

\subsection*{CalculateInvestmentForIndividualPlane}
Given the name (tag\_ID) of the individual plant, calculations of reproductive investment are performed.
Input parameters:
\begin{itemize}
\item \texttt{individual}  String corresponding to tree ID in the reproduction spreadsheet
\end{itemize}
Output parameter is a list including 3 data frames
\begin{itemize}
\item \texttt{Inv} Data frame containing information about investment in creation/progression of specific parts along all censuses.
\item \texttt{Lost} Data frame containing information about lost parts.
\item \texttt{Error} Data frame containing information about possible errors (missing predecessors to preexisting element).
\end{itemize}

\subsection*{CalculateInvestmentForSpecies}
A wrapper around function \texttt{CalculateInvestmentForIndividualPlane} that given string specifying specie name calculates the investment for all individuals of the species and saves the result in csv files.
Input parameters:
\begin{itemize}
\item \texttt{TreeList}  Tree structure (the result of WeightCalculcations function) containing information about the plant.
\end{itemize}
The function does not return anything, however it saves 3 files(\texttt{****} stands for species name):
\begin{itemize}
\item \texttt{****\_Inv} Information about investment in creation/progression of specific parts along all censuses for all the individuals.
\item \texttt{****\_Lost} Information about lost parts for all individuals.
\item \texttt{****\_Error} Information about possible errors (missing predecessors to preexisting element).
\end{itemize}

\subsection{GraphRepresentation}

Script \texttt{GraphRepresentatio.R} contains the definitions of the graph structures defining plant development. This structures mimic to a large extent the plant maps.
Each specie is represented by \texttt{igraph} object and a data frame \texttt{Paths} defining main progression lines for the species.

The graph object consist of:
\begin{itemize}
\item Vertices with name being a part name. Each vertex is also coloured. The distinct progression lines have distinct colour. Moreover the final stages of the accessory tissues have colour with a number larger by 1 from the main path they belong to.
\item Edges that connect the subsequent parts on the map. Each edge has a weight attribute defining how much of the carbon allocated the predecessor is being used for ancestor creation. If there are no accessory tissues created at this point of progression weight will be 1. If there is more than one ancestor the weights are set as the proportion of the ancestor mass to the sum of all ancestors. This is done at that point manually and needs to be adjusted if any new data will be collected.
\end{itemize}
An example of the graph for CEOR species is presented in Figure 1.1.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=6in]{PlantGraph.pdf}
\end{center}
\caption{Graphical presentation of the \texttt{igraph} tree structure of plant map for COER.}
\end{figure}

\chapter{Species Average Weight Summary}
\newpage
\footnotesize

\clearpage
\newpage
\section{BAER}
\begin{multicols}{2}
\includegraphics[width=3in]{BAER.png}
\vfill
\columnbreak
\input{../output/docs/BAER.tex}
\\Comments:
\begin{itemize}
\item \textbf{Fruits just collected and weights will be added soon.
Need to still collect finished flower stigma (didn't realize this) and seed pods}
\end{itemize}
\end{multicols}

\clearpage
\newpage
\section{BOLE}
\begin{multicols}{2}
\includegraphics[width=3in]{BOLE.png}
\vfill
\columnbreak
\input{../output/docs/BOLE.tex}
\\Comments:
\begin{itemize}
\item Missing measurements.
\item Presumably some derivative calculations are necessary for some categories.
\end{itemize}
\end{multicols}

\clearpage
\newpage

\section{COER}
\begin{multicols}{2}
\includegraphics[width=2.7in]{COER.png}
\vfill
\columnbreak
\input{../output/docs/COER.tex}
\\Comments:
\begin{itemize}
\item Missing measurements.
\end{itemize}
\end{multicols}

\clearpage
\newpage

\section{EPMI}
\begin{multicols}{2}
\includegraphics[width=2.5in]{EPMI.png}
\vfill
\columnbreak
\input{../output/docs/EPMI.tex}
\\Comments:
\begin{itemize}
\item OK.
\end{itemize}
\end{multicols}

\clearpage
\newpage

\section{GRBU}
\begin{multicols}{2}
\includegraphics[width=3in]{GRBU.png}
\vfill
\columnbreak

\input{../output/docs/GRBU.tex}\\
Comments:
\begin{itemize}
\item Missing measurements.
\item Otherwise OK.
\end{itemize}

\end{multicols}

\clearpage
\newpage

\section{GRSP}
\begin{multicols}{2}
\includegraphics[width=3in]{GRSP.png}
\vfill
\columnbreak

\input{../output/docs/GRSP.tex}
\\Comments:
\begin{itemize}
\item Missing measurments
\end{itemize}

\end{multicols}

\clearpage
\newpage
\section{HATE}
\begin{multicols}{2}
\includegraphics[width=3in]{HATE.png}
\vfill
\columnbreak
\input{../output/docs/HATE.tex}
\\Comments:
\begin{itemize}
\item Missing measurements.
\end{itemize}

\end{multicols}

\clearpage
\newpage

\section{HEPU}
\begin{multicols}{2}
\includegraphics[width=3in]{HEPU.png}
\vfill
\columnbreak
\input{../output/docs/HEPU.tex}
\\Comments:
\begin{itemize}
\item Warning: fruit large immature = fruit mature
\item Error: Fruit aborted $<$ fruit large immature
\item Otherwise ok.
\end{itemize}
\end{multicols}

\clearpage
\newpage

\section{LEES}
\begin{multicols}{2}
\includegraphics[width=3in]{LEES.png}
\vfill
\columnbreak
%%%%
\input{../output/docs/LEES.tex}
%%%%%
\\
Comments:
\begin{itemize}
\item  OK.
\end{itemize}
\end{multicols}
\clearpage
\newpage

\section{PELA}
\begin{multicols}{2}
\includegraphics[width=2.8in]{PELA.png}
\vfill
\columnbreak
\input{../output/docs/PELA.tex}
\\Comments:
\begin{itemize}
\item Missing measurements.
\end{itemize}

\end{multicols}

\clearpage
\newpage
\section{PEPU}
\begin{multicols}{2}
\includegraphics[width=2.7in]{PEPU.png}
\vfill
\columnbreak
\input{../output/docs/PEPU.tex}
\\Comments:
\begin{itemize}
\item Missing measurements. \textbf{To be collected}.
\end{itemize}

\end{multicols}
\clearpage
\newpage

\clearpage
\newpage
\section{PHPH}
\begin{multicols}{2}
\includegraphics[width=3in]{PHPH.png}
\vfill
\columnbreak
\input{../output/docs/PHPH.tex}
\\Comments:
\begin{itemize}
\item Missing measurements. \textbf{To be collected}.
\end{itemize}
\end{multicols}

\clearpage
\newpage
\section{PILI}
\begin{multicols}{2}
\includegraphics[width=2.7in]{PILI.png}
\vfill
\columnbreak
\input{../output/docs/PILI.tex}
\\Comments:
\begin{itemize}
\item No measurements for "seed aborted".
\item Otherwise ok.
\end{itemize}
\end{multicols}

\clearpage
\newpage
\section{PUTU}
\begin{multicols}{2}
\includegraphics[width=2.5in]{PUTU.png}
\vfill
\columnbreak
\input{../output/docs/PUTU.tex}
\\Comments:
\begin{itemize}
\item OK
\end{itemize}
\end{multicols}

\chapter{Additional preliminary calculations}

\section{Average count/length values}

\begin{figure}[h!]
\begin{center}
\input{../output/docs/AvCountsPerMM.tex}
\end{center}
\caption{Table summarising the average number of elements per mm. To be used for calculations of mass based on the length for conversion to counts.}
\end{figure}

\section{Regression Fits and Coefficients}
\subsection*{GRBU}
\begin{center}
\includegraphics[width=2.7in]{../output/docs/GRBU_fruit_large_immature.pdf}
\includegraphics[width=2.7in]{../output/docs/GRBU_seed_pod.pdf}
\end{center}

\subsection{GRSP}
\begin{center}
\includegraphics[width=2.7in]{../output/docs/GRSP_fruit_large_immature.pdf}
\includegraphics[width=2.7in]{../output/docs/GRSP_seed_pod.pdf}
\end{center}

\subsection{PELA}
\begin{center}
\includegraphics[width=2.7in]{../output/docs/PELA_fruit_large_immature.pdf}
\includegraphics[width=2.7in]{../output/docs/PELA_seed_pod.pdf}\\
\includegraphics[width=2.7in]{../output/docs/PELA_seed.pdf}
\end{center}

\subsection{BAER}
\begin{center}
\includegraphics[width=2.7in]{../output/docs/BAER_cone_young.pdf}
\includegraphics[width=2.7in]{../output/docs/BAER_cone_green.pdf}\\
\includegraphics[width=2.7in]{../output/docs/BAER_cone_brown_no_expanded_follicles.pdf}
\includegraphics[width=2.7in]{../output/docs/BAER_cone_brown.pdf}\\
\includegraphics[width=2.7in]{../output/docs/BAER_cone_aborted.pdf}
\includegraphics[width=2.7in]{../output/docs/BAER_cone_base_green.pdf}\\
\includegraphics[width=2.7in]{../output/docs/BAER_cone_base_brown.pdf}
\end{center}

\subsection{PEPU}
\begin{center}
\includegraphics[width=2.7in]{../output/docs/PEPU_cone_green.pdf}
\includegraphics[width=2.7in]{../output/docs/PEPU_cone_brown.pdf}\\
\includegraphics[width=2.7in]{../output/docs/PEPU_cone_aborted.pdf}
\end{center}
\newpage
\subsection{Summary table for regression}
\begin{figure}[h!]
\begin{center}
\input{../output/docs/RegressionTable.tex}
\end{center}
\caption{Table summarising the equations used to determine weights of individual plant parts by using their size.}
\end{figure}

\chapter{Preliminary results}
\section{Reproductive allocation results}
\subsection{Overview}
\includegraphics[width=1\linewidth]{../output/docs/RA_comparison.pdf}
\section{Individual species}
\subsection{BAER}
\includegraphics[width=1\linewidth]{../output/docs/RA_BAER.pdf}
\subsection{BOLE}
\includegraphics[width=1\linewidth]{../output/docs/RA_BOLE.pdf}
\subsection{COER}
\includegraphics[width=1\linewidth]{../output/docs/RA_COER.pdf}
\subsection{EPMI}
\includegraphics[width=1\linewidth]{../output/docs/RA_EPMI.pdf}
\subsection{GRBU}
\includegraphics[width=1\linewidth]{../output/docs/RA_GRBU.pdf}
\subsection{GRSP}
\includegraphics[width=1\linewidth]{../output/docs/RA_GRSP.pdf}
\subsection{HATE}
\includegraphics[width=1\linewidth]{../output/docs/RA_HATE.pdf}
\subsection{HEPU}
\includegraphics[width=1\linewidth]{../output/docs/RA_HEPU.pdf}
\subsection{LEES}
\includegraphics[width=1\linewidth]{../output/docs/RA_LEES.pdf}
\subsection{PELA}
\includegraphics[width=1\linewidth]{../output/docs/RA_PELA.pdf}
\subsection{PEPU}
\includegraphics[width=1\linewidth]{../output/docs/RA_PEPU.pdf}
\subsection{PHPH}
\includegraphics[width=1\linewidth]{../output/docs/RA_PHPH.pdf}
\subsection{PILI}
\includegraphics[width=1\linewidth]{../output/docs/RA_PILI.pdf}
\subsection{PUTU}
\includegraphics[width=1\linewidth]{../output/docs/RA_PUTU.pdf}

\end{document}

### 2014-08-29 analysis/CalculateInvestmentForIndividualPlant.R

@@ -1,0 +1,45 @@
+source('analysis/WeightCalculationsForTree.R')
+source('analysis/InvestmentCalculations.R')
+source('analysis/GraphRepresentation.R')
+source('analysis/MultiplicityAdjustment.R')
+
+
+CalculateInvestmentForIndiviualPlant<-function(individual)
+{ #Read and extract data
+  Data=read.csv('data/reproduction.csv',sep=',',header=T,stringsAsFactors = FALSE, na.strings="")
+  Tree=Data[Data$individual==individual,]
+  #Transform counts to weights and adjust for multiplicity 
+  TreeListOrig=WeightCalculationsForTree(Tree)
+  #TreeListAdj=TreeListOrig;
+  TreeListAdj=AdjustForMultiplicity(TreeList=TreeListOrig)
+  #Calculate investment
+  Res=InvestmentCalculations(TreeListAdj)
+  #Extract and reorder the results
+  I=Res[["Inv"]]
+  if(!is.null(I))
+  {
+    I["age"]=as.numeric(unique(Tree$age))
+    I=I[,c(8,9,1:7)]
+  }
+  
+  Err=Res[["Err"]]
+  if(!is.null(Err))
+  {
+    Err["Individual"]=individual
+    Err=Err[,c(4,(1:3))]
+  }
+  Lost=Res[["Lost"]]
+  if(!is.null(Lost))
+  {if(nrow(Lost)>0)
+  {  
+    Lost["Individual"]=individual
+    Lost["age"]=as.numeric(unique(Tree$age))
+    Lost=Lost[,c(5,6,1:4)]
+  }
+  if(nrow(Lost)==0)
+  {
+    Lost=NULL
+  }
+  }
+  list(Inv=I,Lost=Lost,Err=Err)
+}

### 2014-08-29 analysis/CalculateMassAndDiameters.R

@@ -1,0 +1,67 @@
+CalculateMassAndDiameters<-function()
+{
+library(smatr)
+library(plyr)
+library(dplyr)
+source("analysis/plot-utils.R")
+
+data <- tbl_df(read.csv("data/2013_Kuringgai_harvest.csv", stringsAsFactors=FALSE)) %.%
+  filter(year==2013) %.%
+  arrange(tag_ID, date, segment)
+
+data$species[data$species=="BAER "] <- "BAER"
+
+segments <- list()
+segments[["1"]] <- c(as.character(1:8,"1.2","1.3","1.2.1","1.2.1.1","1.1.2","1.1.2.1","1.1.1.2"))
+segments[["2"]] <- c(as.character(2:8,"1.1.2","1.1.2.1","1.1.1.2"))
+segments[["3"]] <- c(as.character(3:8,"1.1.1.2"))
+segments[["4"]] <- as.character(4:8)
+segments[["5"]] <- as.character(5:8)
+segments[["6"]] <- as.character(6:8)
+segments[["7"]] <- as.character(7:8)
+segments[["8"]] <- as.character(8)
+segments[["9"]] <- c("1.2","1.2.1","1.2.1.1")
+segments[["10"]] <- c("1.3")
+segments[["11"]] <- c("1.2.1","1.2.1.1")
+segments[["12"]] <- c("1.2.1.1")
+segments[["13"]] <- c("1.1.2","1.1.2.1")
+segments[["14"]] <- c("1.1.2.1")
+segments[["15"]] <- c("1.1.1.2")
+
+## Get total mass of all material subteneded by given node
+
+get.mass.at.node <- function(data, segments){
+  data %.%  filter(segment %in% segments) %.%
+    group_by(tag_ID) %.%
+    summarise(
+      species = species[1],
+      site= site[1],
+      age=age[1],
+      leaf_weight=sum(leaf_weight),
+      stem_weight=sum(stem_weight),
+      total_weight=sum(leaf_weight, stem_weight))
+}
+
+mass <- ldply(segments,  function(x) get.mass.at.node(data, x)) %.%
+  rename(c('.id'='node_above')) %.%  # rename plyr name to somewthing more meaningful
+  arrange(tag_ID, node_above)
+
+# Get avergae diameter for base of segment. This is given by diameter readings for segment
+# with names in list above
+get.diam.node.above <- function(data, level){
+  data %.%  filter(node_above == level) %.%
[…]

### 2014-08-29 analysis/InvestmentInAPartType.R

@@ -1,0 +1,58 @@
+source('analysis/InvestmentInIndividualPart.R')
+source('analysis/GraphRepresentation.R')
+
+
+
+InvestmentInAPartType<-function(TreeList,TreeList_Pred,Element,Progression)
+{
+ #Initialize data frames
+ Inv=From=To=FromCensus=ToCensus=Count=c()
+ Inv_new=data.frame(FromCensus=FromCensus,ToCensus=ToCensus,From=From,To=To,Inv=Inv,Count=Count)
+ Inv_pre.ex=data.frame(FromCensus=FromCensus,ToCensus=ToCensus,From=From,To=To,Inv=Inv,Count=Count)
+ Inv_total=data.frame(FromCensus=FromCensus,ToCensus=ToCensus,From=From,To=To,Inv=Inv,Count=Count)
+
+ N=length(TreeList)
+ #Are there any new parts of that type? If yes, calculate investment
+ I_new=sapply(TreeList[[N]]$new,function(x) x$type)==Element
+ if(sum(unlist(I_new)))
+ {
+     Inv=TreeList[[N]]$new[[which(I_new)]]$weight
+     From=rep("0",length(Inv))
+     To=rep(Element,length(Inv))
+     ToCensus=rep(N-1,length(Inv))
+     FromCensus=rep(N-2,length(Inv))
+     Count=rep(1,length(Inv))
+     Inv_new=data.frame(FromCensus=FromCensus,ToCensus=ToCensus,From=From,To=To,Inv=Inv,Count=Count)
+ }
+ 
+ #Are there any pre-existing parts of that type.
+ I_pre.ex=sapply(TreeList[[N]]$pre.ex,function(x) x$type)==Element
+ Inv=From=To=Census=Count=FromCensus=ToCensus=c()
+ ErrList=data.frame(Element=NA,Census=NA,Count=NA)
+ #If there are there are pre.existing parts and we are at least at Census 2 we try to find a predecessor.
+ if(sum(unlist(I_pre.ex))&N>2)
+ {
+ #Check how many elements of that type there are
+ n_elements=TreeList[[N]]$pre.ex[[which(I_pre.ex)]]$count
+ for(i in 1:n_elements)
+  {
+   #Extract the weight of a single element
+   El_weight=TreeList[[N]]$pre.ex[[which(I_pre.ex)]]$weight[i]
[…]

### 2014-08-29 analysis/InvestmentInIndividualPart.R

@@ -1,0 +1,44 @@
+InvestmentInIndividualPart<-function(Element,TreeList_Pred,Progression,El_weight)
+{
+  #Determine what time are we at
+  N=length(TreeList_Pred)
+  #Go back in time
+  for(t in (N-1):2)
+  {
+    #If there is no possible progression for this part add that to error list
+    if (length(Progression)==1)
+    { 
+      ErrList=data.frame(Element=Element,Census=N-1,Count=1)
+      return(list(TreeList_Pred=TreeList_Pred,Invest=NA,from=NA,to=NA,FromCensus=NA,ToCensus=NA,Count=NA,ErrList=ErrList))
+    }
+    #what are the parts avilable at that time
+    parts.at.time.t=unlist(sapply(TreeList_Pred[[t]]$total, function(x) x$type))
+    #Go backwards on the progression line
+    for(Predecessor in Progression[(length(Progression)-1):1])
+    { #If you find a predecessor
+      if(sum(Predecessor==parts.at.time.t))
+      { 
+       #Use graphd to determine path between predecessor and ancesstor. 
+       Plant.Graph=GraphMaps[[substr(TreeList_Pred[[1]],1,4)]]$graph
+       EdgePath=unlist(get.shortest.paths(Plant.Graph,from=Element,to=Predecessor,output="both",weights=NA)$epath)
+       #proportion of carbon of the predecessors weight that has been used to produce the ancesstor
+       w=prod(get.edge.attribute(Plant.Graph,name="weight",index=EdgePath))
+       #The weight of ancesstor is provided,Find the weight of predecessor
+       I_predecessor=sapply(TreeList_Pred[[t]]$total,function(x) x$type)==Predecessor
+       Pre_weight=TreeList_Pred[[t]]$total[[which(I_predecessor)]]$weight[1]
+       #Reduce the count of predecessors, remove the weight
+       TreeList_Pred[[t]]$total[[which(I_predecessor)]]$weight=TreeList_Pred[[t]]$total[[which(I_predecessor)]]$weight[-1]
+       TreeList_Pred[[t]]$total[[which(I_predecessor)]]$count=TreeList_Pred[[t]]$total[[which(I_predecessor)]]$count-1
+       if(TreeList_Pred[[t]]$total[[which(I_predecessor)]]$count==0)
+       {
+         TreeList_Pred[[t]]$total[[which(I_predecessor)]]=NULL
[…]

### 2014-08-29 analysis/MultiplicityAdjustment.R

@@ -1,0 +1,39 @@
+# Function that takes the tree structure returned by Weight calculations
+# and transforms it to per/seed counts. The parts are not right now to be understand as separate entities rather their fractions that
+# develop to a single seed at the end. Such transformation does not change carbon allocation between the elements with the
+# same count, however can allow to adjust for the fact that one fruit can have multiple seeds.
+MultiplierTable<-read.csv('data/MultiplierTable.csv',header=T,sep=',',stringsAsFactors=FALSE)
+
+AdjustForMultiplicity_List<-function(List,species)
+{
+ if(length(List)>0)
+ {
+ for(i in 1:length(List))
+   {
+   part=List[[i]]$type
+   species.multiplier=MultiplierTable[species]
+   par.multiplier=species.multiplier[MultiplierTable[,1]==part,]
+   List[[i]]$count=(List[[i]]$count)*par.multiplier;
+   List[[i]]$weight=rep((List[[i]]$weight)/par.multiplier,par.multiplier)}
+ }
+ List
+}
+
+
+AdjustForMultiplicity_Census<-function(Census,species)
+{
+  Census$pre.ex=AdjustForMultiplicity_List(Census$pre.ex,species=species)
+  Census$new=AdjustForMultiplicity_List(Census$new,species=species)
+  Census$total =AdjustForMultiplicity_List(Census$total,species=species)
+Census
+}
+
+AdjustForMultiplicity<-function(TreeList)
+{
+  species=substr(TreeList[[1]],1,4)
+  for(i in 2:19)
+  {
+   TreeList[[i]]=AdjustForMultiplicity_Census(TreeList[[i]],species) 
+  }
+TreeList  
+}

### 2014-08-29 analysis/PlotIndividual_RA.R

@@ -1,0 +1,54 @@
+PlotIndividual_RA<-function()
+{
+# Function creating individual pdf RA developenent plots for all the species
+source("analysis/OrderedListsOfParts.R")
+InvSummary=read.csv('output/InvestmentSummary.csv')
+InvSummary["species"]=str_sub(InvSummary$Tree_ID,1,4)
+
+for(j in 1:14)
+{
+species=names(Maps)[j]
+sp_col=rainbow_hcl(14)[j]
+InvBySpecies=InvSummary[InvSummary$species==species,]
+
+InvByAge=data.frame(age=c(),GI=c(),GI_L=c(),GI_U=c(),RI=c(),RI_L=c(),RI_U=c(),RA=c(),RA_L=c(),RA_U=c())
+
+N=c()
+Ages=unique(InvBySpecies$age)
+for(i in 1:length(Ages))
+{
+  D=InvBySpecies[InvBySpecies$age==Ages[i],]
+  n=nrow(D)
+  N[i]=n;
+  InvByAge=rbind(InvByAge,data.frame(age=Ages[i],
+                                     GI=mean(D$GrowthInv),GI_L=mean(D$GrowthInv)-1.96/sqrt(n)*sd(D$GrowthInv),GI_U=mean(D$GrowthInv)+1.96/sqrt(n)*sd(D$GrowthInv),
+                                     RI=mean(D$ReproInv) ,RI_L=mean(D$ReproInv) -1.96/sqrt(n)*sd(D$ReproInv), RI_U=mean(D$ReproInv) +1.96/sqrt(n)*sd(D$ReproInv),
+                                     RA=mean(D$RA),RA_L=mean(D$RA) -1.96/sqrt(n)*sd(D$RA),RA_U=mean(D$RA) +1.96/sqrt(n)*sd(D$RA)))
+}
+
+pdf(file=paste0('output/docs/RA_',species,'.pdf'),width=15,height=5)
+N=N[order(InvByAge$age)]
+InvByAge=InvByAge[order(InvByAge$age),]
+par(mfrow=c(1,3),cex.main=2,cex.lab=1.5)
+plot(InvByAge$age,InvByAge$GI,type="b",lwd=3,pch=as.character(N),cex=1.5,col=sp_col,ylim=range(c(InvBySpecies$ReproInv,InvBySpecies$GrowthInv)),main="Growth Investment",xlab="Age (years)",ylab="Growth Investment (mg)")
[…]

### 2014-08-29 analysis/RA_Calculations.R

@@ -1,0 +1,94 @@
+RA_Calculations<-function()
+{
+# Function that produce the summary of both investment types and calculate RAs.
+source('analysis/OrderedListsOfParts.R')
+WeightDiameterData=read.csv(file="output/WeightDiameterData.csv",stringsAsFactors = FALSE)
+############################################################
+#Calculate Regression coefficients based on common slope and intercept by the basal diameter at year 2013
+############################################################
+RegTable=data.frame(TreeID=c(),Intercept=c(),Slope=c())
+for(species in unique(WeightDiameterData$species))
+{
+WD.species=WeightDiameterData[WeightDiameterData$species==species,]
+lm.fit=lm(log(total_weight)~log(dia),data=WD.species)
+common_slope=coef(lm.fit)[2]
+WD.specie.basal=WD.species[WD.species$node_above==1,]
+intercept.ind=log(WD.specie.basal$total_weight)-common_slope*log(WD.specie.basal$dia)
+RegTable=rbind(RegTable,data.frame(TreeID=WD.specie.basal$tag_ID,Intercept=intercept.ind,Slope=common_slope))
+}
+RegTable=RegTable[!is.na(RegTable$Intercept),]
+write.csv(RegTable,file='output/WeightDiameter_RegressionCoefficients.csv')
+############################################################
+# Use the regrsssion to obtain weights year 2012 (and 2013).
+############################################################
+DiameterData=read.csv('data/2013_Kuringgai_harvest.csv',stringsAsFactors = FALSE)
+#Use only basal diameter of the trees that are alive and have status use.
+DiameterData=DiameterData[DiameterData$segment==1,]
+DiameterData=DiameterData[DiameterData$use_status=="use",]
+DiameterData=DiameterData[DiameterData$plant_status=="alive",]
+DiameterData=DiameterData[,c("tag_ID","year","diameter_1","diameter_2","diameter_3","total_plant_weight")]
+#DiameterData=DiameterData[DiameterData$year,]
+for(i in 1:nrow(DiameterData))
+{
+  individual=DiameterData$tag_ID[i]
+  I=(RegTable$TreeID==individual)
+  if(sum(I)==1)
+  {
+    coef=RegTable[I,]
+    diams=DiameterData[i,c("diameter_1","diameter_2","diameter_3")]
+    diam.av =mean(as.numeric(diams),na.rm=T)
[…]

### 2014-08-29 analysis/RedoDocument.R

@@ -1,0 +1,30 @@
+library(stringr)
+library(colorspace)
+library(parallel)
+
+source('analysis/OrderedListsOfParts.R')
+
+source('analysis/AvWeightForParts.R')
+AvWeightForParts()
+
+source('analysis/AvCountsPerMM.R')
+AvCountsPerMM()
+
+source('analysis/RegressionCoefficients.R')
+RegressionCoefficients()
+
+source('analysis/CalculateMassAndDiameters.R')
+CalculateMassAndDiameters()
+
+source('analysis/CalculateInvestmentForSpecies.R')
+species <- read.csv("data/species_names.csv", stringsAsFactors=FALSE)
+mclapply(species$Abbreviation, CalculateInvestmentForSpecies,  mc.cores=detectCores()-1 )
+
+source('analysis/RA_Calculations.R')
+RA_Calculations()
+
+source('analysis/PlotIndividual_RA.R')
+PlotIndividual_RA()
+
+source('analysis/Plot_RAs.R')
+Plot_RAs()

### 2014-08-29 analysis/RemoveDuplicates.R

@@ -1,0 +1,33 @@
+####################################################################################
+#Removing duplicates from the list
+#- Need to be used if a mixed method was used to obtain the weights at one census
+#- Need to be used for joining the information from old and new census to a total one. 
+####################################################################################
+RemoveDuplicates<-function(C)
+{
+C_new=list()
+parts.names=unique(sapply(C,function(x) x$type))
+k=length(parts.names)
+if(k>0)
+{
+for( i in 1: k)
+{
+  part.name=parts.names[i]
+  repeated.parts = C[unlist(sapply(C,'[[',"type"))==part.name]
+  total.count    = sum(unlist(sapply(repeated.parts,'[[',"count")))
+  total.weights  = as.vector(unlist(sapply(repeated.parts,'[[',"weight")))
+  methods.used   = as.vector(unlist(sapply(repeated.parts,'[[',"m.type")))
+  if(all(methods.used==methods.used[1]))
+  {
+    m.type=methods.used[1]
+  }
+  else
+  {
+    m.type="mixed"
+  }
+  Element=list(type=part.name,m.type=m.type,count=total.count,weight=total.weights)
+  C_new[[i]]=Element
+}
+}
+C_new
+}

### 2014-08-29 analysis/plot-utils.R

@@ -1,0 +1,21 @@
+
+to.pdf <- function(expr, filename, ..., verbose=TRUE) {
+  if(!file.exists(dirname(filename)))
+    dir.create(dirname(filename), recursive=TRUE)
+  if ( verbose )
+    cat(sprintf("Creating %s\n", filename))
+  pdf(filename, ...)
+  on.exit(dev.off())
+  eval.parent(substitute(expr))
+}
+
+
+to.dev <- function(expr, dev, filename, ..., verbose=TRUE){
+  if(!file.exists(dirname(filename)))
+    dir.create(dirname(filename), recursive=TRUE)
+  if ( verbose )
+    cat(sprintf("Creating %s\n", filename))
+  dev(filename, ...)
+  on.exit(dev.off())
+  eval.parent(substitute(expr))
+}

### 2014-09-10 docs/CarbonInvestments.tex
Additional Plots. Incompatible colors between two plots. To be fixed soon.

@@
 \includegraphics[width=1\linewidth]{../output/docs/RA_comparison.pdf}
+\includegraphics[width=1\linewidth]{../output/docs/RA_Diam_comparison.pdf}
+\includegraphics[width=1\linewidth]{../output/docs/RA_Weight_comparison.pdf}
+\clearpage
+\newpage
 \section{Individual species}
@@
 \includegraphics[width=1\linewidth]{../output/docs/RA_BAER.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_BAER_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{BOLE}
 \includegraphics[width=1\linewidth]{../output/docs/RA_BOLE.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_BOLE_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{COER}
 \includegraphics[width=1\linewidth]{../output/docs/RA_COER.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_COER_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{EPMI}
 \includegraphics[width=1\linewidth]{../output/docs/RA_EPMI.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_EPMI_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{GRBU}
 \includegraphics[width=1\linewidth]{../output/docs/RA_GRBU.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_GRBU_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{GRSP}
 \includegraphics[width=1\linewidth]{../output/docs/RA_GRSP.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_GRSP_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{HATE}
 \includegraphics[width=1\linewidth]{../output/docs/RA_HATE.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_HATE_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{HEPU}
 \includegraphics[width=1\linewidth]{../output/docs/RA_HEPU.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_HEPU_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{LEES}
 \includegraphics[width=1\linewidth]{../output/docs/RA_LEES.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_LEES_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{PELA}
 \includegraphics[width=1\linewidth]{../output/docs/RA_PELA.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PELA_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{PEPU}
 \includegraphics[width=1\linewidth]{../output/docs/RA_PEPU.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PEPU_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{PHPH}
 \includegraphics[width=1\linewidth]{../output/docs/RA_PHPH.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PHPH_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{PILI}
 \includegraphics[width=1\linewidth]{../output/docs/RA_PILI.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PILI_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{PUTU}
 \includegraphics[width=1\linewidth]{../output/docs/RA_PUTU.pdf}
+\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PUTU_DW.pdf}}
 

### 2014-09-10 analysis/Plot_RAs.R

@@ -2,7 +2,6 @@ Plot_RAs<-function()
 {
 #Function plotting the comparison plot of RA for all the species.
 InvSummary=read.csv('output/InvestmentSummary.csv')
-InvSummary["species"]=str_sub(InvSummary$Tree_ID,1,4)
 RA=aggregate(RA~species+age,data=InvSummary,FUN=mean)
 
 RA=t(reshape(RA,timevar="age",idvar="species",direction="wide"))

### 2014-09-10 analysis/PlotsRA_vs_Weight_Diameter.R

@@ -1,0 +1,35 @@
+PlotRAs_vs_Diameter<-function()
+{
+  InvSummary=read.csv('output/InvestmentSummary.csv')
+  pdf(file='output/docs/RA_Diam_Comparison.pdf',width=20,height=10)
+  plot(InvSummary$FinalBasalDiamAv,InvSummary$RA,type="p",col=rainbow_hcl(14)[as.numeric(InvSummary$species)],xlab="Basal Diameter, year 2013",ylab="RA",bty="L")
+  legend('topright',legend=as.character(sort(unique(InvSummary$species))),col=rainbow_hcl(14),pch=1)
+  dev.off()
+}
+
+PlotRAs_vs_Weight<-function()
+{
+  InvSummary=read.csv('output/InvestmentSummary.csv')
+  pdf(file='output/docs/RA_Weight_Comparison.pdf',width=20,height=10)
+  plot(InvSummary$FinalWeight,InvSummary$RA,type="p",col=rainbow_hcl(14)[as.numeric(InvSummary$species)],xlab="Tree Weight, year 2013",ylab="RA",bty="L")
+  legend('topright',legend=as.character(sort(unique(InvSummary$species))),col=rainbow_hcl(14),pch=1)
+  dev.off()
+}
+
+
+
+PlotIndividualRAs_vs_Weight_Diam<-function()
+{
+  InvSummary=read.csv('output/InvestmentSummary.csv')
+  species_v=as.character(sort(unique(InvSummary$species)))
+  for(i in 1:14)
+  {
+    species=species_v[i]
+    Data=InvSummary[InvSummary$species==species,]
+    pdf(file=paste0('output/docs/RA_',species,'_DW.pdf'),width=14,height=7)
+    par(mfrow=c(1,2),cex.main=2,cex.lab=1.5)
+    plot(Data$FinalBasalDiamAv,Data$RA,type="p",col=rainbow_hcl(14)[i],xlab="Diameter, year 2013",ylab="RA",bty="L",main="Diameter",cex=1.5)
+    plot(Data$FinalWeight,Data$RA,type="p",col=rainbow_hcl(14)[i],xlab="Weight, year 2013",ylab="RA",bty="L",main="Weight",cex=1.5)
+    dev.off()
+  }
+}

### 2014-09-10 analysis/RA_Calculations.R

@@ -38,12 +38,13 @@ for(i in 1:nrow(DiameterData))
     diams=DiameterData[i,c("diameter_1","diameter_2","diameter_3")]
     diam.av =mean(as.numeric(diams),na.rm=T)
     DiameterData$EstWeight[i]=exp(coef$Intercept+coef$Slope*log(diam.av))
+    DiameterData[i,"Basal.Diameter.Av"]=diam.av
   }
 }
 ############################################################
 #Calculate change in the weight, i.e., Growth Investement
 ############################################################
-GrowthInv=data.frame(Tree_ID=c(),GrowthInv=c())
+GrowthInv=data.frame(Tree_ID=c(),GrowthInv=c(),StartWeight=c(),FinalWeight=c(),StartBasalDiamAv=c(),FinalBasalDiamAv=c())
 for(i in 1:length(unique(DiameterData$tag_ID)))
 {
   individual=unique(DiameterData$tag_ID)[i]
@@ -56,6 +57,10 @@ for(i in 1:length(unique(DiameterData$tag_ID)))
   {
     GrowthInv[i,"Tree_ID"]=individual
     GrowthInv[i,"GrowthInv"]=IndData[IndData$year==2013,"EstWeight"]-IndData[IndData$year==2012,"EstWeight"]
+    GrowthInv[i,"StartWeight"]=IndData[IndData$year==2012,"EstWeight"]
+    GrowthInv[i,"FinalWeight"]=IndData[IndData$year==2013,"EstWeight"]
+    GrowthInv[i,"StartBasalDiamAv"]=IndData[IndData$year==2012,"Basal.Diameter.Av"]
+    GrowthInv[i,"FinalBasalDiamAv"]=IndData[IndData$year==2013,"Basal.Diameter.Av"]
   }
 }
 
@@ -90,5 +95,7 @@ InvestmentSummary[str_sub(InvestmentSummary$Tree_ID,6,6)=="9","age"]=32
 
 InvestmentSummary[["TotalInvestment"]]=InvestmentSummary$ReproInv+InvestmentSummary$GrowthInv
 InvestmentSummary[["RA"]]=InvestmentSummary$ReproInv/InvestmentSummary$TotalInvestment
+row.names(InvestmentSummary)<-NULL
+InvestmentSummary[["species"]]=str_sub(InvestmentSummary$Tree_ID,1,4)
 write.csv(x=InvestmentSummary,file='output/InvestmentSummary.csv')
 }

### 2014-09-13 docs/CarbonInvestments.tex
Update for flower style position for the BAER. Map is still to be changes.

@@
 \input{../output/docs/BAER.tex}
-\\Comments:
-\begin{itemize}
-\item \textbf{Fruits just collected and weights will be added soon.
-Need to still collect finished flower stigma (didn't realize this) and seed pods}
-\end{itemize}
 \end{multicols}
@@
 \input{../output/docs/BOLE.tex}
-\\Comments:
-\begin{itemize}
-\item Missing measurements.
-\item Presumably some derivative calculations are necessary for some categories.
-\end{itemize}
 \end{multicols}
@@
 \input{../output/docs/COER.tex}
-\\Comments:
-\begin{itemize}
-\item Missing measurements.
-\end{itemize}
 \end{multicols}
@@
 \input{../output/docs/EPMI.tex}
-\\Comments:
-\begin{itemize}
-\item OK.
-\end{itemize}
 \end{multicols}
@@
 \input{../output/docs/GRBU.tex}\\
-Comments:
-\begin{itemize}
-\item Missing measurements.
-\item Otherwise OK.
-\end{itemize}
 
@@
 \input{../output/docs/GRSP.tex}
-\\Comments:
-\begin{itemize}
-\item Missing measurments
-\end{itemize}
 
@@
 \input{../output/docs/HATE.tex}
-\\Comments:
-\begin{itemize}
-\item Missing measurements.
-\end{itemize}
 
@@
 \input{../output/docs/HEPU.tex}
-\\Comments:
-\begin{itemize}
-\item Warning: fruit large immature = fruit mature
-\item Error: Fruit aborted $<$ fruit large immature
-\item Otherwise ok.
-\end{itemize}
 \end{multicols}
@@
 \\
-Comments:
-\begin{itemize}
-\item  OK.
-\end{itemize}
 \end{multicols}
@@
 \input{../output/docs/PELA.tex}
-\\Comments:
-\begin{itemize}
-\item Missing measurements.
-\end{itemize}
-
 \end{multicols}
@@
 \input{../output/docs/PEPU.tex}
-\\Comments:
-\begin{itemize}
-\item Missing measurements. \textbf{To be collected}.
-\end{itemize}
-
 \end{multicols}
@@
 \input{../output/docs/PHPH.tex}
-\\Comments:
-\begin{itemize}
-\item Missing measurements. \textbf{To be collected}.
-\end{itemize}
 \end{multicols}
@@
 \input{../output/docs/PILI.tex}
-\\Comments:
-\begin{itemize}
-\item No measurements for "seed aborted".
-\item Otherwise ok.
-\end{itemize}
 \end{multicols}
@@
 \input{../output/docs/PUTU.tex}
-\\Comments:
-\begin{itemize}
-\item OK
-\end{itemize}
 \end{multicols}

### 2014-12-06 docs/CarbonInvestments.tex
Merge branch 'My-branch'

--- 2014-08-29 docs/CarbonInvestments.tex
@@
 \includegraphics[width=1\linewidth]{../output/docs/RA_BAER.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_BAER_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{BOLE}
 \includegraphics[width=1\linewidth]{../output/docs/RA_BOLE.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_BOLE_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{COER}
 \includegraphics[width=1\linewidth]{../output/docs/RA_COER.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_COER_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{EPMI}
 \includegraphics[width=1\linewidth]{../output/docs/RA_EPMI.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_EPMI_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{GRBU}
 \includegraphics[width=1\linewidth]{../output/docs/RA_GRBU.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_GRBU_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{GRSP}
 \includegraphics[width=1\linewidth]{../output/docs/RA_GRSP.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_GRSP_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{HATE}
 \includegraphics[width=1\linewidth]{../output/docs/RA_HATE.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_HATE_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{HEPU}
 \includegraphics[width=1\linewidth]{../output/docs/RA_HEPU.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_HEPU_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{LEES}
 \includegraphics[width=1\linewidth]{../output/docs/RA_LEES.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_LEES_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{PELA}
 \includegraphics[width=1\linewidth]{../output/docs/RA_PELA.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_PELA_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{PEPU}
 \includegraphics[width=1\linewidth]{../output/docs/RA_PEPU.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_PEPU_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{PHPH}
 \includegraphics[width=1\linewidth]{../output/docs/RA_PHPH.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_PHPH_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{PILI}
 \includegraphics[width=1\linewidth]{../output/docs/RA_PILI.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_PILI_DW.pdf}}
+
+\clearpage
+\newpage
 \subsection{PUTU}
 \includegraphics[width=1\linewidth]{../output/docs/RA_PUTU.pdf}
+{\center\includegraphics[width=0.66\linewidth]{../output/docs/RA_PUTU_DW.pdf}}
+
+\newpage
+\section{Investment in Accessory Tissues}
+\subsection{Overview}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_Comparison.pdf}
+\clearpage
+\newpage
+\section{Individual species}
+\subsection{BAER}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_BAER.pdf}
+
+\subsection{BOLE}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_BOLE.pdf}
+
+\subsection{COER}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_COER.pdf}
+
+\subsection{EPMI}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_EPMI.pdf}
+
+\subsection{GRBU}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_GRBU.pdf}
+
+\subsection{GRSP}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_GRSP.pdf}
+
+\subsection{HATE}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_HATE.pdf}
+
+\subsection{HEPU}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_HEPU.pdf}
+
+\subsection{LEES}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_LEES.pdf}
+
+\subsection{PELA}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_PELA.pdf}
+
+\subsection{PEPU}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_PEPU.pdf}
+
+\subsection{PHPH}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_PHPH.pdf}
+
+\subsection{PILI}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_PILI.pdf}
+
+\subsection{PUTU}
+\includegraphics[width=1\linewidth]{../output/docs/IAT_PUTU.pdf}
 

### 2014-12-06 analysis/CalculateInvestmentForIndividualPlant.R

@@ -3,13 +3,13 @@ source('analysis/InvestmentCalculations.R')
 source('analysis/GraphRepresentation.R')
 source('analysis/MultiplicityAdjustment.R')
 
-#individual='BOLE_157'
+individual='BAER_007'
 
 
 CalculateInvestmentForIndiviualPlant<-function(individual)
 { #Read and extract data
   Data=read.csv('data/reproduction.csv',sep=',',header=T,stringsAsFactors = FALSE, na.strings="")
-  Tree=Data[Data$individual==individual,]
+  Tree=unique(Data[Data$individual==individual,])
   #Transform counts to weights and adjust for multiplicity 
   TreeListOrig=WeightCalculationsForTree(Tree)
   #TreeListAdj=TreeListOrig;

### 2014-12-06 analysis/CalculateMassAndDiameters.R

@@ -3,8 +3,7 @@ CalculateMassAndDiameters<-function()
 source("analysis/plot-utils.R")
 
 data <- tbl_df(read.csv("data/2013_Kuringgai_harvest.csv", stringsAsFactors=FALSE)) %.%
-  filter(year==2013) %.%
-#  filter((year==2013)||(year=2014)) %.%
+  filter(start_end=="end") %.%
   arrange(tag_ID, date, segment)
 
 data$species[data$species=="BAER "] <- "BAER"

### 2014-12-06 analysis/GraphRepresentation.R

@@ -342,7 +342,7 @@ rm(PUTU.graph)
 #=====================================================================================
 
 
-BAER.graph=graph.formula("cone_base_green_01"-"cone_base_green_02"-"cone_base_green_03"-"cone_base_green_04"-"cone_base_brown","cone_young_01"-"cone_young_02"-"cone_young_03"-"cone_young_04"-"cone_green_01"-"cone_green_02"-"cone_green_03"-"cone_green_04"-"cone_brown","cone_green_04"-"cone_brown_no_expanded_follicles","cone_green_04"-"cone_aborted","bud_tiny"-"bud_small"-"bud_mid"-"bud_big"-"bud_just_opening"-"flower_stigma"-"finished_flower_stigma"-"fruit_just_starting"-"fruit_young"-"fruit_large_immature_01"-"seed","bud_just_opening"-"flower_petals","bud_just_opening"-"flower_style","fruit_large_immature_01"-"seed_pod","fruit_large_immature_01"-"seed_aborted")
+BAER.graph=graph.formula("cone_base_green_01"-"cone_base_green_02"-"cone_base_green_03"-"cone_base_green_04"-"cone_base_brown","cone_young_01"-"cone_young_02"-"cone_young_03"-"cone_young_04"-"cone_green_01"-"cone_green_02"-"cone_green_03"-"cone_green_04"-"cone_brown","cone_green_04"-"cone_brown_no_expanded_follicles","cone_young_04"-"cone_aborted","bud_tiny"-"bud_small"-"bud_mid"-"bud_big"-"bud_just_opening"-"flower_stigma"-"finished_flower_stigma"-"fruit_just_starting"-"fruit_young"-"fruit_large_immature_01"-"seed","bud_just_opening"-"flower_petals","bud_just_opening"-"flower_style","fruit_large_immature_01"-"seed_pod","fruit_large_immature_01"-"seed_aborted")
 from=c("bud_tiny","cone_young_01","cone_base_green_01")
 to=c("seed","cone_brown","cone_base_brown")
 Paths=data.frame(from=from,to=to)
@@ -353,7 +353,7 @@ BAER.graph=set.vertex.attribute(BAER.graph,name="col",index=c(17:27,31),value=3)
 BAER.graph=set.vertex.attribute(BAER.graph,name="col",index=c(28:30),value=4)
 #Set weights
[…]

### 2014-12-06 analysis/InvestmentInAccessoryTissues.R

@@ -5,12 +5,13 @@ InvestmentInAccessoryTissues<-function(individual)
   
   #Read tree data
   InvestmentCategories=read.csv('data/Accessory_parts_lookup_table.csv',header=T,stringsAsFactors = FALSE, na.strings="")
-  Data=read.csv('data/reproduction.csv',sep=',',header=T,stringsAsFactors = FALSE, na.strings="")
-  Tree=Data[Data$individual==individual,]
+  #Data=read.csv('data/reproduction.csv',sep=',',header=T,stringsAsFactors = FALSE, na.strings="")
+  #Tree=Data[Data$individual==individual,]
   
   #Transform counts to weights and adjust for multiplicity 
-  TreeListOrig=WeightCalculationsForTree(Tree)
-  TreeListAdj=AdjustForMultiplicity(TreeList=TreeListOrig)
+  #TreeListOrig=WeightCalculationsForTree(Tree)
+  #TreeListAdj=AdjustForMultiplicity(TreeList=TreeListOrig)
+  #TreeFrame=TreeListToTotalDataFrame(TreeListAdj)
   
   #Read in the information about lost elements
   SpeciesLoss=read.csv(paste0('output/',species,'_FinDev.csv'),header=T,stringsAsFactors = FALSE, na.strings="")

### 2014-12-06 analysis/Plot_RAs.R

@@ -2,22 +2,33 @@ Plot_RAs<-function()
 {
 #Function plotting the comparison plot of RA for all the species.
 InvSummary=read.csv('output/InvestmentSummary.csv')
-RA=aggregate(RA~species+age,data=InvSummary,FUN=mean)
-
-RA=t(reshape(RA,timevar="age",idvar="species",direction="wide"))
+RAo=aggregate(RA~species+age,data=InvSummary,FUN=mean)
+ages=unique(RAo$age)
+nT=length(ages)
+RA=t(reshape(RAo,timevar="age",idvar="species",direction="wide"))
 colnames(RA)=RA[1,]
 RA=RA[-1,]
-RA=apply(RA,MARGIN=2,FUN=as.numeric)
-for(k in 5:2)
+RA=RA[,order(colnames(RA))]
+RA[is.na(RA)]=0
+# Check if plants at given ages are present for the specie (i.e., distinguish between no measurments and zero investments)
+DiameterData=read.csv('data/2013_Kuringgai_harvest.csv',stringsAsFactors = FALSE)
+#Use only basal diameter of the trees that are alive and have status use.
+DiameterData=DiameterData[DiameterData$segment==1,]
+DiameterData=DiameterData[DiameterData$use_status=="use",]
+DiameterData=DiameterData[DiameterData$plant_status=="alive",]
+
+for(i in 1:14)
 {
-  for(i in 1:14)
+  for(j in 1:nT)
   {
-    if((!is.na(RA[k,i]))&is.na(RA[k-1,i]))
-        RA[k-1,i]=0
+    species=colnames(RA)[i]
+    age=ages[j]
+    if((nrow(DiameterData[(DiameterData$species==species) & (DiameterData$age==age),]))==0)
+      RA[j,i]=NA
   }
 }
-RA=RA[,order(colnames(RA))]
-Age=matrix(ncol=14,nrow=5,c(1.3,5,7,9,32))
+
+Age=matrix(ncol=14,nrow=nT,ages)
 pdf(file='output/docs/RA_Comparison.pdf',width=20,height=10)
 matplot(Age,RA,type="b",pch='o',main="Reproductive Allovation for 14 species along time",col=rainbow_hcl(14),lty=1,lwd=3,xlim=c(0,35),bty="L")
 legend(33,0.7,legend=colnames(RA),col=rainbow_hcl(14),lty=1,lwd=3)

### 2014-12-19 docs/CarbonInvestments.tex
Document now compiles with new data

--- 2014-09-13 docs/CarbonInvestments.tex
@@
 \date{\today}
-
-\graphicspath{../output/docs}
 
@@
 \begin{center}
-\includegraphics[width=0.75\linewidth]{Flow1.png}\\
-\includegraphics[width=0.75\linewidth]{Flow2.png}\\
-\includegraphics[width=0.75\linewidth]{Flow3.png}
+\includegraphics[width=0.75\linewidth]{images/Flow1.png}\\
+\includegraphics[width=0.75\linewidth]{images/Flow2.png}\\
+\includegraphics[width=0.75\linewidth]{images/Flow3.png}
 \end{center}
@@
 \begin{center}
-\includegraphics[width=6in]{PlantGraph.pdf}
+\includegraphics[width=6in]{images/PlantGraph.pdf}
 \end{center}
@@
 \begin{multicols}{2}
-\includegraphics[width=3in]{BAER.png}
+\includegraphics[width=3in]{images/BAER.png}
 \vfill
 \columnbreak
-\input{../output/docs/BAER.tex}
+\input{tables/BAER.tex}
 \end{multicols}
@@
 \begin{multicols}{2}
-\includegraphics[width=3in]{BOLE.png}
+\includegraphics[width=3in]{images/BOLE.png}
 \vfill
 \columnbreak
-\input{../output/docs/BOLE.tex}
+\input{tables/BOLE.tex}
 \end{multicols}
@@
 \begin{multicols}{2}
-\includegraphics[width=2.7in]{COER.png}
+\includegraphics[width=2.7in]{images/COER.png}
 \vfill
 \columnbreak
-\input{../output/docs/COER.tex}
+\input{tables/COER.tex}
 \end{multicols}
@@
 \begin{multicols}{2}
-\includegraphics[width=2.5in]{EPMI.png}
+\includegraphics[width=2.5in]{images/EPMI.png}
 \vfill
 \columnbreak
-\input{../output/docs/EPMI.tex}
+\input{tables/EPMI.tex}
 \end{multicols}
@@
 \begin{multicols}{2}
-\includegraphics[width=3in]{GRBU.png}
+\includegraphics[width=3in]{images/GRBU.png}
 \vfill
@@
 
-\input{../output/docs/GRBU.tex}\\
+\input{tables/GRBU.tex}\\
 
@@
 \begin{multicols}{2}
-\includegraphics[width=3in]{GRSP.png}
+\includegraphics[width=3in]{images/GRSP.png}
 \vfill
@@
 
-\input{../output/docs/GRSP.tex}
+\input{tables/GRSP.tex}
 
@@
 \begin{multicols}{2}
-\includegraphics[width=3in]{HATE.png}
+\includegraphics[width=3in]{images/HATE.png}
 \vfill
 \columnbreak
-\input{../output/docs/HATE.tex}
+\input{tables/HATE.tex}
 
@@
 \begin{multicols}{2}
-\includegraphics[width=3in]{HEPU.png}
+\includegraphics[width=3in]{images/HEPU.png}
 \vfill
 \columnbreak
-\input{../output/docs/HEPU.tex}
+\input{tables/HEPU.tex}
 \end{multicols}
@@
 \begin{multicols}{2}
-\includegraphics[width=3in]{LEES.png}
+\includegraphics[width=3in]{images/LEES.png}
 \vfill
@@
 %%%%
-\input{../output/docs/LEES.tex}
+\input{tables/LEES.tex}
 %%%%%
@@
 \begin{multicols}{2}
-\includegraphics[width=2.8in]{PELA.png}
+\includegraphics[width=2.8in]{images/PELA.png}
 \vfill
 \columnbreak
-\input{../output/docs/PELA.tex}
+\input{tables/PELA.tex}
 \end{multicols}
@@
 \begin{multicols}{2}
-\includegraphics[width=2.7in]{PEPU.png}
+\includegraphics[width=2.7in]{images/PEPU.png}
 \vfill
 \columnbreak
-\input{../output/docs/PEPU.tex}
+\input{tables/PEPU.tex}
 \end{multicols}
@@
 \begin{multicols}{2}
-\includegraphics[width=3in]{PHPH.png}
+\includegraphics[width=3in]{images/PHPH.png}
 \vfill
 \columnbreak
-\input{../output/docs/PHPH.tex}
+\input{tables/PHPH.tex}
 \end{multicols}
@@
 \begin{multicols}{2}
-\includegraphics[width=2.7in]{PILI.png}
+\includegraphics[width=2.7in]{images/PILI.png}
 \vfill
 \columnbreak
-\input{../output/docs/PILI.tex}
+\input{tables/PILI.tex}
 \end{multicols}
@@
 \begin{multicols}{2}
-\includegraphics[width=2.5in]{PUTU.png}
+\includegraphics[width=2.5in]{images/PUTU.png}
 \vfill
 \columnbreak
-\input{../output/docs/PUTU.tex}
+\input{tables/PUTU.tex}
 \end{multicols}
@@
 \begin{center}
-\input{../output/docs/AvCountsPerMM.tex}
+\input{tables/AvCountsPerMM.tex}
 \end{center}
@@
 
-\section{Regression Fits and Coefficients}
-\subsection*{GRBU}
-\begin{center}
-\includegraphics[width=2.7in]{../output/docs/GRBU_fruit_large_immature.pdf}
-\includegraphics[width=2.7in]{../output/docs/GRBU_seed_pod.pdf}
-\end{center}
+% TODO: Include these plots
+% \section{Regression Fits and Coefficients}
+% \subsection*{GRBU}
+% \begin{center}
+% \includegraphics[width=2.7in]{figures/GRBU_fruit_large_immature.pdf}
+% \includegraphics[width=2.7in]{figures/GRBU_seed_pod.pdf}
+% \end{center}
 
-\subsection{GRSP}
-\begin{center}
-\includegraphics[width=2.7in]{../output/docs/GRSP_fruit_large_immature.pdf}
-\includegraphics[width=2.7in]{../output/docs/GRSP_seed_pod.pdf}
-\end{center}
+% \subsection{GRSP}
+% \begin{center}
+% \includegraphics[width=2.7in]{figures/GRSP_fruit_large_immature.pdf}
+% \includegraphics[width=2.7in]{figures/GRSP_seed_pod.pdf}
+% \end{center}
 
-\subsection{PELA}
-\begin{center}
-\includegraphics[width=2.7in]{../output/docs/PELA_fruit_large_immature.pdf}
-\includegraphics[width=2.7in]{../output/docs/PELA_seed_pod.pdf}\\
-\includegraphics[width=2.7in]{../output/docs/PELA_seed.pdf}
-\end{center}
+% \subsection{PELA}
+% \begin{center}
+% \includegraphics[width=2.7in]{figures/PELA_fruit_large_immature.pdf}
+% \includegraphics[width=2.7in]{figures/PELA_seed_pod.pdf}\\
+% \includegraphics[width=2.7in]{figures/PELA_seed.pdf}
+% \end{center}
 
-\subsection{BAER}
-\begin{center}
-\includegraphics[width=2.7in]{../output/docs/BAER_cone_young.pdf}
-\includegraphics[width=2.7in]{../output/docs/BAER_cone_green.pdf}\\
-\includegraphics[width=2.7in]{../output/docs/BAER_cone_brown_no_expanded_follicles.pdf}
-\includegraphics[width=2.7in]{../output/docs/BAER_cone_brown.pdf}\\
-\includegraphics[width=2.7in]{../output/docs/BAER_cone_aborted.pdf}
-\includegraphics[width=2.7in]{../output/docs/BAER_cone_base_green.pdf}\\
-\includegraphics[width=2.7in]{../output/docs/BAER_cone_base_brown.pdf}
-\end{center}
+% \subsection{BAER}
+% \begin{center}
+% \includegraphics[width=2.7in]{figures/BAER_cone_young.pdf}
+% \includegraphics[width=2.7in]{figures/BAER_cone_green.pdf}\\
+% \includegraphics[width=2.7in]{figures/BAER_cone_brown_no_expanded_follicles.pdf}
+% \includegraphics[width=2.7in]{figures/BAER_cone_brown.pdf}\\
+% \includegraphics[width=2.7in]{figures/BAER_cone_aborted.pdf}
+% \includegraphics[width=2.7in]{figures/BAER_cone_base_green.pdf}\\
+% \includegraphics[width=2.7in]{figures/BAER_cone_base_brown.pdf}
+% \end{center}
 
-\subsection{PEPU}
-\begin{center}
-\includegraphics[width=2.7in]{../output/docs/PEPU_cone_green.pdf}
-\includegraphics[width=2.7in]{../output/docs/PEPU_cone_brown.pdf}\\
-\includegraphics[width=2.7in]{../output/docs/PEPU_cone_aborted.pdf}
-\end{center}
+% \subsection{PEPU}
+% \begin{center}
+% \includegraphics[width=2.7in]{figures/PEPU_cone_green.pdf}
+% \includegraphics[width=2.7in]{figures/PEPU_cone_brown.pdf}\\
+% \includegraphics[width=2.7in]{figures/PEPU_cone_aborted.pdf}
+% \end{center}
+
 \newpage
@@
 \begin{center}
-\input{../output/docs/RegressionTable.tex}
+\input{tables/RegressionTable.tex}
 \end{center}
@@
 \subsection{Overview}
-\includegraphics[width=1\linewidth]{../output/docs/RA_comparison.pdf}
-\includegraphics[width=1\linewidth]{../output/docs/RA_Diam_comparison.pdf}
-\includegraphics[width=1\linewidth]{../output/docs/RA_Weight_comparison.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_comparison_age.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_comparison_diam.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_comparison_weight.pdf}
 \clearpage
+
+TODO:Add this material back in
+
 \newpage
@@
 \subsection{BAER}
-\includegraphics[width=1\linewidth]{../output/docs/RA_BAER.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_BAER_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_BAER.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_BAER.pdf}
 
@@
 \subsection{BOLE}
-\includegraphics[width=1\linewidth]{../output/docs/RA_BOLE.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_BOLE_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_BOLE.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_BOLE.pdf}
 
@@
 \subsection{COER}
-\includegraphics[width=1\linewidth]{../output/docs/RA_COER.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_COER_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_COER.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_COER.pdf}
 
@@
 \subsection{EPMI}
-\includegraphics[width=1\linewidth]{../output/docs/RA_EPMI.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_EPMI_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_EPMI.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_EPMI.pdf}
 
@@
 \subsection{GRBU}
-\includegraphics[width=1\linewidth]{../output/docs/RA_GRBU.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_GRBU_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_GRBU.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_GRBU.pdf}
 
@@
 \subsection{GRSP}
-\includegraphics[width=1\linewidth]{../output/docs/RA_GRSP.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_GRSP_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_GRSP.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_GRSP.pdf}
 
@@
 \subsection{HATE}
-\includegraphics[width=1\linewidth]{../output/docs/RA_HATE.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_HATE_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_HATE.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_HATE.pdf}
 
@@
 \subsection{HEPU}
-\includegraphics[width=1\linewidth]{../output/docs/RA_HEPU.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_HEPU_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_HEPU.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_HEPU.pdf}
 
@@
 \subsection{LEES}
-\includegraphics[width=1\linewidth]{../output/docs/RA_LEES.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_LEES_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_LEES.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_LEES.pdf}
 
@@
 \subsection{PELA}
-\includegraphics[width=1\linewidth]{../output/docs/RA_PELA.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PELA_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_PELA.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PELA.pdf}
 
@@
 \subsection{PEPU}
-\includegraphics[width=1\linewidth]{../output/docs/RA_PEPU.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PEPU_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_PEPU.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PEPU.pdf}
 
@@
 \subsection{PHPH}
-\includegraphics[width=1\linewidth]{../output/docs/RA_PHPH.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PHPH_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_PHPH.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PHPH.pdf}
 
@@
 \subsection{PILI}
-\includegraphics[width=1\linewidth]{../output/docs/RA_PILI.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PILI_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_PILI.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PILI.pdf}
 
@@
 \subsection{PUTU}
-\includegraphics[width=1\linewidth]{../output/docs/RA_PUTU.pdf}
-\center{\includegraphics[width=0.66\linewidth]{../output/docs/RA_PUTU_DW.pdf}}
+\includegraphics[width=1\linewidth]{figures/RA_age_PUTU.pdf}
+\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PUTU.pdf}
+
+% \newpage
+% \section{Investment in Accessory Tissues}
+% \subsection{Overview}
+% \includegraphics[width=1\linewidth]{figures/IAT_Comparison.pdf}
+% \clearpage
+% \newpage
+% \section{Individual species}
+% \subsection{BAER}
+% \includegraphics[width=1\linewidth]{figures/IAT_BAER.pdf}
+
+% \subsection{BOLE}
+% \includegraphics[width=1\linewidth]{figures/IAT_BOLE.pdf}
+
+% \subsection{COER}
+% \includegraphics[width=1\linewidth]{figures/IAT_COER.pdf}
+
+% \subsection{EPMI}
+% \includegraphics[width=1\linewidth]{figures/IAT_EPMI.pdf}
+
+% \subsection{GRBU}
+% \includegraphics[width=1\linewidth]{figures/IAT_GRBU.pdf}
+
+% \subsection{GRSP}
+% \includegraphics[width=1\linewidth]{figures/IAT_GRSP.pdf}
+
+% \subsection{HATE}
+% \includegraphics[width=1\linewidth]{figures/IAT_HATE.pdf}
+
+% \subsection{HEPU}
+% \includegraphics[width=1\linewidth]{figures/IAT_HEPU.pdf}
+
+% \subsection{LEES}
+% \includegraphics[width=1\linewidth]{figures/IAT_LEES.pdf}
+
+% \subsection{PELA}
+% \includegraphics[width=1\linewidth]{figures/IAT_PELA.pdf}
+
+% \subsection{PEPU}
+% \includegraphics[width=1\linewidth]{figures/IAT_PEPU.pdf}
+
+% \subsection{PHPH}
+% \includegraphics[width=1\linewidth]{figures/IAT_PHPH.pdf}
+
+% \subsection{PILI}
+% \includegraphics[width=1\linewidth]{figures/IAT_PILI.pdf}
+
+% \subsection{PUTU}
+% \includegraphics[width=1\linewidth]{figures/IAT_PUTU.pdf}
 

### 2014-12-19 analysis/RedoDocument.R

@@ -1,49 +1,0 @@
-
-
-source("analysis/OrderedListsOfParts.R")
-
-source("analysis/AvWeightForParts.R")
-AvWeightForParts()
-
-source("analysis/AvCountsPerMM.R")
-AvCountsPerMM()
-
-source("analysis/RegressionCoefficients.R")
-RegressionCoefficients()
-
-source("analysis/CalculateMassAndDiameters.R")
-CalculateMassAndDiameters()
-
-source("analysis/IndividualBasedWeightsCalculations.R")
-IndividualBasedWeightsCalculations()
-
-source("analysis/CalculateInvestmentForSpecies.R")
-species <- read.csv("data/species_names.csv", stringsAsFactors = FALSE)
-# Korad & daniel
-mclapply(species$Abbreviation, CalculateInvestmentForSpecies, mc.cores = detectCores() - 1)
-# Lizzy - cannot rubn multicore
-lapply(species$Abbreviation, CalculateInvestmentForSpecies)
-
-# Rerun a spp if needed CalculateInvestmentForSpecies('BAER')
-
-source("analysis/RA_Calculations.R")
-RA_Calculations()
-
-source("analysis/PlotIndividual_RA.R")
-PlotIndividual_RA()
-
-source("analysis/Plot_RAs.R")
-Plot_RAs()
-
-source("analysis/PlotsRA_vs_Weight_Diameter.R")
-PlotRAs_vs_Diameter()
-PlotRAs_vs_Weight()
-PlotIndividualRAs_vs_Weight_Diam()
-
-# Investments in diffeernet types of accesorry tissues
-source("analysis/IAT.R")
-IAT()
-
-source("analysis/Plot_IAT_By_Species.R")
-Plot_IAT_By_Species()
-Compare_IProp()

### 2014-12-22 docs/CarbonInvestments.tex
More descritpive names

@@
 \begin{itemize}
-\item \texttt{Plot\_RAs} Function that plots and saves in a pdf RA for all the species on one plot.
-\item \texttt{PlotIndividual\_RA} Function that for each species creates a 3 panel plot with reproductive investment, growth investment and RA.
+\item \texttt{Plot\_ReproductionAllocations} Function that plots and saves in a pdf RA for all the species on one plot.
+\item \texttt{PlotIndividual\_ReproductionAllocation} Function that for each species creates a 3 panel plot with reproductive investment, growth investment and RA.
 \end{itemize}
@@
 \begin{itemize}
-\item \texttt{****\_Inv} Information about investment in creation/progression of specific parts along all censuses for all the individuals.
+\item \texttt{****\_Investment} Information about investment in creation/progression of specific parts along all censuses for all the individuals.
 \item \texttt{****\_Lost} Information about lost parts for all individuals.

### 2014-12-22 R/figures.R

@@ -6,8 +6,8 @@ col.table <- function(){
     PEPU="#CEA472", PHPH= "#B8AC65", PILI="#7BBA7D", PUTU="#46BAC8")
 }
 
-get_RA_means_by_age <- function(RA_all){
-  group_by(RA_all, species, age) %.%
+get_ReproductionAllocation_means_by_age <- function(ReproductionAllocation_all){
+  group_by(ReproductionAllocation_all, species, age) %.%
     summarise(
       n=length(age),
       GI_M = mean(GrowthInv),
@@ -22,9 +22,9 @@ get_RA_means_by_age <- function(RA_all){
     arrange(species, age)
 }
 
-plot_species_RA_age_panel <- function(InvBySpecies) {
+plot_species_ReproductionAllocation_age_panel <- function(InvBySpecies) {
 
-  InvByAge <- get_RA_means_by_age(InvBySpecies)
+  InvByAge <- get_ReproductionAllocation_means_by_age(InvBySpecies)
 
   cols <- col.table()[InvBySpecies$species]
 
@@ -49,9 +49,9 @@ plot_species_RA_age_panel <- function(InvBySpecies) {
   points(InvBySpecies$age, InvBySpecies$RA, pch = "o", cex = 1.5, col = "grey")
 }
 
-plot_RA_comparison_age <- function(RA_all) {
+plot_ReproductionAllocation_comparison_age <- function(ReproductionAllocation_all) {
 
-  InvByAge <- get_RA_means_by_age(RA_all)
+  InvByAge <- get_ReproductionAllocation_means_by_age(ReproductionAllocation_all)
   cols <- col.table()
   plot(InvByAge$age, InvByAge$RA_M, type="n", main = "Reproductive Allovation for 14 species along time", lty = 1, lwd = 3, xlim = c(0, 35), bty = "L", xlab = "Age (years)", ylab = "Reproductive Allocation")
   d_ply(InvByAge, "species", function(x) points(x$age, x$RA_M, type = "b", pch = "o", col= cols[x$species]))
@@ -59,19 +59,19 @@ plot_RA_comparison_age <- function(RA_all) {
 
 }
 
-plot_RA_comparison_diam <- function(RA_all) {
+plot_ReproductionAllocation_comparison_diam <- function(ReproductionAllocation_all) {
   cols <- col.table()
[…]

### 2014-12-22 CarbonInvestments.Rnw
User maker and knitr to generate plot and document

--- 2014-12-22 docs/CarbonInvestments.tex
@@
 
-\clearpage
-\newpage
-\section{BAER}
-\begin{multicols}{2}
-\includegraphics[width=3in]{images/BAER.png}
-\vfill
-\columnbreak
-\input{tables/BAER.tex}
-\end{multicols}
+<<tablepreload1, echo=FALSE>>=
+print_table <- function(x, caption, label=NULL){
+  if(!is.null(x) && nrow(x) > 0)
+ 	  print(xtable(x,caption=caption, label=label,  type="latex"),
+               include.rownames=FALSE, hline.after=c(0,nrow(x)), caption.placement="top")
+}
+@
 
@@
 \newpage
+
+\section{BAER}
+
+\includegraphics[height=6in]{images/BAER.png}
+<<results='asis', echo=FALSE>>=
+ print_table(BAER_PartsSummary$AvWeightPerUnit,
+ caption="BAER: Average weight of parts")
+@
+
+<<results='asis', echo=FALSE>>=
+ print_table(BAER_PartsSummary$AvCountsPerMM,
+ caption="BAER: Average density of parts for per mm")
+@
+
+<<results='asis', echo=FALSE>>=
+ print_table(BAER_PartsSummary$RegressionTable,
+ caption="BAER: Coefficients of regressions used to estimate weights for some parts")
+@
+
+\clearpage
+\newpage
+
 \section{BOLE}
-\begin{multicols}{2}
-\includegraphics[width=3in]{images/BOLE.png}
-\vfill
-\columnbreak
-\input{tables/BOLE.tex}
-\end{multicols}
+
+\includegraphics[height=6in]{images/BOLE.png}
+<<results='asis', echo=FALSE>>=
+ print_table(BOLE_PartsSummary$AvWeightPerUnit,
+ caption="BOLE: Average weight of parts")
+
+ print_table(BOLE_PartsSummary$AvCountsPerMM,
+ caption="BOLE: Average density of parts for per mm")
+
+ print_table(BOLE_PartsSummary$RegressionTable,
+ caption="BOLE: Coefficients of regressions used to estimate weights for some parts")
+@
 
@@
 \section{COER}
-\begin{multicols}{2}
-\includegraphics[width=2.7in]{images/COER.png}
-\vfill
-\columnbreak
-\input{tables/COER.tex}
-\end{multicols}
+
+\includegraphics[height=6in]{images/COER.png}
+<<results='asis', echo=FALSE>>=
+ print_table(COER_PartsSummary$AvWeightPerUnit,
+ caption="COER: Average weight of parts")
+
+ print_table(COER_PartsSummary$AvCountsPerMM,
+ caption="COER: Average density of parts for per mm")
+
+ print_table(COER_PartsSummary$RegressionTable,
+ caption="COER: Coefficients of regressions used to estimate weights for some parts")
+@
 
@@
 \section{EPMI}
-\begin{multicols}{2}
-\includegraphics[width=2.5in]{images/EPMI.png}
-\vfill
-\columnbreak
-\input{tables/EPMI.tex}
-\end{multicols}
+
+\includegraphics[height=6in]{images/EPMI.png}
+<<results='asis', echo=FALSE>>=
+ print_table(EPMI_PartsSummary$AvWeightPerUnit,
+ caption="EPMI: Average weight of parts")
+
+<<results='asis', echo=FALSE>>=
+ print_table(EPMI_PartsSummary$AvCountsPerMM,
+ caption="EPMI: Average density of parts for per mm")
+
+<<results='asis', echo=FALSE>>=
+ print_table(EPMI_PartsSummary$RegressionTable,
+ caption="EPMI: Coefficients of regressions used to estimate weights for some parts")
+@
 
@@
 \section{GRBU}
-\begin{multicols}{2}
-\includegraphics[width=3in]{images/GRBU.png}
-\vfill
-\columnbreak
 
-\input{tables/GRBU.tex}\\
+\includegraphics[height=6in]{images/GRBU.png}
+<<results='asis', echo=FALSE>>=
+ print_table(GRBU_PartsSummary$AvWeightPerUnit,
+ caption="GRBU: Average weight of parts")
 
-\end{multicols}
+<<results='asis', echo=FALSE>>=
+ print_table(GRBU_PartsSummary$AvCountsPerMM,
+ caption="GRBU: Average density of parts for per mm")
+
+<<results='asis', echo=FALSE>>=
+ print_table(GRBU_PartsSummary$RegressionTable,
+ caption="GRBU: Coefficients of regressions used to estimate weights for some parts")
+@
 
@@
 \section{GRSP}
-\begin{multicols}{2}
-\includegraphics[width=3in]{images/GRSP.png}
-\vfill
-\columnbreak
 
-\input{tables/GRSP.tex}
+\includegraphics[height=6in]{images/GRSP.png}
+<<results='asis', echo=FALSE>>=
+ print_table(GRSP_PartsSummary$AvWeightPerUnit,
+ caption="GRSP: Average weight of parts")
 
-\end{multicols}
+<<results='asis', echo=FALSE>>=
+ print_table(GRSP_PartsSummary$AvCountsPerMM,
+ caption="GRSP: Average density of parts for per mm")
+
+<<results='asis', echo=FALSE>>=
+ print_table(GRSP_PartsSummary$RegressionTable,
+ caption="GRSP: Coefficients of regressions used to estimate weights for some parts")
+@
 
@@
 \newpage
+
 \section{HATE}
-\begin{multicols}{2}
-\includegraphics[width=3in]{images/HATE.png}
-\vfill
-\columnbreak
-\input{tables/HATE.tex}
 
-\end{multicols}
+\includegraphics[height=6in]{images/HATE.png}
+<<results='asis', echo=FALSE>>=
+ print_table(HATE_PartsSummary$AvWeightPerUnit,
+ caption="HATE: Average weight of parts")
+
+<<results='asis', echo=FALSE>>=
+ print_table(HATE_PartsSummary$AvCountsPerMM,
+ caption="HATE: Average density of parts for per mm")
+
+<<results='asis', echo=FALSE>>=
+ print_table(HATE_PartsSummary$RegressionTable,
+ caption="HATE: Coefficients of regressions used to estimate weights for some parts")
+@
 
@@
 \section{HEPU}
-\begin{multicols}{2}
-\includegraphics[width=3in]{images/HEPU.png}
-\vfill
-\columnbreak
-\input{tables/HEPU.tex}
-\end{multicols}
+
+\includegraphics[height=6in]{images/HEPU.png}
+<<results='asis', echo=FALSE>>=
+ print_table(HEPU_PartsSummary$AvWeightPerUnit,
+ caption="HEPU: Average weight of parts")
+
+<<results='asis', echo=FALSE>>=
+ print_table(HEPU_PartsSummary$AvCountsPerMM,
+ caption="HEPU: Average density of parts for per mm")
+
+<<results='asis', echo=FALSE>>=
+ print_table(HEPU_PartsSummary$RegressionTable,
+ caption="HEPU: Coefficients of regressions used to estimate weights for some parts")
+@
 
@@
 \section{LEES}
-\begin{multicols}{2}
-\includegraphics[width=3in]{images/LEES.png}
-\vfill
-\columnbreak
-%%%%
-\input{tables/LEES.tex}
-%%%%%
-\\
-\end{multicols}
+
+\includegraphics[height=6in]{images/LEES.png}
+<<results='asis', echo=FALSE>>=
+ print_table(LEES_PartsSummary$AvWeightPerUnit,
+ caption="LEES: Average weight of parts")
+
+<<results='asis', echo=FALSE>>=
+ print_table(LEES_PartsSummary$AvCountsPerMM,
+ caption="LEES: Average density of parts for per mm")
+
+<<results='asis', echo=FALSE>>=
+ print_table(LEES_PartsSummary$RegressionTable,
+ caption="LEES: Coefficients of regressions used to estimate weights for some parts")
+@
+
 \clearpage
@@
 \section{PELA}
-\begin{multicols}{2}
-\includegraphics[width=2.8in]{images/PELA.png}
-\vfill
-\columnbreak
-\input{tables/PELA.tex}
-\end{multicols}
+
+\includegraphics[height=6in]{images/PELA.png}
+<<results='asis', echo=FALSE>>=
+ print_table(PELA_PartsSummary$AvWeightPerUnit,
+ caption="PELA: Average weight of parts")
+
+<<results='asis', echo=FALSE>>=
+ print_table(PELA_PartsSummary$AvCountsPerMM,
+ caption="PELA: Average density of parts for per mm")
+
+<<results='asis', echo=FALSE>>=
+ print_table(PELA_PartsSummary$RegressionTable,
+ caption="PELA: Coefficients of regressions used to estimate weights for some parts")
+@
 
@@
 \newpage
+
 \section{PEPU}
-\begin{multicols}{2}
-\includegraphics[width=2.7in]{images/PEPU.png}
-\vfill
-\columnbreak
-\input{tables/PEPU.tex}
-\end{multicols}
+
+\includegraphics[height=6in]{images/PEPU.png}
+<<results='asis', echo=FALSE>>=
+ print_table(PEPU_PartsSummary$AvWeightPerUnit,
+ caption="PEPU: Average weight of parts")
+
+<<results='asis', echo=FALSE>>=
+ print_table(PEPU_PartsSummary$AvCountsPerMM,
+ caption="PEPU: Average density of parts for per mm")
+
+<<results='asis', echo=FALSE>>=
+ print_table(PEPU_PartsSummary$RegressionTable,
+ caption="PEPU: Coefficients of regressions used to estimate weights for some parts")
+@
+
 \clearpage
@@
 
-\clearpage
-\newpage
 \section{PHPH}
-\begin{multicols}{2}
-\includegraphics[width=3in]{images/PHPH.png}
-\vfill
-\columnbreak
-\input{tables/PHPH.tex}
-\end{multicols}
+
+\includegraphics[height=6in]{images/PHPH.png}
+<<results='asis', echo=FALSE>>=
+ print_table(PHPH_PartsSummary$AvWeightPerUnit,
+ caption="PHPH: Average weight of parts")
+
+<<results='asis', echo=FALSE>>=
+ print_table(PHPH_PartsSummary$AvCountsPerMM,
+ caption="PHPH: Average density of parts for per mm")
+
+<<results='asis', echo=FALSE>>=
+ print_table(PHPH_PartsSummary$RegressionTable,
+ caption="PHPH: Coefficients of regressions used to estimate weights for some parts")
+@
 
@@
 \newpage
+
 \section{PILI}
-\begin{multicols}{2}
-\includegraphics[width=2.7in]{images/PILI.png}
-\vfill
-\columnbreak
-\input{tables/PILI.tex}
-\end{multicols}
+
+\includegraphics[height=6in]{images/PILI.png}
+<<results='asis', echo=FALSE>>=
+ print_table(PILI_PartsSummary$AvWeightPerUnit,
+ caption="PILI: Average weight of parts")
+
+<<results='asis', echo=FALSE>>=
+ print_table(PILI_PartsSummary$AvCountsPerMM,
+ caption="PILI: Average density of parts for per mm")
+
+<<results='asis', echo=FALSE>>=
+ print_table(PILI_PartsSummary$RegressionTable,
+ caption="PILI: Coefficients of regressions used to estimate weights for some parts")
+@
 
@@
 \newpage
+
 \section{PUTU}
-\begin{multicols}{2}
-\includegraphics[width=2.5in]{images/PUTU.png}
-\vfill
-\columnbreak
-\input{tables/PUTU.tex}
-\end{multicols}
 
-\chapter{Additional preliminary calculations}
+\includegraphics[height=6in]{images/PUTU.png}
+<<results='asis', echo=FALSE>>=
+ print_table(PUTU_PartsSummary$AvWeightPerUnit,
+ caption="PUTU: Average weight of parts")
 
-\section{Average count/length values}
+<<results='asis', echo=FALSE>>=
+ print_table(PUTU_PartsSummary$AvCountsPerMM,
+ caption="PUTU: Average density of parts for per mm")
 
-\begin{figure}[h!]
-\begin{center}
-\input{tables/AvCountsPerMM.tex}
-\end{center}
-\caption{Table summarising the average number of elements per mm. To be used for calculations of mass based on the length for conversion to counts.}
-\end{figure}
+<<results='asis', echo=FALSE>>=
+ print_table(PUTU_PartsSummary$RegressionTable,
+ caption="PUTU: Coefficients of regressions used to estimate weights for some parts")
+@
+
+% \chapter{Additional preliminary calculations}
 
@@
 % \begin{center}
-% \includegraphics[width=2.7in]{figures/GRBU_fruit_large_immature.pdf}
-% \includegraphics[width=2.7in]{figures/GRBU_seed_pod.pdf}
+% \includegraphics[width=2.7in]{figure/GRBU_fruit_large_immature.pdf}
+% \includegraphics[width=2.7in]{figure/GRBU_seed_pod.pdf}
 % \end{center}
@@
 % \begin{center}
-% \includegraphics[width=2.7in]{figures/GRSP_fruit_large_immature.pdf}
-% \includegraphics[width=2.7in]{figures/GRSP_seed_pod.pdf}
+% \includegraphics[width=2.7in]{figure/GRSP_fruit_large_immature.pdf}
+% \includegraphics[width=2.7in]{figure/GRSP_seed_pod.pdf}
 % \end{center}
@@
 % \begin{center}
-% \includegraphics[width=2.7in]{figures/PELA_fruit_large_immature.pdf}
-% \includegraphics[width=2.7in]{figures/PELA_seed_pod.pdf}\\
-% \includegraphics[width=2.7in]{figures/PELA_seed.pdf}
+% \includegraphics[width=2.7in]{figure/PELA_fruit_large_immature.pdf}
+% \includegraphics[width=2.7in]{figure/PELA_seed_pod.pdf}\\
+% \includegraphics[width=2.7in]{figure/PELA_seed.pdf}
 % \end{center}
@@
 % \begin{center}
-% \includegraphics[width=2.7in]{figures/BAER_cone_young.pdf}
-% \includegraphics[width=2.7in]{figures/BAER_cone_green.pdf}\\
-% \includegraphics[width=2.7in]{figures/BAER_cone_brown_no_expanded_follicles.pdf}
-% \includegraphics[width=2.7in]{figures/BAER_cone_brown.pdf}\\
-% \includegraphics[width=2.7in]{figures/BAER_cone_aborted.pdf}
-% \includegraphics[width=2.7in]{figures/BAER_cone_base_green.pdf}\\
-% \includegraphics[width=2.7in]{figures/BAER_cone_base_brown.pdf}
+% \includegraphics[width=2.7in]{figure/BAER_cone_young.pdf}
+% \includegraphics[width=2.7in]{figure/BAER_cone_green.pdf}\\
+% \includegraphics[width=2.7in]{figure/BAER_cone_brown_no_expanded_follicles.pdf}
+% \includegraphics[width=2.7in]{figure/BAER_cone_brown.pdf}\\
+% \includegraphics[width=2.7in]{figure/BAER_cone_aborted.pdf}
+% \includegraphics[width=2.7in]{figure/BAER_cone_base_green.pdf}\\
+% \includegraphics[width=2.7in]{figure/BAER_cone_base_brown.pdf}
 % \end{center}
@@
 % \begin{center}
-% \includegraphics[width=2.7in]{figures/PEPU_cone_green.pdf}
-% \includegraphics[width=2.7in]{figures/PEPU_cone_brown.pdf}\\
-% \includegraphics[width=2.7in]{figures/PEPU_cone_aborted.pdf}
+% \includegraphics[width=2.7in]{figure/PEPU_cone_green.pdf}
+% \includegraphics[width=2.7in]{figure/PEPU_cone_brown.pdf}\\
+% \includegraphics[width=2.7in]{figure/PEPU_cone_aborted.pdf}
 % \end{center}
 
+% \newpage
+% \subsection{Summary table for regression}
+% \begin{figure}[h!]
+% \begin{center}
+% \input{tables/RegressionTable.tex}
+% \end{center}
+% \caption{Table summarising the equations used to determine weights of individual plant parts by using their size.}
+% \end{figure}
+
+% \chapter{Preliminary results}
+% \section{Reproductive allocation results}
+% \subsection{Overview}
+% \includegraphics[width=1\linewidth]{figure/RA_comparison_age.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_comparison_diam.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_comparison_weight.pdf}
+% \clearpage
+ \clearpage
  \newpage
-\subsection{Summary table for regression}
-\begin{figure}[h!]
-\begin{center}
-\input{tables/RegressionTable.tex}
-\end{center}
-\caption{Table summarising the equations used to determine weights of individual plant parts by using their size.}
-\end{figure}
 
-\chapter{Preliminary results}
-\section{Reproductive allocation results}
-\subsection{Overview}
-\includegraphics[width=1\linewidth]{figures/RA_comparison_age.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_comparison_diam.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_comparison_weight.pdf}
-\clearpage
+ \subsection{ BAER }
 
-TODO:Add this material back in
-
-\newpage
-\section{Individual species}
-\subsection{BAER}
-\includegraphics[width=1\linewidth]{figures/RA_age_BAER.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_BAER.pdf}
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(BAER_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(BAER_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{BOLE}
-\includegraphics[width=1\linewidth]{figures/RA_age_BOLE.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_BOLE.pdf}
+
+ \subsection{ BOLE }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(BOLE_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(BOLE_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{COER}
-\includegraphics[width=1\linewidth]{figures/RA_age_COER.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_COER.pdf}
+
+ \subsection{ COER }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(COER_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(COER_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{EPMI}
-\includegraphics[width=1\linewidth]{figures/RA_age_EPMI.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_EPMI.pdf}
+
+ \subsection{ EPMI }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(EPMI_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(EPMI_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{GRBU}
-\includegraphics[width=1\linewidth]{figures/RA_age_GRBU.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_GRBU.pdf}
+
+ \subsection{ GRBU }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(GRBU_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(GRBU_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{GRSP}
-\includegraphics[width=1\linewidth]{figures/RA_age_GRSP.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_GRSP.pdf}
+
+ \subsection{ GRSP }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(GRSP_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(GRSP_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{HATE}
-\includegraphics[width=1\linewidth]{figures/RA_age_HATE.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_HATE.pdf}
+
+ \subsection{ HATE }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(HATE_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(HATE_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{HEPU}
-\includegraphics[width=1\linewidth]{figures/RA_age_HEPU.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_HEPU.pdf}
+
+ \subsection{ HEPU }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(HEPU_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(HEPU_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{LEES}
-\includegraphics[width=1\linewidth]{figures/RA_age_LEES.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_LEES.pdf}
+
+ \subsection{ LEES }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(LEES_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(LEES_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{PELA}
-\includegraphics[width=1\linewidth]{figures/RA_age_PELA.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PELA.pdf}
+
+ \subsection{ PELA }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(PELA_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(PELA_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{PEPU}
-\includegraphics[width=1\linewidth]{figures/RA_age_PEPU.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PEPU.pdf}
+
+ \subsection{ PEPU }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(PEPU_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(PEPU_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{PHPH}
-\includegraphics[width=1\linewidth]{figures/RA_age_PHPH.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PHPH.pdf}
+
+ \subsection{ PHPH }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(PHPH_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(PHPH_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{PILI}
-\includegraphics[width=1\linewidth]{figures/RA_age_PILI.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PILI.pdf}
+
+ \subsection{ PILI }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(PILI_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(PILI_ReproductionAllocation)
+@
 
@@
  \newpage
-\subsection{PUTU}
-\includegraphics[width=1\linewidth]{figures/RA_age_PUTU.pdf}
-\includegraphics[width=1\linewidth]{figures/RA_weight_diam_PUTU.pdf}
 
-% \newpage
-% \section{Investment in Accessory Tissues}
-% \subsection{Overview}
-% \includegraphics[width=1\linewidth]{figures/IAT_Comparison.pdf}
+ \subsection{ PUTU }
+
+<<results='asis', echo=FALSE>>=
+	plot_species_ReproductionAllocation_age_panel(PUTU_ReproductionAllocation)
+	plot_species_ReproductionAllocation_weight_diam_panel(PUTU_ReproductionAllocation)
+@
+
 % \clearpage
 % \newpage
-% \section{Individual species}
-% \subsection{BAER}
-% \includegraphics[width=1\linewidth]{figures/IAT_BAER.pdf}
+% \subsection{BOLE}
+% \includegraphics[width=1\linewidth]{figure/RA_age_BOLE.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_BOLE.pdf}
 
-% \subsection{BOLE}
-% \includegraphics[width=1\linewidth]{figures/IAT_BOLE.pdf}
+% \clearpage
+% \newpage
+% \subsection{COER}
+% \includegraphics[width=1\linewidth]{figure/RA_age_COER.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_COER.pdf}
 
-% \subsection{COER}
-% \includegraphics[width=1\linewidth]{figures/IAT_COER.pdf}
+% \clearpage
+% \newpage
+% \subsection{EPMI}
+% \includegraphics[width=1\linewidth]{figure/RA_age_EPMI.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_EPMI.pdf}
 
-% \subsection{EPMI}
-% \includegraphics[width=1\linewidth]{figures/IAT_EPMI.pdf}
+% \clearpage
+% \newpage
+% \subsection{GRBU}
+% \includegraphics[width=1\linewidth]{figure/RA_age_GRBU.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_GRBU.pdf}
 
-% \subsection{GRBU}
-% \includegraphics[width=1\linewidth]{figures/IAT_GRBU.pdf}
+% \clearpage
+% \newpage
+% \subsection{GRSP}
+% \includegraphics[width=1\linewidth]{figure/RA_age_GRSP.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_GRSP.pdf}
 
-% \subsection{GRSP}
-% \includegraphics[width=1\linewidth]{figures/IAT_GRSP.pdf}
+% \clearpage
+% \newpage
+% \subsection{HATE}
+% \includegraphics[width=1\linewidth]{figure/RA_age_HATE.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_HATE.pdf}
 
-% \subsection{HATE}
-% \includegraphics[width=1\linewidth]{figures/IAT_HATE.pdf}
+% \clearpage
+% \newpage
+% \subsection{HEPU}
+% \includegraphics[width=1\linewidth]{figure/RA_age_HEPU.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_HEPU.pdf}
 
-% \subsection{HEPU}
-% \includegraphics[width=1\linewidth]{figures/IAT_HEPU.pdf}
+% \clearpage
+% \newpage
+% \subsection{LEES}
+% \includegraphics[width=1\linewidth]{figure/RA_age_LEES.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_LEES.pdf}
 
-% \subsection{LEES}
-% \includegraphics[width=1\linewidth]{figures/IAT_LEES.pdf}
+% \clearpage
+% \newpage
+% \subsection{PELA}
+% \includegraphics[width=1\linewidth]{figure/RA_age_PELA.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_PELA.pdf}
 
-% \subsection{PELA}
-% \includegraphics[width=1\linewidth]{figures/IAT_PELA.pdf}
+% \clearpage
+% \newpage
+% \subsection{PEPU}
+% \includegraphics[width=1\linewidth]{figure/RA_age_PEPU.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_PEPU.pdf}
 
-% \subsection{PEPU}
-% \includegraphics[width=1\linewidth]{figures/IAT_PEPU.pdf}
+% \clearpage
+% \newpage
+% \subsection{PHPH}
+% \includegraphics[width=1\linewidth]{figure/RA_age_PHPH.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_PHPH.pdf}
 
-% \subsection{PHPH}
-% \includegraphics[width=1\linewidth]{figures/IAT_PHPH.pdf}
+% \clearpage
+% \newpage
+% \subsection{PILI}
+% \includegraphics[width=1\linewidth]{figure/RA_age_PILI.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_PILI.pdf}
 
-% \subsection{PILI}
-% \includegraphics[width=1\linewidth]{figures/IAT_PILI.pdf}
+% \clearpage
+% \newpage
+% \subsection{PUTU}
+% \includegraphics[width=1\linewidth]{figure/RA_age_PUTU.pdf}
+% \includegraphics[width=1\linewidth]{figure/RA_weight_diam_PUTU.pdf}
 
-% \subsection{PUTU}
-% \includegraphics[width=1\linewidth]{figures/IAT_PUTU.pdf}
+% % \newpage
+% % \section{Investment in Accessory Tissues}
+% % \subsection{Overview}
+% % \includegraphics[width=1\linewidth]{figure/IAT_Comparison.pdf}
+% % \clearpage
+% % \newpage
+% % \section{Individual species}
+% % \subsection{BAER}
+% % \includegraphics[width=1\linewidth]{figure/IAT_BAER.pdf}
+
+% % \subsection{BOLE}
+% % \includegraphics[width=1\linewidth]{figure/IAT_BOLE.pdf}
+
+% % \subsection{COER}
+% % \includegraphics[width=1\linewidth]{figure/IAT_COER.pdf}
+
+% % \subsection{EPMI}
+% % \includegraphics[width=1\linewidth]{figure/IAT_EPMI.pdf}
+
+% % \subsection{GRBU}
+% % \includegraphics[width=1\linewidth]{figure/IAT_GRBU.pdf}
+
+% % \subsection{GRSP}
+% % \includegraphics[width=1\linewidth]{figure/IAT_GRSP.pdf}
+
+% % \subsection{HATE}
+% % \includegraphics[width=1\linewidth]{figure/IAT_HATE.pdf}
+
+% % \subsection{HEPU}
+% % \includegraphics[width=1\linewidth]{figure/IAT_HEPU.pdf}
+
+% % \subsection{LEES}
+% % \includegraphics[width=1\linewidth]{figure/IAT_LEES.pdf}
+
+% % \subsection{PELA}
+% % \includegraphics[width=1\linewidth]{figure/IAT_PELA.pdf}
+
+% % \subsection{PEPU}
+% % \includegraphics[width=1\linewidth]{figure/IAT_PEPU.pdf}
+
+% % \subsection{PHPH}
+% % \includegraphics[width=1\linewidth]{figure/IAT_PHPH.pdf}
+
+% % \subsection{PILI}
+% % \includegraphics[width=1\linewidth]{figure/IAT_PILI.pdf}
+
+% % \subsection{PUTU}
+% % \includegraphics[width=1\linewidth]{figure/IAT_PUTU.pdf}
 

### 2014-12-22 R/Utils.R

@@ -1,0 +1,7 @@
+
+tex_2_pdf <- function(texfile){
+  filename <- tools::file_path_sans_ext(texfile)
+  system(sprintf("pdflatex %s", texfile))
+  aux.files <- paste0(filename, c(".log", ".aux", ".bbl", ".blg"))
+  file.remove(aux.files[file.exists(aux.files)])
+}

### 2014-12-22 bootstrap.R

@@ -2,15 +2,10 @@
 library(whisker)
 
 allspecies <- c("BAER", "BOLE", "COER", "EPMI", "GRBU", "GRSP", "HATE", "HEPU", "LEES", "PELA", "PEPU", "PHPH", "PILI", "PUTU")
-#allspecies <- c("EPMI", "PILI")
 
 vals <- list(allspecies=iteratelist(allspecies, value="species"))
 str <- whisker.render(readLines("x_maker_species_data.yml.whisker"), vals)
 writeLines(str, "maker_species_data.yml")
 
-str <- whisker.render(readLines("x_maker_species_figures.yml.whisker"), vals)
-writeLines(str, "maker_species_figures_tables.yml")
-
 str <- whisker.render(readLines("x_species_data.R.whisker"), vals)
 writeLines(str, "R/species_data.R")
-

### 2014-12-22 analysis/GraphRepresentation.R
Last fixes to HEPU problems.

@@ -497,6 +497,24 @@ w1=W1/sum(W1,W2)
 w2=W2/sum(W1,W2)
 HEPU.graph=set.edge.attribute(HEPU.graph,name="weight",index=c(E1,E2),value=c(w1,w2))
 
+
+###############################
+#flower_petals, flower_calyx_aborting from bud_big
+##############################
+#which edges
+E1=AM["bud_big","flower_petals"]
+E2=AM["bud_big","flower_calyx_aborting"]
+
+#av. weights of the parts
+W1=AV_W("HEPU","flower_petals")
+W2=AV_W("HEPU","flower_calyx_aborting")
+#
+w1=W1/sum(W1,W2)
+w2=W2/sum(W1,W2)
+HEPU.graph=set.edge.attribute(HEPU.graph,name="weight",index=c(E1,E2),value=c(w1,w2))
+
+
+
 ###############################
 #calyx_fruit, fruit_young from finished_flower
 ##############################
@@ -511,6 +529,24 @@ W2=AV_W("HEPU","fruit_young")
 w1=W1/sum(W1,W2)
 w2=W2/sum(W1,W2)
 HEPU.graph=set.edge.attribute(HEPU.graph,name="weight",index=c(E1,E2),value=c(w1,w2))
+
+
+###############################
+#calyx_fruit, fruit_young_aborting from finished_flower
+##############################
+#which edges
+E1=AM["finished_flower","calyx_fruit"]
+E2=AM["finished_flower","fruit_young_aborting"]
+
+#av. weights of the parts
+W1=AV_W("HEPU","calyx_fruit")
+W2=AV_W("HEPU","fruit_young_aborting")
+#
+w1=W1/sum(W1,W2)
+w2=W2/sum(W1,W2)
+HEPU.graph=set.edge.attribute(HEPU.graph,name="weight",index=c(E1,E2),value=c(w1,w2))
+
+
 
 
 GraphMaps[["HEPU"]]=list(graph=HEPU.graph,Paths=Paths)

### 2015-03-19 leaflifespan.Rmd
R scripts from yesterday

---
output: html_document
---
#file names
- leaf_counts is file with calculated leaf counts and leaf lifespan data
- LLSummary is file with means of LL - and other variables - by species and age; LMA data is merged to this file
- subsets of LLSummary are created to omit babies or HATE for various analyses

# general results

- strong correlation between LMA and LL when all species*site combinations included
- LL variable across species, as expected; same for LMA
- LL does not change as plants age; LMA does not change as plants age
- leaf count along the leader decreases in older plants for many species - which is why LL appears to decrease

#next to do

- check how overall plant leaf numbers changes with age, diameter

```{r, echo=FALSE,results='hide', message=FALSE}
# load packages
library(tidyr)
library(dplyr)
#library(lme4)

#load files

LMA <- read.csv("data/LMA_short.csv",header=TRUE,as.is=TRUE,stringsAsFactors=FALSE)
#InvestmentSummary <- remake::make("ReproductionAllocation_all")
#names(InvestmentSummary)[1] <- "tag_ID"

#define functions
se <- function(x) sd(x)/sqrt(length(x))
con95 <- function(x) (sd(x)/sqrt(length(x)))*1.96

# leaf lifespan data
raw_leaf_lifespan <- read.csv("data/leaderGrowthLL.csv",header=TRUE,as.is=TRUE,stringsAsFactors=FALSE) %>%
  filter(dont_use!="dead" & dont_use!="dont_use")

# Create new dataset taking only count measures, bc these are ultimately what we want
leaf_lifespan <- raw_leaf_lifespan %>%
  select(species,age,site,tag_ID,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)

# where counts did not previously exists, set as 0
for(v in c("lvs_start_count","lvs_end_count","lvs_new_count","new_but_shed_count")) {
  i <- is.na(leaf_lifespan[[v]])
  leaf_lifespan[[v]][i] <- 0
}

# For individuals with "length" measures, translate into count

# get average leaves per length for spp
leaves_per_length_spp <- read.csv("data/leaves_per_length.csv", header=TRUE, as.is=TRUE,stringsAsFactors=FALSE) %>%
  filter(use=="yes") %>%
  mutate(count_per_length = leaf_count/length_mm) %>%
  group_by(species) %>%
  summarise(count_per_length = mean(count_per_length, na.rm=TRUE))

# get spp average for all individuals 
raw_leaf_lifespan$count_per_length <- leaves_per_length_spp$count_per_length[match(raw_leaf_lifespan$species, leaves_per_length_spp$species)]

# if possible use data for that individual, if it exists
i <- !is.na(raw_leaf_lifespan$mm_lvs)
raw_leaf_lifespan$count_per_length[i] <- (raw_leaf_lifespan$mm_lvs/raw_leaf_lifespan$count_lvs_spec)[i]

#TODO: Check outlier for HATE

"lvs_start_length""lvs_end_length" "lvs_new_length", ,"mm_lvs_spec","count_lvs_spec"
# #turning NAs into zeros
# colnames(leaf_lifespan)
# leaf_lifespan$lvs_start_length[is.na(leaf_lifespan$lvs_start_length)] <-0
# leaf_lifespan$lvs_start_count[is.na(leaf_lifespan$lvs_start_count)] <-0
# leaf_lifespan$lvs_end_length[is.na(leaf_lifespan$lvs_end_length)] <-0
# leaf_lifespan$lvs_end_count[is.na(leaf_lifespan$lvs_end_count)] <-0
# leaf_lifespan$lvs_new_length[is.na(leaf_lifespan$lvs_new_length)] <-0
# leaf_lifespan$lvs_new_count[is.na(leaf_lifespan$lvs_new_count)] <-0
# leaf_lifespan$new_but_shed_count[is.na(leaf_lifespan$new_but_shed_count)] <-0
# leaf_lifespan$mm_lvs_spec[is.na(leaf_lifespan$mm_lvs_spec)] <-0
# leaf_lifespan$count_lvs_spec[is.na(leaf_lifespan$count_lvs_spec)] <-0

# specific leaves per length data
leaf_lifespan_specific <- subset(leaf_lifespan,mm_lvs_spec!="0")
leaf_lifespan_specific$count_per_length <- leaf_lifespan_specific$count_lvs_spec/leaf_lifespan_specific$mm
leaf_lifespan_specific$leaf_start_total <- leaf_lifespan_specific$lvs_start_count + (leaf_lifespan_specific$count_per_length*leaf_lifespan_specific$lvs_start_length)
leaf_lifespan_specific$leaf_end_total <- leaf_lifespan_specific$lvs_end_count + (leaf_lifespan_specific$count_per_length*leaf_lifespan_specific$lvs_end_length)
leaf_lifespan_specific$leaf_new_total <- leaf_lifespan_specific$lvs_new_count + leaf_lifespan_specific$new_but_shed_count + (leaf_lifespan_specific$count_per_length*leaf_lifespan_specific$lvs_new_length)
head(leaf_lifespan_specific)

#generic leaves per length data
leaves_per_length$count_per_length <- leaves_per_length$leaf_count/leaves_per_length$length_mm
per_length_spp <- aggregate(count_per_length ~ species, leaves_per_length, FUN=mean)

leaf_lifespan_generic <- subset(leaf_lifespan,mm_lvs_spec=="0")
leaf_lifespan_generic <- merge(leaf_lifespan_generic, per_length_spp, by.x="species", by.y="species")
leaf_lifespan_generic$leaf_start_total <- leaf_lifespan_generic$lvs_start_count + (leaf_lifespan_generic$count_per_length*leaf_lifespan_generic$lvs_start_length)
leaf_lifespan_generic$leaf_end_total <- leaf_lifespan_generic$lvs_end_count + (leaf_lifespan_generic$count_per_length*leaf_lifespan_generic$lvs_end_length)
leaf_lifespan_generic$leaf_new_total <- leaf_lifespan_generic$lvs_new_count + leaf_lifespan_generic$new_but_shed_count + (leaf_lifespan_generic$count_per_length*leaf_lifespan_generic$lvs_new_length)
leaf_lifespan_generic <- subset(leaf_lifespan_generic,leaf_new_total>"0")
head(leaf_lifespan_generic)

#combine two files into 1
leaf_counts <- bind_rows(leaf_lifespan_specific, leaf_lifespan_generic)
head(leaf_counts)

#calculating leaf lifespan
leaf_counts$LL_bd <- (leaf_counts$leaf_start_total)/(((leaf_counts$leaf_start_total)-(leaf_counts$leaf_end_total))+(leaf_counts$leaf_new_total)/2)
leaf_counts$LL_death <- (leaf_counts$leaf_start_total)/((leaf_counts$leaf_start_total)-(leaf_counts$leaf_end_total))
leaf_counts$LL_birth <- (leaf_counts$leaf_start_total)/(leaf_counts$leaf_new_total)

leaf_counts$LL_death[which(is.infinite(leaf_counts$LL_death))] <- NA
leaf_counts$LL_bd[which(is.infinite(leaf_counts$LL_death))] <- NA
leaf_counts$LL_birth[which(is.infinite(leaf_counts$LL_death))] <- NA

write.csv(leaf_counts, file = "leaf_counts.csv")

#adding leaf, stem weight data from InvestmentSummary to leaf_counts dataframe
leaf_counts <- left_join(leaf_counts, InvestmentSummary, by = "tag_ID")

#adding columns to leaf_counts to look at change across year
leaf_counts$change_shoot_diam <- leaf_counts$d_end - leaf_counts$d_start
leaf_counts$change_basal_diam <- leaf_counts$FinalBasalDiam - leaf_counts$StartBasalDiam
leaf_counts$change_shoot_area <- (3.14*((leaf_counts$d_end/2)^2)) - (3.14*((leaf_counts$d_start/2)^2))
leaf_counts$change_basal_area <- (3.14*((leaf_counts$FinalBasalDiam/2)^2)) - (3.14*((leaf_counts$StartBasalDiam/2)^2))

#removng crazy numbers
leaf_counts <- subset(leaf_counts,LL_bd>0)
leaf_counts <- subset(leaf_counts,LL_bd<6)
leaf_counts <- subset(leaf_counts,LL_birth<8)
leaf_counts <- subset(leaf_counts,LL_death<8)

#leaf lifespan summary by species, age
LLSummary <- leaf_counts %>%
  group_by(species, age) %>%
  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length)

#LMA summary by species, age
LMA_summary <- LMA %>%
  group_by(species, age) %>%
  summarise_each(funs(mean, se, length), LMA)
names(LMA_summary)<-c("species","age","LMA_mean","LMA_se","LMA_length")

leaf_counts_nobabies <- subset(leaf_counts, age>2)
LMA_nobabies <- subset(LMA, age>2)

#leaf lifespan summary by species
LL_spp <- leaf_counts_nobabies %>%
  group_by(species) %>%
  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth)

#LMA summary by species
LMA_spp <- LMA_nobabies %>%
  group_by(species) %>%
  summarise_each(funs(mean, se, length), LMA)
names(LMA_spp)<-c("species", "LMA_mean","LMA_se","LMA_length")

#merge LMA data into LLSummary dataframe
LLSummary <- merge(LLSummary, LMA_summary, by.x=c("species","age"), by.y=c("species","age"))
LL_spp <- merge(LL_spp, LMA_spp, by.x=c("species"), by.y=c("species"))

#plotting and stats
#LL vs LMA
pch.spp <- c(0,1,2,15,16,17,18,0,1,2,15,16,17,18)
col.spp <- c("red", "dark green", "blue", "purple", "orange", "light green","salmon","turquoise","grey", "black","light blue","brown","yellow","salmon")
col.age <-c("purple","pink","green","orange","blue","light blue")
pch.age <- c(1,1,16,16,16,16)
labels.spp <- c("Banksia","Boronia","Conospermum","Epacris", "Grevillea buxifolia","Grevillea speciosa","Hakea","Hemigenia","Leucopogon","Persoonia", "Petrophile", "Phyllota", "Pimelea", "Pultanaea")
names(labels.spp) <- c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU") 
labels.age <- c("1.4","2.4","5","7","9","32")

#remove HATE, babies
LL_nobabies <- subset(LLSummary, age > 2)
LL_noHate <- subset(LLSummary, species != "HATE")
LL_noHatebabies <- subset(LL_nobabies, species != "HATE")
```

# relationship between LMA, LL by age, species

For 2.4 year old plants

```{r, echo=FALSE}
plot(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==2.4), xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1)
mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==2.4))
summary(mod)
abline(mod)
```

# Plotting final leaf number on the leader by diameter increase of the entire plant (basal diameter) and the leader (shoot diameter).

Both show a strong correlation and species effect as expected. For the model with basal diameter there is a strong age effect, but not for shoot diameter. This is presumably because a shoot of a given species should always deploy the same number of leaves for the same diameter increase. In contrast, the whole plant will have many differing shoot numbers with age, so differing effects of a single shoot's increased diameter. Strangely, the model with basal diameter shows a stronger effect between diameter increase and leaf number.

```{r, echo=FALSE,results='hide', message=FALSE}
plot(change_basal_diam ~ leaf_new_total, leaf_counts, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in basal diameter")
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod <- lm(log(leaf_new_total) ~ log(change_basal_diam+1) + species +age, leaf_counts)
summary(mod)

plot(change_shoot_diam ~ leaf_new_total, leaf_counts, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in diameter of leader")
legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
mod <- lm(log(leaf_new_total) ~ log(change_shoot_diam+10) + species +age, data= subset(leaf_counts, !is.na(change_shoot_diam)))
summary(mod)
```

#LL vs LMA using species by site means

Overall plot shows a lack of relationship when HATE included. This is because it has such a high LMA. The youngest and oldest plants have no pattern, presumably because LL data are inaccurate

```{r, echo=FALSE,results='hide', message=FALSE}

col.LMA <-c("black","purple", "pink", "light green", "orange","blue", "light blue","red")
labels.LMA <-c("all except HATE","age 1.4", "age 2.4", "age 5", "age 7", "age 9", "age 32", "including HATE")
plot(LL_birth_mean ~ LMA_mean, LLSummary, type="n", xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1,pch=17, log="xy")
points(LL_birth_mean ~ LMA_mean, LL_noHate, pch=16, cex=1.2, col=col.age[as.factor(age)])
points(LL_birth_mean ~ LMA_mean, col="red", data=subset(LLSummary, species=="HATE"), pch=17)
mod <- lm(LL_birth_mean ~ LMA_mean, LLSummary)
abline(mod, col="red", lty=2)
mod_no_HATE <- lm(LL_birth_mean ~ LMA_mean, LL_noHate)
abline(mod_no_HATE, lwd=2)
mod_no_HATE5 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==5))
abline(mod_no_HATE5, col="light green", lwd=1.5)
mod_no_HATE7 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==7))
abline(mod_no_HATE7, col="orange", lwd=1.5)
mod_no_HATE9 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==9))
abline(mod_no_HATE9, col="blue", lwd=1.5)
mod_no_HATE2.4 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==2.4))
abline(mod_no_HATE2.4, col="pink", lwd=1.5)
mod_no_HATE1 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age<2.4))
abline(mod_no_HATE1, col="purple", lwd=1.5)
mod_no_HATE32 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==32))
abline(mod_no_HATE32, col="light blue", lwd=1.5)

legend("bottomright",col=col.LMA, labels.LMA, pch=16, cex=1.4)
summary(mod)
```

#Leaf lifespan patterns
First a model showing data by age and species, omitting the youngest plants. Uses calculations for "leaf births" only. Plots of leaf lifespan by age for each of the species

Age is not significant, but some significant interactions (COER, HATE, HEPU)
And many species have sigificantly different LL from one another

```{r, echo=FALSE,results='hide', message=FALSE}
mod <- lm(LL_birth ~ age +species + age*species, leaf_counts_nobabies)
summary(mod)

leaf_counts %>% group_by(species) %>%
    summarise(mean(age))

plot_LLvAge <- function(spp) {
  plot(LL_birth ~ age, data=subset(leaf_counts,species==spp), xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1, 
     main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x")  
}

for(n in names(labels.spp)) {
  plot_LLvAge(n)
}
```

#LMA by age, species, without youngest plants

There is also no overall affect of age on LMA, although a few species would show an effect if analyzed independently. (Again, this model omits 1-year old plants.)

```{r, echo=FALSE, message=FALSE}
plot(LMA_mean ~ as.factor(species), LL_nobabies, xlab="species", ylab="LMA", cex.axis=.8, las=1)
mod <- lm(LMA ~ age +species + age*species, LMA)
summary(mod)

plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="BAER"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Banksia ericifolia")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="BOLE"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Boronia ledifolia")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="COER"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Conospermum ericifolium")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="EPMI"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Epacris microphylla")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="GRBU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Grevillea buxifolia")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="GRSP"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Grevillea speciosa")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="HATE"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Hakea teretifolia")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="HEPU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Hemigenia purpurea")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="LEES"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Leucopogon esquamatus")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PELA"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Persoonia lanceolata")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PEPU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Petrophile pulchella")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PHPH"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Phyllota phylicoides")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PILI"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Pimelea linifolia")
plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PUTU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Pultenaea tuberculata")
```

#models with leaf counts per age
The number of leaves on a leader is slightly affected by age however, with a decrease in leaf count along the leader with increasing age. This is what gives the perception of fewer leaves in older plants.

QUESTION: Why does age need to be a factor for the plots to work?
```{r, echo=FALSE,results='hide', message=FALSE}

plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BAER"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Banksia ericifolia")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BOLE"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Boronia ledifolia")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="COER"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Conospermum ericifolium")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="EPMI"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Epacris microphylla")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRBU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Grevillea buxifolia")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRSP"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Grevillea speciosa")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HATE"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Hakea teretifolia")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HEPU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Hemigenia purpurea")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="LEES"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Leucopogon esquamatus")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PELA"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Persoonia lanceolata")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PEPU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Petrophile pulchella")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PHPH"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Phyllota phylicoides")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PILI"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Pimelea linifolia")
plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PUTU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Pultenaea tuberculata")

mod <- lm(leaf_end_total ~ age +species +age*species, leaf_counts_nobabies)
summary(mod)
```

#models with shoot extenstion by age

###combine shoot extension and investment files, by tag_ID

```{r, echo=FALSE,results='hide', message=FALSE}
plot(new_length_mean ~ age, LLSummary, col=col.spp[as.factor(species)])
legend("topright",col=col.spp, labels.spp, pch=16, cex=1.4)

plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BAER"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Banksia ericifolia")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BOLE"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Boronia ledifolia")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="COER"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Conospermum ericifolium")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="EPMI"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Epacris microphylla")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRBU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Grevillea buxifolia")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRSP"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Grevillea speciosa")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HATE"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Hakea teretifolia")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HEPU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Hemigenia purpurea")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="LEES"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Leucopogon esquamatus")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PELA"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Persoonia lanceolata")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PEPU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Petrophile pulchella")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PHPH"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Phyllota phylicoides")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PILI"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Pimelea linifolia")
plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PUTU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Pultenaea tuberculata")

mod <- lm(new_length ~ age +species +age*species, leaf_counts)
summary(mod)
```

### 2015-03-19 leaflifespan.R

@@ -68,28 +68,28 @@ head(leaf_lifespan_generic)
 leaf_counts <- bind_rows(leaf_lifespan_specific, leaf_lifespan_generic)
 head(leaf_counts)
 
-#calculating LeafLifespan
-leaf_counts$leaf_lifespan_db <- (leaf_counts$leaf_start_total)/(((leaf_counts$leaf_start_total)-(leaf_counts$leaf_end_total))+(leaf_counts$leaf_new_total)/2)
-leaf_counts$leaf_lifespan_death <- (leaf_counts$leaf_start_total)/((leaf_counts$leaf_start_total)-(leaf_counts$leaf_end_total))
-leaf_counts$leaf_lifespan_birth <- (leaf_counts$leaf_start_total)/(leaf_counts$leaf_new_total)
+#calculating leaf lifespan
+leaf_counts$LL_bd <- (leaf_counts$leaf_start_total)/(((leaf_counts$leaf_start_total)-(leaf_counts$leaf_end_total))+(leaf_counts$leaf_new_total)/2)
+leaf_counts$LL_death <- (leaf_counts$leaf_start_total)/((leaf_counts$leaf_start_total)-(leaf_counts$leaf_end_total))
+leaf_counts$LL_birth <- (leaf_counts$leaf_start_total)/(leaf_counts$leaf_new_total)
 
-leaf_counts$leaf_lifespan_death[which(is.infinite(leaf_counts$leaf_lifespan_death))] <- NA
-leaf_counts$leaf_lifespan_db[which(is.infinite(leaf_counts$leaf_lifespan_death))] <- NA
-leaf_counts$leaf_lifespan_birth[which(is.infinite(leaf_counts$leaf_lifespan_death))] <- NA
+leaf_counts$LL_death[which(is.infinite(leaf_counts$LL_death))] <- NA
+leaf_counts$LL_bd[which(is.infinite(leaf_counts$LL_death))] <- NA
+leaf_counts$LL_birth[which(is.infinite(leaf_counts$LL_death))] <- NA
 
 write.csv(leaf_counts, file = "leaf_counts.csv")
 
 #removng crazy numbers
-leaf_counts <- subset(leaf_counts,leaf_lifespan_db>0)
-leaf_counts <- subset(leaf_counts,leaf_lifespan_db<6)
-leaf_counts <- subset(leaf_counts,leaf_lifespan_birth<8)
[…]

### 2015-03-24 leaflifespan.Rmd
working to streamline script, use functions for plotting, models

@@
 
-LMA <- read.csv("data/LMA_short.csv",header=TRUE,as.is=TRUE,stringsAsFactors=FALSE)
+LMA <- read.csv("data/LMA_short.csv",header=TRUE,as.is=TRUE,stringsAsFactors=FALSE)%>%
+  filter(species!="" & species!=" ")
 #InvestmentSummary <- remake::make("ReproductionAllocation_all")
@@
 
-# where counts did not previously exists, set as 0
+# where counts did not previously exists, set as 0; CHECK WITH DANIEL THAT "V" IS A SET "NAME" IN THESE FUNCTIONS
 for(v in c("lvs_start_count","lvs_end_count","lvs_new_count","new_but_shed_count")) {
@@
 
-# if possible use data for that individual, if it exists
+# if possible use data for that individual, if it exists; this code substitutes in species count per length #s for individuals where this data is available
 i <- !is.na(raw_leaf_lifespan$mm_lvs)
-raw_leaf_lifespan$count_per_length[i] <- (raw_leaf_lifespan$mm_lvs/raw_leaf_lifespan$count_lvs_spec)[i]
+raw_leaf_lifespan$count_per_length[i] <- (raw_leaf_lifespan$count_lvs_spec/raw_leaf_lifespan$mm_lvs)[i]
+
+#this is the end of the section Daniel helped me rewrite - next section is mine
+
+#get total leaf counts
+for(v in c("lvs_start_length","lvs_start_count","lvs_end_length","lvs_end_count","lvs_new_length","lvs_new_count","new_but_shed_count")) {
+  i <- is.na(raw_leaf_lifespan[[v]])
+  raw_leaf_lifespan[[v]][i] <- 0
+  }
+raw_leaf_lifespan$lvs_start <- raw_leaf_lifespan$lvs_start_count + (raw_leaf_lifespan$lvs_start_length * raw_leaf_lifespan$count_per_length)
+raw_leaf_lifespan$lvs_end <- raw_leaf_lifespan$lvs_end_count + (raw_leaf_lifespan$lvs_end_length * raw_leaf_lifespan$count_per_length)
+raw_leaf_lifespan$lvs_new <- raw_leaf_lifespan$lvs_new_count + (raw_leaf_lifespan$lvs_new_length * raw_leaf_lifespan$count_per_length)
+
+#calculating leaf lifespan
+raw_leaf_lifespan$LL_bd <- (raw_leaf_lifespan$lvs_start)/(((raw_leaf_lifespan$lvs_start)-(raw_leaf_lifespan$lvs_end))+(raw_leaf_lifespan$lvs_new)/2)
+raw_leaf_lifespan$LL_death <- (raw_leaf_lifespan$lvs_start)/((raw_leaf_lifespan$lvs_start)-(raw_leaf_lifespan$lvs_end))
+raw_leaf_lifespan$LL_birth <- (raw_leaf_lifespan$lvs_start)/(raw_leaf_lifespan$lvs_new)
+
+raw_leaf_lifespan$LL_death[which(is.infinite(raw_leaf_lifespan$LL_death))] <- NA
+raw_leaf_lifespan$LL_bd[which(is.infinite(raw_leaf_lifespan$LL_death))] <- NA
+raw_leaf_lifespan$LL_birth[which(is.infinite(raw_leaf_lifespan$LL_death))] <- NA
+
+write.csv(raw_leaf_lifespan, file = "raw_leaf_lifespan.csv")
+```
 
@@
 
-"lvs_start_length""lvs_end_length" "lvs_new_length", ,"mm_lvs_spec","count_lvs_spec"
-# #turning NAs into zeros
-# colnames(leaf_lifespan)
-# leaf_lifespan$lvs_start_length[is.na(leaf_lifespan$lvs_start_length)] <-0
-# leaf_lifespan$lvs_start_count[is.na(leaf_lifespan$lvs_start_count)] <-0
-# leaf_lifespan$lvs_end_length[is.na(leaf_lifespan$lvs_end_length)] <-0
-# leaf_lifespan$lvs_end_count[is.na(leaf_lifespan$lvs_end_count)] <-0
-# leaf_lifespan$lvs_new_length[is.na(leaf_lifespan$lvs_new_length)] <-0
-# leaf_lifespan$lvs_new_count[is.na(leaf_lifespan$lvs_new_count)] <-0
-# leaf_lifespan$new_but_shed_count[is.na(leaf_lifespan$new_but_shed_count)] <-0
-# leaf_lifespan$mm_lvs_spec[is.na(leaf_lifespan$mm_lvs_spec)] <-0
-# leaf_lifespan$count_lvs_spec[is.na(leaf_lifespan$count_lvs_spec)] <-0
+```{r, echo=FALSE,results='hide', message=FALSE}
+#adding leaf, stem weight data from InvestmentSummary to raw_leaf_lifespan dataframe; can't RUN LINES 95-108 UNTIL INVESTMENT SUMMARY OPEN - THEN PROBLEM WITH PLYR
+#raw_leaf_lifespan <- left_join(raw_leaf_lifespan, InvestmentSummary, by = "tag_ID")
 
-# specific leaves per length data
-leaf_lifespan_specific <- subset(leaf_lifespan,mm_lvs_spec!="0")
-leaf_lifespan_specific$count_per_length <- leaf_lifespan_specific$count_lvs_spec/leaf_lifespan_specific$mm
-leaf_lifespan_specific$leaf_start_total <- leaf_lifespan_specific$lvs_start_count + (leaf_lifespan_specific$count_per_length*leaf_lifespan_specific$lvs_start_length)
-leaf_lifespan_specific$leaf_end_total <- leaf_lifespan_specific$lvs_end_count + (leaf_lifespan_specific$count_per_length*leaf_lifespan_specific$lvs_end_length)
-leaf_lifespan_specific$leaf_new_total <- leaf_lifespan_specific$lvs_new_count + leaf_lifespan_specific$new_but_shed_count + (leaf_lifespan_specific$count_per_length*leaf_lifespan_specific$lvs_new_length)
-head(leaf_lifespan_specific)
+#adding columns to raw_leaf_lifespan to look at change across year
+raw_leaf_lifespan$change_shoot_diam <- raw_leaf_lifespan$d_end - raw_leaf_lifespan$d_start
+#raw_leaf_lifespan$change_basal_diam <- raw_leaf_lifespan$FinalBasalDiam - raw_leaf_lifespan$StartBasalDiam
+raw_leaf_lifespan$change_shoot_area <- (3.14*((raw_leaf_lifespan$d_end/2)^2)) - (3.14*((raw_leaf_lifespan$d_start/2)^2))
+#raw_leaf_lifespan$change_basal_area <- (3.14*((raw_leaf_lifespan$FinalBasalDiam/2)^2)) - (3.14*((raw_leaf_lifespan$StartBasalDiam/2)^2))
 
-#generic leaves per length data
-leaves_per_length$count_per_length <- leaves_per_length$leaf_count/leaves_per_length$length_mm
-per_length_spp <- aggregate(count_per_length ~ species, leaves_per_length, FUN=mean)
+#removng crazy numbers; probably better to do this for each analysis than overall, because removing indiviiduals from all three at once
+#raw_leaf_lifespan <- subset(raw_leaf_lifespan,LL_bd>0)
+#raw_leaf_lifespan <- subset(raw_leaf_lifespan,LL_bd<6)
+#raw_leaf_lifespan <- subset(raw_leaf_lifespan,LL_birth<8)
+#raw_leaf_lifespan <- subset(raw_leaf_lifespan,LL_death<8)
 
-leaf_lifespan_generic <- subset(leaf_lifespan,mm_lvs_spec=="0")
-leaf_lifespan_generic <- merge(leaf_lifespan_generic, per_length_spp, by.x="species", by.y="species")
-leaf_lifespan_generic$leaf_start_total <- leaf_lifespan_generic$lvs_start_count + (leaf_lifespan_generic$count_per_length*leaf_lifespan_generic$lvs_start_length)
-leaf_lifespan_generic$leaf_end_total <- leaf_lifespan_generic$lvs_end_count + (leaf_lifespan_generic$count_per_length*leaf_lifespan_generic$lvs_end_length)
-leaf_lifespan_generic$leaf_new_total <- leaf_lifespan_generic$lvs_new_count + leaf_lifespan_generic$new_but_shed_count + (leaf_lifespan_generic$count_per_length*leaf_lifespan_generic$lvs_new_length)
-leaf_lifespan_generic <- subset(leaf_lifespan_generic,leaf_new_total>"0")
-head(leaf_lifespan_generic)
-
-#combine two files into 1
-leaf_counts <- bind_rows(leaf_lifespan_specific, leaf_lifespan_generic)
-head(leaf_counts)
-
-#calculating leaf lifespan
-leaf_counts$LL_bd <- (leaf_counts$leaf_start_total)/(((leaf_counts$leaf_start_total)-(leaf_counts$leaf_end_total))+(leaf_counts$leaf_new_total)/2)
-leaf_counts$LL_death <- (leaf_counts$leaf_start_total)/((leaf_counts$leaf_start_total)-(leaf_counts$leaf_end_total))
-leaf_counts$LL_birth <- (leaf_counts$leaf_start_total)/(leaf_counts$leaf_new_total)
-
-leaf_counts$LL_death[which(is.infinite(leaf_counts$LL_death))] <- NA
-leaf_counts$LL_bd[which(is.infinite(leaf_counts$LL_death))] <- NA
-leaf_counts$LL_birth[which(is.infinite(leaf_counts$LL_death))] <- NA
-
-write.csv(leaf_counts, file = "leaf_counts.csv")
-
-#adding leaf, stem weight data from InvestmentSummary to leaf_counts dataframe
-leaf_counts <- left_join(leaf_counts, InvestmentSummary, by = "tag_ID")
-
-#adding columns to leaf_counts to look at change across year
-leaf_counts$change_shoot_diam <- leaf_counts$d_end - leaf_counts$d_start
-leaf_counts$change_basal_diam <- leaf_counts$FinalBasalDiam - leaf_counts$StartBasalDiam
-leaf_counts$change_shoot_area <- (3.14*((leaf_counts$d_end/2)^2)) - (3.14*((leaf_counts$d_start/2)^2))
-leaf_counts$change_basal_area <- (3.14*((leaf_counts$FinalBasalDiam/2)^2)) - (3.14*((leaf_counts$StartBasalDiam/2)^2))
-
-#removng crazy numbers
-leaf_counts <- subset(leaf_counts,LL_bd>0)
-leaf_counts <- subset(leaf_counts,LL_bd<6)
-leaf_counts <- subset(leaf_counts,LL_birth<8)
-leaf_counts <- subset(leaf_counts,LL_death<8)
-
+#creating summary files
 #leaf lifespan summary by species, age
-LLSummary <- leaf_counts %>%
+LLSummary <- raw_leaf_lifespan %>%
+  filter(LL_bd>0 & LL_bd<6 & LL_birth<8 & LL_death<8) %>%
   group_by(species, age) %>%
-  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length)
+  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length, lvs_end)
 
@@
 
-leaf_counts_nobabies <- subset(leaf_counts, age>2)
-LMA_nobabies <- subset(LMA, age>2)
+#leaf lifespan summary by species
 
-#leaf lifespan summary by species
-LL_spp <- leaf_counts_nobabies %>%
+LL_spp <- raw_leaf_lifespan %>%
+  filter(age>2) %>%
   group_by(species) %>%
@@
 #LMA summary by species
-LMA_spp <- LMA_nobabies %>%
+LMA_spp <- LMA %>%
+  filter(age>2) %>%
   group_by(species) %>%
@@
 #plotting and stats
-#LL vs LMA
+#creating lists of information for plotting symbols, colors, labels
 pch.spp <- c(0,1,2,15,16,17,18,0,1,2,15,16,17,18)
@@
 pch.age <- c(1,1,16,16,16,16)
-labels.spp <- c("Banksia","Boronia","Conospermum","Epacris", "Grevillea buxifolia","Grevillea speciosa","Hakea","Hemigenia","Leucopogon","Persoonia", "Petrophile", "Phyllota", "Pimelea", "Pultanaea")
+labels.spp <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris micraphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
 names(labels.spp) <- c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU") 
@@
 
+#LL vs LMA
 #remove HATE, babies
-LL_nobabies <- subset(LLSummary, age > 2)
-LL_noHate <- subset(LLSummary, species != "HATE")
-LL_noHatebabies <- subset(LL_nobabies, species != "HATE")
+#instead of separate dataframes, can probably incorporate this information directly into plotting and analysis commands
+#LL_nobabies <- subset(raw_leaf_lifespan, age>2)
+#LMA_nobabies <- subset(LMA, age>2)
+#LL_noHate <- subset(LLSummary, species != "HATE")
+#LL_noHatebabies <- subset(LL_nobabies, species != "HATE")
 ```
@@
 
-For 2.4 year old plants
-
+For 7 year old plants
 ```{r, echo=FALSE}
-plot(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==2.4), xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1)
-mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==2.4))
+plot(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==7), xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA", las=1, pch=16)
+text(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==7), labels=species, pos=1, offset=-0.9, cex=0.9,col="blue")
+text(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==7 & species=="HATE"), labels=species, pos=1, offset=-0.9, cex=0.9,col="red")
+mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,species!="HATE" & age==7))
 summary(mod)
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(change_basal_diam ~ leaf_new_total, leaf_counts, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in basal diameter")
+plot(change_basal_diam ~ leaf_new_total, raw_leaf_lifespan, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in basal diameter")
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <- lm(log(leaf_new_total) ~ log(change_basal_diam+1) + species +age, leaf_counts)
+mod <- lm(log(leaf_new_total) ~ log(change_basal_diam+1) + species +age, raw_leaf_lifespan)
 summary(mod)
 
-plot(change_shoot_diam ~ leaf_new_total, leaf_counts, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in diameter of leader")
+plot(change_shoot_diam ~ leaf_new_total, raw_leaf_lifespan, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in diameter of leader")
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <- lm(log(leaf_new_total) ~ log(change_shoot_diam+10) + species +age, data= subset(leaf_counts, !is.na(change_shoot_diam)))
+mod <- lm(log(leaf_new_total) ~ log(change_shoot_diam+10) + species +age, data= subset(raw_leaf_lifespan, !is.na(change_shoot_diam)))
 summary(mod)
@@
 plot(LL_birth_mean ~ LMA_mean, LLSummary, type="n", xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1,pch=17, log="xy")
-points(LL_birth_mean ~ LMA_mean, LL_noHate, pch=16, cex=1.2, col=col.age[as.factor(age)])
+points(LL_birth_mean ~ LMA_mean, data=subset(LLSummary, species!="HATE"), pch=16, cex=1.2, col=col.age[as.factor(age)])
 points(LL_birth_mean ~ LMA_mean, col="red", data=subset(LLSummary, species=="HATE"), pch=17)
+#need log transformation to get these to plot onto axes
 mod <- lm(LL_birth_mean ~ LMA_mean, LLSummary)
 abline(mod, col="red", lty=2)
-mod_no_HATE <- lm(LL_birth_mean ~ LMA_mean, LL_noHate)
+mod_no_HATE <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary, species!="HATE"))
 abline(mod_no_HATE, lwd=2)
-mod_no_HATE5 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==5))
+mod_no_HATE5 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==5&species!="HATE"))
 abline(mod_no_HATE5, col="light green", lwd=1.5)
-mod_no_HATE7 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==7))
+mod_no_HATE7 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==7&species!="HATE"))
 abline(mod_no_HATE7, col="orange", lwd=1.5)
-mod_no_HATE9 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==9))
+mod_no_HATE9 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==9&species!="HATE"))
 abline(mod_no_HATE9, col="blue", lwd=1.5)
-mod_no_HATE2.4 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==2.4))
+mod_no_HATE2.4 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==2.4&species!="HATE"))
 abline(mod_no_HATE2.4, col="pink", lwd=1.5)
-mod_no_HATE1 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age<2.4))
+mod_no_HATE1 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age<2.4&species!="HATE"))
 abline(mod_no_HATE1, col="purple", lwd=1.5)
-mod_no_HATE32 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LL_noHate,age==32))
+mod_no_HATE32 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==32&species!="HATE"))
 abline(mod_no_HATE32, col="light blue", lwd=1.5)
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-mod <- lm(LL_birth ~ age +species + age*species, leaf_counts_nobabies)
+mod <- lm(LL_birth ~ age + species +age*species, data=subset(raw_leaf_lifespan,age>3 & LL_birth!="Inf"))
 summary(mod)
 
-leaf_counts %>% group_by(species) %>%
-    summarise(mean(age))
+#WHY ARE THE FOLLOWING TWO LINES OF CODE NEEDED?
+raw_leaf_lifespan %>% group_by(species) %>%
+    summarise(mean(LL_birth))
 
+#where does the [spp] comes from? This is the first place in the script it is used like this - I assume it could be any name?
 plot_LLvAge <- function(spp) {
-  plot(LL_birth ~ age, data=subset(leaf_counts,species==spp), xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1, 
-     main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x")  
+  plot(LL_birth ~ age, data=subset(raw_leaf_lifespan,species==spp), xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1, 
+     main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)  
+  points(LL_birth_mean ~ age, data=subset(LLSummary, species==spp), cex=1.3, pch=8)
+  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=25)
+  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=24)
 }
@@
 }
+
 ```
@@
 ```{r, echo=FALSE, message=FALSE}
-plot(LMA_mean ~ as.factor(species), LL_nobabies, xlab="species", ylab="LMA", cex.axis=.8, las=1)
-mod <- lm(LMA ~ age +species + age*species, LMA)
-summary(mod)
+#plot(LMA_mean ~ as.factor(species), data=subset(LLSummary,age>3), xlab="species", ylab="LMA", cex.axis=.8, las=1)
+#mod <- lm(LMA ~ age +species + age*species, LMA)
+#summary(mod)
 
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="BAER"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Banksia ericifolia")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="BOLE"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Boronia ledifolia")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="COER"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Conospermum ericifolium")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="EPMI"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Epacris microphylla")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="GRBU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Grevillea buxifolia")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="GRSP"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Grevillea speciosa")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="HATE"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Hakea teretifolia")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="HEPU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Hemigenia purpurea")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="LEES"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Leucopogon esquamatus")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PELA"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Persoonia lanceolata")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PEPU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Petrophile pulchella")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PHPH"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Phyllota phylicoides")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PILI"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Pimelea linifolia")
-plot(LMA ~ as.factor(age), LMA, data=subset(LMA,species=="PUTU"), xlab="age", ylab="LMA", cex.axis=.8, las=1, main="Pultenaea tuberculata")
+LMA %>% group_by(species) %>%
+  summarise(mean(LMA))
+
+labels.spp <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris micraphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(labels.spp) <- c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")
+
+plot_LMAvAge <- function(spp) {
+  plot(LMA ~ age, data=subset(LMA,species==spp), xlab="age", ylab="LMA", cex.axis=.8, las=1, pch=16, log="x",
+  main=labels.spp[spp]) 
+  points(LMA_mean ~ age, data=subset(LLSummary, species==spp), cex=1.3, pch=8)
+  points((LMA_mean+LMA_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=25)
+  points((LMA_mean-LMA_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=24)
+  #I want to add a line of code that plots over the means for each age. I did this above by calling in another file, but wondering about on-the-spot calculations
+}
+
+mod_LMAvAge <- function(spp) {
+  lm(LMA ~ age, data=subset(LMA,species==spp))
+}
+
+for(n in names(labels.spp)) {
+  plot_LMAvAge(n)
+  mod_LMAvAge(n)
+  summary(mod_LMAvAge(n))
+}
+
 ```
@@
 The number of leaves on a leader is slightly affected by age however, with a decrease in leaf count along the leader with increasing age.
-This is what gives the perception of fewer leaves in older plants.
+This is what gives the perception of fewer leaves in some older plants.
 
-QUESTION: Why does age need to be a factor for the plots to work?
 ```{r, echo=FALSE,results='hide', message=FALSE}
 
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BAER"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Banksia ericifolia")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BOLE"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Boronia ledifolia")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="COER"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Conospermum ericifolium")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="EPMI"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Epacris microphylla")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRBU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Grevillea buxifolia")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRSP"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Grevillea speciosa")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HATE"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Hakea teretifolia")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HEPU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Hemigenia purpurea")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="LEES"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Leucopogon esquamatus")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PELA"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Persoonia lanceolata")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PEPU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Petrophile pulchella")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PHPH"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Phyllota phylicoides")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PILI"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Pimelea linifolia")
-plot(leaf_end_total ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PUTU"), xlab="age", ylab="leaf counts", cex.axis=.8, las=1, main="Pultenaea tuberculata")
+labels.spp <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris micraphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(labels.spp) <- c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")
 
-mod <- lm(leaf_end_total ~ age +species +age*species, leaf_counts_nobabies)
-summary(mod)
+plot_lfcountvAge <- function(spp) {
+  plot(lvs_end ~ age, data=subset(raw_leaf_lifespan,species==spp), xlab="age", ylab="leaf count along shoot", cex.axis=.8, las=1, pch=16, log="x",
+  main=labels.spp[spp]) 
+  points(lvs_end_mean ~ age, data=subset(LLSummary, species==spp), cex=1.3, pch=8)
+  points((lvs_end_mean+lvs_end_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=25)
+  points((lvs_end_mean-lvs_end_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=24)
+}
+
+mod_lfcountvAge <- function(spp) {
+  lm(lvs_end ~ age, data=subset(raw_leaf_lifespan,age>2.4 & species==spp))
+}
+
+for(n in names(labels.spp)) {
+  plot_lfcountvAge(n)
+  mod_lfcountvAge(n)
+  summary(mod_lfcountvAge(n))
+}
+
 ```
@@
 #models with shoot extenstion by age
-
-###combine shoot extension and investment files, by tag_ID
+These models show that for some species, shoot extension decreases enormously in the older plants.
+This effect is larger than with number of leaves, indicating that some of these individuals have more leaves per length as they get older
 
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(new_length_mean ~ age, LLSummary, col=col.spp[as.factor(species)])
-legend("topright",col=col.spp, labels.spp, pch=16, cex=1.4)
+labels.spp <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris micraphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(labels.spp) <- c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")
 
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BAER"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Banksia ericifolia")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="BOLE"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Boronia ledifolia")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="COER"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Conospermum ericifolium")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="EPMI"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Epacris microphylla")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRBU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Grevillea buxifolia")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="GRSP"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Grevillea speciosa")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HATE"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Hakea teretifolia")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="HEPU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Hemigenia purpurea")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="LEES"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Leucopogon esquamatus")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PELA"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Persoonia lanceolata")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PEPU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Petrophile pulchella")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PHPH"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Phyllota phylicoides")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PILI"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Pimelea linifolia")
-plot(new_length ~ as.factor(age), leaf_counts, data=subset(leaf_counts,species=="PUTU"), xlab="age", ylab="shoot extension (mm)", cex.axis=.8, las=1, main="Pultenaea tuberculata")
+plot_newlengthvAge <- function(spp) {
+  plot(new_length ~ age, data=subset(raw_leaf_lifespan,species==spp), xlab="age", ylab="leader shoot extention", cex.axis=.8, las=1, pch=16, log="x",
+  main=labels.spp[spp]) 
+  points(new_length_mean ~ age, data=subset(LLSummary, species==spp), cex=1.3, pch=8)
+  points((new_length_mean+new_length_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=25)
+  points((new_length_mean-new_length_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=24)
+}
 
-mod <- lm(new_length ~ age +species +age*species, leaf_counts)
-summary(mod)
+mod_newlengthvAge <- function(spp) {
+  lm(new_length ~ age, data=subset(raw_leaf_lifespan,age>2.4 & species==spp))
+}
+
+for(n in names(labels.spp)) {
+  plot_newlengthvAge(n)
+  mod_newlengthvAge(n)
+  summary(mod_newlengthvAge(n))
+}
 ```
+
+#plots regressing variables against one another

### 2015-03-24 leaflifespan.Rmd
Move functions into utils file, move packages into remake.yml

@@
 # load packages
-library(tidyr)
-library(dplyr)
-#library(lme4)
 
-#load files
+library(remake)
+create_bindings()
 
-LMA <- read.csv("data/LMA_short.csv",header=TRUE,as.is=TRUE,stringsAsFactors=FALSE)%>%
+# InvestmentSummary <- InvestmentSummary
+# names(InvestmentSummary)[1] <- "tag_ID"
+
+LMA <- read.csv("data/LMA_short.csv",header=TRUE,stringsAsFactors=FALSE)%>%
   filter(species!="" & species!=" ")
-#InvestmentSummary <- remake::make("ReproductionAllocation_all")
-#names(InvestmentSummary)[1] <- "tag_ID"
 
-#define functions
-se <- function(x) sd(x)/sqrt(length(x))
-con95 <- function(x) (sd(x)/sqrt(length(x)))*1.96
+wood <- read.csv("data/woodDensity.csv", header=TRUE,stringsAsFactors=FALSE)%>%
+  filter(use=="use")
+
+seedsize <- read.csv("data/seedsize.csv", header=TRUE,stringsAsFactors=FALSE)
 
 # leaf lifespan data
-raw_leaf_lifespan <- read.csv("data/leaderGrowthLL.csv",header=TRUE,as.is=TRUE,stringsAsFactors=FALSE) %>%
+raw_leaf_lifespan <- read.csv("data/leaderGrowthLL.csv",header=TRUE,stringsAsFactors=FALSE) %>%
   filter(dont_use!="dead" & dont_use!="dont_use")
@@
 # get average leaves per length for spp
-leaves_per_length_spp <- read.csv("data/leaves_per_length.csv", header=TRUE, as.is=TRUE,stringsAsFactors=FALSE) %>%
+leaves_per_length_spp <- read.csv("data/leaves_per_length.csv", header=TRUE, stringsAsFactors=FALSE) %>%
   filter(use=="yes") %>%
@@
 
-write.csv(raw_leaf_lifespan, file = "raw_leaf_lifespan.csv")
+#write.csv(raw_leaf_lifespan, file = "raw_leaf_lifespan.csv")
 ```
@@
   group_by(species, age) %>%
-  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length, lvs_end)
+  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length, lvs_end, lvs_end_total)
 
@@
 
+#wood density summary by species
+Wood_summary <- wood %>%
+  group_by(species) %>%
+  summarise_each(funs(mean, se, length), density)
+names(Wood_summary)<-c("species","WD_mean","WD_se","WD_length")
+
 #leaf lifespan summary by species
-
 LL_spp <- raw_leaf_lifespan %>%
@@
 
-#merge LMA data into LLSummary dataframe
+#merge LMA, wood density, seed size data into LLSummary dataframe
 LLSummary <- merge(LLSummary, LMA_summary, by.x=c("species","age"), by.y=c("species","age"))
+LLSummary <- merge(LLSummary, Wood_summary, by.x=c("species"), by.y=c("species"))
+LLSummary <- merge(LLSummary, seedsize, by.x=c("species"), by.y=c("species"))
 LL_spp <- merge(LL_spp, LMA_spp, by.x=c("species"), by.y=c("species"))
+LL_spp <- merge(LL_spp, Wood_summary, by.x=c("species"), by.y=c("species"))
+LL_spp <- merge(LL_spp, seedsize, by.x=c("species"), by.y=c("species"))
+#still to add, max H from Investment data, absolute and relative growth measures
 
@@
 col.spp <- c("red", "dark green", "blue", "purple", "orange", "light green","salmon","turquoise","grey", "black","light blue","brown","yellow","salmon")
-col.age <-c("purple","pink","green","orange","blue","light blue")
+col.age <-c("purple","pink","green","orange","blue","dark green")
 pch.age <- c(1,1,16,16,16,16)
@@
 
-labels.spp <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris micraphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(labels.spp) <- c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")
-
 plot_LMAvAge <- function(spp) {
@@
 This is what gives the perception of fewer leaves in some older plants.
+I'm not sure why this pattern looks stronger than leaf lifespan.
 
@@
 
-labels.spp <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris micraphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(labels.spp) <- c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")
-
 plot_lfcountvAge <- function(spp) {
-  plot(lvs_end ~ age, data=subset(raw_leaf_lifespan,species==spp), xlab="age", ylab="leaf count along shoot", cex.axis=.8, las=1, pch=16, log="x",
+  plot(lvs_end_total ~ age, data=subset(raw_leaf_lifespan,species==spp), xlab="age", ylab="leaf count along shoot", cex.axis=.8, las=1, pch=16, log="x",
   main=labels.spp[spp]) 
-  points(lvs_end_mean ~ age, data=subset(LLSummary, species==spp), cex=1.3, pch=8)
-  points((lvs_end_mean+lvs_end_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=25)
-  points((lvs_end_mean-lvs_end_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=24)
+  points(lvs_end_total_mean ~ age, data=subset(LLSummary, species==spp), cex=1.3, pch=8)
+  points((lvs_end_total_mean+lvs_end_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=25)
+  points((lvs_end_total_mean-lvs_end_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=24)
 }
@@
 #models with shoot extenstion by age
-These models show that for some species, shoot extension decreases enormously in the older plants.
-This effect is larger than with number of leaves, indicating that some of these individuals have more leaves per length as they get older
+These models show that for some species, shoot extension decreases enormously in the older plants. This effect is larger than with number of leaves.
 
 ```{r, echo=FALSE,results='hide', message=FALSE}
-labels.spp <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris micraphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(labels.spp) <- c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")
 
@@
 #plots regressing variables against one another
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(change_shoot_area~new_length,data=subset(raw_leaf_lifespan,change_shoot_area<1000000), log="xy",col=col.age[as.factor(age)], pch=16, cex=.8, xlab="shoot extension (mm)", ylab="increased shoot cross sectional area")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod <- lm(change_shoot_area~new_length +age,data=subset(raw_leaf_lifespan,change_shoot_area<1000000))
+summary(mod)
+
+raw_leaf_lifespan$lvs_end_total <- raw_leaf_lifespan$lvs_end + raw_leaf_lifespan$lvs_new
+plot(lvs_end_total~lvs_start,raw_leaf_lifespan, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8, xlab="starting leaf count", ylab="ending leaf count")
+
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod <- lm(lvs_start~lvs_end_total+age +age*lvs_end_total, raw_leaf_lifespan)
+summary(mod)
+#IS THERE AN EASY WAY TO ADD A 1:1 LINE TO THIS PLOT?
+
+plot(LL_birth_mean~LMA_mean,data=subset(LLSummary,species!="HATE"),col=col.age[as.factor(age)], pch=16, cex=.8, log="xy",xlab="LMA", ylab="leaf lifespan (calculated from leaf births")
+points(LL_birth_mean~LMA_mean,data=subset(LLSummary,species=="HATE"),col="red", pch=19, cex=.8)

### 2015-03-24 R/Utils.R

@@ -1,7 +1,20 @@
 
+read_csv <- function(filename) {
+  read.csv(filename, header = TRUE, sep = ",", stringsAsFactors = FALSE)
+}
+
 tex_2_pdf <- function(texfile){
   filename <- tools::file_path_sans_ext(texfile)
   system(sprintf("pdflatex %s", texfile))
   aux.files <- paste0(filename, c(".log", ".aux", ".bbl", ".blg"))
   file.remove(aux.files[file.exists(aux.files)])
+}
+
+#define functions
+se <- function(x) {
+  sd(x)/sqrt(length(x))
+}
+
+con95 <- function(x){
+  (sd(x)/sqrt(length(x)))*1.96
 }

### 2015-03-24 leaflifespan.Rmd
Change variable name tag_ID -> individual

@@
 # InvestmentSummary <- InvestmentSummary
-# names(InvestmentSummary)[1] <- "tag_ID"
+# names(InvestmentSummary)[1] <- "individual"
 
@@
 leaf_lifespan <- raw_leaf_lifespan %>%
-  select(species,age,site,tag_ID,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)
+  select(species,age,site,individual,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)
 
@@
 #adding leaf, stem weight data from InvestmentSummary to raw_leaf_lifespan dataframe; can't RUN LINES 95-108 UNTIL INVESTMENT SUMMARY OPEN - THEN PROBLEM WITH PLYR
-#raw_leaf_lifespan <- left_join(raw_leaf_lifespan, InvestmentSummary, by = "tag_ID")
+#raw_leaf_lifespan <- left_join(raw_leaf_lifespan, InvestmentSummary, by = "individual")
 

### 2015-03-24 leaflifespan.Rmd
Load all data files via remake

@@
 
-# InvestmentSummary <- InvestmentSummary
-# names(InvestmentSummary)[1] <- "individual"
+LMA <- filter(LMA_raw, species!="" & species!=" ")
 
-LMA <- read.csv("data/LMA_short.csv",header=TRUE,stringsAsFactors=FALSE)%>%
-  filter(species!="" & species!=" ")
+wood <- filter(woodDensity_raw, use=="use")
 
-wood <- read.csv("data/woodDensity.csv", header=TRUE,stringsAsFactors=FALSE)%>%
-  filter(use=="use")
-
-seedsize <- read.csv("data/seedsize.csv", header=TRUE,stringsAsFactors=FALSE)
+seedsize <- seedSize_raw
 
 # leaf lifespan data
-raw_leaf_lifespan <- read.csv("data/leaderGrowthLL.csv",header=TRUE,stringsAsFactors=FALSE) %>%
-  filter(dont_use!="dead" & dont_use!="dont_use")
-
-# Create new dataset taking only count measures, bc these are ultimately what we want
-leaf_lifespan <- raw_leaf_lifespan %>%
-  select(species,age,site,individual,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)
+leaf_lifespan <- filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use")
+              select(species,age,site,tag_ID,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)
 
@@
 # get average leaves per length for spp
-leaves_per_length_spp <- read.csv("data/leaves_per_length.csv", header=TRUE, stringsAsFactors=FALSE) %>%
-  filter(use=="yes") %>%
+leaves_per_length_spp <-  filter(leavesPerLength_raw,use=="yes") %>%
   mutate(count_per_length = leaf_count/length_mm) %>%

### 2015-03-24 leaflifespan.Rmd
Small bug fix

@@
 # leaf lifespan data
-leaf_lifespan <- filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use")
+raw_leaf_lifespan <-  filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use")
+
+leaf_lifespan <- raw_leaf_lifespan %>%
               select(species,age,site,tag_ID,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)

### 2015-03-25 leaflifespan.Rmd
-script runs all the way and generate html file -script generates 3 dataframes with summaries by individual, species*age, species; each including all applicable data - strange problems: still one use of tagID in input file, and reruning all investment calculations if I close and re-open R - need to figure out how to avoid duplicating columns when merging data (in a nicer way than I've implemented)

--- 2015-03-24 leaflifespan.Rmd
@@
 - leaf_counts is file with calculated leaf counts and leaf lifespan data
-- LLSummary is file with means of LL - and other variables - by species and age; LMA data is merged to this file
-- subsets of LLSummary are created to omit babies or HATE for various analyses
+- SummarySppAge is file with means of LL - and other variables - by species and age; LMA data is merged to this file
+- subsets of SummarySppAge are created to omit babies or HATE for various analyses
 
-# general results
+#variables in my dataset
+Measures of biomass and growth include:
+- basal diameter
+- "leader" diameter
+- total biomass
+- leaf mass (calculations not yet done)
+- leaf area (calculations not yet done)
+- stem biomass (calculations not yet done)
+- leaf count along leaders
+- shoot extension
+
+* all these can be plotted against age as actual values or as change from a year earlier
+* these measures are all done at the level of "individual" with 7 individuals of each species at each of 6 sites
+
+Reproduction measures include:
+- total reproductive investment (biomass)
+- RA (ratio of reproductive investment to total surplus energy)
+- investment in each of 5 different categories of reproductive investment:
+  * tissues aborted pre-pollination (ie. aborted bud)
+  * tissues that reach their final pre-pollination stage (i.e. open flower)
+  * tissues aborted after pollination (i.e. aborted immature fruit)
+  * tissues associated with packaging and dispersal of successful, mature fruit (i.e. cones, wings, seed pods)
+  * the propagule itself (either the seed or the seed with fused fruit tissue)
+- % investment in accessory tissues versus the propagule
+- seed set (calculations not yet done)
+
+  !!!TO DISCUSS: I only have my own seed weights for species where the seed isn't fused to any fruit tissue.
+However, I do have seed weights from the literature and global databases for all species and calculations could be redone based on actual seed weights for all species.!!!
+
+Traits are:
+- leaf lifespan (individuals)
+- LMA (species * age = site)
+- wood density (species)
+- maximum height (species or site)
+- seed size (species)
+
+!!!TO DISCUSS: There are many way to calculate leaf lifespan, resulting in somewhat different patterns!!!
+
+#previously observed patterns that are - fortunately - also true for my dataset
+- correlation between LMA and leaf lifespan. (True when HATE is removed.)
+- larger seeds have higher accessory costs
+
+##GENERAL THOUGHTS (and conclusions)
+
+#Leaf lifespan, LMA, leaf area, leaf weight changes with age:
+
+In the field, it seemed that older plants had fewer leaves on their shoots, indicating either decreasing lower leaf lifespan (opposite accepted trend) and/or decreasing shoot extension with age.
+
+* results show no overall change in leaf lifespan with age, although some species have slightly increasing leaf lifespan
+* both the number of leaves on a shoot and shoot extension decline with age, with some species having quite dramatic shifts (and others no shift)
+* TO DO: Total plant leaf area (and leaf number) with age, scaled to basal area and to stem weight
+* TO DO: Plot leaf weight against height (same plot as Daniel used in the data paper in Ecology)
+
+Revised thoughts: The leading shoots show a slight decline in leaf number with age.
+Overall, the plant will look a lot "leggier" because non-leading shoots with show less new growth and even fewer leaves.
+This pattern should be captured in by looking at shifts in the ratio of leaf count (or area) to basal stem area (ir total stem weight) across ages.
+
+# overall LL, LMA results
 
@@
 
+#Accessory costs
+
+Accessory costs account for the vast majority of my plant's reproductive investment - and presumably for other perennial plants worldwide - but this is an often ignored pool.
+* Overall, larger seeds have higher accessory costs (as has been shown for other angiosperm species and given as one of the reasons why angiosperms can have smaller seeds than gymnosperms)
+
+While overall accessory costs are not clearly affected by age, several of the sub-categories do change with age:
+- proportion of reproductive energy investment in aborted buds and flowers declines after the first few reproductive years
+
+#Correlation between each of the five "traits" and growth and reproductive measures
+* TO DO: Re
+
+#discuss with Daniel
+- once we are certain about leaf lifespan calculations, those calculations should go into a separate file, since that is background processing, but like calculating investment.
+Then this becomes the file where variables are summarized, plotted analyzed.
+- make sure regressions exist (or are done), to separately look at leaf and stem biomass
+- seed weight vs. propagule weight dilemma
+- sites that are aged 1.35 vs 1.4 years
+
 #next to do
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-# load packages
 
+# load packages and "open" dataframes to use
 library(remake)
@@
 
-# leaf lifespan data
-leaf_lifespan <- filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use")
-              select(species,age,site,tag_ID,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)
+harvest <- filter(HarvestData, use_status=="use" & segment==1 & start_end=="end")
+
+investment <- ReproductionAllocation_all
+names(investment) <- c("individual","ReproInv","age","GrowthInv","StartWeight","FinalWeight","StartBasalDiamAv","FinalBasalDiamAv","TotalInvestment","RA","species")
+#still have tagId as label
+#remaking this from scratch
+
+accessory <- AccessoryCosts_all
+
+leafLifespan <- filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use")
+leafLifespan$individual <- as.factor(leafLifespan$individual)
+#loading this column as character, so using this for now
+
+# Calculating Leaf Lifespan
 
 # where counts did not previously exists, set as 0; CHECK WITH DANIEL THAT "V" IS A SET "NAME" IN THESE FUNCTIONS
+
+leaf_lifespan_temp <- leafLifespan %>%
+              select(species,age,site,individual,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)
+
 for(v in c("lvs_start_count","lvs_end_count","lvs_new_count","new_but_shed_count")) {
-  i <- is.na(leaf_lifespan[[v]])
-  leaf_lifespan[[v]][i] <- 0
+  i <- is.na(leaf_lifespan_temp[[v]])
+  leaf_lifespan_temp[[v]][i] <- 0
 }
@@
 # get spp average for all individuals
-raw_leaf_lifespan$count_per_length <- leaves_per_length_spp$count_per_length[match(raw_leaf_lifespan$species, leaves_per_length_spp$species)]
+leafLifespan$count_per_length <- leaves_per_length_spp$count_per_length[match(leafLifespan$species, leaves_per_length_spp$species)]
 
 # if possible use data for that individual, if it exists; this code substitutes in species count per length #s for individuals where this data is available
-i <- !is.na(raw_leaf_lifespan$mm_lvs)
-raw_leaf_lifespan$count_per_length[i] <- (raw_leaf_lifespan$count_lvs_spec/raw_leaf_lifespan$mm_lvs)[i]
+i <- !is.na(leafLifespan$mm_lvs)
+leafLifespan$count_per_length[i] <- (leafLifespan$count_lvs_spec/leafLifespan$mm_lvs)[i]
 
@@
 for(v in c("lvs_start_length","lvs_start_count","lvs_end_length","lvs_end_count","lvs_new_length","lvs_new_count","new_but_shed_count")) {
-  i <- is.na(raw_leaf_lifespan[[v]])
-  raw_leaf_lifespan[[v]][i] <- 0
+  i <- is.na(leafLifespan[[v]])
+  leafLifespan[[v]][i] <- 0
   }
-raw_leaf_lifespan$lvs_start <- raw_leaf_lifespan$lvs_start_count + (raw_leaf_lifespan$lvs_start_length * raw_leaf_lifespan$count_per_length)
-raw_leaf_lifespan$lvs_end <- raw_leaf_lifespan$lvs_end_count + (raw_leaf_lifespan$lvs_end_length * raw_leaf_lifespan$count_per_length)
-raw_leaf_lifespan$lvs_new <- raw_leaf_lifespan$lvs_new_count + (raw_leaf_lifespan$lvs_new_length * raw_leaf_lifespan$count_per_length)
+leafLifespan$lvs_start <- leafLifespan$lvs_start_count + (leafLifespan$lvs_start_length * leafLifespan$count_per_length)
+leafLifespan$lvs_end <- leafLifespan$lvs_end_count + (leafLifespan$lvs_end_length * leafLifespan$count_per_length)
+leafLifespan$lvs_new <- leafLifespan$lvs_new_count + (leafLifespan$lvs_new_length * leafLifespan$count_per_length)
 
 #calculating leaf lifespan
-raw_leaf_lifespan$LL_bd <- (raw_leaf_lifespan$lvs_start)/(((raw_leaf_lifespan$lvs_start)-(raw_leaf_lifespan$lvs_end))+(raw_leaf_lifespan$lvs_new)/2)
-raw_leaf_lifespan$LL_death <- (raw_leaf_lifespan$lvs_start)/((raw_leaf_lifespan$lvs_start)-(raw_leaf_lifespan$lvs_end))
-raw_leaf_lifespan$LL_birth <- (raw_leaf_lifespan$lvs_start)/(raw_leaf_lifespan$lvs_new)
+leafLifespan$LL_bd <- (leafLifespan$lvs_start)/(((leafLifespan$lvs_start)-(leafLifespan$lvs_end))+(leafLifespan$lvs_new)/2)
+leafLifespan$LL_death <- (leafLifespan$lvs_start)/((leafLifespan$lvs_start)-(leafLifespan$lvs_end))
+leafLifespan$LL_birth <- (leafLifespan$lvs_start)/(leafLifespan$lvs_new)
 
-raw_leaf_lifespan$LL_death[which(is.infinite(raw_leaf_lifespan$LL_death))] <- NA
-raw_leaf_lifespan$LL_bd[which(is.infinite(raw_leaf_lifespan$LL_death))] <- NA
-raw_leaf_lifespan$LL_birth[which(is.infinite(raw_leaf_lifespan$LL_death))] <- NA
+leafLifespan$LL_death[which(is.infinite(leafLifespan$LL_death))] <- NA
+leafLifespan$LL_bd[which(is.infinite(leafLifespan$LL_death))] <- NA
+leafLifespan$LL_birth[which(is.infinite(leafLifespan$LL_death))] <- NA
 
-#write.csv(raw_leaf_lifespan, file = "raw_leaf_lifespan.csv")
+#adding investment and accessory costs data to leafLifespan dataframe to create a dataframe with all individual level data
+#SummaryInd <- left_join(leafLifespan, investment, by = "individual")
+#SummaryInd <- left_join(SummaryInd, accessory, by = "individual")
+#SummaryInd <- left_join(SummaryInd, harvest, by = "individual")
+#not sure why the above text isn't working... using merge instead
+
+SummaryInd <- merge(leafLifespan, investment, by.x=c("individual"), by.y=c("individual"))
+SummaryInd <- subset(SummaryInd, select = -c(age.y,species.y) )
+SummaryInd <- merge(SummaryInd, accessory, by.x=c("individual"), by.y=c("individual"))
+SummaryInd <- subset(SummaryInd, select = -c(age,species) )
+SummaryInd <- merge(SummaryInd, harvest, by.x=c("individual"), by.y=c("individual"))
+#problem here, because duplicates number of entries
+SummaryInd <- subset(SummaryInd, select = -c(age.x,species.x) )
+
+#adding variables to look at change across years
+SummaryInd$change_shoot_diam <- SummaryInd$d_end - SummaryInd$d_start
+SummaryInd$change_basal_diam <- SummaryInd$FinalBasalDiam - SummaryInd$StartBasalDiam
+SummaryInd$change_shoot_area <- (3.14*((SummaryInd$d_end/2)^2)) - (3.14*((SummaryInd$d_start/2)^2))
+SummaryInd$change_basal_area <- (3.14*((SummaryInd$FinalBasalDiam/2)^2)) - (3.14*((SummaryInd$StartBasalDiam/2)^2))
+SummaryInd$lvs_end_total <- SummaryInd$lvs_end + SummaryInd$lvs_new
 ```
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-#adding leaf, stem weight data from InvestmentSummary to raw_leaf_lifespan dataframe; can't RUN LINES 95-108 UNTIL INVESTMENT SUMMARY OPEN - THEN PROBLEM WITH PLYR
-#raw_leaf_lifespan <- left_join(raw_leaf_lifespan, InvestmentSummary, by = "individual")
+#summarizing data by species, age
 
-#adding columns to raw_leaf_lifespan to look at change across year
-raw_leaf_lifespan$change_shoot_diam <- raw_leaf_lifespan$d_end - raw_leaf_lifespan$d_start
-#raw_leaf_lifespan$change_basal_diam <- raw_leaf_lifespan$FinalBasalDiam - raw_leaf_lifespan$StartBasalDiam
-raw_leaf_lifespan$change_shoot_area <- (3.14*((raw_leaf_lifespan$d_end/2)^2)) - (3.14*((raw_leaf_lifespan$d_start/2)^2))
-#raw_leaf_lifespan$change_basal_area <- (3.14*((raw_leaf_lifespan$FinalBasalDiam/2)^2)) - (3.14*((raw_leaf_lifespan$StartBasalDiam/2)^2))
-
-#removng crazy numbers; probably better to do this for each analysis than overall, because removing indiviiduals from all three at once
-#raw_leaf_lifespan <- subset(raw_leaf_lifespan,LL_bd>0)
-#raw_leaf_lifespan <- subset(raw_leaf_lifespan,LL_bd<6)
-#raw_leaf_lifespan <- subset(raw_leaf_lifespan,LL_birth<8)
-#raw_leaf_lifespan <- subset(raw_leaf_lifespan,LL_death<8)
-
-#creating summary files
 #leaf lifespan summary by species, age
-LLSummary <- raw_leaf_lifespan %>%
+LL_summary <- SummaryInd %>%
   filter(LL_bd>0 & LL_bd<6 & LL_birth<8 & LL_death<8) %>%
   group_by(species, age) %>%
-  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length, lvs_end, lvs_end_total)
+  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length, lvs_end, lvs_end_total, change_shoot_diam, change_basal_diam, change_shoot_area, change_basal_area)
+
+#LMA summary by species, age
+LMA_summary <- LMA %>%
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), LMA)
+names(LMA_summary)<-c("species","age","LMA_mean","LMA_se","LMA_length")
+
+#accessory tissue summary by species, age
+accessory_summary <- accessory %>%
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), PrePol_A, PrePol_S, PostPol_A, PD, Prop)
+
+#investment summary by species, age
+investment_summary <- investment %>%
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), GrowthInv, FinalWeight, FinalBasalDiamAv, TotalInvestment, RA)
+
+#harvest summary by species, age
+harvest_summary <- harvest %>%
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), total_stem_weight, total_leaf_weight, height)
+
+#RA for each species/age combination                 
+maxRA <- investment %>%
+  group_by(species, age) %>%
+  summarise_each(funs(max), RA)
+names(maxRA)<-c("species","age","maxRA")
+
+#maximum H for each species/age combination                 
+maxH <- harvest %>%
+  group_by(species, age) %>%
+  summarise_each(funs(max), height)
+names(maxH)<-c("species","age","maxH")
 
@@
 #leaf lifespan summary by species
-LL_spp <- raw_leaf_lifespan %>%
+LL_spp <- leafLifespan %>%
   filter(age>2) %>%
@@
 
-#merge LMA, wood density, seed size data into LLSummary dataframe
-LLSummary <- merge(LLSummary, LMA_summary, by.x=c("species","age"), by.y=c("species","age"))
-LLSummary <- merge(LLSummary, Wood_summary, by.x=c("species"), by.y=c("species"))
-LLSummary <- merge(LLSummary, seedsize, by.x=c("species"), by.y=c("species"))
-LL_spp <- merge(LL_spp, LMA_spp, by.x=c("species"), by.y=c("species"))
-LL_spp <- merge(LL_spp, Wood_summary, by.x=c("species"), by.y=c("species"))
-LL_spp <- merge(LL_spp, seedsize, by.x=c("species"), by.y=c("species"))
-#still to add, max H from Investment data, absolute and relative growth measures
+#maximum height for each species
+MaxH_spp <- harvest %>%
+  group_by(species) %>%
+  summarise_each(funs(max), height)
+names(LMA_spp)<-c("species", "maxH_spp")
+
+SummaryInd <- merge(SummaryInd,Wood_summary, by.x=c("species"), by.y=c("species"))
+SummaryInd <- merge(SummaryInd,LMA_summary, by.x=c("species","age"), by.y=c("species","age"))
+SummaryInd <- merge(SummaryInd,MaxH_spp, by.x=c("species"), by.y=c("species"))
+SummaryInd <- merge(SummaryInd,seedsize, by.x=c("species"), by.y=c("species"))
+#TO DO: REMOVE DUPLICATE COLUMNS FOR AGE and SPECIES
+
+#merge various data summaries into SummarySppAge dataframe
+SummarySppAge <- merge(LL_summary, LMA_summary, by.x=c("species","age"), by.y=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, Wood_summary, by.x=c("species"), by.y=c("species"))
+SummarySppAge <- merge(SummarySppAge, seedsize, by.x=c("species"), by.y=c("species"))
+SummarySppAge <- merge(SummarySppAge, MaxH_spp, by.x=c("species"), by.y=c("species"))
+SummarySppAge <- merge(SummarySppAge, maxH, by.x=c("species","age"), by.y=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, investment_summary, by.x=c("species","age"), by.y=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, accessory_summary, by.x=c("species","age"), by.y=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, harvest_summary, by.x=c("species","age"), by.y=c("species","age"))
+#TO DO: REMOVE DUPLICATE COLUMNS FOR AGE
+
+#merge various data summaries into SummarySpp dataframe
+SummarySpp <- merge(LL_spp, LMA_spp, by.x=c("species"), by.y=c("species"))
+SummarySpp <- merge(SummarySpp, Wood_summary, by.x=c("species"), by.y=c("species"))
+SummarySpp <- merge(SummarySpp, seedsize, by.x=c("species"), by.y=c("species"))
+SummarySpp <- merge(SummarySpp, maxH, by.x=c("species"), by.y=c("species"))
+
+#WONDERING IF I SHOULD AT THIS POINT HAVE THE DATA FRAME CALLED "sUMMARYINDIVIDUAL" INSTEAD, SINCE NOW CONTAINS FAR MORE THAN LL DATA
 
@@
 labels.age <- c("1.4","2.4","5","7","9","32")
-
-#LL vs LMA
-#remove HATE, babies
-#instead of separate dataframes, can probably incorporate this information directly into plotting and analysis commands
-#LL_nobabies <- subset(raw_leaf_lifespan, age>2)
-#LMA_nobabies <- subset(LMA, age>2)
-#LL_noHate <- subset(LLSummary, species != "HATE")
-#LL_noHatebabies <- subset(LL_nobabies, species != "HATE")
-```
-
-# relationship between LMA, LL by age, species
-
-For 7 year old plants
-```{r, echo=FALSE}
-plot(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==7), xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA", las=1, pch=16)
-text(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==7), labels=species, pos=1, offset=-0.9, cex=0.9,col="blue")
-text(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==7 & species=="HATE"), labels=species, pos=1, offset=-0.9, cex=0.9,col="red")
-mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,species!="HATE" & age==7))
-summary(mod)
-abline(mod)
+names(labels.age) <- c("1.4","2.4","5","7","9","32")
 ```
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(change_basal_diam ~ leaf_new_total, raw_leaf_lifespan, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in basal diameter")
+plot(change_basal_diam ~ lvs_end_total, SummaryInd, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in basal diameter")
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <- lm(log(leaf_new_total) ~ log(change_basal_diam+1) + species +age, raw_leaf_lifespan)
+mod <- lm(log(lvs_end_total) ~ log(change_basal_diam+1) + species +age, SummaryInd)
 summary(mod)
 
-plot(change_shoot_diam ~ leaf_new_total, raw_leaf_lifespan, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in diameter of leader")
+plot(change_shoot_diam ~ lvs_end_total, SummaryInd, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in diameter of leader")
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <- lm(log(leaf_new_total) ~ log(change_shoot_diam+10) + species +age, data= subset(raw_leaf_lifespan, !is.na(change_shoot_diam)))
+mod <- lm(log(lvs_end_total) ~ log(change_shoot_diam+10) + species +age, data= subset(SummaryInd, !is.na(change_shoot_diam)))
 summary(mod)
@@
 #LL vs LMA using species by site means
-
 Overall plot shows a lack of relationship when HATE included. This is because it has such a high LMA. The youngest and oldest plants have no pattern, presumably because LL data are inaccurate
@@
 labels.LMA <-c("all except HATE","age 1.4", "age 2.4", "age 5", "age 7", "age 9", "age 32", "including HATE")
-plot(LL_birth_mean ~ LMA_mean, LLSummary, type="n", xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1,pch=17, log="xy")
-points(LL_birth_mean ~ LMA_mean, data=subset(LLSummary, species!="HATE"), pch=16, cex=1.2, col=col.age[as.factor(age)])
-points(LL_birth_mean ~ LMA_mean, col="red", data=subset(LLSummary, species=="HATE"), pch=17)
+plot(LL_birth_mean ~ LMA_mean, SummarySppAge, type="n", xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1,pch=17, log="xy")
+points(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE"), pch=16, cex=1.2, col=col.age[as.factor(age)])
+points(LL_birth_mean ~ LMA_mean, col="red", data=subset(SummarySppAge, species=="HATE"), pch=17)
 #need log transformation to get these to plot onto axes
-mod <- lm(LL_birth_mean ~ LMA_mean, LLSummary)
+mod <- lm(LL_birth_mean ~ LMA_mean, SummarySppAge)
 abline(mod, col="red", lty=2)
-mod_no_HATE <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary, species!="HATE"))
+mod_no_HATE <- lm(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE"))
 abline(mod_no_HATE, lwd=2)
-mod_no_HATE5 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==5&species!="HATE"))
-abline(mod_no_HATE5, col="light green", lwd=1.5)
-mod_no_HATE7 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==7&species!="HATE"))
-abline(mod_no_HATE7, col="orange", lwd=1.5)
-mod_no_HATE9 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==9&species!="HATE"))
-abline(mod_no_HATE9, col="blue", lwd=1.5)
-mod_no_HATE2.4 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==2.4&species!="HATE"))
-abline(mod_no_HATE2.4, col="pink", lwd=1.5)
-mod_no_HATE1 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age<2.4&species!="HATE"))
-abline(mod_no_HATE1, col="purple", lwd=1.5)
-mod_no_HATE32 <- lm(LL_birth_mean ~ LMA_mean, data=subset(LLSummary,age==32&species!="HATE"))
-abline(mod_no_HATE32, col="light blue", lwd=1.5)
+legend("bottomright",col=col.LMA, labels.LMA, pch=16, cex=1.4)
+summary(mod_no_HATE)
 
-legend("bottomright",col=col.LMA, labels.LMA, pch=16, cex=1.4)
+#plot_by_age <- function(age) {
+#  mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==age&species!="HATE")
+#  abline(mod, col=col.age[age], lwd=1.5)
+#}
+
+#for(n in names(labels.age)) {
+#  plot_by_age(n)
+#}
+
+# Relationship between LMA, LL for 7 year old plants
+# There would be a similar plot for any other age as well. As with the overall LMA analyses, HATE needs to be removed.
+
+plot(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==7), xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA", las=1, pch=16)
+text(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-0.9, cex=0.9,col="blue")
+text(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==7 & species=="HATE"), labels=species, pos=1, offset=-0.9, cex=0.9,col="red")
+mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,species!="HATE" & age==7))
 summary(mod)
+abline(mod)
 ```
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-mod <- lm(LL_birth ~ age + species +age*species, data=subset(raw_leaf_lifespan,age>3 & LL_birth!="Inf"))
+mod <- lm(LL_birth ~ age + species +age*species, data=subset(SummaryInd,age>3 & LL_birth!="Inf"))
 summary(mod)
@@
 #WHY ARE THE FOLLOWING TWO LINES OF CODE NEEDED?
-raw_leaf_lifespan %>% group_by(species) %>%
+leafLifespan %>% group_by(species) %>%
     summarise(mean(LL_birth))
@@
 plot_LLvAge <- function(spp) {
-  plot(LL_birth ~ age, data=subset(raw_leaf_lifespan,species==spp), xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
+  plot(LL_birth ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
      main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
-  points(LL_birth_mean ~ age, data=subset(LLSummary, species==spp), cex=1.3, pch=8)
-  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=25)
-  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=24)
+  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
+  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
+  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
 }
@@
 ```{r, echo=FALSE, message=FALSE}
-#plot(LMA_mean ~ as.factor(species), data=subset(LLSummary,age>3), xlab="species", ylab="LMA", cex.axis=.8, las=1)
+#plot(LMA_mean ~ as.factor(species), data=subset(SummarySppAge,age>3), xlab="species", ylab="LMA", cex.axis=.8, las=1)
 #mod <- lm(LMA ~ age +species + age*species, LMA)
@@
   main=labels.spp[spp])
-  points(LMA_mean ~ age, data=subset(LLSummary, species==spp), cex=1.3, pch=8)
-  points((LMA_mean+LMA_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=25)
-  points((LMA_mean-LMA_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=24)
+  points(LMA_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
+  points((LMA_mean+LMA_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
+  points((LMA_mean-LMA_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
+  }
   #I want to add a line of code that plots over the means for each age. I did this above by calling in another file, but wondering about on-the-spot calculations
-}
 
@@
 }
-
 ```
@@
 plot_lfcountvAge <- function(spp) {
-  plot(lvs_end_total ~ age, data=subset(raw_leaf_lifespan,species==spp), xlab="age", ylab="leaf count along shoot", cex.axis=.8, las=1, pch=16, log="x",
+  plot(lvs_end_total ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leaf count along shoot", cex.axis=.8, las=1, pch=16, log="x",
   main=labels.spp[spp])
-  points(lvs_end_total_mean ~ age, data=subset(LLSummary, species==spp), cex=1.3, pch=8)
-  points((lvs_end_total_mean+lvs_end_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=25)
-  points((lvs_end_total_mean-lvs_end_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=24)
+  points(lvs_end_total_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
+  points((lvs_end_total_mean+lvs_end_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
+  points((lvs_end_total_mean-lvs_end_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
 }
@@
 mod_lfcountvAge <- function(spp) {
-  lm(lvs_end ~ age, data=subset(raw_leaf_lifespan,age>2.4 & species==spp))
+  lm(lvs_end ~ age, data=subset(SummaryInd,age>2.4 & species==spp))
 }
@@
 plot_newlengthvAge <- function(spp) {
-  plot(new_length ~ age, data=subset(raw_leaf_lifespan,species==spp), xlab="age", ylab="leader shoot extention", cex.axis=.8, las=1, pch=16, log="x",
+  plot(new_length ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leader shoot extention", cex.axis=.8, las=1, pch=16, log="x",
   main=labels.spp[spp])
-  points(new_length_mean ~ age, data=subset(LLSummary, species==spp), cex=1.3, pch=8)
-  points((new_length_mean+new_length_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=25)
-  points((new_length_mean-new_length_se) ~ age, data=subset(LLSummary, species==spp), cex=1.5, pch=24)
+  points(new_length_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
+  points((new_length_mean+new_length_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
+  points((new_length_mean-new_length_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
 }
@@
 mod_newlengthvAge <- function(spp) {
-  lm(new_length ~ age, data=subset(raw_leaf_lifespan,age>2.4 & species==spp))
+  lm(new_length ~ age, data=subset(SummaryInd,age>2.4 & species==spp))
 }
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(change_shoot_area~new_length,data=subset(raw_leaf_lifespan,change_shoot_area<1000000), log="xy",col=col.age[as.factor(age)], pch=16, cex=.8, xlab="shoot extension (mm)", ylab="increased shoot cross sectional area")
+plot(change_shoot_area~new_length,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8, xlab="shoot extension (mm)", ylab="increased shoot cross sectional area")
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <- lm(change_shoot_area~new_length +age,data=subset(raw_leaf_lifespan,change_shoot_area<1000000))
+mod <- lm(change_shoot_area~new_length +age,data=subset(SummaryInd,change_shoot_area<1000000))
 summary(mod)
 
-raw_leaf_lifespan$lvs_end_total <- raw_leaf_lifespan$lvs_end + raw_leaf_lifespan$lvs_new
-plot(lvs_end_total~lvs_start,raw_leaf_lifespan, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8, xlab="starting leaf count", ylab="ending leaf count")
+plot(lvs_end_total~lvs_start,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8, xlab="starting leaf count", ylab="ending leaf count")
 
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <- lm(lvs_start~lvs_end_total+age +age*lvs_end_total, raw_leaf_lifespan)
+mod <- lm(lvs_start~lvs_end_total+age +age*lvs_end_total, SummaryInd)
 summary(mod)
@@
 
-plot(LL_birth_mean~LMA_mean,data=subset(LLSummary,species!="HATE"),col=col.age[as.factor(age)], pch=16, cex=.8, log="xy",xlab="LMA", ylab="leaf lifespan (calculated from leaf births")
-points(LL_birth_mean~LMA_mean,data=subset(LLSummary,species=="HATE"),col="red", pch=19, cex=.8)
+plot(LL_birth_mean~LMA_mean,data=subset(SummarySppAge,species!="HATE"),col=col.age[as.factor(age)], pch=16, cex=.8, log="xy",xlab="LMA", ylab="leaf lifespan (calculated from leaf births")
+points(LL_birth_mean~LMA_mean,data=subset(SummarySppAge,species=="HATE"),col="red", pch=19, cex=.8)
+```

### 2015-03-25 leaflifespan.Rmd
-adding column to individuals indicating whether each individual is reproductively mature for easy subsetting -continued work on script

@@
 - total biomass
-- leaf mass (calculations not yet done)
-- leaf area (calculations not yet done)
+- leaf mass
+- leaf area
 - stem biomass (calculations not yet done)
@@
 SummaryInd <- merge(SummaryInd,seedsize, by.x=c("species"), by.y=c("species"))
-#TO DO: REMOVE DUPLICATE COLUMNS FOR AGE and SPECIES
+SummaryInd$leafArea <- SummaryInd$total_leaf_weight * SummaryInd$LMA_mean
+#TO DO: REMOVE DUPLICATE COLUMNS FOR AGE and SPECIES MORE ELEGANTLY
+#TO DO: REMOVE COLUMNS I DON'T NEED
 
@@
 ```
+
+#beginning with a large number of regressions to look for general pattern across variables
+A few stand out, noticeably that growth at the shoot level and whole plant level are well-correlated, indicating that a plant, even old ones, are distributing their available energy evenly to all shoots
+Also, max height and LMA (at a species*age level) are well correlated, There is obviously a strong effect of age, since older plants are taller.
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+pairs(SummarySppAge[c("RA_mean", "GrowthInv_mean", "Prop_mean", "LL_birth_mean","LL_death_mean","new_length_mean", "change_shoot_area_mean","change_basal_area_mean","LMA_mean","WD_mean","seed_size","maxH")], log="xy")
+
+plot(maxH ~ LMA_mean,SummarySppAge,log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(LMA_mean~maxH+age,data=subset(SummarySppAge,species!="PEPU"))
+summary(mod)
+
+plot(maxH ~ LMA_mean,SummarySppAge,log="xy",col=col.spp[as.factor(species)],pch=16,cex=.7)
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+
+plot(GrowthInv_mean ~ LMA_mean,SummarySppAge,log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(LMA_mean~GrowthInv+age,data=subset(SummarySppAge,species!="PEPU"))
+summary(mod)
+```
+
+#Plots of interest to Anais' analyses
+The following plots look at the correlation between growth (absolute growth in this case) versus LMA, wood density, maxH (at that age), and seed size.
+
+They show,
+for LMA: slight positive correlation for youngest plants, no correlation for intermediate plants, strong positive correlation for adult plants
+for wood density: no correlation for yougest plants, intermediate plants, but strong negative correlation for adult plants
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(LMA_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age==1.4))
+summary(mod)
+
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(LMA_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age==2.4))
+summary(mod)
+
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(LMA_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age>3))
+summary(mod)
+
+plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(WD_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age==1.4))
+summary(mod)
+
+plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(WD_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age==2.4))
+summary(mod)
+
+plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(WD_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age>3))
+summary(mod)
+
+plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(seed_size~GrowthInv_mean+age,data=subset(SummarySppAge,age==1.4))
+summary(mod)
+
+plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(seed_size~GrowthInv_mean+age,data=subset(SummarySppAge,age==2.4))
+summary(mod)
+
+plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(seed_size~GrowthInv_mean+age,data=subset(SummarySppAge,age>3))
+summary(mod)
+
+plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(maxH~GrowthInv_mean,data=subset(SummarySppAge,age==1.4))
+summary(mod)
+
+plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(maxH~GrowthInv_mean,data=subset(SummarySppAge,age==2.4))
+summary(mod)
+
+plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod<-lm(maxH~GrowthInv_mean+age,data=subset(SummarySppAge,age>3))
+summary(mod)
+```

### 2015-03-25 R/ReproductionAllocation.R
Change variable name tag_ID -> individual (cases missed in earlier commit)

@@ -35,7 +35,7 @@ RA_Calculations <- function(thisSpecies, Species_Investment, HarvestData, Maps, 
   DiameterData <- DiameterData[!is.na(DiameterData$EstWeight), ]
 
   ### Calculate change in the weight, i.e., Growth Investement
-  GrowthInv <- data.frame(tag_ID = c(), GrowthInv = c(), StartWeight = c(), FinalWeight = c(), StartBasalDiamAv = c(), FinalBasalDiamAv = c(), age = c())
+  GrowthInv <- data.frame(individual = c(), GrowthInv = c(), StartWeight = c(), FinalWeight = c(), StartBasalDiamAv = c(), FinalBasalDiamAv = c(), age = c())
   for (i in 1:length(unique(DiameterData$individual))) {
     end <- "end"
     individual <- unique(DiameterData$individual)[i]
@@ -44,7 +44,7 @@ RA_Calculations <- function(thisSpecies, Species_Investment, HarvestData, Maps, 
       print(paste0("Incorrect number of measurments for ", individual))
     }
     if (nrow(IndData) == 2) {
-      GrowthInv[i, "tag_ID"] <- individual
+      GrowthInv[i, "individual"] <- individual
       GrowthInv[i, "age"] <- unique(IndData$age)
       GrowthInv[i, "GrowthInv"] <- IndData[IndData$start_end == end, "EstWeight"] - IndData[IndData$start_end == "start", "EstWeight"]
       GrowthInv[i, "StartWeight"] <- IndData[IndData$start_end == "start", "EstWeight"]
@@ -59,26 +59,26 @@ RA_Calculations <- function(thisSpecies, Species_Investment, HarvestData, Maps, 
   ### Use saved data to calculate total reproduction investment per individual plant
   InvSpecies <- Species_Investment$Investment
 
-  RepoInv <- data.frame(tag_ID = c(), ReproInv = c())
+  RepoInv <- data.frame(individual = c(), ReproInv = c())
   for (individual in unique(InvSpecies$Individual)) {
       InvIndividual <- InvSpecies[InvSpecies$Individual == individual, ]
-      RepoInv <- rbind(RepoInv, data.frame(tag_ID = individual, ReproInv = c(sum(InvIndividual$Total))))
[…]

### 2015-03-25 leaflifespan.Rmd
Change variable name tag_ID -> individual (cases missed in earlier commit)
continud work on script

@@
 - sites that are aged 1.35 vs 1.4 years
+
+technical:
+-parts remake not working
+-tag_ID still exists in 1 file
+-avoiding duplicate columns with name "age" "species" (how to subset columns that are merged, how to delete columns)
+-getting model summaries to show up when looping through species/ages
 
@@
 harvest_summary <- harvest %>%
-  group_by(species, age) %>%
+  group_by(species, age2) %>%
   summarise_each(funs(mean, se, length), total_stem_weight, total_leaf_weight, height)
@@
 
-plot(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==7), xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA", las=1, pch=16)
-text(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-0.9, cex=0.9,col="blue")
-text(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==7 & species=="HATE"), labels=species, pos=1, offset=-0.9, cex=0.9,col="red")
-mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,species!="HATE" & age==7))
+plot(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==5), xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA", las=1, pch=16)
+text(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-0.9, cex=0.9,col="blue")
+text(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,age==5 & species=="HATE"), labels=species, pos=1, offset=-0.9, cex=0.9,col="red")
+mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge,species!="HATE" & age==5))
 summary(mod)
@@
 
-#where does the [spp] comes from? This is the first place in the script it is used like this - I assume it could be any name?
 plot_LLvAge <- function(spp) {
@@
 
-#plots regressing variables against one another
+#models looking at how the relationship between leaf weight (or area) and total plant weight shifts with age
+this should be another way to get at the decreasing "leafiness" of plants with age
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod <-lm(FinalWeight~leaf_weight+age+species,SummaryInd)
+summary(mod)
+
+plot_LeafWeight <- function(spp) {
+  plot(leaf_weight~FinalWeight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
+  legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+  mod <-lm(FinalWeight~leaf_weight+age,data=subset(SummaryInd,species==spp))
+  abline(mod)
+  summary(mod)
+}
+
+for(n in names(labels.spp)) {
+  plot_LeafWeight(n)
+
+#plot looking at leaf area versus plant weight
+#USE THIS PLOT IN LAB MEETING - CLEARLY SHOWS DECLINE IN INTERCEPT WITH AGE  
+plot(leafArea~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod <-lm(FinalWeight~leafArea+age+species,SummaryInd)
+summary(mod)
+
+plot_LeafArea <- function(spp) {
+  plot(leafArea~FinalWeight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
+  legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+  mod <-lm(FinalWeight~leafArea+age,data=subset(SummaryInd,species==spp))
+  abline(mod)
+  summary(mod)
+}
+
+for(n in names(labels.spp)) {
+  plot_LeafArea(n)
+}
+
+#plots looking at shoot extension versus plant size
+plot(new_length~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod <-lm(FinalWeight~new_length+age+species,SummaryInd)
+summary(mod)
+
+plot_LeaderExtension <- function(spp) {
+  plot(new_length~FinalWeight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
+  legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+  mod <-lm(FinalWeight~new_length+age,data=subset(SummaryInd,species==spp))
+  abline(mod)
+  summary(mod)
+}
+
+for(n in names(labels.spp)) {
+  plot_LeaderExtension(n)
+} 
+```
+
+#many plots regressing variables against one another
 ```{r, echo=FALSE,results='hide', message=FALSE}

### 2015-03-26 talk.Rmd
build talk in remake

---
title: "Untitled"
output:
     pdf_document:
       toc: true
       highlight: zenburn
     html_document:
       toc: true
       theme: united
---

# file names

- leaf_counts is file with calculated leaf counts and leaf lifespan data
- SummarySppAge is file with means of LL - and other variables - by species and age; LMA data is merged to this file
- subsets of SummarySppAge are created to omit babies or HATE for various analyses

### 2015-03-26 leaflifespan.Rmd
work on scripts

@@
 Then this becomes the file where variables are summarized, plotted analyzed.
-- make sure regressions exist (or are done), to separately look at leaf and stem biomass
+- add final leaf and stem biomass output to "investment" output file
 - seed weight vs. propagule weight dilemma
-- sites that are aged 1.35 vs 1.4 years
 
@@
 
+#data to check
+- HATE outlier in LL
+
 ```{r, echo=FALSE,results='hide', message=FALSE}
@@
 create_bindings()
+```
 
-LMA <- filter(LMA_raw, species!="" & species!=" ")
+```{r, echo=FALSE,results='hide', message=FALSE}
+LMA <- filter(LMA_raw, species!="" & species!=" ") %>%
+  select(species,age,LMA)
 
-wood <- filter(woodDensity_raw, use=="use")
+wood <- filter(woodDensity_raw, use=="use") %>%
+  select(species,density)
 
-seedsize <- seedSize_raw
+seedsize <- seedSize_raw %>%
+  select(species,seed_size)
 
-harvest <- filter(HarvestData, use_status=="use" & segment==1 & start_end=="end")
+harvest <- filter(HarvestData, use_status=="use" & segment==1 & start_end=="end") %>%
+  select(species,individual,age,age2,height,total_leaf_weight,site)
 
 investment <- ReproductionAllocation_all
-names(investment) <- c("individual","ReproInv","age","GrowthInv","StartWeight","FinalWeight","StartBasalDiamAv","FinalBasalDiamAv","TotalInvestment","RA","species")
-#still have tagId as label
-#remaking this from scratch
+investment$age2 <- investment$age
+investment$age <- round(investment$age, digits=1)
 
 accessory <- AccessoryCosts_all
+accessory$age2 <- accessory$age
+accessory$age <- round(accessory$age, digits=1)
+#accessory$PerAccessory <- {
+#  select(accessory, Total >0,
+#  1 - (accessory$Prop/accessory$Total)
+#}
 
-leafLifespan <- filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use")
+#accessory$PerPropagule = 1 - accessory$PerAccessory
+
+leafLifespan <- filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use") %>%
+  select(species,age,individual,d_start,d_end,length_start,new_length,lvs_start_length,lvs_start_count,lvs_end_length,lvs_end_count,lvs_new_length,lvs_new_count,new_but_shed_count,mm_lvs_spec,count_lvs_spec)
+
 leafLifespan$individual <- as.factor(leafLifespan$individual)
+leafLifespan$species <- as.factor(leafLifespan$species)
+
 #loading this column as character, so using this for now
@@
 leaf_lifespan_temp <- leafLifespan %>%
-              select(species,age,site,individual,d_start,d_end,length_start,new_length,segment,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)
+              select(species,age,individual,d_start,d_end,length_start,new_length,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)
 
@@
 #adding investment and accessory costs data to leafLifespan dataframe to create a dataframe with all individual level data
-#SummaryInd <- left_join(leafLifespan, investment, by = "individual")
-#SummaryInd <- left_join(SummaryInd, accessory, by = "individual")
-#SummaryInd <- left_join(SummaryInd, harvest, by = "individual")
-#not sure why the above text isn't working... using merge instead
-
-SummaryInd <- merge(leafLifespan, investment, by.x=c("individual"), by.y=c("individual"))
-SummaryInd <- subset(SummaryInd, select = -c(age.y,species.y) )
-SummaryInd <- merge(SummaryInd, accessory, by.x=c("individual"), by.y=c("individual"))
-SummaryInd <- subset(SummaryInd, select = -c(age,species) )
-SummaryInd <- merge(SummaryInd, harvest, by.x=c("individual"), by.y=c("individual"))
-#problem here, because duplicates number of entries
-SummaryInd <- subset(SummaryInd, select = -c(age.x,species.x) )
+SummaryInd <- merge(leafLifespan, select(investment, -species, -age), by="individual")
+SummaryInd <- merge(SummaryInd, select(accessory, -species, -age, -age2), by="individual")
+SummaryInd <- merge(SummaryInd, select(harvest, -species, -age, -age2), by="individual")
 
@@
 ```
-
-#TODO: Check outlier for HATE
 
@@
 harvest_summary <- harvest %>%
-  group_by(species, age2) %>%
-  summarise_each(funs(mean, se, length), total_stem_weight, total_leaf_weight, height)
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), height,total_leaf_weight)
+#names(harvest_summary)<-c("species","age","height_mean","height_se","height_length")
 
@@
 #wood density summary by species
-Wood_summary <- wood %>%
+wood_summary <- wood %>%
   group_by(species) %>%
   summarise_each(funs(mean, se, length), density)
-names(Wood_summary)<-c("species","WD_mean","WD_se","WD_length")
+names(wood_summary)<-c("species","WD_mean","WD_se","WD_length")
 
@@
 #maximum height for each species
-MaxH_spp <- harvest %>%
+maxH_spp <- harvest %>%
   group_by(species) %>%
   summarise_each(funs(max), height)
-names(LMA_spp)<-c("species", "maxH_spp")
+names(maxH_spp)<-c("species", "maxH_spp")
 
-SummaryInd <- merge(SummaryInd,Wood_summary, by.x=c("species"), by.y=c("species"))
-SummaryInd <- merge(SummaryInd,LMA_summary, by.x=c("species","age"), by.y=c("species","age"))
-SummaryInd <- merge(SummaryInd,MaxH_spp, by.x=c("species"), by.y=c("species"))
-SummaryInd <- merge(SummaryInd,seedsize, by.x=c("species"), by.y=c("species"))
+SummaryInd <- merge(SummaryInd,wood_summary, by=c("species"))
+SummaryInd <- merge(SummaryInd,LMA_summary, by=c("species","age"))
+SummaryInd <- merge(SummaryInd,maxH_spp, by=c("species"))
+SummaryInd <- merge(SummaryInd,seedsize, by=c("species"))
+
 SummaryInd$leafArea <- SummaryInd$total_leaf_weight * SummaryInd$LMA_mean
-#TO DO: REMOVE DUPLICATE COLUMNS FOR AGE and SPECIES MORE ELEGANTLY
-#TO DO: REMOVE COLUMNS I DON'T NEED
 
 #merge various data summaries into SummarySppAge dataframe
-SummarySppAge <- merge(LL_summary, LMA_summary, by.x=c("species","age"), by.y=c("species","age"))
-SummarySppAge <- merge(SummarySppAge, Wood_summary, by.x=c("species"), by.y=c("species"))
-SummarySppAge <- merge(SummarySppAge, seedsize, by.x=c("species"), by.y=c("species"))
-SummarySppAge <- merge(SummarySppAge, MaxH_spp, by.x=c("species"), by.y=c("species"))
-SummarySppAge <- merge(SummarySppAge, maxH, by.x=c("species","age"), by.y=c("species","age"))
-SummarySppAge <- merge(SummarySppAge, investment_summary, by.x=c("species","age"), by.y=c("species","age"))
-SummarySppAge <- merge(SummarySppAge, accessory_summary, by.x=c("species","age"), by.y=c("species","age"))
-SummarySppAge <- merge(SummarySppAge, harvest_summary, by.x=c("species","age"), by.y=c("species","age"))
-#TO DO: REMOVE DUPLICATE COLUMNS FOR AGE
+SummarySppAge <- merge(LL_summary, LMA_summary, by=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, wood_summary, by=c("species"))
+SummarySppAge <- merge(SummarySppAge, seedsize, by=c("species"))
+SummarySppAge <- merge(SummarySppAge, maxH_spp, by=c("species"))
+SummarySppAge <- merge(SummarySppAge, maxH, by=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, investment_summary, by=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, accessory_summary, by=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, harvest_summary, by=c("species","age"))
 
 #merge various data summaries into SummarySpp dataframe
-SummarySpp <- merge(LL_spp, LMA_spp, by.x=c("species"), by.y=c("species"))
-SummarySpp <- merge(SummarySpp, Wood_summary, by.x=c("species"), by.y=c("species"))
-SummarySpp <- merge(SummarySpp, seedsize, by.x=c("species"), by.y=c("species"))
-SummarySpp <- merge(SummarySpp, maxH, by.x=c("species"), by.y=c("species"))
-
-#WONDERING IF I SHOULD AT THIS POINT HAVE THE DATA FRAME CALLED "sUMMARYINDIVIDUAL" INSTEAD, SINCE NOW CONTAINS FAR MORE THAN LL DATA
+SummarySpp <- merge(LL_spp, LMA_spp, by=c("species"))
+SummarySpp <- merge(SummarySpp, wood_summary, by=c("species"))
+SummarySpp <- merge(SummarySpp, seedsize, by=c("species"))
+SummarySpp <- merge(SummarySpp, select(maxH, -age), by=c("species"))
 
@@
 names(labels.age) <- c("1.4","2.4","5","7","9","32")
-```
-
-# Plotting final leaf number on the leader by diameter increase of the entire plant (basal diameter) and the leader (shoot diameter).
-
-Both show a strong correlation and species effect as expected.
-For the model with basal diameter there is a strong age effect, but not for shoot diameter.
-This is presumably because a shoot of a given species should always deploy the same number of leaves for the same diameter increase.
-In contrast, the whole plant will have many differing shoot numbers with age, so differing effects of a single shoot's increased diameter.
-Strangely, the model with basal diameter shows a stronger effect between diameter increase and leaf number.
-
-```{r, echo=FALSE,results='hide', message=FALSE}
-plot(change_basal_diam ~ lvs_end_total, SummaryInd, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in basal diameter")
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <- lm(log(lvs_end_total) ~ log(change_basal_diam+1) + species +age, SummaryInd)
-summary(mod)
-
-plot(change_shoot_diam ~ lvs_end_total, SummaryInd, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in diameter of leader")
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <- lm(log(lvs_end_total) ~ log(change_shoot_diam+10) + species +age, data= subset(SummaryInd, !is.na(change_shoot_diam)))
-summary(mod)
 ```
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-mod <- lm(LL_birth ~ age + species +age*species, data=subset(SummaryInd,age>3 & LL_birth!="Inf"))
+plot(LL_birth~age,SummaryInd,log="xy", xlab="age",ylab="leaf lifespan (based on leaf births",col=col.spp[as.factor(species)])
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+
+mod <- lm(LL_birth ~ age + species, data=subset(SummaryInd,age>3 & LL_birth!="Inf"))
 summary(mod)
@@
 #summary(mod)
+
+plot(LMA_mean~age,SummarySppAge,log="xy", xlab="age",ylab="LMA",col=col.spp[as.factor(species)],pch=16)
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
 
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
+plot(lvs_end_total~age,SummaryInd,log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+mod <- lm(lvs_end_total~age+species+age*species,SummaryInd)
+summary(mod)
 
@@
 
-#models looking at how the relationship between leaf weight (or area) and total plant weight shifts with age
+# Plotting final leaf number on the leader by diameter increase of the entire plant (basal diameter) and the leader (shoot diameter).
+
+Both show a strong correlation and species effect as expected.
+For the model with basal diameter there is a strong age effect, but not for shoot diameter.
+This is presumably because a shoot of a given species should always deploy the same number of leaves for the same diameter increase.
+In contrast, the whole plant will have many differing shoot numbers with age, so differing effects of a single shoot's increased diameter.
+Strangely, the model with basal diameter shows a stronger effect between diameter increase and leaf number.
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(change_basal_diam ~ lvs_end_total, SummaryInd, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in basal diameter")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod <- lm(log(lvs_end_total) ~ log(change_basal_diam+1) + species +age, SummaryInd)
+summary(mod)
+
+plot(change_shoot_diam ~ lvs_end_total, SummaryInd, log="xy", col=col.age[as.factor(age)], pch=16, xlab="leaf number on leader", ylab="change in diameter of leader")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod <- lm(log(lvs_end_total) ~ log(change_shoot_diam+10) + species +age, data= subset(SummaryInd, !is.na(change_shoot_diam)))
+summary(mod)
+```
+
+#other models looking at how the relationship between leaf weight (or area) and total plant weight shifts with age
 this should be another way to get at the decreasing "leafiness" of plants with age
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+plot(total_leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <-lm(FinalWeight~leaf_weight+age+species,SummaryInd)
+mod <-lm(FinalWeight~total_leaf_weight+age+species,SummaryInd)
 summary(mod)
@@
 plot_LeafWeight <- function(spp) {
-  plot(leaf_weight~FinalWeight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
+  plot(total_leaf_weight~FinalWeight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
   legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-  mod <-lm(FinalWeight~leaf_weight+age,data=subset(SummaryInd,species==spp))
+  mod <-lm(FinalWeight~total_leaf_weight+age,data=subset(SummaryInd,species==spp))
   abline(mod)
@@
 ```
+
+#Plots with RA by age 
+Will include a couple of the obviously different species in lab meeting
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot_RAbyAge <- function(spp) {
+  plot(RA~age, data=subset(SummaryInd,species==spp), xlab="age",ylab="reproductive allocation", log="x", main=labels.spp[spp])
+  points(RA_mean~age, data=subset(SummarySppAge, species==spp),pch=16,cex=1.2)
+}
+
+for(n in names(labels.spp)) {
+  plot_RAbyAge(n)
+} 
+```
+
+#Plots of Accessory costs by age
+```{r, echo=FALSE,results='hide', message=FALSE}
+
+plot_PropagulebyAge <- function(spp) {
+  plot(Prop~age, data=subset(SummaryInd,species==spp), xlab="age",ylab="investment on propagule", log="x", main=labels.spp[spp])
+  points(Prop_mean~age, data=subset(SummarySppAge, species==spp),pch=16,cex=1.2)
+}
+
+for(n in names(labels.spp)) {
+  plot_PropagulebyAge(n)
+}
+
+```

### 2015-03-26 leaflifespan.Rmd
lab meeting presentation changes

@@
 LMA <- filter(LMA_raw, species!="" & species!=" ") %>%
-  select(species,age,LMA)
+  select(species,age,LMA,branch_age)
 
@@
 
-col.LMA <-c("black","purple", "pink", "light green", "orange","blue", "light blue","red")
-labels.LMA <-c("all except HATE","age 1.4", "age 2.4", "age 5", "age 7", "age 9", "age 32", "including HATE")
+col.LMA <-c("purple", "pink", "light green", "orange","blue", "light blue","red")
+labels.LMA <-c("age 1.4", "age 2.4", "age 5", "age 7", "age 9", "age 32", "HATE")
 plot(LL_birth_mean ~ LMA_mean, SummarySppAge, type="n", xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1,pch=17, log="xy")
@@
 points(LL_birth_mean ~ LMA_mean, col="red", data=subset(SummarySppAge, species=="HATE"), pch=17)
+legend("bottomright",col=col.LMA, labels.LMA, pch=16, cex=1.4)
+
+plot(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5), pch=16, cex=1.2, col=col.age[as.factor(age)])
+mod <- lm(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5))
+summary(mod)
+
+plot(LL_death_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5), pch=16, cex=1.2, col=col.age[as.factor(age)])
+mod <- lm(LL_death_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5))
+summary(mod)
+
+plot(LL_bd_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5), pch=16, cex=1.2, col=col.age[as.factor(age)])
+legend("bottomright",col=col.age,labels.age,pch=16)
+mod <- lm(LL_bd_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5))
+summary(mod)
+
 #need log transformation to get these to plot onto axes
@@
 abline(mod_no_HATE, lwd=2)
-legend("bottomright",col=col.LMA, labels.LMA, pch=16, cex=1.4)
+
 summary(mod_no_HATE)
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(LL_birth~age,SummaryInd,log="xy", xlab="age",ylab="leaf lifespan (based on leaf births",col=col.spp[as.factor(species)])
+plot(LL_birth~age,SummaryInd,log="xy", xlab="age",ylab="leaf lifespan (based on leaf births)",col=col.spp[as.factor(species)])
 legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
@@
 
-plot(LMA_mean~age,SummarySppAge,log="xy", xlab="age",ylab="LMA",col=col.spp[as.factor(species)],pch=16)
+plot(LMA~age,data=subset(LMA,branch_age=="mid"),log="xy", xlab="age",ylab="LMA",col=col.spp[as.factor(species)],pch=16)
 legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+mod<- lm(LMA~age+species,data=subset(LMA,branch_age=="mid" & age>2))
+summary(mod)
 
@@
 legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
-mod <- lm(lvs_end_total~age+species+age*species,SummaryInd)
+mod <- lm(lvs_end_total~age+species,SummaryInd)
 summary(mod)
@@
 plot_RAbyAge <- function(spp) {
-  plot(RA~age, data=subset(SummaryInd,species==spp), xlab="age",ylab="reproductive allocation", log="x", main=labels.spp[spp])
-  points(RA_mean~age, data=subset(SummarySppAge, species==spp),pch=16,cex=1.2)
+  plot(RA~age, data=subset(SummaryInd,species==spp), xlab="age (years)",ylab="reproductive allocation (%)", log="x", main=labels.spp[spp],xlim=c(1,35),ylim=c(0,1))
+  points(RA_mean~age, data=subset(SummarySppAge, species==spp),pch=16,cex=1.4)
 }

### 2015-03-26 talk.Rmd
lab meeting presentation changes

@@
 ---
+```{r, echo=FALSE,results='hide', message=FALSE}
+
+# load packages and "open" dataframes to use
+#library(remake)
+#create_bindings()
+```
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+LMA <- filter(LMA_raw, species!="" & species!=" ") %>%
+  select(species,age,LMA,branch_age)
+
+wood <- filter(woodDensity_raw, use=="use") %>%
+  select(species,density)
+
+seedsize <- seedSize_raw %>%
+  select(species,seed_size)
+
+harvest <- filter(HarvestData, use_status=="use" & segment==1 & start_end=="end") %>%
+  select(species,individual,age,age2,height,total_leaf_weight,site)
+
+investment <- ReproductionAllocation_all
+investment$age2 <- investment$age
+investment$age <- round(investment$age, digits=1)
+
+accessory <- AccessoryCosts_all
+accessory$age2 <- accessory$age
+accessory$age <- round(accessory$age, digits=1)
+#accessory$PerAccessory <- {
+#  select(accessory, Total >0,
+#  1 - (accessory$Prop/accessory$Total)
+#}
+
+#accessory$PerPropagule = 1 - accessory$PerAccessory
+
+leafLifespan <- filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use") %>%
+  select(species,age,individual,d_start,d_end,length_start,new_length,lvs_start_length,lvs_start_count,lvs_end_length,lvs_end_count,lvs_new_length,lvs_new_count,new_but_shed_count,mm_lvs_spec,count_lvs_spec)
+
+leafLifespan$individual <- as.factor(leafLifespan$individual)
+leafLifespan$species <- as.factor(leafLifespan$species)
+
+#loading this column as character, so using this for now
+
+# Calculating Leaf Lifespan
+
+# where counts did not previously exists, set as 0; CHECK WITH DANIEL THAT "V" IS A SET "NAME" IN THESE FUNCTIONS
+
+leaf_lifespan_temp <- leafLifespan %>%
+              select(species,age,individual,d_start,d_end,length_start,new_length,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)
+
+for(v in c("lvs_start_count","lvs_end_count","lvs_new_count","new_but_shed_count")) {
+  i <- is.na(leaf_lifespan_temp[[v]])
+  leaf_lifespan_temp[[v]][i] <- 0
+}
+
+# For individuals with "length" measures, translate into count
+
+# get average leaves per length for spp
+leaves_per_length_spp <-  filter(leavesPerLength_raw,use=="yes") %>%
+  mutate(count_per_length = leaf_count/length_mm) %>%
+  group_by(species) %>%
+  summarise(count_per_length = mean(count_per_length, na.rm=TRUE))
+
+# get spp average for all individuals
+leafLifespan$count_per_length <- leaves_per_length_spp$count_per_length[match(leafLifespan$species, leaves_per_length_spp$species)]
+
+# if possible use data for that individual, if it exists; this code substitutes in species count per length #s for individuals where this data is available
+i <- !is.na(leafLifespan$mm_lvs)
+leafLifespan$count_per_length[i] <- (leafLifespan$count_lvs_spec/leafLifespan$mm_lvs)[i]
+
+#this is the end of the section Daniel helped me rewrite - next section is mine
+
+#get total leaf counts
+for(v in c("lvs_start_length","lvs_start_count","lvs_end_length","lvs_end_count","lvs_new_length","lvs_new_count","new_but_shed_count")) {
+  i <- is.na(leafLifespan[[v]])
+  leafLifespan[[v]][i] <- 0
+  }
+leafLifespan$lvs_start <- leafLifespan$lvs_start_count + (leafLifespan$lvs_start_length * leafLifespan$count_per_length)
+leafLifespan$lvs_end <- leafLifespan$lvs_end_count + (leafLifespan$lvs_end_length * leafLifespan$count_per_length)
+leafLifespan$lvs_new <- leafLifespan$lvs_new_count + (leafLifespan$lvs_new_length * leafLifespan$count_per_length)
+
+#calculating leaf lifespan
+leafLifespan$LL_bd <- (leafLifespan$lvs_start)/(((leafLifespan$lvs_start)-(leafLifespan$lvs_end))+(leafLifespan$lvs_new)/2)
+leafLifespan$LL_death <- (leafLifespan$lvs_start)/((leafLifespan$lvs_start)-(leafLifespan$lvs_end))
+leafLifespan$LL_birth <- (leafLifespan$lvs_start)/(leafLifespan$lvs_new)
+
+leafLifespan$LL_death[which(is.infinite(leafLifespan$LL_death))] <- NA
+leafLifespan$LL_bd[which(is.infinite(leafLifespan$LL_death))] <- NA
+leafLifespan$LL_birth[which(is.infinite(leafLifespan$LL_death))] <- NA
+
+#adding investment and accessory costs data to leafLifespan dataframe to create a dataframe with all individual level data
+SummaryInd <- merge(leafLifespan, select(investment, -species, -age), by="individual")
+SummaryInd <- merge(SummaryInd, select(accessory, -species, -age, -age2), by="individual")
+SummaryInd <- merge(SummaryInd, select(harvest, -species, -age, -age2), by="individual")
+
+#adding variables to look at change across years
+SummaryInd$change_shoot_diam <- SummaryInd$d_end - SummaryInd$d_start
+SummaryInd$change_basal_diam <- SummaryInd$FinalBasalDiam - SummaryInd$StartBasalDiam
+SummaryInd$change_shoot_area <- (3.14*((SummaryInd$d_end/2)^2)) - (3.14*((SummaryInd$d_start/2)^2))
+SummaryInd$change_basal_area <- (3.14*((SummaryInd$FinalBasalDiam/2)^2)) - (3.14*((SummaryInd$StartBasalDiam/2)^2))
+SummaryInd$lvs_end_total <- SummaryInd$lvs_end + SummaryInd$lvs_new
+```
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+#summarizing data by species, age
+
+#leaf lifespan summary by species, age
+LL_summary <- SummaryInd %>%
+  filter(LL_bd>0 & LL_bd<6 & LL_birth<8 & LL_death<8) %>%
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length, lvs_end, lvs_end_total, change_shoot_diam, change_basal_diam, change_shoot_area, change_basal_area)
+
+#LMA summary by species, age
+LMA_summary <- LMA %>%
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), LMA)
+names(LMA_summary)<-c("species","age","LMA_mean","LMA_se","LMA_length")
+
+#accessory tissue summary by species, age
+accessory_summary <- accessory %>%
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), PrePol_A, PrePol_S, PostPol_A, PD, Prop)
+
+#investment summary by species, age
+investment_summary <- investment %>%
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), GrowthInv, FinalWeight, FinalBasalDiamAv, TotalInvestment, RA)
+
+#harvest summary by species, age
+harvest_summary <- harvest %>%
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), height,total_leaf_weight)
+#names(harvest_summary)<-c("species","age","height_mean","height_se","height_length")
+
+#RA for each species/age combination
+maxRA <- investment %>%
+  group_by(species, age) %>%
+  summarise_each(funs(max), RA)
+names(maxRA)<-c("species","age","maxRA")
+
+#maximum H for each species/age combination
+maxH <- harvest %>%
+  group_by(species, age) %>%
+  summarise_each(funs(max), height)
+names(maxH)<-c("species","age","maxH")
+
+#LMA summary by species, age
+LMA_summary <- LMA %>%
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), LMA)
+names(LMA_summary)<-c("species","age","LMA_mean","LMA_se","LMA_length")
+
+#wood density summary by species
+wood_summary <- wood %>%
+  group_by(species) %>%
+  summarise_each(funs(mean, se, length), density)
+names(wood_summary)<-c("species","WD_mean","WD_se","WD_length")
+
+#leaf lifespan summary by species
+LL_spp <- leafLifespan %>%
+  filter(age>2) %>%
+  group_by(species) %>%
+  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth)
+
+#LMA summary by species
+LMA_spp <- LMA %>%
+  filter(age>2) %>%
+  group_by(species) %>%
+  summarise_each(funs(mean, se, length), LMA)
+  names(LMA_spp)<-c("species", "LMA_mean","LMA_se","LMA_length")
+
+#maximum height for each species
+maxH_spp <- harvest %>%
+  group_by(species) %>%
+  summarise_each(funs(max), height)
+names(maxH_spp)<-c("species", "maxH_spp")
+
+SummaryInd <- merge(SummaryInd,wood_summary, by=c("species"))
+SummaryInd <- merge(SummaryInd,LMA_summary, by=c("species","age"))
+SummaryInd <- merge(SummaryInd,maxH_spp, by=c("species"))
+SummaryInd <- merge(SummaryInd,seedsize, by=c("species"))
+
+SummaryInd$leafArea <- SummaryInd$total_leaf_weight * SummaryInd$LMA_mean
+
+#merge various data summaries into SummarySppAge dataframe
+SummarySppAge <- merge(LL_summary, LMA_summary, by=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, wood_summary, by=c("species"))
+SummarySppAge <- merge(SummarySppAge, seedsize, by=c("species"))
+SummarySppAge <- merge(SummarySppAge, maxH_spp, by=c("species"))
+SummarySppAge <- merge(SummarySppAge, maxH, by=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, investment_summary, by=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, accessory_summary, by=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, harvest_summary, by=c("species","age"))
+
+#merge various data summaries into SummarySpp dataframe
+SummarySpp <- merge(LL_spp, LMA_spp, by=c("species"))
+SummarySpp <- merge(SummarySpp, wood_summary, by=c("species"))
+SummarySpp <- merge(SummarySpp, seedsize, by=c("species"))
+SummarySpp <- merge(SummarySpp, select(maxH, -age), by=c("species"))
+
+#plotting and stats
+#creating lists of information for plotting symbols, colors, labels
+pch.spp <- c(0,1,2,15,16,17,18,0,1,2,15,16,17,18)
+col.spp <- c("red", "dark green", "blue", "purple", "orange", "light green","salmon","turquoise","grey", "black","light blue","brown","yellow","salmon")
+col.age <-c("purple","pink","green","orange","blue","dark green")
+pch.age <- c(1,1,16,16,16,16)
+labels.spp <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris micraphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(labels.spp) <- c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")
+labels.age <- c("1.4","2.4","5","7","9","32")
+names(labels.age) <- c("1.4","2.4","5","7","9","32")
+```
 
@@
 - subsets of SummarySppAge are created to omit babies or HATE for various analyses
+
+#What causes RA to shift with age in species?
+Theoretical models indicate that there need to be size (or age) related shifts in *some* trade-off to create graded RA schedules.
+
+For instance, shifts in a variable such as leaf lifespan, fecundity per RA, photosynthetic rates with size (or other variables) will change the RA schedule.
+
+I have both RA schedules and lots of other data across multiple ages:
+- leaf lifespa
+- LMA
+- accessory tissue costs
+
+#Shifts in RA with age
+
+Showing just a few of the RA schedules from my last lab meeting.
+
+They show that species differ greatly in RA, that there is a general increase with age, but also that the data are noisy.
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot_RAbyAge <- function(spp) {
+  plot(RA~age, data=subset(SummaryInd,species==spp), xlab="age (years)",ylab="reproductive allocation (%)", log="x", main=labels.spp[spp],xlim=c(1,35),ylim=c(0,1))
+  points(RA_mean~age, data=subset(SummarySppAge, species==spp),pch=16,cex=1.4)
+}
+
+for(n in names(labels.spp)) {
+  plot_RAbyAge(n)
+}
+```
+#Individual shoots looked decidedly "less leafy" in many older plants
+This led me to wonder how leaf lifespan - or some other variable - was shifting with age
+
+The number of leaves along a leader is overall uneffected by age, although some species show a marked decline
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(lvs_end_total~age,SummaryInd,log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+```
+
+#LMA versus age
+The plot below is a bulked LMA sample from each site, of leaves from the second most recent cohort
+
+There is a significant increase with age (p=0.002) and many species differ from one another, despite the very few points
+Age is only borderline significant (p=0.04) when the seedlings are removed
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(LMA~age,data=subset(LMA,branch_age=="mid"),log="xy", xlab="age",ylab="LMA",col=col.spp[as.factor(species)],pch=16)
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+```
+
+#Leaf lifespan with age
+Leaf lifespan increases from seedlings (1.4 yrs) to saplings (2.4 years) to adults (>4 years), but there are no differences between the different adult populations
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(LL_birth~age,SummaryInd,log="xy", xlab="age",ylab="leaf lifespan (based on leaf births)",col=col.spp[as.factor(species)])
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+```
+
+#Plots of individual species show that no species has a significant change either - although several show slight declines at the end
+```{r, echo=FALSE,results='hide', message=FALSE}
+#DF: Here is a place where it would be good to run the statistical model on each of the species. I have the function I wrote below, ut hashed out
+
+plot_LLvAge <- function(spp) {
+  plot(LL_birth ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
+     main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
+  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
+  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
+  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
+}
+
+#mod_LLvAge <- function(spp) {
+#  lm(LL_birth ~ age, data=subset(SummaryInd,species==spp))
+#}
+
+for(n in names(labels.spp)) {
+  plot_LLvAge(n)
+#  mod_LMAvAge(n)
+#  summary(mod_LMAvAge(n))
+}
+```
+#Had expected a stronger pattern either in leaf lifespan or leaf count on a shoot
+Apparently it is simply that older plants have more stem - plotting total leaf weight against final weight, shows bigger plants have relatively fewer leaves
+(Yes, I know the 2.4 yr olds are missing...)
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(total_leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+```
+
+#LMA vs Leaf lifespan
+This correlation is as expected, except for the babies
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+col.LMA <-c("purple", "pink", "light green", "orange","blue", "light blue","red")
+labels.LMA <-c("age 1.4", "age 2.4", "age 5", "age 7", "age 9", "age 32", "HATE")
+plot(LL_birth_mean ~ LMA_mean, SummarySppAge, type="n", xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1,pch=17, log="xy")
+points(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE"), pch=16, cex=1.2, col=col.age[as.factor(age)])
+points(LL_birth_mean ~ LMA_mean, col="red", data=subset(SummarySppAge, species=="HATE"), pch=17)
+legend("bottomright",col=col.LMA, labels.LMA, pch=16, cex=1.4)
+```
+
+#Some other teasers for the future

### 2015-03-26 leaflifespan.Rmd
final changes before lab meeting

@@
 names(labels.age) <- c("1.4","2.4","5","7","9","32")
+labels.age2 <- c("2.4","5","7","9","32")
+col.age2 <-c("pink","green","orange","blue","dark green")
 ```
@@
 
-plot(LL_bd_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5), pch=16, cex=1.2, col=col.age[as.factor(age)])
-legend("bottomright",col=col.age,labels.age,pch=16)
+plot(LL_bd_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5), pch=16, cex=1.2, col=col.age2[as.factor(age)])
+legend("bottomright",col=col.age2,labels.age2,pch=16)
+
 mod <- lm(LL_bd_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5))
@@
 
+plot(new_length ~ age,SummaryInd,col=col.spp[specie],log="xy")
+
 plot_newlengthvAge <- function(spp) {
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(change_shoot_area~new_length,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8, xlab="shoot extension (mm)", ylab="increased shoot cross sectional area")
+plot(change_shoot_area~new_length,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8, xlab="shoot extension (mm)", ylab="increased shoot cross sectional area",main="How well do growth at the shoot level and whole plant level match?")
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+
+plot(change_shoot_area~new_length,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=.8, xlab="shoot extension (mm)", ylab="increased shoot cross sectional area",main="How well do growth at the shoot level and whole plant level match?")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+
 mod <- lm(change_shoot_area~new_length +age,data=subset(SummaryInd,change_shoot_area<1000000))
 summary(mod)
+
+plot(change_shoot_area~change_basal_area,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+mod <- lm(change_shoot_area~change_basal_area+age,subset(SummaryInd,age>3))
+summary(mod)
+
+plot(change_shoot_area~change_basal_area,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
 
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="LMA",ylab="growth investment (mg per year)",main="Seedlings")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
 mod<-lm(LMA_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age==1.4))
@@
 
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="LMA",ylab="growth investment (mg per year)",main="Saplings")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
 mod<-lm(LMA_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age==2.4))
@@
 
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Adults")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
 mod<-lm(LMA_mean~GrowthInv_mean+age,data=subset(SummarySppAge,age>3))
@@
 
-plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=.7)
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
@@
 
-plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1)
+legend("topleft",col=col.age, labels.age, pch=16, cex=1)
 mod<-lm(seed_size~GrowthInv_mean+age,data=subset(SummarySppAge,age>3))
@@
 
-plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age==2.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod<-lm(maxH~GrowthInv_mean,data=subset(SummarySppAge,age==2.4))
+mod<-lm(maxH_spp~GrowthInv_mean,data=subset(SummarySppAge,age==2.4))
 summary(mod)
 
-plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=.7)
+plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age>3),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.2)
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)

### 2015-03-26 talk.Rmd
final changes before lab meeting

@@
 # load packages and "open" dataframes to use
-#library(remake)
-#create_bindings()
+library(remake)
+create_bindings()
 ```
@@
 SummarySpp <- merge(SummarySpp, select(maxH, -age), by=c("species"))
+```
 
 #plotting and stats
+```{r, echo=FALSE,results='hide', message=FALSE}
 #creating lists of information for plotting symbols, colors, labels
@@
 names(labels.age) <- c("1.4","2.4","5","7","9","32")
+labels.age2 <- c("2.4","5","7","9","32")
+col.age2 <-c("pink","green","orange","blue","dark green")
+col.age3 <-c("green","orange","blue","dark green")
 ```
@@
 ```
+
+#Several species show significant declines in shoot extension with age
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot_newlengthvAge <- function(spp) {
+  plot(new_length ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leader shoot extention", cex.axis=.8, las=1, pch=16, log="x",
+  main=labels.spp[spp])
+  points(new_length_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
+  points((new_length_mean+new_length_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
+  points((new_length_mean-new_length_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
+}
+
+mod_newlengthvAge <- function(spp) {
+  lm(new_length ~ age, data=subset(SummaryInd,age>2.4 & species==spp))
+}
+
+for(n in names(labels.spp)) {
+  plot_newlengthvAge(n)
+  mod_newlengthvAge(n)
+  summary(mod_newlengthvAge(n))
+}
+```
+
 #Had expected a stronger pattern either in leaf lifespan or leaf count on a shoot
@@
 ```
+#Next steps?
+As I begin to analyze RA patterns, think more specifically about the species that do show a distinct change with age in one of hte "leaf" parameters.
+
+For instance, is there some way to capture "change with age" as a variabe of its own that is worth comparing across species.
+
+Afterall, the energy allocation models suggest that different RA schedules may be due to different amounts of "shifting" across species - some species might be predicted to shift more than others.
 
@@
 
-#Some other teasers for the future
+#LMA vs LL without young plants
+The pattern becomes more obvious when young plants (and Hakea) are omitted
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(LL_bd_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5), pch=16, cex=1.2, col=col.age2[as.factor(age)])
+legend("bottomright",col=col.age2,labels.age2,pch=16)
+```
+
+#Growth rates increase with increasing LMA in adult plants
+But there is no relationship in seedlings (age=1.4) or saplings (age=2.4)
+This is not predicted by Daniel's model or Anais' review
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Seedlings")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="pink",pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Saplings")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Adults")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+legend("bottomright",col=col.age,labels.age,pch=16)
+```
+
+#Species with greater wood density have higher growth rates
+Again there is no relationship in younger plants
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="wood density",ylab="growth investment (mg per year)",xlim=c(0.57,0.9),main="Relationship between wood density and growth rates")
+text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+```
+
+#Species with larger seeds have higher growth rates
+The same basic relationship exists across all ages, so combined all data here
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
+legend("topleft",col=col.age, labels.age, pch=16, cex=1)
+text(GrowthInv_mean ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+```
+
+#Species with greater maximum height have higher growth rates
+For younger plants there is no relationship with *SPECIES* overall maximum H, but there is a positive correlation with the maximum height the species reaches at a given age -i.e.
+fast growing young plants are tall when young.
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="maximum height (mm)",ylab="growth investment (mg per year)",xlim=c(500,3200),main="Relationship between growth rates on maximum H")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+```
+
+#Correlations between different growth measures
+Increased cross-sectional area of a leader and the entire plant are fairly correlated and uneffected by age (once not baby)
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(change_shoot_area~change_basal_area,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+```

### 2015-03-26 talk.Rmd
small fixes to talk

@@
 ---
-title: "Untitled"
+title: "Age-related changes in plant growth and traits"
+author: Lizzy Wenk
+date: 2015.03.26
 output:
@@
 
-#Plots of individual species show that no species has a significant change either - although several show slight declines at the end
+# Plots of individual species show that no species has a significant change either - although several show slight declines at the end
 ```{r, echo=FALSE,results='hide', message=FALSE}
-#DF: Here is a place where it would be good to run the statistical model on each of the species. I have the function I wrote below, ut hashed out
-
 plot_LLvAge <- function(spp) {
-  plot(LL_birth ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
+  data2 <- filter(SummaryInd, species==spp)
+  plot(LL_birth ~ age, data=data2, xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
      main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
@@
   points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
+
+  # fit <- lm(LL_birth ~ log10(age), data=data2)
+  # abline(fit)
 }
-
-#mod_LLvAge <- function(spp) {
-#  lm(LL_birth ~ age, data=subset(SummaryInd,species==spp))
-#}
 

### 2015-03-31 leaflifespan.Rmd
creating separate R scripts for analysis of different variables

@@
 Then this becomes the file where variables are summarized, plotted analyzed.
+-Similarly, have separate file where all teh summary calculations occur
 - add final leaf and stem biomass output to "investment" output file
@@
 
+#calculating percentages of various accessory tissues
+
+accessory$PerPrePol_A <- accessory$PrePol_A / accessory$Total
+accessory$PerPrePol_S <- accessory$PrePol_S / accessory$Total
+accessory$PerPostPol_A <- accessory$PostPol_A / accessory$Total
+accessory$PerPackDisp <- accessory$PD / accessory$Total
+accessory$PerPropagule <- accessory$Prop / accessory$Total
+accessory$PerAcc <- 1- accessory$PerPropagule
+
+accessory$PerPrePol_A[which(is.nan(accessory$PerPrePol_A))] <- NA
+accessory$PerPrePol_S[which(is.nan(accessory$PerPrePol_S))] <- NA
+accessory$PerPostPol_A[which(is.nan(accessory$PerPostPol_A))] <- NA
+accessory$PerPackDisp[which(is.nan(accessory$PerPackDisp))] <- NA
+accessory$PerPropagule[which(is.nan(accessory$PerPropagule))] <- NA
+accessory$PerAcc[which(is.nan(accessory$PerAcc))] <- NA
+
 #adding investment and accessory costs data to leafLifespan dataframe to create a dataframe with all individual level data
@@
 
-#adding variables to look at change across years
+#adding variables to look at change across years, RGR
 SummaryInd$change_shoot_diam <- SummaryInd$d_end - SummaryInd$d_start
@@
 SummaryInd$lvs_end_total <- SummaryInd$lvs_end + SummaryInd$lvs_new
+SummaryInd$RGR <- log(SummaryInd$FinalWeight)-log(SummaryInd$FinalWeight-SummaryInd$GrowthInv)
 ```
@@
   group_by(species, age) %>%
-  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length, lvs_end, lvs_end_total, change_shoot_diam, change_basal_diam, change_shoot_area, change_basal_area)
+  summarise_each(funs(mean, se, length), LL_bd, LL_death,LL_birth,new_length, lvs_end, lvs_end_total, change_shoot_diam, change_basal_diam, change_shoot_area, change_basal_area,RGR)
 
@@
   summarise_each(funs(mean, se, length), PrePol_A, PrePol_S, PostPol_A, PD, Prop)
+
+accessory_summary2 <- accessory %>%
+  filter(Total!=0) %>%
+  group_by(species, age) %>%
+  summarise_each(funs(mean, se, length), PerPrePol_A, PerPrePol_S, PerPostPol_A, PerPackDisp, PerPropagule, PerAcc)
 
@@
 SummarySppAge <- merge(SummarySppAge, accessory_summary, by=c("species","age"))
+SummarySppAge <- merge(SummarySppAge, accessory_summary2, by=c("species","age"))
 SummarySppAge <- merge(SummarySppAge, harvest_summary, by=c("species","age"))
@@
 
+#Plots indicating there is a fundamental problem with leaf lifespan measurements
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(LL_death ~ LL_birth, data=subset(SummaryInd,LL_bd>0&LL_bd<5&LL_death<5&age>2.4))
+mod <- lm(LL_death ~ LL_birth, data=subset(SummaryInd,LL_bd>0&LL_bd<5&LL_death<5&age>2.4&LL_birth!=Inf))
+summary(mod)
+
+plot(LL_death ~ LL_bd, data=subset(SummaryInd,LL_bd>0&LL_bd<5&LL_death<5&age>2.4))
+mod <- lm(LL_death ~ LL_bd, data=subset(SummaryInd,LL_bd>0&LL_bd<5&LL_death<5&age>2.4))
+summary(mod)
+```
+
 #Plots of interest to Anais' analyses

### 2015-03-31 scripts in progress/accessory.R

@@ -1,0 +1,91 @@
+
+
+
+plot((PerPropagule+.01) ~ age, SummaryInd, log="xy", col=col.spp[is.factor(species)])
+
+plot((PerPrePol_A+.01) ~ age, SummaryInd, log="xy", col=col.spp[is.factor(species)])
+
+mod <- lm((PerPrePol_A +.01) ~ age+ species +age*species, SummaryInd)
+summary(mod)
+
+plot((PerPrePol_S+.01) ~ age, SummaryInd, log="x", col=col.spp[is.factor(species)])
+mod <- lm((PerPrePol_S +.01) ~ age+ species +age*species + species + age*species, SummaryInd)
+summary(mod)
+
+plot((PerPostPol_A+.01) ~ age, SummaryInd, log="xy", col=col.spp[is.factor(species)])
+mod <- lm((PerPostPol_A +.01) ~ age+ species +age*species, SummaryInd)
+summary(mod)
+
+plot((PerPackDisp+.01) ~ age, SummaryInd, log="xy", col=col.spp[is.factor(species)])
+
+plot_packdisp <- function(spp) {
+    points((PerPackDisp_mean+.01) ~ age,data=subset(SummarySppAge,species==spp), col=col.spp[is.factor(species)], pch=16, cex=1.5)
+}
+  
+for(n in names(labels.spp)) {
+  plot_packdisp(n)
+}
+###can't get colors to work here
+
+plot((PerPrePol_A+.01) ~ age, SummaryInd, log="xy", col=col.spp[is.factor(species)])
+
+plot_prepolA <- function(spp) {
+  points((PerPrePol_A_mean+.01) ~ age,data=subset(SummarySppAge,species==spp), col=col.spp[is.factor(species)], pch=16, cex=1.5)
+}
+
+for(n in names(labels.spp)) {
+  plot_prepolA(n)
+}
+
+
+
+
+points((PerPackDisp_mean+.01) ~ age,data=subset(SummarySppAge,species=="PILI"), col="yellow", pch=16, cex=2)
+points((PerPackDisp_mean+.01) ~ age,data=subset(SummarySppAge,species=="BOLE"), col="salmon", pch=16, cex=2)
+
+
+mod <- lm((PerPackDisp +.01) ~ age+ species +age*species, SummaryInd)
+summary(mod)
+
[…]

### 2015-03-31 scripts in progress/accessory_better.R

@@ -1,0 +1,39 @@
+#Looking at how the relative proportion of various accessory costs shifts as RA shifts. Looked at 1 at a time, 
+#higher RA=
+# - lower pre-pollination aborted
+# - higher pre-pollination successful
+# - higher post-pollination aborted
+# - higher packaging and dispersal
+# - higher investment in propagules
+
+#When all combined into a single model with PerPrePol_A or PerPropagule become much less significant because they are inversely correlated. But which is significant depends on the order in which I add the terms 
+
+#how can I tell R to figure out for itself the correct order to add variables to the model - depending on order, different variables become significant
+
+mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule))+asin(sqrt(PerPrePol_A))+ asin(sqrt(PerPrePol_S))+ asin(sqrt(PerPostPol_A))+ asin(sqrt(PerPackDisp)),data=subset(SummaryInd,RA>0))
+summary(mod)
+plot(mod)
+
+mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPrePol_A)),data=subset(SummaryInd,RA>0))
+summary(mod)
+
+mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPrePol_S)),data=subset(SummaryInd,RA>0))
+summary(mod)
+
+mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPostPol_A)),data=subset(SummaryInd,RA>0))
+summary(mod)
+
+mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPackDisp)),data=subset(SummaryInd,RA>0))
+summary(mod)
+
+mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule)),data=subset(SummaryInd,RA>0))
+summary(mod)
+
+
+
+plot(PerPrePol_A~PerPropagule,data=subset(SummaryInd,RA>0))
+mod <- lm(PerPrePol_A~PerPropagule,data=subset(SummaryInd,RA>0))
+summary(mod)
+
+
+pairs(SummaryInd[c("PerPrePol_A", "PerPrePol_S", "PerPostPol_A", "PerPackDisp", "PerPropagule")])

### 2015-03-31 scripts in progress/growth variables.R

@@ -1,0 +1,15 @@
+#correlations between the three "growth variables"
+
+plot(RGR ~ GrowthInv, data=subset(SummaryInd), log="x",col=col.age[as.factor(age)])
+
+plot(new_length ~ GrowthInv, SummaryInd, log="xy", col=col.age[as.factor(age)])
+
+plot(RGR ~ new_length, SummaryInd, log="xy", col=col.age[as.factor(age)])
+
+
+pairs(SummaryInd[c("RGR", "GrowthInv", "new_length", "change_shoot_area", "change_basal_area","maxH_spp","height","lvs_end_total","FinalWeight")])
+
+mod <- lm(new_length~height + maxH_spp + WD_mean + LL_bd + RA + seed_size + age, SummaryInd)
+summary(mod)
+anova(mod)
+step(mod)

### 2015-04-01 leaflifespan.Rmd
continued work on R scripts - starting to build RA model

@@
 accessory$age <- round(accessory$age, digits=1)
+accessory$PrePol_S[which(is.na(accessory$PrePol_S))] <- 0
+accessory$Total= (accessory$PrePol_A + accessory$PrePol_S + accessory$PostPol_A + accessory$PD + accessory$Prop)
+
 #accessory$PerAccessory <- {

### 2015-04-01 scripts in progress/summary_dataframes.R

@@ -1,0 +1,242 @@
+```{r, echo=FALSE,results='hide', message=FALSE}
+
+# load packages and "open" dataframes to use
+library(remake)
+create_bindings()
+```
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+LMA <- filter(LMA_raw, species!="" & species!=" ") %>%
+  select(species,age,LMA,branch_age)
+
+wood <- filter(woodDensity_raw, use=="use") %>%
+  select(species,density)
+
+seedsize <- seedSize_raw %>%
+  select(species,seed_size)
+
+harvest <- filter(HarvestData, use_status=="use" & segment==1 & start_end=="end") %>%
+  select(species,individual,age,age2,height,total_leaf_weight,site)
+
+investment <- ReproductionAllocation_all
+investment$age2 <- investment$age
+investment$age <- round(investment$age, digits=1)
+
+accessory <- AccessoryCosts_all
+accessory$age2 <- accessory$age
+accessory$age <- round(accessory$age, digits=1)
+
+#accessory$PerAccessory <- {
+#  select(accessory, Total >0,
+#  1 - (accessory$Prop/accessory$Total)
+#}
+
+#accessory$PerPropagule = 1 - accessory$PerAccessory
+
+leafLifespan <- filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use") %>%
+  select(species,age,individual,d_start,d_end,length_start,new_length,lvs_start_length,lvs_start_count,lvs_end_length,lvs_end_count,lvs_new_length,lvs_new_count,new_but_shed_count,mm_lvs_spec,count_lvs_spec)
+
+leafLifespan$individual <- as.factor(leafLifespan$individual)
+leafLifespan$species <- as.factor(leafLifespan$species)
+
+#loading this column as character, so using this for now
+
+# Calculating Leaf Lifespan
+
+# where counts did not previously exists, set as 0; CHECK WITH DANIEL THAT "V" IS A SET "NAME" IN THESE FUNCTIONS
+
+leaf_lifespan_temp <- leafLifespan %>%
+  select(species,age,individual,d_start,d_end,length_start,new_length,lvs_start_count,lvs_end_count,lvs_new_count,new_but_shed_count)
+
+for(v in c("lvs_start_count","lvs_end_count","lvs_new_count","new_but_shed_count")) {
[…]

### 2015-04-01 R/AccessoryTissues.R
Transfer extra calculations into accesrory costs

@@ -7,16 +7,22 @@ IAT_Species <- function(species, Reproduction, HarvestData, InvestmentCategories
     select(age, individual)
       )
 
-  InvDist <- data.frame(species=c(), individual = c(), PrePol_A = c(), PrePol_S = c(), PostPol_A = c(), PD = c(), Prop = c(), Total = c(), age = c())
+  InvDist <- data.frame(species=c(), individual = c(), PrePol_A = c(), PrePol_S = c(), PostPol_A = c(), PD = c(), Prop = c(), Total = c(), age = c(), ageExact = c())
 
   for (individual in unique(Reproduction$individual)) {
     # print(individual)
     Ind <- InvestmentInAccessoryTissues(individual, species, InvestmentCategories[, c("flower_part", species)], species_INV)
     if (length(AgeData[AgeData[, 2] == individual, 1]) == 1) {
-      Ind <- cbind(species, Ind, age = AgeData[AgeData[, 2] == individual, 1])
+      age <- AgeData[AgeData[, 2] == individual, 1]
+      Ind <- cbind(species, Ind, age=round(age, digits=1), age_exact = age)
       InvDist <- rbind(InvDist, Ind)
     }
   }
+
+# TODO: This is temp fix to remove some NAs in PrePol_S. Figure out why these are needed
+  InvDist$PrePol_S[which(is.na(InvDist$PrePol_S))] <- 0
+  InvDist$Total= (InvDist$PrePol_A + InvDist$PrePol_S + InvDist$PostPol_A + InvDist$PD + InvDist$Prop)
+
   InvDist
 }
 

### 2015-04-01 leaflifespan.Rmd
Transfer extra calculations into accesrory costs
Rename age2 to age_exact

--- 2015-03-31 leaflifespan.Rmd
@@
 harvest <- filter(HarvestData, use_status=="use" & segment==1 & start_end=="end") %>%
-  select(species,individual,age,age2,height,total_leaf_weight,site)
+  select(species,individual,age,height,total_leaf_weight,site)
 
 investment <- ReproductionAllocation_all
-investment$age2 <- investment$age
-investment$age <- round(investment$age, digits=1)
-
 accessory <- AccessoryCosts_all
-accessory$age2 <- accessory$age
-accessory$age <- round(accessory$age, digits=1)
-#accessory$PerAccessory <- {
-#  select(accessory, Total >0,
-#  1 - (accessory$Prop/accessory$Total)
-#}
-
-#accessory$PerPropagule = 1 - accessory$PerAccessory
 
@@
 SummaryInd <- merge(leafLifespan, select(investment, -species, -age), by="individual")
-SummaryInd <- merge(SummaryInd, select(accessory, -species, -age, -age2), by="individual")
-SummaryInd <- merge(SummaryInd, select(harvest, -species, -age, -age2), by="individual")
+SummaryInd <- merge(SummaryInd, select(accessory, -species, -age), by="individual")
+SummaryInd <- merge(SummaryInd, select(harvest, -species, -age), by="individual")
 

### 2015-04-01 talk.Rmd
creating separate R scripts for analysis of different variables
Rename age2 to age_exact

@@
 harvest <- filter(HarvestData, use_status=="use" & segment==1 & start_end=="end") %>%
-  select(species,individual,age,age2,height,total_leaf_weight,site)
+  select(species,individual,age,height,total_leaf_weight,site)
 
 investment <- ReproductionAllocation_all
-investment$age2 <- investment$age
-investment$age <- round(investment$age, digits=1)
 
 accessory <- AccessoryCosts_all
-accessory$age2 <- accessory$age
-accessory$age <- round(accessory$age, digits=1)
-#accessory$PerAccessory <- {
-#  select(accessory, Total >0,
-#  1 - (accessory$Prop/accessory$Total)
-#}
-
-#accessory$PerPropagule = 1 - accessory$PerAccessory
 

### 2015-04-17 results.Rmd
Add stub for results file

```{r, echo=FALSE,results='hide', message=FALSE}
# create_bindings()

LMA <- filter(LMA_raw, species!="" & species!=" ") %>%
  select(species,age,LMA,branch_age)

wood <- filter(woodDensity_raw, use=="use") %>%
  select(species,density)

seedsize <- seedSize_raw %>%
  select(species,seed_size)

individuals <- IndividualsList

harvest <- filter(HarvestData,
                  individuals$use_for_allocation_calculations[match(HarvestData$individual, individuals$individual)] & segment==1 & start_end=="end") %>%
  select(species,individual,age,height,total_leaf_weight,site)

investment <- ReproductionAllocation_all

investment$age <- round(investment$age, digits=1)

accessory <- AccessoryCosts_all

```

### 2015-04-21 results.Rmd
use lab meeting stuff as start of key results

@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-# create_bindings()
+library(remake)
+create_bindings()
 
-LMA <- filter(LMA_raw, species!="" & species!=" ") %>%
-  select(species,age,LMA,branch_age)
+source("scripts/summary_dataframes.R")
+```
+# file names
 
-wood <- filter(woodDensity_raw, use=="use") %>%
-  select(species,density)
+- leaf_counts is file with calculated leaf counts and leaf lifespan data
+- SummarySppAge is file with means of LL - and other variables - by species and age; LMA data is merged to this file
+- subsets of SummarySppAge are created to omit babies or HATE for various analyses
 
-seedsize <- seedSize_raw %>%
-  select(species,seed_size)
+# What causes RA to shift with age in species?
+Theoretical models indicate that there need to be size (or age) related shifts in *some* trade-off to create graded RA schedules.
 
-individuals <- IndividualsList
+For instance, shifts in a variable such as leaf lifespan, fecundity per RA, photosynthetic rates with size (or other variables) will change the RA schedule.
 
-harvest <- filter(HarvestData,
-                  individuals$use_for_allocation_calculations[match(HarvestData$individual, individuals$individual)] & segment==1 & start_end=="end") %>%
-  select(species,individual,age,height,total_leaf_weight,site)
+I have both RA schedules and lots of other data across multiple ages:
+  - leaf lifespa
+- LMA
+- accessory tissue costs
 
-investment <- ReproductionAllocation_all
+#Shifts in RA with age
 
-investment$age <- round(investment$age, digits=1)
+Showing just a few of the RA schedules from my last lab meeting.
 
-accessory <- AccessoryCosts_all
+They show that species differ greatly in RA, that there is a general increase with age, but also that the data are noisy.
 
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot_RAbyAge <- function(spp) {
+  plot(RA~age, data=subset(SummaryInd,species==spp), xlab="age (years)",ylab="reproductive allocation (%)", log="x", main=labels.spp[spp],xlim=c(1,35),ylim=c(0,1))
+  points(RA_mean~age, data=subset(SummarySppAge, species==spp),pch=16,cex=1.4)
+}
+
+for(n in names(labels.spp)) {
+  plot_RAbyAge(n)
+}
 ```
+# Individual shoots looked decidedly "less leafy" in many older plants
+This led me to wonder how leaf lifespan - or some other variable - was shifting with age
+
+The number of leaves along a leader is overall uneffected by age, although some species show a marked decline
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(lvs_end_total~age,SummaryInd,log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+```
+
+# LMA versus age
+The plot below is a bulked LMA sample from each site, of leaves from the second most recent cohort
+
+There is a significant increase with age (p=0.002) and many species differ from one another, despite the very few points
+Age is only borderline significant (p=0.04) when the seedlings are removed
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(LMA~age,data=subset(LMA,branch_age=="mid"),log="xy", xlab="age",ylab="LMA",col=col.spp[as.factor(species)],pch=16)
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+```
+
+# Leaf lifespan with age
+Leaf lifespan increases from seedlings (1.4 yrs) to saplings (2.4 years) to adults (>4 years), but there are no differences between the different adult populations
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(LL_birth~age,SummaryInd,log="xy", xlab="age",ylab="leaf lifespan (based on leaf births)",col=col.spp[as.factor(species)])
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+```
+
+# Plots of individual species show that no species has a significant change either - although several show slight declines at the end
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot_LLvAge <- function(spp) {
+  data2 <- filter(SummaryInd, species==spp)
+  plot(LL_birth ~ age, data=data2, xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
+       main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
+  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
+  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
+  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
+
+  # fit <- lm(LL_birth ~ log10(age), data=data2)
+  # abline(fit)
+}
+
+for(n in names(labels.spp)) {
+  plot_LLvAge(n)
+  #  mod_LMAvAge(n)
+  #  summary(mod_LMAvAge(n))
+}
+```
+
+# Several species show significant declines in shoot extension with age
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot_newlengthvAge <- function(spp) {
+  plot(new_length ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leader shoot extention", cex.axis=.8, las=1, pch=16, log="x",
+       main=labels.spp[spp])
+  points(new_length_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
+  points((new_length_mean+new_length_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
+  points((new_length_mean-new_length_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
+}
+
+mod_newlengthvAge <- function(spp) {
+  lm(new_length ~ age, data=subset(SummaryInd,age>2.4 & species==spp))
+}
+
+for(n in names(labels.spp)) {
+  plot_newlengthvAge(n)
+  mod_newlengthvAge(n)
+  summary(mod_newlengthvAge(n))
+}
+```
+
+# Had expected a stronger pattern either in leaf lifespan or leaf count on a shoot
+Apparently it is simply that older plants have more stem - plotting total leaf weight against final weight, shows bigger plants have relatively fewer leaves
+(Yes, I know the 2.4 yr olds are missing...)
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(total_leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+```
+# Next steps?
+As I begin to analyze RA patterns, think more specifically about the species that do show a distinct change with age in one of hte "leaf" parameters.
+
+For instance, is there some way to capture "change with age" as a variabe of its own that is worth comparing across species.
+
+Afterall, the energy allocation models suggest that different RA schedules may be due to different amounts of "shifting" across species - some species might be predicted to shift more than others.
+
+# LMA vs Leaf lifespan
+This correlation is as expected, except for the babies
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+col.LMA <-c("purple", "pink", "light green", "orange","blue", "light blue","red")
+labels.LMA <-c("age 1.4", "age 2.4", "age 5", "age 7", "age 9", "age 32", "HATE")
+plot(LL_birth_mean ~ LMA_mean, SummarySppAge, type="n", xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1,pch=17, log="xy")
+points(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE"), pch=16, cex=1.2, col=col.age[as.factor(age)])
+points(LL_birth_mean ~ LMA_mean, col="red", data=subset(SummarySppAge, species=="HATE"), pch=17)
+legend("bottomright",col=col.LMA, labels.LMA, pch=16, cex=1.4)
+```
+
+# LMA vs LL without young plants
+The pattern becomes more obvious when young plants (and Hakea) are omitted
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(LL_bd_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5), pch=16, cex=1.2, col=col.age2[as.factor(age)])
+legend("bottomright",col=col.age2,labels.age2,pch=16)
+```
+
+# Growth rates increase with increasing LMA in adult plants
+But there is no relationship in seedlings (age=1.4) or saplings (age=2.4)
+This is not predicted by Daniel's model or Anais' review
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Seedlings")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="pink",pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Saplings")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Adults")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+legend("bottomright",col=col.age,labels.age,pch=16)
+```
+
+# Species with greater wood density have higher growth rates
+Again there is no relationship in younger plants
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="wood density",ylab="growth investment (mg per year)",xlim=c(0.57,0.9),main="Relationship between wood density and growth rates")
+text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+```
+
+# Species with larger seeds have higher growth rates
+The same basic relationship exists across all ages, so combined all data here
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
+legend("topleft",col=col.age, labels.age, pch=16, cex=1)
+text(GrowthInv_mean ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+```
+
+# Species with greater maximum height have higher growth rates
+For younger plants there is no relationship with *SPECIES* overall maximum H, but there is a positive correlation with the maximum height the species reaches at a given age -i.e.
+fast growing young plants are tall when young.
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="maximum height (mm)",ylab="growth investment (mg per year)",xlim=c(500,3200),main="Relationship between growth rates on maximum H")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+```
+
+# Correlations between different growth measures
+Increased cross-sectional area of a leader and the entire plant are fairly correlated and uneffected by age (once not baby)
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(change_shoot_area~change_basal_area,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+```

### 2015-04-21 results.Rmd
Example fitting linear model. Closes #11

@@
 
-#Shifts in RA with age
+# Shifts in RA with age
 
@@
 ```
+
 # Individual shoots looked decidedly "less leafy" in many older plants
@@
 # Plots of individual species show that no species has a significant change either - although several show slight declines at the end
+
 ```{r, echo=FALSE,results='hide', message=FALSE}
@@
 # Several species show significant declines in shoot extension with age
+
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot_newlengthvAge <- function(spp) {
-  plot(new_length ~ age, data=subset(SummaryInd,species==spp), xlab="age", ylab="leader shoot extention", cex.axis=.8, las=1, pch=16, log="x",
-       main=labels.spp[spp])
-  points(new_length_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
-  points((new_length_mean+new_length_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
-  points((new_length_mean-new_length_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
+
+plot_newlengthvAge <- function(data, yvar = "new_length", xvar = "age", ...) {
+	Y <- data[[yvar]]
+	X <- data[[xvar]]
+  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
+  # points(new_length_mean ~ age, data=data, cex=1.3, pch=8)
+  # points((new_length_mean+new_length_se) ~ age, data=data, cex=1.5, pch=25)
+  # points((new_length_mean-new_length_se) ~ age, data=data, cex=1.5, pch=24)
 }
 
-mod_newlengthvAge <- function(spp) {
-  lm(new_length ~ age, data=subset(SummaryInd,age>2.4 & species==spp))
+summarise_fit <- function(x) {
+	data.frame(
+		select(glance(x), r.squared, p.value),
+		n= length(resid(x)),
+		a = coef(x)[1],
+		b = coef(x)[2]
+	)
 }
 
-for(n in names(labels.spp)) {
-  plot_newlengthvAge(n)
-  mod_newlengthvAge(n)
-  summary(mod_newlengthvAge(n))
+summarise_all_fits <- function(x) {
+	tmp <- lapply(x, summarise_fit) %>%
+		bind_rows
+	data.frame(species=names(x), tmp)
 }
+
+yvar <- "new_length"
+xvar <- "age"
+
+data <- filter(SummaryInd, age > 2.4)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(x[[yvar]] ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+for(spp in names(data)) {
+  plot_newlengthvAge(data[[spp]], yvar, xvar, log="x",
+  	ylim=c(0,150),  main=spp, xlab="age", ylab="leader shoot extention")
+  abline(lmfits[[spp]])
+}
+
 ```

### 2015-04-22 scripts/Accessory_results.rmd
Basic results for Accessory tissues should now be complete. I've deleted the old file and reworked the code in a new "rmd" file

#Accessory costs
Overall results:
- Accessory costs higher for bigger seeds
- A number of species show fairly consistent declines in accessory costs with various measures of "bigger", including size, age, RA. Other species show no patterns
- 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases. in other words, they get better returns on investment the more they invest.
- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e. Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers
- For most of the statistical analyses, the youngest site has been removed, since it included individuals that were harvested while flowering (and therefore never "got to" set fruit) and automatically have no "successful" reproduction. There are of course some individuals like this at other ages as well, but far fewer

#Generic functions for most plotting below
```{r, echo=FALSE,results='hide', message=FALSE}
plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
  Y <- data[[yvar]]
  X <- data[[xvar]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

summarise_fit <- function(x) {
  data.frame(
    select(glance(x), r.squared, p.value),
    n= length(resid(x)),
    a = coef(x)[1],
    b = coef(x)[2]
  )
}

summarise_all_fits <- function(x) {
  tmp <- lapply(x, summarise_fit) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}
```

#How do accessory costs shift with seed size?
Larger-seeded species have higher accessory costs. 
Also shown in other studies and suggested as a mechanism for why angiosperms were able to have such small seeds (relative to gymnosperms, with no decrease in proportional accessory costs with decreasing size)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerAcc_mean"
xvar <- "seed_size"
data <- SummarySpp

plot_yvar_vs_xvar(data, yvar, xvar,log="x",
                  xlab=xvar, ylab=yvar)
mod <- lm(log(seed_size)~PerAcc_mean,SummarySpp)
summary(mod)
anova(mod)
```

#Do species differ in the proportional energy allocated to propagules (vs. accessory tissues)
COER, EPMI, HEPU, LEES, PILI invest the most energy in propagules
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPropagule"
xvar <- "species"
data <- filter(SummaryInd,Total>0)

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar)
mod <- lm(asin(sqrt(PerPropagule)) ~ species, data)
summary(mod)
```

#Do species differ in the proportional energy allocated to aborted pre-pollination tissues
BOLE, EPMI, GRSP, HATE invest the most energy in aborted pre-pollination tissues
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_A"
xvar <- "species"
data <- filter(SummaryInd,Total>0 & age>2)

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar)
mod <- lm(asin(sqrt(PerPrePol_A)) ~ species, data)
summary(mod)
```

#Do individual species decrease accessory costs as they increase in size, age or RA?
First looking at size:
PerAcc is arcsine transformed, size is log transformed
COER, HATE, and PILI show a significant decrease in accessory costs with increasing size (p<0.05)
GRSP, PILI shows a marginally significant decrease in accessory costs with increasing size (0.05<p<0.10)
PEPU shows a marginally significant INCREASE in accessory costs with increasing size (0.05<p<0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerAcc"
xvar <- "FinalWeight"

data <- filter(SummaryInd,Total>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to age:
PerAcc is arcsine transformed, age is log transformed
BOLE, COER, HATE, HEPU, PELA show a significant decrease in accessory costs with increasing age (p<0.05)
EPMI, GRSP, HATE shows a marginally significant decrease in accessory costs with increasing age (0.05<p<0.10)
PUTU shows a sig INCREASE in accessory costs with increasing age
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerAcc"
xvar <- "age"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to RA:
both RA and PerAcc are arcsine transformed
BAER, COER, GRBU, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in accessory costs with increasing RA (p<0.05)
BOLE shows a marginally significant decrease in accessory costs with increasing RA (p ~ 0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerAcc"
xvar <- "RA"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```
Overall, proportion of energy allocation to accessory tissues (versus propagules) is best explained by RA

#Next considering if the amount of energy spent on aborted buds shifts with age, size, RA
First looking at size:
PerPrePol_A is arcsine transformed, size is log transformed
GRSP, HATE, HEPU, PUTU show a significant decrease in aborted buds with increasing size (p<0.05)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_A"
xvar <- "FinalWeight"

data <- filter(SummaryInd,Total>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to age:
PerPrePol_A is arcsine transformed, age is log transformed
BAER, BOLE, COER, EPMI, LEES, PHPH, PILI show a significant decrease in aborted buds with increasing age (p<0.05)
GRSP, HATE show a marginally significant decrease in aborted buds with increasing age (0.05<p<0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_A"
xvar <- "age"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to RA:
both RA and PerPrePol_A are arcsine transformed
BAER, BOLE, COER, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in aborted buds with increasing RA (p<0.05)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_A"
xvar <- "RA"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

#Do individual species decrease total pre-pollination costs as they increase in size, age or RA?
First looking at size:
PerPrePol_All is arcsine transformed, size is log transformed
GRSP, HATE show a significant decrease in total pre-pollination costs with increasing size (p<0.05)
HEPU shows a marginally significant decrease in total pre-pollination costs with increasing size (0.05<p<0.10)

```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "FinalWeight"

data <- filter(SummaryInd,Total>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to age:
PerPrePol_All is arcsine transformed, age is log transformed
BAER, BOLE, COER, HEPU, LEES, PILI show a significant decrease in total pre-pollination costs with increasing age (p<0.05)
EPMI, GRBU, GRSP, HATE shows a marginally significant decrease in total pre-pollination costs with increasing age (0.05<p<0.10)
PUTU shows a sig INCREASE in total pre-pollination  costs with increasing age
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "age"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to RA:
both RA and PerPrePol_All are arcsine transformed
BAER, BOLE, COER, GRSP, HATE, HEPU, LEES, PELA, PEPU show a significant decrease in total pre-pollination costs with increasing RA (p<0.05)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "RA"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to Reproductive Investment:
PerPrePol_All is arcsine transformed, ReproInv is log transformed
COER, GRBU, GRSP, HATE, PEPU, PHPH, PILI show a significant decrease in total pre-pollination costs with increasing reproductive investment (p<0.05)
LEES and PELA show a marginally significant decrease in total pre-pollination costs with increasing reproductive investment (0.05<p<0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "ReproInv"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

#For each species, look at pattern of investment in different tissues across ages
Most obvious pattern is that different species invest more or less in different tissue types - across all species this is bigger pattern than shifts across age
```{r, echo=FALSE,results='hide', message=FALSE}
plot_Acc_by_Spp <- function(spp) {
data2 <- filter(SummarySppAge, species==spp)
plot(PerPropagule_mean ~ age, data=data2, xlab="age", ylab="proportion tissue", cex.axis=.8, las=1,
       main=labels.spp[spp], ylim=c(0,1), xlim=c(1,35), log="x", pch=16,col="orange")
points(PerPrePol_A_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8, col="red")
points(PerPrePol_S_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=17, col="blue")
points(PerPostPol_A_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=18, col="black")
points(PerPackDisp_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=19, col="light green")
legend(.9,.7, pch=c(16,8,17,18,19),legend=c("Propagule","Aborted pre-poll","Successful pre-poll","Aborted post-poll","Packaging & disp"), col=c("orange","red","blue","black","light green"), cex=.8, bty="n")
}

for(n in names(labels.spp)) {
  plot_Acc_by_Spp(n)
  }
```

#Using models that look at all the various factors at once - but need to include species in these models and probably use some sort of a MANOVA
also issues because significance of various variables changes enormously with transformations
```{r, echo=FALSE,results='hide', message=FALSE}
mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule))+asin(sqrt(PerPrePol_A))+ asin(sqrt(PerPrePol_S))+ asin(sqrt(PerPostPol_A))+ asin(sqrt(PerPackDisp)) + species,data=subset(SummaryInd,Total>0))

mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule))+asin(sqrt(PerPrePol_A))+ asin(sqrt(PerPrePol_S))+ asin(sqrt(PerPostPol_A))+ asin(sqrt(PerPackDisp)) +asin(sqrt(PerPropagule))*species+asin(sqrt(PerPrePol_A))*species+ asin(sqrt(PerPrePol_S))*species+ asin(sqrt(PerPostPol_A))*species+ asin(sqrt(PerPackDisp))*species+ species,data=subset(SummaryInd,Total>0))
summary(mod)
plot(mod)
step(mod)
```

### 2015-04-22 scripts/Accessory_tissues.R

@@ -1,270 +1,0 @@
-#Looking at how the relative proportion of various accessory costs shifts as RA shifts. Looked at 1 at a time, 
-#higher RA=
-# - lower pre-pollination aborted (or higher, depending on model)
-# - higher pre-pollination successful
-# - higher post-pollination aborted
-# - higher packaging and dispersal
-# - higher investment in propagules
-
-#When all combined into a single model with PerPrePol_A or PerPropagule become much less significant because they are inversely correlated. But which is significant depends on the order in which I add the terms 
-
-#how can I tell R to figure out for itself the correct order to add variables to the model - depending on order, different variables become significant
-
-mod <- lm(log(Total)~asin(sqrt(PerPropagule))+asin(sqrt(PerPrePol_A))+ asin(sqrt(PerPackDisp))+ asin(sqrt(PerPrePol_S))+ asin(sqrt(PerPostPol_A)),data=subset(SummaryInd,RA>0))
-summary(mod)
-plot(mod)
-step(mod)
-hist(log(SummaryInd$Total))
-
-
-hist(SummaryInd$PerPropagule)
-hist(asin(sqrt(SummaryInd$PerPropagule)))
-
-hist(SummaryInd$PerPropagule)
-hist(asin(sqrt(SummaryInd$PerPropagule)))
-
-
-mod <- lm(log(Total)~asin(sqrt(PerAcc)),data=subset(SummaryInd,RA>0))
-summary(mod)
-#As Total investment in reproduction changes, effect of lots of reproductive components, but Propagule % (and hence total accesory %) doesn't matter
-Y<-cbind(asin(sqrt(SummaryInd$PerPropagule)),asin(sqrt(SummaryInd$PerPrePol_A)),asin(sqrt(SummaryInd$PerPackDisp)),asin(sqrt(SummaryInd$PerPrePol_S)),asin(sqrt(SummaryInd$PerPostPol_A)))
[…]

### 2015-04-22 results.Rmd
minor changes to each

@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot_LLvAge <- function(spp) {
-  data2 <- filter(SummaryInd, species==spp)
-  plot(LL_birth ~ age, data=data2, xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
-       main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
-  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
-  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
-  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
 
@@
 ```
+
+#22 April 2015
+Generic code to create plots, run lm, summarize results, by species
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
+  Y <- data[[yvar]]
+  X <- data[[xvar]]
+  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
+}
+
+summarise_fit <- function(x) {
+  data.frame(
+    select(glance(x), r.squared, p.value),
+    n= length(resid(x)),
+    a = coef(x)[1],
+    b = coef(x)[2]
+  )
+}
+
+summarise_all_fits <- function(x) {
+  tmp <- lapply(x, summarise_fit) %>%
+    bind_rows
+  data.frame(species=names(x), tmp)
+}
+```
+
+#RV curves
+```{r, echo=FALSE,results='hide', message=FALSE}
+yvar <- "ReproInv"
+xvar <- "FinalWeight"
+
+data <- filter(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,plot_LLvAge <- function(spp) {
+  data2 <- filter(SummaryInd, species==spp)
+  plot(LL_birth ~ age, data=data2, xlab="age", ylab="leaf lifespan (leaf births)", cex.axis=.8, las=1,
+       main=labels.spp[spp], xlim=c(1,35), ylim=c(0,8), log="x", pch=16)
+  points(LL_birth_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8)
+  points((LL_birth_mean+LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=25)
+  points((LL_birth_mean-LL_birth_se) ~ age, data=subset(SummarySppAge, species==spp), cex=1.5, pch=24)
+                    main=spp, log="xy",xlab=xvar, ylab=yvar)
+
+  abline(lmfits[[spp]])
+}
+```

### 2015-04-22 scripts/summary_dataframes.R

@@ -11,6 +11,7 @@ seedsize <- seedSize_raw %>%
 
 individuals <- IndividualsList
 
+axis_labels <- read_csv("data/axis_labels.csv")
 
 harvest <- filter(HarvestData,
                   individuals$use_for_allocation_calculations[match(HarvestData$individual, individuals$individual)] & segment==1 & start_end=="end") %>%
@@ -117,6 +118,8 @@ SummaryInd$change_shoot_area <- (3.14*((SummaryInd$d_end/2)^2)) - (3.14*((Summar
 SummaryInd$change_basal_area <- (3.14*((SummaryInd$FinalBasalDiam/2)^2)) - (3.14*((SummaryInd$StartBasalDiam/2)^2))
 SummaryInd$lvs_end_total <- SummaryInd$lvs_end + SummaryInd$lvs_new
 SummaryInd$RGR <- log(SummaryInd$FinalWeight)-log(SummaryInd$FinalWeight-SummaryInd$GrowthInv)
+SummaryInd$PrePol_All <- SummaryInd$PrePol_A + SummaryInd$PrePol_S
+SummaryInd$PerPrePol_All <- SummaryInd$PerPrePol_A + SummaryInd$PerPrePol_S
 
 #summarizing data by species, age
 

### 2015-04-23 Accessory_results.rmd
small work on Accessory tissue results

--- 2015-04-22 scripts/Accessory_results.rmd
@@
+```{r, echo=FALSE,results='hide', message=FALSE}
+library(remake)
+create_bindings()
+
+source("scripts/summary_dataframes.R")
+```
+
 #Accessory costs
@@
 
-plot_yvar_vs_xvar(data, yvar, xvar,
-                  xlab=xvar, ylab=yvar)
+plot_yvar_vs_xvar(data, yvar, xvar)
 mod <- lm(asin(sqrt(PerPropagule)) ~ species, data)
@@
 COER, HATE, and PILI show a significant decrease in accessory costs with increasing size (p<0.05)
-GRSP, PILI shows a marginally significant decrease in accessory costs with increasing size (0.05<p<0.10)
+GRSP shows a marginally significant decrease in accessory costs with increasing size (0.05<p<0.10)
 PEPU shows a marginally significant INCREASE in accessory costs with increasing size (0.05<p<0.10)
@@
 PerAcc is arcsine transformed, age is log transformed
-BOLE, COER, HATE, HEPU, PELA show a significant decrease in accessory costs with increasing age (p<0.05)
-EPMI, GRSP, HATE shows a marginally significant decrease in accessory costs with increasing age (0.05<p<0.10)
+BOLE, COER, GRSP, HATE, HEPU, PELA show a significant decrease in accessory costs with increasing age (p<0.05)
+EPMI, GRBU shows a marginally significant decrease in accessory costs with increasing age (0.05<p<0.10)
 PUTU shows a sig INCREASE in accessory costs with increasing age
@@
 PerPrePol_A is arcsine transformed, size is log transformed
-GRSP, HATE, HEPU, PUTU show a significant decrease in aborted buds with increasing size (p<0.05)
+GRSP, HATE, HEPU show a significant decrease in aborted buds with increasing size (p<0.05)
+PUTU shows a marginally significant decrease in accessory costs with increasing RA (p ~ 0.10)
 ```{r, echo=FALSE,results='hide', message=FALSE}
@@
 both RA and PerPrePol_All are arcsine transformed
-BAER, BOLE, COER, GRSP, HATE, HEPU, LEES, PELA, PEPU show a significant decrease in total pre-pollination costs with increasing RA (p<0.05)
+BAER, BOLE, COER, GRSP, HATE, HEPU, LEES, PEPU show a significant decrease in total pre-pollination costs with increasing RA (p<0.05)
+PELA shows a marginally significant decrease in total pre-pollination costs with increasing RA (0.05<p<0.10)
 ```{r, echo=FALSE,results='hide', message=FALSE}
@@
 COER, GRBU, GRSP, HATE, PEPU, PHPH, PILI show a significant decrease in total pre-pollination costs with increasing reproductive investment (p<0.05)
-LEES and PELA show a marginally significant decrease in total pre-pollination costs with increasing reproductive investment (0.05<p<0.10)
+LEES shows a marginally significant decrease in total pre-pollination costs with increasing reproductive investment (0.05<p<0.10)
 ```{r, echo=FALSE,results='hide', message=FALSE}

### 2015-04-23 scripts/results_leaf_lifespan.rmd
updated analyses for leaf lifespan and LMA data with more detailed results descriptions

```{r, echo=FALSE,results='hide', message=FALSE}
library(remake)
create_bindings()

source("scripts/summary_dataframes.R")
```

#Leaf lifespan data
General results:

#Generic functions for most plotting below
```{r, echo=FALSE,results='hide', message=FALSE}
plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
  Y <- data[[yvar]]
  X <- data[[xvar]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

summarise_fit <- function(x) {
  data.frame(
    select(glance(x), r.squared, p.value),
    n= length(resid(x)),
    a = coef(x)[1],
    b = coef(x)[2]
  )
}

summarise_all_fits <- function(x) {
  tmp <- lapply(x, summarise_fit) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}
```

#First issue is how to calculate leaf lifespan
A plot of leaf lifespan calculated using birth of leaves, death of leaves, and the mean of the two shows they are poorly correlated, even when the youngest plants are omitted

```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LL_birth"
xvar <- "LL_death"
data <- filter(SummaryInd, age>2, LL_birth<10&LL_death<10)

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar,col=col.spp[as.factor(data$species)])
legend("bottomright",legend=labels.spp,pch=16,col=col.spp,bty="n",cex=.8)
mod <- lm(LL_birth~LL_death + age,data=data)
anova(mod)

yvar <- "LL_birth"
xvar <- "LL_bd"
data <- filter(SummaryInd, age>2, LL_birth<10&LL_death<10)

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar, ,col=col.spp[as.factor(data$species)])
legend("bottomright",legend=labels.spp,pch=16,col=col.spp,bty="n",cex=.8)
mod <- lm(LL_birth~LL_bd,data=data)
summary(mod)

yvar <- "LL_death"
xvar <- "LL_bd"
data <- filter(SummaryInd, age>2, LL_birth<10&LL_death<10)

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar,col=col.spp[as.factor(data$species)])
legend("bottomright",legend=labels.spp,pch=16,col=col.spp,bty="n",cex=.8)
mod <- lm(LL_death~LL_bd,data=data)
summary(mod)
```

#Starting with the basics: Are leaf lifespan and LMA correlated?
Plotting species*site means
Figures shown using all three measures of leaf lifespan
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LMA_mean"
xvar <- "LL_death_mean"
data <- filter(SummarySppAge)

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar,col=col.spp[as.factor(data$species)])
legend("bottomright",legend=labels.spp,pch=16,col=col.spp,bty="n",cex=.8)
mod <- lm(LL_death_mean~LMA_mean,data=data)
summary(mod)

yvar <- "LMA_mean"
xvar <- "LL_birth_mean"
data <- filter(SummarySppAge)

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar,col=col.spp[as.factor(data$species)])
legend("bottomright",legend=labels.spp,pch=16,col=col.spp,bty="n",cex=.8)
mod <- lm(LL_birth_mean~LMA_mean,data=data)
summary(mod)

yvar <- "LMA_mean"
xvar <- "LL_bd_mean"
data <- filter(SummarySppAge)

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar,col=col.spp[as.factor(data$species)])
legend("bottomright",legend=labels.spp,pch=16,col=col.spp,bty="n",cex=.8)
mod <- lm(LL_bd_mean~LMA_mean,data=data)
summary(mod)
```

#Same plots as above, but omitting HATE, which has much higher LMA than any other species due to its round "leaves"
Using leaf deaths gives the poorest fit...
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LMA_mean"
xvar <- "LL_death_mean"
data <- filter(SummarySppAge, species!="HATE")

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar,col=col.spp[as.factor(data$species)])
legend("bottomright",legend=labels.spp.noHATE,pch=16,col=col.spp.noHATE,bty="n",cex=.8)
mod <- lm(LL_death_mean~LMA_mean+species,data=data)
summary(mod)
anova(mod)

yvar <- "LMA_mean"
xvar <- "LL_birth_mean"
data <- filter(SummarySppAge, species!="HATE")

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar,col=col.spp[as.factor(data$species)])
legend("bottomright",legend=labels.spp.noHATE,pch=16,col=col.spp.noHATE,bty="n",cex=.8)
mod <- lm(LL_birth_mean~LMA_mean+species,data=data)
summary(mod)
anova(mod)

yvar <- "LMA_mean"
xvar <- "LL_bd_mean"
data <- filter(SummarySppAge, species!="HATE")

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar,col=col.spp[as.factor(data$species)])
legend("bottomright",legend=labels.spp.noHATE,pch=16,col=col.spp.noHATE,bty="n",cex=.8)
mod <- lm(LL_bd_mean~LMA_mean+species,data=data)
summary(mod)
anova(mod)

yvar <- "LMA_mean"
xvar <- "LL_death_mean"
data <- filter(SummarySpp)

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar)
text(LMA_mean ~LL_death_mean, data=data, labels=SummarySpp$species, pos=1, offset=-1.1, cex=0.9,col="blue")
mod <- lm(LL_death_mean~LMA_mean,data=subset(data,species!="HATE"))
summary(mod)
```

#How does leaf lifespan change with age and size across all species and within each species
Using leaf deaths for the following plots and removing the youngest individuals

Age is log transformed.
BAER, HEPU, PUTU show a significant DECREASE in leaf lifespan with increasing age (p<0.05)
LEES, PEPU shows a marginally significant DECREASE in accessory costs with increasing age (0.05<p<0.10)
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LL_death"
xvar <- "age"
data <- filter(SummaryInd,LL_death<10&age>2)

data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(x[[yvar]] ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=3)
results$b <- round(results$b,digits=3)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

And using size...
Size is log transformed.
BAER, COER, EPMI show a significant DECREASE in leaf lifespan with increasing size (p<0.05)
PEPU, PHPH show a marginally significant DECREASE in accessory costs with increasing size (0.05<p<0.10)

If leaf lifespan based on leaf births is used instead, there are a number of significant INCREASES in leaf lifespan with increasing size
```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LL_death"
xvar <- "FinalWeight"
data <- filter(SummaryInd,LL_death<8&age>2)

data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(x[[yvar]] ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=3)
results$b <- round(results$b,digits=3)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#Higher growth rates correlated with lower leaf lifespan in a handful of species
BAER, EPMI, PEPU show declining LL and COER shows marginally significant decline with increasing absolute growth investment.

```{r, echo=FALSE,results='hide', message=FALSE}
yvar <- "LL_death"
xvar <- "GrowthInv"
data <- filter(SummaryInd,LL_death<8&age>2)

data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(x[[yvar]] ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=3)
results$b <- round(results$b,digits=3)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#Putting age and speices together in a model shows, not surprisingly, that both age and species contribute to the variation and that species matters much more.
```{r, echo=FALSE,results='hide', message=FALSE}
plot(LL_death ~ age, data=SummaryInd, cex.axis=.8, las=1, xlim=c(1,35), ylim=c(.95,10), log="xy", pch=16,col=col.spp[as.factor(species)])
legend(14,8,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(LL_death~age*species, data=SummaryInd)
summary(mod)
anova(mod)
```

#Plotting leaf lifespan against the number of leaves on a branch shows that for the babies, "LL_birth" is negatively correlated with the number of leaves - i.e. the shoots grow a lot during the year and the more they grow the lower the LL, because there are so few leaves to begin with. Indicates that for "LL_birth", but not "LL_death", the youngest site should be omitted

However for LL_death most species show a positive correlation between number of leaves on the leader and leaf lifespan. For some species this is driven by a few individuals with high LL_death values, but 6 species still significant when LL > 6 removed (and 4 more species near-significant).

This trend worries me - is leaf count very variable across years?

```{r, echo=FALSE,results='hide', message=FALSE}
plot(LL_death ~ lvs_end_total, data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(LL_birth ~ lvs_end_total, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(LL_death ~ lvs_end_total, SummaryInd, log="xy",col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

plot(LL_birth ~ lvs_end_total, data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

mod <- lm(LL_death ~ lvs_end_total*species*age, SummaryInd)
summary(mod)
anova(mod)
step(mod)

mod2 <- lm(formula = LL_death ~ lvs_end_total + species + age + lvs_end_total:species + 
    species:age, data = SummaryInd)
summary(mod2)
anova(mod2)

yvar <- "LL_death"
xvar <- "lvs_end_total"
data <- filter(SummaryInd,LL_death<6)

data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(x[[yvar]] ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=3)
results$b <- round(results$b,digits=3)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#Plotting LMA vs. age
older plants have marginally higher LMA, but the effect mostly disappears when the youngest plants are excluded
there is enormous variation in LMA across species

```{r, echo=FALSE,results='hide', message=FALSE}
mod <- lm(LMA_mean~species*age, SummarySppAge)
summary(mod)
anova(mod)

mod <- lm(LMA_mean~species*age, data=subset(SummarySppAge,age>2))
summary(mod)
anova(mod)

plot(LMA_mean ~age, SummarySppAge, log="xy", col=col.spp[as.factor(species)], pch=16)
#text(LMA_mean~age, data=subset(SummarySppAge,age==5), labels=SummarySpp$species, pos=4, offset=.5, cex=0.7,col="blue")
legend(12,.04,col=col.spp, pch=16,legend=labels.spp,cex=.8,bty="n")
```

#Plotting LMA vs. weight
There is a stronger trend with respect to weight, even after the effect of species is taken into account

The interactions terms weren't significant and were removed from the model
```{r, echo=FALSE,results='hide', message=FALSE}
mod <- lm(LMA_mean~species+log(FinalWeight_mean), SummarySppAge)
summary(mod)
anova(mod)

mod <- lm(LMA_mean~species+log(FinalWeight_mean), data=subset(SummarySppAge,age>2))
summary(mod)
anova(mod)

plot(LMA_mean ~FinalWeight_mean, SummarySppAge, log="xy", col=col.spp[as.factor(species)], pch=16)
legend("topleft",col=col.spp, pch=16,legend=labels.spp,cex=.8,bty="n")

plot(LMA_mean ~FinalWeight_mean, data=subset(SummarySppAge), log="xy", col=col.age[as.factor(age)], pch=16, cex=1)
legend("topleft",col=col.age, pch=16,legend=labels.age,cex=.8,bty="n")

```

```{r, echo=FALSE,results='hide', message=FALSE}

```

### 2015-04-28 results_RAschedules.Rmd
mostly looking at growth patterns

```{r, echo=FALSE,results='hide', message=FALSE}
library(remake)
create_bindings()

source("scripts/summary_dataframes.R")
```
#RV curves and RA schedules, general patterns

#Generic functions for most plotting below
```{r, echo=FALSE, message=FALSE}
plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
  Y <- data[[yvar]]
  X <- data[[xvar]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

summarise_fit <- function(x) {
  data.frame(
    select(glance(x), r.squared, p.value),
    n= length(resid(x)),
    a = coef(x)[1],
    b = coef(x)[2]
  )
}

summarise_all_fits <- function(x) {
  tmp <- lapply(x, summarise_fit) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}
```

#RV curves
```{r, echo=FALSE,message=FALSE}
plot(ReproInv~FinalWeight, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(ReproInv~FinalWeight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

plot((1+ReproInv_mean)~FinalWeight_mean,SummarySppAge,log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "ReproInv"
xvar <- "FinalWeight"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="xy", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#RV curves (by age)
```{r, echo=FALSE,message=FALSE}
plot(ReproInv~age, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend(15,5000,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot((1+ReproInv_mean)~age,SummarySppAge,log="xy", col=col.spp[as.factor(species)],pch=16)
legend(15,5000,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "ReproInv"
xvar <- "age"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="xy", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#RA schedules (by age)
```{r, echo=FALSE,message=FALSE}
plot(RA~age, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
legend(15,.9,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(RA_mean~age,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
legend(15,.5,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "RA"
xvar <- "age"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#RA schedules (by size)
```{r, echo=FALSE,message=FALSE}
plot(RA~FinalWeight, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(RA_mean~FinalWeight_mean,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "RA"
xvar <- "FinalWeight"

data <- SummaryInd
data <- split(data, data$species)

lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#Reproductive Investment by Growth Investment
```{r, echo=FALSE,message=FALSE}
plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

plot((1+ReproInv_mean)~GrowthInv_mean,SummarySppAge,log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "ReproInv"
xvar <- "GrowthInv"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="xy", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#RA by Growth Investment
```{r, echo=FALSE,message=FALSE}
plot(RA~GrowthInv, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(RA~GrowthInv, SummaryInd, log="x", col=col.age[as.factor(age)],pch=16)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

plot(RA_mean~GrowthInv_mean,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "RA"
xvar <- "GrowthInv"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#Reproductive Investment by scaled height 
For these calculations, height is scaled relative to max height. This should be a way to determine RSOM - RSOM would be the PropH at which Reproductive Investment begins.

```{r, echo=FALSE, message=FALSE}
plot((1+ReproInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot((1+ReproInv)~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "PropH"
xvar <- "ReproInv"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]]+1)))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

```{r, echo=FALSE, message=FALSE}
plot((RA~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(RA~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "RA"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

#Growth Investment versus proportion max H
This turns out to be one of the most interesting sets of graphs
For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH
For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)
Quite interesting, there is a distinctly negative relationship for GRBU
For many of the species with a good relationship, it seems that there are two breakpoints in the curve - wondering what these mean with respect to reproductive onset and RA

```{r, echo=FALSE, message=FALSE}
plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(GrowthInv~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "GrowthInv"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}
```

These plots show very clearly that for all species RGR suddenly dips when RA becomes non-zero. Plotting against "FinalWeight" or "GrowthInvestment" is much less clear - in other words, an individual's height is the best way to sort them into plants investing more in growth vs reproduction. There are of course some non-reproductive plants with "PropH" above the obvious cut-off, but these are almost certainly "reproductively mature" plants not reproducing in a given year.

The canopy species have, not suprisingly, a very obvious maxH, with Growth Investment or RGR tapering markedly at the maxH is approached. In these species growth investment is poorly correlated with RA, but well correlated with height.
In some of the mid-height species (GRSP, BOLE, GRBU), growth investment is very poorly correlated with height, but well correlated with RA - in other words, increased RA = less growth.
Some species are correated with neither.

Now my current analyses still lack the ability to tease apart the most obvious pattern - because I don't actually want to show that growth and height are correlated, so much as that the asymptoting of growth is correlated with height - i.e. the change in slope of the relationship.

```{r, echo=FALSE, message=FALSE}
yvar <- "GrowthInv"
xvar <- "RA"
x2var <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])+(x[[x2var]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)
  abline(lmfits[[spp]])
}
```

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="BOLE"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="GRBU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="GRSP"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PELA"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="HATE"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="BAER"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PEPU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="EPMI"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="LEES"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PHPH"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PUTU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="HEPU"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PILI"))
summary(mod)
anova(mod)

mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="COER"))
summary(mod)
anova(mod)
```{r, echo=FALSE, message=FALSE}
plot((RGR~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "RGR"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)
  abline(lmfits[[spp]])
}
```

#Plotting RGR and RA vs. proportion maxH and simply RA vs RGR

```{r, echo=FALSE, message=FALSE}
plot(RGR~PropH,data=subset(SummaryInd, species=="BAER"),pch=16, col="black")
points((5*RA)~PropH,data=subset(SummaryInd, species=="BAER"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="HATE"),pch=16, col="black")
points((10*RA)~PropH,data=subset(SummaryInd, species=="HATE"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="EPMI"),pch=16, col="black")
points((5*RA)~PropH,data=subset(SummaryInd, species=="EPMI"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="PEPU"),pch=16, col="black")
points((3*RA)~PropH,data=subset(SummaryInd, species=="PEPU"),pch=16, col="red")

plot(RGR~PropH,data=subset(SummaryInd, species=="BOLE"),pch=16, col="black")
points((3*RA)~PropH,data=subset(SummaryInd, species=="BOLE"),pch=16, col="red")

plot((1/RGR)~(RA),SummaryInd,log="y",col=col.spp[as.factor(species)],pch=16)
plot((RGR)~(RA),data=subset(SummaryInd,species=="BOLE"),log="y",col=col.spp[as.factor(species)],pch=16)
mod <- lm(RA~log(RGR),data=subset(SummaryInd,species=="BOLE"))
summary(mod)

yvar <- "GrowthInv"
xvar <- "RA"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                    main=spp, xlab=xvar, ylab=yvar)
  abline(lmfits[[spp]])
}

### 2015-04-28 results_growth.Rmd
mostly looking at growth patterns

--- 2015-04-28 results_RAschedules.Rmd
@@
 ```
-#RV curves and RA schedules, general patterns
+#Growth data, general patterns
 
@@
 
-#RV curves
-```{r, echo=FALSE,message=FALSE}
-plot(ReproInv~FinalWeight, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```{r, echo=FALSE, message=FALSE}
+yvar <- ""
+xvar <- ""
+data <- filter(SummaryInd,
 
-plot(ReproInv~FinalWeight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
-legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+plot_yvar_vs_xvar(data, yvar, xvar,
+                  xlab=xvar, ylab=yvar)
 
-plot((1+ReproInv_mean)~FinalWeight_mean,SummarySppAge,log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-yvar <- "ReproInv"
-xvar <- "FinalWeight"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, log="xy", xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
-```
-
-#RV curves (by age)
-```{r, echo=FALSE,message=FALSE}
-plot(ReproInv~age, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend(15,5000,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-plot((1+ReproInv_mean)~age,SummarySppAge,log="xy", col=col.spp[as.factor(species)],pch=16)
-legend(15,5000,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-yvar <- "ReproInv"
-xvar <- "age"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, log="xy", xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
-```
-
-#RA schedules (by age)
-```{r, echo=FALSE,message=FALSE}
-plot(RA~age, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
-legend(15,.9,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-plot(RA_mean~age,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
-legend(15,.5,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-yvar <- "RA"
-xvar <- "age"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, log="x", xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
-```
-
-#RA schedules (by size)
-```{r, echo=FALSE,message=FALSE}
-plot(RA~FinalWeight, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-plot(RA_mean~FinalWeight_mean,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-yvar <- "RA"
-xvar <- "FinalWeight"
-
-data <- SummaryInd
-data <- split(data, data$species)
-
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, log="x", xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
-```
-
-#Reproductive Investment by Growth Investment
-```{r, echo=FALSE,message=FALSE}
-plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
-legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
-
-plot((1+ReproInv_mean)~GrowthInv_mean,SummarySppAge,log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-yvar <- "ReproInv"
-xvar <- "GrowthInv"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, log="xy", xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
-```
-
-#RA by Growth Investment
-```{r, echo=FALSE,message=FALSE}
-plot(RA~GrowthInv, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-plot(RA~GrowthInv, SummaryInd, log="x", col=col.age[as.factor(age)],pch=16)
-legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
-
-plot(RA_mean~GrowthInv_mean,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-yvar <- "RA"
-xvar <- "GrowthInv"
-
-data <- subset(SummaryInd,RA>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, log="x", xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
-```
-
-#Reproductive Investment by scaled height 
-For these calculations, height is scaled relative to max height. This should be a way to determine RSOM - RSOM would be the PropH at which Reproductive Investment begins.
-
-```{r, echo=FALSE, message=FALSE}
-plot((1+ReproInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-plot((1+ReproInv)~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
-legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
-
-yvar <- "PropH"
-xvar <- "ReproInv"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]]+1)))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, log="x", xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
+summary(mod)
+anova(mod)
 ```
@@
 ```{r, echo=FALSE, message=FALSE}
-plot((RA~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(RA~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
-
-yvar <- "RA"
-xvar <- "PropH"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
 ```
-
-#Growth Investment versus proportion max H
-This turns out to be one of the most interesting sets of graphs
-For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH
-For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)
-Quite interesting, there is a distinctly negative relationship for GRBU
-For many of the species with a good relationship, it seems that there are two breakpoints in the curve - wondering what these mean with respect to reproductive onset and RA
-
-```{r, echo=FALSE, message=FALSE}
-plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-plot(GrowthInv~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
-
-yvar <- "GrowthInv"
-xvar <- "PropH"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
-                    main=spp, xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
-```
-
-These plots show very clearly that for all species RGR suddenly dips when RA becomes non-zero.
-Plotting against "FinalWeight" or "GrowthInvestment" is much less clear - in other words, an individual's height is the best way to sort them into plants investing more in growth vs reproduction.
-There are of course some non-reproductive plants with "PropH" above the obvious cut-off, but these are almost certainly "reproductively mature" plants not reproducing in a given year.
-
-The canopy species have, not suprisingly, a very obvious maxH, with Growth Investment or RGR tapering markedly at the maxH is approached.
-In these species growth investment is poorly correlated with RA, but well correlated with height.
-In some of the mid-height species (GRSP, BOLE, GRBU), growth investment is very poorly correlated with height, but well correlated with RA - in other words, increased RA = less growth.
-Some species are correated with neither.
-
-Now my current analyses still lack the ability to tease apart the most obvious pattern - because I don't actually want to show that growth and height are correlated, so much as that the asymptoting of growth is correlated with height - i.e.
-the change in slope of the relationship.
-
-```{r, echo=FALSE, message=FALSE}
-yvar <- "GrowthInv"
-xvar <- "RA"
-x2var <- "PropH"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])+(x[[x2var]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
-                    main=spp, xlab=xvar, ylab=yvar)
-  abline(lmfits[[spp]])
-}
-```
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="BOLE"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="GRBU"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="GRSP"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PELA"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="HATE"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="BAER"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PEPU"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="EPMI"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="LEES"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PHPH"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PUTU"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="HEPU"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PILI"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="COER"))
-summary(mod)
-anova(mod)
-```{r, echo=FALSE, message=FALSE}
-plot((RGR~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-yvar <- "RGR"
-xvar <- "PropH"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
-                    main=spp, xlab=xvar, ylab=yvar)
-  abline(lmfits[[spp]])
-}
-```
-
-#Plotting RGR and RA vs. proportion maxH and simply RA vs RGR
-
-```{r, echo=FALSE, message=FALSE}
-plot(RGR~PropH,data=subset(SummaryInd, species=="BAER"),pch=16, col="black")
-points((5*RA)~PropH,data=subset(SummaryInd, species=="BAER"),pch=16, col="red")
-
-plot(RGR~PropH,data=subset(SummaryInd, species=="HATE"),pch=16, col="black")
-points((10*RA)~PropH,data=subset(SummaryInd, species=="HATE"),pch=16, col="red")
-
-plot(RGR~PropH,data=subset(SummaryInd, species=="EPMI"),pch=16, col="black")
-points((5*RA)~PropH,data=subset(SummaryInd, species=="EPMI"),pch=16, col="red")
-
-plot(RGR~PropH,data=subset(SummaryInd, species=="PEPU"),pch=16, col="black")
-points((3*RA)~PropH,data=subset(SummaryInd, species=="PEPU"),pch=16, col="red")
-
-plot(RGR~PropH,data=subset(SummaryInd, species=="BOLE"),pch=16, col="black")
-points((3*RA)~PropH,data=subset(SummaryInd, species=="BOLE"),pch=16, col="red")
-
-plot((1/RGR)~(RA),SummaryInd,log="y",col=col.spp[as.factor(species)],pch=16)
-plot((RGR)~(RA),data=subset(SummaryInd,species=="BOLE"),log="y",col=col.spp[as.factor(species)],pch=16)
-mod <- lm(RA~log(RGR),data=subset(SummaryInd,species=="BOLE"))
-summary(mod)
-
-yvar <- "GrowthInv"
-xvar <- "RA"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
-                    main=spp, xlab=xvar, ylab=yvar)
-  abline(lmfits[[spp]])
-}

### 2015-04-28 results_leaf_lifespan.rmd
mostly looking at growth patterns

--- 2015-04-23 scripts/results_leaf_lifespan.rmd
@@
 General results:
+  - Leaf lifespan increases from seedlings (1.4 yrs) to saplings (2.4 years) to adults (>4 years), but there are no differences between the different adult populations
+  - Species differ en
 
@@
 
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE, message=FALSE}
 yvar <- "LL_birth"
@@
 plot_yvar_vs_xvar(data, yvar, xvar,
-                  xlab=xvar, ylab=yvar, ,col=col.spp[as.factor(data$species)])
+                  xlab=xvar, ylab=yvar,col=col.spp[as.factor(data$species)])
 legend("bottomright",legend=labels.spp,pch=16,col=col.spp,bty="n",cex=.8)
@@
 Figures shown using all three measures of leaf lifespan
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 yvar <- "LMA_mean"
@@
 Using leaf deaths gives the poorest fit...
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 yvar <- "LMA_mean"
@@
 LEES, PEPU shows a marginally significant DECREASE in accessory costs with increasing age (0.05<p<0.10)
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 yvar <- "LL_death"
@@
 If leaf lifespan based on leaf births is used instead, there are a number of significant INCREASES in leaf lifespan with increasing size
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 yvar <- "LL_death"
@@
 
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 yvar <- "LL_death"
@@
 #Putting age and speices together in a model shows, not surprisingly, that both age and species contribute to the variation and that species matters much more.
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 plot(LL_death ~ age, data=SummaryInd, cex.axis=.8, las=1, xlim=c(1,35), ylim=c(.95,10), log="xy", pch=16,col=col.spp[as.factor(species)])
@@
 
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 plot(LL_death ~ lvs_end_total, data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)],pch=16)
@@
 
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 mod <- lm(LMA_mean~species*age, SummarySppAge)
@@
 The interactions terms weren't significant and were removed from the model
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 mod <- lm(LMA_mean~species+log(FinalWeight_mean), SummarySppAge)
@@
 
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 

### 2015-04-29 results_RAschedules.Rmd
Continuing to explore patterns of RA, RGR, growth, repro investment Strong correlations between shifts in growth vs. repro and height (within species) is particularly interesting - "cleaner" RA schedules against height than age or weight

@@
 #RV curves and RA schedules, general patterns
+- RA best plotted against height for many species - much clearer pattern than against weight or age - this seems to support Daniel's suspicion that deadwood shouldn't be included in the "weight" of the plant
+- A number of species show an abrupt decrease in RGR (or tapering of growth investment) at the height where reproduction begins. This is evidence of the growth-reproduction trade-off
+- RV curves are mostly quite pretty, but not necessarily very meaningful
 
@@
 }
+
+summarise_fit_2var <- function(x) {
+  data.frame(
+    select(glance(x), r.squared, p.value),
+    n= length(resid(x)),
+    intercept = coef(x)[1],
+    coef_var1 = coef(x)[2],
+    coef_var2 = coef(x)[3],
+    coef_var1var2 = coef(x)[4],
+    SS_var1 = anova(x)[1,2],
+    SS_var2 = anova(x)[2,2],
+    SS_var1var2 =anova(x)[3,2]
+      )
+}
+
+summarise_all_fits_2var <- function(x) {
+  tmp <- lapply(x, summarise_fit_2var) %>%
+    bind_rows
+  data.frame(species=names(x), tmp)
+}
 ```
@@
 #RV curves
+These are mostly reasonably nice - of course need to fit quadratic curve to these and haven't figured out how to do it correctly
+
 ```{r, echo=FALSE,message=FALSE}
@@
                     main=spp, log="xy", xlab=xvar, ylab=yvar)
+
+  abline(lmfits[[spp]])
+}
+```
+
+#RA schedules (vs. propH)
+- these curves are particularly good for a number of species such as EPMI, COER, PELA
+- they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing propH
+
+```{r, echo=FALSE, message=FALSE}
+plot((RA~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+plot(RA~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+
+yvar <- "RA"
+xvar <- "PropH"
+
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
+                    main=spp, xlab=xvar, ylab=yvar)
 
@@
 #Reproductive Investment by Growth Investment
+Overall, these are not a strong set of results, but HATE shows a very strong relationship that shows reproductive investment (not growth investment) asymptoting
+Interestingly, PHPH, which is generally a complete scatter plot, has one of the strongest correlations between these variables, indicating that indeed most measures of "size" for this multi-stemmed plant aren't very meaningful and it should be analyzed differently.
+
+Note that the analyses are just being done on reproducing individuals at the moment.
 ```{r, echo=FALSE,message=FALSE}
@@
 
-yvar <- "ReproInv"
-xvar <- "GrowthInv"
+yvar <- "GrowthInv"
+xvar <- "ReproInv"
 
-data <- SummaryInd
+data <- subset(SummaryInd,RA>0)
 data <- split(data, data$species)
@@
 #RA by Growth Investment
+Across all species, high RA = low growth investment.
+This pattern exists mostly because of shifts in species from high reproducers to high growers - i.e.
+BOLE in one corner, and BAER & HATE in another.
+For analyses within individual species
 ```{r, echo=FALSE,message=FALSE}
@@
 
-yvar <- "RA"
-xvar <- "GrowthInv"
+plot(GrowthInv~RA, data=subset(SummaryInd,RA>0), log="y", col=col.spp[as.factor(species)],pch=16)
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+mod <- lm(log(GrowthInv)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
+summary(mod)
+plot(mod)
+
+yvar <- "GrowthInv"
+xvar <- "RA"
 
@@
 data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))))
 results <- summarise_all_fits(lmfits)
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, log="x", xlab=xvar, ylab=yvar)
+                    main=spp, log="xy", xlab=xvar, ylab=yvar)
 
@@
 
-#Reproductive Investment by scaled height 
-For these calculations, height is scaled relative to max height. This should be a way to determine RSOM - RSOM would be the PropH at which Reproductive Investment begins.
-
-```{r, echo=FALSE, message=FALSE}
-plot((1+ReproInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
+#RA vs RGR - 
+similar to the plots of RA vs Growth Investment, but relationships stronger. For these plots, all but one species (PEPU) have a significantly negative slope
+the results are more of less the same regardless of whether one includes or excluded individuals where RA=0
+```{r, echo=FALSE,message=FALSE}
+plot(RA~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot((1+ReproInv)~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
+plot(RA~RGR, SummaryInd, log="x", col=col.age[as.factor(age)],pch=16)
 legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
 
-yvar <- "PropH"
-xvar <- "ReproInv"
+plot(RA_mean~GrowthInv_mean,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
+legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-data <- SummaryInd
+plot(RGR~RA, data=subset(SummaryInd,RA>0), log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+mod <- lm(log(GrowthInv)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
+summary(mod)
+plot(mod)
+
+yvar <- "RGR"
+xvar <- "RA"
+
+data <- subset(SummaryInd,RA>0)
 data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]]+1)))
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))))
 results <- summarise_all_fits(lmfits)
@@
 
+#Reproductive Investment by scaled height 
+For these calculations, height is scaled relative to max height. This should be a way to determine RSOM - RSOM would be the PropH at which Reproductive Investment begins.
+For species such as BOLE which begin reproduction so young, data could be included that have pre-reproductive heights from mid-year censuses of "babies"
+
 ```{r, echo=FALSE, message=FALSE}
 plot((RA~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(RA~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+plot((RA)~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
+legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
 
@@
 
-data <- SummaryInd
+data <- subset(SummaryInd)
 data <- split(data, data$species)
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
-```
-
-#Growth Investment versus proportion max H
-This turns out to be one of the most interesting sets of graphs
-For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH
-For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)
-Quite interesting, there is a distinctly negative relationship for GRBU
-For many of the species with a good relationship, it seems that there are two breakpoints in the curve - wondering what these mean with respect to reproductive onset and RA
-
-```{r, echo=FALSE, message=FALSE}
-plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-plot(GrowthInv~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
-
-yvar <- "GrowthInv"
-xvar <- "PropH"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
                     main=spp, xlab=xvar, ylab=yvar)
@@
 data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])+(x[[x2var]])))
-results <- summarise_all_fits(lmfits)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))*asin(sqrt(x[[x2var]]))))
+results <- summarise_all_fits_2var(lmfits)
 
@@
 ```
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="BOLE"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="GRBU"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="GRSP"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PELA"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="HATE"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="BAER"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PEPU"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="EPMI"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="LEES"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PHPH"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PUTU"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="HEPU"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="PILI"))
-summary(mod)
-anova(mod)
-
-mod <- lm(GrowthInv~PropH*RA,data=subset(SummaryInd, species=="COER"))
-summary(mod)
-anova(mod)
-```{r, echo=FALSE, message=FALSE}
-plot((RGR~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-yvar <- "RGR"
-xvar <- "PropH"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
-                    main=spp, xlab=xvar, ylab=yvar)
-  abline(lmfits[[spp]])
-}
-```
-
-#Plotting RGR and RA vs. proportion maxH and simply RA vs RGR
-
-```{r, echo=FALSE, message=FALSE}
-plot(RGR~PropH,data=subset(SummaryInd, species=="BAER"),pch=16, col="black")
-points((5*RA)~PropH,data=subset(SummaryInd, species=="BAER"),pch=16, col="red")
-
-plot(RGR~PropH,data=subset(SummaryInd, species=="HATE"),pch=16, col="black")
-points((10*RA)~PropH,data=subset(SummaryInd, species=="HATE"),pch=16, col="red")
-
-plot(RGR~PropH,data=subset(SummaryInd, species=="EPMI"),pch=16, col="black")
-points((5*RA)~PropH,data=subset(SummaryInd, species=="EPMI"),pch=16, col="red")
-
-plot(RGR~PropH,data=subset(SummaryInd, species=="PEPU"),pch=16, col="black")
-points((3*RA)~PropH,data=subset(SummaryInd, species=="PEPU"),pch=16, col="red")
-
-plot(RGR~PropH,data=subset(SummaryInd, species=="BOLE"),pch=16, col="black")
-points((3*RA)~PropH,data=subset(SummaryInd, species=="BOLE"),pch=16, col="red")
-
-plot((1/RGR)~(RA),SummaryInd,log="y",col=col.spp[as.factor(species)],pch=16)
-plot((RGR)~(RA),data=subset(SummaryInd,species=="BOLE"),log="y",col=col.spp[as.factor(species)],pch=16)
-mod <- lm(RA~log(RGR),data=subset(SummaryInd,species=="BOLE"))
-summary(mod)
-
-yvar <- "GrowthInv"
-xvar <- "RA"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
-                    main=spp, xlab=xvar, ylab=yvar)
-  abline(lmfits[[spp]])
-}

### 2015-04-29 results_growth.Rmd
Continuing to explore patterns of RA, RGR, growth, repro investment Strong correlations between shifts in growth vs. repro and height (within species) is particularly interesting - "cleaner" RA schedules against height than age or weight

@@
 #Growth data, general patterns
+- proportion of maxH matters more for some species than others. 
+1. The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  
+2. The lower-growing species are more variable, with "prop maxH mattering more for some than others"
+
+- For almost all species there is a strong negative relationship between RGR and RA - indeed, more reproduction = less growth  
+1. Meanwhile there is the strong positive relationship between growth investment and reproductive investment, because bigger plants grow and reproduce more.  
+2. It is good to have a big enough data set to capture both trends - and to capture them consistently across many species
+
+- Many plants have a clear upturn in RA and corresponding downturn in RGR at a specific prop maxH  
+1. e.g. see EPMI for distinct pattern
 
@@
 
+#Growth Investment versus proportion max H
+This turns out to be one of the most interesting sets of graphs
+For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH
+For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)
+Quite interesting, there is a distinctly negative relationship for GRBU
+For many of the species with a good relationship, it seems that there are two breakpoints in the curve - wondering what these mean with respect to reproductive onset and RA
+
+```{r, echo=FALSE, message=FALSE}
+plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+plot(GrowthInv~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+
+yvar <- "GrowthInv"
+xvar <- "PropH"
+
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
+                    main=spp, xlab=xvar, ylab=yvar)
+
+  abline(lmfits[[spp]])
+}
+```
+
+#A series of models by species showing the relative influence "RA" and "proportion of max H" have on growth investment.
+- These models show that the relative contribution of these two factors differs across species, with the 4 canopy species (PELA, HATE, BAER, PEPU) more influenced by height and other many of the species more influenced by RA.
+- This reflects in part, the fact that many of the "canopy" species show lots of year-to-year variation in reproductive output   
+- Across the board, most species have quite high R^2 values   
+- Model with RA, PropH, and species has R^2 = 0.8231
+
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(GrowthInv)~asin(sqrt(PropH))*asin(sqrt(RA))*species,data=subset(SummaryInd))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="BAER"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="BOLE"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="COER"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="EPMI"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="GRBU"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="GRSP"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="HATE"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="HEPU"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="LEES"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="PELA"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="PEPU"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="PHPH"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="PILI"))
+summary(mod)
+anova(mod)
+plot(mod)
+
+mod <- lm(log(GrowthInv)~PropH*asin(sqrt(RA)),data=subset(SummaryInd, species=="PUTU"))
+summary(mod)
+anova(mod)
+plot(mod)
+```
+
+#Proportion max H by RGR
+Excepting some outliers, RGR declines with increasing height  
+Except in a few species there is little pattern - HEPU, PILI  
+The species with a room correlation are mostly shorter ones that are presumably often broken off 
+These are continued ways to look at the question of how important is height (relative to the species maxH) in understanding its growth and reproduction
+
+```{r, echo=FALSE, message=FALSE}
+plot((RGR~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+yvar <- "RGR"
+xvar <- "PropH"
+
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
+                    main=spp, xlab=xvar, ylab=yvar)
+  abline(lmfits[[spp]])
+}
+```
+
+#Plots of Growth Inv versus weight - showing that slope continues to be 1:1, but intercept decreases with time because more standing biomass
+```{r, echo=FALSE, message=FALSE}
+plot((GrowthInv~FinalWeight), SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+abline(0,1,lwd=2)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+plot(GrowthInv~FinalWeight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
+abline(0,1,lwd=2)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+```
+
+#Plotting RA vs RGR
+Higher RA = lower RGR, for all species except PEPU  
+1. PEPU an exception because so few individuals reproducing and those that are reproducing have intermediate RGR - neither the young plants nor the older plants just hanging on
+2. PELA doesn't have a relationship either, because so few reproducing individuals. But if the many individuals with RA=0 added back in, strong negative relationship for PELA
+
 ```{r, echo=FALSE, message=FALSE}
 
+plot(RGR~RA,data=subset(SummaryInd,RA>0&RGR>.04),log="y",col=col.spp[as.factor(species)],pch=16)
+mod <-lm(log(RGR)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&RGR>.04))
+summary(mod)
+plot(mod)
+
+yvar <- "RGR"
+xvar <- "RA"
+
+data <- subset(SummaryInd, RA>0&RGR>.04)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
+                    main=spp, xlab=xvar, ylab=yvar)
+
+  abline(lmfits[[spp]])
+}
 ```

### 2015-04-30 results.Rmd
Continuing to explore patterns of RA, RGR, growth, repro investment Strong correlations between shifts in growth vs. repro and height (within species) is particularly interesting - "cleaner" RA schedules against height than age or weight
continuing to organize results

--- 2015-04-21 results.Rmd
@@
 
-# LMA versus age
-The plot below is a bulked LMA sample from each site, of leaves from the second most recent cohort
-
-There is a significant increase with age (p=0.002) and many species differ from one another, despite the very few points
-Age is only borderline significant (p=0.04) when the seedlings are removed
-
-```{r, echo=FALSE,results='hide', message=FALSE}
-plot(LMA~age,data=subset(LMA,branch_age=="mid"),log="xy", xlab="age",ylab="LMA",col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
-```
-
-# Leaf lifespan with age
-Leaf lifespan increases from seedlings (1.4 yrs) to saplings (2.4 years) to adults (>4 years), but there are no differences between the different adult populations
-```{r, echo=FALSE,results='hide', message=FALSE}
-plot(LL_birth~age,SummaryInd,log="xy", xlab="age",ylab="leaf lifespan (based on leaf births)",col=col.spp[as.factor(species)])
-legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
-```
-
 # Plots of individual species show that no species has a significant change either - although several show slight declines at the end
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-col.LMA <-c("purple", "pink", "light green", "orange","blue", "light blue","red")
-labels.LMA <-c("age 1.4", "age 2.4", "age 5", "age 7", "age 9", "age 32", "HATE")
+
 plot(LL_birth_mean ~ LMA_mean, SummarySppAge, type="n", xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1,pch=17, log="xy")
@@
 legend("bottomright",col=col.LMA, labels.LMA, pch=16, cex=1.4)
-```
-
-# LMA vs LL without young plants
-The pattern becomes more obvious when young plants (and Hakea) are omitted
-
-```{r, echo=FALSE,results='hide', message=FALSE}
-plot(LL_bd_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE" & age>1.5), pch=16, cex=1.2, col=col.age2[as.factor(age)])
-legend("bottomright",col=col.age2,labels.age2,pch=16)
 ```
@@
 
-# Species with greater wood density have higher growth rates
-Again there is no relationship in younger plants
+#22 April 2015
+Generic code to create plots, run lm, summarize results, by species
+
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="wood density",ylab="growth investment (mg per year)",xlim=c(0.57,0.9),main="Relationship between wood density and growth rates")
-text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
+plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
+  Y <- data[[yvar]]
+  X <- data[[xvar]]
+  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
+}
+
+summarise_fit <- function(x) {
+  data.frame(
+    select(glance(x), r.squared, p.value),
+    n= length(resid(x)),
+    a = coef(x)[1],
+    b = coef(x)[2]
+  )
+}
+
+summarise_all_fits <- function(x) {
+  tmp <- lapply(x, summarise_fit) %>%
+    bind_rows
+  data.frame(species=names(x), tmp)
+}
 ```
-
-# Species with larger seeds have higher growth rates
-The same basic relationship exists across all ages, so combined all data here
-```{r, echo=FALSE,results='hide', message=FALSE}
-plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
-legend("topleft",col=col.age, labels.age, pch=16, cex=1)
-text(GrowthInv_mean ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
-```
-
-# Species with greater maximum height have higher growth rates
-For younger plants there is no relationship with *SPECIES* overall maximum H, but there is a positive correlation with the maximum height the species reaches at a given age -i.e.
-fast growing young plants are tall when young.
-```{r, echo=FALSE,results='hide', message=FALSE}
-plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="maximum height (mm)",ylab="growth investment (mg per year)",xlim=c(500,3200),main="Relationship between growth rates on maximum H")
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
-```
-
-# Correlations between different growth measures
-Increased cross-sectional area of a leader and the entire plant are fairly correlated and uneffected by age (once not baby)
-```{r, echo=FALSE,results='hide', message=FALSE}
-plot(change_shoot_area~change_basal_area,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-```

### 2015-04-30 results_RAschedules.Rmd
continuing to organize results

@@
 - they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing propH  
+- when all data points are included, all species except PEPU, PHPH, and PULU show increasing RA with increasing height  
+- when RA =0 is excluded, the following species still have a significant positive correlation: BOLE, COER, EPMI, GRBU, GRSP, HATE. LEES and PELA have a p-value between 0.05-0.10   
+- PEPU has a negative correlation - matches Mark's suggestion that it is "hanging on"
+
+ NOTE: Again, a linear line is not necessarily the most appropriate
 
@@
 #RA schedules (by size)
+1. These plots have always been unsatisfying - with few exceptions (PULU, PEPU, LEES) plots against height are stronger. And both PILI and PEPU have very low R^2 by either method  
+2.
+If Only individuals with RA>0 are included only COER, EPMI, GRBU, HATE and LEES still have a significant positive correlation - for the remaining species correlation only exists because of small, non-reproductive plants having a strong effect on the curve
+
 ```{r, echo=FALSE,message=FALSE}
@@
 #RA vs RGR - 
-similar to the plots of RA vs Growth Investment, but relationships stronger. For these plots, all but one species (PEPU) have a significantly negative slope
-the results are more of less the same regardless of whether one includes or excluded individuals where RA=0
+1. this is another way to look at the growth-reproduction trade-off 
+2. similar to the plots of RA vs Growth Investment, but relationships stronger. For these plots, all but one species (PEPU) have a significantly negative slope  
+3. the results are more of less the same regardless of whether one includes or excluded individuals where RA=0  
+4. PEPU an exception because so few individuals reproducing and those that are reproducing have intermediate RGR - neither the young plants nor the older plants just hanging on  
+5. PELA doesn't have a relationship either, because so few reproducing individuals. But if the many individuals with RA=0 added back in, strong negative relationship for PELA
+
 ```{r, echo=FALSE,message=FALSE}
@@
 
-data <- subset(SummaryInd,RA>0)
+data <- subset(SummaryInd,RA>0&RGR>.04)
 data <- split(data, data$species)
@@
 results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
 

### 2015-04-30 results_accessory_tissues.rmd
continuing to organize results

```{r, echo=FALSE,results='hide', message=FALSE}
library(remake)
create_bindings()

source("scripts/summary_dataframes.R")
```

#Accessory costs
Overall results:
- Accessory costs higher for bigger seeds
- A number of species show fairly consistent declines in accessory costs with various measures of "bigger", including size, age, RA. Other species show no patterns
- 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases. in other words, they get better returns on investment the more they invest.
- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e. Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers
- For most of the statistical analyses, the youngest site has been removed, since it included individuals that were harvested while flowering (and therefore never "got to" set fruit) and automatically have no "successful" reproduction. There are of course some individuals like this at other ages as well, but far fewer

#Generic functions for most plotting below
```{r, echo=FALSE,results='hide', message=FALSE}
plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
  Y <- data[[yvar]]
  X <- data[[xvar]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

summarise_fit <- function(x) {
  data.frame(
    select(glance(x), r.squared, p.value),
    n= length(resid(x)),
    a = coef(x)[1],
    b = coef(x)[2]
  )
}

summarise_all_fits <- function(x) {
  tmp <- lapply(x, summarise_fit) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}

```

#How do accessory costs shift with seed size?
Larger-seeded species have higher accessory costs. 
Also shown in other studies and suggested as a mechanism for why angiosperms were able to have such small seeds (relative to gymnosperms, with no decrease in proportional accessory costs with decreasing size)
```{r, echo=FALSE,message=FALSE}
yvar <- "PerAcc_mean"
xvar <- "seed_size"
data <- SummarySpp

plot_yvar_vs_xvar(data, yvar, xvar,log="x",
                  xlab=xvar, ylab=yvar)
mod <- lm(log(seed_size)~PerAcc_mean,SummarySpp)
summary(mod)
anova(mod)
```

#Do species differ in the proportional energy allocated to propagules (vs. accessory tissues)
COER, EPMI, HEPU, LEES, PILI invest the most energy in propagules
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPropagule"
xvar <- "species"
data <- filter(SummaryInd,Total>0)

plot_yvar_vs_xvar(data, yvar, xvar,
                 xlab=xvar, ylab=yvar)
mod <- lm(asin(sqrt(PerPropagule)) ~ species, data)
summary(mod)
```

#Do species differ in the proportional energy allocated to aborted pre-pollination tissues
BOLE, EPMI, GRSP, HATE invest the most energy in aborted pre-pollination tissues
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_A"
xvar <- "species"
data <- filter(SummaryInd,Total>0 & age>2)

plot_yvar_vs_xvar(data, yvar, xvar,
                  xlab=xvar, ylab=yvar)
mod <- lm(asin(sqrt(PerPrePol_A)) ~ species, data)
summary(mod)
```

#Do individual species decrease accessory costs as they increase in size, age or RA?
First looking at size:
PerAcc is arcsine transformed, size is log transformed
COER, HATE, and PILI show a significant decrease in accessory costs with increasing size (p<0.05)
GRSP shows a marginally significant decrease in accessory costs with increasing size (0.05<p<0.10)
PEPU shows a marginally significant INCREASE in accessory costs with increasing size (0.05<p<0.10)
```{r, echo=FALSE, message=FALSE}
yvar <- "PerAcc"
xvar <- "FinalWeight"

data <- filter(SummaryInd,Total>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to age:
PerAcc is arcsine transformed, age is log transformed
BOLE, COER, GRSP, HATE, HEPU, PELA show a significant decrease in accessory costs with increasing age (p<0.05)
EPMI, GRBU shows a marginally significant decrease in accessory costs with increasing age (0.05<p<0.10)
PUTU shows a sig INCREASE in accessory costs with increasing age
```{r, echo=FALSE, message=FALSE}
yvar <- "PerAcc"
xvar <- "age"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to RA:
both RA and PerAcc are arcsine transformed
BAER, COER, GRBU, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in accessory costs with increasing RA (p<0.05)
BOLE shows a marginally significant decrease in accessory costs with increasing RA (p ~ 0.10)
```{r, echo=FALSE, message=FALSE}
yvar <- "PerAcc"
xvar <- "RA"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```
Overall, proportion of energy allocation to accessory tissues (versus propagules) is best explained by RA

#Next considering if the amount of energy spent on aborted buds shifts with age, size, RA
First looking at size:
PerPrePol_A is arcsine transformed, size is log transformed
GRSP, HATE, HEPU show a significant decrease in aborted buds with increasing size (p<0.05)
PUTU shows a marginally significant decrease in accessory costs with increasing RA (p ~ 0.10)
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_A"
xvar <- "FinalWeight"

data <- filter(SummaryInd,Total>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to age:
PerPrePol_A is arcsine transformed, age is log transformed
BAER, BOLE, COER, EPMI, LEES, PHPH, PILI show a significant decrease in aborted buds with increasing age (p<0.05)
GRSP, HATE show a marginally significant decrease in aborted buds with increasing age (0.05<p<0.10)
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_A"
xvar <- "age"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to RA:
both RA and PerPrePol_A are arcsine transformed
BAER, BOLE, COER, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in aborted buds with increasing RA (p<0.05)
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_A"
xvar <- "RA"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

#Do individual species decrease total pre-pollination costs as they increase in size, age or RA?
First looking at size:
PerPrePol_All is arcsine transformed, size is log transformed
GRSP, HATE show a significant decrease in total pre-pollination costs with increasing size (p<0.05)
HEPU shows a marginally significant decrease in total pre-pollination costs with increasing size (0.05<p<0.10)

```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "FinalWeight"

data <- filter(SummaryInd,Total>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to age:
PerPrePol_All is arcsine transformed, age is log transformed
BAER, BOLE, COER, HEPU, LEES, PILI show a significant decrease in total pre-pollination costs with increasing age (p<0.05)
EPMI, GRBU, GRSP, HATE shows a marginally significant decrease in total pre-pollination costs with increasing age (0.05<p<0.10)
PUTU shows a sig INCREASE in total pre-pollination  costs with increasing age
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "age"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, log="x", xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to RA:
both RA and PerPrePol_All are arcsine transformed
BAER, BOLE, COER, GRSP, HATE, HEPU, LEES, PEPU show a significant decrease in total pre-pollination costs with increasing RA (p<0.05)
PELA shows a marginally significant decrease in total pre-pollination costs with increasing RA (0.05<p<0.10)
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "RA"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

With respect to Reproductive Investment:
PerPrePol_All is arcsine transformed, ReproInv is log transformed
COER, GRBU, GRSP, HATE, PEPU, PHPH, PILI show a significant decrease in total pre-pollination costs with increasing reproductive investment (p<0.05)
LEES shows a marginally significant decrease in total pre-pollination costs with increasing reproductive investment (0.05<p<0.10)
```{r, echo=FALSE, message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "ReproInv"

data <- filter(SummaryInd,Total>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",
                    main=spp, xlab=xvar, ylab=yvar)

  abline(lmfits[[spp]])
}

```

#For each species, look at pattern of investment in different tissues across ages
Most obvious pattern is that different species invest more or less in different tissue types - across all species this is bigger pattern than shifts across age
```{r, echo=FALSE, message=FALSE}
plot_Acc_by_Spp <- function(spp) {
data2 <- filter(SummarySppAge, species==spp)
plot(PerPropagule_mean ~ age, data=data2, xlab="age", ylab="proportion tissue", cex.axis=.8, las=1,
       main=labels.spp[spp], ylim=c(0,1), xlim=c(1,35), log="x", pch=16,col="orange")
points(PerPrePol_A_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8, col="red")
points(PerPrePol_S_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=17, col="blue")
points(PerPostPol_A_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=18, col="black")
points(PerPackDisp_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=19, col="light green")
legend(.9,.7, pch=c(16,8,17,18,19),legend=c("Propagule","Aborted pre-poll","Successful pre-poll","Aborted post-poll","Packaging & disp"), col=c("orange","red","blue","black","light green"), cex=.8, bty="n")
}

for(n in names(labels.spp)) {
  plot_Acc_by_Spp(n)
  }
```

#Using models that look at all the various factors at once - but need to include species in these models and probably use some sort of a MANOVA
also issues because significance of various variables changes enormously with transformations
```{r, echo=FALSE, message=FALSE}
mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule))+asin(sqrt(PerPrePol_A))+ asin(sqrt(PerPrePol_S))+ asin(sqrt(PerPostPol_A))+ asin(sqrt(PerPackDisp)) + species,data=subset(SummaryInd,Total>0))

mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule))+asin(sqrt(PerPrePol_A))+ asin(sqrt(PerPrePol_S))+ asin(sqrt(PerPostPol_A))+ asin(sqrt(PerPackDisp)) +asin(sqrt(PerPropagule))*species+asin(sqrt(PerPrePol_A))*species+ asin(sqrt(PerPrePol_S))*species+ asin(sqrt(PerPostPol_A))*species+ asin(sqrt(PerPackDisp))*species+ species,data=subset(SummaryInd,Total>0))
summary(mod)
plot(mod)
step(mod)
```

### 2015-04-30 results_growth.Rmd
continuing to organize results

--- 2015-04-28 results_growth.Rmd
@@
 #Growth data, general patterns
+- proportion of maxH matters more for some species than others. 
+1. The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  
+2. The lower-growing species are more variable, with "prop maxH mattering more for some than others"
 
-#Generic functions for most plotting below
+- For almost all species there is a strong negative relationship between RGR and RA - indeed, more reproduction = less growth  
+1. Meanwhile there is the strong positive relationship between growth investment and reproductive investment, because bigger plants grow and reproduce more.  
+2. It is good to have a big enough data set to capture both trends - and to capture them consistently across many species
+
+- Many plants have a clear upturn in RA and corresponding downturn in RGR at a specific prop maxH  
+1. e.g. see EPMI for distinct pattern
+
+Generic functions for most plotting below
 ```{r, echo=FALSE, message=FALSE}
@@
 
+#Comparing growth between different measures and across age
+
+###Weight vs. height
+- No surprises here , but need to fit proper lines to the data
+- Plants asymptote in weight as they reach their maximum height. This is true for all species, although some species, like BOLE and GRBU, have a much messier scatter than others  
+- The follow on of course is to look at growth measures vs. height   
+- NOTE: All heights have been scaled 0-1 based on the maximum height of each species across all of the sites.
+This has no effect on within species analyses, but lets data from all species to be plotted together
+
 ```{r, echo=FALSE, message=FALSE}
-yvar <- ""
-xvar <- ""
-data <- filter(SummaryInd,
+plot((FinalWeight~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot((FinalWeight~StartBasalDiamAv), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy")
 
-plot_yvar_vs_xvar(data, yvar, xvar,
-                  xlab=xvar, ylab=yvar)
+yvar <- "FinalWeight"
+xvar <- "PropH"
 
-summary(mod)
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",
+                    main=spp, xlab=xvar, ylab=yvar)
+  abline(lmfits[[spp]])
+}
+```
+
+###Growth Investment versus proportion max H
+- This turns out to be one of the most interesting sets of graphs  
+- For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH  
+- For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)  
+- Quite interesting, there is a distinctly negative relationship for GRBU; its absolute growth investment actually declines as it increases in size  
+- For many of the species with a good relationship, it seems that there are two breakpoints in the curve - wondering what these mean with respect to reproductive onset and RA
+
+```{r, echo=FALSE, message=FALSE}
+plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+plot(GrowthInv~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+
+yvar <- "GrowthInv"
+xvar <- "PropH"
+
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
+                    main=spp, xlab=xvar, ylab=yvar)
+
+  abline(lmfits[[spp]])
+}
+```
+
+###Proportion max H by RGR
+- Ignoring a few outliers, RGR declines with increasing height is 12 species  
+- Only in HEPU and PILI is there no significant trend  
+- The species with a poorer correlation are mostly shorter ones that are presumably often broken off   
+- These are continued ways to look at the question of how important is height (relative to the species maxH) in understanding its growth and reproduction
+
+```{r, echo=FALSE, message=FALSE}
+plot((RGR~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+yvar <- "RGR"
+xvar <- "PropH"
+
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
+                    main=spp, xlab=xvar, ylab=yvar)
+  abline(lmfits[[spp]])
+}
+```
+
+###PropH by age
+- Confirming that species get taller as they get older  
+- Obviously true for most species, but some (i.e.
+PILI, somewhat BOLE, HEPU) they reach their "maxH" within a few years and then the relationship is mostly flat.
+These are of course also the species which are shorter lived and have high levels of early reproduction
+
+```{r, echo=FALSE, message=FALSE}
+yvar <- "PropH"
+xvar <- "age"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="x",
+                    main=spp, xlab=xvar, ylab=yvar)
+
+  abline(lmfits[[spp]])
+}
+```
+
+###Growth Investment versus weight   
+- showing that slope continues to be 1:1, but intercept decreases with time because more standing biomass
+```{r, echo=FALSE, message=FALSE}
+plot((GrowthInv~FinalWeight), SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+abline(0,1,lwd=2)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+plot(GrowthInv~FinalWeight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
+abline(0,1,lwd=2)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+```
+
+#Comparing growth of whole plant vs. leader
+
+###Correlations between different growth measures
+- Increased cross-sectional area of a leader and the entire plant are fairly correlated and uneffected by age (once not baby)
+
+TO DO: species should be a random effect for these stats- I want to know the effect of age on the relationship once the effect of species has been accounted for
+
+```{r, echo=FALSE,message=FALSE}
+plot(change_shoot_area~change_basal_area,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1,bty="n")
+mod <- lm(change_shoot_area~change_basal_area*age*species,SummaryInd)
 anova(mod)
@@
 
-```{r, echo=FALSE, message=FALSE}
+#Comparing growth rates of species with different trait values
 
+### Species with larger seeds have higher growth rates  
+- The same basic relationship exists across all ages, so combined all data here  
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
+legend("topleft",col=col.age, labels.age, pch=16, cex=1,bty="n")
+text(GrowthInv_mean ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
 ```
+
+### Species with greater maximum height have higher growth rates
+- For younger plants there is no relationship with *SPECIES* overall maximum H  
+- There is a positive correlation with the maximum height the species reaches at a given age -i.e. fast growing young plants are tall when young.  
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age<3),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.1,xlab="maximum height (mm)",ylab="growth investment (mg per year)",xlim=c(500,3200),main="Relationship between growth rates on maximum H")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1,bty="n")
+text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==2.4), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+
+plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.1,xlab="maximum height (mm)",ylab="growth investment (mg per year)",xlim=c(500,3200),main="Relationship between growth rates on maximum H")
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1,bty="n")
+text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+```
+
+### Species with higher wood density have lower growth rates  
+- Adult plants strongly show this pattern
+- However there is no relationship in younger plants  
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="wood density",ylab="growth investment (mg per year)",xlim=c(0.57,0.9),main="Relationship between wood density and growth rates")
+text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+legend("bottomleft",col=col.age, labels.age, pch=16, cex=1, bty="n")
+
+plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age<3),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="wood density",ylab="growth investment (mg per year)",xlim=c(0.57,0.9),main="Relationship between wood density and growth rates")
+text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+legend("bottomleft",col=col.age, labels.age, pch=16, cex=1, bty="n")
+```

### 2015-04-30 results_leaf_lifespan.rmd
continuing to organize results

@@
 
-#Plotting LMA vs. age
-older plants have marginally higher LMA, but the effect mostly disappears when the youngest plants are excluded
-there is enormous variation in LMA across species
+#LMA vs. age
+- older plants have marginally higher LMA, but the effect mostly disappears when the youngest plants are excluded  
+- there is enormous variation in LMA across species  
+- also had plot of just branches from 2nd-last leaf cohort - no real difference, so using mean LMA of up to 3 leaf cohorts
 
 ```{r, echo=FALSE,message=FALSE}
+
+plot(LMA_mean~age, SummarySppAge,log="xy", col=col.spp[as.factor(species)], pch=16)
 mod <- lm(LMA_mean~species*age, SummarySppAge)
@@
 legend(12,.04,col=col.spp, pch=16,legend=labels.spp,cex=.8,bty="n")
+```
+
+```{r, echo=FALSE,results='hide', message=FALSE}
+plot(LMA~age,data=subset(LMA,branch_age=="mid"),log="xy", xlab="age",ylab="LMA",col=col.spp[as.factor(species)],pch=16)
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
 ```
@@
 
+#PropH vs LL_death
+- Have just plotted overall data, because no relationships across or within species; only GRSP has significant negative relationship and BOLE has significant positive relationship
+```{r, echo=FALSE,message=FALSE}
+plot((LL_death~PropH), data=subset(SummaryInd,LL_death<10), col=col.spp[as.factor(species)],pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+plot((PropH~log(age)), data=subset(SummaryInd), col=col.spp[as.factor(species)],pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```
+
 ```{r, echo=FALSE,message=FALSE}

### 2015-04-30 results.Rmd
more cleaning up of results

@@
 create_bindings()
-
 source("scripts/summary_dataframes.R")
 ```
-# file names
-
-- leaf_counts is file with calculated leaf counts and leaf lifespan data
-- SummarySppAge is file with means of LL - and other variables - by species and age; LMA data is merged to this file
-- subsets of SummarySppAge are created to omit babies or HATE for various analyses
-
 # What causes RA to shift with age in species?
@@
 I have both RA schedules and lots of other data across multiple ages:
-  - leaf lifespa
+- leaf lifespan
 - LMA
@@
 
-# Shifts in RA with age
-
-Showing just a few of the RA schedules from my last lab meeting.
-
-They show that species differ greatly in RA, that there is a general increase with age, but also that the data are noisy.
-
-```{r, echo=FALSE,results='hide', message=FALSE}
-plot_RAbyAge <- function(spp) {
-  plot(RA~age, data=subset(SummaryInd,species==spp), xlab="age (years)",ylab="reproductive allocation (%)", log="x", main=labels.spp[spp],xlim=c(1,35),ylim=c(0,1))
-  points(RA_mean~age, data=subset(SummarySppAge, species==spp),pch=16,cex=1.4)
-}
-
-for(n in names(labels.spp)) {
-  plot_RAbyAge(n)
-}
-```
-
-# Individual shoots looked decidedly "less leafy" in many older plants
-This led me to wonder how leaf lifespan - or some other variable - was shifting with age
-
-The number of leaves along a leader is overall uneffected by age, although some species show a marked decline
-
-```{r, echo=FALSE,results='hide', message=FALSE}
-plot(lvs_end_total~age,SummaryInd,log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
-legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
-```
-
-# Plots of individual species show that no species has a significant change either - although several show slight declines at the end
-
-```{r, echo=FALSE,results='hide', message=FALSE}
-
-  # fit <- lm(LL_birth ~ log10(age), data=data2)
-  # abline(fit)
-}
-
-for(n in names(labels.spp)) {
-  plot_LLvAge(n)
-  #  mod_LMAvAge(n)
-  #  summary(mod_LMAvAge(n))
-}
-```
-
-# Several species show significant declines in shoot extension with age
-
-```{r, echo=FALSE,results='hide', message=FALSE}
-
-plot_newlengthvAge <- function(data, yvar = "new_length", xvar = "age", ...) {
-	Y <- data[[yvar]]
-	X <- data[[xvar]]
-  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
-  # points(new_length_mean ~ age, data=data, cex=1.3, pch=8)
-  # points((new_length_mean+new_length_se) ~ age, data=data, cex=1.5, pch=25)
-  # points((new_length_mean-new_length_se) ~ age, data=data, cex=1.5, pch=24)
-}
-
-summarise_fit <- function(x) {
-	data.frame(
-		select(glance(x), r.squared, p.value),
-		n= length(resid(x)),
-		a = coef(x)[1],
-		b = coef(x)[2]
-	)
-}
-
-summarise_all_fits <- function(x) {
-	tmp <- lapply(x, summarise_fit) %>%
-		bind_rows
-	data.frame(species=names(x), tmp)
-}
-
-yvar <- "new_length"
-xvar <- "age"
-
-data <- filter(SummaryInd, age > 2.4)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(x[[yvar]] ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-for(spp in names(data)) {
-  plot_newlengthvAge(data[[spp]], yvar, xvar, log="x",
-  	ylim=c(0,150),  main=spp, xlab="age", ylab="leader shoot extention")
-  abline(lmfits[[spp]])
-}
-
-```
-
-# Had expected a stronger pattern either in leaf lifespan or leaf count on a shoot
-Apparently it is simply that older plants have more stem - plotting total leaf weight against final weight, shows bigger plants have relatively fewer leaves
-(Yes, I know the 2.4 yr olds are missing...)
-
-```{r, echo=FALSE,results='hide', message=FALSE}
-plot(total_leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-```
 # Next steps?
@@
 Afterall, the energy allocation models suggest that different RA schedules may be due to different amounts of "shifting" across species - some species might be predicted to shift more than others.
-
-# LMA vs Leaf lifespan
-This correlation is as expected, except for the babies
-
-```{r, echo=FALSE,results='hide', message=FALSE}
-
-plot(LL_birth_mean ~ LMA_mean, SummarySppAge, type="n", xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1,pch=17, log="xy")
-points(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE"), pch=16, cex=1.2, col=col.age[as.factor(age)])
-points(LL_birth_mean ~ LMA_mean, col="red", data=subset(SummarySppAge, species=="HATE"), pch=17)
-legend("bottomright",col=col.LMA, labels.LMA, pch=16, cex=1.4)
-```
-
-# Growth rates increase with increasing LMA in adult plants
-But there is no relationship in seedlings (age=1.4) or saplings (age=2.4)
-This is not predicted by Daniel's model or Anais' review
-```{r, echo=FALSE,results='hide', message=FALSE}
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Seedlings")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
-
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="pink",pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Saplings")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
-
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Adults")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-legend("bottomright",col=col.age,labels.age,pch=16)
-```
 

### 2015-04-30 results_accessory_tissues.rmd
more cleaning up of results

@@
 #Accessory costs
-Overall results:
+###Overall results 
 - Accessory costs higher for bigger seeds  
@@
 
-#Generic functions for most plotting below
+###Generic functions for most plotting below
 ```{r, echo=FALSE,results='hide', message=FALSE}
@@
 
-#How do accessory costs shift with seed size?
-Larger-seeded species have higher accessory costs. 
-Also shown in other studies and suggested as a mechanism for why angiosperms were able to have such small seeds (relative to gymnosperms, with no decrease in proportional accessory costs with decreasing size)
+###How do accessory costs shift with seed size?
+- Larger-seeded species have higher accessory costs. 
+- Also shown in other studies and suggested as a mechanism for why angiosperms were able to have such small seeds (relative to gymnosperms, with no decrease in proportional accessory costs - with decreasing size)
 ```{r, echo=FALSE,message=FALSE}
@@
 
-#Do species differ in the proportional energy allocated to propagules (vs. accessory tissues)
-COER, EPMI, HEPU, LEES, PILI invest the most energy in propagules
+###Do species differ in the proportional energy allocated to propagules (vs. accessory tissues)  
+- COER, EPMI, HEPU, LEES, PILI invest the most energy in propagules  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-#Do species differ in the proportional energy allocated to aborted pre-pollination tissues
-BOLE, EPMI, GRSP, HATE invest the most energy in aborted pre-pollination tissues
+###Do species differ in the proportional energy allocated to aborted pre-pollination tissues
+- BOLE, EPMI, GRSP, HATE invest the most energy in aborted pre-pollination tissues  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-#Do individual species decrease accessory costs as they increase in size, age or RA?
-First looking at size:
-PerAcc is arcsine transformed, size is log transformed
-COER, HATE, and PILI show a significant decrease in accessory costs with increasing size (p<0.05)
-GRSP shows a marginally significant decrease in accessory costs with increasing size (0.05<p<0.10)
-PEPU shows a marginally significant INCREASE in accessory costs with increasing size (0.05<p<0.10)
+##Do individual species decrease accessory costs as they increase in size, age or RA?
+###Change in accesory costs With size:  
+- PerAcc is arcsine transformed, size is log transformed  
+- COER, HATE, and PILI show a significant decrease in accessory costs with increasing size (p<0.05)  
+- GRSP shows a marginally significant decrease in accessory costs with increasing size (0.05<p<0.10)  
+- PEPU shows a marginally significant INCREASE in accessory costs with increasing size (0.05<p<0.10)  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-With respect to age:
-PerAcc is arcsine transformed, age is log transformed
-BOLE, COER, GRSP, HATE, HEPU, PELA show a significant decrease in accessory costs with increasing age (p<0.05)
-EPMI, GRBU shows a marginally significant decrease in accessory costs with increasing age (0.05<p<0.10)
-PUTU shows a sig INCREASE in accessory costs with increasing age
+###Change in accesory costs With age:
+- PerAcc is arcsine transformed, age is log transformed  
+- BOLE, COER, GRSP, HATE, HEPU, PELA show a significant decrease in accessory costs with increasing age (p<0.05)  
+- EPMI, GRBU shows a marginally significant decrease in accessory costs with increasing age (0.05<p<0.10)  
+- PUTU shows a sig INCREASE in accessory costs with increasing age  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-With respect to RA:
-both RA and PerAcc are arcsine transformed
-BAER, COER, GRBU, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in accessory costs with increasing RA (p<0.05)
-BOLE shows a marginally significant decrease in accessory costs with increasing RA (p ~ 0.10)
+###Change in accesory costs With respect to RA:  
+- both RA and PerAcc are arcsine transformed  
+- BAER, COER, GRBU, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in accessory costs with increasing RA (p<0.05)  
+- BOLE shows a marginally significant decrease in accessory costs with increasing RA (p ~ 0.10)  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-#Next considering if the amount of energy spent on aborted buds shifts with age, size, RA
-First looking at size:
-PerPrePol_A is arcsine transformed, size is log transformed
-GRSP, HATE, HEPU show a significant decrease in aborted buds with increasing size (p<0.05)
-PUTU shows a marginally significant decrease in accessory costs with increasing RA (p ~ 0.10)
+##Next considering if the amount of energy spent on aborted buds shifts with age, size, RA  
+###Change in aborted bud investment with size:  
+- PerPrePol_A is arcsine transformed, size is log transformed  
+- GRSP, HATE, HEPU show a significant decrease in aborted buds with increasing size (p<0.05)  
+- PUTU shows a marginally significant decrease in accessory costs with increasing RA (p ~ 0.10)  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-With respect to age:
-PerPrePol_A is arcsine transformed, age is log transformed
-BAER, BOLE, COER, EPMI, LEES, PHPH, PILI show a significant decrease in aborted buds with increasing age (p<0.05)
-GRSP, HATE show a marginally significant decrease in aborted buds with increasing age (0.05<p<0.10)
+###Change in aborted bud investment with respect to age:  
+- PerPrePol_A is arcsine transformed, age is log transformed  
+- BAER, BOLE, COER, EPMI, LEES, PHPH, PILI show a significant decrease in aborted buds with increasing age (p<0.05)  
+- GRSP, HATE show a marginally significant decrease in aborted buds with increasing age (0.05<p<0.10)  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-With respect to RA:
-both RA and PerPrePol_A are arcsine transformed
-BAER, BOLE, COER, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in aborted buds with increasing RA (p<0.05)
+###Change in aborted bud investment with respect to RA:
+- both RA and PerPrePol_A are arcsine transformed  
+- BAER, BOLE, COER, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in aborted buds with increasing RA (p<0.05)  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-#Do individual species decrease total pre-pollination costs as they increase in size, age or RA?
-First looking at size:
-PerPrePol_All is arcsine transformed, size is log transformed
-GRSP, HATE show a significant decrease in total pre-pollination costs with increasing size (p<0.05)
-HEPU shows a marginally significant decrease in total pre-pollination costs with increasing size (0.05<p<0.10)
+##Do individual species decrease total pre-pollination costs as they increase in size, age or RA?  
+###Do total pre-pollination costs change with respect to size:  
+- PerPrePol_All is arcsine transformed, size is log transformed  
+- GRSP, HATE show a significant decrease in total pre-pollination costs with increasing size (p<0.05)  
+- HEPU shows a marginally significant decrease in total pre-pollination costs with increasing size (0.05<p<0.10)
 
@@
 
-With respect to age:
-PerPrePol_All is arcsine transformed, age is log transformed
-BAER, BOLE, COER, HEPU, LEES, PILI show a significant decrease in total pre-pollination costs with increasing age (p<0.05)
-EPMI, GRBU, GRSP, HATE shows a marginally significant decrease in total pre-pollination costs with increasing age (0.05<p<0.10)
-PUTU shows a sig INCREASE in total pre-pollination  costs with increasing age
+###Do total pre-pollination costs change with respect to age:
+- PerPrePol_All is arcsine transformed, age is log transformed  
+- BAER, BOLE, COER, HEPU, LEES, PILI show a significant decrease in total pre-pollination costs with increasing age (p<0.05)  
+- EPMI, GRBU, GRSP, HATE shows a marginally significant decrease in total pre-pollination costs with increasing age (0.05<p<0.10)  
+- PUTU shows a sig INCREASE in total pre-pollination  costs with increasing age  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-With respect to RA:
-both RA and PerPrePol_All are arcsine transformed
-BAER, BOLE, COER, GRSP, HATE, HEPU, LEES, PEPU show a significant decrease in total pre-pollination costs with increasing RA (p<0.05)
-PELA shows a marginally significant decrease in total pre-pollination costs with increasing RA (0.05<p<0.10)
+### Do total pre-pollination costs change with respect to RA:  
+- both RA and PerPrePol_All are arcsine transformed    
+- BAER, BOLE, COER, GRSP, HATE, HEPU, LEES, PEPU show a significant decrease in total pre-pollination costs with increasing RA (p<0.05)  
+- PELA shows a marginally significant decrease in total pre-pollination costs with increasing RA (0.05<p<0.10)  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-With respect to Reproductive Investment:
-PerPrePol_All is arcsine transformed, ReproInv is log transformed
-COER, GRBU, GRSP, HATE, PEPU, PHPH, PILI show a significant decrease in total pre-pollination costs with increasing reproductive investment (p<0.05)
-LEES shows a marginally significant decrease in total pre-pollination costs with increasing reproductive investment (0.05<p<0.10)
+### Do total pre-pollination costs change with respect to Reproductive Investment:
+- PerPrePol_All is arcsine transformed, ReproInv is log transformed  
+- COER, GRBU, GRSP, HATE, PEPU, PHPH, PILI show a significant decrease in total pre-pollination costs with increasing reproductive investment (p<0.05)  
+- LEES shows a marginally significant decrease in total pre-pollination costs with increasing reproductive investment (0.05<p<0.10)  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-#For each species, look at pattern of investment in different tissues across ages
-Most obvious pattern is that different species invest more or less in different tissue types - across all species this is bigger pattern than shifts across age
+###For each species, look at pattern of investment in different tissues across ages  
+- Most obvious pattern is that different species invest more or less in different tissue types - across all species this is bigger pattern than shifts across age  
 ```{r, echo=FALSE, message=FALSE}
@@
 
-#Using models that look at all the various factors at once - but need to include species in these models and probably use some sort of a MANOVA
-also issues because significance of various variables changes enormously with transformations
+###Considering relative effect of different accessory costs on RA
+- Using models that look at all the various factors at once - but need to include species in these models and probably use some sort of a MANOVA  
+- also issues because significance of various variables changes enormously with transformations  
 ```{r, echo=FALSE, message=FALSE}

### 2015-04-30 results_growth.Rmd
more cleaning up of results

@@
 
+###Shifts in leafiness with age  
+- Individual shoots looked decidedly "less leafy" in many older plants  
+- This led me to wonder how leaf lifespan - or some other variable - was shifting with age   
+- The number of leaves along a leader is overall uneffected by age  
+- However, looking at individual species: BOLE, GRBU, GRSP, HEPU, PILI, PUTU have declining leaf counts along a shoot with age  
+- And PELA, PEPU show a significant increase in leaf counts along a single shoot with age
+
+```{r, echo=FALSE,message=FALSE}
+plot(lvs_end_total~age,SummaryInd,log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1,bty="n")
+
+yvar <- "lvs_end_total"
+xvar <- "age"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="x",
+                    main=spp, xlab=xvar, ylab=yvar)
+
+  abline(lmfits[[spp]])
+}
+```
+
+###Leaf weight (relative to total weight) also declines with age  
+- These numbers are currently incomplete - waiting for full set of "leaf weight" numbers to finalize this
+
+```{r, echo=FALSE,message=FALSE}
+plot(total_leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")
+
+plot(total_leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
+legend("bottomright",col=col.spp, labels.spp, pch=16, cex=.8, bty="n")
+```
+
+###Shifts in shoot extension with age
+- The decrease in leaf number along a shoot is largely caused by declining shoot extension, not shifts in leaf lifespan  
+- BAER, BOLE, EPMI, GRBU, GRSP, HATE, HEPU, PHPH, PILI, and PUTU all show significant declines in shoot extension with age  
+- For many of these species, the shift is between the "sapling" and "adult" stages - i.e. when they begin reproducing  
+- PELA stands out by showing increasing shoot extension with age - because it grows so slowly in the beginning
+
+```{r, echo=FALSE,message=FALSE}
+plot(new_length~age,SummaryInd,log="xy", xlab="age",ylab="shoot extension (mm)",col=col.spp[as.factor(species)])
+legend(12,200,col=col.spp, labels.spp, pch=16, cex=.8,bty="n")
+
+yvar <- "new_length"
+xvar <- "age"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="x",
+                    main=spp, xlab=xvar, ylab=yvar)
+
+  abline(lmfits[[spp]])
+}
+```
+
 #Comparing growth rates of species with different trait values
@@
 - The same basic relationship exists across all ages, so combined all data here  
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
@@
 - There is a positive correlation with the maximum height the species reaches at a given age -i.e. fast growing young plants are tall when young.  
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age<3),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.1,xlab="maximum height (mm)",ylab="growth investment (mg per year)",xlim=c(500,3200),main="Relationship between growth rates on maximum H")
@@
 - However there is no relationship in younger plants  
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,message=FALSE}
 plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="wood density",ylab="growth investment (mg per year)",xlim=c(0.57,0.9),main="Relationship between wood density and growth rates")
@@
 ```
+
+### Species with higher LMA have higher growth rates  
+- This pattern is true for adult plants  
+- But there is no relationship in seedlings (age=1.4) or saplings (age=2.4)  
+- This is not predicted by Daniel's model or Anais' review; re-run with RGR
+```{r, echo=FALSE,message=FALSE}
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Seedlings")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4))
+summary(mod)
+
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="pink",pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Saplings")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4))
+summary(mod)
+
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Adults")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+legend("bottomright",col=col.age,labels.age,pch=16, bty="n")
+mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3))
+summary(mod)
+```
+
+###Looking at LMA relative to RGR
+- There are no significant relationships at any age when RGR is used instead of actual growth investment 
+```{r, echo=FALSE,message=FALSE}
+plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="RGR=",main="Seedlings")
+text(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4))
+summary(mod)
+
+plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="pink",pch=16,cex=1.2,xlab="LMA",ylab="RGR",main="Saplings")
+text(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+mod <- lm(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4))
+summary(mod)
+
+plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="RGR",main="Adults")
+text(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+legend("bottomright",col=col.age,labels.age,pch=16, bty="n")
+mod <- lm(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age>3))
+summary(mod)
+```
+
+###Leaf lifespan vs growth investment
+- There is no relationship between leaf lifespan and growth investment for any age group
+- And just barely a significant relationship between RGR and leaflifespan for adult plants
+```{r, echo=FALSE,message=FALSE}
+plot(GrowthInv ~ LL_death,data=subset(SummaryInd,age==1.4),log="xy",col=col.spp[as.factor(species)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="growth investment (mg per year)",main="Seedlings")
+legend(4.5,1600,col=col.spp,labels.spp,pch=16, bty="n",cex=.8)
+mod <- lm(GrowthInv ~ LL_death, data=subset(SummaryInd,age==1.4))
+summary(mod)
+
+plot(GrowthInv ~ LL_death,data=subset(SummaryInd,age==2.4),log="xy",col=col.spp[as.factor(species)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="growth investment (mg per year)",main="Saplings")
+legend("bottomright",col=col.spp,labels.spp,pch=16, bty="n",cex=.8)
+mod <- lm(GrowthInv ~ LL_death, data=subset(SummaryInd,age==2.4))
+summary(mod)
+
+plot(GrowthInv ~ LL_death,data=subset(SummaryInd,age>3&LL_death<10),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="growth investment (mg per year)",main="Adults")
+legend("bottomright",col=col.age,labels.age,pch=16, bty="n")
+mod <- lm(GrowthInv ~ LL_death*species, data=subset(SummaryInd,age>3))
+anova(mod)
+```
+
+```{r, echo=FALSE,message=FALSE}
+plot(RGR ~ LL_death,data=subset(SummaryInd,age==1.4),log="xy",col=col.spp[as.factor(species)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="RGR",main="Seedlings")
+legend(4.5,1600,col=col.spp,labels.spp,pch=16, bty="n",cex=.8)
+mod <- lm(RGR ~ LL_death, data=subset(SummaryInd,age==1.4))
+summary(mod)
+
+plot(RGR ~ LL_death,data=subset(SummaryInd,age==2.4),log="xy",col=col.spp[as.factor(species)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="RGR",main="Saplings")
+legend("bottomright",col=col.spp,labels.spp,pch=16, bty="n",cex=.8)
+mod <- lm(RGR ~ LL_death, data=subset(SummaryInd,age==2.4))
+summary(mod)
+
+plot(RGR ~ LL_death,data=subset(SummaryInd,age>3&LL_death<10&RGR>0.04),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="RGR",main="Adults")
+legend("bottomright",col=col.age,labels.age,pch=16, bty="n")
+mod <- lm(RGR ~ LL_death*species, data=subset(SummaryInd,age>3&LL_death<10&RGR>0.04))
+anova(mod)
+```

### 2015-04-30 results_leaf_lifespan.rmd
more cleaning up of results

@@
 
-#Starting with the basics: Are leaf lifespan and LMA correlated?
-Plotting species*site means
-Figures shown using all three measures of leaf lifespan
+###Starting with the basics: Are leaf lifespan and LMA correlated?  
+- Plotting species*site means  
+- Figures shown using all three measures of leaf lifespan  
 ```{r, echo=FALSE,message=FALSE}
@@
 
-#Same plots as above, but omitting HATE, which has much higher LMA than any other species due to its round "leaves"
-Using leaf deaths gives the poorest fit...
+###Same plots as above, but omitting HATE, which has much higher LMA than any other species due to its round "leaves"  
+- Using leaf deaths gives the poorest fit...
 ```{r, echo=FALSE,message=FALSE}
@@
 anova(mod)
+
+plot(LL_birth_mean ~ LMA_mean, SummarySppAge, type="n", xlab="LMA", ylab="leaf lifespan (years)", main="leaf lifespan versus LMA (all species and ages)", las=1,pch=17, log="xy")
+points(LL_birth_mean ~ LMA_mean, data=subset(SummarySppAge, species!="HATE"), pch=16, cex=1.2, col=col.age[as.factor(age)])
+points(LL_birth_mean ~ LMA_mean, col="red", data=subset(SummarySppAge, species=="HATE"), pch=15)
+legend("bottomright",col=col.LMA, labels.LMA, pch=16, cex=1,bty="n")
 

### 2015-05-05 results_RAschedules.Rmd
starting to summarize results deleted some outdates, duplicate scripts few thoughts about shoot extension - to be improved upon

@@
 #RV curves
-These are mostly reasonably nice - of course need to fit quadratic curve to these and haven't figured out how to do it correctly
-
+###Classic RV curves - reproductive investment versus weight
+- These are mostly reasonably nice - of course need to fit quadratic curve to these and haven't figured out how to do it correctly  
+- The plot that includes all species shows that *once* a given species has ramped up reproduction, the log-log plot of reproductive investment vs final weight is nearly linear across all species; in other words, to first order, all species allocate the same amount to reproduction relative to their weight.
+- However, it is important to note that species early in their reproductive trajectory do not follow this pattern
 ```{r, echo=FALSE,message=FALSE}
-plot(ReproInv~FinalWeight, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(ReproInv~FinalWeight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
@@
 
-#RV curves (by age)
+###RV curves (by age)
 ```{r, echo=FALSE,message=FALSE}
@@
                     main=spp, log="xy", xlab=xvar, ylab=yvar)
+
+  abline(lmfits[[spp]])
+}
+```
+
+###RV curves (by proportion max H)
+- In a sense, by using proportion max H, these figures are showing the proportion of total growth the plant undergoes before starting reproduction
+- You could also plot against "PropMaxWeight", the proportion of the heaviest individual of that species. The two measures look "best" for different species
+```{r, echo=FALSE,message=FALSE}
+plot((PropMaxRepro+.1)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+yvar <- "ReproInv"
+xvar <- "PropH"
+
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
+                    main=spp, log="y", xlab=xvar, ylab=yvar)
 
@@
 plot(RA~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
@@
 legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-mod <- lm(log(GrowthInv)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
+mod <- lm(log(GrowthInv)~asin(sqrt(RA))*species, data=subset(SummaryInd,RA>0))
 summary(mod)
+anova(mod)
 plot(mod)

### 2015-05-05 results_best.Rmd
starting to summarize results deleted some outdates, duplicate scripts few thoughts about shoot extension - to be improved upon

```{r, echo=FALSE,results='hide', message=FALSE}
library(remake)
create_bindings()

source("scripts/summary_dataframes.R")

plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
  Y <- data[[yvar]]
  X <- data[[xvar]]
  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
}

summarise_fit <- function(x) {
  data.frame(
    select(glance(x), r.squared, p.value),
    n= length(resid(x)),
    a = coef(x)[1],
    b = coef(x)[2]
  )
}

summarise_all_fits <- function(x) {
  tmp <- lapply(x, summarise_fit) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}

summarise_fit_2var <- function(x) {
  data.frame(
    select(glance(x), r.squared, p.value),
    n= length(resid(x)),
    intercept = coef(x)[1],
    coef_var1 = coef(x)[2],
    coef_var2 = coef(x)[3],
    coef_var1var2 = coef(x)[4],
    SS_var1 = anova(x)[1,2],
    SS_var2 = anova(x)[2,2],
    SS_var1var2 =anova(x)[3,2]
      )
}

summarise_all_fits_2var <- function(x) {
  tmp <- lapply(x, summarise_fit_2var) %>%
    bind_rows
  data.frame(species=names(x), tmp)
}
```

#Ideas and plots to include in a paper looking at the ways in which reproductive investment impacts growth
* Part of this paper would be to look at how different "types of" species fall out with respect to the various plots - i.e. canopy species (BAER, HATE, PELA), short-lived species (BOLE, PILI, COER), longer-lived understory species 
* Plants that grow more also reproduce more, but plants that allocate more to reproduction have lower RGR (Same paper as RA curves?)
* There is a disinct decline in RGR (or Growth Investment) at the exact "PropH" that plants begin to reproduce (Same paper as RA curves?)

##Growth-reproduction trade-off
###Bigger plants reproduce more
- There is a positive correlation between reproductive investment vs growth investment among individuals that are reproducing: plants that grow more also allocate more to reproduction.  
- It is also true that bigger plants allocate more to reproduction.

```{r, echo=FALSE,message=FALSE}
plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

###Plants that allocate more to reproduction (higher RA) have a lower RGR
- When looked at individually, this pattern holds for all species except PEPU and PELA, although there is lots of variation in the exact trade-off pattern displayed by different species  
- You can also look at the plots of RGR vs RA and identify the RA at which RGR is impacted. Some plots show a very linear decline throught, whereas for others there is a distinct "knickpoint" -i.e. BOLE, EPMI, HATE

```{r, echo=FALSE,message=FALSE}
plot(RA~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(RGR~asin(sqrt(RA))*species,SummaryInd)
anova(mod)
```

###More ways to ask how much - and when - reproduction impacts growth  
- It is clear that different species reach a different "proportion maxH" (RSOM) before reproducing. Need to do curve fitting to determine where this occurs.  
- The plot of Growth Investment vs. PropH shows a decrease in growth rate at a given PropH (for most species). Is this the same PropH at which reproduction begins?  
- It seems that some of the early reproducers begin reproducing at a larger PropH, as predicted by others. But because they allocate so much to reproduction, their growth rate declines more precipitously with the onset of reproduction.

#Ideas and plots to include in RA schedule paper
* I have a dataset with enough resolution across species and ages to show patterns of growth and reproductive investment across ages  
* This includes both RA schedules and RV curves, as well as other potential plots

###RV curves (by proportion max H)
- In a sense, by using proportion max H, these figures are showing the proportion of total growth the plant undergoes before starting reproduction
- You could also plot against "PropMaxWeight", the proportion of the heaviest individual of that species. The two measures look "best" for different species
```{r, echo=FALSE,message=FALSE}
plot((ReproInv)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "ReproInv"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="y", xlab=xvar, ylab=yvar)
}
```

#RA schedules (vs. propH)  
- these curves are particularly good for a number of species such as EPMI, COER, PELA  
- they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing propH  
- when all data points are included, all species except PEPU, PHPH, and PULU show increasing RA with increasing height  
- when RA =0 is excluded, the following species still have a significant positive correlation: BOLE, COER, EPMI, GRBU, GRSP, HATE. LEES and PELA have a p-value between 0.05-0.10   
- PEPU has a negative correlation - matches Mark's suggestion that it is "hanging on"  
- There are species - such as BOLE - which have a much "cleaner" plot against age instead of PropH (or any other size measure). This indicates that these species are programmed to reproduce at a certain "rate" regardless of their size

 NOTE: Again, a linear line is not necessarily the most appropriate

```{r, echo=FALSE, message=FALSE}
plot((RA~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

plot(RA~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

yvar <- "RA"
xvar <- "PropH"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
                    main=spp, xlab=xvar, ylab=yvar)
}
```

###To think about regarding RA schedules and RV curves
- What does it mean that PropH is the better correlate that plant weight?  
1. That "plant weight" is a mis-leading number, since it includes dead "heartwood"  
2. That this is a community where height is the most important variable? Because height = light access or because of some relationship between height and leaf area.  
** Once I have leaf weights, I'll be curious how leaf weight plots against PropH, this might be more of the story

### 2015-05-05 results_growth.Rmd
starting to summarize results deleted some outdates, duplicate scripts few thoughts about shoot extension - to be improved upon

@@
 ```
+###Diameter increase in shoots vs. whole plant
+- The slope of the relationship lessens with age  
+- There is quite a bit of noise in the relationship  
+- However, in many cases, older plants show less of a change in shoot diameter for a given change in basal diameter; the opposite pattern as is predicted if ever fewer shoots are sustaining growth  
+- Instead, each shoot matters ever less to the overall increase in basal area in larger plants
+- NOTE: Plots not correct right now - wrong number of points in some and definitely wrong coloring by age
+```{r, echo=FALSE,message=FALSE}
+plot((change_shoot_diam/100) ~ change_basal_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.spp[as.factor(species)], pch=16)
+abline(0,1)
+
+mod <- lm (change_shoot_diam ~ change_basal_diam*age,data=subset(SummaryInd, age>1.4))
+summary(mod)
+anova(mod)
+
+plot((change_shoot_diam/100) ~ change_basal_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.age2[as.factor(age)], pch=16)
+abline(0,1)
+legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")
+
+plot((change_shoot_area/10000) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16,ylim=c(0.01,500),cex=.7)
+points((change_basal_area) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=1)
+
+plot((change_shoot_area/10000) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=16,ylim=c(0.01,500),cex=.7)
+points((change_basal_area) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=1)
+
+yvar <- "change_shoot_diam"
+xvar <- "change_basal_diam"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="xy", col=col.age[as.factor(SummaryInd$age)],
+                    main=spp, xlab=xvar, ylab=yvar)
+  legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")
+}
+```
 

### 2015-05-06 results_RAschedules.Rmd
- Results_best new file with most interesting graphs and stories - Thoughts about RA schedules and RV curves mostly developed - Making progress with accessory tissues - Wrote a looping function that works to add se bars - very pleased to have gotten that

@@
 
+plot(ReproInv~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
 plot(RA~RGR, SummaryInd, log="x", col=col.age[as.factor(age)],pch=16)
@@
 lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
+                    main=spp, log="xy", xlab=xvar, ylab=yvar)
+
+  abline(lmfits[[spp]])
+}
+
+yvar <- "RGR"
+xvar <- "ReproInv"
+
+data <- subset(SummaryInd,RA>0&RGR>.04)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
 results <- summarise_all_fits(lmfits)
@@
 
+Model analyzed is: lm(log([[GrowthInv]]) ~  asin(sqrt([[RA]]))*asin(sqrt([[PropH]]))))
+
 The canopy species have, not suprisingly, a very obvious maxH, with Growth Investment or RGR tapering markedly at the maxH is approached.
@@
 the change in slope of the relationship.
-
 ```{r, echo=FALSE, message=FALSE}
@@
 results$p.value <- round(results$p.value,digits=3)
-
+names(results) <- c("species","r.sq_total","p-total","n","intercept","coef_RA","coef_PropH","coef_interaction","SS_RA","SS_PropH","SS_interaction")
 results
 
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
-                    main=spp, xlab=xvar, ylab=yvar)
-  abline(lmfits[[spp]])
-}
+yvar <- "GrowthInv"
+xvar <- "PropH"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))))
+results2 <- summarise_all_fits(lmfits)
+
+results2$r.squared <- round(results2$r.squared,digits=3)
+results2$p.value <- round(results2$p.value,digits=3)
+names(results2) <- c("species","r.sq.PropH","p.PropH","n","a","b")
+results2
+
+yvar <- "GrowthInv"
+xvar <- "RA"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))))
+results3 <- summarise_all_fits(lmfits)
+
+results3$r.squared <- round(results3$r.squared,digits=3)
+results3$p.value <- round(results3$p.value,digits=3)
+names(results3) <- c("species","r.sq.RA","p.RA","n","a","b")
+results3
+
+results <- merge(results, select(results2, -n, -a,-b), by="species")
+results <- merge(results, select(results3, -n, -a,-b), by="species")
+results
 ```

### 2015-05-06 results_accessory_tissues.rmd
- Results_best new file with most interesting graphs and stories - Thoughts about RA schedules and RV curves mostly developed - Making progress with accessory tissues - Wrote a looping function that works to add se bars - very pleased to have gotten that

@@
 
+se_function <- function(mean1,se1) {
+for(i in 1:14) {
+arrows(i,mean1[i]+se1[i],i,mean1[i]-se1[i],code=3,angle=90, length=0.1)
+}
+}
 ```
@@
                  xlab=xvar, ylab=yvar)
-mod <- lm(asin(sqrt(PerPropagule)) ~ species, data)
+mod <- lm(asin(sqrt(PerPropagule)) ~ species-1, data)
 summary(mod)
+data.frame(
+    select(glance(mod), r.squared, p.value),
+    n= length(resid(mod)),
+    a = coef(mod)[1],
+    b = coef(mod)[2]
+  )
+
+tmp <- summary(mod)
+tmp <- tmp$coefficients
+tmp <-as.data.frame(tmp)
+tmp <- cbind(names(labels.spp),tmp)
+names(tmp) <- c("species","estimate.trans","se.trans","t.value","p.value")
+tmp2 <- select(SummarySpp, species, PerPropagule_mean, PerPropagule_se)
+tmp <- merge(tmp, tmp2, by="species")
+tmp
+plot(PerPropagule_mean~species,tmp,cex.axis=.8,pch=16,log="y",ylim=c(.001,.25),main="Percent reproductive investment put into propagules")
+
+mean1 <- tmp$PerPropagule_mean
+se1 <- tmp$PerPropagule_se
+
+se_function(mean1,se1)
+
+#for(i in 1:14) {
+#arrows(i,tmp$PerPropagule_mean[i]+tmp$PerPropagule_se[i],i,tmp$PerPropagule_mean[i]-tmp$PerPropagule_se[i],code=3,angle=90, length=0.1)}
+
+#barplot(height=test$PerPropagule_mean, names=test$species,cex.axis=.8,ylim=c(0,.25),cex.names=.8)
+#xv <- barplot(height=test$PerPropagule_mean, names=test$species,cex.axis=.8,ylim=c(0,.25),cex.names=.8)
+#xv
+
+#points((PerPropagule_mean+PerPropagule_se)~species,test,pch=25)
+#points((PerPropagule_mean-PerPropagule_se)~species,test,pch=24)
+
+#Tuk <- TukeyHSD(mod)
 ```
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerAcc"
+yvar <- "PerPropagule"
 xvar <- "RA"

### 2015-05-06 results_best.Rmd
- Results_best new file with most interesting graphs and stories - Thoughts about RA schedules and RV curves mostly developed - Making progress with accessory tissues - Wrote a looping function that works to add se bars - very pleased to have gotten that

@@
 }
+
+xy.error.bars <- function (x,y,xbar,ybar) {
+  plot(x,y,pch=16, ylim=c(min(y-ybar),max(y+ybar)),xlim=c(min(x-xbar),max(x+xbar)))
+  arrows(x,y-ybar,x,y+ybar,code=3,angle=90, length=0.1)
+  arrows(x-xbar,y,x+xbar,y,code=3,angle=90, length=0.1)
+}
+
+se_function <- function(mean1,se1) {
+for(i in 1:14) {
+arrows(i,mean1[i]+se1[i],i,mean1[i]-se1[i],code=3,angle=90, length=0.1)
+}
+}
 ```
 
-#Ideas and plots to include in a paper looking at the ways in which reproductive investment impacts growth
+#Changes in growth and tissue allocation with age and size
 * Part of this paper would be to look at how different "types of" species fall out with respect to the various plots - i.e.
 canopy species (BAER, HATE, PELA), short-lived species (BOLE, PILI, COER), longer-lived understory species
-* Plants that grow more also reproduce more, but plants that allocate more to reproduction have lower RGR (Same paper as RA curves?)
-* There is a disinct decline in RGR (or Growth Investment) at the exact "PropH" that plants begin to reproduce (Same paper as RA curves?)
-
-##Growth-reproduction trade-off
-###Bigger plants reproduce more
-- There is a positive correlation between reproductive investment vs growth investment among individuals that are reproducing: plants that grow more also allocate more to reproduction.  
-- It is also true that bigger plants allocate more to reproduction.
-
-```{r, echo=FALSE,message=FALSE}
-plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-```
-
-###Plants that allocate more to reproduction (higher RA) have a lower RGR
-- When looked at individually, this pattern holds for all species except PEPU and PELA, although there is lots of variation in the exact trade-off pattern displayed by different species  
-- You can also look at the plots of RGR vs RA and identify the RA at which RGR is impacted.
-Some plots show a very linear decline throught, whereas for others there is a distinct "knickpoint" -i.e.
-BOLE, EPMI, HATE
-
-```{r, echo=FALSE,message=FALSE}
-plot(RA~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-mod <- lm(RGR~asin(sqrt(RA))*species,SummaryInd)
-anova(mod)
-```
 
@@
 
-#Ideas and plots to include in RA schedule paper
+#RA schedule paper
 * I have a dataset with enough resolution across species and ages to show patterns of growth and reproductive investment across ages  
-* This includes both RA schedules and RV curves, as well as other potential plots
+* This includes both RA schedules and RV curves  
+* Below are curves plotted relative to "PropH", which is a better fit for most species - but other species should be plotted against total plant weight  
+* Plants that grow more also reproduce more, but plants that allocate more to reproduction have lower RGR 
+* There is a disinct decline in RGR (or Growth Investment) at the exact "PropH" that plants begin to reproduce 
+* Plotting reproductive investment (ReproInv) against RGR yields a much lower r^2 - for every single species.
+Only RA captures the actual trade-off incurred by plants that allocate more to reproduction, showing one way RA schedules are important
+  - As discussed in the review, RA schedule differentiate between greater reproductive output because you are bigger (a positive correlation with plant growth) and greater reproductive output because you are allocating more to reproduction (a negative correlation with plant growth)
+* RV curves continue to be the more relevent metric to determine the actual amount of reproductive output produced by a plant of a given size or height
 
-###RV curves (by proportion max H)
+##RV curves (by proportion max H)
 - In a sense, by using proportion max H, these figures are showing the proportion of total growth the plant undergoes before starting reproduction
-- You could also plot against "PropMaxWeight", the proportion of the heaviest individual of that species. The two measures look "best" for different species
+- The plot across all species of reproductive investment vs. Prop H is much less tight than reproductive investment vs. total weight, but within a species not as obviously different  
+- The plot that includes all species shows that *once* a given species has ramped up reproduction, the log-log plot of reproductive investment vs final weight is nearly linear across all species; in other words, to first order, all species allocate the same amount to reproduction relative to their weight.
+- This is presumably the basic allometric scaling relationship discussed by others and wondering if slope I get is same as theirs    
+- However, it is important to note that species early in their reproductive trajectory do not follow this pattern  
 ```{r, echo=FALSE,message=FALSE}
 plot((ReproInv)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+plot(ReproInv~FinalWeight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+plot(ReproInv~height, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-#RA schedules (vs. propH)  
+##RA schedules (vs. propH)  
+- RA schedules still look "best" plotted against age; not shown here  
 - these curves are particularly good for a number of species such as EPMI, COER, PELA  
@@
 
+##Growth-reproduction trade-off
+###Bigger plants reproduce more
+- There is a positive correlation between reproductive investment vs growth investment among individuals that are reproducing: plants that grow more also allocate more to reproduction.  
+- It is also true that bigger plants allocate more to reproduction.
+
+```{r, echo=FALSE,message=FALSE}
+plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```
+
+###Plants that allocate more to reproduction (higher RA) have a lower RGR
+- When looked at individually, this pattern holds for all species except PEPU and PELA, although there is lots of variation in the exact trade-off pattern displayed by different species  
+- You can also look at the plots of RGR vs RA and identify the RA at which RGR is impacted.
+Some plots show a very linear decline throught, whereas for others there is a distinct "knickpoint" -i.e.
+BOLE, EPMI, HATE
+
+```{r, echo=FALSE,message=FALSE}
+plot(RA~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mod <- lm(RGR~asin(sqrt(RA))*species,SummaryInd)
+anova(mod)
+```
+
 ###To think about regarding RA schedules and RV curves
@@
 ** Once I have leaf weights, I'll be curious how leaf weight plots against PropH, this might be more of the story
+
+###Looking jointly at effects of RA and PropH on growth inveestment
+- Model analyzed is: lm(log([[GrowthInv]]) ~  asin(sqrt([[RA]]))*asin(sqrt([[PropH]]))))  
+- The canopy species have, not suprisingly, a very obvious maxH, with Growth Investment or RGR tapering markedly at the maxH is approached.
+In these species growth investment is poorly correlated with RA, but well correlated with height.
+- In some of the mid-height species (GRSP, BOLE, GRBU), growth investment is very poorly correlated with height, but better correlated with RA - in other words, increased RA = less growth.  
+- One of the difficult features interpreting this, is that there are species with overall higher correlations and overall lower correlations, and this pattern dominates, not the relative strength  
+- My current analyses still lack the ability to tease apart the most obvious pattern - because I don't actually want to show that growth and height are correlated, so much as that the   asymptoting of growth is correlated with height - i.e.
+the change in slope of the relationship.
+```{r, echo=FALSE, message=FALSE}
+yvar <- "GrowthInv"
+xvar <- "RA"
+x2var <- "PropH"
+
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))*asin(sqrt(x[[x2var]]))))
+results <- summarise_all_fits_2var(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+names(results) <- c("species","r,squared","p-value","n","intercept","coef_RA","coef_PropH","coef_interaction","SS_RA","SS_PropH","SS_interaction")
+results
+```
+
+#Shifts in accessory costs across species and ages
+##Overall results
+- Accessory costs higher for bigger seeds  
+- A number of species show fairly consistent declines in accessory costs with various measures of "bigger", including size, age, RA. Other species show no patterns  
+- 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases. in other words, they get better returns on investment the more they invest.  
+- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e.
+Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers
+- For most of the statistical analyses, the youngest site has been removed, since it included individuals that were harvested while flowering (and therefore never "got to" set fruit) and automatically have no "successful" reproduction.
+There are of course some individuals like this at other ages as well, but far fewer
+
+###How do accessory costs shift with seed size?
+- Larger-seeded species have higher accessory costs. 
+- Also shown in other studies and suggested as a mechanism for why angiosperms were able to have such small seeds (relative to gymnosperms, with no decrease in proportional accessory costs - with decreasing size)
+```{r, echo=FALSE,message=FALSE}
+yvar <- "PerAcc_mean"
+xvar <- "seed_size"
+data <- SummarySpp
+
+plot_yvar_vs_xvar(data, yvar, xvar,log="x",
+                  xlab=xvar, ylab=yvar)
+mod <- lm(log(seed_size)~PerAcc_mean,SummarySpp)
+summary(mod)
+anova(mod)
+```
+###Size versus proportion propagule
+- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
+- This is a much stronger relationship than shifts in RA by plant size  
+- There is also no relationship between RA and proportion of energy invested in propagules  
+- The model including both PerPropagule and RA confirms this - there is a strong species effect and strong PerPropagule effect, but RA not significant
+
+* This means: The larger species get less of a return on their investment in reproduction. They have higher accessory costs.
+
+- Species with larger seeds also have higher accessory costs - what we don't know is if "seed size" or "plant size" that is most important
+
+```{r, echo=FALSE, message=FALSE}
+plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>00),log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPropagule))*species,data=subset(SummaryInd,ReproInv>0))
+summary(mod)
+anova(mod)
+
+plot(PerPropagule_mean ~FinalWeight_mean, data=subset(SummarySppAge,RA_mean>0),log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mod <- lm(log(FinalWeight_mean) ~ asin(sqrt(PerPropagule_mean))*species,data=subset(SummarySppAge,RA_mean>0))
+#summary(mod)
+anova(mod)
+
+mod <- lm(log(FinalWeight) ~asin(sqrt(PerPropagule))*asin(sqrt(RA))*species,data=subset(SummaryInd,ReproInv>0))
+anova(mod)
+```
+
+### Shifts in PerPropagule and RA within species
+- The above models indicate that there is no overall "PerPropagule" by "species" interaction.
+Looking at individual species also indicates few species show a pattern - those that do show an increase in propagule investment (decreasing accessory costs) with increasing size
+    - COER, HATE, and PILI show a significant decrease in accessory costs with increasing size (p<0.05)  
+    - GRSP shows a marginally significant decrease in accessory costs with increasing size (0.05<p<0.10)  
+    - PEPU shows a marginally significant INCREASE in accessory costs with increasing size (0.05<p<0.10)  
+    - the plots are in the file with all accessory tissues results
+
+- There is of course also an increase in RA with increased plant weight (see RA section)
+- An added piece of this, is that WITHIN species, there is an INCREASE in allocation to propagules with increasing size (age) for many species
+    - BAER, COER, GRBU, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in accessory costs with increasing RA (p<0.05)  
+    - BOLE shows a marginally significant decrease in accessory costs with increasing RA (p ~ 0.10)
+
+```{r, echo=FALSE, message=FALSE}
+yvar <- "PerPropagule"
+xvar <- "FinalWeight"
+
+data <- filter(SummaryInd,Total>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+yvar <- "PerPropagule"
+xvar <- "RA"
+
+data <- filter(SummaryInd,Total>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+```
+
+###Do species differ in the proportional energy allocated to propagules (vs. accessory tissues)  
+- COER, EPMI, LEES, PILI invest the most energy in propagules  
+- HATE invests by far the least into propagules
+
+```{r, echo=FALSE, message=FALSE}
+yvar <- "PerPropagule"
+xvar <- "species"
+data <- filter(SummaryInd,Total>0)
+
+mod <- lm(asin(sqrt(PerPropagule)) ~ species-1, data)
+summary(mod)
+data.frame(
+    select(glance(mod), r.squared, p.value),
+    n= length(resid(mod)),
+    a = coef(mod)[1],
+    b = coef(mod)[2]
+  )
+
+tmp <- summary(mod)
+tmp <- tmp$coefficients
+tmp <-as.data.frame(tmp)
+tmp <- cbind(names(labels.spp),tmp)
+names(tmp) <- c("species","estimate.trans","se.trans","t.value","p.value")
+tmp2 <- select(SummarySpp, species, PerPropagule_mean, PerPropagule_se)
+tmp <- merge(tmp, tmp2, by="species")
+tmp
+plot(PerPropagule_mean~species,tmp,cex.axis=.8,pch=16,log="y",ylim=c(.001,.25),main="Percent reproductive investment put into propagules")
+
+mean1 <- tmp$PerPropagule_mean
+se1 <- tmp$PerPropagule_se
+
+se_function(mean1,se1)
+```

### 2015-05-07 results_best.Rmd
continued work thinking about accessory parts patterns

@@
 - Accessory costs higher for bigger seeds  
+- Accessory costs higher for bigger species; these are the same species that invest less in RA  
+- Of course there is also a correlation between seed size and plant size, but actually not as strong as the accessory cost one, presumably because older plants have lower accessory costs as well as species that are inherently bigger
 - A number of species show fairly consistent declines in accessory costs with various measures of "bigger", including size, age, RA. Other species show no patterns  
-- 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases. in other words, they get better returns on investment the more they invest.  
+- Lower pre-pollination costs in plants with higher RA: 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases.
+in other words, they get better returns on investment the more they invest.
+(This is just a pattern within, not across, species)
 - Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e.
 Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers
+- Haven't actually run all the rest, but assume all reproductive tissue types will differ in proportional allocation across species
 - For most of the statistical analyses, the youngest site has been removed, since it included individuals that were harvested while flowering (and therefore never "got to" set fruit) and automatically have no "successful" reproduction.
@@
 - Species with larger seeds also have higher accessory costs - what we don't know is if "seed size" or "plant size" that is most important  
+- I've also included the plot of "Propagule Allocation", the proportion of total surplus energy allocated to propagules, which combines the RA and Proportion Propagule effects  
+- Not shown, but there is a just barely significant relationship between RA and PerPropagule - in other words, although bigger species have slightly lower RA values than smaller species, this is not an important trend
+
+- Overall with plant weight:  
+within species:  
+- greater plant weight = higher RA  (plants allocate more to reproduction when bigger/older)**
+- plant weight = little effect on proportion to propagules  
+- plant weight = little effect on pre-pollination tissues
+
+across species  
+- greater plant weight = lower RA  (spending more on growth and survival)**
+- greater plant weight = lower proportion to propagules  (bigger species get less for their allocation)**
+- plant weight = little effect on pre-pollination tissues
+
+finally,
+
+within species:
+- higher RA = lower allocation to pre-pollination tissues (compounding returns)**
 
 ```{r, echo=FALSE, message=FALSE}
-plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>00),log="xy", col=col.spp[as.factor(species)],pch=16)
+plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPropagule))*species,data=subset(SummaryInd,ReproInv>0))
+mod <- lm(log(FinalWeight) ~ (log(PerPropagule))*species,data=subset(SummaryInd,PerPropagule>0))
 summary(mod)
@@
 
-plot(PerPropagule_mean ~FinalWeight_mean, data=subset(SummarySppAge,RA_mean>0),log="xy", col=col.spp[as.factor(species)],pch=16)
+plot(PropAllocation ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-mod <- lm(log(FinalWeight_mean) ~ asin(sqrt(PerPropagule_mean))*species,data=subset(SummarySppAge,RA_mean>0))
-#summary(mod)
+mod <- lm(log(FinalWeight) ~ (log(PropAllocation))*species*age,data=subset(SummaryInd,PerPropagule>0))
+summary(mod)
 anova(mod)
 
-mod <- lm(log(FinalWeight) ~asin(sqrt(PerPropagule))*asin(sqrt(RA))*species,data=subset(SummaryInd,ReproInv>0))
-anova(mod)
+#plot(RA ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16,ylim=c(.02,1))
+#legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+#plot(PerPropagule ~RA, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
+#legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+```
+
+###Shifts in proportional pre-pollination costs with plant weight
+- No pattern within or across species when plotted against size  
+- However, higher RA = lower pre-pollination costs
+
+```{r, echo=FALSE, message=FALSE}
+mean1 <- SummarySpp$PerPrePol_All_mean
+se1 <- SummarySpp$PerPrePol_All_se
+
+plot(mean1~species,SummarySpp,cex.axis=.8,pch=16,ylim=c(.1,1),main="Percent reproductive investment put into packaging and dispersal")
+se_function(mean1,se1)
+
+plot(asin(sqrt(PerPrePol_All))~FinalWeight, data=subset(SummaryInd,PerPrePol_All>0),log="x", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+yvar <- "PerPrePol_All"
+xvar <- "FinalWeight"
+
+data <- subset(SummaryInd, Total>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+plot(asin(sqrt(PerPrePol_All))~RA, data=subset(SummaryInd,PerPrePol_All>0),log="x", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+yvar <- "PerPrePol_All"
+xvar <- "RA"
+
+data <- subset(SummaryInd, Total>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+```
+
+#Shifts in packaging and dispersal costs with plant weight
+- Species very different from one another, but no shift with size  
+- However quite a few species (BAER, BOLE, COER, GRBU. GRSP, HATE, HEPU, PILI increase the percent reproductive investment spent on packaging and dispersal with age  
+```{r, echo=FALSE, message=FALSE}
+plot(asin(sqrt(PerPackDisp)) ~FinalWeight, data=subset(SummaryInd,PerPackDisp>0),log="x", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+plot(asin(sqrt(PerPackDisp)) ~RA, data=subset(SummaryInd,PerPackDisp>0),log="x", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+yvar <- "PerPackDisp"
+xvar <- "FinalWeight"
+
+data <- subset(SummaryInd, Total>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+mean1 <- SummarySpp$PerPackDisp_mean
+se1 <- SummarySpp$PerPackDisp_se
+
+plot(mean1~species,SummarySpp,cex.axis=.8,pch=16,log="y",ylim=c(.01,1),main="Percent reproductive investment put into packaging and dispersal")
+se_function(mean1,se1)
 ```
@@
 lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~ log(x[[xvar]])))
+
 results <- summarise_all_fits(lmfits)

### 2015-05-07 results_best.Rmd
some script at bottom starting to extract counts of reproductive parts from Konrad's data

@@
 ```
+
+#Working to get counts out of Konrad's reproduction data
+tmpBAER <- BAER_Investment
+FD_BAER <- as.data.frame(tmpBAER$FD)
+Error_BAER <- as.data.frame(tmpBAER$Error)
+View(FD_BAER)
+
+BAER_count <- FD_BAER %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+
+BAER_count2 <- Error_BAER %>%
+  group_by(Individual, Element) %>%
+  summarise_each(funs(sum), Count)
+
+BAER_count2 <- subset(BAER_count2,Count>0)
+
+names(BAER_count2)=c("Individual","what","Error")
+BAER_count <- merge(BAER_count,BAER_count2,by=c("Individual","what"),all=TRUE)

### 2015-05-12 results_best.Rmd
-mostly finished thinking through accessory costs data -extracted "counts" of flower and fruit parts from Konrad's data, but some problems with it

--- 2015-05-06 results_best.Rmd
@@
 }
+}
+
+words.top.right.logxy <- function (x) {
+output <- data.frame(select(glance(x), r.squared, p.value))
+output <- round(output,4)
+text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
+text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
+}
+
+words.top.right.logx <- function (x) {
+output <- data.frame(select(glance(x), r.squared, p.value))
+output <- round(output,4)
+text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
+text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
+}
+
+words.top.right <- function (x) {
+output <- data.frame(select(glance(x), r.squared, p.value))
+output <- round(output,4)
+text(((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
+text(((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
+}
+
+words.bottom.right.logxy <- function (x) {
+output <- data.frame(select(glance(x), r.squared, p.value))
+output <- round(output,4)
+text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.1*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
+text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.05*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
 }
@@
 - Accessory costs higher for bigger seeds
+
+- Accessory costs higher for bigger species; these are the same species that invest less in RA
+
+- Of course there is also a correlation between seed size and plant size, but actually not as strong as the accessory cost one, presumably because older plants have lower accessory costs as well as species that are inherently bigger
+
 - A number of species show fairly consistent declines in accessory costs with various measures of "bigger", including size, age, RA. Other species show no patterns  
-- 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases. in other words, they get better returns on investment the more they invest.  
+- Lower pre-pollination costs in plants with higher RA: 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases.
+in other words, they get better returns on investment the more they invest.
+(This is just a pattern within, not across, species)
 - Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e.
 Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers
+- Haven't actually run all the tests, but assume all reproductive tissue types will differ in proportional allocation across species
 - For most of the statistical analyses, the youngest site has been removed, since it included individuals that were harvested while flowering (and therefore never "got to" set fruit) and automatically have no "successful" reproduction.
@@
 
+##Basic questions
 ###How do accessory costs shift with seed size?
@@
 - Also shown in other studies and suggested as a mechanism for why angiosperms were able to have such small seeds (relative to gymnosperms, with no decrease in proportional accessory costs - with decreasing size)
+-  As shown below, bigger species also have higher accessory costs (and also bigger seeds - cause vs. effect unknown)
 ```{r, echo=FALSE,message=FALSE}
-yvar <- "PerAcc_mean"
-xvar <- "seed_size"
-data <- SummarySpp
+mod <- lm(log(seed_size)~asin(sqrt(PerAcc_mean)),SummarySpp)
+plot(PerAcc_mean~seed_size,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)])
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+```
 
-plot_yvar_vs_xvar(data, yvar, xvar,log="x",
-                  xlab=xvar, ylab=yvar)
-mod <- lm(log(seed_size)~PerAcc_mean,SummarySpp)
-summary(mod)
+###Why measure "Total Reproductive Investment" instead of "seed weight" or "fruit weight"?  
+- The R^2 for the plot of total reproductive investment against total plant size is much stronger than plotting seed weight against total plant size (R^2 = 0.61 vs 0.33)  
+- Adding propagule + packaging & dispersal (i.e. successful reproduction costs), improves the fit somewhat (R^2 =0.55)  
+- Total pre-pollination costs are also well-correlated with plant size, indicating bigger plants have more flowers
+- NEXT: Once I have all parts weights, plot against fruit weight
+
+```{r, echo=FALSE,message=FALSE}
+mod <- lm (log(FinalWeight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
+plot(ReproInv~FinalWeight,data=subset(SummaryInd,ReproInv>0), log="xy",col=col.spp[as.factor(species)], pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+mod <- lm (log(FinalWeight)~log(Prop), data=subset(SummaryInd,Prop>0))
+plot(Prop~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+mod <- lm (log(FinalWeight)~log(Prop+PD), data=subset(SummaryInd,Prop>0))
+plot((Prop+PD)~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+mod <- lm (log(FinalWeight)~log(PrePol_All), data=subset(SummaryInd,PrePol_All>0))
+plot((PrePol_All)~FinalWeight,data=subset(SummaryInd,PrePol_All>0), log="xy",col=col.spp[as.factor(species)], pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+```
+
+###Looking at counts
+- Final weight vs. #flowers+buds
+- Final weight vs. #fruit
+
+##Across species patterns of note
+###Size versus proportional propagule investment
+- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
+   1.  This is another way of showing that larger species get less of a return on their investment in reproduction. They have higher accessory costs. 
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+species,data=subset(SummaryInd,PerPropagule>0))
 anova(mod)
+plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logxy(mod)
+text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes species effect",adj=0) 
 ```
-###Size versus proportion propagule
-- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
-- This is a much stronger relationship than shifts in RA by plant size  
-- There is also no relationship between RA and proportion of energy invested in propagules  
-- The model including both PerPropagule and RA confirms this - there is a strong species effect and strong PerPropagule effect, but RA not significant
 
-* This means: The larger species get less of a return on their investment in reproduction. They have higher accessory costs.
-
-- Species with larger seeds also have higher accessory costs - what we don't know is if "seed size" or "plant size" that is most important
-
+- Species that are bigger also invest a lower proportion of their TOTAL surplus energy in propagules (proportion propagules*RA) 
+  + This is noisier than looking simply at proportion reproductive allocation to propagules, because of the RA effects - see below
 ```{r, echo=FALSE, message=FALSE}
-plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>00),log="xy", col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(FinalWeight) ~ (log(PropAllocation))*species*age,data=subset(SummaryInd,PerPropagule>0))
+plot(PropAllocation ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPropagule))*species,data=subset(SummaryInd,ReproInv>0))
-summary(mod)
-anova(mod)
-
-plot(PerPropagule_mean ~FinalWeight_mean, data=subset(SummarySppAge,RA_mean>0),log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-mod <- lm(log(FinalWeight_mean) ~ asin(sqrt(PerPropagule_mean))*species,data=subset(SummarySppAge,RA_mean>0))
-#summary(mod)
-anova(mod)
-
-mod <- lm(log(FinalWeight) ~asin(sqrt(PerPropagule))*asin(sqrt(RA))*species,data=subset(SummaryInd,ReproInv>0))
+words.top.right.logxy(mod)
+text(1000,.6e-4,"includes species effect",adj=0)
 anova(mod)
@@
 
-### Shifts in PerPropagule and RA within species
-- The above models indicate that there is no overall "PerPropagule" by "species" interaction.
-Looking at individual species also indicates few species show a pattern - those that do show an increase in propagule investment (decreasing accessory costs) with increasing size
-    - COER, HATE, and PILI show a significant decrease in accessory costs with increasing size (p<0.05)  
-    - GRSP shows a marginally significant decrease in accessory costs with increasing size (0.05<p<0.10)  
-    - PEPU shows a marginally significant INCREASE in accessory costs with increasing size (0.05<p<0.10)  
-    - the plots are in the file with all accessory tissues results
+- Looking at RA with plant size is not very informative, because:
+  1. RA increases with plant size within a species  
+  2. decreases with plant size across species  
+  3. in combination they are noisy
+- The first plot is all points  
+- The second plot is just 7-year olds, showing the decrease in RA with plant size  
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(FinalWeight) ~ (log(RA)),data=subset(SummaryInd,RA>0))
+plot(RA ~FinalWeight, data=subset(SummaryInd,RA>0),log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+anova(mod)
 
-- There is of course also an increase in RA with increased plant weight (see RA section)
-- An added piece of this, is that WITHIN species, there is an INCREASE in allocation to propagules with increasing size (age) for many species
-    - BAER, COER, GRBU, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in accessory costs with increasing RA (p<0.05)  
-    - BOLE shows a marginally significant decrease in accessory costs with increasing RA (p ~ 0.10)
+mod <- lm(log(FinalWeight) ~ (log(RA)),data=subset(SummaryInd,RA>5e-3&age==7))
+plot(RA ~FinalWeight, data=subset(SummaryInd,RA>5e-3&age==7),log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logxy(mod)
+```
 
+- A model including the effect of both PerPropagule and RA on FinalWeight confirms this - there is a strong species effect and strong PerPropagule effect, but RA is much less significant  
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(FinalWeight) ~ (log(RA))*log(PerPropagule)*species,data=subset(SummaryInd,PerPropagule>0))
+anova(mod)
+```
+
+- Proportional investment in all pre-pollination tissues is uncorrelated with plant size (at most ages)  
+  +  if age included in model, becomes highly significant  
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0&age>3))
+plot(asin(sqrt(PerPrePol_All)) ~ FinalWeight, data=subset(SummaryInd,PerPrePol_All>0),log="x", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logx(mod)
+```
+
+- Shifts in packaging and dispersal costs with plant weight
+- Species very different from one another, but no shift with size 
+- Also no pattern w/r RA (not shown)
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPackDisp)),data=subset(SummaryInd,PerPackDisp>0))
+plot(asin(sqrt(PerPackDisp)) ~FinalWeight, data=subset(SummaryInd,PerPackDisp>0),log="x", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logx(mod)
+```
+
+###Across species summary
+- greater plant weight = lower RA  (spending more on growth and survival)**  
+- greater plant weight = lower proportion to propagules  (bigger species get less for their allocation)**  
+- plant weight = little effect on pre-pollination tissues
+
+##Within species (across age, size, or RA) patterns to note
+- Only COER and HATE increase allocation to propagules with increased plant size  
+- This, together with other plots, indicates that only the plants (of a species) that have higher RA, have higher propagule investment; but not all bigger individuals have higher RA
+NOTE: Plot nearly same as above, except y-axis arcsine transformed, not log transformed and R^2 values without species term
 ```{r, echo=FALSE, message=FALSE}
@@
 
-data <- filter(SummaryInd,Total>0)
+data <- subset(SummaryInd, Total>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+mod <- lm(log(FinalWeight)~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
+plot(asin(sqrt(PerPropagule))~log(FinalWeight), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right(mod)
+```
+
+- Allocation to propagules increases with RA in all species except EPMI, PHPH, PILI, PUTU  
+- again, probably a figment of overall increased allocation (higher RA) if propagules form  
+```{r, echo=FALSE, message=FALSE}
+yvar <- "PerPropagule"
+xvar <- "RA"
+
+data <- subset(SummaryInd, Total>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
+plot(asin(sqrt(PerPropagule))~asin(sqrt(RA)), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right(mod)
+```
+
+###Change in proportional allocation to pre-pollination tissues with plant weight 
+- only a few species show a significant correlation -> as plants grow, they don't shift this allocation  
+```{r, echo=FALSE, message=FALSE}
+yvar <- "PerPrePol_All"
+xvar <- "FinalWeight"
+
+data <- subset(SummaryInd, Total>0)
 data <- split(data, data$species)
@@
 results
+```
 
-yvar <- "PerPropagule"
+###Change in proportional allocation to pre-pollination tissues with RA
+- 9 species decrease allocation to pre-pollination tissues with increased RA  
+- this could simply be because when/if flowers are pollinated, there is increased reproductive investment, increasing RA and decreasing pre-pollination allocation  
+- Interesting that RA increases with plant size, and pre-pollination decreases with RA, but very low correlation between pre- pollination allocation and plant size  
+```{r, echo=FALSE, message=FALSE}
+yvar <- "PerPrePol_All"
 xvar <- "RA"
 
-data <- filter(SummaryInd,Total>0&age>2)
+data <- subset(SummaryInd, Total>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0))
+plot(asin(sqrt(PerPrePol_All))~asin(sqrt(RA)), data=subset(SummaryInd,PerPrePol_All>0),col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right(mod)
+```
+
+- Quite a few species (BAER, BOLE, COER, GRBU, GRSP, HATE, HEPU, PEPU, PHPH increase the percent reproductive investment spent on packaging and dispersal with age 
+- This probably reflects increased seed set with age and the simulatenous increase in this pool
+```{r, echo=FALSE, message=FALSE}
+yvar <- "PerPackDisp"
+xvar <- "RA"
+
+data <- subset(SummaryInd, Total>0)
 data <- split(data, data$species)
@@
 
-###Do species differ in the proportional energy allocated to propagules (vs. accessory tissues)  
+###Within species summary
+- greater plant weight = higher RA  (plants allocate more to reproduction when bigger/older)**
+- plant weight = little effect on proportion to propagules  
+- plant weight = little effect on pre-pollination tissues  
+- higher RA = lower allocation to pre-pollination tissues (probably because more seed set)
+- higher RA = greater allocation to propagules (probably because more seed set)
+
+##Shifts in proportion to tissue types across species  
+- Propagule allocation across species  
 - COER, EPMI, LEES, PILI invest the most energy in propagules  
 - HATE invests by far the least into propagules  
+```{r, echo=FALSE, message=FALSE}
+#mod <- lm(asin(sqrt(PerPropagule)) ~ species-1, data=subset((SummaryInd,Total>0))
+#tmp <- summary(mod)
+#tmp <- tmp$coefficients
+#tmp <-as.data.frame(tmp)
+#tmp <- cbind(names(labels.spp),tmp)
+#names(tmp) <- c("species","estimate.trans","se.trans","t.value","p.value")
+mean1 <- SummarySpp$PerPropagule_mean
+se1 <- SummarySpp$PerPropagule_se
+plot(mean1~species,SummarySpp,cex.axis=.7,pch=16,log="y",ylim=c(.002,.25),main="Percent reproductive investment put into propagules")
+se_function(mean1,se1)
+```
+
+- pre-pollination allocation across species
 
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPropagule"
-xvar <- "species"
-data <- filter(SummaryInd,Total>0)
+mean1 <- SummarySpp$PerPrePol_All_mean
+se1 <- SummarySpp$PerPrePol_All_se
+plot(mean1~species,data=subset(SummarySpp),cex.axis=.8,pch=16,ylim=c(.1,1),main="Percent reproductive investment put into pre-pollination tissues")
+se_function(mean1,se1)
+```
 
-mod <- lm(asin(sqrt(PerPropagule)) ~ species-1, data)
-summary(mod)
-data.frame(
-    select(glance(mod), r.squared, p.value),
-    n= length(resid(mod)),
-    a = coef(mod)[1],
-    b = coef(mod)[2]
-  )
+- just looking among plants >3 years old
 
-tmp <- summary(mod)
-tmp <- tmp$coefficients
-tmp <-as.data.frame(tmp)
-tmp <- cbind(names(labels.spp),tmp)
-names(tmp) <- c("species","estimate.trans","se.trans","t.value","p.value")
-tmp2 <- select(SummarySpp, species, PerPropagule_mean, PerPropagule_se)
-tmp <- merge(tmp, tmp2, by="species")
-tmp
-plot(PerPropagule_mean~species,tmp,cex.axis=.8,pch=16,log="y",ylim=c(.001,.25),main="Percent reproductive investment put into propagules")
+```{r, echo=FALSE, message=FALSE}
+tmp <- SummaryInd %>%
+  filter(Total!=0&age>3) %>%
+  group_by(species) %>%
+  summarise_each(funs(mean, se), PerPrePol_All)
 
-mean1 <- tmp$PerPropagule_mean
-se1 <- tmp$PerPropagule_se
+plot(mean~species,
+    tmp,
+     cex.axis=.7,pch=16,log="y",ylim=c(.1,1),
+     main="Percent reproductive investment put into pre-pollination tissues")
+
+mean1 <- tmp$mean
+se1 <- tmp$se
+se_function(mean1,se1)
+```
+
+- Packaging and dispersal allocation across species
+
+```{r, echo=FALSE, message=FALSE}
+mean1 <- SummarySpp$PerPackDisp_mean
+se1 <- SummarySpp$PerPackDisp_se
+
+plot(mean1~species,SummarySpp,cex.axis=.8,pch=16,log="y",ylim=c(.02,1),main="Percent reproductive investment put into packaging and dispersal")
+se_function(mean1,se1)
+```
+
+- just looking among plants >3 years old
+
+```{r, echo=FALSE, message=FALSE}
+tmp2 <- SummaryInd %>%
+  filter(Total!=0&age>3) %>%
+  group_by(species) %>%
+  summarise_each(funs(mean, se), PerPackDisp)
+
+plot(mean~species,
+    tmp2,
+     cex.axis=.7,pch=16,log="y",ylim=c(0.02,.8),
+     main="Percent reproductive investment put into packaging & dispersal tissues")
+
+mean1 <- tmp2$mean
+se1 <- tmp2$se
 
@@
 ```
+
+###Across species summary
+- nothing much shifts with plant size
+- most pool shift with RA, but that is likely because higher RA often means increased seed set - higher RA occurs because some flowers pollinated and mature, which shifts proportional allocation to post-pollination pools
+- has interesting implications for what RA means if it is closely linked to increased seed set (or aborted fruit production)
+
+#Working to get counts out of Konrad's reproduction data
+```{r, echo=FALSE, message=FALSE}
+tmp <- BAER_Investment
+FD <- as.data.frame(tmp$FD)
+BAER_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+BAER_count <- subset(BAER_count, count!=0)
+BAER_count$species <- "BAER"
+
+tmp <- BOLE_Investment
+FD <- as.data.frame(tmp$FD)
+BOLE_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+BOLE_count <- subset(BOLE_count, count!=0)
+BOLE_count$species <- "BOLE"
+
+tmp <- COER_Investment
+FD <- as.data.frame(tmp$FD)
+COER_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+COER_count <- subset(COER_count, count!=0)
+COER_count$species <- "COER"
+
+tmp <- EPMI_Investment
+FD <- as.data.frame(tmp$FD)
+EPMI_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+EPMI_count <- subset(EPMI_count, count!=0)
+EPMI_count$species <- "EPMI"
+
+tmp <- GRBU_Investment
+FD <- as.data.frame(tmp$FD)
+GRBU_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+GRBU_count <- subset(GRBU_count, count!=0)
+GRBU_count$species <- "GRBU"
+
+tmp <- GRSP_Investment
+FD <- as.data.frame(tmp$FD)
+GRSP_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+GRSP_count <- subset(GRSP_count, count!=0)
+GRSP_count$species <- "GRSP"
+
+##haven't continued with remaining species, because of problems described
+accessory_count <- rbind(BAER_count,BOLE_count,COER_count,EPMI_count,GRBU_count,GRSP_count)
+```
+
+TO DO
+- seed set with age - this is probably what explains a lot of changes in proportional tissue alotment. 
+-Big question is if seed set changes with plant size or age

### 2015-05-12 results_best.Rmd
forgot to save final changes before

@@
 
-#Working to get counts out of Konrad's reproduction data
+#getting counts out of Konrad's reproduction data
 ```{r, echo=FALSE, message=FALSE}
@@
 
-##haven't continued with remaining species, because of problems described
-accessory_count <- rbind(BAER_count,BOLE_count,COER_count,EPMI_count,GRBU_count,GRSP_count)
+tmp <- HATE_Investment
+FD <- as.data.frame(tmp$FD)
+HATE_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+HATE_count <- subset(HATE_count, count!=0)
+HATE_count$species <- "HATE"
+
+tmp <- HEPU_Investment
+FD <- as.data.frame(tmp$FD)
+HEPU_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+HEPU_count <- subset(HEPU_count, count!=0)
+HEPU_count$species <- "HEPU"
+
+tmp <- LEES_Investment
+FD <- as.data.frame(tmp$FD)
+LEES_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+LEES_count <- subset(LEES_count, count!=0)
+LEES_count$species <- "LEES"
+
+tmp <- PELA_Investment
+FD <- as.data.frame(tmp$FD)
+PELA_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+PELA_count <- subset(PELA_count, count!=0)
+PELA_count$species <- "PELA"
+
+tmp <- PEPU_Investment
+FD <- as.data.frame(tmp$FD)
+PEPU_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+PEPU_count <- subset(PEPU_count, count!=0)
+PEPU_count$species <- "PEPU"
+
+tmp <- PHPH_Investment
+FD <- as.data.frame(tmp$FD)
+PHPH_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+PHPH_count <- subset(PHPH_count, count!=0)
+PHPH_count$species <- "PHPH"
+
+tmp <- PILI_Investment
+FD <- as.data.frame(tmp$FD)
+PILI_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+PILI_count <- subset(PILI_count, count!=0)
+PILI_count$species <- "PILI"
+
+tmp <- PUTU_Investment
+FD <- as.data.frame(tmp$FD)
+PUTU_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+PUTU_count <- subset(PUTU_count, count!=0)
+PUTU_count$species <- "PUTU"
+
+accessory_count <- rbind(BAER_count,BOLE_count,COER_count,EPMI_count,GRBU_count,GRSP_count,HATE_count,HEPU_count,LEES_count,PELA_count,PEPU_count,PHPH_count,PILI_count,PUTU_count)
 ```

### 2015-05-14 counts.rmd
scripts I'm testing - nothing real

SummaryInd <- merge(SummaryInd,select(accessory_count, -species), by="individual",all.x=TRUE)

count_lots_columns <- separate(accessory_count, count,c("bud_small","bud_mid","bud_big","flower_aborted","bud_just_opening","flower_petals_small","flower_petals","fruit_aborted","flower_stigma","flower_calyx","bract_flower_or_finished_flower","flower_style","finished_flower","finished_flower_stigma","late_finished_flower","inflorescence_stalk_in_fruit_large","inflorescence_stalk_in_fruit_very_large","fruit_just_starting","calyx_fruit",fruit_young","pedicel","fruit_large_immature_01","fruit_large_immature_02","fruit_large_immature_03","fruit_large_immature_04","fruit_large_immature_05","fruit_large_immature_06","fruit_empty","fruit_mature","bract_fruit","seed_pod","seed_immature","seed_aborted","seed","cone_just_starting_01","cone_just_starting_02","cone_just_starting_03","cone_just_starting_04","cone_just_starting_05","cone_young_01","cone_young_02","cone_young_03","cone_young_04","cone_green_01","cone_green_02","cone_green_03","cone_green_04","cone_brown_no_expanded_follicles","cone_brown","cone_aborted","cone_base_green_01","cone_base_green_02","cone_base_green_03","cone_base_green_04","cone_base_brown"),sep=",",remove=TRUE,extra="drop")

View(accessory_count)
View(count_lots_columns)

count_lots_columns <- separate(accessory_count,count,into=c("bud_small","bud_mid","bud_big","flower_aborted","bud_just_opening","flower_petals_small","flower_petals","fruit_aborted","flower_stigma"),sep=",",remove=TRUE,extra="drop")

par(mfrow=c(1,2), cex=1, omi=c(.1,0.1,0.1,0.1), mai=c(1.2,1,0.1,0.1))

plot(seedset ~ FinalWeight,data=subset(SummaryInd,seedset>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",xlab="plant weight",ylab="seed set") 
plot(seedset ~ RA,data=subset(SummaryInd,seedset>0),
          col=col.spp[as.factor(species)],
          pch=16,log="xy",ylab="")
plot.new()

td.means.comp$whole.stem.density,td.means.comp$stature,td.means.comp$genus,
           xlabel="",ylabel="Whole stem density",
           my.colors = unique(color.by.comp),
           yrange = c(0,1), xrange=c(0.5,2.5))
axis(1, at=c(1,2), labels=c("Short", "Tall"))
line.plot( td.means.comp$pith.density,td.means.comp$stature,td.means.comp$genus,
           xlabel="",ylabel="Pith density",
           my.colors = unique(color.by.comp),
           yrange = c(0,1), xrange=c(0.5,2.5))
axis(1, at=c(1,2), labels=c("Short", "Tall"))
plot.new()
line.plot( td.means.comp$wood.density,td.means.comp$stature,td.means.comp$genus,
           xlabel="",ylabel="Wood density",
           my.colors = unique(color.by.comp),
           yrange = c(0,1), xrange=c(0.5,2.5))
axis(1, at=c(1,2), labels=c("Short", "Tall"))
line.plot( td.means.comp$bark.density,td.means.comp$stature,td.means.comp$genus,
           xlabel="",ylabel="Bark density",
           my.colors = unique(color.by.comp),
           yrange = c(0,1), xrange=c(0.5,2.5))
axis(1, at=c(1,2), labels=c("Short", "Tall"))
plot.new()

### 2015-05-14 results_best.Rmd
some work on looking at counts - suspect file doesn't "knit" at the moment

@@
 output <- round(output,4)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
+text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
+text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
+text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
 }
@@
 output <- round(output,4)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
+text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
+text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
+text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
 }
@@
 output <- round(output,4)
-text(((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
-text(((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
+text(((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
+text(((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
+text(((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
 }
@@
 output <- round(output,4)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.1*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.05*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
+text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
+text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
+text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
 }
@@
    1.  This is another way of showing that larger species get less of a return on their investment in reproduction. They have higher accessory costs. 
+   - There is also an increase in propagule investment with age
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+species,data=subset(SummaryInd,PerPropagule>0))
-anova(mod)
+mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+age,data=subset(SummaryInd,PerPropagule>0))
+summary(mod)
 plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
@@
 words.top.right.logxy(mod)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes species effect",adj=0) 
+text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes age effect",adj=0) 
 ```
@@
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ (log(PropAllocation))*species*age,data=subset(SummaryInd,PerPropagule>0))
+mod <- lm(log(FinalWeight) ~ (log(PropAllocation))*age,data=subset(SummaryInd,PerPropagule>0))
 plot(PropAllocation ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
@@
 words.top.right.logxy(mod)
-text(1000,.6e-4,"includes species effect",adj=0)
-anova(mod)
+text(1000,.6e-4,"includes age effect (increase in Prop Allocation with age)",adj=0)
+summary(mod)
 ```
@@
 
-#getting counts out of Konrad's reproduction data
+##Looking at 
+- Species that are smaller have lower seed set -> this is likely what is causing Propagule allocation to decrease with size
+- Also a small increase in seedset with age - but a smaller effect
+
+```{r, echo=FALSE, message=FALSE}
+par(mfrow=c(2,2), cex=1, omi=c(.1,0.1,0.1,0.1), mai=c(1.2,1,0.1,0.1))
+mod <- lm(log(FinalWeight)~log(seedset),data=subset(SummaryInd,seedset>0))
+plot(seedset ~ FinalWeight,data=subset(SummaryInd,seedset>0),
+          col=col.spp[as.factor(species)],
+          pch=16,log="xy",xlab="",ylab="seed set")
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(RA)~log(seedset),data=subset(SummaryInd,seedset>0))
+plot(seedset ~ RA,data=subset(SummaryInd,seedset>0),
+          col=col.spp[as.factor(species)],
+          pch=16,log="xy",ylab="",xlab="")
+words.bottom.right.logxy(mod)
+mod <- lm(log(FinalWeight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
+plot(seed_count ~ FinalWeight,data=subset(SummaryInd,seed_count>0),
+          col=col.spp[as.factor(species)],
+          pch=16,log="xy",xlab="plant weight",ylab="seed count")
+words.bottom.right.logxy(mod)
+mod <- lm(log(RA)~log(seed_count),data=subset(SummaryInd,seed_count>0))
+plot(seed_count ~ RA,data=subset(SummaryInd,seed_count>0),
+          col=col.spp[as.factor(species)],
+          pch=16,log="xy",ylab="")
+words.bottom.right.logxy(mod)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```
+
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(FinalWeight)~log(PerPropagule),data=subset(SummaryInd,seedset>0))
+plot(PerPropagule~FinalWeight,data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logxy(mod)
+```
+
+- However, as shown above, there is no clear shift across plant size in pre-pollination allocation   
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(asin(sqrt(PerPrePol_All)) ~log(FinalWeight)*age, data=subset(SummaryInd,PerPrePol_All>0))
+anova(mod)
+```
+
+- There is however a decrease in RA with plant size at a given age (across species effect)
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(asin(sqrt(RA)) ~ log(FinalWeight)*age, data=subset(SummaryInd,RA>0))
+plot(asin(sqrt(RA))~FinalWeight,data=subset(SummaryInd,seedset>0),col=col.spp[as.factor(species)],pch=16,log="x")
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logx(mod)
+anova(mod)
+```
+
+- Together this indicates that increased propagule allocation is due to increased seedset, which increases RA in smaller-sized species
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(asin(sqrt(RA))~age*species,data=subset(SummaryInd,RA>0))
+anova(mod)
+```
+
+- seedset and Proportional allocation to propagules (vs. all accessory tissues) are well correlated, within and across species  
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(seedset)~log(PerPropagule),data=subset(SummaryInd,seedset>0))
+plot(PerPropagule~seedset,data=subset(SummaryInd,seedset>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+anova(mod)
+```
+
+- however, seedset and seed size are much less well correlated
+- so for this collection of species, shifts in accessory costs are closely linked to seed_set
+- seed set therefore clearly plays a role in the (small) shifts in RA with plant size
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(seedset)~log(seed_size),data=subset(SummaryInd,seedset>0))
+
+plot(seed_size~seedset,data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logxy(mod)
+```
+
+- there is no relationship between seed_count and Final Weight
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(FinalWeight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
+plot(seed_count~FinalWeight,data=subset(SummaryInd,seed_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+```
+
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(FinalWeight)~log(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
+plot(fruit_weight~FinalWeight,data=subset(SummaryInd,fruit_weight>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+```
+
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(ReproInv)~log(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
+plot(fruit_weight~ReproInv,data=subset(SummaryInd,fruit_weight>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+```
+
+- producing more seeds has a limited effect on RA  
+- it is proprtion of flowers/buds that become seeds (seed set) that matters
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(RA)~log(seed_count),data=subset(SummaryInd,seed_count>0))
+plot(seed_count~RA,data=subset(SummaryInd,seed_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+yvar <- "seed_count"
+xvar <- "RA"
+
+data <- subset(SummaryInd, seed_count>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+```
+
+- However, producing more reproductive units increases RA  - this is a within species effect mostly  
+```{r, echo=FALSE, message=FALSE}
+mod <- lm(log(RA)~log(repro_count),data=subset(SummaryInd,repro_count>0))
+plot(repro_count~RA,data=subset(SummaryInd,repro_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+yvar <- "repro_count"
+xvar <- "RA"
+
+data <- subset(SummaryInd, repro_count>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+```
+#getting counts out of Konrad's reproduction data - this code now also appears in "summary_dataframe.R", where it belongs in the end
+
 ```{r, echo=FALSE, message=FALSE}

### 2015-05-14 scripts/summary_dataframes.R

@@ -251,6 +251,174 @@ SummarySpp <- merge(SummarySpp, accessory_spp, by=c("species"))
 SummaryInd$species <- as.factor(SummaryInd$species)
 SummarySppAge$species <- as.factor(SummarySppAge$species)
 
+#getting counts out of Konrad's reproduction data
+tmp <- BAER_Investment
+FD <- as.data.frame(tmp$FD)
+BAER_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+BAER_count <- subset(BAER_count, count!=0)
+BAER_count$species <- "BAER"
+
+tmp <- BOLE_Investment
+FD <- as.data.frame(tmp$FD)
+BOLE_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+BOLE_count <- subset(BOLE_count, count!=0)
+BOLE_count$species <- "BOLE"
+
+tmp <- COER_Investment
+FD <- as.data.frame(tmp$FD)
+COER_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+COER_count <- subset(COER_count, count!=0)
+COER_count$species <- "COER"
+
+tmp <- EPMI_Investment
+FD <- as.data.frame(tmp$FD)
+EPMI_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+EPMI_count <- subset(EPMI_count, count!=0)
+EPMI_count$species <- "EPMI"
+
+tmp <- GRBU_Investment
+FD <- as.data.frame(tmp$FD)
+GRBU_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+GRBU_count <- subset(GRBU_count, count!=0)
+GRBU_count$species <- "GRBU"
+
+tmp <- GRSP_Investment
+FD <- as.data.frame(tmp$FD)
+GRSP_count <- FD %>%
+  group_by(Individual, what) %>%
+  summarise_each(funs(sum), count, weight)
+GRSP_count <- subset(GRSP_count, count!=0)
+GRSP_count$species <- "GRSP"
+
+tmp <- HATE_Investment
+FD <- as.data.frame(tmp$FD)
+HATE_count <- FD %>%
+  group_by(Individual, what) %>%
[…]

### 2015-05-19 results_accessory_shorter.rmd
file "results_accessory_shorter" includes a synthesis of most accessory costs thoughts

```{r, echo=FALSE,results='hide', message=FALSE}
library(remake)
create_bindings()

source("scripts/summary_dataframes.R")
source("scripts/functions.R")
```

#Accessory costs
##Basic questions
* Total reproductive investment can be divided into energy invested in propagules vs. other reproductive tissues (accessory costs)
* Reproductive investment can be considered on an energy or "count" (fecundity) basis

* A couple of questions:
    1. What should one measure?
    2. What does it mean as proportional energy shifts between accessory cost pools?

##Summary of outcomes
1. Total reproductive investment is by far the best correlate with total plant size (or growth investment)
2. Plants with smaller seeds, smaller adult sizes, and higher seedset have lower accessory costs. It is mathematically plausable that the concept of "accessory costs" is not all that different from "seed set"
  * In other words, plants with higher seed set, have lower accessory costs due to calculations
  * It is nice to have a data set that shows, across 14 species, that larger plants have lower seed set.
3. Bigger plants have higher RA. 
  * Plants that produce more buds, invest more absolute energy into either pre-pollination tissues or propagules also have higher RA.
  * As plants get bigger, there is a slight shift of energy from pre-pollination tissues to propagules, but this is a small effect 
  *(i.e. accessory costs decline slightly with increasing plant size)
4. Among reproducing individuals, bigger or older plants DO NOT have higher seedset, although more individuals become reproductively mature over time. 
  * Proportional pre-pollination costs also decrease with plant age in most species
5. Species differ enormously in their relative investment in different reproductive tissue types

##Still thinking about
1. Most analyses look at propagules and pre-pollination tissues, but allocation can be further divided - it would be interesting to look at proportion energy to aborted buds vs. flowers (I do know aborted buds decrease)
###Which measure of reproductive output best correlates with plant size or growth (growth plotted here)
* Measuring total reproductive output has a much stronger correlation than any of the other measures
* Note that each of these figures (and models) only includes individuals with non-zero reproductive investment

```{r, echo=FALSE,message=FALSE,,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(2,0.3,.5,0.3), mai=c(.5,1,.5,0.3))
mod <- lm (log(FinalWeight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
plot(ReproInv~FinalWeight,data=subset(SummaryInd,ReproInv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
words.bottom.right.logxy(mod)

mod <- lm (log(FinalWeight)~log(fruit_weight), data=subset(SummaryInd,fruit_weight>0))
plot(fruit_weight~FinalWeight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Fruit weight (mg)",xlim=c(100,2000000),xlab="")
words.bottom.right.logxy(mod)

mod <- lm (log(FinalWeight)~log(Prop), data=subset(SummaryInd,Prop>0))
plot(Prop~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(FinalWeight)~log(PerPropagule), data=subset(SummaryInd,PerPropagule>0))
plot(PerPropagule~FinalWeight,data=subset(SummaryInd,PerPropagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Proportion reproductive investment to propagules",xlim=c(100,2000000),xlab="Total size (mg)")
words.bottom.right.logxy(mod)
text((par("fin")[1]*.5),(par("fin")[2]*.2),"Total size (mg)")
```

###How do accessory costs shift with seed size?
- Larger-seeded species have higher accessory costs, as has been shown in other studies
- However, it is also true that "larger species" have higher accessory costs and than species with higher seed set have lower accessory costs
- In contrast, there is a relatively low correlation between accessory costs and proportion reproductive energy invested in pre-pollination tissues DESPITE this being the biggest pool of energy for most species
- Taken together these data (and various other plots, not shown) suggest that accessory costs (as a proportion) are most strongly driven by seedset
- In other words, if flowers are pollinated and develop into mature seeds, the plants ends up investing more energy in reproduction and that extra energy is being invested into propagules.
- Therefore, seed set goes up and by default, a greater proportion of energy goes into propagules and less into "accessory costs"

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))  
mod <- lm(log(seed_size)~asin(sqrt(PerAcc_mean)),SummarySpp)
plot(asin(sqrt(PerAcc_mean))~seed_size,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed size (mg)",cex=1.3)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logx(mod)

mod <- lm(log(FinalWeight_mean)~asin(sqrt(PerAcc_mean)),SummarySpp)
plot(asin(sqrt(PerAcc_mean))~FinalWeight_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
words.bottom.right.logx(mod)

mod <- lm(log(seedset_mean)~asin(sqrt(PerAcc_mean)),SummarySpp)
plot(asin(sqrt(PerAcc_mean))~seedset_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed set",cex=1.3)
words.top.right.logx(mod)

mod <- lm(asin(sqrt(seedset_mean))~asin(sqrt(PerPrePol_All_mean)),SummarySpp)
plot(asin(sqrt(PerAcc_mean))~PerPrePol_All_mean,SummarySpp, log="", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
words.top.right(mod)
```

* Here is the plot just of seed set by propagule investment (for all individuals), showing the effect is true within and across species
* This is the complement to the plot of accessory costs  
```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm(asin(sqrt(seedset))~log(PerPropagule),data=subset(SummaryInd,seedset>0&seedset<1))
plot(PerPropagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed set")
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

* Replotting the same data by age, shows that the pattern is not age-driven
* At most, there are most "old" plants with very low seedset  
```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm(asin(sqrt(seedset))~log(PerPropagule),data=subset(SummaryInd,seedset>0&seedset<1))
plot(PerPropagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="Accessory costs (asin transformed)",xlab="seed set")
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
```

###Relationship between tissue allocation and reproductive investment
* these data also tell the story of seedset being an important "component" and being lower in bigger species
* Proption pre-pollination costs completely unrelated to reproductive investment
* However, proportional investment in propagules decreases with increasing reproductive investment, because the bigger species investment more overall in reproduction and less in propagules
* There is also no pattern with respect to proportional investment in packaging and dispersal (R^2=0, p-value=0.959) and a slight decrease in aborted post-pollination tissues with increasing reproductive investment (R^2=0.0661, p-value=0.0002)
```{r, echo=FALSE,message=FALSE, ,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm(asin(sqrt(PerPrePol_All))~log((ReproInv)),data=subset(SummaryInd,PerPrePol_All>0&PerPrePol_All<1))
plot(asin(sqrt(PerPrePol_All))~ReproInv,data=subset(SummaryInd,PerPrePol_All>0&PerPrePol_All<1), log="x", pch=16,col=col.spp[as.factor(species)])
words.top.right.logx(mod)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(asin(sqrt(PerPropagule))~log((ReproInv)),data=subset(SummaryInd,PerPropagule>0))
plot(asin(sqrt(PerPropagule))~ReproInv,data=subset(SummaryInd,PerPropagule>0), log="x", pch=16,col=col.spp[as.factor(species)])
words.top.right.logx(mod)
```

###What happens against RA
* Overall RA is correlated with reproductive investment and age
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm(log(RA)~log((ReproInv)),data=subset(SummaryInd,RA>0))
plot(RA~(ReproInv),data=subset(SummaryInd,RA>0), pch=16,col=col.spp[as.factor(species)],log="xy")
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(log(RA)~log((age)),data=subset(SummaryInd,RA>0))
plot(RA~(age),data=subset(SummaryInd,RA>0), pch=16,col=col.spp[as.factor(species)],log="xy")
words.bottom.right.logxy(mod)
```

* RA is also correlated with count of floral units - the total number of buds produced (i.e. final development stage can be buds, flowers, aborted fruit or fruit)
* This is true for many individual species as well as across species
```{r, echo=FALSE,message=FALSE}
mod <- lm(log(RA)~log(repro_count),data=subset(SummaryInd,repro_count>0))
plot(repro_count~RA,data=subset(SummaryInd,repro_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

yvar <- "repro_count"
xvar <- "RA"

data <- subset(SummaryInd, repro_count>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results
```

* This same pattern is true just looking  at pre-pollination tissues and at propagule allocation
* Plants that invest more in some reproductive tissues, on average, invest more in other reproductive tissues, so have a higher RA
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm(log(RA)~log((PrePol_All)),data=subset(SummaryInd,RA>0&PrePol_All>0))
plot(PrePol_All~(RA),data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination tissues (mg)")
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
mod <- lm(log(RA)~log((Prop)),data=subset(SummaryInd,RA>0&Prop>0))
plot(Prop~(RA),data=subset(SummaryInd,RA>0&Prop>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
```

* Looking at proportions, the pattern is much less informative
* Plants with higher RA have lower allocation to pre-pollination tissues, probably because of their higher seedset
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,RA>0&PerPrePol_All>0))
plot(asin(sqrt(PerPrePol_All))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&PerPrePol_All>0), pch=16,col=col.spp[as.factor(species)])
words.top.right(mod)

mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule)),data=subset(SummaryInd,RA>0))
plot(asin(sqrt(PerPropagule))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&PerPropagule>0), pch=16,col=col.spp[as.factor(species)])
words.top.right(mod)
```

###Shifts across age
* Seedset shows a slight decrease with proportional plant height (the best proxy for "relative size"), but certainly no trend of increased seed set in older plants. 
* there is a similar pattern for Propagule investment (not shown)  
* a greater number of individuals become reproductively mature, but among reproducing individuals there is no shift in seedset or proportional propagule investment with age
* same pattern using "age" as xvar

*Results, by species, for seedset by proportional height
```{r, echo=FALSE,message=FALSE}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
mod <- lm(asin(sqrt(PropH))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset<1&seedset>0))
plot(asin(sqrt(seedset))~PropH,data=subset(SummaryInd,seedset<1&seedset>0), pch=16,col=col.spp[as.factor(species)])
words.top.right(mod)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "seedset"
xvar <- "PropH"

data <- subset(SummaryInd, seedset>0&seedset<1)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results
```

*Results, by species, for seedset by age
```{r, echo=FALSE,message=FALSE}
yvar <- "seedset"
xvar <- "age"

data <- subset(SummaryInd, seedset>0&seedset<1)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results
```

* A number of species show declines in accessory costs with age, but this effect disappears once you include only individuals that set *any* seed
```{r, echo=FALSE,message=FALSE}
yvar <- "PerAcc"
xvar <- "age"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results
```

* 8 of the 14 species show declines in allocation to pre-pollination tissues with increasing age
```{r, echo=FALSE,message=FALSE}
yvar <- "PerPrePol_All"
xvar <- "age"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results
```

##Shifts in proportion to tissue types across species  
- Reasonably idiosyncratic patterns
- Propagule allocation across species  
- COER, EPMI, LEES, PILI invest the most energy in propagules  
- HATE invests by far the least into propagules  
```{r, echo=FALSE, message=FALSE}
mean1 <- SummarySpp$PerPropagule_mean
se1 <- SummarySpp$PerPropagule_se
plot(mean1~species,SummarySpp,cex.axis=.7,pch=16,log="y",ylim=c(.002,.25),main="Percent reproductive investment put into propagules")
se_function(mean1,se1)
```

- pre-pollination allocation across species  
```{r, echo=FALSE, message=FALSE}
mean1 <- SummarySpp$PerPrePol_All_mean
se1 <- SummarySpp$PerPrePol_All_se
plot(mean1~species,data=subset(SummarySpp),cex.axis=.8,pch=16,ylim=c(.1,1),main="Percent reproductive investment put into pre-pollination tissues")
se_function(mean1,se1)
```

- just looking among plants >3 years old  
```{r, echo=FALSE, message=FALSE}
tmp <- SummaryInd %>%
  filter(Total!=0&age>3) %>%
  group_by(species) %>%
  summarise_each(funs(mean, se), PerPrePol_All)

plot(mean~species,
    tmp,
     cex.axis=.7,pch=16,log="y",ylim=c(.1,1),
     main="Percent reproductive investment put into pre-pollination tissues")

mean1 <- tmp$mean
se1 <- tmp$se
se_function(mean1,se1)
```

- Packaging and dispersal allocation across species  
```{r, echo=FALSE, message=FALSE}
mean1 <- SummarySpp$PerPackDisp_mean
se1 <- SummarySpp$PerPackDisp_se

plot(mean1~species,SummarySpp,cex.axis=.8,pch=16,log="y",ylim=c(.02,1),main="Percent reproductive investment put into packaging and dispersal")
se_function(mean1,se1)
```

- just looking among plants >3 years old  
```{r, echo=FALSE, message=FALSE}
tmp2 <- SummaryInd %>%
  filter(Total!=0&age>3) %>%
  group_by(species) %>%
  summarise_each(funs(mean, se), PerPackDisp)

plot(mean~species,
    tmp2,
     cex.axis=.7,pch=16,log="y",ylim=c(0.02,.8),
     main="Percent reproductive investment put into packaging & dispersal tissues")

mean1 <- tmp2$mean
se1 <- tmp2$se

se_function(mean1,se1)
```

### 2015-05-19 results_best.Rmd
file "results_accessory_shorter" includes a synthesis of most accessory costs thoughts

@@
 source("scripts/summary_dataframes.R")
-
 plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
@@
   X <- data[[xvar]]
+  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
+}
+
+plot_yvar2_vs_xvar2 <- function(data, yvar2 = "y", xvar2 = "x", ...) {
+  Y <- data[[yvar2]]
+  X <- data[[xvar2]]
   plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
@@
 }
+
+words.bottom.right.logx <- function (x) {
+  output <- data.frame(select(glance(x), r.squared, p.value))
+  output <- round(output,4)
+  text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
+  text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
+  text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
+}
 ```
@@
 - However, it is important to note that species early in their reproductive trajectory do not follow this pattern
-```{r, echo=FALSE,message=FALSE}
-plot((ReproInv)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
+
+```{r, echo=FALSE,message=FALSE, fig.width=12, fig.height=6, out.width=792, out.height=576}
+yvar <- "RA"
+xvar <- "PropH"
+
+yvar2 <- "RA"
+xvar2 <- "FinalWeight"
+
+data <- SummaryInd
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.2,1,.5,0.2))  
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
+                    main=spp, xlab=xvar, ylab=yvar)
+  plot_yvar2_vs_xvar2(data[[spp]], yvar2, xvar2, 
+                    main=spp, log="x", xlab=xvar2, ylab="")
+
+}
+
+plot.new()
+```
+
+```{r, echo=FALSE,message=FALSE, fig.width=12, fig.height=6, out.width=792, out.height=576}
+yvar <- "ReproInv"
+xvar <- "PropH"
+
+yvar2 <- "ReproInv"
+xvar2 <- "FinalWeight"
+
+data <- SummaryInd
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.2,1,.5,0.2))  
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
+                    main=spp, ,log="y", xlab=xvar, ylab=yvar)
+  plot_yvar2_vs_xvar2(data[[spp]], yvar2, xvar2, 
+                    main=spp, log="xy", xlab=xvar2, ylab="")
+
+}
+
+par(mfrow=c(1,1), pin=c(5,7),mar=c(5,4,4,2)+.1,omi=c(.1,.1,.1,.1))
+```
+
+```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7, out.width=792, out.height=576}
+plot((ReproInv)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1),xlab=xvar)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```
 
+* Reproductive investment vs. PropH
+```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7, out.width=792, out.height=576}
 yvar <- "ReproInv"
@@
 results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, log="y", xlab=xvar, ylab=yvar)
-}
 ```
@@
 results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
-                    main=spp, xlab=xvar, ylab=yvar)
-}
 ```
@@
    - There is also an increase in propagule investment with age
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7, out.width=792, out.height=576}
 mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+age,data=subset(SummaryInd,PerPropagule>0))
@@
 ```
-#getting counts out of Konrad's reproduction data - this code now also appears in "summary_dataframe.R", where it belongs in the end
-
-```{r, echo=FALSE, message=FALSE}
-tmp <- BAER_Investment
-FD <- as.data.frame(tmp$FD)
-BAER_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-BAER_count <- subset(BAER_count, count!=0)
-BAER_count$species <- "BAER"
-
-tmp <- BOLE_Investment
-FD <- as.data.frame(tmp$FD)
-BOLE_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-BOLE_count <- subset(BOLE_count, count!=0)
-BOLE_count$species <- "BOLE"
-
-tmp <- COER_Investment
-FD <- as.data.frame(tmp$FD)
-COER_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-COER_count <- subset(COER_count, count!=0)
-COER_count$species <- "COER"
-
-tmp <- EPMI_Investment
-FD <- as.data.frame(tmp$FD)
-EPMI_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-EPMI_count <- subset(EPMI_count, count!=0)
-EPMI_count$species <- "EPMI"
-
-tmp <- GRBU_Investment
-FD <- as.data.frame(tmp$FD)
-GRBU_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-GRBU_count <- subset(GRBU_count, count!=0)
-GRBU_count$species <- "GRBU"
-
-tmp <- GRSP_Investment
-FD <- as.data.frame(tmp$FD)
-GRSP_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-GRSP_count <- subset(GRSP_count, count!=0)
-GRSP_count$species <- "GRSP"
-
-tmp <- HATE_Investment
-FD <- as.data.frame(tmp$FD)
-HATE_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-HATE_count <- subset(HATE_count, count!=0)
-HATE_count$species <- "HATE"
-
-tmp <- HEPU_Investment
-FD <- as.data.frame(tmp$FD)
-HEPU_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-HEPU_count <- subset(HEPU_count, count!=0)
-HEPU_count$species <- "HEPU"
-
-tmp <- LEES_Investment
-FD <- as.data.frame(tmp$FD)
-LEES_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-LEES_count <- subset(LEES_count, count!=0)
-LEES_count$species <- "LEES"
-
-tmp <- PELA_Investment
-FD <- as.data.frame(tmp$FD)
-PELA_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-PELA_count <- subset(PELA_count, count!=0)
-PELA_count$species <- "PELA"
-
-tmp <- PEPU_Investment
-FD <- as.data.frame(tmp$FD)
-PEPU_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-PEPU_count <- subset(PEPU_count, count!=0)
-PEPU_count$species <- "PEPU"
-
-tmp <- PHPH_Investment
-FD <- as.data.frame(tmp$FD)
-PHPH_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-PHPH_count <- subset(PHPH_count, count!=0)
-PHPH_count$species <- "PHPH"
-
-tmp <- PILI_Investment
-FD <- as.data.frame(tmp$FD)
-PILI_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-PILI_count <- subset(PILI_count, count!=0)
-PILI_count$species <- "PILI"
-
-tmp <- PUTU_Investment
-FD <- as.data.frame(tmp$FD)
-PUTU_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-PUTU_count <- subset(PUTU_count, count!=0)
-PUTU_count$species <- "PUTU"
-
-accessory_count <- rbind(BAER_count,BOLE_count,COER_count,EPMI_count,GRBU_count,GRSP_count,HATE_count,HEPU_count,LEES_count,PELA_count,PEPU_count,PHPH_count,PILI_count,PUTU_count)
-```
-
-TO DO
-- seed set with age - this is probably what explains a lot of changes in proportional tissue alotment. 
--Big question is if seed set changes with plant size or age

### 2015-05-19 scripts/functions.R

@@ -1,0 +1,98 @@
+plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
+  Y <- data[[yvar]]
+  X <- data[[xvar]]
+  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
+}
+
+plot_yvar2_vs_xvar2 <- function(data, yvar2 = "y", xvar2 = "x", ...) {
+  Y <- data[[yvar2]]
+  X <- data[[xvar2]]
+  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
+}
+
+summarise_fit <- function(x) {
+  data.frame(
+    select(glance(x), r.squared, p.value),
+    n= length(resid(x)),
+    a = coef(x)[1],
+    b = coef(x)[2]
+  )
+}
+
+summarise_all_fits <- function(x) {
+  tmp <- lapply(x, summarise_fit) %>%
+    bind_rows
+  data.frame(species=names(x), tmp)
+}
+
+summarise_fit_2var <- function(x) {
+  data.frame(
+    select(glance(x), r.squared, p.value),
+    n= length(resid(x)),
+    intercept = coef(x)[1],
+    coef_var1 = coef(x)[2],
+    coef_var2 = coef(x)[3],
+    coef_var1var2 = coef(x)[4],
+    SS_var1 = anova(x)[1,2],
+    SS_var2 = anova(x)[2,2],
+    SS_var1var2 =anova(x)[3,2]
+  )
+}
+
+summarise_all_fits_2var <- function(x) {
+  tmp <- lapply(x, summarise_fit_2var) %>%
+    bind_rows
+  data.frame(species=names(x), tmp)
+}
+
+xy.error.bars <- function (x,y,xbar,ybar) {
+  plot(x,y,pch=16, ylim=c(min(y-ybar),max(y+ybar)),xlim=c(min(x-xbar),max(x+xbar)))
+  arrows(x,y-ybar,x,y+ybar,code=3,angle=90, length=0.1)
+  arrows(x-xbar,y,x+xbar,y,code=3,angle=90, length=0.1)
+}
+
+se_function <- function(mean1,se1) {
+  for(i in 1:14) {
+    arrows(i,mean1[i]+se1[i],i,mean1[i]-se1[i],code=3,angle=90, length=0.1)
+  }
+}
+
+words.top.right.logxy <- function (x) {
[…]

### 2015-05-19 scripts/summary_dataframes.R

@@ -205,6 +205,11 @@ LMA_spp <- LMA %>%
   summarise_each(funs(mean, se, length), LMA)
 names(LMA_spp)<-c("species", "LMA_mean","LMA_se","LMA_length")
 
+#investment summary by species
+investment_spp <- investment %>%
+    group_by(species) %>%
+  summarise_each(funs(mean, se, length), FinalWeight,ReproInv)
+
 #maximum height for each species
 maxH_spp <- harvest %>%
   group_by(species) %>%
@@ -247,6 +252,7 @@ SummarySpp <- merge(SummarySpp, wood_summary, by=c("species"))
 SummarySpp <- merge(SummarySpp, seedsize, by=c("species"))
 SummarySpp <- merge(SummarySpp, maxH_spp, by=c("species"))
 SummarySpp <- merge(SummarySpp, accessory_spp, by=c("species"))
+SummarySpp <- merge(SummarySpp, investment_spp, by=c("species"))
 
 SummaryInd$species <- as.factor(SummaryInd$species)
 SummarySppAge$species <- as.factor(SummarySppAge$species)
@@ -399,6 +405,7 @@ count_fruit_mature <- subset(accessory_count, what=="fruit_mature",select=c("Ind
 names(count_fruit_mature) <- c("individual","fruit_weight")
 count_fruit_mature$individual <- as.factor(count_fruit_mature$individual)
 
+
 SummaryInd <- merge(SummaryInd, count_flower, by="individual",all.x=TRUE)
 SummaryInd <- merge(SummaryInd, count_bud, by="individual",all.x=TRUE)
 SummaryInd <- merge(SummaryInd, count_fruit_aborted, by="individual",all.x=TRUE)
@@ -411,13 +418,23 @@ for(v in c("flower_count","bud_count","seed_count","aborted_fruit_count","seedpo
   SummaryInd[[v]][i] <- 0
 }
 
-SummaryInd$seedset <- SummaryInd$seed_count/(SummaryInd$bud_count+SummaryInd$flower_count+SummaryInd$seed_count)
-#not quite perfect, because I don't yet have counts of aborted parts in this (+SummaryInd$aborted_fruit_count) because lots of negative counts
[…]

### 2015-05-19 results_RAschedules_shorter.Rmd
created separate "RA_schedules_shorter" results file.

--- 2015-05-12 results_best.Rmd
@@
 source("scripts/summary_dataframes.R")
-
-plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
-  Y <- data[[yvar]]
-  X <- data[[xvar]]
-  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
-}
-
-summarise_fit <- function(x) {
-  data.frame(
-    select(glance(x), r.squared, p.value),
-    n= length(resid(x)),
-    a = coef(x)[1],
-    b = coef(x)[2]
-  )
-}
-
-summarise_all_fits <- function(x) {
-  tmp <- lapply(x, summarise_fit) %>%
-    bind_rows
-  data.frame(species=names(x), tmp)
-}
-
-summarise_fit_2var <- function(x) {
-  data.frame(
-    select(glance(x), r.squared, p.value),
-    n= length(resid(x)),
-    intercept = coef(x)[1],
-    coef_var1 = coef(x)[2],
-    coef_var2 = coef(x)[3],
-    coef_var1var2 = coef(x)[4],
-    SS_var1 = anova(x)[1,2],
-    SS_var2 = anova(x)[2,2],
-    SS_var1var2 =anova(x)[3,2]
-      )
-}
-
-summarise_all_fits_2var <- function(x) {
-  tmp <- lapply(x, summarise_fit_2var) %>%
-    bind_rows
-  data.frame(species=names(x), tmp)
-}
-
-xy.error.bars <- function (x,y,xbar,ybar) {
-  plot(x,y,pch=16, ylim=c(min(y-ybar),max(y+ybar)),xlim=c(min(x-xbar),max(x+xbar)))
-  arrows(x,y-ybar,x,y+ybar,code=3,angle=90, length=0.1)
-  arrows(x-xbar,y,x+xbar,y,code=3,angle=90, length=0.1)
-}
-
-se_function <- function(mean1,se1) {
-for(i in 1:14) {
-arrows(i,mean1[i]+se1[i],i,mean1[i]-se1[i],code=3,angle=90, length=0.1)
-}
-}
-
-words.top.right.logxy <- function (x) {
-output <- data.frame(select(glance(x), r.squared, p.value))
-output <- round(output,4)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
-}
-
-words.top.right.logx <- function (x) {
-output <- data.frame(select(glance(x), r.squared, p.value))
-output <- round(output,4)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
-}
-
-words.top.right <- function (x) {
-output <- data.frame(select(glance(x), r.squared, p.value))
-output <- round(output,4)
-text(((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.95*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
-text(((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.9*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
-}
-
-words.bottom.right.logxy <- function (x) {
-output <- data.frame(select(glance(x), r.squared, p.value))
-output <- round(output,4)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.1*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.05*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0)
-}
+source("scripts/functions.R")
 ```
-
-#Changes in growth and tissue allocation with age and size
-* Part of this paper would be to look at how different "types of" species fall out with respect to the various plots - i.e.
-canopy species (BAER, HATE, PELA), short-lived species (BOLE, PILI, COER), longer-lived understory species
-
-###More ways to ask how much - and when - reproduction impacts growth  
-- It is clear that different species reach a different "proportion maxH" (RSOM) before reproducing. Need to do curve fitting to determine where this occurs.  
-- The plot of Growth Investment vs. PropH shows a decrease in growth rate at a given PropH (for most species). Is this the same PropH at which reproduction begins?  
-- It seems that some of the early reproducers begin reproducing at a larger PropH, as predicted by others.
-But because they allocate so much to reproduction, their growth rate declines more precipitously with the onset of reproduction.
 
@@
 - However, it is important to note that species early in their reproductive trajectory do not follow this pattern
-```{r, echo=FALSE,message=FALSE}
+
+###Plots of size against reproductive investment
+* Plots of total reproductive investment against size or height are both highly significant
+```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
+mod <- lm(log(FinalWeight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
+plot(ReproInv~FinalWeight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(height)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
+plot(ReproInv~height, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+mod <- lm((PropH)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
 plot((ReproInv)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```
 
-plot(ReproInv~FinalWeight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
+###Plots of size against RA
+* RA not significantly correlated with total height or weight, but of course across and within species effects opposite - bigger individuals of a species have higher RA, but species that are overall bigger have lower RA
+* Therefore, there is a negative correlation between PropH (proportion of a species' maximum height) and RA; highly significant, but very low R^2
+
+```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
+mod <- lm(log(FinalWeight)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
+plot(asin(sqrt(RA))~FinalWeight, SummaryInd, log="x",col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logx(mod)
 
-plot(ReproInv~height, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(height)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
+plot(asin(sqrt(RA))~height, SummaryInd, log="x",col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logx(mod)
 
+mod <- lm((PropH)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
+plot((asin(sqrt(RA)))~(PropH), SummaryInd,col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right(mod)
+```
+
+##RA schedules (vs. age and height)  
+- RA schedules still look "best" plotted against age  
+- RA schedules plotted against height are particularly good for a number of species such as EPMI, COER, PELA  
+  1. they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing propH  
+  2. when all data points are included, all species except PEPU, PHPH, and PULU show increasing RA with increasing height  
+  3. when RA =0 is excluded, the following species still have a significant positive correlation: BOLE, COER, EPMI, GRBU, GRSP, HATE. LEES and PELA have a p-value between 0.05-0.10   
+  4. PEPU has the lowest slope - matches Mark's suggestion that it is "hanging on"  
+- There are species - such as BOLE - which have a much "cleaner" plot against age instead of height (or any other size measure).
+This indicates that these species are programmed to reproduce at a certain "rate" regardless of their size
+
+NOTE: Again, a linear line is not necessarily the most appropriate
+
+```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7}
+yvar <- "RA"
+xvar <- "age"
+
+yvar2 <- "RA"
+xvar2 <- "height"
+
+data <- SummaryInd
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.2,1,.5,0.2))  
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
+                    main=spp, xlab=xvar, ylab=yvar)
+  plot_yvar2_vs_xvar2(data[[spp]], yvar2, xvar2, 
+                      main=spp, log="x", xlab=xvar2, ylab="")
+
+}  
+```
+
+* RA vs. height by species  
+```{r, echo=FALSE, message=FALSE}
+yvar <- "RA"
+xvar <- "height"
+
+data <- subset(SummaryInd,RA>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+```
+
+* RA vs. age by species  
+```{r, echo=FALSE, message=FALSE}
+yvar <- "RA"
+xvar <- "age"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+```
+
+###RV curves, by age, weight and height
+```{r, echo=FALSE,message=FALSE, fig.width=21, fig.height=7}
 yvar <- "ReproInv"
-xvar <- "PropH"
+xvar <- "age"
+
+yvar2 <- "ReproInv"
+xvar2 <- "FinalWeight"
+
+yvar3 <- "ReproInv"
+xvar3 <- "height"
+
+data <- SummaryInd
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  par(mfrow=c(1,3), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.2,1,.5,0.2))  
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
+                    main=spp, ,log="xy", xlab=xvar, ylab=yvar)
+  plot_yvar2_vs_xvar2(data[[spp]], yvar2, xvar2, 
+                      main=spp, log="xy", xlab=xvar2, ylab="")
+  plot_yvar3_vs_xvar3(data[[spp]], yvar3, xvar3, 
+                      main=spp, log="xy", xlab=xvar3, ylab="")
+}  
+```
+
+* Reproductive investment vs. height for each species
+```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
+yvar <- "ReproInv"
+xvar <- "height"
+
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  log(x[[xvar]]+1)))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+```
+
+* Reproductive investment vs. weight for each species
+```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
+yvar <- "ReproInv"
+xvar <- "FinalWeight"
 
@@
 results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
-                    main=spp, log="y", xlab=xvar, ylab=yvar)
-}
-```
-
-##RA schedules (vs. propH)  
-- RA schedules still look "best" plotted against age; not shown here  
-- these curves are particularly good for a number of species such as EPMI, COER, PELA  
-- they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing propH  
-- when all data points are included, all species except PEPU, PHPH, and PULU show increasing RA with increasing height  
-- when RA =0 is excluded, the following species still have a significant positive correlation: BOLE, COER, EPMI, GRBU, GRSP, HATE. LEES and PELA have a p-value between 0.05-0.10   
-- PEPU has a negative correlation - matches Mark's suggestion that it is "hanging on"  
-- There are species - such as BOLE - which have a much "cleaner" plot against age instead of PropH (or any other size measure).
-This indicates that these species are programmed to reproduce at a certain "rate" regardless of their size
-
- NOTE: Again, a linear line is not necessarily the most appropriate
-
-```{r, echo=FALSE, message=FALSE}
-plot((RA~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-plot(RA~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
-
-yvar <- "RA"
-xvar <- "PropH"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
-                    main=spp, xlab=xvar, ylab=yvar)
-}
 ```
@@
 ```{r, echo=FALSE,message=FALSE}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
+mod <- lm(log(GrowthInv)~log(ReproInv),data=subset(SummaryInd,ReproInv>0))
 plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
 ```
@@
 ```{r, echo=FALSE,message=FALSE}
-plot(RA~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
+mod <- lm(RGR~asin(sqrt(RA))*species,data=subset(SummaryInd,RA>0))
+plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-mod <- lm(RGR~asin(sqrt(RA))*species,SummaryInd)
-anova(mod)
+words.top.right.logxy(mod)
 ```
@@
 the change in slope of the relationship.
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE, message=FALSE, out.width=900, out.height=576}
 yvar <- "GrowthInv"
@@
 ```
-
-#Shifts in accessory costs across species and ages
-##Overall results
-- Accessory costs higher for bigger seeds
-
-- Accessory costs higher for bigger species; these are the same species that invest less in RA
-
-- Of course there is also a correlation between seed size and plant size, but actually not as strong as the accessory cost one, presumably because older plants have lower accessory costs as well as species that are inherently bigger
-
-- A number of species show fairly consistent declines in accessory costs with various measures of "bigger", including size, age, RA. Other species show no patterns  
-- Lower pre-pollination costs in plants with higher RA: 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases.
-in other words, they get better returns on investment the more they invest.
-(This is just a pattern within, not across, species)
-- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e.
-Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers
-- Haven't actually run all the tests, but assume all reproductive tissue types will differ in proportional allocation across species
-- For most of the statistical analyses, the youngest site has been removed, since it included individuals that were harvested while flowering (and therefore never "got to" set fruit) and automatically have no "successful" reproduction.
-There are of course some individuals like this at other ages as well, but far fewer
-
-##Basic questions
-###How do accessory costs shift with seed size?
-- Larger-seeded species have higher accessory costs. 
-- Also shown in other studies and suggested as a mechanism for why angiosperms were able to have such small seeds (relative to gymnosperms, with no decrease in proportional accessory costs - with decreasing size)
--  As shown below, bigger species also have higher accessory costs (and also bigger seeds - cause vs. effect unknown)
-```{r, echo=FALSE,message=FALSE}
-mod <- lm(log(seed_size)~asin(sqrt(PerAcc_mean)),SummarySpp)
-plot(PerAcc_mean~seed_size,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)])
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-```
-
-###Why measure "Total Reproductive Investment" instead of "seed weight" or "fruit weight"?  
-- The R^2 for the plot of total reproductive investment against total plant size is much stronger than plotting seed weight against total plant size (R^2 = 0.61 vs 0.33)  
-- Adding propagule + packaging & dispersal (i.e. successful reproduction costs), improves the fit somewhat (R^2 =0.55)  
-- Total pre-pollination costs are also well-correlated with plant size, indicating bigger plants have more flowers
-- NEXT: Once I have all parts weights, plot against fruit weight
-
-```{r, echo=FALSE,message=FALSE}
-mod <- lm (log(FinalWeight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot(ReproInv~FinalWeight,data=subset(SummaryInd,ReproInv>0), log="xy",col=col.spp[as.factor(species)], pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-
-mod <- lm (log(FinalWeight)~log(Prop), data=subset(SummaryInd,Prop>0))
-plot(Prop~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-
-mod <- lm (log(FinalWeight)~log(Prop+PD), data=subset(SummaryInd,Prop>0))
-plot((Prop+PD)~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-
-mod <- lm (log(FinalWeight)~log(PrePol_All), data=subset(SummaryInd,PrePol_All>0))
-plot((PrePol_All)~FinalWeight,data=subset(SummaryInd,PrePol_All>0), log="xy",col=col.spp[as.factor(species)], pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-```
-
-###Looking at counts
-- Final weight vs. #flowers+buds
-- Final weight vs. #fruit
-
-##Across species patterns of note
-###Size versus proportional propagule investment
-- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
-   1.  This is another way of showing that larger species get less of a return on their investment in reproduction. They have higher accessory costs. 
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+species,data=subset(SummaryInd,PerPropagule>0))
-anova(mod)
-plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logxy(mod)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes species effect",adj=0) 
-```
-
-- Species that are bigger also invest a lower proportion of their TOTAL surplus energy in propagules (proportion propagules*RA) 
-  + This is noisier than looking simply at proportion reproductive allocation to propagules, because of the RA effects - see below
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ (log(PropAllocation))*species*age,data=subset(SummaryInd,PerPropagule>0))
-plot(PropAllocation ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logxy(mod)
-text(1000,.6e-4,"includes species effect",adj=0)
-anova(mod)
-```
-
-- Looking at RA with plant size is not very informative, because:
-  1. RA increases with plant size within a species  
-  2. decreases with plant size across species  
-  3. in combination they are noisy
-- The first plot is all points  
-- The second plot is just 7-year olds, showing the decrease in RA with plant size  
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ (log(RA)),data=subset(SummaryInd,RA>0))
-plot(RA ~FinalWeight, data=subset(SummaryInd,RA>0),log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-anova(mod)
-
-mod <- lm(log(FinalWeight) ~ (log(RA)),data=subset(SummaryInd,RA>5e-3&age==7))
-plot(RA ~FinalWeight, data=subset(SummaryInd,RA>5e-3&age==7),log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logxy(mod)
-```
-
-- A model including the effect of both PerPropagule and RA on FinalWeight confirms this - there is a strong species effect and strong PerPropagule effect, but RA is much less significant  
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ (log(RA))*log(PerPropagule)*species,data=subset(SummaryInd,PerPropagule>0))
-anova(mod)
-```
-
-- Proportional investment in all pre-pollination tissues is uncorrelated with plant size (at most ages)  
-  +  if age included in model, becomes highly significant  
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0&age>3))
-plot(asin(sqrt(PerPrePol_All)) ~ FinalWeight, data=subset(SummaryInd,PerPrePol_All>0),log="x", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logx(mod)
-```
-
-- Shifts in packaging and dispersal costs with plant weight
-- Species very different from one another, but no shift with size 
-- Also no pattern w/r RA (not shown)
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPackDisp)),data=subset(SummaryInd,PerPackDisp>0))
-plot(asin(sqrt(PerPackDisp)) ~FinalWeight, data=subset(SummaryInd,PerPackDisp>0),log="x", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logx(mod)
-```
-
-###Across species summary
-- greater plant weight = lower RA  (spending more on growth and survival)**  
-- greater plant weight = lower proportion to propagules  (bigger species get less for their allocation)**  
-- plant weight = little effect on pre-pollination tissues
-
-##Within species (across age, size, or RA) patterns to note
-- Only COER and HATE increase allocation to propagules with increased plant size  
-- This, together with other plots, indicates that only the plants (of a species) that have higher RA, have higher propagule investment; but not all bigger individuals have higher RA
-NOTE: Plot nearly same as above, except y-axis arcsine transformed, not log transformed and R^2 values without species term
-```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPropagule"
-xvar <- "FinalWeight"
-
-data <- subset(SummaryInd, Total>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
-
-mod <- lm(log(FinalWeight)~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
-plot(asin(sqrt(PerPropagule))~log(FinalWeight), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right(mod)
-```
-
-- Allocation to propagules increases with RA in all species except EPMI, PHPH, PILI, PUTU  
-- again, probably a figment of overall increased allocation (higher RA) if propagules form  
-```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPropagule"
-xvar <- "RA"
-
-data <- subset(SummaryInd, Total>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
-plot(asin(sqrt(PerPropagule))~asin(sqrt(RA)), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right(mod)
-```
-
-###Change in proportional allocation to pre-pollination tissues with plant weight 
-- only a few species show a significant correlation -> as plants grow, they don't shift this allocation  
-```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_All"
-xvar <- "FinalWeight"
-
-data <- subset(SummaryInd, Total>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-###Change in proportional allocation to pre-pollination tissues with RA
-- 9 species decrease allocation to pre-pollination tissues with increased RA  
-- this could simply be because when/if flowers are pollinated, there is increased reproductive investment, increasing RA and decreasing pre-pollination allocation  
-- Interesting that RA increases with plant size, and pre-pollination decreases with RA, but very low correlation between pre- pollination allocation and plant size  
-```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_All"
-xvar <- "RA"
-
-data <- subset(SummaryInd, Total>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0))
-plot(asin(sqrt(PerPrePol_All))~asin(sqrt(RA)), data=subset(SummaryInd,PerPrePol_All>0),col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right(mod)
-```
-
-- Quite a few species (BAER, BOLE, COER, GRBU, GRSP, HATE, HEPU, PEPU, PHPH increase the percent reproductive investment spent on packaging and dispersal with age 
-- This probably reflects increased seed set with age and the simulatenous increase in this pool
-```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPackDisp"
-xvar <- "RA"
-
-data <- subset(SummaryInd, Total>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-###Within species summary
-- greater plant weight = higher RA  (plants allocate more to reproduction when bigger/older)**
-- plant weight = little effect on proportion to propagules  
-- plant weight = little effect on pre-pollination tissues  
-- higher RA = lower allocation to pre-pollination tissues (probably because more seed set)
-- higher RA = greater allocation to propagules (probably because more seed set)
-
-##Shifts in proportion to tissue types across species  
-- Propagule allocation across species  
-- COER, EPMI, LEES, PILI invest the most energy in propagules  
-- HATE invests by far the least into propagules  
-```{r, echo=FALSE, message=FALSE}
-#mod <- lm(asin(sqrt(PerPropagule)) ~ species-1, data=subset((SummaryInd,Total>0))
-#tmp <- summary(mod)
-#tmp <- tmp$coefficients
-#tmp <-as.data.frame(tmp)
-#tmp <- cbind(names(labels.spp),tmp)
-#names(tmp) <- c("species","estimate.trans","se.trans","t.value","p.value")
-mean1 <- SummarySpp$PerPropagule_mean
-se1 <- SummarySpp$PerPropagule_se
-plot(mean1~species,SummarySpp,cex.axis=.7,pch=16,log="y",ylim=c(.002,.25),main="Percent reproductive investment put into propagules")
-se_function(mean1,se1)
-```
-
-- pre-pollination allocation across species
-
-```{r, echo=FALSE, message=FALSE}
-mean1 <- SummarySpp$PerPrePol_All_mean
-se1 <- SummarySpp$PerPrePol_All_se
-plot(mean1~species,data=subset(SummarySpp),cex.axis=.8,pch=16,ylim=c(.1,1),main="Percent reproductive investment put into pre-pollination tissues")
-se_function(mean1,se1)
-```
-
-- just looking among plants >3 years old
-
-```{r, echo=FALSE, message=FALSE}
-tmp <- SummaryInd %>%
-  filter(Total!=0&age>3) %>%
-  group_by(species) %>%
-  summarise_each(funs(mean, se), PerPrePol_All)
-
-plot(mean~species,
-    tmp,
-     cex.axis=.7,pch=16,log="y",ylim=c(.1,1),
-     main="Percent reproductive investment put into pre-pollination tissues")
-
-mean1 <- tmp$mean
-se1 <- tmp$se
-se_function(mean1,se1)
-```
-
-- Packaging and dispersal allocation across species
-
-```{r, echo=FALSE, message=FALSE}
-mean1 <- SummarySpp$PerPackDisp_mean
-se1 <- SummarySpp$PerPackDisp_se
-
-plot(mean1~species,SummarySpp,cex.axis=.8,pch=16,log="y",ylim=c(.02,1),main="Percent reproductive investment put into packaging and dispersal")
-se_function(mean1,se1)
-```
-
-- just looking among plants >3 years old
-
-```{r, echo=FALSE, message=FALSE}
-tmp2 <- SummaryInd %>%
-  filter(Total!=0&age>3) %>%
-  group_by(species) %>%
-  summarise_each(funs(mean, se), PerPackDisp)
-
-plot(mean~species,
-    tmp2,
-     cex.axis=.7,pch=16,log="y",ylim=c(0.02,.8),
-     main="Percent reproductive investment put into packaging & dispersal tissues")
-
-mean1 <- tmp2$mean
-se1 <- tmp2$se
-
-se_function(mean1,se1)
-```
-
-###Across species summary
-- nothing much shifts with plant size
-- most pool shift with RA, but that is likely because higher RA often means increased seed set - higher RA occurs because some flowers pollinated and mature, which shifts proportional allocation to post-pollination pools
-- has interesting implications for what RA means if it is closely linked to increased seed set (or aborted fruit production)
-
-#getting counts out of Konrad's reproduction data
-```{r, echo=FALSE, message=FALSE}
-tmp <- BAER_Investment
-FD <- as.data.frame(tmp$FD)
-BAER_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-BAER_count <- subset(BAER_count, count!=0)
-BAER_count$species <- "BAER"
-
-tmp <- BOLE_Investment
-FD <- as.data.frame(tmp$FD)
-BOLE_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-BOLE_count <- subset(BOLE_count, count!=0)
-BOLE_count$species <- "BOLE"
-
-tmp <- COER_Investment
-FD <- as.data.frame(tmp$FD)
-COER_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-COER_count <- subset(COER_count, count!=0)
-COER_count$species <- "COER"
-
-tmp <- EPMI_Investment
-FD <- as.data.frame(tmp$FD)
-EPMI_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-EPMI_count <- subset(EPMI_count, count!=0)
-EPMI_count$species <- "EPMI"
-
-tmp <- GRBU_Investment
-FD <- as.data.frame(tmp$FD)
-GRBU_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-GRBU_count <- subset(GRBU_count, count!=0)
-GRBU_count$species <- "GRBU"
-
-tmp <- GRSP_Investment
-FD <- as.data.frame(tmp$FD)
-GRSP_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-GRSP_count <- subset(GRSP_count, count!=0)
-GRSP_count$species <- "GRSP"
-
-tmp <- HATE_Investment
-FD <- as.data.frame(tmp$FD)
-HATE_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-HATE_count <- subset(HATE_count, count!=0)
-HATE_count$species <- "HATE"
-
-tmp <- HEPU_Investment
-FD <- as.data.frame(tmp$FD)
-HEPU_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-HEPU_count <- subset(HEPU_count, count!=0)
-HEPU_count$species <- "HEPU"
-
-tmp <- LEES_Investment
-FD <- as.data.frame(tmp$FD)
-LEES_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-LEES_count <- subset(LEES_count, count!=0)
-LEES_count$species <- "LEES"
-
-tmp <- PELA_Investment
-FD <- as.data.frame(tmp$FD)
-PELA_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-PELA_count <- subset(PELA_count, count!=0)
-PELA_count$species <- "PELA"
-
-tmp <- PEPU_Investment
-FD <- as.data.frame(tmp$FD)
-PEPU_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-PEPU_count <- subset(PEPU_count, count!=0)
-PEPU_count$species <- "PEPU"
-
-tmp <- PHPH_Investment
-FD <- as.data.frame(tmp$FD)
-PHPH_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-PHPH_count <- subset(PHPH_count, count!=0)
-PHPH_count$species <- "PHPH"
-
-tmp <- PILI_Investment
-FD <- as.data.frame(tmp$FD)
-PILI_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-PILI_count <- subset(PILI_count, count!=0)
-PILI_count$species <- "PILI"
-
-tmp <- PUTU_Investment
-FD <- as.data.frame(tmp$FD)
-PUTU_count <- FD %>%
-  group_by(Individual, what) %>%
-  summarise_each(funs(sum), count, weight)
-PUTU_count <- subset(PUTU_count, count!=0)
-PUTU_count$species <- "PUTU"
-
-accessory_count <- rbind(BAER_count,BOLE_count,COER_count,EPMI_count,GRBU_count,GRSP_count,HATE_count,HEPU_count,LEES_count,PELA_count,PEPU_count,PHPH_count,PILI_count,PUTU_count)
-```
-
-TO DO
-- seed set with age - this is probably what explains a lot of changes in proportional tissue alotment. 
--Big question is if seed set changes with plant size or age

### 2015-05-19 results_accessory_shorter.rmd
created separate "RA_schedules_shorter" results file.

@@
 
-* A couple of questions:
-    1. What should one measure?
-    2. What does it mean as proportional energy shifts between accessory cost pools?
+    1. What reproduction "pool" should one measure?
+      * Is fecundity good enough?
+      * Is fruit or propagule weight good enough?
+    2. What might cause shifts in accessory costs across species?
+      * Previous studies have shown smaller-seeded species have lower accessory costs.
+      * This data set also lets us look at individual pools of accessory tissues and see how they change across species.
+    3. How does alotment to different accessory tissue types shift within a species as it ages, grows, or increases RA? 
+      * If accessory costs decrease with increased RA, increasing RA yields compounding returns.
 
@@
 * Plants with higher RA have lower allocation to pre-pollination tissues, probably because of their higher seedset
+* Total accessory costs and RA and rather unrelated - the plot shows a significant increase in accessory costs as RA increases, but this is mostly driven by BOLE
+
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}

### 2015-05-19 results_best.Rmd
created separate "RA_schedules_shorter" results file.

@@
 
-```{r, echo=FALSE,message=FALSE, fig.width=12, fig.height=6, out.width=792, out.height=576}
+```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7}
 yvar <- "RA"
@@
 
-```{r, echo=FALSE,message=FALSE, fig.width=12, fig.height=6, out.width=792, out.height=576}
+```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7}
 yvar <- "ReproInv"

### 2015-05-19 scripts/functions.R

@@ -10,6 +10,12 @@ plot_yvar2_vs_xvar2 <- function(data, yvar2 = "y", xvar2 = "x", ...) {
   plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
 }
 
+plot_yvar3_vs_xvar3 <- function(data, yvar3 = "y", xvar3 = "x", ...) {
+  Y <- data[[yvar3]]
+  X <- data[[xvar3]]
+  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
+}
+
 summarise_fit <- function(x) {
   data.frame(
     select(glance(x), r.squared, p.value),
@@ -95,4 +101,12 @@ words.bottom.right.logx <- function (x) {
   text(10^((0.7*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
   text(10^((0.7*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
   text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
+}
+
+words.bottom.right <- function (x) {
+  output <- data.frame(select(glance(x), r.squared, p.value))
+  output <- round(output,4)
+  text(((0.7*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
+  text(((0.7*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
+  text(((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
 }

### 2015-05-19 results_growth.Rmd
bit of work on growth file

@@
 source("scripts/summary_dataframes.R")
+source("scripts/functions.R")
 ```
@@
 
-Generic functions for most plotting below
-```{r, echo=FALSE, message=FALSE}
-plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
-  Y <- data[[yvar]]
-  X <- data[[xvar]]
-  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
-}
-
-summarise_fit <- function(x) {
-  data.frame(
-    select(glance(x), r.squared, p.value),
-    n= length(resid(x)),
-    a = coef(x)[1],
-    b = coef(x)[2]
-  )
-}
-
-summarise_all_fits <- function(x) {
-  tmp <- lapply(x, summarise_fit) %>%
-    bind_rows
-  data.frame(species=names(x), tmp)
-}
-```
-
 #Comparing growth between different measures and across age
@@
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-plot((FinalWeight~StartBasalDiamAv), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy")
 
@@
 
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))
 plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
@@
 results
+```
 
+```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
 for(spp in names(data)) {
@@
 ```{r, echo=FALSE, message=FALSE}
-plot((RGR~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
 yvar <- "RGR"
@@
 results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
-                    main=spp, xlab=xvar, ylab=yvar)
-  abline(lmfits[[spp]])
-}
-```
-
-###PropH by age
-- Confirming that species get taller as they get older  
-- Obviously true for most species, but some (i.e.
-PILI, somewhat BOLE, HEPU) they reach their "maxH" within a few years and then the relationship is mostly flat.
-These are of course also the species which are shorter lived and have high levels of early reproduction
-
-```{r, echo=FALSE, message=FALSE}
-yvar <- "PropH"
-xvar <- "age"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="x",
-                    main=spp, xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
 ```

### 2015-05-20 results_accessory_shorter.Rmd
Rename with correct extension

--- 2015-05-19 results_accessory_shorter.rmd
@@
 words.bottom.right.logxy(mod)
-text((par("fin")[1]*.5),(par("fin")[2]*.2),"Total size (mg)")
+mtext("Total size (mg)", 1, outer=TRUE)
 ```

### 2015-05-20 counts.Rmd
Rename downstream variables

--- 2015-05-14 counts.rmd
@@
 
-plot(seedset ~ FinalWeight,data=subset(SummaryInd,seedset>0),
+plot(seedset ~ total_weight,data=subset(SummaryInd,seedset>0),
           col=col.spp[as.factor(species)],

### 2015-05-20 leaflifespan.Rmd
Rename downstream variables

@@
 SummaryInd$change_shoot_diam <- SummaryInd$d_end - SummaryInd$d_start
-SummaryInd$change_basal_diam <- SummaryInd$FinalBasalDiam - SummaryInd$StartBasalDiam
+SummaryInd$change_basal_diam <- SummaryInd$growth_stem_diam
 SummaryInd$change_shoot_area <- (3.14*((SummaryInd$d_end/2)^2)) - (3.14*((SummaryInd$d_start/2)^2))
-SummaryInd$change_basal_area <- (3.14*((SummaryInd$FinalBasalDiam/2)^2)) - (3.14*((SummaryInd$StartBasalDiam/2)^2))
+SummaryInd$change_basal_area <- SummaryInd$growth_stem_area
 SummaryInd$lvs_end_total <- SummaryInd$lvs_end + SummaryInd$lvs_new
-SummaryInd$RGR <- log(SummaryInd$FinalWeight)-log(SummaryInd$FinalWeight-SummaryInd$GrowthInv)
+SummaryInd$RGR <- log(SummaryInd$total_weight)-log(SummaryInd$total_weight-SummaryInd$GrowthInv)
 ```
@@
   group_by(species, age) %>%
-  summarise_each(funs(mean, se, length), GrowthInv, FinalWeight, FinalBasalDiamAv, TotalInvestment, RA)
+  summarise_each(funs(mean, se, length), GrowthInv, total_weight, dia, TotalInvestment, RA)
 
@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(total_leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+plot(total_leaf_weight~total_weight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <-lm(FinalWeight~total_leaf_weight+age+species,SummaryInd)
+mod <-lm(total_weight~total_leaf_weight+age+species,SummaryInd)
 summary(mod)
@@
 plot_LeafWeight <- function(spp) {
-  plot(total_leaf_weight~FinalWeight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
+  plot(total_leaf_weight~total_weight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
   legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-  mod <-lm(FinalWeight~total_leaf_weight+age,data=subset(SummaryInd,species==spp))
+  mod <-lm(total_weight~total_leaf_weight+age,data=subset(SummaryInd,species==spp))
   abline(mod)
@@
 #USE THIS PLOT IN LAB MEETING - CLEARLY SHOWS DECLINE IN INTERCEPT WITH AGE
-plot(leafArea~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+plot(leafArea~total_weight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <-lm(FinalWeight~leafArea+age+species,SummaryInd)
+mod <-lm(total_weight~leafArea+age+species,SummaryInd)
 summary(mod)
@@
 plot_LeafArea <- function(spp) {
-  plot(leafArea~FinalWeight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
+  plot(leafArea~total_weight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
   legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-  mod <-lm(FinalWeight~leafArea+age,data=subset(SummaryInd,species==spp))
+  mod <-lm(total_weight~leafArea+age,data=subset(SummaryInd,species==spp))
   abline(mod)
@@
 #plots looking at shoot extension versus plant size
-plot(new_length~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+plot(new_length~total_weight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-mod <-lm(FinalWeight~new_length+age+species,SummaryInd)
+mod <-lm(total_weight~new_length+age+species,SummaryInd)
 summary(mod)
@@
 plot_LeaderExtension <- function(spp) {
-  plot(new_length~FinalWeight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
+  plot(new_length~total_weight,data=subset(SummaryInd,species==spp), xlab="total weight (mg)", ylab ="leaf weight (mg)", log="xy",col=col.age[as.factor(age)], pch=16,     cex=0.8,main=labels.spp[spp])
   legend("bottomright",col=col.age, labels.age, pch=16, cex=1)
-  mod <-lm(FinalWeight~new_length+age,data=subset(SummaryInd,species==spp))
+  mod <-lm(total_weight~new_length+age,data=subset(SummaryInd,species==spp))
   abline(mod)

### 2015-05-20 results_RAschedules.Rmd
Rename downstream variables

@@
 ```{r, echo=FALSE,message=FALSE}
-plot(ReproInv~FinalWeight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
+plot(ReproInv~total_weight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(ReproInv~FinalWeight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
+plot(ReproInv~total_weight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
 legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
 
-plot((1+ReproInv_mean)~FinalWeight_mean,SummarySppAge,log="xy", col=col.spp[as.factor(species)],pch=16)
+plot((1+ReproInv_mean)~total_weight_mean,SummarySppAge,log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 yvar <- "ReproInv"
-xvar <- "FinalWeight"
+xvar <- "total_weight"
 
@@
 ```{r, echo=FALSE,message=FALSE}
-plot(RA~FinalWeight, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
+plot(RA~total_weight, SummaryInd, log="x", col=col.spp[as.factor(species)],pch=16)
 legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(RA_mean~FinalWeight_mean,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
+plot(RA_mean~total_weight_mean,SummarySppAge,log="x", col=col.spp[as.factor(species)],pch=16)
 legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 yvar <- "RA"
-xvar <- "FinalWeight"
+xvar <- "total_weight"
 
@@
 These plots show very clearly that for all species RGR suddenly dips when RA becomes non-zero.
-Plotting against "FinalWeight" or "GrowthInvestment" is much less clear - in other words, an individual's height is the best way to sort them into plants investing more in growth vs reproduction.
+Plotting against "total_weight" or "GrowthInvestment" is much less clear - in other words, an individual's height is the best way to sort them into plants investing more in growth vs reproduction.
 There are of course some non-reproductive plants with "PropH" above the obvious cut-off, but these are almost certainly "reproductively mature" plants not reproducing in a given year.

### 2015-05-20 results_RAschedules_shorter.Rmd
Rename downstream variables

@@
 ```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
-mod <- lm(log(FinalWeight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot(ReproInv~FinalWeight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
+plot(ReproInv~total_weight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
-mod <- lm(log(FinalWeight)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
-plot(asin(sqrt(RA))~FinalWeight, SummaryInd, log="x",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(total_weight)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
+plot(asin(sqrt(RA))~total_weight, SummaryInd, log="x",col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 yvar2 <- "ReproInv"
-xvar2 <- "FinalWeight"
+xvar2 <- "total_weight"
 

### 2015-05-20 results_accessory_shorter.Rmd
Rename downstream variables

@@
 par(mfrow=c(2,2), cex=1, omi=c(2,0.3,.5,0.3), mai=c(.5,1,.5,0.3))
-mod <- lm (log(FinalWeight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot(ReproInv~FinalWeight,data=subset(SummaryInd,ReproInv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
+mod <- lm (log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
+plot(ReproInv~total_weight,data=subset(SummaryInd,ReproInv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
 words.bottom.right.logxy(mod)
 
-mod <- lm (log(FinalWeight)~log(fruit_weight), data=subset(SummaryInd,fruit_weight>0))
-plot(fruit_weight~FinalWeight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Fruit weight (mg)",xlim=c(100,2000000),xlab="")
+mod <- lm (log(total_weight)~log(fruit_weight), data=subset(SummaryInd,fruit_weight>0))
+plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Fruit weight (mg)",xlim=c(100,2000000),xlab="")
 words.bottom.right.logxy(mod)
 
-mod <- lm (log(FinalWeight)~log(Prop), data=subset(SummaryInd,Prop>0))
-plot(Prop~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
+mod <- lm (log(total_weight)~log(Prop), data=subset(SummaryInd,Prop>0))
+plot(Prop~total_weight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-mod <- lm (log(FinalWeight)~log(PerPropagule), data=subset(SummaryInd,PerPropagule>0))
-plot(PerPropagule~FinalWeight,data=subset(SummaryInd,PerPropagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Proportion reproductive investment to propagules",xlim=c(100,2000000),xlab="Total size (mg)")
+mod <- lm (log(total_weight)~log(PerPropagule), data=subset(SummaryInd,PerPropagule>0))
+plot(PerPropagule~total_weight,data=subset(SummaryInd,PerPropagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Proportion reproductive investment to propagules",xlim=c(100,2000000),xlab="Total size (mg)")
 words.bottom.right.logxy(mod)
@@
 
-mod <- lm(log(FinalWeight_mean)~asin(sqrt(PerAcc_mean)),SummarySpp)
-plot(asin(sqrt(PerAcc_mean))~FinalWeight_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
+mod <- lm(log(total_weight_mean)~asin(sqrt(PerAcc_mean)),SummarySpp)
+plot(asin(sqrt(PerAcc_mean))~total_weight_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
 words.bottom.right.logx(mod)

### 2015-05-20 results_accessory_tissues.Rmd
Rename downstream variables

--- 2015-05-06 results_accessory_tissues.rmd
@@
 yvar <- "PerAcc"
-xvar <- "FinalWeight"
+xvar <- "total_weight"
 
@@
 yvar <- "PerPrePol_A"
-xvar <- "FinalWeight"
+xvar <- "total_weight"
 
@@
 yvar <- "PerPrePol_All"
-xvar <- "FinalWeight"
+xvar <- "total_weight"
 

### 2015-05-20 results_best.Rmd
Rename downstream variables

@@
 yvar2 <- "RA"
-xvar2 <- "FinalWeight"
+xvar2 <- "total_weight"
 
@@
 
-plot(ReproInv~FinalWeight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
+plot(ReproInv~total_weight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 ```{r, echo=FALSE,message=FALSE}
-mod <- lm (log(FinalWeight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot(ReproInv~FinalWeight,data=subset(SummaryInd,ReproInv>0), log="xy",col=col.spp[as.factor(species)], pch=16)
+mod <- lm (log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
+plot(ReproInv~total_weight,data=subset(SummaryInd,ReproInv>0), log="xy",col=col.spp[as.factor(species)], pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-mod <- lm (log(FinalWeight)~log(Prop), data=subset(SummaryInd,Prop>0))
-plot(Prop~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
+mod <- lm (log(total_weight)~log(Prop), data=subset(SummaryInd,Prop>0))
+plot(Prop~total_weight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-mod <- lm (log(FinalWeight)~log(Prop+PD), data=subset(SummaryInd,Prop>0))
-plot((Prop+PD)~FinalWeight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
+mod <- lm (log(total_weight)~log(Prop+PD), data=subset(SummaryInd,Prop>0))
+plot((Prop+PD)~total_weight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-mod <- lm (log(FinalWeight)~log(PrePol_All), data=subset(SummaryInd,PrePol_All>0))
-plot((PrePol_All)~FinalWeight,data=subset(SummaryInd,PrePol_All>0), log="xy",col=col.spp[as.factor(species)], pch=16)
+mod <- lm (log(total_weight)~log(PrePol_All), data=subset(SummaryInd,PrePol_All>0))
+plot((PrePol_All)~total_weight,data=subset(SummaryInd,PrePol_All>0), log="xy",col=col.spp[as.factor(species)], pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 ```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7, out.width=792, out.height=576}
-mod <- lm(log(FinalWeight) ~ (log(PerPropagule))+age,data=subset(SummaryInd,PerPropagule>0))
+mod <- lm(log(total_weight) ~ (log(PerPropagule))+age,data=subset(SummaryInd,PerPropagule>0))
 summary(mod)
-plot(PerPropagule ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
+plot(PerPropagule ~total_weight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ (log(PropAllocation))*age,data=subset(SummaryInd,PerPropagule>0))
-plot(PropAllocation ~FinalWeight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(total_weight) ~ (log(PropAllocation))*age,data=subset(SummaryInd,PerPropagule>0))
+plot(PropAllocation ~total_weight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ (log(RA)),data=subset(SummaryInd,RA>0))
-plot(RA ~FinalWeight, data=subset(SummaryInd,RA>0),log="xy", col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(total_weight) ~ (log(RA)),data=subset(SummaryInd,RA>0))
+plot(RA ~total_weight, data=subset(SummaryInd,RA>0),log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-mod <- lm(log(FinalWeight) ~ (log(RA)),data=subset(SummaryInd,RA>5e-3&age==7))
-plot(RA ~FinalWeight, data=subset(SummaryInd,RA>5e-3&age==7),log="xy", col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(total_weight) ~ (log(RA)),data=subset(SummaryInd,RA>5e-3&age==7))
+plot(RA ~total_weight, data=subset(SummaryInd,RA>5e-3&age==7),log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-- A model including the effect of both PerPropagule and RA on FinalWeight confirms this - there is a strong species effect and strong PerPropagule effect, but RA is much less significant  
+- A model including the effect of both PerPropagule and RA on total_weight confirms this - there is a strong species effect and strong PerPropagule effect, but RA is much less significant  
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ (log(RA))*log(PerPropagule)*species,data=subset(SummaryInd,PerPropagule>0))
+mod <- lm(log(total_weight) ~ (log(RA))*log(PerPropagule)*species,data=subset(SummaryInd,PerPropagule>0))
 anova(mod)
@@
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0&age>3))
-plot(asin(sqrt(PerPrePol_All)) ~ FinalWeight, data=subset(SummaryInd,PerPrePol_All>0),log="x", col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(total_weight) ~ asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0&age>3))
+plot(asin(sqrt(PerPrePol_All)) ~ total_weight, data=subset(SummaryInd,PerPrePol_All>0),log="x", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight) ~ asin(sqrt(PerPackDisp)),data=subset(SummaryInd,PerPackDisp>0))
-plot(asin(sqrt(PerPackDisp)) ~FinalWeight, data=subset(SummaryInd,PerPackDisp>0),log="x", col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(total_weight) ~ asin(sqrt(PerPackDisp)),data=subset(SummaryInd,PerPackDisp>0))
+plot(asin(sqrt(PerPackDisp)) ~total_weight, data=subset(SummaryInd,PerPackDisp>0),log="x", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 yvar <- "PerPropagule"
-xvar <- "FinalWeight"
+xvar <- "total_weight"
 
@@
 
-mod <- lm(log(FinalWeight)~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
-plot(asin(sqrt(PerPropagule))~log(FinalWeight), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(total_weight)~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
+plot(asin(sqrt(PerPropagule))~log(total_weight), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 par(mfrow=c(2,2), cex=1, omi=c(.1,0.1,0.1,0.1), mai=c(1.2,1,0.1,0.1))
-mod <- lm(log(FinalWeight)~log(seedset),data=subset(SummaryInd,seedset>0))
-plot(seedset ~ FinalWeight,data=subset(SummaryInd,seedset>0),
+mod <- lm(log(total_weight)~log(seedset),data=subset(SummaryInd,seedset>0))
+plot(seedset ~ total_weight,data=subset(SummaryInd,seedset>0),
           col=col.spp[as.factor(species)],
@@
 words.bottom.right.logxy(mod)
-mod <- lm(log(FinalWeight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
-plot(seed_count ~ FinalWeight,data=subset(SummaryInd,seed_count>0),
+mod <- lm(log(total_weight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
+plot(seed_count ~ total_weight,data=subset(SummaryInd,seed_count>0),
           col=col.spp[as.factor(species)],
@@
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight)~log(PerPropagule),data=subset(SummaryInd,seedset>0))
-plot(PerPropagule~FinalWeight,data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+mod <- lm(log(total_weight)~log(PerPropagule),data=subset(SummaryInd,seedset>0))
+plot(PerPropagule~total_weight,data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16,log="xy")
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(asin(sqrt(PerPrePol_All)) ~log(FinalWeight)*age, data=subset(SummaryInd,PerPrePol_All>0))
+mod <- lm(asin(sqrt(PerPrePol_All)) ~log(total_weight)*age, data=subset(SummaryInd,PerPrePol_All>0))
 anova(mod)
@@
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(asin(sqrt(RA)) ~ log(FinalWeight)*age, data=subset(SummaryInd,RA>0))
-plot(asin(sqrt(RA))~FinalWeight,data=subset(SummaryInd,seedset>0),col=col.spp[as.factor(species)],pch=16,log="x")
+mod <- lm(asin(sqrt(RA)) ~ log(total_weight)*age, data=subset(SummaryInd,RA>0))
+plot(asin(sqrt(RA))~total_weight,data=subset(SummaryInd,seedset>0),col=col.spp[as.factor(species)],pch=16,log="x")
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
-plot(seed_count~FinalWeight,data=subset(SummaryInd,seed_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+mod <- lm(log(total_weight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
+plot(seed_count~total_weight,data=subset(SummaryInd,seed_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(FinalWeight)~log(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
-plot(fruit_weight~FinalWeight,data=subset(SummaryInd,fruit_weight>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+mod <- lm(log(total_weight)~log(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
+plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0),col=col.spp[as.factor(species)],pch=16,log="xy")
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

### 2015-05-20 results_growth.Rmd
Rename downstream variables

@@
 ```{r, echo=FALSE, message=FALSE}
-plot((FinalWeight~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
+plot((total_weight~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-yvar <- "FinalWeight"
+yvar <- "total_weight"
 xvar <- "PropH"
@@
 ```{r, echo=FALSE, message=FALSE}
-plot((GrowthInv~FinalWeight), SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+plot((GrowthInv~total_weight), SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
 abline(0,1,lwd=2)
@@
 
-plot(GrowthInv~FinalWeight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
+plot(GrowthInv~total_weight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
 abline(0,1,lwd=2)
@@
 ```{r, echo=FALSE,message=FALSE}
-plot(total_leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+plot(total_leaf_weight~total_weight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")
 
-plot(total_leaf_weight~FinalWeight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
+plot(total_leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
 legend("bottomright",col=col.spp, labels.spp, pch=16, cex=.8, bty="n")
@@
 
-plot((change_shoot_area/10000) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16,ylim=c(0.01,500),cex=.7)
-points((change_basal_area) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=1)
+plot((change_shoot_area/10000) ~ dia,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16,ylim=c(0.01,500),cex=.7)
+points((change_basal_area) ~ dia,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=1)
 
-plot((change_shoot_area/10000) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=16,ylim=c(0.01,500),cex=.7)
-points((change_basal_area) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=1)
+plot((change_shoot_area/10000) ~ dia,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=16,ylim=c(0.01,500),cex=.7)
+points((change_basal_area) ~ dia,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=1)
 

### 2015-05-20 results_leaf_lifespan.rmd
Rename downstream variables

@@
 yvar <- "LL_death"
-xvar <- "FinalWeight"
+xvar <- "total_weight"
 data <- filter(SummaryInd,LL_death<8&age>2)
@@
 ```{r, echo=FALSE,message=FALSE}
-mod <- lm(LMA_mean~species+log(FinalWeight_mean), SummarySppAge)
+mod <- lm(LMA_mean~species+log(total_weight_mean), SummarySppAge)
 summary(mod)
@@
 
-mod <- lm(LMA_mean~species+log(FinalWeight_mean), data=subset(SummarySppAge,age>2))
+mod <- lm(LMA_mean~species+log(total_weight_mean), data=subset(SummarySppAge,age>2))
 summary(mod)
@@
 
-plot(LMA_mean ~FinalWeight_mean, SummarySppAge, log="xy", col=col.spp[as.factor(species)], pch=16)
+plot(LMA_mean ~total_weight_mean, SummarySppAge, log="xy", col=col.spp[as.factor(species)], pch=16)
 legend("topleft",col=col.spp, pch=16,legend=labels.spp,cex=.8,bty="n")
 
-plot(LMA_mean ~FinalWeight_mean, data=subset(SummarySppAge), log="xy", col=col.age[as.factor(age)], pch=16, cex=1)
+plot(LMA_mean ~total_weight_mean, data=subset(SummarySppAge), log="xy", col=col.age[as.factor(age)], pch=16, cex=1)
 legend("topleft",col=col.age, pch=16,legend=labels.age,cex=.8,bty="n")

### 2015-05-20 R/ReproductionAllocation.R

@@ -40,10 +40,11 @@ RA_Calculations <- function(thisSpecies, Species_Investment, HarvestData, Maps, 
            stem_weight_est = predict_stem_weight(dia, individual[1]),
            growth_stem = c(NA, diff(stem_weight_est)),
            growth_leaf =  GrowthInv - growth_stem,
-           growth_dia = c(NA, diff(dia))
+           growth_stem_diam = c(NA, diff(dia)),
+           growth_stem_area = c(NA, diff(stem.area))
            ) %>%
     filter(start_end == "end") %>%
-    select(species, individual, age, dia, stem.area, leaf_weight, stem_weight, total_weight, GrowthInv, growth_stem, growth_leaf, growth_dia)
+    select(species, individual, age, dia, stem.area, leaf_weight, stem_weight, total_weight, GrowthInv, growth_stem, growth_leaf, growth_stem_diam, growth_stem_area)
 
     # Use saved data to calculate total reproduction investment per individual plant
     ReproTotal <- Species_Investment$Investment %>%

### 2015-05-20 R/figures.R

@@ -61,22 +61,22 @@ plot_ReproductionAllocation_comparison_age <- function(ReproductionAllocation_al
 
 plot_ReproductionAllocation_comparison_diam <- function(ReproductionAllocation_all) {
   cols <- col.table()
-  plot(ReproductionAllocation_all$FinalBasalDiamAv, ReproductionAllocation_all$RA, type = "p", col = cols[ReproductionAllocation_all$species], xlab = "Basal Diameter, year 2013", ylab = "RA", bty = "L")
+  plot(ReproductionAllocation_all$dia, ReproductionAllocation_all$RA, type = "p", col = cols[ReproductionAllocation_all$species], xlab = "Basal Diameter, year 2013", ylab = "RA", bty = "L")
   legend("topright", legend = names(cols), col = cols, pch = 1)
 }
 
 plot_ReproductionAllocation_comparison_weight <- function(ReproductionAllocation_all) {
   cols <- col.table()
-  plot(ReproductionAllocation_all$FinalWeight, ReproductionAllocation_all$RA, type = "p", col = cols[ReproductionAllocation_all$species], xlab = "Weight, year 2013", ylab = "RA", bty = "L")
+  plot(ReproductionAllocation_all$total_weight, ReproductionAllocation_all$RA, type = "p", col = cols[ReproductionAllocation_all$species], xlab = "Weight, year 2013", ylab = "RA", bty = "L")
   legend("topright", legend = names(cols), col = cols, pch = 1)
 }
 
 plot_species_ReproductionAllocation_weight_diam_panel <- function(Data) {
     cols <- col.table()[Data$species]
     par(mfrow = c(1, 2), cex.main = 1, cex.lab = 1)
-    plot(Data$FinalBasalDiamAv, Data$RA, type = "p", col = cols, xlab = "Diameter, year 2013", ylab = "RA", bty = "L", main = "Diameter", cex = 1)
+    plot(Data$dia, Data$RA, type = "p", col = cols, xlab = "Diameter, year 2013", ylab = "RA", bty = "L", main = "Diameter", cex = 1)
 
-    plot(Data$FinalWeight, Data$RA, type = "p", col = cols, xlab = "Weight, year 2013", ylab = "RA", bty = "L", main = "Weight", cex = 1)
+    plot(Data$total_weight, Data$RA, type = "p", col = cols, xlab = "Weight, year 2013", ylab = "RA", bty = "L", main = "Weight", cex = 1)
 }
 
 print_xtable_for_species <- function(thisSpecies, data, file){

### 2015-05-20 results_accessory_shorter.Rmd
making variable names more consistent

@@
       * Previous studies have shown smaller-seeded species have lower accessory costs.
-      * This data set also lets us look at individual pools of accessory tissues and see how they change across species.
     3. How does alotment to different accessory tissue types shift within a species as it ages, grows, or increases RA? 
@@
 
-mod <- lm (log(total_weight)~log(Prop), data=subset(SummaryInd,Prop>0))
-plot(Prop~total_weight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
+mod <- lm (log(total_weight)~log(propagules), data=subset(SummaryInd,propagules>0))
+plot(propagules~total_weight,data=subset(SummaryInd,propagules>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-mod <- lm (log(total_weight)~log(PerPropagule), data=subset(SummaryInd,PerPropagule>0))
-plot(PerPropagule~total_weight,data=subset(SummaryInd,PerPropagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Proportion reproductive investment to propagules",xlim=c(100,2000000),xlab="Total size (mg)")
+mod <- lm (log(total_weight)~log(prop_propagules), data=subset(SummaryInd,prop_propagules>0))
+plot(prop_propagules~total_weight,data=subset(SummaryInd,prop_propagules>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Proportion reproductive investment to propagules",xlim=c(100,2000000),xlab="Total size (mg)")
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))  
-mod <- lm(log(seed_size)~asin(sqrt(PerAcc_mean)),SummarySpp)
-plot(asin(sqrt(PerAcc_mean))~seed_size,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed size (mg)",cex=1.3)
+mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean),SummarySpp))
+plot(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed size (mg)",cex=1.3)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-mod <- lm(log(total_weight_mean)~asin(sqrt(PerAcc_mean)),SummarySpp)
-plot(asin(sqrt(PerAcc_mean))~total_weight_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
+mod <- lm(log(total_weight_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
+plot(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
 words.bottom.right.logx(mod)
 
-mod <- lm(log(seedset_mean)~asin(sqrt(PerAcc_mean)),SummarySpp)
-plot(asin(sqrt(PerAcc_mean))~seedset_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed set",cex=1.3)
+mod <- lm(log(seedset_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
+plot(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed set",cex=1.3)
 words.top.right.logx(mod)
 
-mod <- lm(asin(sqrt(seedset_mean))~asin(sqrt(PerPrePol_All_mean)),SummarySpp)
-plot(asin(sqrt(PerAcc_mean))~PerPrePol_All_mean,SummarySpp, log="", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
+mod <- lm(asin(sqrt(seedset_mean))~asin(sqrt(prop_prepollen_all)),SummarySpp)
+plot(asin(sqrt(prop_prepollen_all))~seedset_mean,SummarySpp, log="", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
 words.top.right(mod)
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(asin(sqrt(seedset))~log(PerPropagule),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(PerPropagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed set")
+mod <- lm(asin(sqrt(seedset))~log(prop_propagules),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(prop_propagules~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed set")
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(asin(sqrt(seedset))~log(PerPropagule),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(PerPropagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="Accessory costs (asin transformed)",xlab="seed set")
+mod <- lm(asin(sqrt(seedset))~log(prop_propagules),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(prop_propagules~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="Accessory costs (asin transformed)",xlab="seed set")
 words.bottom.right.logxy(mod)

### 2015-05-21 results_RAschedules.Rmd
lots of standardizing names also recalculated accessory costs on a per seed basis and added figures

@@
 ```{r, echo=FALSE,message=FALSE}
-plot((PropMaxRepro+.1)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
+plot((prop_max_repro+.1)~(prop_maxH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 yvar <- "ReproInv"
-xvar <- "PropH"
+xvar <- "prop_maxH"
 
@@
 
-#RA schedules (vs. propH)  
+#RA schedules (vs. prop_maxH)  
 - these curves are particularly good for a number of species such as EPMI, COER, PELA  
-- they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing propH  
+- they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing prop_maxH  
 - when all data points are included, all species except PEPU, PHPH, and PULU show increasing RA with increasing height  
@@
 ```{r, echo=FALSE, message=FALSE}
-plot((RA~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
+plot((RA~prop_maxH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(RA~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
+plot(RA~prop_maxH, SummaryInd, col=col.age[as.factor(age)],pch=16)
 legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
@@
 yvar <- "RA"
-xvar <- "PropH"
+xvar <- "prop_maxH"
 
@@
 #Reproductive Investment by scaled height 
-For these calculations, height is scaled relative to max height. This should be a way to determine RSOM - RSOM would be the PropH at which Reproductive Investment begins.
+For these calculations, height is scaled relative to max height. This should be a way to determine RSOM - RSOM would be the prop_maxH at which Reproductive Investment begins.
 For species such as BOLE which begin reproduction so young, data could be included that have pre-reproductive heights from mid-year censuses of "babies"
@@
 ```{r, echo=FALSE, message=FALSE}
-plot((RA~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
+plot((RA~prop_maxH), SummaryInd, col=col.spp[as.factor(species)],pch=16)
 legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot((RA)~PropH, SummaryInd, col=col.age[as.factor(age)],pch=16)
+plot((RA)~prop_maxH, SummaryInd, col=col.age[as.factor(age)],pch=16)
 legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
@@
 Plotting against "total_weight" or "GrowthInvestment" is much less clear - in other words, an individual's height is the best way to sort them into plants investing more in growth vs reproduction.
-There are of course some non-reproductive plants with "PropH" above the obvious cut-off, but these are almost certainly "reproductively mature" plants not reproducing in a given year.
+There are of course some non-reproductive plants with "prop_maxH" above the obvious cut-off, but these are almost certainly "reproductively mature" plants not reproducing in a given year.
 
-Model analyzed is: lm(log([[GrowthInv]]) ~  asin(sqrt([[RA]]))*asin(sqrt([[PropH]]))))
+Model analyzed is: lm(log([[GrowthInv]]) ~  asin(sqrt([[RA]]))*asin(sqrt([[prop_maxH]]))))
 
@@
 xvar <- "RA"
-x2var <- "PropH"
+x2var <- "prop_maxH"
 
@@
 results$p.value <- round(results$p.value,digits=3)
-names(results) <- c("species","r.sq_total","p-total","n","intercept","coef_RA","coef_PropH","coef_interaction","SS_RA","SS_PropH","SS_interaction")
+names(results) <- c("species","r.sq_total","p-total","n","intercept","coef_RA","coef_prop_maxH","coef_interaction","SS_RA","SS_prop_maxH","SS_interaction")
 results
@@
 yvar <- "GrowthInv"
-xvar <- "PropH"
+xvar <- "prop_maxH"
 
@@
 results2$p.value <- round(results2$p.value,digits=3)
-names(results2) <- c("species","r.sq.PropH","p.PropH","n","a","b")
+names(results2) <- c("species","r.sq.prop_maxH","p.prop_maxH","n","a","b")
 results2

### 2015-05-21 results_RAschedules_shorter.Rmd
lots of standardizing names also recalculated accessory costs on a per seed basis and added figures

@@
 * This includes both RA schedules and RV curves  
-* Below are curves plotted relative to "PropH", which is a better fit for most species - but other species should be plotted against total plant weight  
+* Below are curves plotted relative to "prop_maxH", which is a better fit for most species - but other species should be plotted against total plant weight  
 * Plants that grow more also reproduce more, but plants that allocate more to reproduction have lower RGR 
-* There is a disinct decline in RGR (or Growth Investment) at the exact "PropH" that plants begin to reproduce 
+* There is a disinct decline in RGR (or Growth Investment) at the exact "prop_maxH" that plants begin to reproduce 
 * Plotting reproductive investment (ReproInv) against RGR yields a much lower r^2 - for every single species.
@@
 
-mod <- lm((PropH)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot((ReproInv)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
+mod <- lm((prop_maxH)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
+plot((ReproInv)~(prop_maxH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 * RA not significantly correlated with total height or weight, but of course across and within species effects opposite - bigger individuals of a species have higher RA, but species that are overall bigger have lower RA
-* Therefore, there is a negative correlation between PropH (proportion of a species' maximum height) and RA; highly significant, but very low R^2
+* Therefore, there is a negative correlation between prop_maxH (proportion of a species' maximum height) and RA; highly significant, but very low R^2
 
@@
 
-mod <- lm((PropH)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
-plot((asin(sqrt(RA)))~(PropH), SummaryInd,col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
+mod <- lm((prop_maxH)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
+plot((asin(sqrt(RA)))~(prop_maxH), SummaryInd,col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 - RA schedules plotted against height are particularly good for a number of species such as EPMI, COER, PELA  
-  1. they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing propH  
+  1. they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing prop_maxH  
   2. when all data points are included, all species except PEPU, PHPH, and PULU show increasing RA with increasing height  
@@
 ###To think about regarding RA schedules and RV curves
-- What does it mean that PropH is the better correlate that plant weight?  
+- What does it mean that prop_maxH is the better correlate that plant weight?  
 1. That "plant weight" is a mis-leading number, since it includes dead "heartwood"  
 2. That this is a community where height is the most important variable? Because height = light access or because of some relationship between height and leaf area.  
-** Once I have leaf weights, I'll be curious how leaf weight plots against PropH, this might be more of the story
+** Once I have leaf weights, I'll be curious how leaf weight plots against prop_maxH, this might be more of the story
 
-###Looking jointly at effects of RA and PropH on growth inveestment
-- Model analyzed is: lm(log([[GrowthInv]]) ~  asin(sqrt([[RA]]))*asin(sqrt([[PropH]]))))  
+###Looking jointly at effects of RA and prop_maxH on growth inveestment
+- Model analyzed is: lm(log([[GrowthInv]]) ~  asin(sqrt([[RA]]))*asin(sqrt([[prop_maxH]]))))  
 - The canopy species have, not suprisingly, a very obvious maxH, with Growth Investment or RGR tapering markedly at the maxH is approached.
@@
 results$p.value <- round(results$p.value,digits=3)
-names(results) <- c("species","r,squared","p-value","n","intercept","coef_RA","coef_PropH","coef_interaction","SS_RA","SS_PropH","SS_interaction")
+names(results) <- c("species","r,squared","p-value","n","intercept","coef_RA","coef_prop_maxH","coef_interaction","SS_RA","SS_prop_maxH","SS_interaction")
 results

### 2015-05-21 results_accessory_shorter.Rmd
lots of standardizing names also recalculated accessory costs on a per seed basis and added figures

@@
 
-mod <- lm (log(total_weight)~log(propagules), data=subset(SummaryInd,propagules>0))
-plot(propagules~total_weight,data=subset(SummaryInd,propagules>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
+mod <- lm (log(total_weight)~log(propagule_inv), data=subset(SummaryInd,propagule_inv>0))
+plot(propagule_inv~total_weight,data=subset(SummaryInd,propagule_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-mod <- lm (log(total_weight)~log(prop_propagules), data=subset(SummaryInd,prop_propagules>0))
-plot(prop_propagules~total_weight,data=subset(SummaryInd,prop_propagules>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Proportion reproductive investment to propagules",xlim=c(100,2000000),xlab="Total size (mg)")
+mod <- lm (log(total_weight)~log(seedset), data=subset(SummaryInd,seedset>0))
+plot(seedset~total_weight,data=subset(SummaryInd,prop_propagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="seedset",xlim=c(100,2000000),xlab="Total size (mg)")
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))  
-mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean),SummarySpp))
-plot(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed size (mg)",cex=1.3)
+mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean)),SummarySpp)
+plot(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="seed size (mg)",cex=1.3)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 mod <- lm(log(seedset_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed set",cex=1.3)
+plot(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",cex=1.3)
 words.top.right.logx(mod)
 
-mod <- lm(asin(sqrt(seedset_mean))~asin(sqrt(prop_prepollen_all)),SummarySpp)
-plot(asin(sqrt(prop_prepollen_all))~seedset_mean,SummarySpp, log="", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
+mod <- lm(asin(sqrt(prop_prepollen_all_mean))~asin(sqrt(prop_accessory_mean)),SummarySpp)
+plot(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, log="", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
 words.top.right(mod)
+mtext("Proportion accessory investment (asin transformed)",2, outer=TRUE)
+```
+###Looking at investment vs. costs per successful seed
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))  
+mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
+plot(accessory_per_seed_mean~seed_size,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="seed size (mg)",cex=1.3)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(total_weight_mean)~log(accessory_per_seed_mean),SummarySpp)
+plot(accessory_per_seed_mean~total_weight_mean,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(seedset_mean)~log(accessory_per_seed_mean),SummarySpp)
+plot((accessory_per_seed_mean)~seedset_mean,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",cex=1.3)
+words.top.right.logxy(mod)
+
+mod <- lm(log(prepollen_all_per_seed_mean)~log(accessory_per_seed_mean),SummarySpp)
+plot(log(accessory_per_seed_mean)~log(prepollen_all_per_seed_mean),SummarySpp, log="", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
+words.top.right(mod)
+mtext("Accessory investment per successful seed (log scale)",2, outer=TRUE)
+```
+
+###Plotting accessory costs that go into making a single seed - ignoring aborted tissues
+* Bigger seeds have bigger fixed costs of making that seed (1st plot)
+* But other than LEES having much lower costs, no shifts across species in their relative costs to make a seed (2nd plot)
+* In other words, patterns of accessory costs vs. seed size, plant size, etc come about due to the differential effect of bud, flower abortion across species  
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
+plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp[as.factor(species)])
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
+plot(seed_size~costs_per_seed,data=subset(SummarySpp),log="y",pch=16,col=col.spp[as.factor(species)])
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 ```
@@
 ```{r, echo=FALSE,message=FALSE}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(asin(sqrt(seedset))~log(prop_propagules),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_propagules~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],ylab="Accessory costs (asin transformed)",xlab="seed set")
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
+mod <- lm(log(seedset)~(prop_accessory),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(prop_accessory~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="x", pch=16,col=col.spp[as.factor(species)],xlab="seed set")
+words.bottom.right.logx(mod)
+
+mod <- lm(log(seedset)~log(accessory_per_seed),data=subset(SummaryInd,seedset>0&seedset<1&accessory_per_seed>0))
+plot(accessory_per_seed~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="seed set")
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 ```
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(asin(sqrt(seedset))~log(prop_propagules),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_propagules~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="Accessory costs (asin transformed)",xlab="seed set")
+mod <- lm(asin(sqrt(seedset))~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="Accessory costs (asin transformed)",xlab="seed set")
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(asin(sqrt(PerPrePol_All))~log((ReproInv)),data=subset(SummaryInd,PerPrePol_All>0&PerPrePol_All<1))
-plot(asin(sqrt(PerPrePol_All))~ReproInv,data=subset(SummaryInd,PerPrePol_All>0&PerPrePol_All<1), log="x", pch=16,col=col.spp[as.factor(species)])
+mod <- lm(asin(sqrt(prop_prepollen_all))~log((ReproInv)),data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1))
+plot(asin(sqrt(prop_prepollen_all))~ReproInv,data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1), log="x", pch=16,col=col.spp[as.factor(species)])
 words.top.right.logx(mod)
@@
 
-mod <- lm(asin(sqrt(PerPropagule))~log((ReproInv)),data=subset(SummaryInd,PerPropagule>0))
-plot(asin(sqrt(PerPropagule))~ReproInv,data=subset(SummaryInd,PerPropagule>0), log="x", pch=16,col=col.spp[as.factor(species)])
+mod <- lm(asin(sqrt(prop_propagule))~log((ReproInv)),data=subset(SummaryInd,prop_propagule>0))
+plot(asin(sqrt(prop_propagule))~ReproInv,data=subset(SummaryInd,prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)])
 words.top.right.logx(mod)
@@
 ```{r, echo=FALSE,message=FALSE}
-mod <- lm(log(RA)~log(repro_count),data=subset(SummaryInd,repro_count>0))
-plot(repro_count~RA,data=subset(SummaryInd,repro_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+mod <- lm(log(RA)~log(repro_all_count),data=subset(SummaryInd,repro_all_count>0))
+plot(repro_all_count~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-yvar <- "repro_count"
+yvar <- "repro_all_count"
 xvar <- "RA"
 
-data <- subset(SummaryInd, repro_count>0)
+data <- subset(SummaryInd, repro_all_count>0)
 data <- split(data, data$species)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(log(RA)~log((PrePol_All)),data=subset(SummaryInd,RA>0&PrePol_All>0))
-plot(PrePol_All~(RA),data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination tissues (mg)")
+mod <- lm(log(RA)~log((prepollen_all_inv)),data=subset(SummaryInd,RA>0&prepollen_all_inv>0))
+plot(prepollen_all_inv~(RA),data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination tissues (mg)")
 words.bottom.right.logxy(mod)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-mod <- lm(log(RA)~log((Prop)),data=subset(SummaryInd,RA>0&Prop>0))
-plot(Prop~(RA),data=subset(SummaryInd,RA>0&Prop>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
+mod <- lm(log(RA)~log((propagule_inv)),data=subset(SummaryInd,RA>0&propagule_inv>0))
+plot(propagule_inv~(RA),data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,RA>0&PerPrePol_All>0))
-plot(asin(sqrt(PerPrePol_All))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&PerPrePol_All>0), pch=16,col=col.spp[as.factor(species)])
+mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_prepollen_all)),data=subset(SummaryInd,RA>0&prop_prepollen_all>0))
+plot(asin(sqrt(prop_prepollen_all))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&prop_prepollen_all>0), pch=16,col=col.spp[as.factor(species)])
 words.top.right(mod)
 
-mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule)),data=subset(SummaryInd,RA>0))
-plot(asin(sqrt(PerPropagule))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&PerPropagule>0), pch=16,col=col.spp[as.factor(species)])
+mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,RA>0))
+plot(asin(sqrt(prop_propagule))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&prop_propagule>0), pch=16,col=col.spp[as.factor(species)])
 words.top.right(mod)
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(asin(sqrt(PropH))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset<1&seedset>0))
-plot(asin(sqrt(seedset))~PropH,data=subset(SummaryInd,seedset<1&seedset>0), pch=16,col=col.spp[as.factor(species)])
+mod <- lm(asin(sqrt(prop_maxH))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset<1&seedset>0))
+plot(asin(sqrt(seedset))~prop_maxH,data=subset(SummaryInd,seedset<1&seedset>0), pch=16,col=col.spp[as.factor(species)])
 words.top.right(mod)
@@
 yvar <- "seedset"
-xvar <- "PropH"
+xvar <- "prop_maxH"
 
@@
 ```{r, echo=FALSE,message=FALSE}
-yvar <- "PerAcc"
+yvar <- "prop_accessory"
 xvar <- "age"
@@
 ```{r, echo=FALSE,message=FALSE}
-yvar <- "PerPrePol_All"
+yvar <- "prop_prepollen_all"
 xvar <- "age"
@@
 ```{r, echo=FALSE, message=FALSE}
-mean1 <- SummarySpp$PerPropagule_mean
-se1 <- SummarySpp$PerPropagule_se
+mean1 <- SummarySpp$prop_propagule_mean
+se1 <- SummarySpp$prop_propagule_se
 plot(mean1~species,SummarySpp,cex.axis=.7,pch=16,log="y",ylim=c(.002,.25),main="Percent reproductive investment put into propagules")
@@
 ```{r, echo=FALSE, message=FALSE}
-mean1 <- SummarySpp$PerPrePol_All_mean
-se1 <- SummarySpp$PerPrePol_All_se
+mean1 <- SummarySpp$prop_prepollen_all_mean
+se1 <- SummarySpp$prop_prepollen_all_se
 plot(mean1~species,data=subset(SummarySpp),cex.axis=.8,pch=16,ylim=c(.1,1),main="Percent reproductive investment put into pre-pollination tissues")
@@
 tmp <- SummaryInd %>%
-  filter(Total!=0&age>3) %>%
+  filter(ReproInv!=0&age>3) %>%
   group_by(species) %>%
-  summarise_each(funs(mean, se), PerPrePol_All)
+  summarise_each(funs(mean, se), prop_prepollen_all)
 
@@
 ```{r, echo=FALSE, message=FALSE}
-mean1 <- SummarySpp$PerPackDisp_mean
-se1 <- SummarySpp$PerPackDisp_se
+mean1 <- SummarySpp$prop_packaging_dispersal_mean
+se1 <- SummarySpp$prop_packaging_dispersal_se
 
@@
 tmp2 <- SummaryInd %>%
-  filter(Total!=0&age>3) %>%
+  filter(ReproInv!=0&age>3) %>%
   group_by(species) %>%
-  summarise_each(funs(mean, se), PerPackDisp)
+  summarise_each(funs(mean, se), prop_packaging_dispersal)
 
@@
 ```
+
+#Shifts in accessory costs across species and ages
+##Overall results
+- Accessory costs higher for bigger seeds
+
+- Accessory costs higher for bigger species; these are the same species that invest less in RA
+
+- Of course there is also a correlation between seed size and plant size, but actually not as strong as the accessory cost one, presumably because older plants have lower accessory costs as well as species that are inherently bigger
+
+- A number of species show fairly consistent declines in accessory costs with various measures of "bigger", including size, age, RA. Other species show no patterns  
+- Lower pre-pollination costs in plants with higher RA: 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases.
+in other words, they get better returns on investment the more they invest.
+(This is just a pattern within, not across, species)
+- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e.
+Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers
+- Haven't actually run all the tests, but assume all reproductive tissue types will differ in proportional allocation across species
+- For most of the statistical analyses, the youngest site has been removed, since it included individuals that were harvested while flowering (and therefore never "got to" set fruit) and automatically have no "successful" reproduction.
+There are of course some individuals like this at other ages as well, but far fewer

### 2015-05-21 results_accessory_tissues.Rmd
lots of standardizing names also recalculated accessory costs on a per seed basis and added figures

--- 2015-04-30 results_accessory_tissues.rmd
@@
 ```{r, echo=FALSE,message=FALSE}
-yvar <- "PerAcc_mean"
+yvar <- "prop_accessory_mean"
 xvar <- "seed_size"
@@
                   xlab=xvar, ylab=yvar)
-mod <- lm(log(seed_size)~PerAcc_mean,SummarySpp)
+mod <- lm(log(seed_size)~prop_accessory_mean,SummarySpp)
 summary(mod)
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPropagule"
+yvar <- "prop_propagule"
 xvar <- "species"
@@
                  xlab=xvar, ylab=yvar)
-mod <- lm(asin(sqrt(PerPropagule)) ~ species, data)
+mod <- lm(asin(sqrt(prop_propagule)) ~ species-1, data)
 summary(mod)
+data.frame(
+    select(glance(mod), r.squared, p.value),
+    n= length(resid(mod)),
+    a = coef(mod)[1],
+    b = coef(mod)[2]
+  )
+
+tmp <- summary(mod)
+tmp <- tmp$coefficients
+tmp <-as.data.frame(tmp)
+tmp <- cbind(names(labels.spp),tmp)
+names(tmp) <- c("species","estimate.trans","se.trans","t.value","p.value")
+tmp2 <- select(SummarySpp, species, prop_propagule_mean, prop_propagule_se)
+tmp <- merge(tmp, tmp2, by="species")
+tmp
+plot(prop_propagule_mean~species,tmp,cex.axis=.8,pch=16,log="y",ylim=c(.001,.25),main="Percent reproductive investment put into propagules")
+
+mean1 <- tmp$prop_propagule_mean
+se1 <- tmp$prop_propagule_se
+
+se_function(mean1,se1)
+
+#for(i in 1:14) {
+#arrows(i,tmp$prop_propagule_mean[i]+tmp$prop_propagule_se[i],i,tmp$prop_propagule_mean[i]-tmp$prop_propagule_se[i],code=3,angle=90, length=0.1)}
+
+#barplot(height=test$prop_propagule_mean, names=test$species,cex.axis=.8,ylim=c(0,.25),cex.names=.8)
+#xv <- barplot(height=test$prop_propagule_mean, names=test$species,cex.axis=.8,ylim=c(0,.25),cex.names=.8)
+#xv
+
+#points((prop_propagule_mean+prop_propagule_se)~species,test,pch=25)
+#points((prop_propagule_mean-prop_propagule_se)~species,test,pch=24)
+
+#Tuk <- TukeyHSD(mod)
 ```
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_A"
+yvar <- "prop_prepollen_aborted"
 xvar <- "species"
@@
                   xlab=xvar, ylab=yvar)
-mod <- lm(asin(sqrt(PerPrePol_A)) ~ species, data)
+mod <- lm(asin(sqrt(prop_prepollen_aborted)) ~ species, data)
 summary(mod)
@@
 ###Change in accesory costs With size:  
-- PerAcc is arcsine transformed, size is log transformed  
+- prop_accessory is arcsine transformed, size is log transformed  
 - COER, HATE, and PILI show a significant decrease in accessory costs with increasing size (p<0.05)  
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerAcc"
-xvar <- "FinalWeight"
+yvar <- "prop_accessory"
+xvar <- "total_weight"
 
@@
 ###Change in accesory costs With age:
-- PerAcc is arcsine transformed, age is log transformed  
+- prop_accessory is arcsine transformed, age is log transformed  
 - BOLE, COER, GRSP, HATE, HEPU, PELA show a significant decrease in accessory costs with increasing age (p<0.05)  
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerAcc"
+yvar <- "prop_accessory"
 xvar <- "age"
@@
 ###Change in accesory costs With respect to RA:  
-- both RA and PerAcc are arcsine transformed  
+- both RA and prop_accessory are arcsine transformed  
 - BAER, COER, GRBU, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in accessory costs with increasing RA (p<0.05)  
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerAcc"
+yvar <- "prop_propagule"
 xvar <- "RA"
@@
 ###Change in aborted bud investment with size:  
-- PerPrePol_A is arcsine transformed, size is log transformed  
+- prop_prepollen_aborted is arcsine transformed, size is log transformed  
 - GRSP, HATE, HEPU show a significant decrease in aborted buds with increasing size (p<0.05)  
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_A"
-xvar <- "FinalWeight"
+yvar <- "prop_prepollen_aborted"
+xvar <- "total_weight"
 
@@
 ###Change in aborted bud investment with respect to age:  
-- PerPrePol_A is arcsine transformed, age is log transformed  
+- prop_prepollen_aborted is arcsine transformed, age is log transformed  
 - BAER, BOLE, COER, EPMI, LEES, PHPH, PILI show a significant decrease in aborted buds with increasing age (p<0.05)  
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_A"
+yvar <- "prop_prepollen_aborted"
 xvar <- "age"
@@
 ###Change in aborted bud investment with respect to RA:
-- both RA and PerPrePol_A are arcsine transformed  
+- both RA and prop_prepollen_aborted are arcsine transformed  
 - BAER, BOLE, COER, GRSP, HATE, LEES, PELA, PEPU show a significant decrease in aborted buds with increasing RA (p<0.05)  
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_A"
+yvar <- "prop_prepollen_aborted"
 xvar <- "RA"
@@
 ###Do total pre-pollination costs change with respect to size:  
-- PerPrePol_All is arcsine transformed, size is log transformed  
+- prop_prepollen_all is arcsine transformed, size is log transformed  
 - GRSP, HATE show a significant decrease in total pre-pollination costs with increasing size (p<0.05)  
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_All"
-xvar <- "FinalWeight"
+yvar <- "prop_prepollen_all"
+xvar <- "total_weight"
 
-data <- filter(SummaryInd,Total>0)
+data <- filter(SummaryInd,ReproInv>0)
 data <- split(data, data$species)
@@
 ###Do total pre-pollination costs change with respect to age:
-- PerPrePol_All is arcsine transformed, age is log transformed  
+- prop_prepollen_all is arcsine transformed, age is log transformed  
 - BAER, BOLE, COER, HEPU, LEES, PILI show a significant decrease in total pre-pollination costs with increasing age (p<0.05)  
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_All"
+yvar <- "prop_prepollen_all"
 xvar <- "age"
 
-data <- filter(SummaryInd,Total>0&age>2)
+data <- filter(SummaryInd,ReproInv>0&age>2)
 data <- split(data, data$species)
@@
 ### Do total pre-pollination costs change with respect to RA:  
-- both RA and PerPrePol_All are arcsine transformed    
+- both RA and prop_prepollen_all are arcsine transformed    
 - BAER, BOLE, COER, GRSP, HATE, HEPU, LEES, PEPU show a significant decrease in total pre-pollination costs with increasing RA (p<0.05)  
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_All"
+yvar <- "prop_prepollen_all"
 xvar <- "RA"
 
-data <- filter(SummaryInd,Total>0&age>2)
+data <- filter(SummaryInd,ReproInv>0&age>2)
 data <- split(data, data$species)
@@
 ### Do total pre-pollination costs change with respect to Reproductive Investment:
-- PerPrePol_All is arcsine transformed, ReproInv is log transformed  
+- prop_prepollen_all is arcsine transformed, ReproInv is log transformed  
 - COER, GRBU, GRSP, HATE, PEPU, PHPH, PILI show a significant decrease in total pre-pollination costs with increasing reproductive investment (p<0.05)  
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_All"
+yvar <- "prop_prepollen_all"
 xvar <- "ReproInv"
 
-data <- filter(SummaryInd,Total>0&age>2)
+data <- filter(SummaryInd,ReproInv>0&age>2)
 data <- split(data, data$species)
@@
 data2 <- filter(SummarySppAge, species==spp)
-plot(PerPropagule_mean ~ age, data=data2, xlab="age", ylab="proportion tissue", cex.axis=.8, las=1,
+plot(prop_propagule_mean ~ age, data=data2, xlab="age", ylab="proportion tissue", cex.axis=.8, las=1,
        main=labels.spp[spp], ylim=c(0,1), xlim=c(1,35), log="x", pch=16,col="orange")
-points(PerPrePol_A_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8, col="red")
-points(PerPrePol_S_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=17, col="blue")
-points(PerPostPol_A_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=18, col="black")
-points(PerPackDisp_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=19, col="light green")
+points(prop_prepollen_aborted_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=8, col="red")
+points(prop_prepollen_success_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=17, col="blue")
+points(prop_postpollen_aborted_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=18, col="black")
+points(prop_packaging_dispersal_mean ~ age, data=subset(SummarySppAge, species==spp), cex=1.3, pch=19, col="light green")
 legend(.9,.7, pch=c(16,8,17,18,19),legend=c("Propagule","Aborted pre-poll","Successful pre-poll","Aborted post-poll","Packaging & disp"), col=c("orange","red","blue","black","light green"), cex=.8, bty="n")
@@
 ```{r, echo=FALSE, message=FALSE}
-mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule))+asin(sqrt(PerPrePol_A))+ asin(sqrt(PerPrePol_S))+ asin(sqrt(PerPostPol_A))+ asin(sqrt(PerPackDisp)) + species,data=subset(SummaryInd,Total>0))
+mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_propagule))+asin(sqrt(prop_prepollen_aborted))+ asin(sqrt(prop_prepollen_success))+ asin(sqrt(prop_postpollen_aborted))+ asin(sqrt(prop_packaging_dispersal)) + species,data=subset(SummaryInd,Total>0))
 
-mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule))+asin(sqrt(PerPrePol_A))+ asin(sqrt(PerPrePol_S))+ asin(sqrt(PerPostPol_A))+ asin(sqrt(PerPackDisp)) +asin(sqrt(PerPropagule))*species+asin(sqrt(PerPrePol_A))*species+ asin(sqrt(PerPrePol_S))*species+ asin(sqrt(PerPostPol_A))*species+ asin(sqrt(PerPackDisp))*species+ species,data=subset(SummaryInd,Total>0))
+mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_propagule))+asin(sqrt(prop_prepollen_aborted))+ asin(sqrt(prop_prepollen_success))+ asin(sqrt(prop_postpollen_aborted))+ asin(sqrt(prop_packaging_dispersal)) +asin(sqrt(prop_propagule))*species+asin(sqrt(prop_prepollen_aborted))*species+ asin(sqrt(prop_prepollen_success))*species+ asin(sqrt(prop_postpollen_aborted))*species+ asin(sqrt(prop_packaging_dispersal))*species+ species,data=subset(SummaryInd,Total>0))
 summary(mod)

### 2015-05-21 results_best.Rmd
lots of standardizing names also recalculated accessory costs on a per seed basis and added figures

@@
 source("scripts/summary_dataframes.R")
-plot_yvar_vs_xvar <- function(data, yvar = "y", xvar = "x", ...) {
-  Y <- data[[yvar]]
-  X <- data[[xvar]]
-  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
-}
-
-plot_yvar2_vs_xvar2 <- function(data, yvar2 = "y", xvar2 = "x", ...) {
-  Y <- data[[yvar2]]
-  X <- data[[xvar2]]
-  plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
-}
-
-summarise_fit <- function(x) {
-  data.frame(
-    select(glance(x), r.squared, p.value),
-    n= length(resid(x)),
-    a = coef(x)[1],
-    b = coef(x)[2]
-  )
-}
-
-summarise_all_fits <- function(x) {
-  tmp <- lapply(x, summarise_fit) %>%
-    bind_rows
-  data.frame(species=names(x), tmp)
-}
-
-summarise_fit_2var <- function(x) {
-  data.frame(
-    select(glance(x), r.squared, p.value),
-    n= length(resid(x)),
-    intercept = coef(x)[1],
-    coef_var1 = coef(x)[2],
-    coef_var2 = coef(x)[3],
-    coef_var1var2 = coef(x)[4],
-    SS_var1 = anova(x)[1,2],
-    SS_var2 = anova(x)[2,2],
-    SS_var1var2 =anova(x)[3,2]
-      )
-}
-
-summarise_all_fits_2var <- function(x) {
-  tmp <- lapply(x, summarise_fit_2var) %>%
-    bind_rows
-  data.frame(species=names(x), tmp)
-}
-
-xy.error.bars <- function (x,y,xbar,ybar) {
-  plot(x,y,pch=16, ylim=c(min(y-ybar),max(y+ybar)),xlim=c(min(x-xbar),max(x+xbar)))
-  arrows(x,y-ybar,x,y+ybar,code=3,angle=90, length=0.1)
-  arrows(x-xbar,y,x+xbar,y,code=3,angle=90, length=0.1)
-}
-
-se_function <- function(mean1,se1) {
-for(i in 1:14) {
-arrows(i,mean1[i]+se1[i],i,mean1[i]-se1[i],code=3,angle=90, length=0.1)
-}
-}
-
-words.top.right.logxy <- function (x) {
-output <- data.frame(select(glance(x), r.squared, p.value))
-output <- round(output,4)
-text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
-text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
-text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
-}
-
-words.top.right.logx <- function (x) {
-output <- data.frame(select(glance(x), r.squared, p.value))
-output <- round(output,4)
-text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
-text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
-text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
-}
-
-words.top.right <- function (x) {
-output <- data.frame(select(glance(x), r.squared, p.value))
-output <- round(output,4)
-text(((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
-text(((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
-text(((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
-}
-
-words.bottom.right.logxy <- function (x) {
-output <- data.frame(select(glance(x), r.squared, p.value))
-output <- round(output,4)
-text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
-text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
-text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
-}
-
-words.bottom.right.logx <- function (x) {
-  output <- data.frame(select(glance(x), r.squared, p.value))
-  output <- round(output,4)
-  text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.12*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
-  text(10^((0.75*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
-  text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=1)
-}
+source("scripts/functions.R")
 ```
@@
 - It is clear that different species reach a different "proportion maxH" (RSOM) before reproducing. Need to do curve fitting to determine where this occurs.  
-- The plot of Growth Investment vs. PropH shows a decrease in growth rate at a given PropH (for most species). Is this the same PropH at which reproduction begins?  
-- It seems that some of the early reproducers begin reproducing at a larger PropH, as predicted by others.
+- The plot of Growth Investment vs. prop_maxH shows a decrease in growth rate at a given prop_maxH (for most species). Is this the same prop_maxH at which reproduction begins?  
+- It seems that some of the early reproducers begin reproducing at a larger prop_maxH, as predicted by others.
 But because they allocate so much to reproduction, their growth rate declines more precipitously with the onset of reproduction.
@@
 ```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7, out.width=792, out.height=576}
-plot((ReproInv)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1),xlab=xvar)
+plot((ReproInv)~(prop_maxH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1),xlab=xvar)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-* Reproductive investment vs. PropH
+* Reproductive investment vs. prop_maxH
 ```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7, out.width=792, out.height=576}
 yvar <- "ReproInv"
-xvar <- "PropH"
+xvar <- "prop_maxH"
 
@@
 
-##RA schedules (vs. propH)  
+##RA schedules (vs. prop_maxH)  
 - RA schedules still look "best" plotted against age; not shown here  
 - these curves are particularly good for a number of species such as EPMI, COER, PELA  
-- they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing propH  
+- they also show that for PILI that among individuals that reproduce, the "potential" RA decreases with increasing prop_maxH  
 - when all data points are included, all species except PEPU, PHPH, and PULU show increasing RA with increasing height  
@@
 - PEPU has a negative correlation - matches Mark's suggestion that it is "hanging on"  
-- There are species - such as BOLE - which have a much "cleaner" plot against age instead of PropH (or any other size measure).
+- There are species - such as BOLE - which have a much "cleaner" plot against age instead of prop_maxH (or any other size measure).
 This indicates that these species are programmed to reproduce at a certain "rate" regardless of their size
@@
 results$p.value <- round(results$p.value,digits=3)
-names(results) <- c("species","r,squared","p-value","n","intercept","coef_RA","coef_PropH","coef_interaction","SS_RA","SS_PropH","SS_interaction")
+names(results) <- c("species","r,squared","p-value","n","intercept","coef_RA","coef_prop_maxH","coef_interaction","SS_RA","SS_prop_maxH","SS_interaction")
 results
 ```
-
-#Shifts in accessory costs across species and ages
-##Overall results
-- Accessory costs higher for bigger seeds
-
-- Accessory costs higher for bigger species; these are the same species that invest less in RA
-
-- Of course there is also a correlation between seed size and plant size, but actually not as strong as the accessory cost one, presumably because older plants have lower accessory costs as well as species that are inherently bigger
-
-- A number of species show fairly consistent declines in accessory costs with various measures of "bigger", including size, age, RA. Other species show no patterns  
-- Lower pre-pollination costs in plants with higher RA: 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases.
-in other words, they get better returns on investment the more they invest.
-(This is just a pattern within, not across, species)
-- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e.
-Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers
-- Haven't actually run all the tests, but assume all reproductive tissue types will differ in proportional allocation across species
-- For most of the statistical analyses, the youngest site has been removed, since it included individuals that were harvested while flowering (and therefore never "got to" set fruit) and automatically have no "successful" reproduction.
-There are of course some individuals like this at other ages as well, but far fewer
-
-##Basic questions
-###How do accessory costs shift with seed size?
-- Larger-seeded species have higher accessory costs. 
-- Also shown in other studies and suggested as a mechanism for why angiosperms were able to have such small seeds (relative to gymnosperms, with no decrease in proportional accessory costs - with decreasing size)
--  As shown below, bigger species also have higher accessory costs (and also bigger seeds - cause vs. effect unknown)
-```{r, echo=FALSE,message=FALSE}
-mod <- lm(log(seed_size)~asin(sqrt(PerAcc_mean)),SummarySpp)
-plot(PerAcc_mean~seed_size,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)])
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-```
-
-###Why measure "Total Reproductive Investment" instead of "seed weight" or "fruit weight"?  
-- The R^2 for the plot of total reproductive investment against total plant size is much stronger than plotting seed weight against total plant size (R^2 = 0.61 vs 0.33)  
-- Adding propagule + packaging & dispersal (i.e. successful reproduction costs), improves the fit somewhat (R^2 =0.55)  
-- Total pre-pollination costs are also well-correlated with plant size, indicating bigger plants have more flowers
-- NEXT: Once I have all parts weights, plot against fruit weight
-
-```{r, echo=FALSE,message=FALSE}
-mod <- lm (log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot(ReproInv~total_weight,data=subset(SummaryInd,ReproInv>0), log="xy",col=col.spp[as.factor(species)], pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-
-mod <- lm (log(total_weight)~log(Prop), data=subset(SummaryInd,Prop>0))
-plot(Prop~total_weight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-
-mod <- lm (log(total_weight)~log(Prop+PD), data=subset(SummaryInd,Prop>0))
-plot((Prop+PD)~total_weight,data=subset(SummaryInd,Prop>0), log="xy",col=col.spp[as.factor(species)], pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-
-mod <- lm (log(total_weight)~log(PrePol_All), data=subset(SummaryInd,PrePol_All>0))
-plot((PrePol_All)~total_weight,data=subset(SummaryInd,PrePol_All>0), log="xy",col=col.spp[as.factor(species)], pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-```
-
-###Looking at counts
-- Final weight vs. #flowers+buds
-- Final weight vs. #fruit
-
-##Across species patterns of note
-###Size versus proportional propagule investment
-- Species that are bigger (by weight) invest a lower proportion of their reproduction in propagules  
-   1.  This is another way of showing that larger species get less of a return on their investment in reproduction. They have higher accessory costs. 
-   - There is also an increase in propagule investment with age
-```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7, out.width=792, out.height=576}
-mod <- lm(log(total_weight) ~ (log(PerPropagule))+age,data=subset(SummaryInd,PerPropagule>0))
-summary(mod)
-plot(PerPropagule ~total_weight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logxy(mod)
-text(10^((0.70*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.85*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),"includes age effect",adj=0) 
-```
-
-- Species that are bigger also invest a lower proportion of their TOTAL surplus energy in propagules (proportion propagules*RA) 
-  + This is noisier than looking simply at proportion reproductive allocation to propagules, because of the RA effects - see below
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(total_weight) ~ (log(PropAllocation))*age,data=subset(SummaryInd,PerPropagule>0))
-plot(PropAllocation ~total_weight, data=subset(SummaryInd,RA>0&PerPropagule>0),log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logxy(mod)
-text(1000,.6e-4,"includes age effect (increase in Prop Allocation with age)",adj=0)
-summary(mod)
-```
-
-- Looking at RA with plant size is not very informative, because:
-  1. RA increases with plant size within a species  
-  2. decreases with plant size across species  
-  3. in combination they are noisy
-- The first plot is all points  
-- The second plot is just 7-year olds, showing the decrease in RA with plant size  
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(total_weight) ~ (log(RA)),data=subset(SummaryInd,RA>0))
-plot(RA ~total_weight, data=subset(SummaryInd,RA>0),log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-anova(mod)
-
-mod <- lm(log(total_weight) ~ (log(RA)),data=subset(SummaryInd,RA>5e-3&age==7))
-plot(RA ~total_weight, data=subset(SummaryInd,RA>5e-3&age==7),log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logxy(mod)
-```
-
-- A model including the effect of both PerPropagule and RA on total_weight confirms this - there is a strong species effect and strong PerPropagule effect, but RA is much less significant  
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(total_weight) ~ (log(RA))*log(PerPropagule)*species,data=subset(SummaryInd,PerPropagule>0))
-anova(mod)
-```
-
-- Proportional investment in all pre-pollination tissues is uncorrelated with plant size (at most ages)  
-  +  if age included in model, becomes highly significant  
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(total_weight) ~ asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0&age>3))
-plot(asin(sqrt(PerPrePol_All)) ~ total_weight, data=subset(SummaryInd,PerPrePol_All>0),log="x", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logx(mod)
-```
-
-- Shifts in packaging and dispersal costs with plant weight
-- Species very different from one another, but no shift with size 
-- Also no pattern w/r RA (not shown)
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(total_weight) ~ asin(sqrt(PerPackDisp)),data=subset(SummaryInd,PerPackDisp>0))
-plot(asin(sqrt(PerPackDisp)) ~total_weight, data=subset(SummaryInd,PerPackDisp>0),log="x", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logx(mod)
-```
-
-###Across species summary
-- greater plant weight = lower RA  (spending more on growth and survival)**  
-- greater plant weight = lower proportion to propagules  (bigger species get less for their allocation)**  
-- plant weight = little effect on pre-pollination tissues
-
-##Within species (across age, size, or RA) patterns to note
-- Only COER and HATE increase allocation to propagules with increased plant size  
-- This, together with other plots, indicates that only the plants (of a species) that have higher RA, have higher propagule investment; but not all bigger individuals have higher RA
-NOTE: Plot nearly same as above, except y-axis arcsine transformed, not log transformed and R^2 values without species term
-```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPropagule"
-xvar <- "total_weight"
-
-data <- subset(SummaryInd, Total>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
-
-mod <- lm(log(total_weight)~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
-plot(asin(sqrt(PerPropagule))~log(total_weight), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right(mod)
-```
-
-- Allocation to propagules increases with RA in all species except EPMI, PHPH, PILI, PUTU  
-- again, probably a figment of overall increased allocation (higher RA) if propagules form  
-```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPropagule"
-xvar <- "RA"
-
-data <- subset(SummaryInd, Total>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPropagule)),data=subset(SummaryInd,PerPropagule>0))
-plot(asin(sqrt(PerPropagule))~asin(sqrt(RA)), data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right(mod)
-```
-
-###Change in proportional allocation to pre-pollination tissues with plant weight 
-- only a few species show a significant correlation -> as plants grow, they don't shift this allocation  
-```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_All"
-xvar <- "total_weight"
-
-data <- subset(SummaryInd, Total>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-###Change in proportional allocation to pre-pollination tissues with RA
-- 9 species decrease allocation to pre-pollination tissues with increased RA  
-- this could simply be because when/if flowers are pollinated, there is increased reproductive investment, increasing RA and decreasing pre-pollination allocation  
-- Interesting that RA increases with plant size, and pre-pollination decreases with RA, but very low correlation between pre- pollination allocation and plant size  
-```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPrePol_All"
-xvar <- "RA"
-
-data <- subset(SummaryInd, Total>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-mod <- lm(asin(sqrt(RA))~asin(sqrt(PerPrePol_All)),data=subset(SummaryInd,PerPrePol_All>0))
-plot(asin(sqrt(PerPrePol_All))~asin(sqrt(RA)), data=subset(SummaryInd,PerPrePol_All>0),col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right(mod)
-```
-
-- Quite a few species (BAER, BOLE, COER, GRBU, GRSP, HATE, HEPU, PEPU, PHPH increase the percent reproductive investment spent on packaging and dispersal with age 
-- This probably reflects increased seed set with age and the simulatenous increase in this pool
-```{r, echo=FALSE, message=FALSE}
-yvar <- "PerPackDisp"
-xvar <- "RA"
-
-data <- subset(SummaryInd, Total>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  asin(sqrt(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-###Within species summary
-- greater plant weight = higher RA  (plants allocate more to reproduction when bigger/older)**
-- plant weight = little effect on proportion to propagules  
-- plant weight = little effect on pre-pollination tissues  
-- higher RA = lower allocation to pre-pollination tissues (probably because more seed set)
-- higher RA = greater allocation to propagules (probably because more seed set)
-
-##Shifts in proportion to tissue types across species  
-- Propagule allocation across species  
-- COER, EPMI, LEES, PILI invest the most energy in propagules  
-- HATE invests by far the least into propagules  
-```{r, echo=FALSE, message=FALSE}
-#mod <- lm(asin(sqrt(PerPropagule)) ~ species-1, data=subset((SummaryInd,Total>0))
-#tmp <- summary(mod)
-#tmp <- tmp$coefficients
-#tmp <-as.data.frame(tmp)
-#tmp <- cbind(names(labels.spp),tmp)
-#names(tmp) <- c("species","estimate.trans","se.trans","t.value","p.value")
-mean1 <- SummarySpp$PerPropagule_mean
-se1 <- SummarySpp$PerPropagule_se
-plot(mean1~species,SummarySpp,cex.axis=.7,pch=16,log="y",ylim=c(.002,.25),main="Percent reproductive investment put into propagules")
-se_function(mean1,se1)
-```
-
-- pre-pollination allocation across species
-
-```{r, echo=FALSE, message=FALSE}
-mean1 <- SummarySpp$PerPrePol_All_mean
-se1 <- SummarySpp$PerPrePol_All_se
-plot(mean1~species,data=subset(SummarySpp),cex.axis=.8,pch=16,ylim=c(.1,1),main="Percent reproductive investment put into pre-pollination tissues")
-se_function(mean1,se1)
-```
-
-- just looking among plants >3 years old
-
-```{r, echo=FALSE, message=FALSE}
-tmp <- SummaryInd %>%
-  filter(Total!=0&age>3) %>%
-  group_by(species) %>%
-  summarise_each(funs(mean, se), PerPrePol_All)
-
-plot(mean~species,
-    tmp,
-     cex.axis=.7,pch=16,log="y",ylim=c(.1,1),
-     main="Percent reproductive investment put into pre-pollination tissues")
-
-mean1 <- tmp$mean
-se1 <- tmp$se
-se_function(mean1,se1)
-```
-
-- Packaging and dispersal allocation across species
-
-```{r, echo=FALSE, message=FALSE}
-mean1 <- SummarySpp$PerPackDisp_mean
-se1 <- SummarySpp$PerPackDisp_se
-
-plot(mean1~species,SummarySpp,cex.axis=.8,pch=16,log="y",ylim=c(.02,1),main="Percent reproductive investment put into packaging and dispersal")
-se_function(mean1,se1)
-```
-
-- just looking among plants >3 years old
-
-```{r, echo=FALSE, message=FALSE}
-tmp2 <- SummaryInd %>%
-  filter(Total!=0&age>3) %>%
-  group_by(species) %>%
-  summarise_each(funs(mean, se), PerPackDisp)
-
-plot(mean~species,
-    tmp2,
-     cex.axis=.7,pch=16,log="y",ylim=c(0.02,.8),
-     main="Percent reproductive investment put into packaging & dispersal tissues")
-
-mean1 <- tmp2$mean
-se1 <- tmp2$se
-
-se_function(mean1,se1)
-```
-
-###Across species summary
-- nothing much shifts with plant size
-- most pool shift with RA, but that is likely because higher RA often means increased seed set - higher RA occurs because some flowers pollinated and mature, which shifts proportional allocation to post-pollination pools
-- has interesting implications for what RA means if it is closely linked to increased seed set (or aborted fruit production)
-
-##Looking at 
-- Species that are smaller have lower seed set -> this is likely what is causing Propagule allocation to decrease with size
-- Also a small increase in seedset with age - but a smaller effect
-
-```{r, echo=FALSE, message=FALSE}
-par(mfrow=c(2,2), cex=1, omi=c(.1,0.1,0.1,0.1), mai=c(1.2,1,0.1,0.1))
-mod <- lm(log(total_weight)~log(seedset),data=subset(SummaryInd,seedset>0))
-plot(seedset ~ total_weight,data=subset(SummaryInd,seedset>0),
-          col=col.spp[as.factor(species)],
-          pch=16,log="xy",xlab="",ylab="seed set")
-words.bottom.right.logxy(mod)
-
-mod <- lm(log(RA)~log(seedset),data=subset(SummaryInd,seedset>0))
-plot(seedset ~ RA,data=subset(SummaryInd,seedset>0),
-          col=col.spp[as.factor(species)],
-          pch=16,log="xy",ylab="",xlab="")
-words.bottom.right.logxy(mod)
-mod <- lm(log(total_weight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
-plot(seed_count ~ total_weight,data=subset(SummaryInd,seed_count>0),
-          col=col.spp[as.factor(species)],
-          pch=16,log="xy",xlab="plant weight",ylab="seed count")
-words.bottom.right.logxy(mod)
-mod <- lm(log(RA)~log(seed_count),data=subset(SummaryInd,seed_count>0))
-plot(seed_count ~ RA,data=subset(SummaryInd,seed_count>0),
-          col=col.spp[as.factor(species)],
-          pch=16,log="xy",ylab="")
-words.bottom.right.logxy(mod)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-```
-
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(total_weight)~log(PerPropagule),data=subset(SummaryInd,seedset>0))
-plot(PerPropagule~total_weight,data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16,log="xy")
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logxy(mod)
-```
-
-- However, as shown above, there is no clear shift across plant size in pre-pollination allocation   
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(asin(sqrt(PerPrePol_All)) ~log(total_weight)*age, data=subset(SummaryInd,PerPrePol_All>0))
-anova(mod)
-```
-
-- There is however a decrease in RA with plant size at a given age (across species effect)
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(asin(sqrt(RA)) ~ log(total_weight)*age, data=subset(SummaryInd,RA>0))
-plot(asin(sqrt(RA))~total_weight,data=subset(SummaryInd,seedset>0),col=col.spp[as.factor(species)],pch=16,log="x")
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logx(mod)
-anova(mod)
-```
-
-- Together this indicates that increased propagule allocation is due to increased seedset, which increases RA in smaller-sized species
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(asin(sqrt(RA))~age*species,data=subset(SummaryInd,RA>0))
-anova(mod)
-```
-
-- seedset and Proportional allocation to propagules (vs. all accessory tissues) are well correlated, within and across species  
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(seedset)~log(PerPropagule),data=subset(SummaryInd,seedset>0))
-plot(PerPropagule~seedset,data=subset(SummaryInd,seedset>0),col=col.spp[as.factor(species)],pch=16,log="xy")
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-
-anova(mod)
-```
-
-- however, seedset and seed size are much less well correlated
-- so for this collection of species, shifts in accessory costs are closely linked to seed_set
-- seed set therefore clearly plays a role in the (small) shifts in RA with plant size
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(seedset)~log(seed_size),data=subset(SummaryInd,seedset>0))
-
-plot(seed_size~seedset,data=subset(SummaryInd,PerPropagule>0),col=col.spp[as.factor(species)],pch=16,log="xy")
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logxy(mod)
-```
-
-- there is no relationship between seed_count and Final Weight
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(total_weight)~log(seed_count),data=subset(SummaryInd,seed_count>0))
-plot(seed_count~total_weight,data=subset(SummaryInd,seed_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-```
-
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(total_weight)~log(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
-plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0),col=col.spp[as.factor(species)],pch=16,log="xy")
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-```
-
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(ReproInv)~log(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
-plot(fruit_weight~ReproInv,data=subset(SummaryInd,fruit_weight>0),col=col.spp[as.factor(species)],pch=16,log="xy")
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-```
-
-- producing more seeds has a limited effect on RA  
-- it is proprtion of flowers/buds that become seeds (seed set) that matters
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(RA)~log(seed_count),data=subset(SummaryInd,seed_count>0))
-plot(seed_count~RA,data=subset(SummaryInd,seed_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-
-yvar <- "seed_count"
-xvar <- "RA"
-
-data <- subset(SummaryInd, seed_count>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-- However, producing more reproductive units increases RA  - this is a within species effect mostly  
-```{r, echo=FALSE, message=FALSE}
-mod <- lm(log(RA)~log(repro_count),data=subset(SummaryInd,repro_count>0))
-plot(repro_count~RA,data=subset(SummaryInd,repro_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-
-yvar <- "repro_count"
-xvar <- "RA"
-
-data <- subset(SummaryInd, repro_count>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```

### 2015-05-21 results_growth.Rmd
lots of standardizing names also recalculated accessory costs on a per seed basis and added figures

@@
 ```{r, echo=FALSE, message=FALSE}
-plot((total_weight~PropH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
+plot((total_weight~prop_maxH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 yvar <- "total_weight"
-xvar <- "PropH"
+xvar <- "prop_maxH"
 
@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))
-plot((GrowthInv~PropH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
+plot((GrowthInv~prop_maxH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(GrowthInv~PropH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
+plot(GrowthInv~prop_maxH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
 legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
@@
 yvar <- "RGR"
-xvar <- "PropH"
+xvar <- "prop_maxH"
 
@@
 ```{r, echo=FALSE,message=FALSE}
-plot(change_shoot_area~change_basal_area,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
+plot(growth_shoot_area~growth_stem_area,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1,bty="n")
-mod <- lm(change_shoot_area~change_basal_area*age*species,SummaryInd)
+mod <- lm(growth_shoot_area~growth_stem_area*age*species,SummaryInd)
 anova(mod)
@@
 ```{r, echo=FALSE,message=FALSE}
-plot(total_leaf_weight~total_weight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
+plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
 legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")
 
-plot(total_leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
+plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
 legend("bottomright",col=col.spp, labels.spp, pch=16, cex=.8, bty="n")
@@
 ```{r, echo=FALSE,message=FALSE}
-plot((change_shoot_diam/100) ~ change_basal_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.spp[as.factor(species)], pch=16)
+plot((growth_shoot_diam/100) ~ growth_stem_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.spp[as.factor(species)], pch=16)
 abline(0,1)
 
-mod <- lm (change_shoot_diam ~ change_basal_diam*age,data=subset(SummaryInd, age>1.4))
+mod <- lm (growth_shoot_diam ~ growth_stem_diam*age,data=subset(SummaryInd, age>1.4))
 summary(mod)
@@
 
-plot((change_shoot_diam/100) ~ change_basal_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.age2[as.factor(age)], pch=16)
+plot((growth_shoot_diam/100) ~ growth_stem_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.age2[as.factor(age)], pch=16)
 abline(0,1)
@@
 
-plot((change_shoot_area/10000) ~ dia,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16,ylim=c(0.01,500),cex=.7)
-points((change_basal_area) ~ dia,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=1)
+plot((growth_shoot_area/10000) ~ diameter,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16,ylim=c(0.01,500),cex=.7)
+points((growth_stem_area) ~ diameter,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=1)
 
-plot((change_shoot_area/10000) ~ dia,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=16,ylim=c(0.01,500),cex=.7)
-points((change_basal_area) ~ dia,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=1)
+plot((growth_shoot_area/10000) ~ diameter,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=16,ylim=c(0.01,500),cex=.7)
+points((growth_stem_area) ~ diameter,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=1)
 
-yvar <- "change_shoot_diam"
-xvar <- "change_basal_diam"
+yvar <- "growth_shoot_diam"
+xvar <- "growth_stem_diam"
 

### 2015-05-21 results_leaf_lifespan.rmd
lots of standardizing names also recalculated accessory costs on a per seed basis and added figures

@@
 
-#PropH vs LL_death
+#prop_maxH vs LL_death
 - Have just plotted overall data, because no relationships across or within species; only GRSP has significant negative relationship and BOLE has significant positive relationship
 ```{r, echo=FALSE,message=FALSE}
-plot((LL_death~PropH), data=subset(SummaryInd,LL_death<10), col=col.spp[as.factor(species)],pch=16)
+plot((LL_death~prop_maxH), data=subset(SummaryInd,LL_death<10), col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot((PropH~log(age)), data=subset(SummaryInd), col=col.spp[as.factor(species)],pch=16)
+plot((prop_maxH~log(age)), data=subset(SummaryInd), col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

### 2015-05-21 scripts/summary_dataframes.R

@@ -18,16 +18,18 @@ axis_labels <- read_csv("data/axis_labels.csv")
 
 investment <- ReproductionAllocation_all
 
+names(investment) <-  c("individual","ReproInv","species","site","age","height","diameter","stem_area","leaf_weight","stem_weight","total_weight","GrowthInv","growth_stem","growth_leaf","growth_stem_diam","growth_stem_area","TotalInv","RA")
+
 investment$age <- round(investment$age, digits=1)
 
 accessory <- AccessoryCosts_all
-names(accessory) <- c("individual","species","age","prepollen_aborted","prepollen_success","postpollen_aborted","packaging_dispersal","propagules","total_repro_inv")
+names(accessory) <- c("individual","species","age","prepollen_aborted_inv","prepollen_success_inv","postpollen_aborted_inv","packaging_dispersal_inv","propagule_inv","total_repro_inv")
 #accessory$age2 <- accessory$age
 #accessory$age <- round(accessory$age, digits=1)
 
 #accessory$PerAccessory <- {
 #  select(accessory, Total >0,
-#  1 - (accessory$Prop/accessory$Total)
+#  1 - (accessory$propagule_inv/accessory$Total)
 #}
 
 #accessory$PerPropagule = 1 - accessory$PerAccessory
@@ -89,22 +91,23 @@ leafLifespan$LL_birth[which(is.infinite(leafLifespan$LL_death))] <- NA
 
 #calculating percentages of various accessory tissues
 
-accessory$prop_prepollen_aborted <- accessory$prepollen_aborted / accessory$total_repro_inv
-accessory$prop_prepollen_success <- accessory$prepollen_success / accessory$total_repro_inv
-accessory$prop_postpollen_aborted <- accessory$postpollen_aborted / accessory$total_repro_inv
-accessory$prop_packaging_dispersal <- accessory$packaging_dispersal / accessory$total_repro_inv
-accessory$prop_propagules <- accessory$propagules / accessory$total_repro_inv
-accessory$prop_accessory <- 1- accessory$prop_propagules
+accessory$accessory_inv <- accessory$total_repro_inv - accessory$propagule_inv
[…]

### 2015-05-22 results_accessory_shorter.Rmd
fixing up errors

@@
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mod <- lm(log(RA)~species*age*log((ReproInv)),data=subset(SummaryInd,RA>0))
+anova(mod)
 
@@
 
+###Plots across species, with accessory costs on a per seed produced basis
+```{r, echo=FALSE, message=FALSE}
+mean1 <- SummarySpp$prepollen_all_per_seed_mean
+se1 <- SummarySpp$prepollen_all_per_seed_se
+plot(mean1~species,data=subset(SummarySpp),cex.axis=.8,pch=16,main="Investment into pre-pollination tissues per seed produced",log="y")
+se_function(mean1,se1)
+```{r, echo=FALSE, message=FALSE}
+
+```{r, echo=FALSE, message=FALSE}
+mean1 <- SummarySpp$accessory_per_seed_mean
+se1 <- SummarySpp$accessory_per_seed_se
+plot(mean1~species,data=subset(SummarySpp),cex.axis=.8,pch=16,main="Investment into all accessory tissues per seed produced",log="y")
+se_function(mean1,se1)
+```{r, echo=FALSE, message=FALSE}
+
+```{r, echo=FALSE, message=FALSE}
+mean1 <- SummarySpp$packaging_dispersal_per_seed_mean
+se1 <- SummarySpp$packaging_dispersal_per_seed_se
+plot((mean1)~species,data=subset(SummarySpp),cex.axis=.8,pch=16,main="Investment into packaging and dispersal tissues per seed produced")
+se_function(mean1,se1)
+```{r, echo=FALSE, message=FALSE}
 #Shifts in accessory costs across species and ages

### 2015-05-22 results_growth.Rmd
fixing up errors

@@
 ```{r, echo=FALSE, message=FALSE}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.6,0.2))
 plot((total_weight~prop_maxH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
@@
 - There is a positive correlation with the maximum height the species reaches at a given age -i.e. fast growing young plants are tall when young.  
-```{r, echo=FALSE,message=FALSE}
-plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age<3),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.1,xlab="maximum height (mm)",ylab="growth investment (mg per year)",xlim=c(500,3200),main="Relationship between growth rates on maximum H")
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1,bty="n")
-text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==2.4), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
+plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==1.4))
+words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.1,xlab="maximum height (mm)",ylab="growth investment (mg per year)",xlim=c(500,3200),main="Relationship between growth rates on maximum H")
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1,bty="n")
-text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==2.4))
+words.bottom.right.logxy(mod)
+
+plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age>3))
+words.bottom.right.logxy(mod)
+legend("topleft",col=col.age,labels.age,pch=16, bty="n")
+
+mtext("maximum H",1,outer=TRUE)
+mtext("yearly growth (mg)",2,outer=TRUE)
 ```
@@
 - However there is no relationship in younger plants  
-```{r, echo=FALSE,message=FALSE}
-plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="wood density",ylab="growth investment (mg per year)",xlim=c(0.57,0.9),main="Relationship between wood density and growth rates")
-text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
-legend("bottomleft",col=col.age, labels.age, pch=16, cex=1, bty="n")
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
+plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
+words.top.right.logxy(mod)
 
-plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age<3),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="wood density",ylab="growth investment (mg per year)",xlim=c(0.57,0.9),main="Relationship between wood density and growth rates")
-text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
-legend("bottomleft",col=col.age, labels.age, pch=16, cex=1, bty="n")
+plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
+words.bottom.right.logxy(mod)
+legend("topright",col=col.age,labels.age,pch=16, bty="n")
+
+plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age>3))
+words.top.right.logxy(mod)
+
+mtext("wood density",1,outer=TRUE)
+mtext("yearly growth (mg)",2,outer=TRUE)
+```
+
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
+plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
+words.bottom.right.logxy(mod)
+
+plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
+words.bottom.right.logxy(mod)
+legend("topright",col=col.age,labels.age,pch=16, bty="n")
+
+plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age>3))
+words.bottom.right.logxy(mod)
+
+mtext("wood density",1,outer=TRUE)
+mtext("yearly growth (mg)",2,outer=TRUE)
+```
+
+* Leaf area
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
+plot(GrowthInv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
+text(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4))
+words.bottom.right.logxy(mod)
+
+plot(GrowthInv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings",ylim=c(100,100000))
+text(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==2.4))
+words.bottom.right.logxy(mod)
+
+plot(GrowthInv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
+text(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age>3))
+words.bottom.right.logxy(mod)
+legend("topleft",col=col.age,labels.age,pch=16, bty="n")
+
+mtext("leaf area",1,outer=TRUE)
+mtext("yearly growth (mg)",2,outer=TRUE)
 ```
@@
 - This is not predicted by Daniel's model or Anais' review; re-run with RGR
-```{r, echo=FALSE,message=FALSE}
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Seedlings")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
 mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4))
-summary(mod)
+words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="pink",pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Saplings")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
 mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4))
-summary(mod)
+words.bottom.right.logxy(mod)
+legend("topright",col=col.age,labels.age,pch=16, bty="n")
 
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Adults")
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
 text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-legend("bottomright",col=col.age,labels.age,pch=16, bty="n")
 mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3))
-summary(mod)
+words.bottom.right.logxy(mod)
+
+mtext("LMA",1,outer=TRUE)
+mtext("yearly growth (mg)",2,outer=TRUE)
 ```
@@
 - There are no significant relationships at any age when RGR is used instead of actual growth investment 
-```{r, echo=FALSE,message=FALSE}
-plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="RGR=",main="Seedlings")
-text(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
+plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
 mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4))
-summary(mod)
+words.bottom.right.logxy(mod)
 
-plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="pink",pch=16,cex=1.2,xlab="LMA",ylab="RGR",main="Saplings")
-text(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
 mod <- lm(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4))
-summary(mod)
+words.bottom.right.logxy(mod)
+legend("topright",col=col.age,labels.age,pch=16, bty="n")
 
-plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="RGR",main="Adults")
+plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
 text(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-legend("bottomright",col=col.age,labels.age,pch=16, bty="n")
 mod <- lm(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age>3))
-summary(mod)
+words.bottom.right.logxy(mod)
+
+mtext("LMA",1,outer=TRUE)
+mtext("RGR",2,outer=TRUE)
 ```

### 2015-05-22 scripts/summary_dataframes.R

@@ -127,7 +127,7 @@ names(BAER_parts) <- c("species","what","count","weight")
 BOLE_parts <- as.data.frame(BOLE_PartsSummary[4])
 names(BOLE_parts) <- c("species","what","count","weight")
 COER_parts <- as.data.frame(COER_PartsSummary[4])
-names(EPMI_parts) <- c("species","what","count","weight")
+names(COER_parts) <- c("species","what","count","weight")
 EPMI_parts <- as.data.frame(EPMI_PartsSummary[4])
 names(EPMI_parts) <- c("species","what","count","weight")
 GRBU_parts <- as.data.frame(GRBU_PartsSummary[4])
@@ -288,6 +288,7 @@ SummarySppAge <- merge(SummarySppAge, maxRA, by=c("species","age"))
 SummarySppAge <- merge(SummarySppAge, investment_summary, by=c("species","age"))
 SummarySppAge <- merge(SummarySppAge, accessory_summary, by=c("species","age"))
 SummarySppAge <- merge(SummarySppAge, accessory_summary2, by=c("species","age"),all=TRUE)
+SummarySppAge$leaf_area_mean <- SummarySppAge$leaf_weight_mean / SummarySppAge$LMA_mean
 #SummarySppAge <- merge(SummarySppAge, harvest_summary, by=c("species","age"))
 
 #merge various data summaries into SummarySpp dataframe
@@ -484,7 +485,7 @@ for(v in c("seedset")) {
 count_spp <- SummaryInd %>%
   filter(ReproInv>0) %>%
   group_by(species) %>%
-  summarise_each(funs(mean, se, length), seedset,seed_count,flower_count,fruit_weight)
+  summarise_each(funs(mean, se, length), seedset,seed_count,flower_count,fruit_weight,leaf_area)
 
 per_seed <- SummaryInd %>%
   filter(seed_count>0) %>%

### 2015-05-26 results_accessory_shorter.Rmd
lots of work on growth data today, bit of continued cleaning on accessory costs

--- 2015-05-21 results_accessory_shorter.Rmd
@@
 ```{r, echo=FALSE,message=FALSE,,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(2,0.3,.5,0.3), mai=c(.5,1,.5,0.3))
+par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
 mod <- lm (log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
@@
 mod <- lm (log(total_weight)~log(seedset), data=subset(SummaryInd,seedset>0))
-plot(seedset~total_weight,data=subset(SummaryInd,prop_propagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="seedset",xlim=c(100,2000000),xlab="Total size (mg)")
+plot(seedset~total_weight,data=subset(SummaryInd,prop_propagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="seedset",xlim=c(100,2000000),xlab="")
 words.bottom.right.logxy(mod)
-mtext("Total size (mg)", 1, outer=TRUE)
+mtext("Total size (mg)", 1, outer=TRUE,cex=1.2)
 ```
 
-###How do accessory costs shift with seed size?
+### How do accessory costs shift with seed size?
 - Larger-seeded species have higher accessory costs, as has been shown in other studies
@@
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))  
+par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3))
 mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean)),SummarySpp)
@@
 words.top.right(mod)
-mtext("Proportion accessory investment (asin transformed)",2, outer=TRUE)
+mtext("Proportion reproductive investment to accessory tissues (asin transformed)",2, outer=TRUE,cex=1.2)
 ```
-###Looking at investment vs. costs per successful seed
+
+* investment vs. costs per successful seed
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))  
+par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3)) 
 mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
@@
 words.top.right(mod)
-mtext("Accessory investment per successful seed (log scale)",2, outer=TRUE)
+mtext("Accessory tissue investment per successful seed (mg)",2, outer=TRUE,cex=1.2)
 ```
 
-###Plotting accessory costs that go into making a single seed - ignoring aborted tissues
+### Plotting accessory costs that go into making a single seed - ignoring aborted tissues
 * Bigger seeds have bigger fixed costs of making that seed (1st plot)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
-plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp[as.factor(species)])
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp[as.factor(species)],xlab="costs to make 1 seed (mg)",cex=1.2)
+mod <- lm(seedcosts~seed_size, SummarySpp)
+words.bottom.right.logxy(mod)
+text(seed_size~seedcosts,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")
 
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
-plot(seed_size~costs_per_seed,data=subset(SummarySpp),log="y",pch=16,col=col.spp[as.factor(species)])
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(seed_size~costs_per_seed,data=subset(SummarySpp),log="y",pch=16,col=col.spp[as.factor(species)],ylab="",xlab="proportional accessory costs, scaled by seed weight",cex=1.2)
+text(seed_size~costs_per_seed,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")
+mod <- lm(costs_per_seed~seed_size, SummarySpp)
+words.bottom.left.logy(mod)
 ```
@@
 * This is the complement to the plot of accessory costs  
-```{r, echo=FALSE,message=FALSE}
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(log(seedset)~(prop_accessory),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_accessory~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="x", pch=16,col=col.spp[as.factor(species)],xlab="seed set")
-words.bottom.right.logx(mod)
+* Replotting the same data by age, shows that the pattern is not age-driven
+* At most, there are most "old" plants with very low seedset 
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.3,0.3), mai=c(0.8,1,0.3,0.3))  
+mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="proportion reproduction to propagules (1-accessory)")
+words.bottom.right.logxy(mod)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="proportion reproduction to propagules (1-accessory)",xlab="")
+words.bottom.right.logxy(mod)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+mtext("Seed set",1, outer=TRUE,cex=1.1)
+```
+
+*Comparing proportion energy to propagules vs accessory cost per seed
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.3,0.3), mai=c(0.8,1,0.3,0.3))  
+mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="proportion reproduction to propagules (1-accessory)")
+words.bottom.right.logxy(mod)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm(log(seedset)~log(accessory_per_seed),data=subset(SummaryInd,seedset>0&seedset<1&accessory_per_seed>0))
-plot(accessory_per_seed~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="seed set")
-words.bottom.right.logxy(mod)
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-```
-
-* Replotting the same data by age, shows that the pattern is not age-driven
-* At most, there are most "old" plants with very low seedset  
-```{r, echo=FALSE,message=FALSE}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(asin(sqrt(seedset))~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="Accessory costs (asin transformed)",xlab="seed set")
-words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+plot(accessory_per_seed~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="accessory costs per seed produced (mg)")
+words.bottom.left.logxy(mod)
+mtext("Seed set",1, outer=TRUE,cex=1.1)
 ```
@@
 ```{r, echo=FALSE,message=FALSE, ,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(asin(sqrt(prop_prepollen_all))~log((ReproInv)),data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1))
-plot(asin(sqrt(prop_prepollen_all))~ReproInv,data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1), log="x", pch=16,col=col.spp[as.factor(species)])
+par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
+mod <- lm(log(ReproInv)~(prop_prepollen_all),data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1))
+plot((prop_prepollen_all)~ReproInv,data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1), log="x", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Pre-pollination tissues (as proportion repro inv)")
 words.top.right.logx(mod)
@@
 
-mod <- lm(asin(sqrt(prop_propagule))~log((ReproInv)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(prop_propagule))~ReproInv,data=subset(SummaryInd,prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)])
-words.top.right.logx(mod)
+mod <- lm(log(ReproInv)~log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
+plot(prop_propagule~ReproInv,data=subset(SummaryInd,prop_propagule>0), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Propagules (as proportion repro inv)")
+words.top.right.logxy(mod)
+mtext("Reproductive investment (mg)",1, outer=TRUE,cex=1.1)
 ```
@@
 * Overall RA is correlated with reproductive investment and age
+* These plots only include individuals that have some reproductive investment
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
+par(mfrow=c(1,2), cex=1, omi=c(0.3,0.3,0.1,0.3), mai=c(1.1,1,0.3,0.3)) 
 mod <- lm(log(RA)~log((ReproInv)),data=subset(SummaryInd,RA>0))
@@
 
+mod <- lm(log(RA)~species*age*log((ReproInv)),data=subset(SummaryInd,RA>0))
+anova(mod)
+
 mod <- lm(log(RA)~log((age)),data=subset(SummaryInd,RA>0))
-plot(RA~(age),data=subset(SummaryInd,RA>0), pch=16,col=col.spp[as.factor(species)],log="xy")
+plot(RA~(age),data=subset(SummaryInd,RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="")
 words.bottom.right.logxy(mod)
@@
 * This is true for many individual species as well as across species
-```{r, echo=FALSE,message=FALSE}
+* RA and seed count are also correlated, but mainly that no low RA individuals have high seed counts
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
 mod <- lm(log(RA)~log(repro_all_count),data=subset(SummaryInd,repro_all_count>0))
-plot(repro_all_count~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp[as.factor(species)],pch=16,log="xy")
+plot(repro_all_count~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp[as.factor(species)],pch=16,log="xy",ylab="# of buds produced",xlab="")
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
+
+mod <- lm(log(RA)~log(seed_count+.1),data=subset(SummaryInd,repro_all_count>0))
+plot((.1+seed_count)~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp[as.factor(species)],pch=16,log="xy",ylab="# of seeds produced",xlab="")
+words.bottom.right.logxy(mod)
+mtext("RA",1, outer=TRUE,cex=1.1)
 
@@
 
-* This same pattern is true just looking  at pre-pollination tissues and at propagule allocation
+* This same pattern is true just looking  at energy invested in pre-pollination tissues and at propagule allocation
 * Plants that invest more in some reproductive tissues, on average, invest more in other reproductive tissues, so have a higher RA
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
+
+* Looking at proportions, the pattern is much less informative
+* Plants with higher RA have lower allocation to pre-pollination tissues, probably because of their higher seedset
+* Relationship between RA and proportion energy to propagules simply shows a species effect - different species have different RA values and different proportional propagule investment
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
 mod <- lm(log(RA)~log((prepollen_all_inv)),data=subset(SummaryInd,RA>0&prepollen_all_inv>0))
@@
 words.bottom.right.logxy(mod)
+
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-```
 
-* Looking at proportions, the pattern is much less informative
-* Plants with higher RA have lower allocation to pre-pollination tissues, probably because of their higher seedset
-* Total accessory costs and RA and rather unrelated - the plot shows a significant increase in accessory costs as RA increases, but this is mostly driven by BOLE
-
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
 mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_prepollen_all)),data=subset(SummaryInd,RA>0&prop_prepollen_all>0))
-plot(asin(sqrt(prop_prepollen_all))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&prop_prepollen_all>0), pch=16,col=col.spp[as.factor(species)])
+plot(asin(sqrt(prop_prepollen_all))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&prop_prepollen_all>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination tissues (as proportion repro inv) (asin)")
 words.top.right(mod)
 
-mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,RA>0))
-plot(asin(sqrt(prop_propagule))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&prop_propagule>0), pch=16,col=col.spp[as.factor(species)])
-words.top.right(mod)
+mod <- lm(log(RA)~log((prop_propagule)),data=subset(SummaryInd,RA>0&prop_propagule>0))
+plot((prop_propagule)~(RA),data=subset(SummaryInd,RA>0&prop_propagule>0), log="xy", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+words.bottom.left.logxy(mod)
 ```
@@
 ###Shifts across age
-* Seedset shows a slight decrease with proportional plant height (the best proxy for "relative size"), but certainly no trend of increased seed set in older plants. 
+* Seedset shows a slight decrease with proportional plant height (the best proxy for "relative size")  
+* this pattern likely exists because species that begin reproducing at shorter proportional heights have higher seedset  
+* only LEES shows a significant decline with age, although most species have a segative slope  
 * there is a similar pattern for Propagule investment (not shown)  
-* a greater number of individuals become reproductively mature, but among reproducing individuals there is no shift in seedset or proportional propagule investment with age
-* same pattern using "age" as xvar
-
-*Results, by species, for seedset by proportional height
+* Table shows results, by species, for seedset by proportional height  
 ```{r, echo=FALSE,message=FALSE}
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(asin(sqrt(prop_maxH))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset<1&seedset>0))
+mod <- lm((prop_maxH)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset<1&seedset>0))
 plot(asin(sqrt(seedset))~prop_maxH,data=subset(SummaryInd,seedset<1&seedset>0), pch=16,col=col.spp[as.factor(species)])
@@
 
-*Results, by species, for seedset by age
+* Results, by species, for seedset by age  
+* Only HEPU, LEES show significant decline, but again mostly negative slopes
 ```{r, echo=FALSE,message=FALSE}
@@
 - Reasonably idiosyncratic patterns
-- Propagule allocation across species  
 - COER, EPMI, LEES, PILI invest the most energy in propagules  
 - HATE invests by far the least into propagules  
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=28}
+par(mfrow=c(4,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  
 mean1 <- SummarySpp$prop_propagule_mean
 se1 <- SummarySpp$prop_propagule_se
-plot(mean1~species,SummarySpp,cex.axis=.7,pch=16,log="y",ylim=c(.002,.25),main="Percent reproductive investment put into propagules")
+plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylim=c(.002,.25),ylab="propagules",xlab="")
 se_function(mean1,se1)
-```
 
-- pre-pollination allocation across species  
-```{r, echo=FALSE, message=FALSE}
+mean1 <- SummarySpp$propagule_per_seed_mean
+se1 <- SummarySpp$propagule_per_seed_se
+plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
+se_function(mean1,se1)
+
 mean1 <- SummarySpp$prop_prepollen_all_mean
 se1 <- SummarySpp$prop_prepollen_all_se
-plot(mean1~species,data=subset(SummarySpp),cex.axis=.8,pch=16,ylim=c(.1,1),main="Percent reproductive investment put into pre-pollination tissues")
+plot(mean1~species,data=subset(SummarySpp),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
 se_function(mean1,se1)
+
+mean1 <- SummarySpp$prepollen_all_per_seed_mean
+se1 <- SummarySpp$prepollen_all_per_seed_se
+plot((.01+prepollen_all_per_seed_mean)~species,data=subset(SummarySpp),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
+se_function(mean1,se1)
+
+mean1 <- SummarySpp$prop_packaging_dispersal_mean
+se1 <- SummarySpp$prop_packaging_dispersal_se
+plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
+se_function(mean1,se1)
+
+mean1 <- SummarySpp$packaging_dispersal_per_seed_mean
+se1 <- SummarySpp$packaging_dispersal_per_seed_se
+plot((packaging_dispersal_per_seed_mean+.1)~species,SummarySpp,cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
+se_function(mean1,se1)
+
+mean1 <- SummarySpp$prop_postpollen_aborted_mean
+se1 <- SummarySpp$prop_postpollen_aborted_se
+plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="aborted post-pollination tissues")
+se_function(mean1,se1)
+
+mean1 <- SummarySpp$postpollen_aborted_per_seed_mean
+se1 <- SummarySpp$postpollen_aborted_per_seed_se
+plot((postpollen_aborted_per_seed_mean+.1)~species,SummarySpp,cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")
+se_function(mean1,se1)
+
+mtext("proportion of reproductive investment                                                                       mg investment per seed",3,outer=TRUE,cex=1.1)
+mtext("species",1, outer=TRUE,cex=1.1)
 ```
@@
 - just looking among plants >3 years old  
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2)) 
 tmp <- SummaryInd %>%
@@
     tmp,
-     cex.axis=.7,pch=16,log="y",ylim=c(.1,1),
-     main="Percent reproductive investment put into pre-pollination tissues")
+     cex.axis=.5,pch=16,log="y",ylim=c(.02,1),
+     ylab="Prop reproductive investment put into pre-pollination tissues")
 
@@
 se_function(mean1,se1)
-```
 
-- Packaging and dispersal allocation across species  
-```{r, echo=FALSE, message=FALSE}
-mean1 <- SummarySpp$prop_packaging_dispersal_mean
-se1 <- SummarySpp$prop_packaging_dispersal_se
-
-plot(mean1~species,SummarySpp,cex.axis=.8,pch=16,log="y",ylim=c(.02,1),main="Percent reproductive investment put into packaging and dispersal")
-se_function(mean1,se1)
-```
-
-- just looking among plants >3 years old  
-```{r, echo=FALSE, message=FALSE}
 tmp2 <- SummaryInd %>%
@@
     tmp2,
-     cex.axis=.7,pch=16,log="y",ylim=c(0.02,.8),
-     main="Percent reproductive investment put into packaging & dispersal tissues")
+     cex.axis=.5,pch=16,log="y",ylim=c(0.08,.8),
+     ylab="Prop reproductive investment put into packaging & dispersal tissues")
 

### 2015-05-26 results_growth.Rmd
lots of work on growth data today, bit of continued cleaning on accessory costs

@@
 This has no effect on within species analyses, but lets data from all species to be plotted together
-
-```{r, echo=FALSE, message=FALSE}
+```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.6,0.2))
@@
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```
 
+```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=35}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
 yvar <- "total_weight"
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",
-                    main=spp, xlab=xvar, ylab=yvar)
+                    main=spp, xlab="", ylab="")
   abline(lmfits[[spp]])
 }
+
+mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
+mtext("Total weight", 2, outer=TRUE,cex=1.2)
 ```
@@
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(.1,0.3,.5,0.2), mai=c(1.1,1,.1,0.2))
-plot((GrowthInv~prop_maxH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16)
+par(mfrow=c(1,2), cex=1, omi=c(.8,0.3,.5,0.2), mai=c(.7,1,.1,0.2))
+plot((GrowthInv~prop_maxH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16,xlab="")
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(GrowthInv~prop_maxH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16)
+plot(GrowthInv~prop_maxH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16,ylab="",xlab="")
 legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
+```
 
+### Growth investment by Proportion Hmax
+```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=35}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
 yvar <- "GrowthInv"
 xvar <- "prop_maxH"
-
 data <- SummaryInd
 data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
 
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
 for(spp in names(data)) {
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
-                    main=spp, xlab=xvar, ylab=yvar)
+                    main=spp, xlab="",ylab="")
+}
 
-  abline(lmfits[[spp]])
-}
-```
-
-###Proportion max H by RGR
-- Ignoring a few outliers, RGR declines with increasing height is 12 species  
-- Only in HEPU and PILI is there no significant trend  
-- The species with a poorer correlation are mostly shorter ones that are presumably often broken off   
-- These are continued ways to look at the question of how important is height (relative to the species maxH) in understanding its growth and reproduction
-
-```{r, echo=FALSE, message=FALSE}
-yvar <- "RGR"
-xvar <- "prop_maxH"
+mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
+mtext("Growth investment", 2, outer=TRUE,cex=1.2)
 
@@
 
-###Growth Investment versus weight   
-- showing that slope continues to be 1:1, but intercept decreases with time because more standing biomass
-```{r, echo=FALSE, message=FALSE}
-plot((GrowthInv~total_weight), SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-abline(0,1,lwd=2)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+### RGR by proportion Hmax
+- Ignoring a few outliers, RGR declines with increasing height is 12 species  
+- Only in HEPU and PILI is there no significant trend  
+- The species with a poorer correlation are mostly shorter ones that are presumably often broken off   
+- These are continued ways to look at the question of how important is height (relative to the species maxH) in understanding its growth and reproduction
 
-plot(GrowthInv~total_weight, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16)
-abline(0,1,lwd=2)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
+plot(RGR~prop_maxH,SummaryInd,col=col.spp[as.factor(species)],pch=16)
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```
+
+```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=35}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.7,.5,0.2)) 
+yvar <- "RGR"
+xvar <- "prop_maxH"
+data <- SummaryInd
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
+                    main=spp, xlab="",ylab="")
+}
+
+mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
+mtext("RGR", 2, outer=TRUE,cex=1.2)
+
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
 ```
@@
 ###Correlations between different growth measures
-- Increased cross-sectional area of a leader and the entire plant are fairly correlated and uneffected by age (once not baby)
-
+- Increased cross-sectional area of a leader and the entire plant are fairly correlated and uneffected by age (once not seedlings)  
+- however, some species, such as BAER are much branciers and lower correlation
 TO DO: species should be a random effect for these stats- I want to know the effect of age on the relationship once the effect of species has been accounted for
 
-```{r, echo=FALSE,message=FALSE}
-plot(growth_shoot_area~growth_stem_area,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1,bty="n")
-mod <- lm(growth_shoot_area~growth_stem_area*age*species,SummaryInd)
+```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
+plot(growth_shoot_area~growth_stem_area,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
+legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=1,bty="n")
+
+mod <- lm(growth_shoot_area~species*age*growth_stem_area,SummaryInd)
 anova(mod)
@@
 
-```{r, echo=FALSE,message=FALSE}
+```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
 plot(lvs_end_total~age,SummaryInd,log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
-legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1,bty="n")
+legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=1,bty="n")
 
@@
 results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="x",
-                    main=spp, xlab=xvar, ylab=yvar)
-
-  abline(lmfits[[spp]])
-}
 ```
@@
 
-```{r, echo=FALSE,message=FALSE}
-plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.age[as.factor(age)], pch=16, cex=0.8)
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")
-
+```{r, echo=FALSE,message=FALSE,, fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
 plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
-legend("bottomright",col=col.spp, labels.spp, pch=16, cex=.8, bty="n")
+legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=.8, bty="n")
 ```
@@
 - The decrease in leaf number along a shoot is largely caused by declining shoot extension, not shifts in leaf lifespan  
-- BAER, BOLE, EPMI, GRBU, GRSP, HATE, HEPU, PHPH, PILI, and PUTU all show significant declines in shoot extension with age  
 - For many of these species, the shift is between the "sapling" and "adult" stages - i.e. when they begin reproducing  
-- PELA stands out by showing increasing shoot extension with age - because it grows so slowly in the beginning
+- PELA, PEPU stands out by showing increasing shoot extension with age - because it grows so slowly in the beginning; regression for these two species becomes highly significant when seedlings are included
+- this decline in shoot extension only appears when plotted against age, not prop maxH- not sure why this would be
 
-```{r, echo=FALSE,message=FALSE}
-plot(new_length~age,SummaryInd,log="xy", xlab="age",ylab="shoot extension (mm)",col=col.spp[as.factor(species)])
-legend(12,200,col=col.spp, labels.spp, pch=16, cex=.8,bty="n")
+```{r, echo=FALSE,message=FALSE,, fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
+mod <- lm(prop_maxH~new_length,data=subset(SummaryInd,age>2))
+plot(new_length~prop_maxH,data=subset(SummaryInd,age>2),log="y", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
+legend(12,200,col=col.spp, legend=names(labels.spp), pch=16, cex=.8,bty="n")
+words.bottom.right.logy(mod)
+
+mod <- lm(age~species*new_length,data=subset(SummaryInd,age>2))
+plot(new_length~age,data=subset(SummaryInd,age>2),log="xy", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
+words.bottom.right.logxy(mod)
+anova(mod)
 
@@
 
-data <- subset(SummaryInd)
+data <- subset(SummaryInd, age>2)
 data <- split(data, data$species)
@@
 results
+```
+
+```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=35}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.7,.5,0.2)) 
+yvar <- "new_length"
+xvar <- "age"
+data <- subset(SummaryInd, age>2)
+data <- split(data, data$species)
 
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="x",
-                    main=spp, xlab=xvar, ylab=yvar)
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
+                    main=spp, xlab="",ylab="")
+}
 
-  abline(lmfits[[spp]])
-}
+mtext("age", 1, outer=TRUE,cex=1.2)
+mtext("shoot extension (mm)", 2, outer=TRUE,cex=1.2)
 ```
+
 ###Diameter increase in shoots vs. whole plant
@@
 ```{r, echo=FALSE,message=FALSE}
-plot((growth_shoot_diam/100) ~ growth_stem_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.spp[as.factor(species)], pch=16)
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
+mod <- lm (growth_shoot_area ~ growth_stem_area*species*age,data=subset(SummaryInd, age>1.4))
+plot((growth_shoot_area/10000) ~ growth_stem_area,data=subset(SummaryInd, age>1.4), log="xy",col=col.age2[as.factor(age)], pch=16)
 abline(0,1)
+words.bottom.right.logxy(mod)
+legend("topleft",col=col.age, labels.age, pch=16, cex=1, bty="n")
+anova(mod)
+```
 
-mod <- lm (growth_shoot_diam ~ growth_stem_diam*age,data=subset(SummaryInd, age>1.4))
-summary(mod)
-anova(mod)
-
-plot((growth_shoot_diam/100) ~ growth_stem_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.age2[as.factor(age)], pch=16)
-abline(0,1)
-legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")
-
-plot((growth_shoot_area/10000) ~ diameter,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16,ylim=c(0.01,500),cex=.7)
-points((growth_stem_area) ~ diameter,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=1)
-
-plot((growth_shoot_area/10000) ~ diameter,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=16,ylim=c(0.01,500),cex=.7)
-points((growth_stem_area) ~ diameter,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=1)
-
-yvar <- "growth_shoot_diam"
-xvar <- "growth_stem_diam"
+* For all species except BAER and HATE, growth in shoot (leader) area and basal stem area well correlated  
+* there two species obviously much-branched, and the number of growing shoots probably matters more than what the leader is doing
+```{r, echo=FALSE,message=FALSE}
+yvar <- "growth_shoot_area"
+xvar <- "growth_stem_area"
 
@@
 results
+```
+
+* results by species  
+* trying to color points by age, but can't get it to work correctly with loop. age stored as data$spp$age, but can't figure out syntax to call this within col  
+```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=35}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.5,0.2)) 
+yvar <- "growth_shoot_area"
+xvar <- "growth_stem_area"
+
+data <- subset(SummaryInd,age>2)
+data <- split(data, data$species)
 
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="xy", col=col.age[as.factor(SummaryInd$age)],
-                    main=spp, xlab=xvar, ylab=yvar)
-  legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="xy",
+                    main=spp, xlab="", ylab="")
   }
+
+legend("topleft",col=col.age2, labels.age2, pch=16, cex=1, bty="n")
+mtext("growth in basal stem area", 1, outer=TRUE,cex=1.2)
+mtext("growth in leader stem area", 2, outer=TRUE,cex=1.2)
 ```
 
-#Comparing growth rates of species with different trait values
+### Leaf area versus plant size and height
+```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
+plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.age[as.factor(age)], pch=16)
+mod <- lm(log(total_weight)~log(leaf_area), SummaryInd)
+words.bottom.right.logxy(mod)
+
+plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.age[as.factor(age)], pch=16)
+
+plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.spp[as.factor(species)], pch=16)
+words.bottom.right.logxy(mod)
+
+plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.spp[as.factor(species)], pch=16)
+```
+
+### Leaf weight versus plant size and height
+* One of the things I find most interesting here is how different clusters of species follow different trajectories (4th graph)  
+* BAER, HATE, PELA, and PEPU have similar curves to one another; then comes a band with GRBU and GRSP, followed by all other species except PILI  
+* oldest plants (&PILI) fall below the main line of points  
+```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
+plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.age[as.factor(age)], pch=16)
+mod <- lm(log(total_weight)~log(leaf_weight), SummaryInd)
+words.bottom.right.logxy(mod)
+
+plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.age[as.factor(age)], pch=16)
+
+plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.spp[as.factor(species)], pch=16)
+words.bottom.right.logxy(mod)
+
+plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.spp[as.factor(species)], pch=16)
+```
+
+###changes in leaf growth and area over time
+* different species have different leaf area/growth to stem weight - in particular, the "canopy species" have higher leaf area relative to their stem weight
+* all species show declines in leaf weight vs. stem weight as they age, but this is a much smaller effect than the across species effect
+```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
+mod <- lm(leaf_area ~stem_weight*species*age, SummaryInd)
+anova(mod)
+
+par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
+plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.age[as.factor(age)], pch=16,ylim=c(-1,4))
+abline(0,0)
+abline(0,1)
+legend("topleft",col=col.age, labels.age, pch=16, cex=1, bty="n")
+
+plot((leaf_area)~(stem_weight), SummaryInd,col=col.age[as.factor(age)], pch=16,log="xy")
+abline(0,1)
+text(1000,1800,srt=39,labels="1:1 line")
+
+plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.spp[as.factor(species)], pch=16,ylim=c(-1,4),xlab="")
+abline(0,0)
+abline(0,1)
+legend("topleft",col=col.spp, legend=names(labels.spp), pch=16, cex=.9, bty="n")
+
+plot((leaf_area)~(stem_weight), SummaryInd,col=col.spp[as.factor(species)], pch=16,log="xy",xlab="")
+abline(0,1)
+text(1000,1800,srt=39,labels="1:1 line")
+words.bottom.right.logxy(mod)
+```
+
+##Comparing growth rates of species with different trait values
+* same as for Anais review, looking at growth rates against maxH, leaf area, wood density, LMA, leaf lifespan, and seedsize
+* splitting plants into seedlings (1 yr), saplings (2 yr), and adults (3+ yrs)  
+* RGR never "adds" to the analyses - which suggests "seedlings" are already past being "seedlings"  
+* I do have half year diameters for youngest plants
 
@@
 - The same basic relationship exists across all ages, so combined all data here  
-```{r, echo=FALSE,message=FALSE}
+```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
 plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
@@
 mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
-words.top.right.logxy(mod)
+words.bottom.left.logxy(mod)
 
@@
 mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
-words.bottom.right.logxy(mod)
+words.bottom.left.logxy(mod)
 legend("topright",col=col.age,labels.age,pch=16, bty="n")
@@
 mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age>3))
-words.top.right.logxy(mod)
+words.bottom.left.logxy(mod)
 
@@
 
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
+* same wood density data plotted against RGR instead - also no pattern with young
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
 plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
@@
 
-plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age>3))
-words.bottom.right.logxy(mod)
-
 mtext("wood density",1,outer=TRUE)
-mtext("yearly growth (mg)",2,outer=TRUE)
+mtext("RGR",2,outer=TRUE)
 ```
 
-* Leaf area
+### Leaf area vs growth investment
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
@@
 - But there is no relationship in seedlings (age=1.4) or saplings (age=2.4)  
-- This is not predicted by Daniel's model or Anais' review; re-run with RGR
+- This is not predicted by Daniel's model or Anais' review; re-runing with RGR yields same results
+- But relationship in adults disappears when HATE is removed...
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
@@
 
-mtext("LMA",1,outer=TRUE)
-mtext("yearly growth (mg)",2,outer=TRUE)
-```
-
-###Looking at LMA relative to RGR
-- There are no significant relationships at any age when RGR is used instead of actual growth investment 
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4))
-words.bottom.right.logxy(mod)
-
-plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4))
-words.bottom.right.logxy(mod)
-legend("topright",col=col.age,labels.age,pch=16, bty="n")
-
-plot(RGR_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(RGR_mean ~ LMA_mean, data=subset(SummarySppAge,age>3))
+plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3&species!="HATE"),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3&species!="HATE"), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3&species!="HATE"))
 words.bottom.right.logxy(mod)
@@
 mtext("LMA",1,outer=TRUE)
-mtext("RGR",2,outer=TRUE)
+mtext("yearly growth (mg)",2,outer=TRUE)
 ```
@@
 - And just barely a significant relationship between RGR and leaflifespan for adult plants
-```{r, echo=FALSE,message=FALSE}
-plot(GrowthInv ~ LL_death,data=subset(SummaryInd,age==1.4),log="xy",col=col.spp[as.factor(species)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="growth investment (mg per year)",main="Seedlings")
-legend(4.5,1600,col=col.spp,labels.spp,pch=16, bty="n",cex=.8)
-mod <- lm(GrowthInv ~ LL_death, data=subset(SummaryInd,age==1.4))
-summary(mod)
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2))
+plot(GrowthInv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(log(LL_death_mean)~log(GrowthInv_mean), data=subset(SummarySppAge,age==1.4))
+words.bottom.right.logxy(mod)
 
-plot(GrowthInv ~ LL_death,data=subset(SummaryInd,age==2.4),log="xy",col=col.spp[as.factor(species)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="growth investment (mg per year)",main="Saplings")
-legend("bottomright",col=col.spp,labels.spp,pch=16, bty="n",cex=.8)
-mod <- lm(GrowthInv ~ LL_death, data=subset(SummaryInd,age==2.4))
-summary(mod)
+plot(GrowthInv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==2.4))
+words.bottom.right.logxy(mod)
 
-plot(GrowthInv ~ LL_death,data=subset(SummaryInd,age>3&LL_death<10),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="growth investment (mg per year)",main="Adults")
-legend("bottomright",col=col.age,labels.age,pch=16, bty="n")
-mod <- lm(GrowthInv ~ LL_death*species, data=subset(SummaryInd,age>3))
-anova(mod)
+plot(GrowthInv_mean ~ LL_death_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3))
+legend("topright",col=col.age,labels.age,pch=16, bty="n")
+words.bottom.right.logxy(mod)
+
+mtext("leaf lifespan",1,outer=TRUE)
+mtext("yearly growth (mg)",2,outer=TRUE)
 ```
-
-```{r, echo=FALSE,message=FALSE}
-plot(RGR ~ LL_death,data=subset(SummaryInd,age==1.4),log="xy",col=col.spp[as.factor(species)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="RGR",main="Seedlings")
-legend(4.5,1600,col=col.spp,labels.spp,pch=16, bty="n",cex=.8)
-mod <- lm(RGR ~ LL_death, data=subset(SummaryInd,age==1.4))
-summary(mod)
-
-plot(RGR ~ LL_death,data=subset(SummaryInd,age==2.4),log="xy",col=col.spp[as.factor(species)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="RGR",main="Saplings")
-legend("bottomright",col=col.spp,labels.spp,pch=16, bty="n",cex=.8)
-mod <- lm(RGR ~ LL_death, data=subset(SummaryInd,age==2.4))
-summary(mod)
-
-plot(RGR ~ LL_death,data=subset(SummaryInd,age>3&LL_death<10&RGR>0.04),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="leaf lifespan",ylab="RGR",main="Adults")
-legend("bottomright",col=col.age,labels.age,pch=16, bty="n")
-mod <- lm(RGR ~ LL_death*species, data=subset(SummaryInd,age>3&LL_death<10&RGR>0.04))
-anova(mod)
-```

### 2015-05-27 results_RAschedules_shorter.Rmd
looking more at growth variables learning about PCA in R

@@
 ```
+
+###Plotting RA species means against various traits
+* species with higher wood density have higher RA
+* taller species have lower RA
+* species with higher LMA have lower RA
+* no relationship between RA and seed size
+* these are mean RA values across all plants, including babies and other non-reproducing individuals
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
+plot(RA_mean~WD_mean,data=subset(SummarySpp,RA_mean>0), col=col.spp[as.factor(species)],pch=16,log="y",ylab="")
+mod <- lm(WD_mean~asin(sqrt(RA_mean)),SummarySpp)
+words.bottom.left.logy(mod)
+plot(RA_mean~seed_size, SummarySpp, col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+mod <- lm(log(seed_size)~asin(sqrt(RA_mean)), SummarySpp)
+words.bottom.left.logxy(mod)
+legend(.05,.28,col=col.spp, legend=names(labels.spp), pch=16, cex=.8,bty="n")
+plot(RA_mean~LMA_mean, SummarySpp, col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+mod <- lm(log(LMA_mean)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
+words.top.right.logxy(mod)
+plot(RA_mean~maxH_spp, SummarySpp, col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+mod <- lm(log(maxH_spp)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
+words.bottom.left.logxy(mod)
+mtext("RA",2,outer=TRUE)
+```
+
+*just plotting mean RA of mature plants is similar, although BAER throws off many plots - surprised by how high its RA is, and wondering if something is wrong with these #s
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
+plot(maxH_spp~WD_mean,data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="y",ylab="")
+mod <- lm(mature_RA_mean~asin(sqrt(mature_RA_mean)),data=subset(SummarySpp,species!="BAER"))
+words.bottom.left.logy(mod)
+plot(mature_RA_mean~seed_size, data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+mod <- lm(log(seed_size)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
+words.bottom.left.logxy(mod)
+legend(.05,.28,col=col.spp, legend=names(labels.spp), pch=16, cex=.8,bty="n")
+plot(mature_RA_mean~LMA_mean, data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+mod <- lm(log(LMA_mean)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
+words.top.right.logxy(mod)
+plot(mature_RA_mean~maxH_spp, data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+mod <- lm(log(maxH_spp)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
+words.bottom.left.logxy(mod)
+mtext("RA (mature plants only)",2,outer=TRUE)
+```
+
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+mod <- lm(log(growth_stem_diam) ~ age*WD_mean*LMA_mean*maxH_spp*RA, SummaryInd)
+anova(mod)
+
+spp_zero_RA <- SummaryInd %>%
+  filter(RA==0) %>%
+  group_by(species) %>%
+  summarise_each(funs(length),RA)
+spp_zero_RA$RAcex <- (((spp_zero_RA$RA)/20))
+
+sppage_zero_RA <- SummaryInd %>%
+  filter(RA==0) %>%
+  group_by(species,age) %>%
+  summarise_each(funs(length),RA)
+sppage_zero_RA$RAcex <- (((sppage_zero_RA$RA)/10))
+
+par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1,1,.6,0.2))
+plot(RA~WD_mean,data=subset(SummaryInd,RA>0), col=col.spp[as.factor(species)],pch=16,log="y",ylim=c(.0008,1))
+points((RA+.001)~WD_mean,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=spp_zero_RA$RAcex)
+mod <- lm(WD_mean~asin(sqrt(RA)),SummaryInd)
+words.bottom.left.logy(mod)
+plot(RA~seed_size, SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy",ylim=c(.0008,1))
+points((RA+.001)~seed_size,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=spp_zero_RA$RAcex)
+mod <- lm(log(seed_size)~asin(sqrt(RA)), SummaryInd)
+words.bottom.left.logxy(mod)
+plot(RA~LMA_mean, SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy",ylim=c(.0008,1))
+points((RA+.001)~LMA_mean,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=sppage_zero_RA$RAcex)
+mod <- lm(log(LMA_mean)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
+words.top.right.logxy(mod)
+plot(RA~maxH_spp, SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy",ylim=c(.0008,1))
+points((RA+.001)~maxH_spp,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=spp_zero_RA$RAcex)
+mod <- lm(log(maxH_spp)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
+words.bottom.left.logxy(mod)
+```

### 2015-05-27 results_growth.Rmd
looking more at growth variables learning about PCA in R

@@
 ```
+
+###Traits correlated
+- species maxH and wood density are highly correlated
+- the two species lying a bit outside are PUTU and PHPH which both often have multiple stems from the base - the second chart omits them
+-
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+plot(WD_mean~maxH_spp,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(maxH_spp)~WD_mean,SummaryInd)
+words.bottom.left.logx(mod)
+
+plot(WD_mean~maxH_spp,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"), log="x",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(maxH_spp)~WD_mean,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"))
+words.bottom.left.logx(mod)
+
+plot(seedset_mean~total_weight_mean,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(total_weight_mean) ~ (seedset_mean),SummarySpp)
+words.bottom.left.logx(mod)
+
+plot(seedset_mean~maxH_spp,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(maxH_spp) ~ (seedset_mean),SummarySpp)
+words.bottom.left.logx(mod)

### 2015-05-27 scripts/summary_dataframes.R

@@ -9,7 +9,8 @@ wood <- filter(woodDensity_raw, use=="use") %>%
 seedsize <- seedSize_raw %>%
   select(species,seed_size)
 
-individuals <- IndividualsList
+individuals <- IndividualsList %>%
+  select(individual,species, age, mature)
 
 axis_labels <- read_csv("data/axis_labels.csv")
 
@@ -113,6 +114,7 @@ accessory$prop_accessory[which(is.nan(accessory$prop_accessory))] <- NA
 #adding investment and accessory costs data to leafLifespan dataframe to create a dataframe with all individual level data
 SummaryInd <- merge(investment, select(leafLifespan, -species, -age), by="individual",all.x=TRUE)
 SummaryInd <- merge(SummaryInd, select(accessory, -species, -age), by="individual",all.x=TRUE)
+SummaryInd <- merge(SummaryInd, select(individuals, -species, -age), by="individual",all.x=TRUE)
 #SummaryInd <- merge(SummaryInd, select(harvest, -species, -age), by="individual",all.x=TRUE)
 
 #adding variables to look at change across years, RGR
@@ -210,6 +212,15 @@ investment_summary <- investment %>%
   group_by(species, age) %>%
   summarise_each(funs(mean, se, length), height, GrowthInv, ReproInv, total_weight, TotalInv, RA, diameter, stem_area, leaf_weight, stem_weight, growth_stem_diam, growth_stem_area, growth_leaf, growth_stem)
 
+investment_spp_age <- investment_summary %>%
+  select(species, age, height_mean,RA_mean)
+  
+mature_RA <- SummaryInd %>%
+  filter(mature==TRUE) %>%
+  group_by(species) %>%
+  summarise_each(funs(mean, se, length), RA, ReproInv)
+names(mature_RA) <- c("species","mature_RA_mean" ,"ReproInv_mean","mature_RA_se","ReproInv_se","mature_RA_length","ReproInv_length")
+
 #harvest summary by species, age
 #harvest_summary <- harvest %>%
  # group_by(species, age) %>%
@@ -249,7 +260,7 @@ names(LMA_spp)<-c("species", "LMA_mean","LMA_se","LMA_length")
 #investment summary by species
 investment_spp <- investment %>%
     group_by(species) %>%
[…]

### 2015-05-27 results_growth.Rmd
working through PCA analyses

@@
 
+###PCA analysis
+* This combination of variables shows that RGR is approximately opposite a collection of variables that indicate a plant is "bigger" - so smaller plants have higher RGR
+* Orthoganal to these in WD vs.
+maxH, LMA_mean, seed_size, and shoot_growth - taller plants have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their actual size
+* fine tuning above; no accessory proportions, because then have to use subset of reproducing individuals - see below
+* remove RGR leaf (similar to RGR)
+* remove prop_max_weight and prop_max_repro (similar to prop_maxH)
+
+```{r, echo=FALSE,message=FALSE,fig.width=10, fig.height=10}
+par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+SummaryIndPCA <- SummaryInd %>%
+  filter(lvs_end_total>0) %>%
+  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
+         RGR,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
+         RA,seedset,repro_all_count,accessory_inv,propagule_inv)
+
+SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
+SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
+SummaryIndPCA$height <- log(SummaryIndPCA$height)
+SummaryIndPCA$maxH_spp <- log(SummaryIndPCA$maxH_spp)
+SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
+SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
+SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
+SummaryIndPCA$growth_shoot_area <- log(SummaryIndPCA$growth_shoot_area)
+SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
+SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
+SummaryIndPCA$lvs_end_total <- log(SummaryIndPCA$lvs_end_total)
+SummaryIndPCA$growth_stem_area <- log(SummaryIndPCA$growth_stem_area)
+
+PCA_mod <- prcomp(SummaryIndPCA, scale=TRUE)
+summary(PCA_mod)
+biplot(PCA_mod,xlim=c(-.1,.15),ylim=c(-.1,.1),cex=.8)
+
+PCA_loadings <- as.data.frame(PCA_mod$rotation)
+PCA_loadings$variables <- row.names(PCA_loadings)
+
+PCA_scaling <- as.data.frame(PCA_mod$scale)
+PCA_scaling$variables <- row.names(PCA_scaling)
+names(PCA_scaling) <- c("scale","variables")
+PCA_loadings <- merge(PCA_loadings,PCA_scaling,by="variables")
+PCA_loadings$PC1 <- PCA_loadings$PC1*PCA_loadings$scale
+PCA_loadings$PC2 <- PCA_loadings$PC2*PCA_loadings$scale
+PCA_loadings$PC3 <- PCA_loadings$PC3*PCA_loadings$scale
+
+PCA_rotated <- as.data.frame(PCA_mod$x)
+PCA_rotated$individual <- subset(SummaryInd$individual, SummaryInd$lvs_end_total>0)
+SummaryInd_PCA_results <- merge(SummaryInd,PCA_rotated, by="individual", all.x=TRUE)
+
+plot(PC1~PC2,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+text(PC1~PC2,PCA_loadings,labels=variables, pos=2, offset=0, cex=0.9,col="black")
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```
+PCA_mod$rotation
+plot(PCA_mod)
+pairs(SummaryIndPCA,log="xy")
+
+looking at reproducing individuals - changes patterns quite a bit, with variables like maxH_spp pulling toward all the "big size" arrows
+SummaryIndPCA <- SummaryInd %>%
+  filter(lvs_end_total>0&accessory_inv>0) %>%
+  select(prop_maxH,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
+         RGR,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
+         RA,seedset,repro_all_count,accessory_inv,prop_accessory)
+
+###PCA analyses indicate a few clusters of variables
+* one is between RGR vs RA, maxH and various other measures of reproductive investment
+* the model shows that indeed RA and maxH explain most of the variation in RGR once species accounted for
+* and total plant weight is not significant - whether put before or after "repro_all_count"
+* patterns quite different when species removed and other traits that vary by species included
+
+```{r, echo=FALSE,message=FALSE}
+mod <- lm(RGR~species*asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1),SummaryInd)
+anova(mod)
+glance(mod)[1]
+
+mod <- lm(RGR~asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1)+WD_mean+LMA_mean+maxH_spp,SummaryInd)
+anova(mod)
+glance(mod)[1]
+```
+
+* another of the interesting pattern is that the increase in shoot area of leaders is correlated with maxH and seed_size (and opposite WD_mean) and somewhat offset from whole plant growth measures and whole plant size measures
+* seed_size removed, because no additional explanatory power after WD and maxH_spp included
+
+```{r, echo=FALSE,message=FALSE}
+mod <- lm(log(growth_shoot_area)~log(maxH_spp)*WD_mean*log(growth_stem_area)*log(total_weight)*RGR*asin(sqrt(RA))*LMA_mean,SummaryInd)
+anova(mod)
+glance(mod)
+```
+
+plot(mod)
 ###Traits correlated

### 2015-05-27 PCA_results.R

@@ -1,35 +1,40 @@
+
+* This combination of variables shows that RGR is approximately opposite a collection of variables that indicate a plant is "bigger" - so smaller plants have higher RGR
+* Orthoganal to these in WD vs. maxH, LMA_mean, seed_size, and shoot_growth - taller plants have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their actual size
+* fine tuning above; no accessory proportions, because then have to use subset of reproducing individuals - see below
+* remove RGR leaf (similar to RGR)
+* remove prop_max_weight and prop_max_repro (similar to prop_maxH)
+
 par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
 SummaryIndPCA <- SummaryInd %>%
   filter(lvs_end_total>0) %>%
-  select(height,maxH_spp,WD_mean,LMA_mean,seedset,seed_size,growth_leaf,propagule_inv,prepollen_all_inv,RGR,leaf_area, seed_count,costs_per_seed,growth_shoot_area,growth_stem_area,lvs_end_total)
+  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
+         RGR,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
+         RA,seedset,repro_all_count,accessory_inv,propagule_inv)
 
-SummaryIndPCA <- SummaryInd %>%
-  select(seedset,RA,growth_leaf,propagule_inv,prepollen_all_inv,RGR,leaf_area, seed_count,costs_per_seed,growth_shoot_area,growth_stem_area,ReproInv,lvs_end_total)
+SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
+SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
+SummaryIndPCA$height <- log(SummaryIndPCA$height)
+SummaryIndPCA$maxH_spp <- log(SummaryIndPCA$maxH_spp)
+SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
+SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
[…]

### 2015-05-28 results_growth.Rmd
PCA analyses completed - show quite interesting and consistent patterns (in results_growth)

--- 2015-05-27 results_growth.Rmd
@@
 
+###PCA analysis
+* This combination of variables shows that RGR is approximately opposite a collection of variables that indicate a plant is "bigger" - so smaller plants have higher RGR
+* Orthoganal to these in WD vs.
+maxH, LMA_mean, seed_size, and shoot_growth - taller plants have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their actual size
+* fine tuning above; no accessory proportions, because then have to use subset of reproducing individuals - see below
+* remove RGR leaf (similar to RGR)
+* remove prop_max_weight and prop_max_repro (similar to prop_maxH)
+
+```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+SummaryIndPCA <- SummaryInd %>%
+  filter(lvs_end_total>0&shoot_leaf_area>0&shoot_leaf_area_growth!=0) %>%
+  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
+         RGR,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
+         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth)
+
+SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
+SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
+SummaryIndPCA$height <- log(SummaryIndPCA$height)
+SummaryIndPCA$maxH_spp <- log(SummaryIndPCA$maxH_spp)
+SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
+SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
+SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
+SummaryIndPCA$growth_shoot_area <- log(SummaryIndPCA$growth_shoot_area)
+SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
+SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
+SummaryIndPCA$lvs_end_total <- log(SummaryIndPCA$lvs_end_total)
+SummaryIndPCA$growth_stem_area <- log(SummaryIndPCA$growth_stem_area)
+SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
+SummaryIndPCA$shoot_leaf_area_growth <- log(SummaryIndPCA$shoot_leaf_area_growth)
+
+PCA_mod <- prcomp(SummaryIndPCA, scale=TRUE)
+summary(PCA_mod)
+biplot(PCA_mod,xlim=c(-.1,.15),ylim=c(-.1,.1),cex=.8)
+
+PCA_loadings <- as.data.frame(PCA_mod$rotation)
+PCA_loadings$variables <- row.names(PCA_loadings)
+
+PCA_scaling <- as.data.frame(PCA_mod$scale)
+PCA_scaling$variables <- row.names(PCA_scaling)
+names(PCA_scaling) <- c("scale","variables")
+PCA_loadings <- merge(PCA_loadings,PCA_scaling,by="variables")
+
+PCA_lambda <- as.data.frame(PCA_mod$sdev)
+
+PCA_scores <- as.data.frame(PCA_mod$x)
+PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$lvs_end_total>0&SummaryInd$shoot_leaf_area_growth!=0)
+SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)
+
+n <- NROW(PCA_scores)
+scale =1
+
+PCA_lambda <- PCA_lambda*sqrt(n)
+PCA_lambda <- PCA_lambda^scale
+
+SummaryInd_PCA_results$PC1_scale <- SummaryInd_PCA_results$PC1/PCA_lambda[1]
+SummaryInd_PCA_results$PC2_scale <- SummaryInd_PCA_results$PC2/PCA_lambda[2]
+SummaryInd_PCA_results$PC3_scale <- SummaryInd_PCA_results$PC3/PCA_lambda[3]
+SummaryInd_PCA_results$PC4_scale <- SummaryInd_PCA_results$PC4/PCA_lambda[4]
+PCA_loadings$PC1_scale <- PCA_loadings$PC1 / 4.5
+PCA_loadings$PC2_scale <- PCA_loadings$PC2 / 4.5
+PCA_loadings$PC3_scale <- PCA_loadings$PC3 / 4.5
+PCA_loadings$PC4_scale <- PCA_loadings$PC4 / 4.5
+```
+
+#Looking at PCA by species
+* Main axis are across species affects (PC1) and within species shifts in RGR vs RA (PC2)
+* PC1 is WD vs a whole collection of traits that equate with "big plants" including measures of size, height, and growth increment
+* For PC2, interesting that "growth_shoot_area"" and other variables associated with shoot growth and species max H correlate somewhat with RGR, but "growth_stem_area" and other whole plant "size" variables do not
+* PC3 primarily separates LMA and maxH from WD; high wood density is also somewhat associated with higher RGR and various shoot growth and leafiness measures, reflecting that younger individuals have more shoot growth and higher RGR
+* PC4 is effectively leaf count on shoots ("lvs_end_total") vs.
+seed size, shoot leaf area and shoot leaf area growth - to first order, some plants have lots of small leaves and others have fewer leaves but greater leaf area, Not sure how seed size fits in
+* amazing that RA and RGR almost completely orthoganal to PC1 and PC4; they are really a set of variables that are little correlated with an inter-specific traits or measures of plant size
+* these plots are another way of affirming that RA (and RGR) is a variable that does a good job of comparing trends across species * in other words there is a trade-off between RA and RGR in all species.
+And even though the RA trends are messy, individuals that are proportionally taller (prop_maxH) or invest more in reproduction (investment, count, or seedset) have a higher RA.
+* this last set of variables are all ones that do not vary with the PC1 axis
+
+PCA related code to keep:  
+* plot(PCA_mod)
+* pairs(SummaryIndPCA,log="xy")
+* yy <- t(t(PCA_loadings[,2:3])*PCA_lambda[1:2])
+* xx <- t(t(SummaryInd_PCA_results[,105:106])/PCA_lambda[1:2])
+* biplot(xx,yy)
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+
+PCA_by_species <- SummaryInd_PCA_results %>%
+  filter(lvs_end_total>0) %>%
+  group_by(species) %>%
+  summarise_each(funs(mean, se), PC1_scale, PC2_scale, PC3_scale, PC4_scale)
+
+plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mean1 <- PCA_by_species$PC1_scale_mean
+se1 <- PCA_by_species$PC1_scale_se
+plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 1")
+se_function(mean1,se1)
+
+plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+
+mean1 <- PCA_by_species$PC2_scale_mean
+se1 <- PCA_by_species$PC2_scale_se
+plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 2")
+se_function(mean1,se1)
+
+plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+
+mean1 <- PCA_by_species$PC3_scale_mean
+se1 <- PCA_by_species$PC3_scale_se
+plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 3")
+se_function(mean1,se1)
+
+plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.12))
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mean1 <- PCA_by_species$PC4_scale_mean
+se1 <- PCA_by_species$PC4_scale_se
+plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4")
+se_function(mean1,se1)
+```
+
+###Coloring data by age
+* this confirms that PC2 is an axis the changes primarly by age - it is the RGR vs reproduction shift
+* PC1 has a slight age component, but more about species - across species, plant size is mostly a species effect, but of course age also matters
+* PC3 & PC4 all about species
+
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+
+plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+
+plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)],ylim=c(-.15,.12))
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+
+plot(PC3_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
+arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC3_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+```
+
+### Looking only at reproducing individuals - 
+* can now add in "prop_propagule","prop_accessory", but not "accessory_per_seed"
+* changes patterns quite a bit
+* PC1 is still WD vs lots of growth variables, but now reproductive investment (propagule_inv and accessory_inv) associate with "big size" not high RA
+* PC2 is RA, seedset, and prop_propagule vs. RGR, shoot growth variables and prop_accessory; interesting, but not surprising that prop_propagule and prop_accessory pulled to opposite ends
+* PC3 is somewhat similar. It is also prop_accessory and prop_maxH vs seed set and prop_propagule, but it now separates out all teh shoot growth values
+* PC4 is now the axis that separates LMA_mean and maxH vs. WD_mean
+
+, with variables like maxH_spp pulling toward all the "big size" arrows
+
+```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+SummaryIndPCA <- SummaryInd %>%
+  filter(lvs_end_total>0&accessory_inv>0&shoot_leaf_area_growth!=0) %>%
+  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
+         RGR,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
+         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth,
+         prop_propagule, prop_accessory)
+
+SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
+SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
+SummaryIndPCA$height <- log(SummaryIndPCA$height)
+SummaryIndPCA$maxH_spp <- log(SummaryIndPCA$maxH_spp)
+SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
+SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
+SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
+SummaryIndPCA$growth_shoot_area <- log(SummaryIndPCA$growth_shoot_area)
+SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
+SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
+SummaryIndPCA$lvs_end_total <- log(SummaryIndPCA$lvs_end_total)
+SummaryIndPCA$growth_stem_area <- log(SummaryIndPCA$growth_stem_area)
+SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
+SummaryIndPCA$shoot_leaf_area_growth <- log(SummaryIndPCA$shoot_leaf_area_growth)
+
+PCA_mod <- prcomp(SummaryIndPCA, scale=TRUE)
+summary(PCA_mod)
+biplot(PCA_mod)
+
+PCA_loadings <- as.data.frame(PCA_mod$rotation)
+PCA_loadings$variables <- row.names(PCA_loadings)
+
+PCA_scaling <- as.data.frame(PCA_mod$scale)
+PCA_scaling$variables <- row.names(PCA_scaling)
+names(PCA_scaling) <- c("scale","variables")
+PCA_loadings <- merge(PCA_loadings,PCA_scaling,by="variables")
+
+PCA_lambda <- as.data.frame(PCA_mod$sdev)
+
+PCA_scores <- as.data.frame(PCA_mod$x)
+PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$lvs_end_total>0&SummaryInd$shoot_leaf_area_growth!=0&SummaryInd$accessory_inv>0)
+SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)
+
+n <- NROW(PCA_scores)
+scale =1
+
+PCA_lambda <- PCA_lambda*sqrt(n)
+PCA_lambda <- PCA_lambda^scale
+
+SummaryInd_PCA_results$PC1_scale <- SummaryInd_PCA_results$PC1/PCA_lambda[1]
+SummaryInd_PCA_results$PC2_scale <- SummaryInd_PCA_results$PC2/PCA_lambda[2]
+SummaryInd_PCA_results$PC3_scale <- SummaryInd_PCA_results$PC3/PCA_lambda[3]
+SummaryInd_PCA_results$PC4_scale <- SummaryInd_PCA_results$PC4/PCA_lambda[4]
+PCA_loadings$PC1_scale <- PCA_loadings$PC1 / 4.5
+PCA_loadings$PC2_scale <- PCA_loadings$PC2 / 4.5
+PCA_loadings$PC3_scale <- PCA_loadings$PC3 / 4.5
+PCA_loadings$PC4_scale <- PCA_loadings$PC4 / 4.5
+```
+
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+
+plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+
+plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.12))
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+
+plot(PC3_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC3_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+```
+
+comparing
+```{r, echo=FALSE,message=FALSE}
+mod <- lm(RGR~species+asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1),SummaryInd)
+anova(mod)
+glance(mod)[1]
+
+mod <- lm(RGR~asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1)+WD_mean+LMA_mean+maxH_spp,SummaryInd)
+anova(mod)
+glance(mod)[1]
+```
+
+* another of the interesting pattern is that the increase in shoot area of leaders is correlated with maxH and seed_size (and opposite WD_mean) and somewhat offset from whole plant growth measures and whole plant size measures
+* seed_size removed, because no additional explanatory power after WD and maxH_spp included
+
+```{r, echo=FALSE,message=FALSE}
+mod <- lm(log(growth_shoot_area)~log(maxH_spp)+WD_mean+log(growth_stem_area)+log(total_weight)+RGR+asin(sqrt(RA))+LMA_mean,SummaryInd)
+anova(mod)
+glance(mod)
+```
+
+plot(mod)
 ###Traits correlated

### 2015-06-25 results_RAschedules_shorter.Rmd
PCA analyses completed - show quite interesting and consistent patterns (in results_growth)
checking all the leaf weight, stem weight regression data to make sure it looks reasonable

@@
 ###RV curves, by age, weight and height
-```{r, echo=FALSE,message=FALSE, fig.width=21, fig.height=7}
+```{r, echo=FALSE,message=FALSE, warning=FALSE, fig.width=21, fig.height=7}
 yvar <- "ReproInv"
@@
 the change in slope of the relationship.
-```{r, echo=FALSE, message=FALSE, out.width=900, out.height=576}
+```{r, echo=FALSE, message=FALSE}
 yvar <- "GrowthInv"

### 2015-06-25 results_accessory_shorter.Rmd
checking all the leaf weight, stem weight regression data to make sure it looks reasonable

@@
 
-* investment vs. costs per successful seed
+### Investment vs. costs per successful seed
+- calculating accessory costs on a per seed basis stratify the data much more by species  
+- there are also within species shifts, those associated with shifting seedset with age/size, but the across species differences are very pronounced at a given size/age for "per seed" accessory costs, and much less so for "prop total reproductive investment" accessory costs
+- I suppose this is because the plants that have more seeds, also have higher seedset, so cross-species variation is accentuated.
+
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
@@
 mtext("Accessory tissue investment per successful seed (mg)",2, outer=TRUE,cex=1.2)
+```
+
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3)) 
+mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="seed size (mg)",cex=1.3)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(total_weight)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(accessory_per_seed~total_weight,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(seedset)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot((accessory_per_seed)~seedset,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",cex=1.3)
+words.top.right.logxy(mod)
+
+mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
+plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
+words.bottom.right.logxy(mod)
+mtext("Accessory tissue investment per successful seed (mg)",2, outer=TRUE,cex=1.2)
+```
+
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3)) 
+mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="seed size (mg)",cex=1.3)
+words.bottom.right.logx(mod)
+
+mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(asin(sqrt(prop_accessory))~total_weight,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
+words.bottom.right.logx(mod)
+
+mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",cex=1.3)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logx(mod)
+
+mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
+plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
+words.bottom.right(mod)
+mtext("Proportion reproductive investment to accessory tissues (asin transformed)",2, outer=TRUE,cex=1.2)
 ```

### 2015-06-25 diameter_weight_checking.R

@@ -1,0 +1,165 @@
+check <- BAER_HarvestData
+check <- BOLE_HarvestData
+check <- COER_HarvestData
+check <- EPMI_HarvestData
+check <- GRBU_HarvestData
+check <- GRSP_HarvestData
+check <- HATE_HarvestData
+check <- HEPU_HarvestData
+check <- LEES_HarvestData
+check <- PELA_HarvestData
+check <- PEPU_HarvestData
+check <- PHPH_HarvestData
+check <- PILI_HarvestData
+check <- PUTU_HarvestData
+
+plot(leaf_weight~stem_weight,data=subset(check), pch=16,log="xy",col="red")
+text(leaf_weight~stem_weight,data=subset(check),labels=individual,cex=.5,pos=2,offset=-1)
+mod <- lm(log(stem_weight)~log(leaf_weight),data=subset(check))
+words.bottom.right.logxy(mod)
+
+#age 10 break (e.g. slightly BAER, GRSP)
+plot(leaf_weight~stem_weight,data=subset(check,age<10), pch=16,log="xy",col="red")
+points(leaf_weight~stem_weight,data=subset(check,age>10), pch=16,log="xy",col="blue")
+text(leaf_weight~stem_weight,data=subset(check,age<10),labels=individual,cex=.5,pos=2,offset=-1)
+mod <- lm(log(stem_weight)~log(leaf_weight),data=subset(check,age<10))
+words.bottom.right.logxy(mod)
+
+#age 8 break (e.g. GRBU, COER, LEES)
+plot(leaf_weight~stem_weight,data=subset(check,age<8), pch=16,log="xy",col="red")
+points(leaf_weight~stem_weight,data=subset(check,age>8), pch=16,log="xy",col="blue")
+text(leaf_weight~stem_weight,data=subset(check,age<8),labels=individual,cex=.5,pos=2,offset=-1)
+mod <- lm(log(stem_weight)~log(leaf_weight),data=subset(check,age<8))
+words.bottom.right.logxy(mod)
+
+#age 6 break 
+plot(leaf_weight~stem_weight,data=subset(check,age<6), pch=16,log="xy",col="red")
+points(leaf_weight~stem_weight,data=subset(check,age>6), pch=16,log="xy",col="blue")
+text(leaf_weight~stem_weight,data=subset(check,age<6),labels=individual,cex=.5,pos=2,offset=-1)
[…]

### 2015-07-30 results_accessory_v3.Rmd
lots of small changes -currently growth=growth3, Lizzy's version trying to add in side branches -harvest now has renamed segments (with segment2 for old segment names) - streamlining lots of data thoughts

--- 2015-05-26 results_accessory_shorter.Rmd
@@
 
-##Still thinking about
+###Still thinking about
 1.
@@
 flowers (I do know aborted buds decrease)
-###Which measure of reproductive output best correlates with plant size or growth (growth plotted here)
-* Measuring total reproductive output has a much stronger correlation than any of the other measures
-* Note that each of these figures (and models) only includes individuals with non-zero reproductive investment
+
+##Which measure of reproductive output best correlates with plant size or growth (growth plotted here)
+* Measuring total reproductive output has a much stronger correlation than investment in fruit weight or propagules
+* To demonstrate the point that most investment is in prepollination tissues, the regression of total weight against prepollination investment is as good as total reproductive investment - one could just count buds + flowers!
+* Note that each of these figures (and models) only includes individuals with non-zero investment in the reproductive pool of interest
 
@@
 
-mod <- lm (log(total_weight)~log(seedset), data=subset(SummaryInd,seedset>0))
-plot(seedset~total_weight,data=subset(SummaryInd,prop_propagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="seedset",xlim=c(100,2000000),xlab="")
+mod <- lm (log(total_weight)~log(prepollen_all_inv), data=subset(SummaryInd,prepollen_all_inv>0))
+plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="prepollen investment (mg)", xlim=c(100,2000000))
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
-mtext("Total size (mg)", 1, outer=TRUE,cex=1.2)
 ```
 
-### How do accessory costs shift with seed size?
+##How do accessory costs shift with seed size?
 - Larger-seeded species have higher accessory costs, as has been shown in other studies
-- However, it is also true that "larger species" have higher accessory costs and than species with higher seed set have lower accessory costs
-- In contrast, there is a relatively low correlation between accessory costs and proportion reproductive energy invested in pre-pollination tissues DESPITE this being the biggest pool of energy for most species
+- However, it is also true that "larger species" and species with lower seed set have higher accessory costs
+- In contrast, there is no correlation between accessory costs and proportion reproductive energy invested in pre-pollination tissues DESPITE this being the biggest pool of energy for most species (looking at species means; if only individuals with some seed production as included, then higher pre-pollination investment = higher accessory costs)
 - Taken together these data (and various other plots, not shown) suggest that accessory costs (as a proportion) are most strongly driven by seedset
@@
 
+###First figures with y-axis "proportion reproductive investment to accessory costs"
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
@@
 mod <- lm(log(total_weight_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
+plot(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg) = species size",cex=1.3)
 words.bottom.right.logx(mod)
@@
 
-* investment vs. costs per successful seed
+### Investment vs. costs per successful seed
+- calculating accessory costs on a per seed basis stratify the data much more by species  
+- cross-species variation is accentuated in these plots (vs.
+those with proportional accessory costs), because the species that have more seeds (lower proportional accessory costs), also have higher seedset
+
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
@@
 mod <- lm(log(total_weight_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot(accessory_per_seed_mean~total_weight_mean,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
+plot(accessory_per_seed_mean~total_weight_mean,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg) = Species size",cex=1.3)
 words.bottom.right.logxy(mod)
@@
 mtext("Accessory tissue investment per successful seed (mg)",2, outer=TRUE,cex=1.2)
+```
+
+### Comparing "per successful seed" and "proportion reproductive investment" accessory cost calculations  
+* all individuals included here
+```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=6}
+par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(.7,1,0.3,0.3)) 
+mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=1.3)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=1.3)
+words.bottom.right.logx(mod)
+mtext("Seed size (mg)",1, outer=TRUE,cex=1.2)
+
+mod <- lm(log(total_weight)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(accessory_per_seed~total_weight,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=1.3)
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(asin(sqrt(prop_accessory))~total_weight,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=1.3)
+words.bottom.right.logx(mod)
+mtext("Total weight (mg)",1, outer=TRUE,cex=1.2)
+
+mod <- lm(log(seedset)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot((accessory_per_seed)~seedset,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=1.3)
+words.top.right.logxy(mod)
+
+mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",cex=1.3)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logx(mod)
+mtext("seedset",1, outer=TRUE,cex=1.2)
+
+mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
+plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=1.3)
+words.bottom.right.logxy(mod)
+
+mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
+plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=1.3)
+words.bottom.right(mod)
+
+mtext("pre-pollination costs (proportional)",1, outer=TRUE,cex=1.2)
 ```

### 2015-07-30 results_growth.Rmd
lots of small changes -currently growth=growth3, Lizzy's version trying to add in side branches -harvest now has renamed segments (with segment2 for old segment names) - streamlining lots of data thoughts

@@
 - proportion of maxH matters more for some species than others. 
-  1. The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  
-  2. The lower-growing species are more variable, with "prop maxH mattering more for some than others"
+    1. The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  (HATE, BAER, PELA, PEPU)
+    2.
+The lower-growing species are more variable, with "prop maxH"" mattering more for some than others - not surprising since some species like BOLE, PILI show inconsistent increases in H with increasing age, due to breakage, shedding
 
-- For almost all species there is a strong negative relationship between RGR and RA - indeed, more reproduction = less growth  
-  1. Meanwhile there is the strong positive relationship between growth investment and reproductive investment, because bigger plants grow and reproduce more.  
-  2. It is good to have a big enough data set to capture both trends - and to capture them consistently across many species
+- For almost all species there is a strong negative relationship between RGR and RA - more reproduction = less growth  
+    1. As expected, a cost of reproduction is reduced growth
+    2. Meanwhile there is the strong positive relationship between growth investment and reproductive investment, because bigger plants grow and reproduce more.  
+    3. It is good to have a big enough data set to capture both trends across a single dataset - and to capture them consistently across many species
 
@@
     1. e.g. see EPMI for distinct pattern
+    2. More robust curve-fitting techniques are required to better illustrate this pattern (**CURVE FITTING**)
 
-#Comparing growth between different measures and across age
+#Comparing different measures of growth and how these measures shift with age
 
 ###Weight vs. height
-- No surprises here , but need to fit proper lines to the data
+- No surprises here , but need to fit proper lines to the data (**CURVE FITTING**)
 - Plants asymptote in weight as they reach their maximum height. This is true for all species, although some species, like BOLE and GRBU, have a much messier scatter than others  
 - The follow on of course is to look at growth measures vs. height   
-- NOTE: All heights have been scaled 0-1 based on the maximum height of each species across all of the sites.
-This has no effect on within species analyses, but lets data from all species to be plotted together
+- NOTE: The variable "prop_maxH" is "current height/maximum species height (across all sites)", hence varying from 0-1. This lets data from all species to be plotted together  
 ```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
@@
 
-```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=35}
+```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=28}
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
@@
 ###Growth Investment versus proportion max H
-- This turns out to be one of the most interesting sets of graphs  
 - For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH
+- I think this suggests that relative height is a good predictor of growth investment in these species, but not in some of the lower-growing species
 - For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)  
@@
 ### Growth investment by Proportion Hmax
-```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=35}
+```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=21}
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
@@
 - Increased cross-sectional area of a leader and the entire plant are fairly correlated and uneffected by age (once not seedlings)  
-- however, some species, such as BAER are much branciers and lower correlation
+- however, some species, such as BAER are much branchier and lower correlation
 TO DO: species should be a random effect for these stats- I want to know the effect of age on the relationship once the effect of species has been accounted for
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(growth_shoot_area~growth_stem_area,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
+plot(growth_shoot_area~growth_stem_area,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
 legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=1,bty="n")
@@
 - The number of leaves along a leader is overall uneffected by age  
-- However, looking at individual species: BOLE, GRBU, GRSP, HEPU, PILI, PUTU have declining leaf counts along a shoot with age  
-- And PELA, PEPU show a significant increase in leaf counts along a single shoot with age
+- However, looking at individual species: BAER, BOLE, GRBU, GRSP, HEPU, PUTU have declining leaf counts along a shoot with age (omitting youngest cohort only)
+- And PELA, PEPU show a significant increase in leaf counts along a single shoot with age, probably because they have very few leaves when young and are slow to "start growing"
 
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(lvs_end_total~age,SummaryInd,log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
+plot(lvs_end_total~age,data=subset(SummaryInd,age>2),log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
 legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=1,bty="n")
@@
 
-data <- subset(SummaryInd)
+data <- subset(SummaryInd,age>2)
 data <- split(data, data$species)
@@
 ###Shifts in shoot extension with age
+- This is a weak effect - probably not worth pursuing
 - The decrease in leaf number along a shoot is largely caused by declining shoot extension, not shifts in leaf lifespan  
@@
 - PELA, PEPU stands out by showing increasing shoot extension with age - because it grows so slowly in the beginning; regression for these two species becomes highly significant when seedlings are included
-- this decline in shoot extension only appears when plotted against age, not prop maxH- not sure why this would be
+- this decline in shoot extension only appears when plotted against age, not prop maxH, emphasizing that it is not a very robust finding
+- I am surprised there isn't more of an effect, because the plants look so much less leafy when larger/older
 
@@
 * Orthoganal to these in WD vs.
-maxH, LMA_mean, seed_size, and shoot_growth - taller plants have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their actual size
-* fine tuning above; no accessory proportions, because then have to use subset of reproducing individuals - see below
-* remove RGR leaf (similar to RGR)
-* remove prop_max_weight and prop_max_repro (similar to prop_maxH)
+maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
+* this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals - see below - greatly reducing sample size
+* fine tuning:  
+  ** remove RGR leaf (similar to RGR)
+  ** remove prop_max_weight and prop_max_repro (similar to prop_maxH)
 
@@
 #Looking at PCA by species
-* Main axis are across species affects (PC1) and within species shifts in RGR vs RA (PC2)
-* PC1 is WD vs a whole collection of traits that equate with "big plants" including measures of size, height, and growth increment
+* Main axes are (1) across species affects in trait values (PC1) and (2) within species shifts in RGR vs RA with plant size/age (PC2)
+* PC1 is WD vs a whole collection of traits that have higher "values" in plants that are larger as adults, including measures of size, height, and growth increment; PELA is a rare exception in shifting along this axis.
+* PC2 most strongly separates RGR from RA (and a collection of strongly correlated traits, such as propagule investment, prop maxH). 
+* PC3 primarily separates LMA and maxH from WD; high wood density is also somewhat associated with higher RGR and various shoot growth and leafiness measures, reflecting that younger individuals have more shoot growth and higher RGR
+* PC4 is effectively leaf count on shoots ("lvs_end_total") and seed set vs.
+seed size, shoot leaf area and shoot leaf area growth - to first order, some plants have lots of small leaves and others have fewer leaves but greater leaf area, Not sure how seed size fits in
+
+* amazing that RA and RGR almost completely orthoganal to PC1 and PC4; To reiterate, RA and RGR are 2 variables that shift across each species' lifetime and much less across species.
+I suspect the inter-specific difference are effectively what proportion of individuals in this study are reproductively mature - with early maturing species having overall higher RA and lower RGR (i.e.
+BOLE) than do late maturing species (i.e.
+PELA).
+
+* Continuing, RGR and RA are measures that give little insight to a species trait values - or vice versa, trait values do not provide much information about RA...
+
+* "growth_stem_area" and "growth leaf", two whole plant measures of size increase are orthoganal to RGR, while some shoot-level variables (i.e.
+"growth_shoot_area") and other whole plant variables (e.g.
+"leaf_area_growth"), are somewhat correlated with both RGR (PC2) and the "maxH" direction (PC1).
+I suppose this suggests that for plants with high
+
 * For PC2, interesting that "growth_shoot_area"" and other variables associated with shoot growth and species max H correlate somewhat with RGR, but "growth_stem_area" and other whole plant "size" variables do not
-* PC3 primarily separates LMA and maxH from WD; high wood density is also somewhat associated with higher RGR and various shoot growth and leafiness measures, reflecting that younger individuals have more shoot growth and higher RGR
-* PC4 is effectively leaf count on shoots ("lvs_end_total") vs.
-seed size, shoot leaf area and shoot leaf area growth - to first order, some plants have lots of small leaves and others have fewer leaves but greater leaf area, Not sure how seed size fits in
-* amazing that RA and RGR almost completely orthoganal to PC1 and PC4; they are really a set of variables that are little correlated with an inter-specific traits or measures of plant size
 * these plots are another way of affirming that RA (and RGR) is a variable that does a good job of comparing trends across species * in other words there is a trade-off between RA and RGR in all species.
 And even though the RA trends are messy, individuals that are proportionally taller (prop_maxH) or invest more in reproduction (investment, count, or seedset) have a higher RA.
+
 * this last set of variables are all ones that do not vary with the PC1 axis
@@
 
-plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],xlim=c(-.1,.1))
 arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.12))
+plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.15))
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 se1 <- PCA_by_species$PC4_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4")
+plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",,ylim=c(-.07,.04))
 se_function(mean1,se1)
@@
 * changes patterns quite a bit
-* PC1 is still WD vs lots of growth variables, but now reproductive investment (propagule_inv and accessory_inv) associate with "big size" not high RA
-* PC2 is RA, seedset, and prop_propagule vs. RGR, shoot growth variables and prop_accessory; interesting, but not surprising that prop_propagule and prop_accessory pulled to opposite ends
-* PC3 is somewhat similar. It is also prop_accessory and prop_maxH vs seed set and prop_propagule, but it now separates out all teh shoot growth values
-* PC4 is now the axis that separates LMA_mean and maxH vs. WD_mean
-
-, with variables like maxH_spp pulling toward all the "big size" arrows
+* PC1 is still WD vs lots of growth variables, but now absolute measures of reproductive investment (propagule_inv and accessory_inv) associate with absolute "big size" not high RA
+* PC2 is RA, seedset, and prop_propagule vs. RGR, shoot growth variables and prop_accessory; not surprising that prop_propagule and prop_accessory pulled to opposite ends
+* PC3 is somewhat similar. It is also prop_accessory and prop_maxH vs seed set and prop_propagule, but it now separates out all the shoot growth values
+* PC4 is now the axis that separates LMA_mean and maxH vs. WD_mean, with variables like maxH_spp pulling toward all the "big size" arrows
 

### 2015-07-30 results_growth_short.Rmd
lots of small changes -currently growth=growth3, Lizzy's version trying to add in side branches -harvest now has renamed segments (with segment2 for old segment names) - streamlining lots of data thoughts

--- 2015-07-30 results_growth.Rmd
@@
 ```
-#Growth data, general patterns
-- proportion of maxH matters more for some species than others. 
-    1. The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  (HATE, BAER, PELA, PEPU)
-    2.
-The lower-growing species are more variable, with "prop maxH"" mattering more for some than others - not surprising since some species like BOLE, PILI show inconsistent increases in H with increasing age, due to breakage, shedding
+##Growth data, general patterns
+1. Growth-reproduction trade-off illustrated by plots of RA vs RGR
+    -  As expected, a cost of reproduction is reduced growth
+    -  Meanwhile there is the strong positive relationship between growth investment and reproductive investment, because bigger plants grow and reproduce more.  
+    -  It is good to have a big enough data set to capture both trends across a single dataset - and to capture them consistently across many species
 
-- For almost all species there is a strong negative relationship between RGR and RA - more reproduction = less growth  
-    1. As expected, a cost of reproduction is reduced growth
-    2. Meanwhile there is the strong positive relationship between growth investment and reproductive investment, because bigger plants grow and reproduce more.  
-    3. It is good to have a big enough data set to capture both trends across a single dataset - and to capture them consistently across many species
+2. Some species have more obvious asymptoting in growth with increasing relative H ("prop_maxH") than others
+    -  The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  (HATE, BAER, PELA, PEPU)
+    -  The lower-growing species are more variable, with "prop maxH"" mattering more for some than others - not surprising since some species like BOLE, PILI show inconsistent     increases in H with increasing age, due to breakage, shedding
 
-- Many plants have a clear upturn in RA and corresponding downturn in RGR at a specific prop maxH  
-    1. e.g. see EPMI for distinct pattern
-    2. More robust curve-fitting techniques are required to better illustrate this pattern (**CURVE FITTING**)
+##Growth-reproduction trade-off
+###Bigger plants reproduce more
+- There is a positive correlation between reproductive investment vs growth investment among individuals that are reproducing: plants that grow more also allocate more to reproduction.  
+- It is also true that bigger plants allocate more to reproduction.
 
-#Comparing different measures of growth and how these measures shift with age
-
-###Weight vs. height
-- No surprises here , but need to fit proper lines to the data (**CURVE FITTING**)
-- Plants asymptote in weight as they reach their maximum height. This is true for all species, although some species, like BOLE and GRBU, have a much messier scatter than others  
-- The follow on of course is to look at growth measures vs. height   
-- NOTE: The variable "prop_maxH" is "current height/maximum species height (across all sites)", hence varying from 0-1. This lets data from all species to be plotted together  
-```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.6,0.2))
-plot((total_weight~prop_maxH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-```
-
-```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=28}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "total_weight"
-xvar <- "prop_maxH"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",
-                    main=spp, xlab="", ylab="")
-  abline(lmfits[[spp]])
-}
-
-mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
-mtext("Total weight", 2, outer=TRUE,cex=1.2)
-```
-
-###Growth Investment versus proportion max H
-- For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH
-- I think this suggests that relative height is a good predictor of growth investment in these species, but not in some of the lower-growing species
-- For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)  
-- Quite interesting, there is a distinctly negative relationship for GRBU; its absolute growth investment actually declines as it increases in size  
-- For many of the species with a good relationship, it seems that there are two breakpoints in the curve - wondering what these mean with respect to reproductive onset and RA
-
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(.8,0.3,.5,0.2), mai=c(.7,1,.1,0.2))
-plot((GrowthInv~prop_maxH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16,xlab="")
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-plot(GrowthInv~prop_maxH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16,ylab="",xlab="")
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
-mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
-```
-
-### Growth investment by Proportion Hmax
-```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=21}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "GrowthInv"
-xvar <- "prop_maxH"
-data <- SummaryInd
-data <- split(data, data$species)
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
-                    main=spp, xlab="",ylab="")
-}
-
-mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
-mtext("Growth investment", 2, outer=TRUE,cex=1.2)
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-### RGR by proportion Hmax
-- Ignoring a few outliers, RGR declines with increasing height is 12 species  
-- Only in HEPU and PILI is there no significant trend  
-- The species with a poorer correlation are mostly shorter ones that are presumably often broken off   
-- These are continued ways to look at the question of how important is height (relative to the species maxH) in understanding its growth and reproduction
-
-```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(RGR~prop_maxH,SummaryInd,col=col.spp[as.factor(species)],pch=16)
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-```
-
-```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=35}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.7,.5,0.2)) 
-yvar <- "RGR"
-xvar <- "prop_maxH"
-data <- SummaryInd
-data <- split(data, data$species)
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
-                    main=spp, xlab="",ylab="")
-}
-
-mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
-mtext("RGR", 2, outer=TRUE,cex=1.2)
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-#Comparing growth of whole plant vs. leader
-
-###Correlations between different growth measures
-- Increased cross-sectional area of a leader and the entire plant are fairly correlated and uneffected by age (once not seedlings)  
-- however, some species, such as BAER are much branchier and lower correlation
-TO DO: species should be a random effect for these stats- I want to know the effect of age on the relationship once the effect of species has been accounted for
-
-```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(growth_shoot_area~growth_stem_area,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
-legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=1,bty="n")
-
-mod <- lm(growth_shoot_area~species*age*growth_stem_area,SummaryInd)
-anova(mod)
-```
-
-###Shifts in leafiness with age  
-- Individual shoots looked decidedly "less leafy" in many older plants  
-- This led me to wonder how leaf lifespan - or some other variable - was shifting with age   
-- The number of leaves along a leader is overall uneffected by age  
-- However, looking at individual species: BAER, BOLE, GRBU, GRSP, HEPU, PUTU have declining leaf counts along a shoot with age (omitting youngest cohort only)
-- And PELA, PEPU show a significant increase in leaf counts along a single shoot with age, probably because they have very few leaves when young and are slow to "start growing"
-
-```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(lvs_end_total~age,data=subset(SummaryInd,age>2),log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
-legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=1,bty="n")
-
-yvar <- "lvs_end_total"
-xvar <- "age"
-
-data <- subset(SummaryInd,age>2)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-###Leaf weight (relative to total weight) also declines with age  
-- These numbers are currently incomplete - waiting for full set of "leaf weight" numbers to finalize this
-
-```{r, echo=FALSE,message=FALSE,, fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
-legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=.8, bty="n")
-```
-
-###Shifts in shoot extension with age
-- This is a weak effect - probably not worth pursuing
-- The decrease in leaf number along a shoot is largely caused by declining shoot extension, not shifts in leaf lifespan  
-- For many of these species, the shift is between the "sapling" and "adult" stages - i.e. when they begin reproducing  
-- PELA, PEPU stands out by showing increasing shoot extension with age - because it grows so slowly in the beginning; regression for these two species becomes highly significant when seedlings are included
-- this decline in shoot extension only appears when plotted against age, not prop maxH, emphasizing that it is not a very robust finding
-- I am surprised there isn't more of an effect, because the plants look so much less leafy when larger/older
-
-```{r, echo=FALSE,message=FALSE,, fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-mod <- lm(prop_maxH~new_length,data=subset(SummaryInd,age>2))
-plot(new_length~prop_maxH,data=subset(SummaryInd,age>2),log="y", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
-legend(12,200,col=col.spp, legend=names(labels.spp), pch=16, cex=.8,bty="n")
-words.bottom.right.logy(mod)
-
-mod <- lm(age~species*new_length,data=subset(SummaryInd,age>2))
-plot(new_length~age,data=subset(SummaryInd,age>2),log="xy", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
-words.bottom.right.logxy(mod)
-anova(mod)
-
-yvar <- "new_length"
-xvar <- "age"
-
-data <- subset(SummaryInd, age>2)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=35}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.7,.5,0.2)) 
-yvar <- "new_length"
-xvar <- "age"
-data <- subset(SummaryInd, age>2)
-data <- split(data, data$species)
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
-                    main=spp, xlab="",ylab="")
-}
-
-mtext("age", 1, outer=TRUE,cex=1.2)
-mtext("shoot extension (mm)", 2, outer=TRUE,cex=1.2)
-```
-
-###Diameter increase in shoots vs. whole plant
-- The slope of the relationship lessens with age  
-- There is quite a bit of noise in the relationship  
-- However, in many cases, older plants show less of a change in shoot diameter for a given change in basal diameter; the opposite pattern as is predicted if ever fewer shoots are sustaining growth  
-- Instead, each shoot matters ever less to the overall increase in basal area in larger plants
-- NOTE: Plots not correct right now - wrong number of points in some and definitely wrong coloring by age
 ```{r, echo=FALSE,message=FALSE}
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-mod <- lm (growth_shoot_area ~ growth_stem_area*species*age,data=subset(SummaryInd, age>1.4))
-plot((growth_shoot_area/10000) ~ growth_stem_area,data=subset(SummaryInd, age>1.4), log="xy",col=col.age2[as.factor(age)], pch=16)
-abline(0,1)
-words.bottom.right.logxy(mod)
-legend("topleft",col=col.age, labels.age, pch=16, cex=1, bty="n")
-anova(mod)
-```
-
-* For all species except BAER and HATE, growth in shoot (leader) area and basal stem area well correlated  
-* there two species obviously much-branched, and the number of growing shoots probably matters more than what the leader is doing
-```{r, echo=FALSE,message=FALSE}
-yvar <- "growth_shoot_area"
-xvar <- "growth_stem_area"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-* results by species  
-* trying to color points by age, but can't get it to work correctly with loop. age stored as data$spp$age, but can't figure out syntax to call this within col  
-```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=35}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.5,0.2)) 
-yvar <- "growth_shoot_area"
-xvar <- "growth_stem_area"
-
-data <- subset(SummaryInd,age>2)
-data <- split(data, data$species)
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="xy",
-                    main=spp, xlab="", ylab="")
-  }
-
-legend("topleft",col=col.age2, labels.age2, pch=16, cex=1, bty="n")
-mtext("growth in basal stem area", 1, outer=TRUE,cex=1.2)
-mtext("growth in leader stem area", 2, outer=TRUE,cex=1.2)
-```
-
-### Leaf area versus plant size and height
-```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
-plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.age[as.factor(age)], pch=16)
-mod <- lm(log(total_weight)~log(leaf_area), SummaryInd)
-words.bottom.right.logxy(mod)
-
-plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.age[as.factor(age)], pch=16)
-
-plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.spp[as.factor(species)], pch=16)
-words.bottom.right.logxy(mod)
-
-plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.spp[as.factor(species)], pch=16)
-```
-
-### Leaf weight versus plant size and height
-* One of the things I find most interesting here is how different clusters of species follow different trajectories (4th graph)  
-* BAER, HATE, PELA, and PEPU have similar curves to one another; then comes a band with GRBU and GRSP, followed by all other species except PILI  
-* oldest plants (&PILI) fall below the main line of points  
-```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
-plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.age[as.factor(age)], pch=16)
-mod <- lm(log(total_weight)~log(leaf_weight), SummaryInd)
-words.bottom.right.logxy(mod)
-
-plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.age[as.factor(age)], pch=16)
-
-plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.spp[as.factor(species)], pch=16)
-words.bottom.right.logxy(mod)
-
-plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.spp[as.factor(species)], pch=16)
-```
-
-###changes in leaf growth and area over time
-* different species have different leaf area/growth to stem weight - in particular, the "canopy species" have higher leaf area relative to their stem weight
-* all species show declines in leaf weight vs. stem weight as they age, but this is a much smaller effect than the across species effect
-```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
-mod <- lm(leaf_area ~stem_weight*species*age, SummaryInd)
-anova(mod)
-
-par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
-plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.age[as.factor(age)], pch=16,ylim=c(-1,4))
-abline(0,0)
-abline(0,1)
-legend("topleft",col=col.age, labels.age, pch=16, cex=1, bty="n")
-
-plot((leaf_area)~(stem_weight), SummaryInd,col=col.age[as.factor(age)], pch=16,log="xy")
-abline(0,1)
-text(1000,1800,srt=39,labels="1:1 line")
-
-plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.spp[as.factor(species)], pch=16,ylim=c(-1,4),xlab="")
-abline(0,0)
-abline(0,1)
-legend("topleft",col=col.spp, legend=names(labels.spp), pch=16, cex=.9, bty="n")
-
-plot((leaf_area)~(stem_weight), SummaryInd,col=col.spp[as.factor(species)], pch=16,log="xy",xlab="")
-abline(0,1)
-text(1000,1800,srt=39,labels="1:1 line")
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
+mod <- lm(log(GrowthInv)~log(ReproInv),data=subset(SummaryInd,ReproInv>0))
+plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 
-##Comparing growth rates of species with different trait values
-* same as for Anais review, looking at growth rates against maxH, leaf area, wood density, LMA, leaf lifespan, and seedsize
-* splitting plants into seedlings (1 yr), saplings (2 yr), and adults (3+ yrs)  
-* RGR never "adds" to the analyses - which suggests "seedlings" are already past being "seedlings"  
-* I do have half year diameters for youngest plants
+###Plants that allocate more to reproduction (higher RA) have a lower RGR
+- When looked at individually, this pattern holds for all species except PEPU and PELA, although there is lots of variation in the exact trade-off pattern displayed by different species  
+- You can also look at the plots of RGR vs RA and identify the RA at which RGR is impacted.
+Some plots show a very linear decline throught, whereas for others there is a distinct "knickpoint" -i.e.
+BOLE, EPMI, HATE
+- More robust curve-fitting techniques are required to better illustrate this pattern (**CURVE FITTING**)
 
-### Species with larger seeds have higher growth rates  
-- The same basic relationship exists across all ages, so combined all data here  
-```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
-legend("topleft",col=col.age, labels.age, pch=16, cex=1,bty="n")
-text(GrowthInv_mean ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+```{r, echo=FALSE,message=FALSE}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
+mod <- lm(RGR~asin(sqrt(RA))*species,data=subset(SummaryInd,RA>0))
+plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logxy(mod)
 ```
 
-### Species with greater maximum height have higher growth rates
-- For younger plants there is no relationship with *SPECIES* overall maximum H  
-- There is a positive correlation with the maximum height the species reaches at a given age -i.e. fast growing young plants are tall when young.  
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==1.4))
-words.bottom.right.logxy(mod)
-
-plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==2.4))
-words.bottom.right.logxy(mod)
-
-plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age>3))
-words.bottom.right.logxy(mod)
-legend("topleft",col=col.age,labels.age,pch=16, bty="n")
-
-mtext("maximum H",1,outer=TRUE)
-mtext("yearly growth (mg)",2,outer=TRUE)
-```
-
-### Species with higher wood density have lower growth rates  
-- Adult plants strongly show this pattern
-- However there is no relationship in younger plants  
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
-words.bottom.left.logxy(mod)
-
-plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
-words.bottom.left.logxy(mod)
-legend("topright",col=col.age,labels.age,pch=16, bty="n")
-
-plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age>3))
-words.bottom.left.logxy(mod)
-
-mtext("wood density",1,outer=TRUE)
-mtext("yearly growth (mg)",2,outer=TRUE)
-```
-
-* same wood density data plotted against RGR instead - also no pattern with young
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
-words.bottom.right.logxy(mod)
-
-plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
-words.bottom.right.logxy(mod)
-legend("topright",col=col.age,labels.age,pch=16, bty="n")
-
-mtext("wood density",1,outer=TRUE)
-mtext("RGR",2,outer=TRUE)
-```
-
-### Leaf area vs growth investment
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(GrowthInv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
-text(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4))
-words.bottom.right.logxy(mod)
-
-plot(GrowthInv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings",ylim=c(100,100000))
-text(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==2.4))
-words.bottom.right.logxy(mod)
-
-plot(GrowthInv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
-text(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age>3))
-words.bottom.right.logxy(mod)
-legend("topleft",col=col.age,labels.age,pch=16, bty="n")
-
-mtext("leaf area",1,outer=TRUE)
-mtext("yearly growth (mg)",2,outer=TRUE)
-```
-
-### Species with higher LMA have higher growth rates  
-- This pattern is true for adult plants  
-- But there is no relationship in seedlings (age=1.4) or saplings (age=2.4)  
-- This is not predicted by Daniel's model or Anais' review; re-runing with RGR yields same results
-- But relationship in adults disappears when HATE is removed...
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4))
-words.bottom.right.logxy(mod)
-
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4))
-words.bottom.right.logxy(mod)
-legend("topright",col=col.age,labels.age,pch=16, bty="n")
-
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3))
-words.bottom.right.logxy(mod)
-
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3&species!="HATE"),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3&species!="HATE"), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3&species!="HATE"))
-words.bottom.right.logxy(mod)
-
-mtext("LMA",1,outer=TRUE)
-mtext("yearly growth (mg)",2,outer=TRUE)
-```
-
-###Leaf lifespan vs growth investment
-- There is no relationship between leaf lifespan and growth investment for any age group
-- And just barely a significant relationship between RGR and leaflifespan for adult plants
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2))
-plot(GrowthInv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(log(LL_death_mean)~log(GrowthInv_mean), data=subset(SummarySppAge,age==1.4))
-words.bottom.right.logxy(mod)
-
-plot(GrowthInv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==2.4))
-words.bottom.right.logxy(mod)
-
-plot(GrowthInv_mean ~ LL_death_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3))
-legend("topright",col=col.age,labels.age,pch=16, bty="n")
-words.bottom.right.logxy(mod)
-
-mtext("leaf lifespan",1,outer=TRUE)
-mtext("yearly growth (mg)",2,outer=TRUE)
-```
-
-###PCA analysis
+###PCA analysis indicates the same two patterns
 * This combination of variables shows that RGR is approximately opposite a collection of variables that indicate a plant is "bigger" - so smaller plants have higher RGR
@@
 maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
-* this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals - see below - greatly reducing sample size
+* I interpret this to mean that the three traits (Hmax, LMA, WD) strongly influence each other - presumably, Hmax a function of WD and LMA), but do not particularly 
+* this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals, greatly reducing sample size.
+Including these variables, doesn't change the basic story.
 * fine tuning:  
@@
 se1 <- PCA_by_species$PC4_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",,ylim=c(-.07,.04))
+plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",ylim=c(-.07,.04))
 se_function(mean1,se1)
@@
 
-###Coloring data by age
-* this confirms that PC2 is an axis the changes primarly by age - it is the RGR vs reproduction shift
-* PC1 has a slight age component, but more about species - across species, plant size is mostly a species effect, but of course age also matters
-* PC3 & PC4 all about species
+##How do growth and reproduction shift was Hmax is approached?
 
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+###Growth Investment versus proportion max H
+- For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH
+- I think this suggests that relative height is a good predictor of growth investment in these species, but not in some of the lower-growing species
 
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(.8,0.3,.5,0.2), mai=c(.7,1,.1,0.2))
+plot((GrowthInv~prop_maxH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16,xlab="")
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)],ylim=c(-.15,.12))
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-plot(PC3_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
-arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC3_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+plot(GrowthInv~prop_maxH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16,ylab="",xlab="")
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
 ```
 
-### Looking only at reproducing individuals - 
-* can now add in "prop_propagule","prop_accessory", but not "accessory_per_seed"
-* changes patterns quite a bit
-* PC1 is still WD vs lots of growth variables, but now absolute measures of reproductive investment (propagule_inv and accessory_inv) associate with absolute "big size" not high RA
-* PC2 is RA, seedset, and prop_propagule vs. RGR, shoot growth variables and prop_accessory; not surprising that prop_propagule and prop_accessory pulled to opposite ends
-* PC3 is somewhat similar. It is also prop_accessory and prop_maxH vs seed set and prop_propagule, but it now separates out all the shoot growth values
-* PC4 is now the axis that separates LMA_mean and maxH vs. WD_mean, with variables like maxH_spp pulling toward all the "big size" arrows
+- For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)  
+- Quite interesting, there is a distinctly negative relationship for GRBU; its absolute growth investment actually declines as it increases in size  
+- For many of the species with a good relationship, it seems that there are two breakpoints in the curve - wondering what these mean with respect to reproductive onset and RA 
+- **Need to fit proper curves to identify "knickpoints**
 
-```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-SummaryIndPCA <- SummaryInd %>%
-  filter(lvs_end_total>0&accessory_inv>0&shoot_leaf_area_growth!=0) %>%
-  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
-         RGR,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
-         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth,
-         prop_propagule, prop_accessory)
+###Looking at species individually
+```{r, echo=FALSE, message=FALSE, fig.width=24, fig.height=24}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "GrowthInv"
+xvar <- "prop_maxH"
+data <- SummaryInd
+data <- split(data, data$species)
 
-SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
-SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
-SummaryIndPCA$height <- log(SummaryIndPCA$height)
-SummaryIndPCA$maxH_spp <- log(SummaryIndPCA$maxH_spp)
-SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
-SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
-SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
-SummaryIndPCA$growth_shoot_area <- log(SummaryIndPCA$growth_shoot_area)
-SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
-SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
-SummaryIndPCA$lvs_end_total <- log(SummaryIndPCA$lvs_end_total)
-SummaryIndPCA$growth_stem_area <- log(SummaryIndPCA$growth_stem_area)
-SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
-SummaryIndPCA$shoot_leaf_area_growth <- log(SummaryIndPCA$shoot_leaf_area_growth)
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
+                    main=spp, xlab="",ylab="")
+}
 
-PCA_mod <- prcomp(SummaryIndPCA, scale=TRUE)
-summary(PCA_mod)
-biplot(PCA_mod)
+mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
+mtext("Growth investment", 2, outer=TRUE,cex=1.2)
 
-PCA_loadings <- as.data.frame(PCA_mod$rotation)
-PCA_loadings$variables <- row.names(PCA_loadings)
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
 
-PCA_scaling <- as.data.frame(PCA_mod$scale)
-PCA_scaling$variables <- row.names(PCA_scaling)
-names(PCA_scaling) <- c("scale","variables")
-PCA_loadings <- merge(PCA_loadings,PCA_scaling,by="variables")
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
 
-PCA_lambda <- as.data.frame(PCA_mod$sdev)
-
-PCA_scores <- as.data.frame(PCA_mod$x)
-PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$lvs_end_total>0&SummaryInd$shoot_leaf_area_growth!=0&SummaryInd$accessory_inv>0)
-SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)
-
-n <- NROW(PCA_scores)
-scale =1
-
-PCA_lambda <- PCA_lambda*sqrt(n)
-PCA_lambda <- PCA_lambda^scale
-
-SummaryInd_PCA_results$PC1_scale <- SummaryInd_PCA_results$PC1/PCA_lambda[1]
-SummaryInd_PCA_results$PC2_scale <- SummaryInd_PCA_results$PC2/PCA_lambda[2]
-SummaryInd_PCA_results$PC3_scale <- SummaryInd_PCA_results$PC3/PCA_lambda[3]
-SummaryInd_PCA_results$PC4_scale <- SummaryInd_PCA_results$PC4/PCA_lambda[4]
-PCA_loadings$PC1_scale <- PCA_loadings$PC1 / 4.5
-PCA_loadings$PC2_scale <- PCA_loadings$PC2 / 4.5
-PCA_loadings$PC3_scale <- PCA_loadings$PC3 / 4.5
-PCA_loadings$PC4_scale <- PCA_loadings$PC4 / 4.5
+results
 ```
 
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+### RGR by proportion Hmax
+- Ignoring a few outliers, RGR declines with increasing height is 12 species  
+- Only in HEPU and PILI is there no significant trend  
+- The species with a poorer correlation are mostly shorter ones that are presumably often broken off   
+- These are continued ways to look at the question of how important is height (relative to the species maxH) in understanding its growth and reproduction
 
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
+plot(RGR~prop_maxH,SummaryInd,col=col.spp[as.factor(species)],pch=16)
 legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.12))
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-plot(PC3_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
-arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC3_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
 ```
 
-comparing
-```{r, echo=FALSE,message=FALSE}
-mod <- lm(RGR~species+asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1),SummaryInd)
-anova(mod)
-glance(mod)[1]
+```{r, echo=FALSE, message=FALSE, fig.width=24, fig.height=24}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.7,.5,0.2)) 
+yvar <- "RGR"
+xvar <- "prop_maxH"
+data <- SummaryInd
+data <- split(data, data$species)
 
-mod <- lm(RGR~asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1)+WD_mean+LMA_mean+maxH_spp,SummaryInd)
-anova(mod)
-glance(mod)[1]
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
+                    main=spp, xlab="",ylab="")
+}
+
+mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
+mtext("RGR", 2, outer=TRUE,cex=1.2)
+
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
 ```
 
-* another of the interesting pattern is that the increase in shoot area of leaders is correlated with maxH and seed_size (and opposite WD_mean) and somewhat offset from whole plant growth measures and whole plant size measures
-* seed_size removed, because no additional explanatory power after WD and maxH_spp included
-
-```{r, echo=FALSE,message=FALSE}
-mod <- lm(log(growth_shoot_area)~log(maxH_spp)+WD_mean+log(growth_stem_area)+log(total_weight)+RGR+asin(sqrt(RA))+LMA_mean,SummaryInd)
-anova(mod)
-glance(mod)
+###RA by proportion Hmax
+```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
+plot(RA~prop_maxH,SummaryInd,col=col.spp[as.factor(species)],pch=16)
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 ```
 
-plot(mod)
-###Traits correlated
-- species maxH and wood density are highly correlated
-- the two species lying a bit outside are PUTU and PHPH which both often have multiple stems from the base - the second chart omits them
--
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-plot(WD_mean~maxH_spp,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
-mod <- lm(log(maxH_spp)~WD_mean,SummaryInd)
-words.bottom.left.logx(mod)
+```{r, echo=FALSE, message=FALSE, fig.width=24, fig.height=24}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.7,.5,0.2)) 
+yvar <- "RA"
+xvar <- "prop_maxH"
+data <- SummaryInd
+data <- split(data, data$species)
 
-plot(WD_mean~maxH_spp,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"), log="x",col=col.spp[as.factor(species)],pch=16)
-mod <- lm(log(maxH_spp)~WD_mean,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"))
-words.bottom.left.logx(mod)
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
+                    main=spp, xlab="",ylab="")
+}
 
-plot(seedset_mean~total_weight_mean,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
-mod <- lm(log(total_weight_mean) ~ (seedset_mean),SummarySpp)
-words.bottom.left.logx(mod)
+mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
+mtext("RA", 2, outer=TRUE,cex=1.2)
 
-plot(seedset_mean~maxH_spp,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
-mod <- lm(log(maxH_spp) ~ (seedset_mean),SummarySpp)
-words.bottom.left.logx(mod)
+data <- SummaryInd
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+```

### 2015-07-30 error_checking.rmd
mostly addition of "error_checking.rmd" which should show problems with leaf weight vs diameter

```{r, echo=FALSE,results='hide', message=FALSE}
library(remake)
create_bindings()

source("scripts/summary_dataframes.R")
source("scripts/functions.R")
```

* you can see that for all plants, even old ones, if just the upper segments are used, the leaf weight vs. diameter still plots on the main line, but if the lower stem segment(s), where leaves are few or lacking (even on side branches), there is increased diameter with little increase in leaf weight. 
* this means that for the plots, segment 1 (which are mostly the labeled dots) fall "above" the main line of points

```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
check <- BOLE_HarvestData

plot(dia~stem_weight,data=subset(check), pch=16,log="xy",col=col.lots[as.factor(segment)])
text(dia~stem_weight,data=subset(check,segment==1),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check), pch=16,log="xy",col=col.lots[as.factor(segment)])
text(dia~leaf_weight,data=subset(check,segment==1),labels=individual,cex=.5,pos=3,offset=-.7)

#colors represent segments, with red the entire plant, then purple, gray, green
#for stems, linear no matter what portion plant included
#for leaves, with older plants (ages 5,7,9 for BOLE, older for other species) have continued diameter increase with little increase in leaf area

plot(dia~stem_weight,data=subset(check,age==7), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~stem_weight,data=subset(check,segment==1&age==7),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age==7), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~leaf_weight,data=subset(check,segment==1&age==7),labels=individual,cex=.5,pos=3,offset=-.7)

#second set of plots just fpr 7 year old plants
#colors now by individual, with labels on "whole plant" measures

check <- PELA_HarvestData

plot(dia~stem_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~stem_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~leaf_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)

#at the other extreme, with PELA, effect only seed among age 32 plants, and only among 5 of the 7 reps (colors here represent individuals)

check <- HATE_HarvestData

plot(dia~stem_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~stem_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~leaf_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)

#and no asymptoting at all for HATE

check <- COER_HarvestData

plot(dia~stem_weight,data=subset(check,age>5), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~stem_weight,data=subset(check,segment==1&age>5),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age>5), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~leaf_weight,data=subset(check,segment==1&age>5),labels=individual,cex=.5,pos=3,offset=-.7)

#COER here

```

### 2015-07-30 scripts/summary_dataframes.R

@@ -533,4 +533,6 @@ col.spp.noHATE <- c("red", "darkolivegreen4", "blue", "purple", "grey", "light g
 col.LMA <-c("orchid1","gold1","darkolivegreen3","cyan2","dodgerblue","purple","red")
 labels.LMA <-c("age 1.4", "age 2.4", "age 5", "age 7", "age 9", "age 32", "HATE")
 col.lots <- c("red", "darkolivegreen4", "blue", "purple", "grey", "light green","gold1","cyan2","black", "chocolate1","light blue","brown","deep pink","orchid1",
+              "dodgerblue","darkcyan","brown2","bisque4","blue4","cadetblue","darkseagreen","darkslateblue","firebrick4","red", "darkolivegreen4", "blue", "purple", "grey", "light green","gold1","cyan2","black", "chocolate1","light blue","brown","deep pink","orchid1",
+              "dodgerblue","darkcyan","brown2","bisque4","blue4","cadetblue","darkseagreen","darkslateblue","firebrick4","red", "darkolivegreen4", "blue", "purple", "grey", "light green","gold1","cyan2","black", "chocolate1","light blue","brown","deep pink","orchid1",
               "dodgerblue","darkcyan","brown2","bisque4","blue4","cadetblue","darkseagreen","darkslateblue","firebrick4")

### 2015-08-04 results_accessory_v3.Rmd
Continuing to rework my way through various sscripts, trying to condense figures, message

--- 2015-05-26 results_accessory_shorter.Rmd
@@
 flowers (I do know aborted buds decrease)
-###Which measure of reproductive output best correlates with plant size or growth (growth plotted here)
-* Measuring total reproductive output has a much stronger correlation than any of the other measures
-* Note that each of these figures (and models) only includes individuals with non-zero reproductive investment
 
-```{r, echo=FALSE,message=FALSE,,fig.width=14, fig.height=14}
+##Which measure of reproductive output best correlates with plant size or growth (growth plotted here)
+* Measuring total reproductive output has a much stronger correlation than investment in fruit weight or propagules
+* To demonstrate the point that most investment is in prepollination tissues, the regression of total weight against prepollination investment is as good as total reproductive investment - one could just count buds + flowers!
+* Note that each of these figures (and models) only includes individuals with non-zero investment in the reproductive pool of interest
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
@@
 
-mod <- lm (log(total_weight)~log(seedset), data=subset(SummaryInd,seedset>0))
-plot(seedset~total_weight,data=subset(SummaryInd,prop_propagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="seedset",xlim=c(100,2000000),xlab="")
+mod <- lm (log(total_weight)~log(prepollen_all_inv), data=subset(SummaryInd,prepollen_all_inv>0))
+plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="prepollen investment (mg)", xlim=c(100,2000000))
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
-mtext("Total size (mg)", 1, outer=TRUE,cex=1.2)
 ```
 
-### How do accessory costs shift with seed size?
+##How do accessory costs shift with seed size?
+
+### Comparing "per successful seed" and "proportion reproductive investment" accessory cost calculations 
+  - calculating accessory costs on a per seed basis stratify the data much more by species 
+  - cross-species variation is accentuated in plots calculated as "per successful seed" (vs.
+those with proportional accessory costs), because the species that have more seeds (lower proportional accessory costs), also have higher seedset
+
     - Larger-seeded species have higher accessory costs, as has been shown in other studies
-- However, it is also true that "larger species" have higher accessory costs and than species with higher seed set have lower accessory costs
-- In contrast, there is a relatively low correlation between accessory costs and proportion reproductive energy invested in pre-pollination tissues DESPITE this being the biggest pool of energy for most species
+    - However, it is also true that "larger species" and species with lower seed set have higher accessory costs
+    - And that species with greater prepollination investment have higher accessory costs (since this is nearly the complement to propagule investment)
+
 - Taken together these data (and various other plots, not shown) suggest that accessory costs (as a proportion) are most strongly driven by seedset
@@
 
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3))
+```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=12, fig.height=6}
+options(scipen=999)
+par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(.7,1,0.3,0.3))
+
+#mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
+plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=.9)
+points((accessory_per_seed_mean)~seed_size,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+words.bottom.right.logxy(mod)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+#mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
 mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="seed size (mg)",cex=1.3)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=.9)
 words.bottom.right.logx(mod)
+points(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+mtext("Seed size (mg)",1, outer=TRUE,cex=1.2)
 
+#mod <- lm(log(total_weight)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+mod <- lm(log(total_weight_mean)~log(accessory_per_seed_mean),SummarySpp)
+plot(accessory_per_seed~total_weight,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=.9)
+points((accessory_per_seed_mean)~total_weight_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+words.bottom.right.logxy(mod)
+
+#mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
 mod <- lm(log(total_weight_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
+plot(asin(sqrt(prop_accessory))~total_weight,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=0.9)
+points(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
 words.bottom.right.logx(mod)
+mtext("Total plant weight (mg)",1, outer=TRUE,cex=1.2)
 
+#mod <- lm(log(seedset)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+mod <- lm(log(seedset_mean)~log(accessory_per_seed_mean),SummarySpp)
+plot((accessory_per_seed)~seedset,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=0.9)
+points((accessory_per_seed_mean)~seedset_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+words.top.right.logxy(mod)
+
+#mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
 mod <- lm(log(seedset_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",cex=1.3)
+plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",cex=0.9)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+points(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
 words.top.right.logx(mod)
+mtext("seedset",1, outer=TRUE,cex=1.2)
 
+#mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
+mod <- lm(log(prepollen_all_per_seed_mean)~log(accessory_per_seed_mean),SummarySpp)
+plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=0.9)
+points((accessory_per_seed_mean)~prepollen_all_per_seed_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+words.bottom.right.logxy(mod)
+
+#mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
 mod <- lm(asin(sqrt(prop_prepollen_all_mean))~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, log="", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
-words.top.right(mod)
-mtext("Proportion reproductive investment to accessory tissues (asin transformed)",2, outer=TRUE,cex=1.2)
+plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=0.9)
+points(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+words.bottom.right(mod)
+mtext("pre-pollination costs (proportional)",1, outer=TRUE,cex=1.2)
 ```
 
-* investment vs. costs per successful seed
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3)) 
-mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
-plot(accessory_per_seed_mean~seed_size,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="seed size (mg)",cex=1.3)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
+### Plotting accessory costs that go into making a single seed
+- These calculations sum up all the tissue parts required to make a single seed, ignoring the cost of aborted tissues  
+- They are a bit rough at the moment, with estimates for the cost of tissues that support multiple seeds (i.e. a cone)
 
-mod <- lm(log(total_weight_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot(accessory_per_seed_mean~total_weight_mean,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
-words.bottom.right.logxy(mod)
-
-mod <- lm(log(seedset_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot((accessory_per_seed_mean)~seedset_mean,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",cex=1.3)
-words.top.right.logxy(mod)
-
-mod <- lm(log(prepollen_all_per_seed_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot(log(accessory_per_seed_mean)~log(prepollen_all_per_seed_mean),SummarySpp, log="", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
-words.top.right(mod)
-mtext("Accessory tissue investment per successful seed (mg)",2, outer=TRUE,cex=1.2)
-```
-
-### Plotting accessory costs that go into making a single seed - ignoring aborted tissues
 * Bigger seeds have bigger fixed costs of making that seed (1st plot)
-* But other than LEES having much lower costs, no shifts across species in their relative costs to make a seed (2nd plot)
+* But other than LEES having much lower costs, no shifts across species in their relative costs to make a seed (2nd plot); and LEES is one of the species where I use "propagule" not a single seed, so its "seed size" is higher and "accessory costs" slightly lower, since all fruit parts are part of the propagule
 * In other words, patterns of accessory costs vs. seed size, plant size, etc come about due to the differential effect of bud, flower abortion across species  
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
+```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=12, fig.height=6}
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
@@
 
-* Here is the plot just of seed set by propagule investment (for all individuals), showing the effect is true within and across species
-* This is the complement to the plot of accessory costs  
-* Replotting the same data by age, shows that the pattern is not age-driven
+###Seedset by age
+* Replotting the seedset data by age, showing that the correlation between seedset and accessory costs is not primarily age related
 * At most, there are most "old" plants with very low seedset 
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.3,0.3), mai=c(0.8,1,0.3,0.3))  
-mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="proportion reproduction to propagules (1-accessory)")
-words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```{r, echo=FALSE,message=FALSE,fig.width=6, fig.height=6}
+par(mfrow=c(1,1), cex=1, omi=c(0.6,0.3,0.3,0.3), mai=c(0.8,1,0.3,0.3))
 
@@
 
-*Comparing proportion energy to propagules vs accessory cost per seed
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.3,0.3), mai=c(0.8,1,0.3,0.3))  
-mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="proportion reproduction to propagules (1-accessory)")
-words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-mod <- lm(log(seedset)~log(accessory_per_seed),data=subset(SummaryInd,seedset>0&seedset<1&accessory_per_seed>0))
-plot(accessory_per_seed~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="accessory costs per seed produced (mg)")
-words.bottom.left.logxy(mod)
-mtext("Seed set",1, outer=TRUE,cex=1.1)
-```
-
 ###Relationship between tissue allocation and reproductive investment
 * these data also tell the story of seedset being an important "component" and being lower in bigger species
-* Proption pre-pollination costs completely unrelated to reproductive investment
+* Proportion pre-pollination costs completely unrelated to reproductive investment
 * However, proportional investment in propagules decreases with increasing reproductive investment, because the bigger species investment more overall in reproduction and less in propagules
@@
 
-* This same pattern is true just looking  at energy invested in pre-pollination tissues and at propagule allocation
+###What causes the correlation between RA and plant size (or total reproductive investment)?
+* Do plants invest equally more in all reproductive tissues as they get bigger or do they increase allocation to certain types of reproductive tissues more than others?
+
+* If they shifted their proportional investment, there would be a relationship between RA and the proportional investment in 1 (or more) of the 5 reproductive energy pools.
+If they do not shift their proportional investment, all 5 would have no relationship.
+    ** Only "proportional energy to pre-pollination aborted tissues" shows a significant decline with increasing RA - and it has a very convincing decline.
+Since no other pool shows an increase in proportional investment, that extra energy must be distributed fairly randomly across other pools
+
+* Simultaneously, all tissue pools should show a positive relationship between actual investment amounts (mg) and RA
+  ** Indeed, all pools increase with increasing RA, although only "pre-pollination successful tissues" and "energy to propagules" have a convincing r-squared value (across all species)
+
+* 
+* It might be interesting to look at this pattern by species
+
+```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=30}
+par(mfrow=c(5,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
+
+mod <- lm(log(RA)~log((propagule_inv)),data=subset(SummaryInd,RA>0&propagule_inv>0))
+plot(propagule_inv~RA,data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(RA)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,RA>0&prop_propagule>0))
+plot(asin(sqrt(prop_propagule))~RA,data=subset(SummaryInd,RA>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+words.bottom.left.logx(mod)
+
+mod <- lm(log(RA)~log((prepollen_aborted_inv)),data=subset(SummaryInd,RA>0&prepollen_aborted_inv>0))
+plot(prepollen_aborted_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(RA)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0))
+plot(asin(sqrt(prop_prepollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
+words.bottom.right.logx(mod)
+
+mod <- lm(log(RA)~log((prepollen_success_inv)),data=subset(SummaryInd,RA>0&prepollen_success_inv>0))
+plot(prepollen_success_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(RA)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,RA>0&prop_prepollen_success>0))
+plot(asin(sqrt(prop_prepollen_success))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
+words.bottom.right.logx(mod)
+
+mod <- lm(log(RA)~log((packaging_dispersal_inv)),data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0))
+plot(packaging_dispersal_inv~RA,data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
+words.bottom.right.logxy(mod)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mod <- lm(log(RA)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0))
+plot(asin(sqrt(prop_packaging_dispersal))~RA,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
+words.bottom.left.logx(mod)
+
+mod <- lm(log(RA)~log((postpollen_aborted_inv)),data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0))
+plot(postpollen_aborted_inv~RA,data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(RA)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0))
+plot(asin(sqrt(prop_postpollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
+words.bottom.left.logx(mod)
+```
+
 * Plants that invest more in some reproductive tissues, on average, invest more in other reproductive tissues, so have a higher RA
 
-* Looking at proportions, the pattern is much less informative
+  * This same pattern is true just looking  at energy invested in pre-pollination tissues and at propagule allocation
+
 * Plants with higher RA have lower allocation to pre-pollination tissues, probably because of their higher seedset
@@
 
+```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=36}
+par(mfrow=c(6,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
+
+mod <- lm((prop_maxH)~log((ReproInv)),data=subset(SummaryInd,prop_maxH>0&ReproInv>0))
+plot(ReproInv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="total reproductive investment (mg)")
+words.bottom.right.logy(mod)
+
+mod <- lm((prop_maxH)~asin(sqrt(RA)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(RA))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="RA")
+words.bottom.left(mod)
+
+mod <- lm((prop_maxH)~log((propagule_inv)),data=subset(SummaryInd,prop_maxH>0&propagule_inv>0))
+plot(propagule_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to propagules (mg)")
+words.bottom.right.logy(mod)
+
+mod <- lm((prop_maxH)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(prop_propagule))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+words.bottom.left(mod)
+
+mod <- lm((prop_maxH)~log((prepollen_aborted_inv)),data=subset(SummaryInd,prop_maxH>0&prepollen_aborted_inv>0))
+plot(prepollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="y",ylab="pre-pollination aborted tissues (mg)")
+words.bottom.right.logy(mod)
+
+mod <- lm((prop_maxH)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(prop_prepollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
+words.bottom.left(mod)
+
+mod <- lm((prop_maxH)~log((prepollen_success_inv)),data=subset(SummaryInd,prop_maxH>0&prepollen_success_inv>0))
+plot(prepollen_success_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_success_inv>0), pch=16,col=col.spp[as.factor(species)],log="y",ylab="pre-pollination successful tissues (mg)")
+words.bottom.right.logy(mod)
+
+mod <- lm((prop_maxH)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(prop_prepollen_success))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
+words.bottom.left(mod)
+
+mod <- lm((prop_maxH)~log((packaging_dispersal_inv)),data=subset(SummaryInd,prop_maxH>0&packaging_dispersal_inv>0))
+plot(packaging_dispersal_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to packaging and dispersal (mg)")
+words.bottom.right.logy(mod)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mod <- lm((prop_maxH)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(prop_packaging_dispersal))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
+words.bottom.left(mod)
+
+mod <- lm((prop_maxH)~log((postpollen_aborted_inv)),data=subset(SummaryInd,prop_maxH>0&postpollen_aborted_inv>0))
+plot(postpollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to tissues aborted postpollination (mg)")
+words.bottom.right.logy(mod)
+
+mod <- lm((prop_maxH)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(prop_postpollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
+words.bottom.left(mod)
+```
+
 #Shifts in accessory costs across species and ages

### 2015-08-04 results_growth_short.Rmd
Continuing to rework my way through various sscripts, trying to condense figures, message

@@
 source("scripts/functions.R")
+
 ```
@@
 mod <- lm(log(GrowthInv)~log(ReproInv),data=subset(SummaryInd,ReproInv>0))
-plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+words.top.left.logxy(mod)
 legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
+abline(0,1)
+text(5,6.5,srt=38,"RA = 0.5")
+abline(log10(9),1)
+text(2,23,srt=38,"RA = 0.9")
+abline(log10(.1),1)
+text(20,2.6,srt=38,"RA = 0.1")
+abline(log10(.01),1)
+text(170,2.2,srt=38,"RA = 0.01")
 ```
@@
 ```{r, echo=FALSE,message=FALSE}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
-mod <- lm(RGR~asin(sqrt(RA))*species,data=subset(SummaryInd,RA>0))
+par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
+mod <- lm(RGR~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
 plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
@@
 words.top.right.logxy(mod)
+
+mod <- lm(log(growth_stem_diam)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
+plot((RA+.01)~growth_stem_diam, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logxy(mod)
+
+mod <- lm(log(growth_stem_area)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
+plot((RA+.01)~growth_stem_area, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logxy(mod)
+
+SummaryInd$prop_growth_height <- SummaryInd$growth_height/SummaryInd$maxH_spp
+
+mod <- lm(log(prop_growth_height)~asin(sqrt(RA)),data=subset(SummaryInd,growth_height>0&species!="PEPU"&species!="PELA"&species!="COER"))
+plot((RA+.01)~(prop_growth_height), data=subset(SummaryInd,species!="PEPU"&species!="PELA"), log="xy", col=col.spp[as.factor(species)],pch=16)
+
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logxy(mod)
+
+mod <- lm(log(growth_height)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&growth_height>0))
+plot((RA+.01)~(growth_height), SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
 ```
@@
   select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
-         RGR,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
-         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth)
+         growth_stem_diam,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
+         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth,RGR)
 
@@
 SummaryIndPCA$growth_stem_area <- log(SummaryIndPCA$growth_stem_area)
+SummaryIndPCA$growth_stem_diam <- log(SummaryIndPCA$growth_stem_diam)
 SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)

### 2015-08-04 scripts/functions.R

@@ -158,3 +158,11 @@ words.bottom.left.logxy <- function (x) {
   text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.07*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
   text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.02*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=0)
 }
+
+words.top.left.logxy <- function (x) {
+  output <- data.frame(select(glance(x), r.squared, p.value))
+  output <- round(output,4)
+  text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
+  text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
+  text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=0)
+}

### 2015-08-05 Panalysis.rmd
continuing to clean up little bits of analyses
found several little mistakes...

```{r, echo=FALSE,results='hide', message=FALSE}
libReproInvry(remake)
create_bindings()

source("scripts/summary_datafReproInvmes.R")
source("scripts/functions.R")
```

```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
par(mfrow=c(5,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))

mod <- lm(log(ReproInv)~log((propagule_inv)),data=subset(SummaryInd,ReproInv>0&propagule_inv>0))
plot(propagule_inv~ReproInv,data=subset(SummaryInd,ReproInv>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(ReproInv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,ReproInv>0&prop_propagule>0))
plot(asin(sqrt(prop_propagule))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(ReproInv)~log((prepollen_aborted_inv)),data=subset(SummaryInd,ReproInv>0&prepollen_aborted_inv>0))
plot(prepollen_aborted_inv~ReproInv,data=subset(SummaryInd,ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(ReproInv)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,ReproInv>0&prop_prepollen_aborted>0))
plot(asin(sqrt(prop_prepollen_aborted))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(ReproInv)~log((prepollen_success_inv)),data=subset(SummaryInd,ReproInv>0&prepollen_success_inv>0))
plot(prepollen_success_inv~ReproInv,data=subset(SummaryInd,ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(ReproInv)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,ReproInv>0&prop_prepollen_success>0))
plot(asin(sqrt(prop_prepollen_success))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
words.bottom.right.logx(mod)

mod <- lm(log(ReproInv)~log((packaging_dispersal_inv)),data=subset(SummaryInd,ReproInv>0&packaging_dispersal_inv>0))
plot(packaging_dispersal_inv~ReproInv,data=subset(SummaryInd,ReproInv>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
abline(0,1)
words.bottom.right.logxy(mod)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mod <- lm(log(ReproInv)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,ReproInv>0&prop_packaging_dispersal>0))
plot(asin(sqrt(prop_packaging_dispersal))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
words.bottom.left.logx(mod)

mod <- lm(log(ReproInv)~log((postpollen_aborted_inv)),data=subset(SummaryInd,ReproInv>0&postpollen_aborted_inv>0))
plot(postpollen_aborted_inv~ReproInv,data=subset(SummaryInd,ReproInv>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
abline(0,1)
words.bottom.right.logxy(mod)

mod <- lm(log(ReproInv)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,ReproInv>0&prop_postpollen_aborted>0))
plot(asin(sqrt(prop_postpollen_aborted))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
words.bottom.left.logx(mod)
```

par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "repro_all_count"
xvar <- "ReproInv"

data <- 
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
                    main=spp)
    }

plot(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),log="xy")
text(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),labels=individual, pos=1,offset=.6,cex=0.8,col="black")

check <- PEPU_Investment
check_FD <-check[3]
View(check_FD)
check3 <- subset(check_FD,FD.what=="cone_aborted")

names(check_FD)

```{r}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "leaf_a"
xvar <- "seed_count"

data <- subset(SummaryInd,seedset>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
                    main=spp)
    }

mtext("RA", 1, outer=TRUE,cex=1.2)
mtext("Yearly increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)

par(mfrow=c(1,1), cex=1, omi=c(.8,.8,.1,.1), mai=c(1.1,1,.4,0.2)) 
plot(asin(sqrt(prop_growth_stem_diam))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0),pch=16,col=col.spp[as.factor(species)])
mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_growth_stem_diam)),data=subset(SummaryInd,RA>0))
words.bottom.left(mod)
```

### 2015-08-05 results_accessory_v3.Rmd
continuing to clean up little bits of analyses
found several little mistakes...

@@
-```{r, echo=FALSE,results='hide', message=FALSE}
+```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
 library(remake)
@@
 ##Summary of outcomes
-1. Total reproductive investment is by far the best correlate with total plant size (or growth investment)
+1. Total reproductive investment is the best correlate with total plant size (or growth investment)
 2.
@@
     * In other words, plants with higher seed set, have lower accessory costs due to calculations
-  * It is nice to have a data set that shows, across 14 species, that larger plants have lower seed set.
+    * Across  the 14 species, plants with larger adult size have lower seed set.
 3. Bigger plants have higher RA. 
@@
 
-##Which measure of reproductive output best correlates with plant size or growth (growth plotted here)
+##Which measure of reproductive output best correlates with plant size or growth
 * Measuring total reproductive output has a much stronger correlation than investment in fruit weight or propagules
-* To demonstrate the point that most investment is in prepollination tissues, the regression of total weight against prepollination investment is as good as total reproductive investment - one could just count buds + flowers!
-* Note that each of these figures (and models) only includes individuals with non-zero investment in the reproductive pool of interest
+* The regression of total weight against prepollination investment is as good as total reproductive investment - one could just count buds + flowers!
+    * This is likely because prepollination investment is much a large proportion of total reproductive investment
+* Note that each of these figures (and models) only includes individuals with non-zero investment in the reproductive pool plotted
 
@@
 words.bottom.right.logxy(mod)
+
+mtext("Total plant size (mg)",1, outer=TRUE,cex=1.2)
 ```
 
-##How do accessory costs shift with seed size?
+### Comparing accessory cost calculations expressed as "per successful seed" versus "proportion reproductive investment"  
+  - The difference between the two calculations is seed count
+  - calculating accessory costs on a per seed basis stratify the data much more by species 
+      * this is because the species that have more seeds (lower proportional accessory costs), also have higher seedset
+  - Calculations per seed tell you energy input relative to fecundity
+```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=7}
+options(scipen=10)
+par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(1.1,1,0.3,0.3)) 
+mod <- lm(log(seed_count)~species*accessory_per_seed,data=subset(SummaryInd,seed_count>0))
+plot(seed_count~accessory_per_seed,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="seed count",xlab="accessory costs per successful seed (mg)",cex=.9)
+words.bottom.left.logxy(mod)
 
-### Comparing "per successful seed" and "proportion reproductive investment" accessory cost calculations 
-  - calculating accessory costs on a per seed basis stratify the data much more by species 
-  - cross-species variation is accentuated in plots calculated as "per successful seed" (vs.
-those with proportional accessory costs), because the species that have more seeds (lower proportional accessory costs), also have higher seedset
+plot(seed_count~asin(sqrt(prop_accessory)),SummaryInd, log="y", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="proportion of reproduction to accessory tissues (asin)",cex=.9)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```
+###Do accessory costs shift with seed size?
+    * These plots presented using both accessory cost calculations
 
+Results:  
     - Larger-seeded species have higher accessory costs, as has been shown in other studies  
-    - However, it is also true that "larger species" and species with lower seed set have higher accessory costs
-    - And that species with greater prepollination investment have higher accessory costs (since this is nearly the complement to propagule investment)
+    - Also: "larger species" and species with lower seed set have higher accessory costs  
+    - And: species with greater prepollination investment have higher accessory costs (since this is the majority of accessory costs for most species)  
+    - When all 4 variables put into a single model, regardless of "accessory cost" calculation, seedset always by far the most significant correlate   
+        * seed size is least frequently a correlate in models, although of course highly significant when analyzed on its own
 
-- Taken together these data (and various other plots, not shown) suggest that accessory costs (as a proportion) are most strongly driven by seedset
-- In other words, if flowers are pollinated and develop into mature seeds, the plants ends up investing more energy in reproduction and that extra energy is being invested into propagules.
-- Therefore, seed set goes up and by default, a greater proportion of energy goes into propagules and less into "accessory costs"
+Interpretation:  
+    - Not sure one can separate the effect of plant size, seed set, seed size on what drive accessory costs  
+    - the reason seed set is strongly correlated, is because if flowers are pollinated and develop into mature seeds, the individual plant ends up investing more energy in reproduction and that extra energy is being invested into propagules, reducing accessory costs.
+        * This is true at the species and individual level.
 
-```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=12, fig.height=6}
-options(scipen=999)
+mod <- lm(log(accessory_per_seed)~(seedset)*log(prepollen_all_inv)*log(total_weight)*log(seed_size),data=subset(SummaryInd,seedset>0&prepollen_all_per_seed>0))
+summary(mod)
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=7}
 par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(.7,1,0.3,0.3))
-
 #mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
@@
 * In other words, patterns of accessory costs vs. seed size, plant size, etc come about due to the differential effect of bud, flower abortion across species  
-```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=12, fig.height=6}
+```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=7}
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
@@
 
-###Seedset by age
-* Replotting the seedset data by age, showing that the correlation between seedset and accessory costs is not primarily age related
+###Seedset,seed count by age, size, RA
+* Replotting the seedset data by age, showing that the correlation between seedset and accessory costs is not age related
 * At most, there are most "old" plants with very low seedset  
-```{r, echo=FALSE,message=FALSE,fig.width=6, fig.height=6}
-par(mfrow=c(1,1), cex=1, omi=c(0.6,0.3,0.3,0.3), mai=c(0.8,1,0.3,0.3))
+* these plots only include individuals with some seedset, thereby ignoring most young plants
+
+```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3))
 
 mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="proportion reproduction to propagules (1-accessory)",xlab="")
+plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="proportion RE to propagules (1-accessory)",xlab="seed set")
 words.bottom.right.logxy(mod)
 legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
-mtext("Seed set",1, outer=TRUE,cex=1.1)
 ```
+
+* There is no overall shift in either seedset or proportional allocation to propagules with increasing RA  
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7,warning=FALSE}
+par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
+mod <- lm(asin(sqrt(seedset))~asin(sqrt(RA)),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(asin(sqrt(RA))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+words.bottom.right(mod)
+
+mod <- lm(asin(sqrt(prop_propagule))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
+plot(asin(sqrt(RA))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), log="x", pch=16,col=col.spp[as.factor(species)])
+words.bottom.right.logx(mod)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```
+
+* Furthermore, looking within species  
+    - Not a single species shows an increase in prop_propagule with increasing RA  
+    - And for seedset vs RA, only HATE shows an increase, and HEPU a decrease  
+    - So no, there are no compounding benefits to increasing RA
+
+```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7,warning=FALSE}
+yvar <- "RA_asin"
+xvar <- "seedset"
+
+data <- subset(SummaryInd,seedset>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(x[[yvar]] ~  asin(sqrt(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+```
+
+* And there are absolutely no patterns of interest relative to seed count   
+    * it doesn't even correlate very well with RA or plant size
 
@@
 
-mod <- lm(log(ReproInv)~log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
+options(scipen=5)
+mod <- aov(log(ReproInv)~species*log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
+summary(mod)
+
+options(scipen=20)
+mod <- lm(log(ReproInv)~species*log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
 plot(prop_propagule~ReproInv,data=subset(SummaryInd,prop_propagule>0), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Propagules (as proportion repro inv)")
@@
 * This is true for many individual species as well as across species
-* RA and seed count are also correlated, but mainly that no low RA individuals have high seed counts
+
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
@@
 words.bottom.right.logxy(mod)
+mtext("RA",1, outer=TRUE,cex=1.1)
+```
 
-mod <- lm(log(RA)~log(seed_count+.1),data=subset(SummaryInd,repro_all_count>0))
-plot((.1+seed_count)~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp[as.factor(species)],pch=16,log="xy",ylab="# of seeds produced",xlab="")
-words.bottom.right.logxy(mod)
-mtext("RA",1, outer=TRUE,cex=1.1)
-
+```{r, echo=FALSE,message=FALSE,fig.width=28, fig.height=28}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
 yvar <- "repro_all_count"
-xvar <- "RA"
+xvar <- "RA_asin"
 
@@
 data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  log(x[[xvar]])))
+lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  (x[[xvar]])))
 results <- summarise_all_fits(lmfits)
@@
 results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",
+                    main=spp)
+    }
 ```
@@
 If they do not shift their proportional investment, all 5 would have no relationship.
-    ** Only "proportional energy to pre-pollination aborted tissues" shows a significant decline with increasing RA - and it has a very convincing decline.
-Since no other pool shows an increase in proportional investment, that extra energy must be distributed fairly randomly across other pools
+      * Only "proportional energy to pre-pollination aborted tissues" shows a significant decline with increasing RA - and it has a very convincing decline.   
+      * Since no other pool shows an increase in proportional investment, that extra energy must be distributed fairly randomly across other pools
 
 * Simultaneously, all tissue pools should show a positive relationship between actual investment amounts (mg) and RA  
-  ** Indeed, all pools increase with increasing RA, although only "pre-pollination successful tissues" and "energy to propagules" have a convincing r-squared value (across all species)
+      * However, only "pre-pollination successful tissues" and "energy to propagules" have a convincing r-squared value (across all species)
 
-* 
 * It might be interesting to look at this pattern by species
@@
 
-###Shifts across age
+###Shifts across age and height
 * Seedset shows a slight decrease with proportional plant height (the best proxy for "relative size")  
     * this pattern likely exists because species that begin reproducing at shorter proportional heights have higher seedset  
-* only LEES shows a significant decline with age, although most species have a segative slope  
-* there is a similar pattern for Propagule investment (not shown)  
-* Table shows results, by species, for seedset by proportional height  
+    * only LEES shows a significant decline
+
+* the same analysis can be done on seedset by age, with similar response    
+    * Only HEPU, LEES show significant decline
+
+yvar <- "seedset"
+xvar <- "prop_maxH""
 ```{r, echo=FALSE,message=FALSE}
@@
 
-* Results, by species, for seedset by age  
-* Only HEPU, LEES show significant decline, but again mostly negative slopes
+yvar <- "prop_propagule"
+xvar <- "total_weight"
+
+* Only EPMI shows a decline in prop propagule with increasing plant weight  
+* No species show an increase in prop propagule with increasing plant weight  
+* Of course the proportion of species with prop propagule > 0 increases with plant size
+
 ```{r, echo=FALSE,message=FALSE}
-yvar <- "seedset"
-xvar <- "age"
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "prop_propagule"
+xvar <- "total_weight"
 
-data <- subset(SummaryInd, seedset>0&seedset<1)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-* A number of species show declines in accessory costs with age, but this effect disappears once you include only individuals that set *any* seed
-```{r, echo=FALSE,message=FALSE}
-yvar <- "prop_accessory"
-xvar <- "age"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-* 8 of the 14 species show declines in allocation to pre-pollination tissues with increasing age
-```{r, echo=FALSE,message=FALSE}
-yvar <- "prop_prepollen_all"
-xvar <- "age"
-
-data <- subset(SummaryInd)
+data <- subset(SummaryInd,prop_propagule>0)
 data <- split(data, data$species)
@@
 ##Overall results
-- Accessory costs higher for bigger seeds
-
-- Accessory costs higher for bigger species; these are the same species that invest less in RA
-
 - Of course there is also a correlation between seed size and plant size, but actually not as strong as the accessory cost one, presumably because older plants have lower accessory costs as well as species that are inherently bigger

### 2015-08-05 results_growth_short.Rmd
continuing to clean up little bits of analyses
found several little mistakes...

@@
 
-###Plants that allocate more to reproduction (higher RA) have a lower RGR
-- When looked at individually, this pattern holds for all species except PEPU and PELA, although there is lots of variation in the exact trade-off pattern displayed by different species  
-- You can also look at the plots of RGR vs RA and identify the RA at which RGR is impacted.
-Some plots show a very linear decline throught, whereas for others there is a distinct "knickpoint" -i.e.
-BOLE, EPMI, HATE
-- More robust curve-fitting techniques are required to better illustrate this pattern (**CURVE FITTING**)
+###Plants that allocate more to reproduction (higher RA) have lower growth
+- When looked at individually, this pattern holds for most species, although there is lots of variation in the exact trade-off pattern displayed by different species  
+    * when plotted again stem diameter increment, most species show a distinctly linear pattern - decline in stem diameter increment fairly exactly offset by increases in RA across all individuals of the species
+    * for plots of RGR vs RA some species have a distinct "knickpoint" where growth impacted -i.e. BOLE, EPMI, HATE
 
-```{r, echo=FALSE,message=FALSE}
+```{r, echo=FALSE,message=FALSE, warning=FALSE}
 par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
@@
 
-mod <- lm(log(growth_stem_area)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
-plot((RA+.01)~growth_stem_area, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(prop_growth_stem_diam)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
+plot((RA+.01)~prop_growth_stem_diam, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 plot((RA+.01)~(prop_growth_height), data=subset(SummaryInd,species!="PEPU"&species!="PELA"), log="xy", col=col.spp[as.factor(species)],pch=16)
-
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.top.right.logxy(mod)
-
-mod <- lm(log(growth_height)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&growth_height>0))
-plot((RA+.01)~(growth_height), SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
 ```
 
+```{r, echo=FALSE,message=FALSE, warning=FALSE}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "growth_stem_diam"
+xvar <- "RA"
+
+data <- subset(SummaryInd,RA>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  asin(sqrt(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",
+                    main=spp)
+    }
+
+mtext("RA", 1, outer=TRUE,cex=1.2)
+mtext("Yearly increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
+```
 ###PCA analysis indicates the same two patterns

### 2015-08-06 Panalysis.rmd
new file on details of errors to fix - same info as in "issues" I've posted
new file that is follow up on today's conversation with Mark and needs to be intregrated into other files

continued bits of other work, mostly trying to tidy up accessory tissue thoughts

@@
 
-check <- PEPU_Investment
-check_FD <-check[3]
-View(check_FD)
-check3 <- subset(check_FD,FD.what=="cone_aborted")
+check_FD <-as.data.frame(PEPU_Investment[3])
+check_FD_aborted <- subset(check_FD,FD.what=="cone_aborted")
+check_FD_aborted
 
-names(check_FD)
+check_parts <- subset(as.data.frame(PEPU_FlowerPartsData),what=="cone_aborted")
+check_parts <- subset(as.data.frame(PEPU_FlowerPartsData),part=="cone_aborted")
+check_parts
+
+names(check_parts)
 

### 2015-08-06 results_accessory_v3.Rmd
new file on details of errors to fix - same info as in "issues" I've posted
new file that is follow up on today's conversation with Mark and needs to be intregrated into other files

continued bits of other work, mostly trying to tidy up accessory tissue thoughts

@@
 1. Total reproductive investment is the best correlate with total plant size (or growth investment)  
+2. Accessory costs are enormous across all species
 2.
@@
 5. Species differ enormously in their relative investment in different reproductive tissue types
+6.
+Lower pre-pollination costs in plants with higher RA: 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases.
+in other words, they get better returns on investment the more they invest.
+(This is just a pattern within, not across, species)
 
@@
 flowers (I do know aborted buds decrease)
+
+###Looking at reproductive investment, total accessory tissue investment, and pre-pollination tissue investment  
+* Something needs fixing here, for there are points that have higher accesory investment than reproductive investment  
+* Also, don't think the results for PUTU and PILI are accurate
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
+plot(accessory_inv~ReproInv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
+abline(0,1)
+abline(-0.30103,1)
+abline(-1,1)
+text(120,350,"all RE to accessory tissues",srt=43)
+text(12000,720,"10% RE to accessory tissues",srt=43)
+text(5,1.5,"50%",srt=43)
+
+plot(prepollen_all_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
+abline(0,1)
+abline(-0.30103,1)
+abline(-1,1)
+text(120,250,"all acc costs pre-pollination",srt=45)
+text(3000,180,"10% acc costs pre-pollination",srt=45)
+text(10,3,"50%",srt=45)
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+```
 
@@
 ```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
+options(scipen=10)
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
@@
 
-plot(seed_count~asin(sqrt(prop_accessory)),SummaryInd, log="y", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="proportion of reproduction to accessory tissues (asin)",cex=.9)
+plot(seed_count~(prop_accessory),SummaryInd, log="y", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="proportion of reproduction to accessory tissues",cex=.9)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 ```
-###Do accessory costs shift with seed size?
+
+### Do accessory costs shift with seed size?
     * These plots presented using both accessory cost calculations
@@
     - And: species with greater prepollination investment have higher accessory costs (since this is the majority of accessory costs for most species)  
-    - When all 4 variables put into a single model, regardless of "accessory cost" calculation, seedset always by far the most significant correlate   
-        * seed size is least frequently a correlate in models, although of course highly significant when analyzed on its own
+    - When all 4 variables put into a single model, depending on lots of little changes, different factors (seedset, seed size, maxH-species, pre-pollination costs come out as have the best explanatory power)
 
@@
         * This is true at the species and individual level.
-
-mod <- lm(log(accessory_per_seed)~(seedset)*log(prepollen_all_inv)*log(total_weight)*log(seed_size),data=subset(SummaryInd,seedset>0&prepollen_all_per_seed>0))
-summary(mod)
 
@@
 points(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
-mtext("Seed size (mg)",1, outer=TRUE,cex=1.2)
+mtext("seed size (mg)",1, outer=TRUE,cex=1.2)
 
@@
 words.bottom.right.logx(mod)
-mtext("Total plant weight (mg)",1, outer=TRUE,cex=1.2)
+mtext("total plant weight (mg)",1, outer=TRUE,cex=1.2)
 
@@
 mod <- lm(log(seedset_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",cex=0.9)
+plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=0.9)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
-plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp[as.factor(species)],xlab="costs to make 1 seed (mg)",cex=1.2)
+plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp[as.factor(species)],xlab="costs to make 1 seed (mg)",ylab="seed size (mg)",cex=1.2)
 mod <- lm(seedcosts~seed_size, SummarySpp)
-words.bottom.right.logxy(mod)
+abline(0,1)
+abline(-1,1)
+abline(-2,1)
+text(5,6.5,srt=40,"no accessory costs")
+text(2.5,.35,srt=40,"90%")
+text(7,.1,srt=40,"accessory costs = 99%")
+words.top.left.logxy(mod)
 text(seed_size~seedcosts,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")
@@
 
-###Seedset,seed count by age, size, RA
 * Replotting the seedset data by age, showing that the correlation between seedset and accessory costs is not age related
@@
 
-* There is no overall shift in either seedset or proportional allocation to propagules with increasing RA  
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7,warning=FALSE}
-par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
+###Does increasing RA yield compounding returns in the form of higher seedset or increased propagule allocation?
+* NO - seedset and relative propagule investment do not increase with increasing RA 
+* Furthermore, looking within species  
+    - Not a single species shows an increase in prop_propagule with increasing RA  
+    - And for seedset vs RA, only HATE shows an increase, and HEPU a decrease  
+    - So no, there are no compounding benefits to increasing RA
+
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
+par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
 mod <- lm(asin(sqrt(seedset))~asin(sqrt(RA)),data=subset(SummaryInd,seedset>0&seedset<1))
@@
 mod <- lm(asin(sqrt(prop_propagule))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(RA))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), log="x", pch=16,col=col.spp[as.factor(species)])
+plot(asin(sqrt(RA))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+words.bottom.right(mod)
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mod <- lm(asin(sqrt(propagule_per_seed))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
+plot(asin(sqrt(RA))~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="x",pch=16,col=col.spp[as.factor(species)])
 words.bottom.right.logx(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 ```
 
-* Furthermore, looking within species  
-    - Not a single species shows an increase in prop_propagule with increasing RA  
-    - And for seedset vs RA, only HATE shows an increase, and HEPU a decrease  
-    - So no, there are no compounding benefits to increasing RA
+###Does increasing overall reproductive investment yield compoinding returns in the form of higher seedset or increased propagule allocation?  
+* Not within species - as total reproductive investment increases there are no within species shifts with respect to seed set, proportional propagule allocation, or propagule allocation per seed
+* Plotting all data shows the between species effect - that species with larger adult plants have lower seedset and proportional propagule investment  
+* the third plot shows scatter for species where some (or all) individuals have actual seeds weighed, but not for species that really just have a mean seed weight plugged in for all individuals
 
-```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7,warning=FALSE}
-yvar <- "RA_asin"
-xvar <- "seedset"
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
+par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
+options(scipen=20)
+mod <- lm(asin(sqrt(seedset))~log(ReproInv),data=subset(SummaryInd,seedset>0&seedset<1))
+plot((ReproInv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
+words.bottom.right.logy(mod)
 
-data <- subset(SummaryInd,seedset>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(x[[yvar]] ~  asin(sqrt(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
+mod <- lm(asin(sqrt(prop_propagule))~log(ReproInv),data=subset(SummaryInd,prop_propagule>0))
+plot((ReproInv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
+words.bottom.right.logy(mod)
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-* And there are absolutely no patterns of interest relative to seed count   
-    * it doesn't even correlate very well with RA or plant size
-
-###Relationship between tissue allocation and reproductive investment
-* these data also tell the story of seedset being an important "component" and being lower in bigger species
-* Proportion pre-pollination costs completely unrelated to reproductive investment
-* However, proportional investment in propagules decreases with increasing reproductive investment, because the bigger species investment more overall in reproduction and less in propagules
-* There is also no pattern with respect to proportional investment in packaging and dispersal (R^2=0, p-value=0.959) and a slight decrease in aborted post-pollination tissues with increasing reproductive investment (R^2=0.0661, p-value=0.0002)
-```{r, echo=FALSE,message=FALSE, ,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
-mod <- lm(log(ReproInv)~(prop_prepollen_all),data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1))
-plot((prop_prepollen_all)~ReproInv,data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1), log="x", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Pre-pollination tissues (as proportion repro inv)")
-words.top.right.logx(mod)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-options(scipen=5)
-mod <- aov(log(ReproInv)~species*log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
-summary(mod)
-
-options(scipen=20)
-mod <- lm(log(ReproInv)~species*log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
-plot(prop_propagule~ReproInv,data=subset(SummaryInd,prop_propagule>0), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Propagules (as proportion repro inv)")
-words.top.right.logxy(mod)
-mtext("Reproductive investment (mg)",1, outer=TRUE,cex=1.1)
-```
-
-###What happens against RA
-* Overall RA is correlated with reproductive investment and age
-* These plots only include individuals that have some reproductive investment
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(0.3,0.3,0.1,0.3), mai=c(1.1,1,0.3,0.3)) 
-mod <- lm(log(RA)~log((ReproInv)),data=subset(SummaryInd,RA>0))
-plot(RA~(ReproInv),data=subset(SummaryInd,RA>0), pch=16,col=col.spp[as.factor(species)],log="xy")
-words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-mod <- lm(log(RA)~species*age*log((ReproInv)),data=subset(SummaryInd,RA>0))
-anova(mod)
-
-mod <- lm(log(RA)~log((age)),data=subset(SummaryInd,RA>0))
-plot(RA~(age),data=subset(SummaryInd,RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="")
+mod <- lm(log(propagule_per_seed)~log(ReproInv),data=subset(SummaryInd,seedset>0&seedset<1))
+plot((ReproInv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp[as.factor(species)])
 words.bottom.right.logxy(mod)
@@
 
-* RA is also correlated with count of floral units - the total number of buds produced (i.e. final development stage can be buds, flowers, aborted fruit or fruit)
-* This is true for many individual species as well as across species
+###Does seedset or allocation to propagules shift with prop_maxH?
+* Not within species - looked at within species regressions for prop_maxH against seedset, prop_propagule, propagule_per_seed and no consistent patterns  
+* However there is a strong across species effect, such that species where more of the reproducing individuals have lower "prop_maxH" have higher seed set vs. the opposites  
+* This indicates that species that begin reproducing at smaller sizes have higher seedset  
+    * We already knew that individuals from species with shorter Hmax and individuals that are overall shorter have higher seedset  
+    * In part this is suggetsing that the species with high seedset have, on average, mostly individuals that are much 
+      shorter than the maxH achieved and that reproduction is curtailing their growth even more than maxH_spp indicates
 
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
-mod <- lm(log(RA)~log(repro_all_count),data=subset(SummaryInd,repro_all_count>0))
-plot(repro_all_count~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp[as.factor(species)],pch=16,log="xy",ylab="# of buds produced",xlab="")
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-mtext("RA",1, outer=TRUE,cex=1.1)
-```
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14,warning=FALSE}
+par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
+options(scipen=20)
+mod <- lm((prop_maxH)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(asin(sqrt(seedset))~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+words.bottom.right(mod)
 
-```{r, echo=FALSE,message=FALSE,fig.width=28, fig.height=28}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "repro_all_count"
-xvar <- "RA_asin"
+mod <- lm(log(height)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(asin(sqrt(seedset))~(height),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="x")
+words.bottom.right.logx(mod)
 
-data <- subset(SummaryInd, repro_all_count>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
+mod <- lm((prop_maxH)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,prop_propagule>0))
+plot(asin(sqrt(prop_propagule))~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+words.bottom.right(mod)
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",
-                    main=spp)
-    }
+mod <- lm((prop_maxH)~log(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1))
+plot((propagule_per_seed)~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), log="y",pch=16,col=col.spp[as.factor(species)])
+words.bottom.right.logy(mod)
 ```
@@
 ###What causes the correlation between RA and plant size (or total reproductive investment)?
-* Do plants invest equally more in all reproductive tissues as they get bigger or do they increase allocation to certain types of reproductive tissues more than others?
-
-* If they shifted their proportional investment, there would be a relationship between RA and the proportional investment in 1 (or more) of the 5 reproductive energy pools.
-If they do not shift their proportional investment, all 5 would have no relationship.
-      * Only "proportional energy to pre-pollination aborted tissues" shows a significant decline with increasing RA - and it has a very convincing decline.   
-      * Since no other pool shows an increase in proportional investment, that extra energy must be distributed fairly randomly across other pools
-
-* Simultaneously, all tissue pools should show a positive relationship between actual investment amounts (mg) and RA  
-      * However, only "pre-pollination successful tissues" and "energy to propagules" have a convincing r-squared value (across all species)
-
-* It might be interesting to look at this pattern by species
-
 ```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=30}
@@
 
-* Plants that invest more in some reproductive tissues, on average, invest more in other reproductive tissues, so have a higher RA
+### Looking at the same patterns against maxH
 
-  * This same pattern is true just looking  at energy invested in pre-pollination tissues and at propagule allocation
+```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=36}
+par(mfrow=c(6,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
 
-* Plants with higher RA have lower allocation to pre-pollination tissues, probably because of their higher seedset
-* Relationship between RA and proportion energy to propagules simply shows a species effect - different species have different RA values and different proportional propagule investment
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm(log(RA)~log((prepollen_all_inv)),data=subset(SummaryInd,RA>0&prepollen_all_inv>0))
-plot(prepollen_all_inv~(RA),data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination tissues (mg)")
-words.bottom.right.logxy(mod)
+mod <- lm((prop_maxH)~log((ReproInv)),data=subset(SummaryInd,prop_maxH>0&ReproInv>0))
+plot(ReproInv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="total reproductive investment (mg)")
+words.bottom.right.logy(mod)
 
+mod <- lm((prop_maxH)~asin(sqrt(RA)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(RA))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="RA")
+words.bottom.left(mod)
+
+mod <- lm((prop_maxH)~log((propagule_inv)),data=subset(SummaryInd,prop_maxH>0&propagule_inv>0))
+plot(propagule_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to propagules (mg)")
+words.bottom.right.logy(mod)
+
+mod <- lm((prop_maxH)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(prop_propagule))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+words.bottom.left(mod)
+
+mod <- lm((prop_maxH)~log((prepollen_aborted_inv)),data=subset(SummaryInd,prop_maxH>0&prepollen_aborted_inv>0))
+plot(prepollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="y",ylab="pre-pollination aborted tissues (mg)")
+words.bottom.right.logy(mod)
+
+mod <- lm((prop_maxH)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(prop_prepollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
+words.bottom.left(mod)
+
+mod <- lm((prop_maxH)~log((prepollen_success_inv)),data=subset(SummaryInd,prop_maxH>0&prepollen_success_inv>0))
+plot(prepollen_success_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_success_inv>0), pch=16,col=col.spp[as.factor(species)],log="y",ylab="pre-pollination successful tissues (mg)")
+words.bottom.right.logy(mod)
+
+mod <- lm((prop_maxH)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(prop_prepollen_success))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
+words.bottom.left(mod)
+
+mod <- lm((prop_maxH)~log((packaging_dispersal_inv)),data=subset(SummaryInd,prop_maxH>0&packaging_dispersal_inv>0))
+plot(packaging_dispersal_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to packaging and dispersal (mg)")
+words.bottom.right.logy(mod)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-mod <- lm(log(RA)~log((propagule_inv)),data=subset(SummaryInd,RA>0&propagule_inv>0))
-plot(propagule_inv~(RA),data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
-words.bottom.right.logxy(mod)
 
-mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_prepollen_all)),data=subset(SummaryInd,RA>0&prop_prepollen_all>0))
-plot(asin(sqrt(prop_prepollen_all))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&prop_prepollen_all>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination tissues (as proportion repro inv) (asin)")
-words.top.right(mod)
+mod <- lm((prop_maxH)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(prop_packaging_dispersal))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
+words.bottom.left(mod)
 
-mod <- lm(log(RA)~log((prop_propagule)),data=subset(SummaryInd,RA>0&prop_propagule>0))
-plot((prop_propagule)~(RA),data=subset(SummaryInd,RA>0&prop_propagule>0), log="xy", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
-words.bottom.left.logxy(mod)
-```
+mod <- lm((prop_maxH)~log((postpollen_aborted_inv)),data=subset(SummaryInd,prop_maxH>0&postpollen_aborted_inv>0))
+plot(postpollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to tissues aborted postpollination (mg)")
+words.bottom.right.logy(mod)
 
-###Shifts across age and height
-* Seedset shows a slight decrease with proportional plant height (the best proxy for "relative size")  
-    * this pattern likely exists because species that begin reproducing at shorter proportional heights have higher seedset  
-    * only LEES shows a significant decline
-
-* the same analysis can be done on seedset by age, with similar response    
-    * Only HEPU, LEES show significant decline
-
-yvar <- "seedset"
-xvar <- "prop_maxH""
-```{r, echo=FALSE,message=FALSE}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))  
-mod <- lm((prop_maxH)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset<1&seedset>0))
-plot(asin(sqrt(seedset))~prop_maxH,data=subset(SummaryInd,seedset<1&seedset>0), pch=16,col=col.spp[as.factor(species)])
-words.top.right(mod)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-yvar <- "seedset"
-xvar <- "prop_maxH"
-
-data <- subset(SummaryInd, seedset>0&seedset<1)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-yvar <- "prop_propagule"
-xvar <- "total_weight"
-
-* Only EPMI shows a decline in prop propagule with increasing plant weight  
-* No species show an increase in prop propagule with increasing plant weight  
-* Of course the proportion of species with prop propagule > 0 increases with plant size
-
-```{r, echo=FALSE,message=FALSE}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "prop_propagule"
-xvar <- "total_weight"
-
-data <- subset(SummaryInd,prop_propagule>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
+mod <- lm((prop_maxH)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(prop_postpollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
+words.bottom.left(mod)
 ```
@@
 - Reasonably idiosyncratic patterns  
+- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e.
+Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers
 - COER, EPMI, LEES, PILI invest the most energy in propagules  
@@
 ```
-
-```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=36}
-par(mfrow=c(6,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
-
-mod <- lm((prop_maxH)~log((ReproInv)),data=subset(SummaryInd,prop_maxH>0&ReproInv>0))
-plot(ReproInv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="total reproductive investment (mg)")
-words.bottom.right.logy(mod)
-
-mod <- lm((prop_maxH)~asin(sqrt(RA)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(RA))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="RA")
-words.bottom.left(mod)
-
-mod <- lm((prop_maxH)~log((propagule_inv)),data=subset(SummaryInd,prop_maxH>0&propagule_inv>0))
-plot(propagule_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to propagules (mg)")
-words.bottom.right.logy(mod)
-
-mod <- lm((prop_maxH)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_propagule))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
-words.bottom.left(mod)
-
-mod <- lm((prop_maxH)~log((prepollen_aborted_inv)),data=subset(SummaryInd,prop_maxH>0&prepollen_aborted_inv>0))
-plot(prepollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="y",ylab="pre-pollination aborted tissues (mg)")
-words.bottom.right.logy(mod)
-
-mod <- lm((prop_maxH)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_prepollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
-words.bottom.left(mod)
-
-mod <- lm((prop_maxH)~log((prepollen_success_inv)),data=subset(SummaryInd,prop_maxH>0&prepollen_success_inv>0))
-plot(prepollen_success_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_success_inv>0), pch=16,col=col.spp[as.factor(species)],log="y",ylab="pre-pollination successful tissues (mg)")
-words.bottom.right.logy(mod)
-
-mod <- lm((prop_maxH)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_prepollen_success))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
-words.bottom.left(mod)
-
-mod <- lm((prop_maxH)~log((packaging_dispersal_inv)),data=subset(SummaryInd,prop_maxH>0&packaging_dispersal_inv>0))
-plot(packaging_dispersal_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to packaging and dispersal (mg)")
-words.bottom.right.logy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-mod <- lm((prop_maxH)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_packaging_dispersal))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
-words.bottom.left(mod)
-
-mod <- lm((prop_maxH)~log((postpollen_aborted_inv)),data=subset(SummaryInd,prop_maxH>0&postpollen_aborted_inv>0))
-plot(postpollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to tissues aborted postpollination (mg)")
-words.bottom.right.logy(mod)
-
-mod <- lm((prop_maxH)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_postpollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
-words.bottom.left(mod)
-```
-
-#Shifts in accessory costs across species and ages
-##Overall results
-- Of course there is also a correlation between seed size and plant size, but actually not as strong as the accessory cost one, presumably because older plants have lower accessory costs as well as species that are inherently bigger
-
-- A number of species show fairly consistent declines in accessory costs with various measures of "bigger", including size, age, RA. Other species show no patterns  
-- Lower pre-pollination costs in plants with higher RA: 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases.
-in other words, they get better returns on investment the more they invest.
-(This is just a pattern within, not across, species)
-- Species very different in which accessory tissues they invest the most in - which reflects the differences in basic structure (i.e.
-Banksia cones), but also more subtlely that some species abort lots of buds (pre-pollination aborted), while other species abort more fully formed flowers
-- Haven't actually run all the tests, but assume all reproductive tissue types will differ in proportional allocation across species
-- For most of the statistical analyses, the youngest site has been removed, since it included individuals that were harvested while flowering (and therefore never "got to" set fruit) and automatically have no "successful" reproduction.
-There are of course some individuals like this at other ages as well, but far fewer

### 2015-08-06 results_growth_short.Rmd
new file on details of errors to fix - same info as in "issues" I've posted
new file that is follow up on today's conversation with Mark and needs to be intregrated into other files

continued bits of other work, mostly trying to tidy up accessory tissue thoughts

@@
 ```
-
 ```{r, echo=FALSE,message=FALSE, warning=FALSE}
@@
 ```
+
+```{r, echo=FALSE,message=FALSE, warning=FALSE}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "RA"
+xvar <- "age"
+
+data <- subset(SummaryInd,RA>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",
+                    main=spp,xlim=c(1,35))
+}
+
+mtext("RA", 1, outer=TRUE,cex=1.2)
+mtext("age", 2, outer=TRUE,cex=1.2)
+```
+
+```{r, echo=FALSE,message=FALSE, warning=FALSE}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "RA"
+xvar <- "diameter"
+
+data <- subset(SummaryInd,RA>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  log(x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",
+                    main=spp)
+}
+
+mtext("RA", 1, outer=TRUE,cex=1.2)
+mtext("basal diameter", 2, outer=TRUE,cex=1.2)
+```
+
 ###PCA analysis indicates the same two patterns

### 2015-08-06 Mark_20150806_ideas.R

@@ -1,0 +1,273 @@
+###RV curves by species
+```{r, echo=FALSE,message=FALSE, warning=FALSE}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "ReproInv"
+xvar <- "total_weight"
+
+data <- subset(SummaryInd,RA>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
+                    main=spp)
+}
+
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "total_repro_inv"
+xvar <- "total_weight"
+
+data <- subset(SummaryInd,RA>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
+                    main=spp)
+}
+
+
+mtext("Plant size (mg)", 1, outer=TRUE,cex=1.2)
+mtext("Reproductive investment (mg)", 2, outer=TRUE,cex=1.2)
+```
+###Vegetative growth by plant size
+```{r, echo=FALSE,message=FALSE, warning=FALSE}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "GrowthInv"
+xvar <- "total_weight"
+
+data <- subset(SummaryInd,RA>0)
[…]

### 2015-08-11 Accessory_figs.rmd
- continuing to narrow down figures for Accessory manuscript
- lots of reworking of PCA, including figuring out how to sort variables

- PCA now without RGR

--- 2015-08-06 results_accessory_v3.Rmd
@@
 ```
+#Summary  
+1. Total reproductive investment (vs. propagule investment or fruit investment) shows the strongest correlation with total plant size
+2. Accessory costs represent the majority of reproductive investment  
+3. Accessory costs are higher in large species, species with low seedset, and species with large seeds
+4. Accessory costs within a species do not shift with increasing RA, total reproductive investment, or prop_maxH, 
+indicating no compounding returns with greater relative or absolute reproductive investment or with aging (not sure what manuscript this goes in)
+5. There are ACROSS species shifts in investment going to some of the 5 tissue pools with increasing RA:  
+      ***waiting for correct calculations to draw conclusions for 5***
+6. Proportion of reproductive investment going to each of the 5 tissue pools (pre-pollen aborted, pre-pollen successful, post-pollen aborted, packaging&dispersal, propagule) 
+is idiosyncratic across species
 
-#Accessory costs
-##Basic questions
-* Total reproductive investment can be divided into energy invested in propagules vs. other reproductive tissues (accessory costs)
-* Reproductive investment can be considered on an energy or "count" (fecundity) basis
-
-    1. What reproduction "pool" should one measure?
-        * Is fecundity good enough?
-        * Is fruit or propagule weight good enough?
-    2. What might cause shifts in accessory costs across species?
-        * Previous studies have shown smaller-seeded species have lower accessory costs.
-    3. How does alotment to different accessory tissue types shift within a species as it ages, grows, or increases RA? 
-        * If accessory costs decrease with increased RA, increasing RA yields compounding returns.
-
-##Summary of outcomes
-1. Total reproductive investment is the best correlate with total plant size (or growth investment)  
-2. Accessory costs are enormous across all species
-2.
-Plants with smaller seeds, smaller adult sizes, and higher seedset have lower accessory costs.
-It is mathematically plausable that the concept of "accessory costs" is not all that different from "seed set"
-    * In other words, plants with higher seed set, have lower accessory costs due to calculations
-    * Across  the 14 species, plants with larger adult size have lower seed set.
-3. Bigger plants have higher RA. 
-    * Plants that produce more buds, invest more absolute energy into either pre-pollination tissues or propagules also have higher RA.
-    * As plants get bigger, there is a slight shift of energy from pre-pollination tissues to propagules, but this is a small effect 
-    *(i.e. accessory costs decline slightly with increasing plant size)
-4. Among reproducing individuals, bigger or older plants DO NOT have higher seedset, although more individuals become reproductively mature over time. 
-    * Proportional pre-pollination costs also decrease with plant age in most species
-5. Species differ enormously in their relative investment in different reproductive tissue types
-6.
-Lower pre-pollination costs in plants with higher RA: 9 (of 14) species decrease the proportion of reproductive investment in "pre-pollination" tissues as their RA increases.
-in other words, they get better returns on investment the more they invest.
-(This is just a pattern within, not across, species)
-
-###Still thinking about
-1.
-Most analyses look at propagules and pre-pollination tissues, but allocation can be further divided - it would be interesting to look at proportion energy to aborted buds vs.
-flowers (I do know aborted buds decrease)
-
-###Looking at reproductive investment, total accessory tissue investment, and pre-pollination tissue investment  
-* Something needs fixing here, for there are points that have higher accesory investment than reproductive investment  
-* Also, don't think the results for PUTU and PILI are accurate
+##1. Total reproductive investment is the best correlate with total plant size 
+* Measuring total reproductive output has a much stronger correlation than investment in fruit weight or propagules
+* The regression of total weight against prepollination investment is as good as total reproductive investment - one could just count buds + flowers!
+    * This is likely because prepollination investment is much a large proportion of total reproductive investment
+* Note that each of these figures (and models) only includes individuals with non-zero investment in the reproductive pool plotted
+* Important for research that wishes to predict reproductive investment from plant size  
+* Of course propagule investment is the correlate with seed count
 
 ```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
+options(scipen=10)
+par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
+mod <- lm (log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
+plot(ReproInv~total_weight,data=subset(SummaryInd,ReproInv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
+words.bottom.right.logxy(mod)
+
+mod <- lm (log(total_weight)~log(fruit_weight), data=subset(SummaryInd,fruit_weight>0))
+plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Fruit investment (mg)",xlim=c(100,2000000),xlab="")
+words.bottom.right.logxy(mod)
+
+mod <- lm (log(total_weight)~log(propagule_inv), data=subset(SummaryInd,propagule_inv>0))
+plot(propagule_inv~total_weight,data=subset(SummaryInd,propagule_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+mod <- lm (log(total_weight)~log(prepollen_all_inv), data=subset(SummaryInd,prepollen_all_inv>0))
+plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Prepollen investment (mg)", xlim=c(100,2000000))
+legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+mtext("Total plant size (mg)",1, outer=TRUE,cex=1.2)
+```
+
+##2. Accessory costs are the majority of reproductive investment for most species  
+* Also, most accessory costs are due to pre-pollination investment
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=7.5}
 par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-plot(accessory_inv~ReproInv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
+plot(accessory_inv~ReproInv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)],
+     xlim=c(1,700000),ylim=c(1,700000),xlab="Total reproductive investment (mg)",ylab="Investment in accessory tissues (mg)")
 abline(0,1)
@@
 abline(-1,1)
-text(120,350,"all RE to accessory tissues",srt=43)
-text(12000,720,"10% RE to accessory tissues",srt=43)
-text(5,1.5,"50%",srt=43)
+text(120,350,"all RE to accessory tissues",srt=45)
+text(12000,720,"10% RE to accessory tissues",srt=45)
+text(5,1.5,"50%",srt=45)
 
-plot(prepollen_all_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
+plot(prepollen_all_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)],
+     xlim=c(1,700000),ylim=c(1,700000),ylab="Investment in pre-pollination tissues (mg)",xlab="Investment in all accessory tissues (mg)")
 abline(0,1)
@@
 
-##Which measure of reproductive output best correlates with plant size or growth
-* Measuring total reproductive output has a much stronger correlation than investment in fruit weight or propagules
-* The regression of total weight against prepollination investment is as good as total reproductive investment - one could just count buds + flowers!
-    * This is likely because prepollination investment is much a large proportion of total reproductive investment
-* Note that each of these figures (and models) only includes individuals with non-zero investment in the reproductive pool plotted
-
-```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
-options(scipen=10)
-par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
-mod <- lm (log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot(ReproInv~total_weight,data=subset(SummaryInd,ReproInv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
-words.bottom.right.logxy(mod)
-
-mod <- lm (log(total_weight)~log(fruit_weight), data=subset(SummaryInd,fruit_weight>0))
-plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Fruit weight (mg)",xlim=c(100,2000000),xlab="")
-words.bottom.right.logxy(mod)
-
-mod <- lm (log(total_weight)~log(propagule_inv), data=subset(SummaryInd,propagule_inv>0))
-plot(propagule_inv~total_weight,data=subset(SummaryInd,propagule_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-
-mod <- lm (log(total_weight)~log(prepollen_all_inv), data=subset(SummaryInd,prepollen_all_inv>0))
-plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="prepollen investment (mg)", xlim=c(100,2000000))
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-words.bottom.right.logxy(mod)
-
-mtext("Total plant size (mg)",1, outer=TRUE,cex=1.2)
-```
-
-### Comparing accessory cost calculations expressed as "per successful seed" versus "proportion reproductive investment"  
-  - The difference between the two calculations is seed count
-  - calculating accessory costs on a per seed basis stratify the data much more by species 
-      * this is because the species that have more seeds (lower proportional accessory costs), also have higher seedset
-  - Calculations per seed tell you energy input relative to fecundity
-```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=7}
-options(scipen=10)
-par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(1.1,1,0.3,0.3)) 
-mod <- lm(log(seed_count)~species*accessory_per_seed,data=subset(SummaryInd,seed_count>0))
-plot(seed_count~accessory_per_seed,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="seed count",xlab="accessory costs per successful seed (mg)",cex=.9)
-words.bottom.left.logxy(mod)
-
-plot(seed_count~(prop_accessory),SummaryInd, log="y", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="proportion of reproduction to accessory tissues",cex=.9)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-```
-
-### Do accessory costs shift with seed size?
-    * These plots presented using both accessory cost calculations
-
+##3. What do accessory costs correlate with?
 Results:  
@@
     - And: species with greater prepollination investment have higher accessory costs (since this is the majority of accessory costs for most species)  
-    - When all 4 variables put into a single model, depending on lots of little changes, different factors (seedset, seed size, maxH-species, pre-pollination costs come out as have the best explanatory power)
+    - When all 4 variables put into a single model, depending on how variables expressed, transformed, different factors (seedset, seed size, maxH-species, pre-pollination costs) come out as have the best explanatory power
 
@@
     - Not sure one can separate the effect of plant size, seed set, seed size on what drive accessory costs  
-    - the reason seed set is strongly correlated, is because if flowers are pollinated and develop into mature seeds, the individual plant ends up investing more energy in reproduction and that extra energy is being invested into propagules, reducing accessory costs.
+    - the reason seed set is strongly correlated, is because if flowers are pollinated and develop into mature seeds, the individual plant ends up investing more energy in reproduction and that extra energy is being invested into propagules,
+    reducing accessory costs.
+
 * This is true at the species and individual level.
@@
 par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(.7,1,0.3,0.3))
-#mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+
 mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
@@
 
-#mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
 mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean)),SummarySpp)
@@
 
-#mod <- lm(log(total_weight)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
 mod <- lm(log(total_weight_mean)~log(accessory_per_seed_mean),SummarySpp)
@@
 
-#mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
 mod <- lm(log(total_weight_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
@@
 
-#mod <- lm(log(seedset)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
 mod <- lm(log(seedset_mean)~log(accessory_per_seed_mean),SummarySpp)
@@
 
-#mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
 mod <- lm(log(seedset_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
@@
 
-#mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
+par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(1.1,1,0.3,0.3))
 mod <- lm(log(prepollen_all_per_seed_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=0.9)
+plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",cex=0.9)
 points((accessory_per_seed_mean)~prepollen_all_per_seed_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
@@
 
-#mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
 mod <- lm(asin(sqrt(prop_prepollen_all_mean))~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=0.9)
+plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",cex=0.9)
 points(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
 words.bottom.right(mod)
-mtext("pre-pollination costs (proportional)",1, outer=TRUE,cex=1.2)
 ```
 
-### Plotting accessory costs that go into making a single seed
-- These calculations sum up all the tissue parts required to make a single seed, ignoring the cost of aborted tissues  
-- They are a bit rough at the moment, with estimates for the cost of tissues that support multiple seeds (i.e. a cone)
+###To discuss: Which measure of "accessory costs" should one use? 
+* "accessory costs per successful seed" vs "proportion of reproductive investment to accessory tissues"  
+* "per seed" is the formulation characteristically used and best relates the results to fecundity
+* the "per seed" variant greatly reduces the accessory costs of species that produce lots of seeds - and since species vary considerably in seed production it stratifies species more  
+* the "proportional" calculation essentially assumes total propagule investment (by weight) is equivalent, whether it is many small seeds or fewer big ones
 
-* Bigger seeds have bigger fixed costs of making that seed (1st plot)
-* But other than LEES having much lower costs, no shifts across species in their relative costs to make a seed (2nd plot); and LEES is one of the species where I use "propagule" not a single seed, so its "seed size" is higher and "accessory costs" slightly lower, since all fruit parts are part of the propagule
-* In other words, patterns of accessory costs vs. seed size, plant size, etc come about due to the differential effect of bud, flower abortion across species  
-```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
-plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp[as.factor(species)],xlab="costs to make 1 seed (mg)",ylab="seed size (mg)",cex=1.2)
-mod <- lm(seedcosts~seed_size, SummarySpp)
-abline(0,1)
-abline(-1,1)
-abline(-2,1)
-text(5,6.5,srt=40,"no accessory costs")
-text(2.5,.35,srt=40,"90%")
-text(7,.1,srt=40,"accessory costs = 99%")
-words.top.left.logxy(mod)
-text(seed_size~seedcosts,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")
+##4. Does increasing RA, Reproductive investment or relative height yield compounding returns in the form of higher seedset or increased propagule allocation?
 
-plot(seed_size~costs_per_seed,data=subset(SummarySpp),log="y",pch=16,col=col.spp[as.factor(species)],ylab="",xlab="proportional accessory costs, scaled by seed weight",cex=1.2)
-text(seed_size~costs_per_seed,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")
-mod <- lm(costs_per_seed~seed_size, SummarySpp)
-words.bottom.left.logy(mod)
-```
-
-* Replotting the seedset data by age, showing that the correlation between seedset and accessory costs is not age related
-* At most, there are most "old" plants with very low seedset  
-* these plots only include individuals with some seedset, thereby ignoring most young plants
-
-```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3))
-
-mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="proportion RE to propagules (1-accessory)",xlab="seed set")
-words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
-```
-
-###Does increasing RA yield compounding returns in the form of higher seedset or increased propagule allocation?
+###for RA:
 * NO - seedset and relative propagule investment do not increase with increasing RA 
@@
 
-###Does increasing overall reproductive investment yield compoinding returns in the form of higher seedset or increased propagule allocation?  
+###for total reproductive investment:  
 * Not within species - as total reproductive investment increases there are no within species shifts with respect to seed set, proportional propagule allocation, or propagule allocation per seed
@@
 
-###Does seedset or allocation to propagules shift with prop_maxH?
+###for proportional height:
 * Not within species - looked at within species regressions for prop_maxH against seedset, prop_propagule, propagule_per_seed and no consistent patterns  
@@
 
-###What causes the correlation between RA and plant size (or total reproductive investment)?
+###5. What influences the correlation between RA and plant size (or total reproductive investment)?
+  ***Don't trust anything until I know RA and ReproInv are correct, because PHPH and PUTU have huge influence on patterns
 ```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=30}
@@
 
-### Looking at the same patterns against maxH
-
-```{r, echo=FALSE, message=FALSE, fig.width=12, fig.height=36}
-par(mfrow=c(6,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
-
-mod <- lm((prop_maxH)~log((ReproInv)),data=subset(SummaryInd,prop_maxH>0&ReproInv>0))
-plot(ReproInv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="total reproductive investment (mg)")
-words.bottom.right.logy(mod)
-
-mod <- lm((prop_maxH)~asin(sqrt(RA)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(RA))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="RA")
-words.bottom.left(mod)
-
-mod <- lm((prop_maxH)~log((propagule_inv)),data=subset(SummaryInd,prop_maxH>0&propagule_inv>0))
-plot(propagule_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to propagules (mg)")
-words.bottom.right.logy(mod)
-
-mod <- lm((prop_maxH)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_propagule))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
-words.bottom.left(mod)
-
-mod <- lm((prop_maxH)~log((prepollen_aborted_inv)),data=subset(SummaryInd,prop_maxH>0&prepollen_aborted_inv>0))
-plot(prepollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="y",ylab="pre-pollination aborted tissues (mg)")
-words.bottom.right.logy(mod)
-
-mod <- lm((prop_maxH)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_prepollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
-words.bottom.left(mod)
-
-mod <- lm((prop_maxH)~log((prepollen_success_inv)),data=subset(SummaryInd,prop_maxH>0&prepollen_success_inv>0))
-plot(prepollen_success_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_success_inv>0), pch=16,col=col.spp[as.factor(species)],log="y",ylab="pre-pollination successful tissues (mg)")
-words.bottom.right.logy(mod)
-
-mod <- lm((prop_maxH)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_prepollen_success))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
-words.bottom.left(mod)
-
-mod <- lm((prop_maxH)~log((packaging_dispersal_inv)),data=subset(SummaryInd,prop_maxH>0&packaging_dispersal_inv>0))
-plot(packaging_dispersal_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to packaging and dispersal (mg)")
-words.bottom.right.logy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-mod <- lm((prop_maxH)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_packaging_dispersal))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
-words.bottom.left(mod)
-
-mod <- lm((prop_maxH)~log((postpollen_aborted_inv)),data=subset(SummaryInd,prop_maxH>0&postpollen_aborted_inv>0))
-plot(postpollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to tissues aborted postpollination (mg)")
-words.bottom.right.logy(mod)
-
-mod <- lm((prop_maxH)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_postpollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
-words.bottom.left(mod)
-```
-
-##Shifts in proportion to tissue types across species  
+##6. Shifts in proportion to tissue types across species  
 - Reasonably idiosyncratic patterns  
@@
 - HATE invests by far the least into propagules  
-```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=28}
+```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=28,warning=FALSE}
 par(mfrow=c(4,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  

### 2015-08-11 Growth_figs.rmd
- continuing to narrow down figures for Accessory manuscript
- lots of reworking of PCA, including figuring out how to sort variables

- PCA now without RGR

```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
library(remake)
create_bindings()

source("scripts/summary_dataframes.R")
source("scripts/functions.R")
```

##Summary
    1. Species show a marked decline in leaf investment with age and a most limited decline in stem investment with age
    2.

###1. Vegetative investment by size curves by species  
  * Individuals within a site show a remarkably linear increase in total vegetative investment with increasing size  
  * However, across species, there is a distinct decrease in the intercept of the line as plants age, turning into a scatter plot at the oldest sites
  * This is because of a rapid decrease in investment in leaves with age  
  * For most species there is only a decline in stem investment at the oldest sites

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "GrowthInv"
xvar <- "total_weight"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4,
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_leaf"
xvar <- "total_weight"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("Investment in leaves (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "growth_stem"
xvar <- "total_weight"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
```

###2. Plants that allocate more to reproduction (higher RA) have lower growth
* When plotted again stem diameter increment, most species show a distinct trade-off 
* The pattern is weaker for growth in shoot diameter

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "RA"
xvar <- "growth_stem_diam"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
                    main=spp,,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("Shoot diameter growth", 1, outer=TRUE,cex=1.2)
mtext("RA", 2, outer=TRUE,cex=1.2)  
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "RA"
xvar <- "growth_shoot_diam"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)

for(spp in names(data)) {
plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
                        main=spp,,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("Shoot diameter growth", 1, outer=TRUE,cex=1.2)
mtext("RA", 2, outer=TRUE,cex=1.2)  
```

###3.PCA analysis also indicates a decline in growth with increasing RA - as well as species level differences
* This combination of variables shows that RGR is approximately opposite a collection of variables that indicate a plant is "bigger" - so smaller plants have higher RGR
* Orthoganal to these in WD vs. maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
* I interpret this to mean that the three traits (Hmax, LMA, WD) strongly influence each other - presumably, Hmax a function of WD and LMA), but do not particularly 
* this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals, greatly reducing sample size. Including these variables, doesn't change the basic story.
* fine tuning:  
  ** remove RGR leaf (similar to RGR)
** remove prop_max_weight and prop_max_repro (similar to prop_maxH)

    plot(shoot_leaf_area_growth~total_weight,SummaryInd,col=col.spp[as.factor(species)],log="xy",pch=16)
```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
SummaryIndPCA <- SummaryInd %>%
  filter(lvs_end_total>0&shoot_leaf_area>0&shoot_leaf_area_growth!=0) %>%
  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
         growth_stem_diam,leaf_area,growth_shoot_diam,growth_stem_area,lvs_end_total,total_weight,
         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth,scaled_growth_stem_diam)

SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
SummaryIndPCA$height <- log(SummaryIndPCA$height)
SummaryIndPCA$maxH_spp <- log(SummaryIndPCA$maxH_spp)
SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
SummaryIndPCA$growth_shoot_diam <- log(SummaryIndPCA$growth_shoot_diam+.001)
SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
SummaryIndPCA$lvs_end_total <- log(SummaryIndPCA$lvs_end_total)
SummaryIndPCA$growth_stem_diam <- log(SummaryIndPCA$growth_stem_diam)
SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
SummaryIndPCA$shoot_leaf_area_growth <- log(SummaryIndPCA$shoot_leaf_area_growth)
SummaryIndPCA$scaled_growth_stem_diam <- log(SummaryIndPCA$scaled_growth_stem_diam)

PCA_mod <- prcomp(SummaryIndPCA, scale=TRUE)
summary(PCA_mod)
biplot(PCA_mod,xlim=c(-.1,.15),ylim=c(-.15,.1),cex=.8)

PCA_loadings <- as.data.frame(PCA_mod$rotation)
PCA_loadings$variables <- row.names(PCA_loadings)

PCA_scaling <- as.data.frame(PCA_mod$scale)
PCA_scaling$variables <- row.names(PCA_scaling)
names(PCA_scaling) <- c("scale","variables")
PCA_loadings <- merge(PCA_loadings,PCA_scaling,by="variables")

PCA_lambda <- as.data.frame(PCA_mod$sdev)

PCA_scores <- as.data.frame(PCA_mod$x)
PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$lvs_end_total>0&SummaryInd$shoot_leaf_area_growth!=0)
SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)

n <- NROW(PCA_scores)
scale =1

PCA_lambda <- PCA_lambda*sqrt(n)
PCA_lambda <- PCA_lambda^scale

SummaryInd_PCA_results$PC1_scale <- SummaryInd_PCA_results$PC1/PCA_lambda[1]
SummaryInd_PCA_results$PC2_scale <- SummaryInd_PCA_results$PC2/PCA_lambda[2]
SummaryInd_PCA_results$PC3_scale <- SummaryInd_PCA_results$PC3/PCA_lambda[3]
SummaryInd_PCA_results$PC4_scale <- SummaryInd_PCA_results$PC4/PCA_lambda[4]
PCA_loadings$PC1_scale <- PCA_loadings$PC1 / 4.5
PCA_loadings$PC2_scale <- PCA_loadings$PC2 / 4.5
PCA_loadings$PC3_scale <- PCA_loadings$PC3 / 4.5
PCA_loadings$PC4_scale <- PCA_loadings$PC4 / 4.5
```

#Looking at PCA by species
* I have removed RGR from the PCA and added in a scaled stem diameter measure  
* Although RGR and "Stem diameter increment" have a similar negative correlation with RA, RGR created a much easer to describe PCA - it fell out wonderfully opposite RGR and orthogonal to WD, seedsize, LMA, total plant size

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
  filter(complete.cases(SummaryInd_PCA_results$PC1_scale))

SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
  filter(complete.cases(SummaryInd_PCA_results$PC2_scale))

SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
  filter(complete.cases(SummaryInd_PCA_results$PC3_scale))

SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
  filter(complete.cases(SummaryInd_PCA_results$PC4_scale))

PCA_by_species <- SummaryInd_PCA_results %>%
  group_by(species) %>%
summarise_each(funs(mean, se), PC1_scale, PC2_scale, PC3_scale, PC4_scale)

PCA_by_age <- SummaryInd_PCA_results %>%
group_by(age) %>%
summarise_each(funs(mean, se), PC1_scale, PC2_scale, PC3_scale, PC4_scale)
```

###PCA axis 1 is across species  
* it separates species with high wood density (WD_mean), seedset, RA versus species with large total size, high leaf area, high LMA, large seedsize etc
* the age indepentent measures like prop_maxH and scaled_growth_stem_area have near-zero loadings
* BAER, HATE have by far the highest loadings and BOLE, COER, EPMI, HEPU, LEES, PILI the lowest  
* not sure why high wood density species also have high seedset - is this just by chance with my species?

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],xlim=c(-.1,.1))
arrows(0, 0, (.8*PCA_loadings$PC2_scale), (.8*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mean1 <- PCA_by_species$PC1_scale_mean
se1 <- PCA_by_species$PC1_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 1")
se_function(mean1,se1)

plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
legend("topright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")

mean1 <- PCA_by_age$PC1_scale_mean
se1 <- PCA_by_age$PC1_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 1")
se_function(mean1,se1)
```

###PCA axis 2 is about age  
* top variable loadings: shoot_leaf_area_growth and growth_shoot_diam vs repro_all_count, RA, prop_maxH - a collection of variables that shift fro each to late in life   
* COER, EPMI,PELA, and PEPU have the higher loadings and BOLE, LEES have the lowest, but mostly about age

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")

mean1 <- PCA_by_species$PC2_scale_mean
se1 <- PCA_by_species$PC2_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)

plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")

mean1 <- PCA_by_age$PC2_scale_mean
se1 <- PCA_by_age$PC2_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

#PCA axis 3 again divides by species
* top variable loadings: scaled_growth_stem_diam, WD_mean,growth_stem_diam, lvs_end_total vs. maxH_spp, LMA_mean, seed_size, RA  
* not terribly interpretable, since doesn't make sense that scaled_growth_stem_diam with WD_mean

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.15))

arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(1.1*PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=.8,col="black")

mean1 <- PCA_by_species$PC3_scale_mean
se1 <- PCA_by_species$PC3_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 3")
se_function(mean1,se1)

plot(PC3_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)],ylim=c(-.15,.15))
arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(1.1*PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")

mean1 <- PCA_by_age$PC3_scale_mean
se1 <- PCA_by_age$PC3_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

#PCA axis 4  
* this axis explains only 5% of the total, but quite interesting that it divides stem vs shoot growth variables  
* high loadings for growth_stem_area, growth_leaf, LMA_mean, seed_set vs low loadings for shoot_leaf_area_growth, WD_mean, prop_maxH, seed_size  
* BAER, EPMI, HATE and HEPU have higher values vs. BOLE, GRBU, GRSP with lower values; in a sense these later species have more shoot growth than stem growth and spend more of their life close to their maxH - which is true  
* there is no significant age component  
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))

plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.15))
arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

mean1 <- PCA_by_species$PC4_scale_mean
se1 <- PCA_by_species$PC4_scale_se
plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",ylim=c(-.05,.06))
se_function(mean1,se1)

plot(PC4_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)],ylim=c(-.15,.15))
arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
text(1.1*PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")

mean1 <- PCA_by_age$PC4_scale_mean
se1 <- PCA_by_age$PC4_scale_se
plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
se_function(mean1,se1)
```

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(2,1,.6,0.2))
PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC1_scale))
plot(PC1_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC2_scale))
plot(PC2_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC3_scale))
plot(PC3_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC4_scale))
plot(PC4_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
```

### 2015-08-11 RA_figs.rmd
- continuing to narrow down figures for Accessory manuscript
- lots of reworking of PCA, including figuring out how to sort variables

- PCA now without RGR

```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
library(remake)
create_bindings()

source("scripts/summary_dataframes.R")
source("scripts/functions.R")
```

##Summary

##1. RA schedules, RV curves, and VV curves across all species

##1. RA shifts enormously across species  
* There is also an age effect, with increasing RA with age

```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
mod <- lm(log(GrowthInv)~log(ReproInv),data=subset(SummaryInd,ReproInv>0))
plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
words.top.left.logxy(mod)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5")
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75")
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9")
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95")
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1")
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01")

plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
abline(0,1)
text(2.1,3,srt=45,"RA = 0.5")
abline(log10(3),1)
text(2,9,srt=45,"RA = 0.75")
abline(log10(9),1)
text(2,25,srt=45,"RA = 0.9")
abline(log10(19),1)
text(2,60,srt=45,"RA = 0.95")
abline(log10(.111),1)
text(19,3,srt=45,"RA = 0.1")
abline(log10(.010101),1)
text(170,2.4,srt=45,"RA = 0.01")
```

##2. RA, RV, and "Veg investment by size" (VV) curves for each species  
* These plots show a lot of scatter...I think it is real  
* Interestingly, different species have a "good" RV vs VV curve  
    * BOLE, COER, EPMI, GRSP, HATE, LEES, sort-of PHPH show consistent increase in reproductive investment with increasing size
    * BAER, GRSP, HATE, HEPU, PEPU, PHPH, PUTU, and sort-of BOLE, COER, EPMI show a consistent increase in vegetative investment with size
* Not surprisingly, COER, EPMI and HATE which have some of the best regressions for both RV and VV-curves have the cleanest RA schedules
* if VV-curves plotted including non-reproducing individuals, get beautiful curves - wonderfully consistent when young, but becoming scattered once reproducing
    ***it would be nice to plot the VV-curves, with different colors for reproducing and non-reproducing individuals***

###RA curves by species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "RA"
xvar <- "total_weight"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("RA", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
```

###RV curves by species
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "ReproInv"
xvar <- "total_weight"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("Reproductive investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
```

###Vegetative invesment by size curves by species, only including reproducing individuals  
* colored by age, but legend not correct, because "age 1" color used for youngest age with reproducing individuals
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7.5}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "GrowthInv"
xvar <- "total_weight"

data <- subset(SummaryInd, RA>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
```
###Vegetative invesment by size curves by species, including all individuls
* 
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "GrowthInv"
xvar <- "total_weight"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
}

mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
```

##3. RA is a population level parameter, so noise expected across individuals
* None of these species is known to mast, but of course environmental variation year-to-year
* Within a population, some individuals invest more or less in repro in a given year, but overall population should change with time
* This indicates it is informative to consider site level means - which would show an increase in RA with age in many species

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(1,.9,.4,0.2)) 
yvar <- "RA"
xvar <- "age"

data <- subset(SummaryInd,RA>0)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",
                    main=spp,xlim=c(1,35))
}

mtext("RA", 1, outer=TRUE,cex=1.2)
mtext("age", 2, outer=TRUE,cex=1.2)
```

### 2015-08-11 scripts/functions.R

@@ -16,6 +16,8 @@ plot_yvar3_vs_xvar3 <- function(data, yvar3 = "y", xvar3 = "x", ...) {
   plot(Y ~ X, data=data,  cex.axis=.8, las=1, pch=16, ...)
 }
 
+
+
 summarise_fit <- function(x) {
   data.frame(
     select(glance(x), r.squared, p.value),

### 2015-08-11 scripts/summary_dataframes.R

@@ -265,8 +265,8 @@ investment_spp <- investment %>%
 #maximum height for each species
 maxH_spp <- investment %>%
   group_by(species) %>%
-  summarise_each(funs(max), height, stem_area, growth_stem_diam)
-names(maxH_spp)<-c("species", "maxH_spp","max_stem_area_spp","max_growth_stem_diam_spp")
+  summarise_each(funs(max), height, stem_area, diameter)
+names(maxH_spp)<-c("species", "maxH_spp","max_stem_area_spp","max_stem_diam_spp")
 
 #maximum height for each species
 max_investment_spp <- investment %>%
@@ -284,14 +284,24 @@ SummaryInd$prop_maxH <- SummaryInd$height / SummaryInd$maxH_spp
 SummaryInd$prop_max_weight <- SummaryInd$total_weight / SummaryInd$max_total_weight
 SummaryInd$prop_max_repro <- SummaryInd$ReproInv / SummaryInd$max_repro_inv
 SummaryInd$prop_allocation <- SummaryInd$propagule_inv/(SummaryInd$GrowthInv + SummaryInd$ReproInv)
-SummaryInd$prop_growth_stem_diam <- SummaryInd$growth_stem_diam / SummaryInd$max_growth_stem_diam_spp
 SummaryInd$leaf_area <- SummaryInd$leaf_weight / (1000*SummaryInd$LMA_mean)
 SummaryInd$leaf_area_growth <- SummaryInd$growth_leaf / (1000*SummaryInd$LMA_mean)
 SummaryInd$shoot_leaf_area <- SummaryInd$lvs_end_total*SummaryInd$leaf_size_mean
 SummaryInd$shoot_leaf_area_growth <- SummaryInd$lvs_new*SummaryInd$leaf_size_mean
+SummaryInd$RA2 <- SummaryInd$total_repro_inv/SummaryInd$TotalInv
 
 SummaryInd$RA_asin <- asin(sqrt(SummaryInd$RA))
 SummaryInd$prop_propagule_asin <- asin(sqrt(SummaryInd$prop_propagule))
+
+#mean stem, shoot diam for each species
+mean_value_spp <- SummaryInd %>%
+  group_by(species) %>%
+  summarise_each(funs(median), stem_area, diameter, d_end)
+names(mean_value_spp)<-c("species", "mean_stem_area_spp","mean_stem_diam_spp","mean_shoot_diam_spp")
+
[…]

### 2015-08-12 Accessory_figs.rmd
continued work on figures.
Accessory_figs and RA_figs telling story, growth_figs still exploratory

@@
 
-##4. Does increasing RA, Reproductive investment or relative height yield compounding returns in the form of higher seedset or increased propagule allocation?
+##4. Does increasing RA, reproductive investment or relative height yield compounding returns in the form of higher seedset or increased propagule allocation?
 
@@
 ###5. What influences the correlation between RA and plant size (or total reproductive investment)?
-  ***Don't trust anything until I know RA and ReproInv are correct, because PHPH and PUTU have huge influence on patterns
-```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=30}
+  ***Don't trust anything until I know RA and ReproInv are correct, because PHPH and PUTU have huge influence on patterns***
+```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=30,warning=FALSE}
 par(mfrow=c(5,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))

### 2015-08-12 Growth_figs.rmd
continued work on figures.
Accessory_figs and RA_figs telling story, growth_figs still exploratory

@@
 ##Summary
-    1. Species show a marked decline in leaf investment with age and a most limited decline in stem investment with age
-    2.
+    1. Species show a marked decline in leaf investment with age and a limited decline in stem investment with age
+    2. Some species have a very narrow height range where they all become reproductively mature, while others are more spread out  
+        * canopy species - those where height matters - have a clearer transition with height
+    4. Species with higher leaf lifespan have greater shoot leaf area  
+        * there is a much smaller effect at the whole plant level
 
@@
 yvar <- "GrowthInv"
-xvar <- "total_weight"
+xvar <- "prop_maxH"
 
@@
 data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+lmfits <- lapply(data, function(x) lm((log(x[[yvar]])) ~  ((x[[xvar]]))))
 results <- summarise_all_fits(lmfits)
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4,
-                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
+                    main=spp,col=col.mature[as.factor(data[[spp]]$mature)])
 }
 
-mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+mtext("Vegetative investment", 2, outer=TRUE,cex=1.2)
+mtext("proportion maximum H", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")
 ```
@@
 data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
 
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
                     main=spp,col=col.age[as.factor(data[[spp]]$age)])
@@
 mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
 ```
@@
 data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
+                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+}
+
+mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2)
+mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
+```
+
+####Growth along shoot vs. stem  
+* For many species, increased relative growth along leaders (shoots) vs. stems as plants age  
+* far more dark purple dots below the 1:1 line
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "growth_stem_diam"
+xvar <- "growth_shoot_diam"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
+                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+  abline(0,1)
+}
+
+mtext("increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
+mtext("increase in shoot diameter (mm)", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=0.9,bty="n")
+```
+
+####Plots of increase in whole plant versus shoot leaf area  
+* Very different, patterns across species
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "leaf_area_growth"
+xvar <- "shoot_leaf_area_growth"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
+                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+  abline(0,1)
+}
+
+mtext("increase in whole plant leaf area", 2, outer=TRUE,cex=1.2)
+mtext("increase in shoot leaf area", 1, outer=TRUE,cex=1.2)
+```
+
+####leaf lifespan versus leaf area  
+* at the shoot level, there is a within species and across all data point correlation  
+    * not surprising, because this is how leaf lifespan is calculated  
+    * however, it is interesting that there is an age trajectory for many species  
+* for whole plant leaf area, there is only a within species shift in PELA - this species shows increasing leaf lifespan with age (except at old age) as well as increased total leaf area  
+    * interesting in that this is the species reproducing last and might well have additional mechanisms for increasing leaf area during its long juvenile period
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
+plot(LL_death~shoot_leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp[as.factor(species)])
+mod <- lm(log(shoot_leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
+words.top.right.logx(mod)
+
+plot(LL_death~leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp[as.factor(species)])
+mod <- lm(log(leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
+words.top.right.logx(mod)
+```
+
+***leaf lifespan vs. shoot leaf area***
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "LL_death"
+xvar <- "shoot_leaf_area"
+
+data <- subset(SummaryInd, LL_death<6)
+data <- split(data, data$species)
+
+lmfits <- lapply(data, function(x) lm(((x[[yvar]])) ~  (log(x[[xvar]]))))
 results <- summarise_all_fits(lmfits)
@@
 
+results
+
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
                     main=spp,col=col.age[as.factor(data[[spp]]$age)])
@@
 
-mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+mtext("ll death", 2, outer=TRUE,cex=1.2)
+mtext("shoot leaf area", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
 ```
 
-###2. Plants that allocate more to reproduction (higher RA) have lower growth
-* When plotted again stem diameter increment, most species show a distinct trade-off 
-* The pattern is weaker for growth in shoot diameter
-
+***leaf lifespan vs. whole plant leaf area***  
+*the regression results below exclude young individuals  
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "RA"
-xvar <- "growth_stem_diam"
+yvar <- "LL_death"
+xvar <- "leaf_area"
 
-data <- subset(SummaryInd,RA>0)
+data <- subset(SummaryInd, LL_death<6)
 data <- split(data, data$species)
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
-                    main=spp,,col=col.age[as.factor(data[[spp]]$age)])
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
+                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
 }
 
-mtext("Shoot diameter growth", 1, outer=TRUE,cex=1.2)
-mtext("RA", 2, outer=TRUE,cex=1.2)  
+mtext("ll death", 2, outer=TRUE,cex=1.2)
+mtext("leaf area", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
+
+yvar <- "LL_death"
+xvar <- "leaf_area"
+
+data <- subset(SummaryInd, LL_death<6&age>2)
+data <- split(data, data$species)
+
+lmfits <- lapply(data, function(x) lm(((x[[yvar]])) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+```
+
+***growth stem diam vs. prop maxH***
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
+plot(growth_stem_diam~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp[as.factor(species)])
 ```
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "RA"
-xvar <- "growth_shoot_diam"
+yvar <- "growth_stem_diam"
+xvar <- "prop_maxH"
 
-data <- subset(SummaryInd,RA>0)
+data <- subset(SummaryInd)
 data <- split(data, data$species)
@@
 for(spp in names(data)) {
-plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
-                        main=spp,,col=col.age[as.factor(data[[spp]]$age)])
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
+                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
 }
 
-mtext("Shoot diameter growth", 1, outer=TRUE,cex=1.2)
-mtext("RA", 2, outer=TRUE,cex=1.2)  
+mtext("growth_stem_diam", 2, outer=TRUE,cex=1.2)
+mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
 ```
 
-###3.PCA analysis also indicates a decline in growth with increasing RA - as well as species level differences
-* This combination of variables shows that RGR is approximately opposite a collection of variables that indicate a plant is "bigger" - so smaller plants have higher RGR
-* Orthoganal to these in WD vs.
-maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
-* I interpret this to mean that the three traits (Hmax, LMA, WD) strongly influence each other - presumably, Hmax a function of WD and LMA), but do not particularly 
-* this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals, greatly reducing sample size.
-Including these variables, doesn't change the basic story.
-* fine tuning:  
-  ** remove RGR leaf (similar to RGR)
-** remove prop_max_weight and prop_max_repro (similar to prop_maxH)
-
-    plot(shoot_leaf_area_growth~total_weight,SummaryInd,col=col.spp[as.factor(species)],log="xy",pch=16)
-```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-SummaryIndPCA <- SummaryInd %>%
-  filter(lvs_end_total>0&shoot_leaf_area>0&shoot_leaf_area_growth!=0) %>%
-  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
-         growth_stem_diam,leaf_area,growth_shoot_diam,growth_stem_area,lvs_end_total,total_weight,
-         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth,scaled_growth_stem_diam)
-
-SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
-SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
-SummaryIndPCA$height <- log(SummaryIndPCA$height)
-SummaryIndPCA$maxH_spp <- log(SummaryIndPCA$maxH_spp)
-SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
-SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
-SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
-SummaryIndPCA$growth_shoot_diam <- log(SummaryIndPCA$growth_shoot_diam+.001)
-SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
-SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
-SummaryIndPCA$lvs_end_total <- log(SummaryIndPCA$lvs_end_total)
-SummaryIndPCA$growth_stem_diam <- log(SummaryIndPCA$growth_stem_diam)
-SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
-SummaryIndPCA$shoot_leaf_area_growth <- log(SummaryIndPCA$shoot_leaf_area_growth)
-SummaryIndPCA$scaled_growth_stem_diam <- log(SummaryIndPCA$scaled_growth_stem_diam)
-
-PCA_mod <- prcomp(SummaryIndPCA, scale=TRUE)
-summary(PCA_mod)
-biplot(PCA_mod,xlim=c(-.1,.15),ylim=c(-.15,.1),cex=.8)
-
-PCA_loadings <- as.data.frame(PCA_mod$rotation)
-PCA_loadings$variables <- row.names(PCA_loadings)
-
-PCA_scaling <- as.data.frame(PCA_mod$scale)
-PCA_scaling$variables <- row.names(PCA_scaling)
-names(PCA_scaling) <- c("scale","variables")
-PCA_loadings <- merge(PCA_loadings,PCA_scaling,by="variables")
-
-PCA_lambda <- as.data.frame(PCA_mod$sdev)
-
-PCA_scores <- as.data.frame(PCA_mod$x)
-PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$lvs_end_total>0&SummaryInd$shoot_leaf_area_growth!=0)
-SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)
-
-n <- NROW(PCA_scores)
-scale =1
-
-PCA_lambda <- PCA_lambda*sqrt(n)
-PCA_lambda <- PCA_lambda^scale
-
-SummaryInd_PCA_results$PC1_scale <- SummaryInd_PCA_results$PC1/PCA_lambda[1]
-SummaryInd_PCA_results$PC2_scale <- SummaryInd_PCA_results$PC2/PCA_lambda[2]
-SummaryInd_PCA_results$PC3_scale <- SummaryInd_PCA_results$PC3/PCA_lambda[3]
-SummaryInd_PCA_results$PC4_scale <- SummaryInd_PCA_results$PC4/PCA_lambda[4]
-PCA_loadings$PC1_scale <- PCA_loadings$PC1 / 4.5
-PCA_loadings$PC2_scale <- PCA_loadings$PC2 / 4.5
-PCA_loadings$PC3_scale <- PCA_loadings$PC3 / 4.5
-PCA_loadings$PC4_scale <- PCA_loadings$PC4 / 4.5
+***growth leaf area vs. prop maxH***
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
+plot(leaf_area_growth~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp[as.factor(species)])
 ```
 
-#Looking at PCA by species
-* I have removed RGR from the PCA and added in a scaled stem diameter measure  
-* Although RGR and "Stem diameter increment" have a similar negative correlation with RA, RGR created a much easer to describe PCA - it fell out wonderfully opposite RGR and orthogonal to WD, seedsize, LMA, total plant size
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "leaf_area_growth"
+xvar <- "prop_maxH"
 
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
-  filter(complete.cases(SummaryInd_PCA_results$PC1_scale))
+data <- subset(SummaryInd)
+data <- split(data, data$species)
 
-SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
-  filter(complete.cases(SummaryInd_PCA_results$PC2_scale))
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
+                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+}
 
-SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
-  filter(complete.cases(SummaryInd_PCA_results$PC3_scale))
-
-SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
-  filter(complete.cases(SummaryInd_PCA_results$PC4_scale))
-
-PCA_by_species <- SummaryInd_PCA_results %>%
-  group_by(species) %>%
-summarise_each(funs(mean, se), PC1_scale, PC2_scale, PC3_scale, PC4_scale)
-
-PCA_by_age <- SummaryInd_PCA_results %>%
-group_by(age) %>%
-summarise_each(funs(mean, se), PC1_scale, PC2_scale, PC3_scale, PC4_scale)
+mtext("increase in leaf area", 2, outer=TRUE,cex=1.2)
+mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
 ```
 
-###PCA axis 1 is across species  
-* it separates species with high wood density (WD_mean), seedset, RA versus species with large total size, high leaf area, high LMA, large seedsize etc
-* the age indepentent measures like prop_maxH and scaled_growth_stem_area have near-zero loadings
-* BAER, HATE have by far the highest loadings and BOLE, COER, EPMI, HEPU, LEES, PILI the lowest  
-* not sure why high wood density species also have high seedset - is this just by chance with my species?
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "total_weight"
+xvar <- "prop_maxH"
 
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],xlim=c(-.1,.1))
-arrows(0, 0, (.8*PCA_loadings$PC2_scale), (.8*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+data <- subset(SummaryInd)
+data <- split(data, data$species)
 
-mean1 <- PCA_by_species$PC1_scale_mean
-se1 <- PCA_by_species$PC1_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 1")
-se_function(mean1,se1)
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
+                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+}
 
-plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
-arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
-
-mean1 <- PCA_by_age$PC1_scale_mean
-se1 <- PCA_by_age$PC1_scale_se
-plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 1")
-se_function(mean1,se1)
+mtext("total size", 2, outer=TRUE,cex=1.2)
+mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
 ```
 
-###PCA axis 2 is about age  
-* top variable loadings: shoot_leaf_area_growth and growth_shoot_diam vs repro_all_count, RA, prop_maxH - a collection of variables that shift fro each to late in life   
-* COER, EPMI,PELA, and PEPU have the higher loadings and BOLE, LEES have the lowest, but mostly about age
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "total_weight"
+xvar <- "prop_maxH"
 
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+data <- subset(SummaryInd)
+data <- split(data, data$species)
 
-mean1 <- PCA_by_species$PC2_scale_mean
-se1 <- PCA_by_species$PC2_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 2")
-se_function(mean1,se1)
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
+                    main=spp,col=col.mature[as.factor(data[[spp]]$mature)])
+}
 
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-mean1 <- PCA_by_age$PC2_scale_mean
-se1 <- PCA_by_age$PC2_scale_se
-plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
-se_function(mean1,se1)
+mtext("total size", 2, outer=TRUE,cex=1.2)
+mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
+legend("bottomright",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")
 ```
 
-#PCA axis 3 again divides by species
-* top variable loadings: scaled_growth_stem_diam, WD_mean,growth_stem_diam, lvs_end_total vs. maxH_spp, LMA_mean, seed_size, RA  
-* not terribly interpretable, since doesn't make sense that scaled_growth_stem_diam with WD_mean
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3))
 
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.15))
-
-arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(1.1*PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=.8,col="black")
-
-mean1 <- PCA_by_species$PC3_scale_mean
-se1 <- PCA_by_species$PC3_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 3")
-se_function(mean1,se1)
-
-plot(PC3_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)],ylim=c(-.15,.15))
-arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(1.1*PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-mean1 <- PCA_by_age$PC3_scale_mean
-se1 <- PCA_by_age$PC3_scale_se
-plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
-se_function(mean1,se1)
+plot(WD_mean~leaf_area_growth,SummaryInd,log="y",pch=16,col=col.age[as.factor(age)])
+mod <- lm(log(leaf_area_growth)~age*WD_mean,SummaryInd)
+summary(mod)
 ```
-
-#PCA axis 4  
-* this axis explains only 5% of the total, but quite interesting that it divides stem vs shoot growth variables  
-* high loadings for growth_stem_area, growth_leaf, LMA_mean, seed_set vs low loadings for shoot_leaf_area_growth, WD_mean, prop_maxH, seed_size  
-* BAER, EPMI, HATE and HEPU have higher values vs.
-BOLE, GRBU, GRSP with lower values; in a sense these later species have more shoot growth than stem growth and spend more of their life close to their maxH - which is true
-* there is no significant age component  
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-
-plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.15))
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-
-mean1 <- PCA_by_species$PC4_scale_mean
-se1 <- PCA_by_species$PC4_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",ylim=c(-.05,.06))
-se_function(mean1,se1)
-
-plot(PC4_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)],ylim=c(-.15,.15))
-arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(1.1*PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-mean1 <- PCA_by_age$PC4_scale_mean
-se1 <- PCA_by_age$PC4_scale_se
-plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
-se_function(mean1,se1)
-```
-
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(2,1,.6,0.2))
-PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC1_scale))
-plot(PC1_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
-PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC2_scale))
-plot(PC2_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
-PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC3_scale))
-plot(PC3_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
-PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC4_scale))
-plot(PC4_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
-```

### 2015-08-12 RA_figs.rmd
continued work on figures.
Accessory_figs and RA_figs telling story, growth_figs still exploratory

@@
 ##Summary  
-
-##1. RA schedules, RV curves, and VV curves across all species
+1. RA shifts across species and, on average, increases with increasing age  
+2. Plots of RA and investment against proportion maxH show  
+    * COER, EPMI, GRBU, HATE, PELA show decent curves; BOLE, GRSP, HEPU, LEES, PHPH have noisier curves  
+    * different species show predictable increase in repro vs. veg investment with size, once reproductively mature  
+    * all species show predictable increase in veg investment before reproductive maturity
+3. Plants that allocate more to reproduction (higher RA) have lower growth  
+    * pattern holds against proportional increase in shoot diameter or stem diameter, both across and within species  
+    * pattern also true against RGR, but probably less biologically relevent  
+4. PCA indicates variables that explain more across vs. within species shifts  
+    * against relative growth vs. RA (and absolute reproduction) important (age related effect)  
+    * species separated by size, WD, LMA, seedsize  
+    * 3rd and 4th axes finetune parts of these patterns, in particular separating canopy species from others  
+5. Overall, data set shows increasing RA with age (despite messay RA schedules) and differences across species in community
 
@@
 ###RA curves by species  
+* curves here plotted against prop_maxH, not total weight, because on average "cleaner"  
+    * take account for inter-site discrepencies in plant weight, that don't seem to affect plant height or reproductive maturity as much
+
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
@@
 yvar <- "RA"
-xvar <- "total_weight"
+xvar <- "prop_maxH"
 
@@
 data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  (log(x[[xvar]]))))
+lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  ((x[[xvar]]))))
 results <- summarise_all_fits(lmfits)
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
                     main=spp,col=col.age[as.factor(data[[spp]]$age)])
@@
 mtext("RA", 2, outer=TRUE,cex=1.2)
-mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+mtext("proportion maximum H", 1, outer=TRUE,cex=1.2)
+legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
 ```
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
                     main=spp,col=col.age[as.factor(data[[spp]]$age)])
@@
 * colored by age, but legend not correct, because "age 1" color used for youngest age with reproducing individuals
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7.5}
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
                     main=spp,col=col.age[as.factor(data[[spp]]$age)])
@@
 mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
 ```
+
 ###Vegetative invesment by size curves by species, including all individuls  
-* 
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
+* at younger ages, species follow very predictable growth curves  
+* Once reproductively mature, plants no longer following predictable vegetative investment vs. size  
+    ***What does this mean in terms of models?*** 
+* If these plots were colored by age, they would show that the 5-year old site has somewhat stunted plants (site used for "young plants" by growth project)
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",
-                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
+                    main=spp,col=col.mature[as.factor(data[[spp]]$mature)])
 }
@@
 mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")
 ```
 
-##3. RA is a population level parameter, so noise expected across individuals
+####RA is a population level parameter, so noise expected across individuals
 * None of these species is known to mast, but of course environmental variation year-to-year
@@
 
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(1,.9,.4,0.2)) 
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="", cex=1.3,
                     main=spp,xlim=c(1,35))
@@
 ```
+
+###3. Plants that allocate more to reproduction (higher RA) have lower growth
+* When plotted again stem diameter increment, most species show a distinct trade-off 
+* The pattern is weaker for growth in shoot diameter
+* There is also a very distinct correlation across individuals of all species
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
+par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
+plot(asin(sqrt(RA))~growth_stem_diam,data=subset(SummaryInd,RA>0),log="x",col=col.spp[as.factor(species)], pch=16)
+mod <- lm(log(growth_stem_diam)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
+words.top.right.logx(mod)
+legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=0.8,bty="n")
+
+plot(asin(sqrt(RA))~growth_shoot_diam,data=subset(SummaryInd,RA>0),log="x",col=col.spp[as.factor(species)], pch=16)
+mod <- lm(log(growth_shoot_diam)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
+words.top.right.logx(mod)
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "RA"
+xvar <- "growth_stem_diam"
+
+data <- subset(SummaryInd,RA>0)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
+                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+}
+
+mtext("Stem diameter growth", 1, outer=TRUE,cex=1.2)
+mtext("RA", 2, outer=TRUE,cex=1.2)  
+legend("bottomleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "RA"
+xvar <- "growth_shoot_diam"
+
+data <- subset(SummaryInd,RA>0)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
+                        main=spp,col=col.age[as.factor(data[[spp]]$age)])
+}
+
+mtext("Shoot diameter growth", 1, outer=TRUE,cex=1.2)
+mtext("RA", 2, outer=TRUE,cex=1.2)  
+legend("bottomleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
+```
+
+###4. PCA analysis also indicates a decline in growth/increasing age with increasing RA - as well as species level differences
+* Axis 2 groups a collection of variables indicating increased reproduction; opposite these is relative diameter growth  
+    * I have removed RGR from the PCA and added in a scaled stem diameter measure  
+    * Although RGR and "Stem diameter increment" have a similar negative correlation with RA, 
+    RGR created a much easer to describe PCA - it fell out wonderfully opposite RGR and orthogonal to 
+    WD, seedsize, LMA, total plant size
+
+* Orthoganal to these in WD vs.
+maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
+
+* I interpret this to mean that the three traits (Hmax, LMA, WD) are strongly correlated and shift predictably across the species; confirms that I have selected a wide range of species from the community
+
+*** this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals, greatly reducing sample size.
+Including these variables, doesn't change the basic story.***
+
+```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
+par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+SummaryIndPCA <- SummaryInd %>%
+  filter(lvs_end_total>0&shoot_leaf_area>0&shoot_leaf_area_growth!=0) %>%
+  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
+         growth_stem_diam,leaf_area,growth_shoot_diam,growth_stem_area,lvs_end_total,total_weight,
+         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth,scaled_growth_stem_diam)
+
+SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
+SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
+SummaryIndPCA$height <- log(SummaryIndPCA$height)
+SummaryIndPCA$maxH_spp <- log(SummaryIndPCA$maxH_spp)
+SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
+SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
+SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
+SummaryIndPCA$growth_shoot_diam <- log(SummaryIndPCA$growth_shoot_diam+.001)
+SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
+SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
+SummaryIndPCA$lvs_end_total <- log(SummaryIndPCA$lvs_end_total)
+SummaryIndPCA$growth_stem_diam <- log(SummaryIndPCA$growth_stem_diam)
+SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
+SummaryIndPCA$shoot_leaf_area_growth <- log(SummaryIndPCA$shoot_leaf_area_growth)
+SummaryIndPCA$scaled_growth_stem_diam <- log(SummaryIndPCA$scaled_growth_stem_diam)
+SummaryIndPCA$RA <- asin(sqrt(SummaryIndPCA$RA))
+
+PCA_mod <- prcomp(SummaryIndPCA, scale=TRUE)
+summary(PCA_mod)
+biplot(PCA_mod,xlim=c(-.1,.15),ylim=c(-.15,.1),cex=.8)
+
+PCA_loadings <- as.data.frame(PCA_mod$rotation)
+PCA_loadings$variables <- row.names(PCA_loadings)
+
+PCA_scaling <- as.data.frame(PCA_mod$scale)
+PCA_scaling$variables <- row.names(PCA_scaling)
+names(PCA_scaling) <- c("scale","variables")
+PCA_loadings <- merge(PCA_loadings,PCA_scaling,by="variables")
+
+PCA_lambda <- as.data.frame(PCA_mod$sdev)
+
+PCA_scores <- as.data.frame(PCA_mod$x)
+PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$lvs_end_total>0&SummaryInd$shoot_leaf_area_growth!=0)
+SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)
+
+n <- NROW(PCA_scores)
+scale =1
+
+PCA_lambda <- PCA_lambda*sqrt(n)
+PCA_lambda <- PCA_lambda^scale
+
+SummaryInd_PCA_results$PC1_scale <- SummaryInd_PCA_results$PC1/PCA_lambda[1]
+SummaryInd_PCA_results$PC2_scale <- SummaryInd_PCA_results$PC2/PCA_lambda[2]
+SummaryInd_PCA_results$PC3_scale <- SummaryInd_PCA_results$PC3/PCA_lambda[3]
+SummaryInd_PCA_results$PC4_scale <- SummaryInd_PCA_results$PC4/PCA_lambda[4]
+PCA_loadings$PC1_scale <- PCA_loadings$PC1 / 4.5
+PCA_loadings$PC2_scale <- PCA_loadings$PC2 / 4.5
+PCA_loadings$PC3_scale <- PCA_loadings$PC3 / 4.5
+PCA_loadings$PC4_scale <- PCA_loadings$PC4 / 4.5
+
+SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
+  filter(complete.cases(SummaryInd_PCA_results$PC1_scale))
+
+SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
+  filter(complete.cases(SummaryInd_PCA_results$PC2_scale))
+
+SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
+  filter(complete.cases(SummaryInd_PCA_results$PC3_scale))
+
+SummaryInd_PCA_results <-SummaryInd_PCA_results %>%
+  filter(complete.cases(SummaryInd_PCA_results$PC4_scale))
+
+PCA_by_species <- SummaryInd_PCA_results %>%
+  group_by(species) %>%
+summarise_each(funs(mean, se), PC1_scale, PC2_scale, PC3_scale, PC4_scale)
+
+PCA_by_age <- SummaryInd_PCA_results %>%
+group_by(age) %>%
+summarise_each(funs(mean, se), PC1_scale, PC2_scale, PC3_scale, PC4_scale)
+```
+
+####PCA axis 1 is across species  
+* it explains 34% of the variance  
+* it separates species with high wood density (WD_mean), seedset, RA versus species with large total size, high leaf area, high LMA, large seedsize etc
+* the age indepentent measures like prop_maxH and scaled_growth_stem_area have near-zero loadings
+* BAER, HATE have by far the highest loadings and BOLE, COER, EPMI, HEPU, LEES, PILI the lowest  
+* not sure why high wood density species also have high seedset - is this just by chance with my species?
+
+```{r, echo=FALSE,message=FALSE,fig.width=20, fig.height=14}
+par(mfrow=c(2,3), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+
+plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],xlim=c(-.1,.1))
+arrows(0, 0, (.8*PCA_loadings$PC2_scale), (.8*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mean1 <- PCA_by_species$PC1_scale_mean
+se1 <- PCA_by_species$PC1_scale_se
+plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 1")
+se_function(mean1,se1)
+
+PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC1_scale))
+plot(PC1_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
+
+plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
+arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+legend("topright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+
+mean1 <- PCA_by_age$PC1_scale_mean
+se1 <- PCA_by_age$PC1_scale_se
+plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 1")
+se_function(mean1,se1)
+```
+
+####PCA axis 2 is about age  
+* it explains 23% of the variance 
+* top variable loadings: shoot_leaf_area_growth and growth_shoot_diam vs repro_all_count, RA, prop_maxH - a collection of variables that shift fro each to late in life   
+* COER, EPMI,PELA, and PEPU have the higher loadings and BOLE, LEES have the lowest - to first order these differences are about the average age of reproducing individuals of each species
+```{r, echo=FALSE,message=FALSE,fig.width=20, fig.height=14}
+par(mfrow=c(2,3), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+
+plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+
+mean1 <- PCA_by_species$PC2_scale_mean
+se1 <- PCA_by_species$PC2_scale_se
+plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 2")
+se_function(mean1,se1)
+
+PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC2_scale))
+plot(PC2_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
+
+plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+
+mean1 <- PCA_by_age$PC2_scale_mean
+se1 <- PCA_by_age$PC2_scale_se
+plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
+se_function(mean1,se1)
+```
+
+####PCA axis 3 again divides mainly by species
+* it explains 9% of the variance (total variance explained now at 68%)  
+* It is dividing the three (of 4) canopy species, HATE, PEPU, PELA, (BAER) versus
+* top variable loadings: scaled_growth_stem_diam, WD_mean,growth_stem_diam, lvs_end_total vs. maxH_spp, LMA_mean, seed_size, RA  
+* not terribly interpretable, since doesn't make sense that scaled_growth_stem_diam with WD_mean
+
+```{r, echo=FALSE,message=FALSE,fig.width=20, fig.height=14}
+par(mfrow=c(2,3), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+
+plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.15))
+arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(1.1*PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=.8,col="black")
+
+mean1 <- PCA_by_species$PC3_scale_mean
+se1 <- PCA_by_species$PC3_scale_se
+plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 3")
+se_function(mean1,se1)
+
+PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC3_scale))
+plot(PC3_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
+
+plot(PC3_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)],ylim=c(-.15,.15))
+arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(1.1*PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+
+mean1 <- PCA_by_age$PC3_scale_mean
+se1 <- PCA_by_age$PC3_scale_se
+plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
+se_function(mean1,se1)
+```
+
+####PCA axis 4  
+* it explains 7% of the variance (total variance explained now at 74%)
+* it divides stem vs shoot growth variables  
+* high loadings for growth_stem_area, growth_leaf, LMA_mean, seed_set vs low loadings for shoot_leaf_area_growth, WD_mean, prop_maxH, seed_size  
+* BAER, EPMI, HATE and HEPU have higher values vs.
+BOLE, GRBU, GRSP with lower values; in a sense these later species have more shoot growth than stem growth and spend more of their life close to their maxH - which is true
+* there is no significant age component  
+```{r, echo=FALSE,message=FALSE,fig.width=20, fig.height=14}
+par(mfrow=c(2,3), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
+
+plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.15))
+arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+
+mean1 <- PCA_by_species$PC4_scale_mean
+se1 <- PCA_by_species$PC4_scale_se
+plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",ylim=c(-.05,.06))
+se_function(mean1,se1)
+
+PCA_loadings <- transform(PCA_loadings,variables=reorder(variables,-PC4_scale))
+plot(PC4_scale~as.factor(variables),PCA_loadings,cex.axis=.8,las=3,xlab="")
+
+plot(PC4_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)],ylim=c(-.15,.15))
+arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+text(1.1*PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
+
+mean1 <- PCA_by_age$PC4_scale_mean
+se1 <- PCA_by_age$PC4_scale_se
+plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
+se_function(mean1,se1)
+```

### 2015-08-14 RA_figs.rmd
Streamlined function for merging by individual

@@
   filter(lvs_end_total>0&shoot_leaf_area>0&shoot_leaf_area_growth!=0) %>%
-  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
+  select(prop_maxH,height,maxH_spp,wood_density,LMA_mean,seed_size,growth_leaf,
          growth_stem_diam,leaf_area,growth_shoot_diam,growth_stem_area,lvs_end_total,total_weight,
@@
 * it explains 34% of the variance  
-* it separates species with high wood density (WD_mean), seedset, RA versus species with large total size, high leaf area, high LMA, large seedsize etc
+* it separates species with high wood density (wood_density), seedset, RA versus species with large total size, high leaf area, high LMA, large seedsize etc
 * the age indepentent measures like prop_maxH and scaled_growth_stem_area have near-zero loadings
@@
 * It is dividing the three (of 4) canopy species, HATE, PEPU, PELA, (BAER) versus
-* top variable loadings: scaled_growth_stem_diam, WD_mean,growth_stem_diam, lvs_end_total vs. maxH_spp, LMA_mean, seed_size, RA  
-* not terribly interpretable, since doesn't make sense that scaled_growth_stem_diam with WD_mean
+* top variable loadings: scaled_growth_stem_diam, wood_density,growth_stem_diam, lvs_end_total vs. maxH_spp, LMA_mean, seed_size, RA  
+* not terribly interpretable, since doesn't make sense that scaled_growth_stem_diam with wood_density
 
@@
 * it divides stem vs shoot growth variables  
-* high loadings for growth_stem_area, growth_leaf, LMA_mean, seed_set vs low loadings for shoot_leaf_area_growth, WD_mean, prop_maxH, seed_size  
+* high loadings for growth_stem_area, growth_leaf, LMA_mean, seed_set vs low loadings for shoot_leaf_area_growth, wood_density, prop_maxH, seed_size  
 * BAER, EPMI, HATE and HEPU have higher values vs.

### 2015-08-14 R/Summaries.R

@@ -43,9 +43,12 @@ process_seed_costs <- function(seedSize_raw, PartsSummary_all) {
 
 process_LMA <- function(LMA_raw) {
   LMA <- filter(LMA_raw, species!="" & species!=" ") %>%
-    select(species, age, LMA, branch_age, leaf_number, leaf_area)
+    select(species, age, LMA, branch_age, leaf_number, leaf_area) 
+
   LMA$leaf_size <- LMA$leaf_area/LMA$leaf_number
-  LMA
+
+  LMA %>%  group_by(species, age) %>%
+    summarise_each(funs(mean), LMA, leaf_size)
 }
 
 process_leaves_per_length <- function(leavesPerLength_raw) {
@@ -61,12 +64,6 @@ process_leaf_lifespan <- function(leafLifespan_raw, leavesPerLength) {
 
   leafLifespan <- filter(leafLifespan_raw, dont_use!="dead" & dont_use!="dont_use") %>%
     select(species, age, individual, d_start, d_end, length_start, new_length, lvs_start_length, lvs_start_count, lvs_end_length, lvs_end_count, lvs_new_length, lvs_new_count, new_but_shed_count, mm_lvs_spec, count_lvs_spec)
-
-  #TODO Lizzy: why do we need this next line?
-  leafLifespan$individual <- as.factor(leafLifespan$individual)
-  leafLifespan$species <- as.factor(leafLifespan$species)
-
-  #loading this column as character, so using this for now
 
   # Calculating Leaf Lifespan
 
@@ -90,16 +87,19 @@ process_leaf_lifespan <- function(leafLifespan_raw, leavesPerLength) {
   for(v in c("lvs_start_length","lvs_start_count","lvs_end_length","lvs_end_count","lvs_new_length","lvs_new_count","new_but_shed_count")) {
     i <- is.na(leafLifespan[[v]])
     leafLifespan[[v]][i] <- 0
-  }
+   }
 
   #calculating leaf lifespan
-  leafLifespan <- leafLifespan %>% mutate(
+  leafLifespan <- mutate(leafLifespan,
     lvs_start = lvs_start_count + (lvs_start_length * count_per_length),
     lvs_end = lvs_end_count + (lvs_end_length * count_per_length),
     lvs_new = lvs_new_count + (lvs_new_length * count_per_length),
     LL_bd = (lvs_start)/(((lvs_start)-(lvs_end)) + (lvs_new)/2),
[…]

### 2015-08-14 scripts/summary_dataframes.R

@@ -1,7 +1,106 @@
 # load packages and "open" dataframes to use
 
 
+  SummaryInd <- Individual_all
 
+
+  #summarizing data by species, age
+
+  #leaf lifespan summary by species, age
+  LL_summary <- SummaryInd %>%
+    filter(LL_bd>0 & LL_bd<6 & LL_birth<8 & LL_death<8) %>%
+    group_by(species, age) %>%
+    summarise_each(funs(mean, se, length), LL_bd, LL_death, LL_birth, new_length, lvs_end, lvs_end_total, growth_shoot_diam, growth_shoot_area, RGR)
+
+  #accessory tissue summary by species, age
+  accessory_summary <- SummaryInd %>%
+    group_by(species, age) %>%
+    summarise_each(funs(mean, se, length), prepollen_aborted_inv, prepollen_success_inv, postpollen_aborted_inv, packaging_dispersal_inv, propagule_inv, prepollen_all_inv)
+
+  accessory_summary2 <- SummaryInd %>%
+    filter(total_repro_inv!=0) %>%
+    group_by(species, age) %>%
+    summarise_each(funs(mean, se, length), prop_prepollen_aborted, prop_prepollen_success, prop_postpollen_aborted, prop_packaging_dispersal, prop_propagule, prop_prepollen_all, prop_accessory)
+
+  #accessory tissue by species
+  accessory_spp <- SummaryInd %>%
+    filter(total_repro_inv!=0) %>%
+    group_by(species) %>%
+    summarise_each(funs(mean, se, length), prop_prepollen_aborted, prop_prepollen_success, prop_postpollen_aborted, prop_packaging_dispersal, prop_propagule, prop_prepollen_all, prop_accessory)
+
+  #investment summary by species, age
+  investment_summary <- ReproductionAllocation_all %>%
+    group_by(species, age) %>%
+    summarise_each(funs(mean, se, length), height, GrowthInv, ReproInv, total_weight, TotalInv, RA, diameter, stem_area, leaf_weight, stem_weight, growth_stem_diam, growth_stem_area, growth_leaf, growth_stem)
+
+  investment_spp_age <- investment_summary %>%
+    select(species, age, height_mean, RA_mean)
+    
+  mature_RA <- SummaryInd %>%
+    filter(mature==TRUE) %>%
+    group_by(species) %>%
[…]

### 2015-08-17 Growth_figs.rmd
Embed derived quntities into remake workflow
Closes #18

Squashed commit of the following:

commit f868cdc0b9638356f9e65a5188b2aa58865e840f
Author: Daniel Falster <daniel.falster@mq.edu.au>
Date:   Mon Aug 17 16:01:37 2015 +1000

    averages by species and patch age

commit 1030d59fd886f0f680620b0dd2761db14eb506eb
Author: Daniel Falster <daniel.falster@mq.edu.au>
Date:   Mon Aug 17 13:51:01 2015 +1000

    Remove as.factor

commit 6b94e4820873bd85e838013782e451e9c3d021c3
Author: Daniel Falster <daniel.falster@mq.edu.au>
Date:   Mon Aug 17 13:50:46 2015 +1000

    Remove some outdated stuff

c

@@
 
-plot(WD_mean~leaf_area_growth,SummaryInd,log="y",pch=16,col=col.age[as.factor(age)])
-mod <- lm(log(leaf_area_growth)~age*WD_mean,SummaryInd)
+plot(wood_density~leaf_area_growth,SummaryInd,log="y",pch=16,col=col.age[as.factor(age)])
+mod <- lm(log(leaf_area_growth)~age*wood_density,SummaryInd)
 summary(mod)

### 2015-08-17 R/AccessoryTissues.R

@@ -9,11 +9,33 @@ AccessoryCosts <- function(species, IndividualsList, InvestmentCategories, speci
                 species=species, InvestmentCategories=InvestmentCategories[, c("flower_part", species)],
                 species_INV= species_INV) %>% rbind_all
 
-# TODO: This is temp fix to remove some NAs in PrePol_S. Figure out why these are needed
-  InvDist$PrePol_S[which(is.na(InvDist$PrePol_S))] <- 0
-  InvDist$Total= (InvDist$PrePol_A + InvDist$PrePol_S + InvDist$PostPol_A + InvDist$PD + InvDist$Prop)
+  # TODO: This is temp fix to remove some NAs in prepollen_success_inv. 
+  # Figure out why these are needed
+  InvDist$prepollen_success_inv[which(is.na(InvDist$prepollen_success_inv))] <- 0
 
-  merge(AgeData, InvDist, by="individual")
+# TODO: Lizzy - is this next line needed? causes errors
+#  InvDist$Total= (InvDist$prepollen_aborted_inv + InvDist$prepollen_success_inv + InvDist$postpollen_aborted_inv + InvDist$PD + InvDist$Prop)
+
+  accessory <- merge(AgeData, InvDist, by="individual")
+
+  #calculating percentages of various accessory tissues
+  accessory <- accessory %>%
+    mutate(accessory_inv = total_repro_inv - propagule_inv,
+        prepollen_all_inv = prepollen_aborted_inv + prepollen_success_inv,
+        prop_prepollen_aborted = prepollen_aborted_inv / total_repro_inv,
+        prop_prepollen_success = prepollen_success_inv / total_repro_inv,
+        prop_postpollen_aborted = postpollen_aborted_inv / total_repro_inv,
+        prop_packaging_dispersal = packaging_dispersal_inv / total_repro_inv,
+        prop_propagule = propagule_inv / total_repro_inv,
+        prop_accessory = 1 - prop_propagule,
+        prop_prepollen_all = prop_prepollen_aborted + prop_prepollen_success
+        )
+
+  for(v in c("prop_prepollen_aborted", "prop_prepollen_success", "prop_postpollen_aborted",
+        "prop_packaging_dispersal", "prop_propagule", "prop_accessory")) {
[…]

### 2015-08-17 R/GraphRepresentation.R

@@ -1,5 +1,5 @@
 AV_W <- function(species, part, AvWeightPerUnit) {
-  AvWeightPerUnit[(AvWeightPerUnit$species == species) & (AvWeightPerUnit$part == part), "av.weight"]
+  AvWeightPerUnit[(AvWeightPerUnit$species == species) & (AvWeightPerUnit$part == part), "weight"]
 }
 
 AdjustEdgeWeightsForMultiplicity <- function(graph, species, MultiplierTable) {

### 2015-08-17 R/Investment.R

@@ -12,12 +12,52 @@ CalculateInvestmentForSpecies <- function(species, Reproduction, FloweringCatego
     ldply(d, function(x) x[[name]])
   }
 
-  R <- llply(unique(Reproduction$individual), function(x) CalculateInvestmentForIndiviualPlant(x,
-    filter(Reproduction,  individual==x), FloweringCategories, MultiplierTable, GraphMaps, PartsSummary))
+  R <- llply(unique(Reproduction$individual), function(x) 
+      CalculateInvestmentForIndiviualPlant(x,
+                  filter(Reproduction,  individual==x), 
+                  FloweringCategories, MultiplierTable, GraphMaps, PartsSummary))
+    R <- llply(unique(Reproduction$individual), function(x) 
+      CalculateInvestmentForIndiviualPlant(x,
+                  filter(Reproduction,  individual==x), 
+                  FloweringCategories, MultiplierTable, GraphMaps, PartsSummary))
+  
+  FD <- combine("FD", R)
+
+  accessory_count <- FD %>%
+      group_by(individual, part) %>%
+      summarise_each(funs(sum), count, weight) %>%
+      filter(count > 0)
+
+  parts_counts <- list(
+      flower_count= c("flower_petals","flower_petals_small"),
+      bud_count = c("bud_tiny","bud_small","bud_mid","bud_large","flower_aborted_without_petals"),
+      seed_count= c("seed"),
+      aborted_fruit_count = c("fruit_just_starting","fruit_young","fruit_large_immature_01","fruit_large_immature_02","fruit_large_immature_03","fruit_large_immature_04"," fruit_large_immature_05"," fruit_large_immature_06","fruit_empty")
+      )
+
+  counts <- ddply(accessory_count, "individual", function(x) {
+      sapply(names(parts_counts), function(n)
+         sum(filter(x, part %in% parts_counts[[n]])$count))}) 
+
+  counts <- mutate(counts,
+    seedset = seed_count/(bud_count + flower_count + seed_count + aborted_fruit_count),
+    prepollen_all_count = bud_count + flower_count,
+    prop_prepollen_count = (bud_count + flower_count)/(bud_count + flower_count + seed_count + aborted_fruit_count),
+    repro_all_count = bud_count + flower_count + seed_count
+    )
+
+  parts_weights <- list(
+      seedpod_weight = "seed_pod",
[…]

### 2015-08-17 R/figures.R

@@ -61,7 +61,7 @@ plot_ReproductionAllocation_comparison_age <- function(ReproductionAllocation_al
 
 plot_ReproductionAllocation_comparison_diam <- function(ReproductionAllocation_all) {
   cols <- col.table()
-  plot(ReproductionAllocation_all$dia, ReproductionAllocation_all$RA, type = "p", col = cols[ReproductionAllocation_all$species], xlab = "Basal Diameter, year 2013", ylab = "RA", bty = "L")
+  plot(ReproductionAllocation_all$diameter, ReproductionAllocation_all$RA, type = "p", col = cols[ReproductionAllocation_all$species], xlab = "Basal Diameter, year 2013", ylab = "RA", bty = "L")
   legend("topright", legend = names(cols), col = cols, pch = 1)
 }
 
@@ -74,7 +74,7 @@ plot_ReproductionAllocation_comparison_weight <- function(ReproductionAllocation
 plot_species_ReproductionAllocation_weight_diam_panel <- function(Data) {
     cols <- col.table()[Data$species]
     par(mfrow = c(1, 2), cex.main = 1, cex.lab = 1)
-    plot(Data$dia, Data$RA, type = "p", col = cols, xlab = "Diameter, year 2013", ylab = "RA", bty = "L", main = "Diameter", cex = 1)
+    plot(Data$diameter, Data$RA, type = "p", col = cols, xlab = "Diameter, year 2013", ylab = "RA", bty = "L", main = "Diameter", cex = 1)
 
     plot(Data$total_weight, Data$RA, type = "p", col = cols, xlab = "Weight, year 2013", ylab = "RA", bty = "L", main = "Weight", cex = 1)
 }

### 2015-08-18 errors_to_fix.rmd
moving files back from "ignore" for name changes

```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
library(remake)
create_bindings()

source("scripts/summary_dataframes.R")
source("scripts/functions.R")
```

###Problem.  
* There are two problems with the calculation of PEPU cones. I discovered this, because there were a few plants, especially PEPU_802, with huge ReproInv relative to repro_all_count  
* Looking at various data sources I discovered that the estimated FD (Final Development) parts weights for those cones were much too big, for PEPU_802 more than 10x too big  
* In addition, for PEPU_802 and PEPU_807 the aborted cones were actually collected and marked as "to use" in the flower parts data, but aren't being used
* I've looked at Konrad's scripts and can't immediately see what would be wrong

```{r}
plot(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),log="xy")
text(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),labels=individual, pos=1,offset=.6,cex=0.8,col="black")

check_FD <-as.data.frame(PEPU_Investment[3])
check_FD_aborted <- subset(check_FD,FD.what=="cone_aborted")
check_FD_aborted

check_parts <- subset(as.data.frame(PEPU_FlowerPartsData),part=="cone_aborted")
check_parts
```

###Problem.  
* As described below, I don't think using a linear fit to estimate leaf growth is appropriate, especially in the older plants
* The plots below show that for all plants, even old ones, if just the upper (narrower diameter) segments are used, the leaf weight vs. diameter plots on the main line
* However, for the points that are "basal diameter,all leaves on plant" or even (diameter of segment 2, leaf weight above segment 2), the diameter increases with little increase in leaf weight  
* this is of course because there are few leaves on the lower branches of an older plant and overall, much lower increase in whole plant leaf weight vs basal diameter  
* this means that for the plots, segment 1 (which are mostly the labeled dots) fall "above" the main line of points; for some individuals segment 2 does the same  
* This leads to an overestimate in leaf weight increase in older plants
* stem weights always look good

* looking at BOLE, age 7
    * colors represent segments, with red the entire plant, then purple, gray, green  
    * for stems, linear no matter what portion plant included  
    * for leaves, with older plants (ages 5,7,9 for BOLE, older for other species) have continued diameter increase with little increase in leaf area  
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
check <- BOLE_HarvestData

plot(dia~stem_weight,data=subset(check), pch=16,log="xy",col=col.lots[as.factor(segment)])
text(dia~stem_weight,data=subset(check,segment==1),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check), pch=16,log="xy",col=col.lots[as.factor(segment)])
text(dia~leaf_weight,data=subset(check,segment==1),labels=individual,cex=.5,pos=3,offset=-.7)
```

* Plot just have age 7 BOLE individuals
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
plot(dia~stem_weight,data=subset(check,age==7), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~stem_weight,data=subset(check,segment==1&age==7),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age==7), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~leaf_weight,data=subset(check,segment==1&age==7),labels=individual,cex=.5,pos=3,offset=-.7)
```

* At the other extreme, with PELA, effect only seed among age 32 plants, and only among 5 of the 7 reps (colors here represent individuals)
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
check <- PELA_HarvestData

plot(dia~stem_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~stem_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~leaf_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)
```

* Similarly no asymptoting at all for HATE
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
check <- HATE_HarvestData

plot(dia~stem_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~stem_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age==32), pch=16,log="xy",col=col.spp[as.factor(individual)])
text(dia~leaf_weight,data=subset(check,segment==1&age==32),labels=individual,cex=.5,pos=3,offset=-.7)
```

* COER is similar - as are many other species  
* Dots colored by age, only including 7 & 9 year old plants
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
check <- COER_HarvestData

plot(dia~stem_weight,data=subset(check,age>5), pch=16,log="xy",col=col.spp[as.factor(segment)])
text(dia~stem_weight,data=subset(check,segment==1&age>5),labels=individual,cex=.5,pos=3,offset=-.7)

plot(dia~leaf_weight,data=subset(check,age>5), pch=16,log="xy",col=col.spp[as.factor(segment)])
text(dia~leaf_weight,data=subset(check,segment==1&age>5),labels=individual,cex=.5,pos=3,offset=-.7)
```

###Problem.
* The first plot below shows that there are individuals where absolute investment in accessory tissues is larger than total reproductive investmen* There are two different sources of reproductive investment, one which comes from the file "accessory" and is the sum of all the different accessory tissues and one which comes from the dataframe "investment". The "investment" variant is what is currently being used, but not sure which one should be being used
* They are quite different from each other
```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
plot(accessory_inv~ReproInv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
abline(0,1)
text(120,350,"all RE to accessory tissues",srt=45)

plot(investment$ReproInv~accessory$total_repro_inv,log="xy",pch=16,col=col.spp[as.factor(investment$species)])
```

###Todo.  
* We have never quite finished the calculation for BAER reproductive investment. Right now investment is over-estimated, because the "cone weight" used includes the weight of the "seed pods" (since they are fused to the cone), but there is also a separate weight of "seed pods" included. So the cone weight for each "brown cone" needs to be reduced by the number of seed pods for that cone. If easiest I can do this manually

###ToDo.  
* The total plant weights for many PHPH are a huge underestimate, because they are only the weights of one of several stems emerging from the ground. RA should be accurate, since it is the ratio of reproduction to (growth + repro) on a single stem. But plots of plant size vs. RA will be very strange. Since I don't have repro from the side branches, this means I need (at least for PHPH) to introduce two "plant weight" columns, one to calculate total plant weight, leaf weight, growth, and a second to calculate RA. Happy to take this one myself.

###Question.  
* Daniel, you said that there should be graphs stored somewhere from all my .rmd files - I'm not finding these

### 2015-08-18 results_RAschedules_shorter.Rmd
moving files back from "ignore" for name changes

@@
 ```
+
+As plants approach maximum height, less of their reproductive investment is going to propagules...This only includes individuals with some propagule investment
+```{r, echo=FALSE,message=FALSE,fig.width=6, fig.height=6}
+mod <- lm(log(prop_maxH)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(prop_propagule))~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+words.bottom.left.logx(mod)
+```

### 2015-08-18 results_accessory_v3.Rmd
moving files back from "ignore" for name changes

@@
 mod <- lm (log(total_weight)~log(fruit_weight), data=subset(SummaryInd,fruit_weight>0))
-plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Fruit weight (mg)",xlim=c(100,2000000),xlab="")
+plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Fruit investment (mg)",xlim=c(100,2000000),xlab="")
 words.bottom.right.logxy(mod)
@@
 mod <- lm (log(total_weight)~log(prepollen_all_inv), data=subset(SummaryInd,prepollen_all_inv>0))
-plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="prepollen investment (mg)", xlim=c(100,2000000))
+plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Prepollen investment (mg)", xlim=c(100,2000000))
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
     - And: species with greater prepollination investment have higher accessory costs (since this is the majority of accessory costs for most species)  
-    - When all 4 variables put into a single model, depending on lots of little changes, different factors (seedset, seed size, maxH-species, pre-pollination costs come out as have the best explanatory power)
+    - When all 4 variables put into a single model, depending on how variables expressed, transforme, different factors (seedset, seed size, maxH-species, pre-pollination costs) come out as have the best explanatory power
 

### 2015-08-18 results_accessory_v3_alt_reproInv.Rmd
moving files back from "ignore" for name changes

--- 2015-08-06 results_accessory_v3.Rmd
@@
 par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-plot(accessory_inv~ReproInv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
+plot(accessory_inv~total_repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
 abline(0,1)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
-mod <- lm (log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot(ReproInv~total_weight,data=subset(SummaryInd,ReproInv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
+mod <- lm (log(total_weight)~log(total_repro_inv), data=subset(SummaryInd,total_repro_inv>0))
+plot(total_repro_inv~total_weight,data=subset(SummaryInd,total_repro_inv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
-mod <- lm(asin(sqrt(seedset))~asin(sqrt(RA)),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(asin(sqrt(RA))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+mod <- lm(asin(sqrt(seedset))~asin(sqrt(RA2)),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(asin(sqrt(RA2))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
 words.bottom.right(mod)
 
-mod <- lm(asin(sqrt(prop_propagule))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(RA))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+mod <- lm(asin(sqrt(prop_propagule))~asin(sqrt(RA2)),data=subset(SummaryInd,prop_propagule>0))
+plot(asin(sqrt(RA2))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
 words.bottom.right(mod)
@@
 
-mod <- lm(asin(sqrt(propagule_per_seed))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(RA))~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="x",pch=16,col=col.spp[as.factor(species)])
+mod <- lm(asin(sqrt(propagule_per_seed))~asin(sqrt(RA2)),data=subset(SummaryInd,prop_propagule>0))
+plot(asin(sqrt(RA2))~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="x",pch=16,col=col.spp[as.factor(species)])
 words.bottom.right.logx(mod)
@@
 options(scipen=20)
-mod <- lm(asin(sqrt(seedset))~log(ReproInv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((ReproInv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
+mod <- lm(asin(sqrt(seedset))~log(total_repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
+plot((total_repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
 words.bottom.right.logy(mod)
 
-mod <- lm(asin(sqrt(prop_propagule))~log(ReproInv),data=subset(SummaryInd,prop_propagule>0))
-plot((ReproInv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
+mod <- lm(asin(sqrt(prop_propagule))~log(total_repro_inv),data=subset(SummaryInd,prop_propagule>0))
+plot((total_repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
 words.bottom.right.logy(mod)
@@
 
-mod <- lm(log(propagule_per_seed)~log(ReproInv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((ReproInv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp[as.factor(species)])
+mod <- lm(log(propagule_per_seed)~log(total_repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
+plot((total_repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp[as.factor(species)])
 words.bottom.right.logxy(mod)
@@
 
-mod <- lm(log(RA)~log((propagule_inv)),data=subset(SummaryInd,RA>0&propagule_inv>0))
-plot(propagule_inv~RA,data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
+mod <- lm(log(RA2)~log((propagule_inv)),data=subset(SummaryInd,RA2>0&propagule_inv>0))
+plot(propagule_inv~RA2,data=subset(SummaryInd,RA2>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
 words.bottom.right.logxy(mod)
 
-mod <- lm(log(RA)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,RA>0&prop_propagule>0))
-plot(asin(sqrt(prop_propagule))~RA,data=subset(SummaryInd,RA>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+mod <- lm(log(RA2)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,RA2>0&prop_propagule>0))
+plot(asin(sqrt(prop_propagule))~RA2,data=subset(SummaryInd,RA2>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
 words.bottom.left.logx(mod)
 
-mod <- lm(log(RA)~log((prepollen_aborted_inv)),data=subset(SummaryInd,RA>0&prepollen_aborted_inv>0))
-plot(prepollen_aborted_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
+mod <- lm(log(RA2)~log((prepollen_aborted_inv)),data=subset(SummaryInd,RA2>0&prepollen_aborted_inv>0))
+plot(prepollen_aborted_inv~RA2,data=subset(SummaryInd,RA2<1&RA2>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
 words.bottom.right.logxy(mod)
 
-mod <- lm(log(RA)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0))
-plot(asin(sqrt(prop_prepollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
+mod <- lm(log(RA2)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,RA2>0&prop_prepollen_aborted>0))
+plot(asin(sqrt(prop_prepollen_aborted))~RA2,data=subset(SummaryInd,RA2>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
 words.bottom.right.logx(mod)
 
-mod <- lm(log(RA)~log((prepollen_success_inv)),data=subset(SummaryInd,RA>0&prepollen_success_inv>0))
-plot(prepollen_success_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
+mod <- lm(log(RA2)~log((prepollen_success_inv)),data=subset(SummaryInd,RA2>0&prepollen_success_inv>0))
+plot(prepollen_success_inv~RA2,data=subset(SummaryInd,RA2<1&RA2>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
 words.bottom.right.logxy(mod)
 
-mod <- lm(log(RA)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,RA>0&prop_prepollen_success>0))
-plot(asin(sqrt(prop_prepollen_success))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
+mod <- lm(log(RA2)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,RA2>0&prop_prepollen_success>0))
+plot(asin(sqrt(prop_prepollen_success))~RA2,data=subset(SummaryInd,RA2>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
 words.bottom.right.logx(mod)
 
-mod <- lm(log(RA)~log((packaging_dispersal_inv)),data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0))
-plot(packaging_dispersal_inv~RA,data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
+mod <- lm(log(RA2)~log((packaging_dispersal_inv)),data=subset(SummaryInd,RA2>0&packaging_dispersal_inv>0))
+plot(packaging_dispersal_inv~RA2,data=subset(SummaryInd,RA2>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
 words.bottom.right.logxy(mod)
@@
 
-mod <- lm(log(RA)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0))
-plot(asin(sqrt(prop_packaging_dispersal))~RA,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
+mod <- lm(log(RA2)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,RA2>0&prop_packaging_dispersal>0))
+plot(asin(sqrt(prop_packaging_dispersal))~RA2,data=subset(SummaryInd,RA2>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
 words.bottom.left.logx(mod)
 
-mod <- lm(log(RA)~log((postpollen_aborted_inv)),data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0))
-plot(postpollen_aborted_inv~RA,data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
+mod <- lm(log(RA2)~log((postpollen_aborted_inv)),data=subset(SummaryInd,RA2>0&postpollen_aborted_inv>0))
+plot(postpollen_aborted_inv~RA2,data=subset(SummaryInd,RA2>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
 words.bottom.right.logxy(mod)
 
-mod <- lm(log(RA)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0))
-plot(asin(sqrt(prop_postpollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
+mod <- lm(log(RA2)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,RA2>0&prop_postpollen_aborted>0))
+plot(asin(sqrt(prop_postpollen_aborted))~RA2,data=subset(SummaryInd,RA2>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
 words.bottom.left.logx(mod)
@@
 
-mod <- lm((prop_maxH)~log((ReproInv)),data=subset(SummaryInd,prop_maxH>0&ReproInv>0))
-plot(ReproInv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="total reproductive investment (mg)")
+mod <- lm((prop_maxH)~log((total_repro_inv)),data=subset(SummaryInd,prop_maxH>0&total_repro_inv>0))
+plot(total_repro_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&total_repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="total reproductive investment (mg)")
 words.bottom.right.logy(mod)
 
-mod <- lm((prop_maxH)~asin(sqrt(RA)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(RA))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="RA")
+mod <- lm((prop_maxH)~asin(sqrt(RA2)),data=subset(SummaryInd,prop_maxH>0))
+plot(asin(sqrt(RA2))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="RA2")
 words.bottom.left(mod)
@@
 tmp <- SummaryInd %>%
-  filter(ReproInv!=0&age>3) %>%
+  filter(total_repro_inv!=0&age>3) %>%
   group_by(species) %>%
@@
 tmp2 <- SummaryInd %>%
-  filter(ReproInv!=0&age>3) %>%
+  filter(total_repro_inv!=0&age>3) %>%
   group_by(species) %>%

### 2015-08-18 results_growth.Rmd
moving files back from "ignore" for name changes

@@
 mtext("Total weight", 2, outer=TRUE,cex=1.2)
+```
+
+```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=28}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "growth_stem_area"
+xvar <- "RA"
+
+data <- subset(SummaryInd,RA>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",
+                    main=spp)
+  abline(lmfits[[spp]])
+}
+
 ```

### 2015-08-18 results_growth_short.Rmd
moving files back from "ignore" for name changes

@@
 
-```{r, echo=FALSE,message=FALSE}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
 mod <- lm(log(GrowthInv)~log(ReproInv),data=subset(SummaryInd,ReproInv>0))
@@
 abline(0,1)
-text(5,6.5,srt=38,"RA = 0.5")
+text(2.1,3,srt=45,"RA = 0.5")
+abline(log10(3),1)
+text(2,9,srt=45,"RA = 0.75")
 abline(log10(9),1)
-text(2,23,srt=38,"RA = 0.9")
-abline(log10(.1),1)
-text(20,2.6,srt=38,"RA = 0.1")
-abline(log10(.01),1)
-text(170,2.2,srt=38,"RA = 0.01")
+text(2,25,srt=45,"RA = 0.9")
+abline(log10(19),1)
+text(2,60,srt=45,"RA = 0.95")
+abline(log10(.111),1)
+text(19,3,srt=45,"RA = 0.1")
+abline(log10(.010101),1)
+text(170,2.4,srt=45,"RA = 0.01")
+
+plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+abline(0,1)
+text(2.1,3,srt=45,"RA = 0.5")
+abline(log10(3),1)
+text(2,9,srt=45,"RA = 0.75")
+abline(log10(9),1)
+text(2,25,srt=45,"RA = 0.9")
+abline(log10(19),1)
+text(2,60,srt=45,"RA = 0.95")
+abline(log10(.111),1)
+text(19,3,srt=45,"RA = 0.1")
+abline(log10(.010101),1)
+text(170,2.4,srt=45,"RA = 0.01")
 ```

### 2015-08-18 diameter_weight_checking.R

@@ -1,0 +1,275 @@
+check <- BAER_HarvestData
+check <- BOLE_HarvestData
+check <- COER_HarvestData
+check <- EPMI_HarvestData
+check <- GRBU_HarvestData
+check <- GRSP_HarvestData
+check <- HATE_HarvestData
+check <- HEPU_HarvestData
+check <- LEES_HarvestData
+check <- PELA_HarvestData
+check <- PEPU_HarvestData
+check <- PHPH_HarvestData
+check <- PILI_HarvestData
+check <- PUTU_HarvestData
+
+plot(dia~stem_weight,data=subset(check,segment==1), pch=16,log="xy",col=col.lots[as.factor(individual)])
+text(dia~stem_weight,data=subset(check,segment==1),labels=individual,cex=.5,pos=3,offset=-.7)
+mod <- lm(log(stem_weight)~log(dia),data=subset(check,segment==1))
+words.bottom.right.logxy(mod)
+
+
+
+
+plot(leaf_weight~stem_weight,data=subset(check), pch=16,log="xy",col="red")
+text(leaf_weight~stem_weight,data=subset(check),labels=individual,cex=.5,pos=2,offset=-1)
+mod <- lm(log(stem_weight)~log(leaf_weight),data=subset(check))
+words.bottom.right.logxy(mod)
+
+#age 10 break (e.g. slightly BAER, GRSP)
+plot(leaf_weight~stem_weight,data=subset(check,age<10), pch=16,log="xy",col="red")
+points(leaf_weight~stem_weight,data=subset(check,age>10), pch=16,log="xy",col="blue")
+text(leaf_weight~stem_weight,data=subset(check,age<10),labels=individual,cex=.5,pos=2,offset=-1)
+mod <- lm(log(stem_weight)~log(leaf_weight),data=subset(check,age<10))
+words.bottom.right.logxy(mod)
+
+#age 8 break (e.g. GRBU, COER, LEES)
+plot(leaf_weight~stem_weight,data=subset(check,age<8), pch=16,log="xy",col="red")
+points(leaf_weight~stem_weight,data=subset(check,age>8), pch=16,log="xy",col="blue")
+text(leaf_weight~stem_weight,data=subset(check,age<8),labels=individual,cex=.5,pos=2,offset=-1)
+mod <- lm(log(stem_weight)~log(leaf_weight),data=subset(check,age<8))
+words.bottom.right.logxy(mod)
+
+#age 6 break 
[…]

### 2015-08-19 RA_figs.rmd
adding in additional height growth calcs

@@
 
-source("scripts/summary_dataframes.R")
 source("scripts/functions.R")
@@
 mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")
+```
+
+###Including all investment vs. growth  
+* reproducing individuals now plot closer to the "expected line" (as defined by juvenile individuals), but for most species there is still a considerable discrepency
+* fit line of veg investment vs. total plant weight through non-reproductive plants
+* derive "predicted" total investment (veg+repro) for reproducing individuals
+* determine proportional reproductive cost for reproducing individuals; probably look by age
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "TotalInv"
+xvar <- "total_weight"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
+                    main=spp,col=col.mature[as.factor(data[[spp]]$mature)])
+}
+
+mtext("Vegetative + reproductive investment (mg)", 2, outer=TRUE,cex=1.2)
+mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "growth_height"
+xvar <- "height"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
+                    main=spp,col=col.mature[as.factor(data[[spp]]$mature)])
+}
+
+###calc_veg <- merge(SummaryInd, select(results, -species), by="species",all.x=TRUE)
+###WORK HERE
+
+mtext("Increase in plant height (mm)", 2, outer=TRUE,cex=1.2)
+mtext("Plant height (mm)", 1, outer=TRUE,cex=1.2)
 legend("topleft",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")

### 2015-08-19 Accessory_figs.rmd
Add maxH as variable

@@
     * In part this is suggetsing that the species with high seedset have, on average, mostly individuals that are much 
-      shorter than the maxH achieved and that reproduction is curtailing their growth even more than maxH_spp indicates
+      shorter than the maxH achieved and that reproduction is curtailing their growth even more than maxH indicates
 

### 2015-08-19 RA_figs.rmd
Add maxH as variable

@@
   filter(lvs_end_total>0&shoot_leaf_area>0&shoot_leaf_area_growth!=0) %>%
-  select(prop_maxH,height,maxH_spp,wood_density,LMA_mean,seed_size,growth_leaf,
+  select(prop_maxH,height,maxH,wood_density,LMA_mean,seed_size,growth_leaf,
          growth_stem_diam,leaf_area,growth_shoot_diam,growth_stem_area,lvs_end_total,total_weight,
@@
 SummaryIndPCA$height <- log(SummaryIndPCA$height)
-SummaryIndPCA$maxH_spp <- log(SummaryIndPCA$maxH_spp)
+SummaryIndPCA$maxH <- log(SummaryIndPCA$maxH)
 SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
@@
 * It is dividing the three (of 4) canopy species, HATE, PEPU, PELA, (BAER) versus
-* top variable loadings: scaled_growth_stem_diam, wood_density,growth_stem_diam, lvs_end_total vs. maxH_spp, LMA_mean, seed_size, RA  
+* top variable loadings: scaled_growth_stem_diam, wood_density,growth_stem_diam, lvs_end_total vs. maxH, LMA_mean, seed_size, RA  
 * not terribly interpretable, since doesn't make sense that scaled_growth_stem_diam with wood_density

### 2015-08-19 results_RAschedules_shorter.Rmd
Add maxH as variable

@@
 words.top.right.logxy(mod)
-plot(RA_mean~maxH_spp, SummarySpp, col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
-mod <- lm(log(maxH_spp)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
+plot(RA_mean~maxH, SummarySpp, col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+mod <- lm(log(maxH)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
 words.bottom.left.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
-plot(maxH_spp~WD_mean,data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="y",ylab="")
+plot(maxH~WD_mean,data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="y",ylab="")
 mod <- lm(mature_RA_mean~asin(sqrt(mature_RA_mean)),data=subset(SummarySpp,species!="BAER"))
@@
 words.top.right.logxy(mod)
-plot(mature_RA_mean~maxH_spp, data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
-mod <- lm(log(maxH_spp)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
+plot(mature_RA_mean~maxH, data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+mod <- lm(log(maxH)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
 words.bottom.left.logxy(mod)
@@
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-mod <- lm(log(growth_stem_diam) ~ age*WD_mean*LMA_mean*maxH_spp*RA, SummaryInd)
+mod <- lm(log(growth_stem_diam) ~ age*WD_mean*LMA_mean*maxH*RA, SummaryInd)
 anova(mod)
@@
 words.top.right.logxy(mod)
-plot(RA~maxH_spp, SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy",ylim=c(.0008,1))
-points((RA+.001)~maxH_spp,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=spp_zero_RA$RAcex)
-mod <- lm(log(maxH_spp)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
+plot(RA~maxH, SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy",ylim=c(.0008,1))
+points((RA+.001)~maxH,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=spp_zero_RA$RAcex)
+mod <- lm(log(maxH)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
 words.bottom.left.logxy(mod)

### 2015-08-19 results_growth.Rmd
Add maxH as variable

@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==1.4))
+plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==2.4))
+plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age==2.4))
 words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ maxH_spp,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ maxH_spp, data=subset(SummarySppAge,age>3))
+plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age>3))
 words.bottom.right.logxy(mod)
@@
   filter(lvs_end_total>0&shoot_leaf_area>0&shoot_leaf_area_growth!=0) %>%
-  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
+  select(prop_maxH,height,maxH,WD_mean,LMA_mean,seed_size,growth_leaf,
          RGR,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
@@
 * PC3 is somewhat similar. It is also prop_accessory and prop_maxH vs seed set and prop_propagule, but it now separates out all the shoot growth values
-* PC4 is now the axis that separates LMA_mean and maxH vs. WD_mean, with variables like maxH_spp pulling toward all the "big size" arrows
+* PC4 is now the axis that separates LMA_mean and maxH vs. WD_mean, with variables like maxH pulling toward all the "big size" arrows
 
@@
   filter(lvs_end_total>0&accessory_inv>0&shoot_leaf_area_growth!=0) %>%
-  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
+  select(prop_maxH,height,maxH,WD_mean,LMA_mean,seed_size,growth_leaf,
          RGR,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
@@
 
-mod <- lm(RGR~asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1)+WD_mean+LMA_mean+maxH_spp,SummaryInd)
+mod <- lm(RGR~asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1)+WD_mean+LMA_mean+maxH,SummaryInd)
 anova(mod)
@@
 * another of the interesting pattern is that the increase in shoot area of leaders is correlated with maxH and seed_size (and opposite WD_mean) and somewhat offset from whole plant growth measures and whole plant size measures
-* seed_size removed, because no additional explanatory power after WD and maxH_spp included
+* seed_size removed, because no additional explanatory power after WD and maxH included
 
 ```{r, echo=FALSE,message=FALSE}
-mod <- lm(log(growth_shoot_area)~log(maxH_spp)+WD_mean+log(growth_stem_area)+log(total_weight)+RGR+asin(sqrt(RA))+LMA_mean,SummaryInd)
+mod <- lm(log(growth_shoot_area)~log(maxH)+WD_mean+log(growth_stem_area)+log(total_weight)+RGR+asin(sqrt(RA))+LMA_mean,SummaryInd)
 anova(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-plot(WD_mean~maxH_spp,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
-mod <- lm(log(maxH_spp)~WD_mean,SummaryInd)
+plot(WD_mean~maxH,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(maxH)~WD_mean,SummaryInd)
 words.bottom.left.logx(mod)
 
-plot(WD_mean~maxH_spp,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"), log="x",col=col.spp[as.factor(species)],pch=16)
-mod <- lm(log(maxH_spp)~WD_mean,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"))
+plot(WD_mean~maxH,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"), log="x",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(maxH)~WD_mean,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"))
 words.bottom.left.logx(mod)
@@
 
-plot(seedset_mean~maxH_spp,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
-mod <- lm(log(maxH_spp) ~ (seedset_mean),SummarySpp)
+plot(seedset_mean~maxH,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(maxH) ~ (seedset_mean),SummarySpp)
 words.bottom.left.logx(mod)

### 2015-08-19 results_growth_short.Rmd
Add maxH as variable

@@
 
-SummaryInd$prop_growth_height <- SummaryInd$growth_height/SummaryInd$maxH_spp
+SummaryInd$prop_growth_height <- SummaryInd$growth_height/SummaryInd$maxH
 
@@
   filter(lvs_end_total>0&shoot_leaf_area>0&shoot_leaf_area_growth!=0) %>%
-  select(prop_maxH,height,maxH_spp,WD_mean,LMA_mean,seed_size,growth_leaf,
+  select(prop_maxH,height,maxH,WD_mean,LMA_mean,seed_size,growth_leaf,
          growth_stem_diam,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,

### 2015-08-19 Accessory_figs.rmd
Rename *Inv variables

@@
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
-mod <- lm (log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot(ReproInv~total_weight,data=subset(SummaryInd,ReproInv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
+mod <- lm (log(total_weight)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
+plot(repro_inv~total_weight,data=subset(SummaryInd,repro_inv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-plot(accessory_inv~ReproInv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)],
+plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)],
      xlim=c(1,700000),ylim=c(1,700000),xlab="Total reproductive investment (mg)",ylab="Investment in accessory tissues (mg)")
@@
 options(scipen=20)
-mod <- lm(asin(sqrt(seedset))~log(ReproInv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((ReproInv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
+mod <- lm(asin(sqrt(seedset))~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
+plot((repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
 words.bottom.right.logy(mod)
 
-mod <- lm(asin(sqrt(prop_propagule))~log(ReproInv),data=subset(SummaryInd,prop_propagule>0))
-plot((ReproInv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
+mod <- lm(asin(sqrt(prop_propagule))~log(repro_inv),data=subset(SummaryInd,prop_propagule>0))
+plot((repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
 words.bottom.right.logy(mod)
@@
 
-mod <- lm(log(propagule_per_seed)~log(ReproInv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((ReproInv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp[as.factor(species)])
+mod <- lm(log(propagule_per_seed)~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
+plot((repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp[as.factor(species)])
 words.bottom.right.logxy(mod)
@@
 ###5. What influences the correlation between RA and plant size (or total reproductive investment)?
-  ***Don't trust anything until I know RA and ReproInv are correct, because PHPH and PUTU have huge influence on patterns***
+  ***Don't trust anything until I know RA and repro_inv are correct, because PHPH and PUTU have huge influence on patterns***
 ```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=30,warning=FALSE}
@@
 tmp <- SummaryInd %>%
-  filter(ReproInv!=0&age>3) %>%
+  filter(repro_inv!=0&age>3) %>%
   group_by(species) %>%
@@
 tmp2 <- SummaryInd %>%
-  filter(ReproInv!=0&age>3) %>%
+  filter(repro_inv!=0&age>3) %>%
   group_by(species) %>%

### 2015-08-19 Growth_figs.rmd
Rename *Inv variables

@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "GrowthInv"
+yvar <- "growth_inv"
 xvar <- "prop_maxH"

### 2015-08-19 Panalysis.rmd
Rename *Inv variables

@@
 ```{r, echo=FALSE,results='hide', message=FALSE}
-libReproInvry(remake)
+librepro_invry(remake)
 create_bindings()
 
-source("scripts/summary_datafReproInvmes.R")
+source("scripts/summary_datafrepro_invmes.R")
 source("scripts/functions.R")
@@
 
-mod <- lm(log(ReproInv)~log((propagule_inv)),data=subset(SummaryInd,ReproInv>0&propagule_inv>0))
-plot(propagule_inv~ReproInv,data=subset(SummaryInd,ReproInv>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
+mod <- lm(log(repro_inv)~log((propagule_inv)),data=subset(SummaryInd,repro_inv>0&propagule_inv>0))
+plot(propagule_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
 abline(0,1)
@@
 
-mod <- lm(log(ReproInv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,ReproInv>0&prop_propagule>0))
-plot(asin(sqrt(prop_propagule))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+mod <- lm(log(repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,repro_inv>0&prop_propagule>0))
+plot(asin(sqrt(prop_propagule))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
 words.bottom.left.logx(mod)
 
-mod <- lm(log(ReproInv)~log((prepollen_aborted_inv)),data=subset(SummaryInd,ReproInv>0&prepollen_aborted_inv>0))
-plot(prepollen_aborted_inv~ReproInv,data=subset(SummaryInd,ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
+mod <- lm(log(repro_inv)~log((prepollen_aborted_inv)),data=subset(SummaryInd,repro_inv>0&prepollen_aborted_inv>0))
+plot(prepollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
 abline(0,1)
@@
 
-mod <- lm(log(ReproInv)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,ReproInv>0&prop_prepollen_aborted>0))
-plot(asin(sqrt(prop_prepollen_aborted))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
+mod <- lm(log(repro_inv)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,repro_inv>0&prop_prepollen_aborted>0))
+plot(asin(sqrt(prop_prepollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
 words.bottom.right.logx(mod)
 
-mod <- lm(log(ReproInv)~log((prepollen_success_inv)),data=subset(SummaryInd,ReproInv>0&prepollen_success_inv>0))
-plot(prepollen_success_inv~ReproInv,data=subset(SummaryInd,ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
+mod <- lm(log(repro_inv)~log((prepollen_success_inv)),data=subset(SummaryInd,repro_inv>0&prepollen_success_inv>0))
+plot(prepollen_success_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
 abline(0,1)
@@
 
-mod <- lm(log(ReproInv)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,ReproInv>0&prop_prepollen_success>0))
-plot(asin(sqrt(prop_prepollen_success))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
+mod <- lm(log(repro_inv)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,repro_inv>0&prop_prepollen_success>0))
+plot(asin(sqrt(prop_prepollen_success))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
 words.bottom.right.logx(mod)
 
-mod <- lm(log(ReproInv)~log((packaging_dispersal_inv)),data=subset(SummaryInd,ReproInv>0&packaging_dispersal_inv>0))
-plot(packaging_dispersal_inv~ReproInv,data=subset(SummaryInd,ReproInv>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
+mod <- lm(log(repro_inv)~log((packaging_dispersal_inv)),data=subset(SummaryInd,repro_inv>0&packaging_dispersal_inv>0))
+plot(packaging_dispersal_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
 abline(0,1)
@@
 
-mod <- lm(log(ReproInv)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,ReproInv>0&prop_packaging_dispersal>0))
-plot(asin(sqrt(prop_packaging_dispersal))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
+mod <- lm(log(repro_inv)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,repro_inv>0&prop_packaging_dispersal>0))
+plot(asin(sqrt(prop_packaging_dispersal))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
 words.bottom.left.logx(mod)
 
-mod <- lm(log(ReproInv)~log((postpollen_aborted_inv)),data=subset(SummaryInd,ReproInv>0&postpollen_aborted_inv>0))
-plot(postpollen_aborted_inv~ReproInv,data=subset(SummaryInd,ReproInv>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
+mod <- lm(log(repro_inv)~log((postpollen_aborted_inv)),data=subset(SummaryInd,repro_inv>0&postpollen_aborted_inv>0))
+plot(postpollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
 abline(0,1)
@@
 
-mod <- lm(log(ReproInv)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,ReproInv>0&prop_postpollen_aborted>0))
-plot(asin(sqrt(prop_postpollen_aborted))~ReproInv,data=subset(SummaryInd,ReproInv>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
+mod <- lm(log(repro_inv)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,repro_inv>0&prop_postpollen_aborted>0))
+plot(asin(sqrt(prop_postpollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
 words.bottom.left.logx(mod)
@@
 yvar <- "repro_all_count"
-xvar <- "ReproInv"
+xvar <- "repro_inv"
 
@@
 
-plot(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),log="xy")
-text(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),labels=individual, pos=1,offset=.6,cex=0.8,col="black")
+plot(repro_inv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),log="xy")
+text(repro_inv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),labels=individual, pos=1,offset=.6,cex=0.8,col="black")
 

### 2015-08-19 RA_figs.rmd
Rename *Inv variables

@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
-mod <- lm(log(GrowthInv)~log(ReproInv),data=subset(SummaryInd,ReproInv>0))
-plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
+plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
 words.top.left.logxy(mod)
@@
 
-plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
 legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "ReproInv"
+yvar <- "repro_inv"
 xvar <- "total_weight"
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "GrowthInv"
+yvar <- "growth_inv"
 xvar <- "total_weight"
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "TotalInv"
+yvar <- "total_inv"
 xvar <- "total_weight"

### 2015-08-19 errors_to_fix.rmd
Rename *Inv variables

@@
 ###Problem.  
-* There are two problems with the calculation of PEPU cones. I discovered this, because there were a few plants, especially PEPU_802, with huge ReproInv relative to repro_all_count  
+* There are two problems with the calculation of PEPU cones. I discovered this, because there were a few plants, especially PEPU_802, with huge repro_inv relative to repro_all_count  
 * Looking at various data sources I discovered that the estimated FD (Final Development) parts weights for those cones were much too big, for PEPU_802 more than 10x too big  
@@
 ```{r}
-plot(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),log="xy")
-text(ReproInv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),labels=individual, pos=1,offset=.6,cex=0.8,col="black")
+plot(repro_inv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),log="xy")
+text(repro_inv~repro_all_count,data=subset(SummaryInd, repro_all_count>0&species=="PEPU"),labels=individual, pos=1,offset=.6,cex=0.8,col="black")
 
@@
 ```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
-plot(accessory_inv~ReproInv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
+plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
 abline(0,1)
@@
 
-plot(investment$ReproInv~accessory$total_repro_inv,log="xy",pch=16,col=col.spp[as.factor(investment$species)])
+plot(investment$repro_inv~accessory$total_repro_inv,log="xy",pch=16,col=col.spp[as.factor(investment$species)])
 ```

### 2015-08-19 results_RAschedules_shorter.Rmd
Rename *Inv variables

@@
 * There is a disinct decline in RGR (or Growth Investment) at the exact "prop_maxH" that plants begin to reproduce 
-* Plotting reproductive investment (ReproInv) against RGR yields a much lower r^2 - for every single species.
+* Plotting reproductive investment (repro_inv) against RGR yields a much lower r^2 - for every single species.
 Only RA captures the actual trade-off incurred by plants that allocate more to reproduction, showing one way RA schedules are important
@@
 ```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
-mod <- lm(log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot(ReproInv~total_weight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(total_weight)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
+plot(repro_inv~total_weight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-mod <- lm(log(height)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot(ReproInv~height, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(height)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
+plot(repro_inv~height, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-mod <- lm((prop_maxH)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot((ReproInv)~(prop_maxH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
+mod <- lm((prop_maxH)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
+plot((repro_inv)~(prop_maxH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
-mod <- lm(log(total_weight)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
+mod <- lm(log(total_weight)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
 plot(asin(sqrt(RA))~total_weight, SummaryInd, log="x",col=col.spp[as.factor(species)],pch=16)
@@
 
-mod <- lm(log(height)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
+mod <- lm(log(height)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
 plot(asin(sqrt(RA))~height, SummaryInd, log="x",col=col.spp[as.factor(species)],pch=16)
@@
 
-mod <- lm((prop_maxH)~asin(sqrt(RA)), data=subset(SummaryInd,ReproInv>0))
+mod <- lm((prop_maxH)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
 plot((asin(sqrt(RA)))~(prop_maxH), SummaryInd,col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
@@
 ```{r, echo=FALSE,message=FALSE, warning=FALSE, fig.width=21, fig.height=7}
-yvar <- "ReproInv"
+yvar <- "repro_inv"
 xvar <- "age"
 
-yvar2 <- "ReproInv"
+yvar2 <- "repro_inv"
 xvar2 <- "total_weight"
 
-yvar3 <- "ReproInv"
+yvar3 <- "repro_inv"
 xvar3 <- "height"
@@
 ```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
-yvar <- "ReproInv"
+yvar <- "repro_inv"
 xvar <- "height"
@@
 ```{r, echo=FALSE,message=FALSE, fig.width=7, fig.height=7}
-yvar <- "ReproInv"
+yvar <- "repro_inv"
 xvar <- "total_weight"
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
-mod <- lm(log(GrowthInv)~log(ReproInv),data=subset(SummaryInd,ReproInv>0))
-plot((1+ReproInv)~GrowthInv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
+plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 ###Looking jointly at effects of RA and prop_maxH on growth inveestment
-- Model analyzed is: lm(log([[GrowthInv]]) ~  asin(sqrt([[RA]]))*asin(sqrt([[prop_maxH]]))))  
+- Model analyzed is: lm(log([[growth_inv]]) ~  asin(sqrt([[RA]]))*asin(sqrt([[prop_maxH]]))))  
 - The canopy species have, not suprisingly, a very obvious maxH, with Growth Investment or RGR tapering markedly at the maxH is approached.
@@
 ```{r, echo=FALSE, message=FALSE}
-yvar <- "GrowthInv"
+yvar <- "growth_inv"
 xvar <- "RA"

### 2015-08-19 results_accessory_shorter.Rmd
Rename *Inv variables

@@
 par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
-mod <- lm(log(ReproInv)~(prop_prepollen_all),data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1))
-plot((prop_prepollen_all)~ReproInv,data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1), log="x", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Pre-pollination tissues (as proportion repro inv)")
+mod <- lm(log(repro_inv)~(prop_prepollen_all),data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1))
+plot((prop_prepollen_all)~repro_inv,data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1), log="x", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Pre-pollination tissues (as proportion repro inv)")
 words.top.right.logx(mod)
@@
 
-mod <- lm(log(ReproInv)~log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
-plot(prop_propagule~ReproInv,data=subset(SummaryInd,prop_propagule>0), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Propagules (as proportion repro inv)")
+mod <- lm(log(repro_inv)~log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
+plot(prop_propagule~repro_inv,data=subset(SummaryInd,prop_propagule>0), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Propagules (as proportion repro inv)")
 words.top.right.logxy(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(0.3,0.3,0.1,0.3), mai=c(1.1,1,0.3,0.3)) 
-mod <- lm(log(RA)~log((ReproInv)),data=subset(SummaryInd,RA>0))
-plot(RA~(ReproInv),data=subset(SummaryInd,RA>0), pch=16,col=col.spp[as.factor(species)],log="xy")
+mod <- lm(log(RA)~log((repro_inv)),data=subset(SummaryInd,RA>0))
+plot(RA~(repro_inv),data=subset(SummaryInd,RA>0), pch=16,col=col.spp[as.factor(species)],log="xy")
 words.bottom.right.logxy(mod)
@@
 
-mod <- lm(log(RA)~species*age*log((ReproInv)),data=subset(SummaryInd,RA>0))
+mod <- lm(log(RA)~species*age*log((repro_inv)),data=subset(SummaryInd,RA>0))
 anova(mod)

### 2015-08-19 results_accessory_v3.Rmd
Rename *Inv variables

@@
 par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-plot(accessory_inv~ReproInv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
+plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
 abline(0,1)
@@
 
-mod <- lm((prop_maxH)~log((ReproInv)),data=subset(SummaryInd,prop_maxH>0&ReproInv>0))
-plot(ReproInv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&ReproInv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="total reproductive investment (mg)")
+mod <- lm((prop_maxH)~log((repro_inv)),data=subset(SummaryInd,prop_maxH>0&repro_inv>0))
+plot(repro_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="total reproductive investment (mg)")
 words.bottom.right.logy(mod)

### 2015-08-19 results_growth.Rmd
Rename *Inv variables

@@
 par(mfrow=c(1,2), cex=1, omi=c(.8,0.3,.5,0.2), mai=c(.7,1,.1,0.2))
-plot((GrowthInv~prop_maxH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16,xlab="")
+plot((growth_inv~prop_maxH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16,xlab="")
 legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(GrowthInv~prop_maxH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16,ylab="",xlab="")
+plot(growth_inv~prop_maxH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16,ylab="",xlab="")
 legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(GrowthInv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
+plot(growth_inv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
 legend("topleft",col=col.age, labels.age, pch=16, cex=1,bty="n")
-text(GrowthInv_mean ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+text(growth_inv_mean ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
 ```
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age==1.4))
+plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age==2.4))
+plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==2.4))
 words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ maxH, data=subset(SummarySppAge,age>3))
+plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age>3))
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
+plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
 words.bottom.left.logxy(mod)
 
-plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
+plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
 words.bottom.left.logxy(mod)
@@
 
-plot(GrowthInv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ WD_mean, data=subset(SummarySppAge,age>3))
+plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age>3))
 words.bottom.left.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(GrowthInv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
-text(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4))
+plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
+text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings",ylim=c(100,100000))
-text(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==2.4))
+plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings",ylim=c(100,100000))
+text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==2.4))
 words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
-text(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age>3))
+plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
+text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age>3))
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4))
+plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4))
+plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4))
 words.bottom.right.logxy(mod)
@@
 
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3))
+plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3))
 words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3&species!="HATE"),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3&species!="HATE"), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3&species!="HATE"))
+plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3&species!="HATE"),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3&species!="HATE"), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3&species!="HATE"))
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2))
-plot(GrowthInv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(log(LL_death_mean)~log(GrowthInv_mean), data=subset(SummarySppAge,age==1.4))
+plot(growth_inv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(log(LL_death_mean)~log(growth_inv_mean), data=subset(SummarySppAge,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==2.4))
+plot(growth_inv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==2.4))
 words.bottom.right.logxy(mod)
 
-plot(GrowthInv_mean ~ LL_death_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(GrowthInv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3))
+plot(growth_inv_mean ~ LL_death_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3))
 legend("topright",col=col.age,labels.age,pch=16, bty="n")

### 2015-08-19 R/ReproductionAllocation.R

@@ -36,22 +36,22 @@ RA_Calculations <- function(thisSpecies, Species_Investment, HarvestData, Maps, 
   GrowthEst <- HarvestData_basal %>%
     group_by(individual) %>%
     mutate(total_weight_est =  predict_total_weight(diameter, individual[1]),
-           GrowthInv = c(NA, diff(total_weight_est)),
+           growth_inv = c(NA, diff(total_weight_est)),
            stem_weight_est = predict_stem_weight(diameter, individual[1]),
            growth_stem = c(NA, diff(stem_weight_est)),
-           growth_leaf =  GrowthInv - growth_stem,
+           growth_leaf =  growth_inv - growth_stem,
            growth_height = c(NA, diff(height)),
            growth_stem_diam = c(NA, diff(diameter)),
            growth_stem_area = c(NA, diff(stem_area))
            ) %>%
     filter(start_end == "end") %>%
-    select(species, site, individual, age, height, diameter, stem_area, leaf_weight, stem_weight, total_weight, GrowthInv, growth_stem, growth_leaf, growth_height, growth_stem_diam, growth_stem_area)
+    select(species, site, individual, age, height, diameter, stem_area, leaf_weight, stem_weight, total_weight, growth_inv, growth_stem, growth_leaf, growth_height, growth_stem_diam, growth_stem_area)
 
     # Use saved data to calculate total reproduction investment per individual plant
     ReproTotal <- Species_Investment$Investment %>%
      group_by(individual) %>%
      summarise(
-      ReproInv = sum(Total)
+      repro_inv = sum(Total)
       )
 
   # Merge two tables and calculate total investment and RAR
@@ -61,6 +61,6 @@ RA_Calculations <- function(thisSpecies, Species_Investment, HarvestData, Maps, 
 
   InvestmentSummary %>%
     mutate(
-      TotalInv = ReproInv + GrowthInv,
-      RA = ReproInv/TotalInv)
+      total_inv = repro_inv + growth_inv,
+      RA = repro_inv/total_inv)
 }

### 2015-08-19 scripts/lab_meeting_20150328.R

@@ -139,39 +139,39 @@ legend("bottomright",col=col.age2,labels.age2,pch=16)
 But there is no relationship in seedlings (age=1.4) or saplings (age=2.4)
 This is not predicted by Daniel's model or Anais' review
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Seedlings")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Seedlings")
+text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
 
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="pink",pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Saplings")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
+plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="pink",pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Saplings")
+text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.9,col="blue")
 
-plot(GrowthInv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1.2,xlab="LMA",ylab="growth investment (mg per year)",main="Adults")
-text(GrowthInv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
[…]

### 2015-08-19 Growth_figs.rmd
Big variable rename

@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "growth_stem_diam"
-xvar <- "growth_shoot_diam"
+yvar <- "growth_stem_diameter"
+xvar <- "growth_shoot_diameter"
 
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "leaf_area_growth"
-xvar <- "shoot_leaf_area_growth"
+yvar <- "growth_leaf_area"
+xvar <- "shoot_growth_leaf_area"
 
@@
 par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
-plot(growth_stem_diam~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp[as.factor(species)])
+plot(growth_stem_diameter~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp[as.factor(species)])
 ```
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "growth_stem_diam"
+yvar <- "growth_stem_diameter"
 xvar <- "prop_maxH"
@@
 
-mtext("growth_stem_diam", 2, outer=TRUE,cex=1.2)
+mtext("growth_stem_diameter", 2, outer=TRUE,cex=1.2)
 mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
@@
 par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
-plot(leaf_area_growth~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp[as.factor(species)])
+plot(growth_leaf_area~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp[as.factor(species)])
 ```
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "leaf_area_growth"
+yvar <- "growth_leaf_area"
 xvar <- "prop_maxH"
@@
 
-plot(wood_density~leaf_area_growth,SummaryInd,log="y",pch=16,col=col.age[as.factor(age)])
-mod <- lm(log(leaf_area_growth)~age*wood_density,SummaryInd)
+plot(wood_density~growth_leaf_area,SummaryInd,log="y",pch=16,col=col.age[as.factor(age)])
+mod <- lm(log(growth_leaf_area)~age*wood_density,SummaryInd)
 summary(mod)

### 2015-08-19 Panalysis.rmd
Big variable rename

@@
 par(mfrow=c(1,1), cex=1, omi=c(.8,.8,.1,.1), mai=c(1.1,1,.4,0.2)) 
-plot(asin(sqrt(prop_growth_stem_diam))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0),pch=16,col=col.spp[as.factor(species)])
-mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_growth_stem_diam)),data=subset(SummaryInd,RA>0))
+plot(asin(sqrt(prop_growth_stem_diameter))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0),pch=16,col=col.spp[as.factor(species)])
+mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_growth_stem_diameter)),data=subset(SummaryInd,RA>0))
 words.bottom.left(mod)

### 2015-08-19 RA_figs.rmd
Big variable rename

@@
 par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
-plot(asin(sqrt(RA))~growth_stem_diam,data=subset(SummaryInd,RA>0),log="x",col=col.spp[as.factor(species)], pch=16)
-mod <- lm(log(growth_stem_diam)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
+plot(asin(sqrt(RA))~growth_stem_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp[as.factor(species)], pch=16)
+mod <- lm(log(growth_stem_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
 words.top.right.logx(mod)
@@
 
-plot(asin(sqrt(RA))~growth_shoot_diam,data=subset(SummaryInd,RA>0),log="x",col=col.spp[as.factor(species)], pch=16)
-mod <- lm(log(growth_shoot_diam)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
+plot(asin(sqrt(RA))~growth_shoot_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp[as.factor(species)], pch=16)
+mod <- lm(log(growth_shoot_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
 words.top.right.logx(mod)
@@
 yvar <- "RA"
-xvar <- "growth_stem_diam"
+xvar <- "growth_stem_diameter"
 
@@
 yvar <- "RA"
-xvar <- "growth_shoot_diam"
+xvar <- "growth_shoot_diameter"
 
@@
 SummaryIndPCA <- SummaryInd %>%
-  filter(lvs_end_total>0&shoot_leaf_area>0&shoot_leaf_area_growth!=0) %>%
+  filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
   select(prop_maxH,height,maxH,wood_density,LMA_mean,seed_size,growth_leaf,
-         growth_stem_diam,leaf_area,growth_shoot_diam,growth_stem_area,lvs_end_total,total_weight,
-         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth,scaled_growth_stem_diam)
+         growth_stem_diameter,leaf_area,growth_shoot_diameter,growth_stem_area,shoot_leaf_count,total_weight,
+         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area,scaled_growth_stem_diameter)
 
@@
 SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
-SummaryIndPCA$growth_shoot_diam <- log(SummaryIndPCA$growth_shoot_diam+.001)
+SummaryIndPCA$growth_shoot_diameter <- log(SummaryIndPCA$growth_shoot_diameter+.001)
 SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
 SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
-SummaryIndPCA$lvs_end_total <- log(SummaryIndPCA$lvs_end_total)
-SummaryIndPCA$growth_stem_diam <- log(SummaryIndPCA$growth_stem_diam)
+SummaryIndPCA$shoot_leaf_count <- log(SummaryIndPCA$shoot_leaf_count)
+SummaryIndPCA$growth_stem_diameter <- log(SummaryIndPCA$growth_stem_diameter)
 SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
-SummaryIndPCA$shoot_leaf_area_growth <- log(SummaryIndPCA$shoot_leaf_area_growth)
-SummaryIndPCA$scaled_growth_stem_diam <- log(SummaryIndPCA$scaled_growth_stem_diam)
+SummaryIndPCA$shoot_growth_leaf_area <- log(SummaryIndPCA$shoot_growth_leaf_area)
+SummaryIndPCA$scaled_growth_stem_diameter <- log(SummaryIndPCA$scaled_growth_stem_diameter)
 SummaryIndPCA$RA <- asin(sqrt(SummaryIndPCA$RA))
@@
 PCA_scores <- as.data.frame(PCA_mod$x)
-PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$lvs_end_total>0&SummaryInd$shoot_leaf_area_growth!=0)
+PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$shoot_leaf_count>0&SummaryInd$shoot_growth_leaf_area!=0)
 SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)
@@
 * it explains 23% of the variance 
-* top variable loadings: shoot_leaf_area_growth and growth_shoot_diam vs repro_all_count, RA, prop_maxH - a collection of variables that shift fro each to late in life   
+* top variable loadings: shoot_growth_leaf_area and growth_shoot_diameter vs repro_all_count, RA, prop_maxH - a collection of variables that shift fro each to late in life   
 * COER, EPMI,PELA, and PEPU have the higher loadings and BOLE, LEES have the lowest - to first order these differences are about the average age of reproducing individuals of each species
@@
 * It is dividing the three (of 4) canopy species, HATE, PEPU, PELA, (BAER) versus
-* top variable loadings: scaled_growth_stem_diam, wood_density,growth_stem_diam, lvs_end_total vs. maxH, LMA_mean, seed_size, RA  
-* not terribly interpretable, since doesn't make sense that scaled_growth_stem_diam with wood_density
+* top variable loadings: scaled_growth_stem_diameter, wood_density,growth_stem_diameter, shoot_leaf_count vs. maxH, LMA_mean, seed_size, RA  
+* not terribly interpretable, since doesn't make sense that scaled_growth_stem_diameter with wood_density
 
@@
 * it divides stem vs shoot growth variables  
-* high loadings for growth_stem_area, growth_leaf, LMA_mean, seed_set vs low loadings for shoot_leaf_area_growth, wood_density, prop_maxH, seed_size  
+* high loadings for growth_stem_area, growth_leaf, LMA_mean, seed_set vs low loadings for shoot_growth_leaf_area, wood_density, prop_maxH, seed_size  
 * BAER, EPMI, HATE and HEPU have higher values vs.

### 2015-08-19 results_growth.Rmd
Big variable rename

@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(lvs_end_total~age,data=subset(SummaryInd,age>2),log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
+plot(shoot_leaf_count~age,data=subset(SummaryInd,age>2),log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
 legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=1,bty="n")
 
-yvar <- "lvs_end_total"
+yvar <- "shoot_leaf_count"
 xvar <- "age"
@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-mod <- lm(prop_maxH~new_length,data=subset(SummaryInd,age>2))
-plot(new_length~prop_maxH,data=subset(SummaryInd,age>2),log="y", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(prop_maxH~growth_shoot_length,data=subset(SummaryInd,age>2))
+plot(growth_shoot_length~prop_maxH,data=subset(SummaryInd,age>2),log="y", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
 legend(12,200,col=col.spp, legend=names(labels.spp), pch=16, cex=.8,bty="n")
@@
 
-mod <- lm(age~species*new_length,data=subset(SummaryInd,age>2))
-plot(new_length~age,data=subset(SummaryInd,age>2),log="xy", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
+mod <- lm(age~species*growth_shoot_length,data=subset(SummaryInd,age>2))
+plot(growth_shoot_length~age,data=subset(SummaryInd,age>2),log="xy", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
 words.bottom.right.logxy(mod)
@@
 
-yvar <- "new_length"
+yvar <- "growth_shoot_length"
 xvar <- "age"
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.7,.5,0.2)) 
-yvar <- "new_length"
+yvar <- "growth_shoot_length"
 xvar <- "age"
@@
 SummaryIndPCA <- SummaryInd %>%
-  filter(lvs_end_total>0&shoot_leaf_area>0&shoot_leaf_area_growth!=0) %>%
+  filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
   select(prop_maxH,height,maxH,WD_mean,LMA_mean,seed_size,growth_leaf,
-         RGR,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
-         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth)
+         RGR,leaf_area,growth_shoot_area,growth_stem_area,shoot_leaf_count,total_weight,
+         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area)
 
@@
 SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
-SummaryIndPCA$lvs_end_total <- log(SummaryIndPCA$lvs_end_total)
+SummaryIndPCA$shoot_leaf_count <- log(SummaryIndPCA$shoot_leaf_count)
 SummaryIndPCA$growth_stem_area <- log(SummaryIndPCA$growth_stem_area)
 SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
-SummaryIndPCA$shoot_leaf_area_growth <- log(SummaryIndPCA$shoot_leaf_area_growth)
+SummaryIndPCA$shoot_growth_leaf_area <- log(SummaryIndPCA$shoot_growth_leaf_area)
 
@@
 * PC3 primarily separates LMA and maxH from WD; high wood density is also somewhat associated with higher RGR and various shoot growth and leafiness measures, reflecting that younger individuals have more shoot growth and higher RGR
-* PC4 is effectively leaf count on shoots ("lvs_end_total") and seed set vs.
+* PC4 is effectively leaf count on shoots ("shoot_leaf_count") and seed set vs.
 seed size, shoot leaf area and shoot leaf area growth - to first order, some plants have lots of small leaves and others have fewer leaves but greater leaf area, Not sure how seed size fits in
@@
 "growth_shoot_area") and other whole plant variables (e.g.
-"leaf_area_growth"), are somewhat correlated with both RGR (PC2) and the "maxH" direction (PC1).
+"growth_leaf_area"), are somewhat correlated with both RGR (PC2) and the "maxH" direction (PC1).
 I suppose this suggests that for plants with high
@@
 PCA_by_species <- SummaryInd_PCA_results %>%
-  filter(lvs_end_total>0) %>%
+  filter(shoot_leaf_count>0) %>%
   group_by(species) %>%
@@
 SummaryIndPCA <- SummaryInd %>%
-  filter(lvs_end_total>0&accessory_inv>0&shoot_leaf_area_growth!=0) %>%
+  filter(shoot_leaf_count>0&accessory_inv>0&shoot_growth_leaf_area!=0) %>%
   select(prop_maxH,height,maxH,WD_mean,LMA_mean,seed_size,growth_leaf,
-         RGR,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
-         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth,
+         RGR,leaf_area,growth_shoot_area,growth_stem_area,shoot_leaf_count,total_weight,
+         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area,
          prop_propagule, prop_accessory)
@@
 PCA_scores <- as.data.frame(PCA_mod$x)
-PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$lvs_end_total>0&SummaryInd$shoot_leaf_area_growth!=0&SummaryInd$accessory_inv>0)
+PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$shoot_leaf_count>0&SummaryInd$shoot_growth_leaf_area!=0&SummaryInd$accessory_inv>0)
 SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)

### 2015-08-19 results_growth_short.Rmd
Big variable rename

@@
 
-mod <- lm(log(growth_stem_diam)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
-plot((RA+.01)~growth_stem_diam, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(growth_stem_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
+plot((RA+.01)~growth_stem_diameter, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 
-mod <- lm(log(prop_growth_stem_diam)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
-plot((RA+.01)~prop_growth_stem_diam, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
+mod <- lm(log(prop_growth_stem_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
+plot((RA+.01)~prop_growth_stem_diameter, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
 legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "growth_stem_diam"
+yvar <- "growth_stem_diameter"
 xvar <- "RA"
@@
 SummaryIndPCA <- SummaryInd %>%
-  filter(lvs_end_total>0&shoot_leaf_area>0&shoot_leaf_area_growth!=0) %>%
+  filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
   select(prop_maxH,height,maxH,WD_mean,LMA_mean,seed_size,growth_leaf,
-         growth_stem_diam,leaf_area,growth_shoot_area,growth_stem_area,lvs_end_total,total_weight,
-         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_leaf_area_growth,RGR)
+         growth_stem_diameter,leaf_area,growth_shoot_area,growth_stem_area,shoot_leaf_count,total_weight,
+         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area,RGR)
 
@@
 SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
-SummaryIndPCA$lvs_end_total <- log(SummaryIndPCA$lvs_end_total)
+SummaryIndPCA$shoot_leaf_count <- log(SummaryIndPCA$shoot_leaf_count)
 SummaryIndPCA$growth_stem_area <- log(SummaryIndPCA$growth_stem_area)
-SummaryIndPCA$growth_stem_diam <- log(SummaryIndPCA$growth_stem_diam)
+SummaryIndPCA$growth_stem_diameter <- log(SummaryIndPCA$growth_stem_diameter)
 SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
-SummaryIndPCA$shoot_leaf_area_growth <- log(SummaryIndPCA$shoot_leaf_area_growth)
+SummaryIndPCA$shoot_growth_leaf_area <- log(SummaryIndPCA$shoot_growth_leaf_area)
 

### 2015-08-19 R/ReproductionAllocation.R

@@ -41,11 +41,11 @@ RA_Calculations <- function(thisSpecies, Species_Investment, HarvestData, Maps, 
            growth_stem = c(NA, diff(stem_weight_est)),
            growth_leaf =  growth_inv - growth_stem,
            growth_height = c(NA, diff(height)),
-           growth_stem_diam = c(NA, diff(diameter)),
+           growth_stem_diameter = c(NA, diff(diameter)),
            growth_stem_area = c(NA, diff(stem_area))
            ) %>%
     filter(start_end == "end") %>%
-    select(species, site, individual, age, height, diameter, stem_area, leaf_weight, stem_weight, total_weight, growth_inv, growth_stem, growth_leaf, growth_height, growth_stem_diam, growth_stem_area)
+    select(species, site, individual, age, height, diameter, stem_area, leaf_weight, stem_weight, total_weight, growth_inv, growth_stem, growth_leaf, growth_height, growth_stem_diameter, growth_stem_area)
 
     # Use saved data to calculate total reproduction investment per individual plant
     ReproTotal <- Species_Investment$Investment %>%

### 2015-08-19 Accessory_figs.rmd
Attempt at simplifying color and label selection

@@
 mod <- lm (log(total_weight)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
-plot(repro_inv~total_weight,data=subset(SummaryInd,repro_inv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
+plot(repro_inv~total_weight,data=subset(SummaryInd,repro_inv>0), log="xy",xlab="", col=col.spp(species), pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
 words.bottom.right.logxy(mod)
@@
 mod <- lm (log(total_weight)~log(fruit_weight), data=subset(SummaryInd,fruit_weight>0))
-plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Fruit investment (mg)",xlim=c(100,2000000),xlab="")
+plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp(species), pch=16, ylab="Fruit investment (mg)",xlim=c(100,2000000),xlab="")
 words.bottom.right.logxy(mod)
@@
 mod <- lm (log(total_weight)~log(propagule_inv), data=subset(SummaryInd,propagule_inv>0))
-plot(propagule_inv~total_weight,data=subset(SummaryInd,propagule_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(propagule_inv~total_weight,data=subset(SummaryInd,propagule_inv>0), log="xy",col=col.spp(species), pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 mod <- lm (log(total_weight)~log(prepollen_all_inv), data=subset(SummaryInd,prepollen_all_inv>0))
-plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="Prepollen investment (mg)", xlim=c(100,2000000))
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp(species), pch=16, xlab="", ylab="Prepollen investment (mg)", xlim=c(100,2000000))
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)],
+plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp(species),
      xlim=c(1,700000),ylim=c(1,700000),xlab="Total reproductive investment (mg)",ylab="Investment in accessory tissues (mg)")
@@
 
-plot(prepollen_all_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)],
+plot(prepollen_all_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp(species),
      xlim=c(1,700000),ylim=c(1,700000),ylab="Investment in pre-pollination tissues (mg)",xlab="Investment in all accessory tissues (mg)")
@@
 text(10,3,"50%",srt=45)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 ```
@@
 mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
-plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=.9)
-points((accessory_per_seed_mean)~seed_size,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=.9)
+points((accessory_per_seed_mean)~seed_size,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=.9)
+plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=.9)
 words.bottom.right.logx(mod)
-points(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+points(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 mtext("seed size (mg)",1, outer=TRUE,cex=1.2)
@@
 mod <- lm(log(total_weight_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot(accessory_per_seed~total_weight,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=.9)
-points((accessory_per_seed_mean)~total_weight_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+plot(accessory_per_seed~total_weight,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=.9)
+points((accessory_per_seed_mean)~total_weight_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(total_weight_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory))~total_weight,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=0.9)
-points(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+plot(asin(sqrt(prop_accessory))~total_weight,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
+points(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logx(mod)
@@
 mod <- lm(log(seedset_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot((accessory_per_seed)~seedset,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=0.9)
-points((accessory_per_seed_mean)~seedset_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+plot((accessory_per_seed)~seedset,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=0.9)
+points((accessory_per_seed_mean)~seedset_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 words.top.right.logxy(mod)
@@
 mod <- lm(log(seedset_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=0.9)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
-points(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
+legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+points(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 words.top.right.logx(mod)
@@
 mod <- lm(log(prepollen_all_per_seed_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",cex=0.9)
-points((accessory_per_seed_mean)~prepollen_all_per_seed_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp(species),ylab="accessory costs per successful seed",cex=0.9)
+points((accessory_per_seed_mean)~prepollen_all_per_seed_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
@@
 mod <- lm(asin(sqrt(prop_prepollen_all_mean))~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",cex=0.9)
-points(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp(species),ylab="proportional accessory costs",cex=0.9)
+points(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right(mod)
@@
 mod <- lm(asin(sqrt(seedset))~asin(sqrt(RA)),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(asin(sqrt(RA))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+plot(asin(sqrt(RA))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
 words.bottom.right(mod)
@@
 mod <- lm(asin(sqrt(prop_propagule))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(RA))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+plot(asin(sqrt(RA))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
 words.bottom.right(mod)
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm(asin(sqrt(propagule_per_seed))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(RA))~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="x",pch=16,col=col.spp[as.factor(species)])
+plot(asin(sqrt(RA))~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="x",pch=16,col=col.spp(species))
 words.bottom.right.logx(mod)
@@
 mod <- lm(asin(sqrt(seedset))~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
+plot((repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
 words.bottom.right.logy(mod)
@@
 mod <- lm(asin(sqrt(prop_propagule))~log(repro_inv),data=subset(SummaryInd,prop_propagule>0))
-plot((repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
+plot((repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
 words.bottom.right.logy(mod)
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm(log(propagule_per_seed)~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp[as.factor(species)])
+plot((repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp(species))
 words.bottom.right.logxy(mod)
@@
 mod <- lm((prop_maxH)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(asin(sqrt(seedset))~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+plot(asin(sqrt(seedset))~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
 words.bottom.right(mod)
@@
 mod <- lm(log(height)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(asin(sqrt(seedset))~(height),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="x")
+plot(asin(sqrt(seedset))~(height),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="x")
 words.bottom.right.logx(mod)
@@
 mod <- lm((prop_maxH)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(prop_propagule))~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+plot(asin(sqrt(prop_propagule))~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
 words.bottom.right(mod)
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm((prop_maxH)~log(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((propagule_per_seed)~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), log="y",pch=16,col=col.spp[as.factor(species)])
+plot((propagule_per_seed)~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), log="y",pch=16,col=col.spp(species))
 words.bottom.right.logy(mod)
@@
 mod <- lm(log(RA)~log((propagule_inv)),data=subset(SummaryInd,RA>0&propagule_inv>0))
-plot(propagule_inv~RA,data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
+plot(propagule_inv~RA,data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to propagules (mg)")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,RA>0&prop_propagule>0))
-plot(asin(sqrt(prop_propagule))~RA,data=subset(SummaryInd,RA>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+plot(asin(sqrt(prop_propagule))~RA,data=subset(SummaryInd,RA>0&prop_propagule>0), log="x", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
 words.bottom.left.logx(mod)
@@
 mod <- lm(log(RA)~log((prepollen_aborted_inv)),data=subset(SummaryInd,RA>0&prepollen_aborted_inv>0))
-plot(prepollen_aborted_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
+plot(prepollen_aborted_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination aborted tissues (mg)")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0))
-plot(asin(sqrt(prop_prepollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
+plot(asin(sqrt(prop_prepollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
 words.bottom.right.logx(mod)
@@
 mod <- lm(log(RA)~log((prepollen_success_inv)),data=subset(SummaryInd,RA>0&prepollen_success_inv>0))
-plot(prepollen_success_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
+plot(prepollen_success_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination successful tissues (mg)")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,RA>0&prop_prepollen_success>0))
-plot(asin(sqrt(prop_prepollen_success))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
+plot(asin(sqrt(prop_prepollen_success))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_success>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
 words.bottom.right.logx(mod)
@@
 mod <- lm(log(RA)~log((packaging_dispersal_inv)),data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0))
-plot(packaging_dispersal_inv~RA,data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
+plot(packaging_dispersal_inv~RA,data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to packaging and dispersal (mg)")
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm(log(RA)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0))
-plot(asin(sqrt(prop_packaging_dispersal))~RA,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
+plot(asin(sqrt(prop_packaging_dispersal))~RA,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
 words.bottom.left.logx(mod)
@@
 mod <- lm(log(RA)~log((postpollen_aborted_inv)),data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0))
-plot(postpollen_aborted_inv~RA,data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
+plot(postpollen_aborted_inv~RA,data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to tissues aborted postpollination (mg)")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0))
-plot(asin(sqrt(prop_postpollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
+plot(asin(sqrt(prop_postpollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
 words.bottom.left.logx(mod)

### 2015-08-19 Growth_figs.rmd
Attempt at simplifying color and label selection

@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.mature[as.factor(data[[spp]]$mature)])
+                    main=spp,col=col.mature(data[[spp]]$mature)
 }
@@
 mtext("proportion maximum H", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")
+legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
 ```
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
-                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+                    main=spp,col=col.age(data[[spp]]$age)
 }
@@
 mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
-legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
+legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
 ```
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+                    main=spp,col=col.age(data[[spp]]$age)
   abline(0,1)
@@
 mtext("increase in shoot diameter (mm)", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=0.9,bty="n")
+legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=0.9,bty="n")
 ```
@@
 par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
-plot(LL_death~shoot_leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp[as.factor(species)])
+plot(LL_death~shoot_leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
 mod <- lm(log(shoot_leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
@@
 
-plot(LL_death~leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp[as.factor(species)])
+plot(LL_death~leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
 mod <- lm(log(leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+                    main=spp,col=col.age(data[[spp]]$age)
 }
@@
 mtext("shoot leaf area", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
+legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
 ```
@@
 mtext("leaf area", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
+legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
 
@@
 par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
-plot(growth_stem_diameter~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp[as.factor(species)])
+plot(growth_stem_diameter~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp(species))
 ```
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+                    main=spp,col=col.age(data[[spp]]$age)
 }
@@
 mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
+legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
 ```
@@
 par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
-plot(growth_leaf_area~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp[as.factor(species)])
+plot(growth_leaf_area~prop_maxH,SummaryInd,log="y",pch=16,col=col.spp(species))
 ```
@@
 mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
-legend("bottomright",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")
+legend("bottomright",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
 ```
@@
 
-plot(wood_density~growth_leaf_area,SummaryInd,log="y",pch=16,col=col.age[as.factor(age)])
+plot(wood_density~growth_leaf_area,SummaryInd,log="y",pch=16,col=col.age(age)
 mod <- lm(log(growth_leaf_area)~age*wood_density,SummaryInd)

### 2015-08-19 Panalysis.rmd
Attempt at simplifying color and label selection

--- 2015-08-19 Panalysis.rmd
@@
 mod <- lm(log(repro_inv)~log((propagule_inv)),data=subset(SummaryInd,repro_inv>0&propagule_inv>0))
-plot(propagule_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
+plot(propagule_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&propagule_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to propagules (mg)")
 abline(0,1)
@@
 mod <- lm(log(repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,repro_inv>0&prop_propagule>0))
-plot(asin(sqrt(prop_propagule))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+plot(asin(sqrt(prop_propagule))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_propagule>0), log="x", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
 words.bottom.left.logx(mod)
@@
 mod <- lm(log(repro_inv)~log((prepollen_aborted_inv)),data=subset(SummaryInd,repro_inv>0&prepollen_aborted_inv>0))
-plot(prepollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
+plot(prepollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination aborted tissues (mg)")
 abline(0,1)
@@
 mod <- lm(log(repro_inv)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,repro_inv>0&prop_prepollen_aborted>0))
-plot(asin(sqrt(prop_prepollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
+plot(asin(sqrt(prop_prepollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_aborted>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
 words.bottom.right.logx(mod)
@@
 mod <- lm(log(repro_inv)~log((prepollen_success_inv)),data=subset(SummaryInd,repro_inv>0&prepollen_success_inv>0))
-plot(prepollen_success_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
+plot(prepollen_success_inv~repro_inv,data=subset(SummaryInd,repro_inv>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination successful tissues (mg)")
 abline(0,1)
@@
 mod <- lm(log(repro_inv)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,repro_inv>0&prop_prepollen_success>0))
-plot(asin(sqrt(prop_prepollen_success))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
+plot(asin(sqrt(prop_prepollen_success))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_prepollen_success>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
 words.bottom.right.logx(mod)
@@
 mod <- lm(log(repro_inv)~log((packaging_dispersal_inv)),data=subset(SummaryInd,repro_inv>0&packaging_dispersal_inv>0))
-plot(packaging_dispersal_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
+plot(packaging_dispersal_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to packaging and dispersal (mg)")
 abline(0,1)
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm(log(repro_inv)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,repro_inv>0&prop_packaging_dispersal>0))
-plot(asin(sqrt(prop_packaging_dispersal))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
+plot(asin(sqrt(prop_packaging_dispersal))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
 words.bottom.left.logx(mod)
@@
 mod <- lm(log(repro_inv)~log((postpollen_aborted_inv)),data=subset(SummaryInd,repro_inv>0&postpollen_aborted_inv>0))
-plot(postpollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
+plot(postpollen_aborted_inv~repro_inv,data=subset(SummaryInd,repro_inv>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to tissues aborted postpollination (mg)")
 abline(0,1)
@@
 mod <- lm(log(repro_inv)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,repro_inv>0&prop_postpollen_aborted>0))
-plot(asin(sqrt(prop_postpollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
+plot(asin(sqrt(prop_postpollen_aborted))~repro_inv,data=subset(SummaryInd,repro_inv>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
 words.bottom.left.logx(mod)
@@
 par(mfrow=c(1,1), cex=1, omi=c(.8,.8,.1,.1), mai=c(1.1,1,.4,0.2)) 
-plot(asin(sqrt(prop_growth_stem_diam))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0),pch=16,col=col.spp[as.factor(species)])
-mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_growth_stem_diam)),data=subset(SummaryInd,RA>0))
+plot(asin(sqrt(prop_growth_stem_diameter))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0),pch=16,col=col.spp(species))
+mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_growth_stem_diameter)),data=subset(SummaryInd,RA>0))
 words.bottom.left(mod)

### 2015-08-19 RA_figs.rmd
Attempt at simplifying color and label selection

@@
 mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
-plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
 words.top.left.logxy(mod)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 abline(0,1)
@@
 
-plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.age[as.factor(age)],pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
-legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=.8,bty="n")
 abline(0,1)
@@
 mtext("proportion maximum H", 1, outer=TRUE,cex=1.2)
-legend("bottomright",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
+legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
 ```
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+                    main=spp,col=col.age(data[[spp]]$age)
 }
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
-                    main=spp,col=col.age[as.factor(data[[spp]]$age)])
+                    main=spp,col=col.age(data[[spp]]$age)
 }
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
-                    main=spp,col=col.mature[as.factor(data[[spp]]$mature)])
+                    main=spp,col=col.mature(data[[spp]]$mature)
 }
@@
 mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")
+legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
 ```
@@
 mtext("Plant height (mm)", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=names(labels.mature),col=col.mature,pch=16, cex=1.1,bty="n")
+legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
 ```
@@
 par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
-plot(asin(sqrt(RA))~growth_stem_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp[as.factor(species)], pch=16)
+plot(asin(sqrt(RA))~growth_stem_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp(species), pch=16)
 mod <- lm(log(growth_stem_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
 words.top.right.logx(mod)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=0.8,bty="n")
+legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=0.8,bty="n")
 
-plot(asin(sqrt(RA))~growth_shoot_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp[as.factor(species)], pch=16)
+plot(asin(sqrt(RA))~growth_shoot_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp(species), pch=16)
 mod <- lm(log(growth_shoot_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
@@
 mtext("RA", 2, outer=TRUE,cex=1.2)  
-legend("bottomleft",legend=names(labels.age),col=col.age,pch=16, cex=1.1,bty="n")
+legend("bottomleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
 ```
@@
 plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
-                        main=spp,col=col.age[as.factor(data[[spp]]$age)])
+                        main=spp,col=col.age(data[[spp]]$age)
 }
@@
 
-plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],xlim=c(-.1,.1))
+plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species),xlim=c(-.1,.1))
 arrows(0, 0, (.8*PCA_loadings$PC2_scale), (.8*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
 text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
@@
 
-plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
+plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.age(age)
 arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
 text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.age(),col=col.age,pch=16, cex=.8,bty="n")
 
@@
 
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species))
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
+plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age(age)
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.15))
+plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species),ylim=c(-.15,.15))
 arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-plot(PC3_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)],ylim=c(-.15,.15))
+plot(PC3_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age(age),ylim=c(-.15,.15))
 arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.15))
+plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species),ylim=c(-.15,.15))
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
 text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
@@
 
-plot(PC4_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)],ylim=c(-.15,.15))
+plot(PC4_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age(age),ylim=c(-.15,.15))
 arrows(0, 0, (.8*PCA_loadings$PC1_scale), (.8*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)

### 2015-08-19 errors_to_fix.rmd
Attempt at simplifying color and label selection

@@
 
-plot(dia~stem_weight,data=subset(check), pch=16,log="xy",col=col.lots[as.factor(segment)])
+plot(dia~stem_weight,data=subset(check), pch=16,log="xy",col=col.lots(segment)
 text(dia~stem_weight,data=subset(check,segment==1),labels=individual,cex=.5,pos=3,offset=-.7)
 
-plot(dia~leaf_weight,data=subset(check), pch=16,log="xy",col=col.lots[as.factor(segment)])
+plot(dia~leaf_weight,data=subset(check), pch=16,log="xy",col=col.lots(segment)
 text(dia~leaf_weight,data=subset(check,segment==1),labels=individual,cex=.5,pos=3,offset=-.7)
@@
 ```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
-plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
+plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp(species))
 abline(0,1)

### 2015-08-19 results_RAschedules_shorter.Rmd
Big variable rename
Attempt at simplifying color and label selection

@@
 mod <- lm(log(total_weight)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
-plot(repro_inv~total_weight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(repro_inv~total_weight, SummaryInd, log="xy",col=col.spp(species),pch=16)
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(height)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
-plot(repro_inv~height, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(repro_inv~height, SummaryInd, log="xy",col=col.spp(species),pch=16)
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 mod <- lm((prop_maxH)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
-plot((repro_inv)~(prop_maxH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot((repro_inv)~(prop_maxH), SummaryInd, log="y",col=col.spp(species),pch=16,xlim=c(4e-03,1))
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 ```
@@
 mod <- lm(log(total_weight)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
-plot(asin(sqrt(RA))~total_weight, SummaryInd, log="x",col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(asin(sqrt(RA))~total_weight, SummaryInd, log="x",col=col.spp(species),pch=16)
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.top.right.logx(mod)
@@
 mod <- lm(log(height)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
-plot(asin(sqrt(RA))~height, SummaryInd, log="x",col=col.spp[as.factor(species)],pch=16)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(asin(sqrt(RA))~height, SummaryInd, log="x",col=col.spp(species),pch=16)
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.top.right.logx(mod)
@@
 mod <- lm((prop_maxH)~asin(sqrt(RA)), data=subset(SummaryInd,repro_inv>0))
-plot((asin(sqrt(RA)))~(prop_maxH), SummaryInd,col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot((asin(sqrt(RA)))~(prop_maxH), SummaryInd,col=col.spp(species),pch=16,xlim=c(4e-03,1))
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right(mod)
@@
 mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
-plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp(species),pch=16)
+legend("bottomright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(RGR~asin(sqrt(RA))*species,data=subset(SummaryInd,RA>0))
-plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp(species),pch=16)
+legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.top.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
-plot(RA_mean~WD_mean,data=subset(SummarySpp,RA_mean>0), col=col.spp[as.factor(species)],pch=16,log="y",ylab="")
+plot(RA_mean~WD_mean,data=subset(SummarySpp,RA_mean>0), col=col.spp(species),pch=16,log="y",ylab="")
 mod <- lm(WD_mean~asin(sqrt(RA_mean)),SummarySpp)
 words.bottom.left.logy(mod)
-plot(RA_mean~seed_size, SummarySpp, col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+plot(RA_mean~seed_size, SummarySpp, col=col.spp(species),pch=16,log="xy",ylab="")
 mod <- lm(log(seed_size)~asin(sqrt(RA_mean)), SummarySpp)
 words.bottom.left.logxy(mod)
-legend(.05,.28,col=col.spp, legend=names(labels.spp), pch=16, cex=.8,bty="n")
-plot(RA_mean~LMA_mean, SummarySpp, col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+legend(.05,.28,col=col.spp, legend=labels.spp(), pch=16, cex=.8,bty="n")
+plot(RA_mean~LMA_mean, SummarySpp, col=col.spp(species),pch=16,log="xy",ylab="")
 mod <- lm(log(LMA_mean)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
 words.top.right.logxy(mod)
-plot(RA_mean~maxH, SummarySpp, col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+plot(RA_mean~maxH, SummarySpp, col=col.spp(species),pch=16,log="xy",ylab="")
 mod <- lm(log(maxH)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
@@
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
-plot(maxH~WD_mean,data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="y",ylab="")
+plot(maxH~WD_mean,data=subset(SummarySpp), col=col.spp(species),pch=16,log="y",ylab="")
 mod <- lm(mature_RA_mean~asin(sqrt(mature_RA_mean)),data=subset(SummarySpp,species!="BAER"))
 words.bottom.left.logy(mod)
-plot(mature_RA_mean~seed_size, data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+plot(mature_RA_mean~seed_size, data=subset(SummarySpp), col=col.spp(species),pch=16,log="xy",ylab="")
 mod <- lm(log(seed_size)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
 words.bottom.left.logxy(mod)
-legend(.05,.28,col=col.spp, legend=names(labels.spp), pch=16, cex=.8,bty="n")
-plot(mature_RA_mean~LMA_mean, data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+legend(.05,.28,col=col.spp, legend=labels.spp(), pch=16, cex=.8,bty="n")
+plot(mature_RA_mean~LMA_mean, data=subset(SummarySpp), col=col.spp(species),pch=16,log="xy",ylab="")
 mod <- lm(log(LMA_mean)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
 words.top.right.logxy(mod)
-plot(mature_RA_mean~maxH, data=subset(SummarySpp), col=col.spp[as.factor(species)],pch=16,log="xy",ylab="")
+plot(mature_RA_mean~maxH, data=subset(SummarySpp), col=col.spp(species),pch=16,log="xy",ylab="")
 mod <- lm(log(maxH)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
@@
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-mod <- lm(log(growth_stem_diam) ~ age*WD_mean*LMA_mean*maxH*RA, SummaryInd)
+mod <- lm(log(growth_stem_diameter) ~ age*WD_mean*LMA_mean*maxH*RA, SummaryInd)
 anova(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1,1,.6,0.2))
-plot(RA~WD_mean,data=subset(SummaryInd,RA>0), col=col.spp[as.factor(species)],pch=16,log="y",ylim=c(.0008,1))
-points((RA+.001)~WD_mean,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=spp_zero_RA$RAcex)
+plot(RA~WD_mean,data=subset(SummaryInd,RA>0), col=col.spp(species),pch=16,log="y",ylim=c(.0008,1))
+points((RA+.001)~WD_mean,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=spp_zero_RA$RAcex)
 mod <- lm(WD_mean~asin(sqrt(RA)),SummaryInd)
 words.bottom.left.logy(mod)
-plot(RA~seed_size, SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy",ylim=c(.0008,1))
-points((RA+.001)~seed_size,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=spp_zero_RA$RAcex)
+plot(RA~seed_size, SummaryInd, col=col.spp(species),pch=16,log="xy",ylim=c(.0008,1))
+points((RA+.001)~seed_size,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=spp_zero_RA$RAcex)
 mod <- lm(log(seed_size)~asin(sqrt(RA)), SummaryInd)
 words.bottom.left.logxy(mod)
-plot(RA~LMA_mean, SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy",ylim=c(.0008,1))
-points((RA+.001)~LMA_mean,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=sppage_zero_RA$RAcex)
+plot(RA~LMA_mean, SummaryInd, col=col.spp(species),pch=16,log="xy",ylim=c(.0008,1))
+points((RA+.001)~LMA_mean,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=sppage_zero_RA$RAcex)
 mod <- lm(log(LMA_mean)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
 words.top.right.logxy(mod)
-plot(RA~maxH, SummaryInd, col=col.spp[as.factor(species)],pch=16,log="xy",ylim=c(.0008,1))
-points((RA+.001)~maxH,data=subset(SummaryInd,RA==0),col=col.spp[as.factor(species)],pch=16, cex=spp_zero_RA$RAcex)
+plot(RA~maxH, SummaryInd, col=col.spp(species),pch=16,log="xy",ylim=c(.0008,1))
+points((RA+.001)~maxH,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=spp_zero_RA$RAcex)
 mod <- lm(log(maxH)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
@@
 mod <- lm(log(prop_maxH)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_propagule))~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+plot(asin(sqrt(prop_propagule))~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prop_propagule>0), log="x", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
 words.bottom.left.logx(mod)

### 2015-08-19 results_accessory_shorter.Rmd
Attempt at simplifying color and label selection

--- 2015-05-26 results_accessory_shorter.Rmd
@@
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
-mod <- lm (log(total_weight)~log(ReproInv), data=subset(SummaryInd,ReproInv>0))
-plot(ReproInv~total_weight,data=subset(SummaryInd,ReproInv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
+mod <- lm (log(total_weight)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
+plot(repro_inv~total_weight,data=subset(SummaryInd,repro_inv>0), log="xy",xlab="", col=col.spp(species), pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
 words.bottom.right.logxy(mod)
@@
 mod <- lm (log(total_weight)~log(fruit_weight), data=subset(SummaryInd,fruit_weight>0))
-plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="Fruit weight (mg)",xlim=c(100,2000000),xlab="")
+plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp(species), pch=16, ylab="Fruit weight (mg)",xlim=c(100,2000000),xlab="")
 words.bottom.right.logxy(mod)
@@
 mod <- lm (log(total_weight)~log(seedset), data=subset(SummaryInd,seedset>0))
-plot(seedset~total_weight,data=subset(SummaryInd,prop_propagule>0), log="xy",col=col.spp[as.factor(species)], pch=16, ylab="seedset",xlim=c(100,2000000),xlab="")
+plot(seedset~total_weight,data=subset(SummaryInd,prop_propagule>0), log="xy",col=col.spp(species), pch=16, ylab="seedset",xlim=c(100,2000000),xlab="")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="seed size (mg)",cex=1.3)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, log="x", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logx(mod)
@@
 mod <- lm(log(total_weight_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
+plot(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, log="x", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
 words.bottom.right.logx(mod)
@@
 mod <- lm(log(seedset_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, log="x", pch=16,col=col.spp[as.factor(species)],ylab="",cex=1.3)
+plot(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, log="x", pch=16,col=col.spp(species),ylab="",cex=1.3)
 words.top.right.logx(mod)
@@
 mod <- lm(asin(sqrt(prop_prepollen_all_mean))~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, log="", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
+plot(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, log="", pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
 words.top.right(mod)
@@
 mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
-plot(accessory_per_seed_mean~seed_size,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="seed size (mg)",cex=1.3)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(accessory_per_seed_mean~seed_size,SummarySpp, log="xy", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(total_weight_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot(accessory_per_seed_mean~total_weight_mean,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="Total weight (mg)",cex=1.3)
+plot(accessory_per_seed_mean~total_weight_mean,SummarySpp, log="xy", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(seedset_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot((accessory_per_seed_mean)~seedset_mean,SummarySpp, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="",cex=1.3)
+plot((accessory_per_seed_mean)~seedset_mean,SummarySpp, log="xy", pch=16,col=col.spp(species),ylab="",cex=1.3)
 words.top.right.logxy(mod)
@@
 mod <- lm(log(prepollen_all_per_seed_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot(log(accessory_per_seed_mean)~log(prepollen_all_per_seed_mean),SummarySpp, log="", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
+plot(log(accessory_per_seed_mean)~log(prepollen_all_per_seed_mean),SummarySpp, log="", pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
 words.top.right(mod)
 mtext("Accessory tissue investment per successful seed (mg)",2, outer=TRUE,cex=1.2)
+```
+
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3)) 
+mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(total_weight)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(accessory_per_seed~total_weight,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
+words.bottom.right.logxy(mod)
+
+mod <- lm(log(seedset)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot((accessory_per_seed)~seedset,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="",cex=1.3)
+words.top.right.logxy(mod)
+
+mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
+plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
+words.bottom.right.logxy(mod)
+mtext("Accessory tissue investment per successful seed (mg)",2, outer=TRUE,cex=1.2)
+```
+
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
+par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3)) 
+mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
+words.bottom.right.logx(mod)
+
+mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(asin(sqrt(prop_accessory))~total_weight,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
+words.bottom.right.logx(mod)
+
+mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
+plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="",cex=1.3)
+legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+words.top.right.logx(mod)
+
+mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
+plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
+words.bottom.right(mod)
+mtext("Proportion reproductive investment to accessory tissues (asin transformed)",2, outer=TRUE,cex=1.2)
 ```
@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
-plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp[as.factor(species)],xlab="costs to make 1 seed (mg)",cex=1.2)
+plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp(species),xlab="costs to make 1 seed (mg)",cex=1.2)
 mod <- lm(seedcosts~seed_size, SummarySpp)
@@
 
-plot(seed_size~costs_per_seed,data=subset(SummarySpp),log="y",pch=16,col=col.spp[as.factor(species)],ylab="",xlab="proportional accessory costs, scaled by seed weight",cex=1.2)
+plot(seed_size~costs_per_seed,data=subset(SummarySpp),log="y",pch=16,col=col.spp(species),ylab="",xlab="proportional accessory costs, scaled by seed weight",cex=1.2)
 text(seed_size~costs_per_seed,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")
@@
 mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="proportion reproduction to propagules (1-accessory)")
+plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp(species),xlab="",ylab="proportion reproduction to propagules (1-accessory)")
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="proportion reproduction to propagules (1-accessory)",xlab="")
+plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age(age),ylab="proportion reproduction to propagules (1-accessory)",xlab="")
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=.8,bty="n")
 mtext("Seed set",1, outer=TRUE,cex=1.1)
@@
 mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="proportion reproduction to propagules (1-accessory)")
+plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp(species),xlab="",ylab="proportion reproduction to propagules (1-accessory)")
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm(log(seedset)~log(accessory_per_seed),data=subset(SummaryInd,seedset>0&seedset<1&accessory_per_seed>0))
-plot(accessory_per_seed~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="accessory costs per seed produced (mg)")
+plot(accessory_per_seed~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.spp(species),xlab="",ylab="accessory costs per seed produced (mg)")
 words.bottom.left.logxy(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(0.6,0.3,0.1,0.3), mai=c(0.8,1,0.3,0.3))  
-mod <- lm(log(ReproInv)~(prop_prepollen_all),data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1))
-plot((prop_prepollen_all)~ReproInv,data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1), log="x", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Pre-pollination tissues (as proportion repro inv)")
+mod <- lm(log(repro_inv)~(prop_prepollen_all),data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1))
+plot((prop_prepollen_all)~repro_inv,data=subset(SummaryInd,prop_prepollen_all>0&prop_prepollen_all<1), log="x", pch=16,col=col.spp(species),xlab="",ylab="Pre-pollination tissues (as proportion repro inv)")
 words.top.right.logx(mod)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
-mod <- lm(log(ReproInv)~log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
-plot(prop_propagule~ReproInv,data=subset(SummaryInd,prop_propagule>0), log="xy", pch=16,col=col.spp[as.factor(species)],xlab="",ylab="Propagules (as proportion repro inv)")
+mod <- lm(log(repro_inv)~log(prop_propagule),data=subset(SummaryInd,prop_propagule>0))
+plot(prop_propagule~repro_inv,data=subset(SummaryInd,prop_propagule>0), log="xy", pch=16,col=col.spp(species),xlab="",ylab="Propagules (as proportion repro inv)")
 words.top.right.logxy(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(0.3,0.3,0.1,0.3), mai=c(1.1,1,0.3,0.3)) 
-mod <- lm(log(RA)~log((ReproInv)),data=subset(SummaryInd,RA>0))
-plot(RA~(ReproInv),data=subset(SummaryInd,RA>0), pch=16,col=col.spp[as.factor(species)],log="xy")
+mod <- lm(log(RA)~log((repro_inv)),data=subset(SummaryInd,RA>0))
+plot(RA~(repro_inv),data=subset(SummaryInd,RA>0), pch=16,col=col.spp(species),log="xy")
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
-mod <- lm(log(RA)~species*age*log((ReproInv)),data=subset(SummaryInd,RA>0))
+mod <- lm(log(RA)~species*age*log((repro_inv)),data=subset(SummaryInd,RA>0))
 anova(mod)
@@
 mod <- lm(log(RA)~log((age)),data=subset(SummaryInd,RA>0))
-plot(RA~(age),data=subset(SummaryInd,RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="")
+plot(RA~(age),data=subset(SummaryInd,RA>0), pch=16,col=col.spp(species),log="xy",ylab="")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA)~log(repro_all_count),data=subset(SummaryInd,repro_all_count>0))
-plot(repro_all_count~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp[as.factor(species)],pch=16,log="xy",ylab="# of buds produced",xlab="")
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(repro_all_count~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp(species),pch=16,log="xy",ylab="# of buds produced",xlab="")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA)~log(seed_count+.1),data=subset(SummaryInd,repro_all_count>0))
-plot((.1+seed_count)~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp[as.factor(species)],pch=16,log="xy",ylab="# of seeds produced",xlab="")
+plot((.1+seed_count)~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp(species),pch=16,log="xy",ylab="# of seeds produced",xlab="")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA)~log((prepollen_all_inv)),data=subset(SummaryInd,RA>0&prepollen_all_inv>0))
-plot(prepollen_all_inv~(RA),data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination tissues (mg)")
+plot(prepollen_all_inv~(RA),data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination tissues (mg)")
 words.bottom.right.logxy(mod)
 
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 mod <- lm(log(RA)~log((propagule_inv)),data=subset(SummaryInd,RA>0&propagule_inv>0))
-plot(propagule_inv~(RA),data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
+plot(propagule_inv~(RA),data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to propagules (mg)")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(asin(sqrt(RA))~asin(sqrt(prop_prepollen_all)),data=subset(SummaryInd,RA>0&prop_prepollen_all>0))
-plot(asin(sqrt(prop_prepollen_all))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&prop_prepollen_all>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination tissues (as proportion repro inv) (asin)")
+plot(asin(sqrt(prop_prepollen_all))~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&prop_prepollen_all>0), pch=16,col=col.spp(species), ylab="pre-pollination tissues (as proportion repro inv) (asin)")
 words.top.right(mod)
@@
 mod <- lm(log(RA)~log((prop_propagule)),data=subset(SummaryInd,RA>0&prop_propagule>0))
-plot((prop_propagule)~(RA),data=subset(SummaryInd,RA>0&prop_propagule>0), log="xy", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+plot((prop_propagule)~(RA),data=subset(SummaryInd,RA>0&prop_propagule>0), log="xy", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
 words.bottom.left.logxy(mod)
@@
 mod <- lm((prop_maxH)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset<1&seedset>0))
-plot(asin(sqrt(seedset))~prop_maxH,data=subset(SummaryInd,seedset<1&seedset>0), pch=16,col=col.spp[as.factor(species)])
+plot(asin(sqrt(seedset))~prop_maxH,data=subset(SummaryInd,seedset<1&seedset>0), pch=16,col=col.spp(species))
 words.top.right(mod)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 

### 2015-08-19 results_accessory_v3.Rmd
Attempt at simplifying color and label selection

@@
 par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
+plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp(species))
 abline(0,1)
@@
 
-plot(prepollen_all_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
+plot(prepollen_all_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp(species))
 abline(0,1)
@@
 mod <- lm(log(seed_count)~species*accessory_per_seed,data=subset(SummaryInd,seed_count>0))
-plot(seed_count~accessory_per_seed,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="seed count",xlab="accessory costs per successful seed (mg)",cex=.9)
+plot(seed_count~accessory_per_seed,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="seed count",xlab="accessory costs per successful seed (mg)",cex=.9)
 words.bottom.left.logxy(mod)
 
-plot(seed_count~(prop_accessory),SummaryInd, log="y", pch=16,col=col.spp[as.factor(species)],ylab="",xlab="proportion of reproduction to accessory tissues",cex=.9)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(seed_count~(prop_accessory),SummaryInd, log="y", pch=16,col=col.spp(species),ylab="",xlab="proportion of reproduction to accessory tissues",cex=.9)
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 ```
@@
 mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
-plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=.9)
-points((accessory_per_seed_mean)~seed_size,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=.9)
+points((accessory_per_seed_mean)~seed_size,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
@@
 mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=.9)
+plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=.9)
 words.bottom.right.logx(mod)
-points(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+points(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 mtext("seed size (mg)",1, outer=TRUE,cex=1.2)
@@
 mod <- lm(log(prepollen_all_per_seed_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp[as.factor(species)],ylab="accessory costs per successful seed",xlab="",cex=0.9)
-points((accessory_per_seed_mean)~prepollen_all_per_seed_mean,SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=0.9)
+points((accessory_per_seed_mean)~prepollen_all_per_seed_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
@@
 mod <- lm(asin(sqrt(prop_prepollen_all_mean))~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp[as.factor(species)],ylab="proportional accessory costs",xlab="",cex=0.9)
-points(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, pch=16,col=col.spp[as.factor(species)],cex=1.8)
+plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
+points(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
-plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp[as.factor(species)],xlab="costs to make 1 seed (mg)",ylab="seed size (mg)",cex=1.2)
+plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp(species),xlab="costs to make 1 seed (mg)",ylab="seed size (mg)",cex=1.2)
 mod <- lm(seedcosts~seed_size, SummarySpp)
@@
 mod <- lm(log(seedset)~log(prop_propagule),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age[as.factor(age)],ylab="proportion RE to propagules (1-accessory)",xlab="seed set")
+plot(prop_propagule~seedset,data=subset(SummaryInd,seedset>0&seedset<1), log="xy", pch=16,col=col.age(age),ylab="proportion RE to propagules (1-accessory)",xlab="seed set")
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=.8,bty="n")
 ```
@@
 mod <- lm((prop_maxH)~log((repro_inv)),data=subset(SummaryInd,prop_maxH>0&repro_inv>0))
-plot(repro_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="total reproductive investment (mg)")
+plot(repro_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&repro_inv>0), pch=16,col=col.spp(species),log="y", ylab="total reproductive investment (mg)")
 words.bottom.right.logy(mod)
@@
 mod <- lm((prop_maxH)~asin(sqrt(RA)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(RA))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="RA")
+plot(asin(sqrt(RA))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp(species),ylab="RA")
 words.bottom.left(mod)
@@
 mod <- lm((prop_maxH)~log((propagule_inv)),data=subset(SummaryInd,prop_maxH>0&propagule_inv>0))
-plot(propagule_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to propagules (mg)")
+plot(propagule_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&propagule_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to propagules (mg)")
 words.bottom.right.logy(mod)
@@
 mod <- lm((prop_maxH)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_propagule))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+plot(asin(sqrt(prop_propagule))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
 words.bottom.left(mod)
@@
 mod <- lm((prop_maxH)~log((prepollen_aborted_inv)),data=subset(SummaryInd,prop_maxH>0&prepollen_aborted_inv>0))
-plot(prepollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="y",ylab="pre-pollination aborted tissues (mg)")
+plot(prepollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_aborted_inv>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination aborted tissues (mg)")
 words.bottom.right.logy(mod)
@@
 mod <- lm((prop_maxH)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_prepollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
+plot(asin(sqrt(prop_prepollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp(species), ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
 words.bottom.left(mod)
@@
 mod <- lm((prop_maxH)~log((prepollen_success_inv)),data=subset(SummaryInd,prop_maxH>0&prepollen_success_inv>0))
-plot(prepollen_success_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_success_inv>0), pch=16,col=col.spp[as.factor(species)],log="y",ylab="pre-pollination successful tissues (mg)")
+plot(prepollen_success_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&prepollen_success_inv>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination successful tissues (mg)")
 words.bottom.right.logy(mod)
@@
 mod <- lm((prop_maxH)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_prepollen_success))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)], ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
+plot(asin(sqrt(prop_prepollen_success))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp(species), ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
 words.bottom.left(mod)
@@
 mod <- lm((prop_maxH)~log((packaging_dispersal_inv)),data=subset(SummaryInd,prop_maxH>0&packaging_dispersal_inv>0))
-plot(packaging_dispersal_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to packaging and dispersal (mg)")
+plot(packaging_dispersal_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to packaging and dispersal (mg)")
 words.bottom.right.logy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm((prop_maxH)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_packaging_dispersal))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
+plot(asin(sqrt(prop_packaging_dispersal))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
 words.bottom.left(mod)
@@
 mod <- lm((prop_maxH)~log((postpollen_aborted_inv)),data=subset(SummaryInd,prop_maxH>0&postpollen_aborted_inv>0))
-plot(postpollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="energy to tissues aborted postpollination (mg)")
+plot(postpollen_aborted_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to tissues aborted postpollination (mg)")
 words.bottom.right.logy(mod)
@@
 mod <- lm((prop_maxH)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(prop_postpollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
+plot(asin(sqrt(prop_postpollen_aborted))~prop_maxH,data=subset(SummaryInd,prop_maxH>0), pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
 words.bottom.left(mod)

### 2015-08-19 results_accessory_v3_alt_reproInv.Rmd
Attempt at simplifying color and label selection

@@
 par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-plot(accessory_inv~total_repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp[as.factor(species)])
+plot(accessory_inv~total_repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp(species))
 abline(0,1)
@@
 mod <- lm (log(total_weight)~log(total_repro_inv), data=subset(SummaryInd,total_repro_inv>0))
-plot(total_repro_inv~total_weight,data=subset(SummaryInd,total_repro_inv>0), log="xy",xlab="", col=col.spp[as.factor(species)], pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
+plot(total_repro_inv~total_weight,data=subset(SummaryInd,total_repro_inv>0), log="xy",xlab="", col=col.spp(species), pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
 words.bottom.right.logxy(mod)
@@
 mod <- lm (log(total_weight)~log(prepollen_all_inv), data=subset(SummaryInd,prepollen_all_inv>0))
-plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp[as.factor(species)], pch=16, xlab="", ylab="prepollen investment (mg)", xlim=c(100,2000000))
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp(species), pch=16, xlab="", ylab="prepollen investment (mg)", xlim=c(100,2000000))
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(asin(sqrt(seedset))~asin(sqrt(RA2)),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(asin(sqrt(RA2))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+plot(asin(sqrt(RA2))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
 words.bottom.right(mod)
@@
 mod <- lm(asin(sqrt(prop_propagule))~asin(sqrt(RA2)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(RA2))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)])
+plot(asin(sqrt(RA2))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
 words.bottom.right(mod)
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm(asin(sqrt(propagule_per_seed))~asin(sqrt(RA2)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(RA2))~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="x",pch=16,col=col.spp[as.factor(species)])
+plot(asin(sqrt(RA2))~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="x",pch=16,col=col.spp(species))
 words.bottom.right.logx(mod)
@@
 mod <- lm(asin(sqrt(seedset))~log(total_repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((total_repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
+plot((total_repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
 words.bottom.right.logy(mod)
@@
 mod <- lm(asin(sqrt(prop_propagule))~log(total_repro_inv),data=subset(SummaryInd,prop_propagule>0))
-plot((total_repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp[as.factor(species)],log="y")
+plot((total_repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
 words.bottom.right.logy(mod)
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm(log(propagule_per_seed)~log(total_repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((total_repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp[as.factor(species)])
+plot((total_repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp(species))
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA2)~log((propagule_inv)),data=subset(SummaryInd,RA2>0&propagule_inv>0))
-plot(propagule_inv~RA2,data=subset(SummaryInd,RA2>0&propagule_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to propagules (mg)")
+plot(propagule_inv~RA2,data=subset(SummaryInd,RA2>0&propagule_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to propagules (mg)")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA2)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,RA2>0&prop_propagule>0))
-plot(asin(sqrt(prop_propagule))~RA2,data=subset(SummaryInd,RA2>0&prop_propagule>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="propagules (as proportion repro inv)")
+plot(asin(sqrt(prop_propagule))~RA2,data=subset(SummaryInd,RA2>0&prop_propagule>0), log="x", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
 words.bottom.left.logx(mod)
@@
 mod <- lm(log(RA2)~log((prepollen_aborted_inv)),data=subset(SummaryInd,RA2>0&prepollen_aborted_inv>0))
-plot(prepollen_aborted_inv~RA2,data=subset(SummaryInd,RA2<1&RA2>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination aborted tissues (mg)")
+plot(prepollen_aborted_inv~RA2,data=subset(SummaryInd,RA2<1&RA2>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination aborted tissues (mg)")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA2)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,RA2>0&prop_prepollen_aborted>0))
-plot(asin(sqrt(prop_prepollen_aborted))~RA2,data=subset(SummaryInd,RA2>0&prop_prepollen_aborted>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
+plot(asin(sqrt(prop_prepollen_aborted))~RA2,data=subset(SummaryInd,RA2>0&prop_prepollen_aborted>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
 words.bottom.right.logx(mod)
@@
 mod <- lm(log(RA2)~log((prepollen_success_inv)),data=subset(SummaryInd,RA2>0&prepollen_success_inv>0))
-plot(prepollen_success_inv~RA2,data=subset(SummaryInd,RA2<1&RA2>0), pch=16,col=col.spp[as.factor(species)],log="xy",ylab="pre-pollination successful tissues (mg)")
+plot(prepollen_success_inv~RA2,data=subset(SummaryInd,RA2<1&RA2>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination successful tissues (mg)")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA2)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,RA2>0&prop_prepollen_success>0))
-plot(asin(sqrt(prop_prepollen_success))~RA2,data=subset(SummaryInd,RA2>0&prop_prepollen_success>0), pch=16,col=col.spp[as.factor(species)], log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
+plot(asin(sqrt(prop_prepollen_success))~RA2,data=subset(SummaryInd,RA2>0&prop_prepollen_success>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
 words.bottom.right.logx(mod)
@@
 mod <- lm(log(RA2)~log((packaging_dispersal_inv)),data=subset(SummaryInd,RA2>0&packaging_dispersal_inv>0))
-plot(packaging_dispersal_inv~RA2,data=subset(SummaryInd,RA2>0&packaging_dispersal_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to packaging and dispersal (mg)")
+plot(packaging_dispersal_inv~RA2,data=subset(SummaryInd,RA2>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to packaging and dispersal (mg)")
 words.bottom.right.logxy(mod)
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
 mod <- lm(log(RA2)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,RA2>0&prop_packaging_dispersal>0))
-plot(asin(sqrt(prop_packaging_dispersal))~RA2,data=subset(SummaryInd,RA2>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="packaging and dispersal (as proportion repro inv)")
+plot(asin(sqrt(prop_packaging_dispersal))~RA2,data=subset(SummaryInd,RA2>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
 words.bottom.left.logx(mod)
@@
 mod <- lm(log(RA2)~log((postpollen_aborted_inv)),data=subset(SummaryInd,RA2>0&postpollen_aborted_inv>0))
-plot(postpollen_aborted_inv~RA2,data=subset(SummaryInd,RA2>0&postpollen_aborted_inv>0), pch=16,col=col.spp[as.factor(species)],log="xy", ylab="energy to tissues aborted postpollination (mg)")
+plot(postpollen_aborted_inv~RA2,data=subset(SummaryInd,RA2>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to tissues aborted postpollination (mg)")
 words.bottom.right.logxy(mod)
@@
 mod <- lm(log(RA2)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,RA2>0&prop_postpollen_aborted>0))
-plot(asin(sqrt(prop_postpollen_aborted))~RA2,data=subset(SummaryInd,RA2>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp[as.factor(species)],ylab="tissues aborted postpollination (as proportion repro inv)")
+plot(asin(sqrt(prop_postpollen_aborted))~RA2,data=subset(SummaryInd,RA2>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
 words.bottom.left.logx(mod)
@@
 mod <- lm((prop_maxH)~log((total_repro_inv)),data=subset(SummaryInd,prop_maxH>0&total_repro_inv>0))
-plot(total_repro_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&total_repro_inv>0), pch=16,col=col.spp[as.factor(species)],log="y", ylab="total reproductive investment (mg)")
+plot(total_repro_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&total_repro_inv>0), pch=16,col=col.spp(species),log="y", ylab="total reproductive investment (mg)")
 words.bottom.right.logy(mod)
@@
 mod <- lm((prop_maxH)~asin(sqrt(RA2)),data=subset(SummaryInd,prop_maxH>0))
-plot(asin(sqrt(RA2))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp[as.factor(species)],ylab="RA2")
+plot(asin(sqrt(RA2))~prop_maxH,data=subset(SummaryInd,prop_maxH>0),pch=16,col=col.spp(species),ylab="RA2")
 words.bottom.left(mod)

### 2015-08-19 results_growth.Rmd
Attempt at simplifying color and label selection

@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.6,0.2))
-plot((total_weight~prop_maxH), SummaryInd, col=col.spp[as.factor(species)],pch=16,log="y")
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot((total_weight~prop_maxH), SummaryInd, col=col.spp(species),pch=16,log="y")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 ```
@@
 par(mfrow=c(1,2), cex=1, omi=c(.8,0.3,.5,0.2), mai=c(.7,1,.1,0.2))
-plot((growth_inv~prop_maxH), SummaryInd, log="y", col=col.spp[as.factor(species)],pch=16,xlab="")
-legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot((growth_inv~prop_maxH), SummaryInd, log="y", col=col.spp(species),pch=16,xlab="")
+legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(growth_inv~prop_maxH, SummaryInd, log="y", col=col.age[as.factor(age)],pch=16,ylab="",xlab="")
-legend("topleft",legend=names(labels.age),col=col.age,pch=16, cex=.8,bty="n")
+plot(growth_inv~prop_maxH, SummaryInd, log="y", col=col.age(age),pch=16,ylab="",xlab="")
+legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=.8,bty="n")
 mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(RGR~prop_maxH,SummaryInd,col=col.spp[as.factor(species)],pch=16)
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(RGR~prop_maxH,SummaryInd,col=col.spp(species),pch=16)
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 ```
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(growth_shoot_area~growth_stem_area,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
-legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=1,bty="n")
+plot(growth_shoot_area~growth_stem_area,data=subset(SummaryInd), log="xy",col=col.spp(species), pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
+legend("bottomright",col=col.spp, legend=labels.spp(), pch=16, cex=1,bty="n")
 
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(shoot_leaf_count~age,data=subset(SummaryInd,age>2),log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
-legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=1,bty="n")
+plot(shoot_leaf_count~age,data=subset(SummaryInd,age>2),log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp(species))
+legend("bottomright",col=col.spp, legend=labels.spp(), pch=16, cex=1,bty="n")
 
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp[as.factor(species)], pch=16, cex=0.8)
-legend("bottomright",col=col.spp, legend=names(labels.spp), pch=16, cex=.8, bty="n")
+plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp(species), pch=16, cex=0.8)
+legend("bottomright",col=col.spp, legend=labels.spp(), pch=16, cex=.8, bty="n")
 ```
@@
 mod <- lm(prop_maxH~growth_shoot_length,data=subset(SummaryInd,age>2))
-plot(growth_shoot_length~prop_maxH,data=subset(SummaryInd,age>2),log="y", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
-legend(12,200,col=col.spp, legend=names(labels.spp), pch=16, cex=.8,bty="n")
+plot(growth_shoot_length~prop_maxH,data=subset(SummaryInd,age>2),log="y", ylab="shoot extension (mm)",col=col.spp(species),pch=16)
+legend(12,200,col=col.spp, legend=labels.spp(), pch=16, cex=.8,bty="n")
 words.bottom.right.logy(mod)
@@
 mod <- lm(age~species*growth_shoot_length,data=subset(SummaryInd,age>2))
-plot(growth_shoot_length~age,data=subset(SummaryInd,age>2),log="xy", ylab="shoot extension (mm)",col=col.spp[as.factor(species)],pch=16)
+plot(growth_shoot_length~age,data=subset(SummaryInd,age>2),log="xy", ylab="shoot extension (mm)",col=col.spp(species),pch=16)
 words.bottom.right.logxy(mod)
@@
 mod <- lm (growth_shoot_area ~ growth_stem_area*species*age,data=subset(SummaryInd, age>1.4))
-plot((growth_shoot_area/10000) ~ growth_stem_area,data=subset(SummaryInd, age>1.4), log="xy",col=col.age2[as.factor(age)], pch=16)
+plot((growth_shoot_area/10000) ~ growth_stem_area,data=subset(SummaryInd, age>1.4), log="xy",col=col.age(age), pch=16)
 abline(0,1)
 words.bottom.right.logxy(mod)
-legend("topleft",col=col.age, labels.age, pch=16, cex=1, bty="n")
+legend("topleft",col=col.age, labels.age(), pch=16, cex=1, bty="n")
 anova(mod)
@@
 
-legend("topleft",col=col.age2, labels.age2, pch=16, cex=1, bty="n")
+legend("topleft",col=col.age, labels.age(), pch=16, cex=1, bty="n")
 mtext("growth in basal stem area", 1, outer=TRUE,cex=1.2)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
-plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.age[as.factor(age)], pch=16)
+plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.age(age), pch=16)
 mod <- lm(log(total_weight)~log(leaf_area), SummaryInd)
@@
 
-plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.age[as.factor(age)], pch=16)
+plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.age(age), pch=16)
 
-plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.spp[as.factor(species)], pch=16)
+plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.spp(species), pch=16)
 words.bottom.right.logxy(mod)
 
-plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.spp[as.factor(species)], pch=16)
+plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.spp(species), pch=16)
 ```
@@
 par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
-plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.age[as.factor(age)], pch=16)
+plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.age(age), pch=16)
 mod <- lm(log(total_weight)~log(leaf_weight), SummaryInd)
@@
 
-plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.age[as.factor(age)], pch=16)
+plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.age(age), pch=16)
 
-plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.spp[as.factor(species)], pch=16)
+plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.spp(species), pch=16)
 words.bottom.right.logxy(mod)
 
-plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.spp[as.factor(species)], pch=16)
+plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.spp(species), pch=16)
 ```
@@
 par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
-plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.age[as.factor(age)], pch=16,ylim=c(-1,4))
+plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.age(age), pch=16,ylim=c(-1,4))
 abline(0,0)
 abline(0,1)
-legend("topleft",col=col.age, labels.age, pch=16, cex=1, bty="n")
+legend("topleft",col=col.age, labels.age(), pch=16, cex=1, bty="n")
 
-plot((leaf_area)~(stem_weight), SummaryInd,col=col.age[as.factor(age)], pch=16,log="xy")
+plot((leaf_area)~(stem_weight), SummaryInd,col=col.age(age), pch=16,log="xy")
 abline(0,1)
@@
 
-plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.spp[as.factor(species)], pch=16,ylim=c(-1,4),xlab="")
+plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.spp(species), pch=16,ylim=c(-1,4),xlab="")
 abline(0,0)
 abline(0,1)
-legend("topleft",col=col.spp, legend=names(labels.spp), pch=16, cex=.9, bty="n")
+legend("topleft",col=col.spp, legend=labels.spp(), pch=16, cex=.9, bty="n")
 
-plot((leaf_area)~(stem_weight), SummaryInd,col=col.spp[as.factor(species)], pch=16,log="xy",xlab="")
+plot((leaf_area)~(stem_weight), SummaryInd,col=col.spp(species), pch=16,log="xy",xlab="")
 abline(0,1)
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(growth_inv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
-legend("topleft",col=col.age, labels.age, pch=16, cex=1,bty="n")
+plot(growth_inv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age(age),pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
+legend("topleft",col=col.age, labels.age(), pch=16, cex=1,bty="n")
 text(growth_inv_mean ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
 text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
@@
 
-plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
 text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
@@
 words.bottom.right.logxy(mod)
-legend("topleft",col=col.age,labels.age,pch=16, bty="n")
+legend("topleft",col=col.age,labels.age(),pch=16, bty="n")
 
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
 text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
@@
 words.bottom.left.logxy(mod)
-legend("topright",col=col.age,labels.age,pch=16, bty="n")
+legend("topright",col=col.age,labels.age(),pch=16, bty="n")
 
-plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
 text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
@@
 par(mfrow=c(1,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
 text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
@@
 words.bottom.right.logxy(mod)
-legend("topright",col=col.age,labels.age,pch=16, bty="n")
+legend("topright",col=col.age,labels.age(),pch=16, bty="n")
 
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
+plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
 text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
@@
 
-plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
+plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
 text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
 text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
@@
 words.bottom.right.logxy(mod)
-legend("topright",col=col.age,labels.age,pch=16, bty="n")
+legend("topright",col=col.age,labels.age(),pch=16, bty="n")
 
-plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
 text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
@@
 
-plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3&species!="HATE"),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3&species!="HATE"),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
 text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3&species!="HATE"), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2))
-plot(growth_inv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+plot(growth_inv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
 text(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
@@
 
-plot(growth_inv_mean ~ LL_death_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age3[as.factor(age)],pch=16,cex=1,xlab="",ylab="",main="Adults")
+plot(growth_inv_mean ~ LL_death_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
 text(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
 mod <- lm(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3))
-legend("topright",col=col.age,labels.age,pch=16, bty="n")
+legend("topright",col=col.age,labels.age(),pch=16, bty="n")
 words.bottom.right.logxy(mod)
@@
 
-plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],xlim=c(-.1,.1))
+plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species),xlim=c(-.1,.1))
 arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
 text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
@@
 
-plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species))
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
+plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age(age)
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
 text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
+plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.age(age)
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)],ylim=c(-.15,.12))
+plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.age(age),ylim=c(-.15,.12))
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-plot(PC3_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.age[as.factor(age)])
+plot(PC3_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.age(age)
 arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species))
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
 text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 
-plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species))
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)],ylim=c(-.15,.12))
+plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species),ylim=c(-.15,.12))
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-plot(PC3_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.spp[as.factor(species)])
+plot(PC3_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species))
 arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-plot(WD_mean~maxH,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
+plot(WD_mean~maxH,SummarySpp, log="x",col=col.spp(species),pch=16)
 mod <- lm(log(maxH)~WD_mean,SummaryInd)
@@
 
-plot(WD_mean~maxH,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"), log="x",col=col.spp[as.factor(species)],pch=16)
+plot(WD_mean~maxH,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"), log="x",col=col.spp(species),pch=16)
 mod <- lm(log(maxH)~WD_mean,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"))
@@
 
-plot(seedset_mean~total_weight_mean,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
+plot(seedset_mean~total_weight_mean,SummarySpp, log="x",col=col.spp(species),pch=16)
 mod <- lm(log(total_weight_mean) ~ (seedset_mean),SummarySpp)
@@
 
-plot(seedset_mean~maxH,SummarySpp, log="x",col=col.spp[as.factor(species)],pch=16)
+plot(seedset_mean~maxH,SummarySpp, log="x",col=col.spp(species),pch=16)
 mod <- lm(log(maxH) ~ (seedset_mean),SummarySpp)

### 2015-08-19 results_growth_short.Rmd
Attempt at simplifying color and label selection

@@
 mod <- lm(RGR~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
-plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp(species),pch=16)
+legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.top.right.logxy(mod)
@@
 mod <- lm(log(growth_stem_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
-plot((RA+.01)~growth_stem_diameter, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot((RA+.01)~growth_stem_diameter, SummaryInd, log="xy", col=col.spp(species),pch=16)
+legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.top.right.logxy(mod)
@@
 mod <- lm(log(prop_growth_stem_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
-plot((RA+.01)~prop_growth_stem_diameter, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
-legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot((RA+.01)~prop_growth_stem_diameter, SummaryInd, log="xy", col=col.spp(species),pch=16)
+legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 words.top.right.logxy(mod)
@@
 mod <- lm(log(prop_growth_height)~asin(sqrt(RA)),data=subset(SummaryInd,growth_height>0&species!="PEPU"&species!="PELA"&species!="COER"))
-plot((RA+.01)~(prop_growth_height), data=subset(SummaryInd,species!="PEPU"&species!="PELA"), log="xy", col=col.spp[as.factor(species)],pch=16)
+plot((RA+.01)~(prop_growth_height), data=subset(SummaryInd,species!="PEPU"&species!="PELA"), log="xy", col=col.spp(species),pch=16)
 ```
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(RA~prop_maxH,SummaryInd,col=col.spp[as.factor(species)],pch=16)
-legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
+plot(RA~prop_maxH,SummaryInd,col=col.spp(species),pch=16)
+legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
 ```

### 2015-08-19 Mark_20150806_ideas.R

@@ -212,15 +212,15 @@ mtext("Shoot diameter growth", 1, outer=TRUE,cex=1.2)
 mtext("RA", 2, outer=TRUE,cex=1.2)
 
 par(mfrow=c(2,2), cex=1, omi=c(.4,.,.1,.1), mai=c(1,1,.4,0.2)) 
-plot(RA~growth_shoot_diameter,data=subset(SummaryInd,RA>0),log="xy", col=col.spp[as.factor(species)],pch=16)
+plot(RA~growth_shoot_diameter,data=subset(SummaryInd,RA>0),log="xy", col=col.spp(species),pch=16)
 mod <- lm(log(growth_shoot_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
 words.bottom.left.logxy(mod)
 
-plot(RA~growth_shoot_length,data=subset(SummaryInd,RA>0),log="xy", col=col.spp[as.factor(species)],pch=16)
+plot(RA~growth_shoot_length,data=subset(SummaryInd,RA>0),log="xy", col=col.spp(species),pch=16)
 mod <- lm(log(growth_shoot_length)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
 words.bottom.left.logxy(mod)
 
-plot(RA~shoot_growth_leaf_area,data=subset(SummaryInd,RA>0),log="xy", col=col.spp[as.factor(species)],pch=16)
+plot(RA~shoot_growth_leaf_area,data=subset(SummaryInd,RA>0),log="xy", col=col.spp(species),pch=16)
 mod <- lm(log(shoot_growth_leaf_area)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0&shoot_growth_leaf_area>0))
 words.bottom.left.logxy(mod)
 

### 2015-08-19 diameter_weight_checking.R

@@ -13,7 +13,7 @@ check <- PHPH_HarvestData
 check <- PILI_HarvestData
 check <- PUTU_HarvestData
 
-plot(dia~stem_weight,data=subset(check,segment==1), pch=16,log="xy",col=col.lots[as.factor(individual)])
+plot(dia~stem_weight,data=subset(check,segment==1), pch=16,log="xy",col=col.lots(individual))
 text(dia~stem_weight,data=subset(check,segment==1),labels=individual,cex=.5,pos=3,offset=-.7)
 mod <- lm(log(stem_weight)~log(dia),data=subset(check,segment==1))
 words.bottom.right.logxy(mod)
@@ -119,19 +119,19 @@ plot(leaf_weight~stem_weight,data=subset(check,age==2.4), pch=16,log="xy",col=co
 text(leaf_weight~stem_weight,data=subset(check,segment==1&age==2.4),labels=individual,cex=.5,pos=3,offset=-.7)
 
 
-plot(dia~stem_weight,data=subset(check,age<=1.4), pch=16,log="xy",col=col.lots[as.factor(individual)])
+plot(dia~stem_weight,data=subset(check,age<=1.4), pch=16,log="xy",col=col.lots(individual))
 text(dia~stem_weight,data=subset(check,segment==1&age<=1.4),labels=individual,cex=.5,pos=3,offset=-.7)
 mod <- lm(log(stem_weight)~log(dia),data=subset(check,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(dia~leaf_weight,data=subset(check,age<=1.4), pch=16,log="xy",col=col.lots[as.factor(individual)])
+plot(dia~leaf_weight,data=subset(check,age<=1.4), pch=16,log="xy",col=col.lots(individual))
 text(dia~leaf_weight,data=subset(check,segment==1&age<=1.4),labels=individual,cex=.5,pos=3,offset=-.7)
 
-plot(leaf_weight~stem_weight,data=subset(check,age<=1.4), pch=16,log="xy",col=col.lots[as.factor(individual)])
+plot(leaf_weight~stem_weight,data=subset(check,age<=1.4), pch=16,log="xy",col=col.lots(individual))
 text(leaf_weight~stem_weight,data=subset(check,segment==1&age<=1.4),labels=individual,cex=.5,pos=3,offset=-.7)
 
 
[…]

### 2015-08-19 scripts/lab_meeting_20150328.R

@@ -27,7 +27,7 @@ plot_RAbyAge <- function(spp) {
 }
 
 
-for(n in names(labels.spp)) {
+for(n in labels.spp()) {
   plot_RAbyAge(n)
 }
 ```
@@ -36,8 +36,8 @@ This led me to wonder how leaf lifespan - or some other variable - was shifting 
 
 The number of leaves along a leader is overall uneffected by age, although some species show a marked decline
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(shoot_leaf_count~age,SummaryInd,log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp[as.factor(species)])
-legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+plot(shoot_leaf_count~age,SummaryInd,log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp(species))
+legend("bottomright",col=col.spp, labels.spp.full(), pch=16, cex=1)
 ```
 
 #LMA versus age
@@ -47,15 +47,15 @@ There is a significant increase with age (p=0.002) and many species differ from 
 Age is only borderline significant (p=0.04) when the seedlings are removed
 
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(LMA~age,data=subset(LMA,branch_age=="mid"),log="xy", xlab="age",ylab="LMA",col=col.spp[as.factor(species)],pch=16)
-legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+plot(LMA~age,data=subset(LMA,branch_age=="mid"),log="xy", xlab="age",ylab="LMA",col=col.spp(species),pch=16)
+legend("bottomright",col=col.spp, labels.spp.full(), pch=16, cex=1)
 ```
 
 #Leaf lifespan with age
 Leaf lifespan increases from seedlings (1.4 yrs) to saplings (2.4 years) to adults (>4 years), but there are no differences between the different adult populations
 ```{r, echo=FALSE,results='hide', message=FALSE}
-plot(LL_birth~age,SummaryInd,log="xy", xlab="age",ylab="leaf lifespan (based on leaf births)",col=col.spp[as.factor(species)])
-legend("bottomright",col=col.spp, labels.spp, pch=16, cex=1)
+plot(LL_birth~age,SummaryInd,log="xy", xlab="age",ylab="leaf lifespan (based on leaf births)",col=col.spp(species))
[…]

### 2015-08-19 results_growth.Rmd
Tidy up use of remake and functions

@@
-```{r, echo=FALSE,results='hide', message=FALSE}
-library(remake)
-create_bindings()
-
-source("scripts/functions.R")
-```
 #Growth data, general patterns

### 2015-08-19 results_growth_short.R

@@ -1,10 +1,4 @@
-```{r, echo=FALSE,results='hide', message=FALSE}
-library(remake)
-create_bindings()
 
-
-source("scripts/functions.R")
-```
 #Growth data, general patterns
 - proportion of maxH matters more for some species than others. 
 1. The 4 "canopy" species all tend to have high correlations between "prop maxH" and growth and reproductive investment (both relative and absolute)  (HATE, BAER, PELA, PEPU)

### 2015-08-20 results_accessory_v3_alt_reproInv.Rmd
Tidy up use of remake and functions
fixing variable names

@@
-```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
-library(remake)
-create_bindings()
-
-source("scripts/functions.R")
-```
-
 #Accessory costs
@@
 par(mfrow=c(1,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-plot(accessory_inv~total_repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp(species))
+plot(accessory_inv~repro_inv,data=subset(SummaryInd,accessory_inv>0),log="xy",pch=16,col=col.spp(species))
 abline(0,1)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
-mod <- lm (log(total_weight)~log(total_repro_inv), data=subset(SummaryInd,total_repro_inv>0))
-plot(total_repro_inv~total_weight,data=subset(SummaryInd,total_repro_inv>0), log="xy",xlab="", col=col.spp(species), pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
+mod <- lm (log(total_weight)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
+plot(repro_inv~total_weight,data=subset(SummaryInd,repro_inv>0), log="xy",xlab="", col=col.spp(species), pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
 words.bottom.right.logxy(mod)
@@
 options(scipen=20)
-mod <- lm(asin(sqrt(seedset))~log(total_repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((total_repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
+mod <- lm(asin(sqrt(seedset))~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
+plot((repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
 words.bottom.right.logy(mod)
 
-mod <- lm(asin(sqrt(prop_propagule))~log(total_repro_inv),data=subset(SummaryInd,prop_propagule>0))
-plot((total_repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
+mod <- lm(asin(sqrt(prop_propagule))~log(repro_inv),data=subset(SummaryInd,prop_propagule>0))
+plot((repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
 words.bottom.right.logy(mod)
@@
 
-mod <- lm(log(propagule_per_seed)~log(total_repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((total_repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp(species))
+mod <- lm(log(propagule_per_seed)~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
+plot((repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp(species))
 words.bottom.right.logxy(mod)
@@
 
-mod <- lm((prop_maxH)~log((total_repro_inv)),data=subset(SummaryInd,prop_maxH>0&total_repro_inv>0))
-plot(total_repro_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&total_repro_inv>0), pch=16,col=col.spp(species),log="y", ylab="total reproductive investment (mg)")
+mod <- lm((prop_maxH)~log((repro_inv)),data=subset(SummaryInd,prop_maxH>0&repro_inv>0))
+plot(repro_inv~prop_maxH,data=subset(SummaryInd,prop_maxH>0&repro_inv>0), pch=16,col=col.spp(species),log="y", ylab="total reproductive investment (mg)")
 words.bottom.right.logy(mod)
@@
 tmp <- SummaryInd %>%
-  filter(total_repro_inv!=0&age>3) %>%
+  filter(repro_inv!=0&age>3) %>%
   group_by(species) %>%
@@
 tmp2 <- SummaryInd %>%
-  filter(total_repro_inv!=0&age>3) %>%
+  filter(repro_inv!=0&age>3) %>%
   group_by(species) %>%

### 2015-08-20 RA_figs.rmd
Tidy up use of remake and functions
fixing typos introduced by recent changes adding calcs for "growth deficit"

@@
-```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
-library(remake)
-create_bindings()
-
-source("scripts/functions.R")
-```
-
 ##Summary  
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age(data[[spp]]$age)
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1.4, xlim=c(0,1), ylim=c(0,1),
+                    main=spp,col=col.age(data[[spp]]$age))
 }
@@
 mtext("proportion maximum H", 1, outer=TRUE,cex=1.2)
-legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
+legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 ```
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age(data[[spp]]$age)
+                    main=spp,col=col.age(data[[spp]]$age))
 }
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
-                    main=spp,col=col.age(data[[spp]]$age)
+                    main=spp,col=col.age(data[[spp]]$age))
 }
@@
 results$b <- round(results$b,digits=2)
+results
 
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
-                    main=spp,col=col.mature(data[[spp]]$mature)
+                    main=spp,col=col.mature(data[[spp]]$mature))
 }
@@
 ```
+lmfits
+
+###Calculating cost of reproduction as a growth deficit
+```
+par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
+Summary2 <- SummaryInd
+Summary2 <- merge(Summary2,select(results, -n), by=c("species"), all=TRUE)
+Summary2$predict_growth <- ((Summary2$total_weight)*(10^(Summary2$b))) + (Summary2$a)
+Summary2$cost <- Summary2$predict_growth - Summary2$growth_inv
+Summary2$cost_plus_growth <- Summary2$cost + Summary2$growth_inv
+plot(total_weight ~ cost_plus_growth,data=subset(Summary2),log="xy",col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+abline(0,1)
+
+legend("bottomright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "cost"
+xvar <- "repro_inv"
+
+data <- subset(Summary2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
+                    main=spp,col=col.age(data[[spp]]$age))
+  abline(0,1)                  
+}
+
+mtext("Growth deficit (mg)", 2, outer=TRUE,cex=1.2)
+mtext("Reproductive investment (mg)", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 

### 2015-08-24 Accessory_figs.rmd
Tidy up use of remake and functions
fixing little errors due to remake

@@
-```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
-library(remake)
-create_bindings()
-
-source("scripts/functions.R")
-```
 #Summary  
@@
 plot(propagule_inv~total_weight,data=subset(SummaryInd,propagule_inv>0), log="xy",col=col.spp(species), pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp(species), pch=16, xlab="", ylab="Prepollen investment (mg)", xlim=c(100,2000000))
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 text(10,3,"50%",srt=45)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 ```
@@
 
-mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
+mod <- lm(log(seed_size)~(accessory_per_seed),SummarySpp[["mean"]])
 plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=.9)
-points((accessory_per_seed_mean)~seed_size,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points((accessory_per_seed)~seed_size,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean)),SummarySpp)
+mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
 plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=.9)
 words.bottom.right.logx(mod)
-points(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points(asin(sqrt(prop_accessory))~seed_size,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 mtext("seed size (mg)",1, outer=TRUE,cex=1.2)
 
-mod <- lm(log(total_weight_mean)~log(accessory_per_seed_mean),SummarySpp)
+mod <- lm(log(total_weight)~log(accessory_per_seed),SummarySpp[["mean"]])
 plot(accessory_per_seed~total_weight,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=.9)
-points((accessory_per_seed_mean)~total_weight_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points((accessory_per_seed)~total_weight,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
 
-mod <- lm(log(total_weight_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
+mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
 plot(asin(sqrt(prop_accessory))~total_weight,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
-points(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points(asin(sqrt(prop_accessory))~total_weight,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logx(mod)
@@
 
-mod <- lm(log(seedset_mean)~log(accessory_per_seed_mean),SummarySpp)
+mod <- lm(log(seedset)~log(accessory_per_seed),SummarySpp[["mean"]])
 plot((accessory_per_seed)~seedset,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=0.9)
-points((accessory_per_seed_mean)~seedset_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points((accessory_per_seed)~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.top.right.logxy(mod)
 
-mod <- lm(log(seedset_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
+mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
 plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
-legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
-points(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+points(asin(sqrt(prop_accessory))~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.top.right.logx(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(0.4,0.6,0.7,0.3), mai=c(1.1,1,0.3,0.3))
-mod <- lm(log(prepollen_all_per_seed_mean)~log(accessory_per_seed_mean),SummarySpp)
+mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),SummarySpp[["mean"]])
 plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp(species),ylab="accessory costs per successful seed",cex=0.9)
-points((accessory_per_seed_mean)~prepollen_all_per_seed_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points((accessory_per_seed)~prepollen_all_per_seed,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
 
-mod <- lm(asin(sqrt(prop_prepollen_all_mean))~asin(sqrt(prop_accessory_mean)),SummarySpp)
+mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
 plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp(species),ylab="proportional accessory costs",cex=0.9)
-points(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right(mod)
@@
 words.bottom.right(mod)
-legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
@@
 words.bottom.right.logy(mod)
-legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
@@
 words.bottom.right.logxy(mod)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
@@
 par(mfrow=c(4,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  
-mean1 <- SummarySpp$prop_propagule_mean
+mean1 <- SummarySpp$prop_propagule
 se1 <- SummarySpp$prop_propagule_se
-plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylim=c(.002,.25),ylab="propagules",xlab="")
+plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.002,.25),ylab="propagules",xlab="")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$propagule_per_seed_mean
+mean1 <- SummarySpp$propagule_per_seed
 se1 <- SummarySpp$propagule_per_seed_se
-plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
+plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$prop_prepollen_all_mean
+mean1 <- SummarySpp$prop_prepollen_all
 se1 <- SummarySpp$prop_prepollen_all_se
-plot(mean1~species,data=subset(SummarySpp),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
+plot(mean1~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$prepollen_all_per_seed_mean
+mean1 <- SummarySpp$prepollen_all_per_seed
 se1 <- SummarySpp$prepollen_all_per_seed_se
-plot((.01+prepollen_all_per_seed_mean)~species,data=subset(SummarySpp),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
+plot((.01+prepollen_all_per_seed)~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$prop_packaging_dispersal_mean
+mean1 <- SummarySpp$prop_packaging_dispersal
 se1 <- SummarySpp$prop_packaging_dispersal_se
-plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
+plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$packaging_dispersal_per_seed_mean
+mean1 <- SummarySpp$packaging_dispersal_per_seed
 se1 <- SummarySpp$packaging_dispersal_per_seed_se
-plot((packaging_dispersal_per_seed_mean+.1)~species,SummarySpp,cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
+plot((packaging_dispersal_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$prop_postpollen_aborted_mean
+mean1 <- SummarySpp$prop_postpollen_aborted
 se1 <- SummarySpp$prop_postpollen_aborted_se
-plot(mean1~species,SummarySpp,cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="aborted post-pollination tissues")
+plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="aborted post-pollination tissues")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$postpollen_aborted_per_seed_mean
+mean1 <- SummarySpp$postpollen_aborted_per_seed
 se1 <- SummarySpp$postpollen_aborted_per_seed_se
-plot((postpollen_aborted_per_seed_mean+.1)~species,SummarySpp,cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")
+plot((postpollen_aborted_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")
 se_function(mean1,se1)

### 2015-08-24 RA_figs.rmd
fixing little errors due to remake

@@
 words.top.left.logxy(mod)
-legend("bottomright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 abline(0,1)
@@
 
-legend("bottomright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
@@
 words.top.right.logx(mod)
-legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=0.8,bty="n")
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=0.8,bty="n")
 
@@
 * Orthoganal to these in WD vs.
-maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
+maxH, LMA, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
 
@@
   filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
-  select(prop_maxH,height,maxH,wood_density,LMA_mean,seed_size,growth_leaf,
+  select(prop_maxH,height,maxH,wood_density,LMA,seed_size,growth_leaf,
          growth_stem_diameter,leaf_area,growth_shoot_diameter,growth_stem_area,shoot_leaf_count,total_weight,
@@
 text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-mean1 <- PCA_by_species$PC1_scale_mean
+mean1 <- PCA_by_species$PC1_scale
 se1 <- PCA_by_species$PC1_scale_se
@@
 
-mean1 <- PCA_by_age$PC1_scale_mean
+mean1 <- PCA_by_age$PC1_scale
 se1 <- PCA_by_age$PC1_scale_se
@@
 
-mean1 <- PCA_by_species$PC2_scale_mean
+mean1 <- PCA_by_species$PC2_scale
 se1 <- PCA_by_species$PC2_scale_se
@@
 
-mean1 <- PCA_by_age$PC2_scale_mean
+mean1 <- PCA_by_age$PC2_scale
 se1 <- PCA_by_age$PC2_scale_se
@@
 * It is dividing the three (of 4) canopy species, HATE, PEPU, PELA, (BAER) versus
-* top variable loadings: scaled_growth_stem_diameter, wood_density,growth_stem_diameter, shoot_leaf_count vs. maxH, LMA_mean, seed_size, RA  
+* top variable loadings: scaled_growth_stem_diameter, wood_density,growth_stem_diameter, shoot_leaf_count vs. maxH, LMA, seed_size, RA  
 * not terribly interpretable, since doesn't make sense that scaled_growth_stem_diameter with wood_density
@@
 
-mean1 <- PCA_by_species$PC3_scale_mean
+mean1 <- PCA_by_species$PC3_scale
 se1 <- PCA_by_species$PC3_scale_se
@@
 
-mean1 <- PCA_by_age$PC3_scale_mean
+mean1 <- PCA_by_age$PC3_scale
 se1 <- PCA_by_age$PC3_scale_se
@@
 * it divides stem vs shoot growth variables  
-* high loadings for growth_stem_area, growth_leaf, LMA_mean, seed_set vs low loadings for shoot_growth_leaf_area, wood_density, prop_maxH, seed_size  
+* high loadings for growth_stem_area, growth_leaf, LMA, seed_set vs low loadings for shoot_growth_leaf_area, wood_density, prop_maxH, seed_size  
 * BAER, EPMI, HATE and HEPU have higher values vs.
@@
 text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-mean1 <- PCA_by_species$PC4_scale_mean
+mean1 <- PCA_by_species$PC4_scale
 se1 <- PCA_by_species$PC4_scale_se
@@
 
-mean1 <- PCA_by_age$PC4_scale_mean
+mean1 <- PCA_by_age$PC4_scale
 se1 <- PCA_by_age$PC4_scale_se

### 2015-08-24 results_RAschedules_shorter.Rmd
Tidy up use of remake and functions
fixing little errors due to remake

@@
-```{r, echo=FALSE,results='hide', message=FALSE}
-library(remake)
-create_bindings()
-
-source("scripts/functions.R")
-```
-
 #RA schedule paper
@@
 plot(repro_inv~total_weight, SummaryInd, log="xy",col=col.spp(species),pch=16)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 plot(repro_inv~height, SummaryInd, log="xy",col=col.spp(species),pch=16)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 plot((repro_inv)~(prop_maxH), SummaryInd, log="y",col=col.spp(species),pch=16,xlim=c(4e-03,1))
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 ```
@@
 plot(asin(sqrt(RA))~total_weight, SummaryInd, log="x",col=col.spp(species),pch=16)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.top.right.logx(mod)
@@
 plot(asin(sqrt(RA))~height, SummaryInd, log="x",col=col.spp(species),pch=16)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.top.right.logx(mod)
@@
 plot((asin(sqrt(RA)))~(prop_maxH), SummaryInd,col=col.spp(species),pch=16,xlim=c(4e-03,1))
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.bottom.right(mod)
@@
 plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp(species),pch=16)
-legend("bottomright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 plot((RA+.01)~RGR, SummaryInd, log="xy", col=col.spp(species),pch=16)
-legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.top.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
-plot(RA_mean~WD_mean,data=subset(SummarySpp,RA_mean>0), col=col.spp(species),pch=16,log="y",ylab="")
-mod <- lm(WD_mean~asin(sqrt(RA_mean)),SummarySpp)
+plot(RA~WD,data=subset(SummarySpp[["mean"]],RA>0), col=col.spp(species),pch=16,log="y",ylab="")
+mod <- lm(WD~asin(sqrt(RA)),SummarySpp[["mean"]])
 words.bottom.left.logy(mod)
-plot(RA_mean~seed_size, SummarySpp, col=col.spp(species),pch=16,log="xy",ylab="")
-mod <- lm(log(seed_size)~asin(sqrt(RA_mean)), SummarySpp)
+plot(RA~seed_size, SummarySpp[["mean"]], col=col.spp(species),pch=16,log="xy",ylab="")
+mod <- lm(log(seed_size)~asin(sqrt(RA)), SummarySpp[["mean"]])
 words.bottom.left.logxy(mod)
-legend(.05,.28,col=col.spp, legend=labels.spp(), pch=16, cex=.8,bty="n")
-plot(RA_mean~LMA_mean, SummarySpp, col=col.spp(species),pch=16,log="xy",ylab="")
-mod <- lm(log(LMA_mean)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
+legend(.05,.28,col=col.spp(), legend=labels.spp(), pch=16, cex=.8,bty="n")
+plot(RA~LMA, SummarySpp[["mean"]], col=col.spp(species),pch=16,log="xy",ylab="")
+mod <- lm(log(LMA)~asin(sqrt(RA)), data=subset(SummarySpp[["mean"]],RA>0))
 words.top.right.logxy(mod)
-plot(RA_mean~maxH, SummarySpp, col=col.spp(species),pch=16,log="xy",ylab="")
-mod <- lm(log(maxH)~asin(sqrt(RA_mean)), data=subset(SummarySpp,RA_mean>0))
+plot(RA~maxH, SummarySpp[["mean"]], col=col.spp(species),pch=16,log="xy",ylab="")
+mod <- lm(log(maxH)~asin(sqrt(RA)), data=subset(SummarySpp[["mean"]],RA>0))
 words.bottom.left.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1.1,1,.5,0.2))
-plot(maxH~WD_mean,data=subset(SummarySpp), col=col.spp(species),pch=16,log="y",ylab="")
-mod <- lm(mature_RA_mean~asin(sqrt(mature_RA_mean)),data=subset(SummarySpp,species!="BAER"))
+plot(maxH~WD,data=subset(SummarySpp[["mean"]]), col=col.spp(species),pch=16,log="y",ylab="")
+mod <- lm(mature_RA~asin(sqrt(mature_RA)),data=subset(SummarySpp[["mean"]],species!="BAER"))
 words.bottom.left.logy(mod)
-plot(mature_RA_mean~seed_size, data=subset(SummarySpp), col=col.spp(species),pch=16,log="xy",ylab="")
-mod <- lm(log(seed_size)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
+plot(mature_RA~seed_size, data=subset(SummarySpp[["mean"]]), col=col.spp(species),pch=16,log="xy",ylab="")
+mod <- lm(log(seed_size)~asin(sqrt(mature_RA)), data=subset(SummarySpp[["mean"]],species!="BAER"))
 words.bottom.left.logxy(mod)
-legend(.05,.28,col=col.spp, legend=labels.spp(), pch=16, cex=.8,bty="n")
-plot(mature_RA_mean~LMA_mean, data=subset(SummarySpp), col=col.spp(species),pch=16,log="xy",ylab="")
-mod <- lm(log(LMA_mean)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
+legend(.05,.28,col=col.spp(), legend=labels.spp(), pch=16, cex=.8,bty="n")
+plot(mature_RA~LMA, data=subset(SummarySpp[["mean"]]), col=col.spp(species),pch=16,log="xy",ylab="")
+mod <- lm(log(LMA)~asin(sqrt(mature_RA)), data=subset(SummarySpp[["mean"]],species!="BAER"))
 words.top.right.logxy(mod)
-plot(mature_RA_mean~maxH, data=subset(SummarySpp), col=col.spp(species),pch=16,log="xy",ylab="")
-mod <- lm(log(maxH)~asin(sqrt(mature_RA_mean)), data=subset(SummarySpp,species!="BAER"))
+plot(mature_RA~maxH, data=subset(SummarySpp[["mean"]]), col=col.spp(species),pch=16,log="xy",ylab="")
+mod <- lm(log(maxH)~asin(sqrt(mature_RA)), data=subset(SummarySpp[["mean"]],species!="BAER"))
 words.bottom.left.logxy(mod)
@@
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-mod <- lm(log(growth_stem_diameter) ~ age*WD_mean*LMA_mean*maxH*RA, SummaryInd)
+mod <- lm(log(growth_stem_diameter) ~ age*WD*LMA*maxH*RA, SummaryInd)
 anova(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.1,0.2), mai=c(1,1,.6,0.2))
-plot(RA~WD_mean,data=subset(SummaryInd,RA>0), col=col.spp(species),pch=16,log="y",ylim=c(.0008,1))
-points((RA+.001)~WD_mean,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=spp_zero_RA$RAcex)
-mod <- lm(WD_mean~asin(sqrt(RA)),SummaryInd)
+plot(RA~WD,data=subset(SummaryInd,RA>0), col=col.spp(species),pch=16,log="y",ylim=c(.0008,1))
+points((RA+.001)~WD,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=spp_zero_RA$RAcex)
+mod <- lm(WD~asin(sqrt(RA)),SummaryInd)
 words.bottom.left.logy(mod)
@@
 words.bottom.left.logxy(mod)
-plot(RA~LMA_mean, SummaryInd, col=col.spp(species),pch=16,log="xy",ylim=c(.0008,1))
-points((RA+.001)~LMA_mean,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=sppage_zero_RA$RAcex)
-mod <- lm(log(LMA_mean)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
+plot(RA~LMA, SummaryInd, col=col.spp(species),pch=16,log="xy",ylim=c(.0008,1))
+points((RA+.001)~LMA,data=subset(SummaryInd,RA==0),col=col.spp(species),pch=16, cex=sppage_zero_RA$RAcex)
+mod <- lm(log(LMA)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
 words.top.right.logxy(mod)

### 2015-08-24 results_growth.Rmd
fixing little errors due to remake

@@
 plot((total_weight~prop_maxH), SummaryInd, col=col.spp(species),pch=16,log="y")
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 ```
@@
 plot((growth_inv~prop_maxH), SummaryInd, log="y", col=col.spp(species),pch=16,xlab="")
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
@@
 plot(RGR~prop_maxH,SummaryInd,col=col.spp(species),pch=16)
-legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 ```
@@
 plot(growth_shoot_area~growth_stem_area,data=subset(SummaryInd), log="xy",col=col.spp(species), pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
-legend("bottomright",col=col.spp, legend=labels.spp(), pch=16, cex=1,bty="n")
+legend("bottomright",col=col.spp(), legend=labels.spp(), pch=16, cex=1,bty="n")
 
@@
 plot(shoot_leaf_count~age,data=subset(SummaryInd,age>2),log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp(species))
-legend("bottomright",col=col.spp, legend=labels.spp(), pch=16, cex=1,bty="n")
+legend("bottomright",col=col.spp(), legend=labels.spp(), pch=16, cex=1,bty="n")
 
@@
 plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp(species), pch=16, cex=0.8)
-legend("bottomright",col=col.spp, legend=labels.spp(), pch=16, cex=.8, bty="n")
+legend("bottomright",col=col.spp(), legend=labels.spp(), pch=16, cex=.8, bty="n")
 ```
@@
 plot(growth_shoot_length~prop_maxH,data=subset(SummaryInd,age>2),log="y", ylab="shoot extension (mm)",col=col.spp(species),pch=16)
-legend(12,200,col=col.spp, legend=labels.spp(), pch=16, cex=.8,bty="n")
+legend(12,200,col=col.spp(), legend=labels.spp(), pch=16, cex=.8,bty="n")
 words.bottom.right.logy(mod)
@@
 abline(0,1)
-legend("topleft",col=col.spp, legend=labels.spp(), pch=16, cex=.9, bty="n")
+legend("topleft",col=col.spp(), legend=labels.spp(), pch=16, cex=.9, bty="n")
 
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(growth_inv_mean ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age(age),pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
+plot(growth_inv ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age(age),pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
 legend("topleft",col=col.age, labels.age(), pch=16, cex=1,bty="n")
-text(growth_inv_mean ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
+text(growth_inv ~ seed_size, data=subset(SummarySppAge,age==9), labels=species, pos=2, offset=-2.4, cex=0.9,col="blue")
 ```
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==1.4))
+plot(growth_inv ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(growth_inv ~ maxH, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv ~ maxH, data=subset(SummarySppAge,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==2.4))
+plot(growth_inv ~ maxH,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(growth_inv ~ maxH, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv ~ maxH, data=subset(SummarySppAge,age==2.4))
 words.bottom.right.logxy(mod)
 
-plot(growth_inv_mean ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(growth_inv_mean ~ maxH, data=subset(SummarySppAge,age>3))
+plot(growth_inv ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_inv ~ maxH, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv ~ maxH, data=subset(SummarySppAge,age>3))
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
+plot(growth_inv ~ WD,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(growth_inv ~ WD, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv ~ WD, data=subset(SummarySppAge,age==1.4))
 words.bottom.left.logxy(mod)
 
-plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
+plot(growth_inv ~ WD,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(growth_inv ~ WD, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv ~ WD, data=subset(SummarySppAge,age==2.4))
 words.bottom.left.logxy(mod)
@@
 
-plot(growth_inv_mean ~ WD_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(growth_inv_mean ~ WD_mean, data=subset(SummarySppAge,age>3))
+plot(growth_inv ~ WD,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_inv ~ WD, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv ~ WD, data=subset(SummarySppAge,age>3))
 words.bottom.left.logxy(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==1.4))
+plot(RGR ~ WD,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(RGR ~ WD, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(RGR ~ WD, data=subset(SummarySppAge,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(RGR_mean ~ WD_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(RGR_mean ~ WD_mean, data=subset(SummarySppAge,age==2.4))
+plot(RGR ~ WD,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(RGR ~ WD, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(RGR ~ WD, data=subset(SummarySppAge,age==2.4))
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
-text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==1.4))
+plot(growth_inv ~ leaf_area,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
+text(growth_inv ~ leaf_area, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv ~ leaf_area, data=subset(SummarySppAge,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings",ylim=c(100,100000))
-text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==2.4))
+plot(growth_inv ~ leaf_area,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings",ylim=c(100,100000))
+text(growth_inv ~ leaf_area, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv ~ leaf_area, data=subset(SummarySppAge,age==2.4))
 words.bottom.right.logxy(mod)
 
-plot(growth_inv_mean ~ leaf_area_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
-text(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(growth_inv_mean ~ leaf_area_mean, data=subset(SummarySppAge,age>3))
+plot(growth_inv ~ leaf_area,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
+text(growth_inv ~ leaf_area, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv ~ leaf_area, data=subset(SummarySppAge,age>3))
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==1.4))
+plot(growth_inv ~ LMA,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(growth_inv ~ LMA, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv ~ LMA, data=subset(SummarySppAge,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age==2.4))
+plot(growth_inv ~ LMA,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(growth_inv ~ LMA, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv ~ LMA, data=subset(SummarySppAge,age==2.4))
 words.bottom.right.logxy(mod)
@@
 
-plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3))
+plot(growth_inv ~ LMA,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_inv ~ LMA, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv ~ LMA, data=subset(SummarySppAge,age>3))
 words.bottom.right.logxy(mod)
 
-plot(growth_inv_mean ~ LMA_mean,data=subset(SummarySppAge,age>3&species!="HATE"),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3&species!="HATE"), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(growth_inv_mean ~ LMA_mean, data=subset(SummarySppAge,age>3&species!="HATE"))
+plot(growth_inv ~ LMA,data=subset(SummarySppAge,age>3&species!="HATE"),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_inv ~ LMA, data=subset(SummarySppAge,age>3&species!="HATE"), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv ~ LMA, data=subset(SummarySppAge,age>3&species!="HATE"))
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2))
-plot(growth_inv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(log(LL_death_mean)~log(growth_inv_mean), data=subset(SummarySppAge,age==1.4))
+plot(growth_inv ~ LL_death,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(growth_inv ~ LL_death, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(log(LL_death)~log(growth_inv), data=subset(SummarySppAge,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(growth_inv_mean ~ LL_death_mean,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age==2.4))
+plot(growth_inv ~ LL_death,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(growth_inv ~ LL_death, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv ~ LL_death, data=subset(SummarySppAge,age==2.4))
 words.bottom.right.logxy(mod)
 
-plot(growth_inv_mean ~ LL_death_mean,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(growth_inv_mean ~ LL_death_mean, data=subset(SummarySppAge,age>3))
+plot(growth_inv ~ LL_death,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_inv ~ LL_death, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv ~ LL_death, data=subset(SummarySppAge,age>3))
 legend("topright",col=col.age,labels.age(),pch=16, bty="n")
@@
 * Orthoganal to these in WD vs.
-maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
+maxH, LMA, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
 * this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals - see below - greatly reducing sample size
@@
   filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
-  select(prop_maxH,height,maxH,WD_mean,LMA_mean,seed_size,growth_leaf,
+  select(prop_maxH,height,maxH,WD,LMA,seed_size,growth_leaf,
          RGR,leaf_area,growth_shoot_area,growth_stem_area,shoot_leaf_count,total_weight,
@@
 text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
@@
 * PC3 is somewhat similar. It is also prop_accessory and prop_maxH vs seed set and prop_propagule, but it now separates out all the shoot growth values
-* PC4 is now the axis that separates LMA_mean and maxH vs. WD_mean, with variables like maxH pulling toward all the "big size" arrows
+* PC4 is now the axis that separates LMA and maxH vs. WD, with variables like maxH pulling toward all the "big size" arrows
 
@@
   filter(shoot_leaf_count>0&accessory_inv>0&shoot_growth_leaf_area!=0) %>%
-  select(prop_maxH,height,maxH,WD_mean,LMA_mean,seed_size,growth_leaf,
+  select(prop_maxH,height,maxH,WD,LMA,seed_size,growth_leaf,
          RGR,leaf_area,growth_shoot_area,growth_stem_area,shoot_leaf_count,total_weight,
@@
 
-mod <- lm(RGR~asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1)+WD_mean+LMA_mean+maxH,SummaryInd)
+mod <- lm(RGR~asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1)+WD+LMA+maxH,SummaryInd)
 anova(mod)
@@
 
-* another of the interesting pattern is that the increase in shoot area of leaders is correlated with maxH and seed_size (and opposite WD_mean) and somewhat offset from whole plant growth measures and whole plant size measures
+* another of the interesting pattern is that the increase in shoot area of leaders is correlated with maxH and seed_size (and opposite WD) and somewhat offset from whole plant growth measures and whole plant size measures
 * seed_size removed, because no additional explanatory power after WD and maxH included
@@
 ```{r, echo=FALSE,message=FALSE}
-mod <- lm(log(growth_shoot_area)~log(maxH)+WD_mean+log(growth_stem_area)+log(total_weight)+RGR+asin(sqrt(RA))+LMA_mean,SummaryInd)
+mod <- lm(log(growth_shoot_area)~log(maxH)+WD+log(growth_stem_area)+log(total_weight)+RGR+asin(sqrt(RA))+LMA,SummaryInd)
 anova(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-plot(WD_mean~maxH,SummarySpp, log="x",col=col.spp(species),pch=16)
-mod <- lm(log(maxH)~WD_mean,SummaryInd)
+plot(WD~maxH,SummarySpp[["mean"]], log="x",col=col.spp(species),pch=16)
+mod <- lm(log(maxH)~WD,SummaryInd)
 words.bottom.left.logx(mod)
 
-plot(WD_mean~maxH,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"), log="x",col=col.spp(species),pch=16)
-mod <- lm(log(maxH)~WD_mean,data=subset(SummarySpp,species!="PUTU"&species!="PHPH"))
+plot(WD~maxH,data=subset(SummarySpp[["mean"]],species!="PUTU"&species!="PHPH"), log="x",col=col.spp(species),pch=16)
+mod <- lm(log(maxH)~WD,data=subset(SummarySpp[["mean"]],species!="PUTU"&species!="PHPH"))
 words.bottom.left.logx(mod)
 
-plot(seedset_mean~total_weight_mean,SummarySpp, log="x",col=col.spp(species),pch=16)
-mod <- lm(log(total_weight_mean) ~ (seedset_mean),SummarySpp)
+plot(seedset~total_weight,SummarySpp[["mean"]], log="x",col=col.spp(species),pch=16)
+mod <- lm(log(total_weight) ~ (seedset),SummarySpp[["mean"]])
 words.bottom.left.logx(mod)
 
-plot(seedset_mean~maxH,SummarySpp, log="x",col=col.spp(species),pch=16)
-mod <- lm(log(maxH) ~ (seedset_mean),SummarySpp)
+plot(seedset~maxH,SummarySpp[["mean"]], log="x",col=col.spp(species),pch=16)
+mod <- lm(log(maxH) ~ (seedset),SummarySpp[["mean"]])
 words.bottom.left.logx(mod)

### 2015-08-24 results_growth_short.Rmd
Tidy up use of remake and functions
fixing little errors due to remake

@@
- ```{r, echo=FALSE,results='hide', message=FALSE}
-library(remake)
-create_bindings()
-
-source("scripts/functions.R")
-
-```
 ##Growth data, general patterns
@@
 plot((RA+.01)~growth_stem_diameter, SummaryInd, log="xy", col=col.spp(species),pch=16)
-legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.top.right.logxy(mod)
@@
 plot((RA+.01)~prop_growth_stem_diameter, SummaryInd, log="xy", col=col.spp(species),pch=16)
-legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.top.right.logxy(mod)
@@
 * Orthoganal to these in WD vs.
-maxH, LMA_mean, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
+maxH, LMA, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
 * I interpret this to mean that the three traits (Hmax, LMA, WD) strongly influence each other - presumably, Hmax a function of WD and LMA), but do not particularly 
@@
   filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
-  select(prop_maxH,height,maxH,WD_mean,LMA_mean,seed_size,growth_leaf,
+  select(prop_maxH,height,maxH,WD,LMA,seed_size,growth_leaf,
          growth_stem_diameter,leaf_area,growth_shoot_area,growth_stem_area,shoot_leaf_count,total_weight,
@@
 plot(RA~prop_maxH,SummaryInd,col=col.spp(species),pch=16)
-legend("topright",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 ```

### 2015-08-24 R/ReproductionAllocation.R

@@ -1,0 +1,68 @@
+RA_Calculations <- function(thisSpecies, Species_Investment, HarvestData, Maps, IndividualsList) {
+
+  individuals <- filter(IndividualsList, use_for_allocation_calculations & alive)$individual
+  HarvestData_basal <- filter(HarvestData,  individual %in% individuals & segment == 1)
+  HarvestData_basal_end  <- filter(HarvestData_basal, start_end=="end")
+
+  ### Calculate Regression coefficients based on common slope and intercept by the basal diameter at year 2013
+  ## allow intercept to vary by individual
+
+  lm.fit <- function(var, data) {
+    lm(log(data[[var]]) ~ log(data[["diameter"]]))
+  }
+
+  fit_total <- lm.fit("total_weight", HarvestData_basal_end)
+  fit_stem <- lm.fit("stem_weight", HarvestData_basal_end)
+
+  HarvestData_basal_end <- HarvestData_basal_end %>%
+    mutate(
+      slope_total  = as.numeric(coef( fit_total)[2]),
+      intercept_total = log(total_weight) - slope_total * log(diameter),
+      slope_stem  = as.numeric(coef( fit_stem)[2]),
+      intercept_stem = log(stem_weight) - slope_stem * log(diameter))
+
+
+  predict_total_weight <- function(diameter, thisindividual) {
+    x <- HarvestData_basal_end %>% filter(individual==thisindividual)
+    exp(x$intercept_total + x$slope_total * log(diameter))
+  }
+
+  predict_stem_weight <- function(diameter, thisindividual) {
+    x <- HarvestData_basal_end %>% filter(individual==thisindividual)
+    exp(x$intercept_stem + x$slope_stem * log(diameter))
+  }
+
+  ## Estimate weight at beginning and end  (year 2012 and 2013) using fitted regression
+  GrowthEst <- HarvestData_basal %>%
+    group_by(individual) %>%
+    mutate(total_weight_est =  predict_total_weight(diameter, individual[1]),
+           growth_inv = c(NA, diff(total_weight_est)),
+           stem_weight_est = predict_stem_weight(diameter, individual[1]),
+           growth_stem = c(NA, diff(stem_weight_est)),
+           growth_leaf =  growth_inv - growth_stem,
+           growth_height = c(NA, diff(height)),
+           growth_stem_diameter = c(NA, diff(diameter)),
+           growth_stem_area = c(NA, diff(stem_area))
+           ) %>%
[…]

### 2015-08-24 scripts/lab_meeting_20150328.R

@@ -23,7 +23,7 @@ They show that species differ greatly in RA, that there is a general increase wi
 ```{r, echo=FALSE,results='hide', message=FALSE}
 plot_RAbyAge <- function(spp) {
   plot(RA~age, data=subset(SummaryInd,species==spp), xlab="age (years)",ylab="reproductive allocation (%)", log="x", main=labels.spp[spp],xlim=c(1,35),ylim=c(0,1))
-  points(RA_mean~age, data=subset(SummarySppAge, species==spp),pch=16,cex=1.4)
+  points(RA~age, data=subset(SummarySppAge, species==spp),pch=16,cex=1.4)
 }
 
 
@@ -37,7 +37,7 @@ This led me to wonder how leaf lifespan - or some other variable - was shifting 
 The number of leaves along a leader is overall uneffected by age, although some species show a marked decline
 ```{r, echo=FALSE,results='hide', message=FALSE}
 plot(shoot_leaf_count~age,SummaryInd,log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp(species))
-legend("bottomright",col=col.spp, labels.spp.full(), pch=16, cex=1)
+legend("bottomright",col=col.spp(), labels.spp.full(), pch=16, cex=1)
 ```
 
 #LMA versus age
@@ -48,14 +48,14 @@ Age is only borderline significant (p=0.04) when the seedlings are removed
 
 ```{r, echo=FALSE,results='hide', message=FALSE}
 plot(LMA~age,data=subset(LMA,branch_age=="mid"),log="xy", xlab="age",ylab="LMA",col=col.spp(species),pch=16)
-legend("bottomright",col=col.spp, labels.spp.full(), pch=16, cex=1)
+legend("bottomright",col=col.spp(), labels.spp.full(), pch=16, cex=1)
 ```
 
 #Leaf lifespan with age
 Leaf lifespan increases from seedlings (1.4 yrs) to saplings (2.4 years) to adults (>4 years), but there are no differences between the different adult populations
 ```{r, echo=FALSE,results='hide', message=FALSE}
 plot(LL_birth~age,SummaryInd,log="xy", xlab="age",ylab="leaf lifespan (based on leaf births)",col=col.spp(species))
-legend("bottomright",col=col.spp, labels.spp.full(), pch=16, cex=1)
[…]

### 2015-08-26 Accessory_figs.rmd
starting to get scripts to run again - accessory_figs runs with a few small hitches (i.e. not using SE)

@@
+```{r}
+remake::make("export")
+
+SummaryInd <- readRDS("export/SummaryInd.rds")
+SummarySpp <- readRDS("export/SummarySpp.rds")
+SummarySppAge <- readRDS("export/SummarySppAge.rds")
+
+source("R/figures.R")
+```
+
 #Summary  
@@
 
-mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
-plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=.9)
+mod <- lm(log(seed_size)~prop_accessory,SummarySpp[["mean"]])
+plot(prop_accessory~seed_size,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=.9)
 words.bottom.right.logx(mod)
-points(asin(sqrt(prop_accessory))~seed_size,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
+points(prop_accessory~seed_size,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 mtext("seed size (mg)",1, outer=TRUE,cex=1.2)
@@
 
-mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
-plot(asin(sqrt(prop_accessory))~total_weight,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
-points(asin(sqrt(prop_accessory))~total_weight,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
+mod <- lm(log(total_weight)~prop_accessory,SummarySpp[["mean"]])
+plot(prop_accessory~total_weight,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
+points(prop_accessory~total_weight,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logx(mod)
@@
 mod <- lm(log(seedset)~log(accessory_per_seed),SummarySpp[["mean"]])
-plot((accessory_per_seed)~seedset,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=0.9)
-points((accessory_per_seed)~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
+plot(accessory_per_seed~seedset,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=0.9)
+points(accessory_per_seed~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.top.right.logxy(mod)
 
-mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
-plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
+mod <- lm(log(seedset)~prop_accessory,SummarySpp[["mean"]])
+plot(prop_accessory~seedset,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-points(asin(sqrt(prop_accessory))~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
+points(prop_accessory~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.top.right.logx(mod)
@@
 mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),SummarySpp[["mean"]])
-plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp(species),ylab="accessory costs per successful seed",cex=0.9)
-points((accessory_per_seed)~prepollen_all_per_seed,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
+plot(accessory_per_seed~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp(species),ylab="accessory costs per successful seed",cex=0.9)
+points(accessory_per_seed~prepollen_all_per_seed,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
 
-mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
-plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp(species),ylab="proportional accessory costs",cex=0.9)
-points(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
+mod <- lm(prop_prepollen_all~prop_accessory,SummarySpp[["mean"]])
+plot(prop_accessory~prop_prepollen_all,SummaryInd, log="", pch=16,col=col.spp(species),ylab="proportional accessory costs",cex=0.9)
+points(prop_accessory~prop_prepollen_all,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right(mod)
 ```
+
+SummarySpp[["mean"]]$accessory_per_seed
 
@@
 par(mfrow=c(2,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
-mod <- lm(asin(sqrt(seedset))~asin(sqrt(RA)),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(asin(sqrt(RA))~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
+mod <- lm(seedset~RA,data=subset(SummaryInd,seedset>0&seedset<1))
+plot(RA~seedset,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
 words.bottom.right(mod)
 
-mod <- lm(asin(sqrt(prop_propagule))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(RA))~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
+mod <- lm(prop_propagule~RA,data=subset(SummaryInd,prop_propagule>0))
+plot(RA~prop_propagule,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
 words.bottom.right(mod)
@@
 
-mod <- lm(asin(sqrt(propagule_per_seed))~asin(sqrt(RA)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(RA))~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="x",pch=16,col=col.spp(species))
+mod <- lm(propagule_per_seed~RA,data=subset(SummaryInd,seedset>0&seedset<1))
+plot(RA~propagule_per_seed,data=subset(SummaryInd,seedset>0&seedset<1), log="x",pch=16,col=col.spp(species))
 words.bottom.right.logx(mod)
@@
 options(scipen=20)
-mod <- lm(asin(sqrt(seedset))~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((repro_inv)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
+mod <- lm(seedset~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(repro_inv~seedset,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
 words.bottom.right.logy(mod)
 
-mod <- lm(asin(sqrt(prop_propagule))~log(repro_inv),data=subset(SummaryInd,prop_propagule>0))
-plot((repro_inv)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
+mod <- lm(prop_propagule~log(repro_inv),data=subset(SummaryInd,prop_propagule>0))
+plot(repro_inv~prop_propagule,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="y")
 words.bottom.right.logy(mod)
@@
 mod <- lm(log(propagule_per_seed)~log(repro_inv),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((repro_inv)~(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp(species))
+plot(repro_inv~propagule_per_seed,data=subset(SummaryInd,seedset>0&seedset<1), log="xy",pch=16,col=col.spp(species))
 words.bottom.right.logxy(mod)
@@
 options(scipen=20)
-mod <- lm((prop_maxH)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(asin(sqrt(seedset))~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
+mod <- lm(prop_maxH~seedset,data=subset(SummaryInd,seedset>0&seedset<1))
+plot(seedset~prop_maxH,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
 words.bottom.right(mod)
 
-mod <- lm(log(height)~asin(sqrt(seedset)),data=subset(SummaryInd,seedset>0&seedset<1))
-plot(asin(sqrt(seedset))~(height),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="x")
+mod <- lm(log(height)~seedset,data=subset(SummaryInd,seedset>0&seedset<1))
+plot(seedset~height,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species),log="x")
 words.bottom.right.logx(mod)
 
-mod <- lm((prop_maxH)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,prop_propagule>0))
-plot(asin(sqrt(prop_propagule))~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
+mod <- lm(prop_maxH~prop_propagule,data=subset(SummaryInd,prop_propagule>0))
+plot(prop_propagule~prop_maxH,data=subset(SummaryInd,seedset>0&seedset<1), pch=16,col=col.spp(species))
 words.bottom.right(mod)
@@
 
-mod <- lm((prop_maxH)~log(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1))
-plot((propagule_per_seed)~(prop_maxH),data=subset(SummaryInd,seedset>0&seedset<1), log="y",pch=16,col=col.spp(species))
+mod <- lm(prop_maxH~log(propagule_per_seed),data=subset(SummaryInd,seedset>0&seedset<1))
+plot(propagule_per_seed~prop_maxH,data=subset(SummaryInd,seedset>0&seedset<1), log="y",pch=16,col=col.spp(species))
 words.bottom.right.logy(mod)
@@
 
-mod <- lm(log(RA)~log((propagule_inv)),data=subset(SummaryInd,RA>0&propagule_inv>0))
-plot(propagule_inv~RA,data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to propagules (mg)")
-words.bottom.right.logxy(mod)
+mod <- lm(RA~log(propagule_inv),data=subset(SummaryInd,RA>0&propagule_inv>0))
+plot(propagule_inv~RA,data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to propagules (mg)")
+words.top.left.logxy(mod)
 
-mod <- lm(log(RA)~asin(sqrt(prop_propagule)),data=subset(SummaryInd,RA>0&prop_propagule>0))
-plot(asin(sqrt(prop_propagule))~RA,data=subset(SummaryInd,RA>0&prop_propagule>0), log="x", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
+mod <- lm(RA~prop_propagule,data=subset(SummaryInd,RA>0&prop_propagule>0))
+plot(prop_propagule~RA,data=subset(SummaryInd,RA>0&prop_propagule>0), log="", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
 words.bottom.left.logx(mod)
 
-mod <- lm(log(RA)~log((prepollen_aborted_inv)),data=subset(SummaryInd,RA>0&prepollen_aborted_inv>0))
-plot(prepollen_aborted_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination aborted tissues (mg)")
-words.bottom.right.logxy(mod)
+mod <- lm(RA~log(prepollen_aborted_inv),data=subset(SummaryInd,RA>0&prepollen_aborted_inv>0))
+plot(prepollen_aborted_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination aborted tissues (mg)")
+words.top.left.logxy(mod)
 
-mod <- lm(log(RA)~asin(sqrt(prop_prepollen_aborted)),data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0))
-plot(asin(sqrt(prop_prepollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination aborted tissues (as proportion repro inv) (asin)")
+mod <- lm(RA~prop_prepollen_aborted,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0))
+plot(prop_prepollen_aborted~RA,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0), pch=16,col=col.spp(species), log="",ylab="pre-pollination aborted tissues (as proportion repro inv)")
 words.bottom.right.logx(mod)
 
-mod <- lm(log(RA)~log((prepollen_success_inv)),data=subset(SummaryInd,RA>0&prepollen_success_inv>0))
-plot(prepollen_success_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="xy",ylab="pre-pollination successful tissues (mg)")
-words.bottom.right.logxy(mod)
+mod <- lm(RA~log(prepollen_success_inv),data=subset(SummaryInd,RA>0&prepollen_success_inv>0))
+plot(prepollen_success_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination successful tissues (mg)")
+words.top.left.logxy(mod)
 
-mod <- lm(log(RA)~asin(sqrt(prop_prepollen_success)),data=subset(SummaryInd,RA>0&prop_prepollen_success>0))
-plot(asin(sqrt(prop_prepollen_success))~RA,data=subset(SummaryInd,RA>0&prop_prepollen_success>0), pch=16,col=col.spp(species), log="x",ylab="pre-pollination successful tissues (as proportion repro inv) (asin)")
+mod <- lm(RA~prop_prepollen_success,data=subset(SummaryInd,RA>0&prop_prepollen_success>0))
+plot(prop_prepollen_success~RA,data=subset(SummaryInd,RA>0&prop_prepollen_success>0), pch=16,col=col.spp(species), log="",ylab="pre-pollination successful tissues (as proportion repro inv)")
 words.bottom.right.logx(mod)
 
-mod <- lm(log(RA)~log((packaging_dispersal_inv)),data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0))
-plot(packaging_dispersal_inv~RA,data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to packaging and dispersal (mg)")
+mod <- lm(RA~log(packaging_dispersal_inv),data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0))
+plot(packaging_dispersal_inv~RA,data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to packaging and dispersal (mg)")
 words.bottom.right.logxy(mod)
@@
 
-mod <- lm(log(RA)~asin(sqrt(prop_packaging_dispersal)),data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0))
-plot(asin(sqrt(prop_packaging_dispersal))~RA,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0), log="x", pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
+mod <- lm(RA~prop_packaging_dispersal,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0))
+plot(prop_packaging_dispersal~RA,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0), log="", pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
 words.bottom.left.logx(mod)
 
-mod <- lm(log(RA)~log((postpollen_aborted_inv)),data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0))
-plot(postpollen_aborted_inv~RA,data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="xy", ylab="energy to tissues aborted postpollination (mg)")
+mod <- lm(RA~log(postpollen_aborted_inv),data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0))
+plot(postpollen_aborted_inv~RA,data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to tissues aborted postpollination (mg)")
 words.bottom.right.logxy(mod)
 
-mod <- lm(log(RA)~asin(sqrt(prop_postpollen_aborted)),data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0))
-plot(asin(sqrt(prop_postpollen_aborted))~RA,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0), log="x", pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
+mod <- lm(RA~prop_postpollen_aborted,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0))
+plot(prop_postpollen_aborted~RA,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0), log="", pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
 words.bottom.left.logx(mod)
@@
 par(mfrow=c(4,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  
-mean1 <- SummarySpp$prop_propagule
-se1 <- SummarySpp$prop_propagule_se
-plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.002,.25),ylab="propagules",xlab="")
+mean1 <- SummarySpp[["mean"]]$prop_propagule
+se1 <- SummarySpp[["sd"]]$prop_propagule
+boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="proportion propagules",xlab="")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$propagule_per_seed
-se1 <- SummarySpp$propagule_per_seed_se
-plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
+mean1 <- SummarySpp[["mean"]]$propagule_per_seed
+se1 <- SummarySpp[["sd"]]$propagule_per_seed
+boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$prop_prepollen_all
-se1 <- SummarySpp$prop_prepollen_all_se
-plot(mean1~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
+mean1 <- SummarySpp[["mean"]]$prop_prepollen_all
+se1 <- SummarySpp[["sd"]]$prop_prepollen_all
+boxplot(mean1~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$prepollen_all_per_seed
-se1 <- SummarySpp$prepollen_all_per_seed_se
-plot((.01+prepollen_all_per_seed)~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
+mean1 <- SummarySpp[["mean"]]$prepollen_all_per_seed
+se1 <- SummarySpp[["sd"]]$prepollen_all_per_seed
+boxplot((.01+prepollen_all_per_seed)~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$prop_packaging_dispersal
-se1 <- SummarySpp$prop_packaging_dispersal_se
-plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
+mean1 <- SummarySpp[["mean"]]$prop_packaging_dispersal
+se1 <- SummarySpp[["sd"]]$prop_packaging_dispersal
+boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$packaging_dispersal_per_seed
-se1 <- SummarySpp$packaging_dispersal_per_seed_se
-plot((packaging_dispersal_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
+mean1 <- SummarySpp[["mean"]]$packaging_dispersal_per_seed
+se1 <- SummarySpp[["sd"]]$packaging_dispersal_per_seed
+boxplot((packaging_dispersal_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$prop_postpollen_aborted
-se1 <- SummarySpp$prop_postpollen_aborted_se
-plot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="aborted post-pollination tissues")
+mean1 <- SummarySpp[["mean"]]$prop_postpollen_aborted
+se1 <- SummarySpp[["sd"]]$prop_postpollen_aborted
+boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="aborted post-pollination tissues")
 se_function(mean1,se1)
 
-mean1 <- SummarySpp$postpollen_aborted_per_seed
-se1 <- SummarySpp$postpollen_aborted_per_seed_se
-plot((postpollen_aborted_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")
+mean1 <- SummarySpp[["mean"]]$postpollen_aborted_per_seed
+se1 <- SummarySpp[["sd"]]$postpollen_aborted_per_seed
+boxplot((postpollen_aborted_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")
 se_function(mean1,se1)
@@
 
-plot(mean~species,
+plot(mean~as.factor(species),
      tmp,
@@
 
-plot(mean~species,
+plot(mean~as.factor(species),
      tmp2,

### 2015-08-26 RA_figs.rmd
starting to get scripts to run again - accessory_figs runs with a few small hitches (i.e. not using SE)

@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1.4, xlim=c(0,1), ylim=c(0,1),
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1, xlim=c(0,1), 
                     main=spp,col=col.age(data[[spp]]$age))

### 2015-08-26 RA_figs.rmd
continued fixes to old scripts

@@
 data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(asin(sqrt(x[[yvar]])) ~  ((x[[xvar]]))))
+lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  ((x[[xvar]]))))
 results <- summarise_all_fits(lmfits)
@@
 mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
-legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
+legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 ```
@@
 }
-
+#doesn't like preceding lines of text - PROBLEM
 ###calc_veg <- merge(SummaryInd, select(results, -species), by="species",all.x=TRUE)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
-plot(asin(sqrt(RA))~growth_stem_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp(species), pch=16)
-mod <- lm(log(growth_stem_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
+plot(RA~growth_stem_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp(species), pch=16)
+mod <- lm(log(growth_stem_diameter)~RA,data=subset(SummaryInd,RA>0))
 words.top.right.logx(mod)
@@
 
-plot(asin(sqrt(RA))~growth_shoot_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp(species), pch=16)
-mod <- lm(log(growth_shoot_diameter)~asin(sqrt(RA)),data=subset(SummaryInd,RA>0))
+plot(RA~growth_shoot_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp(species), pch=16)
+mod <- lm(log(growth_shoot_diameter)~RA,data=subset(SummaryInd,RA>0))
 words.top.right.logx(mod)

### 2015-08-27 Accessory_figs.rmd
scripts now mostly working. Adding new information on costs of reproduction

@@
 ###5. What influences the correlation between RA and plant size (or total reproductive investment)?  
-  ***Don't trust anything until I know RA and repro_inv are correct, because PHPH and PUTU have huge influence on patterns***
+* we know bigger plants have higher RA - do all accessory tissue components shift equally or do some have greater proportional effects
+* total energy to propagules increases with RA, because RA increases with plant size  
+* relative investment in pre-pollination aborted tissues decreases with RA - but that energy is split across lots of different pools
+* other regressions have significant slopes, but R^2 < .1, so not putting much meaning in them
 ```{r, echo=FALSE,message=FALSE,fig.width=12, fig.height=30,warning=FALSE}
-par(mfrow=c(5,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
+par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
 
@@
 plot(propagule_inv~RA,data=subset(SummaryInd,RA>0&propagule_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to propagules (mg)")
-words.top.left.logxy(mod)
+words.bottom.right.logy(mod)
 
@@
 plot(prop_propagule~RA,data=subset(SummaryInd,RA>0&prop_propagule>0), log="", pch=16,col=col.spp(species),ylab="propagules (as proportion repro inv)")
-words.bottom.left.logx(mod)
+words.bottom.left(mod)
 
@@
 plot(prepollen_aborted_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination aborted tissues (mg)")
-words.top.left.logxy(mod)
+words.bottom.right.logy(mod)
 
@@
 plot(prop_prepollen_aborted~RA,data=subset(SummaryInd,RA>0&prop_prepollen_aborted>0), pch=16,col=col.spp(species), log="",ylab="pre-pollination aborted tissues (as proportion repro inv)")
-words.bottom.right.logx(mod)
+words.bottom.right(mod)
 
@@
 plot(prepollen_success_inv~RA,data=subset(SummaryInd,RA<1&RA>0), pch=16,col=col.spp(species),log="y",ylab="pre-pollination successful tissues (mg)")
-words.top.left.logxy(mod)
+words.bottom.right.logy(mod)
 
@@
 plot(prop_prepollen_success~RA,data=subset(SummaryInd,RA>0&prop_prepollen_success>0), pch=16,col=col.spp(species), log="",ylab="pre-pollination successful tissues (as proportion repro inv)")
-words.bottom.right.logx(mod)
+words.bottom.right(mod)
 
@@
 plot(packaging_dispersal_inv~RA,data=subset(SummaryInd,RA>0&packaging_dispersal_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to packaging and dispersal (mg)")
-words.bottom.right.logxy(mod)
+words.bottom.right.logy(mod)
 legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
@@
 plot(prop_packaging_dispersal~RA,data=subset(SummaryInd,RA>0&prop_packaging_dispersal>0), log="", pch=16,col=col.spp(species),ylab="packaging and dispersal (as proportion repro inv)")
-words.bottom.left.logx(mod)
+words.bottom.left(mod)
 
@@
 plot(postpollen_aborted_inv~RA,data=subset(SummaryInd,RA>0&postpollen_aborted_inv>0), pch=16,col=col.spp(species),log="y", ylab="energy to tissues aborted postpollination (mg)")
-words.bottom.right.logxy(mod)
+words.bottom.right.logy(mod)
 
@@
 plot(prop_postpollen_aborted~RA,data=subset(SummaryInd,RA>0&prop_postpollen_aborted>0), log="", pch=16,col=col.spp(species),ylab="tissues aborted postpollination (as proportion repro inv)")
-words.bottom.left.logx(mod)
+words.bottom.left(mod)
 ```
@@
 ```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=28,warning=FALSE}
-par(mfrow=c(4,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  
+par(mfrow=c(2,2), cex=1, omi=c(1,.1,.7,.1), mai=c(.5,1.1,.2,0.2))  
 mean1 <- SummarySpp[["mean"]]$prop_propagule
-se1 <- SummarySpp[["sd"]]$prop_propagule
+se1 <- SummarySpp[["se"]]$prop_propagule
 boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="proportion propagules",xlab="")
@@
 mean1 <- SummarySpp[["mean"]]$propagule_per_seed
-se1 <- SummarySpp[["sd"]]$propagule_per_seed
+se1 <- SummarySpp[["se"]]$propagule_per_seed
 boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylab="propagules",xlab="")
@@
 mean1 <- SummarySpp[["mean"]]$prop_prepollen_all
-se1 <- SummarySpp[["sd"]]$prop_prepollen_all
+se1 <- SummarySpp[["se"]]$prop_prepollen_all
 boxplot(mean1~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylim=c(.1,1),ylab="pre-pollination tissues",xlab="")
@@
 mean1 <- SummarySpp[["mean"]]$prepollen_all_per_seed
-se1 <- SummarySpp[["sd"]]$prepollen_all_per_seed
+se1 <- SummarySpp[["se"]]$prepollen_all_per_seed
 boxplot((.01+prepollen_all_per_seed)~species,data=subset(SummarySpp[["mean"]]),cex.axis=.5,pch=16,ylab="pre-pollination tissues",xlab="",log="y")
@@
 mean1 <- SummarySpp[["mean"]]$prop_packaging_dispersal
-se1 <- SummarySpp[["sd"]]$prop_packaging_dispersal
+se1 <- SummarySpp[["se"]]$prop_packaging_dispersal
 boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="packaging and dispersal")
@@
 mean1 <- SummarySpp[["mean"]]$packaging_dispersal_per_seed
-se1 <- SummarySpp[["sd"]]$packaging_dispersal_per_seed
+se1 <- SummarySpp[["se"]]$packaging_dispersal_per_seed
 boxplot((packaging_dispersal_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="packaging and dispersal",log="y")
@@
 mean1 <- SummarySpp[["mean"]]$prop_postpollen_aborted
-se1 <- SummarySpp[["sd"]]$prop_postpollen_aborted
-boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.02,1),ylab="aborted post-pollination tissues")
+se1 <- SummarySpp[["se"]]$prop_postpollen_aborted
+boxplot(mean1~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,log="y",ylim=c(.005,1),ylab="aborted post-pollination tissues")
 se_function(mean1,se1)
@@
 mean1 <- SummarySpp[["mean"]]$postpollen_aborted_per_seed
-se1 <- SummarySpp[["sd"]]$postpollen_aborted_per_seed
+se1 <- SummarySpp[["se"]]$postpollen_aborted_per_seed
 boxplot((postpollen_aborted_per_seed+.1)~species,SummarySpp[["mean"]],cex.axis=.5,pch=16,ylab="aborted post-pollination tissues",log="y")

### 2015-08-27 RA_figs.rmd
scripts now mostly working. Adding new information on costs of reproduction

@@
 plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
-legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=.8,bty="n")
+legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
 abline(0,1)
@@
 data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
 results <- summarise_all_fits(lmfits)
@@
 ```
-lmfits
-
-###Calculating cost of reproduction as a growth deficit
-```
-par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
-Summary2 <- SummaryInd
-Summary2 <- merge(Summary2,select(results, -n), by=c("species"), all=TRUE)
-Summary2$predict_growth <- ((Summary2$total_weight)*(10^(Summary2$b))) + (Summary2$a)
-Summary2$cost <- Summary2$predict_growth - Summary2$growth_inv
-Summary2$cost_plus_growth <- Summary2$cost + Summary2$growth_inv
-plot(total_weight ~ cost_plus_growth,data=subset(Summary2),log="xy",col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
-abline(0,1)
-
-legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "cost"
-xvar <- "repro_inv"
-
-data <- subset(Summary2)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
-                    main=spp,col=col.age(data[[spp]]$age))
-  abline(0,1)                  
-}
-
-mtext("Growth deficit (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Reproductive investment (mg)", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 
@@
 * determine proportional reproductive cost for reproducing individuals; probably look by age
-
+*LEES, BOLE, EPMI become much tighter when reproductive investment included - all but 1 species
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
@@
 
+###Calculating cost of reproduction as a growth deficit
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
+pdf("figs2/cost_of_repro1.pdf", height=12, width=12)
+  plot
+par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
+yvar <- "growth_inv"
+xvar <- "total_weight"
+
+data <- subset(SummaryInd,repro_inv=0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results_cost <- summarise_all_fits(lmfits)
+
+results_cost$r.squared <- round(results_cost$r.squared,digits=3)
+results_cost$p.value <- round(results_cost$p.value,digits=3)
+results_cost$a <- round(results_cost$a,digits=2)
+results_cost$b <- round(results_cost$b,digits=2)
+results_cost
+
+Summary2 <- SummaryInd
+Summary2 <- merge(Summary2,select(results_cost, -n), by=c("species"), all=TRUE)
+
+Summary2$predict_growth <- 10^Summary2$a * Summary2$total_weight^Summary2$b
+Summary2$cost <- Summary2$predict_growth - Summary2$growth_inv
+Summary2$cost_plus_growth <- Summary2$cost + Summary2$growth_inv
+Summary2$cost_ratio <- Summary2$predict_growth / Summary2$growth_inv
+
+plot(predict_growth~growth_inv,Summary2,col=col.spp(species),pch=16,log="xy",xlim=c(10,1000000),ylim=c(10,1000000))
+abline(0,1)
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+plot(predict_growth~growth_inv,Summary2,log="xy",col=col.age(age),pch=16,xlim=c(10,1000000),ylim=c(10,1000000))
+abline(0,1)
+legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
+
+plot(cost_ratio~RA,Summary2,col=col.spp(species),pch=16,log="y",ylab="ratio of predicted growth to actual growth")
+mod <- lm(RA~log(cost_ratio),data=subset(Summary2,RA>0))
+words.bottom.left.logy(mod)
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+plot(cost_ratio~RA,Summary2,col=col.age(age),pch=16,log="y",ylab="ratio of predicted growth to actual growth")
+legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+pdf("figs2/cost_of_repro1.pdf", height=12, width=12)
+  plot
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "cost_ratio"
+xvar <- "RA"
+
+data <- subset(Summary2,RA>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  ((x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.3,
+                    main=spp,col=col.age(data[[spp]]$age))
+  }
+
+mtext("ratio of predicted growth to actual growth", 2, outer=TRUE,cex=1.2)
+mtext("RA", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "cost"
+xvar <- "repro_inv"
+
+data <- subset(Summary2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  ((x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1.3,
+                    main=spp,col=col.age(data[[spp]]$age))
+  abline(0,1)                  
+}
+
+mtext("Growth deficit (mg)", 2, outer=TRUE,cex=1.2)
+mtext("Reproductive investment (mg)", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+```
+
+####There is a much less clearcut pattern with respect to height growth - for most species height growth declines dramatically with age, overshadowing any reprodutive maturity affects  
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
-                    main=spp,col=col.mature(data[[spp]]$mature)
+                    main=spp,col=col.age(data[[spp]]$age))
 }
-#doesn't like preceding lines of text - PROBLEM
-###calc_veg <- merge(SummaryInd, select(results, -species), by="species",all.x=TRUE)
-###WORK HERE
+
+mtext("Increase in plant height (mm)", 2, outer=TRUE,cex=1.2)
+mtext("Plant height (mm)", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "growth_height"
+xvar <- "height"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
+                    main=spp,col=col.mature(data[[spp]]$mature))
+}
 
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
-                    main=spp,col=col.age(data[[spp]]$age)
+                    main=spp,col=col.age(data[[spp]]$age))
 }

### 2015-09-01 results_growth.Rmd
old script that I am slowly going through and cutting out unneeded bits

@@
 
-- For almost all species there is a strong negative relationship between RGR and RA - more reproduction = less growth  
-    1. As expected, a cost of reproduction is reduced growth
-    2. Meanwhile there is the strong positive relationship between growth investment and reproductive investment, because bigger plants grow and reproduce more.  
-    3. It is good to have a big enough data set to capture both trends across a single dataset - and to capture them consistently across many species
-
-- Many plants have a clear upturn in RA and corresponding downturn in RGR at a specific prop maxH  
-    1. e.g. see EPMI for distinct pattern
-    2. More robust curve-fitting techniques are required to better illustrate this pattern (**CURVE FITTING**)
-
-#Comparing different measures of growth and how these measures shift with age
-
-###Weight vs. height
-- No surprises here , but need to fit proper lines to the data (**CURVE FITTING**)
-- Plants asymptote in weight as they reach their maximum height. This is true for all species, although some species, like BOLE and GRBU, have a much messier scatter than others  
-- The follow on of course is to look at growth measures vs. height   
-- NOTE: The variable "prop_maxH" is "current height/maximum species height (across all sites)", hence varying from 0-1. This lets data from all species to be plotted together  
-```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.6,0.2))
-plot((total_weight~prop_maxH), SummaryInd, col=col.spp(species),pch=16,log="y")
-legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-```
-
-```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=28}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "total_weight"
-xvar <- "prop_maxH"
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",
-                    main=spp, xlab="", ylab="")
-  abline(lmfits[[spp]])
-}
-
-mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
-mtext("Total weight", 2, outer=TRUE,cex=1.2)
-```
-
-```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=28}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "growth_stem_area"
-xvar <- "RA"
-
-data <- subset(SummaryInd,RA>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",
-                    main=spp)
-  abline(lmfits[[spp]])
-}
-
-```
-
-###Growth Investment versus proportion max H
-- For the canopy species, PELA, HATE, PEPU, BAER, investment in growth plateaus (i.e. growth relative to size decreases) at ~40% maxH
-- I think this suggests that relative height is a good predictor of growth investment in these species, but not in some of the lower-growing species
-- For the shorter and shorter-lived species there is much less of a relationship, or a complete lack of relationship (i.e. BOLE, PHPH)  
-- Quite interesting, there is a distinctly negative relationship for GRBU; its absolute growth investment actually declines as it increases in size  
-- For many of the species with a good relationship, it seems that there are two breakpoints in the curve - wondering what these mean with respect to reproductive onset and RA
-
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7}
-par(mfrow=c(1,2), cex=1, omi=c(.8,0.3,.5,0.2), mai=c(.7,1,.1,0.2))
-plot((growth_inv~prop_maxH), SummaryInd, log="y", col=col.spp(species),pch=16,xlab="")
-legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-
-plot(growth_inv~prop_maxH, SummaryInd, log="y", col=col.age(age),pch=16,ylab="",xlab="")
-legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=.8,bty="n")
-mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
-```
-
-### Growth investment by Proportion Hmax
-```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=21}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "growth_inv"
-xvar <- "prop_maxH"
-data <- SummaryInd
-data <- split(data, data$species)
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="y",
-                    main=spp, xlab="",ylab="")
-}
-
-mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
-mtext("Growth investment", 2, outer=TRUE,cex=1.2)
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
-### RGR by proportion Hmax
-- Ignoring a few outliers, RGR declines with increasing height is 12 species  
-- Only in HEPU and PILI is there no significant trend  
-- The species with a poorer correlation are mostly shorter ones that are presumably often broken off   
-- These are continued ways to look at the question of how important is height (relative to the species maxH) in understanding its growth and reproduction
-
-```{r, echo=FALSE, message=FALSE, fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(RGR~prop_maxH,SummaryInd,col=col.spp(species),pch=16)
-legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-```
-
-```{r, echo=FALSE, message=FALSE, fig.width=21, fig.height=35}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.7,.5,0.2)) 
-yvar <- "RGR"
-xvar <- "prop_maxH"
-data <- SummaryInd
-data <- split(data, data$species)
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,
-                    main=spp, xlab="",ylab="")
-}
-
-mtext("proportion Hmax", 1, outer=TRUE,cex=1.2)
-mtext("RGR", 2, outer=TRUE,cex=1.2)
-
-data <- SummaryInd
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  (x[[xvar]])))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-results
-```
-
 #Comparing growth of whole plant vs. leader
-
-###Correlations between different growth measures
-- Increased cross-sectional area of a leader and the entire plant are fairly correlated and uneffected by age (once not seedlings)  
-- however, some species, such as BAER are much branchier and lower correlation
-TO DO: species should be a random effect for these stats- I want to know the effect of age on the relationship once the effect of species has been accounted for
-
-```{r, echo=FALSE,message=FALSE, fig.width=14, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(growth_shoot_area~growth_stem_area,data=subset(SummaryInd), log="xy",col=col.spp(species), pch=16, cex=.8,xlab="change in basal stem area",ylab="change in shoot area")
-legend("bottomright",col=col.spp(), legend=labels.spp(), pch=16, cex=1,bty="n")
-
-mod <- lm(growth_shoot_area~species*age*growth_stem_area,SummaryInd)
-anova(mod)
-```
 
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(shoot_leaf_count~age,data=subset(SummaryInd,age>2),log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp(species))
+plot(shoot_leaf_count~age,data=subset(SummaryInd,age>2),log="xy", xlab="age",ylab="final leaf count along shoot",col=col.spp())
 legend("bottomright",col=col.spp(), legend=labels.spp(), pch=16, cex=1,bty="n")
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp(species), pch=16, cex=0.8)
+plot(leaf_weight~total_weight,SummaryInd, log="xy",col=col.spp(), pch=16, cex=0.8)
 legend("bottomright",col=col.spp(), legend=labels.spp(), pch=16, cex=.8, bty="n")
@@
 mod <- lm(prop_maxH~growth_shoot_length,data=subset(SummaryInd,age>2))
-plot(growth_shoot_length~prop_maxH,data=subset(SummaryInd,age>2),log="y", ylab="shoot extension (mm)",col=col.spp(species),pch=16)
+plot(growth_shoot_length~prop_maxH,data=subset(SummaryInd,age>2),log="y", ylab="shoot extension (mm)",col=col.spp(),pch=16)
 legend(12,200,col=col.spp(), legend=labels.spp(), pch=16, cex=.8,bty="n")
@@
 mod <- lm(age~species*growth_shoot_length,data=subset(SummaryInd,age>2))
-plot(growth_shoot_length~age,data=subset(SummaryInd,age>2),log="xy", ylab="shoot extension (mm)",col=col.spp(species),pch=16)
+plot(growth_shoot_length~age,data=subset(SummaryInd,age>2),log="xy", ylab="shoot extension (mm)",col=col.spp(),pch=16)
 words.bottom.right.logxy(mod)
@@
 mod <- lm (growth_shoot_area ~ growth_stem_area*species*age,data=subset(SummaryInd, age>1.4))
-plot((growth_shoot_area/10000) ~ growth_stem_area,data=subset(SummaryInd, age>1.4), log="xy",col=col.age(age), pch=16)
+plot((growth_shoot_area/10000) ~ growth_stem_area,data=subset(SummaryInd, age>1.4), log="xy",col=col.age(), pch=16)
 abline(0,1)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
-plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.age(age), pch=16)
+plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.age(), pch=16)
 mod <- lm(log(total_weight)~log(leaf_area), SummaryInd)
@@
 
-plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.age(age), pch=16)
+plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.age(), pch=16)
 
-plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.spp(species), pch=16)
+plot(leaf_area~total_weight, SummaryInd,log="xy",col=col.spp(), pch=16)
 words.bottom.right.logxy(mod)
 
-plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.spp(species), pch=16)
+plot(leaf_area~prop_maxH, SummaryInd,log="y",col=col.spp(), pch=16)
 ```
@@
 par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
-plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.age(age), pch=16)
+plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.age(), pch=16)
 mod <- lm(log(total_weight)~log(leaf_weight), SummaryInd)
@@
 
-plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.age(age), pch=16)
+plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.age(), pch=16)
 
-plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.spp(species), pch=16)
+plot(leaf_weight~total_weight, SummaryInd,log="xy",col=col.spp(), pch=16)
 words.bottom.right.logxy(mod)
 
-plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.spp(species), pch=16)
+plot(leaf_weight~prop_maxH, SummaryInd,log="y",col=col.spp(), pch=16)
 ```
-
-###changes in leaf growth and area over time
-* different species have different leaf area/growth to stem weight - in particular, the "canopy species" have higher leaf area relative to their stem weight
-* all species show declines in leaf weight vs. stem weight as they age, but this is a much smaller effect than the across species effect
-```{r, echo=FALSE, message=FALSE, fig.width=14, fig.height=14}
-mod <- lm(leaf_area ~stem_weight*species*age, SummaryInd)
-anova(mod)
-
-par(mfrow=c(2,2), cex=1, omi=c(.1,.2,.1,.1), mai=c(1,1,.5,0.2)) 
-plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.age(age), pch=16,ylim=c(-1,4))
-abline(0,0)
-abline(0,1)
-legend("topleft",col=col.age, labels.age(), pch=16, cex=1, bty="n")
-
-plot((leaf_area)~(stem_weight), SummaryInd,col=col.age(age), pch=16,log="xy")
-abline(0,1)
-text(1000,1800,srt=39,labels="1:1 line")
-
-plot((RGR_leaf)~(RGR_stem), SummaryInd,col=col.spp(species), pch=16,ylim=c(-1,4),xlab="")
-abline(0,0)
-abline(0,1)
-legend("topleft",col=col.spp(), legend=labels.spp(), pch=16, cex=.9, bty="n")
-
-plot((leaf_area)~(stem_weight), SummaryInd,col=col.spp(species), pch=16,log="xy",xlab="")
-abline(0,1)
-text(1000,1800,srt=39,labels="1:1 line")
-words.bottom.right.logxy(mod)
-```
-
 ##Comparing growth rates of species with different trait values
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,1,0.6)) 
-plot(growth_inv ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age(age),pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
+plot(growth_inv ~ seed_size,data=subset(SummarySppAge,age>.5),log="xy",col=col.age(),pch=16,cex=1,xlab="seed size (mg)",ylab="growth investment (mg per year)",main="Effect of seed size on growth rates")
 legend("topleft",col=col.age, labels.age(), pch=16, cex=1,bty="n")
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+plot(growth_inv ~ maxH,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
 text(growth_inv ~ maxH, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
@@
 
-plot(growth_inv ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
+plot(growth_inv ~ maxH,data=subset(SummarySppAge,age>3),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Adults")
 text(growth_inv ~ maxH, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv ~ WD,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(growth_inv ~ WD, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv ~ WD, data=subset(SummarySppAge,age==1.4))
+plot(growth_inv ~ wood_density,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(growth_inv ~ wood_density, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv ~ wood_density, data=subset(SummarySppAge,age==1.4))
 words.bottom.left.logxy(mod)
 
-plot(growth_inv ~ WD,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(growth_inv ~ WD, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv ~ WD, data=subset(SummarySppAge,age==2.4))
+plot(growth_inv ~ wood_density,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(growth_inv ~ wood_density, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_inv ~ wood_density, data=subset(SummarySppAge,age==2.4))
 words.bottom.left.logxy(mod)
@@
 
-plot(growth_inv ~ WD,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(growth_inv ~ WD, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(growth_inv ~ WD, data=subset(SummarySppAge,age>3))
+plot(growth_inv ~ wood_density,data=subset(SummarySppAge,age>3),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_inv ~ wood_density, data=subset(SummarySppAge,age==5), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_inv ~ wood_density, data=subset(SummarySppAge,age>3))
 words.bottom.left.logxy(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(RGR ~ WD,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(RGR ~ WD, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(RGR ~ WD, data=subset(SummarySppAge,age==1.4))
+plot(RGR ~ wood_density,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(RGR ~ wood_density, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(RGR ~ wood_density, data=subset(SummarySppAge,age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(RGR ~ WD,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(RGR ~ WD, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(RGR ~ WD, data=subset(SummarySppAge,age==2.4))
+plot(RGR ~ wood_density,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(RGR ~ wood_density, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(RGR ~ wood_density, data=subset(SummarySppAge,age==2.4))
 words.bottom.right.logxy(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv ~ leaf_area,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
+plot(growth_inv ~ leaf_area,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Seedlings",ylim=c(100,50000))
 text(growth_inv ~ leaf_area, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
@@
 
-plot(growth_inv ~ leaf_area,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
+plot(growth_inv ~ leaf_area,data=subset(SummarySppAge,age>3),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Adults",ylim=c(100,1000000))
 text(growth_inv ~ leaf_area, data=subset(SummarySppAge,age==7), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv ~ LMA,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+plot(growth_inv ~ LMA,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
 text(growth_inv ~ LMA, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
@@
 
-plot(growth_inv ~ LMA,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
+plot(growth_inv ~ LMA,data=subset(SummarySppAge,age>3),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Adults")
 text(growth_inv ~ LMA, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
@@
 
-plot(growth_inv ~ LMA,data=subset(SummarySppAge,age>3&species!="HATE"),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
+plot(growth_inv ~ LMA,data=subset(SummarySppAge,age>3&species!="HATE"),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Adults")
 text(growth_inv ~ LMA, data=subset(SummarySppAge,age>3&species!="HATE"), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
@@
 
-###Leaf lifespan vs growth investment
-- There is no relationship between leaf lifespan and growth investment for any age group
-- And just barely a significant relationship between RGR and leaflifespan for adult plants
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2))
-plot(growth_inv ~ LL_death,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(growth_inv ~ LL_death, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(log(LL_death)~log(growth_inv), data=subset(SummarySppAge,age==1.4))
-words.bottom.right.logxy(mod)
+* another of the interesting pattern is that the increase in shoot area of leaders is correlated with maxH and seed_size (and opposite wood_density) and somewhat offset from whole plant growth measures and whole plant size measures
+* seed_size removed, because no additional explanatory power after wood_density and maxH included
 
-plot(growth_inv ~ LL_death,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(growth_inv ~ LL_death, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv ~ LL_death, data=subset(SummarySppAge,age==2.4))
-words.bottom.right.logxy(mod)
-
-plot(growth_inv ~ LL_death,data=subset(SummarySppAge,age>3),log="xy",col=col.age(age),pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(growth_inv ~ LL_death, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(growth_inv ~ LL_death, data=subset(SummarySppAge,age>3))
-legend("topright",col=col.age,labels.age(),pch=16, bty="n")
-words.bottom.right.logxy(mod)
-
-mtext("leaf lifespan",1,outer=TRUE)
-mtext("yearly growth (mg)",2,outer=TRUE)
-```
-
-###PCA analysis
-* This combination of variables shows that RGR is approximately opposite a collection of variables that indicate a plant is "bigger" - so smaller plants have higher RGR
-* Orthoganal to these in WD vs.
-maxH, LMA, seed_size, and shoot_growth - species that are taller as adults have bigger seeds, higher LMA, and greater shoot growth (both stem growth & leaf count), independent of their current (age dependent) size
-* this analysis doesn't include accessory proportions, because then I have to use subset of reproducing individuals - see below - greatly reducing sample size
-* fine tuning:  
-  ** remove RGR leaf (similar to RGR)
-  ** remove prop_max_weight and prop_max_repro (similar to prop_maxH)
-
-```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-SummaryIndPCA <- SummaryInd %>%
-  filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
-  select(prop_maxH,height,maxH,WD,LMA,seed_size,growth_leaf,
-         RGR,leaf_area,growth_shoot_area,growth_stem_area,shoot_leaf_count,total_weight,
-         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area)
-
-SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
-SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
-SummaryIndPCA$height <- log(SummaryIndPCA$height)
-SummaryIndPCA$maxH <- log(SummaryIndPCA$maxH)
-SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
-SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
-SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
-SummaryIndPCA$growth_shoot_area <- log(SummaryIndPCA$growth_shoot_area)
-SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
-SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
-SummaryIndPCA$shoot_leaf_count <- log(SummaryIndPCA$shoot_leaf_count)
-SummaryIndPCA$growth_stem_area <- log(SummaryIndPCA$growth_stem_area)
-SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
-SummaryIndPCA$shoot_growth_leaf_area <- log(SummaryIndPCA$shoot_growth_leaf_area)
-
-PCA_mod <- prcomp(SummaryIndPCA, scale=TRUE)
-summary(PCA_mod)
-biplot(PCA_mod,xlim=c(-.1,.15),ylim=c(-.1,.1),cex=.8)
-
-PCA_loadings <- as.data.frame(PCA_mod$rotation)
-PCA_loadings$variables <- row.names(PCA_loadings)
-
-PCA_scaling <- as.data.frame(PCA_mod$scale)
-PCA_scaling$variables <- row.names(PCA_scaling)
-names(PCA_scaling) <- c("scale","variables")
-PCA_loadings <- merge(PCA_loadings,PCA_scaling,by="variables")
-
-PCA_lambda <- as.data.frame(PCA_mod$sdev)
-
-PCA_scores <- as.data.frame(PCA_mod$x)
-PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$shoot_leaf_count>0&SummaryInd$shoot_growth_leaf_area!=0)
-SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)
-
-n <- NROW(PCA_scores)
-scale =1
-
-PCA_lambda <- PCA_lambda*sqrt(n)
-PCA_lambda <- PCA_lambda^scale
-
-SummaryInd_PCA_results$PC1_scale <- SummaryInd_PCA_results$PC1/PCA_lambda[1]
-SummaryInd_PCA_results$PC2_scale <- SummaryInd_PCA_results$PC2/PCA_lambda[2]
-SummaryInd_PCA_results$PC3_scale <- SummaryInd_PCA_results$PC3/PCA_lambda[3]
-SummaryInd_PCA_results$PC4_scale <- SummaryInd_PCA_results$PC4/PCA_lambda[4]
-PCA_loadings$PC1_scale <- PCA_loadings$PC1 / 4.5
-PCA_loadings$PC2_scale <- PCA_loadings$PC2 / 4.5
-PCA_loadings$PC3_scale <- PCA_loadings$PC3 / 4.5
-PCA_loadings$PC4_scale <- PCA_loadings$PC4 / 4.5
-```
-
-#Looking at PCA by species
-* Main axes are (1) across species affects in trait values (PC1) and (2) within species shifts in RGR vs RA with plant size/age (PC2)
-* PC1 is WD vs a whole collection of traits that have higher "values" in plants that are larger as adults, including measures of size, height, and growth increment; PELA is a rare exception in shifting along this axis.
-* PC2 most strongly separates RGR from RA (and a collection of strongly correlated traits, such as propagule investment, prop maxH). 
-* PC3 primarily separates LMA and maxH from WD; high wood density is also somewhat associated with higher RGR and various shoot growth and leafiness measures, reflecting that younger individuals have more shoot growth and higher RGR
-* PC4 is effectively leaf count on shoots ("shoot_leaf_count") and seed set vs.
-seed size, shoot leaf area and shoot leaf area growth - to first order, some plants have lots of small leaves and others have fewer leaves but greater leaf area, Not sure how seed size fits in
-
-* amazing that RA and RGR almost completely orthoganal to PC1 and PC4; To reiterate, RA and RGR are 2 variables that shift across each species' lifetime and much less across species.
-I suspect the inter-specific difference are effectively what proportion of individuals in this study are reproductively mature - with early maturing species having overall higher RA and lower RGR (i.e.
-BOLE) than do late maturing species (i.e.
-PELA).
-
-* Continuing, RGR and RA are measures that give little insight to a species trait values - or vice versa, trait values do not provide much information about RA...
-
-* "growth_stem_area" and "growth leaf", two whole plant measures of size increase are orthoganal to RGR, while some shoot-level variables (i.e.
-"growth_shoot_area") and other whole plant variables (e.g.
-"growth_leaf_area"), are somewhat correlated with both RGR (PC2) and the "maxH" direction (PC1).
-I suppose this suggests that for plants with high
-
-* For PC2, interesting that "growth_shoot_area"" and other variables associated with shoot growth and species max H correlate somewhat with RGR, but "growth_stem_area" and other whole plant "size" variables do not
-* these plots are another way of affirming that RA (and RGR) is a variable that does a good job of comparing trends across species * in other words there is a trade-off between RA and RGR in all species.
-And even though the RA trends are messy, individuals that are proportionally taller (prop_maxH) or invest more in reproduction (investment, count, or seedset) have a higher RA.
-
-* this last set of variables are all ones that do not vary with the PC1 axis
-
-PCA related code to keep:  
-* plot(PCA_mod)
-* pairs(SummaryIndPCA,log="xy")
-* yy <- t(t(PCA_loadings[,2:3])*PCA_lambda[1:2])
-* xx <- t(t(SummaryInd_PCA_results[,105:106])/PCA_lambda[1:2])
-* biplot(xx,yy)
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-
-PCA_by_species <- SummaryInd_PCA_results %>%
-  filter(shoot_leaf_count>0) %>%
-  group_by(species) %>%
-  summarise_each(funs(mean, se), PC1_scale, PC2_scale, PC3_scale, PC4_scale)
-
-plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species),xlim=c(-.1,.1))
-arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-
-mean1 <- PCA_by_species$PC1_scale
-se1 <- PCA_by_species$PC1_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 1")
-se_function(mean1,se1)
-
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species))
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-mean1 <- PCA_by_species$PC2_scale
-se1 <- PCA_by_species$PC2_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 2")
-se_function(mean1,se1)
-
-plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species))
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-mean1 <- PCA_by_species$PC3_scale
-se1 <- PCA_by_species$PC3_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 3")
-se_function(mean1,se1)
-
-plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species),ylim=c(-.15,.15))
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-
-mean1 <- PCA_by_species$PC4_scale
-se1 <- PCA_by_species$PC4_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",,ylim=c(-.07,.04))
-se_function(mean1,se1)
-```
-
-###Coloring data by age
-* this confirms that PC2 is an axis the changes primarly by age - it is the RGR vs reproduction shift
-* PC1 has a slight age component, but more about species - across species, plant size is mostly a species effect, but of course age also matters
-* PC3 & PC4 all about species
-
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age(age)
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-
-plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.age(age)
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.age(age),ylim=c(-.15,.12))
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-plot(PC3_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.age(age)
-arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC3_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-```
-
-### Looking only at reproducing individuals - 
-* can now add in "prop_propagule","prop_accessory", but not "accessory_per_seed"
-* changes patterns quite a bit
-* PC1 is still WD vs lots of growth variables, but now absolute measures of reproductive investment (propagule_inv and accessory_inv) associate with absolute "big size" not high RA
-* PC2 is RA, seedset, and prop_propagule vs. RGR, shoot growth variables and prop_accessory; not surprising that prop_propagule and prop_accessory pulled to opposite ends
-* PC3 is somewhat similar. It is also prop_accessory and prop_maxH vs seed set and prop_propagule, but it now separates out all the shoot growth values
-* PC4 is now the axis that separates LMA and maxH vs. WD, with variables like maxH pulling toward all the "big size" arrows
-
-```{r, echo=FALSE,message=FALSE,fig.width=7, fig.height=7}
-par(mfrow=c(1,1), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-SummaryIndPCA <- SummaryInd %>%
-  filter(shoot_leaf_count>0&accessory_inv>0&shoot_growth_leaf_area!=0) %>%
-  select(prop_maxH,height,maxH,WD,LMA,seed_size,growth_leaf,
-         RGR,leaf_area,growth_shoot_area,growth_stem_area,shoot_leaf_count,total_weight,
-         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area,
-         prop_propagule, prop_accessory)
-
-SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
-SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
-SummaryIndPCA$height <- log(SummaryIndPCA$height)
-SummaryIndPCA$maxH <- log(SummaryIndPCA$maxH)
-SummaryIndPCA$seed_size <- log(SummaryIndPCA$seed_size)
-SummaryIndPCA$accessory_inv <- log(SummaryIndPCA$accessory_inv+.001)
-SummaryIndPCA$propagule_inv <- log(SummaryIndPCA$propagule_inv+.001)
-SummaryIndPCA$growth_shoot_area <- log(SummaryIndPCA$growth_shoot_area)
-SummaryIndPCA$growth_leaf <- log(SummaryIndPCA$growth_leaf+10000)
-SummaryIndPCA$repro_all_count <- log(SummaryIndPCA$repro_all_count+1)
-SummaryIndPCA$shoot_leaf_count <- log(SummaryIndPCA$shoot_leaf_count)
-SummaryIndPCA$growth_stem_area <- log(SummaryIndPCA$growth_stem_area)
-SummaryIndPCA$shoot_leaf_area <- log(SummaryIndPCA$shoot_leaf_area)
-SummaryIndPCA$shoot_growth_leaf_area <- log(SummaryIndPCA$shoot_growth_leaf_area)
-
-PCA_mod <- prcomp(SummaryIndPCA, scale=TRUE)
-summary(PCA_mod)
-biplot(PCA_mod)
-
-PCA_loadings <- as.data.frame(PCA_mod$rotation)
-PCA_loadings$variables <- row.names(PCA_loadings)
-
-PCA_scaling <- as.data.frame(PCA_mod$scale)
-PCA_scaling$variables <- row.names(PCA_scaling)
-names(PCA_scaling) <- c("scale","variables")
-PCA_loadings <- merge(PCA_loadings,PCA_scaling,by="variables")
-
-PCA_lambda <- as.data.frame(PCA_mod$sdev)
-
-PCA_scores <- as.data.frame(PCA_mod$x)
-PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$shoot_leaf_count>0&SummaryInd$shoot_growth_leaf_area!=0&SummaryInd$accessory_inv>0)
-SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)
-
-n <- NROW(PCA_scores)
-scale =1
-
-PCA_lambda <- PCA_lambda*sqrt(n)
-PCA_lambda <- PCA_lambda^scale
-
-SummaryInd_PCA_results$PC1_scale <- SummaryInd_PCA_results$PC1/PCA_lambda[1]
-SummaryInd_PCA_results$PC2_scale <- SummaryInd_PCA_results$PC2/PCA_lambda[2]
-SummaryInd_PCA_results$PC3_scale <- SummaryInd_PCA_results$PC3/PCA_lambda[3]
-SummaryInd_PCA_results$PC4_scale <- SummaryInd_PCA_results$PC4/PCA_lambda[4]
-PCA_loadings$PC1_scale <- PCA_loadings$PC1 / 4.5
-PCA_loadings$PC2_scale <- PCA_loadings$PC2 / 4.5
-PCA_loadings$PC3_scale <- PCA_loadings$PC3 / 4.5
-PCA_loadings$PC4_scale <- PCA_loadings$PC4 / 4.5
-```
-
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=14}
-par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species))
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC2_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-
-plot(PC3_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species))
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC3_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species),ylim=c(-.15,.12))
-arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC4_scale ~ PC1_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-
-plot(PC3_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species))
-arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC3_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
-text(PC3_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-```
-
-comparing
-```{r, echo=FALSE,message=FALSE}
-mod <- lm(RGR~species+asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1),SummaryInd)
-anova(mod)
-glance(mod)[1]
-
-mod <- lm(RGR~asin(sqrt(RA))+prop_maxH+log(propagule_inv+1)+log(accessory_inv+1)+log(total_weight)+log(repro_all_count+1)+WD+LMA+maxH,SummaryInd)
-anova(mod)
-glance(mod)[1]
-```
-
-* another of the interesting pattern is that the increase in shoot area of leaders is correlated with maxH and seed_size (and opposite WD) and somewhat offset from whole plant growth measures and whole plant size measures
-* seed_size removed, because no additional explanatory power after WD and maxH included
-
-```{r, echo=FALSE,message=FALSE}
-mod <- lm(log(growth_shoot_area)~log(maxH)+WD+log(growth_stem_area)+log(total_weight)+RGR+asin(sqrt(RA))+LMA,SummaryInd)
-anova(mod)
-glance(mod)
-```
-
-plot(mod)
 ###Traits correlated
@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(1.1,1,.6,0.2))
-plot(WD~maxH,SummarySpp[["mean"]], log="x",col=col.spp(species),pch=16)
-mod <- lm(log(maxH)~WD,SummaryInd)
+plot(wood_density~maxH,SummarySpp[["mean"]], log="x",col=col.spp(),pch=16)
+mod <- lm(log(maxH)~wood_density,SummaryInd)
 words.bottom.left.logx(mod)
 
-plot(WD~maxH,data=subset(SummarySpp[["mean"]],species!="PUTU"&species!="PHPH"), log="x",col=col.spp(species),pch=16)
-mod <- lm(log(maxH)~WD,data=subset(SummarySpp[["mean"]],species!="PUTU"&species!="PHPH"))
+plot(wood_density~maxH,data=subset(SummarySpp[["mean"]],species!="PUTU"&species!="PHPH"), log="x",col=col.spp(),pch=16)
+mod <- lm(log(maxH)~wood_density,data=subset(SummarySpp[["mean"]],species!="PUTU"&species!="PHPH"))
 words.bottom.left.logx(mod)
 
-plot(seedset~total_weight,SummarySpp[["mean"]], log="x",col=col.spp(species),pch=16)
+plot(seedset~total_weight,SummarySpp[["mean"]], log="x",col=col.spp(),pch=16)
 mod <- lm(log(total_weight) ~ (seedset),SummarySpp[["mean"]])
@@
 
-plot(seedset~maxH,SummarySpp[["mean"]], log="x",col=col.spp(species),pch=16)
+plot(seedset~maxH,SummarySpp[["mean"]], log="x",col=col.spp(),pch=16)
 mod <- lm(log(maxH) ~ (seedset),SummarySpp[["mean"]])

### 2015-09-01 Growth_figs.rmd
Tidy up use of remake and functions
Continued little fixes to main files (Growth_figs, RA_figs) - they now run in Knitr again
Some additional work in RA_figs, incorporating what we talked about in lab meeting last Thursday

@@
-```{r, echo=FALSE,results='hide', message=FALSE,warning=FALSE}
-library(remake)
-create_bindings()
+```{r,message=FALSE,warning=FALSE, echo=FALSE}
+remake::make("export")
 
-source("scripts/functions.R")
+SummaryInd <- readRDS("export/SummaryInd.rds")
+SummarySpp <- readRDS("export/SummarySpp.rds")
+SummarySppAge <- readRDS("export/SummarySppAge.rds")
+
+source("R/figures.R")
 ```
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.mature(data[[spp]]$mature)
+                    main=spp,col=col.mature(data[[spp]]$mature))
 }
@@
 yvar <- "growth_leaf"
-xvar <- "total_weight"
+xvar <- "total_weight_0"
+
+data <- subset(SummaryInd,growth_leaf>0)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+
+mtext("Investment in leaves (mg)", 2, outer=TRUE,cex=1.2)
+mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
+legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "growth_stem"
+xvar <- "total_weight_0"
 
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
-                    main=spp,col=col.age(data[[spp]]$age)
-}
-
-mtext("Investment in leaves (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
-legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
-```
-
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "growth_stem"
-xvar <- "total_weight"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
-                    main=spp,col=col.age(data[[spp]]$age)
+                    main=spp,col=col.age(data[[spp]]$age))
 }
@@
 mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
-legend("bottomright",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
+mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
+legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 ```
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age(data[[spp]]$age)
-  abline(0,1)
+                    main=spp,col=col.age(data[[spp]]$age))
 }
@@
 mtext("increase in shoot diameter (mm)", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=0.9,bty="n")
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=0.9,bty="n")
 ```
@@
 * Very different, patterns across species
+* Overall, the earlier successional species show a stronger correlation (BOLE, COER, HEPU, PHPH, GRSP) suggesting what is happening at the shoot level matters more to these species
 
@@
 par(mfrow=c(1,2), cex=1, omi=c(0.2,0.3,0.3,0.3), mai=c(1.1,1,0.3,0.3)) 
-plot(LL_death~shoot_leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
-mod <- lm(log(shoot_leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
+plot(LL_death~shoot_leaf_area_0,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
+mod <- lm(log(shoot_leaf_area_0)~LL_death,data=subset(SummaryInd,LL_death<6&shoot_leaf_area_0>0))
 words.top.right.logx(mod)
 
-plot(LL_death~leaf_area,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
-mod <- lm(log(leaf_area)~LL_death,data=subset(SummaryInd,LL_death<6))
+plot(LL_death~leaf_area_0,data=subset(SummaryInd,LL_death<6),log="x",pch=16,col=col.spp(species))
+mod <- lm(log(leaf_area_0)~LL_death,data=subset(SummaryInd,LL_death<6))
 words.top.right.logx(mod)
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age(data[[spp]]$age)
+                    main=spp,col=col.age(data[[spp]]$age))
 }
@@
 mtext("shoot leaf area", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 ```
@@
 yvar <- "LL_death"
-xvar <- "leaf_area"
+xvar <- "leaf_area_0"
 
@@
 mtext("ll death", 2, outer=TRUE,cex=1.2)
-mtext("leaf area", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
+mtext("initial leaf area", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 
 yvar <- "LL_death"
-xvar <- "leaf_area"
+xvar <- "leaf_area_0"
 
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age(data[[spp]]$age)
+                    main=spp,col=col.age(data[[spp]]$age))
 }
@@
 mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 ```
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "growth_leaf_area"
+yvar <- "growth_leaf_area_log"
+xvar <- "prop_maxH"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1.4,
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+
+mtext("increase in leaf area (log(LA_final)-log(LA_initial))", 2, outer=TRUE,cex=1.2)
+mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "total_weight_0"
 xvar <- "prop_maxH"
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age(data[[spp]]$age)
+                    main=spp,col=col.age(data[[spp]]$age))
 }
 
-mtext("increase in leaf area", 2, outer=TRUE,cex=1.2)
+mtext("initial size", 2, outer=TRUE,cex=1.2)
 mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 ```
+
+###RSOM: species differ in how much they increase in height after the onset of reproduction.   
+  * Late reproducing, taller species increase less in height after the onset of reproduction
 
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "total_weight"
+yvar <- "total_weight_0"
 xvar <- "prop_maxH"
@@
   plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age(data[[spp]]$age)
+                    main=spp,col=col.mature(data[[spp]]$mature))
 }
 
-mtext("total size", 2, outer=TRUE,cex=1.2)
-mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
-```
-
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "total_weight"
-xvar <- "prop_maxH"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.mature(data[[spp]]$mature)
-}
-
-mtext("total size", 2, outer=TRUE,cex=1.2)
+mtext("intial size", 2, outer=TRUE,cex=1.2)
 mtext("prop_maxH", 1, outer=TRUE,cex=1.2)
@@
 
-plot(wood_density~growth_leaf_area,SummaryInd,log="y",pch=16,col=col.age(age)
+plot(wood_density~growth_leaf_area,SummaryInd,log="y",pch=16,col=col.age())
 mod <- lm(log(growth_leaf_area)~age*wood_density,SummaryInd)

### 2015-09-01 RA_figs.rmd
Continued little fixes to main files (Growth_figs, RA_figs) - they now run in Knitr again
Some additional work in RA_figs, incorporating what we talked about in lab meeting last Thursday

@@
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
+remake::make("export")
+
+SummaryInd <- readRDS("export/SummaryInd.rds")
+SummarySpp <- readRDS("export/SummarySpp.rds")
+SummarySppAge <- readRDS("export/SummarySppAge.rds")
+
+source("R/figures.R")
+```
+
 ##Summary  
@@
 yvar <- "repro_inv"
-xvar <- "total_weight"
+xvar <- "total_weight_0"
 
@@
 mtext("Reproductive investment (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
 legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
@@
 ###Vegetative invesment by size curves by species, only including reproducing individuals  
-* colored by age, but legend not correct, because "age 1" color used for youngest age with reproducing individuals
+* colored by age
 
@@
 yvar <- "growth_inv"
-xvar <- "total_weight"
+xvar <- "total_weight_0"
 
@@
 mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
 legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
@@
 mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
+mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
 legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "growth_inv"
+xvar <- "leaf_area_0"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+
+mtext("Vegetative investment (mg)", 2, outer=TRUE,cex=1.2)
+mtext("Initial leaf area", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "repro_inv"
+xvar <- "leaf_area_0"
+
+data <- subset(SummaryInd,repro_inv>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+
+mtext("Reproductive investment (mg)", 2, outer=TRUE,cex=1.2)
+mtext("Initial leaf area", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "total_inv"
+xvar <- "leaf_area_0"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+
+mtext("Total investment (mg)", 2, outer=TRUE,cex=1.2)
+mtext("Initial leaf area", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=15, fig.height=15}
+par(mfcol=c(3,3), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,1,.4,0.2)) 
+yvar <- "growth_inv"
+xvar <- "leaf_area_0"
+
+yvar2 <- "repro_inv"
+xvar2 <- "leaf_area_0"
+
+yvar3 <- "total_inv"
+xvar3 <- "leaf_area_0"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar3_vs_xvar3(data[[spp]], yvar3, xvar3,log="xy",xlab="",ylab="total invest (mg)",cex=1.3,
+                    main=spp,col=col.age(data[[spp]]$age))
+  arrows(data[[spp]]$leaf_area_0,data[[spp]]$growth_inv,data[[spp]]$leaf_area_0,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="veg invest (mg)",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  plot_yvar2_vs_xvar2(data[[spp]], yvar2, xvar2,log="xy",xlab="",ylab="repro invest (mg)",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  #points(data[[spp]]$leaf_area_0,data[[spp]]$growth_inv,pch=1,cex=.8,col=col.age(data[[spp]]$age))
+}
+
+mtext("Initial leaf area", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 ```
@@
 ###Calculating cost of reproduction as a growth deficit
+    * despite having a clause to subset SummaryInd,
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7}
-pdf("figs2/cost_of_repro1.pdf", height=12, width=12)
-  plot
 par(mfrow=c(1,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
@@
 
-data <- subset(SummaryInd,repro_inv=0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+data_RA0 <- subset(SummaryInd,repro_inv==0&species!="BOLE")
+data_RA0 <- split(data_RA0, data_RA0$species)
+lmfits <- lapply(data_RA0, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
 results_cost <- summarise_all_fits(lmfits)
@@
 
-plot(cost_ratio~RA,Summary2,col=col.spp(species),pch=16,log="y",ylab="ratio of predicted growth to actual growth")
-mod <- lm(RA~log(cost_ratio),data=subset(Summary2,RA>0))
-words.bottom.left.logy(mod)
+plot(cost_ratio~repro_inv,Summary2,col=col.spp(species),pch=16,log="xy",ylab="ratio of predicted growth to actual growth")
+mod <- lm(log(repro_inv)~log(cost_ratio),data=subset(Summary2,RA>0))
+words.bottom.left.logxy(mod)
 legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-plot(cost_ratio~RA,Summary2,col=col.age(age),pch=16,log="y",ylab="ratio of predicted growth to actual growth")
+plot(cost_ratio~repro_inv,Summary2,col=col.age(age),pch=16,log="xy",ylab="ratio of predicted growth to actual growth")
 legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
-dev.off()
-```
-
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-pdf("figs2/cost_of_repro1.pdf", height=12, width=12)
-  plot
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "cost_ratio"
-xvar <- "RA"
-
-data <- subset(Summary2,RA>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  ((x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.3,
-                    main=spp,col=col.age(data[[spp]]$age))
-  }
-
-mtext("ratio of predicted growth to actual growth", 2, outer=TRUE,cex=1.2)
-mtext("RA", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
-dev.off()
 ```
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "cost"
+yvar <- "cost_ratio"
 xvar <- "repro_inv"
 
-data <- subset(Summary2)
+data <- subset(Summary2,species!="BOLE")
 data <- split(data, data$species)
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1.3,
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.3,
                     main=spp,col=col.age(data[[spp]]$age))              
-  abline(0,1)                  
 }
@@
 yvar <- "growth_height"
-xvar <- "height"
+xvar <- "height_0"
 
-data <- subset(SummaryInd)
+data <- subset(SummaryInd,growth_height>0)
 data <- split(data, data$species)
@@
 mtext("Increase in plant height (mm)", 2, outer=TRUE,cex=1.2)
-mtext("Plant height (mm)", 1, outer=TRUE,cex=1.2)
+mtext("Initial plant height (mm)", 1, outer=TRUE,cex=1.2)
 legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
@@
 mtext("Increase in plant height (mm)", 2, outer=TRUE,cex=1.2)
-mtext("Plant height (mm)", 1, outer=TRUE,cex=1.2)
+mtext("Initial plant height (mm)", 1, outer=TRUE,cex=1.2)
 legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
@@
 mtext("RA", 2, outer=TRUE,cex=1.2)  
-legend("bottomleft",legend=labels.age(),col=col.age,pch=16, cex=1.1,bty="n")
+legend("bottomleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 ```
@@
 plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
-                        main=spp,col=col.age(data[[spp]]$age)
+                        main=spp,col=col.age(data[[spp]]$age))
 }
@@
   filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
-  select(prop_maxH,height,maxH,wood_density,LMA,seed_size,growth_leaf,
-         growth_stem_diameter,leaf_area,growth_shoot_diameter,growth_stem_area,shoot_leaf_count,total_weight,
+  select(prop_maxH,height_0,maxH,wood_density,LMA,seed_size,growth_leaf, growth_height,
+         growth_stem_diameter,leaf_area_0,growth_shoot_diameter,growth_stem_area,shoot_leaf_count,total_weight_0,
          RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area,scaled_growth_stem_diameter)
 
-SummaryIndPCA$leaf_area <- log((SummaryIndPCA$leaf_area)+.001)
-SummaryIndPCA$total_weight <- log(SummaryIndPCA$total_weight)
-SummaryIndPCA$height <- log(SummaryIndPCA$height)
+SummaryIndPCA$leaf_area_0 <- log((SummaryIndPCA$leaf_area_0)+.001)
+SummaryIndPCA$total_weight_0 <- log(SummaryIndPCA$total_weight_0)
+SummaryIndPCA$height_0 <- log(SummaryIndPCA$height_0)
 SummaryIndPCA$maxH <- log(SummaryIndPCA$maxH)
@@
 SummaryIndPCA$RA <- asin(sqrt(SummaryIndPCA$RA))
+
+  for(v in c("repro_all_count")) {
+    i <- is.na(SummaryIndPCA[[v]])
+    SummaryIndPCA[[v]][i] <- 0
+  }
 
@@
 PCA_scores <- as.data.frame(PCA_mod$x)
-PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$shoot_leaf_count>0&SummaryInd$shoot_growth_leaf_area!=0)
+PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$shoot_leaf_count>0&SummaryInd$shoot_growth_leaf_area!=0,SummaryInd$shoot_leaf_area>0)
 SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)
@@
 
-plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species),xlim=c(-.1,.1))
+plot(PC1_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species),xlim=c(-.1,.1))
 arrows(0, 0, (.8*PCA_loadings$PC2_scale), (.8*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-mean1 <- PCA_by_species$PC1_scale
+mean1 <- PCA_by_species$PC1_scale_mean
 se1 <- PCA_by_species$PC1_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 1")
+boxplot(PC1_scale_mean~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 1")
 se_function(mean1,se1)
@@
 
-plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.age(age)
+plot(PC1_scale~PC2_scale,SummaryInd_PCA_results,pch=16,col=col.age(age))
 arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
 text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
-legend("topright",legend=labels.age(),col=col.age,pch=16, cex=.8,bty="n")
+legend("topright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
 
-mean1 <- PCA_by_age$PC1_scale
+mean1 <- PCA_by_age$PC1_scale_mean
 se1 <- PCA_by_age$PC1_scale_se
-plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 1")
+boxplot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 1")
 se_function(mean1,se1)
@@
 
-mean1 <- PCA_by_species$PC2_scale
+mean1 <- PCA_by_species$PC2_scale_mean
 se1 <- PCA_by_species$PC2_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 2")
+boxplot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 2")
 se_function(mean1,se1)
@@
 
-plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age(age)
+plot(PC2_scale~(PC1_scale),SummaryInd_PCA_results,pch=16,col=col.age(age))
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC2_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
@@
 
-mean1 <- PCA_by_age$PC2_scale
+mean1 <- PCA_by_age$PC2_scale_mean
 se1 <- PCA_by_age$PC2_scale_se
-plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
+boxplot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
 se_function(mean1,se1)
@@
 
-mean1 <- PCA_by_species$PC3_scale
+mean1 <- PCA_by_species$PC3_scale_mean
 se1 <- PCA_by_species$PC3_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 3")
+boxplot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 3")
 se_function(mean1,se1)
@@
 
-mean1 <- PCA_by_age$PC3_scale
+mean1 <- PCA_by_age$PC3_scale_mean
 se1 <- PCA_by_age$PC3_scale_se
-plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
+boxplot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
 se_function(mean1,se1)
@@
 
-mean1 <- PCA_by_species$PC4_scale
+mean1 <- PCA_by_species$PC4_scale_mean
 se1 <- PCA_by_species$PC4_scale_se
-plot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",ylim=c(-.05,.06))
+boxplot(mean1~species,PCA_by_species,cex.axis=.5,pch=16,ylab="PCA axis 4",ylim=c(-.05,.06))
 se_function(mean1,se1)
@@
 
-mean1 <- PCA_by_age$PC4_scale
+mean1 <- PCA_by_age$PC4_scale_mean
 se1 <- PCA_by_age$PC4_scale_se
-plot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
+boxplot(mean1~as.factor(age),PCA_by_age,cex.axis=.5,pch=16,ylab="PCA axis 2")
 se_function(mean1,se1)

### 2015-09-02 RA_combined_plots.Rmd
created new file with some large plots, looking at different combinations of variables for each species

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7.5}
remake::make("export")

SummaryInd <- readRDS("export/SummaryInd.rds")
SummarySpp <- readRDS("export/SummarySpp.rds")
SummarySppAge <- readRDS("export/SummarySppAge.rds")

source("R/figures.R")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
par(mfcol=c(4,3), cex=1, omi=c(.8,.3,.3,.1), mai=c(.5,1,.1,0.1)) 
yvar <- "growth_inv"
yvar2 <- "repro_inv"
yvar3 <- "total_inv"
yvar4 <- "RA"
xvar <- "leaf_area_0"
xvar2 <- "total_weight_0"
xvar3 <- "prop_maxH"

data <- subset(SummaryInd)
data <- split(data, data$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="veg investment",cex=1.3,
                    col=col.age(data[[spp]]$age))
  legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1,bty="n")
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="xy",xlab="",ylab="repro investment",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="total investment (mg)",cex=1.3,
                    col=col.age(data[[spp]]$age))
  arrows(data[[spp]]$leaf_area_0,data[[spp]]$growth_inv,data[[spp]]$leaf_area_0,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="x",xlab="initial leaf area",ylab="RA",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab=spp,ylab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="xy",xlab="",ylab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar2,log="xy",xlab="",ylab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  arrows(data[[spp]]$total_weight_0,data[[spp]]$growth_inv,data[[spp]]$total_weight_0,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="initial plant weight",ylab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar3,log="y",xlab="",ylab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar3,log="y",xlab="",ylab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar3,log="y",xlab="",ylab="",cex=1.3,
                   col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar3,log="",xlab="prop maxH",ylab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  mtext("Initial leaf area                                                                            initial plant weight                                                                                    prop maxH", 1, line=1,outer=TRUE,cex=1.2)
  mtext(spp, 3, outer=TRUE,cex=1.2)   
}
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
par(mfcol=c(4,3), cex=1, omi=c(.8,.3,.3,.1), mai=c(.5,1,.1,0.1)) 
SummaryInd$repro_inv_log <- SummaryInd$repro_inv + 10
yvar <- "growth_height_log"
yvar2 <- "growth_leaf_area_log"
yvar3 <- "shoot_leaf_area"
yvar4 <- "RA"
xvar <- "repro_inv_log"
xvar2 <- "total_weight_0"
xvar3 <- "prop_maxH"

data <- subset(SummaryInd)
data <- split(data, data$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="height increase (log-log)",cex=1.3, col=col.age(data[[spp]]$age))
  legend("topright",legend=labels.age(),col=col.age(),pch=16, cex=1,bty="n")
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="x",xlab="",ylab="total leaf area increase (log-log)",cex=1.3,col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="increase in shoot leaf area",cex=1.3, col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="x",xlab="reproductive investment",ylab="RA",cex=1.3,col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="x",xlab=spp,ylab="",cex=1.3, col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="x",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar2,log="xy",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="initial plant weight",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar3,log="",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar3,log="",xlab="",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar3,log="y",xlab="",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar3,log="",xlab="prop maxH",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
  mtext("Initial leaf area                                                                            initial plant weight                                                                                    prop maxH", 1, line=1,outer=TRUE,cex=1.2)
  mtext(spp, 3, outer=TRUE,cex=1.2)   
}
```

### 2015-09-02 RA_figs.rmd
created new file with some large plots, looking at different combinations of variables for each species

@@
 results$b <- round(results$b,digits=2)
-results
+results$yvar <- "growth_inv"
+results$xvar <- "total_weight_0"
+results$data <- "SummaryInd"
+results$model <- "log10(yvar)~log10(xvar)"
+saved_results <- as.data.frame(results)
+results[1:6]
 
@@
 results$b <- round(results$b,digits=2)
+results$yvar <- "growth_inv"
+results$xvar <- "leaf_area_0"
+results$data <- "SummaryInd"
+results$model <- "log10(yvar)~log10(xvar)"
+saved_results <- bind_rows(saved_results,results)
 results

### 2015-09-02 RA_combined_plots.Rmd
amendment to previous commit

@@
   plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="x",xlab="",ylab="total leaf area increase (log-log)",cex=1.3,col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="increase in shoot leaf area",cex=1.3, col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="total shoot leaf area",cex=1.3, col=col.age(data[[spp]]$age))
   plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="x",xlab="reproductive investment",ylab="RA",cex=1.3,col=col.age(data[[spp]]$age))
@@
   plot_yvar_vs_xvar(data[[spp]], yvar4, xvar3,log="",xlab="prop maxH",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
-  mtext("Initial leaf area                                                                            initial plant weight                                                                                    prop maxH", 1, line=1,outer=TRUE,cex=1.2)
+  mtext("Reproductive investment (mg)                                                                            initial plant weight                                                                                    prop maxH", 1, line=1,outer=TRUE,cex=1.2)
   mtext(spp, 3, outer=TRUE,cex=1.2)   

### 2015-09-02 RA_figs.rmd
amendment to previous commit

@@
 yvar <- "RA"
-xvar <- "prop_maxH"
+xvar <- "leaf_area_0"
 
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="",ylab="",cex=1, xlim=c(0,1), 
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1, 
                     main=spp,col=col.age(data[[spp]]$age))
@@
 mtext("RA", 2, outer=TRUE,cex=1.2)
-mtext("proportion maximum H", 1, outer=TRUE,cex=1.2)
+mtext("initial leaf area", 1, outer=TRUE,cex=1.2)
 legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")

### 2015-09-03 RA_figs.rmd
figures for lab meeting

@@
 results$model <- "log10(yvar)~log10(xvar)"
-saved_results <- as.data.frame(results)
 results[1:6]
@@
 results$model <- "log10(yvar)~log10(xvar)"
-saved_results <- bind_rows(saved_results,results)
-results
+saved_results <- as.data.frame(results)
+results[1:6]
 
@@
 results$b <- round(results$b,digits=2)
-results
+results$yvar <- "total_inv"
+results$xvar <- "leaf_area_0"
+results$data <- "SummaryInd"
+results$model <- "log10(yvar)~log10(xvar)"
+saved_results <- bind_cols(saved_results[1:2],results[2])
+names(saved_results) <- c("species","r1","r2")
+results[1:6]
 
@@
 legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "leaf_area"
+xvar <- "leaf_area_0"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results$yvar <- "total_inv"
+results$xvar <- "leaf_area_0"
+results$data <- "SummaryInd"
+results$model <- "log10(yvar)~log10(xvar)"
+saved_results <- bind_cols(saved_results[1:2],results[2])
+names(saved_results) <- c("species","r1","r2")
+results[1:6]
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+
+mtext("Leaf area at time 1", 2, outer=TRUE,cex=1.2)
+mtext("Leaf area at time 0", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=6, fig.height=6}
+# pdf("figs2/R2-improve.pdf", height=5, width=5)
+# plot
+par(mfcol=c(1,1), cex=1, omi=c(.2,.2,.01,.01), mai=c(.8,.8,.04,0.2)) 
+plot(r1~r2,saved_results,col=col.spp(species),pch=16,cex=1.1,cex.axis=0.8,cex.lab=0.8,ylab="R2 for veg invest vs leaf area",xlab="R2 for total invest vs leaf area",xlim=c(0,1),ylim=c(0,1))
+abline(0,1)
+text(r1~r2,saved_results, labels=species, pos=c("4","3","4","3","2","2","2","2","3","2","2","2","2","3"), offset=.4, cex=0.7,col="black")
+saved_results$max_RA <- c("0.6","0.9","0.2","0.7","0.9","0.4","0.3","0.4","0.85","0.4","0.4","0.4","0.5","0.3")
+text(r1~r2,saved_results, labels=max_RA, pos=c("1","1","1","1","1","1","4","1","1","1","3","3","1","1"), offset=.4, cex=0.7,col="black")
+# dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+pdf("figs2/shoot_leaf_area_VS_repro_inv.pdf", height=11.69, width=8.27)
+plot
+par(mfrow=c(4,4), cex=1, omi=c(.6,.5,.1,.1), mai=c(.35,.4,.25,0.1)) 
+#par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2))
+yvar <- "shoot_leaf_area"
+xvar <- "repro_inv"
+
+data <- subset(SummaryInd,repro_inv>0)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.1,cex.axis=0.8,cex.main=0.9,
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+
+mtext("Shoot leaf area", 2, outer=TRUE,cex=1.2,line=1.2)
+mtext("Reproductive investment (mg)", 1, outer=TRUE,cex=1.2,line=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+pdf("figs2/leaf_area_increase_VS_repro_inv.pdf", height=11.69, width=8.27)
+plot
+par(mfrow=c(4,4), cex=1, omi=c(.6,.5,.1,.1), mai=c(.35,.4,.25,0.1)) 
+#par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "growth_leaf_area_log"
+xvar <- "repro_inv"
+
+data <- subset(SummaryInd,repro_inv>0)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.1,cex.axis=0.8,cex.main=0.9,
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+
+mtext("Leaf area increase (log-log)", 2, outer=TRUE,cex=1.2,line=1.2)
+mtext("Reproductive investment (mg)", 1, outer=TRUE,cex=1.2,line=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+dev.off()
 ```

### 2015-09-03 tests.Rmd
figures for lab meeting

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "shoot_leaf_area"
xvar <- "leaf_area"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
                    main=spp,col=col.age(data[[spp]]$age))
}

mtext("Shoot leaf area", 2, outer=TRUE,cex=1.2)
mtext("Leaf area", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,.7,.6,0.2)) 
yvar <- "growth_height_log"
xvar <- "RA"
xvar2 <- "growth_inv"

data <- subset(SummaryInd,reproducing==TRUE&age>2)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="repro",ylab="",cex=1.3, main=spp,col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="x",xlab="veg", ylab="", cex=1.3, main=spp,col=col.age(data[[spp]]$age))
}

mtext("Height growth (log-log)", 2, outer=TRUE,cex=1.2)
mtext("Reproductive investment", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
savpar(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,.7,.6,0.2)) 
yvar <- "total_inv"
xvar <- "leaf_area_0"

data <- subset(SummaryInd,age>2)

data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
saved <- results[,1:2]

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3, main=spp,col=col.age(data[[spp]]$age))
 }

mtext("Height growth (log-log)", 2, outer=TRUE,cex=1.2)
mtext("Reproductive investment", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,.7,.6,0.2)) 
yvar <- "total_inv"
xvar <- "leaf_area_0"

data <- subset(SummaryInd)
data <- split(data, data$species)

lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
saved <- bind_cols(saved,results[2])

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3, main=spp,col=col.age(data[[spp]]$age))
 }

mtext("Height growth (log-log)", 2, outer=TRUE,cex=1.2)
mtext("Reproductive investment", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

### 2015-09-03 species_summarys_figs.R

@@ -1,0 +1,47 @@
+yvar <- "growth_inv"
+yvar2 <- "repro_inv"
+yvar3 <- "total_inv"
+yvar4 <- "RA"
+yvar5 <- "growth_height_log"
+yvar6 <- "growth_leaf_area_log"
+yvar7 <- "shoot_leaf_area"
+xvar <- "leaf_area_0"
+xvar2 <- "total_weight_0"
+xvar3 <- "prop_maxH"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+# pdf("figs2/species_summary_plots.pdf", height=12, width=8)
+# plot
+
+for(spp in names(data)) {
+  par(mfcol=c(7,3), omi=c(.5,.1,.5,.03), mai=c(.3,.5,.03,0.03))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="veg investment",cex=1.1, cex.axis=0.9,cex.lab=0.9,col=col.age(data[[spp]]$age))
+  legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1, bty="n")
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="xy",xlab="",ylab="repro investment",cex=1.1, cex.axis=0.9,cex.lab=0.9,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="total investment (mg)",cex=1.1, cex.axis=0.9,cex.lab=0.9,col=col.age(data[[spp]]$age))
+  arrows(data[[spp]]$leaf_area_0,data[[spp]]$growth_inv,data[[spp]]$leaf_area_0,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
+  plot_yvar_vs_xvar(data[[spp]], yvar5, xvar,log="x",xlab="",ylab="height increase (log-log)",cex=1.1, cex.axis=0.9,cex.lab=0.9,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar6, xvar,log="x",xlab="",ylab="total leaf area increase (log-log)",cex=1.1, cex.axis=0.9,cex.lab=0.9,col=col.age(data[[spp]]$age))
[…]

### 2015-09-08 leaf_weight_issue.Rmd
file looking at how leaf area by diameter plots

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=14, fig.height=7.5}
remake::make("export")

SummaryInd <- readRDS("export/SummaryInd.rds")
SummarySpp <- readRDS("export/SummarySpp.rds")
SummarySppAge <- readRDS("export/SummarySppAge.rds")
HarvestData <- readRDS("export/HarvestData.rds")
InvestmentByPart <- readRDS("export/Investment_FD_all.rds")

source("R/figures.R")
```

* Currently a slope isn't being calculated for "leaf vs diameter" only for whole plant and stem - leaves are then determined by subtraction. I think this is probably a mistake.  
* It would be better to fit a line through "leaf weight vs diameter" for the subset of individuals/segments that are linear and then apply a correction to the older plants  
* if helpful, I could create a lookup table that indicates which ageXsegment combinations to use for the linear regression for each species  
* then, for leaves, the "offset" would be calculated as the offset based on the single-point value of (total weight of leave, basal diameter), instead of applying a slope correction  
* In these plots  
    * points are colored by age  
    * basal segments (i.e. whole plant) values are larger and surrounded by a black ring
    * the first plot for each species is all individuals, while the second plot it individuals from the two oldest sites

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=15, fig.height=15}
par(mfcol=c(2,2), cex=1, omi=c(.3,.2,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
data2 <- subset(HarvestData,start_end=="end")
data2 <- split(data2, data2$species)

data1 <- subset(HarvestData,start_end=="end"&age>8)
data1 <- split(data1, data1$species)

for(spp in names(data)) {

plot(leaf_weight~diameter,data2[[spp]],log="xy",pch=16,col=col.age(data[[spp]]$age),main=spp,cex=1.2)
points(leaf_weight~diameter,subset(data2[[spp]],segment==1),cex=1.5)

plot(leaf_weight~diameter,data1[[spp]],log="xy",pch=16,col=col.age(data[[spp]]$age),main=spp,cex=1.2)
points(leaf_weight~diameter,subset(data1[[spp]],segment==1),cex=1.5)

}
```

### 2015-09-08 leaf_weight_issue.Rmd
fixed typo with color scheme

@@
 
-plot(leaf_weight~diameter,data2[[spp]],log="xy",pch=16,col=col.age(data[[spp]]$age),main=spp,cex=1.2)
+plot(leaf_weight~diameter,data2[[spp]],log="xy",pch=16,col=col.age(data2[[spp]]$age),main=spp,cex=1.2)
 points(leaf_weight~diameter,subset(data2[[spp]],segment==1),cex=1.5)
 
-plot(leaf_weight~diameter,data1[[spp]],log="xy",pch=16,col=col.age(data[[spp]]$age),main=spp,cex=1.2)
+plot(leaf_weight~diameter,data1[[spp]],log="xy",pch=16,col=col.age(data1[[spp]]$age),main=spp,cex=1.2)
 points(leaf_weight~diameter,subset(data1[[spp]],segment==1),cex=1.5)

### 2015-09-08 RA_combined_plots.Rmd
additions to plots

@@
 source("R/figures.R")
+```
+
+#modified; original below
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+par(mfcol=c(4,3), cex=1, omi=c(.1,.3,.3,.1), mai=c(1.1,1,.1,0.1)) 
+yvar <- "leaf_area"
+yvar2 <- "height"
+yvar3 <- "total_inv"
+yvar4 <- "RA_leaf_area"
+xvar <- "leaf_area_midyear"
+xvar2 <- "age"
+xvar3 <- "height"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="leaf area (midyear)",ylab="total investment (mg)",cex=1.3,
+                    col=col.age(data[[spp]]$age),main=spp)
+  arrows(data[[spp]]$leaf_area_midyear,data[[spp]]$growth_inv,data[[spp]]$leaf_area_midyear,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="age",ylab="RA",cex=1.3,ylim=c(0,1.4),
+                    col=col.age(data[[spp]]$age))
+  points(RA_leaf_area~age,data2[[spp]],pch=16)
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="age",ylab="final leaf area",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  points(leaf_area~age,data2[[spp]],pch=16)
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="xy",xlab="age",ylab="height",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  points(height~age,data2[[spp]],pch=16)
+  }
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+par(mfcol=c(2,2), cex=1, omi=c(.1,.3,.3,.1), mai=c(1.1,1,.1,0.1)) 
+xvar <- "age"
+
+yvar1 <- "height"
+yvar2 <- "diameter"
+yvar3 <- "leaf_area"
+yvar4 <- "total_weight_0"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar1, xvar,log="xy",ylab="height",xlab="age",cex=1.3,
+                    col=col.age(data[[spp]]$age),main=spp)
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="xy",ylab="diameter",xlab="",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",ylab="leaf area",xlab="",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="xy",ylab="weight",xlab="",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  }
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+par(mfcol=c(4,3), cex=1, omi=c(.8,.3,.3,.1), mai=c(.5,1,.1,0.1)) 
+SummaryInd$repro_inv_log <- SummaryInd$repro_inv + 10
+yvar <- "growth_height_log"
+yvar2 <- "growth_leaf_area_log"
+yvar3 <- "shoot_leaf_area"
+yvar4 <- "RA"
+xvar <- "repro_inv_log"
+xvar2 <- "total_weight_0"
+xvar3 <- "prop_maxH"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="height increase (log-log)",cex=1.3, col=col.age(data[[spp]]$age))
+  legend("topright",legend=labels.age(),col=col.age(),pch=16, cex=1,bty="n")
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="x",xlab="",ylab="total leaf area increase (log-log)",cex=1.3,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="total shoot leaf area",cex=1.3, col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="x",xlab="reproductive investment",ylab="RA",cex=1.3,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="x",xlab=spp,ylab="",cex=1.3, col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="x",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar2,log="xy",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="initial plant weight",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar3,log="",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar3,log="",xlab="",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar3,log="y",xlab="",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar3,log="",xlab="prop maxH",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
+  mtext("Reproductive investment (mg)                                                                            initial plant weight                                                                                    prop maxH", 1, line=1,outer=TRUE,cex=1.2)
+  mtext(spp, 3, outer=TRUE,cex=1.2)   
+}
 ```
@@
 ```
-
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-par(mfcol=c(4,3), cex=1, omi=c(.8,.3,.3,.1), mai=c(.5,1,.1,0.1)) 
-SummaryInd$repro_inv_log <- SummaryInd$repro_inv + 10
-yvar <- "growth_height_log"
-yvar2 <- "growth_leaf_area_log"
-yvar3 <- "shoot_leaf_area"
-yvar4 <- "RA"
-xvar <- "repro_inv_log"
-xvar2 <- "total_weight_0"
-xvar3 <- "prop_maxH"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-
-for(spp in names(data)) {
-
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="height increase (log-log)",cex=1.3, col=col.age(data[[spp]]$age))
-  legend("topright",legend=labels.age(),col=col.age(),pch=16, cex=1,bty="n")
-  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="x",xlab="",ylab="total leaf area increase (log-log)",cex=1.3,col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="total shoot leaf area",cex=1.3, col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="x",xlab="reproductive investment",ylab="RA",cex=1.3,col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="x",xlab=spp,ylab="",cex=1.3, col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="x",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar2,log="xy",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="initial plant weight",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar3,log="",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar3,log="",xlab="",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar3,log="y",xlab="",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar3,log="",xlab="prop maxH",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
-  mtext("Reproductive investment (mg)                                                                            initial plant weight                                                                                    prop maxH", 1, line=1,outer=TRUE,cex=1.2)
-  mtext(spp, 3, outer=TRUE,cex=1.2)   
-}
-```

### 2015-09-08 RA_figs.rmd
additions to plots

@@
 SummarySppAge <- readRDS("export/SummarySppAge.rds")
+HarvestData <- readRDS("export/HarvestData.rds")
+InvestmentByPart <- readRDS("export/Investment_FD_all.rds")
 

### 2015-09-08 tests.Rmd
additions to plots

@@
 yvar <- "shoot_leaf_area"
-xvar <- "leaf_area"
+xvar <- "initial_leaf_area"
 
@@
 
+SummaryInd$growth_height_per <- SummaryInd$growth_height/SummaryInd$height_0
+SummaryInd$growth_leaf_per <- SummaryInd$growth_leaf/SummaryInd$leaf_weight
+SummaryInd$growth_leaf_pos <- SummaryInd$growth_leaf
+
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,.7,.6,0.2)) 
-yvar <- "growth_height_log"
-xvar <- "RA"
-xvar2 <- "growth_inv"
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.3,.7,.6,0.2)) 
+yvar <- "growth_leaf_per"
+xvar2 <- "diameter"
 
-data <- subset(SummaryInd,reproducing==TRUE&age>2)
+data <- subset(SummaryInd)
 data <- split(data, data$species)
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="repro",ylab="",cex=1.3, main=spp,col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="x",xlab="veg", ylab="", cex=1.3, main=spp,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="", ylab="", cex=1.3, main=spp,col=col.age(data[[spp]]$age))
 }
 
-mtext("Height growth (log-log)", 2, outer=TRUE,cex=1.2)
-mtext("Reproductive investment", 1, outer=TRUE,cex=1.2)
+mtext("Height growth (%)", 2, outer=TRUE,cex=1.2)
+mtext("diameter", 1, outer=TRUE,cex=1.2)
 legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
@@
 ```
+
+```{r}
+par(mfrow=c(2,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(.3,.3,.6,0.2)) 
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+plot(leaf_weight~diameter,data[[spp]],log="xy",cex=1.3, main=spp,col=col.age(data[[spp]]$age),pch=16)
+points(leaf_weight_0~diameter_0,data[[spp]],cex=1.3,pch=1,col=col.age(data[[spp]]$age))
+arrows(data[[spp]]$diameter, data[[spp]]$leaf_weight, data[[spp]]$diameter_0,data[[spp]]$leaf_weight_0, length = 0,angle = 30, code = 2, col = col.age(data[[spp]]$age),lwd=.3)
+}
+```
+
+```{r}
+par(mfrow=c(2,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(.3,.3,.6,0.2)) 
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+plot(stem_weight~diameter,data[[spp]],log="xy",cex=1.3, main=spp,col=col.age(data[[spp]]$age),pch=16)
+points(stem_weight_0~diameter_0,data[[spp]],cex=1.3,pch=1,col=col.age(data[[spp]]$age))
+arrows(data[[spp]]$diameter, data[[spp]]$stem_weight, data[[spp]]$diameter_0,data[[spp]]$stem_weight_0, length = 0,angle = 30, code = 2, col = col.age(data[[spp]]$age),lwd=.3)
+points(leaf_weight~diameter,data[[spp]],cex=1.3,pch=17,col=col.age(data[[spp]]$age))
+points(leaf_weight_0~diameter_0,data[[spp]],cex=1.3,pch=2,col=col.age(data[[spp]]$age))
+arrows(data[[spp]]$diameter, data[[spp]]$leaf_weight, data[[spp]]$diameter_0,data[[spp]]$leaf_weight_0, length = 0,angle = 30, code = 1, col = col.age(data[[spp]]$age),lwd=.3,lty=3)
+}
+```

### 2015-09-08 diameter_weight_checking.R

@@ -1,275 +1,0 @@
-check <- BAER_HarvestData
-check <- BOLE_HarvestData
-check <- COER_HarvestData
-check <- EPMI_HarvestData
-check <- GRBU_HarvestData
-check <- GRSP_HarvestData
-check <- HATE_HarvestData
-check <- HEPU_HarvestData
-check <- LEES_HarvestData
-check <- PELA_HarvestData
-check <- PEPU_HarvestData
-check <- PHPH_HarvestData
-check <- PILI_HarvestData
-check <- PUTU_HarvestData
-
-plot(dia~stem_weight,data=subset(check,segment==1), pch=16,log="xy",col=col.lots(individual))
-text(dia~stem_weight,data=subset(check,segment==1),labels=individual,cex=.5,pos=3,offset=-.7)
-mod <- lm(log(stem_weight)~log(dia),data=subset(check,segment==1))
-words.bottom.right.logxy(mod)
-
-
-
-
-plot(leaf_weight~stem_weight,data=subset(check), pch=16,log="xy",col="red")
-text(leaf_weight~stem_weight,data=subset(check),labels=individual,cex=.5,pos=2,offset=-1)
-mod <- lm(log(stem_weight)~log(leaf_weight),data=subset(check))
-words.bottom.right.logxy(mod)
-
-#age 10 break (e.g. slightly BAER, GRSP)
-plot(leaf_weight~stem_weight,data=subset(check,age<10), pch=16,log="xy",col="red")
-points(leaf_weight~stem_weight,data=subset(check,age>10), pch=16,log="xy",col="blue")
-text(leaf_weight~stem_weight,data=subset(check,age<10),labels=individual,cex=.5,pos=2,offset=-1)
-mod <- lm(log(stem_weight)~log(leaf_weight),data=subset(check,age<10))
-words.bottom.right.logxy(mod)
-
-#age 8 break (e.g. GRBU, COER, LEES)
-plot(leaf_weight~stem_weight,data=subset(check,age<8), pch=16,log="xy",col="red")
-points(leaf_weight~stem_weight,data=subset(check,age>8), pch=16,log="xy",col="blue")
-text(leaf_weight~stem_weight,data=subset(check,age<8),labels=individual,cex=.5,pos=2,offset=-1)
-mod <- lm(log(stem_weight)~log(leaf_weight),data=subset(check,age<8))
-words.bottom.right.logxy(mod)
-
-#age 6 break 
[…]

### 2015-09-08 leaf_weight_issue.Rmd
trying to understand problem with leaf weight estimates

--- 2015-09-08 leaf_weight_issue.Rmd
@@
 par(mfcol=c(2,2), cex=1, omi=c(.3,.2,.1,.1), mai=c(1.1,1.1,.4,0.2)) 
-data2 <- subset(HarvestData,start_end=="end")
+xvar <- "diameter"
+yvar <- "leaf_weight"
+
+data2 <- subset(HarvestData, start_end=="end"&segment==1 & !is.na(diameter) )
 data2 <- split(data2, data2$species)
 
-data1 <- subset(HarvestData,start_end=="end"&age>8)
-data1 <- split(data1, data1$species)
+for(spp in names(data2)) {
+data3 <- data2[[spp]]
+x <- data3[[xvar]]
+plot(leaf_weight~diameter,data3,log="xy",pch=16,col=col.age(data2[[spp]]$age),main=spp,cex=1.2)
+points(leaf_weight~diameter,subset(data3,segment==1),cex=1.5)
+fit <- lm(log(data3[[yvar]]) ~  log(x))
+cs <- coef(fit)
+slope <- cs[2]
+curve(exp(cs[1])*x^slope, from=0.1, to=100, add=TRUE, lwd=2)
+intercept_indiv = log(data3[[yvar]]) - slope * log(x)
 
-for(spp in names(data)) {
-
-plot(leaf_weight~diameter,data2[[spp]],log="xy",pch=16,col=col.age(data[[spp]]$age),main=spp,cex=1.2)
-points(leaf_weight~diameter,subset(data2[[spp]],segment==1),cex=1.5)
-
-plot(leaf_weight~diameter,data1[[spp]],log="xy",pch=16,col=col.age(data[[spp]]$age),main=spp,cex=1.2)
-points(leaf_weight~diameter,subset(data1[[spp]],segment==1),cex=1.5)
+for(i in seq_len(nrow(data3))) {
+  curve(exp(intercept_indiv[i])*x^slope, from= 0.9*x[i], to=1.1*x[i], add=TRUE, lwd=1)
+  }
 
 }
+
+#plot(leaf_weight~diameter,data1[[spp]],log="xy",pch=16,col=col.age(data1[[spp]]$age),main=spp,cex=1.2)
+#points(leaf_weight~diameter,subset(data1[[spp]],segment==1),cex=1.5)
+
 ```

### 2015-09-09 RA_combined_plots.Rmd
Small bits of work on RA schedule figures

--- 2015-09-02 RA_combined_plots.Rmd
@@
 source("R/figures.R")
+```
+
+#modified; original below
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+pdf("figs2/RA_schedule_plots", height=11.3, width=8)
+plot
+par(mfcol=c(4,2), cex=1, omi=c(.1,.2,.3,.1), mai=c(.6,.6,.1,0.1)) 
+yvar <- "leaf_area"
+yvar2 <- "height"
+yvar3 <- "total_inv"
+yvar4 <- "RA_leaf_area"
+xvar <- "leaf_area_midyear"
+xvar2 <- "age"
+xvar3 <- "height"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="leaf area (midyear)",ylab="total investment (mg)",cex=1.3,
+                    col=col.age(data[[spp]]$age),main=spp)
+  arrows(data[[spp]]$leaf_area_midyear,data[[spp]]$growth_inv,data[[spp]]$leaf_area_midyear,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="age",ylab="RA",cex=1.3,ylim=c(0,1.4),
+                    col=col.age(data[[spp]]$age))
+  points(RA_leaf_area~age,data2[[spp]],pch=16)
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="age",ylab="final leaf area",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  points(leaf_area~age,data2[[spp]],pch=16)
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="xy",xlab="age",ylab="height",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  points(height~age,data2[[spp]],pch=16)
+  }
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+par(mfcol=c(2,2), cex=1, omi=c(.1,.3,.3,.1), mai=c(1.1,1,.1,0.1)) 
+xvar <- "age"
+
+yvar1 <- "height"
+yvar2 <- "diameter"
+yvar3 <- "leaf_area"
+yvar4 <- "total_weight_0"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar1, xvar,log="xy",ylab="height",xlab="age",cex=1.3,
+                    col=col.age(data[[spp]]$age),main=spp)
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="xy",ylab="diameter",xlab="",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",ylab="leaf area",xlab="",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="xy",ylab="weight",xlab="",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  }
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+par(mfcol=c(4,3), cex=1, omi=c(.8,.3,.3,.1), mai=c(.5,1,.1,0.1)) 
+SummaryInd$repro_inv_log <- SummaryInd$repro_inv + 10
+yvar <- "growth_height_log"
+yvar2 <- "growth_leaf_area_log"
+yvar3 <- "shoot_leaf_area"
+yvar4 <- "RA"
+xvar <- "repro_inv_log"
+xvar2 <- "total_weight_0"
+xvar3 <- "prop_maxH"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="height increase (log-log)",cex=1.3, col=col.age(data[[spp]]$age))
+  legend("topright",legend=labels.age(),col=col.age(),pch=16, cex=1,bty="n")
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="x",xlab="",ylab="total leaf area increase (log-log)",cex=1.3,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="total shoot leaf area",cex=1.3, col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="x",xlab="reproductive investment",ylab="RA",cex=1.3,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="x",xlab=spp,ylab="",cex=1.3, col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="x",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar2,log="xy",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="initial plant weight",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar3,log="",xlab="",ylab="",cex=1.3, col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar3,log="",xlab="",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar3,log="y",xlab="",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar3,log="",xlab="prop maxH",ylab="",cex=1.3,col=col.age(data[[spp]]$age))
+  mtext("Reproductive investment (mg)                                                                            initial plant weight                                                                                    prop maxH", 1, line=1,outer=TRUE,cex=1.2)
+  mtext(spp, 3, outer=TRUE,cex=1.2)   
+}
 ```

### 2015-09-09 tests.Rmd
Small bits of work on RA schedule figures

@@
 ```
+
+```{r}
+par(mfrow=c(2,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(.3,.3,.6,0.2)) 
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+plot(stem_weight~diameter,data[[spp]],log="xy",cex=1.3, main=spp,col=col.age(data[[spp]]$age),pch=16)
+points(stem_weight_0~diameter_0,data[[spp]],cex=1.3,pch=1,col=col.age(data[[spp]]$age))
+arrows(data[[spp]]$diameter, data[[spp]]$stem_weight, data[[spp]]$diameter_0,data[[spp]]$stem_weight_0, length = 0,angle = 30, code = 2, col = col.age(data[[spp]]$age),lwd=.3)
+points(leaf_weight~diameter,data[[spp]],cex=1.3,pch=17,col=col.age(data[[spp]]$age))
+points(leaf_weight_0~diameter_0,data[[spp]],cex=1.3,pch=2,col=col.age(data[[spp]]$age))
+arrows(data[[spp]]$diameter, data[[spp]]$leaf_weight, data[[spp]]$diameter_0,data[[spp]]$leaf_weight_0, length = 0,angle = 30, code = 1, col = col.age(data[[spp]]$age),lwd=.3,lty=3)
+}+
+```

### 2015-09-09 Flowering_parts_charts.Rmd
file name changed

``` {r}
accessoryList <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryList.csv")
accessoryListShort <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryListShort.csv")
accessoryListShortest <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryListShortest.csv")

col.barplot <- function(x=NULL){
  ret <- c("cyan4","cyan1","darkslategray3","firebrick","firebrick1","firebrick2","firebrick3","gold","bisque","chartreuse2","chartreuse3","chartreuse4","chartreuse2","deepskyblue",
           "dodgerblue2","deepskyblue","deepskyblue4","darkorange","darkorange1","darkorange2","darkorange3","darkorange4","darkorange3")
  names(ret) <- c("seed","seed_pod","fruit_mature","bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","fruit_seed_immature",
                  "bract","pedicel","green_parts","inflorescence_stalk","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green","cone")

  if(!is.null(x)) {
    ret <- ret[as.character(x)]
  }
  ret
}

labels.barplot <- function(x=NULL){
  names(col.barplot(x))
}

Invest2 <- merge(InvestmentByPart,select(accessoryList,-sort), by=c("species","part"))

for(v in c("weight")) {
  i <- is.na(Invest2[[v]])
  Invest2[[v]][i] <- 0
}
```

by "parts fewer"
```{r}
SummaryInvest <- 
  Invest2 %>%
  group_by(parts_fewer,species) %>%
  summarise_each(funs(sum),weight)

SummaryInvest <- merge(SummaryInvest,select(accessoryListShort,-sort), by=c("species","parts_fewer"),all.x=TRUE)

SummaryInvestSpp <- 
  Invest2 %>%
  group_by(species) %>%
  summarise_each(funs(sum),weight)

names(SummaryInvestSpp) <- c("species","weight_spp")

SummaryInvest <- merge(SummaryInvest,SummaryInvestSpp,by=c("species"),all.x=TRUE)
SummaryInvest$prop_weight <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)
SummaryInvest$labels <- paste(SummaryInvest$parts_fewer," (",SummaryInvest$prop_weight,")")
SummaryInvest <- SummaryInvest[order(factor(SummaryInvest$parts_fewer,levels=c(c("seed","seed_pod","fruit_mature","bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted",
                                                                                 "bract","pedicel","inflorescence_stalk","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green")))),]
```

by "parts fewer yet"
```{r}
SummaryInvest <- 
  Invest2 %>%
  group_by(parts_fewer_yet,species) %>%
  summarise_each(funs(sum),weight)

SummaryInvest <- merge(SummaryInvest,select(accessoryListShortest,-sort), by=c("species","parts_fewer_yet"),all.x=TRUE)

SummaryInvestSpp <- 
  Invest2 %>%
  group_by(species) %>%
  summarise_each(funs(sum),weight)

names(SummaryInvestSpp) <- c("species","weight_spp")

SummaryInvest <- merge(SummaryInvest,SummaryInvestSpp,by=c("species"),all.x=TRUE)
SummaryInvest$prop_weight_spp <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)
SummaryInvest$labels <- paste(SummaryInvest$parts_fewer_yet," (",SummaryInvest$prop_weight,")")
SummaryInvest <- SummaryInvest[order(factor(SummaryInvest$parts_fewer_yet,levels=c(c("bud","petals","calyx","finished_flower","fruit_seed_immature","seed","seed_pod","fruit_mature","bract","pedicel","inflorescence_stalk","green_parts","cone")))),]
```

by "parts"
```{r}
SummaryInvestParts <- 
  Invest2 %>%
  group_by(part,species) %>%
  summarise_each(funs(sum),weight)

SummaryInvestParts <- merge(SummaryInvestParts,select(accessoryList,-sort), by=c("species","part"),all.x=TRUE)

SummaryInvestSppParts <- 
  Invest2 %>%
  group_by(species) %>%
  summarise_each(funs(sum),weight)

names(SummaryInvestSppParts) <- c("species","weight_spp")

SummaryInvestParts <- merge(SummaryInvestParts,SummaryInvestSppParts,by=c("species"),all.x=TRUE)

names(SummaryInvestParts) <- c("species","part","weight_by_part","accessory_part","parts_fewer","parts_fewer_yet","weight_spp")

SummaryInvestParts <- merge(SummaryInvestParts,select(SummaryInvest,-accessory_part,-weight_spp),by=c("species","parts_fewer_yet"),all.x=TRUE)
SummaryInvestParts$prop_weight_few_parts = round(SummaryInvestParts$weight_by_part / SummaryInvestParts$weight,digits=3)
SummaryInvestParts$labels <- paste(SummaryInvestParts$part," (",SummaryInvestParts$prop_weight_few_parts,")")
SummaryInvestParts$splitting <-paste(SummaryInvestParts$species,"_",SummaryInvestParts$parts_fewer_yet)
```

View(SummaryInvestParts)

``` {r}
pdf("figs2/Dividing_flower_parts2.pdf", height=11, width=8)
plot
par(mfcol=c(4,3), cex=1, omi=c(.01,.01,.01,.01), mai=c(.5,.9,.5,.9)) 
data <- subset(SummaryInvestParts,weight>0)
data <- split(data, data$splitting)

for(spp in names(data)) {
  pie(data[[spp]]$weight_by_part,labels=data[[spp]]$labels,main=spp,cex=0.3,cex.main=0.5,col=col.age())
}
dev.off()
```

```{r}
barplot_data <- select(SummaryInvest,species, parts_fewer_yet, prop_weight)
barplot_data <- spread(barplot_data,species,prop_weight,fill=0,drop=FALSE)
barplot_data <- barplot_data[order(factor(barplot_data$parts_fewer_yet,levels=c(c(
  "bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","fruit_seed_immature","seed","seed_pod","fruit_mature",
  "bract","pedicel","inflorescence_stalk","green_parts","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green","cone")))),]

barplot_data_matrix <- as.matrix(barplot_data[2:15])

#pdf("figs2/Flower_parts_barchart.pdf", height=8, width=11)
#plot
barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.8,cex.names=.8,xlim=c(.5,17.2),col=col.barplot(barplot_data$parts_fewer_yet),ylab="proportion repro investment")
legend(13.5,1,legend=barplot_data$parts_fewer_yet,pch=16, cex=1.2,bty="n",col=col.barplot(barplot_data$parts_fewer_yet))
#dev.off()
##For pie charts

data <- subset(SummaryInvest,weight>0)
data <- split(data, data$species)

pdf("figs2/Flower_parts_fewer.pdf", height=11, width=8)
plot
par(mfrow=c(2,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
for(spp in names(data)) {
  pie(data[[spp]]$weight,labels=data[[spp]]$labels,main=spp,col=col.barplot(data[[spp]]$parts_fewer_yet),cex=0.8)
}
dev.off()
```

### 2015-09-09 RA_combined_plots.Rmd
cleaning up files, adding thoughts

--- 2015-09-02 RA_combined_plots.Rmd
@@
 
+###Current best plots  
+* the plot of investment by leaf area, indicates that allocation to reproduction, leads to less vegetative investment than predicted  
+* plotting by age, shows that leaf investment and height growth are curtailed as plants age  
+* I think there still needs to be more of a link to connect this decreased "growth" with age directly to reproduction - maybe a "new" version of the plot showing individuals with more reproduction have less growth?
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-par(mfcol=c(4,3), cex=1, omi=c(.8,.3,.3,.1), mai=c(.5,1,.1,0.1)) 
-yvar <- "growth_inv"
-yvar2 <- "repro_inv"
+pdf("figs2/RA_schedule_plots_2.pdf", height=11.3, width=8)
+plot
+par(mfcol=c(4,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
+yvar <- "leaf_area"
+yvar2 <- "height"
 yvar3 <- "total_inv"
-yvar4 <- "RA"
-xvar <- "leaf_area_0"
-xvar2 <- "total_weight_0"
-xvar3 <- "prop_maxH"
+yvar4 <- "RA_leaf_area"
+xvar <- "leaf_area_midyear"
+xvar2 <- "age"
+xvar3 <- "height"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="leaf area (midyear)",ylab="total investment (mg)",cex=1.1,
+                    col=col.age(data[[spp]]$age),main=spp)
+  arrows(data[[spp]]$leaf_area_midyear,data[[spp]]$growth_inv,data[[spp]]$leaf_area_midyear,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="age",ylab="RA",cex=1.1,ylim=c(0,1.4),
+                    col=col.age(data[[spp]]$age))
+  points(RA_leaf_area~age,data2[[spp]],pch=16)
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="age",ylab="final leaf area",cex=1.1,
+                    col=col.age(data[[spp]]$age))
+  points(leaf_area~age,data2[[spp]],pch=16)
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="xy",xlab="age",ylab="height",cex=1.1,
+                    col=col.age(data[[spp]]$age))
+  points(height~age,data2[[spp]],pch=16)
+  }
+dev.off()
+```
+
+###Trends by age
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+par(mfcol=c(2,2), cex=1, omi=c(.1,.3,.3,.1), mai=c(1.1,1,.1,0.1)) 
+xvar <- "age"
+
+yvar1 <- "height"
+yvar2 <- "diameter"
+yvar3 <- "leaf_area"
+yvar4 <- "total_weight_0"
 
@@
 
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="veg investment",cex=1.3,
+  plot_yvar_vs_xvar(data[[spp]], yvar1, xvar,log="xy",ylab="height",xlab="age",cex=1.3,
+                    col=col.age(data[[spp]]$age),main=spp)
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="xy",ylab="diameter",xlab="age",cex=1.3,
                     col=col.age(data[[spp]]$age))
-  legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1,bty="n")
-  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="xy",xlab="",ylab="repro investment",cex=1.3,
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",ylab="leaf area",xlab="age",cex=1.3,
                     col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="total investment (mg)",cex=1.3,
+  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="xy",ylab="weight",xlab="age",cex=1.3,
                     col=col.age(data[[spp]]$age))
-  arrows(data[[spp]]$leaf_area_0,data[[spp]]$growth_inv,data[[spp]]$leaf_area_0,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="x",xlab="initial leaf area",ylab="RA",cex=1.3,
-                    col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab=spp,ylab="",cex=1.3,
-                    col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="xy",xlab="",ylab="",cex=1.3,
-                    col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar2,log="xy",xlab="",ylab="",cex=1.3,
-                    col=col.age(data[[spp]]$age))
-  arrows(data[[spp]]$total_weight_0,data[[spp]]$growth_inv,data[[spp]]$total_weight_0,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="initial plant weight",ylab="",cex=1.3,
-                    col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar3,log="y",xlab="",ylab="",cex=1.3,
-                    col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar3,log="y",xlab="",ylab="",cex=1.3,
-                    col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar3,log="y",xlab="",ylab="",cex=1.3,
-                   col=col.age(data[[spp]]$age))
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar3,log="",xlab="prop maxH",ylab="",cex=1.3,
-                    col=col.age(data[[spp]]$age))
-  mtext("Initial leaf area                                                                            initial plant weight                                                                                    prop maxH", 1, line=1,outer=TRUE,cex=1.2)
-  mtext(spp, 3, outer=TRUE,cex=1.2)   
   }
@@
 
+###Figures from lab meeting on Sept 3, 2015
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}

### 2015-09-10 RA_combined_plots.Rmd
thinking about ways to plot the growth-reproduction trade-off

@@
 dev.off()
+```
+SummaryInd$growth_ratio <- SummaryInd$growth_inv /SummaryInd$repro_inv
+
+#How to depict a trade-off?
+- only GRBU has an obvious trade-off, where absolute growth declines
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+  par(mfcol=c(3,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.5,.7,.6,0.2)) 
+xvar <- "growth_leaf"
+xvar2 <- "growth_inv"
+xvar3 <- "age"
+yvar <- "repro_inv"
+yvar2 <- "growth_ratio"
+
+data <- subset(SummaryInd,repro_inv>0)
+data <- split(data, data$species)
+
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3, main=spp,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="",ylab="",cex=1.3, main=spp,col=col.age(data[[spp]]$age))
+    plot_yvar_vs_xvar(data[[spp]], yvar2, xvar3,log="xy",xlab="",ylab="",cex=1.3, main=spp,col=col.age(data[[spp]]$age))
+ }
+
+mtext("repro inv", 2, outer=TRUE,cex=1.2)
+mtext("growth inv", 1, outer=TRUE,cex=1.2)
+legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
 ```

### 2015-09-10 RA_figs.rmd
thinking about ways to plot the growth-reproduction trade-off

@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
-mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
-plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+mod <- lm(log(growth_leaf)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
+plot((1+repro_inv)~growth_leaf, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
 words.top.left.logxy(mod)
@@
 
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "leaf_area"
-xvar <- "leaf_area_0"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results$yvar <- "total_inv"
-results$xvar <- "leaf_area_0"
-results$data <- "SummaryInd"
-results$model <- "log10(yvar)~log10(xvar)"
-saved_results <- bind_cols(saved_results[1:2],results[2])
-names(saved_results) <- c("species","r1","r2")
-results[1:6]
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
-                    main=spp,col=col.age(data[[spp]]$age))
-}
-
-mtext("Leaf area at time 1", 2, outer=TRUE,cex=1.2)
-mtext("Leaf area at time 0", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
-```
-
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=6, fig.height=6}
@@
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-pdf("figs2/shoot_leaf_area_VS_repro_inv.pdf", height=11.69, width=8.27)
-plot
-par(mfrow=c(4,4), cex=1, omi=c(.6,.5,.1,.1), mai=c(.35,.4,.25,0.1)) 
-#par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2))
+#pdf("figs2/shoot_leaf_area_VS_repro_inv.pdf", height=11.69, width=8.27)
+#plot
+#par(mfrow=c(4,4), cex=1, omi=c(.6,.5,.1,.1), mai=c(.35,.4,.25,0.1)) 
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2))
 yvar <- "shoot_leaf_area"
@@
 legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
-dev.off()
+#dev.off()
 ```
@@
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-pdf("figs2/leaf_area_increase_VS_repro_inv.pdf", height=11.69, width=8.27)
-plot
-par(mfrow=c(4,4), cex=1, omi=c(.6,.5,.1,.1), mai=c(.35,.4,.25,0.1)) 
-#par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+#pdf("figs2/leaf_area_increase_VS_repro_inv.pdf", height=11.69, width=8.27)
+#plot
+#par(mfrow=c(4,4), cex=1, omi=c(.6,.5,.1,.1), mai=c(.35,.4,.25,0.1)) 
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
 yvar <- "growth_leaf_area_log"
@@
 legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
-```
-
-###Including all investment vs. growth  
-* reproducing individuals now plot closer to the "expected line" (as defined by juvenile individuals), but for most species there is still a considerable discrepency
-* fit line of veg investment vs. total plant weight through non-reproductive plants
-* derive "predicted" total investment (veg+repro) for reproducing individuals
-* determine proportional reproductive cost for reproducing individuals; probably look by age
-*LEES, BOLE, EPMI become much tighter when reproductive investment included - all but 1 species
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "total_inv"
-xvar <- "total_weight"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
-                    main=spp,col=col.mature(data[[spp]]$mature))
-}
-
-mtext("Vegetative + reproductive investment (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Total plant weight (mg)", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
 ```
@@
 
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "cost_ratio"
-xvar <- "repro_inv"
-
-data <- subset(Summary2,species!="BOLE")
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  ((x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1.3,
-                    main=spp,col=col.age(data[[spp]]$age))              
-}
-
-mtext("Growth deficit (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Reproductive investment (mg)", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
-```
-
 ####There is a much less clearcut pattern with respect to height growth - for most species height growth declines dramatically with age, overshadowing any reprodutive maturity affects  
@@
 legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
-```
-
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "growth_height"
-xvar <- "height_0"
-
-data <- subset(SummaryInd,growth_height>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
-                    main=spp,col=col.mature(data[[spp]]$mature))
-}
-
-mtext("Increase in plant height (mm)", 2, outer=TRUE,cex=1.2)
-mtext("Initial plant height (mm)", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.mature(),col=col.mature(),pch=16, cex=1.1,bty="n")
 ```
@@
 
-plot(RA~growth_shoot_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp(species), pch=16)
-mod <- lm(log(growth_shoot_diameter)~RA,data=subset(SummaryInd,RA>0))
+plot(RA_leaf_area~growth_stem_diameter,data=subset(SummaryInd,RA>0),log="x",col=col.spp(species), pch=16,ylim=c(0,1.5))
+mod <- lm(log(growth_stem_diameter)~RA_leaf_area,data=subset(SummaryInd,RA_leaf_area>0&RA_leaf_area<1.5))
 words.top.right.logx(mod)
@@
 par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
-yvar <- "RA"
+yvar <- "RA_leaf_area"
 xvar <- "growth_stem_diameter"
 
-data <- subset(SummaryInd,RA>0)
+data <- subset(SummaryInd,RA_leaf_area>0&RA_leaf_area<1.5)
 data <- split(data, data$species)
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
-                    main=spp,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",cex=1.4, xlab="",ylab="",main=spp,col=col.age(data[[spp]]$age))
 }
@@
 mtext("Stem diameter growth", 1, outer=TRUE,cex=1.2)
-mtext("RA", 2, outer=TRUE,cex=1.2)  
+mtext("RA (leaf area)", 2, outer=TRUE,cex=1.2)  
 legend("bottomleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")

### 2015-09-10 tests.Rmd
cleaning up files, adding thoughts
thinking about ways to plot the growth-reproduction trade-off

--- 2015-09-08 tests.Rmd
@@
 
-SummaryInd$growth_height_per <- SummaryInd$growth_height/SummaryInd$height_0
-SummaryInd$growth_leaf_per <- SummaryInd$growth_leaf/SummaryInd$leaf_weight
-SummaryInd$growth_leaf_pos <- SummaryInd$growth_leaf
-
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.3,.7,.6,0.2)) 
-yvar <- "growth_leaf_per"
-xvar2 <- "diameter"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="", ylab="", cex=1.3, main=spp,col=col.age(data[[spp]]$age))
-}
-
-mtext("Height growth (%)", 2, outer=TRUE,cex=1.2)
-mtext("diameter", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
-```
+plot(repro_inv~growth_leaf,data=subset(SummaryInd,RA>0),log="xy",col=col.spp(species), pch=16)
+mod <- lm(log(growth_stem_diameter)~RA_leaf_area,data=subset(SummaryInd,RA_leaf_area>0&RA_leaf_area<1.5))
+words.top.right.logx(mod)
 
@@
 
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,.7,.6,0.2)) 
-yvar <- "total_inv"
-xvar <- "leaf_area_0"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
-saved <- bind_cols(saved,results[2])
-
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3, main=spp,col=col.age(data[[spp]]$age))
- }
-
-mtext("Height growth (log-log)", 2, outer=TRUE,cex=1.2)
-mtext("Reproductive investment", 1, outer=TRUE,cex=1.2)
-legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
-```
+SummaryInd$leaf_inv_ratio = SummaryInd$growth_stem / SummaryInd$growth_leaf
 
@@
 ```{r}
-par(mfrow=c(2,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(.3,.3,.6,0.2)) 
+par(mfrow=c(2,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,1.1,.6,0.2)) 
 data <- subset(SummaryInd)
@@
 ```
+
+```{r}
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2)) 
+mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
+plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+words.top.left.logxy(mod)
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+abline(0,1)
+text(2.1,3,srt=45,"RA = 0.5")
+abline(log10(3),1)
+text(2,9,srt=45,"RA = 0.75")
+abline(log10(9),1)
+text(2,25,srt=45,"RA = 0.9")
+abline(log10(19),1)
+text(2,60,srt=45,"RA = 0.95")
+abline(log10(.111),1)
+text(19,3,srt=45,"RA = 0.1")
+abline(log10(.010101),1)
+text(170,2.4,srt=45,"RA = 0.01")
+
+#mod <- lm(log(growth_leaf)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
+plot((1+repro_inv)~growth_leaf, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+#words.top.left.logxy(mod)
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+abline(0,1)
+text(2.1,3,srt=45,"RA = 0.5")
+abline(log10(3),1)
+text(2,9,srt=45,"RA = 0.75")
+abline(log10(9),1)
+text(2,25,srt=45,"RA = 0.9")
+abline(log10(19),1)
+text(2,60,srt=45,"RA = 0.95")
+abline(log10(.111),1)
+text(19,3,srt=45,"RA = 0.1")
+abline(log10(.010101),1)
+text(170,2.4,srt=45,"RA = 0.01")
+```
+
+plot(growth_leaf~growth_stem,SummaryInd, log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+abline(0,1)

### 2015-09-10 RA_combined_plots.Rmd
various for lab meeting
adding leaf turnover calculations

@@
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-pdf("figs2/RA_schedule_plots_2.pdf", height=11.3, width=8)
+SummaryInd <- SummaryInd[order(factor(SummaryInd$species,levels=c(c("HATE","PELA","BAER","PEPU","LEES","EPMI","COER","PUTU","PHPH","GRBU","GRSP","HEPU","PILI","BOLE")))),]
+
+pdf("figs2/RA_schedule_plots_3.pdf", height=11.3, width=8)
 plot

### 2015-09-10 tests.Rmd
various for lab meeting
adding leaf turnover calculations

@@
 abline(0,1)
+
+```{r}
+#pdf("figs2/weight_diameter_segments_2.pdf", height=11.3, width=8)
+#plot
+par(mfcol=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
+data <- subset(HarvestData)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+plot(stem_weight~diameter,data[[spp]],log="xy",cex=.7, main=spp,col=col.age(data[[spp]]$age),pch=16,ylab="stem (circle) + leaf (tri)"
+)
+points(leaf_weight~diameter,data[[spp]],cex=.7,pch=17,col=col.age(data[[spp]]$age))
+}
+#dev.off()
+
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+#pdf("figs2/tradeoff.pdf", height=11.3, width=8)
+#plot
+par(mfcol=c(4,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
+yvar <- "RA_leaf_area"
+xvar <- "growth_stem_diameter"
+
+data <- subset(SummaryInd,RA_leaf_area>0&RA_leaf_area<1.5)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",cex=1.4, xlab="",ylab="",main=spp,col=col.age(data[[spp]]$age))
+}
+
+mtext("Stem diameter growth", 1, outer=TRUE,cex=1.2)
+mtext("RA (leaf area)", 2, outer=TRUE,cex=1.2)  
+legend("bottomleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+#dev.off()
+```
+
+SummaryInd$leaf_turnover <- SummaryInd$leaf_weight_0/SummaryInd$LL_death
+plot(leaf_turnover~age,SummaryInd,log="xy", col=col.spp(species),pch=16)
+SummaryInd$leaf_net <- SummaryInd$growth_leaf + SummaryInd$leaf_turnover
+plot(leaf_net~age,SummaryInd,log="xy", col=col.spp(species),pch=16)
+plot(leaf_turnover~leaf_net,SummaryInd,log="xy", col=col.age(age),pch=16)
+abline(0,1)
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
+par(mfcol=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.3,0.1)) 
+yvar <- "leaf_turnover"
+xvar <- "leaf_net"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",main=spp,col=col.age(data[[spp]]$age))
+  abline(0,1)
+  abline(log10(.111),1)
+  abline(log10(.010101),1)
+}
+```

### 2015-09-11 Mark_20150911.Rmd
adding more plots looking at leaf turnover

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.3,0.1)) 
yvar <- "LMA"
xvar <- "age"

data <- subset(SummaryInd)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",cex=1.4, xlab="",ylab="",main=spp,col=col.age(data[[spp]]$age))
}
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.3,0.1)) 
yvar <- "RA_leaf_turnover"
xvar <- "age"

data <- subset(SummaryInd)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",cex=1.4, xlab="age",ylab="",main=spp,col=col.age(data[[spp]]$age))
}
mtext("RA, including leaf turnover", 2, outer=TRUE,cex=1.2,line=-.6)   
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfcol=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.3,0.1)) 
yvar <- "leaf_turnover"
xvar <- "leaf_net"

data <- subset(SummaryInd)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",main=spp,col=col.age(data[[spp]]$age))
  abline(0,1)
  abline(log10(.111),1)
  abline(log10(.010101),1)
  mtext("net leaf production (mg)", 1, outer=TRUE,cex=1.2,line=-.6)   
  mtext("leaf tunover (mg)", 2, outer=TRUE,cex=1.2,line=-.6)   
}
```

### 2015-09-11 Mark_20150911.Rmd
small changes

@@
+SummaryInd$leaf_turnover <- SummaryInd$leaf_weight_0/SummaryInd$LL_death
+SummaryInd$leaf_net <- SummaryInd$growth_leaf + SummaryInd$leaf_turnover
+SummaryInd$RA_leaf_turnover <- SummaryInd$repro_inv /(SummaryInd$repro_inv + SummaryInd$leaf_net)
+
+pdf("figs2/lab_meeting_followup.pdf", height=11.3, width=8)
+plot
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.3,0.1)) 
+par(mfrow=c(4,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
 yvar <- "LMA"
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",cex=1.4, xlab="",ylab="",main=spp,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",cex=1, xlab="age",ylab="LMA",main=spp,col=col.age(data[[spp]]$age))
 }
@@
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.3,0.1)) 
+
+par(mfcol=c(4,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
 yvar <- "RA_leaf_turnover"
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",cex=1.4, xlab="age",ylab="",main=spp,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",cex=1, xlab="age",ylab="",main=spp,col=col.age(data[[spp]]$age))
 }
 mtext("RA, including leaf turnover", 2, outer=TRUE,cex=1.2,line=-.6)
+
 ```
@@
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
-par(mfcol=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.3,0.1)) 
+par(mfcol=c(4,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
 yvar <- "leaf_turnover"
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",main=spp,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1, xlab="",ylab="",main=spp,col=col.age(data[[spp]]$age))
   abline(0,1)
@@
 ```
+dev.off()

### 2015-10-08 Biology_talk.rmd
figures for biology department talk

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_plot1.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "RA"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
}
mtext("RA", 2, outer=TRUE,cex=1,line=1.8)
mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_plot2.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.7,.01,.01), mai=c(.4,.15,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "RA"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="",cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  arrows(data[[spp]]$leaf_area_midyear,data[[spp]]$growth_inv,data[[spp]]$leaf_area_midyear,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
}
mtext("repro + growth investment (mg)", 2, outer=TRUE,cex=1,line=2.5)
mtext("leaf area (mm^2)", 1, outer=TRUE,cex=1,line=0.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_plot3.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
}
mtext("RA (based on leaf weight only)", 2, outer=TRUE,cex=1,line=1.8)
mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_plot4.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.7,.01,.01), mai=c(.4,.15,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
                    col=col.age(data[[spp]]$age))
}
mtext("leaf weight (mg)", 2, outer=TRUE,cex=1,line=2.5)
mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_plot5.wmf", height=7, width=4)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.7,.01,.01), mai=c(.4,.15,.3,0.1))
yvar <- "stem_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
                    col=col.age(data[[spp]]$age))
}
mtext("stem weight (mg)", 2, outer=TRUE,cex=1,line=2.5)
mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_canopy.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="BAER"|species=="HATE"|species=="PELA"|species=="PEPU")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("canopy species", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_early.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="BOLE"|species=="PILI"|species=="HEPU"|species=="COER")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("early reproducers", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_mid.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="GRBU"|species=="GRSP"|species=="PUTU"|species=="PHPH")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("mid-age reproducers", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_RA_mid-late.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="EPMI"|species=="LEES")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
}
mtext("epacrids", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
?win.metafile("figs2/RA_talk_LA_canopy.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="BAER"|species=="HATE"|species=="PELA"|species=="PEPU")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], xvar, xvar2,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,cex.axis=0.7,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(leaf_area_midyear~age,data2[[spp]],pch=16)
}
mtext("canopy species", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_LA_early.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="BOLE"|species=="PILI"|species=="HEPU"|species=="COER")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], xvar, xvar2,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(leaf_area_midyear~age,data2[[spp]],pch=16)
}
mtext("early reproducers", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_LA_mid.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="GRBU"|species=="GRSP"|species=="PUTU"|species=="PHPH")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], xvar, xvar2,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(leaf_area_midyear~age,data2[[spp]],pch=16)
}
mtext("mid-age reproducers", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
win.metafile("figs2/RA_talk_LA_mid-late.wmf", height=7, width=3)
plot
par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
yvar <- "leaf_weight"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data <- subset(SummaryInd, species=="EPMI"|species=="LEES")
data <- split(data, data$species)

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], xvar, xvar2,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  points(leaf_area_midyear~age,data2[[spp]],pch=16)
}
mtext("epacrids", 3, outer=TRUE,cex=1.2,line=.5)
dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
#win.metafile("figs2/RA_talk_LA_decline2.wmf", height=7, width=3)
#plot
par(mfcol=c(4,4), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
SummaryInd$ratio_leaf_growth = log10(SummaryInd$leaf_area) - log10(SummaryInd$leaf_area_0)

yvar <- "ratio_leaf_growth"
xvar <- "age"

data <- subset(SummaryInd,individual!="GRBU_903"&individual!="PELA_905"&individual!="COER_804"&individual!="PEPU_905"&individual!="GRSP_907"&individual!="LEES_907")
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,xlab="",ylab="",cex=1,log="x",xlim=c(1,33),ylim=c(-0.35,1.75),
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  abline(0,0)
  }
#text("epacrids", 3, outer=TRUE,cex=1.2,line=.5)
#dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
#win.metafile("figs2/RA_talk_LA_decline2.wmf", height=7, width=3)
#plot

  for(v in c("growth_leaf_min")) {
    i <- (SummaryInd[[v]]) > 0
    SummaryInd[[v]][i] <- 0
    }

SummaryInd$growth_leaf_nonzero <- SummaryInd$growth_leaf - SummaryInd$growth_leaf_min +1

par(mfcol=c(4,4), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1))

yvar <- "growth_leaf_nonzero"
xvar <- "repro_inv"

data <- subset(SummaryInd,individual!="GRBU_903"&individual!="PELA_905"&individual!="COER_804"&individual!="PEPU_905"&individual!="GRSP_907"&individual!="LEES_907"&repro_inv>0)
data <- split(data, data$species)

lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,xlab="",ylab="",cex=1,log="xy",
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
    }
#text("epacrids", 3, outer=TRUE,cex=1.2,line=.5)
#dev.off()
```

  for(v in c("growth_leaf_min")) {
    i <- (SummaryInd[[v]]) > 0
    SummaryInd[[v]][i] <- 0
    }

SummaryInd$growth_leaf_min <- 1 + abs(SummaryInd$growth_leaf_min)
SummaryInd$growth_leaf_nonzero <- SummaryInd$growth_leaf + SummaryInd$growth_leaf_min

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
#win.metafile("figs2/RA_talk_LA_decline2.wmf", height=7, width=3)
#plot

par(mfcol=c(4,4), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1))

yvar <- "growth_leaf_nonzero"
xvar <- "age"

data <- subset(SummaryInd,individual!="GRBU_903"&individual!="PELA_905"&individual!="COER_804"&individual!="PEPU_905"&individual!="GRSP_907"&individual!="LEES_907")
data <- split(data, data$species)

lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,xlab="",ylab="",cex=1,log="xy", xlim=c(1,33),yaxt="n", 
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
  abline(log10(data[[spp]]$growth_leaf_min),0,lwd=3)
    }
#text("epacrids", 3, outer=TRUE,cex=1.2,line=.5)
#dev.off()
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
#win.metafile("figs2/RA_talk_LA_decline2.wmf", height=7, width=3)
#plot

  for(v in c("growth_leaf_min")) {
    i <- (SummaryInd[[v]]) > 0
    SummaryInd[[v]][i] <- 0
    }

SummaryInd$growth_leaf_nonzero <- SummaryInd$growth_leaf - SummaryInd$growth_leaf_min

growth_by_site <- SummaryInd %>%
  group_by(species,age) %>%
  summarise_each(funs(mean, se), growth_leaf_nonzero,repro_inv)

growth_by_site$repro_inv_mean <- growth_by_site$repro_inv_mean +1
growth_by_site$growth_leaf_nonzero_mean <- growth_by_site$growth_leaf_nonzero_mean +1

par(mfcol=c(4,4), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1))

yvar <- "growth_leaf_nonzero_mean"
xvar <- "repro_inv_mean"

data <- subset(growth_by_site)
data <- split(data, data$species)

lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,xlab="",ylab="",cex=1,log="xy",
                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
    }
#text("epacrids", 3, outer=TRUE,cex=1.2,line=.5)
#dev.off()
```

### 2015-10-13 Flowering_parts_charts.Rmd
biology talk

@@
 SummaryInvest <- merge(SummaryInvest,SummaryInvestSpp,by=c("species"),all.x=TRUE)
-SummaryInvest$prop_weight_spp <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)
+SummaryInvest$prop_weight <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)
 SummaryInvest$labels <- paste(SummaryInvest$parts_fewer_yet," (",SummaryInvest$prop_weight,")")
@@
 #plot
-barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.8,cex.names=.8,xlim=c(.5,17.2),col=col.barplot(barplot_data$parts_fewer_yet),ylab="proportion repro investment")
-legend(13.5,1,legend=barplot_data$parts_fewer_yet,pch=16, cex=1.2,bty="n",col=col.barplot(barplot_data$parts_fewer_yet))
-#dev.off()
+win.metafile("figs2/RA_talk_barplot.wmf", height=4, width=10)
+plot
+par(mfcol=c(1,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.7,cex.names=.7,xlim=c(.5,17.2),col=col.barplot(barplot_data$parts_fewer_yet),ylab="proportion repro investment")
+legend(13.5,1,legend=barplot_data$parts_fewer_yet,pch=16, cex=1,bty="n",col=col.barplot(barplot_data$parts_fewer_yet))
+
+dev.off()
 ##For pie charts

### 2015-10-13 Biology_talk2.Rmd
updated biology talk

--- 2015-10-08 Biology_talk.rmd
@@
+repro vs. leaf investment for all species
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=8, fig.height=8}
+win.metafile("figs2/RA_all_spp1.wmf", height=5, width=5)
+plot
+par(mfrow=c(1,1), cex=1, omi=c(.7,.7,.1,.1), mai=c(.1,.1,.1,0.1)) 
+mod <- lm(log(growth_leaf)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
+plot((1+repro_inv)~growth_leaf, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),xlab="",ylab="")
+#words.top.left.logxy(mod)
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+abline(0,1)
+text(2.1,3,srt=45,"RA = 0.5",cex=.7)
+abline(log10(3),1)
+text(2,9,srt=45,"RA = 0.75",cex=.7)
+abline(log10(9),1)
+text(2,25,srt=45,"RA = 0.9",cex=.7)
+abline(log10(19),1)
+text(2,60,srt=45,"RA = 0.95",cex=.7)
+abline(log10(.111),1)
+text(19,3,srt=45,"RA = 0.1",cex=.7)
+abline(log10(.010101),1)
+text(170,2.4,srt=45,"RA = 0.01",cex=.7)
+mtext("reproductive investment (mg)", 2, outer=TRUE,cex=1,line=2)
+mtext("leaf investment (mg)", 1, outer=TRUE,cex=1,line=1.7)
+dev.off()
+```
+
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-win.metafile("figs2/RA_talk_plot1.wmf", height=7, width=4)
+win.metafile("figs2/RA_talk_RA_canopy.wmf", height=7, width=3)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
+yvar <- "RA_leaf_area"
+xvar <- "age"
+
+data <- subset(SummaryInd, species=="BAER"|species=="HATE"|species=="PELA"|species=="PEPU")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
+}
+mtext("canopy species", 3, outer=TRUE,cex=1.2,line=.5)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_RA_early.wmf", height=7, width=3)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
+yvar <- "RA_leaf_area"
+xvar <- "age"
+
+data <- subset(SummaryInd, species=="BOLE"|species=="PILI"|species=="HEPU"|species=="COER")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,2),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
+}
+mtext("early reproducers", 3, outer=TRUE,cex=1.2,line=.5)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_RA_mid.wmf", height=7, width=3)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
+yvar <- "RA_leaf_area"
+xvar <- "age"
+
+data <- subset(SummaryInd, species=="GRBU"|species=="GRSP"|species=="PUTU"|species=="PHPH")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
+}
+mtext("mid-age reproducers", 3, outer=TRUE,cex=1.2,line=.5)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_RA_mid-late.wmf", height=7, width=3)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
+yvar <- "RA_leaf_area"
+xvar <- "age"
+
+data <- subset(SummaryInd, species=="EPMI"|species=="LEES")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
+}
+mtext("epacrids", 3, outer=TRUE,cex=1.2,line=.5)
+dev.off()
+```
+
+RA by age for 4 species
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_plot3.wmf", height=7, width=4)
 plot
 par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
-yvar <- "leaf_weight"
-yvar2 <- "RA"
-yvar3 <- "total_inv"
-yvar4 <- "RA_leaf_area"
-xvar <- "leaf_area_midyear"
-xvar2 <- "age"
-xvar3 <- "height"
+yvar <- "RA_leaf_area"
+xvar <- "age"
 
@@
 
-  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1),cex=1,
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                     col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
 }
-mtext("RA", 2, outer=TRUE,cex=1,line=1.8)
+mtext("RA (based on leaf weight only)", 2, outer=TRUE,cex=1,line=1.8)
 mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
@@
 
+reproductive investment by age for 4 species
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-win.metafile("figs2/RA_talk_plot2.wmf", height=7, width=4)
+win.metafile("figs2/RA_talk_reproinv_by_age.wmf", height=7, width=4)
 plot
-par(mfcol=c(4,1), cex=1, omi=c(.3,.7,.01,.01), mai=c(.4,.15,.3,0.1)) 
-yvar <- "leaf_weight"
-yvar2 <- "RA"
-yvar3 <- "total_inv"
-yvar4 <- "RA_leaf_area"
-xvar <- "leaf_area_midyear"
-xvar2 <- "age"
-xvar3 <- "height"
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+xvar <- "age"
+yvar <- "repro_inv"
 
@@
 
-  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="",cex=1,
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
                     col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
-  arrows(data[[spp]]$leaf_area_midyear,data[[spp]]$growth_inv,data[[spp]]$leaf_area_midyear,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
+  points(repro_inv~age,data2[[spp]],pch=16,cex=0.8)
 }
-mtext("repro + growth investment (mg)", 2, outer=TRUE,cex=1,line=2.5)
-mtext("leaf area (mm^2)", 1, outer=TRUE,cex=1,line=0.5)
+mtext("reproductive investment (mg)", 2, outer=TRUE,cex=1,line=2)
+mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
 dev.off()
@@
 
+leaf investment by age for 4 species
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-win.metafile("figs2/RA_talk_plot3.wmf", height=7, width=4)
+win.metafile("figs2/RA_talk_leafinv_by_age.wmf", height=7, width=4)
 plot
 par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
-yvar <- "leaf_weight"
-yvar2 <- "height"
-yvar3 <- "total_inv"
-yvar4 <- "RA_leaf_area"
-xvar <- "leaf_area_midyear"
-xvar2 <- "age"
-xvar3 <- "height"
+xvar <- "age"
+yvar <- "growth_leaf"
 
@@
 
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
                     col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(growth_leaf~age,data2[[spp]],pch=16,cex=0.8)
 }
-mtext("RA (based on leaf weight only)", 2, outer=TRUE,cex=1,line=1.8)
+mtext("leaf investment (mg)", 2, outer=TRUE,cex=1,line=2.2)
 mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
@@
 
+leaf weight by age for 4 species
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-win.metafile("figs2/RA_talk_plot4.wmf", height=7, width=4)
+win.metafile("figs2/RA_talk_leafweight_x_age.wmf", height=7, width=4)
 plot
@@
 yvar <- "leaf_weight"
-yvar2 <- "height"
-yvar3 <- "total_inv"
-yvar4 <- "RA_leaf_area"
-xvar <- "leaf_area_midyear"
-xvar2 <- "age"
-xvar3 <- "height"
+xvar <- "age"
 
@@
 
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
                     col=col.age(data[[spp]]$age))
@@
 mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
+dev.off()
+```
+
+reproductive investment vs. leaf investment for 4 species
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_LA_tradeoff.wmf", height=7, width=4)
+plot
+
+  for(v in c("growth_leaf_min")) {
+    i <- (SummaryInd[[v]]) > 0
+    SummaryInd[[v]][i] <- 0
+    }
+
+SummaryInd$growth_leaf_nonzero <- SummaryInd$growth_leaf - SummaryInd$growth_leaf_min
+
+par(mfcol=c(4,1), cex=1, omi=c(.6,.6,.01,.01), mai=c(.4,.1,.3,0.1))
+
+yvar <- "growth_leaf_nonzero"
+xvar <- "repro_inv"
+
+data <- subset(SummaryInd,individual!="GRBU_903"&individual!="PELA_905"&individual!="COER_804"&individual!="PEPU_905"&individual!="GRSP_907"&individual!="LEES_907"&(species=="BOLE"|species=="EPMI"|species=="GRBU"|species=="HATE"))
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,xlab="",ylab="",cex=1,log="xy",yaxt="n",
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+    }
+
+mtext("leaf investment (mg) (log scale)", 2, outer=TRUE,cex=1,line=1)
+mtext("reproductive investment (mg)", 1, outer=TRUE,cex=1,line=1.7)
+dev.off()
+```
+
+##Daniel, don't worry past here
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_growthinv_by_age.wmf", height=7, width=4)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+xvar <- "age"
+yvar <- "growth_inv"
+
+data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(growth_inv~age,data2[[spp]],pch=16,cex=0.8)
+}
+mtext("vegetative investment (mg)", 2, outer=TRUE,cex=1,line=2.2)
+mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_H_by_age.wmf", height=7, width=4)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+xvar <- "age"
+yvar <- "height"
+
+data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(height~age,data2[[spp]],pch=16,cex=0.8)
+}
+mtext("height (mm)", 2, outer=TRUE,cex=1,line=2)
+mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_weight_by_age.wmf", height=7, width=4)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+yvar <- "total_weight"
+xvar <- "age"
+
+data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+}
+mtext("plant weight (mg)", 2, outer=TRUE,cex=1,line=2.2)
+mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_plot2.wmf", height=7, width=4)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.7,.01,.01), mai=c(.4,.15,.3,0.1)) 
+yvar <- "total_inv"
+xvar <- "leaf_area_midyear"
+
+data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  arrows(data[[spp]]$leaf_area_midyear,data[[spp]]$growth_inv,data[[spp]]$leaf_area_midyear,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
+}
+mtext("repro + growth investment (mg)", 2, outer=TRUE,cex=1,line=2.5)
+mtext("leaf area (mm^2)", 1, outer=TRUE,cex=1,line=0.5)
 dev.off()
@@
 mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
-dev.off()
-```
-
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-win.metafile("figs2/RA_talk_RA_canopy.wmf", height=7, width=3)
-plot
-par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
-yvar <- "leaf_weight"
-yvar2 <- "height"
-yvar3 <- "total_inv"
-yvar4 <- "RA_leaf_area"
-xvar <- "leaf_area_midyear"
-xvar2 <- "age"
-xvar3 <- "height"
-
-data <- subset(SummaryInd, species=="BAER"|species=="HATE"|species=="PELA"|species=="PEPU")
-data <- split(data, data$species)
-
-data2 <- subset(SummarySppAge[["mean"]])
-data2 <- split(data2, data2$species)
-
-for(spp in names(data)) {
-
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
-                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
-  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
-}
-mtext("canopy species", 3, outer=TRUE,cex=1.2,line=.5)
-dev.off()
-```
-
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-win.metafile("figs2/RA_talk_RA_early.wmf", height=7, width=3)
-plot
-par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
-yvar <- "leaf_weight"
-yvar2 <- "height"
-yvar3 <- "total_inv"
-yvar4 <- "RA_leaf_area"
-xvar <- "leaf_area_midyear"
-xvar2 <- "age"
-xvar3 <- "height"
-
-data <- subset(SummaryInd, species=="BOLE"|species=="PILI"|species=="HEPU"|species=="COER")
-data <- split(data, data$species)
-
-data2 <- subset(SummarySppAge[["mean"]])
-data2 <- split(data2, data2$species)
-
-for(spp in names(data)) {
-
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,2),cex=1,
-                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
-  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
-}
-mtext("early reproducers", 3, outer=TRUE,cex=1.2,line=.5)
-dev.off()
-```
-
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-win.metafile("figs2/RA_talk_RA_mid.wmf", height=7, width=3)
-plot
-par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
-yvar <- "leaf_weight"
-yvar2 <- "height"
-yvar3 <- "total_inv"
-yvar4 <- "RA_leaf_area"
-xvar <- "leaf_area_midyear"
-xvar2 <- "age"
-xvar3 <- "height"
-
-data <- subset(SummaryInd, species=="GRBU"|species=="GRSP"|species=="PUTU"|species=="PHPH")
-data <- split(data, data$species)
-
-data2 <- subset(SummarySppAge[["mean"]])
-data2 <- split(data2, data2$species)
-
-for(spp in names(data)) {
-
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
-                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
-  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
-}
-mtext("mid-age reproducers", 3, outer=TRUE,cex=1.2,line=.5)
-dev.off()
-```
-
-```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-win.metafile("figs2/RA_talk_RA_mid-late.wmf", height=7, width=3)
-plot
-par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.3,.01), mai=c(.4,.4,.3,0.1)) 
-yvar <- "leaf_weight"
-yvar2 <- "height"
-yvar3 <- "total_inv"
-yvar4 <- "RA_leaf_area"
-xvar <- "leaf_area_midyear"
-xvar2 <- "age"
-xvar3 <- "height"
-
-data <- subset(SummaryInd, species=="EPMI"|species=="LEES")
-data <- split(data, data$species)
-
-data2 <- subset(SummarySppAge[["mean"]])
-data2 <- split(data2, data2$species)
-
-for(spp in names(data)) {
-
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
-                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
-  points(RA_leaf_area~age,data2[[spp]],pch=16,cex=0.8)
-}
-mtext("epacrids", 3, outer=TRUE,cex=1.2,line=.5)
 dev.off()

### 2015-10-15 Flowering_parts_charts.Rmd
adding estimates of nectar production to reproduction data

--- 2015-09-09 Flowering_parts_charts.Rmd
@@
+Always run
+Opening files
+
 ``` {r}
@@
 accessoryListShortest <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryListShortest.csv")
+tissue_energy <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/tissue_energy.csv")
+nectar <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/nectar.csv")
 
 col.barplot <- function(x=NULL){
-  ret <- c("cyan4","cyan1","darkslategray3","firebrick","firebrick1","firebrick2","firebrick3","gold","bisque","chartreuse2","chartreuse3","chartreuse4","chartreuse2","deepskyblue",
+  ret <- c("black","cyan4","cyan1","darkslategray3","firebrick","firebrick1","firebrick2","firebrick3","gold","bisque","chartreuse2","chartreuse3","chartreuse4","chartreuse2","deepskyblue",
            "dodgerblue2","deepskyblue","deepskyblue4","darkorange","darkorange1","darkorange2","darkorange3","darkorange4","darkorange3")
-  names(ret) <- c("seed","seed_pod","fruit_mature","bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","fruit_seed_immature",
-                  "bract","pedicel","green_parts","inflorescence_stalk","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green","cone")
+  names(ret) <- c("nectar","seed","seed_pod","fruit_mature","bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","fruit_seed_immature","bract","pedicel","green_parts","inflorescence_stalk","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green","cone")
 
@@
 }
+```
+
+Always run 
+process nectar
+```{r}
+Invest_nectar <-subset(Invest2,(species=="BAER"|species=="GRBU"|species=="GRSP"|species=="HATE")&part=="flower_stigma")
+Invest_nectar$part ="nectar"
+Invest_nectar$parts_fewer ="nectar"
+Invest_nectar$parts_fewer_yet ="nectar"
+Invest_nectar$weight = 0
+
+SummaryNectar <- 
+  Invest_nectar %>%
+  group_by(parts_fewer_yet,species) %>%
+  summarise_each(funs(sum),count)
+
+SummaryNectar<- merge(SummaryNectar,nectar, by=c("species"),all.x=TRUE)
+SummaryNectar$tissue_energy <- SummaryNectar$count*SummaryNectar$days*SummaryNectar$energy_daily/1000
+SummaryNectar <- select(SummaryNectar,-count,-days,-energy_daily, -part)
+SummaryNectar$accessory_part = "nectar"
 ```
@@
 ```
+View(SummaryInvest)
 
@@
 SummaryInvest <- merge(SummaryInvest,SummaryInvestSpp,by=c("species"),all.x=TRUE)
-SummaryInvest$prop_weight_spp <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)
+SummaryInvest$prop_weight <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)
+
+SummaryInvest <- merge(SummaryInvest,tissue_energy,by=c("parts_fewer_yet"),all.x=TRUE)
+SummaryInvest$tissue_energy <- SummaryInvest$weight*SummaryInvest$energy/1000
+
+SummaryInvest <- bind_rows(SummaryInvest,SummaryNectar)
+
+SummaryEnergySpp <- 
+  SummaryInvest %>%
+  group_by(species) %>%
+  summarise_each(funs(sum),tissue_energy)
+
+names(SummaryEnergySpp) <- c("species","energy_spp")
+SummaryInvest <- merge(SummaryInvest,SummaryEnergySpp,by=c("species"),all.x=TRUE)
+SummaryInvest$prop_energy <- round(SummaryInvest$tissue_energy / SummaryInvest$energy_spp,digits=3)
+
 SummaryInvest$labels <- paste(SummaryInvest$parts_fewer_yet," (",SummaryInvest$prop_weight,")")
-SummaryInvest <- SummaryInvest[order(factor(SummaryInvest$parts_fewer_yet,levels=c(c("bud","petals","calyx","finished_flower","fruit_seed_immature","seed","seed_pod","fruit_mature","bract","pedicel","inflorescence_stalk","green_parts","cone")))),]
+SummaryInvest <- SummaryInvest[order(factor(SummaryInvest$parts_fewer_yet,levels=c(c("nectar","bud","petals","calyx","finished_flower","fruit_seed_immature","seed","seed_pod","fruit_mature","bract","pedicel","inflorescence_stalk","green_parts","cone")))),]
 ```
+
+View(SummaryInvest)
+View(Invest2)
 
@@
 
-View(SummaryInvestParts)
+unique(SummaryInvestParts$parts_fewer)
 
@@
 
+#barplot by dry weight
 ```{r}
@@
 #plot
-barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.8,cex.names=.8,xlim=c(.5,17.2),col=col.barplot(barplot_data$parts_fewer_yet),ylab="proportion repro investment")
-legend(13.5,1,legend=barplot_data$parts_fewer_yet,pch=16, cex=1.2,bty="n",col=col.barplot(barplot_data$parts_fewer_yet))
+#win.metafile("figs2/RA_talk_barplot.wmf", height=4, width=10)
+#plot
+par(mfcol=c(1,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.7,cex.names=.7,xlim=c(.5,17.2),col=col.barplot(barplot_data$parts_fewer_yet),ylab="proportion repro investment")
+legend(13.5,1,legend=barplot_data$parts_fewer_yet,pch=16, cex=1,bty="n",col=col.barplot(barplot_data$parts_fewer_yet))
+
 #dev.off()
+```
+
+#barchart by kJ
+```{r}
+barplot_data <- select(SummaryInvest,species, parts_fewer_yet, prop_energy)
+barplot_data <- spread(barplot_data,species,prop_energy,fill=0,drop=FALSE)
+barplot_data <- barplot_data[order(factor(barplot_data$parts_fewer_yet,levels=c(c("nectar",
+  "bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","fruit_seed_immature","seed","seed_pod","fruit_mature",
+  "bract","pedicel","inflorescence_stalk","green_parts","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green","cone")))),]
+
+barplot_data_matrix <- as.matrix(barplot_data[2:15])
+
+pdf("figs2/Flower_parts_barchart_energy.pdf", height=8, width=11)
+
+#win.metafile("figs2/RA_talk_barplot_energy.wmf", height=4, width=10)
+plot
+par(mfcol=c(1,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.7,cex.names=.7,xlim=c(.5,17.2),col=col.barplot(barplot_data$parts_fewer_yet),ylab="proportion repro investment")
+legend(13.5,1,legend=barplot_data$parts_fewer_yet,pch=16, cex=1,bty="n",col=col.barplot(barplot_data$parts_fewer_yet))
+
+dev.off()
+```
+
 ##For pie charts
-
+```{r}
 data <- subset(SummaryInvest,weight>0)

### 2015-10-15 results_growth.Rmd
little changes

@@
 par(mfrow=c(2,2), cex=1, omi=c(.5,0.3,.1,0.2), mai=c(.5,1,.6,0.2)) 
-plot(growth_inv ~ LMA,data=subset(SummarySppAge,age==1.4),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Seedlings")
-text(growth_inv ~ LMA, data=subset(SummarySppAge,age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv ~ LMA, data=subset(SummarySppAge,age==1.4))
+plot(growth_leaf ~ LMA,data=subset(SummarySppAge[["mean"]],age==1.4),log="xy",pch=16,cex=1,xlab="",ylab="",main="Seedlings")
+text(growth_leaf ~ LMA, data=subset(SummarySppAge[["mean"]],age==1.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_leaf ~ LMA, data=subset(SummarySppAge[["mean"]],age==1.4))
 words.bottom.right.logxy(mod)
 
-plot(growth_inv ~ LMA,data=subset(SummarySppAge,age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
-text(growth_inv ~ LMA, data=subset(SummarySppAge,age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
-mod <- lm(growth_inv ~ LMA, data=subset(SummarySppAge,age==2.4))
+plot(growth_leaf ~ LMA,data=subset(SummarySppAge[["mean"]],age==2.4),log="xy",col="gold1",pch=16,cex=1,xlab="",ylab="",main="Saplings")
+text(growth_leaf ~ LMA, data=subset(SummarySppAge[["mean"]],age==2.4), labels=species, pos=1, offset=-1.1, cex=0.7,col="blue")
+mod <- lm(growth_leaf ~ LMA, data=subset(SummarySppAge[["mean"]],age==2.4))
 words.bottom.right.logxy(mod)
@@
 
-plot(growth_inv ~ LMA,data=subset(SummarySppAge,age>3),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(growth_inv ~ LMA, data=subset(SummarySppAge,age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(growth_inv ~ LMA, data=subset(SummarySppAge,age>3))
+plot(growth_leaf ~ LMA,data=subset(SummarySppAge[["mean"]],age>3),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_leaf ~ LMA, data=subset(SummarySppAge[["mean"]],age>3), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_leaf ~ LMA, data=subset(SummarySppAge[["mean"]],age>3))
 words.bottom.right.logxy(mod)
 
-plot(growth_inv ~ LMA,data=subset(SummarySppAge,age>3&species!="HATE"),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Adults")
-text(growth_inv ~ LMA, data=subset(SummarySppAge,age>3&species!="HATE"), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
-mod <- lm(growth_inv ~ LMA, data=subset(SummarySppAge,age>3&species!="HATE"))
+plot(growth_leaf~ LMA,data=subset(SummarySppAge[["mean"]],age>3&species!="HATE"),log="xy",col=col.age(),pch=16,cex=1,xlab="",ylab="",main="Adults")
+text(growth_leaf ~ LMA, data=subset(SummarySppAge[["mean"]],age>3&species!="HATE"), labels=species, pos=1, offset=-1.1, cex=0.6,col="blue")
+mod <- lm(growth_leaf ~ LMA, data=subset(SummarySppAge[["mean"]],age>3&species!="HATE"))
 words.bottom.right.logxy(mod)

### 2015-10-15 results_growth_short.Rmd
little changes

@@
 SummaryIndPCA <- SummaryInd %>%
-  filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0) %>%
-  select(prop_maxH,height,maxH,WD,LMA,seed_size,growth_leaf,
+  filter(shoot_leaf_count>0&shoot_leaf_area>0&shoot_growth_leaf_area!=0,RA_leaf_area>0) %>%
+  select(prop_maxH,height,maxH,wood_density,LMA,seed_size,growth_leaf,
          growth_stem_diameter,leaf_area,growth_shoot_area,growth_stem_area,shoot_leaf_count,total_weight,
-         RA,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area,RGR)
+         RA_leaf_area,seedset,repro_all_count,accessory_inv,propagule_inv,shoot_leaf_area,shoot_growth_leaf_area,RGR)
 
@@
 PCA_scores <- as.data.frame(PCA_mod$x)
-PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$shoot_leaf_count>0&SummaryInd$shoot_growth_leaf_area!=0)
+PCA_scores$individual <- subset(SummaryInd$individual, SummaryInd$shoot_leaf_count>0&SummaryInd$shoot_leaf_area>0&SummaryInd$shoot_growth_leaf_area!=0&SummaryInd$RA_leaf_area>0)
 SummaryInd_PCA_results <- merge(SummaryInd,PCA_scores, by="individual", all.x=TRUE)
@@
 PCA_by_species <- SummaryInd_PCA_results %>%
-  filter(shoot_leaf_count>0) %>%
+  filter(SummaryInd$shoot_leaf_count>0&SummaryInd$shoot_leaf_area>0&SummaryInd$shoot_growth_leaf_area!=0&SummaryInd$RA_leaf_area>0) %>%
   group_by(species) %>%
@@
 
-plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species),xlim=c(-.1,.1))
-arrows(0, 0, (.9*PCA_loadings$PC2_scale), (.9*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
+plot(PC1_scale~(PC2_scale),SummaryInd_PCA_results,pch=16,col=col.spp(species))
+arrows(0, 0, (.1*PCA_loadings$PC2_scale), (.1*PCA_loadings$PC1_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)
 text(PC1_scale ~ PC2_scale, PCA_loadings, labels=variables, pos=1, offset=0, cex=1,col="black")
@@
 
-mean1 <- PCA_by_species$PC1_scale
+mean1 <- PCA_by_species$PC1_scale_mean
 se1 <- PCA_by_species$PC1_scale_se
@@
 
-plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species),ylim=c(-.15,.15))
+plot(PC4_scale~PC1_scale,SummaryInd_PCA_results,pch=16,col=col.spp(species))
 arrows(0, 0, (.9*PCA_loadings$PC1_scale), (.9*PCA_loadings$PC4_scale), length = 0.25, angle = 30, code = 2, col = "red",lwd=2)

### 2015-12-03 Flowering_parts_charts.Rmd
small changes

@@
 ```
+View(Invest2)
 
@@
 ```
+
+by "part"
+```{r}
+SummaryInvest <- 
+  Invest2 %>%
+  group_by(part,species) %>%
+  summarise_each(funs(sum),weight)
+
+#SummaryInvest <- merge(SummaryInvest,select(accessoryListShort,-sort), by=c("species","parts_fewer"),all.x=TRUE)
+
+SummaryInvestSpp <- 
+  Invest2 %>%
+  group_by(species) %>%
+  summarise_each(funs(sum),weight)
+
+names(SummaryInvestSpp) <- c("species","weight_spp")
+
+SummaryInvest <- merge(SummaryInvest,SummaryInvestSpp,by=c("species"),all.x=TRUE)
+SummaryInvest$prop_weight <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)
+#SummaryInvest$labels <- paste(SummaryInvest$parts_fewer," (",SummaryInvest$prop_weight,")")
+#SummaryInvest <- SummaryInvest[order(factor(SummaryInvest$parts_fewer,levels=c(c("seed","seed_pod","fruit_mature","bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","bract","pedicel","inflorescence_stalk","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green")))),]
+```
+
 View(SummaryInvest)
@@
 
+##For pie charts for overall species allocation
+```{r}
+data <- subset(SummaryInvest,weight>0)
+data <- split(data, data$species)
+
+pdf("figs2/Flower_parts_species_all.pdf", height=11, width=8)
+plot
+par(mfrow=c(3,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
+for(spp in names(data)) {
+  pie(data[[spp]]$weight,labels=data[[spp]]$part,main=spp,col=col.barplot(data[[spp]]$parts_fewer_yet),cex=0.8)
+}
+dev.off()
+```
+
 ##For pie charts
@@
 }
-dev.off()
+#dev.off()
 ```

### 2015-12-09 Accessory_figs_2015_12.Rmd
looking at data - mostly thinking about accessory costs, seed set

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(seedset~prepollen_all_count,data=subset(SummaryInd,seedset>0),col=col.spp(species),pch=16,log="xy")

plot(total_weight~prepollen_all_count,data=subset(SummaryInd,prepollen_all_count>0),col=col.spp(species),pch=16,log="xy")
plot(seed_size~prepollen_all_count,data=subset(SummaryInd,prepollen_all_count>0),col=col.spp(species),pch=16,log="xy")
#points(seed_size~prepollen_all_count,data=subset(SummarySpp[["mean"]],prepollen_all_count>0),col=col.spp(species),pch=16,cex=2)

plot(seed_size~seed_count,data=subset(SummaryInd,seed_count>0),col=col.spp(species),pch=16,log="xy")
points(seed_size~seed_count,data=subset(SummarySpp[["mean"]],seed_count>0),col=col.spp(species),pch=16,cex=2)

plot(seed_size~seedset,data=subset(SummaryInd,seed_count>0),col=col.spp(species),pch=16,log="xy")
points(seed_size~seedset,data=subset(SummarySpp[["mean"]],seed_count>0),col=col.spp(species),pch=16,cex=2)
mod<-lm(log(seedset)~log(seed_size),data=subset(SummaryInd,seed_count>0))
words.bottom.left.logxy(mod)
```

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(seedset~prop_propagule,SummaryInd,col=col.spp(species),pch=16,log="xy")
abline(0,1)

plot(seedset~propagule_per_seed,SummaryInd,col=col.spp(species),pch=16,log="xy")
points(seedset~propagule_per_seed,SummarySpp[["mean"]],col=col.spp(species),pch=16,cex=2)
mod <- lm(log(propagule_per_seed)~log(seedset),data=subset(SummaryInd,seedset>0))
words.bottom.left.logxy(mod)

plot(seedset~prop_propagule,SummaryInd,col=col.spp(species),pch=16,log="xy")
points(seedset~prop_propagule,SummarySpp[["mean"]],col=col.spp(species),pch=16,cex=2)
mod <- lm(log(prop_propagule)~log(seedset),data=subset(SummaryInd,seedset>0))
words.bottom.left.logxy(mod)
#text(seedset~propagule_per_seed,data=subset(SummaryInd,species=="PELA"),labels=individual,offset=1)

par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
xvar <- "seedset"
yvar <- "prop_propagule"

data <- subset(SummaryInd,seedset>0&prop_propagule>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1, 
                    main=spp,col=col.age(data[[spp]]$age),xlim=c(0.0005,.6),ylim=c(0.0005,.6))
}
```

```{r}
data <- subset(SummaryInd)
data <- split(data, data$species)

#pdf("figs2/Flower_parts_fewer.pdf", height=11, width=8)
#plot
par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
for(spp in names(data)) {
  pie(data[[spp]]$weight,labels=data[[spp]]$labels,main=spp,col=col.barplot(data[[spp]]$parts_fewer_yet),cex=0.8)
}
#dev.off()
```

```{r}
par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(accessory_per_seed~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(accessory_inv~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(seedset~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
plot(seedset~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="y")
```

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
xvar <- "total_weight"
yvar <- "prepollen_all_count"

data <- subset(SummaryInd,prepollen_all_count>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1, 
                    main=spp,col=col.age(data[[spp]]$age))
}
```

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
xvar <- "growth_leaf"
yvar <- "seedset"

data <- subset(SummaryInd,seedset>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1, 
                    main=spp,col=col.age(data[[spp]]$age))
}
```

mod <- lm(log(seedset)~log(prepollen_all_count)*log(growth_leaf)*log(total_weight),data=subset(SummaryInd,seedset>0&growth_leaf>0))
summary(mod)
plot(mod)

mod <- lm(log(prepollen_all_count)~log(growth_leaf)*log(total_weight)*log(maxH),data=subset(SummaryInd,seedset>0&growth_leaf>0))
summary(mod)
plot(mod)

plot(seedset~total_weight,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy")
mod <- lm(log(total_weight)~log(seedset),SummarySpp[["mean"]])
words.top.right.logxy(mod)

plot(seedset~total_weight,data=subset(SummaryInd,seedset>0),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(seedset)~log(total_weight)*species,data=subset(SummaryInd,seedset>0))
words.top.right.logxy(mod)
summary(mod)

plot(seedset~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x")
mod <- lm(log(seed_size)~seedset,SummarySpp[["mean"]])
words.top.right.logx(mod)

plot(seedset~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x")
mod <- lm(log(seed_size)~seedset,SummarySpp[["mean"]])
words.top.right.logx(mod)

plot(seedset~total_weight,data=subset(SummaryInd,seedset>0),col=col.spp(species),pch=16,log="xy")
mod <- lm(log(total_weight)~log(seedset),data=subset(SummaryInd,seedset>0))
words.top.right.logxy(mod)

par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))

plot(accessory_inv~seed_size,SummaryInd,col=col.spp(species),pch=16,log="xy")
points(accessory_inv~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,cex=2)

plot(accessory_per_seed~seed_size,SummaryInd,col=col.spp(species),pch=16,log="xy")
points(accessory_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,cex=2)

plot(prop_propagule~seed_size,SummaryInd,col=col.spp(species),pch=16,log="xy")
points(prop_propagule~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,cex=2)
mod <- lm (log(seed_size)~log(prop_propagule), data=subset(SummaryInd,prop_propagule>0&species!="EPMI"))
words.bottom.right.logxy(mod)

plot(prop_propagule~total_inv,SummaryInd,col=col.spp(species),pch=16,log="xy")
points(prop_propagule~total_inv,SummarySpp[["mean"]],col=col.spp(species),pch=16,cex=2)

names(Table1) <- c("Variable","r2","intercept","slope")
Table1[1] <- c("Total reproductive investment",summary(mod)[8]

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
options(scipen=10)
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
mod <- lm (log(total_weight)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
plot(repro_inv~total_weight,data=subset(SummaryInd,repro_inv>0), log="xy",xlab="", col=col.spp(species), pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
words.bottom.right.logxy(mod)

mod <- lm (log(total_weight)~log(fruit_weight), data=subset(SummaryInd,fruit_weight>0))
plot(fruit_weight~total_weight,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp(species), pch=16, ylab="Fruit investment (mg)",xlim=c(100,2000000),xlab="")
words.bottom.right.logxy(mod)

mod <- lm (log(total_weight)~log(propagule_inv), data=subset(SummaryInd,propagule_inv>0))
plot(propagule_inv~total_weight,data=subset(SummaryInd,propagule_inv>0), log="xy",col=col.spp(species), pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(total_weight)~log(prepollen_all_inv), data=subset(SummaryInd,prepollen_all_inv>0))
plot(prepollen_all_inv~total_weight,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp(species), pch=16, xlab="", ylab="Prepollen investment (mg)", xlim=c(100,2000000))
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mtext("Total plant size (mg)",1, outer=TRUE,cex=1.2)
```

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
options(scipen=10)
par(mfrow=c(2,2), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(.8,1,.3,0.3))
mod <- lm (log(total_inv)~log(repro_inv), data=subset(SummaryInd,repro_inv>0))
plot(repro_inv~total_inv,data=subset(SummaryInd,repro_inv>0), log="xy",xlab="", col=col.spp(species), pch=16, ylab="Total reproductive investment (mg)",xlim=c(100,2000000))
words.bottom.right.logxy(mod)

mod <- lm (log(total_inv)~log(fruit_weight), data=subset(SummaryInd,fruit_weight>0))
plot(fruit_weight~total_inv,data=subset(SummaryInd,fruit_weight>0), log="xy",col=col.spp(species), pch=16, ylab="Fruit investment (mg)",xlim=c(100,2000000),xlab="")
words.bottom.right.logxy(mod)

mod <- lm (log(total_inv)~log(propagule_inv), data=subset(SummaryInd,propagule_inv>0))
plot(propagule_inv~total_inv,data=subset(SummaryInd,propagule_inv>0), log="xy",col=col.spp(species), pch=16, xlab="", ylab="Propagule investment (mg)", xlim=c(100,2000000))
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mod <- lm (log(total_inv)~log(prepollen_all_inv), data=subset(SummaryInd,prepollen_all_inv>0))
plot(prepollen_all_inv~total_inv,data=subset(SummaryInd,prepollen_all_inv>0), log="xy",col=col.spp(species), pch=16, xlab="", ylab="Prepollen investment (mg)", xlim=c(100,2000000))
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logxy(mod)

mtext("Total invesment (mg)",1, outer=TRUE,cex=1.2)
```

mod <- lm (log(total_inv)~(prop_prepollen_all), data=subset(SummaryInd,prepollen_all_inv>0))
plot(prop_prepollen_all~total_inv,data=subset(SummaryInd,prepollen_all_inv>0), log="x",col=col.spp(species), pch=16, xlab="", ylab="Prepollen investment (mg)", xlim=c(100,2000000))
legend("topright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
words.bottom.right.logx(mod)

```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=7.5,fig.height=7.5}
par(mfrow=c(1,1), cex=1, omi=c(.6,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(prop_fruit~RA,data=subset(SummaryInd,prop_propagule>0),log="y",pch=16,col=col.age(age))
mod <- lm(log(prop_fruit)~(RA)*(age),data=subset(SummaryInd,prop_propagule>0&age>3))
  summary(mod)

abline(0,1)
abline(-0.30103,1)
abline(-1,1)
text(120,350,"all RE to accessory tissues",srt=45)
text(12000,720,"10% RE to accessory tissues",srt=45)
text(5,1.5,"50%",srt=45)
```

```
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
xvar <- "RA"
yvar <- "prop_propagule"

data <- subset(SummaryInd,prop_propagule>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  ((x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=1, 
                    main=spp,col=col.age(data[[spp]]$age))
}
```

InvestPetal <- subset(SummaryInvest,parts_fewer=="petals")
View(InvestPetal)
plot(prop_weight,SummaryInvest,color=col.spp(parts_fewer))

SummaryInd$prop_fruit <- SummaryInd$fruit_weight / SummaryInd$repro_inv

### 2015-12-09 Flowering_parts_charts.Rmd
looking at data - mostly thinking about accessory costs, seed set

@@
 
+col.accessory <- function(x=NULL){
+  ret <- c("firebrick1","firebrick","deepskyblue1","deepskyblue3","deepskyblue4")
+  names(ret) <- c("prepollination_abort","prepollination_success","postpollination_abort","packaging_dispersal","propagule")
+
+  if(!is.null(x)) {
+    ret <- ret[as.character(x)]
+  }
+  ret
+}
+
 labels.barplot <- function(x=NULL){
@@
 }
+```
 
+Invest2 for accessory part
+``` {r}
 Invest2 <- merge(InvestmentByPart,select(accessoryList,-sort), by=c("species","part"))
@@
 ```
-View(Invest2)
+
+names(Invest2)
 
@@
   group_by(part,species) %>%
+  summarise_each(funs(sum),weight)
+
+#SummaryInvest <- merge(SummaryInvest,select(accessoryListShort,-sort), by=c("species","parts_fewer"),all.x=TRUE)
+
+SummaryInvestSpp <- 
+  Invest2 %>%
+  group_by(species) %>%
+  summarise_each(funs(sum),weight)
+
+names(SummaryInvestSpp) <- c("species","weight_spp")
+
+SummaryInvest <- merge(SummaryInvest,SummaryInvestSpp,by=c("species"),all.x=TRUE)
+SummaryInvest$prop_weight <- round(SummaryInvest$weight / SummaryInvest$weight_spp,digits=3)
+#SummaryInvest$labels <- paste(SummaryInvest$parts_fewer," (",SummaryInvest$prop_weight,")")
+#SummaryInvest <- SummaryInvest[order(factor(SummaryInvest$parts_fewer,levels=c(c("seed","seed_pod","fruit_mature","bud","petals","stigma","style","finished_flower","calyx","fruit_immature","seed_immature","seed_aborted","bract","pedicel","inflorescence_stalk","cone_aborted","cone_base_brown","cone_base_green","cone_brown","cone_green")))),]
+```
+
+by "accessory_part"
+```{r}
+SummaryInvest <- 
+  Invest2 %>%
+  group_by(accessory_part,species) %>%
   summarise_each(funs(sum),weight)
@@
 
+#barplot by accessory grouping
+```{r}
+barplot_data <- select(SummaryInvest,species, accessory_part, prop_weight)
+barplot_data <- spread(barplot_data,species,prop_weight,fill=0,drop=FALSE)
+barplot_data <- barplot_data[order(factor(barplot_data$accessory_part,levels=c(c(
+  "prepollination_abort","prepollination_success","postpollination_abort","packaging_dispersal","propagule")))),]
+
+barplot_data_matrix <- as.matrix(barplot_data[2:15])
+
+#pdf("figs2/Flower_parts_barchart.pdf", height=8, width=11)
+#plot
+#win.metafile("figs2/RA_talk_barplot.wmf", height=4, width=10)
+#plot
+par(mfcol=c(1,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+midpoints <- barplot(barplot_data_matrix,beside=FALSE,width=0.8,cex.axis=.7,cex.names=.7,xlim=c(.5,17.2),col=col.accessory(barplot_data$accessory_part),ylab="proportion repro investment")
+legend(13.5,1,legend=barplot_data$accessory_part,pch=16, cex=1,bty="n",col=col.accessory(barplot_data$accessory_part))
+
+#text(midpoints,(barplot_data_matrix), labels=barplot_data_matrix)
+#dev.off()
+```
+
 #barchart by kJ
@@
 
-pdf("figs2/Flower_parts_fewer.pdf", height=11, width=8)
+#pdf("figs2/Flower_parts_fewer.pdf", height=11, width=8)
 plot
-par(mfrow=c(2,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
+par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
 for(spp in names(data)) {
-  pie(data[[spp]]$weight,labels=data[[spp]]$labels,main=spp,col=col.barplot(data[[spp]]$parts_fewer_yet),cex=0.8)
+  pie(data[[spp]]$weight,labels=data[[spp]]$accessory_part,main=spp,col=col.accessory(data[[spp]]$accessory_part),cex=0.8)
 }

### 2015-12-16 Accessory_figs_2015_12.Rmd
accessory costs patterns

@@
+```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
+SummaryInd$costs_for_seed <- SummaryInd$seed_count * SummaryInd$seedcosts
+SummaryInd$costs_for_aborted <- SummaryInd$repro_inv - SummaryInd$costs_for_seed
+plot(costs_for_seed ~ costs_for_aborted,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
+SummaryInd$prop_aborted <- SummaryInd$costs_for_aborted / SummaryInd$repro_inv
+plot(prop_aborted ~ age, data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="x")
+
+plot(costs_for_seed ~ repro_inv,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
+abline(0,1)
+
+par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
+xvar <- "costs_for_aborted"
+yvar <- "costs_for_seed"
+
+data <- subset(SummaryInd,seedset>0&prop_propagule>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1, 
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+```
+
+```{r}
+par(mfrow=c(2,3), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
+#total reproductive investment much stronger correlation with total weight 
+win.metafile("figs2/best_correlate2.wmf", height=6, width=12)
+plot
+
+par(mfrow=c(1,3), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
+plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
+mod <- lm(log(total_weight_0)~log(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
+words.top.left.logxy(mod)
+
+plot(repro_inv~total_weight_0,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
+mod <- lm(log(total_weight_0)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
+words.top.left.logxy(mod)
+
+plot(prepollen_all_inv~total_weight_0,data=subset(SummaryInd,prepollen_all_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
+mod <- lm(log(total_weight_0)~log(prepollen_all_inv),data=subset(SummaryInd,prepollen_all_inv>0))
+words.top.left.logxy(mod)
+
+dev.off()
+
+plot(propagule_inv~total_inv,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(total_inv)~log(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
+words.top.left.logxy(mod)
+
+plot(repro_inv~total_inv,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(total_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
+words.top.left.logxy(mod)
+
+plot(prepollen_all_inv~total_inv,data=subset(SummaryInd,prepollen_all_inv>0),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(total_inv)~log(prepollen_all_inv),data=subset(SummaryInd,prepollen_all_inv>0))
+words.top.left.logxy(mod)
+
+#shift in accessory costs per seed with seed size
+par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
+win.metafile("figs2/accessory_per_seed_vs_seed_size.wmf", height=6, width=6)
+plot
+plot(accessory_per_seed~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+points(accessory_per_seed~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummarySpp[["mean"]]))
+words.top.left.logxy(mod)
+summary(mod)
+abline(log(5),1)
+dev.off()
+
+#each species follows its own linear trajectory, but species lines are offset from one another
+#species with lower intercepts have greater benefit if seed count is metric that matters; species with higher intercept less disadvntaged is a few heavy seeds worth as much as many smaller seeds
+win.metafile("figs2/accessory_per_seed_vs_prop_propagule.wmf", height=6, width=6)
+plot
+plot(accessory_per_seed~prop_propagule,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+dev.off()
+```
+
+plot(seed_count~accessory_per_seed,data=subset(SummarySpp[["mean"]],seed_count>1),col=col.spp(species),pch=16,log="xy")
+```{r}
+plot(accessory_per_seed~growth_leaf,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+points(accessory_per_seed~growth_leaf,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log(growth_leaf)~log(accessory_per_seed),data=subset(SummarySpp[["mean"]]))
+words.top.left.logxy(mod)
+
+plot(prop_propagule~growth_leaf,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+points(prop_propagule~growth_leaf,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log(growth_leaf)~log(prop_propagule),data=subset(SummarySpp[["mean"]]))
+words.bottom.left.logxy(mod)
+
+plot(accessory_per_seed~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummarySpp[["mean"]]))
+words.top.left.logxy(mod)
+abline(log(5),1)
+
+plot(prop_propagule~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+points(prop_propagule~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log(seed_size)~log(prop_propagule),data=subset(SummarySpp[["mean"]]))
+words.top.left.logxy(mod)
+
+plot(costs_per_seed~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+plot(seedset~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+```
+
+plot(accessory_per_seed~prop_propagule,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+points(accessory_per_seed~prop_propagule,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
+
 ```{r, echo=FALSE,message=FALSE,warning=FALSE,fig.width=14, fig.height=14}
@@
 ```{r}
+par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
+xvar <- "age"
+yvar <- "seedset"
+
+data <- subset(SummaryInd,seedset>0&age>3)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1, 
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+```
+
+```{r}
 data <- subset(SummaryInd)
@@
 plot(seedset~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="y")
+plot(accessory_per_seed~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="y")
+plot(propagule_inv~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+plot(propagule_inv~repro_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+plot(propagule_inv~total_weight,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+plot(repro_inv~total_weight,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+abline(0,1)
 ```
@@
 
+```{r}
 SummaryInd$prop_fruit <- SummaryInd$fruit_weight / SummaryInd$repro_inv
+
+SummaryInd$costs_for_seeds_produced <- SummaryInd$costs_per_seed*SummaryInd$seed_count
+SummaryInd$costs_for_aborted <- SummaryInd$repro_inv - SummaryInd$costs_for_seeds_produced
+
+plot(costs_for_seeds_produced~costs_for_aborted,data=subset(SummaryInd,seed_count>0),log="xy",col=col.spp(species), pch=16)
+
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+xvar <- "costs_for_aborted"
+yvar <- "costs_for_seeds_produced"
+
+data <- subset(SummaryInd,prop_propagule>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1, 
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+```
+
+plot(seedcosts~seed_size,data=subset(SummaryInd),log="xy",col=col.spp(species), pch=16)
+plot(accessory_per_seed~seed_size,data=subset(SummaryInd),log="xy",col=col.spp(species), pch=16)

### 2015-12-16 Flowering_parts_charts.Rmd
accessory costs patterns

@@
 #plot
-#win.metafile("figs2/RA_talk_barplot.wmf", height=4, width=10)
-#plot
+
+win.metafile("figs2/accessory_cost_barplot.wmf", height=4, width=10)
+plot
 par(mfcol=c(1,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
@@
 #text(midpoints,(barplot_data_matrix), labels=barplot_data_matrix)
-#dev.off()
+dev.off()
 ```

### 2015-12-18 Accessory_figs_2015_12.Rmd
continuing accessory cost analyses; trying to add in calcs for prepollenation costs - still in progress

@@
 ```{r}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
-SummaryInd$costs_for_seed <- SummaryInd$seed_count * SummaryInd$seedcosts
-SummaryInd$costs_for_aborted <- SummaryInd$repro_inv - SummaryInd$costs_for_seed
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.5,.5)) 
+plot(costs_for_seed ~ seed_size,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
+points(costs_for_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log(seed_size) ~ log(costs_for_seed),data=subset(SummarySpp[["mean"]])) 
+words.top.left.logxy(mod)
+
+plot(costs_for_aborted ~ seed_size,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
+points(costs_for_aborted ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log(seed_size) ~ log(costs_for_aborted),data=subset(SummarySpp[["mean"]])) 
+words.top.left.logxy(mod)
+
+plot(accessory_inv ~ seed_size,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
+points(accessory_inv ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log(seed_size) ~ log(accessory_inv),data=subset(SummarySpp[["mean"]])) 
+words.top.left.logxy(mod)
+abline(mod)
+
 plot(costs_for_seed ~ costs_for_aborted,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy")
-SummaryInd$prop_aborted <- SummaryInd$costs_for_aborted / SummaryInd$repro_inv
-plot(prop_aborted ~ age, data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="x")
+points(costs_for_seed ~ costs_for_aborted,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log(costs_for_seed) ~ log(costs_for_aborted),data=subset(SummarySpp[["mean"]]))
+words.top.left.logxy(mod)
 
@@
 abline(0,1)
+```
 
-par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
-xvar <- "costs_for_aborted"
-yvar <- "costs_for_seed"
+SummaryInd$prop_costs_seed <- SummaryInd$costs_for_seed / SummaryInd$repro_inv
+SummaryInd$prop_costs_aborted <- SummaryInd$costs_for_aborted / SummaryInd$repro_inv
 
-data <- subset(SummaryInd,seedset>0&prop_propagule>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
+```{r}
+win.metafile("figs2/acc_cost_seed_size.wmf", height=6, width=6)
 
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
+plot
+plot(prepollencosts~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",cex=1.3)
+mod <- lm(log(seed_size)~log(accessory_costs),data=subset(SummaryInd))
+words.top.left.logxy(mod)
+abline((log(10)^coef(mod)[1]),coef(mod)[2])
+abline((log(10)^coef(mod)[1]),1,col="red")
 
-for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1, 
-                    main=spp,col=col.age(data[[spp]]$age))
-}
+summary(mod)
+dev.off()
 ```
+
+plot(seedset~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",cex=1)
+points(seedset~accessory_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log(accessory_costs)~log(seedset),data=subset(SummaryInd,seedset>0))
+words.bottom.left.logxy(mod)
+abline((log(10)^coef(mod)[1]),(coef(mod)[2]))
+abline((log(10)^coef(mod)[1]),-1,col="red")
+
+summary(mod)
 
@@
 par(mfrow=c(1,3), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
+plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy")
 mod <- lm(log(total_weight_0)~log(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
@@
 par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-win.metafile("figs2/accessory_per_seed_vs_seed_size.wmf", height=6, width=6)
+win.metafile("figs2/accessory_per_seed_vs_seed_size.wmf", height=6, width=12)
 plot
-plot(accessory_per_seed~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
-points(accessory_per_seed~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
-mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummarySpp[["mean"]]))
+plot(costs_per_seed~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+points(costs_per_seed~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log(seed_size)~log(costs_per_seed),data=subset(SummarySpp[["mean"]]))
 words.top.left.logxy(mod)
 summary(mod)
-abline(log(5),1)
+
+plot(seedcosts~seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",cex=1.3)
+mod <- lm(log(seed_size)~log(seedcosts),data=subset(SummaryInd))
+words.top.left.logxy(mod)
 dev.off()
@@
 ```{r}
-par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-plot(accessory_per_seed~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+#par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
+
+```
+
+```{r}
 plot(accessory_inv~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
-plot(seedset~seedcosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
-plot(seedset~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="y")
-plot(accessory_per_seed~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="y")
-plot(propagule_inv~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+plot(seedset~seedcosts,data=subset(SummaryInd,seedset>0),col=col.spp(species),pch=16,log="x")
+plot(seedset~costs_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="x")
+plot(packaging_dispersal_inv~accessory_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
 plot(propagule_inv~repro_inv,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")

### 2015-12-23 Accessory_figs_2015_12.Rmd
playing around with accessory cost components - plots, statistical tests of slopes

@@
 SummaryInd$prop_costs_aborted <- SummaryInd$costs_for_aborted / SummaryInd$repro_inv
+
+SummaryInd$check <- SummaryInd$prepollen_all_inv / (SummaryInd$count_aborted + SummaryInd$seed_count)
+
+plot(check ~ prepollencosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+abline(0,1)
+
+```{r}
+par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.5,.5)) 
+options(scipen = 999)
+
+plot(seedcosts ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ log(seedcosts),data=subset(SummaryInd, seedcosts>0))
+words.bottom.right.logxy(mod)
+
+plot(prepollencosts ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ log(prepollencosts),data=subset(SummaryInd,prepollencosts>0))
+words.bottom.right.logxy(mod)
+
+plot(abortedcosts ~ seed_size,data=subset(SummaryInd, abortedcosts>.001),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ log(abortedcosts),data=subset(SummaryInd, abortedcosts>0.001))
+words.bottom.right.logxy(mod)
+
+plot(b_div_p ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",ylab="per seed cost to procur pollen")
+mod <- lm(log(seed_size) ~ log(b_div_p),data=subset(SummaryInd,b_div_p>0))
+words.bottom.right.logxy(mod)
+
+plot(c_div_p ~ seed_size,data=subset(SummaryInd,c_div_p>0&species!="COER"),col=col.spp(species),pch=16,log="xy",ylab="per seed cost of aborted fruits and seeds")
+mod <- lm(log(seed_size) ~ log(c_div_p),data=subset(SummaryInd,c_div_p>0&species!="COER"))
+words.bottom.right.logxy(mod)
+
+plot(dispersalcosts_increment ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",ylab="cost of dispersal tissues")
+mod <- lm(log(seed_size) ~ log(dispersalcosts_increment),data=subset(SummaryInd))
+words.bottom.right.logxy(mod)
+
+plot(total_accessory_Lord ~ seed_size,data=subset(SummarySppAge[["mean"]]),col=col.age(age),pch=16,log="xy", ylab="total per seed accessory costs")
+mod <- lm(log(total_accessory_Lord) ~ log(seed_size)*age,data=subset(SummaryInd,total_accessory_Lord>0))
+words.bottom.right.logxy(mod)
+summary(mod)
+
+plot(b_div_p ~ seed_size,data=subset(SummarySppAge[["mean"]]),col=col.age(age),pch=16,log="xy", ylab="per seed cost to procur pollen")
+mod <- lm(log(b_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,b_div_p>0))
+words.bottom.right.logxy(mod)
+summary(mod)
+
+plot(c_div_p ~ seed_size,data=subset(SummarySppAge[["mean"]],c_div_p>0.00001),col=col.age(age),pch=16,log="xy", ylab="per seed cost of aborted fruits and seeds")
+mod <- lm(log(c_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,c_div_p>0.00001))
+words.bottom.right.logxy(mod)
+summary(mod)
+
+plot(dispersalcosts_increment ~ seed_size,data=subset(SummarySppAge[["mean"]]),col=col.age(age),pch=16,log="xy", ylab="per seed cost of packaging and disp")
+mod <- lm(log(dispersalcosts_increment) ~ log(seed_size)*age,data=subset(SummaryInd,dispersalcosts_increment>0))
+words.bottom.right.logxy(mod)
+summary(mod)
+confint(mod)
+
+slopes <- sma(log(dispersalcosts_increment) ~ log(seed_size),data=subset(SummaryInd,dispersalcosts_increment>0),slope.test=1)
+summary(slopes)
+
+slopes <- sma(log(c_div_p) ~ log(seed_size),data=subset(SummaryInd,c_div_p>0),slope.test=1)
+summary(slopes)
+
+slopes <- sma(log(b_div_p) ~ log(seed_size),data=subset(SummaryInd,b_div_p>0),slope.test=1)
+summary(slopes)
+
+plot(seed_to_ovule_ratio ~ total_accessory_Lord,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ total_accessory_Lord,data=subset(SummarySpp[["mean"]]))
+words.bottom.left.logx(mod)
+
+plot(seed_to_ovule_ratio ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="x")
+mod <- lm(log(seed_size) ~ seed_to_ovule_ratio,data=subset(SummarySpp[["mean"]]))
+words.bottom.left.logx(mod)
+```
 

### 2015-12-23 Accessory_figs_2015_12.Rmd
additional plots, stats tests looking at how different components of accessory costs shift with seed size, age
confirming that calculations based on Lord's papers match those I did earlier

--- 2015-12-18 Accessory_figs_2015_12.Rmd
@@
 SummaryInd$prop_costs_aborted <- SummaryInd$costs_for_aborted / SummaryInd$repro_inv
+
+SummaryInd$check <- SummaryInd$prepollen_all_inv / (SummaryInd$count_aborted + SummaryInd$seed_count)
+
+plot(check ~ prepollencosts,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+abline(0,1)
+
+```{r}
+par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.5,.5)) 
+options(scipen = 999)
+
+plot(seedcosts ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ log(seedcosts),data=subset(SummaryInd, seedcosts>0))
+words.bottom.right.logxy(mod)
+
+plot(prepollencosts ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ log(prepollencosts),data=subset(SummaryInd,prepollencosts>0))
+words.bottom.right.logxy(mod)
+
+plot(abortedcosts ~ seed_size,data=subset(SummaryInd, abortedcosts>.001),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ log(abortedcosts),data=subset(SummaryInd, abortedcosts>0.001))
+words.bottom.right.logxy(mod)
+
+plot(b_div_p ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",ylab="per seed cost to procur pollen")
+mod <- lm(log(seed_size) ~ log(b_div_p),data=subset(SummaryInd,b_div_p>0))
+words.bottom.right.logxy(mod)
+
+plot(c_div_p ~ seed_size,data=subset(SummaryInd,c_div_p>0&species!="COER"),col=col.spp(species),pch=16,log="xy",ylab="per seed cost of aborted fruits and seeds")
+mod <- lm(log(seed_size) ~ log(c_div_p),data=subset(SummaryInd,c_div_p>0&species!="COER"))
+words.bottom.right.logxy(mod)
+
+plot(dispersalcosts_increment ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy",ylab="cost of dispersal tissues")
+mod <- lm(log(seed_size) ~ log(dispersalcosts_increment),data=subset(SummaryInd))
+words.bottom.right.logxy(mod)
+
+plot(total_accessory_Lord ~ seed_size,data=subset(SummarySppAge[["mean"]]),col=col.age(age),pch=16,log="xy", ylab="total per seed accessory costs")
+mod <- lm(log(total_accessory_Lord) ~ log(seed_size)*age,data=subset(SummaryInd,total_accessory_Lord>0))
+words.bottom.right.logxy(mod)
+summary(mod)
+```
+
+```{r}
+plot(b_div_p ~ seed_size,data=subset(SummarySppAge[["mean"]]),col=col.age(age),pch=16,log="xy", ylab="per seed cost to procur pollen")
+mod <- lm(log(b_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,b_div_p>0))
+words.bottom.right.logxy(mod)
+summary(mod)
+slopes <- sma(log(b_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,b_div_p>0),slope.test=1)
+summary(slopes)
+
+plot(c_div_p ~ seed_size,data=subset(SummarySppAge[["mean"]],c_div_p>0.00001),col=col.age(age),pch=16,log="xy", ylab="per seed cost of aborted fruits and seeds")
+mod <- lm(log(c_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,c_div_p>0.00001))
+words.bottom.right.logxy(mod)
+summary(mod)
+slopes <- sma(log(c_div_p) ~ log(seed_size),data=subset(SummaryInd,c_div_p>0),slope.test=1)
+summary(slopes)
+
+plot(dispersalcosts_increment ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy", ylab="per seed cost of packaging and disp")
+mod <- lm(log(dispersalcosts_increment) ~ log(seed_size)*age,data=subset(SummaryInd,dispersalcosts_increment>0))
+words.bottom.right.logxy(mod)
+slopes <- sma(log(dispersalcosts_increment) ~ log(seed_size),data=subset(SummaryInd,dispersalcosts_increment>0),slope.test=1)
+summary(slopes)
+
+plot(total_accessory_Lord  ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(total_accessory_Lord) ~ log(seed_size)*age,data=subset(SummaryInd,total_accessory_Lord>0))
+words.bottom.right.logxy(mod)
+slopes <- sma(log(total_accessory_Lord) ~ log(seed_size),data=subset(SummaryInd,total_accessory_Lord>0),slope.test=1)
+summary(slopes)
+
+#calculation of total accessory investment divided by seed count (accessory_per_seed) very closely correlated with accessory costs per seed using the equations in Lord
+plot(total_accessory_Lord  ~ accessory_per_seed,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(total_accessory_Lord) ~ log(accessory_per_seed),data=subset(SummaryInd,total_accessory_Lord>0))
+words.bottom.right.logxy(mod)
+slopes <- sma(log(total_accessory_Lord) ~ log(accessory_per_seed),data=subset(SummaryInd,total_accessory_Lord>0),slope.test=1)
+summary(slopes)
+summary(mod)
+
+plot(seed_to_ovule_ratio ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ log(seed_to_ovule_ratio),data=subset(SummaryInd,seed_to_ovule_ratio>0))
+words.bottom.left.logxy(mod)
+
+#on an energy basis, propagule inv and accessory inv increase 1 to 1; implies seed size is sufficient information, but need to account of additional component
+plot(accessory_inv ~ propagule_inv,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(propagule_inv) ~ log(accessory_inv)*age,data=subset(SummaryInd,propagule_inv>0))
+words.bottom.right.logxy(mod)
+slopes <- sma(log(propagule_inv) ~ log(accessory_inv),data=subset(SummaryInd,propagule_inv>0),slope.test=1)
+summary(slopes)
+```
 

### 2016-01-13 Accessory_figs_2016.Rmd
work on accessory costs paper

```{r}
win.metafile("figs2/best_correlate2.wmf", height=6, width=12)
plot

par(mfrow=c(1,3), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy")
mod <- lm(log10(total_weight_0)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
words.top.left.logxy(mod)

plot(repro_inv~total_weight_0,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
words.top.left.logxy(mod)

plot(prepollen_all_inv~total_weight_0,data=subset(SummaryInd,prepollen_all_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
mod <- lm(log10(total_weight_0)~log10(prepollen_all_inv),data=subset(SummaryInd,prepollen_all_inv>0))
words.top.left.logxy(mod)

dev.off()
```

```{r}
win.metafile("figs2/acc_cost_seed_size_4panel.wmf", height=9, width=9)

plot
par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.5,.5)) 
options(scipen = 5)

plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="total per seed accessory costs")
mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
words.top.left.logxy(mod)
slopes <- sma(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],slope.test=1))
summary(slopes)
slopes2 <- as.matrix(coef(slopes))
abline((slopes2[1]),(slopes2[2]))
abline((slopes2[1]),1,col="red")

plot(b_div_p ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="pre-pollination accessory costs")
mod <- lm(log10(b_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
words.top.left.logxy(mod)
slopes <- sma(log10(b_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],slope.test=1))
summary(slopes)
slopes2 <- as.matrix(coef(slopes))
abline((slopes2[1]),(slopes2[2]))
abline((slopes2[1]),1,col="red")

plot(c_div_p ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylab="aborted fruit accessory costs")
mod <- lm(log10(c_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
words.top.left.logxy(mod)
slopes <- sma(log10(c_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1)
summary(slopes)
slopes2 <- as.matrix(coef(slopes))
abline((slopes2[1]),(slopes2[2]))
abline((slopes2[1]),1,col="red")

plot(dispersalcosts_increment ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="dispersal & packaging accessory costs")
mod <- lm(log10(dispersalcosts_increment) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"))
words.top.left.logxy(mod)
slopes <- sma(log10(dispersalcosts_increment) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
summary(slopes)
slopes2 <- as.matrix(coef(slopes))
abline((slopes2[1]),(slopes2[2]))
abline((slopes2[1]),1,col="red")
dev.off()
```

#all species show a strong correlation between seedset and the proportion of reproductive investment that is for propagules. However, the slope of the relationship is hugely different across species - some species can still have very low seedset, but show a big shift in what proportion of their energy goes to propagules
##would be good for lines for each species  to just extend from 0 to max seedset for that species
```{r}
win.metafile("figs2/seedset_vs_propPropagule.wmf", height=6, width=6)

plot
par(mfrow=c(1,1), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))

yvar <- "seedset"
xvar <- "prop_propagule"

data <- subset(SummaryInd,seedset>0&prop_propagule>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

plot(seedset ~ prop_propagule,data=subset(SummaryInd,seedset>0&prop_propagule>0&age>2),col=col.spp(species),pch=16,log="xy")
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}

dev.off()

yvar <- "seedset"
xvar <- "prop_propagule"

data <- subset(SummaryInd,seedset>0&prop_propagule>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
write.csv(results, file="figs2/seedset_vs_proppropagule.csv",row.names=FALSE)
```

```{r}
win.metafile("figs2/seedset_vs_seedsize.wmf", height=6, width=6)
plot

par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.5,.5))

plot(seedset ~ seed_size,data=subset(SummaryInd,seedset>0),col=col.spp(species),pch=16,log="xy")
points(seedset ~ seed_size,data=subset(SummarySpp[["mean"]],seedset>0),col=col.spp(species),pch=16,cex=2)
mod <-lm(log10(seed_size) ~ log10(seedset),data=subset(SummarySpp[["mean"]],seedset>0))
words.bottom.left.logxy(mod)
dev.off()
```

```{r}
xvar <- "seedset"
yvar <- "prop_propagule"

data <- subset(SummaryInd,aprop_propagule>0&seed_count>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
#write.csv(results, file="figs2/seedset_vs_accessory.csv",row.names=FALSE)

#win.metafile("figs2/seedset_vs_accessory.wmf", height=6, width=6)
#plot

par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))

plot(prop_propagule~seedset,data=subset(SummaryInd,prop_propagule>0&seedset>0&age>2),col=col.spp(species),pch=16,log="xy")
points(prop_propagule~seedset,data=subset(SummarySpp[["mean"]],prop_propagule>0&seedset>0),col="black",pch=16,cex=2.5)
points(prop_propagule~seedset,data=subset(SummarySpp[["mean"]],prop_propagule>0&seedset>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(prop_propagule)~log10(seedset),data=subset(SummarySpp[["mean"]]))
words.top.right.logxy(mod)
for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
abline(coef(mod)[1],coef(mod)[2],lwd=3)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
#dev.off()
```

```{r}
xvar <- "seedset"
yvar <- "accessory_per_seed"

data <- subset(SummaryInd,accessory_per_seed>0&seed_count>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
write.csv(results, file="figs2/seedset_vs_accessory.csv",row.names=FALSE)

win.metafile("figs2/seedset_vs_accessory.wmf", height=6, width=6)
plot

par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))

plot(accessory_per_seed~seedset,data=subset(SummaryInd,accessory_per_seed>0&seedset>0&age>2),col=col.spp(species),pch=16,log="xy")
points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col="black",pch=16,cex=2.5)
points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(accessory_per_seed)~log10(seedset),data=subset(SummarySpp[["mean"]]))
words.top.right.logxy(mod)
for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
abline(coef(mod)[1],coef(mod)[2],lwd=3)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
dev.off()
```

```{r}
xvar <- "seed_count"
yvar <- "accessory_per_seed"

data <- subset(SummaryInd,accessory_per_seed>0&seed_count>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results

par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))

plot(accessory_per_seed~seed_count,data=subset(SummaryInd,accessory_per_seed>0&seed_count>0&age>2),col=col.spp(species),pch=16,log="xy")
points(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seed_count>0),col="black",pch=16,cex=2.5)
points(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seed_count>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(accessory_per_seed)~log10(seed_count),data=subset(SummarySpp[["mean"]]))
words.top.right.logxy(mod)
for(i in 1:14) {
abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
}
abline(coef(mod)[1],coef(mod)[2],lwd=3)
legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

```

```{r}
par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
xvar <- "seed_count"
yvar <- "b_div_p"

data <- subset(SummaryInd,b_div_p>0&age>2&seed_count>0)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results
write.csv(results, file="figs2/seedcount_vs_b_div_p.csv",row.names=FALSE)
```

```{r}
par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
xvar <- "seed_count"
yvar <- "c_div_p"

data <- subset(SummaryInd,c_div_p>0&seed_count>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results

write.csv(results, file="figs2/seedcount_vs_c_div_p.csv",row.names=FALSE)
```

```{r}
par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
xvar <- "seed_count"
yvar <- "packaging_dispersal_per_seed"

data <- subset(SummaryInd,packaging_dispersal_per_seed>0&seed_count>0&age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)
results$ovules <- c(60,4,15,15,2,2,2,4,1,40,2,20,2)

write.csv(results, file="figs2/seedcount_vs_packdisp.csv",row.names=FALSE)

win.metafile("figs2/dispcosts_vs_ovules.wmf", height=6, width=6)
plot
par(mfrow=c(1,1), cex=1, omi=c(.4,.4,.1,.1), mai=c(.8,.8,.2,.2)) 
plot(ovules~r.squared,results,log="y",col=col.spp(species),pch=16,cex=2,las=.1)
mod <- lm(r.squared~log10(ovules),results)
words.bottom.right.logy(mod)
dev.off()
```

### 2016-01-15 Accessory_figs_2016.Rmd
work on accessory cost manuscript figures

@@
 
-win.metafile("figs2/seedset_vs_accessory.wmf", height=6, width=6)
-plot
+#win.metafile("figs2/seedset_vs_accessory.wmf", height=6, width=6)
+#plot
 
@@
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-dev.off()
+#dev.off()
 ```
@@
 ```
+
+###RA not correlated with accessory costs
+```{r}
+xvar <- "RA"
+yvar <- "accessory_per_seed"
+
+data <- subset(SummaryInd,accessory_per_seed>0&RA>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  ((x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
+plot(accessory_per_seed~RA,data=subset(SummaryInd,accessory_per_seed>0&RA>0&age>2),col=col.spp(species),pch=16,log="y")
+points(accessory_per_seed~RA,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&RA>0),col="black",pch=16,cex=3)
+points(accessory_per_seed~RA,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&RA>0),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log10(accessory_per_seed)~(RA),data=subset(SummarySpp[["mean"]]))
+words.top.right.logx(mod)
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+abline(coef(mod)[1],coef(mod)[2],lwd=3)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+```
+
+```{r}
+xvar <- "repro_inv"
+yvar <- "accessory_per_seed"
+
+data <- subset(SummaryInd,accessory_per_seed>0&repro_inv>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
+plot(accessory_per_seed~repro_inv,data=subset(SummaryInd,accessory_per_seed>0&repro_inv>0&age>2),col=col.spp(species),pch=16,log="xy")
+points(accessory_per_seed~repro_inv,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&repro_inv>0),col="black",pch=16,cex=3)
+points(accessory_per_seed~repro_inv,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&repro_inv>0),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log10(accessory_per_seed)~log10(repro_inv),data=subset(SummarySpp[["mean"]]))
+words.top.right.logxy(mod)
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+abline(coef(mod)[1],coef(mod)[2],lwd=3)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+```
+
+```{r}
+xvar <- "age"
+yvar <- "accessory_per_seed"
+
+data <- subset(SummaryInd,accessory_per_seed>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+write.csv(results, file="figs2/age_vs_accessory.csv",row.names=FALSE)
+
+par(mfrow=c(1,2), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
+plot(accessory_per_seed~age,data=subset(SummaryInd,accessory_per_seed>0&age>0&age>2&species!="COER"),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+```
+
+```{r}
+xvar <- "age"
+yvar <- "seedset"
+
+data <- subset(SummaryInd,seedset>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+#write.csv(results, file="figs2/age_vs_accessory.csv",row.names=FALSE)
+
+#par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
+plot(seedset~age,data=subset(SummaryInd,seedset>0&age>2),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+```
+
+```{r}
+xvar <- "age"
+yvar <- "seed_count"
+
+data <- subset(SummaryInd,seedset>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+#write.csv(results, file="figs2/age_vs_accessory.csv",row.names=FALSE)
+
+#par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
+plot(seed_count~age,data=subset(SummaryInd,seedset>0&age>2),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+```
+
+```{r}
+xvar <- "age"
+yvar <- "c_div_p"
+
+data <- subset(SummaryInd,c_div_p>0&age>2&species!="COER")
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+```
+
+```{r}
+xvar <- "seedset"
+yvar <- "b_div_p"
+
+data <- subset(SummaryInd,b_div_p>0&seedset>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+# extra1 <- select(SummarySpp[["max"]],species,seedset)
+# names(extra1) <- c("species","seedset_max")
+# extra2 <- select(SummarySpp[["min"]],species,seedset)
+# names(extra2) <- c("species","seedset_min")
+# 
+# results <- merge(results, extra1, by="species", all=TRUE)
+# results <- merge(results, extra2, by="species", all=TRUE)
+# results$seedset_min <- 0.0001
+# 
+# results$max_y <- (10^(results$seedset_max*results$b))*10^(results$a)
+# results$min_y <- (10^(results$seedset_min*results$b))*10^(results$a)
+
+#write.csv(results, file="figs2/age_vs_accessory.csv",row.names=FALSE)
+
+par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
+plot(b_div_p~seedset,data=subset(SummaryInd,b_div_p>0&seedset>0),col=col.spp(species),pch=16,log="xy")
+
+#View(results)
+
+for(i in 1:14) {
+#arrows(results[i,8],results[i,10],results[i,7],results[i,9],col=col.spp(results$species[i]),code=0,lwd=2)  
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+```
+
+```{r}
+xvar <- "total_weight"
+yvar <- "repro_all_count"
+
+data <- subset(SummaryInd,repro_all_count>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
+plot(repro_all_count~total_weight,data=subset(SummaryInd,repro_all_count>0&age>2&total_weight>0),col=col.spp(species),pch=16,log="xy")
+points(repro_all_count~total_weight,data=subset(SummarySpp[["mean"]],repro_all_count>0&total_weight>0),col="black",pch=16,cex=3)
+points(repro_all_count~total_weight,data=subset(SummarySpp[["mean"]],repro_all_count>0&total_weight>0),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log10(total_weight)~log10(repro_all_count),data=subset(SummarySpp[["mean"]]))
+words.top.right.logxy(mod)
+for(i in 1:14) {
+  abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+abline(coef(mod)[1],coef(mod)[2],lwd=3)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+```
+
+```{r}
+xvar <- "total_weight"
+yvar <- "repro_inv"
+
+data <- subset(SummaryInd,repro_inv>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
+plot(repro_inv~total_weight,data=subset(SummaryInd,repro_inv>0&age>2&total_weight>0),col=col.spp(species),pch=16,log="xy")
+points(repro_inv~total_weight,data=subset(SummarySpp[["mean"]],repro_inv>0&total_weight>0),col="black",pch=16,cex=3)
+points(repro_inv~total_weight,data=subset(SummarySpp[["mean"]],repro_inv>0&total_weight>0),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log10(total_weight)~log10(repro_inv),data=subset(SummarySpp[["mean"]]))
+words.top.right.logxy(mod)
+for(i in 1:14) {
+  abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+abline(coef(mod)[1],coef(mod)[2],lwd=3)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+```
+
+```{r}
+xvar <- "total_weight_0"
+yvar <- "propagule_inv"
+
+data <- subset(SummaryInd,propagule_inv>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
+plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0&age>2&total_weight_0>0),col=col.spp(species),pch=16,log="xy")
+points(propagule_inv~total_weight_0,data=subset(SummarySpp[["mean"]],propagule_inv>0&total_weight_0>0),col="black",pch=16,cex=3)
+points(propagule_inv~total_weight_0,data=subset(SummarySpp[["mean"]],propagule_inv>0&total_weight_0>0),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log10(total_weight_0)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0&age>2&total_weight_0>0))
+words.top.right.logxy(mod)
+for(i in 1:14) {
+  abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+#abline(coef(mod)[1],coef(mod)[2],lwd=3)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+```

### 2016-02-02 Accessory_figs_2016.Rmd
continuing to polish up figures and tables for accessory manuscript.
changes to SUmmaries from last week

--- 2016-01-13 Accessory_figs_2016.Rmd
@@
+#Figure 1. Correlations of various reproductive investment categories against plant weight
 ```{r}
-win.metafile("figs2/best_correlate2.wmf", height=6, width=12)
+win.metafile("figs2/Figure01_correlations_with_plant_weight.wmf", height=9, width=13)
 plot
 
-par(mfrow=c(1,3), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
-plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy")
+par(mfrow=c(2,3), cex=1, omi=c(1,0.1,.1,0.05), mai=c(.2,.55,.1,0.1))
+options(scipen = 2)
+
+plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlab="",xlim=c(10,10000000),ylim=c(1,1000000),xaxt="n",ylab="")
 mod <- lm(log10(total_weight_0)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
 words.top.left.logxy(mod)
+mtext(text="investment in propagules (mg)",side=2,line=2.3,outer=FALSE)
 
-plot(repro_inv~total_weight_0,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
+plot(fruit_weight~total_weight_0,data=subset(SummaryInd,fruit_weight>0),col=col.spp(species),pch=16,log="xy",xlab="",xlim=c(10,10000000),ylim=c(1,1000000),xaxt="n",ylab="",yaxt="n")
+mod <- lm(log10(total_weight_0)~log10(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
+words.top.left.logxy(mod)
+mtext(text="investment in fruit (mg)",side=2,line=0.6,outer=FALSE)
+
+plot(repro_all_count~total_weight_0,data=subset(SummaryInd,repro_all_count>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",yaxt="n",xaxt="n")
+mod <- lm(log10(total_weight_0)~log10(repro_all_count),data=subset(SummaryInd,repro_all_count>0))
+words.top.left.logxy(mod)
+mtext(text="count of all reproductive units",side=2,line=0.6,outer=FALSE)
+
+mtext(text="total plant weight (mg)",side=1,line=1.5,outer=TRUE)
+plot(prepollen_all_inv~total_weight_0,data=subset(SummaryInd,prepollen_all_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="")
+mod <- lm(log10(total_weight_0)~log10(prepollen_all_inv),data=subset(SummaryInd,prepollen_all_inv>0))
+words.top.left.logxy(mod)
+mtext(text="investment in prepollination tissues (mg)",side=2,line=2.3,outer=FALSE)
+
+plot(repro_inv~total_weight_0,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",yaxt="n")
 mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
 words.top.left.logxy(mod)
+mtext(text="total reproductive investment (mg)",side=2,line=0.6,outer=FALSE)
 
-plot(prepollen_all_inv~total_weight_0,data=subset(SummaryInd,prepollen_all_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
-mod <- lm(log10(total_weight_0)~log10(prepollen_all_inv),data=subset(SummaryInd,prepollen_all_inv>0))
+plot(seed_count~total_weight_0,data=subset(SummaryInd,seed_count>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",yaxt="n")
+mod <- lm(log10(total_weight_0)~log10(seed_count),data=subset(SummaryInd,seed_count>0))
+words.top.left.logxy(mod)
+mtext(text="seed count",side=2,line=0.6,outer=FALSE)
+
+mtext(text="total plant weight (mg)",side=1,line=1.5,outer=TRUE)
+
+dev.off()
+```
+
+#Appendix Fig 1. Correlations with leaf investment  
+* if you change conditions to "growth_leaf>50" to remove those old individuals that are no longer replacing leaves, the correlations become ~2x as strong
+```{r}
+win.metafile("figs2/Appendix01_correlations_with_leaf_investment.wmf", height=9, width=9)
+plot
+
+par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.1), mai=c(1.1,1,.3,0.1))
+plot(propagule_inv~growth_leaf,data=subset(SummaryInd,propagule_inv>0&growth_leaf>0),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log10(growth_leaf)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0&growth_leaf>0))
+words.top.left.logxy(mod)
+
+plot(fruit_weight~growth_leaf,data=subset(SummaryInd,fruit_weight>0&growth_leaf>0),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log10(growth_leaf)~log10(fruit_weight),data=subset(SummaryInd,fruit_weight>0&growth_leaf>0))
+words.top.left.logxy(mod)
+
+plot(repro_inv~growth_leaf,data=subset(SummaryInd,repro_inv>0&growth_leaf>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
+mod <- lm(log10(growth_leaf)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0&growth_leaf>0))
+words.top.left.logxy(mod)
+
+plot(prepollen_all_inv~growth_leaf,data=subset(SummaryInd,prepollen_all_inv>0&growth_leaf>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
+mod <- lm(log10(growth_leaf)~log10(prepollen_all_inv),data=subset(SummaryInd,prepollen_all_inv>0&growth_leaf>0))
 words.top.left.logxy(mod)
@@
 
+#Table showing accessory cost values for the species
 ```{r}
-win.metafile("figs2/acc_cost_seed_size_4panel.wmf", height=9, width=9)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,seed_to_ovule_ratio,accessory_per_seed,total_accessory_Lord,prepollencosts,b_div_p,c_div_p,dispersalcosts_increment,dispersalcosts_increment2)
+acc_costs_spp$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+acc_costs_spp$seed_to_ovule_ratio <- round(acc_costs_spp$seed_to_ovule_ratio,digits=3)
+acc_costs_spp$accessory_per_seed <- round(acc_costs_spp$accessory_per_seed,digits=2)
+acc_costs_spp$total_accessory_Lord <- round(acc_costs_spp$total_accessory_Lord,digits=2)
+acc_costs_spp$b_div_p <- round(acc_costs_spp$b_div_p,digits=2)
+acc_costs_spp$c_div_p <- round(acc_costs_spp$c_div_p,digits=2)
+acc_costs_spp$dispersalcosts_increment <- round(acc_costs_spp$dispersalcosts_increment,digits=2)
+acc_costs_spp$dispersalcosts_increment2 <- round(acc_costs_spp$dispersalcosts_increment2,digits=2)
 
+write.csv(acc_costs_spp, file="figs2/Table01_AccCosts_by_Species.csv",row.names=FALSE)
+```
+
+#Figure 2 and Table 2. Scaling of accessory costs versus seed size, by species
+```{r}
+win.metafile("figs2/Figure02_acc_cost_seed_size_4panel.wmf", height=9, width=9)
 plot
-par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.5,.5)) 
+
+par(mfrow=c(2,2), cex=1, omi=c(.5,.1,.1,.1), mai=c(.1,1,.3,.1)) 
 options(scipen = 5)
 
-plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="total per seed accessory costs")
+plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="total per seed accessory costs",xlab="",xaxt="n")
 mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
@@
 slopes <- sma(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],slope.test=1))
-summary(slopes)
+#summary(slopes)
 slopes2 <- as.matrix(coef(slopes))
@@
 
-plot(b_div_p ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="pre-pollination accessory costs")
+plot(b_div_p ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="pre-pollination accessory costs",xlab="",xaxt="n")
 mod <- lm(log10(b_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
 words.top.left.logxy(mod)
-slopes <- sma(log10(b_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],slope.test=1))
-summary(slopes)
-slopes2 <- as.matrix(coef(slopes))
-abline((slopes2[1]),(slopes2[2]))
-abline((slopes2[1]),1,col="red")
+slopes <- sma(log10(b_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],slope.test=1,groupsummary=TRUE))
+#summary(slopes)
 
-plot(c_div_p ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylab="aborted fruit accessory costs")
+slopes3 <- as.matrix(coef(slopes))
+abline((slopes3[1]),(slopes2[2]))
+abline((slopes3[1]),1,col="red")
+
+plot(c_div_p ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylab="aborted fruit accessory costs",xlab="")
 mod <- lm(log10(c_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
@@
 slopes <- sma(log10(c_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1)
-summary(slopes)
-slopes2 <- as.matrix(coef(slopes))
-abline((slopes2[1]),(slopes2[2]))
-abline((slopes2[1]),1,col="red")
+#summary(slopes)
+slopes4 <- as.matrix(coef(slopes))
+abline((slopes4[1]),(slopes2[2]))
+abline((slopes4[1]),1,col="red")
 
-plot(dispersalcosts_increment ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="dispersal & packaging accessory costs")
+plot(dispersalcosts_increment ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="dispersal & packaging accessory costs",xlab="")
 mod <- lm(log10(dispersalcosts_increment) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"))
@@
 slopes <- sma(log10(dispersalcosts_increment) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
-summary(slopes)
-slopes2 <- as.matrix(coef(slopes))
-abline((slopes2[1]),(slopes2[2]))
-abline((slopes2[1]),1,col="red")
-dev.off()
-```
+#slopes5 <- as.matrix(sma(log10(dispersalcosts_increment) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)[1])
 
-#all species show a strong correlation between seedset and the proportion of reproductive investment that is for propagules.
-However, the slope of the relationship is hugely different across species - some species can still have very low seedset, but show a big shift in what proportion of their energy goes to propagules
-##would be good for lines for each species  to just extend from 0 to max seedset for that species
-```{r}
-win.metafile("figs2/seedset_vs_propPropagule.wmf", height=6, width=6)
+slopes5 <- as.matrix(coef(slopes))
+abline((slopes5[1]),(slopes2[2]))
+abline((slopes5[1]),1,col="red")
 
-plot
-par(mfrow=c(1,1), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
+Table2 <- data.frame(component=c("total accessory costs","b div p","c div p","dispersal"))
+Table2$intercept = c(slopes2[1],slopes3[1],slopes4[1],slopes5[1])
+Table2$slope = c(slopes2[2],slopes3[2],slopes4[2],slopes5[2])
+write.csv(Table2, file="figs2/Table02_AccCosts_coeff.csv",row.names=FALSE)
 
-yvar <- "seedset"
-xvar <- "prop_propagule"
+mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
 
-data <- subset(SummaryInd,seedset>0&prop_propagule>0&age>2)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-plot(seedset ~ prop_propagule,data=subset(SummaryInd,seedset>0&prop_propagule>0&age>2),col=col.spp(species),pch=16,log="xy")
-legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
-
-dev.off()
-
-yvar <- "seedset"
-xvar <- "prop_propagule"
-
-data <- subset(SummaryInd,seedset>0&prop_propagule>0&age>2)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-write.csv(results, file="figs2/seedset_vs_proppropagule.csv",row.names=FALSE)
-```
-
-```{r}
-win.metafile("figs2/seedset_vs_seedsize.wmf", height=6, width=6)
-plot
-
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.5,.5))
-
-plot(seedset ~ seed_size,data=subset(SummaryInd,seedset>0),col=col.spp(species),pch=16,log="xy")
-points(seedset ~ seed_size,data=subset(SummarySpp[["mean"]],seedset>0),col=col.spp(species),pch=16,cex=2)
-mod <-lm(log10(seed_size) ~ log10(seedset),data=subset(SummarySpp[["mean"]],seedset>0))
-words.bottom.left.logxy(mod)
 dev.off()
@@
 ```{r}
-xvar <- "seedset"
-yvar <- "prop_propagule"
+plot(total_weight_0~seed_size,data=subset(SummaryInd,total_weight_0>0),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log10(seed_size)~log10(total_weight),data=subset(SummarySpp[["mean"]],total_weight>0))
+words.top.left.logxy(mod)
 
-data <- subset(SummaryInd,aprop_propagule>0&seed_count>0&age>2)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
-#write.csv(results, file="figs2/seedset_vs_accessory.csv",row.names=FALSE)
-
-#win.metafile("figs2/seedset_vs_accessory.wmf", height=6, width=6)
-#plot
-
-par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
-
-plot(prop_propagule~seedset,data=subset(SummaryInd,prop_propagule>0&seedset>0&age>2),col=col.spp(species),pch=16,log="xy")
-points(prop_propagule~seedset,data=subset(SummarySpp[["mean"]],prop_propagule>0&seedset>0),col="black",pch=16,cex=2.5)
-points(prop_propagule~seedset,data=subset(SummarySpp[["mean"]],prop_propagule>0&seedset>0),col=col.spp(species),pch=16,cex=2)
-mod <- lm(log10(prop_propagule)~log10(seedset),data=subset(SummarySpp[["mean"]]))
-words.top.right.logxy(mod)
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
-abline(coef(mod)[1],coef(mod)[2],lwd=3)
-legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-#dev.off()
+plot(seedset~seed_size,data=subset(SummaryInd,seedset>0),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log10(seed_size)~log10(seedset),data=subset(SummarySpp[["mean"]],seedset>0))
+words.top.left.logxy(mod)
 ```
 
+#Table 3 and Figure 3.Per seed accessory costs are lower in individuals with higher seed count. 
+###This effect is true across species, since larger-seeded species produce fewer seeds and have higher per seed accessory costs and true within species, since absolute accessory investment is a function of plant size not seedset
 ```{r}
-xvar <- "seedset"
-yvar <- "accessory_per_seed"
-
-data <- subset(SummaryInd,accessory_per_seed>0&seed_count>0&age>2)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
-write.csv(results, file="figs2/seedset_vs_accessory.csv",row.names=FALSE)
-
-win.metafile("figs2/seedset_vs_accessory.wmf", height=6, width=6)
+win.metafile("figs2/Figure_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
 plot
 
-par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
-
-plot(accessory_per_seed~seedset,data=subset(SummaryInd,accessory_per_seed>0&seedset>0&age>2),col=col.spp(species),pch=16,log="xy")
-points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col="black",pch=16,cex=2.5)
-points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col=col.spp(species),pch=16,cex=2)
-mod <- lm(log10(accessory_per_seed)~log10(seedset),data=subset(SummarySpp[["mean"]]))
-words.top.right.logxy(mod)
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
-abline(coef(mod)[1],coef(mod)[2],lwd=3)
-legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-dev.off()
-```
-
-```{r}
 xvar <- "seed_count"
@@
 results$b <- round(results$b,digits=2)
-results
 
@@
 
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
+results
+write.csv(results, file="figs2/Table03_seedcount_vs_accessory.csv",row.names=FALSE)
+
+dev.off()
 ```
 
+#Table 3 extra - showing propagule investment instead of seed_count. Could also replace with seedset
 ```{r}
-par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
-xvar <- "seed_count"
-yvar <- "b_div_p"
+win.metafile("figs2/Figure_EXTRA_acc_cost_by_seedset.wmf", height=5, width=5)
+plot
 
-data <- subset(SummaryInd,b_div_p>0&age>2&seed_count>0)
+xvar <- "seedset"
+yvar <- "accessory_per_seed"
+
+data <- subset(SummaryInd,accessory_per_seed>0&seedset>0&age>2)
 data <- split(data, data$species)
@@
 results$b <- round(results$b,digits=2)
+
+par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
+plot(accessory_per_seed~seedset,data=subset(SummaryInd,accessory_per_seed>0&seedset>0&age>2),col=col.spp(species),pch=16,log="xy")
+#points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col="black",pch=16,cex=2.5)
+#points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col=col.spp(species),pch=16,cex=2)
+mod <- lm(log10(accessory_per_seed)~log10(seedset),data=subset(SummarySpp[["mean"]]))
+#words.top.right.logxy(mod)
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+#abline(coef(mod)[1],coef(mod)[2],lwd=3)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
 results
-write.csv(results, file="figs2/seedcount_vs_b_div_p.csv",row.names=FALSE)
+write.csv(results, file="figs2/Table03a_seedset_vs_accessory.csv",row.names=FALSE)
+
+dev.off()
 ```
 
+#Higher RE does not lead to lower accessory costs
 ```{r}
-par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
-xvar <- "seed_count"
-yvar <- "c_div_p"
+xvar <- "repro_inv"
+yvar <- "accessory_per_seed"
 
-data <- subset(SummaryInd,c_div_p>0&seed_count>0&age>2)
+data <- subset(SummaryInd,accessory_per_seed>0&repro_inv>0)
 data <- split(data, data$species)
@@
 results$b <- round(results$b,digits=2)
+
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
+plot(accessory_per_seed~repro_inv,data=subset(SummaryInd,accessory_per_seed>0&repro_inv),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
 results
-
-write.csv(results, file="figs2/seedcount_vs_c_div_p.csv",row.names=FALSE)
+write.csv(results, file="figs2/Table04_accessory_vs_RE.csv",row.names=FALSE)
 ```
 
+#Higher RA does not lead to lower accessory costs
 ```{r}
-par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
-xvar <- "seed_count"
-yvar <- "packaging_dispersal_per_seed"
+xvar <- "RA"
+yvar <- "accessory_per_seed"
 
-data <- subset(SummaryInd,packaging_dispersal_per_seed>0&seed_count>0&age>2)
+data <- subset(SummaryInd,accessory_per_seed>0&RA>0)
 data <- split(data, data$species)
@@
 results$b <- round(results$b,digits=2)
-results$ovules <- c(60,4,15,15,2,2,2,4,1,40,2,20,2)
 
-write.csv(results, file="figs2/seedcount_vs_packdisp.csv",row.names=FALSE)
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
 
+plot(accessory_per_seed~RA,data=subset(SummaryInd,accessory_per_seed>0&RA),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
+results
+write.csv(results, file="figs2/Table05_accessory_vs_RA.csv",row.names=FALSE)
+```
+
+#Not a single species shows a reduction in per seed accessory costs with increased plant size.Indeed, EPMI has higher pre-pollination accessory costs    (slope = 0.38, r2=0.19, p=0.019) and accessory costs due to aborted fruit and seeds (slope = 0.83, r2=0.268, p=0.019) in larger individuals, as larger individuals of this species have lower seedset (slope = -0.31, r2=0.198, p=0.018).
+GRSP also has a nearly significant decline in seedset in larger individuals (slope = -0.78, r2=0.298, p=0.067).
+```{r}
+xvar <- "total_weight_0"
+yvar <- "accessory_per_seed"
+
+data <- subset(SummaryInd,accessory_per_seed>0&total_weight_0>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
+plot(accessory_per_seed~total_weight_0,data=subset(SummaryInd,accessory_per_seed>0&total_weight_0>0),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
+results
+write.csv(results, file="figs2/Table04c_accessory_vs_total_weight.csv",row.names=FALSE)
+```
+
+```{r}
+xvar <- "age"
+yvar <- "accessory_per_seed"
+
+data <- subset(SummaryInd,accessory_per_seed>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
+plot(accessory_per_seed~age,data=subset(SummaryInd,accessory_per_seed>0&age>2),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
+results
+write.csv(results, file="figs2/Table04d_accessory_vs_age.csv",row.names=FALSE)
+```
+
+```{r}
+xvar <- "total_weight"
+yvar <- "seedset"
+
+data <- subset(SummaryInd,seedset>0&total_weight>0&age<32)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
+plot(seedset~total_weight,data=subset(SummaryInd,seedset>0&total_weight>0),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
+results
+write.csv(results, file="figs2/Table06b_total_size_by_seedset.csv",row.names=FALSE)
+```
+
+#Considering the individual components of accessory costs vs. seedset - since seedset best predictor of accessory costs
+```{r}
+xvar <- "seedset"
+yvar <- "b_div_p"
+
+data <- subset(SummaryInd,b_div_p>0&seedset)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
+plot(b_div_p~seedset,data=subset(SummaryInd,b_div_p>0&seedset>0),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
+results
+write.csv(results, file="figs2/Table08a_b_div_p_vs_seedset.csv",row.names=FALSE)
+```
+
+```{r}
+xvar <- "seedset"
+yvar <- "c_div_p"
+
+data <- subset(SummaryInd,c_div_p>0&seedset>0&species!="BAER"&species!="COER")
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
+plot(c_div_p~seedset,data=subset(SummaryInd,c_div_p>0&seedset>0&species!="BAER"&species!="COER"),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:12) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Boronia ledifolia","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
+results
+write.csv(results, file="figs2/Table08b_c_div_p_vs_seedset.csv",row.names=FALSE)
+```
+
+```{r}
+xvar <- "seedset"
+yvar <- "packaging_dispersal_per_seed"
+
+data <- subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0&species!="LEES")
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
+plot(packaging_dispersal_per_seed~seedset,data=subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0&species!="LEES"),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:13) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
+results
+write.csv(results, file="figs2/Table08c_dispersal_vs_seedset.csv",row.names=FALSE)
+```
+
+#need to redo this, deleted code that created dataframe
+```{r}
 win.metafile("figs2/dispcosts_vs_ovules.wmf", height=6, width=6)
@@
 ```
+
+#For each species the accessory cost components that cause shifts in total accessory costs is different and reflects both which components are largest and whichvary most with some factor - seedset, age, etc.
+```{r}
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="BOLE"))
+summary(mod)
+species_effects <- as.data.frame(coef(mod))
+names(species_effects) = c("BOLE")
+species_effects$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&species=="BAER"))
+summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("BAER")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p")
+
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&species=="COER"))
+summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("COER")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="EPMI"))
+summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("EPMI")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="GRBU"))
+summary(mod)
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="GRSP"))
+summary(mod)
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="HATE"))
+summary(mod)
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="HEPU"))
+summary(mod)
+
+mod <- lm(log10(accessory_per_seed)~log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,age>2&b_div_p>0&c_div_p>0&species=="LEES"))
+summary(mod)
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PELA"))
+summary(mod)
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PEPU"))
+summary(mod)
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PHPH"))
+summary(mod)
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PILI"))
+summary(mod)
+
+mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PUTU"))
+summary(mod)
+```
+#*******************************
+#below this line: results probably not used in manuscript
+#*******************************
+#With increasing seed count, not only do total per seed accessory costs decline, but so do the individual components. 
+```{r}
+xvar <- "seed_count"
+yvar <- "b_div_p"
+
+data <- subset(SummaryInd,b_div_p>0&seed_count)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
+plot(b_div_p~seed_count,data=subset(SummaryInd,b_div_p>0&seed_count>0),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
+results
+write.csv(results, file="figs2/Table07a_b_div_p_vs_seed_count.csv",row.names=FALSE)
+```
+
+```{r}
+xvar <- "seed_count"
+yvar <- "c_div_p"
+
+data <- subset(SummaryInd,c_div_p>0&seed_count>0&species!="BAER"&species!="COER")
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
+plot(c_div_p~seed_count,data=subset(SummaryInd,c_div_p>0&seed_count>0&species!="BAER"&species!="COER"),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:12) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Boronia ledifolia","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
+results
+write.csv(results, file="figs2/Table07b_c_div_p_vs_seed_count.csv",row.names=FALSE)
+```
+
+```{r}
+xvar <- "seed_count"
+yvar <- "packaging_dispersal_per_seed"
+
+data <- subset(SummaryInd,packaging_dispersal_per_seed>0&seed_count>0&species!="LEES")
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
+plot(packaging_dispersal_per_seed~seed_count,data=subset(SummaryInd,packaging_dispersal_per_seed>0&seed_count>0&species!="LEES"),col=col.spp(species),pch=16,log="xy")
+
+for(i in 1:13) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+names(results)=c("species","r2","p-value","n","intercept","slope")
+results
+write.csv(results, file="figs2/Table07c_dispersal_vs_seed_count.csv",row.names=FALSE)
+```

### 2016-02-02 R/Summaries.R

@@ -4,6 +4,7 @@ process_seed_costs <- function(seedSize_raw, PartsSummary_all) {
   seedsize <- seedSize_raw %>%
       select(species, seed_size)
 
+  #all of these calculations should really be done on the individual level, since different scaling per individual and different parts weights
   # adding info on all costs to produce 1 seed
   seedcosts <- list()
   seedcosts[["BAER"]] <- list(parts=c("cone_brown","cone_base_brown","flower_petals","seed_pod","seed","flower_style"), scale=c(1/60,1/60,1/2,1/2,1,1/2))
@@ -91,17 +92,19 @@ dispersalcosts[["PUTU"]] <- list(parts=c("seed_pod"), scale=c(1/2))
                             * dispersalcosts[[sp]][["scale"]])
                       }))
 
+#note, for some species a decimal fraction is given, reflecting that the part turns both into a dispersal component and the actual propagule. 
+#I'm not sure how to figure out the correct value to use
 
 dispersal_at_pollination <- list()
 dispersal_at_pollination[["BAER"]] <- list(parts=c("cone_green","flower_stigma"), scale=c(1/60,1/2))
 dispersal_at_pollination[["BOLE"]] <- list(parts=c("flower_calyx","flower_petals"), scale=c(1/4,1/4))
-dispersal_at_pollination[["COER"]] <- list(parts=c("inflorescence_stalk","flower_stigma"), scale=c(1/6,1))
+dispersal_at_pollination[["COER"]] <- list(parts=c("inflorescence_stalk","flower_stigma"), scale=c(1/6,.5))
 dispersal_at_pollination[["EPMI"]] <- list(parts=c("flower_calyx"), scale=c(1/15))
 dispersal_at_pollination[["GRBU"]] <- list(parts=c("inflorescence_stalk","flower_stigma"), scale=c(1/20,1/2))
 dispersal_at_pollination[["GRSP"]] <- list(parts=c("inflorescence_stalk","flower_stigma"), scale=c(1/20,1/2))
 dispersal_at_pollination[["HATE"]] <- list(parts=c("flower_stigma"), scale=c(1/2))
 dispersal_at_pollination[["HEPU"]] <- list(parts=c("flower_calyx"), scale=c(1/4))
-dispersal_at_pollination[["LEES"]] <- list(parts=c("flower_calyx"), scale=c(1))
+dispersal_at_pollination[["LEES"]] <- list(parts=c("flower_calyx"), scale=c(0.25))
[…]

### 2016-02-04 Accessory_figs_2016.Rmd
work on accessory costs

@@
 ```{r}
-win.metafile("figs2/Figure01_correlations_with_plant_weight.wmf", height=9, width=13)
+win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=9, width=13)
 plot
@@
 
+#In other words, for many species, seed counts do not provide an accurate estimate of reproductive investment
+```{r}
+data <- subset(SummaryInd,seed_count>0)
+data <- split(data, data$species)
+
+xvar <- "repro_inv"
+yvar <- "seed_count"
+
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+
+data <- subset(SummaryInd,seed_count>0)
+data <- split(data, data$species)
+
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+write.csv(results, file="figs2/Accessory_Costs/Table01a_seed_count_vs_repro_inv.csv",row.names=FALSE)
+```
+
+```{r}
+data <- subset(SummaryInd,seed_count>0)
+data <- split(data, data$species)
+
+xvar <- "repro_inv"
+yvar <- "diameter"
+
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+
+data <- subset(SummaryInd,seed_count>0)
+data <- split(data, data$species)
+
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+write.csv(results, file="figs2/Accessory_Costs/Table01b_diameter_vs_repro_inv.csv",row.names=FALSE)
+```
+
+```{r}
+data <- subset(SummaryInd,seed_count>0)
+data <- split(data, data$species)
+
+xvar <- "repro_inv"
+yvar <- "repro_all_count"
+
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+
+data <- subset(SummaryInd,seed_count>0)
+data <- split(data, data$species)
+
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+write.csv(results, file="figs2/Accessory_Costs/Table01c_repro_all_count_vs_repro_inv.csv",row.names=FALSE)
+```
+
 #Appendix Fig 1. Correlations with leaf investment  
@@
 ```{r}
-win.metafile("figs2/Appendix01_correlations_with_leaf_investment.wmf", height=9, width=9)
+win.metafile("figs2/Accessory_Costs/Appendix01_correlations_with_leaf_investment.wmf", height=9, width=9)
 plot
@@
 
-write.csv(acc_costs_spp, file="figs2/Table01_AccCosts_by_Species.csv",row.names=FALSE)
+write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table02_AccCosts_by_Species.csv",row.names=FALSE)
 ```
 
-#Figure 2 and Table 2. Scaling of accessory costs versus seed size, by species
+#Figure 2 and Table 3. Scaling of accessory costs versus seed size, by species
 ```{r}
-win.metafile("figs2/Figure02_acc_cost_seed_size_4panel.wmf", height=9, width=9)
+win.metafile("figs2/Accessory_Costs/Figure02_acc_cost_seed_size_4panel.wmf", height=9, width=9)
 plot
@@
 
-Table2 <- data.frame(component=c("total accessory costs","b div p","c div p","dispersal"))
-Table2$intercept = c(slopes2[1],slopes3[1],slopes4[1],slopes5[1])
-Table2$slope = c(slopes2[2],slopes3[2],slopes4[2],slopes5[2])
-write.csv(Table2, file="figs2/Table02_AccCosts_coeff.csv",row.names=FALSE)
+Table3 <- data.frame(component=c("total accessory costs","b div p","c div p","dispersal"))
+Table3$intercept = c(slopes2[1],slopes3[1],slopes4[1],slopes5[1])
+Table3$slope = c(slopes2[2],slopes3[2],slopes4[2],slopes5[2])
+write.csv(Table3, file="figs2/Accessory_Costs/Table03_AccCosts_coeff.csv",row.names=FALSE)
 
@@
 
-#Table 3 and Figure 3.Per seed accessory costs are lower in individuals with higher seed count. 
+#Table 4 and Figure 3.Per seed accessory costs are lower in individuals with higher seed count. 
 ###This effect is true across species, since larger-seeded species produce fewer seeds and have higher per seed accessory costs and true within species, since absolute accessory investment is a function of plant size not seedset
 ```{r}
-win.metafile("figs2/Figure_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
+win.metafile("figs2/Accessory_Costs/Figure_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
 plot
@@
 results
-write.csv(results, file="figs2/Table03_seedcount_vs_accessory.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table04a_seedcount_vs_accessory.csv",row.names=FALSE)
 
@@
 
-#Table 3 extra - showing propagule investment instead of seed_count. Could also replace with seedset
+#Table 4 extra - showing propagule investment instead of seed_count. Could also replace with seedset
 ```{r}
-win.metafile("figs2/Figure_EXTRA_acc_cost_by_seedset.wmf", height=5, width=5)
+win.metafile("figs2/Accessory_Costs/Figure_EXTRA_acc_cost_by_seedset.wmf", height=5, width=5)
 plot
@@
 results
-write.csv(results, file="figs2/Table03a_seedset_vs_accessory.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table04b_seedset_vs_accessory.csv",row.names=FALSE)
 
@@
 results
-write.csv(results, file="figs2/Table04_accessory_vs_RE.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table05a_accessory_vs_RE.csv",row.names=FALSE)
 ```
@@
 results
-write.csv(results, file="figs2/Table05_accessory_vs_RA.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table05b_accessory_vs_RA.csv",row.names=FALSE)
 ```
@@
 results
-write.csv(results, file="figs2/Table04c_accessory_vs_total_weight.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table05c_accessory_vs_total_weight.csv",row.names=FALSE)
 ```
@@
 results
-write.csv(results, file="figs2/Table04d_accessory_vs_age.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table05d_accessory_vs_age.csv",row.names=FALSE)
 ```
@@
 results
-write.csv(results, file="figs2/Table06b_total_size_by_seedset.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table0xx_total_size_by_seedset.csv",row.names=FALSE)
 ```
@@
 results
-write.csv(results, file="figs2/Table08a_b_div_p_vs_seedset.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table06a_b_div_p_vs_seedset.csv",row.names=FALSE)
 ```
@@
 results
-write.csv(results, file="figs2/Table08b_c_div_p_vs_seedset.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table06b_c_div_p_vs_seedset.csv",row.names=FALSE)
 ```
@@
 
-data <- subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0&species!="LEES")
+data <- subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0)
 data <- split(data, data$species)
@@
 
-plot(packaging_dispersal_per_seed~seedset,data=subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0&species!="LEES"),col=col.spp(species),pch=16,log="xy")
+plot(packaging_dispersal_per_seed~seedset,data=subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0),col=col.spp(species),pch=16,log="xy")
 
@@
 
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
+results$ovules_per_fruit <- c(60,4,1,1,2,2,2,4,1,40,2,20,2)
+max_seedset <- select(SummarySpp[["max"]],species,seedset) 
+min_seedset <- select(SummarySpp[["min"]],species,seedset) 
+results <- merge(results, max_seedset, by=c("species"), all=TRUE)
+results <- merge(results, min_seedset, by=c("species"), all=TRUE)
+names(results)=c("species","r2","p-value","n","intercept","slope","ovules_per_fruit","max_seedset","min_seedset")
+
+#results$min_pack <- (10^results$intercept) + (results$slope*results$max_seedset)
+#results$max_pack <- (10^results$intercept) + (results$slope*results$min_seedset)
 results
-write.csv(results, file="figs2/Table08c_dispersal_vs_seedset.csv",row.names=FALSE)
-```
 
-#need to redo this, deleted code that created dataframe
-```{r}
-win.metafile("figs2/dispcosts_vs_ovules.wmf", height=6, width=6)
+win.metafile("figs2/Accessory_Costs/Table07_dispcosts_vs_ovules.wmf", height=6, width=6)
 plot
+
 par(mfrow=c(1,1), cex=1, omi=c(.4,.4,.1,.1), mai=c(.8,.8,.2,.2)) 
-plot(ovules~r.squared,results,log="y",col=col.spp(species),pch=16,cex=2,las=.1)
-mod <- lm(r.squared~log10(ovules),results)
+plot(ovules_per_fruit~r2,data=subset(results,species!="PELA"),log="y",col=col.spp(species),pch=16,cex=2)
+mod <- lm(r2~log10(ovules_per_fruit),data=subset(results,species!="PELA"))
 words.bottom.right.logy(mod)
 dev.off()
+
+results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
+
+results
+
+write.csv(results, file="figs2/Accessory_Costs/Table06c_dispersal_vs_seedset.csv",row.names=FALSE)
 ```
@@
 summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("GRBU")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
 
@@
 summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("GRSP")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
 
@@
 summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("HATE")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
 
@@
 summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("HEPU")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
 
@@
 summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("LEES")
+species_effects2$effects <- c("intercept","b_div_p","c_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
 
@@
 summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("PELA")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
 
@@
 summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("PEPU")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
 
@@
 summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("PHPH")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
 
@@
 summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("PILI")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
 
@@
 summary(mod)
+species_effects2 <- as.data.frame(coef(mod))
+names(species_effects2) = c("PUTU")
+species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
+
+write.csv(species_effects, file="figs2/Accessory_Costs/Table08_breaking_down_accessory_costs_spp.csv",row.names=FALSE)
 ```
+
+#looking at how the slopes of the relationship between accessory investment and propagule investment shift across species 
+##slopes only statistically different from 1 in 2 species
+##intercepts quite variable - means that the "baseline" accessory investment, before you get any propagules varies
+```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1)) 
+plot(propagule_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0&propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlab="total accessory investment (mg)",ylab="total propagule investment (mg)")
+slope_check <- sma(log10(propagule_inv)~ log10(accessory_inv),data=subset(SummaryInd,propagule_inv>0))
+summary(slope_check)
+
+data <- select(SummaryInd,species,propagule_inv,accessory_inv)
+data <- subset(data,propagule_inv>0)
+data <- split(data, data$species)
+
+for(i in 1:14) {
+slope_check <- sma(log10(propagule_inv)~ log10(accessory_inv),data[[i]],slope.test=1)
+summary(slope_check)
+}
+
+xvar <- "accessory_inv"
+yvar <- "propagule_inv"
+
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+
+data <- subset(SummaryInd,propagule_inv>0)
+data <- split(data, data$species)
+
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+for(i in 1:14) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+```
+
+species with bigger seeds, lower seedset spend less per flower. Here taking the percent of the cost to make a single flower that goes into pre-pollination parts
+
+```{r}
+par(mfrow=c(2,2), cex=1, omi=c(1,0.1,.1,0.05), mai=c(.2,.55,.1,0.1))
+
+plot(percent_prepollencosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)
+mod <- lm(log10(seed_size)~log10(percent_prepollencosts),data=subset(SummarySpp[["mean"]]))
+words.bottom.left.logxy(mod)
+
+plot(percent_prepollencosts~seedset,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)
+mod <- lm(log10(seedset)~log10(percent_prepollencosts),data=subset(SummarySpp[["mean"]]))
+words.top.left.logxy(mod)
+
+plot(percent_dispersalcosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)
+mod <- lm(log10(seed_size)~log10(percent_dispersalcosts),data=subset(SummarySpp[["mean"]]))
+words.bottom.left.logxy(mod)
+
+plot(percent_dispersalcosts~seedset,data=subset(SummarySpp[["mean"]],percent_dispersalcosts>0),col=col.spp(species),pch=16,log="xy",cex=1.5)
+mod <- lm(log10(seedset)~log10(percent_dispersalcosts),data=subset(SummarySpp[["mean"]],percent_dispersalcosts>0))
+words.top.left.logxy(mod)
+```
+
+SummarySpp[["mean"]]$percent_dispersalcosts
 #*******************************
@@
 results
-write.csv(results, file="figs2/Table07a_b_div_p_vs_seed_count.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table0xx_b_div_p_vs_seed_count.csv",row.names=FALSE)
 ```
@@
 results
-write.csv(results, file="figs2/Table07b_c_div_p_vs_seed_count.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table0xx_c_div_p_vs_seed_count.csv",row.names=FALSE)
 ```
@@
 results
-write.csv(results, file="figs2/Table07c_dispersal_vs_seed_count.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table0xx_dispersal_vs_seed_count.csv",row.names=FALSE)
 ```
+
+par(mfrow=c(2,3), cex=1, omi=c(1,0.1,.1,0.05), mai=c(.2,.55,.1,0.1))
+options(scipen = 2)
+
+plot(propagule_inv~repro_inv,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,1000000),ylim=c(1,50000),xaxt="n")
+mod <- lm(log10(repro_inv)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
+words.top.left.logxy(mod)
+#mtext(text="investment in propagules (mg)",side=2,line=2.3,outer=FALSE)
+
+plot(total_weight_0~repro_inv,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,1000000),ylim=c(1,1000000),xaxt="n")
+mod <- lm(log10(repro_inv)~log10(total_weight_0),data=subset(SummaryInd,repro_inv>0))
+words.top.left.logxy(mod)
+#mtext(text="investment in propagules (mg)",side=2,line=2.3,outer=FALSE)
+
+plot(repro_all_count~repro_inv,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,1000000),xaxt="n")
+mod <- lm(log10(repro_inv)~log10(repro_all_count),data=subset(SummaryInd,repro_all_count>0))
+words.top.left.logxy(mod)
+
+plot(costs_for_success~costs_for_failure,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+abline(0,1)
+
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1)) 
+xvar <- "repro_inv"
+yvar <- "percent_for_success"
+
+data <- subset(SummaryInd,percent_for_success>0)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+plot(percent_for_success~repro_inv,data=subset(SummaryInd,percent_for_success>0),col=col.spp(species),pch=16,log="xy")
+points(prop_propagule~repro_inv,data=subset(SummaryInd,prop_propagule>0),pch=1,col=col.spp(species))
+abline(-1,0)
+abline(.0001,0)
+
+plot(prop_propagule~repro_inv,data=subset(SummaryInd,prop_propagule>0),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log10(repro_inv)~log10(repro_all_count),data=subset(SummaryInd,prop_propagule>0))
+summary(mod)
+
+points(prop_propagule_nonzero~repro_inv,data=subset(SummarySpp[["mean"]],prop_propagule>0),col="black",pch=16,cex=2.5)
+points(prop_propagule_nonzero~repro_inv,data=subset(SummarySpp[["mean"]],prop_propagule>0),col=col.spp(species),pch=16,cex=1.5)
+1-mean(SummarySpp[["mean"]]$prop_propagule_nonzero)
+
+for(i in 1:13) {
+abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
+}
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+
+points(prop_propagule~repro_inv,data=subset(SummaryInd,prop_propagule>0),pch=1,col=col.spp(species))
+abline(-1,0)
+abline(.0001,0)

### 2016-02-04 R/Summaries.R

@@ -268,7 +268,16 @@ combine_by_individual <- function(IndividualsList, ReproductionAllocation_all, A
     c_div_p = ((abortedcosts)*(1-seed_to_ovule_ratio))/seed_to_ovule_ratio,
     dispersalcosts_increment2 = accessory_per_seed - b_div_p - c_div_p,
     total_accessory_Lord = dispersalcosts_increment + b_div_p + c_div_p,
-    prepollen_all_inv = prepollen_aborted_inv + prepollen_success_inv
+    prepollen_all_inv = prepollen_aborted_inv + prepollen_success_inv,
+    costs_for_success = seedcosts*seed_count,
+    costs_for_failure = repro_inv - costs_for_success,
+    percent_for_success = costs_for_success/ repro_inv,
+    percent_for_failure = costs_for_failure/ repro_inv,
+    prop_propagule_nonzero = prop_propagule,
+    prop_accessory_nonzero = prop_accessory,
+    percent_prepollencosts = prepollencosts/seedcosts,
+    percent_seedcosts = seed_size/seedcosts,
+    percent_dispersalcosts = 1-percent_prepollencosts-percent_seedcosts
     )
 
   #if seedset is low, prepollen costs increase, because the cost of producing pollen across the whole plant is higher per seed matured  
@@ -355,7 +364,7 @@ get_species_values <- function(SummaryInd, groups) {
     group_by_(.dots=dots) %>%
     summarise_each(f, prop_prepollen_aborted, prop_prepollen_success,
       prop_postpollen_aborted, prop_packaging_dispersal, prop_propagule,
-      prop_prepollen_all, prop_accessory)
+      prop_prepollen_all, prop_accessory, percent_prepollencosts,percent_dispersalcosts,percent_seedcosts)
   })
   names(out[[3]]) <- fs
 
@@ -363,7 +372,7 @@ get_species_values <- function(SummaryInd, groups) {
     SummaryInd %>%
     filter(repro_inv > 0) %>%
     group_by_(.dots=dots) %>%
-    summarise_each(f, seedset, seed_count, flower_count,fruit_weight)
+    summarise_each(f, flower_count,fruit_weight)
   })
   names(out[[4]]) <- fs
 
@@ -374,7 +383,7 @@ get_species_values <- function(SummaryInd, groups) {
     group_by_(.dots=dots) %>%
[…]

### 2016-02-09 Accessory_figs_2016.Rmd
lots of reworking code

@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=9, width=13)
-plot
+#win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=9, width=13)
+#plot
 
@@
 
-plot(propagule_inv~total_weight_0,data=subset(SummaryInd,propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlab="",xlim=c(10,10000000),ylim=c(1,1000000),xaxt="n",ylab="")
-mod <- lm(log10(total_weight_0)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
+library(smatr)
+xvar <- "total_weight_0"
+yvar <- "repro_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",lty=results$linetype,xaxt="n")
+mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
 words.top.left.logxy(mod)
-mtext(text="investment in propagules (mg)",side=2,line=2.3,outer=FALSE)
+mtext(text="total reproductive investment (mg)",side=2,line=2.3,outer=FALSE)
 
-plot(fruit_weight~total_weight_0,data=subset(SummaryInd,fruit_weight>0),col=col.spp(species),pch=16,log="xy",xlab="",xlim=c(10,10000000),ylim=c(1,1000000),xaxt="n",ylab="",yaxt="n")
+xvar <- "total_weight_0"
+yvar <- "fruit_weight"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",lty=results$linetype,xaxt="n",yaxt="n")
 mod <- lm(log10(total_weight_0)~log10(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
@@
 
-plot(repro_all_count~total_weight_0,data=subset(SummaryInd,repro_all_count>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",yaxt="n",xaxt="n")
-mod <- lm(log10(total_weight_0)~log10(repro_all_count),data=subset(SummaryInd,repro_all_count>0))
+xvar <- "total_weight_0"
+yvar <- "propagule_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",lty=results$linetype,xaxt="n",yaxt="n")
+mod <- lm(log10(total_weight_0)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
 words.top.left.logxy(mod)
-mtext(text="count of all reproductive units",side=2,line=0.6,outer=FALSE)
+mtext(text="investment in propagules (mg)",side=2,line=0.6,outer=FALSE)
+mtext(text="total plant weight (mg)",side=1,line=1.5,outer=TRUE)
 
-mtext(text="total plant weight (mg)",side=1,line=1.5,outer=TRUE)
-plot(prepollen_all_inv~total_weight_0,data=subset(SummaryInd,prepollen_all_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="")
+xvar <- "total_weight_0"
+yvar <- "prepollen_all_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",lty=results$linetype)
 mod <- lm(log10(total_weight_0)~log10(prepollen_all_inv),data=subset(SummaryInd,prepollen_all_inv>0))
@@
 
-plot(repro_inv~total_weight_0,data=subset(SummaryInd,repro_inv>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",yaxt="n")
-mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
-words.top.left.logxy(mod)
-mtext(text="total reproductive investment (mg)",side=2,line=0.6,outer=FALSE)
+xvar <- "total_weight_0"
+yvar <- "repro_all_count"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-plot(seed_count~total_weight_0,data=subset(SummaryInd,seed_count>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",yaxt="n")
-mod <- lm(log10(total_weight_0)~log10(seed_count),data=subset(SummaryInd,seed_count>0))
-words.top.left.logxy(mod)
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit, pch=16, col = col.spp(fit$groupsummary$group),lty=results$linetype,xlim=c(10,10000000),ylim=c(1,1000000),xlab="total weight (mg)",ylab="repro all count",yaxt="n")
+mtext(text="count of all reproductive units",side=2,line=0.6,outer=FALSE)
+
+xvar <- "total_weight_0"
+yvar <- "seed_count"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit, pch=16, col = col.spp(fit$groupsummary$group),lty=results$linetype,xlim=c(10,10000000),ylim=c(1,1000000),xlab="total weight (mg)",ylab="repro all count",yaxt="n",lwd=results$linewidth)
 mtext(text="seed count",side=2,line=0.6,outer=FALSE)
-
 mtext(text="total plant weight (mg)",side=1,line=1.5,outer=TRUE)
 
-dev.off()
+#dev.off()
 ```
@@
 ```{r}
-data <- subset(SummaryInd,seed_count>0)
-data <- split(data, data$species)
-
 xvar <- "repro_inv"
 yvar <- "seed_count"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+#plot(fit,xlab=xvar,ylab=yvar,pch=16, col = col.spp(fit$groupsummary$group),lty=results$linetype)
 
-data <- subset(SummaryInd,seed_count>0)
-data <- split(data, data$species)
-
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
 write.csv(results, file="figs2/Accessory_Costs/Table01a_seed_count_vs_repro_inv.csv",row.names=FALSE)
@@
 ```{r}
-data <- subset(SummaryInd,seed_count>0)
-data <- split(data, data$species)
-
 xvar <- "repro_inv"
 yvar <- "diameter"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- fit$groupsummary
 
-data <- subset(SummaryInd,seed_count>0)
-data <- split(data, data$species)
-
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
 write.csv(results, file="figs2/Accessory_Costs/Table01b_diameter_vs_repro_inv.csv",row.names=FALSE)
@@
 ```{r}
-data <- subset(SummaryInd,seed_count>0)
-data <- split(data, data$species)
-
 xvar <- "repro_inv"
 yvar <- "repro_all_count"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- fit$groupsummary
 
-data <- subset(SummaryInd,seed_count>0)
-data <- split(data, data$species)
-
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
 write.csv(results, file="figs2/Accessory_Costs/Table01c_repro_all_count_vs_repro_inv.csv",row.names=FALSE)
@@
 acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,seed_to_ovule_ratio,accessory_per_seed,total_accessory_Lord,prepollencosts,b_div_p,c_div_p,dispersalcosts_increment,dispersalcosts_increment2)
-acc_costs_spp$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-acc_costs_spp$seed_to_ovule_ratio <- round(acc_costs_spp$seed_to_ovule_ratio,digits=3)
-acc_costs_spp$accessory_per_seed <- round(acc_costs_spp$accessory_per_seed,digits=2)
-acc_costs_spp$total_accessory_Lord <- round(acc_costs_spp$total_accessory_Lord,digits=2)
-acc_costs_spp$b_div_p <- round(acc_costs_spp$b_div_p,digits=2)
-acc_costs_spp$c_div_p <- round(acc_costs_spp$c_div_p,digits=2)
-acc_costs_spp$dispersalcosts_increment <- round(acc_costs_spp$dispersalcosts_increment,digits=2)
-acc_costs_spp$dispersalcosts_increment2 <- round(acc_costs_spp$dispersalcosts_increment2,digits=2)
+acc_costs_spp$species <- labels.spp.full()
+acc_costs_spp <- format(acc_costs_spp, digit=2)
 
@@
 
+par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
 xvar <- "seed_count"
 yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,accessory_per_seed>0&seed_count>0&age>2)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
-
-plot(accessory_per_seed~seed_count,data=subset(SummaryInd,accessory_per_seed>0&seed_count>0&age>2),col=col.spp(species),pch=16,log="xy")
 points(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seed_count>0),col="black",pch=16,cex=2.5)
@@
 words.top.right.logxy(mod)
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
-abline(coef(mod)[1],coef(mod)[2],lwd=3)
+#abline(coef(mod)[1],coef(mod)[2],lwd=3)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
 results
@@
 
+par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+
 xvar <- "seedset"
 yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,accessory_per_seed>0&seedset>0&age>2)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
-
-plot(accessory_per_seed~seedset,data=subset(SummaryInd,accessory_per_seed>0&seedset>0&age>2),col=col.spp(species),pch=16,log="xy")
-#points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col="black",pch=16,cex=2.5)
-#points(accessory_per_seed~seedset,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seedset>0),col=col.spp(species),pch=16,cex=2)
-mod <- lm(log10(accessory_per_seed)~log10(seedset),data=subset(SummarySpp[["mean"]]))
-#words.top.right.logxy(mod)
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
-#abline(coef(mod)[1],coef(mod)[2],lwd=3)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
-results
+format(results, digit=2)
 write.csv(results, file="figs2/Accessory_Costs/Table04b_seedset_vs_accessory.csv",row.names=FALSE)
@@
 ```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
 xvar <- "repro_inv"
 yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,accessory_per_seed>0&repro_inv>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
-
-plot(accessory_per_seed~repro_inv,data=subset(SummaryInd,accessory_per_seed>0&repro_inv),col=col.spp(species),pch=16,log="xy")
-
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
-legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
-
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
-results
+format(results, digit=2)
 write.csv(results, file="figs2/Accessory_Costs/Table05a_accessory_vs_RE.csv",row.names=FALSE)
@@
 ```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
 xvar <- "RA"
 yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,accessory_per_seed>0&RA>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
-
-plot(accessory_per_seed~RA,data=subset(SummaryInd,accessory_per_seed>0&RA),col=col.spp(species),pch=16,log="xy")
-
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
-results
+format(results, digit=2)
 write.csv(results, file="figs2/Accessory_Costs/Table05b_accessory_vs_RA.csv",row.names=FALSE)
@@
 ```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
 xvar <- "total_weight_0"
 yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,accessory_per_seed>0&total_weight_0>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
-
-plot(accessory_per_seed~total_weight_0,data=subset(SummaryInd,accessory_per_seed>0&total_weight_0>0),col=col.spp(species),pch=16,log="xy")
-
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
-results
+format(results, digit=2)
 write.csv(results, file="figs2/Accessory_Costs/Table05c_accessory_vs_total_weight.csv",row.names=FALSE)
@@
 ```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
 xvar <- "age"
 yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,accessory_per_seed>0&age>2)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
-
-plot(accessory_per_seed~age,data=subset(SummaryInd,accessory_per_seed>0&age>2),col=col.spp(species),pch=16,log="xy")
-
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
-results
+format(results, digit=2)
 write.csv(results, file="figs2/Accessory_Costs/Table05d_accessory_vs_age.csv",row.names=FALSE)
@@
 ```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
 xvar <- "total_weight"
 yvar <- "seedset"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,seedset>0&total_weight>0&age<32)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
-
-plot(seedset~total_weight,data=subset(SummaryInd,seedset>0&total_weight>0),col=col.spp(species),pch=16,log="xy")
-
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
-results
+format(results, digit=2)
 write.csv(results, file="figs2/Accessory_Costs/Table0xx_total_size_by_seedset.csv",row.names=FALSE)
@@
 ```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
 xvar <- "seedset"
 yvar <- "b_div_p"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,b_div_p>0&seedset)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
-
-plot(b_div_p~seedset,data=subset(SummaryInd,b_div_p>0&seedset>0),col=col.spp(species),pch=16,log="xy")
-
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(results$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
-results
+format(results, digit=2)
 write.csv(results, file="figs2/Accessory_Costs/Table06a_b_div_p_vs_seedset.csv",row.names=FALSE)
@@
 ```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
 xvar <- "seedset"
 yvar <- "c_div_p"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,c_div_p>0&seedset>0&species!="BAER"&species!="COER")
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
-
-plot(c_div_p~seedset,data=subset(SummaryInd,c_div_p>0&seedset>0&species!="BAER"&species!="COER"),col=col.spp(species),pch=16,log="xy")
-
-for(i in 1:12) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy") 
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(results$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$species <- c("Boronia ledifolia","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
-results
+format(results, digit=2)
 write.csv(results, file="figs2/Accessory_Costs/Table06b_c_div_p_vs_seedset.csv",row.names=FALSE)
@@
 yvar <- "packaging_dispersal_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
-
-plot(packaging_dispersal_per_seed~seedset,data=subset(SummaryInd,packaging_dispersal_per_seed>0&seedset>0),col=col.spp(species),pch=16,log="xy")
-
-for(i in 1:13) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(results$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
@@
 
-#results$min_pack <- (10^results$intercept) + (results$slope*results$max_seedset)
-#results$max_pack <- (10^results$intercept) + (results$slope*results$min_seedset)
-results
+format(results, digit=2)
 
@@
 
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-
 results
@@
 ```{r}
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="BOLE"))
-summary(mod)
-species_effects <- as.data.frame(coef(mod))
-names(species_effects) = c("BOLE")
-species_effects$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
+xvar1 <- "packaging_dispersal_per_seed"
+xvar2 <- "b_div_p"
+xvar3 <- "c_div_p"
+yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar1]]>0&SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0)
+data <- split(data, data$species)
 
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&species=="BAER"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("BAER")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p")
+mod <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar1]]))+(log10(x[[xvar2]]))+(log10(x[[xvar3]]))))
 
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
+species_coef <- as.data.frame(c("intercept","packaging&dispersal","b_div_p","c_div_p"))
 
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&species=="COER"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("COER")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[1]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[2]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[3]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[4]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[5]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[6]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[7]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[8]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[9]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[10]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[11]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[12]]$coefficients))
+species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[13]]$coefficients))
+#species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[14]]$coefficients))
+names(species_coef) <- c("effect","BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")
 
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="EPMI"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("EPMI")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
-
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="GRBU"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("GRBU")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
-
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="GRSP"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("GRSP")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
-
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="HATE"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("HATE")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
-
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="HEPU"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("HEPU")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
-
-mod <- lm(log10(accessory_per_seed)~log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,age>2&b_div_p>0&c_div_p>0&species=="LEES"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("LEES")
-species_effects2$effects <- c("intercept","b_div_p","c_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
-
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PELA"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("PELA")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
-
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PEPU"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("PEPU")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
-
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PHPH"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("PHPH")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
-
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PILI"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("PILI")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
-
-mod <- lm(log10(accessory_per_seed)~log10(packaging_dispersal_per_seed)+log10(b_div_p)+log10(c_div_p),data=subset(SummaryInd,packaging_dispersal_per_seed>0&age>2&b_div_p>0&c_div_p>0&species=="PUTU"))
-summary(mod)
-species_effects2 <- as.data.frame(coef(mod))
-names(species_effects2) = c("PUTU")
-species_effects2$effects <- c("intercept","packaging&dispersal","b_div_p","c_div_p")
-species_effects <- dplyr::left_join(species_effects, species_effects2, by = "effects")
-
-write.csv(species_effects, file="figs2/Accessory_Costs/Table08_breaking_down_accessory_costs_spp.csv",row.names=FALSE)
+write.csv(species_coef, file="figs2/Accessory_Costs/Table08_breaking_down_accessory_costs_spp.csv",row.names=FALSE)
 ```
@@
 
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,propagule_inv>0)
-data <- split(data, data$species)
-
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 ```
@@
 ```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
 xvar <- "seed_count"
@@
 
-data <- subset(SummaryInd,b_div_p>0&seed_count)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
-
-plot(b_div_p~seed_count,data=subset(SummaryInd,b_div_p>0&seed_count>0),col=col.spp(species),pch=16,log="xy")
-
-for(i in 1:14) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
 results
@@
 
-data <- subset(SummaryInd,c_div_p>0&seed_count>0&species!="BAER"&species!="COER")
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
-
-plot(c_div_p~seed_count,data=subset(SummaryInd,c_div_p>0&seed_count>0&species!="BAER"&species!="COER"),col=col.spp(species),pch=16,log="xy")
-
-for(i in 1:12) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$species <- c("Boronia ledifolia","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
 results
@@
 ```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
+
 xvar <- "seed_count"
 yvar <- "packaging_dispersal_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,packaging_dispersal_per_seed>0&seed_count>0&species!="LEES")
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1))
-
-plot(packaging_dispersal_per_seed~seed_count,data=subset(SummaryInd,packaging_dispersal_per_seed>0&seed_count>0&species!="LEES"),col=col.spp(species),pch=16,log="xy")
-
-for(i in 1:13) {
-abline((results[i,5]),(results[i,6]),col=col.spp(results$species[i]))
-}
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
-results$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia","Hemigenia purpurea","Persoonia lanceolata", "Petrophile puchella", "Phyllota phyllicoides", "Pimelea linifolia", "Pultanaea tuberculata")
-names(results)=c("species","r2","p-value","n","intercept","slope")
-results
+format(results,digits=2)
 write.csv(results, file="figs2/Accessory_Costs/Table0xx_dispersal_vs_seed_count.csv",row.names=FALSE)
@@
 yvar <- "percent_for_success"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-data <- subset(SummaryInd,percent_for_success>0)
-data <- split(data, data$species)
-lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
-results <- summarise_all_fits(lmfits)
-
-results$r.squared <- round(results$r.squared,digits=3)
-results$p.value <- round(results$p.value,digits=3)
-results$a <- round(results$a,digits=2)
-results$b <- round(results$b,digits=2)
-results
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
 

### 2016-02-09 R/figures.R

@@ -126,7 +126,7 @@ col.spp <- function(x=NULL){
     PEPU="light blue", PHPH= "brown", PILI="deep pink", PUTU="orchid1")
 
   if(!is.null(x)) {
-    ret <- ret[x]
+    ret <- ret[as.character(x)]
   }
   ret
 }
@@ -289,11 +289,15 @@ plot_yvar3_vs_xvar3 <- function(data, yvar3 = "y", xvar3 = "x", ...) {
 }
 
 summarise_fit <- function(x) {
+  
+  xr <- range(x[["model"]][2])
   data.frame(
     select(glance(x), r.squared, p.value),
     n= length(resid(x)),
     a = coef(x)[1],
-    b = coef(x)[2]
+    b = coef(x)[2],
+    x_low = xr[1],
+    x_high = xr[2]
   )
 }
 
@@ -437,4 +441,29 @@ words.top.left.logxy <- function (x) {
   text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
   text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
   text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=0)
+}
+
+lines <- function(results) {
+  results$linetype <- 1
+  results$linewidth <- 2
+  
+  results[as.numeric(results[["pval"]]) > 0.05,"linetype"] <- 2
+  results[as.numeric(results[["pval"]]) > 0.10,"linetype"] <- 3
+  results[as.numeric(results[["pval"]]) > 0.05,"linewidth"] <- 1.5
+  results[as.numeric(results[["pval"]]) > 0.10,"linewidth"] <- 1
+  results
+}
+
+legend_with_r2_bottomright <- function(results) {
+  for_legend <- dplyr::select(results,group,r2)
+  for_legend$r2 <-round(as.numeric(for_legend$r2),digits=3)
+  for_legend$text <- paste(for_legend$group,for_legend$r2,sep="  ")
[…]

### 2016-02-23 Accessory_figs_20160218.Rmd
cleaning up accessory figures

library(smatr)
library(ggtern)
budweight <- dplyr::filter(PartsSummary,part%in%c("bud_big","inflorescence_bud_big_flowers"))
budweight2 <-dplyr::filter(PartsSummary,part=="bud_mid"&species=="PHPH")
budweight <- dplyr::bind_rows(budweight,budweight2)
budweight$species <- as.character(budweight$species)
budweight <-select(budweight,species,weight)
names(budweight) <-c("species","budweight")

SummaryInd <- dplyr::left_join(SummaryInd,budweight,by="species")
SummaryInd$bud_inv <-SummaryInd$budweight*SummaryInd$repro_all_count
SummaryInd$flower_inv <-SummaryInd$prepollencosts*SummaryInd$repro_all_count
SummaryInd$budprop <- SummaryInd$bud_inv + SummaryInd$propagule_inv

#Figure 1. Correlations of various reproductive investment categories against plant weight
```{r}
win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=9, width=13)
plot

par(mfrow=c(2,2), cex=1, omi=c(.1,0.1,.1,0.05), mai=c(.7,.55,.1,0.1))
options(scipen = 2)

library(smatr)
xvar <- "total_weight_0"
yvar <- "repro_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(10,10000000),xlab="",ylab="",lty=results$linetype,pch=20)
mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
words.top.left.logxy(mod)
mtext(text="total reproductive investment (mg)",side=2,line=2.3,outer=FALSE)
mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
Table_best_corr <- as.data.frame("total plant weight")
Table_best_corr <- bind_cols(Table_best_corr,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(Table_best_corr) <- c("investment category (mg)","r squared","p value","intercept","slope")

mod <- lm(log10(fruit_weight)~log10(repro_inv),data=subset(SummaryInd,fruit_weight>0))
new_row <- as.data.frame("fruit")
new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

yvar <- "repro_inv"
xvar <- "propagule_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlab="",ylab="",lty=results$linetype,pch=20)
mod <- lm(log10(propagule_inv)~log10(repro_inv),data=subset(SummaryInd,propagule_inv>0))
words.top.left.logxy(mod)
mtext(text="investment in propagules (mg)",side=1,line=2,outer=FALSE)
new_row <- as.data.frame("propagules")
new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

mod <- lm(log10(prepollen_all_inv)~log10(repro_inv),data=subset(SummaryInd,prepollen_all_inv>0))
new_row <- as.data.frame("prepollination tissues")
new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

mod <- lm(log10(repro_all_count)~log10(repro_inv),data=subset(SummaryInd,repro_all_count>0))
summary(mod)
new_row <- as.data.frame("repro_all_count")
new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

xvar <- "repro_all_count"
yvar <- "repro_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
results <- lines(fit$groupsummary)
plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000))
mtext(text="buds initiated",side=1,line=2,outer=FALSE)

xvar <- "flower_inv"
yvar <- "repro_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
results <- lines(fit$groupsummary)
plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000))
mtext(text="flower weight * bud count",side=2,line=2,outer=FALSE)
mod <- lm(log10(flower_inv)~log10(repro_inv),data=subset(SummaryInd,flower_inv>0))
new_row <- as.data.frame("flower weight * bud count")
new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

write.csv(Table_best_corr, file="figs2/Accessory_Costs/Table01_estimating_reproInv.csv",row.names=FALSE)

dev.off()

yvar <- "repro_inv"
xvar <- "propagule_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- fit$groupsummary

write.csv(results, file="figs2/Accessory_Costs/Table02extra_propagule_invest_vs_repro_inv.csv",row.names=FALSE)

yvar <- "repro_inv"
xvar <- "diameter"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- fit$groupsummary

write.csv(results, file="figs2/Accessory_Costs/Table02extra_basal_diameter_vs_repro_inv.csv",row.names=FALSE)
```

#Table showing accessory cost values for the species
```{r}
acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,seed_to_ovule_ratio,accessory_per_seed,total_accessory_Lord,prepollencosts,b_div_p,c_div_p,dispersalcosts_increment,dispersalcosts_increment2,prop_accessory_nonzero)
acc_costs_spp$species <- labels.spp.full()
acc_costs_spp <- format(acc_costs_spp, digit=2)

write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table02_AccCosts_by_Species.csv",row.names=FALSE)
```

#Figure 2 and Table 3. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure02_acc_cost_seed_size.wmf", height=4, width=4)
plot

par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(.8,.8,.3,.1)) 
options(scipen = 5)

plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="seed size (mg)",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
slopes <- sma(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
dev.off()

plot(prepollencosts ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(prepollencosts) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
extra.topleft.logxy("slope <1, so bigger seeded species have lower fixed costs of making pre-pollination parts")
slopes <- sma(log10(prepollencosts) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(prepollen_failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
slopes <- sma(log10(prepollen_failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_failure_per_seed,SummarySpp[["se"]]$prepollen_failure_per_seed)
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(c_div_p ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
mod <- lm(log10(c_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
words.top.left.logxy(mod)
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$c_div_p,SummarySpp[["se"]]$c_div_p)
slopes <- sma(log10(c_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1)
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

plot(dispersalcosts_increment ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(dispersalcosts_increment) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"))
words.top.left.logxy(mod)
slopes <- sma(log10(dispersalcosts_increment) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)

acc_by_species$variable = c("total accessory costs","prepollen_success","prepollen_failure","c div p","dispersal")

write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_by_species.csv",row.names=FALSE)
```

#species with bigger seeds, lower seedset spend less per flower. Here taking the percent of the cost to make a single flower that goes into pre-pollination parts
```{r}
win.metafile("figs2/Accessory_Costs/Figure_costs_to_make_1_seed.wmf", height=4, width=12)
plot

par(mfrow=c(1,3), cex=1, omi=c(.8,0.1,.1,0.05), mai=c(.1,.8,.1,0.1))

yvar <- "seedcosts"
xvar <- "seed_size"
data <- subset(SummarySpp[["mean"]])
plot(seedcosts~seed_size,data=data,col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="all costs to make 1 seed (mg) = seedcosts")
slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
abline(slopes$groupsummary["Int"][[1]],1,col="red")
extra.topleft.logxy("total accessory costs required to produce 1 seed are lower for smaller seeded species")
seedcosts_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)

yvar <- "percent_prepollencosts"
plot(percent_prepollencosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for prepollination")
extra.topleft.logxy("species with big seeds have low costs of producing a single flower")
slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
# abline(slopes$groupsummary["Int"][[1]],-1,col="red")
seedcosts_by_species <- dplyr::bind_rows(seedcosts_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

yvar <- "percent_dispersalcosts"
plot(percent_dispersalcosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for dispersal")
extra.topleft.logxy("species with big seeds have high packaging and dispersal costs")
slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
# abline(slopes$groupsummary["Int"][[1]],1,col="red")
seedcosts_by_species <- dplyr::bind_rows(seedcosts_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
mtext(text="seed size (mg)",side=1,line=2,outer=TRUE)

seedcosts_by_species$variable = c("total seedcosts","prepollen costs (% of total)","dispersal costs (% of total)")
write.csv(seedcosts_by_species, file="figs2/Accessory_Costs/Table04_seedcosts_by_species.csv",row.names=FALSE)
dev.off()
```

```{r}
win.metafile("figs2/Accessory_Costs/Figure_seedset_vs_seedsize.wmf", height=5, width=5)
plot

par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5)) 
plot(seedset~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=2)
mod <- lm(log10(seed_size)~log10(seedset),data=subset(SummarySpp[["mean"]]))
#abline(mod$coefficients[1],mod$coefficients[2])
words.top.left.logxy(mod)

dev.off()
```

#Table 4 and Figure 3.Per seed accessory costs are lower in individuals with higher seed count. 
###This effect is true across species, since larger-seeded species produce fewer seeds and have higher per seed accessory costs and true within species, since absolute accessory investment is a function of plant size not seedset
```{r}
win.metafile("figs2/Accessory_Costs/Figure_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
plot

par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))

xvar <- "seed_count"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)

points(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seed_count>0),col="black",pch=16,cex=2.5)
points(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seed_count>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(accessory_per_seed)~log10(seed_count),data=subset(SummarySpp[["mean"]]))
words.top.right.logxy(mod)
legend_with_r2(results,"bottomleft")

results
write.csv(results, file="figs2/Accessory_Costs/Table04a_seedcount_vs_accessory.csv",row.names=FALSE)

dev.off()
```

#Table 4 extra - showing propagule investment instead of seed_count. Could also replace with seedset
```{r}
win.metafile("figs2/Accessory_Costs/Figure_acc_cost_by_seedset.wmf", height=9, width=9)
plot

par(mfrow=c(2,2), cex=1, omi=c(.5,.1,.1,.1), mai=c(.1,1,.3,.1))

xvar <- "seedset"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="total accessory costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000),xaxt="n")
legend_with_r2(results,"bottomleft")

write.csv(results, file="figs2/Accessory_Costs/Table04b_seedset_vs_accessory.csv",row.names=FALSE)

xvar <- "seedset"
yvar <- "b_div_p"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab="b div p = pre-pollination costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000),xaxt="n")
legend_with_r2(results,"bottomleft")

write.csv(results, file="figs2/Accessory_Costs/Table06a_b_div_p_vs_seedset.csv",row.names=FALSE)

xvar <- "seedset"
yvar <- "c_div_p"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy") 
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab="c div p = aborted post pollination (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000))
legend_with_r2(results,"bottomleft")

write.csv(results, file="figs2/Accessory_Costs/Table06b_c_div_p_vs_seedset.csv",row.names=FALSE)

xvar <- "seedset"
yvar <- "packaging_dispersal_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab=yvar,lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000))
legend_with_r2(results,"bottomleft")
mtext(text="seedset",side=1,line=1.5,outer=TRUE)

dev.off()
```

```{r}
xvar <- "seedset"
yvar <- "packaging_dispersal_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)

results <- select(results,group,r2,Slope)
names(results) <- c("species","r2","slope")

results$ovules_per_fruit <- c(60,4,1,1,2,2,2,4,1,40,2,20,2)
max_seedset <- select(SummarySpp[["max"]],species,seedset) 
min_seedset <- select(SummarySpp[["min"]],species,seedset) 
results <- merge(results, max_seedset, by=c("species"), all=TRUE)
results <- merge(results, min_seedset, by=c("species"), all=TRUE)
names(results)=c("species","r2","slope","ovules_per_fruit","max_seedset","min_seedset")

win.metafile("figs2/Accessory_Costs/Table07_dispcosts_vs_ovules.wmf", height=6, width=6)
plot

par(mfrow=c(1,1), cex=1, omi=c(.4,.4,.1,.1), mai=c(.8,.8,.2,.2)) 
plot(ovules_per_fruit~slope,data=subset(results),log="y",col=col.spp(species),pch=16,cex=2,ylab="ovules per fruit",xlab="slope between dispersal costs and seedset")

mod <- lm(slope~log10(ovules_per_fruit),data=subset(results))
words.top.right.logy(mod)
dev.off()

write.csv(results, file="figs2/Accessory_Costs/Table06c_dispersal_vs_seedset.csv",row.names=FALSE)
```

#Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
##Not a single species shows a reduction in per seed accessory costs with increased plant size.Indeed, EPMI has higher pre-pollination accessory costs    (slope = 0.38, r2=0.19, p=0.019) and accessory costs due to aborted fruit and seeds (slope = 0.83, r2=0.268, p=0.019) in larger individuals, as larger individuals of this species have lower seedset (slope = -0.31, r2=0.198, p=0.018). GRSP also has a nearly significant decline in seedset in larger individuals (slope = -0.78, r2=0.298, p=0.067).
```{r}
win.metafile("figs2/Accessory_Costs/Figure_RE_RA_size_age_patterns.wmf", height=8, width=8)
plot

par(mfrow=c(2,2), cex=1, omi=c(.1,0.4,.1,0.05), mai=c(.6,.3,.1,0.1))
options(scipen = 2)

xvar <- "repro_inv"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
legend_with_r2(results,"bottomright")

write.csv(results, file="figs2/Accessory_Costs/Table05a_accessory_vs_RE.csv",row.names=FALSE)

xvar <- "RA"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0&SummaryInd$age>2)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
mtext(text="RA",side=1,line=2,outer=FALSE)
legend_with_r2(results,"topleft")

write.csv(results, file="figs2/Accessory_Costs/Table05b_accessory_vs_RA.csv",row.names=FALSE)

xvar <- "total_weight_0"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
legend_with_r2(results,"bottomright")

write.csv(results, file="figs2/Accessory_Costs/Table05c_accessory_vs_total_weight.csv",row.names=FALSE)

xvar <- "age"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
mtext(text="age (years)",side=1,line=2,outer=FALSE)
mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
legend_with_r2(results,"topleft")

write.csv(results, file="figs2/Accessory_Costs/Table05d_accessory_vs_age.csv",row.names=FALSE)
dev.off()
```

#Considering the individual components of accessory costs vs. seedset - since seedset best predictor of accessory costs

#For each species the accessory cost components that cause shifts in total accessory costs is different and reflects both which components are largest and whichvary most with some factor - seedset, age, etc.
```{r}
xvar1 <- "packaging_dispersal_per_seed"
xvar2 <- "b_div_p"
xvar3 <- "c_div_p"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar1]]>0&SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0)
data <- split(data, data$species)

mod <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar1]]))+(log10(x[[xvar2]]))+(log10(x[[xvar3]]))))
mod_LEES <- lm(log10(accessory_per_seed) ~ (log10(b_div_p)+(log10(c_div_p))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species=="LEES"))
mod_BAER <- lm(log10(accessory_per_seed) ~ (log10(b_div_p)+(log10(packaging_dispersal_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="BAER"))
mod_COER <- lm(log10(accessory_per_seed) ~ (log10(b_div_p)+(log10(packaging_dispersal_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="COER"))

species_coef <- as.data.frame(c("intercept","packaging&dispersal","b_div_p","c_div_p"))

for(i in 1:13) {
     species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[i]]$coefficients))
     }

names(species_coef) <- c("effect","BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")

LEES_c <- as.data.frame(mod_LEES$coefficients)
LEES_c$effect <- c("intercept","b_div_p","c_div_p")
names(LEES_c) <- c("LEES","effect")

species_coef <- dplyr::left_join(species_coef,LEES_c,by="effect")

species_t <- as.data.frame(c("intercept","packaging&dispersal","b_div_p","c_div_p"))
#species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod_BAER$coefficient)[,4])))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[2]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[4]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[5]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[6]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[7]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[8]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[9]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[10]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[11]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[12]])$coefficient[,4]))
species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[13]])$coefficient[,4]))
names(species_t) <- c("effect","BOLE","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")

xvar1 <- "packaging_dispersal_per_seed"
xvar2 <- "b_div_p"
xvar3 <- "c_div_p"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species=="LEES")

summary(mod)

write.csv(species_coef, file="figs2/Accessory_Costs/Table08_breaking_down_accessory_costs_spp.csv",row.names=FALSE)
```

#looking at how the slopes of the relationship between accessory investment and propagule investment shift across species 
##slopes only statistically different from 1 in 2 species
##intercepts quite variable - means that the "baseline" accessory investment, before you get any propagules varies
```{r}
par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1)) 
plot(propagule_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0&propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlab="total accessory investment (mg)",ylab="total propagule investment (mg)")
slope_check <- sma(log10(propagule_inv)~ log10(accessory_inv),data=subset(SummaryInd,propagule_inv>0))
summary(slope_check)

data <- select(SummaryInd,species,propagule_inv,accessory_inv)
data <- subset(data,propagule_inv>0)
data <- split(data, data$species)

for(i in 1:14) {
slope_check <- sma(log10(propagule_inv)~ log10(accessory_inv),data[[i]],slope.test=1)
summary(slope_check)
}

xvar <- "accessory_inv"
yvar <- "propagule_inv"

data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
```

```{r}
win.metafile("figs2/Accessory_Costs/Figure_success_vs_failure.wmf", height=6, width=8)
plot

par(mfrow=c(1,2), cex=1, omi=c(.8,.1,.1,.1), mai=c(.1,.8,.1,.1))

xvar <- "repro_inv"
yvar <- "prop_propagule"

data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,lty=results$linetype,ylim=c(.001,1),xlab="",ylab="prop repro energy to propagules")
abline(-0.30103,0,lwd=2)
abline(-1,0,lwd=2)

xvar <- "repro_inv"
yvar <- "percent_for_success"

data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,lty=results$linetype,ylim=c(.001,1),xlab="",ylab="prop repro energy to success")
abline(-0.30103,0,lwd=2)
abline(-1,0,lwd=2)
mtext(text="reproductive investment (mg)",side=1,line=2,outer=TRUE)

dev.off()
```

```{r}
ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollencosts,dispersalcosts)
ternary$seedcosts = ternary$seed_size + ternary$prepollencosts + ternary$dispersalcosts
ternary$per_seed <-100*ternary$seed_size/ternary$seedcosts
ternary$per_poll <-100*ternary$prepollencosts/ternary$seedcosts
ternary$per_disp <-100*ternary$dispersalcosts/ternary$seedcosts
mod_poll <- sma(per_poll~seedcosts,ternary,slope.test=0,method="OLS",log="x")
mod_seed <- sma(per_seed~seedcosts,ternary,slope.test=0,method="OLS",log="x")
mod_disp <- sma(per_disp~seedcosts,ternary,slope.test=0,method="OLS",log="x")

costs_per_seed <- as.data.frame("costs for seed (%)")
costs_per_seed <- cbind(costs_per_seed,select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")

costs_per_seed2 <- as.data.frame("costs for pre-pollination (%)")
costs_per_seed2 <- cbind(costs_per_seed2,select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)

costs_per_seed2 <- as.data.frame("costs for dispersal (%)")
costs_per_seed2 <- cbind(costs_per_seed2,select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)

write.csv(costs_per_seed, file="figs2/Accessory_Costs/Table08_costs_per_seed.csv",row.names=FALSE)

win.metafile("figs2/Accessory_Costs/seedcost_components.wmf", height=6, width=6)
plot

plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="percent of seedcosts")
points(per_poll~seedcosts,ternary,col="red",pch=20,cex=2)
points(per_disp~seedcosts,ternary,col="blue",pch=20,cex=2)

abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
legend("topleft",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
dev.off()
```

```{r}
win.metafile("figs2/Accessory_Costs/Ternary.wmf", height=6, width=6)
plot

ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
  labs(y = "seed weight (%)",x = "prepoll (%)",z = "pack&disp (%)",title = "Seed cost components",size = 1) +
  geom_point(size=sqrt(ternary$seedcosts/2),shape=20,color=col.spp()) +
   theme_bw() + 
  geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seedcosts/500),size=2)

dev.off()
```

?geom_text

### 2016-02-23 starting_commands.R

@@ -6,5 +6,6 @@ SummarySpp <- readRDS("export/SummarySpp.rds")
 SummarySppAge <- readRDS("export/SummarySppAge.rds")
 HarvestData <- readRDS("export/HarvestData.rds")
 InvestmentByPart <- readRDS("export/Investment_FD_all.rds")
+PartsSummary <- readRDS("export/PartsSummary_all.rds")
 
 source("R/figures.R")

### 2016-02-25 Accessory_figs_20160218.Rmd
accessory cost ms

@@
 
+dev.off()
 #Figure 1. Correlations of various reproductive investment categories against plant weight
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=9, width=13)
+win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=10, width=10)
 plot
 
-par(mfrow=c(2,2), cex=1, omi=c(.1,0.1,.1,0.05), mai=c(.7,.55,.1,0.1))
-options(scipen = 2)
+par(mfrow=c(2,2), cex=1, omi=c(.1,.6,.1,.05), mai=c(.8,.1,.1,.05))
+options(scipen = 4)
 
@@
 results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(10,10000000),xlab="",ylab="",lty=results$linetype,pch=20)
+plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,10000000),xlab="",ylab="",lty=results$linetype,pch=16)
 mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
+abline(0,1)
 words.top.left.logxy(mod)
-mtext(text="total reproductive investment (mg)",side=2,line=2.3,outer=FALSE)
+mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
 mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
@@
 results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlab="",ylab="",lty=results$linetype,pch=20)
+plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,300000), xlab="",ylab="",lty=results$linetype,pch=16)
+abline(0,1)
 mod <- lm(log10(propagule_inv)~log10(repro_inv),data=subset(SummaryInd,propagule_inv>0))
@@
 results <- lines(fit$groupsummary)
-plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000))
+plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
 mtext(text="buds initiated",side=1,line=2,outer=FALSE)
@@
 results <- lines(fit$groupsummary)
-plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000))
-mtext(text="flower weight * bud count",side=2,line=2,outer=FALSE)
+plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,300000))
+abline(0,1)
+mtext(text="flower weight * bud count",side=1,line=2,outer=FALSE)
 mod <- lm(log10(flower_inv)~log10(repro_inv),data=subset(SummaryInd,flower_inv>0))
@@
 
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure02_seedsize_vs_reproinv.wmf", height=5, width=10)
+plot
+
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
+
+plot(repro_inv~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
+mod <- lm(log10(repro_inv)~log10(seed_size),SummarySpp[["mean"]])
+abline(mod$coeff[1],mod$coeff[2])
+words.top.left.logxy(mod)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$repro_inv,SummarySpp[["se"]]$repro_inv)
+
+plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
+mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
+abline(mod$coeff[1],mod$coeff[2])
+words.bottom.left.logxy(mod)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+
+dev.off()
+```
+
 #Table showing accessory cost values for the species
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure02_acc_cost_seed_size.wmf", height=4, width=4)
+win.metafile("figs2/Accessory_Costs/Figure02_seed_size_correlations.wmf", height=5, width=20)
 plot
 
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(.8,.8,.3,.1)) 
+par(mfrow=c(1,4), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
 options(scipen = 5)
 
-plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="seed size (mg)",cex=1.5)
+yvar <- "seedcosts"
+xvar <- "seed_size"
+data <- subset(SummarySpp[["mean"]])
+plot(seedcosts~seed_size,data=data,col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="all costs to make 1 seed (mg) = seedcosts",ylim=c(.02,20000), xlim=c(.02,20000))
+slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
+mod <- lm(log10(seedcosts)~log10(seed_size),SummarySpp[["mean"]])
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+#abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(0,1,col="red")
+words.top.left.logxy(mod)
+
+plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
 mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
@@
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
+#abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(0,1,col="red")
+words.bottom.left.logxy(mod)
+
+plot(repro_inv~seed_size,SummarySpp[["mean"]],log="xy",ylab="reproductive investment (mg)",col=col.spp(species),pch=16, ylim=c(.02,20000), xlim=c(.02,20000),cex=1.5)
+mod <- lm(log10(repro_inv)~log10(seed_size),data=subset(SummarySpp[["mean"]],species!="EPMI"))
+abline(mod$coeff[1],mod$coeff[2])
+words.bottom.left.logxy(mod)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$repro_inv,SummarySpp[["se"]]$repro_inv)
+abline(0,1,col="red")
+
+plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.02,20000),cex=1.5)
+mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
+abline(mod$coeff[1],mod$coeff[2])
+words.bottom.left.logxy(mod)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+
+mtext(text="seed size (mg)",side=1,line=2,outer=TRUE)
+
+dev.off()
+```
+
+```{r}
+plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
+slopes <- sma(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+#abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(0,1,col="red")
+words.bottom.right.logxy(mod)
+
 acc_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
-dev.off()
 
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure_costs_to_make_1_seed.wmf", height=4, width=12)
+win.metafile("figs2/Accessory_Costs/Figure_seedcosts_vs_seedsize.wmf", height=5, width=5)
 plot
 
-par(mfrow=c(1,3), cex=1, omi=c(.8,0.1,.1,0.05), mai=c(.1,.8,.1,0.1))
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
 
@@
 data <- subset(SummarySpp[["mean"]])
-plot(seedcosts~seed_size,data=data,col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="all costs to make 1 seed (mg) = seedcosts")
+plot(seedcosts~seed_size,data=data,col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="seed size (mg)",ylab="all costs to make 1 seed (mg) = seedcosts",ylim=c(.02,10000), xlim=c(.02,10000))
 slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
+mod <- lm(log10(seedcosts)~log10(seed_size),SummarySpp[["mean"]])
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
+#abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(0,1,col="red")
 extra.topleft.logxy("total accessory costs required to produce 1 seed are lower for smaller seeded species")
+words.bottom.right.logxy(mod)
 seedcosts_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
+dev.off()
+```
 
+```{r}
+xvar <- "seed_size"
 yvar <- "percent_prepollencosts"
+data <- subset(SummarySpp[["mean"]])
 plot(percent_prepollencosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for prepollination")
@@
 write.csv(seedcosts_by_species, file="figs2/Accessory_Costs/Table04_seedcosts_by_species.csv",row.names=FALSE)
-dev.off()
 ```
@@
 
+dev.off()
+```
+
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure_acc_cost_by_seedset.wmf", height=5, width=5)
+plot
+
+par(mfrow=c(1,1), cex=1, omi=c(.5,.1,.1,.1), mai=c(.1,1,.3,.1))
+
+xvar <- "seed_size"
+yvar <- "seedcosts"
+
+plot(seedcosts~seed_size,data=subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0),log="xy",pch=16,col=col.spp(species),cex=2)
+mod <-lm(log10(seedcosts)~log10(seed_size),SummaryInd)
+abline(mod$coeff[1],mod$coeff[2])
+words.top.left.logxy(mod)
+
+#text((10^(par()$usr[1])*1.4),(10^(par()$usr[4])*.8),summary(mod)$coefficients[1,1])
 dev.off()
@@
 par(mfrow=c(1,1), cex=1, omi=c(.4,.4,.1,.1), mai=c(.8,.8,.2,.2)) 
-plot(ovules_per_fruit~slope,data=subset(results),log="y",col=col.spp(species),pch=16,cex=2,ylab="ovules per fruit",xlab="slope between dispersal costs and seedset")
-
-mod <- lm(slope~log10(ovules_per_fruit),data=subset(results))
-words.top.right.logy(mod)
+plot(ovules_per_fruit~r2,data=subset(results),log="y",col=col.spp(species),pch=16,cex=2,ylab="ovules per fruit",xlab="slope between dispersal costs and seedset")
+mod <- lm(log10(ovules_per_fruit)~r2,data=subset(results,species!="PELA"))
+abline(mod$coeff[1],mod$coeff[2])
+words.top.left.logy(mod)
 dev.off()
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure_RE_RA_size_age_patterns.wmf", height=8, width=8)
+win.metafile("figs2/Accessory_Costs/Figure_RE_RA_size_age_patterns.wmf", height=10, width=10)
 plot
 
-par(mfrow=c(2,2), cex=1, omi=c(.1,0.4,.1,0.05), mai=c(.6,.3,.1,0.1))
+par(mfrow=c(2,2), cex=1, omi=c(.1,.4,.1,.05), mai=c(.6,.3,.1,.1))
 options(scipen = 2)
@@
 
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure_seedcount_reprocount.wmf", height=5, width=5)
+plot
+
+par(mfrow=c(1,1), cex=1, omi=c(.1,0.1.1,0.05), mai=c(.8,.8,.1,0.1))
+options(scipen = 2)
+
+xvar <- "prepollen_all_count"
+yvar <- "seed_count"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="buds initiated (count)",ylab="seed count",lty=results$linetype,xlim=c(0.9,20000),ylim=c(0.9,20000))
+
+abline(0,1,lwd=2)
+abline(-2,1,lwd=2)
+
+legend_with_r2(results,"topleft")
+
+summary(results)
+summary(fit)
+
+fit2 <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], log="xy",slope.text=1)
+summary(fit2)
+
+dev.off()
+```
 #Considering the individual components of accessory costs vs. seedset - since seedset best predictor of accessory costs
@@
 yvar <- "accessory_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar1]]>0&SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0)
+data <- subset(SummaryInd,SummaryInd[[xvar1]]>0&SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species!="BAER"&species!="COER"&species!="LEES")
 data <- split(data, data$species)
@@
 
-for(i in 1:13) {
+for(i in 1:11) {
      species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[i]]$coefficients))
@@
 
-names(species_coef) <- c("effect","BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")
+names(species_coef) <- c("effect","BOLE","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")
+
+BAER_c <- as.data.frame(mod_BAER$coefficients)
+BAER_c$effect <- c("intercept","b_div_p","packaging&dispersal")
+names(BAER_c) <- c("BAER","effect")
+species_coef <- dplyr::left_join(species_coef,BAER_c,by="effect")
+
+COER_c <- as.data.frame(mod_COER$coefficients)
+COER_c$effect <- c("intercept","b_div_p","packaging&dispersal")
+names(COER_c) <- c("COER","effect")
+species_coef <- dplyr::left_join(species_coef,COER_c,by="effect")
 
@@
 names(LEES_c) <- c("LEES","effect")
-
 species_coef <- dplyr::left_join(species_coef,LEES_c,by="effect")
 
+# Reorder by column name
+species_coef <- species_coef[c("effect", "BAER", "BOLE", "COER", "EPMI", "GRBU", "GRSP", "HATE", "HEPU", "LEES", "PELA", "PEPU", "PHPH", "PILI", "PUTU")]
+
+write.csv(species_coef, file="figs2/Accessory_Costs/Table08_accessory_components_coeff.csv",row.names=FALSE)
+
 species_t <- as.data.frame(c("intercept","packaging&dispersal","b_div_p","c_div_p"))
-#species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod_BAER$coefficient)[,4])))
-species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[2]])$coefficient[,4]))
-species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[4]])$coefficient[,4]))
-species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[5]])$coefficient[,4]))
-species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[6]])$coefficient[,4]))
-species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[7]])$coefficient[,4]))
-species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[8]])$coefficient[,4]))
-species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[9]])$coefficient[,4]))
-species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[10]])$coefficient[,4]))
-species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[11]])$coefficient[,4]))
-species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[12]])$coefficient[,4]))
-species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[13]])$coefficient[,4]))
+
+for(i in 1:11) {
+     species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[i]])$coefficient[,4]))
+     }
+
 names(species_t) <- c("effect","BOLE","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")
 
-xvar1 <- "packaging_dispersal_per_seed"
-xvar2 <- "b_div_p"
-xvar3 <- "c_div_p"
-yvar <- "accessory_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species=="LEES")
+BAER_t <- as.data.frame(summary(mod_BAER)$coefficient[,4])
+BAER_t$effect <- c("intercept","b_div_p","packaging&dispersal")
+names(BAER_t) <- c("BAER","effect")
+species_t <- dplyr::left_join(species_t,BAER_t,by="effect")
 
-summary(mod)
+COER_t <- as.data.frame(summary(mod_COER)$coefficient[,4])
+COER_t$effect <- c("intercept","b_div_p","packaging&dispersal")
+names(COER_t) <- c("COER","effect")
+species_t <- dplyr::left_join(species_t,COER_t,by="effect")
 
-write.csv(species_coef, file="figs2/Accessory_Costs/Table08_breaking_down_accessory_costs_spp.csv",row.names=FALSE)
+LEES_t <- as.data.frame(summary(mod_LEES)$coefficient[,4])
+LEES_t$effect <- c("intercept","b_div_p","c_div_p")
+names(LEES_t) <- c("LEES","effect")
+species_t <- dplyr::left_join(species_t,LEES_t,by="effect")
+
+# Reorder by column name
+species_t <- species_t[c("effect", "BAER", "BOLE", "COER", "EPMI", "GRBU", "GRSP", "HATE", "HEPU", "LEES", "PELA", "PEPU", "PHPH", "PILI", "PUTU")]
+
+write.csv(species_t, file="figs2/Accessory_Costs/Table08_accessory_components_t-value.csv",row.names=FALSE)
+
 ```
@@
 plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="percent of seedcosts")
-points(per_poll~seedcosts,ternary,col="red",pch=20,cex=2)
-points(per_disp~seedcosts,ternary,col="blue",pch=20,cex=2)
+points(per_poll~seedcosts,ternary,col="red",pch=16,cex=2)
+points(per_disp~seedcosts,ternary,col="blue",pch=16,cex=2)
 
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Ternary.wmf", height=6, width=6)
+win.metafile("figs2/Accessory_Costs/Ternary.wmf", height=5, width=5)
 plot
@@
 ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
-  labs(y = "seed weight (%)",x = "prepoll (%)",z = "pack&disp (%)",title = "Seed cost components",size = 1) +
+  labs(y = "seed weight (%)",x = "prepoll (%)",z = "pack&disp (%)",title = "Seed cost components",size = .5) +
   geom_point(size=sqrt(ternary$seedcosts/2),shape=20,color=col.spp()) +
@@
 ```
-
-?geom_text

### 2016-02-25 R/figures.R

@@ -451,6 +451,14 @@ words.top.left.logxy <- function (x) {
   text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=0)
 }
 
+words.top.left.logy <- function (x) {
+  output <- data.frame(select(glance(x), r.squared, p.value))
+  output <- round(output,4)
+  text(((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("r squared = ",output[1]),adj=0,cex=.9)
+  text(((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.88*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),paste("p-value = ",output[2]),adj=0,cex=.9)
+  text(((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=0)
+}
+
 extra.topleft.logxy <- function (words) {
   text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.93*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),words,adj=0,cex=.6)
 }

### 2016-03-03 Accessory_figs_20160218.Rmd
some new acc cost analyses

@@
 dev.off()
+
+```{r}
+SummaryInd$scaled_seed <- SummaryInd$seed_count / SummaryInd$total_weight
+SummaryInd$scaled_bud <- SummaryInd$repro_all_count / SummaryInd$total_weight
+SummaryInd$scaled_failure <- SummaryInd$costs_for_failure / SummaryInd$bud_failed_count
+plot(scaled_seed~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),ylim=c(1e-6,10),xlim=c(1e-3,1e3))
+points(scaled_bud~seed_size,SummaryInd,pch=21,col=col.spp(species))
+mod1 <- sma(scaled_seed~seed_size,data=subset(SummaryInd,scaled_seed!=0),log="xy",slope=1)
+mod2 <- sma(scaled_bud~seed_size,data=subset(SummaryInd,scaled_bud!=0),log="xy",slope=1)
+abline(mod1$coef[[1]][1,1],mod1$coef[[1]][2,1])
+abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue")
+
+summary(mod2)
+summary(mod1)
+```
+
+plot(bud_failed_count~costs_for_failure,SummaryInd,pch=16,log="xy",col=col.spp(species))
+points(costs_for_failure~seed_size,SummaryInd,pch=21,col=col.spp(species))
+mod1 <- sma(costs_for_success~seed_size,data=subset(SummaryInd,costs_for_success>0),log="xy",slope=1)
+mod2 <- sma(costs_for_failure~seed_size,data=subset(SummaryInd,costs_for_failure>0),log="xy",slope=1)
+abline(mod1$coef[[1]][1,1],mod1$coef[[1]][2,1])
+abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue")
+
+plot(prepollen_failure_per_seed~seedcosts,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),xlim=c(1e-2,1e5),ylim=c(1e-2,1e5))
+mod1 <- sma(prepollen_failure_per_seed~seedcosts,data=subset(SummarySpp[["mean"]]),log="xy")
+abline(0,1,col="red")
+summary(mod1)
+
+plot(bud_failed_count~seedcosts,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),xlim=c(1e-2,1e5),ylim=c(1e-2,1e5))
+mod1 <- sma(prepollen_failure_per_seed~seedcosts,data=subset(SummarySpp[["mean"]]),log="xy")
+abline(0,1,col="red")
+summary(mod1)
+
+plot(scaled_failure~seedcosts,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species))
+mod1 <- sma(scaled_failure~seed_size,data=subset(SummarySpp[["mean"]],scaled_failure>0),log="xy",slope=1)
+abline(mod1$coef[[1]][1,1],mod1$coef[[1]][2,1])
+summary(mod1)
+
+mod1 <- sma(costs_for_failure~seedcosts,data=subset(SummaryInd,scaled_failure>0),log="xy",slope=1)
+
+points()
+
+points(costs_for_failure~seed_size,SummarySpp[["mean"]],pch=21,col=col.spp(species))
+mod1 <- sma(costs_for_success~seed_size,data=subset(SummaryInd,costs_for_success>0),log="xy",slope=1)
+mod2 <- sma(costs_for_failure~seed_size,data=subset(SummaryInd,costs_for_failure>0),log="xy",slope=1)
+abline(mod1$coef[[1]][1,1],mod1$coef[[1]][2,1])
+abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue")
+
+mod1$coef
+unique(SummaryInd$scaled_seed)
+
 #Figure 1. Correlations of various reproductive investment categories against plant weight

### 2016-03-03 Accessory_figs_20160303.Rmd
some new acc cost analyses

SummaryInd$flower_inv <-SummaryInd$prepollencosts*SummaryInd$repro_all_count
SummaryInd$percent_for_seeds <- SummaryInd$propagule_inv / SummaryInd$repro_inv
mod <- sma(percent_to_seeds~seed_size,data=subset(SummaryInd,percent_to_seeds>0),log="xy")
summary(mod)

plot(percent_for_success~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species))
mod <- sma(percent_for_success~seed_size,data=subset(SummaryInd,percent_for_success>0),method="OLS", log="xy")
abline(mod$coef[[1]][1,1],mod$coef[[1]][2,1])

plot(percent_for_seeds~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species))
mod <- sma(percent_for_seeds~seed_size,data=subset(SummaryInd,percent_for_seeds>0),method="OLS", log="xy")
abline(mod$coef[[1]][1,1],mod$coef[[1]][2,1])

```{r}
#as seed size increases, the cost of making an additional flower decreases
plot(prepollencosts~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(1e-3,1e2),ylim=c(1e-3,1e2))
mod <- sma(prepollencosts~seed_size,data=subset(SummaryInd,prepollencosts>0),method="OLS", log="xy",slope=1)
abline(mod$coef[[1]][1,1],mod$coef[[1]][2,1])
summary(mod)
abline(0,1,col="red")

plot(repro_inv~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(1e-3,1e2))
mod <- sma(repro_inv~seedcosts,data=subset(SummaryInd,repro_inv>0),method="OLS", log="xy",slope=1)
abline(mod$coef[[1]][1,1],mod$coef[[1]][2,1])
summary(mod)
abline(0,1,col="red")
```

```{r}
mod <- sma(total_weight~repro_inv,data=subset(SummaryInd,repro_inv>0),log="xy",method="OLS", slope=1)
Table_best_corr <- as.data.frame("total plant weight")
Table_best_corr <- bind_cols(Table_best_corr,as.data.frame(mod$r2[[1]]),as.data.frame(mod$pval[[1]]),as.data.frame(mod$coef[[1]][1,1]),
                             as.data.frame(mod$coef[[1]][2,1]),as.data.frame(mod$coef[[1]][2,2]),as.data.frame(mod$coef[[1]][2,3]))
names(Table_best_corr) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_min","slope_max")

mod <- sma(costs_for_failure~repro_inv,data=subset(SummaryInd,costs_for_failure>0),log="xy",method="OLS", slope=1)
new_row <- as.data.frame("failed tissues")
new_row <- bind_cols(new_row,as.data.frame(mod$r2[[1]]),as.data.frame(mod$pval[[1]]),as.data.frame(mod$coef[[1]][1,1]),
                     as.data.frame(mod$coef[[1]][2,1]),as.data.frame(mod$coef[[1]][2,2]),as.data.frame(mod$coef[[1]][2,3]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_min","slope_max")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

mod <- sma(costs_for_success~repro_inv,data=subset(SummaryInd,costs_for_success>0),log="xy",method="OLS", slope=1)
new_row <- as.data.frame("successful tissues")
new_row <- bind_cols(new_row,as.data.frame(mod$r2[[1]]),as.data.frame(mod$pval[[1]]),as.data.frame(mod$coef[[1]][1,1]),
                     as.data.frame(mod$coef[[1]][2,1]),as.data.frame(mod$coef[[1]][2,2]),as.data.frame(mod$coef[[1]][2,3]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_min","slope_max")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

mod <- sma(prepollen_required_inv~repro_inv,data=subset(SummaryInd,prepollen_required_inv>0),log="xy",method="OLS", slope=1)
new_row <- as.data.frame("prepollen_required_investment")
new_row <- bind_cols(new_row,as.data.frame(mod$r2[[1]]),as.data.frame(mod$pval[[1]]),as.data.frame(mod$coef[[1]][1,1]),
                     as.data.frame(mod$coef[[1]][2,1]),as.data.frame(mod$coef[[1]][2,2]),as.data.frame(mod$coef[[1]][2,3]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_min","slope_max")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

mod <- sma(packaging_dispersal_inv~repro_inv,data=subset(SummaryInd,packaging_dispersal_inv>0),log="xy",method="OLS", slope=1)
new_row <- as.data.frame("packaging&dispersal")
new_row <- bind_cols(new_row,as.data.frame(mod$r2[[1]]),as.data.frame(mod$pval[[1]]),as.data.frame(mod$coef[[1]][1,1]),
                     as.data.frame(mod$coef[[1]][2,1]),as.data.frame(mod$coef[[1]][2,2]),as.data.frame(mod$coef[[1]][2,3]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_min","slope_max")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

mod <- sma(propagule_inv~repro_inv,data=subset(SummaryInd,propagule_inv>0),log="xy",method="OLS", slope=1)
new_row <- as.data.frame("propagule")
new_row <- bind_cols(new_row,as.data.frame(mod$r2[[1]]),as.data.frame(mod$pval[[1]]),as.data.frame(mod$coef[[1]][1,1]),
                     as.data.frame(mod$coef[[1]][2,1]),as.data.frame(mod$coef[[1]][2,2]),as.data.frame(mod$coef[[1]][2,3]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_min","slope_max")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

mod <- sma(fruit_weight~repro_inv,data=subset(SummaryInd,fruit_weight>0),log="xy",method="OLS", slope=1)
new_row <- as.data.frame("fruit")
new_row <- bind_cols(new_row,as.data.frame(mod$r2[[1]]),as.data.frame(mod$pval[[1]]),as.data.frame(mod$coef[[1]][1,1]),
                     as.data.frame(mod$coef[[1]][2,1]),as.data.frame(mod$coef[[1]][2,2]),as.data.frame(mod$coef[[1]][2,3]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_min","slope_max")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

mod <- sma(prepollen_all_inv~repro_inv,data=subset(SummaryInd,prepollen_all_inv>0),log="xy",method="OLS", slope=1)
new_row <- as.data.frame("all prepollination tissues")
new_row <- bind_cols(new_row,as.data.frame(mod$r2[[1]]),as.data.frame(mod$pval[[1]]),as.data.frame(mod$coef[[1]][1,1]),
                     as.data.frame(mod$coef[[1]][2,1]),as.data.frame(mod$coef[[1]][2,2]),as.data.frame(mod$coef[[1]][2,3]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_min","slope_max")
Table_best_corr <- bind_rows(Table_best_corr,new_row)

mod <- sma(flower_inv~repro_inv,data=subset(SummaryInd,flower_inv>0),log="xy",method="OLS", slope=1)
new_row <- as.data.frame("flower weight * buds initiated")
new_row <- bind_cols(new_row,as.data.frame(mod$r2[[1]]),as.data.frame(mod$pval[[1]]),as.data.frame(mod$coef[[1]][1,1]),
                     as.data.frame(mod$coef[[1]][2,1]),as.data.frame(mod$coef[[1]][2,2]),as.data.frame(mod$coef[[1]][2,3]))
names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_min","slope_max")
Table_best_corr <- bind_rows(Table_best_corr,new_row)
```

### 2016-03-08 Accessory_figs_20160218.Rmd
work on accessory figures to show how cost of buds vs dispersal shifts with seeds size

--- 2016-02-25 Accessory_figs_20160218.Rmd
@@
-library(smatr)
-library(ggtern)
-budweight <- dplyr::filter(PartsSummary,part%in%c("bud_big","inflorescence_bud_big_flowers"))
-budweight2 <-dplyr::filter(PartsSummary,part=="bud_mid"&species=="PHPH")
-budweight <- dplyr::bind_rows(budweight,budweight2)
-budweight$species <- as.character(budweight$species)
-budweight <-select(budweight,species,weight)
-names(budweight) <-c("species","budweight")
+#seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
+```{r}
 
-SummaryInd <- dplyr::left_join(SummaryInd,budweight,by="species")
-SummaryInd$bud_inv <-SummaryInd$budweight*SummaryInd$repro_all_count
-SummaryInd$flower_inv <-SummaryInd$prepollencosts*SummaryInd$repro_all_count
-SummaryInd$budprop <- SummaryInd$bud_inv + SummaryInd$propagule_inv
+win.metafile("figs2/Accessory_Costs/Figure_costs_of_flowers_vs_seed_size.wmf", height=10, width=10)
+plot
 
+# species with bigger seeds abort a disprortionate # of buds
+# plot(seed_size~scaled_failure_count,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),ylim=c(.01,1000),xlim=c(.00001,100))
+# mod <- sma(seed_size~scaled_failure_count,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="OLS")
+# sma_abline(mod)
+# sma_sum(mod)
+# 
+# species with bigger seeds produce disproportionately few seeds
+# plot(seed_size~scaled_seed_count,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),ylim=c(.01,1000),xlim=c(.00001,100))
+# mod <- sma(seed_size~scaled_seed_count,data=subset(SummarySpp[["mean"]]),log="xy",slope=1,method="OLS")
+# sma_abline(mod)
+# sma_sum(mod)
+
+par(mfcol=c(2,2), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
+options(scipen = 4)
+
+#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
+plot(scaled_seed_count~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n")
+points(scaled_bud_count~seed_size,SummaryInd,pch=21,col=col.spp(species))
+points(scaled_failure_count~seed_size,SummaryInd,pch=2,col=col.spp(species))
+axis(2,yaxp=c(0.00001,0.0001,0.01,1))
+mod1 <- sma(scaled_seed_count~seed_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
+mod2 <- sma(scaled_bud_count~seed_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
+mod3 <- sma(scaled_failure_count~seed_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
+sma_abline(mod1)
+abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue")
+abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red")
+
+plot(0,0,type="n", axes=FALSE, ann=FALSE)
+
+#species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
+plot(scaled_failure_count~prop_prepollencosts,SummarySpp[["mean"]],pch=2,log="y",col=col.spp(species),xlim=c(-.2,1),ylim=c(1e-6,10),cex=1.5)
+mod <- sma(scaled_failure_count~prop_prepollencosts,data=subset(SummarySpp[["mean"]]),log="y",slope=1,method="OLS")
+sma_abline(mod)
+sma_sum(mod)
+par("yaxp")
+
+#species that produce a disproportionte number of seeds can do so because they have proportionately lower dispersal costs
+plot(scaled_seed_count~prop_dispersalcosts,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species),xlim=c(-.2,1),ylim=c(1e-6,10),cex=1.5)
+mod <- sma(scaled_seed_count~prop_dispersalcosts,data=subset(SummarySpp[["mean"]]),log="y",slope=1,method="OLS")
+sma_abline(mod)
+sma_sum(mod)
+
+?par
+
+plot(x,y, xaxt="n")
+axis(1, xaxp=c(10, 200, 19), las=2
+
+sma_sum(mod1)
+sma_sum(mod2)
+sma_sum(mod3)
 dev.off()
+```
+
+#Neither within nor across species, does the proportion of reproductive energy spent on "success" correlate with total reproductive investment
+```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.05))
+
+xvar <- "repro_inv"
+yvar <- "prop_success"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], log="x",method="OLS")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),xlab="",ylab="",lty=results$linetype,pch=16,log="x")
+```
+
+#Table 1. correlations with total repro inv
+```{r}
+results <- as.data.frame(matrix(vector(), 0, 8,
+                dimnames=list(c(), c("variable","r2","pval","Slope","Slope_lowCI","Slope_highCI","Int","Slope_test_p"))),
+                stringsAsFactors=F)
+
+for (i in c("total_weight","failure_inv","success_inv","propagule_inv","packaging_dispersal_inv","prepollen_success_inv","fruit_inv","flower_inv")) {
+yvar <- i
+xvar <- "repro_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+fit <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", log="xy",slope=1)
+temp <- as.data.frame(c(yvar,select(fit$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Slope_test_p)))
+colnames(temp)[1]<- "variable"
+results <- bind_rows(results, temp)
+}
+
+write.csv(results, file="figs2/Accessory_Costs/Table02correlations_with_repro_inv.csv",row.names=FALSE)
+```
+
 #Figure 1. Correlations of various reproductive investment categories against plant weight
@@
 
-library(smatr)
 xvar <- "total_weight_0"
@@
 mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
-Table_best_corr <- as.data.frame("total plant weight")
-Table_best_corr <- bind_cols(Table_best_corr,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
-names(Table_best_corr) <- c("investment category (mg)","r squared","p value","intercept","slope")
-
-mod <- lm(log10(fruit_weight)~log10(repro_inv),data=subset(SummaryInd,fruit_weight>0))
-new_row <- as.data.frame("fruit")
-new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
-names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
-Table_best_corr <- bind_rows(Table_best_corr,new_row)
 
@@
 mtext(text="investment in propagules (mg)",side=1,line=2,outer=FALSE)
-new_row <- as.data.frame("propagules")
-new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
-names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
-Table_best_corr <- bind_rows(Table_best_corr,new_row)
-
-mod <- lm(log10(prepollen_all_inv)~log10(repro_inv),data=subset(SummaryInd,prepollen_all_inv>0))
-new_row <- as.data.frame("prepollination tissues")
-new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
-names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
-Table_best_corr <- bind_rows(Table_best_corr,new_row)
-
-mod <- lm(log10(repro_all_count)~log10(repro_inv),data=subset(SummaryInd,repro_all_count>0))
-summary(mod)
-new_row <- as.data.frame("repro_all_count")
-new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
-names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
-Table_best_corr <- bind_rows(Table_best_corr,new_row)
 
@@
 mtext(text="flower weight * bud count",side=1,line=2,outer=FALSE)
-mod <- lm(log10(flower_inv)~log10(repro_inv),data=subset(SummaryInd,flower_inv>0))
-new_row <- as.data.frame("flower weight * bud count")
-new_row <- bind_cols(new_row,select(glance(mod),r.squared,p.value),as.data.frame(mod$coefficients[1]),as.data.frame(mod$coefficients[2]))
-names(new_row) <- c("investment category (mg)","r squared","p value","intercept","slope")
-Table_best_corr <- bind_rows(Table_best_corr,new_row)
-
-write.csv(Table_best_corr, file="figs2/Accessory_Costs/Table01_estimating_reproInv.csv",row.names=FALSE)
 
 dev.off()
+```
 
+#correlations between repro inv and propagule inv by species
+```{r}
 yvar <- "repro_inv"
@@
 write.csv(results, file="figs2/Accessory_Costs/Table02extra_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
+```
 
-yvar <- "repro_inv"
-xvar <- "diameter"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+#when reproductive investment is scaled by leaf area there is no significant difference by seed size - so increase in repro inv with seed size simply because species with bigger seeds are bigger plants
+```{r}
+plot(invest_per_leaf_area~seed_size,SummaryInd, col=col.spp(species),pch=16,log="xy")
+points(invest_per_leaf_area~seed_size,SummarySpp[["mean"]], cex=2, col=col.spp(species),pch=16,log="xy")
+mod <-sma(invest_per_leaf_area~seed_size,SummarySpp[["mean"]],log="xy",method="OLS")
+summary(mod)
+```
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- fit$groupsummary
-
-write.csv(results, file="figs2/Accessory_Costs/Table02extra_basal_diameter_vs_repro_inv.csv",row.names=FALSE)
-```
+#Consider how accessory cost components shift in terms of costs per seed, and cost as fraction total reproductive investment
 
@@
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
-slopes <- sma(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
+slopes <- sma(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-#species with bigger seeds, lower seedset spend less per flower. Here taking the percent of the cost to make a single flower that goes into pre-pollination parts
+#species with bigger seeds, lower seedset spend less per flower. Here taking the prop of the cost to make a single flower that goes into pre-pollination parts
 ```{r}
@@
 xvar <- "seed_size"
-yvar <- "percent_prepollencosts"
+yvar <- "prop_prepollencosts"
 data <- subset(SummarySpp[["mean"]])
-plot(percent_prepollencosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for prepollination")
+plot(prop_prepollencosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for prepollination")
 extra.topleft.logxy("species with big seeds have low costs of producing a single flower")
@@
 
-yvar <- "percent_dispersalcosts"
-plot(percent_dispersalcosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for dispersal")
+yvar <- "prop_dispersalcosts"
+plot(prop_dispersalcosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for dispersal")
 extra.topleft.logxy("species with big seeds have high packaging and dispersal costs")
@@
 
+```{r}
+plot.new()
+par(mfrow=c(2,3), cex=1, omi=c(.1,0.1,0.1,0.05), mai=c(.8,.8,.1,0.1))
+
+results <- as.data.frame(matrix(vector(), 0, 8,
+                dimnames=list(c(), c("variable","r2","pval","Slope","Slope_lowCI","Slope_highCI","Int","Slope_test_p"))),
+                stringsAsFactors=F)
+
+for (i in c("prop_propagule","prop_success","prop_dispersalcosts","prop_prepollencosts","prop_seedcosts")) {
+yvar <- i
+xvar <- "seed_size"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+data2 <- subset(SummarySpp[["mean"]])
+fit <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", log="x",slope=1)
+temp <- as.data.frame(c(yvar,select(fit$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Slope_test_p)))
+colnames(temp)[1]<- "variable"
+results <- bind_rows(results, temp)
+plot(data[[yvar]] ~ data[[xvar]],log="x",col=col.spp(data$species),pch=16,xlim=c(.01,500),ylim=c(.001,1.1))
+points(data2[[yvar]] ~ data2[[xvar]],col=col.spp(data2$species),pch=16,cex=2)
+}
+
+write.csv(results, file="figs2/Accessory_Costs/Table_prop_tissues_inv_by_seed_size.csv",row.names=FALSE) 
+```
+
 #looking at how the slopes of the relationship between accessory investment and propagule investment shift across species 
@@
 xvar <- "repro_inv"
-yvar <- "percent_for_success"
+yvar <- "prop_success"
 
@@
 
-plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="percent of seedcosts")
+plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seedcosts")
 points(per_poll~seedcosts,ternary,col="red",pch=16,cex=2)

### 2016-03-10 Accessory_figs_20160218.Rmd
mainly streamlining variable calculations and names need to change "assignments" of some developing cones, stalks to part of aborted categories

@@
+plot(failure_inv~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species))
+plot(abortedcosts~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),pch=16,log="xy",col=col.spp(species))
+mod <- sma(abortedcosts~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),log="xy",method="OLS",slope=1)
+summary(mod)
+
+plot(prepollen_failure_per_seed~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),pch=16,log="xy",col=col.spp(species))
+mod <- sma(prepollen_failure_per_seed~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),log="xy",method="OLS",slope=1)
+summary(mod)
+
+plot(scaled_failure_count~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),pch=16,log="xy",col=col.spp(species))
+mod <- sma(bud_failed_count~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),log="xy",method="OLS",slope=1)
+summary(mod)
+
 #seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
@@
 
-win.metafile("figs2/Accessory_Costs/Figure_costs_of_flowers_vs_seed_size.wmf", height=10, width=10)
+win.metafile("figs2/Accessory_Costs/Figure_cost_of_flowers_vs_seed_size.wmf", height=4, width=12)
 plot
@@
 
-par(mfcol=c(2,2), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
+par(mfcol=c(1,3), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
 options(scipen = 4)
@@
 #put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
-plot(scaled_seed_count~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n")
+plot(scaled_seed_count~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n",xaxt="n")
 points(scaled_bud_count~seed_size,SummaryInd,pch=21,col=col.spp(species))
-points(scaled_failure_count~seed_size,SummaryInd,pch=2,col=col.spp(species))
-axis(2,yaxp=c(0.00001,0.0001,0.01,1))
+#points(scaled_failure_count~seed_size,SummaryInd,pch=2,col=col.spp(species))
+axis(2, at=c(0.000001,0.0001,0.01,1), labels=c(0.000001,0.0001,0.01,1),cex.axis=0.9)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
+
 mod1 <- sma(scaled_seed_count~seed_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
@@
 
-plot(0,0,type="n", axes=FALSE, ann=FALSE)
+#plot(0,0,type="n", axes=FALSE, ann=FALSE)
 
 #species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
-plot(scaled_failure_count~prop_prepollencosts,SummarySpp[["mean"]],pch=2,log="y",col=col.spp(species),xlim=c(-.2,1),ylim=c(1e-6,10),cex=1.5)
-mod <- sma(scaled_failure_count~prop_prepollencosts,data=subset(SummarySpp[["mean"]]),log="y",slope=1,method="OLS")
-sma_abline(mod)
-sma_sum(mod)
-par("yaxp")
-
-#species that produce a disproportionte number of seeds can do so because they have proportionately lower dispersal costs
-plot(scaled_seed_count~prop_dispersalcosts,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species),xlim=c(-.2,1),ylim=c(1e-6,10),cex=1.5)
-mod <- sma(scaled_seed_count~prop_dispersalcosts,data=subset(SummarySpp[["mean"]]),log="y",slope=1,method="OLS")
+plot(seedset~prop_prepollencosts,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species),xlim=c(-.2,1),cex=1.5)
+mod <- sma(seedset~prop_prepollencosts,data=subset(SummarySpp[["mean"]]),log="y",slope=1,method="OLS")
 sma_abline(mod)
@@
 
-?par
-
-plot(x,y, xaxt="n")
-axis(1, xaxp=c(10, 200, 19), las=2
+#species that produce a disproportionte number of seeds can do so because they have proportionately lower dispersal costs
+plot(seedset~prop_dispersalcosts,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species),xlim=c(-.2,1),cex=1.5)
+mod <- sma(seedset~prop_dispersalcosts,data=subset(SummarySpp[["mean"]]),log="y",slope=1,method="OLS")
+sma_abline(mod)
+sma_sum(mod)
 
@@
 ```{r}
-plot(invest_per_leaf_area~seed_size,SummaryInd, col=col.spp(species),pch=16,log="xy")
-points(invest_per_leaf_area~seed_size,SummarySpp[["mean"]], cex=2, col=col.spp(species),pch=16,log="xy")
-mod <-sma(invest_per_leaf_area~seed_size,SummarySpp[["mean"]],log="xy",method="OLS")
+plot(scaled_repro_inv~seed_size,SummaryInd, col=col.spp(species),pch=16,log="xy")
+points(scaled_repro_inv~seed_size,SummarySpp[["mean"]], cex=2, col=col.spp(species),pch=16,log="xy")
+mod <-sma(scaled_repro_inv~seed_size,SummarySpp[["mean"]],log="xy",method="OLS")
 summary(mod)
@@
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,seed_to_ovule_ratio,accessory_per_seed,total_accessory_Lord,prepollencosts,b_div_p,c_div_p,dispersalcosts_increment,dispersalcosts_increment2,prop_accessory_nonzero)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,seedset,accessory_per_seed,prepollencosts,prepollen_all_per_seed,postpollen_aborted_per_seed,packaging_dispersal_per_seed,prop_accessory_nonzero)
 acc_costs_spp$species <- labels.spp.full()
@@
 
-plot(c_div_p ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-mod <- lm(log10(c_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
+plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
 words.top.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$c_div_p,SummarySpp[["se"]]$c_div_p)
-slopes <- sma(log10(c_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
+slopes <- sma(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1)
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot(dispersalcosts_increment ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(dispersalcosts_increment) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"))
+plot(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(packaging_dispersal_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"))
 words.top.left.logxy(mod)
-slopes <- sma(log10(dispersalcosts_increment) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
+slopes <- sma(log10(packaging_dispersal_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
+remove(SummaryInd)
 #Table 4 extra - showing propagule investment instead of seed_count. Could also replace with seedset
@@
 xvar <- "seedset"
-yvar <- "b_div_p"
+yvar <- "prepollen_all_per_seed"
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table06a_b_div_p_vs_seedset.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table06a_prepollen_all_per_seed_vs_seedset.csv",row.names=FALSE)
 
 xvar <- "seedset"
-yvar <- "c_div_p"
+yvar <- "postpollen_aborted_per_seed"
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table06b_c_div_p_vs_seedset.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table06b_postpollen_aborted_per_seed_vs_seedset.csv",row.names=FALSE)
 
@@
 xvar1 <- "packaging_dispersal_per_seed"
-xvar2 <- "b_div_p"
-xvar3 <- "c_div_p"
+xvar2 <- "prepollen_all_per_seed"
+xvar3 <- "postpollen_aborted_per_seed"
 yvar <- "accessory_per_seed"
@@
 mod <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar1]]))+(log10(x[[xvar2]]))+(log10(x[[xvar3]]))))
-mod_LEES <- lm(log10(accessory_per_seed) ~ (log10(b_div_p)+(log10(c_div_p))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species=="LEES"))
-mod_BAER <- lm(log10(accessory_per_seed) ~ (log10(b_div_p)+(log10(packaging_dispersal_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="BAER"))
-mod_COER <- lm(log10(accessory_per_seed) ~ (log10(b_div_p)+(log10(packaging_dispersal_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="COER"))
+mod_LEES <- lm(log10(accessory_per_seed) ~ (log10(prepollen_all_per_seed)+(log10(postpollen_aborted_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species=="LEES"))
+mod_BAER <- lm(log10(accessory_per_seed) ~ (log10(prepollen_all_per_seed)+(log10(packaging_dispersal_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="BAER"))
+mod_COER <- lm(log10(accessory_per_seed) ~ (log10(prepollen_all_per_seed)+(log10(packaging_dispersal_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="COER"))
 
-species_coef <- as.data.frame(c("intercept","packaging&dispersal","b_div_p","c_div_p"))
+species_coef <- as.data.frame(c("intercept","packaging&dispersal","prepollen_all_per_seed","postpollen_aborted_per_seed"))
 
@@
 BAER_c <- as.data.frame(mod_BAER$coefficients)
-BAER_c$effect <- c("intercept","b_div_p","packaging&dispersal")
+BAER_c$effect <- c("intercept","prepollen_all_per_seed","packaging&dispersal")
 names(BAER_c) <- c("BAER","effect")
@@
 COER_c <- as.data.frame(mod_COER$coefficients)
-COER_c$effect <- c("intercept","b_div_p","packaging&dispersal")
+COER_c$effect <- c("intercept","prepollen_all_per_seed","packaging&dispersal")
 names(COER_c) <- c("COER","effect")
@@
 LEES_c <- as.data.frame(mod_LEES$coefficients)
-LEES_c$effect <- c("intercept","b_div_p","c_div_p")
+LEES_c$effect <- c("intercept","prepollen_all_per_seed","postpollen_aborted_per_seed")
 names(LEES_c) <- c("LEES","effect")
@@
 
-species_t <- as.data.frame(c("intercept","packaging&dispersal","b_div_p","c_div_p"))
+species_t <- as.data.frame(c("intercept","packaging&dispersal","prepollen_all_per_seed","postpollen_aborted_per_seed"))
 
@@
 BAER_t <- as.data.frame(summary(mod_BAER)$coefficient[,4])
-BAER_t$effect <- c("intercept","b_div_p","packaging&dispersal")
+BAER_t$effect <- c("intercept","prepollen_all_per_seed","packaging&dispersal")
 names(BAER_t) <- c("BAER","effect")
@@
 COER_t <- as.data.frame(summary(mod_COER)$coefficient[,4])
-COER_t$effect <- c("intercept","b_div_p","packaging&dispersal")
+COER_t$effect <- c("intercept","prepollen_all_per_seed","packaging&dispersal")
 names(COER_t) <- c("COER","effect")
@@
 LEES_t <- as.data.frame(summary(mod_LEES)$coefficient[,4])
-LEES_t$effect <- c("intercept","b_div_p","c_div_p")
+LEES_t$effect <- c("intercept","prepollen_all_per_seed","postpollen_aborted_per_seed")
 names(LEES_t) <- c("LEES","effect")

### 2016-03-10 R/Summaries.R

@@ -39,28 +39,28 @@ process_prepollination_costs <- function(seedsize, PartsSummary_all) {
  
 
 # adding info on all costs to produce flower at time of pollination
-  prepollencosts <- list()
-  prepollencosts[["BAER"]] <- list(parts=c("cone_green","flower_petals","flower_stigma","flower_style"), scale=c(1/60,1/2,1/2,1/2))
-  prepollencosts[["BOLE"]] <- list(parts=c("flower_petals","flower_calyx","pedicel"), scale=c(1/4,1/4,1/4))
-  prepollencosts[["COER"]] <- list(parts=c("inflorescence_stalk","flower_petals", "flower_stigma"), scale=c(1/6,1,1))
-  prepollencosts[["EPMI"]] <- list(parts=c("flower_petals", "flower_calyx"), scale=c(1/15,1/15))
-  prepollencosts[["GRBU"]] <- list(parts=c("inflorescence_stalk","flower_petals","flower_stigma"), scale=c(1/20,1/2,1/2))
-  prepollencosts[["GRSP"]] <- list(parts=c("inflorescence_stalk","flower_petals","flower_stigma"), scale=c(1/20,1/2,1/2))
-  prepollencosts[["HATE"]] <- list(parts=c("inflorescence_bud_big_bracts","flower_petals","flower_stigma"), scale=c(1/2,1/2,1/2))
-  prepollencosts[["HEPU"]] <- list(parts=c("flower_petals","flower_calyx"), scale=c(1/4,1/4))
-  prepollencosts[["LEES"]] <- list(parts=c("flower_petals","flower_calyx"), scale=c(1,1))
-  prepollencosts[["PELA"]] <- list(parts=c("flower_petals","pedicel","flower_stigma"), scale=c(1,1,1))
-  prepollencosts[["PEPU"]] <- list(parts=c("cone_green","flower_petals","flower_calyx","flower_stigma"), scale=c(1/40,1,1,1))
-  prepollencosts[["PHPH"]] <- list(parts=c("flower_petals","flower_calyx","bract_flower_or_finished_flower","flower_stigma"), scale=c(1/2,1/2,1/2,1/2))
-  prepollencosts[["PILI"]] <- list(parts=c("inflorescence_stalk","bract_flower_or_finished_flower","flower_petals","flower_calyx","flower_stigma"), scale=c(1/10,1/10,1/10,1/10,1))
[…]

### 2016-03-15 Accessory_figs_20160218.Rmd
fine-tuning calculations for accessory costs

@@
 
+plot(seedset~prop_prepollencosts,data=subset(SummaryInd,seedset>0),pch=16,log="y",col=col.spp(species))
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")
+mod <-sma(seedset~prop_prepollencosts,data=subset(SummarySpp[["mean"]],seedset>0&species!="PHPH"&species!="PUTU"),log="",method="OLS")
+summary(mod)
+sma_abline(mod)
+
+write.csv(PartsSummary, file="figs2/Accessory_Costs/PartsSummary.csv",row.names=FALSE)
+
 #seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
@@
 
-win.metafile("figs2/Accessory_Costs/Figure_cost_of_flowers_vs_seed_size.wmf", height=4, width=12)
+win.metafile("figs2/Accessory_Costs/Figure_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
 plot
 
-# species with bigger seeds abort a disprortionate # of buds
-# plot(seed_size~scaled_failure_count,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),ylim=c(.01,1000),xlim=c(.00001,100))
-# mod <- sma(seed_size~scaled_failure_count,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="OLS")
-# sma_abline(mod)
-# sma_sum(mod)
-# 
-# species with bigger seeds produce disproportionately few seeds
-# plot(seed_size~scaled_seed_count,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),ylim=c(.01,1000),xlim=c(.00001,100))
-# mod <- sma(seed_size~scaled_seed_count,data=subset(SummarySpp[["mean"]]),log="xy",slope=1,method="OLS")
-# sma_abline(mod)
-# sma_sum(mod)
-
-par(mfcol=c(1,3), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
+par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
 options(scipen = 4)
@@
 #put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
-plot(scaled_seed_count~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n",xaxt="n")
+plot(scaled_seed_count~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="seed size (mg)",ylab="count, scaled to plant size")
 points(scaled_bud_count~seed_size,SummaryInd,pch=21,col=col.spp(species))
@@
 abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red")
+legend("topright",legend=c("seed count","total bud count","failed flower count"),col=c("black","blue","red"),pch=c(16,21,8),bty="n")
 
-#plot(0,0,type="n", axes=FALSE, ann=FALSE)
+plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,1000),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="seed size (mg)",ylab="seed set")
+mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
+abline(mod$coeff[1],mod$coeff[2])
+text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
+     paste("r2 = ",round(glance(mod)[1],2)),adj=1)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")
 
 #species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
-plot(seedset~prop_prepollencosts,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species),xlim=c(-.2,1),cex=1.5)
-mod <- sma(seedset~prop_prepollencosts,data=subset(SummarySpp[["mean"]]),log="y",slope=1,method="OLS")
+plot(prop_prepollencosts~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.01,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
+mod <- sma(prop_prepollencosts~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
+y.error.bars(SummarySpp[["mean"]]$seedset,SummarySpp[["mean"]]$prop_prepollencosts,SummarySpp[["se"]]$prop_prepollencosts)
 sma_abline(mod)
 sma_sum(mod)
+text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
+     paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
+axis(2, at=c(-0.2,0,.2,.4,.6,.8,1), labels=c("",0.0,0.2,0.4,0.6,0.8,""),cex.axis=1)
 
-#species that produce a disproportionte number of seeds can do so because they have proportionately lower dispersal costs
-plot(seedset~prop_dispersalcosts,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species),xlim=c(-.2,1),cex=1.5)
-mod <- sma(seedset~prop_dispersalcosts,data=subset(SummarySpp[["mean"]]),log="y",slope=1,method="OLS")
-sma_abline(mod)
-sma_sum(mod)
-
-sma_sum(mod1)
-sma_sum(mod2)
-sma_sum(mod3)
 dev.off()
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=10, width=10)
+win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=5, width=10)
 plot
 
-par(mfrow=c(2,2), cex=1, omi=c(.1,.6,.1,.05), mai=c(.8,.1,.1,.05))
+par(mfrow=c(1,2), cex=1, omi=c(.1,.6,.1,.05), mai=c(.8,.1,.1,.05))
 options(scipen = 4)
@@
 results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,10000000),xlab="",ylab="",lty=results$linetype,pch=16)
+#plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,10000000),xlab="",ylab="",lty=results$linetype,pch=16)
 mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
 abline(0,1)
-words.top.left.logxy(mod)
-mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
-mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
+#words.top.left.logxy(mod)
+#mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
+#mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
 
@@
 mod <- lm(log10(propagule_inv)~log10(repro_inv),data=subset(SummaryInd,propagule_inv>0))
-words.top.left.logxy(mod)
 mtext(text="investment in propagules (mg)",side=1,line=2,outer=FALSE)
+mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
 
@@
 results <- lines(fit$groupsummary)
-plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
-mtext(text="buds initiated",side=1,line=2,outer=FALSE)
+#plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
+#mtext(text="buds initiated",side=1,line=2,outer=FALSE)
 
@@
 results <- lines(fit$groupsummary)
-plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,300000))
+plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,300000),yaxt="n")
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 abline(0,1)
-mtext(text="flower weight * bud count",side=1,line=2,outer=FALSE)
+mtext(text="flower weight * bud count (mg)",side=1,line=2,outer=FALSE)
 
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure02_seedsize_vs_reproinv.wmf", height=5, width=10)
-plot
-
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
 
@@
 
+win.metafile("figs2/Accessory_Costs/Figure02_seedsize_vs_reproinv.wmf", height=5, width=5)
+plot
+
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
 plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
@@
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,seedset,accessory_per_seed,prepollencosts,prepollen_all_per_seed,postpollen_aborted_per_seed,packaging_dispersal_per_seed,prop_accessory_nonzero)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,seedset,accessory_per_seed,prepollencosts,prepollen_all_per_seed,prepollen_failure_per_seed,postpollen_aborted_per_seed,packaging_dispersal_per_seed,prop_accessory_nonzero)
 acc_costs_spp$species <- labels.spp.full()
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure02_seed_size_correlations.wmf", height=5, width=20)
+win.metafile("figs2/Accessory_Costs/Figure02_seed_size_correlations.wmf", height=5, width=15)
 plot
 
-par(mfrow=c(1,4), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+par(mfrow=c(1,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
 options(scipen = 5)
 
-yvar <- "seedcosts"
-xvar <- "seed_size"
-data <- subset(SummarySpp[["mean"]])
-plot(seedcosts~seed_size,data=data,col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="all costs to make 1 seed (mg) = seedcosts",ylim=c(.02,20000), xlim=c(.02,20000))
-slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
-mod <- lm(log10(seedcosts)~log10(seed_size),SummarySpp[["mean"]])
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-#abline(slopes$groupsummary["Int"][[1]],1,col="red")
-abline(0,1,col="red")
-words.top.left.logxy(mod)
-
-plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
+plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
 mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
-slopes <- sma(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,log="xy")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-#abline(slopes$groupsummary["Int"][[1]],1,col="red")
-abline(0,1,col="red")
-words.bottom.left.logxy(mod)
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
 
-plot(repro_inv~seed_size,SummarySpp[["mean"]],log="xy",ylab="reproductive investment (mg)",col=col.spp(species),pch=16, ylim=c(.02,20000), xlim=c(.02,20000),cex=1.5)
-mod <- lm(log10(repro_inv)~log10(seed_size),data=subset(SummarySpp[["mean"]],species!="EPMI"))
-abline(mod$coeff[1],mod$coeff[2])
-words.bottom.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$repro_inv,SummarySpp[["se"]]$repro_inv)
-abline(0,1,col="red")
+plot(prepollencosts~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pre-pollination costs per seed (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
+mod <- lm(log10(prepollencosts)~log10(seed_size),SummarySpp[["mean"]])
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
 
-plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.02,20000),cex=1.5)
-mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
-abline(mod$coeff[1],mod$coeff[2])
-words.bottom.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
-
-mtext(text="seed size (mg)",side=1,line=2,outer=TRUE)
-
+plot(packaging_dispersal_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="packaging and dispersal costs per seed (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
+mod <- lm(log10(packaging_dispersal_per_seed)~log10(seed_size),SummarySpp[["mean"]])
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
 dev.off()
@@
 ```{r}
+par(mfrow=c(2,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+options(scipen = 5)
+
 plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
@@
 words.top.left.logxy(mod)
-slopes <- sma(log10(packaging_dispersal_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
+slopes <- sma(log10(packaging_dispersal_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"),slope.test=1)
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_by_species.csv",row.names=FALSE)
-```
-
-#species with bigger seeds, lower seedset spend less per flower. Here taking the prop of the cost to make a single flower that goes into pre-pollination parts
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure_seedcosts_vs_seedsize.wmf", height=5, width=5)
-plot
-
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
-
-yvar <- "seedcosts"
-xvar <- "seed_size"
-data <- subset(SummarySpp[["mean"]])
-plot(seedcosts~seed_size,data=data,col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="seed size (mg)",ylab="all costs to make 1 seed (mg) = seedcosts",ylim=c(.02,10000), xlim=c(.02,10000))
-slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
-mod <- lm(log10(seedcosts)~log10(seed_size),SummarySpp[["mean"]])
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-#abline(slopes$groupsummary["Int"][[1]],1,col="red")
-abline(0,1,col="red")
-extra.topleft.logxy("total accessory costs required to produce 1 seed are lower for smaller seeded species")
-words.bottom.right.logxy(mod)
-seedcosts_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
-dev.off()
-```
-
-```{r}
-xvar <- "seed_size"
-yvar <- "prop_prepollencosts"
-data <- subset(SummarySpp[["mean"]])
-plot(prop_prepollencosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for prepollination")
-extra.topleft.logxy("species with big seeds have low costs of producing a single flower")
-slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-# abline(slopes$groupsummary["Int"][[1]],-1,col="red")
-seedcosts_by_species <- dplyr::bind_rows(seedcosts_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-yvar <- "prop_dispersalcosts"
-plot(prop_dispersalcosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for dispersal")
-extra.topleft.logxy("species with big seeds have high packaging and dispersal costs")
-slopes <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", slope.test=1,log="xy")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-# abline(slopes$groupsummary["Int"][[1]],1,col="red")
-seedcosts_by_species <- dplyr::bind_rows(seedcosts_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-mtext(text="seed size (mg)",side=1,line=2,outer=TRUE)
-
-seedcosts_by_species$variable = c("total seedcosts","prepollen costs (% of total)","dispersal costs (% of total)")
-write.csv(seedcosts_by_species, file="figs2/Accessory_Costs/Table04_seedcosts_by_species.csv",row.names=FALSE)
-```
-
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure_seedset_vs_seedsize.wmf", height=5, width=5)
-plot
-
-par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5)) 
-plot(seedset~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=2)
-mod <- lm(log10(seed_size)~log10(seedset),data=subset(SummarySpp[["mean"]]))
-#abline(mod$coefficients[1],mod$coefficients[2])
-words.top.left.logxy(mod)
-
-dev.off()
 ```
@@
 
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure_acc_cost_by_seedset.wmf", height=5, width=5)
-plot
-
-par(mfrow=c(1,1), cex=1, omi=c(.5,.1,.1,.1), mai=c(.1,1,.3,.1))
-
-xvar <- "seed_size"
-yvar <- "seedcosts"
-
-plot(seedcosts~seed_size,data=subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0),log="xy",pch=16,col=col.spp(species),cex=2)
-mod <-lm(log10(seedcosts)~log10(seed_size),SummaryInd)
-abline(mod$coeff[1],mod$coeff[2])
-words.top.left.logxy(mod)
-
-#text((10^(par()$usr[1])*1.4),(10^(par()$usr[4])*.8),summary(mod)$coefficients[1,1])
-dev.off()
-```
-
-remove(SummaryInd)
 #Table 4 extra - showing propagule investment instead of seed_count. Could also replace with seedset
@@
 results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab="b div p = pre-pollination costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000),xaxt="n")
+plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab="pre-pollination costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000),xaxt="n")
 legend_with_r2(results,"bottomleft")
@@
 results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab="c div p = aborted post pollination (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000))
+plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab="aborted post pollination costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000))
 legend_with_r2(results,"bottomleft")
@@
 
-results$ovules_per_fruit <- c(60,4,1,1,2,2,2,4,1,40,2,20,2)
+results$ovules_per_fruit <- c(60,4,1,1,2,2,2,4,1,40,2,1,2)
 max_seedset <- select(SummarySpp[["max"]],species,seedset) 
@@
 par(mfrow=c(1,1), cex=1, omi=c(.4,.4,.1,.1), mai=c(.8,.8,.2,.2)) 
-plot(ovules_per_fruit~r2,data=subset(results),log="y",col=col.spp(species),pch=16,cex=2,ylab="ovules per fruit",xlab="slope between dispersal costs and seedset")
+plot(ovules_per_fruit~r2,data=subset(results),log="y",col=col.spp(species),pch=16,cex=2,ylab="ovules per flower",xlab="slope between dispersal costs and seedset")
 mod <- lm(log10(ovules_per_fruit)~r2,data=subset(results,species!="PELA"))
@@
 write.csv(results, file="figs2/Accessory_Costs/Table05a_accessory_vs_RE.csv",row.names=FALSE)
-
-xvar <- "RA"
-yvar <- "accessory_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0&SummaryInd$age>2)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
-mtext(text="RA",side=1,line=2,outer=FALSE)
-legend_with_r2(results,"topleft")
-
-write.csv(results, file="figs2/Accessory_Costs/Table05b_accessory_vs_RA.csv",row.names=FALSE)
 
@@
 
-par(mfrow=c(1,1), cex=1, omi=c(.1,0.1.1,0.05), mai=c(.8,.8,.1,0.1))
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,0.05), mai=c(.8,.8,.1,0.1))
 options(scipen = 2)
@@
 
-summary(results)
-summary(fit)
-
-fit2 <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], log="xy",slope.text=1)
-summary(fit2)
-
 dev.off()
@@
 xvar1 <- "packaging_dispersal_per_seed"
-xvar2 <- "prepollen_all_per_seed"
+xvar2 <- "prepollencosts"
 xvar3 <- "postpollen_aborted_per_seed"
+xvar4 <- "prepollen_failure_per_seed"
 yvar <- "accessory_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar1]]>0&SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species!="BAER"&species!="COER"&species!="LEES")
+data <- subset(SummaryInd,SummaryInd[[xvar1]]>0&SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&SummaryInd[[xvar4]]>0&SummaryInd[[yvar]]>0&species!="BAER"&species!="COER"&species!="LEES")
 data <- split(data, data$species)
 
-mod <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar1]]))+(log10(x[[xvar2]]))+(log10(x[[xvar3]]))))
-mod_LEES <- lm(log10(accessory_per_seed) ~ (log10(prepollen_all_per_seed)+(log10(postpollen_aborted_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species=="LEES"))
-mod_BAER <- lm(log10(accessory_per_seed) ~ (log10(prepollen_all_per_seed)+(log10(packaging_dispersal_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="BAER"))
-mod_COER <- lm(log10(accessory_per_seed) ~ (log10(prepollen_all_per_seed)+(log10(packaging_dispersal_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="COER"))
+mod <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar1]]))+(log10(x[[xvar2]]))+(log10(x[[xvar3]])+(log10(x[[xvar4]])))))
+mod_LEES <- lm(log10(accessory_per_seed) ~ (log10(prepollencosts)+(log10(postpollen_aborted_per_seed))+(log10(prepollen_failure_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species=="LEES"))
+mod_BAER <- lm(log10(accessory_per_seed) ~ (log10(prepollencosts)+(log10(packaging_dispersal_per_seed))+(log10(prepollen_failure_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="BAER"))
+mod_COER <- lm(log10(accessory_per_seed) ~ (log10(prepollencosts)+(log10(packaging_dispersal_per_seed))+(log10(prepollen_failure_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="COER"))
 
-species_coef <- as.data.frame(c("intercept","packaging&dispersal","prepollen_all_per_seed","postpollen_aborted_per_seed"))
+species_coef <- as.data.frame(c("intercept","packaging&dispersal","prepollencosts","postpollen_aborted_per_seed","pre-pollen failure per seed"))
 
@@
 BAER_c <- as.data.frame(mod_BAER$coefficients)
-BAER_c$effect <- c("intercept","prepollen_all_per_seed","packaging&dispersal")
+BAER_c$effect <- c("intercept","prepollencosts","packaging&dispersal","pre-pollen failure per seed")
 names(BAER_c) <- c("BAER","effect")
@@
 COER_c <- as.data.frame(mod_COER$coefficients)
-COER_c$effect <- c("intercept","prepollen_all_per_seed","packaging&dispersal")
+COER_c$effect <- c("intercept","prepollencosts","packaging&dispersal","pre-pollen failure per seed")
 names(COER_c) <- c("COER","effect")
@@
 LEES_c <- as.data.frame(mod_LEES$coefficients)
-LEES_c$effect <- c("intercept","prepollen_all_per_seed","postpollen_aborted_per_seed")
+LEES_c$effect <- c("intercept","prepollencosts","postpollen_aborted_per_seed","pre-pollen failure per seed")
 names(LEES_c) <- c("LEES","effect")
@@
 
-species_t <- as.data.frame(c("intercept","packaging&dispersal","prepollen_all_per_seed","postpollen_aborted_per_seed"))
+species_t <- as.data.frame(c("intercept","packaging&dispersal","prepollencosts","postpollen_aborted_per_seed","pre-pollen failure per seed"))
 
@@
 ```{r}
-ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollencosts,dispersalcosts)
-ternary$seedcosts = ternary$seed_size + ternary$prepollencosts + ternary$dispersalcosts
+ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollencosts,packaging_dispersal_per_seed)
+ternary$packaging_dispersal_per_seed[9] <- 0.1
+
+ternary$seedcosts = ternary$seed_size + ternary$prepollencosts + ternary$packaging_dispersal_per_seed
 ternary$per_seed <-100*ternary$seed_size/ternary$seedcosts
 ternary$per_poll <-100*ternary$prepollencosts/ternary$seedcosts
-ternary$per_disp <-100*ternary$dispersalcosts/ternary$seedcosts
+
+ternary$per_disp <-100*ternary$packaging_dispersal_per_seed/ternary$seedcosts
 mod_poll <- sma(per_poll~seedcosts,ternary,slope.test=0,method="OLS",log="x")
@@
 
+par(mfrow=c(1,1), cex=1, omi=c(1,1,1,1), mai=c(.1,.1,.1,.1))
+
 ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
-  labs(y = "seed weight (%)",x = "prepoll (%)",z = "pack&disp (%)",title = "Seed cost components",size = .5) +
+  labs(y = "seed",
+       x = "pre-poll",
+       z = "pack&disp",
+       Tarrow = "seed weight (%)",
+       Larrow = "pre-pollination costs (%)",
+       Rarrow = "packaging & dispersal costs (%)",
+       title = "Seed cost components",
+       size = 3) +
   geom_point(size=sqrt(ternary$seedcosts/2),shape=20,color=col.spp()) +
    theme_bw() + 
+  theme_showarrows() +
   geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seedcosts/500),size=2)

### 2016-03-15 Investment_calcs_20160308.R

@@ -11,7 +11,7 @@ SummaryInd$flower_inv <-SummaryInd$prepollencosts*SummaryInd$repro_all_count
 SummaryInd$budprop <- SummaryInd$bud_inv + SummaryInd$propagule_inv
 
 
-
+View(InvestmentByPart)
 
 #dispersalcosts_increment = dispersalcosts - dispersal_at_pollination,
 #abortedcosts = ((prepollen_failure_inv + postpollen_aborted_inv)/seed_count),

### 2016-03-15 R/Summaries.R

@@ -254,7 +254,7 @@ combine_by_individual <- function(IndividualsList, ReproductionAllocation_all, A
     prop_allocation = propagule_inv/(growth_inv + repro_inv),
     RA_leaf_area = repro_inv / (repro_inv + growth_leaf),
     leaf_area_midyear = (leaf_area_0 + leaf_area)/2,
-    prepollencosts = prepollen_success_inv/flower_count,
+    prepollencosts = prepollencosts_spp,
     count_aborted = repro_all_count - seed_count,
     flower_inv = prepollencosts*repro_all_count,    
     fruit_inv = propagule_inv + (seed_count*seedpod_weight),
@@ -270,6 +270,7 @@ combine_by_individual <- function(IndividualsList, ReproductionAllocation_all, A
     prepollen_success_per_seed = prepollencosts,
     postpollen_aborted_per_seed = postpollen_aborted_inv/seed_count,
     packaging_dispersal_per_seed = (packaging_dispersal_inv - (seed_count*dispersal_at_pollination))/seed_count,
+    seedcosts = seed_size + packaging_dispersal_per_seed + prepollencosts,
     success_inv = seedcosts*seed_count,
     failure_inv = repro_inv - success_inv,
     failure_to_ovule_ratio = 1 - seedset,
@@ -284,6 +285,7 @@ combine_by_individual <- function(IndividualsList, ReproductionAllocation_all, A
     prop_propagule_nonzero = prop_propagule,
     prop_accessory_nonzero = prop_accessory,
     prop_prepollencosts = prepollencosts/seedcosts,
+    prop_postpollencosts = 1 - prop_prepollencosts,
     prop_seedcosts = seed_size/seedcosts,
     prop_dispersalcosts = 1-prop_prepollencosts-prop_seedcosts,
     prop_dispersalcosts2 = packaging_dispersal_per_seed / seedcosts,
@@ -298,14 +300,14 @@ combine_by_individual <- function(IndividualsList, ReproductionAllocation_all, A
   
    
   
-  for(v in c("prepollencosts","count_aborted","flower_inv","fruit_inv","prepollen_all_inv","prepollen_success_inv",
+  for(v in c("seedcosts","prepollencosts","count_aborted","flower_inv","fruit_inv","prepollen_all_inv","prepollen_success_inv",
[…]

### 2016-03-17 Accessory_figs_20160218.Rmd
accessory cost work

@@
 
-#seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
+means, counts to include in manuscript
 ```{r}
-
-win.metafile("figs2/Accessory_Costs/Figure_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
-plot
-
-par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
-options(scipen = 4)
-
-#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
-plot(scaled_seed_count~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="seed size (mg)",ylab="count, scaled to plant size")
-points(scaled_bud_count~seed_size,SummaryInd,pch=21,col=col.spp(species))
-#points(scaled_failure_count~seed_size,SummaryInd,pch=2,col=col.spp(species))
-axis(2, at=c(0.000001,0.0001,0.01,1), labels=c(0.000001,0.0001,0.01,1),cex.axis=0.9)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
-
-mod1 <- sma(scaled_seed_count~seed_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
-mod2 <- sma(scaled_bud_count~seed_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
-mod3 <- sma(scaled_failure_count~seed_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
-sma_abline(mod1)
-abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue")
-abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red")
-legend("topright",legend=c("seed count","total bud count","failed flower count"),col=c("black","blue","red"),pch=c(16,21,8),bty="n")
-
-plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,1000),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="seed size (mg)",ylab="seed set")
-mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
-abline(mod$coeff[1],mod$coeff[2])
-text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
-     paste("r2 = ",round(glance(mod)[1],2)),adj=1)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
-legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")
-
-#species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
-plot(prop_prepollencosts~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.01,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
-mod <- sma(prop_prepollencosts~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
-y.error.bars(SummarySpp[["mean"]]$seedset,SummarySpp[["mean"]]$prop_prepollencosts,SummarySpp[["se"]]$prop_prepollencosts)
-sma_abline(mod)
-sma_sum(mod)
-text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
-     paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
-axis(2, at=c(-0.2,0,.2,.4,.6,.8,1), labels=c("",0.0,0.2,0.4,0.6,0.8,""),cex.axis=1)
-
-dev.off()
-```
-
-#Neither within nor across species, does the proportion of reproductive energy spent on "success" correlate with total reproductive investment
-```{r}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.05))
-
-xvar <- "repro_inv"
-yvar <- "prop_success"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], log="x",method="OLS")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),xlab="",ylab="",lty=results$linetype,pch=16,log="x")
+count(SummaryInd)
+count(subset(SummaryInd,seed_count>0))
+count(subset(SummaryInd,repro_inv>0))
+mean(subset(SummaryInd$prop_failure,SummaryInd$prop_failure>0))
+mean(subset(SummaryInd$prop_accessory,SummaryInd$seed_count>0))
 ```
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table02correlations_with_repro_inv.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table01_correlations_with_repro_inv.csv",row.names=FALSE)
 ```
 
-#Figure 1. Correlations of various reproductive investment categories against plant weight
+#Figure 2. Correlations of various reproductive investment categories against plant weight
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=5, width=10)
+win.metafile("figs2/Accessory_Costs/Figure02_correlations_with_plant_weight.wmf", height=5, width=10)
 plot
@@
 
-#correlations between repro inv and propagule inv by species
+#Table 3 showing accessory cost values for the species
 ```{r}
-yvar <- "repro_inv"
-xvar <- "propagule_inv"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seedcosts,prop_success,
+                               prepollencosts,packaging_dispersal_per_seed,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
+acc_costs_spp$species <- labels.spp.full()
+acc_costs_spp <- format(acc_costs_spp, digit=2)
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- fit$groupsummary
-
-write.csv(results, file="figs2/Accessory_Costs/Table02extra_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
+write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table03_AccCosts_by_Species.csv",row.names=FALSE)
 ```
 
-#when reproductive investment is scaled by leaf area there is no significant difference by seed size - so increase in repro inv with seed size simply because species with bigger seeds are bigger plants
+#Figure 3. Ternary diagram showing seedcosts
 ```{r}
-plot(scaled_repro_inv~seed_size,SummaryInd, col=col.spp(species),pch=16,log="xy")
-points(scaled_repro_inv~seed_size,SummarySpp[["mean"]], cex=2, col=col.spp(species),pch=16,log="xy")
-mod <-sma(scaled_repro_inv~seed_size,SummarySpp[["mean"]],log="xy",method="OLS")
-summary(mod)
+ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollencosts,packaging_dispersal_per_seed)
+ternary$packaging_dispersal_per_seed[9] <- 0.1
+
+ternary$seedcosts = ternary$seed_size + ternary$prepollencosts + ternary$packaging_dispersal_per_seed
+ternary$per_seed <-100*ternary$seed_size/ternary$seedcosts
+ternary$per_poll <-100*ternary$prepollencosts/ternary$seedcosts
+
+ternary$per_disp <-100*ternary$packaging_dispersal_per_seed/ternary$seedcosts
+mod_poll <- sma(per_poll~seedcosts,ternary,slope.test=0,method="OLS",log="x")
+mod_seed <- sma(per_seed~seedcosts,ternary,slope.test=0,method="OLS",log="x")
+mod_disp <- sma(per_disp~seedcosts,ternary,slope.test=0,method="OLS",log="x")
+
+costs_per_seed <- as.data.frame("costs for seed (%)")
+costs_per_seed <- cbind(costs_per_seed,select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+
+costs_per_seed2 <- as.data.frame("costs for pre-pollination (%)")
+costs_per_seed2 <- cbind(costs_per_seed2,select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
+
+costs_per_seed2 <- as.data.frame("costs for dispersal (%)")
+costs_per_seed2 <- cbind(costs_per_seed2,select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
+
+write.csv(costs_per_seed, file="figs2/Accessory_Costs/Table00_in_text_costs_per_seed.csv",row.names=FALSE)
+
+win.metafile("figs2/Accessory_Costs/FigureXX_seedcost_components.wmf", height=6, width=6)
+plot
+
+plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seedcosts")
+points(per_poll~seedcosts,ternary,col="red",pch=16,cex=2)
+points(per_disp~seedcosts,ternary,col="blue",pch=16,cex=2)
+
+abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
+abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
+abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
+legend("topleft",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
+dev.off()
 ```
 
-#Consider how accessory cost components shift in terms of costs per seed, and cost as fraction total reproductive investment
-
 ```{r}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
-
-plot(repro_inv~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
-mod <- lm(log10(repro_inv)~log10(seed_size),SummarySpp[["mean"]])
-abline(mod$coeff[1],mod$coeff[2])
-words.top.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$repro_inv,SummarySpp[["se"]]$repro_inv)
-
-win.metafile("figs2/Accessory_Costs/Figure02_seedsize_vs_reproinv.wmf", height=5, width=5)
+win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seedcosts.wmf", height=5, width=5)
 plot
 
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
-plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
-mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
-abline(mod$coeff[1],mod$coeff[2])
-words.bottom.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+par(mfrow=c(1,1), cex=1, omi=c(1,1,1,1), mai=c(.1,.1,.1,.1))
+
+ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
+  labs(y = "seed",
+       x = "pre-poll",
+       z = "pack&disp",
+       Tarrow = "seed weight (%)",
+       Larrow = "pre-pollination costs (%)",
+       Rarrow = "packaging & dispersal costs (%)",
+       title = "Seed cost components",
+       size = 3) +
+  geom_point(size=sqrt(ternary$seedcosts/2),shape=20,color=col.spp()) +
+   theme_bw() + 
+  theme_showarrows() +
+  geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seedcosts/500),size=2)
 
@@
 
-#Table showing accessory cost values for the species
+#Table 4 showing seedcost breakdown into components, by species
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,seedset,accessory_per_seed,prepollencosts,prepollen_all_per_seed,prepollen_failure_per_seed,postpollen_aborted_per_seed,packaging_dispersal_per_seed,prop_accessory_nonzero)
-acc_costs_spp$species <- labels.spp.full()
-acc_costs_spp <- format(acc_costs_spp, digit=2)
-
-write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table02_AccCosts_by_Species.csv",row.names=FALSE)
+prop_seedcosts_spp <- dplyr::select(SummarySpp[["mean"]],species,seedcosts,prop_prepollencosts,prop_dispersalcosts,prop_seedcosts)
+prop_seedcosts_spp$species <- labels.spp.full()
+prop_seedcosts_spp <- format(prop_seedcosts_spp, digit=2)
+write.csv(prop_seedcosts_spp, file="figs2/Accessory_Costs/Table04_Prop_seedcosts_by_Species.csv",row.names=FALSE)
 ```
 
-#Figure 2 and Table 3. Scaling of accessory costs versus seed size, by species
+#Figure 4. Scaling of accessory costs versus seed size, by species
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure02_seed_size_correlations.wmf", height=5, width=15)
+win.metafile("figs2/Accessory_Costs/Figure04_seed_size_acc_cost_correlations.wmf", height=5, width=15)
 plot
@@
 plot(prepollencosts~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pre-pollination costs per seed (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
 mod <- lm(log10(prepollencosts)~log10(seed_size),SummarySpp[["mean"]])
@@
 plot(packaging_dispersal_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="packaging and dispersal costs per seed (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
 mod <- lm(log10(packaging_dispersal_per_seed)~log10(seed_size),SummarySpp[["mean"]])
@@
 
+#Table 5. Slopes for various seed size by acc cost regressions
 ```{r}
@@
 
-write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_by_species.csv",row.names=FALSE)
+write.csv(acc_by_species, file="figs2/Accessory_Costs/Table05_acc_cost_seed_size_slopes.csv",row.names=FALSE)
 ```
 
-#Table 4 and Figure 3.Per seed accessory costs are lower in individuals with higher seed count. 
-###This effect is true across species, since larger-seeded species produce fewer seeds and have higher per seed accessory costs and true within species, since absolute accessory investment is a function of plant size not seedset
+#Figure 5 seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
+
+win.metafile("figs2/Accessory_Costs/Figure05_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
+plot
+
+par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
+options(scipen = 4)
+
+plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,1000),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="seed size (mg)",ylab="seed set")
+mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
+abline(mod$coeff[1],mod$coeff[2])
+text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
+     paste("r2 = ",round(glance(mod)[1],2)),adj=1)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")
+
+#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
+plot(scaled_seed_count~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="seed size (mg)",ylab="count, scaled to plant size")
+points(scaled_bud_count~seed_size,SummaryInd,pch=21,col=col.spp(species))
+#points(scaled_failure_count~seed_size,SummaryInd,pch=2,col=col.spp(species))
+axis(2, at=c(0.000001,0.0001,0.01,1), labels=c(0.000001,0.0001,0.01,1),cex.axis=0.9)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
+
+summary(mod2)
+mod1 <- sma(scaled_seed_count~seed_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
+mod2 <- sma(scaled_bud_count~seed_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
+mod3 <- sma(scaled_failure_count~seed_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
+sma_abline(mod1)
+abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue")
+abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red")
+legend("topright",legend=c("seed count","total bud count","failed flower count"),col=c("black","blue","red"),pch=c(16,21,8),bty="n")
+
+#species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
+plot(prop_prepollencosts~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.01,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
+mod <- sma(prop_prepollencosts~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
+y.error.bars(SummarySpp[["mean"]]$seedset,SummarySpp[["mean"]]$prop_prepollencosts,SummarySpp[["se"]]$prop_prepollencosts)
+sma_abline(mod)
+sma_sum(mod)
+text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
+     paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
+axis(2, at=c(-0.2,0,.2,.4,.6,.8,1), labels=c("",0.0,0.2,0.4,0.6,0.8,""),cex.axis=1)
+
+dev.off()
+```
+
+#Table 6. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
+```{r}
+win.metafile("figs2/Accessory_Costs/FigureXX_RE_RA_size_age_patterns.wmf", height=10, width=10)
+plot
+
+par(mfrow=c(2,2), cex=1, omi=c(.1,.4,.1,.05), mai=c(.6,.3,.1,.1))
+options(scipen = 2)
+
+xvar <- "repro_inv"
+yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
+mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
+legend_with_r2(results,"bottomright")
+
+write.csv(results, file="figs2/Accessory_Costs/Table06a_accessory_vs_RE.csv",row.names=FALSE)
+
+xvar <- "total_weight_0"
+yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
+mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
+legend_with_r2(results,"bottomright")
+
+write.csv(results, file="figs2/Accessory_Costs/Table06b_accessory_vs_total_weight.csv",row.names=FALSE)
+
+xvar <- "age"
+yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
+mtext(text="age (years)",side=1,line=2,outer=FALSE)
+mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
+legend_with_r2(results,"topleft")
+
+write.csv(results, file="figs2/Accessory_Costs/Table06c_accessory_vs_age.csv",row.names=FALSE)
+dev.off()
+```
+
+###GOOD VISUALS - not currently in manuscript
+```{r}
+win.metafile("figs2/Accessory_Costs/FigureXX_seedcount_reprocount.wmf", height=5, width=5)
+plot
+
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,0.05), mai=c(.8,.8,.1,0.1))
+options(scipen = 2)
+
+xvar <- "prepollen_all_count"
+yvar <- "seed_count"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="buds initiated (count)",ylab="seed count",lty=results$linetype,xlim=c(0.9,20000),ylim=c(0.9,20000))
+
+abline(0,1,lwd=2)
+abline(-2,1,lwd=2)
+
+legend_with_r2(results,"topleft")
+
+dev.off()
+```
+
+```{r}
+win.metafile("figs2/Accessory_Costs/FigureXX_success_vs_failure.wmf", height=6, width=8)
+plot
+
+par(mfrow=c(1,2), cex=1, omi=c(.8,.1,.1,.1), mai=c(.1,.8,.1,.1))
+
+xvar <- "repro_inv"
+yvar <- "prop_propagule"
+
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,lty=results$linetype,ylim=c(.001,1),xlab="",ylab="prop repro energy to propagules")
+abline(-0.30103,0,lwd=2)
+abline(-1,0,lwd=2)
+
+xvar <- "repro_inv"
+yvar <- "prop_success"
+
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,lty=results$linetype,ylim=c(.001,1),xlab="",ylab="prop repro energy to success")
+abline(-0.30103,0,lwd=2)
+abline(-1,0,lwd=2)
+mtext(text="reproductive investment (mg)",side=1,line=2,outer=TRUE)
+
+dev.off()
+```
+
+#EXTRAS - not in manuscript
+#Neither within nor across species, does the proportion of reproductive energy spent on "success" correlate with total reproductive investment
+```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.05))
+
+xvar <- "repro_inv"
+yvar <- "prop_success"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], log="x",method="OLS")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),xlab="",ylab="",lty=results$linetype,pch=16,log="x")
+```
+
+#correlations between repro inv and propagule inv by species
+```{r}
+yvar <- "repro_inv"
+xvar <- "propagule_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- fit$groupsummary
+
+write.csv(results, file="figs2/Accessory_Costs/Table02_extra_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
+```
+
+#when reproductive investment is scaled by leaf area there is no significant difference by seed size - so increase in repro inv with seed size simply because species with bigger seeds are bigger plants
+```{r}
+plot(scaled_repro_inv~seed_size,SummaryInd, col=col.spp(species),pch=16,log="xy")
+points(scaled_repro_inv~seed_size,SummarySpp[["mean"]], cex=2, col=col.spp(species),pch=16)
+mod <-sma(scaled_repro_inv~seed_size,SummarySpp[["mean"]],log="xy",method="OLS")
+summary(mod)
+```
+
+#Consider how accessory cost components shift in terms of costs per seed, and cost as fraction total reproductive investment
+```{r}
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
+
+plot(repro_inv~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
+mod <- lm(log10(repro_inv)~log10(seed_size),SummarySpp[["mean"]])
+abline(mod$coeff[1],mod$coeff[2])
+words.top.left.logxy(mod)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$repro_inv,SummarySpp[["se"]]$repro_inv)
+
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
+plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
+mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
+abline(mod$coeff[1],mod$coeff[2])
+words.bottom.left.logxy(mod)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+```
+
+#This effect is true across species, since larger-seeded species produce fewer seeds and have higher per seed accessory costs and true within species, since absolute accessory investment is a function of plant size not seedset
+```{r}
+win.metafile("figs2/Accessory_Costs/FigureXX_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
 plot
@@
 
-results
-write.csv(results, file="figs2/Accessory_Costs/Table04a_seedcount_vs_accessory.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/TableXX_seedcount_vs_accessory.csv",row.names=FALSE)
 
@@
 
-#Table 4 extra - showing propagule investment instead of seed_count. Could also replace with seedset
+#propagule investment instead of seed_count. Could also replace with seedset
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure_acc_cost_by_seedset.wmf", height=9, width=9)
+win.metafile("figs2/Accessory_Costs/FigureXX_acc_cost_by_seedset.wmf", height=9, width=9)
 plot
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table04b_seedset_vs_accessory.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/TableXX_seedset_vs_accessory.csv",row.names=FALSE)
 
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table06a_prepollen_all_per_seed_vs_seedset.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/TableXX_prepollen_all_per_seed_vs_seedset.csv",row.names=FALSE)
 
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table06b_postpollen_aborted_per_seed_vs_seedset.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/TableXX_postpollen_aborted_per_seed_vs_seedset.csv",row.names=FALSE)
 
@@
 
-win.metafile("figs2/Accessory_Costs/Table07_dispcosts_vs_ovules.wmf", height=6, width=6)
+win.metafile("figs2/Accessory_Costs/FigureXX_dispcosts_vs_ovules.wmf", height=6, width=6)
 plot
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table06c_dispersal_vs_seedset.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/TableXX_dispersal_vs_seedset.csv",row.names=FALSE)
 ```
 
-#Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
-##Not a single species shows a reduction in per seed accessory costs with increased plant size.Indeed, EPMI has higher pre-pollination accessory costs    (slope = 0.38, r2=0.19, p=0.019) and accessory costs due to aborted fruit and seeds (slope = 0.83, r2=0.268, p=0.019) in larger individuals, as larger individuals of this species have lower seedset (slope = -0.31, r2=0.198, p=0.018).
-GRSP also has a nearly significant decline in seedset in larger individuals (slope = -0.78, r2=0.298, p=0.067).
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure_RE_RA_size_age_patterns.wmf", height=10, width=10)
-plot
-
-par(mfrow=c(2,2), cex=1, omi=c(.1,.4,.1,.05), mai=c(.6,.3,.1,.1))
-options(scipen = 2)
-
-xvar <- "repro_inv"
-yvar <- "accessory_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
-mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
-legend_with_r2(results,"bottomright")
-
-write.csv(results, file="figs2/Accessory_Costs/Table05a_accessory_vs_RE.csv",row.names=FALSE)
-
-xvar <- "total_weight_0"
-yvar <- "accessory_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
-mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
-legend_with_r2(results,"bottomright")
-
-write.csv(results, file="figs2/Accessory_Costs/Table05c_accessory_vs_total_weight.csv",row.names=FALSE)
-
-xvar <- "age"
-yvar <- "accessory_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
-mtext(text="age (years)",side=1,line=2,outer=FALSE)
-mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
-legend_with_r2(results,"topleft")
-
-write.csv(results, file="figs2/Accessory_Costs/Table05d_accessory_vs_age.csv",row.names=FALSE)
-dev.off()
-```
-
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure_seedcount_reprocount.wmf", height=5, width=5)
-plot
-
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,0.05), mai=c(.8,.8,.1,0.1))
-options(scipen = 2)
-
-xvar <- "prepollen_all_count"
-yvar <- "seed_count"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="buds initiated (count)",ylab="seed count",lty=results$linetype,xlim=c(0.9,20000),ylim=c(0.9,20000))
-
-abline(0,1,lwd=2)
-abline(-2,1,lwd=2)
-
-legend_with_r2(results,"topleft")
-
-dev.off()
-```
 #Considering the individual components of accessory costs vs. seedset - since seedset best predictor of accessory costs
@@
 #For each species the accessory cost components that cause shifts in total accessory costs is different and reflects both which components are largest and whichvary most with some factor - seedset, age, etc.
+#CODE CURRENTLY DOESN"T WORK
 ```{r}
@@
 
-write.csv(species_coef, file="figs2/Accessory_Costs/Table08_accessory_components_coeff.csv",row.names=FALSE)
+write.csv(species_coef, file="figs2/Accessory_Costs/TableXX_accessory_components_coeff.csv",row.names=FALSE)
 
@@
 
-write.csv(species_t, file="figs2/Accessory_Costs/Table08_accessory_components_t-value.csv",row.names=FALSE)
+write.csv(species_t, file="figs2/Accessory_Costs/TableXX_accessory_components_t-value.csv",row.names=FALSE)
 
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table_prop_tissues_inv_by_seed_size.csv",row.names=FALSE) 
+write.csv(results, file="figs2/Accessory_Costs/TableXX_prop_tissues_inv_by_seed_size.csv",row.names=FALSE) 
 ```
@@
 ```
-
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure_success_vs_failure.wmf", height=6, width=8)
-plot
-
-par(mfrow=c(1,2), cex=1, omi=c(.8,.1,.1,.1), mai=c(.1,.8,.1,.1))
-
-xvar <- "repro_inv"
-yvar <- "prop_propagule"
-
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,lty=results$linetype,ylim=c(.001,1),xlab="",ylab="prop repro energy to propagules")
-abline(-0.30103,0,lwd=2)
-abline(-1,0,lwd=2)
-
-xvar <- "repro_inv"
-yvar <- "prop_success"
-
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,lty=results$linetype,ylim=c(.001,1),xlab="",ylab="prop repro energy to success")
-abline(-0.30103,0,lwd=2)
-abline(-1,0,lwd=2)
-mtext(text="reproductive investment (mg)",side=1,line=2,outer=TRUE)
-
-dev.off()
-```
-
-```{r}
-ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollencosts,packaging_dispersal_per_seed)
-ternary$packaging_dispersal_per_seed[9] <- 0.1
-
-ternary$seedcosts = ternary$seed_size + ternary$prepollencosts + ternary$packaging_dispersal_per_seed
-ternary$per_seed <-100*ternary$seed_size/ternary$seedcosts
-ternary$per_poll <-100*ternary$prepollencosts/ternary$seedcosts
-
-ternary$per_disp <-100*ternary$packaging_dispersal_per_seed/ternary$seedcosts
-mod_poll <- sma(per_poll~seedcosts,ternary,slope.test=0,method="OLS",log="x")
-mod_seed <- sma(per_seed~seedcosts,ternary,slope.test=0,method="OLS",log="x")
-mod_disp <- sma(per_disp~seedcosts,ternary,slope.test=0,method="OLS",log="x")
-
-costs_per_seed <- as.data.frame("costs for seed (%)")
-costs_per_seed <- cbind(costs_per_seed,select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-
-costs_per_seed2 <- as.data.frame("costs for pre-pollination (%)")
-costs_per_seed2 <- cbind(costs_per_seed2,select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
-
-costs_per_seed2 <- as.data.frame("costs for dispersal (%)")
-costs_per_seed2 <- cbind(costs_per_seed2,select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
-
-write.csv(costs_per_seed, file="figs2/Accessory_Costs/Table08_costs_per_seed.csv",row.names=FALSE)
-
-win.metafile("figs2/Accessory_Costs/seedcost_components.wmf", height=6, width=6)
-plot
-
-plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seedcosts")
-points(per_poll~seedcosts,ternary,col="red",pch=16,cex=2)
-points(per_disp~seedcosts,ternary,col="blue",pch=16,cex=2)
-
-abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
-abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
-abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
-legend("topleft",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
-dev.off()
-```
-
-```{r}
-win.metafile("figs2/Accessory_Costs/Ternary.wmf", height=5, width=5)
-plot
-
-par(mfrow=c(1,1), cex=1, omi=c(1,1,1,1), mai=c(.1,.1,.1,.1))
-
-ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
-  labs(y = "seed",
-       x = "pre-poll",
-       z = "pack&disp",
-       Tarrow = "seed weight (%)",
-       Larrow = "pre-pollination costs (%)",
-       Rarrow = "packaging & dispersal costs (%)",
-       title = "Seed cost components",
-       size = 3) +
-  geom_point(size=sqrt(ternary$seedcosts/2),shape=20,color=col.spp()) +
-   theme_bw() + 
-  theme_showarrows() +
-  geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seedcosts/500),size=2)
-
-dev.off()
-```

### 2016-04-05 Accessory_figs_20160218.Rmd
notes at top that may be added into acc cost figures

@@
-plot(failure_inv~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species))
-plot(abortedcosts~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),pch=16,log="xy",col=col.spp(species))
-mod <- sma(abortedcosts~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),log="xy",method="OLS",slope=1)
+plot(prop_prepollen_all~seed_size,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species))
+mod <- sma(propagule_inv~seed_size,data=subset(SummarySpp[["mean"]],species!="EPMI"), log="xy",slope=1, method="OLS")
 summary(mod)
 
-plot(prepollen_failure_per_seed~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),pch=16,log="xy",col=col.spp(species))
-mod <- sma(prepollen_failure_per_seed~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),log="xy",method="OLS",slope=1)
+par(mfrow=c(1,2), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+options(scipen = 5)
+plot(repro_all_count~total_weight,SummaryInd,pch=16,log="xy",col=col.spp(species))
+mod <- sma(repro_all_count~total_weight,data=subset(SummaryInd,species!="EPMI"), log="xy",slope=1, method="OLS")
 summary(mod)
 
-plot(scaled_failure_count~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),pch=16,log="xy",col=col.spp(species))
-mod <- sma(bud_failed_count~seed_size,data=subset(SummaryInd,abortedcosts>1e-8),log="xy",method="OLS",slope=1)
+plot(prop_prepollen_success~age,SummaryInd,pch=16,log="xy",col=col.spp(species))
+
+yvar <- "accessory_per_seed"
+xvar <- "age"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>2&SummaryInd[[yvar]]>0&SummaryInd[[yvar]]<40000)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope=1)
+results <- lines(fit$groupsummary)
+results
+plot(fit,col=col.spp(fit$groupsummary$group),log="xy",lty=results$linetype,pch=16,xlab=xvar,ylab=yvar)
+
+mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
+abline(0,1)
+
+SummaryInd$flower_seed_inv <- SummaryInd$propagule_inv + SummaryInd$flower_inv
+SummaryInd$prop_post <- SummaryInd$prop_packaging_dispersal + SummaryInd$prop_propagule
+plot(flower_seed_inv~repro_inv,SummaryInd,pch=16,log="xy",col=col.spp(species))
+mod <- lm(log(flower_inv)~log(repro_inv),subset(SummaryInd,flower_seed_inv>0))
 summary(mod)
 
-plot(seedset~prop_prepollencosts,data=subset(SummaryInd,seedset>0),pch=16,log="y",col=col.spp(species))
-legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")
-mod <-sma(seedset~prop_prepollencosts,data=subset(SummarySpp[["mean"]],seedset>0&species!="PHPH"&species!="PUTU"),log="",method="OLS")
+plot(propagule_inv~leaf_area_0,SummaryInd,pch=16,log="xy",col=col.spp(species))
+
+plot(prepollen_failure_per_seed~seed_size,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species))
+mod <- lm(log(propagule_inv)~log(seed_size),data=subset(SummarySpp[["mean"]],species!="EPMI"))
 summary(mod)
-sma_abline(mod)
 
-write.csv(PartsSummary, file="figs2/Accessory_Costs/PartsSummary.csv",row.names=FALSE)
+#Discussion or Appendix: proportion energy to prepollen tissues decreases with plant age
+```{r}
+yvar <- "accessory_per_seed"
+xvar <- "age"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>2&SummaryInd[[yvar]]>0&SummaryInd[[yvar]]<1)
 
-means, counts to include in manuscript
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="x",slope=1)
+results <- lines(fit$groupsummary)
+results
+plot(fit,col=col.spp(fit$groupsummary$group),log="x",lty=results$linetype,pch=16,xlab=xvar,ylab=yvar)
+````
+
+#Data 0. means, counts to include in manuscript
 ```{r}
@@
 mean(subset(SummaryInd$prop_accessory,SummaryInd$seed_count>0))
+
+mod <- sma(repro_all_count~total_weight,SummaryInd,method="OLS",log="xy",slope=1)
+summary(mod)
+
+mod <- lm(log10(seedcosts) ~prop_seedcosts,SummarySpp[["mean"]])
+summary(mod)
+
+mod <- lm(log10(seedcosts) ~prop_prepollencosts,SummarySpp[["mean"]])
+summary(mod)
+
+mod <- lm(log10(seedcosts) ~prop_dispersalcosts,SummarySpp[["mean"]])
+summary(mod)
+
+yvar <- "repro_all_count"
+xvar <- "repro_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
+results <- lines(fit$groupsummary)
+plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
+results
+
+yvar <- "repro_all_count"
+xvar <- "leaf_area_0"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
+results <- lines(fit$groupsummary)
+plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
+results
+
+yvar <- "propagule_inv"
+xvar <- "leaf_area_0"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
+results <- lines(fit$groupsummary)
+plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
+results
+
+yvar <- "propagule_inv"
+xvar <- "leaf_area_0_mature"
+data <- subset(SummarySppAge[["mean"]],SummarySppAge[["mean"]][[xvar]]>0&SummarySppAge[["mean"]][[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
+results
+
+mod <- lm(log10(leaf_area_0)~log10(propagule_inv),data=subset(SummaryInd,leaf_area_0>0&propagule_inv>0))
+summary(mod)
+mod <- lm(log10(leaf_area_0)~log10(propagule_inv),SummarySpp[["mean"]])
+summary(mod)
+
+plot(leaf_area_0_mature~propagule_inv,SummarySppAge[["mean"]],log="xy",cex=1.5,pch=16,col=col.spp(species))
+points(leaf_area~propagule_inv,SummaryInd,pch=16,col=col.spp(species))
+mod <- lm(log10(leaf_area_0_mature)~log10(propagule_inv),SummarySppAge[["mean"]])
+summary(mod)
+mod <- lm(log10(leaf_area_0_mature)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0&leaf_area>0))
+summary(mod)
+
+plot(leaf_area_0_mature~propagule_inv,SummarySppAge[["mean"]],log="xy",cex=1.5,pch=16,col=col.spp(species))
+
+plot(repro_inv~propagule_inv,SummaryInd,pch=16,col=col.spp(species),log="xy")
+mod <- lm(log10(repro_inv_mature)~log10(propagule_inv),SummarySppAge[["mean"]])
+summary(mod)
+mod <- lm(log10(repro_inv_mature)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0&repro_inv>0))
+summary(mod)
+
+plot(repro_all_count_mature~seed_count,SummarySppAge[["mean"]],log="xy",cex=1.5,pch=16,col=col.spp(species))
+mod <- lm(log10(total_weight)~log10(seedset),SummarySppAge[["mean"]])
+
+mod <- lm(log10(leaf_area_0_mature)~log10(propagule_inv),SummarySpp[["mean"]])
+summary(mod)
+mod <- lm(log10(repro_inv_mature)~log10(propagule_inv),SummarySpp[["mean"]])
+summary(mod)
 ```
 
-#Table 1. correlations with total repro inv
+#Table 1 showing accessory cost values for the species
 ```{r}
-results <- as.data.frame(matrix(vector(), 0, 8,
-                dimnames=list(c(), c("variable","r2","pval","Slope","Slope_lowCI","Slope_highCI","Int","Slope_test_p"))),
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seedcosts,prop_success,
+                               prepollencosts,packaging_dispersal_per_seed,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
+acc_costs_spp$species <- labels.spp.full()
+acc_costs_spp <- format(acc_costs_spp, digit=2)
+
+write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table03_AccCosts_by_Species.csv",row.names=FALSE)
+```
+
+#Figure 2. Ternary diagram showing seedcosts
+```{r}
+ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollencosts,packaging_dispersal_per_seed)
+ternary$packaging_dispersal_per_seed[9] <- 0.1
+
+ternary$seedcosts = ternary$seed_size + ternary$prepollencosts + ternary$packaging_dispersal_per_seed
+ternary$per_seed <-100*ternary$seed_size/ternary$seedcosts
+ternary$per_poll <-100*ternary$prepollencosts/ternary$seedcosts
+
+ternary$per_disp <-100*ternary$packaging_dispersal_per_seed/ternary$seedcosts
+mod_poll <- sma(per_poll~seedcosts,ternary,slope.test=0,method="OLS",log="x")
+mod_seed <- sma(per_seed~seedcosts,ternary,slope.test=0,method="OLS",log="x")
+mod_disp <- sma(per_disp~seedcosts,ternary,slope.test=0,method="OLS",log="x")
+
+costs_per_seed <- as.data.frame("costs for seed (%)")
+costs_per_seed <- cbind(costs_per_seed,select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+
+costs_per_seed2 <- as.data.frame("costs for pre-pollination (%)")
+costs_per_seed2 <- cbind(costs_per_seed2,select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
+
+costs_per_seed2 <- as.data.frame("costs for dispersal (%)")
+costs_per_seed2 <- cbind(costs_per_seed2,select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
+
+write.csv(costs_per_seed, file="figs2/Accessory_Costs/Table00_in_text_costs_per_seed.csv",row.names=FALSE)
+
+win.metafile("figs2/Accessory_Costs/FigureXX_seedcost_components.wmf", height=6, width=6)
+plot
+
+plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seedcosts")
+points(per_poll~seedcosts,ternary,col="red",pch=16,cex=2)
+points(per_disp~seedcosts,ternary,col="blue",pch=16,cex=2)
+
+abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
+abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
+abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
+legend("topleft",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
+dev.off()
+```
+
+#Figure 2 continued
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seedcosts.wmf", height=5, width=5)
+plot
+
+par(mfrow=c(1,1), cex=1, omi=c(1,1,1,1), mai=c(.1,.1,.1,.1))
+
+ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
+  labs(y = "seed",
+       x = "pre-poll",
+       z = "pack&disp",
+       Tarrow = "seed weight (%)",
+       Larrow = "pre-pollination costs (%)",
+       Rarrow = "packaging & dispersal costs (%)",
+       title = "Seed cost components",
+       size = 3) +
+  geom_point(size=sqrt(ternary$seedcosts/2),shape=20,color=col.spp()) +
+   theme_bw() + 
+  theme_showarrows() +
+  geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seedcosts/500),size=2)
+
+dev.off()
+```
+
+#Table 2 showing seedcost breakdown into components, by species
+```{r}
+prop_seedcosts_spp <- dplyr::select(SummarySpp[["mean"]],species,seedcosts,prop_prepollencosts,prop_dispersalcosts,prop_seedcosts)
+prop_seedcosts_spp$species <- labels.spp.full()
+prop_seedcosts_spp <- format(prop_seedcosts_spp, digit=2)
+write.csv(prop_seedcosts_spp, file="figs2/Accessory_Costs/Table04_Prop_seedcosts_by_Species.csv",row.names=FALSE)
+```
+
+#Figure 3. Scaling of accessory costs versus seed size, by species
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure04_seed_size_acc_cost_correlations.wmf", height=5, width=15)
+plot
+
+par(mfrow=c(1,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+options(scipen = 5)
+
+plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+
+plot(prepollencosts~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pre-pollination costs per seed (mg/seed)",xlab="",cex=1.5)
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
+mod <- lm(log10(prepollencosts)~log10(seed_size),SummarySpp[["mean"]])
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+
+plot(packaging_dispersal_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="packaging and dispersal costs per seed (mg/seed)",xlab="",cex=1.5)
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
+mod <- lm(log10(packaging_dispersal_per_seed)~log10(seed_size),SummarySpp[["mean"]])
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
+dev.off()
+```
+
+#Table 3. Slopes for various seed size by acc cost regressions
+```{r}
+par(mfrow=c(2,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+options(scipen = 5)
+
+plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
+slopes <- sma(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+#abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(0,1,col="red")
+words.bottom.right.logxy(mod)
+
+acc_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
+
+plot(prepollencosts ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(prepollencosts) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
+words.bottom.right.logxy(mod)
+extra.topleft.logxy("slope <1, so bigger seeded species have lower fixed costs of making pre-pollination parts")
+slopes <- sma(prepollencosts ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+plot(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(prepollen_failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
+words.bottom.right.logxy(mod)
+extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
+slopes <- sma(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_failure_per_seed,SummarySpp[["se"]]$prepollen_failure_per_seed)
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+plot(prepollen_all_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(prepollen_all_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
+words.bottom.right.logxy(mod)
+slopes <- sma(prepollen_all_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
+words.top.left.logxy(mod)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
+slopes <- sma(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+plot(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(packaging_dispersal_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"))
+words.top.left.logxy(mod)
+slopes <- sma(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="LEES"),slope.test=1, log="xy",method="OLS")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
+
+acc_by_species$variable = c("total accessory costs","prepollen_success","prepollen_failure","total prepollen","c div p","dispersal")
+
+write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_seed_size_slopes.csv",row.names=FALSE)
+```
+
+#Figure 4 seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
+```{r}
+
+win.metafile("figs2/Accessory_Costs/Figure04_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
+plot
+
+par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
+options(scipen = 4)
+
+plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,1000),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="seed size (mg)",ylab="seed set")
+mod <- sma(seedset~seed_size,SummarySpp[["mean"]],log="xy", method="OLS")
+sma_abline(mod)
+text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
+     paste("r2 = ",round(glance(mod)[1],2)),adj=1)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")
+
+#species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
+plot(prop_prepollencosts~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.01,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
+mod <- sma(prop_prepollencosts~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
+y.error.bars(SummarySpp[["mean"]]$seedset,SummarySpp[["mean"]]$prop_prepollencosts,SummarySpp[["se"]]$prop_prepollencosts)
+sma_abline(mod)
+sma_sum(mod)
+text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
+     paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
+axis(2, at=c(-0.2,0,.2,.4,.6,.8,1), labels=c("",0.0,0.2,0.4,0.6,0.8,""),cex.axis=1)
+
+#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
+plot(scaled_seed_count~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="seed size (mg)",ylab="count, scaled to plant size")
+points(scaled_bud_count~seed_size,SummaryInd,pch=21,col=col.spp(species))
+#points(scaled_failure_count~seed_size,SummaryInd,pch=2,col=col.spp(species))
+axis(2, at=c(0.000001,0.0001,0.01,1), labels=c(0.000001,0.0001,0.01,1),cex.axis=0.9)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
+
+summary(mod2)
+mod1 <- sma(scaled_seed_count~seed_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
+mod2 <- sma(scaled_bud_count~seed_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
+mod3 <- sma(scaled_failure_count~seed_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
+sma_abline(mod1)
+abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue")
+abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red")
+legend("topright",legend=c("seed count","total bud count","failed flower count"),col=c("black","blue","red"),pch=c(16,21,8),bty="n")
+
+dev.off()
+```
+
+#Table 4.correlations between seedset and accessory costs by species
+```{r}
+yvar <- "accessory_per_seed"
+xvar <- "seedset"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope=-1)
+results <- fit$groupsummary
+
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="seedset (seeds:ovule)",ylab="total accessory costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000))
+
+write.csv(results, file="figs2/Accessory_Costs/Table06_eacc_cost_vs_seedset_by_spp.csv",row.names=FALSE)
+```
+
+#Table 5. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
+```{r}
+win.metafile("figs2/Accessory_Costs/FigureXX_RE_RA_size_age_patterns.wmf", height=10, width=10)
+plot
+
+par(mfrow=c(2,2), cex=1, omi=c(.1,.4,.1,.05), mai=c(.6,.3,.1,.1))
+options(scipen = 2)
+
+xvar <- "repro_inv"
+yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
+mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
+legend_with_r2(results,"bottomright")
+
+write.csv(results, file="figs2/Accessory_Costs/Table07a_accessory_vs_RE.csv",row.names=FALSE)
+
+xvar <- "total_weight_0"
+yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
+mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
+legend_with_r2(results,"bottomright")
+
+write.csv(results, file="figs2/Accessory_Costs/Table07b_accessory_vs_total_weight.csv",row.names=FALSE)
+
+xvar <- "age"
+yvar <- "accessory_per_seed"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
+mtext(text="age (years)",side=1,line=2,outer=FALSE)
+mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
+legend_with_r2(results,"topleft")
+
+write.csv(results, file="figs2/Accessory_Costs/Table07c_accessory_vs_age.csv",row.names=FALSE)
+dev.off()
+```
+
+#Table 6.correlations between repro inv and propagule inv by species
+```{r}
+yvar <- "repro_inv"
+xvar <- "propagule_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- fit$groupsummary
+
+write.csv(results, file="figs2/Accessory_Costs/Table01_extra_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
+```
+
+#Table 7. correlations with total repro inv
+```{r}
+results <- as.data.frame(matrix(vector(), 0, 9,
+                dimnames=list(c(), c("xvar","variable","r2","pval","Slope","Slope_lowCI","Slope_highCI","Int","Slope_test_p"))),
                 stringsAsFactors=F)
 
-for (i in c("total_weight","failure_inv","success_inv","propagule_inv","packaging_dispersal_inv","prepollen_success_inv","fruit_inv","flower_inv")) {
+for (i in c("total_weight","repro_inv","failure_inv","success_inv","propagule_inv","packaging_dispersal_inv","prepollen_success_inv","fruit_inv","flower_inv")) {
+  for (j in c("total_weight","leaf_area_0","diameter_0","repro_inv","propagule_inv")) {
 yvar <- i
-xvar <- "repro_inv"
+xvar <- j
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-fit <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", log="xy",slope=1)
-temp <- as.data.frame(c(yvar,select(fit$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Slope_test_p)))
-colnames(temp)[1]<- "variable"
+fit <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", log="xy",slope.test=1)
+temp <- as.data.frame(c(xvar, yvar,select(fit$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Slope_test_p,n)))
+colnames(temp)[2]<- "variable"
+colnames(temp)[1]<- "xvar"
 results <- bind_rows(results, temp)
   }
+}
 
-write.csv(results, file="figs2/Accessory_Costs/Table01_correlations_with_repro_inv.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table07_correlations_with_repro_inv.csv",row.names=FALSE)
 ```
 
-#Figure 2. Correlations of various reproductive investment categories against plant weight
+#Figure 5. Correlations of various reproductive investment categories against plant weight
 ```{r}
@@
 dev.off()
+
+xvar <- "diameter_0"
+yvar <- "repro_all_count"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
+results <- lines(fit$groupsummary)
+plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,yaxt="n")
+points((repro_inv)~(diameter_0),SummarySpp[["mean"]],cex=2,col=col.spp(species),pch=16)
+
+abline(0,1)
+#mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
+
+xvar <- "diameter_0"
+yvar <- "seed_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
+results <- lines(fit$groupsummary)
+plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,yaxt="n")
+points((repro_inv)~(diameter_0),SummarySpp[["mean"]],cex=2,col=col.spp(species),pch=16)
+
+abline(0,1)
+mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
 ```
+names(SummaryInd)
+###GOOD VISUALS - not currently in manuscript
 
-#Table 3 showing accessory cost values for the species
-```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seedcosts,prop_success,
-                               prepollencosts,packaging_dispersal_per_seed,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
-acc_costs_spp$species <- labels.spp.full()
-acc_costs_spp <- format(acc_costs_spp, digit=2)
-
-write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table03_AccCosts_by_Species.csv",row.names=FALSE)
-```
-
-#Figure 3. Ternary diagram showing seedcosts
-```{r}
-ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollencosts,packaging_dispersal_per_seed)
-ternary$packaging_dispersal_per_seed[9] <- 0.1
-
-ternary$seedcosts = ternary$seed_size + ternary$prepollencosts + ternary$packaging_dispersal_per_seed
-ternary$per_seed <-100*ternary$seed_size/ternary$seedcosts
-ternary$per_poll <-100*ternary$prepollencosts/ternary$seedcosts
-
-ternary$per_disp <-100*ternary$packaging_dispersal_per_seed/ternary$seedcosts
-mod_poll <- sma(per_poll~seedcosts,ternary,slope.test=0,method="OLS",log="x")
-mod_seed <- sma(per_seed~seedcosts,ternary,slope.test=0,method="OLS",log="x")
-mod_disp <- sma(per_disp~seedcosts,ternary,slope.test=0,method="OLS",log="x")
-
-costs_per_seed <- as.data.frame("costs for seed (%)")
-costs_per_seed <- cbind(costs_per_seed,select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-
-costs_per_seed2 <- as.data.frame("costs for pre-pollination (%)")
-costs_per_seed2 <- cbind(costs_per_seed2,select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
-
-costs_per_seed2 <- as.data.frame("costs for dispersal (%)")
-costs_per_seed2 <- cbind(costs_per_seed2,select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
-
-write.csv(costs_per_seed, file="figs2/Accessory_Costs/Table00_in_text_costs_per_seed.csv",row.names=FALSE)
-
-win.metafile("figs2/Accessory_Costs/FigureXX_seedcost_components.wmf", height=6, width=6)
-plot
-
-plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seedcosts")
-points(per_poll~seedcosts,ternary,col="red",pch=16,cex=2)
-points(per_disp~seedcosts,ternary,col="blue",pch=16,cex=2)
-
-abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
-abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
-abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
-legend("topleft",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
-dev.off()
-```
-
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seedcosts.wmf", height=5, width=5)
-plot
-
-par(mfrow=c(1,1), cex=1, omi=c(1,1,1,1), mai=c(.1,.1,.1,.1))
-
-ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
-  labs(y = "seed",
-       x = "pre-poll",
-       z = "pack&disp",
-       Tarrow = "seed weight (%)",
-       Larrow = "pre-pollination costs (%)",
-       Rarrow = "packaging & dispersal costs (%)",
-       title = "Seed cost components",
-       size = 3) +
-  geom_point(size=sqrt(ternary$seedcosts/2),shape=20,color=col.spp()) +
-   theme_bw() + 
-  theme_showarrows() +
-  geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seedcosts/500),size=2)
-
-dev.off()
-```
-
-#Table 4 showing seedcost breakdown into components, by species
-```{r}
-prop_seedcosts_spp <- dplyr::select(SummarySpp[["mean"]],species,seedcosts,prop_prepollencosts,prop_dispersalcosts,prop_seedcosts)
-prop_seedcosts_spp$species <- labels.spp.full()
-prop_seedcosts_spp <- format(prop_seedcosts_spp, digit=2)
-write.csv(prop_seedcosts_spp, file="figs2/Accessory_Costs/Table04_Prop_seedcosts_by_Species.csv",row.names=FALSE)
-```
-
-#Figure 4. Scaling of accessory costs versus seed size, by species
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure04_seed_size_acc_cost_correlations.wmf", height=5, width=15)
-plot
-
-par(mfrow=c(1,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
-options(scipen = 5)
-
-plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
-abline(coef(mod)[1],coef(mod)[2])
-abline(coef(mod)[1],1,col="red")
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-
-plot(prepollencosts~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pre-pollination costs per seed (mg/seed)",xlab="",cex=1.5)
-#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
-mod <- lm(log10(prepollencosts)~log10(seed_size),SummarySpp[["mean"]])
-abline(coef(mod)[1],coef(mod)[2])
-abline(coef(mod)[1],1,col="red")
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-
-plot(packaging_dispersal_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="packaging and dispersal costs per seed (mg/seed)",xlab="",cex=1.5)
-#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
-mod <- lm(log10(packaging_dispersal_per_seed)~log10(seed_size),SummarySpp[["mean"]])
-abline(coef(mod)[1],coef(mod)[2])
-abline(coef(mod)[1],1,col="red")
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
-dev.off()
-```
-
-#Table 5. Slopes for various seed size by acc cost regressions
-```{r}
-par(mfrow=c(2,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
-options(scipen = 5)
-
-plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
-slopes <- sma(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-#abline(slopes$groupsummary["Int"][[1]],1,col="red")
-abline(0,1,col="red")
-words.bottom.right.logxy(mod)
-
-acc_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
-
-plot(prepollencosts ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(prepollencosts) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
-words.bottom.right.logxy(mod)
-extra.topleft.logxy("slope <1, so bigger seeded species have lower fixed costs of making pre-pollination parts")
-slopes <- sma(log10(prepollencosts) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-plot(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(prepollen_failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
-words.bottom.right.logxy(mod)
-extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
-slopes <- sma(log10(prepollen_failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_failure_per_seed,SummarySpp[["se"]]$prepollen_failure_per_seed)
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
-words.top.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
-slopes <- sma(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1)
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-plot(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(packaging_dispersal_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"))
-words.top.left.logxy(mod)
-slopes <- sma(log10(packaging_dispersal_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"),slope.test=1)
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
-
-acc_by_species$variable = c("total accessory costs","prepollen_success","prepollen_failure","c div p","dispersal")
-
-write.csv(acc_by_species, file="figs2/Accessory_Costs/Table05_acc_cost_seed_size_slopes.csv",row.names=FALSE)
-```
-
-#Figure 5 seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
-```{r}
-
-win.metafile("figs2/Accessory_Costs/Figure05_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
-plot
-
-par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
-options(scipen = 4)
-
-plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,1000),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="seed size (mg)",ylab="seed set")
-mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
-abline(mod$coeff[1],mod$coeff[2])
-text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
-     paste("r2 = ",round(glance(mod)[1],2)),adj=1)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
-legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")
-
-#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
-plot(scaled_seed_count~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="seed size (mg)",ylab="count, scaled to plant size")
-points(scaled_bud_count~seed_size,SummaryInd,pch=21,col=col.spp(species))
-#points(scaled_failure_count~seed_size,SummaryInd,pch=2,col=col.spp(species))
-axis(2, at=c(0.000001,0.0001,0.01,1), labels=c(0.000001,0.0001,0.01,1),cex.axis=0.9)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
-
-summary(mod2)
-mod1 <- sma(scaled_seed_count~seed_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
-mod2 <- sma(scaled_bud_count~seed_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
-mod3 <- sma(scaled_failure_count~seed_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
-sma_abline(mod1)
-abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue")
-abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red")
-legend("topright",legend=c("seed count","total bud count","failed flower count"),col=c("black","blue","red"),pch=c(16,21,8),bty="n")
-
-#species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
-plot(prop_prepollencosts~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.01,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
-mod <- sma(prop_prepollencosts~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
-y.error.bars(SummarySpp[["mean"]]$seedset,SummarySpp[["mean"]]$prop_prepollencosts,SummarySpp[["se"]]$prop_prepollencosts)
-sma_abline(mod)
-sma_sum(mod)
-text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
-     paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
-axis(2, at=c(-0.2,0,.2,.4,.6,.8,1), labels=c("",0.0,0.2,0.4,0.6,0.8,""),cex.axis=1)
-
-dev.off()
-```
-
-#Table 6. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
-```{r}
-win.metafile("figs2/Accessory_Costs/FigureXX_RE_RA_size_age_patterns.wmf", height=10, width=10)
-plot
-
-par(mfrow=c(2,2), cex=1, omi=c(.1,.4,.1,.05), mai=c(.6,.3,.1,.1))
-options(scipen = 2)
-
-xvar <- "repro_inv"
-yvar <- "accessory_per_seed"
+xvar <- "leaf_area_0"
+yvar <- "flower_inv"
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
-mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
-legend_with_r2(results,"bottomright")
+plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,10000000),xlab="",ylab="",lty=results$linetype,pch=16)
+results
 
-write.csv(results, file="figs2/Accessory_Costs/Table06a_accessory_vs_RE.csv",row.names=FALSE)
+plot(seed_size~total_weight_0,SummaryInd,log="xy",pch=16,col=col.spp(species))
+plot(seed_size~total_weight_0,SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
-xvar <- "total_weight_0"
-yvar <- "accessory_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+plot(seedset~prop_failure,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),log="xy",pch=16,col=col.spp(species))
+mod <- lm(log(seed_size)~log(total_weight_0),data=subset(SummarySpp[["mean"]])
+summary(mod)
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
-mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
-legend_with_r2(results,"bottomright")
-
-write.csv(results, file="figs2/Accessory_Costs/Table06b_accessory_vs_total_weight.csv",row.names=FALSE)
-
-xvar <- "age"
-yvar <- "accessory_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
-mtext(text="age (years)",side=1,line=2,outer=FALSE)
-mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
-legend_with_r2(results,"topleft")
-
-write.csv(results, file="figs2/Accessory_Costs/Table06c_accessory_vs_age.csv",row.names=FALSE)
-dev.off()
-```
-
-###GOOD VISUALS - not currently in manuscript
 ```{r}
@@
 plot(fit,col=col.spp(fit$groupsummary$group),xlab="",ylab="",lty=results$linetype,pch=16,log="x")
-```
-
-#correlations between repro inv and propagule inv by species
-```{r}
-yvar <- "repro_inv"
-xvar <- "propagule_inv"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- fit$groupsummary
-
-write.csv(results, file="figs2/Accessory_Costs/Table02_extra_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
 ```

### 2016-04-28 Accessory_figs_20160218.Rmd
small changes

@@
 
-plot(prepollen_failure_per_seed~seed_size,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species))
-mod <- lm(log(propagule_inv)~log(seed_size),data=subset(SummarySpp[["mean"]],species!="EPMI"))
+plot(prop_failure~seedset,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),pch=16,log="",col=col.spp(species))
+mod <- lm(prop_failure~seedset,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"))
 summary(mod)
@@
 summary(mod)
+
+#seed size by propagule investment - all species
+mod <- sma(propagule_inv ~ seed_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
+summary(mod)
+plot(propagule_inv ~ seed_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+#seed size by propagule investment - without EPMI
+mod <- sma(propagule_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="OLS", log="xy",slope.test=1)
+summary(mod)
+plot(propagule_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
+
+#seed size by reproductive investment - all species
+mod <- sma(repro_inv ~ seed_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
+summary(mod)
+plot(repro_inv ~ seed_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+#seed size by reproductive investment - without EPMI
+mod <- sma(repro_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="OLS", log="xy",slope.test=1)
+summary(mod)
+plot(repro_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
+
+#seed size by reproductive investment - all species
+mod <- sma(total_weight_0 ~ seed_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
+summary(mod)
+plot(total_weight_0 ~ seed_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 
-write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table03_AccCosts_by_Species.csv",row.names=FALSE)
+write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table01_AccCosts_by_Species.csv",row.names=FALSE)
 ```
@@
 
-acc_by_species$variable = c("total accessory costs","prepollen_success","prepollen_failure","total prepollen","c div p","dispersal")
+slopes <- sma(postpollen_all_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+acc_by_species$variable = c("total accessory costs","prepollen_success","prepollen_failure","total prepollen","c div p","dispersal","total postpollen")
 
@@
 ```
+plot(prop_prepollen_all~seed_size,SummarySpp[["mean"]],pch=16,col=col.spp(species),log="x")
 

### 2016-04-28 R/Summaries.R

@@ -297,7 +297,8 @@ combine_by_individual <- function(IndividualsList, ReproductionAllocation_all, A
     scaled_repro_inv = repro_inv/ total_weight,
     repro_inv_mature = repro_inv,
     repro_all_count_mature = repro_all_count,
-    leaf_area_0_mature = leaf_area_0
+    leaf_area_0_mature = leaf_area_0,
+    postpollen_all_per_seed = postpollen_aborted_per_seed + seed_size + packaging_dispersal_per_seed
     )
 
   #if seedset is low, prepollen costs increase, because the cost of producing pollen across the whole plant is higher per seed matured  
@@ -312,7 +313,7 @@ combine_by_individual <- function(IndividualsList, ReproductionAllocation_all, A
               "prop_propagule","prop_postpollen_aborted","prop_prepollen_success","prop_prepollen_aborted","prop_prepollen_all",
               "prop_accessory","prop_propagule_nonzero","prop_accessory_nonzero","prop_prepollencosts","prop_seedcosts",
               "prop_dispersalcosts","prop_dispersalcosts2","scaled_failure_count","scaled_seed_count","scaled_bud_count",
-             "scaled_repro_inv","prop_postpollencosts","failure_per_seed","leaf_area_0","leaf_area_0_mature","total_weight_0")) {
+             "scaled_repro_inv","prop_postpollencosts","failure_per_seed","leaf_area_0","leaf_area_0_mature","total_weight_0","postpollen_all_per_seed")) {
     i <- is.na(SummaryInd[[v]])
     SummaryInd[[v]][i] <- 0
     i <- is.infinite(SummaryInd[[v]])
@@ -405,7 +406,7 @@ get_species_values <- function(SummaryInd, groups) {
       prepollen_aborted_per_seed, prepollen_success_per_seed, postpollen_aborted_per_seed,repro_inv_per_seed,failure_inv,
       scaled_failure_count,scaled_bud_count,prop_prepollencosts,prepollencosts,
       accessory_inv, prepollen_aborted_inv, prepollen_success_inv,prepollen_all_inv,prop_prepollen_aborted, prop_prepollen_success,
-      prop_prepollen_all, prop_accessory,prop_failure,prop_success,scaled_repro_inv,failure_to_ovule_ratio,failure_per_seed)
+      prop_prepollen_all, prop_accessory,prop_failure,prop_success,scaled_repro_inv,failure_to_ovule_ratio,failure_per_seed,postpollen_all_per_seed)
   })
   names(out[[5]]) <- fs
 

### 2016-05-05 Accessory_figs_20160218.Rmd
data on missing branches small changes to accessory costs following lab meeting

@@
 ternary$per_poll <-100*ternary$prepollencosts/ternary$seedcosts
+ternary$post_poll <- 100-ternary$per_poll
 
@@
 mod_disp <- sma(per_disp~seedcosts,ternary,slope.test=0,method="OLS",log="x")
+mod_post_poll <- sma(post_poll~seedcosts,ternary,slope.test=0,method="OLS",log="x")
 
@@
 points(per_disp~seedcosts,ternary,col="blue",pch=16,cex=2)
+
+abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
+abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
+abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
+legend("topleft",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
+dev.off()
+
+win.metafile("figs2/Accessory_Costs/FigureXX_prepoll_vs_postpoll.wmf", height=6, width=6)
+plot
+
+plot(per_poll~seedcosts,ternary,col="black",log="x",pch=16,cex=2,ylim=c(0,100),ylab="prop of seedcosts")
+points(post_poll~seedcosts,ternary,col="red",pch=16,cex=2)
+abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="black",lwd=2)
+abline(mod_post_poll$groupsummary["Int"][[1]],mod_post_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
+summary(mod_post_poll)
 
@@
 
-summary(mod2)
 mod1 <- sma(scaled_seed_count~seed_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")

### 2016-05-17 scripts/Accessory_figs_20160218.Rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

--- 2016-05-05 Accessory_figs_20160218.Rmd
@@
 summary(mod)
+
+#SummarySpp[["mean"]]$embryo_endo_West1990 <- c(22.246,3.6828,1.0961,0.02,31.234,10.961,12.446,0.29716,0.8064,12.328,3.2274,1.7127,1.1583,1.274)
+SummarySpp[["mean"]]$embryo_endo_West1990 <- c(120,3.6828,0.8,0.02,31.234,10.961,12.446,0.29716,0.8064,12.328,3.2274,1.7127,0.72,1.274)
+SummarySpp[["mean"]]$provisioning2 <- SummarySpp[["mean"]]$postpollen_all_per_seed - SummarySpp[["mean"]]$embryo_endo_West1990
 
@@
 ```
+$embryo_endo_West1990
 
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure04_seed_size_acc_cost_correlations.wmf", height=5, width=15)
+win.metafile("figs2/Accessory_Costs/Figure03_seed_size_acc_cost_correlations.wmf", height=5, width=15)
 plot
@@
 
-plot(prepollencosts~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pre-pollination costs per seed (mg/seed)",xlab="",cex=1.5)
+plot(prepollencosts~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
 #y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
@@
 
-plot(packaging_dispersal_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="packaging and dispersal costs per seed (mg/seed)",xlab="",cex=1.5)
+plot(postpollen_all_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
 #y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
-mod <- lm(log10(packaging_dispersal_per_seed)~log10(seed_size),SummarySpp[["mean"]])
+mod <- lm(log10(postpollen_all_per_seed)~log10(seed_size),SummarySpp[["mean"]])
 abline(coef(mod)[1],coef(mod)[2])
@@
 mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
+dev.off()
+```
+
+#Figure 3 v2. Scaling of accessory costs versus weight of embryo + endosperm, by species
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure03_embryo_size_acc_cost_correlations.wmf", height=5, width=15)
+plot
+
+par(mfrow=c(1,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+options(scipen = 5)
+
+plot(accessory_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(accessory_per_seed) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
+words.top.left.logxy(mod)
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+
+plot(prepollencosts~embryo_endo_West1990,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
+mod <- lm(log10(prepollencosts)~log10(embryo_endo_West1990),SummarySpp[["mean"]])
+words.top.left.logxy(mod)
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+
+plot(postpollen_all_per_seed~embryo_endo_West1990,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
+mod <- lm(log10(postpollen_all_per_seed)~log10(embryo_endo_West1990),SummarySpp[["mean"]])
+words.top.left.logxy(mod)
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+mtext(text="embryo + endosperm (mg)",side=1,line=1.5,outer=TRUE)
+
 dev.off()
@@
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-#abline(slopes$groupsummary["Int"][[1]],1,col="red")
-abline(0,1,col="red")
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+#abline(0,1,col="red")
 words.bottom.right.logxy(mod)
@@
 
-plot(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(prepollen_failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
+plot(failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
 words.bottom.right.logxy(mod)
-extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
-slopes <- sma(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+#extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
+slopes <- sma(failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
 abline(slopes$groupsummary["Int"][[1]],1,col="red")
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_failure_per_seed,SummarySpp[["se"]]$prepollen_failure_per_seed)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
 acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
@@
 
-plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
-words.top.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
-slopes <- sma(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+# plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
+# words.top.left.logxy(mod)
+# y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
+# slopes <- sma(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
+# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+# abline(slopes$groupsummary["Int"][[1]],1,col="red")
+# acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
@@
 
-acc_by_species$variable = c("total accessory costs","prepollen_success","prepollen_failure","total prepollen","c div p","dispersal","total postpollen")
+acc_by_species$variable = c("total accessory costs","prepollen_success","failed_tissues","total prepollen","dispersal","total postpollen")
 
@@
 ```
-plot(prop_prepollen_all~seed_size,SummarySpp[["mean"]],pch=16,col=col.spp(species),log="x")
+
+#Table 3 v2. Slopes for various embryo size by acc cost regressions
+```{r}
+par(mfrow=c(2,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+options(scipen = 5)
+
+plot(accessory_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(accessory_per_seed) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
+slopes <- sma(accessory_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+#abline(0,1,col="red")
+words.bottom.right.logxy(mod)
+
+acc_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
+
+plot(prepollencosts ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(prepollencosts) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]]))
+words.bottom.right.logxy(mod)
+extra.topleft.logxy("slope <1, so bigger seeded species have lower fixed costs of making pre-pollination parts")
+slopes <- sma(prepollencosts ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+plot(failure_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(failure_per_seed) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]]))
+words.bottom.right.logxy(mod)
+#extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
+slopes <- sma(failure_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+plot(prepollen_all_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(prepollen_all_per_seed) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]]))
+words.bottom.right.logxy(mod)
+slopes <- sma(prepollen_all_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+# plot(postpollen_aborted_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
+# words.top.left.logxy(mod)
+# y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
+# slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
+# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+# abline(slopes$groupsummary["Int"][[1]],1,col="red")
+# acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+SummarySpp[["mean"]]$provisioning2 <- SummarySpp[["mean"]]$postpollen_all_per_seed - SummarySpp[["mean"]]$embryo_endo_West1990
+plot(provisioning2 ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(provisioning2) ~ log10(embryo_endo_West1990),data=subset(SummarySpp[["mean"]]))
+words.top.left.logxy(mod)
+slopes <- sma(provisioning2 ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
+
+slopes <- sma(postpollen_all_per_seed ~ embryo_endo_West1990,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+acc_by_species$variable = c("total accessory costs","prepollen_success","failed_tissues","total prepollen","dispersal","total postpollen")
+
+write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_embryo_endo_West1990_slopes.csv",row.names=FALSE)
+```
 

### 2016-05-17 scripts/Biology_talk.rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

--- 2015-10-08 Biology_talk.rmd
@@
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=8, fig.height=8}
+win.metafile("figs2/RA_all_spp1.wmf", height=5, width=5)
+plot
+par(mfrow=c(1,1), cex=1, omi=c(.7,.7,.1,.1), mai=c(.1,.1,.1,0.1)) 
+mod <- lm(log(growth_inv)~log(repro_inv),data=subset(SummaryInd,repro_inv>0))
+plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),xlab="",ylab="")
+words.top.left.logxy(mod)
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+abline(0,1)
+text(2.1,3,srt=45,"RA = 0.5",cex=.7)
+abline(log10(3),1)
+text(2,9,srt=45,"RA = 0.75",cex=.7)
+abline(log10(9),1)
+text(2,25,srt=45,"RA = 0.9",cex=.7)
+abline(log10(19),1)
+text(2,60,srt=45,"RA = 0.95",cex=.7)
+abline(log10(.111),1)
+text(19,3,srt=45,"RA = 0.1",cex=.7)
+abline(log10(.010101),1)
+text(170,2.4,srt=45,"RA = 0.01",cex=.7)
+mtext("reproductive investment (mg)", 2, outer=TRUE,cex=1,line=2)
+mtext("growth investment (mg)", 1, outer=TRUE,cex=1,line=1.7)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=8, fig.height=8}
+win.metafile("figs2/RA_all_spp2.wmf", height=5, width=5)
+plot
+par(mfrow=c(1,1), cex=1, omi=c(.7,.7,.1,.1), mai=c(.1,.1,.1,0.1))  
+plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
+abline(0,1)
+text(2.1,3,srt=45,"RA = 0.5",cex=.7)
+abline(log10(3),1)
+text(2,9,srt=45,"RA = 0.75",cex=.7)
+abline(log10(9),1)
+text(2,25,srt=45,"RA = 0.9",cex=.7)
+abline(log10(19),1)
+text(2,60,srt=45,"RA = 0.95",cex=.7)
+abline(log10(.111),1)
+text(19,3,srt=45,"RA = 0.1",cex=.7)
+abline(log10(.010101),1)
+text(170,2.4,srt=45,"RA = 0.01",cex=.7)
+mtext("reproductive investment (mg)", 2, outer=TRUE,cex=1,line=2)
+mtext("growth investment (mg)", 1, outer=TRUE,cex=1,line=1.7)
+dev.off()
+```
+
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-win.metafile("figs2/RA_talk_plot1.wmf", height=7, width=4)
+win.metafile("figs2/RA_talk_reproinv_by_age.wmf", height=7, width=4)
 plot
 par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
-yvar <- "leaf_weight"
-yvar2 <- "RA"
-yvar3 <- "total_inv"
-yvar4 <- "RA_leaf_area"
-xvar <- "leaf_area_midyear"
-xvar2 <- "age"
-xvar3 <- "height"
+xvar <- "age"
+yvar <- "repro_inv"
 
@@
 
-  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1),cex=1,
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(repro_inv~age,data2[[spp]],pch=16,cex=0.8)
+}
+mtext("reproductive investment (mg)", 2, outer=TRUE,cex=1,line=2)
+mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_growthinv_by_age.wmf", height=7, width=4)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+xvar <- "age"
+yvar <- "growth_inv"
+
+data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(growth_inv~age,data2[[spp]],pch=16,cex=0.8)
+}
+mtext("vegetative investment (mg)", 2, outer=TRUE,cex=1,line=2.2)
+mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_leafinv_by_age.wmf", height=7, width=4)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+xvar <- "age"
+yvar <- "growth_leaf"
+
+data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(growth_leaf~age,data2[[spp]],pch=16,cex=0.8)
+}
+mtext("leaf investment (mg)", 2, outer=TRUE,cex=1,line=2.2)
+mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_H_by_age.wmf", height=7, width=4)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+xvar <- "age"
+yvar <- "height"
+
+data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+  points(height~age,data2[[spp]],pch=16,cex=0.8)
+}
+mtext("height (mm)", 2, outer=TRUE,cex=1,line=2)
+mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_weight_by_age.wmf", height=7, width=4)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+yvar <- "total_weight"
+xvar <- "age"
+
+data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",xlim=c(1,33),cex=1,
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+}
+mtext("plant weight (mg)", 2, outer=TRUE,cex=1,line=2.2)
+mtext("age (years)", 1, outer=TRUE,cex=1,line=0.5)
+dev.off()
+```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_plot1.wmf", height=7, width=4)
+plot
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
+yvar <- "RA"
+xvar <- "age"
+
+data <- subset(SummaryInd, species=="BOLE"|species=="GRBU"|species=="EPMI"|species=="HATE")
+data <- split(data, data$species)
+
+data2 <- subset(SummarySppAge[["mean"]])
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1),cex=1,
                     col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
@@
 par(mfcol=c(4,1), cex=1, omi=c(.3,.7,.01,.01), mai=c(.4,.15,.3,0.1)) 
-yvar <- "leaf_weight"
-yvar2 <- "RA"
-yvar3 <- "total_inv"
-yvar4 <- "RA_leaf_area"
+yvar <- "total_inv"
 xvar <- "leaf_area_midyear"
-xvar2 <- "age"
-xvar3 <- "height"
 
@@
 
-  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="",ylab="",cex=1,
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1,
                     col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
@@
 par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)) 
-yvar <- "leaf_weight"
-yvar2 <- "height"
-yvar3 <- "total_inv"
-yvar4 <- "RA_leaf_area"
-xvar <- "leaf_area_midyear"
-xvar2 <- "age"
-xvar3 <- "height"
+yvar <- "RA_leaf_area"
+xvar <- "age"
 
@@
 
-  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",xlim=c(1,33),ylim=c(0,1.2),cex=1,
                     col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
@@
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
-win.metafile("figs2/RA_talk_plot4.wmf", height=7, width=4)
+win.metafile("figs2/RA_talk_leafweight_x_age.wmf", height=7, width=4)
 plot
@@
 ```
+
+```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
+win.metafile("figs2/RA_talk_LA_tradeoff.wmf", height=7, width=4)
+plot
+
+  for(v in c("growth_leaf_min")) {
+    i <- (SummaryInd[[v]]) > 0
+    SummaryInd[[v]][i] <- 0
+    }
+
+SummaryInd$growth_leaf_nonzero <- SummaryInd$growth_leaf - SummaryInd$growth_leaf_min
+
+par(mfcol=c(4,1), cex=1, omi=c(.3,.6,.01,.01), mai=c(.4,.15,.3,0.1)
+
+yvar <- "growth_leaf_nonzero"
+xvar <- "repro_inv"
+
+data <- subset(SummaryInd,individual!="GRBU_903"&individual!="PELA_905"&individual!="COER_804"&individual!="PEPU_905"&individual!="GRSP_907"&individual!="LEES_907"&(species=="BOLE"|species=="EPMI"|species=="GRBU"|species=="HATE"))
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,xlab="",ylab="",cex=1,log="xy",yaxt="n",
+                    col=col.age(data[[spp]]$age),main=labels.spp.full(spp),cex.main=0.9)
+    }
+
+mtext("leaf investment (mg)", 2, outer=TRUE,cex=1,line=2)
+mtext("reproductive investment (mg)", 1, outer=TRUE,cex=1,line=1.7)
+dev.off()
+```

### 2016-05-17 scripts/Growth_figs.rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

--- 2015-09-01 Growth_figs.rmd
@@
 ```
+
+```{r}
+#plot(LMA ~ age,data=subset(SummarySppAge[["mean"]]),col=col.spp(species),pch=16,log="x")
+
+par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+yvar <- "shoot_leaf_area"
+xvar <- "growth_leaf"
+
+data <- subset(SummaryInd,age>2&growth_leaf>0)
+data <- split(data, data$species)
+
+lmfits <- lapply(data, function(x) lm(log((x[[yvar]])) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+```

### 2016-05-17 scripts/RA_combined_plots.Rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

--- 2015-09-10 RA_combined_plots.Rmd
@@
 
-pdf("figs2/RA_schedule_plots_3.pdf", height=11.3, width=8)
-plot
+#pdf("figs2/RA_schedule_plots_3.pdf", height=11.3, width=8)
+#plot
 par(mfcol=c(4,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.1,0.1)) 
-yvar <- "leaf_area"
+yvar <- "leaf_weight"
 yvar2 <- "height"
@@
   }
-dev.off()
+#dev.off()
 ```

### 2016-05-17 scripts/investment_in_parts.Rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

InvestInd <- 
  InvestmentByPart %>%
  group_by(individual) %>%
  summarise_each(funs(sum),weight)
InvestInd$species <- substr(InvestInd$species,1,nchar(InvestInd$species)-4)

```{r}
InvestIndPart <- 
  InvestmentByPart %>%
  group_by(individual,part) %>%
  summarise_each(funs(sum),weight)
InvestIndPart$species <- InvestIndPart$individual
InvestIndPart$species <- substr(InvestIndPart$species,1,nchar(InvestIndPart$species)-4)
InvestIndPart <- merge(InvestIndPart,accessoryList,by=c("species","part"),all.x=TRUE)
```

```{r}
InvestIndAcc <-
  InvestIndPart %>%
  group_by(individual,accessory_part) %>%
  summarise_each(funs(sum),weight)

  for(v in c("weight")) {
    i <- is.na(InvestIndAcc[[v]])
    InvestIndAcc[[v]][i] <- 0
   }

InvestIndAcc1 <- tidyr::spread(InvestIndAcc,accessory_part,weight,fill=0,drop=FALSE)
View(InvestIndAcc)
```

InvestPetal <- subset(InvestmentByPart,part=="flower_petals")
InvestPetal <- 
  InvestPetal %>%
  group_by(individual) %>%
  summarise_each(funs(sum),weight)

names(InvestPetal) <- c("individual","weight_petal")

InvestInd <- dplyr::left_join(InvestInd,InvestPetal, by = "individual")
InvestInd$prop_petal <- InvestInd$weight_petal / InvestInd$weight
InvestInd$species <-InvestInd$individual
InvestInd$species <- substr(InvestInd$species,1,nchar(InvestInd$species)-4)

plot(prop_petal~weight,InvestInd,pch=16,log="x",col=col.spp(species))
mod <- lm(log(weight)~prop_petal,InvestInd)
summary(mod)

InvestIndPart <- tidyr::spread(InvestIndPart,part,weight)

### 2016-05-17 scripts/results_accessory_shorter.Rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

--- 2015-08-19 results_accessory_shorter.Rmd
@@
-```{r, echo=FALSE,results='hide', message=FALSE}
-library(remake)
-create_bindings()
-
-source("scripts/functions.R")
-```
-
 #Accessory costs
@@
 par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3))
-mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, log="x", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
+plot(asin(sqrt(prop_accessory))~seed_size,SummarySpp[["mean"]], log="x", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.bottom.right.logx(mod)
 
-mod <- lm(log(total_weight_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, log="x", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
+mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
+plot(asin(sqrt(prop_accessory))~total_weight,SummarySpp[["mean"]], log="x", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
 words.bottom.right.logx(mod)
 
-mod <- lm(log(seedset_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, log="x", pch=16,col=col.spp(species),ylab="",cex=1.3)
+mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
+plot(asin(sqrt(prop_accessory))~seedset,SummarySpp[["mean"]], log="x", pch=16,col=col.spp(species),ylab="",cex=1.3)
 words.top.right.logx(mod)
 
-mod <- lm(asin(sqrt(prop_prepollen_all_mean))~asin(sqrt(prop_accessory_mean)),SummarySpp)
-plot(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, log="", pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
+mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
+plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummarySpp[["mean"]], log="", pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
 words.top.right(mod)
@@
 par(mfrow=c(2,2), cex=1, omi=c(0.4,0.6,0.3,0.3), mai=c(1.1,0.8,0.3,0.3)) 
-mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
-plot(accessory_per_seed_mean~seed_size,SummarySpp, log="xy", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+mod <- lm(log(seed_size)~(accessory_per_seed),SummarySpp[["mean"]])
+plot(accessory_per_seed~seed_size,SummarySpp[["mean"]], log="xy", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
 
-mod <- lm(log(total_weight_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot(accessory_per_seed_mean~total_weight_mean,SummarySpp, log="xy", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
+mod <- lm(log(total_weight)~log(accessory_per_seed),SummarySpp[["mean"]])
+plot(accessory_per_seed~total_weight,SummarySpp[["mean"]], log="xy", pch=16,col=col.spp(species),ylab="",xlab="Total weight (mg)",cex=1.3)
 words.bottom.right.logxy(mod)
 
-mod <- lm(log(seedset_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot((accessory_per_seed_mean)~seedset_mean,SummarySpp, log="xy", pch=16,col=col.spp(species),ylab="",cex=1.3)
+mod <- lm(log(seedset)~log(accessory_per_seed),SummarySpp[["mean"]])
+plot((accessory_per_seed)~seedset,SummarySpp[["mean"]], log="xy", pch=16,col=col.spp(species),ylab="",cex=1.3)
 words.top.right.logxy(mod)
 
-mod <- lm(log(prepollen_all_per_seed_mean)~log(accessory_per_seed_mean),SummarySpp)
-plot(log(accessory_per_seed_mean)~log(prepollen_all_per_seed_mean),SummarySpp, log="", pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
+mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),SummarySpp[["mean"]])
+plot(log(accessory_per_seed)~log(prepollen_all_per_seed),SummarySpp[["mean"]], log="", pch=16,col=col.spp(species),ylab="",xlab="pre-pollination costs (proportional)",cex=1.3)
 words.top.right(mod)
@@
 plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="",xlab="seed size (mg)",cex=1.3)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="",cex=1.3)
-legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.top.right.logx(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
-plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp(species),xlab="costs to make 1 seed (mg)",cex=1.2)
-mod <- lm(seedcosts~seed_size, SummarySpp)
+plot(seed_size~seedcosts,data=subset(SummarySpp[["mean"]]),log="xy",pch=16,col=col.spp(species),xlab="costs to make 1 seed (mg)",cex=1.2)
+mod <- lm(seedcosts~seed_size, SummarySpp[["mean"]])
 words.bottom.right.logxy(mod)
-text(seed_size~seedcosts,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")
+text(seed_size~seedcosts,data=subset(SummarySpp[["mean"]]),labels=species, pos=1,offset=.6,cex=0.8,col="black")
 
-plot(seed_size~costs_per_seed,data=subset(SummarySpp),log="y",pch=16,col=col.spp(species),ylab="",xlab="proportional accessory costs, scaled by seed weight",cex=1.2)
-text(seed_size~costs_per_seed,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")
-mod <- lm(costs_per_seed~seed_size, SummarySpp)
+plot(seed_size~costs_per_seed,data=subset(SummarySpp[["mean"]]),log="y",pch=16,col=col.spp(species),ylab="",xlab="proportional accessory costs, scaled by seed weight",cex=1.2)
+text(seed_size~costs_per_seed,data=subset(SummarySpp[["mean"]]),labels=species, pos=1,offset=.6,cex=0.8,col="black")
+mod <- lm(costs_per_seed~seed_size, SummarySpp[["mean"]])
 words.bottom.left.logy(mod)
@@
 words.top.right.logx(mod)
-legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
@@
 plot(repro_all_count~RA,data=subset(SummaryInd,repro_all_count>0),col=col.spp(species),pch=16,log="xy",ylab="# of buds produced",xlab="")
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 words.bottom.right.logxy(mod)
@@
 
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 mod <- lm(log(RA)~log((propagule_inv)),data=subset(SummaryInd,RA>0&propagule_inv>0))
@@
 words.top.right(mod)
-legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 

### 2016-05-17 scripts/results_accessory_v3.Rmd
Move scripts into subfolder, remove from remake
Remove old plotting functions

--- 2015-08-19 results_accessory_v3.Rmd
@@
 plot(seed_count~(prop_accessory),SummaryInd, log="y", pch=16,col=col.spp(species),ylab="",xlab="proportion of reproduction to accessory tissues",cex=.9)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 ```
@@
 #mod <- lm(log(seed_size)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
-mod <- lm(log(seed_size)~(accessory_per_seed_mean),SummarySpp)
+mod <- lm(log(seed_size)~(accessory_per_seed),SummarySpp[["mean"]])
 plot(accessory_per_seed~seed_size,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=.9)
-points((accessory_per_seed_mean)~seed_size,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points((accessory_per_seed)~seed_size,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 
 #mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
-mod <- lm(log(seed_size)~asin(sqrt(prop_accessory_mean)),SummarySpp)
+mod <- lm(log(seed_size)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
 plot(asin(sqrt(prop_accessory))~seed_size,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=.9)
 words.bottom.right.logx(mod)
-points(asin(sqrt(prop_accessory_mean))~seed_size,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points(asin(sqrt(prop_accessory))~seed_size,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 mtext("seed size (mg)",1, outer=TRUE,cex=1.2)
@@
 #mod <- lm(log(total_weight)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
-mod <- lm(log(total_weight_mean)~log(accessory_per_seed_mean),SummarySpp)
+mod <- lm(log(total_weight)~log(accessory_per_seed),SummarySpp[["mean"]])
 plot(accessory_per_seed~total_weight,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=.9)
-points((accessory_per_seed_mean)~total_weight_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points((accessory_per_seed)~total_weight,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
@@
 #mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
-mod <- lm(log(total_weight_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
+mod <- lm(log(total_weight)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
 plot(asin(sqrt(prop_accessory))~total_weight,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
-points(asin(sqrt(prop_accessory_mean))~total_weight_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points(asin(sqrt(prop_accessory))~total_weight,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logx(mod)
@@
 #mod <- lm(log(seedset)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
-mod <- lm(log(seedset_mean)~log(accessory_per_seed_mean),SummarySpp)
+mod <- lm(log(seedset)~log(accessory_per_seed),SummarySpp[["mean"]])
 plot((accessory_per_seed)~seedset,SummaryInd, log="xy", pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=0.9)
-points((accessory_per_seed_mean)~seedset_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points((accessory_per_seed)~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.top.right.logxy(mod)
@@
 #mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0))
-mod <- lm(log(seedset_mean)~asin(sqrt(prop_accessory_mean)),SummarySpp)
+mod <- lm(log(seedset)~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
 plot(asin(sqrt(prop_accessory))~seedset,SummaryInd, log="x", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
-legend("bottomleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
-points(asin(sqrt(prop_accessory_mean))~seedset_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+points(asin(sqrt(prop_accessory))~seedset,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.top.right.logx(mod)
@@
 #mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
-mod <- lm(log(prepollen_all_per_seed_mean)~log(accessory_per_seed_mean),SummarySpp)
+mod <- lm(log(prepollen_all_per_seed)~log(accessory_per_seed),SummarySpp[["mean"]])
 plot((accessory_per_seed)~(prepollen_all_per_seed),SummaryInd, log="xy",pch=16,col=col.spp(species),ylab="accessory costs per successful seed",xlab="",cex=0.9)
-points((accessory_per_seed_mean)~prepollen_all_per_seed_mean,SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points((accessory_per_seed)~prepollen_all_per_seed,SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right.logxy(mod)
@@
 #mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),data=subset(SummaryInd,seed_count>0&accessory_per_seed>0&prepollen_all_per_seed>0))
-mod <- lm(asin(sqrt(prop_prepollen_all_mean))~asin(sqrt(prop_accessory_mean)),SummarySpp)
+mod <- lm(asin(sqrt(prop_prepollen_all))~asin(sqrt(prop_accessory)),SummarySpp[["mean"]])
 plot(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummaryInd, log="", pch=16,col=col.spp(species),ylab="proportional accessory costs",xlab="",cex=0.9)
-points(asin(sqrt(prop_accessory_mean))~asin(sqrt(prop_prepollen_all_mean)),SummarySpp, pch=16,col=col.spp(species),cex=1.8)
+points(asin(sqrt(prop_accessory))~asin(sqrt(prop_prepollen_all)),SummarySpp[["mean"]], pch=16,col=col.spp(species),cex=1.8)
 words.bottom.right(mod)
@@
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(1.1,1.1,.1,0.2))
-plot(seed_size~seedcosts,data=subset(SummarySpp),log="xy",pch=16,col=col.spp(species),xlab="costs to make 1 seed (mg)",ylab="seed size (mg)",cex=1.2)
-mod <- lm(seedcosts~seed_size, SummarySpp)
+plot(seed_size~seedcosts,data=subset(SummarySpp[["mean"]]),log="xy",pch=16,col=col.spp(species),xlab="costs to make 1 seed (mg)",ylab="seed size (mg)",cex=1.2)
+mod <- lm(seedcosts~seed_size, SummarySpp[["mean"]])
 abline(0,1)
@@
 words.top.left.logxy(mod)
-text(seed_size~seedcosts,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")
+text(seed_size~seedcosts,data=subset(SummarySpp[["mean"]]),labels=species, pos=1,offset=.6,cex=0.8,col="black")
 
-plot(seed_size~costs_per_seed,data=subset(SummarySpp),log="y",pch=16,col=col.spp(species),ylab="",xlab="proportional accessory costs, scaled by seed weight",cex=1.2)
-text(seed_size~costs_per_seed,data=subset(SummarySpp),labels=species, pos=1,offset=.6,cex=0.8,col="black")
-mod <- lm(costs_per_seed~seed_size, SummarySpp)
+plot(seed_size~costs_per_seed,data=subset(SummarySpp[["mean"]]),log="y",pch=16,col=col.spp(species),ylab="",xlab="proportional accessory costs, scaled by seed weight",cex=1.2)
+text(seed_size~costs_per_seed,data=subset(SummarySpp[["mean"]]),labels=species, pos=1,offset=.6,cex=0.8,col="black")
+mod <- lm(costs_per_seed~seed_size, SummarySpp[["mean"]])
 words.bottom.left.logy(mod)
@@
 words.bottom.right.logy(mod)
-legend("topleft",legend=labels.spp(),col=col.spp,pch=16, cex=.8,bty="n")
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 

### 2016-05-17 R/figures.R

@@ -184,78 +184,6 @@ col.lots <- function(x) {
             ceiling(n/80))
   cols[as.factor(x)]
 }
-get_ReproductionAllocations_by_age <- function(ReproductionAllocation_all){
-  group_by(ReproductionAllocation_all, species, age) %>%
-    summarise(
-      n=length(age),
-      GI_M = mean(growth_inv),
-      GI_L = mean(growth_inv) - 1.96/sqrt(n) * sd(growth_inv),
-      GI_U = mean(growth_inv) + 1.96/sqrt(n) * sd(growth_inv),
-      RI_M = mean(repro_inv),
-      RI_L = mean(repro_inv) - 1.96/sqrt(n) * sd(repro_inv),
-      RI_U = mean(repro_inv) + 1.96/sqrt(n) * sd(repro_inv),
-      RA_M = mean(RA),
-      RA_L = mean(RA) - 1.96/sqrt(n) * sd(RA),
-      RA_U = mean(RA) + 1.96/sqrt(n) * sd(RA)) %>%
-    arrange(species, age)
-}
-
-plot_species_ReproductionAllocation_age_panel <- function(InvBySpecies) {
-
-  InvByAge <- get_ReproductionAllocations_by_age(InvBySpecies)
-
-  cols <- col.spp()[InvBySpecies$species]
-
-  par(mfrow = c(1, 3), cex.main = 1, cex.lab = 1)
-  plot(InvByAge$age, InvByAge$GI_M, type = "b", lwd = 3, pch = as.character(InvByAge$age), cex = 1, col = cols, ylim = range(c(InvBySpecies$repro_inv, InvBySpecies$growth_inv)),
-    main = "Growth Investment", xlab = "Age (years)", ylab = "Growth Investment (mg)")
-  points(InvByAge$age, InvByAge$GI_L, pch = 2, cex = 1, col = cols)
-  points(InvByAge$age, InvByAge$GI_U, pch = 6, cex = 1, col = cols)
-  points(InvBySpecies$age, InvBySpecies$growth_inv, pch = "o", cex = 1, col = "grey")
-
-  plot(InvByAge$age, InvByAge$RI_M, type = "b", lwd = 1, pch = as.character(InvByAge$age), cex = 1, col = cols, ylim = range(c(InvBySpecies$repro_inv, InvBySpecies$growth_inv)),
[…]

### 2016-05-19 scripts/Accessory_figs_20160218.Rmd
changing variable names making sure script runs adding in other lists to calculate "dispersal costs" - still in progress

--- 2016-05-05 Accessory_figs_20160218.Rmd
@@
+#ideas in progress
+``` {r}
 plot(prop_prepollen_all~seed_size,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species))
@@
 summary(mod)
+```
 
@@
 
-mod <- lm(log10(seedcosts) ~prop_seedcosts,SummarySpp[["mean"]])
+mod <- lm(log10(seed_costs) ~prop_seed_costs,SummarySpp[["mean"]])
 summary(mod)
 
-mod <- lm(log10(seedcosts) ~prop_prepollencosts,SummarySpp[["mean"]])
+mod <- lm(log10(seed_costs) ~prop_prepollen_costs,SummarySpp[["mean"]])
 summary(mod)
 
-mod <- lm(log10(seedcosts) ~prop_dispersalcosts,SummarySpp[["mean"]])
+mod <- lm(log10(seed_costs) ~prop_dispersalcosts,SummarySpp[["mean"]])
 summary(mod)
@@
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seedcosts,prop_success,
-                               prepollencosts,packaging_dispersal_per_seed,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seed_costs,prop_success, prepollen_costs,packaging_dispersal_per_seed,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
 acc_costs_spp$species <- labels.spp.full()
@@
 
-#Figure 2. Ternary diagram showing seedcosts
+#Figure 2. Ternary diagram showing seed_costs
 ```{r}
-ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollencosts,packaging_dispersal_per_seed)
-ternary$packaging_dispersal_per_seed[9] <- 0.1
+ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs_corr)
+ternary$pack_disp_costs_corr[9] <- 0.1
 
-ternary$seedcosts = ternary$seed_size + ternary$prepollencosts + ternary$packaging_dispersal_per_seed
-ternary$per_seed <-100*ternary$seed_size/ternary$seedcosts
-ternary$per_poll <-100*ternary$prepollencosts/ternary$seedcosts
+ternary$seed_costs = ternary$seed_size + ternary$prepollen_costs + ternary$pack_disp_costs_corr
+ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
 ternary$post_poll <- 100-ternary$per_poll
+ternary$per_seed <-100*ternary$seed_size/ternary$seed_costs
+ternary$per_disp <-100*ternary$pack_disp_costs/ternary$seed_costs
 
-ternary$per_disp <-100*ternary$packaging_dispersal_per_seed/ternary$seedcosts
-mod_poll <- sma(per_poll~seedcosts,ternary,slope.test=0,method="OLS",log="x")
-mod_seed <- sma(per_seed~seedcosts,ternary,slope.test=0,method="OLS",log="x")
-mod_disp <- sma(per_disp~seedcosts,ternary,slope.test=0,method="OLS",log="x")
-mod_post_poll <- sma(post_poll~seedcosts,ternary,slope.test=0,method="OLS",log="x")
+mod_poll <- sma(per_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")
+mod_seed <- sma(per_seed~seed_costs,ternary,slope.test=0,method="OLS",log="x")
+mod_disp <- sma(per_disp~seed_costs,ternary,slope.test=0,method="OLS",log="x")
+mod_post_poll <- sma(post_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")
 
@@
 
-plot(per_seed~seedcosts,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seedcosts")
-points(per_poll~seedcosts,ternary,col="red",pch=16,cex=2)
-points(per_disp~seedcosts,ternary,col="blue",pch=16,cex=2)
+plot(per_seed~seed_costs,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seed_costs")
+points(per_poll~seed_costs,ternary,col="red",pch=16,cex=2)
+points(per_disp~seed_costs,ternary,col="blue",pch=16,cex=2)
 
@@
 
-plot(per_poll~seedcosts,ternary,col="black",log="x",pch=16,cex=2,ylim=c(0,100),ylab="prop of seedcosts")
-points(post_poll~seedcosts,ternary,col="red",pch=16,cex=2)
+plot(per_poll~seed_costs,ternary,col="black",log="x",pch=16,cex=2,ylim=c(0,100),ylab="prop of seed_costs")
+points(post_poll~seed_costs,ternary,col="red",pch=16,cex=2)
 abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="black",lwd=2)
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seedcosts.wmf", height=5, width=5)
+win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
 plot
@@
        size = 3) +
-  geom_point(size=sqrt(ternary$seedcosts/2),shape=20,color=col.spp()) +
+  geom_point(size=sqrt(ternary$seed_costs/2),shape=20,color=col.spp()) +
    theme_bw() + 
   theme_showarrows() +
-  geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seedcosts/500),size=2)
+  geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seed_costs/500),size=2)
 
@@
 ```{r}
-prop_seedcosts_spp <- dplyr::select(SummarySpp[["mean"]],species,seedcosts,prop_prepollencosts,prop_dispersalcosts,prop_seedcosts)
-prop_seedcosts_spp$species <- labels.spp.full()
-prop_seedcosts_spp <- format(prop_seedcosts_spp, digit=2)
-write.csv(prop_seedcosts_spp, file="figs2/Accessory_Costs/Table04_Prop_seedcosts_by_Species.csv",row.names=FALSE)
+prop_seed_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_costs,prop_prepollen_costs,prop_dispersalcosts,prop_seed_costs)
+prop_seed_costs_spp$species <- labels.spp.full()
+prop_seed_costs_spp <- format(prop_seed_costs_spp, digit=2)
+write.csv(prop_seed_costs_spp, file="figs2/Accessory_Costs/Table04_Prop_seed_costs_by_Species.csv",row.names=FALSE)
 ```
+$embryo_endo_size
 
@@
 
-plot(prepollencosts~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pre-pollination costs per seed (mg/seed)",xlab="",cex=1.5)
-#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollencosts,SummarySpp[["se"]]$prepollencosts)
-mod <- lm(log10(prepollencosts)~log10(seed_size),SummarySpp[["mean"]])
+plot(prepollen_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
+mod <- lm(log10(prepollen_costs)~log10(seed_size),SummarySpp[["mean"]])
 abline(coef(mod)[1],coef(mod)[2])
@@
 
-plot(packaging_dispersal_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="packaging and dispersal costs per seed (mg/seed)",xlab="",cex=1.5)
-#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollencosts)
-mod <- lm(log10(packaging_dispersal_per_seed)~log10(seed_size),SummarySpp[["mean"]])
+plot(postpollen_all_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollen_costs)
+mod <- lm(log10(postpollen_all_per_seed)~log10(seed_size),SummarySpp[["mean"]])
 abline(coef(mod)[1],coef(mod)[2])
@@
 mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
+dev.off()
+```
+
+#Figure 3 v2. Scaling of accessory costs versus weight of embryo + endosperm, by species
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure03_embryo_size_acc_cost_correlations.wmf", height=5, width=15)
+plot
+
+par(mfrow=c(1,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+options(scipen = 5)
+
+plot(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(accessory_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
+words.top.left.logxy(mod)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+
+plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
+mod <- lm(log10(prepollen_costs)~log10(embryo_endo_size),SummarySpp[["mean"]])
+words.top.left.logxy(mod)
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+
+plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollen_costs)
+mod <- lm(log10(postpollen_all_per_seed)~log10(embryo_endo_size),SummarySpp[["mean"]])
+words.top.left.logxy(mod)
+abline(coef(mod)[1],coef(mod)[2])
+abline(coef(mod)[1],1,col="red")
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+mtext(text="embryo + endosperm (mg)",side=1,line=1.5,outer=TRUE)
+
 dev.off()
@@
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-#abline(slopes$groupsummary["Int"][[1]],1,col="red")
-abline(0,1,col="red")
-words.bottom.right.logxy(mod)
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+words.bottom.left.logxy(mod)
 
@@
 
-plot(prepollencosts ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(prepollencosts) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
-words.bottom.right.logxy(mod)
-extra.topleft.logxy("slope <1, so bigger seeded species have lower fixed costs of making pre-pollination parts")
-slopes <- sma(prepollencosts ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+plot(prepollen_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
+mod <- lm(log10(prepollen_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
+words.bottom.left.logxy(mod)
+slopes <- sma(prepollen_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(prepollen_failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
-words.bottom.right.logxy(mod)
-extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
-slopes <- sma(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+plot(failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
+words.bottom.left.logxy(mod)
+slopes <- sma(failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
 abline(slopes$groupsummary["Int"][[1]],1,col="red")
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_failure_per_seed,SummarySpp[["se"]]$prepollen_failure_per_seed)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
 acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
@@
 
-plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
-words.top.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
-slopes <- sma(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+# plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
+# words.top.left.logxy(mod)
+# y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
+# slopes <- sma(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
+# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+# abline(slopes$groupsummary["Int"][[1]],1,col="red")
+# acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-plot(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(packaging_dispersal_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"))
+plot(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(pack_disp_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
 words.top.left.logxy(mod)
@@
 abline(slopes$groupsummary["Int"][[1]],1,col="red")
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
 acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
@@
 ```
-plot(prop_prepollen_all~seed_size,SummarySpp[["mean"]],pch=16,col=col.spp(species),log="x")
+
+#Table 3 v2. Slopes for various embryo size by acc cost regressions
+```{r}
+par(mfrow=c(2,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+options(scipen = 5)
+
+plot(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(accessory_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
+slopes <- sma(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+words.bottom.left.logxy(mod)
+
+acc_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
+
+plot(prepollen_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
+mod <- lm(log10(prepollen_costs) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
+words.bottom.left.logxy(mod)
+slopes <- sma(prepollen_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+plot(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(failure_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
+words.bottom.left.logxy(mod)
+slopes <- sma(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+plot(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(prepollen_all_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
+words.bottom.right.logxy(mod)
+slopes <- sma(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+# plot(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
+# words.top.left.logxy(mod)
+# y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
+# slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
+# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+# abline(slopes$groupsummary["Int"][[1]],1,col="red")
+# acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(pack_disp_costs) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
+words.top.left.logxy(mod)
+slopes <- sma(packaging_dispersal_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="LEES"),slope.test=1, log="xy",method="OLS")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+mtext(text="embryo + endosperm size (mg)",side=1,line=1.5,outer=TRUE)
+
+slopes <- sma(postpollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+acc_by_species$variable = c("total accessory costs","prepollen_success","failed_tissues","total prepollen","dispersal","total postpollen")
+
+write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_embryo_endo_size_slopes.csv",row.names=FALSE)
+```
 
@@
 sma_abline(mod)
-text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
-     paste("r2 = ",round(glance(mod)[1],2)),adj=1)
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
@@
 #species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
-plot(prop_prepollencosts~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.01,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
-mod <- sma(prop_prepollencosts~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
-y.error.bars(SummarySpp[["mean"]]$seedset,SummarySpp[["mean"]]$prop_prepollencosts,SummarySpp[["se"]]$prop_prepollencosts)
+plot(prop_prepollen_costs~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.01,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
+mod <- sma(prop_prepollen_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
+y.error.bars(SummarySpp[["mean"]]$seedset,SummarySpp[["mean"]]$prop_prepollen_costs,SummarySpp[["se"]]$prop_prepollen_costs)
 sma_abline(mod)
@@
 mod3 <- sma(scaled_failure_count~seed_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
+sma_abline(mod1)
+abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue")
+abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red")
+legend("topright",legend=c("seed count","total bud count","failed flower count"),col=c("black","blue","red"),pch=c(16,21,8),bty="n")
+
+dev.off()
+```
+
+#Figure 4, using embryo + endosperm
+```{r}
+
+win.metafile("figs2/Accessory_Costs/Figure04_cost_of_flowers_vs_embryo_endo_size.wmf", height=5, width=15)
+plot
+
+par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
+options(scipen = 4)
+
+plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,1000),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="seed size (mg)",ylab="seed set")
+mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
+sma_abline(mod)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
+legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")
+
+#species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
+plot(prop_prepollen_costs~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.01,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
+mod <- sma(prop_prepollen_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
+y.error.bars(SummarySpp[["mean"]]$seedset,SummarySpp[["mean"]]$prop_prepollen_costs,SummarySpp[["se"]]$prop_prepollen_costs)
+sma_abline(mod)
+sma_sum(mod)
+text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
+     paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
+axis(2, at=c(-0.2,0,.2,.4,.6,.8,1), labels=c("",0.0,0.2,0.4,0.6,0.8,""),cex.axis=1)
+
+#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
+plot(scaled_seed_count~embryo_endo_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="seed size (mg)",ylab="count, scaled to plant size")
+points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
+#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
+axis(2, at=c(0.000001,0.0001,0.01,1), labels=c(0.000001,0.0001,0.01,1),cex.axis=0.9)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
+
+mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
+mod2 <- sma(scaled_bud_count~embryo_endo_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
+mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
 sma_abline(mod1)
@@
 ```
-names(SummaryInd)
+
 ###GOOD VISUALS - not currently in manuscript
-
+```{r}
 xvar <- "leaf_area_0"
@@
 plot(seedset~prop_failure,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),log="xy",pch=16,col=col.spp(species))
-mod <- lm(log(seed_size)~log(total_weight_0),data=subset(SummarySpp[["mean"]])
+mod <- lm(log10(seed_size)~log10(total_weight_0),data=subset(SummarySpp[["mean"]]))
 summary(mod)
+```
 
@@
 par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
-plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
-mod <- lm(log10(seedset)~log10(seed_size),SummarySpp[["mean"]])
+plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
+mod <- lm(log10(seedset)~log10(embryo_endo_size),SummarySpp[["mean"]])
 abline(mod$coeff[1],mod$coeff[2])
 words.bottom.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
 ```
@@
 xvar <- "seedset"
-yvar <- "packaging_dispersal_per_seed"
+yvar <- "pack_disp_costs"
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 
-results$ovules_per_fruit <- c(60,4,1,1,2,2,2,4,1,40,2,1,2)
+results$ovules_per_fruit <- c(60,4,1,1,2,2,2,4,1,1,40,2,1,2)
 max_seedset <- select(SummarySpp[["max"]],species,seedset) 
@@
 write.csv(results, file="figs2/Accessory_Costs/TableXX_dispersal_vs_seedset.csv",row.names=FALSE)
-```
-
-#Considering the individual components of accessory costs vs. seedset - since seedset best predictor of accessory costs
-
-#For each species the accessory cost components that cause shifts in total accessory costs is different and reflects both which components are largest and whichvary most with some factor - seedset, age, etc.
-#CODE CURRENTLY DOESN"T WORK
-```{r}
-xvar1 <- "packaging_dispersal_per_seed"
-xvar2 <- "prepollencosts"
-xvar3 <- "postpollen_aborted_per_seed"
-xvar4 <- "prepollen_failure_per_seed"
-yvar <- "accessory_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar1]]>0&SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&SummaryInd[[xvar4]]>0&SummaryInd[[yvar]]>0&species!="BAER"&species!="COER"&species!="LEES")
-data <- split(data, data$species)
-
-mod <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar1]]))+(log10(x[[xvar2]]))+(log10(x[[xvar3]])+(log10(x[[xvar4]])))))
-mod_LEES <- lm(log10(accessory_per_seed) ~ (log10(prepollencosts)+(log10(postpollen_aborted_per_seed))+(log10(prepollen_failure_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0&species=="LEES"))
-mod_BAER <- lm(log10(accessory_per_seed) ~ (log10(prepollencosts)+(log10(packaging_dispersal_per_seed))+(log10(prepollen_failure_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="BAER"))
-mod_COER <- lm(log10(accessory_per_seed) ~ (log10(prepollencosts)+(log10(packaging_dispersal_per_seed))+(log10(prepollen_failure_per_seed))),data=subset(SummaryInd,SummaryInd[[xvar2]]>0&SummaryInd[[xvar1]]>0&species=="COER"))
-
-species_coef <- as.data.frame(c("intercept","packaging&dispersal","prepollencosts","postpollen_aborted_per_seed","pre-pollen failure per seed"))
-
-for(i in 1:11) {
-     species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[i]]$coefficients))
-     }
-
-names(species_coef) <- c("effect","BOLE","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")
-
-BAER_c <- as.data.frame(mod_BAER$coefficients)
-BAER_c$effect <- c("intercept","prepollencosts","packaging&dispersal","pre-pollen failure per seed")
-names(BAER_c) <- c("BAER","effect")
-species_coef <- dplyr::left_join(species_coef,BAER_c,by="effect")
-
-COER_c <- as.data.frame(mod_COER$coefficients)
-COER_c$effect <- c("intercept","prepollencosts","packaging&dispersal","pre-pollen failure per seed")
-names(COER_c) <- c("COER","effect")
-species_coef <- dplyr::left_join(species_coef,COER_c,by="effect")
-
-LEES_c <- as.data.frame(mod_LEES$coefficients)
-LEES_c$effect <- c("intercept","prepollencosts","postpollen_aborted_per_seed","pre-pollen failure per seed")
-names(LEES_c) <- c("LEES","effect")
-species_coef <- dplyr::left_join(species_coef,LEES_c,by="effect")
-
-# Reorder by column name
-species_coef <- species_coef[c("effect", "BAER", "BOLE", "COER", "EPMI", "GRBU", "GRSP", "HATE", "HEPU", "LEES", "PELA", "PEPU", "PHPH", "PILI", "PUTU")]
-
-write.csv(species_coef, file="figs2/Accessory_Costs/TableXX_accessory_components_coeff.csv",row.names=FALSE)
-
-species_t <- as.data.frame(c("intercept","packaging&dispersal","prepollencosts","postpollen_aborted_per_seed","pre-pollen failure per seed"))
-
-for(i in 1:11) {
-     species_t <- dplyr::bind_cols(species_t, as.data.frame(summary(mod[[i]])$coefficient[,4]))
-     }
-
-names(species_t) <- c("effect","BOLE","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")
-
-BAER_t <- as.data.frame(summary(mod_BAER)$coefficient[,4])
-BAER_t$effect <- c("intercept","prepollen_all_per_seed","packaging&dispersal")
-names(BAER_t) <- c("BAER","effect")
-species_t <- dplyr::left_join(species_t,BAER_t,by="effect")
-
-COER_t <- as.data.frame(summary(mod_COER)$coefficient[,4])
-COER_t$effect <- c("intercept","prepollen_all_per_seed","packaging&dispersal")
-names(COER_t) <- c("COER","effect")
-species_t <- dplyr::left_join(species_t,COER_t,by="effect")
-
-LEES_t <- as.data.frame(summary(mod_LEES)$coefficient[,4])
-LEES_t$effect <- c("intercept","prepollen_all_per_seed","postpollen_aborted_per_seed")
-names(LEES_t) <- c("LEES","effect")
-species_t <- dplyr::left_join(species_t,LEES_t,by="effect")
-
-# Reorder by column name
-species_t <- species_t[c("effect", "BAER", "BOLE", "COER", "EPMI", "GRBU", "GRSP", "HATE", "HEPU", "LEES", "PELA", "PEPU", "PHPH", "PILI", "PUTU")]
-
-write.csv(species_t, file="figs2/Accessory_Costs/TableXX_accessory_components_t-value.csv",row.names=FALSE)
-
-```
-
-```{r}
-plot.new()
-par(mfrow=c(2,3), cex=1, omi=c(.1,0.1,0.1,0.05), mai=c(.8,.8,.1,0.1))
-
-results <- as.data.frame(matrix(vector(), 0, 8,
-                dimnames=list(c(), c("variable","r2","pval","Slope","Slope_lowCI","Slope_highCI","Int","Slope_test_p"))),
-                stringsAsFactors=F)
-
-for (i in c("prop_propagule","prop_success","prop_dispersalcosts","prop_prepollencosts","prop_seedcosts")) {
-yvar <- i
-xvar <- "seed_size"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-data2 <- subset(SummarySpp[["mean"]])
-fit <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", log="x",slope=1)
-temp <- as.data.frame(c(yvar,select(fit$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Slope_test_p)))
-colnames(temp)[1]<- "variable"
-results <- bind_rows(results, temp)
-plot(data[[yvar]] ~ data[[xvar]],log="x",col=col.spp(data$species),pch=16,xlim=c(.01,500),ylim=c(.001,1.1))
-points(data2[[yvar]] ~ data2[[xvar]],col=col.spp(data2$species),pch=16,cex=2)
-}
-
-write.csv(results, file="figs2/Accessory_Costs/TableXX_prop_tissues_inv_by_seed_size.csv",row.names=FALSE) 
 ```

### 2016-05-19 R/ReproductionTissues.R

@@ -36,8 +36,66 @@ ReproductiveCosts <- function(species, IndividualsList, InvestmentCategories, sp
     sum(weights / counts,  na.rm = TRUE)
   }
 
+  # Identical format to f2, but returns a single column for prepollencosts. The total weight is standardised against the counts of
+  # a parts specified by the variable "prepollen_costs_scale"
+  # Takes as argument the individual
+  f3 <- function(i) {
+    # subset investment data by individual
+    df <- FD[FD$individual== i,]
+    # return 0 if there are 0 flowers produced
+    if(sum(df$count[df$part %in% c("flower_petals")], na.rm=TRUE) ==0) {
+      return(0)
+    }
+    weights <- df$weight[match(InvCat[["prepollen_costs"]], df$part)]
+    counts <- df$count[match(InvCat[["prepollen_costs_scale"]], df$part)]
+    sum(weights / counts,  na.rm = TRUE)
+  }
+  
+  f4 <- function(i) {
+    # subset investment data by individual
+    df <- FD[FD$individual== i,]
+    # return 0 if there are 0 seeds produced
+    if(sum(df$count[df$part %in% c("seed", "fruit_mature")], na.rm=TRUE) ==0) {
+      return(0)
+    }
+    weights <- df$weight[match(InvCat[["dispersal_costs"]], df$part)]
+    counts <- df$count[match(InvCat[["dispersal_costs_scale"]], df$part)]
+    sum(weights / counts,  na.rm = TRUE)
+  }
+  
+  f5 <- function(i) {
+    # subset investment data by individual
+    df <- FD[FD$individual== i,]
+    # return 0 if there are 0 flowers produced
+    if(sum(df$count[df$part %in% c("flower_petals")], na.rm=TRUE) ==0) {
+      return(0)
+    }
+    weights <- df$weight[match(InvCat[["dispersal_before_pollen_costs"]], df$part)]
+    counts <- df$count[match(InvCat[["dispersal_before_pollen_costs_scale"]], df$part)]
+    sum(weights / counts,  na.rm = TRUE)
+  }
+  
+
+  f6 <- function(i) {
+    # subset investment data by individual
+    df <- FD[FD$individual== i,]
+    # return 0 if there are 0 flowers produced
+    if(sum(df$count[df$part %in% c("flower_petals")], na.rm=TRUE) ==0) {
+      return(0)
+    }
[…]

### 2016-05-19 R/Summaries.R

@@ -1,95 +1,3 @@
-
-process_prepollination_costs <- function(seedSize_raw, PartsSummary_all) {
-
-
-  seedsize <- seedSize_raw %>%
-      select(species, seed_size)
- 
-# adding info on all costs to produce flower at time of pollination
-  prepollencosts_spp <- list()
-  prepollencosts_spp[["BAER"]] <- list(parts=c("cone_green","flower_petals","flower_stigma","flower_style"), scale=c(1/60,1/2,1/2,1/2))
-  prepollencosts_spp[["BOLE"]] <- list(parts=c("flower_petals","flower_calyx","pedicel"), scale=c(1/4,1/4,1/4))
-  prepollencosts_spp[["COER"]] <- list(parts=c("inflorescence_stalk","flower_petals", "flower_stigma"), scale=c(1/6,1,1))
-  prepollencosts_spp[["EPMI"]] <- list(parts=c("flower_petals", "flower_calyx"), scale=c(1/15,1/15))
-  prepollencosts_spp[["GRBU"]] <- list(parts=c("inflorescence_stalk","flower_petals","flower_stigma"), scale=c(1/20,1/2,1/2))
-  prepollencosts_spp[["GRSP"]] <- list(parts=c("inflorescence_stalk","flower_petals","flower_stigma"), scale=c(1/20,1/2,1/2))
-  prepollencosts_spp[["HATE"]] <- list(parts=c("inflorescence_bud_big_bracts","flower_petals","flower_stigma"), scale=c(1/2,1/2,1/2))
-  prepollencosts_spp[["HEPU"]] <- list(parts=c("flower_petals","flower_calyx"), scale=c(1/4,1/4))
-  prepollencosts_spp[["LEES"]] <- list(parts=c("flower_petals","flower_calyx"), scale=c(1,1))
-  prepollencosts_spp[["PELA"]] <- list(parts=c("flower_petals","pedicel","flower_stigma"), scale=c(1,1,1))
-  prepollencosts_spp[["PEPU"]] <- list(parts=c("cone_green","flower_petals","flower_calyx","flower_stigma"), scale=c(1/200,1,1,1))
-  prepollencosts_spp[["PHPH"]] <- list(parts=c("flower_petals","flower_calyx","bract_flower_or_finished_flower","flower_stigma"), scale=c(1/2,1/2,1/2,1/2))
[…]

### 2016-05-24 nutrient.Rmd
updating some endosperm + embryo weights preliminary analysis of nutrient data

nutrient <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/nutrient_data.csv")

names(nutrient)
unique(nutrient$tissue_simple)

plot(P~N,nutrient,col=col.spp(species),pch=16,log="xy")

par(mfrow=c(1,1), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
plot(P~K,data=subset(nutrient,tissue_complete=="leaves"),col=col.spp(species),pch=16,ylim=c(0,500),log="x",xlim=c(.02,1))
points(P~K,data=subset(nutrient,tissue_complete=="senescent_leaves"),col=col.spp(species),pch=1,cex=1.5)
points(P~K,data=subset(nutrient,tissue_complete=="senescent_leaves"),col=col.spp(species),pch=1,cex=1)

plot(P~K,data=subset(nutrient,tissue_complete=="wood_from_tip"),col=col.spp(species),pch=16,ylim=c(0,500),log="x",xlim=c(.01,1))
points(P~K,data=subset(nutrient,tissue_complete=="shed_sapwood"),col=col.spp(species),pch=1,cex=1.5)
points(P~K,data=subset(nutrient,tissue_complete=="shed_sapwood"),col=col.spp(species),pch=1,cex=1)

plot(P~N,data=subset(nutrient,tissue_complete=="leaves"),col=col.spp(species),pch=16,ylim=c(0,500),log="x",xlim=c(.4,2.5))
points(P~N,data=subset(nutrient,tissue_complete=="senescent_leaves"),col=col.spp(species),pch=1,cex=1.5)
points(P~N,data=subset(nutrient,tissue_complete=="senescent_leaves"),col=col.spp(species),pch=1,cex=1)

plot(P~N,data=subset(nutrient,tissue_complete=="wood_from_tip"),col=col.spp(species),pch=16,ylim=c(0,500),log="x",xlim=c(.02,1))
points(P~N,data=subset(nutrient,tissue_complete=="shed_sapwood"),col=col.spp(species),pch=1,cex=1.5)
points(P~N,data=subset(nutrient,tissue_complete=="shed_sapwood"),col=col.spp(species),pch=1,cex=1)

pch.tissue <- function(x=NULL){
  ret <- c(wood_from_tip=16, wood_from_middle=10,wood_from_base=7,shed_sapwood=1,bark=15,shed_bark=0,leaves=17,senescent_leaves=2,seed=8,reproductive=4)
  names(ret) <- c("wood_from_tip","wood_from_middle","wood_from_base","shed_sapwood","bark","shed_bark","leaves","senescent_leaves","seed","reproductive")
  if(!is.null(x)) {
    ret <- ret[as.character(x)]
  }
  ret
}

plot(P~N,data=subset(nutrient,tissue_simple=="leaves"),col=col.spp(species),pch=pch.tissue(tissue_simple))

pdf("figs2/Nutrients/N_vs_P.pdf", height=7.5, width=11)
plot
plot(P~N,data=subset(nutrient),col=col.spp(species),pch=pch.tissue(tissue_simple),log="xy")
legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
dev.off()

pdf("figs2/Nutrients/K_vs_P.pdf", height=7.5, width=11)
plot
plot(P~K,data=subset(nutrient),col=col.spp(species),pch=pch.tissue(tissue_simple),log="xy")
legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
dev.off()

pdf("figs2/Nutrients/C_vs_N.pdf", height=7.5, width=11)
plot
plot(C~N,data=subset(nutrient,C>25),col=col.spp(species),pch=pch.tissue(tissue_simple),log="xy")
legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
dev.off()

library(dplyr)

pdf("figs2/Nutrients/age_by_species_NP.pdf", height=7.5, width=11)
plot
for (i in c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")) {
data <- subset(nutrient,species==i)
plot(P~N,data,col=col.age(age),pch=pch.tissue(tissue_simple),log="xy")
text(1,200,i)
data2 <- subset(data,tissue_simple=="reproductive")
text(P~N,data2,label=data2$tissue_complete,col="red")
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
}
dev.off()

pdf("figs2/Nutrients/age_by_species_PK.pdf", height=7.5, width=11)
plot
for (i in c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")) {
data <- subset(nutrient,species==i)
plot(P~K,data,col=col.age(age),pch=pch.tissue(tissue_simple),log="xy")
text(.4,200,i)
data2 <- subset(data,tissue_simple=="reproductive")
text(P~K,data2,label=data2$tissue_complete,col="red")
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
}
dev.off()

View(data)

get_species_nutrient_values <- function(SummaryInd, groups) {

  # function to apply
  fs <- c("max", "min","mean", "sd", "length")

  # note use of `group_by_` below - allows for passing in of
  # character vectors
  dots <-  lapply(groups, as.symbol)

  # summarizing data by species, age
  out <- list()
  out[[1]] <-lapply(fs, function(f) {
    SummaryInd %>%
    group_by_(.dots=dots) %>%
    summarise_each(f, Al,B, Ca, Cu, Fe, K, Mg, Mn, Na, P, S, Zn, C, N)
  })
  names(out[[1]]) <- fs

 ret <- list()
  for(f in fs){
    ret[[f]] <- out[[1]][[f]]

    # reorder to be same as input
    order <- names(SummaryInd)[names(SummaryInd) %in% names(ret[[f]])]
    ret[[f]] <- ret[[f]][, order]
  }
  ret[["se"]] <- ret[["sd"]]
  ii <- sapply(ret[["se"]], is.numeric) & names(ret[["se"]]) != "age"
  ret[["se"]][,ii] <- ret[["se"]][,ii]/sqrt(ret[["length"]][,ii])
  ret
}

nutrient_sum <- get_species_nutrient_values(nutrient, groups=I(c("species", "age", "tissue_complete")))

View(nutrient_sum)

### 2016-05-24 scripts/Accessory_figs_20160218.Rmd
updating some endosperm + embryo weights preliminary analysis of nutrient data

@@
 ```
-$embryo_endo_size
 
@@
 plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollen_costs)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
 mod <- lm(log10(postpollen_all_per_seed)~log10(embryo_endo_size),SummarySpp[["mean"]])
@@
 
-# plot(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
-# words.top.left.logxy(mod)
-# y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
-# slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
-# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-# abline(slopes$groupsummary["Int"][[1]],1,col="red")
-# acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
 plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
@@
 ```{r}
-
 win.metafile("figs2/Accessory_Costs/Figure04_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)

### 2016-05-25 nutrient.Rmd
add soils data

@@
 nutrient <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/nutrient_data.csv")
+soil <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/nutrient_soil.csv")
 
+plot(N~P,soil,col=col.age(age),pch=16,cex=replicate)
+
+names(soil)
 names(nutrient)

### 2016-05-26 nutrient.Rmd
nutrient data plots

@@
 
+pdf("figs2/Nutrients/soil.pdf", height=6, width=6)
+plot
 plot(N~P,soil,col=col.age(age),pch=16,cex=replicate)
+dev.off()
 
@@
 plot
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.05,.05)) 
 for (i in c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")) {
@@
 data2 <- subset(data,tissue_simple=="reproductive")
-text(P~N,data2,label=data2$tissue_complete,col="red")
+text(P~N,data2,label=data2$tissue_complete,col="red",cex=0.7)
 legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
 legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
+
+plot(P~K,data,col=col.age(age),pch=pch.tissue(tissue_simple),log="xy")
+text(.4,200,i)
+data2 <- subset(data,tissue_simple=="reproductive")
+text(P~K,data2,label=data2$tissue_complete,col="red",cex=0.7)
+#legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
+#legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
 }

### 2016-05-26 scripts/Accessory_figs_20160218.Rmd
correcting "dispersal costs to the point of pollination"

@@
+plot(pack_disp_gross_costs ~pack_disp_early_costs, SummaryInd,log="xy",col=col.spp(species),pch=16)
+
 #ideas in progress
@@
 
-plot(postpollen_all_per_seed~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
+plot(pack_disp_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
 #y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollen_costs)
@@
 words.top.left.logxy(mod)
-slopes <- sma(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="LEES"),slope.test=1, log="xy",method="OLS")
+slopes <- sma(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="EPMI"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
 mod <- lm(log10(pack_disp_costs) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
 words.top.left.logxy(mod)
-slopes <- sma(packaging_dispersal_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="LEES"),slope.test=1, log="xy",method="OLS")
+slopes <- sma(packaging_dispersal_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="EPMI"),slope.test=1, log="xy",method="OLS")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])

### 2016-06-01 scripts/Accessory_figs_20160218.Rmd
work on accessory figs

@@
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seed_costs,prop_success, prepollen_costs,packaging_dispersal_per_seed,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seed_costs,prop_success, prepollen_costs,pack_disp_costs,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
 acc_costs_spp$species <- labels.spp.full()
@@
 ```{r}
-ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs_corr)
-ternary$pack_disp_costs_corr[9] <- 0.1
+ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs,seed_costs)
+ternary$seed_costs = ternary$seed_size + ternary$prepollen_costs + ternary$pack_disp_costs
 
-ternary$seed_costs = ternary$seed_size + ternary$prepollen_costs + ternary$pack_disp_costs_corr
 ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
@@
 
-#Figure 3. Scaling of accessory costs versus seed size, by species
+#Figure 4. Scaling of accessory costs versus seed size, by species
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure03_seed_size_acc_cost_correlations.wmf", height=5, width=15)
+win.metafile("figs2/Accessory_Costs/Figure04_seed_size_acc_cost_correlations.wmf", height=5, width=15)
 plot
@@
 plot(pack_disp_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
-#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$packaging_dispersal_per_seed,SummarySpp[["se"]]$prepollen_costs)
+#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$prepollen_costs)
 mod <- lm(log10(postpollen_all_per_seed)~log10(seed_size),SummarySpp[["mean"]])
@@
 
-#Figure 3 v2. Scaling of accessory costs versus weight of embryo + endosperm, by species
+#Figure 4 v2. Scaling of accessory costs versus weight of embryo + endosperm, by species
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure03_embryo_size_acc_cost_correlations.wmf", height=5, width=15)
+win.metafile("figs2/Accessory_Costs/Figure04_embryo_size_acc_cost_correlations.wmf", height=5, width=15)
 plot
@@
 words.top.left.logxy(mod)
-slopes <- sma(packaging_dispersal_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+slopes <- sma(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="EPMI"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
 mod <- lm(log10(pack_disp_costs) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
 words.top.left.logxy(mod)
-slopes <- sma(packaging_dispersal_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="EPMI"),slope.test=1, log="xy",method="OLS")
+slopes <- sma(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-#Figure 4 seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
+#Figure 5 seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure04_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
+win.metafile("figs2/Accessory_Costs/Figure05_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
 plot
@@
 
-#Figure 4, using embryo + endosperm
+#Figure 5, using embryo + endosperm
 ```{r}
 
-win.metafile("figs2/Accessory_Costs/Figure04_cost_of_flowers_vs_embryo_endo_size.wmf", height=5, width=15)
+win.metafile("figs2/Accessory_Costs/Figure05_cost_of_flowers_vs_embryo_endo_size.wmf", height=5, width=15)
 plot
@@
 
-plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,1000),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="seed size (mg)",ylab="seed set")
+plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,100),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="embryo + endosperm size (mg)",ylab="seed set")
 mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+text((10^(0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),(10^(0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
+     paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
 axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
@@
 #put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
-plot(scaled_seed_count~embryo_endo_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="seed size (mg)",ylab="count, scaled to plant size")
+plot(scaled_seed_count~embryo_endo_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,100),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="embryo + endosperm size (mg)",ylab="count, scaled to plant size")
 points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))

### 2016-06-01 scripts/Accessory_figs_20160218.Rmd
figuring out why early dispersal costs are underestimated

@@
 ```
+
+check <- subset(SummarySpp[["mean"]],species=="HEPU")
+check$seed_size
+check$embryo_endo_size
+check$seed_costs
+check$prepollen_costs
+check$pack_disp_costs
+check$pack_disp_costs_plus
+check$pack_disp_early_costs
+check$seed_early_costs
+
+parts <- subset(PartsSummary,species=="HEPU")
+parts
+
+invest <- subset(InvestmentByPart,species=="HEPU"&part=="flower_calyx")
 

### 2016-06-01 R/Summaries.R

@@ -128,8 +128,10 @@ combine_by_individual <- function(IndividualsList, Growth_all, Accessory_counts_
     RA_leaf_area = repro_inv / (repro_inv + growth_leaf),
     leaf_area_midyear = (leaf_area_0 + leaf_area)/2,
     count_aborted = repro_all_count - seed_count,
+    seed_minus_embryo_endo = seed_size - embryo_endo_size,
     prepollen_costs = prepollen_partial_costs + pack_disp_early_costs,
     pack_disp_costs = pack_disp_gross_costs - pack_disp_early_costs - seed_early_costs,  #subtract early
+    pack_disp_costs_plus = pack_disp_costs + seed_minus_embryo_endo,
     prepollen_all_inv = prepollen_aborted_inv + prepollen_success_inv, #prepollen_success_inv is also flowers, so much bigger than investment in flowers that become seeds
     prepollen_failure_inv = prepollen_all_inv - (seed_count*prepollen_costs), #failure is all parts that don't progress to seeds; aborted is parts that don't reach flowering
     postpollen_all_inv = postpollen_aborted_inv + packaging_dispersal_inv,
@@ -181,11 +183,11 @@ combine_by_individual <- function(IndividualsList, Growth_all, Accessory_counts_
   for(v in c("seed_costs","prepollen_costs","count_aborted","flower_inv","fruit_inv","prepollen_all_inv","prepollen_success_inv",
               "prepollen_failure_inv","repro_inv_per_seed","accessory_per_seed","propagule_per_seed","prepollen_all_per_seed",
               "prepollen_aborted_per_seed","prepollen_failure_per_seed", "pack_disp_costs",
-              "prepollen_success_per_seed","postpollen_aborted_per_seed",
+              "prepollen_success_per_seed","postpollen_aborted_per_seed","pack_disp_early_costs", "seed_early_costs",
               "packaging_dispersal_per_seed","success_inv","failure_inv","failure_to_ovule_ratio","prop_success","prop_failure",
               "prop_propagule","prop_postpollen_aborted","prop_prepollen_success","prop_prepollen_aborted","prop_prepollen_all",
               "prop_accessory","prop_propagule_nonzero","prop_accessory_nonzero","prop_prepollen_costs","prop_seed_costs",
[…]

### 2016-06-02 scripts/Accessory_figs_20160218.Rmd
continuing to fix problems with seedcosts

--- 2016-06-01 scripts/Accessory_figs_20160218.Rmd
@@
 ```
+
+check <- subset(SummarySpp[["mean"]],species=="BOLE")
+check$seed_size
+check$embryo_endo_size
+check$seed_costs
+check$prepollen_costs
+check$pack_disp_costs
+check$pack_disp_costs_plus
+check$pack_disp_early_costs
+check$seed_early_costs
+
+parts <- subset(PartsSummary,species=="COER")
+parts
+
+invest <- subset(InvestmentByPart,species=="COER"&part=="flower_petals")
+invest
+
+invest_ind <- subset(InvestmentByPart,individual=="BOLE_154")
+
+ind <- subset(SummaryInd, species=="COER"&seed_count>0)
+check3 <- select(ind,individual,prepollen_costs,seed_early_costs,prepollen_costs,pack_disp_costs,pack_disp_early_costs,propagule_per_seed,seed_costs)
+
+View(check3)
 

### 2016-06-06 scripts/Accessory_figs_20160218.Rmd
testing seedcost categories to make sure no unexpected zeros

--- 2016-06-01 scripts/Accessory_figs_20160218.Rmd
@@
 ```
+
+#fixed = BOLE, GRBU, PUTU,
+
+#nearly fixed = EPMI, PELA, LEES
+check <- subset(SummarySpp[["mean"]],species=="BOLE")
+check$seed_size
+check$embryo_endo_size
+check$seed_costs
+check$prepollen_costs
+check$pack_disp_costs
+check$pack_disp_costs_plus
+check$pack_disp_early_costs
+check$seed_early_costs
+
+parts <- subset(PartsSummary,species=="COER")
+parts
+
+invest <- subset(InvestmentByPart,species=="PUTU"&part=="flower_petals")
+invest
+
+invest_ind <- subset(InvestmentByPart,individual=="PUTU_152")
+
+ind <- subset(SummaryInd, species=="GRBU"&seed_count>0)
+check3 <- select(ind,individual,prepollen_costs,seed_early_costs,prepollen_costs,pack_disp_costs,pack_disp_early_costs,propagule_per_seed,seed_costs)
+
+View(check3)
+
+plot(seed_costs ~pack_disp_costs,check3)
+points(seed_costs ~ propagule_per_seed,check3,col="red",pch=16)
+text(seed_costs ~pack_disp_costs,check3,label=individual)
 

### 2016-06-07 scripts/Accessory_figs_20160218.Rmd
small changes to accessory costs figures

@@
 
-#Figure 2. Ternary diagram showing seed_costs
+#Figure 3. Ternary diagram showing seed_costs
 ```{r}
@@
 
-#Figure 2 continued
+#Figure 3 continued
 ```{r}
@@
 plot(pack_disp_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
-#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$prepollen_costs)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
 mod <- lm(log10(postpollen_all_per_seed)~log10(seed_size),SummarySpp[["mean"]])
@@
 
-#fixed = BOLE, GRBU, PUTU,
-
-#nearly fixed = EPMI, PELA, LEES
+#fixed = BAER, BOLE, EPMI, GRBU, GRSP, HATE, HEPU, LEES, PEPU, PELA, PHPH, PUTU
+
+#nearly fixed = PILI
 check <- subset(SummarySpp[["mean"]],species=="BOLE")
@@
 
-invest_ind <- subset(InvestmentByPart,individual=="PUTU_152")
-
-ind <- subset(SummaryInd, species=="GRBU"&seed_count>0)
-check3 <- select(ind,individual,prepollen_costs,seed_early_costs,prepollen_costs,pack_disp_costs,pack_disp_early_costs,propagule_per_seed,seed_costs)
+invest_ind <- subset(InvestmentByPart,individual=="GRSP_802" & (part=="inflorescence_stalk"| part=="inflorescence_stalk_in_fruit"))
+invest_ind
+weight_total <- sum(invest_ind$weight)
+weight_total
+count2 <- sum(invest_ind$count)
+
+invest_ind2 <- subset(InvestmentByPart,individual=="COER_807")
+invest_ind2
+count_total <- sum(invest_ind2$count)
+count_total
+
+0.7*weight_total/count_total
+
+ind <- subset(SummaryInd, species=="PUTU"&seed_costs>0)
+check3 <- select(ind,individual,prepollen_costs,seed_early_costs,prepollen_costs,pack_disp_costs,pack_disp_gross_costs,pack_disp_early_costs,propagule_per_seed,seed_costs,seed_count,propagule_inv)
 

### 2016-06-15 scripts/Accessory_figs_20160218.Rmd
lots of cleaning of accessory figs file
broke ternary plotting by installing updated package!

@@
-plot(pack_disp_gross_costs ~pack_disp_early_costs, SummaryInd,log="xy",col=col.spp(species),pch=16)
-
-#ideas in progress
-``` {r}
-plot(prop_prepollen_all~seed_size,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species))
-mod <- sma(propagule_inv~seed_size,data=subset(SummarySpp[["mean"]],species!="EPMI"), log="xy",slope=1, method="OLS")
-summary(mod)
-
-par(mfrow=c(1,2), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
-options(scipen = 5)
-plot(repro_all_count~total_weight,SummaryInd,pch=16,log="xy",col=col.spp(species))
-mod <- sma(repro_all_count~total_weight,data=subset(SummaryInd,species!="EPMI"), log="xy",slope=1, method="OLS")
-summary(mod)
-
-plot(prop_prepollen_success~age,SummaryInd,pch=16,log="xy",col=col.spp(species))
-
-yvar <- "accessory_per_seed"
-xvar <- "age"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>2&SummaryInd[[yvar]]>0&SummaryInd[[yvar]]<40000)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope=1)
-results <- lines(fit$groupsummary)
-results
-plot(fit,col=col.spp(fit$groupsummary$group),log="xy",lty=results$linetype,pch=16,xlab=xvar,ylab=yvar)
-
-mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
-abline(0,1)
-
-SummaryInd$flower_seed_inv <- SummaryInd$propagule_inv + SummaryInd$flower_inv
-SummaryInd$prop_post <- SummaryInd$prop_packaging_dispersal + SummaryInd$prop_propagule
-plot(flower_seed_inv~repro_inv,SummaryInd,pch=16,log="xy",col=col.spp(species))
-mod <- lm(log(flower_inv)~log(repro_inv),subset(SummaryInd,flower_seed_inv>0))
-summary(mod)
-
-plot(propagule_inv~leaf_area_0,SummaryInd,pch=16,log="xy",col=col.spp(species))
-
-plot(prop_failure~seedset,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),pch=16,log="",col=col.spp(species))
-mod <- lm(prop_failure~seedset,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"))
-summary(mod)
-```
-
-#Discussion or Appendix: proportion energy to prepollen tissues decreases with plant age
-```{r}
-yvar <- "accessory_per_seed"
-xvar <- "age"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>2&SummaryInd[[yvar]]>0&SummaryInd[[yvar]]<1)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="x",slope=1)
-results <- lines(fit$groupsummary)
-results
-plot(fit,col=col.spp(fit$groupsummary$group),log="x",lty=results$linetype,pch=16,xlab=xvar,ylab=yvar)
-````
-
 #Data 0. means, counts to include in manuscript
 ```{r}
+#number of plants in study
 count(SummaryInd)
+
+#number of reproducing individuals in study
+count(subset(SummaryInd,repro_inv>0))
+
+#number of individuals in study that produce seed
 count(subset(SummaryInd,seed_count>0))
-count(subset(SummaryInd,repro_inv>0))
+
+#average proportion energy going to failed tissues (among reproducing individuals)
 mean(subset(SummaryInd$prop_failure,SummaryInd$prop_failure>0))
+
+#average proportion of energy going to accessory costs (based on propagules, not seeds) (among individuals that produce seed)
 mean(subset(SummaryInd$prop_accessory,SummaryInd$seed_count>0))
 
+#relationship between plant weight and number of ovules initiated - bigger plants produce proportionally fewer buds
 mod <- sma(repro_all_count~total_weight,SummaryInd,method="OLS",log="xy",slope=1)
@@
 
+#there is no relationship between the proportion of energy going to seeds and the total energy for seedcosts
 mod <- lm(log10(seed_costs) ~prop_seed_costs,SummarySpp[["mean"]])
@@
 
-mod <- lm(log10(seed_costs) ~prop_prepollen_costs,SummarySpp[["mean"]])
+#seed size by propagule investment - all species
+mod <- sma(propagule_inv ~ embryo_endo_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
 summary(mod)
-
-mod <- lm(log10(seed_costs) ~prop_dispersalcosts,SummarySpp[["mean"]])
-summary(mod)
-
-#seed size by propagule investment - all species
-mod <- sma(propagule_inv ~ seed_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
-summary(mod)
-plot(propagule_inv ~ seed_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(propagule_inv ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
 #seed size by propagule investment - without EPMI
-mod <- sma(propagule_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="OLS", log="xy",slope.test=1)
+mod <- sma(propagule_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="OLS", log="xy",slope.test=1)
 summary(mod)
-plot(propagule_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
+plot(propagule_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
 
 #seed size by reproductive investment - all species
-mod <- sma(repro_inv ~ seed_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
+mod <- sma(repro_inv ~ embryo_endo_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
 summary(mod)
-plot(repro_inv ~ seed_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(repro_inv ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
 #seed size by reproductive investment - without EPMI
-mod <- sma(repro_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="OLS", log="xy",slope.test=1)
+mod <- sma(repro_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="OLS", log="xy",slope.test=1)
 summary(mod)
-plot(repro_inv ~ seed_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
+plot(repro_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
 
-#seed size by reproductive investment - all species
-mod <- sma(total_weight_0 ~ seed_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
+#seed size by total weight - all species
+mod <- sma(total_weight_0 ~ embryo_endo_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
 summary(mod)
-plot(total_weight_0 ~ seed_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(total_weight_0 ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
 results <- lines(fit$groupsummary)
-plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
+plot(fit,xlab=xvar,ylab=yvar,pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
 results
@@
 results <- lines(fit$groupsummary)
-plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
+plot(fit,xlab=xvar,ylab=yvar,pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
 results
@@
 results <- lines(fit$groupsummary)
-plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
+plot(fit,xlab=xvar,ylab=yvar,pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
 results
 
-mod <- lm(log10(leaf_area_0)~log10(propagule_inv),data=subset(SummaryInd,leaf_area_0>0&propagule_inv>0))
-summary(mod)
-mod <- lm(log10(leaf_area_0)~log10(propagule_inv),SummarySpp[["mean"]])
-summary(mod)
+xvar <- "propagule_inv"
+yvar <- "repro_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-plot(leaf_area_0_mature~propagule_inv,SummarySppAge[["mean"]],log="xy",cex=1.5,pch=16,col=col.spp(species))
-points(leaf_area~propagule_inv,SummaryInd,pch=16,col=col.spp(species))
-mod <- lm(log10(leaf_area_0_mature)~log10(propagule_inv),SummarySppAge[["mean"]])
-summary(mod)
-mod <- lm(log10(leaf_area_0_mature)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0&leaf_area>0))
-summary(mod)
-
-plot(leaf_area_0_mature~propagule_inv,SummarySppAge[["mean"]],log="xy",cex=1.5,pch=16,col=col.spp(species))
-
-plot(repro_inv~propagule_inv,SummaryInd,pch=16,col=col.spp(species),log="xy")
-mod <- lm(log10(repro_inv_mature)~log10(propagule_inv),SummarySppAge[["mean"]])
-summary(mod)
-mod <- lm(log10(repro_inv_mature)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0&repro_inv>0))
-summary(mod)
-
-plot(repro_all_count_mature~seed_count,SummarySppAge[["mean"]],log="xy",cex=1.5,pch=16,col=col.spp(species))
-mod <- lm(log10(total_weight)~log10(seedset),SummarySppAge[["mean"]])
-
-mod <- lm(log10(leaf_area_0_mature)~log10(propagule_inv),SummarySpp[["mean"]])
-summary(mod)
-mod <- lm(log10(repro_inv_mature)~log10(propagule_inv),SummarySpp[["mean"]])
-summary(mod)
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
+results <- lines(fit$groupsummary)
+plot(fit,xlab=xvar,ylab=yvar,pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
+results
 ```
@@
 ```{r}
-ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs,seed_costs)
-ternary$seed_costs = ternary$seed_size + ternary$prepollen_costs + ternary$pack_disp_costs
-
+ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs,seed_costs,embryo_endo_size)
 ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
 ternary$post_poll <- 100-ternary$per_poll
-ternary$per_seed <-100*ternary$seed_size/ternary$seed_costs
+ternary$per_seed <-100*ternary$embryo_endo_size/ternary$seed_costs
 ternary$per_disp <-100*ternary$pack_disp_costs/ternary$seed_costs
@@
 
-win.metafile("figs2/Accessory_Costs/FigureXX_prepoll_vs_postpoll.wmf", height=6, width=6)
-plot
-
-plot(per_poll~seed_costs,ternary,col="black",log="x",pch=16,cex=2,ylim=c(0,100),ylab="prop of seed_costs")
-points(post_poll~seed_costs,ternary,col="red",pch=16,cex=2)
-abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="black",lwd=2)
-abline(mod_post_poll$groupsummary["Int"][[1]],mod_post_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
-summary(mod_post_poll)
-
-abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
-abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
-abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
-legend("topleft",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
-dev.off()
-```
-
-#Figure 3 continued
-```{r}
 win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
@@
 ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
-  labs(y = "seed",
+  labs(y = "embryo+endosperm",
        x = "pre-poll",
        z = "pack&disp",
-       Tarrow = "seed weight (%)",
+       Tarrow = "embryo + endosperm weight (%)",
        Larrow = "pre-pollination costs (%)",
@@
 ```{r}
-prop_seed_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_costs,prop_prepollen_costs,prop_dispersalcosts,prop_seed_costs)
+prop_seed_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_costs,prop_prepollen_costs,prop_dispersal_costs,prop_seed_costs)
 prop_seed_costs_spp$species <- labels.spp.full()
@@
 
-#fixed = BAER, BOLE, EPMI, GRBU, GRSP, HATE, HEPU, LEES, PEPU, PELA, PHPH, PUTU
-
-#nearly fixed = PILI
-check <- subset(SummarySpp[["mean"]],species=="BOLE")
-check$seed_size
-check$embryo_endo_size
-check$seed_costs
-check$prepollen_costs
-check$pack_disp_costs
-check$pack_disp_costs_plus
-check$pack_disp_early_costs
-check$seed_early_costs
-
-parts <- subset(PartsSummary,species=="COER")
-parts
-
-invest <- subset(InvestmentByPart,species=="PUTU"&part=="flower_petals")
-invest
-
-invest_ind <- subset(InvestmentByPart,individual=="GRSP_802" & (part=="inflorescence_stalk"| part=="inflorescence_stalk_in_fruit"))
-invest_ind
-weight_total <- sum(invest_ind$weight)
-weight_total
-count2 <- sum(invest_ind$count)
-
-invest_ind2 <- subset(InvestmentByPart,individual=="COER_807")
-invest_ind2
-count_total <- sum(invest_ind2$count)
-count_total
-
-0.7*weight_total/count_total
-
-ind <- subset(SummaryInd, species=="PUTU"&seed_costs>0)
-check3 <- select(ind,individual,prepollen_costs,seed_early_costs,prepollen_costs,pack_disp_costs,pack_disp_gross_costs,pack_disp_early_costs,propagule_per_seed,seed_costs,seed_count,propagule_inv)
-
-View(check3)
-
-  plot(seed_costs ~pack_disp_costs,check3)
-points(seed_costs ~ propagule_per_seed,check3,col="red",pch=16)
-text(seed_costs ~pack_disp_costs,check3,label=individual)
-
 #Figure 5 seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
@@
 
-plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,100),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="embryo + endosperm size (mg)",ylab="seed set")
+plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,100),ylim=c(.004,.3),cex=1.5,xaxt="n",xlab="embryo + endosperm size (mg)",ylab="seed set")
 mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
-text((10^(0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),(10^(0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
+text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.98*(par("usr")[4]-par("usr")[3])+par("usr")[3])),
      paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
@@
 #species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
-plot(prop_prepollen_costs~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.01,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
+plot(prop_prepollen_costs~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.004,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
 mod <- sma(prop_prepollen_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
@@
 xvar <- "diameter_0"
-yvar <- "seed_inv"
+yvar <- "propagule_inv"
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,yaxt="n")
-points((repro_inv)~(diameter_0),SummarySpp[["mean"]],cex=2,col=col.spp(species),pch=16)
+points((propagule_inv)~(diameter_0),SummarySpp[["mean"]],cex=2,col=col.spp(species),pch=16)
 
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/FigureXX_seedcount_reprocount.wmf", height=5, width=5)
+Cairo("figs2/Accessory_Costs/FigureXX_seedcount_reprocount.svg", height=5, width=5,type="svg",pointsize=10,units="in")
+#win.metafile("figs2/Accessory_Costs/FigureXX_seedcount_reprocount.wmf", height=5, width=5)
+
 plot
@@
 
-xvar <- "prepollen_all_count"
+xvar <- "repro_all_count"
 yvar <- "seed_count"
@@
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope=1)
 results <- lines(fit$groupsummary)
@@
 
+select(results,group,n,r2,pval,Slope,Slope_test_p)
 abline(0,1,lwd=2)
@@
 
+#Although very little energy goes into propagules (or embryos) a notable amount of energy is required for successful seeds to form
 ```{r}
@@
 
-#EXTRAS - not in manuscript
 #Neither within nor across species, does the proportion of reproductive energy spent on "success" correlate with total reproductive investment
 ```{r}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.05))
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(1.2,1.2,.1,.05))
 
@@
 results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),xlab="",ylab="",lty=results$linetype,pch=16,log="x")
+plot(fit,col=col.spp(fit$groupsummary$group),xlab=xvar,ylab=yvar,lty=results$linetype,pch=16,log="x")
 ```
 
-#when reproductive investment is scaled by leaf area there is no significant difference by seed size - so increase in repro inv with seed size simply because species with bigger seeds are bigger plants
+#when reproductive investment is scaled by plant size there is no significant difference by seed size - so increase in repro inv with seed size simply because species with bigger seeds are bigger plants
 ```{r}
@@
 
-#Consider how accessory cost components shift in terms of costs per seed, and cost as fraction total reproductive investment
-```{r}
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
-
-plot(repro_inv~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
-mod <- lm(log10(repro_inv)~log10(seed_size),SummarySpp[["mean"]])
-abline(mod$coeff[1],mod$coeff[2])
-words.top.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$repro_inv,SummarySpp[["se"]]$repro_inv)
-
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.05), mai=c(.8,.8,.1,.1))
-plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
-mod <- lm(log10(seedset)~log10(embryo_endo_size),SummarySpp[["mean"]])
-abline(mod$coeff[1],mod$coeff[2])
-words.bottom.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
-```
-
 #This effect is true across species, since larger-seeded species produce fewer seeds and have higher per seed accessory costs and true within species, since absolute accessory investment is a function of plant size not seedset
@@
 
-par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,.1), mai=c(1,1,.5,.5))
 
@@
 ```
-
-#propagule investment instead of seed_count. Could also replace with seedset
-```{r}
-win.metafile("figs2/Accessory_Costs/FigureXX_acc_cost_by_seedset.wmf", height=9, width=9)
-plot
-
-par(mfrow=c(2,2), cex=1, omi=c(.5,.1,.1,.1), mai=c(.1,1,.3,.1))
-
-xvar <- "seedset"
-yvar <- "accessory_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="total accessory costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000),xaxt="n")
-legend_with_r2(results,"bottomleft")
-
-write.csv(results, file="figs2/Accessory_Costs/TableXX_seedset_vs_accessory.csv",row.names=FALSE)
-
-xvar <- "seedset"
-yvar <- "prepollen_all_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab="pre-pollination costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000),xaxt="n")
-legend_with_r2(results,"bottomleft")
-
-write.csv(results, file="figs2/Accessory_Costs/TableXX_prepollen_all_per_seed_vs_seedset.csv",row.names=FALSE)
-
-xvar <- "seedset"
-yvar <- "postpollen_aborted_per_seed"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy") 
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab="aborted post pollination costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000))
-legend_with_r2(results,"bottomleft")
-
-write.csv(results, file="figs2/Accessory_Costs/TableXX_postpollen_aborted_per_seed_vs_seedset.csv",row.names=FALSE)
-
-xvar <- "seedset"
-yvar <- "pack_disp_costs"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab=yvar,lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000))
-legend_with_r2(results,"bottomleft")
-mtext(text="seedset",side=1,line=1.5,outer=TRUE)
-
-dev.off()
-```
-
-```{r}
-xvar <- "seedset"
-yvar <- "pack_disp_costs"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-
-results <- select(results,group,r2,Slope)
-names(results) <- c("species","r2","slope")
-
-results$ovules_per_fruit <- c(60,4,1,1,2,2,2,4,1,1,40,2,1,2)
-max_seedset <- select(SummarySpp[["max"]],species,seedset) 
-min_seedset <- select(SummarySpp[["min"]],species,seedset) 
-results <- merge(results, max_seedset, by=c("species"), all=TRUE)
-results <- merge(results, min_seedset, by=c("species"), all=TRUE)
-names(results)=c("species","r2","slope","ovules_per_fruit","max_seedset","min_seedset")
-
-win.metafile("figs2/Accessory_Costs/FigureXX_dispcosts_vs_ovules.wmf", height=6, width=6)
-plot
-
-par(mfrow=c(1,1), cex=1, omi=c(.4,.4,.1,.1), mai=c(.8,.8,.2,.2)) 
-plot(ovules_per_fruit~r2,data=subset(results),log="y",col=col.spp(species),pch=16,cex=2,ylab="ovules per flower",xlab="slope between dispersal costs and seedset")
-mod <- lm(log10(ovules_per_fruit)~r2,data=subset(results,species!="PELA"))
-abline(mod$coeff[1],mod$coeff[2])
-words.top.left.logy(mod)
-dev.off()
-
-write.csv(results, file="figs2/Accessory_Costs/TableXX_dispersal_vs_seedset.csv",row.names=FALSE)
-```
-
-#looking at how the slopes of the relationship between accessory investment and propagule investment shift across species 
-##slopes only statistically different from 1 in 2 species
-##intercepts quite variable - means that the "baseline" accessory investment, before you get any propagules varies
-```{r}
-par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1)) 
-plot(propagule_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0&propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlab="total accessory investment (mg)",ylab="total propagule investment (mg)")
-slope_check <- sma(log10(propagule_inv)~ log10(accessory_inv),data=subset(SummaryInd,propagule_inv>0))
-summary(slope_check)
-
-data <- select(SummaryInd,species,propagule_inv,accessory_inv)
-data <- subset(data,propagule_inv>0)
-data <- split(data, data$species)
-
-for(i in 1:14) {
-slope_check <- sma(log10(propagule_inv)~ log10(accessory_inv),data[[i]],slope.test=1)
-summary(slope_check)
-}
-
-xvar <- "accessory_inv"
-yvar <- "propagule_inv"
-
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
-```

### 2016-06-16 scripts/Accessory_figs_20160218.Rmd
polishing up figures for manuscript

@@
 ```{r}
-ternary <- select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs,seed_costs,embryo_endo_size)
+ternary <- dplyr::select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs,seed_costs,embryo_endo_size)
 ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
@@
 costs_per_seed <- as.data.frame("costs for seed (%)")
-costs_per_seed <- cbind(costs_per_seed,select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+costs_per_seed <- cbind(costs_per_seed,dplyr::select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
 names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
@@
 costs_per_seed2 <- as.data.frame("costs for pre-pollination (%)")
-costs_per_seed2 <- cbind(costs_per_seed2,select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
 names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
@@
 costs_per_seed2 <- as.data.frame("costs for dispersal (%)")
-costs_per_seed2 <- cbind(costs_per_seed2,select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
 names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
@@
 abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
-legend("topleft",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
+legend("topright",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
+v <- sqrt(ternary$seed_costs/500)
+ternary$horz <- c(1.8,1.3,1.2,-0.3,0.6,0.6,0.5,-0.2,1.3,1.7,1.4,-0.2,-0.3,-0.3)
+ternary$vert <- c(v[1]*-1.7,v[2]*1.1,v[3]*1.2,v[4],v[5]*-2.3,v[6]*4.5,v[7],v[8]*1.6,v[9],v[10]*0.2,v[11],v[12],v[13],v[14])
+ternary = ternary[with(ternary, order(-seed_costs)), ]
+label <- 20
+
 dev.off()
-
+library(ggtern)
 win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
@@
 
-par(mfrow=c(1,1), cex=1, omi=c(1,1,1,1), mai=c(.1,.1,.1,.1))
+par(mfrow=c(1,1), cex=1, omi=c(2,2,2,2), mai=c(2,2,2,2))
 
 ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
-  labs(y = "embryo+endosperm",
-       x = "pre-poll",
-       z = "pack&disp",
-       Tarrow = "embryo + endosperm weight (%)",
-       Larrow = "pre-pollination costs (%)",
-       Rarrow = "packaging & dispersal costs (%)",
-       title = "Seed cost components",
-       size = 3) +
-       geom_point(size=sqrt(ternary$seed_costs/2),shape=20,color=col.spp()) +
+      geom_point(size=sqrt(ternary$seed_costs/2),shape=20,color=col.spp(ternary$species)) +
       theme_bw() + 
       theme_showarrows() +
-       geom_text(label=ternary$species, color="black", hjust=-.3, vjust=sqrt(ternary$seed_costs/500),size=2)
+      geom_text(label=ternary$species, color="black", hjust=ternary$horz, 
+                 vjust=ternary$vert,size=2) +
+      ggtitle("Seed cost components")+
+      labs(T="embryo+endosperm",L="pre-pollination",R="provisioning")+
+      Tarrowlab("embryo + endosperm weight (%)")+
+      Larrowlab("pre-pollination costs (%)")+
+      Rarrowlab("provisioning costs (%)")+
+      theme(plot.title = element_text(size=11,face="bold"))+
+      theme(tern.axis.title.T = element_text(size=9,face="plain"))+
+      theme(tern.axis.title.L = element_text(size=9,face="plain",hjust=0,vjust=1.7))+
+      theme(tern.axis.title.R = element_text(size=9,face="plain",hjust=1,vjust=1.7))+
+      theme(tern.axis.arrow.text = element_text(size=9,face="plain"))+
+      theme(tern.axis.arrow.start= 0.2)+ 
+      theme(tern.axis.arrow.finish=0.8)
 
@@
 
+      labs(
+        y = "embryo+endosperm",
+        x = "pre-pollination",
+        z = "provisioning",
+        Tarrow = "embryo + endosperm weight (%)",
+        Larrow = "pre-pollination costs (%)",
+        Rarrow = "provisioning costs (%)")+
 #Table 2 showing seedcost breakdown into components, by species
@@
 mod <- lm(log10(accessory_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
-words.top.left.logxy(mod)
+#words.top.left.logxy(mod)
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
@@
 axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+legend("bottomright",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=0.9,bty="n",text.font=3)
 
@@
 mod <- lm(log10(prepollen_costs)~log10(embryo_endo_size),SummarySpp[["mean"]])
-words.top.left.logxy(mod)
+#words.top.left.logxy(mod)
 abline(coef(mod)[1],coef(mod)[2])
@@
 mod <- lm(log10(postpollen_all_per_seed)~log10(embryo_endo_size),SummarySpp[["mean"]])
-words.top.left.logxy(mod)
+#words.top.left.logxy(mod)
 abline(coef(mod)[1],coef(mod)[2])
@@
 
-acc_by_species <- select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
+acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
 
@@
 abline(slopes$groupsummary["Int"][[1]],1,col="red")
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
@@
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
@@
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
@@
 # abline(slopes$groupsummary["Int"][[1]],1,col="red")
-# acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+# acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
@@
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
@@
 slopes <- sma(postpollen_all_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 mtext(text="embryo + endosperm size (mg)",side=1,line=1.5,outer=TRUE)
@@
 slopes <- sma(postpollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
-acc_by_species <- dplyr::bind_rows(acc_by_species, select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
@@
 axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
-legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")
+legend("bottomleft",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=.9,bty="n",text.font=3)
 
@@
 
-plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,100),ylim=c(.004,.3),cex=1.5,xaxt="n",xlab="embryo + endosperm size (mg)",ylab="seed set")
+plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,100),ylim=c(.004,.3),cex=1.5,xaxt="n",yaxt="n",xlab="embryo + endosperm size (mg)",ylab="seed set")
 mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
-text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.98*(par("usr")[4]-par("usr")[3])+par("usr")[3])),
-     paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
+text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.98*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
 axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
-legend("bottomleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.9,bty="n")
+axis(2, at=c(0.005,0.01,0.02,0.05,.1,.2), labels=c(.005,.01,.02,.05,.1,.2),cex.axis=0.9)
+legend("bottomleft",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=0.9,bty="n",text.font=3)
 
 #species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
-plot(prop_prepollen_costs~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.004,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
+plot(jitter(prop_prepollen_costs)~jitter(seedset),SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.004,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
 mod <- sma(prop_prepollen_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
@@
 sma_sum(mod)
-text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
+text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
  paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
@@
 abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red")
-legend("topright",legend=c("seed count","total bud count","failed flower count"),col=c("black","blue","red"),pch=c(16,21,8),bty="n")
+legend("topright",legend=c("seed count","total bud count","failed flower count"),col=c("black","blue","red"),pch="_",bty="n")
 
@@
 fit <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", log="xy",slope.test=1)
-temp <- as.data.frame(c(xvar, yvar,select(fit$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Slope_test_p,n)))
+temp <- as.data.frame(c(xvar, yvar,dplyr::select(fit$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Slope_test_p,n)))
 colnames(temp)[2]<- "variable"
@@
 
-#Figure 5. Correlations of various reproductive investment categories against plant weight
+#Figure 6. Correlations of various reproductive investment categories against plant weight
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure02_correlations_with_plant_weight.wmf", height=5, width=10)
+win.metafile("figs2/Accessory_Costs/Figure06_correlations_with_plant_weight.wmf", height=5, width=10)
 plot
@@
 yvar <- "repro_inv"
-xvar <- "propagule_inv"
+xvar <- "embryo_endo_inv"
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 mod <- lm(log10(propagule_inv)~log10(repro_inv),data=subset(SummaryInd,propagule_inv>0))
-mtext(text="investment in propagules (mg)",side=1,line=2,outer=FALSE)
+mtext(text="investment in propagules (embryos & endosperm) (mg)",side=1,line=2,outer=FALSE)
 mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
@@
 
-select(results,group,n,r2,pval,Slope,Slope_test_p)
+dplyr::select(results,group,n,r2,pval,Slope,Slope_test_p)
 abline(0,1,lwd=2)

### 2016-06-20 scripts/Accessory_figs_20160218.Rmd
formatting figures/tables for Accessory Costs manuscript

@@
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,accessory_per_seed,prop_accessory_nonzero,seed_costs,prop_success, prepollen_costs,pack_disp_costs,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,embryo_endo_size,accessory_per_seed,prop_accessory_nonzero,seed_costs,prop_success, prepollen_costs,pack_disp_costs,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
 acc_costs_spp$species <- labels.spp.full()
-acc_costs_spp <- format(acc_costs_spp, digit=2)
+acc_costs_spp_format <- acc_costs_spp
+acc_costs_spp_format$seed_size <- round(acc_costs_spp_format$seed_size,digits=3)
+acc_costs_spp_format$embryo_endo_size <- round(acc_costs_spp_format$embryo_endo_size,digits=3)
+acc_costs_spp_format$accessory_per_seed <- paste(round(acc_costs_spp_format$accessory_per_seed,digits=1)," (",
+                                                 round(acc_costs_spp_format$prop_accessory_nonzero,digits=2),")")
+acc_costs_spp_format$seed_costs <- paste(round(acc_costs_spp_format$seed_costs,digits=2)," (",
+                                                 round(acc_costs_spp_format$prop_success,digits=2),")")
+acc_costs_spp_format$prepollen_costs <- round(acc_costs_spp_format$prepollen_costs,digits=2)
+acc_costs_spp_format$pack_disp_costs <- round(acc_costs_spp_format$pack_disp_costs,digits=2)
+acc_costs_spp_format$failure_per_seed <- paste(round(acc_costs_spp_format$failure_per_seed,digits=2)," (",
+                                                 round(acc_costs_spp_format$prop_failure,digits=2),")")
+acc_costs_spp_format$prepollen_failure_per_seed <- round(acc_costs_spp_format$prepollen_failure_per_seed,digits=2)
+acc_costs_spp_format$postpollen_aborted_per_seed <- round(acc_costs_spp_format$postpollen_aborted_per_seed,digits=2)
+acc_costs_spp_format$seedset <- round(acc_costs_spp_format$seedset,digits=3)
+acc_costs_spp_format <- dplyr::select(acc_costs_spp_format,species,seed_size,embryo_endo_size,accessory_per_seed,seed_costs,prepollen_costs,pack_disp_costs
+                                      ,failure_per_seed,prepollen_failure_per_seed,postpollen_aborted_per_seed,seedset)
+acc_costs_spp_format
 
-write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table01_AccCosts_by_Species.csv",row.names=FALSE)
+write.csv(acc_costs_spp_format, file="figs2/Accessory_Costs/Table01_AccCosts_by_Species.csv",row.names=FALSE)
 ```
@@
 
-      labs(
-        y = "embryo+endosperm",
-        x = "pre-pollination",
-        z = "provisioning",
-        Tarrow = "embryo + endosperm weight (%)",
-        Larrow = "pre-pollination costs (%)",
-        Rarrow = "provisioning costs (%)")+
 #Table 2 showing seedcost breakdown into components, by species
 ```{r}
-prop_seed_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_costs,prop_prepollen_costs,prop_dispersal_costs,prop_seed_costs)
+prop_seed_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_costs,prop_prepollen_costs,prop_dispersal_costs,prop_embryo_endo_costs)
 prop_seed_costs_spp$species <- labels.spp.full()
-prop_seed_costs_spp <- format(prop_seed_costs_spp, digit=2)
-write.csv(prop_seed_costs_spp, file="figs2/Accessory_Costs/Table04_Prop_seed_costs_by_Species.csv",row.names=FALSE)
+
+mod_1 <- sma(seed_costs~prop_prepollen_costs,SummarySpp[["mean"]],log="y")
+mod_2 <- sma(seed_costs~prop_dispersal_costs,SummarySpp[["mean"]],log="y")
+mod_3 <- sma(seed_costs~prop_embryo_endo_costs,SummarySpp[["mean"]],log="y")
+
+row_x <- as.data.frame(0)
+row_1 <- as.data.frame("r2")
+row_1 <- as.data.frame(dplyr::bind_cols(row_1,row_x,as.data.frame(mod_1$groupsummary[1,3]),as.data.frame(mod_2$groupsummary[1,3]),as.data.frame(mod_3$groupsummary[1,3])))
+names(row_1) <- c("species","seed_costs","prop_prepollen_costs","prop_dispersal_costs","prop_embryo_endo_costs")
+
+row_2 <- as.data.frame("p-value")
+row_2 <- dplyr::bind_cols(row_2,row_x,as.data.frame(mod_1$groupsummary[1,4]),as.data.frame(mod_2$groupsummary[1,4]),as.data.frame(mod_3$groupsummary[1,4]))
+names(row_2) <- c("species","seed_costs","prop_prepollen_costs","prop_dispersal_costs","prop_embryo_endo_costs")
+
+row_3 <- as.data.frame("slope")
+row_3 <- dplyr::bind_cols(row_3,row_x,as.data.frame(mod_1$groupsummary[1,5]),as.data.frame(mod_2$groupsummary[1,5]),as.data.frame(mod_3$groupsummary[1,5]))
+names(row_3) <- c("species","seed_costs","prop_prepollen_costs","prop_dispersal_costs","prop_embryo_endo_costs")
+
+prop_seed_costs_spp <- dplyr::bind_rows(prop_seed_costs_spp,row_1,row_2,row_3)
+
+write.csv(prop_seed_costs_spp, file="figs2/Accessory_Costs/Table02_Prop_seed_costs_by_Species.csv",row.names=FALSE)
 ```
@@
 
+plot(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(pack_disp_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
+words.top.left.logxy(mod)
+slopes <- sma(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
+
 plot(failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
@@
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+#acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
@@
 
-plot(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(pack_disp_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
-words.top.left.logxy(mod)
-slopes <- sma(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
+#slopes <- sma(postpollen_all_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+#acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-slopes <- sma(postpollen_all_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-acc_by_species$variable = c("total accessory costs","prepollen_success","failed_tissues","total prepollen","dispersal","total postpollen")
+acc_by_species$variable = c("total accessory costs","pre-pollination costs","provisioning costs", "failed_tissues")
 
@@
 
+plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(pack_disp_costs) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
+words.top.left.logxy(mod)
+slopes <- sma(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
+
 plot(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+#acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(pack_disp_costs) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
-words.top.left.logxy(mod)
-slopes <- sma(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-mtext(text="embryo + endosperm size (mg)",side=1,line=1.5,outer=TRUE)
+# plot(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
+# words.top.left.logxy(mod)
+# y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
+# slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
+# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+# abline(slopes$groupsummary["Int"][[1]],1,col="red")
+# acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-slopes <- sma(postpollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+#slopes <- sma(postpollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+#acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-acc_by_species$variable = c("total accessory costs","prepollen_success","failed_tissues","total prepollen","dispersal","total postpollen")
+acc_by_species$variable = c("total accessory costs","pre-pollination costs","provisioning costs", "failed_tissues")
 
-write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_embryo_endo_size_slopes.csv",row.names=FALSE)
+acc_by_species$slope2 <- paste(format(acc_by_species$Slope,digits=3)," (",format(acc_by_species$Slope_lowCI,digits=3)," - ",format(acc_by_species$Slope_highCI,digits=3),")",sep="")
+
+acc_by_species$r2 <- format(acc_by_species$r2,digits=2)
+acc_by_species$pval <- format(acc_by_species$pval,digits=2)
+acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=3)
+acc_slopes <- dplyr::select(acc_by_species,variable,r2,pval,slope2,Slope_test_p)
+
+write.csv(acc_slopes, file="figs2/Accessory_Costs/Table03_acc_cost_embryo_size_slopes.csv",row.names=FALSE)
 ```
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure05_cost_of_flowers_vs_seed_size.wmf", height=5, width=15)
+win.metafile("figs2/Accessory_Costs/Figure05_cost_of_flowers_vs_embryo_endo_size.wmf", height=5, width=15)
 plot
@@
 yvar <- "repro_inv"
-xvar <- "embryo_endo_inv"
+xvar <- "propagule_inv"
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 mod <- lm(log10(propagule_inv)~log10(repro_inv),data=subset(SummaryInd,propagule_inv>0))
-mtext(text="investment in propagules (embryos & endosperm) (mg)",side=1,line=2,outer=FALSE)
+mtext(text="investment in propagules (mg)",side=1,line=2,outer=FALSE)
 mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
+legend("bottomright",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=0.9,bty="n",text.font=3)
 
@@
 plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,300000),yaxt="n")
-legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
 abline(0,1)

### 2016-06-20 scripts/Accessory_figs_20160218.Rmd
continued work on figs for ms

@@
 
-acc_by_species$slope2 <- paste(format(acc_by_species$Slope,digits=3)," (",format(acc_by_species$Slope_lowCI,digits=3)," - ",format(acc_by_species$Slope_highCI,digits=3),")",sep="")
+acc_by_species$slope2 <- paste(format(acc_by_species$Slope,digits=3)," (",format(acc_by_species$Slope_lowCI,digits=3)," ̶ ",format(acc_by_species$Slope_highCI,digits=3),")",sep="")
 
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table06_eacc_cost_vs_seedset_by_spp.csv",row.names=FALSE)
+results$slope2 <- paste(format(results$Slope,digits=3)," (",format(results$Slope_lowCI,digits=3)," ̶ ",format(results$Slope_highCI,digits=3),")",sep="")
+
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=2)
+results$Slope_test_p <- format(results$Slope_test_p,digits=3)
+acc_slopes <- dplyr::select(results,variable,r2,pval,slope2,Slope_test_p)
+
+write.csv(results, file="figs2/Accessory_Costs/Table04_eacc_cost_vs_seedset_by_spp.csv",row.names=FALSE)
 ```
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table07a_accessory_vs_RE.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table05a_accessory_vs_RE.csv",row.names=FALSE)
 
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table07b_accessory_vs_total_weight.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)
 
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table07c_accessory_vs_age.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table05c_accessory_vs_age.csv",row.names=FALSE)
 dev.off()

### 2016-06-20 scripts/Accessory_figs_20160218.Rmd
edits to ms figures

@@
 results$Slope_test_p <- format(results$Slope_test_p,digits=3)
-acc_slopes <- dplyr::select(results,variable,r2,pval,slope2,Slope_test_p)
+results <- dplyr::select(results,variable,r2,pval,slope2,Slope_test_p)
 
@@
 results <- fit$groupsummary
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=3)
+acc_slopes <- dplyr::select(results,variable,n,r2,pval)
 
-write.csv(results, file="figs2/Accessory_Costs/Table01_extra_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table06_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
 ```
 
-#Table 7. correlations with total repro inv
+#Table 7 extra. correlations with total repro inv
 ```{r}
@@
 }
+
+write.csv(results, file="figs2/Accessory_Costs/Table07_EXTRA_correlations_with_repro_inv.csv",row.names=FALSE)
+```
+
+#Table 7. correlations with total repro inv
+```{r}
+results <- as.data.frame(matrix(vector(), 0, 9,
+                dimnames=list(c(), c("xvar","variable","r2","pval","Slope","Slope_lowCI","Slope_highCI","Int","Slope_test_p"))),
+                stringsAsFactors=F)
+
+for (i in c("total_weight","failure_inv","success_inv","propagule_inv","packaging_dispersal_inv","prepollen_success_inv","fruit_inv","flower_inv")) {
+  for (j in c("repro_inv")) {
+yvar <- i
+xvar <- j
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+fit <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", log="xy",slope.test=1)
+temp <- as.data.frame(c(xvar, yvar,dplyr::select(fit$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Slope_test_p,n)))
+colnames(temp)[2]<- "variable"
+colnames(temp)[1]<- "xvar"
+results <- bind_rows(results, temp)
+  }
+}
+
+results$slope2 <- paste(format(results$Slope,digits=3)," (",format(results$Slope_lowCI,digits=3)," - ",format(results$Slope_highCI,digits=3),")",sep="")
+
+results$r2 <- format(results$r2,digits=3)
+results$pval <- format(results$pval,digits=3)
+results$Slope_test_p <- format(results$Slope_test_p,digits=3)
+results  <- dplyr::select(results,variable,n,r2,pval,slope2,Slope_test_p)
 

### 2016-06-21 scripts/Growth_figs.rmd
edits to figures

@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="y",xlab="",ylab="",cex=1.4,ylim=c(1)
                     main=spp,col=col.mature(data[[spp]]$mature))
@@
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+par(mfrow=c(4,4), cex=1, omi=c(1.1,.5,.1,.1), mai=c(.1,.8,.5,0.1)) 
 yvar <- "growth_leaf"
@@
 
-data <- subset(SummaryInd,growth_leaf>0)
+data <- subset(SummaryInd)
 data <- split(data, data$species)
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
-                    main=spp,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",cex=1.4, xlab="",ylab="",
+                    col=col.age(data[[spp]]$age))
+  abline(0,0)
+  mtext(spp,3,line=0)
 }
 
-mtext("Investment in leaves (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
-legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
+mtext("Investment in leaves (mg)", 2, outer=TRUE,cex=1.2,line=0)
+mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2,line=2)
+legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
 ```
@@
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+par(mfrow=c(4,4), cex=1, omi=c(1.1,.5,.1,.1), mai=c(.1,.8,.5,0.1))
 yvar <- "growth_stem"
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.4, xlab="",ylab="",
-                    main=spp,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",cex=1.3, xlab="",ylab="",
+                    col=col.age(data[[spp]]$age))
+  mtext(spp,3,line=0)
 }
 
-mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2)
-mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2)
+mtext("Investment in stems (mg)", 2, outer=TRUE,cex=1.2,line=0)
+mtext("Initial plant weight (mg)", 1, outer=TRUE,cex=1.2,line=2)
 legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
@@
 ```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=28, fig.height=28}
-par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
+par(mfrow=c(4,4), cex=1, omi=c(1.1,.5,.1,.1), mai=c(.1,.8,.5,0.1))
 yvar <- "growth_stem_diameter"
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.4,
-                    main=spp,col=col.age(data[[spp]]$age))
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1.3,
+                    col=col.age(data[[spp]]$age))
+  mtext(spp,3,line=0)
 }
@@
 mtext("increase in stem diameter (mm)", 2, outer=TRUE,cex=1.2)
-mtext("increase in shoot diameter (mm)", 1, outer=TRUE,cex=1.2)
+mtext("increase in shoot diameter (mm)", 1, outer=TRUE,cex=1.2,line=2)
 legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=0.9,bty="n")

### 2016-06-28 scripts/Accessory_figs_20160218.Rmd
edits to figures
work on figures for Accessory Costs and RA

@@
 #number of plants in study
-count(SummaryInd)
+count(subset(SummaryInd,age>1))
 
@@
 #average proportion of energy going to accessory costs (based on propagules, not seeds) (among individuals that produce seed)
-mean(subset(SummaryInd$prop_accessory,SummaryInd$seed_count>0))
+mean(subset(SummaryInd$prop_accessory_seed,SummaryInd$seed_count>0))
+mean(subset(SummaryInd$prop_accessory_ee,SummaryInd$seed_count>0))
+SummarySpp[["mean"]]$prop_accessory_seed
+
+check <- dplyr::select(SummarySpp[["mean"]],species,prop_accessory_ee,prop_accessory_seed)
+check <- dplyr::arrange(check,prop_accessory_ee)
+
+#individual with lowest accessory costs
+check <- subset(SummaryInd,prop_propagule_ee>.1)
+check <- dplyr::select(check,individual,prop_propagule_ee)
+max(check$prop_propagule_ee)
 
@@
 
+#more failure = lower seedset across species - in discussion
+mod <- sma(seedset ~ prop_failure, data=subset(SummarySpp[["mean"]],species!="BAER"),method="OLS", log="",slope.test=1)
+summary(mod)
+plot(seedset ~ prop_failure, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))
+
 #seed size by propagule investment - all species
@@
 summary(mod)
-plot(propagule_inv ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(propagule_inv_ee ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 acc_costs_spp_format$embryo_endo_size <- round(acc_costs_spp_format$embryo_endo_size,digits=3)
-acc_costs_spp_format$accessory_per_seed <- paste(round(acc_costs_spp_format$accessory_per_seed,digits=1)," (",
+acc_costs_spp_format$accessory_per_seed2 <- paste(round(acc_costs_spp_format$accessory_per_seed,digits=1)," (",
                                                  round(acc_costs_spp_format$prop_accessory_nonzero,digits=2),")")
-acc_costs_spp_format$seed_costs <- paste(round(acc_costs_spp_format$seed_costs,digits=2)," (",
+acc_costs_spp_format$seed_costs2 <- paste(round(acc_costs_spp_format$seed_costs,digits=2)," (",
                                                  round(acc_costs_spp_format$prop_success,digits=2),")")
@@
 acc_costs_spp_format$seedset <- round(acc_costs_spp_format$seedset,digits=3)
-acc_costs_spp_format <- dplyr::select(acc_costs_spp_format,species,seed_size,embryo_endo_size,accessory_per_seed,seed_costs,prepollen_costs,pack_disp_costs
-                                      ,failure_per_seed,prepollen_failure_per_seed,postpollen_aborted_per_seed,seedset)
+acc_costs_spp_format <- dplyr::select(acc_costs_spp_format,species,seed_size,embryo_endo_size,accessory_per_seed2,seed_costs2,prepollen_costs,pack_disp_costs ,failure_per_seed,prepollen_failure_per_seed,postpollen_aborted_per_seed,seedset,accessory_per_seed,seedcosts)
 acc_costs_spp_format
@@
 #Table 3. Slopes for various seed size by acc cost regressions
+#NO LONGER AN EXACT PARALLEL TO To TABLE 3 embryo version - redo if using
 ```{r}
@@
 plot(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(accessory_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
-mod <- lm(log10(prepollen_costs) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
-words.bottom.left.logxy(mod)
 slopes <- sma(prepollen_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
@@
 plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(pack_disp_costs) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
-words.top.left.logxy(mod)
 slopes <- sma(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
@@
 
-plot(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(failure_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
-words.bottom.left.logxy(mod)
+plot(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all failure costs (mg/seed)",xlab="",cex=1.5)
 slopes <- sma(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
@@
 
-plot(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(prepollen_all_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]]))
-words.bottom.right.logxy(mod)
-slopes <- sma(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+plot(prepollen_failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_failure_per_seed,SummarySpp[["se"]]$prepollen_failure_per_seed)
+slopes <- sma(prepollen_failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
 abline(slopes$groupsummary["Int"][[1]],1,col="red")
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
-#acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-# plot(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
-# words.top.left.logxy(mod)
-# y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
-# slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
-# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-# abline(slopes$groupsummary["Int"][[1]],1,col="red")
-# acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+plot(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted during provisioning costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
+slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,col="red")
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-#slopes <- sma(postpollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
-#acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+acc_by_species$variable = c("total accessory costs","pre-pollination costs","provisioning costs", "failed tissues costs","failed pre-pollination costs","failed provisioning costs")
 
-acc_by_species$variable = c("total accessory costs","pre-pollination costs","provisioning costs", "failed_tissues")
-
-acc_by_species$slope2 <- paste(format(acc_by_species$Slope,digits=3)," (",format(acc_by_species$Slope_lowCI,digits=3)," ̶ ",format(acc_by_species$Slope_highCI,digits=3),")",sep="")
+acc_by_species$slope2 <- paste(format(acc_by_species$Slope,digits=3)," (",format(acc_by_species$Slope_lowCI,digits=3)," - ",format(acc_by_species$Slope_highCI,digits=3),")",sep="")
 
@@
 acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=3)
-acc_slopes <- dplyr::select(acc_by_species,variable,r2,pval,slope2,Slope_test_p)
+acc_slopes <- dplyr::select(acc_by_species,variable,r2,pval,slope2,Slope_test_p,Slope,Slope_lowCI)
 
@@
 legend("bottomleft",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=0.9,bty="n",text.font=3)
+mod
+
+#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
+plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,100),ylim=c(1e-4,1000),yaxt="n",xaxt="n",xlab="embryo + endosperm size (mg)",ylab="count, scaled to plant size")
+points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
+#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
+axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=0.9)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
+
+mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
+mod2 <- sma(scaled_bud_count~embryo_endo_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
+mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
+abline(mod1$coef[[1]][1,1],mod1$coef[[1]][2,1],col="black",lwd=2)
+abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue",lwd=2)
+abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red",lwd=2)
+
+legend("topright",legend=c("seed count","bud count","failed flower count"),col=c("black","blue","red"),pch=c(16,1,NA),bty="n",lty=c(1,1,1))
 
@@
 
-#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
-plot(scaled_seed_count~embryo_endo_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,100),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="embryo + endosperm size (mg)",ylab="count, scaled to plant size")
-points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
-#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
-axis(2, at=c(0.000001,0.0001,0.01,1), labels=c(0.000001,0.0001,0.01,1),cex.axis=0.9)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
-
-mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
-mod2 <- sma(scaled_bud_count~embryo_endo_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
-mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
-sma_abline(mod1)
-abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue")
-abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red")
-legend("topright",legend=c("seed count","total bud count","failed flower count"),col=c("black","blue","red"),pch="_",bty="n")
+Fig5_data <- dplyr::select(mod1$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
+Fig5_data <- dplyr::bind_rows(Fig5_data,dplyr::select(mod2$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+Fig5_data <- dplyr::bind_rows(Fig5_data,dplyr::select(mod3$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+Fig5_data$variable <- c("seed count","bud count","failure count")
+write.csv(Fig5_data, file="figs2/Accessory_Costs/Figure05_data_slopes.csv",row.names=FALSE)
 
@@
 
-results$slope2 <- paste(format(results$Slope,digits=3)," (",format(results$Slope_lowCI,digits=3)," ̶ ",format(results$Slope_highCI,digits=3),")",sep="")
+results$slope2 <- paste(format(results$Slope,digits=3)," (",format(results$Slope_lowCI,digits=3)," - ",format(results$Slope_highCI,digits=3),")",sep="")
 
@@
 results$Slope_test_p <- format(results$Slope_test_p,digits=3)
-results <- dplyr::select(results,variable,r2,pval,slope2,Slope_test_p)
-
+results$full_name <- labels.spp.full(results$group)
+results$seed_size <- SummarySpp[["mean"]]$embryo_endo_size
+results <- dplyr::select(results,group,full_name,n, r2,pval,slope2,Slope_test_p,Slope,seed_size)
 write.csv(results, file="figs2/Accessory_Costs/Table04_eacc_cost_vs_seedset_by_spp.csv",row.names=FALSE)
@@
 results$pval <- format(results$pval,digits=3)
-acc_slopes <- dplyr::select(results,variable,n,r2,pval)
+acc_slopes <- dplyr::select(results,group,n,r2,pval)
 
 write.csv(results, file="figs2/Accessory_Costs/Table06_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
+```
+
+#Table 6.correlations between repro inv and flower inv by species (noted in Discussiong)
+```{r}
+yvar <- "repro_inv"
+xvar <- "flower_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- fit$groupsummary
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=3)
+acc_slopes <- dplyr::select(results,group,n,r2,pval)
+
+write.csv(results, file="figs2/Accessory_Costs/Table06extra_flower_invest_vs_repro_inv.csv",row.names=FALSE)
 ```

### 2016-06-28 scripts/RA_figs.rmd
work on figures for Accessory Costs and RA

--- 2015-09-10 RA_figs.rmd
@@
 plot((1+repro_inv)~growth_leaf, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
-words.top.left.logxy(mod)
+#words.top.left.logxy(mod)
 legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
@@
 
-plot((1+repro_inv)~growth_inv, SummaryInd, log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
+plot((1+repro_inv)~growth_leaf, SummaryInd, log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000))
 legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")

### 2016-06-28 scripts/RA_figs_20160627.R

@@ -1,0 +1,246 @@
+#Different species have different RA values. But biggest shift in RA is with age
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
+if (min(SummaryInd$growth_leaf) <= 0) {
+  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf - SummaryInd$growth_leaf_min + 1
+} else {
+  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf
+}
+
+SummaryInd$repro_inv_log <- 0
+for (i in 1:length(SummaryInd$individual)) {
+  if (SummaryInd$repro_inv[i] > 0) {
+    SummaryInd$repro_inv_log[i] <- log10(SummaryInd$repro_inv[i])
+  }else{
+    SummaryInd$repro_inv_log[i] <- 0  
+  }
+}
+
+SummaryInd$leaf_inv_log <- 0
+for (i in 1:length(SummaryInd$individual)) {
+  if (SummaryInd$growth_leaf[i] > 0) {
+    SummaryInd$leaf_inv_log[i] <- log10(SummaryInd$growth_leaf[i])
+  }else{
+    SummaryInd$leaf_inv_log[i] <- -(log10(-SummaryInd$growth_leaf[i]))  
+  }
+}
+
+
+par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
+plot(repro_inv~growth_leaf_positive, SummaryInd, log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),xlab="",ylab="")
+legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
+abline(0,1)
+text(2.1,3,srt=45,"RA = 0.5")
+abline(log10(3),1)
+text(2,9,srt=45,"RA = 0.75")
+abline(log10(9),1)
+text(2,25,srt=45,"RA = 0.9")
+abline(log10(19),1)
+text(2,60,srt=45,"RA = 0.95")
+abline(log10(.111),1)
+text(19,3,srt=45,"RA = 0.1")
+abline(log10(.010101),1)
+text(170,2.4,srt=45,"RA = 0.01")
+mtext("reproductive investment (mg)",2,line=1,outer=TRUE)
+
[…]

### 2016-08-30 scripts/Accessory_figs_20160218.Rmd
small changes to accessory costs
beginning work on RA figures

@@
 #there is no relationship between the proportion of energy going to seeds and the total energy for seedcosts
-mod <- lm(log10(seed_costs) ~prop_seed_costs,SummarySpp[["mean"]])
+mod <- sma(seed_costs~prop_seed_costs,SummarySpp[["mean"]],method="OLS",log="y")
 summary(mod)
@@
 
-par(mfrow=c(1,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+par(mfcol=c(3,1), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
 options(scipen = 5)
@@
 plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
+mod <- sma(accessory_per_seed~seed_size,data=subset(SummarySpp[["mean"]],accessory_per_seed>0),log="xy",method="OLS")
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
-abline(coef(mod)[1],coef(mod)[2])
-abline(coef(mod)[1],1,col="red")
+sma_abline(mod)
+abline(mod$groupsummary["Int"][[1]],1,lty=2)
 axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
 
@@
 #y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
-mod <- lm(log10(prepollen_costs)~log10(seed_size),SummarySpp[["mean"]])
-abline(coef(mod)[1],coef(mod)[2])
-abline(coef(mod)[1],1,col="red")
+mod <- sma(prepollen_costs~seed_size,SummarySpp[["mean"]],log="xy",method="OLS")
+sma_abline(mod)
+abline(mod$groupsummary["Int"][[1]],1,lty=2)
 axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
 
@@
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
-mod <- lm(log10(postpollen_all_per_seed)~log10(seed_size),SummarySpp[["mean"]])
-abline(coef(mod)[1],coef(mod)[2])
-abline(coef(mod)[1],1,col="red")
+mod <- sma(postpollen_all_per_seed~seed_size,SummarySpp[["mean"]],log="xy",method="OLS")
+sma_abline(mod)
+abline(mod$groupsummary["Int"][[1]],1,lty=2)
 axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure04_embryo_size_acc_cost_correlations.wmf", height=5, width=15)
+win.metafile("figs2/Accessory_Costs/Figure04_embryo_size_acc_cost_correlations.wmf", height=15, width=5)
 plot
 
-par(mfrow=c(1,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+par(mfcol=c(3,1), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
 options(scipen = 5)
@@
 plot(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(accessory_per_seed) ~ log10(embryo_endo_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
+mod <- sma(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],accessory_per_seed>0),log="xy",method="OLS")
 #words.top.left.logxy(mod)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
-abline(coef(mod)[1],coef(mod)[2])
-abline(coef(mod)[1],1,col="red")
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
+sma_abline(mod)
+abline(mod$groupsummary["Int"][[1]],1,lty=2)
 axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
 legend("bottomright",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=0.9,bty="n",text.font=3)
@@
 plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
-mod <- lm(log10(prepollen_costs)~log10(embryo_endo_size),SummarySpp[["mean"]])
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
+mod <- sma(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
 #words.top.left.logxy(mod)
-abline(coef(mod)[1],coef(mod)[2])
-abline(coef(mod)[1],1,col="red")
+sma_abline(mod)
+abline(mod$groupsummary["Int"][[1]],1,lty=2)
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
+
+plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
+mod <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
+#words.top.left.logxy(mod)
+sma_abline(mod)
+abline(mod$groupsummary["Int"][[1]],1,lty=2)
 axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
 axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-
-plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
-mod <- lm(log10(postpollen_all_per_seed)~log10(embryo_endo_size),SummarySpp[["mean"]])
-#words.top.left.logxy(mod)
-abline(coef(mod)[1],coef(mod)[2])
-abline(coef(mod)[1],1,col="red")
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-mtext(text="embryo + endosperm (mg)",side=1,line=1.5,outer=TRUE)
+mtext(text="     embryo + endosperm (mg)",side=1,line=1.5,outer=TRUE,adj=0.5)
 
@@
 
+glance(mod)
 #Table 3. Slopes for various seed size by acc cost regressions
@@
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(slopes$groupsummary["Int"][[1]],1,lty=2)
 words.bottom.left.logxy(mod)
@@
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(slopes$groupsummary["Int"][[1]],1,lty=2)
 acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
@@
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(slopes$groupsummary["Int"][[1]],1,lty=2)
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
@@
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(slopes$groupsummary["Int"][[1]],1,lty=2)
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
@@
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(slopes$groupsummary["Int"][[1]],1,lty=2)
 y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
@@
 # abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-# abline(slopes$groupsummary["Int"][[1]],1,col="red")
+# abline(slopes$groupsummary["Int"][[1]],1,lty=2)
 # acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
@@
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(slopes$groupsummary["Int"][[1]],1,lty=2)
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
@@
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,col="red")
+abline(slopes$groupsummary["Int"][[1]],1,lty=2)
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
@@
 sma_abline(mod1)
-abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue")
-abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red")
+abline(mod2$groupsummary["Int"][[1]],mod2$groupsummary["Slope"][[1]],col="blue")
+abline(mod3$groupsummary["Int"][[1]],mod3$groupsummary["Slope"][[1]],col="red")
 legend("topright",legend=c("seed count","total bud count","failed flower count"),col=c("black","blue","red"),pch=c(16,21,8),bty="n")
@@
 mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
-abline(mod1$coef[[1]][1,1],mod1$coef[[1]][2,1],col="black",lwd=2)
-abline(mod2$coef[[1]][1,1],mod2$coef[[1]][2,1],col="blue",lwd=2)
-abline(mod3$coef[[1]][1,1],mod3$coef[[1]][2,1],col="red",lwd=2)
+abline(mod1$groupsummary["Int"][[1]],mod1$groupsummary["Slope"][[1]],col="black",lwd=2)
+abline(mod2$groupsummary["Int"][[1]],mod2$groupsummary["Slope"][[1]],col="blue",lwd=2)
+abline(mod3$groupsummary["Int"][[1]],mod3$groupsummary["Slope"][[1]],col="red",lwd=2)
 
@@
 #plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,10000000),xlab="",ylab="",lty=results$linetype,pch=16)
-mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
+mod <- sma(total_weight_0~repro_inv,data=subset(SummaryInd,repro_inv>0),log="xy",method="OLS")
 abline(0,1)
@@
 abline(0,1)
-mod <- lm(log10(propagule_inv)~log10(repro_inv),data=subset(SummaryInd,propagule_inv>0))
+mod <- sma(propagule_inv~repro_inv,data=subset(SummaryInd,propagule_inv>0),log="xy",method="OLS")
 mtext(text="investment in propagules (mg)",side=1,line=2,outer=FALSE)
@@
 plot(seedset~prop_failure,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),log="xy",pch=16,col=col.spp(species))
-mod <- lm(log10(seed_size)~log10(total_weight_0),data=subset(SummarySpp[["mean"]]))
+mod <- sma(seed_size~total_weight_0,data=subset(SummarySpp[["mean"]]),log="xy",method="OLS")
 summary(mod)
@@
 points(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seed_count>0),col=col.spp(species),pch=16,cex=2)
-mod <- lm(log10(accessory_per_seed)~log10(seed_count),data=subset(SummarySpp[["mean"]]))
-words.top.right.logxy(mod)
+mod <- sma(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]]),method="OLS", log="xy")
+#words.top.right.logxy(mod)
 legend_with_r2(results,"bottomleft")

### 2016-08-30 scripts/RA_figs_20160627.Rmd
small changes to accessory costs
beginning work on RA figures

#Figure 1 Different species have different RA values. But biggest shift in RA is with age
```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
if (min(SummaryInd$growth_leaf) <= 0) {
  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf - SummaryInd$growth_leaf_min + 1
} else {
  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf
}

SummaryInd$repro_inv_log <- 0
for (i in 1:length(SummaryInd$individual)) {
  if (SummaryInd$repro_inv[i] > 0) {
    SummaryInd$repro_inv_log[i] <- log10(SummaryInd$repro_inv[i])
  }else{
    SummaryInd$repro_inv_log[i] <- 0  
  }
}

SummaryInd$leaf_inv_log <- 0
for (i in 1:length(SummaryInd$individual)) {
  if (SummaryInd$growth_leaf[i] > 0) {
    SummaryInd$leaf_inv_log[i] <- log10(SummaryInd$growth_leaf[i])
  }else{
    SummaryInd$leaf_inv_log[i] <- -(log10(-SummaryInd$growth_leaf[i]))  
  }
}

SummaryInd$leaf_repro_inv_log <- 0
for (i in 1:length(SummaryInd$individual)) {
  if (SummaryInd$leaf_repro_inv[i] > 0) {
    SummaryInd$leaf_repro_inv_log[i] <- log10(SummaryInd$leaf_repro_inv[i])
  }else{
    SummaryInd$leaf_repro_inv_log[i] <- -(log10(-SummaryInd$leaf_repro_inv[i]))  
  }
}

#pdf("figs2/RA/Figure_1_leaf_vs_repro.pdf", height=4.3, width=8)
win.metafile("figs2/RA/Figure_1_leaf_vs_repro.wmf", height=4.3, width=8)
plot
par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
plot(repro_inv~growth_leaf_positive, subset(SummaryInd,growth_leaf_positive>1), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",yaxt="n",xaxt="n",cex=0.8)
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
mtext("reproductive investment (mg)",2,line=1,outer=TRUE)

plot(repro_inv~growth_leaf_positive, subset(SummaryInd,growth_leaf_positive>1), log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
     xlab="",ylab="",yaxt="n",xaxt="n",cex=0.8)
axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.6,bty="n")
abline(0,1)
text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
mtext("leaf investment, scaled to be positive (mg)",1,line=2,outer=TRUE)
dev.off()
```

#Figure 1 - shed leaves, gross leaf production
```{r}
par(mfrow=c(1,2), cex=1, omi=c(.1,0.1,.1,.1), mai=c(0.8,.8,.1,0.2)) 
plot(leaf_shed ~ leaf_inv_gross,SummaryInd,log="xy",pch=16, col=col.spp(species),xlim=c(1,10^7),ylim=c(1,10^7))
abline(0,1)
plot(leaf_shed ~ leaf_inv_gross,SummaryInd,log="xy",pch=16, col=col.age(age),xlim=c(1,10^7),ylim=c(1,10^7))

abline(0,1)

library(scatterplot3d)

scatterplot3d(SummaryInd$leaf_shed,SummaryInd$leaf_inv_gross,SummaryInd$repro_inv,log="xyz",color=col.spp(SummaryInd$species),pch=16)
```

#Figure 1 - alternate rendition, not scaling leaf investment to be positive
```{r}
pdf("figs2/RA/Figure_1_alt_leaf_vs_repro.pdf", height=4.3, width=8)
plot
par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
plot(repro_inv_log~leaf_inv_log, subset(SummaryInd), log="", col=col.spp(species),pch=16,xlim=c(-4,6),ylim=c(-1,6),
     xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
axis(1, at=c(-4,-2,0,2,4,6), labels=c(-10000,-100,0,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(0,2,4,6), labels=c(0,100,10000,"1000000"),cex.axis=0.9)
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
abline(0,1)
text(5.6,5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(5.13,5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(4.67,5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(4.33,5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(5.6,4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(5.6,3.8,srt=45,"RA = 0.01",cex=.6)
mtext("reproductive investment (mg)",2,line=1,outer=TRUE)

plot(repro_inv_log~leaf_inv_log, subset(SummaryInd), log="", col=col.age(age),pch=16,xlim=c(-4,6),ylim=c(-1,6),
     xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
axis(1, at=c(-4,-2,0,2,4,6), labels=c(-10000,-100,0,100,10000,"1000000"),cex.axis=0.9)
axis(2, at=c(0,2,4,6), labels=c(0,100,10000,"1000000"),cex.axis=0.9)
legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=.6,bty="n")
abline(0,1)
text(5.6,5.8,srt=45,"RA = 0.5",cex=.6)
abline(log10(3),1)
text(5.13,5.8,srt=45,"RA = 0.75",cex=.6)
abline(log10(9),1)
text(4.67,5.8,srt=45,"RA = 0.9",cex=.6)
abline(log10(19),1)
text(4.33,5.8,srt=45,"RA = 0.95",cex=.6)
abline(log10(.111),1)
text(5.6,4.85,srt=45,"RA = 0.1",cex=.6)
abline(log10(.010101),1)
text(5.6,3.8,srt=45,"RA = 0.01",cex=.6)
mtext("leaf investment (mg)",1,line=2,outer=TRUE)
dev.off()
```

#Figure 2 - RA schedules for species, including indication of schedule-type
```{r}
win.metafile("figs2/RA/Figure_2_RA_schedules.wmf", height=11, width=8)
plot
#pdf("figs2/RA/Figure_2_RA_schedules.pdf", height=11, width=8)
par(mfcol=c(5,3), cex=1, omi=c(.7,.7,.1,.1), mai=c(0.15,.15,0.05,0.05))

yvar <- "leaf_inv_log"
xvar <- "total_weight_0"

data <- subset(SummarySppAge[["mean"]])
data <- split(data, data$species)

data2 <- subset(SummaryInd,RA_leaf_area>-2&RA_leaf_area<3)
data2 <- split(data2, data2$species)

curves <- as.data.frame(c("determinate: gradual","determinate: gradual","indeterminate: asymptotic","indeterminate: asymptotic","determinate: bang-bang","determinate: bang-bang","indeterminate: gradual","determinate: bang-bang","determinate: gradual","determinate: gradual","indeterminate: declining","determinate: gradual","determinate: bang-bang","determinate: gradual"))

curves <- cbind(curves, SummarySpp[["mean"]]$species)
names(curves) <- c("RA_type","species")

data3 <- curves
data3 <- split(data3, data3$species)

for(spp in names(data)) {
  plot(RA_leaf_area~age,data2[[spp]],col=col.age(data2[[spp]]$age),pch=16,xlab="",ylab="",log="x",xlim=c(1,40),ylim=c(-0.25,1.75),yaxt="n",xaxt="n")
  points(RA_leaf_area~age,data[[spp]],pch=151,col=col.age(data[[spp]]$age),cex=1.5)
   if(spp=="BOLE"|spp=="COER") {
    rect(14,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
  }
    if(spp=="GRSP"|spp=="HEPU") {
    rect(20,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
  }
  if(spp=="PILI") {
    rect(10,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
  }
  abline(0,0)
  abline(1,0,lty=3)
  axis(1, at=c(1,2,5,10,20,30), labels=c("","","","","",""),cex.axis=.8,las=1,tck=-.03) 
  axis(2, at=c(-0,0.5,1,1.5), labels=c("","","",""),cex.axis=.8,las=1,tck=-.03)

  if(spp=="GRBU"|spp=="PELA"|spp=="PUTU"){
    axis(1, at=c(1,2,5,10,20,30), labels=c(1,2,5,10,20,30),cex.axis=.8,las=1) 
      } else{}
  if(spp=="BAER"|spp=="BOLE"|spp=="COER"|spp=="EPMI"|spp=="GRBU"){
    axis(2, at=c(-0,0.5,1,1.5), labels=c(-0,0.5,1,1.5),cex.axis=.8,las=1)
  } else{}
  extra.top.left.logx(labels.spp.full(spp),3)
  extra.bottom.left.logx(data3[[spp]]$RA_type,1)
}

mtext("RA", 2, outer=TRUE,cex=1,line=2)
mtext("age",1, outer=TRUE,cex=1,line=1.8)

dev.off()
```

#Figure 3, Table 1 - comparing max RA to various functional traits and life history traits
```{r}
RA_test <- as.data.frame(c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU"))
names(RA_test) <- c("species")
RA_test$min_age <- c(8,6,6,8,8,6,8,6,8,8,6,8,4,8)
test <- SummaryInd
test <- dplyr::left_join(SummaryInd, RA_test, by = "species")
test <- subset(test,age>min_age)
test2 <- test %>% 
          group_by(species) %>% 
          summarise_each(funs(mean), maxH,RA_leaf_area)
names(test2) <- c("species","maxH","maxRA_leaf_area")
test2$mature <- c(7,1.4,2.4,2.4,5,2.4,7,1.4,2.4,9,7,2.4,1.4,2.4)
test2$lifespan <- c(40,9,12,40,30,20,40,20,40,40,40,30,7,30)

Table_01 <- as.data.frame(select(SummarySpp[["mean"]],species,RA_leaf_area,embryo_endo_size,LMA,wood_density,growth_shoot_length,seed_count))
Table_01 <- dplyr::right_join(Table_01,test2,by="species")
Table_01$RA_per_year <- Table_01$RA_leaf_area/Table_01$lifespan

win.metafile("figs2/RA/Figure_3_maxRA_correlates.wmf", height=11, width=8)
plot
par(mfcol=c(3,2), cex=1, omi=c(.1,.7,.1,.1), mai=c(.8,.3,.1,0.2))

plot(maxRA_leaf_area~lifespan,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("lifespan (years)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
mod <- lm(log10(lifespan)~maxRA_leaf_area,Table_01)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
mtext("maximum RA",2,outer=TRUE,line=1)

plot(maxRA_leaf_area~mature,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("age at maturity (years)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
mod <- lm(mature~log10(maxRA_leaf_area),Table_01)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))

plot(maxRA_leaf_area~embryo_endo_size,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n",xlim=c(.005,30),xaxt="n")
mtext("embryo + endosperm weight (mg)",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
axis(1, at=c(.01,.1,1,10), labels=c(.01,.1,1,10),las=1)
mod <- lm(log10(embryo_endo_size)~maxRA_leaf_area,Table_01)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")

plot(maxRA_leaf_area~maxH,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
mtext("maximum height (mm)",1,outer=FALSE,line=2)
mod <- lm(log10(maxH)~maxRA_leaf_area,Table_01)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))

plot(maxRA_leaf_area~LMA,Table_01,col=col.spp(species),pch=16,cex=1.5,xlab="",yaxt="n")
mtext("LMA",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
mod <- lm(LMA~RA_leaf_area,Table_01)
extra.bottom.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))

plot(maxRA_leaf_area~wood_density,Table_01,col=col.spp(species),pch=16,cex=1.5,xlab="",yaxt="n")
mtext("wood density",1,outer=FALSE,line=2)
axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
mod <- lm(wood_density~maxRA_leaf_area,Table_01)
extra.top.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
dev.off()

write.csv(Table_01, file="figs2/RA/Table01_maxRA_correlates.csv",row.names=FALSE)

plot(RA_per_year ~ maxRA_leaf_area,Table_01,col=col.spp(species),pch=16,cex=2,log="y")
mod <- lm(maxRA_leaf_area~log10(RA_per_year),Table_01)
summary(mod)

plot(seed_count ~ maxRA_leaf_area,Table_01,col=col.spp(species),pch=16,cex=2,log="y")
```

#Figure 4a - reproductive vs leaf investment across plant weights
#Shows clearly how there is a crossover in leaf vs reproductive investment for all species, but magnitude of effect is very different
```{r}
win.metafile("figs2/RA/Figure_4a_investment.wmf", height=11, width=8)
plot
#pdf("figs2/RA/Figure_4a_investment.pdf", height=11, width=8)
par(mfcol=c(5,3), cex=1, omi=c(.3,.7,.1,.1), mai=c(0.5,.15,0.05,0.05))

yvar <- "leaf_inv_log"
xvar <- "total_weight_0"

data <- subset(SummaryInd)
data <- split(data, data$species)

data2 <- subset(SummaryInd,RA_leaf_area>-2&RA_leaf_area<3)
data2 <- split(data2, data2$species)

for(spp in names(data)) {

  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=.8,ylim=c(-4,6),
                    col=col.age(data[[spp]]$age),cex.main=0.9, yaxt="n")

  points(repro_inv_log~total_weight_0,data[[spp]],pch=1,cex=1.2,col=col.age(data[[spp]]$age))
  points(leaf_repro_inv_log~total_weight_0,data[[spp]],pch=151,cex=1,col=col.age(data[[spp]]$age))
  extra.top.left.logx(labels.spp.full(spp),3)
  #arrows(data[[spp]]$total_weight_0,data[[spp]]$leaf_inv_log,data[[spp]]$total_weight_0,data[[spp]]$repro_inv_log,lwd=1,length=.08,
  #col=col.age(data[[spp]]$age))
  abline(0,0)
  axis(2, at=c(-4,-2,0,2,4), labels=c("","","","",""),cex.axis=.8,las=1,tck=-.03)

  if(spp=="BAER"|spp=="BOLE"|spp=="COER"|spp=="EPMI"|spp=="GRBU"){
    axis(2, at=c(-4,-2,0,2,4), labels=c(-10000,-100,0,100,10000),cex.axis=.8,las=1)
      } else {}
}

mtext("investment (mg)", 2, outer=TRUE,cex=1,line=2.5)
mtext("plant weight (mg)",1,outer=TRUE,cex=1,line=-.3)

dev.off()
```

#Figure 4b leaf area declines with age in some species, plateaus in others, and in a few continues to increase
```{r}
win.metafile("figs2/RA/Figure_4b_leaf_area_vs_age.wmf", height=11, width=8)
plot
par(mfcol=c(5,3), cex=1, omi=c(.5,.4,.1,.1), mai=c(0.15,.5,0.05,0.05))
xvar <- "age"
yvar <- "leaf_area"

data <- subset(SummaryInd)
data <- split(data, data$species)
data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab=xvar,ylab=yvar,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,40),yaxt="n",xaxt="n")
  points(leaf_area~age,data2[[spp]],cex=1.5,col=col.age(data2[[spp]]$age),pch=151)
  extra.top.left.logxy(labels.spp.full(spp),3)
   if(spp=="BOLE"|spp=="COER") {
    rect(14,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
  }
    if(spp=="GRSP"|spp=="HEPU") {
    rect(20,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
  }
  if(spp=="PILI") {
    rect(10,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
  }
  axis(1, at=c(1,2,5,10,20,30), labels=c("","","","","",""),cex.axis=.8,las=1,tck=-.03) 
  axis(2, at=c(5,10,50,100,500,1000,5000,10000,50000,100000,500000,1000000),labels=c("",10,"",100,"",1000,"","10000","","100000","","1000000"),
    cex.axis=0.8,las=2,hadj=.8,)
  if(spp=="GRBU"|spp=="PELA"|spp=="PUTU"){
    axis(1, at=c(1,2,5,10,20,30), labels=c(1,2,5,10,20,30),cex.axis=.8,las=1) 
  } else{}
}
mtext("leaf area (mm^2)",outer=TRUE,2,line=0.2)
mtext("age (years)",outer=TRUE,1,line=1.2)
dev.off()
```

#RV curves
```{r}
win.metafile("figs2/RA/Figure_EXTRA_RV_curves.wmf", height=11, width=8)
plot
par(mfcol=c(5,3), cex=1, omi=c(.3,.3,.1,.1), mai=c(0.4,.7,0.05,0.05))

yvar <- "repro_inv_log"
xvar <- "total_weight_0"

data <- subset(SummaryInd)
data <- split(data, data$species)

for(spp in names(data)) {
    plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=.8,yaxt="n",col=col.age(data[[spp]]$age),cex.main=0.9)
  extra.top.left.logx(labels.spp.full(spp),3)
  axis(2, at=c(0,1,2,3,4,5), labels=c(0,10,100,1000,10000,"100000"),cex.axis=0.9,las=1)
}
mtext("reproductive investment (mg)", 2, outer=TRUE,cex=1,line=0)
mtext("weight", 1, outer=TRUE,cex=1,line=0)
dev.off()
```

#predicting growth from leaf area versus plant weight
#using leaf area at the start of the year is a better predictor of total investment than is total plant weight
```{r}
par(mfrow=c(7,2), cex=1, omi=c(.7,.8,.1,.1), mai=c(.3,.4,.4,0.2)) 
xvar <- "leaf_area_0"
xvar2 <- "total_weight_0"
yvar <- "leaf_repro_inv"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  ((x[[xvar]]))))
results <- summarise_all_fits(lmfits)

results$r.squared <- round(results$r.squared,digits=3)
results$p.value <- round(results$p.value,digits=3)
results$a <- round(results$a,digits=2)
results$b <- round(results$b,digits=2)

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm((x[[yvar]]) ~  ((x[[xvar2]]))))
results2 <- summarise_all_fits(lmfits)

results2$r.squared <- round(results2$r.squared,digits=3)
results2$p.value <- round(results2$p.value,digits=3)
results2$a <- round(results2$a,digits=2)
results2$b <- round(results2$b,digits=2)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab=xvar,ylab=yvar,cex=1,col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab=xvar2,ylab="",cex=1,main=spp,col=col.age(data[[spp]]$age),yaxt="n")
}
```

#Extra - leaf area is a better predictor of subsequent investment than is total plant weight. In particular, the age effect basically disappears
```{r}
#Leaf area is a better predictor of the subsequent years growth than is total weight. 
#result could be quite different if stem weight, even part of it were included
win.metafile("figs2/RA/Figure_EXTRA_leaf_area_better.wmf", height=11, width=8)
plot

par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.1,.1), mai=c(.9,.9,.4,0.2)) 
compare <- select(results, species, r.squared)
compare2 <- select(results2, r.squared)
compare <- cbind(compare, compare2)
names(compare) <- c("species","leaf_area","total_weight")

plot(leaf_repro_inv~leaf_area_0,SummaryInd,col=col.age(age),pch=16,log="xy",xlab="leaf area at time=0",ylab="investment in reproduction and leaves")
abline(0,1)

plot(leaf_repro_inv~total_weight_0,SummaryInd,col=col.age(age),pch=16,log="xy",xlab="total plant weight at time=0",ylab="investment in reproduction and leaves")
abline(0,1)

plot(leaf_area~total_weight,compare,col=col.spp(species),pch=16,xlab="r2 of total weight vs. investment",ylab="r2 of leaf area vs. investment")
abline(0,1)

dev.off()
```

#Extra - shoot extenstion and increase in shoot leaf area also decline with age in most species
#the first plot is of increase in shoot leaf area on the leader - only for PEPU does the leader's leaf area continue to increase until the end. Some species, such as EPMI plateau and show limited decline, but most continue to decline steeply
```{r}
win.metafile("figs2/RA/Figure_EXTRA_shoot_growth.wmf", height=11, width=8)
plot
par(mfcol=c(5,3), cex=1, omi=c(.5,.4,.1,.1), mai=c(0.15,.5,0.05,0.05))

data <- subset(SummaryInd)
data <- split(data, data$species)

for(spp in names(data)) {
  plot(shoot_growth_leaf_area~age,data[[spp]],log="xy",pch=16,col=col.age(age),cex.main=0.9,xlim=c(1,40),xaxt="n",cex.axis=0.9)
  axis(1, at=c(1,2,5,10,20,30), labels=c("","","","","",""),cex.axis=.8,las=1,tck=-.03) 
  if(spp=="BOLE"|spp=="COER") {
    rect(14,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
  }
  if(spp=="GRSP"|spp=="HEPU") {
    rect(20,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
  }
  if(spp=="PILI") {
    rect(10,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
  }
  if(spp=="GRBU"|spp=="PELA"|spp=="PUTU"){
    axis(1, at=c(1,2,5,10,20,30), labels=c(1,2,5,10,20,30),cex.axis=0.9,las=1) 
  } else{}
  extra.top.left.logxy(labels.spp.full(spp),3)
}

mtext("increase in leaf area on leader shoot (mm^2/year)",outer=TRUE,2,line=0.4)
mtext("age (years)",outer=TRUE,1,line=1)
dev.off()
```

### 2016-08-30 R/Summaries.R

@@ -125,6 +125,9 @@ combine_by_individual <- function(IndividualsList, Growth_all, Accessory_counts_
     shoot_leaf_area = shoot_leaf_count*leaf_size,
     shoot_growth_leaf_area = shoot_leaf_count_new*leaf_size,
     shoot_leaf_area_0 = shoot_leaf_area - shoot_growth_leaf_area,
+    prop_shoot_growth_leaf_area = shoot_growth_leaf_area / shoot_leaf_area_0,
+    leaf_shed = leaf_weight_0 * LL_death,
+    leaf_inv_gross = leaf_shed + growth_leaf,
     reproducing = RA>0,
     propagule_allocation = (seed_count*seed_size)/(growth_inv + repro_inv),
     embryo_allocation = (seed_count*embryo_endo_size)/(growth_inv + repro_inv),

### 2016-09-01 scripts/Accessory_figs_20160218.Rmd
mostly fixing up figures for accessory costs paper and working on manuscript

@@
 ```{r}
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,repro_inv_per_seed,prop_failure,prop_prepollen_vs_RE, prop_dispersal_vs_RE,prop_embryo_endo_vs_RE,seed_costs,prop_prepollen_costs,prop_postpollen_costs)
+acc_costs_spp$species <- labels.spp.full()
+acc_costs_spp_format <- acc_costs_spp
+for (i in c("embryo_endo_size","repro_inv_per_seed","prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","seed_costs","prop_prepollen_costs","prop_postpollen_costs")) {
+  acc_costs_spp_format[[i]] <- round(acc_costs_spp_format[[i]],digits=3)
+}
+
+write.csv(acc_costs_spp_format, file="figs2/Accessory_Costs/Table01_AccCosts_by_Species.csv",row.names=FALSE)
+```
+
+#Table 1 OLD showing accessory cost values for the species
+```{r}
 acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,embryo_endo_size,accessory_per_seed,prop_accessory_nonzero,seed_costs,prop_success, prepollen_costs,pack_disp_costs,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
@@
 
-write.csv(acc_costs_spp_format, file="figs2/Accessory_Costs/Table01_AccCosts_by_Species.csv",row.names=FALSE)
+write.csv(acc_costs_spp_format, file="figs2/Accessory_Costs/Table01_OLD_AccCosts_by_Species.csv",row.names=FALSE)
 ```
@@
 
-par(mfcol=c(3,1), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+par(mfrow=c(2,2), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
 options(scipen = 5)
 
-plot(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
-mod <- sma(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],accessory_per_seed>0),log="xy",method="OLS")
-#words.top.left.logxy(mod)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
-sma_abline(mod)
-abline(mod$groupsummary["Int"][[1]],1,lty=2)
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
-legend("bottomright",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=0.9,bty="n",text.font=3)
+# plot(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
+# mod <- sma(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],accessory_per_seed>0),log="xy",method="OLS")
+# plot(mod,pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5,col="black")
+# points(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,cex=1.5)
+# y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
+# #sma_abline(mod)
+# abline(mod$groupsummary["Int"][[1]],1,lty=2)
+# axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+# axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
 
-plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
+plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.015,60),ylim=c(.01,.6),cex=1.5,xaxt="n",xlab="seed size (mg)",ylab="seed set")
+mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+axis(1, at=c(0.1,1,10), labels=c("","",""),cex.axis=1)
+
+plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.015,60),ylim=c(1e-4,1000),yaxt="n",xaxt="n",xlab="embryo + endosperm size (mg)",ylab="count, scaled to plant size")
+points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
+#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
+axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
+axis(1, at=c(0.1,1,10), labels=c("","",""),cex.axis=1)
+
+mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
+mod2 <- sma(scaled_bud_count~embryo_endo_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
+mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
+
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod1,1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,2)
+legend("topright",legend=c("seed count","initiated ovules count"),col=c("black","black"),pch=c(16,21),bty="n")
+
+plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.015,60), ylab="pollen attraction costs (mg/seed)",xlab="",cex=1.5)
 y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
 mod <- sma(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
-#words.top.left.logxy(mod)
-sma_abline(mod)
-abline(mod$groupsummary["Int"][[1]],1,lty=2)
+#abline(mod$groupsummary["Int"][[1]],1,lty=2)
 axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
+axis(1, at=c(0.1,1,10), labels=c(0.1,1,10),cex.axis=1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
 
-plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
+plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.015,60), ylab="provisioning costs (mg/seed)",xlab="",cex=1.5)
 y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
 mod <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
-#words.top.left.logxy(mod)
-sma_abline(mod)
-abline(mod$groupsummary["Int"][[1]],1,lty=2)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
 axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-mtext(text="     embryo + endosperm (mg)",side=1,line=1.5,outer=TRUE,adj=0.5)
+axis(1, at=c(0.1,1,10), labels=c(0.1,1,10),cex.axis=1)
+mtext(text="     seed size (mg)",side=1,line=1.5,outer=TRUE,adj=0.5)
 
@@
 
-glance(mod)
 #Table 3. Slopes for various seed size by acc cost regressions
@@
 ```{r}
+library(smatr)
 win.metafile("figs2/Accessory_Costs/Figure06_correlations_with_plant_weight.wmf", height=5, width=10)
@@
 mod <- sma(total_weight_0~repro_inv,data=subset(SummaryInd,repro_inv>0),log="xy",method="OLS")
-abline(0,1)
+#abline(0,1)
 #words.top.left.logxy(mod)
@@
 mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
-legend("bottomright",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=0.9,bty="n",text.font=3)
+#legend("bottomright",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=0.9,bty="n",text.font=3)
 
@@
 plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,300000),yaxt="n")
+axis(2, at=c(1,100,10000),labels=c("","",""))
 abline(0,1)

### 2016-09-01 scripts/RA_figs_20160627.Rmd
mostly fixing up figures for accessory costs paper and working on manuscript

@@
     SummaryInd$leaf_repro_inv_log[i] <- -(log10(-SummaryInd$leaf_repro_inv[i]))  
+  }
+}
+
+SummaryInd$growth_leaf_no_neg_values = SummaryInd$growth_leaf
+for (i in 1:length(SummaryInd$individual)) {
+  if (SummaryInd$growth_leaf_no_neg_values[i] < 0) {
+  SummaryInd$growth_leaf_no_neg_values[i] = SummaryInd$repro_inv[i]*.01
   }
@@
 ```{r}
+pdf("figs2/RA/Figure_0_gross_leaf_inv.pdf", height=4.3, width=8)
+plot
 par(mfrow=c(1,2), cex=1, omi=c(.1,0.1,.1,.1), mai=c(0.8,.8,.1,0.2)) 
@@
 
-library(scatterplot3d)
+dev.off()
 
@@
 plot
+
 par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2))
-plot(repro_inv_log~leaf_inv_log, subset(SummaryInd), log="", col=col.spp(species),pch=16,xlim=c(-4,6),ylim=c(-1,6),
+
+plot(repro_inv~jitter(growth_leaf_no_neg_values), subset(SummaryInd), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
      xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
-axis(1, at=c(-4,-2,0,2,4,6), labels=c(-10000,-100,0,100,10000,"1000000"),cex.axis=0.9)
-axis(2, at=c(0,2,4,6), labels=c(0,100,10000,"1000000"),cex.axis=0.9)
-legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
+axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
+axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
+#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
 abline(0,1)
-text(5.6,5.8,srt=45,"RA = 0.5",cex=.6)
+text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
 abline(log10(3),1)
-text(5.13,5.8,srt=45,"RA = 0.75",cex=.6)
+text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
 abline(log10(9),1)
-text(4.67,5.8,srt=45,"RA = 0.9",cex=.6)
+text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
 abline(log10(19),1)
-text(4.33,5.8,srt=45,"RA = 0.95",cex=.6)
+text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
 abline(log10(.111),1)
-text(5.6,4.85,srt=45,"RA = 0.1",cex=.6)
+text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
 abline(log10(.010101),1)
-text(5.6,3.8,srt=45,"RA = 0.01",cex=.6)
+text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
 mtext("reproductive investment (mg)",2,line=1,outer=TRUE)
 
-plot(repro_inv_log~leaf_inv_log, subset(SummaryInd), log="", col=col.age(age),pch=16,xlim=c(-4,6),ylim=c(-1,6),
+plot(repro_inv~growth_leaf_no_neg_values, subset(SummaryInd), log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
      xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
-axis(1, at=c(-4,-2,0,2,4,6), labels=c(-10000,-100,0,100,10000,"1000000"),cex.axis=0.9)
-axis(2, at=c(0,2,4,6), labels=c(0,100,10000,"1000000"),cex.axis=0.9)
-legend("topleft",legend=labels.age(),col=col.age,pch=16, cex=.6,bty="n")
+axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
+axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
+#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
 abline(0,1)
-text(5.6,5.8,srt=45,"RA = 0.5",cex=.6)
+text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
 abline(log10(3),1)
-text(5.13,5.8,srt=45,"RA = 0.75",cex=.6)
+text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
 abline(log10(9),1)
-text(4.67,5.8,srt=45,"RA = 0.9",cex=.6)
+text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
 abline(log10(19),1)
-text(4.33,5.8,srt=45,"RA = 0.95",cex=.6)
+text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
 abline(log10(.111),1)
-text(5.6,4.85,srt=45,"RA = 0.1",cex=.6)
+text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
 abline(log10(.010101),1)
-text(5.6,3.8,srt=45,"RA = 0.01",cex=.6)
+text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
+
 mtext("leaf investment (mg)",1,line=2,outer=TRUE)

### 2016-09-05 scripts/Accessory_figs_20160218.Rmd
work on accessory cost manuscript. Have created new file name for figures, because substantial renumbering and composition of figures. Wanted to retain copy of what I had previously. In manuscript, work on introduction and parts of discussion - more still to go.

@@
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,repro_inv_per_seed,prop_failure,prop_prepollen_vs_RE, prop_dispersal_vs_RE,prop_embryo_endo_vs_RE,seed_costs,prop_prepollen_costs,prop_postpollen_costs)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,repro_inv_per_seed,seedset,prop_failure,prop_prepollen_vs_RE, prop_dispersal_vs_RE,prop_embryo_endo_vs_RE,seed_costs,prop_prepollen_costs,prop_postpollen_costs)
 acc_costs_spp$species <- labels.spp.full()
 acc_costs_spp_format <- acc_costs_spp
-for (i in c("embryo_endo_size","repro_inv_per_seed","prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","seed_costs","prop_prepollen_costs","prop_postpollen_costs")) {
+for (i in c("embryo_endo_size","repro_inv_per_seed","seedset","prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","seed_costs","prop_prepollen_costs","prop_postpollen_costs")) {
   acc_costs_spp_format[[i]] <- round(acc_costs_spp_format[[i]],digits=3)
@@
 
+#Table 3 - possible replacement
+```{r}
+ternary <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,prepollen_costs,provisioning_costs,failure_per_seed,repro_inv_per_seed)
+ternary$per_pollen <-100*ternary$prepollen_costs/ternary$repro_inv_per_seed
+ternary$per_provision <-100*ternary$provisioning_costs/ternary$repro_inv_per_seed
+ternary$per_failure <-100*ternary$failure_per_seed/ternary$repro_inv_per_seed
+
+mod_pollen <- sma(per_pollen~repro_inv_per_seed,ternary,slope.test=0,method="OLS",log="x")
+mod_provision <- sma(per_provision~repro_inv_per_seed,ternary,slope.test=0,method="OLS",log="x")
+mod_failure <- sma(per_failure~repro_inv_per_seed,ternary,slope.test=0,method="OLS",log="x")
+
+costs_per_seed <- as.data.frame("costs for pollen attraction (%)")
+costs_per_seed <- cbind(costs_per_seed,dplyr::select(mod_pollen$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+
+costs_per_seed2 <- as.data.frame("costs for provisioning (%)")
+costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_provision$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
+
+costs_per_seed2 <- as.data.frame("costs for failure (%)")
+costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_failure$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
+
+write.csv(costs_per_seed, file="figs2/Accessory_Costs/Table00_in_text_costs_per_seed.csv",row.names=FALSE)
+
+v <- sqrt(ternary$embryo_endo_size/500)
+ternary$horz <- c(1.8,1.3,1.2,-0.3,0.6,0.6,0.5,-0.2,1.3,1.7,1.4,-0.2,-0.3,-0.3)
+ternary$vert <- c(v[1]*-1.7,v[2]*1.1,v[3]*1.2,v[4],v[5]*-2.3,v[6]*4.5,v[7],v[8]*1.6,v[9],v[10]*0.2,v[11],v[12],v[13],v[14])
+ternary = ternary[with(ternary, order(-repro_inv_per_seed)), ]
+label <- 20
+
+library(ggtern)
+#win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
+#plot
+
+par(mfrow=c(1,1), cex=1, omi=c(2,2,2,2), mai=c(2,2,2,2))
+
+ggtern(data=ternary,aes(x=per_pollen,z=per_provision,y=per_failure)) +
+      geom_point(size=sqrt(ternary$repro_inv_per_seed/2),shape=20,color=col.spp(ternary$species)) +
+      theme_bw() + 
+      theme_showarrows() +
+      geom_text(label=ternary$species, color="black", hjust=ternary$horz, 
+                 vjust=ternary$vert,size=2) +
+      ggtitle("")+
+      labs(L="pollen-attraction",R="provisioning",T="failure")+
+      Tarrowlab("failure costs (%)")+
+      Larrowlab("pollen attraction costs (%)")+
+      Rarrowlab("provisioning costs (%)")+
+      theme(plot.title = element_text(size=11,face="bold"))+
+      theme(tern.axis.title.T = element_text(size=9,face="plain"))+
+      theme(tern.axis.title.L = element_text(size=9,face="plain",hjust=0,vjust=1.7))+
+      theme(tern.axis.title.R = element_text(size=9,face="plain",hjust=1,vjust=1.7))+
+      theme(tern.axis.arrow.text = element_text(size=9,face="plain"))+
+      theme(tern.axis.arrow.start= 0.2)+ 
+      theme(tern.axis.arrow.finish=0.8)
+
+dev.off()
+```
+
 #Table 2 showing seedcost breakdown into components, by species
@@
 
-plot(pack_disp_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
+plot(provisioning_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$pack_disp_costs)
 mod <- sma(postpollen_all_per_seed~seed_size,SummarySpp[["mean"]],log="xy",method="OLS")
@@
 
-plot(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(pack_disp_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
+plot(provisioning_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+mod <- lm(log10(provisioning_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
 words.top.left.logxy(mod)
-slopes <- sma(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+slopes <- sma(provisioning_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
 abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
+y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)
 acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
@@
 ```{r}
+library(smatr)
+
 par(mfrow=c(2,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
@@
 
-plot(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-slopes <- sma(pack_disp_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+plot(provisioning_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+slopes <- sma(provisioning_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
 abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)
 acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

### 2016-09-05 scripts/Accessory_figs_20160905.Rmd
work on accessory cost manuscript. Have created new file name for figures, because substantial renumbering and composition of figures. Wanted to retain copy of what I had previously. In manuscript, work on introduction and parts of discussion - more still to go.

--- 2016-08-30 scripts/Accessory_figs_20160218.Rmd
@@
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,embryo_endo_size,accessory_per_seed,prop_accessory_nonzero,seed_costs,prop_success, prepollen_costs,pack_disp_costs,failure_per_seed,prop_failure,prepollen_failure_per_seed,postpollen_aborted_per_seed, seedset)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,repro_inv_per_seed,seedset,prop_failure,prop_prepollen_vs_RE, prop_dispersal_vs_RE,prop_embryo_endo_vs_RE,seed_costs,prop_prepollen_costs,prop_postpollen_costs)
 acc_costs_spp$species <- labels.spp.full()
 acc_costs_spp_format <- acc_costs_spp
-acc_costs_spp_format$seed_size <- round(acc_costs_spp_format$seed_size,digits=3)
-acc_costs_spp_format$embryo_endo_size <- round(acc_costs_spp_format$embryo_endo_size,digits=3)
-acc_costs_spp_format$accessory_per_seed2 <- paste(round(acc_costs_spp_format$accessory_per_seed,digits=1)," (",
-                                                 round(acc_costs_spp_format$prop_accessory_nonzero,digits=2),")")
-acc_costs_spp_format$seed_costs2 <- paste(round(acc_costs_spp_format$seed_costs,digits=2)," (",
-                                                 round(acc_costs_spp_format$prop_success,digits=2),")")
-acc_costs_spp_format$prepollen_costs <- round(acc_costs_spp_format$prepollen_costs,digits=2)
-acc_costs_spp_format$pack_disp_costs <- round(acc_costs_spp_format$pack_disp_costs,digits=2)
-acc_costs_spp_format$failure_per_seed <- paste(round(acc_costs_spp_format$failure_per_seed,digits=2)," (",
-                                                 round(acc_costs_spp_format$prop_failure,digits=2),")")
-acc_costs_spp_format$prepollen_failure_per_seed <- round(acc_costs_spp_format$prepollen_failure_per_seed,digits=2)
-acc_costs_spp_format$postpollen_aborted_per_seed <- round(acc_costs_spp_format$postpollen_aborted_per_seed,digits=2)
-acc_costs_spp_format$seedset <- round(acc_costs_spp_format$seedset,digits=3)
-acc_costs_spp_format <- dplyr::select(acc_costs_spp_format,species,seed_size,embryo_endo_size,accessory_per_seed2,seed_costs2,prepollen_costs,pack_disp_costs ,failure_per_seed,prepollen_failure_per_seed,postpollen_aborted_per_seed,seedset,accessory_per_seed,seedcosts)
-acc_costs_spp_format
+for (i in c("embryo_endo_size","repro_inv_per_seed","seedset","prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","seed_costs","prop_prepollen_costs","prop_postpollen_costs")) {
+  acc_costs_spp_format[[i]] <- round(acc_costs_spp_format[[i]],digits=3)
+}
 
@@
 
-#Figure 3. Ternary diagram showing seed_costs
-```{r}
-ternary <- dplyr::select(SummarySpp[["mean"]],species,seed_size,prepollen_costs,pack_disp_costs,seed_costs,embryo_endo_size)
-ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
-ternary$post_poll <- 100-ternary$per_poll
-ternary$per_seed <-100*ternary$embryo_endo_size/ternary$seed_costs
-ternary$per_disp <-100*ternary$pack_disp_costs/ternary$seed_costs
-
-mod_poll <- sma(per_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")
-mod_seed <- sma(per_seed~seed_costs,ternary,slope.test=0,method="OLS",log="x")
-mod_disp <- sma(per_disp~seed_costs,ternary,slope.test=0,method="OLS",log="x")
-mod_post_poll <- sma(post_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")
-
-costs_per_seed <- as.data.frame("costs for seed (%)")
-costs_per_seed <- cbind(costs_per_seed,dplyr::select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-
-costs_per_seed2 <- as.data.frame("costs for pre-pollination (%)")
-costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
-
-costs_per_seed2 <- as.data.frame("costs for dispersal (%)")
-costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
-
-write.csv(costs_per_seed, file="figs2/Accessory_Costs/Table00_in_text_costs_per_seed.csv",row.names=FALSE)
-
-win.metafile("figs2/Accessory_Costs/FigureXX_seedcost_components.wmf", height=6, width=6)
-plot
-
-plot(per_seed~seed_costs,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seed_costs")
-points(per_poll~seed_costs,ternary,col="red",pch=16,cex=2)
-points(per_disp~seed_costs,ternary,col="blue",pch=16,cex=2)
-
-abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
-abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
-abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
-legend("topright",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
-v <- sqrt(ternary$seed_costs/500)
-ternary$horz <- c(1.8,1.3,1.2,-0.3,0.6,0.6,0.5,-0.2,1.3,1.7,1.4,-0.2,-0.3,-0.3)
-ternary$vert <- c(v[1]*-1.7,v[2]*1.1,v[3]*1.2,v[4],v[5]*-2.3,v[6]*4.5,v[7],v[8]*1.6,v[9],v[10]*0.2,v[11],v[12],v[13],v[14])
-ternary = ternary[with(ternary, order(-seed_costs)), ]
-label <- 20
-
-dev.off()
-library(ggtern)
-win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
-plot
-
-par(mfrow=c(1,1), cex=1, omi=c(2,2,2,2), mai=c(2,2,2,2))
-
-ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
-      geom_point(size=sqrt(ternary$seed_costs/2),shape=20,color=col.spp(ternary$species)) +
-      theme_bw() + 
-      theme_showarrows() +
-      geom_text(label=ternary$species, color="black", hjust=ternary$horz, 
-                 vjust=ternary$vert,size=2) +
-      ggtitle("Seed cost components")+
-      labs(T="embryo+endosperm",L="pre-pollination",R="provisioning")+
-      Tarrowlab("embryo + endosperm weight (%)")+
-      Larrowlab("pre-pollination costs (%)")+
-      Rarrowlab("provisioning costs (%)")+
-      theme(plot.title = element_text(size=11,face="bold"))+
-      theme(tern.axis.title.T = element_text(size=9,face="plain"))+
-      theme(tern.axis.title.L = element_text(size=9,face="plain",hjust=0,vjust=1.7))+
-      theme(tern.axis.title.R = element_text(size=9,face="plain",hjust=1,vjust=1.7))+
-      theme(tern.axis.arrow.text = element_text(size=9,face="plain"))+
-      theme(tern.axis.arrow.start= 0.2)+ 
-      theme(tern.axis.arrow.finish=0.8)
-
-dev.off()
-```
-
-#Table 2 showing seedcost breakdown into components, by species
-```{r}
-prop_seed_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_costs,prop_prepollen_costs,prop_dispersal_costs,prop_embryo_endo_costs)
-prop_seed_costs_spp$species <- labels.spp.full()
-
-mod_1 <- sma(seed_costs~prop_prepollen_costs,SummarySpp[["mean"]],log="y")
-mod_2 <- sma(seed_costs~prop_dispersal_costs,SummarySpp[["mean"]],log="y")
-mod_3 <- sma(seed_costs~prop_embryo_endo_costs,SummarySpp[["mean"]],log="y")
-
-row_x <- as.data.frame(0)
-row_1 <- as.data.frame("r2")
-row_1 <- as.data.frame(dplyr::bind_cols(row_1,row_x,as.data.frame(mod_1$groupsummary[1,3]),as.data.frame(mod_2$groupsummary[1,3]),as.data.frame(mod_3$groupsummary[1,3])))
-names(row_1) <- c("species","seed_costs","prop_prepollen_costs","prop_dispersal_costs","prop_embryo_endo_costs")
-
-row_2 <- as.data.frame("p-value")
-row_2 <- dplyr::bind_cols(row_2,row_x,as.data.frame(mod_1$groupsummary[1,4]),as.data.frame(mod_2$groupsummary[1,4]),as.data.frame(mod_3$groupsummary[1,4]))
-names(row_2) <- c("species","seed_costs","prop_prepollen_costs","prop_dispersal_costs","prop_embryo_endo_costs")
-
-row_3 <- as.data.frame("slope")
-row_3 <- dplyr::bind_cols(row_3,row_x,as.data.frame(mod_1$groupsummary[1,5]),as.data.frame(mod_2$groupsummary[1,5]),as.data.frame(mod_3$groupsummary[1,5]))
-names(row_3) <- c("species","seed_costs","prop_prepollen_costs","prop_dispersal_costs","prop_embryo_endo_costs")
-
-prop_seed_costs_spp <- dplyr::bind_rows(prop_seed_costs_spp,row_1,row_2,row_3)
-
-write.csv(prop_seed_costs_spp, file="figs2/Accessory_Costs/Table02_Prop_seed_costs_by_Species.csv",row.names=FALSE)
-```
-
-#Figure 4. Scaling of accessory costs versus seed size, by species
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure04_seed_size_acc_cost_correlations.wmf", height=5, width=15)
-plot
-
-par(mfcol=c(3,1), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
-options(scipen = 5)
-
-plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
-mod <- sma(accessory_per_seed~seed_size,data=subset(SummarySpp[["mean"]],accessory_per_seed>0),log="xy",method="OLS")
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
-sma_abline(mod)
-abline(mod$groupsummary["Int"][[1]],1,lty=2)
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
-
-plot(prepollen_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
-#y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
-mod <- sma(prepollen_costs~seed_size,SummarySpp[["mean"]],log="xy",method="OLS")
-sma_abline(mod)
-abline(mod$groupsummary["Int"][[1]],1,lty=2)
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
-
-plot(pack_disp_costs~seed_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
-mod <- sma(postpollen_all_per_seed~seed_size,SummarySpp[["mean"]],log="xy",method="OLS")
-sma_abline(mod)
-abline(mod$groupsummary["Int"][[1]],1,lty=2)
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
-dev.off()
-```
-
-#Figure 4 v2. Scaling of accessory costs versus weight of embryo + endosperm, by species
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure04_embryo_size_acc_cost_correlations.wmf", height=15, width=5)
-plot
-
-par(mfcol=c(3,1), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
-options(scipen = 5)
-
-plot(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="total accessory costs per seed (mg/seed)",xlab="",cex=1.5)
-mod <- sma(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]],accessory_per_seed>0),log="xy",method="OLS")
-#words.top.left.logxy(mod)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
-sma_abline(mod)
-abline(mod$groupsummary["Int"][[1]],1,lty=2)
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
-legend("bottomright",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=0.9,bty="n",text.font=3)
-
-plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required pollinator attraction costs per seed (mg/seed)",xlab="",cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
-mod <- sma(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
-#words.top.left.logxy(mod)
-sma_abline(mod)
-abline(mod$groupsummary["Int"][[1]],1,lty=2)
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
-
-plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,20000), xlim=c(.02,20000), ylab="required provisioning costs per seed (mg/seed)",xlab="",cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
-mod <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
-#words.top.left.logxy(mod)
-sma_abline(mod)
-abline(mod$groupsummary["Int"][[1]],1,lty=2)
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-mtext(text="     embryo + endosperm (mg)",side=1,line=1.5,outer=TRUE,adj=0.5)
-
-dev.off()
-```
-
-glance(mod)
-#Table 3. Slopes for various seed size by acc cost regressions
-#NO LONGER AN EXACT PARALLEL TO To TABLE 3 embryo version - redo if using
+#Table 2. Slopes for various embryo size by acc cost regressions
 ```{r}
@@
 
-plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
-slopes <- sma(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-words.bottom.left.logxy(mod)
-
-acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
-
-plot(prepollen_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
-mod <- lm(log10(prepollen_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
-words.bottom.left.logxy(mod)
-slopes <- sma(prepollen_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-plot(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(pack_disp_costs) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
-words.top.left.logxy(mod)
-slopes <- sma(pack_disp_costs ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$pack_disp_costs,SummarySpp[["se"]]$pack_disp_costs)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
-
-plot(failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
-words.bottom.left.logxy(mod)
-slopes <- sma(failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-plot(prepollen_all_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
-mod <- lm(log10(prepollen_all_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
-words.bottom.right.logxy(mod)
-slopes <- sma(prepollen_all_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
-#acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-# plot(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-# mod <- lm(log10(postpollen_aborted_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
-# words.top.left.logxy(mod)
-# y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
-# slopes <- sma(postpollen_aborted_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1, log="xy",method="OLS")
-# abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-# abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-# acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-#slopes <- sma(postpollen_all_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
-#acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-acc_by_species$variable = c("total accessory costs","pre-pollination costs","provisioning costs", "failed_tissues")
-
-write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_cost_seed_size_slopes.csv",row.names=FALSE)
-```
-
-#Table 3 v2. Slopes for various embryo size by acc cost regressions
-```{r}
-par(mfrow=c(2,3), cex=1, omi=c(.6,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
-options(scipen = 5)
+library(smatr)
 
@@
 acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=3)
-acc_slopes <- dplyr::select(acc_by_species,variable,r2,pval,slope2,Slope_test_p,Slope,Slope_lowCI)
+acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
 
-write.csv(acc_slopes, file="figs2/Accessory_Costs/Table03_acc_cost_embryo_size_slopes.csv",row.names=FALSE)
+write.csv(acc_slopes, file="figs2/Accessory_Costs/Table02_acc_cost_embryo_size_slopes.csv",row.names=FALSE)
 ```
 
-#Figure 5 seed count, scaled to plant size, decreases 1:1 with seed size, while bud count decreases less steeply; indication that seed count is what is actually "programmed in"
+#Table 3.correlations between repro inv and propagule inv by species
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure05_cost_of_flowers_vs_embryo_endo_size.wmf", height=5, width=15)
+yvar <- "repro_inv"
+xvar <- "propagule_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- fit$groupsummary
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=3)
+acc_slopes <- dplyr::select(results,group,n,r2,pval)
+
+write.csv(results, file="figs2/Accessory_Costs/Table03_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
+```
+
+#Table 4. correlations with total repro inv
+```{r}
+results <- as.data.frame(matrix(vector(), 0, 9,
+                dimnames=list(c(), c("xvar","variable","r2","pval","Slope","Slope_lowCI","Slope_highCI","Int","Slope_test_p"))),
+                stringsAsFactors=F)
+
+for (i in c("total_weight","failure_inv","success_inv","propagule_inv","packaging_dispersal_inv","prepollen_success_inv","fruit_inv","flower_inv")) {
+  for (j in c("repro_inv")) {
+yvar <- i
+xvar <- j
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+fit <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", log="xy",slope.test=1)
+temp <- as.data.frame(c(xvar, yvar,dplyr::select(fit$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Slope_test_p,n)))
+colnames(temp)[2]<- "variable"
+colnames(temp)[1]<- "xvar"
+results <- bind_rows(results, temp)
+  }
+}
+
+results$slope2 <- paste(format(results$Slope,digits=3)," (",format(results$Slope_lowCI,digits=3)," - ",format(results$Slope_highCI,digits=3),")",sep="")
+
+results$r2 <- format(results$r2,digits=3)
+results$pval <- format(results$pval,digits=3)
+results$Slope_test_p <- format(results$Slope_test_p,digits=3)
+#results  <- dplyr::select(results,variable,n,r2,pval,slope2,Slope_test_p)
+results  <- dplyr::select(results,variable,n,r2,pval)
+
+write.csv(results, file="figs2/Accessory_Costs/Table04_correlations_with_repro_inv.csv",row.names=FALSE)
+```
+
+#Figure 2. Scaling of accessory costs versus weight of embryo + endosperm, by species
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure04_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
 plot
 
-par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
-options(scipen = 4)
+par(mfrow=c(2,2), cex=1, omi=c(1,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+options(scipen = 5)
 
-plot(seedset~seed_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,1000),ylim=c(.01,.3),cex=1.5,xaxt="n",xlab="seed size (mg)",ylab="seed set")
-mod <- sma(seedset~seed_size,SummarySpp[["mean"]],log="xy", method="OLS")
-sma_abline(mod)
-y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
-legend("bottomleft",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=.9,bty="n",text.font=3)
+plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.02,5000),ylim=c(.004,.5),cex=1.5,xaxt="n",xlab="",ylab="")
+mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
+mtext("seed set",2,line=2.3)
+extra.bottom.left.logxy("a",2,1.2)
 
-#species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
-plot(prop_prepollen_costs~seedset,SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.01,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
-mod <- sma(prop_prepollen_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
-y.error.bars(SummarySpp[["mean"]]$seedset,SummarySpp[["mean"]]$prop_prepollen_costs,SummarySpp[["se"]]$prop_prepollen_costs)
-sma_abline(mod)
-sma_sum(mod)
-text(10^((0.99*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
-     paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
-axis(2, at=c(-0.2,0,.2,.4,.6,.8,1), labels=c("",0.0,0.2,0.4,0.6,0.8,""),cex.axis=1)
+plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.02,5000),ylim=c(1e-4,1000),yaxt="n",xaxt="n",ylab="")
+points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
+#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
+axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
+extra.bottom.left.logxy("b",2,1.2)
+mtext("count, scaled to plant size",2,line=2.3)
 
-#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
-plot(scaled_seed_count~seed_size,SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,1000),ylim=c(1e-6,10),yaxt="n",xaxt="n",xlab="seed size (mg)",ylab="count, scaled to plant size")
-points(scaled_bud_count~seed_size,SummaryInd,pch=21,col=col.spp(species))
-#points(scaled_failure_count~seed_size,SummaryInd,pch=2,col=col.spp(species))
-axis(2, at=c(0.000001,0.0001,0.01,1), labels=c(0.000001,0.0001,0.01,1),cex.axis=0.9)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
+mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
+mod2 <- sma(scaled_bud_count~embryo_endo_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
+mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
 
-mod1 <- sma(scaled_seed_count~seed_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
-mod2 <- sma(scaled_bud_count~seed_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
-mod3 <- sma(scaled_failure_count~seed_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
-sma_abline(mod1)
-abline(mod2$groupsummary["Int"][[1]],mod2$groupsummary["Slope"][[1]],col="blue")
-abline(mod3$groupsummary["Int"][[1]],mod3$groupsummary["Slope"][[1]],col="red")
-legend("topright",legend=c("seed count","total bud count","failed flower count"),col=c("black","blue","red"),pch=c(16,21,8),bty="n")
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod1,1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,2)
+legend("topright",legend=c("seed count","initiated ovules count"),col=c("black","black"),pch=c(16,21),bty="n")
+
+plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.02,5000), ylab="",xlab="",cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
+mod <- sma(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
+#abline(mod$groupsummary["Int"][[1]],1,lty=2)
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+mtext("pollen attraction costs (mg/seed)",2,line=2.3)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+extra.top.left.logxy("c",2,1.2)
+
+plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.02,5000), ylab="",xlab="",cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
+mod <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+mtext("provisioning costs (mg/seed)",2,line=2.3)
+extra.top.left.logxy("d",2,1.2)
+
+mtext(text="     seed size (mg)",side=1,line=1.5,outer=TRUE,adj=0.5)
+mtext(text="                     parental pessimist",line=3,side=1,adj=0,outer=TRUE,font=3)
+mtext(text="parental optimist    ",line=3,side=1,adj=1,outer=TRUE,font=3)
 
@@
 
-#Figure 5, using embryo + endosperm
+#Figure 3. Correlations of various reproductive investment categories against plant weight
 ```{r}
-
-win.metafile("figs2/Accessory_Costs/Figure05_cost_of_flowers_vs_embryo_endo_size.wmf", height=5, width=15)
+win.metafile("figs2/Accessory_Costs/Figure03_correlations_with_plant_weight.wmf", height=5, width=10)
 plot
 
-par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.1,.05), mai=c(1,1,.1,.05))
+par(mfrow=c(1,2), cex=1, omi=c(.1,.6,.1,.05), mai=c(.8,.1,.1,.05))
 options(scipen = 4)
 
-plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.01,100),ylim=c(.004,.3),cex=1.5,xaxt="n",yaxt="n",xlab="embryo + endosperm size (mg)",ylab="seed set")
-mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
-sma_abline(mod)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
-text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.98*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
-axis(2, at=c(0.005,0.01,0.02,0.05,.1,.2), labels=c(.005,.01,.02,.05,.1,.2),cex.axis=0.9)
-legend("bottomleft",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=0.9,bty="n",text.font=3)
-mod
+library(smatr)
 
-#put together, big-seeded plants produce lots more buds than predicted from 1:1 relationship, but the "correct" number of seeds
-plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.01,100),ylim=c(1e-4,1000),yaxt="n",xaxt="n",xlab="embryo + endosperm size (mg)",ylab="count, scaled to plant size")
-points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
-#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
-axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=0.9)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.9)
+yvar <- "repro_inv"
+xvar <- "propagule_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
-mod2 <- sma(scaled_bud_count~embryo_endo_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
-mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
-abline(mod1$groupsummary["Int"][[1]],mod1$groupsummary["Slope"][[1]],col="black",lwd=2)
-abline(mod2$groupsummary["Int"][[1]],mod2$groupsummary["Slope"][[1]],col="blue",lwd=2)
-abline(mod3$groupsummary["Int"][[1]],mod3$groupsummary["Slope"][[1]],col="red",lwd=2)
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,300000), xlab="",ylab="",lty=results$linetype,pch=16)
+abline(0,1)
+mod <- sma(propagule_inv~repro_inv,data=subset(SummaryInd,propagule_inv>0),log="xy",method="OLS")
+mtext(text="total propagule investment (mg)",side=1,line=2.2,outer=FALSE)
+mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
+extra.top.left.logxy("a",2,1.2)
 
-legend("topright",legend=c("seed count","bud count","failed flower count"),col=c("black","blue","red"),pch=c(16,1,NA),bty="n",lty=c(1,1,1))
+xvar <- "flower_inv"
+yvar <- "repro_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-#species that abort a disprortionate # of buds can do so because the relative cost of buds (relative to seeds, dispersal) is small
-plot(jitter(prop_prepollen_costs)~jitter(seedset),SummarySpp[["mean"]],pch=16,log="x",col=col.spp(species),ylim=c(-.2,1),xlim=c(.004,.3),cex=1.5,yaxt="n",ylab="pre-pollination costs (proportion of total seed costs)",xlab="seed set")
-mod <- sma(prop_prepollen_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
-y.error.bars(SummarySpp[["mean"]]$seedset,SummarySpp[["mean"]]$prop_prepollen_costs,SummarySpp[["se"]]$prop_prepollen_costs)
-sma_abline(mod)
-sma_sum(mod)
-text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),
- paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
-axis(2, at=c(-0.2,0,.2,.4,.6,.8,1), labels=c("",0.0,0.2,0.4,0.6,0.8,""),cex.axis=1)
-
-Fig5_data <- dplyr::select(mod1$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
-Fig5_data <- dplyr::bind_rows(Fig5_data,dplyr::select(mod2$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-Fig5_data <- dplyr::bind_rows(Fig5_data,dplyr::select(mod3$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-Fig5_data$variable <- c("seed count","bud count","failure count")
-write.csv(Fig5_data, file="figs2/Accessory_Costs/Figure05_data_slopes.csv",row.names=FALSE)
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
+results <- lines(fit$groupsummary)
+plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,300000),yaxt="n")
+axis(2, at=c(1,100,10000),labels=c("","",""))
+abline(0,1)
+mtext(text="flower weight * bud count (mg)",side=1,line=2.2,outer=FALSE)
+extra.top.left.logxy("b",2,1.2)
 
@@
 
-#Table 4.correlations between seedset and accessory costs by species
+#Supplementary Table. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
 ```{r}
-yvar <- "accessory_per_seed"
-xvar <- "seedset"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope=-1)
-results <- fit$groupsummary
-
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="seedset (seeds:ovule)",ylab="total accessory costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000))
-
-results$slope2 <- paste(format(results$Slope,digits=3)," (",format(results$Slope_lowCI,digits=3)," - ",format(results$Slope_highCI,digits=3),")",sep="")
-
-results$r2 <- format(results$r2,digits=2)
-results$pval <- format(results$pval,digits=2)
-results$Slope_test_p <- format(results$Slope_test_p,digits=3)
-results$full_name <- labels.spp.full(results$group)
-results$seed_size <- SummarySpp[["mean"]]$embryo_endo_size
-results <- dplyr::select(results,group,full_name,n, r2,pval,slope2,Slope_test_p,Slope,seed_size)
-write.csv(results, file="figs2/Accessory_Costs/Table04_eacc_cost_vs_seedset_by_spp.csv",row.names=FALSE)
-```
-
-#Table 5. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
-```{r}
-win.metafile("figs2/Accessory_Costs/FigureXX_RE_RA_size_age_patterns.wmf", height=10, width=10)
+win.metafile("figs2/Accessory_Costs/Figure_SXX_RE_RA_size_age_patterns.wmf", height=10, width=10)
 plot
@@
 
-#Table 6.correlations between repro inv and propagule inv by species
-```{r}
-yvar <- "repro_inv"
-xvar <- "propagule_inv"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- fit$groupsummary
-results$r2 <- format(results$r2,digits=2)
-results$pval <- format(results$pval,digits=3)
-acc_slopes <- dplyr::select(results,group,n,r2,pval)
-
-write.csv(results, file="figs2/Accessory_Costs/Table06_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
-```
-
-#Table 6.correlations between repro inv and flower inv by species (noted in Discussiong)
+#Table X.correlations between repro inv and flower inv by species (noted in Discussiong)
 ```{r}
@@
 write.csv(results, file="figs2/Accessory_Costs/Table07_EXTRA_correlations_with_repro_inv.csv",row.names=FALSE)
-```
-
-#Table 7. correlations with total repro inv
-```{r}
-results <- as.data.frame(matrix(vector(), 0, 9,
-                dimnames=list(c(), c("xvar","variable","r2","pval","Slope","Slope_lowCI","Slope_highCI","Int","Slope_test_p"))),
-                stringsAsFactors=F)
-
-for (i in c("total_weight","failure_inv","success_inv","propagule_inv","packaging_dispersal_inv","prepollen_success_inv","fruit_inv","flower_inv")) {
-  for (j in c("repro_inv")) {
-yvar <- i
-xvar <- j
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-fit <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", log="xy",slope.test=1)
-temp <- as.data.frame(c(xvar, yvar,dplyr::select(fit$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Slope_test_p,n)))
-colnames(temp)[2]<- "variable"
-colnames(temp)[1]<- "xvar"
-results <- bind_rows(results, temp)
-  }
-}
-
-results$slope2 <- paste(format(results$Slope,digits=3)," (",format(results$Slope_lowCI,digits=3)," - ",format(results$Slope_highCI,digits=3),")",sep="")
-
-results$r2 <- format(results$r2,digits=3)
-results$pval <- format(results$pval,digits=3)
-results$Slope_test_p <- format(results$Slope_test_p,digits=3)
-results  <- dplyr::select(results,variable,n,r2,pval,slope2,Slope_test_p)
-
-write.csv(results, file="figs2/Accessory_Costs/Table07_correlations_with_repro_inv.csv",row.names=FALSE)
-```
-
-#Figure 6. Correlations of various reproductive investment categories against plant weight
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure06_correlations_with_plant_weight.wmf", height=5, width=10)
-plot
-
-par(mfrow=c(1,2), cex=1, omi=c(.1,.6,.1,.05), mai=c(.8,.1,.1,.05))
-options(scipen = 4)
-
-xvar <- "total_weight_0"
-yvar <- "repro_inv"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-#plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,10000000),xlab="",ylab="",lty=results$linetype,pch=16)
-mod <- sma(total_weight_0~repro_inv,data=subset(SummaryInd,repro_inv>0),log="xy",method="OLS")
-abline(0,1)
-#words.top.left.logxy(mod)
-#mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
-#mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
-
-yvar <- "repro_inv"
-xvar <- "propagule_inv"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,300000), xlab="",ylab="",lty=results$linetype,pch=16)
-abline(0,1)
-mod <- sma(propagule_inv~repro_inv,data=subset(SummaryInd,propagule_inv>0),log="xy",method="OLS")
-mtext(text="investment in propagules (mg)",side=1,line=2,outer=FALSE)
-mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
-legend("bottomright",legend=labels.spp.genus(),col=col.spp(),pch=16, cex=0.9,bty="n",text.font=3)
-
-xvar <- "repro_all_count"
-yvar <- "repro_inv"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
-results <- lines(fit$groupsummary)
-#plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
-#mtext(text="buds initiated",side=1,line=2,outer=FALSE)
-
-xvar <- "flower_inv"
-yvar <- "repro_inv"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
-results <- lines(fit$groupsummary)
-plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,300000),yaxt="n")
-abline(0,1)
-mtext(text="flower weight * bud count (mg)",side=1,line=2,outer=FALSE)
-
-dev.off()
-
-xvar <- "diameter_0"
-yvar <- "repro_all_count"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
-results <- lines(fit$groupsummary)
-plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,yaxt="n")
-points((repro_inv)~(diameter_0),SummarySpp[["mean"]],cex=2,col=col.spp(species),pch=16)
-
-abline(0,1)
-#mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
-
-xvar <- "diameter_0"
-yvar <- "propagule_inv"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
-results <- lines(fit$groupsummary)
-plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,yaxt="n")
-points((propagule_inv)~(diameter_0),SummarySpp[["mean"]],cex=2,col=col.spp(species),pch=16)
-
-abline(0,1)
-mtext(text="total plant weight (mg)",side=1,line=2,outer=FALSE)
 ```

### 2016-09-05 R/figures.R

@@ -424,32 +424,37 @@ words.top.left.logy <- function (x) {
   text(((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.98*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),summary(mod)[1],cex=.7,adj=0)
 }
 
-extra.top.left.logxy <- function (words,fontx) {
-  text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.96*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),words,adj=0,cex=.75,font=fontx)
+extra.top.left.logxy <- function (words,fontx,cexx) {
+  text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),10^((0.96*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),words,adj=0,font=fontx,cex=cexx)
 }
 
 extra.top.left.logx <- function (words,fontx) {
-  text(10^((0.01*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.96*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),words,adj=0,cex=.75,font=fontx)
+  text(10^((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.96*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),words,adj=0,cex=.75,font=fontx)
 }
 
 extra.top.left <- function (words) {
-  text(((0.01*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.96*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),words,adj=0,cex=.75)
+  text(((0.02*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.96*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),words,adj=0,cex=.75)
 }
 
-extra.bottom.left.logx <- function (words,fontx) {
-  text(10^((0.01*(par("usr")[2]-par("usr")[1]))+par("usr")[1]),((0.04*(par("usr")[4]-par("usr")[3]))+par("usr")[3]),words,adj=0,cex=.75,font=fontx)
+extra.bottom.left.logxy <- function (words,fontx,cexx) {
[…]

### 2016-09-09 scripts/Accessory_figs_20160905.Rmd
continued work on all different parts of Accessory Costs manuscript

@@
+plot(scaled_seed_count ~ scaled_bud_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),xlim=c(.1,5000),ylim=c(0.001,50))
+mod <- sma(scaled_seed_count ~ scaled_bud_count, SummarySpp[["mean"]],log="xy",slope=1,method="OLS")
+summary(mod)
+line_function_log_xy(SummarySpp[["mean"]]$scaled_bud_count,mod,1)
+line_function_log_xy_zero(SummarySpp[["mean"]]$scaled_bud_count,mod,1)
+
+plot(scaled_bud_count ~ seedset, SummarySpp[["mean"]],log="y",pch=16,col=col.spp(species))
+
 #Data 0. means, counts to include in manuscript
@@
 
+#proportion energy invested in accessory tissues unrelated to seedsize
+mod <- sma(seed_size ~ prop_accessory_ee, data=subset(SummarySpp[["mean"]],species!="BAER"),method="OLS", log="y",slope.test=1)
+summary(mod)
+plot(seed_size ~ prop_accessory_ee, SummarySpp[["mean"]],log="y",pch=16,col=col.spp(species))
+
 #more failure = lower seedset across species - in discussion
@@
 plot(repro_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
+
+#seedset by pollen attraction
+mod <- sma(prop_prepollen_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
+summary(mod)
 
@@
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,repro_inv_per_seed,seedset,prop_failure,prop_prepollen_vs_RE, prop_dispersal_vs_RE,prop_embryo_endo_vs_RE,seed_costs,prop_prepollen_costs,prop_postpollen_costs)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,seedset,repro_inv_per_seed,prop_failure,prop_prepollen_vs_RE, prop_dispersal_vs_RE,prop_embryo_endo_vs_RE,seed_costs,prop_prepollen_costs,prop_postpollen_costs,embryo_endo_size,pack_disp_costs,prepollen_costs,failure_inv,repro_inv,seed_count)
 acc_costs_spp$species <- labels.spp.full()
 acc_costs_spp_format <- acc_costs_spp
-for (i in c("embryo_endo_size","repro_inv_per_seed","seedset","prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","seed_costs","prop_prepollen_costs","prop_postpollen_costs")) {
+for (i in c("embryo_endo_size","seedset","repro_inv_per_seed","prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","seed_costs","prop_prepollen_costs","prop_postpollen_costs")) {
   acc_costs_spp_format[[i]] <- round(acc_costs_spp_format[[i]],digits=3)
@@
 
+for (i in c("prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","prop_prepollen_costs","prop_postpollen_costs")) {
+  acc_costs_spp_format[[i]] <- round(100*acc_costs_spp_format[[i]],digits=1)
+}
+
 write.csv(acc_costs_spp_format, file="figs2/Accessory_Costs/Table01_AccCosts_by_Species.csv",row.names=FALSE)
+```
+
+#Table 1. color dots
+```{r}
+win.metafile("figs2/Accessory_Costs/Table01_dots.wmf", height=3, width=.2)
+plot
+
+par(mfrow=c(1,1), cex=1, omi=c(.01,.01,.01,.01), mai=c(.01,.01,.01,.01)) 
+dots <- dplyr::select(SummarySpp[["mean"]],species)
+dots$x <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1)
+dots$y <- c(28,26,24,22,20,18,16,14,12,10,8,6,4,2)
+plot(y~x,dots,cex=1.5,pch=16,xlab="",ylab="",xaxt="n",yaxt="n",col=col.spp(dots$species),bty="n",xlim=c(0.8,1.2),ylim=c(1.8,28.2))
+
+dev.off()
 ```
@@
 acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
+
+plot(seed_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="seed costs (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seed_costs,SummarySpp[["se"]]$seed_costs)
+slopes <- sma(seed_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,lty=2)
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
@@
 
+plot(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
+slopes <- sma(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
+abline(slopes$groupsummary["Int"][[1]],1,lty=2)
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
 plot(prepollen_failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
@@
 
-acc_by_species$variable = c("total accessory costs","pre-pollination costs","provisioning costs", "failed tissues costs","failed pre-pollination costs","failed provisioning costs")
+acc_by_species$variable = c("total accessory costs","seed costs","pollen attraction costs","provisioning costs", "failed tissues costs","all pre-pollen costs per seed","failed pre-pollination costs","failed provisioning costs")
 
@@
 
-#Table 3.correlations between repro inv and propagule inv by species
+#Table Supplementary.correlations between repro inv and propagule inv by species
 ```{r}
@@
 acc_slopes <- dplyr::select(results,group,n,r2,pval)
+names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule")
 
-write.csv(results, file="figs2/Accessory_Costs/Table03_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
+yvar <- "repro_inv"
+xvar <- "flower_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+results <- fit$groupsummary
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=3)
+acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
+names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
+acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
+
+write.csv(acc_slopes, file="figs2/Accessory_Costs/Table_S3_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
 ```
 
-#Table 4. correlations with total repro inv
+#Table 3. correlations with total repro inv
 ```{r}
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table04_correlations_with_repro_inv.csv",row.names=FALSE)
+write.csv(results, file="figs2/Accessory_Costs/Table03_correlations_with_repro_inv.csv",row.names=FALSE)
 ```
+
+plot(scaled_seed_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species))
+points(scaled_bud_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=21,col=col.spp(species))
+#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
+axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
+axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
+mtext("count, scaled to plant size",2,line=2.3)
+mod1 <- sma(scaled_seed_count~prop_prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_seed_count!=0),log="y",slope=-1,method="OLS")
+mod2 <- sma(scaled_bud_count~prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_bud_count!=0),log="xy",slope=3.23,method="OLS")
+mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
+
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod1,1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,2)
+legend("topright",legend=c("seed count","initiated ovules count"),col=c("black","black"),pch=c(16,21),bty="n")
+
+summary(mod1)
+summary(mod2)
+extra.top.left.logxy("a",2,1.2)
 
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure04_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
+win.metafile("figs2/Accessory_Costs/Figure02_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
 plot
 
-par(mfrow=c(2,2), cex=1, omi=c(1,.1,.05,.05), mai=c(.1,.8,.05,.05)) 
+par(mfrow=c(2,2), cex=1, omi=c(1,.1,.05,.05), mai=c(.2,.8,.1,.05)) 
 options(scipen = 5)
 
-plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.02,5000),ylim=c(.004,.5),cex=1.5,xaxt="n",xlab="",ylab="")
-mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
-text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
-axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
-mtext("seed set",2,line=2.3)
-extra.bottom.left.logxy("a",2,1.2)
-
-plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.02,5000),ylim=c(1e-4,1000),yaxt="n",xaxt="n",ylab="")
+plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,1000),yaxt="n",xaxt="n",ylab="")
 points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
@@
 axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c("","",""),cex.axis=1)
-extra.bottom.left.logxy("b",2,1.2)
+axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
 mtext("count, scaled to plant size",2,line=2.3)
-
 mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
@@
 
-plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.02,5000), ylab="",xlab="",cex=1.5)
+extra.top.left.logxy("a",2,1.2)
+
+plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.002,500),ylim=c(.004,.6),cex=1.5,xaxt="n",xlab="",ylab="")
+mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+#text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
+mtext("seed set",2,line=2.3)
+extra.top.left.logxy("b",2,1.2)
+
+plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
 y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
@@
 axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
 mtext("pollen attraction costs (mg/seed)",2,line=2.3)
@@
 
-plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.02,5000), ylab="",xlab="",cex=1.5)
+plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
 y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
@@
 axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
 mtext("provisioning costs (mg/seed)",2,line=2.3)

### 2016-09-19 scripts/Accessory_figs_20160905.Rmd
work on accessory costs ms

@@
-plot(scaled_seed_count ~ scaled_bud_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),xlim=c(.1,5000),ylim=c(0.001,50))
-mod <- sma(scaled_seed_count ~ scaled_bud_count, SummarySpp[["mean"]],log="xy",slope=1,method="OLS")
+pdf("figs2/Accessory_Costs/scaled_ovule count.pdf", height=6, width=6)
+plot
+
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.1,.05)) 
+options(scipen = 5)
+
+mod1 <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]],species!="PEPU"),method="OLS", log="xy",slope.test=-1)
+mod2 <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
+plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,200),ylab="scaled count",xlim=c(.01,100),cex=1.5)
+points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
+line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod1,3)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,1)
+#points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
+arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0)
+
+#mod <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
+summary(mod1)
+plot(success_inv ~ prepollen_success_inv, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),xlim=c(10,100000),ylim=c(10,100000))
+mod <- sma(success_inv ~ prepollen_success_inv, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=1)
+line_function_log_xy(SummarySpp[["mean"]]$prepollen_success_inv,mod,1)
+line_function_log_xy_zero(SummarySpp[["mean"]]$prepollen_success_inv,mod,1)
+
+SummaryInd$ovule_ratio <- SummaryInd$prepollen_costs/SummaryInd$embryo_endo_size
+
+SummarySpp[["mean"]]$pre_pollen_all_inv_scaled <- SummarySpp[["mean"]]$prepollen_all_inv /SummarySpp[["mean"]]$leaf_area
+
+plot(leaf_area~prepollen_all_inv,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
+mod <- sma(leaf_area~prepollen_all_inv,SummarySpp[["mean"]],log="xy",slope=1, method="OLS")
 summary(mod)
-line_function_log_xy(SummarySpp[["mean"]]$scaled_bud_count,mod,1)
-line_function_log_xy_zero(SummarySpp[["mean"]]$scaled_bud_count,mod,1)
 
-plot(scaled_bud_count ~ seedset, SummarySpp[["mean"]],log="y",pch=16,col=col.spp(species))
+plot(pre_pollen_all_inv_scaled~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
+mod <- sma(pre_pollen_all_inv_scaled~embryo_endo_size,SummarySpp[["mean"]],log="xy",slope=1, method="OLS")
+
+dev.off()
 
@@
 
-#proportion energy invested in accessory tissues unrelated to seedsize
-mod <- sma(seed_size ~ prop_accessory_ee, data=subset(SummarySpp[["mean"]],species!="BAER"),method="OLS", log="y",slope.test=1)
+#RE per seed unrelated to seedsize
+mod <- sma(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
 summary(mod)
-plot(seed_size ~ prop_accessory_ee, SummarySpp[["mean"]],log="y",pch=16,col=col.spp(species))
+plot(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+#energy invested in accessory tissues unrelated to seedsize
+mod <- sma(accessory_per_seed_using_ee ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=1)
+summary(mod)
+plot(accessory_per_seed_using_ee ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+#total seed costs unrelated to seedsize
+mod <- sma(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
+summary(mod)
+plot(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+#failure per seed unrelated to seedsize
+mod <- sma(failure_per_seed ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=1)
+summary(mod)
+plot(failure_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(prop_prepollen_costs ~ seedset, data=subset(SummarySpp[["mean"]]),method="OLS", log="x",slope.test=1)
+summary(mod)
+plot(prop_prepollen_costs ~ seedset, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))
+
+mod <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
+summary(mod)
+plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
+summary(mod)
+plot(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(scaled_seed_count ~ provisioning_costs, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
+summary(mod)
+plot(scaled_seed_count ~ provisioning_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(scaled_seed_count ~ seed_costs, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=-1)
+summary(mod)
+plot(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(prepollen_all_per_seed ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="OLS", log="xy",slope.test=1)
+summary(mod)
+plot(prepollen_failure_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.02,10000))
+points(prepollen_costs~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species))
 
@@
 plot(total_weight_0 ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+#scaled ovule production vs prop pollen attraction  - all species
+mod <- sma(prop_prepollen_costs~scaled_ovule_count,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
+summary(mod)
+plot(prop_prepollen_costs ~ scaled_ovule_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 plot(scaled_seed_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species))
-points(scaled_bud_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=21,col=col.spp(species))
+points(scaled_ovule_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=21,col=col.spp(species))
 #points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
@@
 mod1 <- sma(scaled_seed_count~prop_prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_seed_count!=0),log="y",slope=-1,method="OLS")
-mod2 <- sma(scaled_bud_count~prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_bud_count!=0),log="xy",slope=3.23,method="OLS")
+mod2 <- sma(scaled_ovule_count~prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_ovule_count!=0),log="xy",slope=3.23,method="OLS")
 mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
@@
 plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,1000),yaxt="n",xaxt="n",ylab="")
-points(scaled_bud_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
+points(scaled_ovule_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
 #points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
@@
 mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
-mod2 <- sma(scaled_bud_count~embryo_endo_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
+mod2 <- sma(scaled_ovule_count~embryo_endo_size,data=subset(SummaryInd,scaled_ovule_count!=0),log="xy",slope=-1,method="OLS")
 mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")

### 2016-09-19 scripts/starting_commands.R

@@ -7,6 +7,7 @@ SummarySppAge <- readRDS("export/SummarySppAge.rds")
 HarvestData <- readRDS("export/HarvestData.rds")
 InvestmentByPart <- readRDS("export/Investment_FD_all.rds")
 PartsSummary <- readRDS("export/PartsSummary_all.rds")
+library(smatr)
 
 source("R/figures.R")
 

### 2016-09-20 scripts/Accessory_figs_20160905.Rmd
work on accessory cost ms among other things, switching to method SMA

--- 2016-09-09 scripts/Accessory_figs_20160905.Rmd
@@
-plot(scaled_seed_count ~ scaled_bud_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),xlim=c(.1,5000),ylim=c(0.001,50))
-mod <- sma(scaled_seed_count ~ scaled_bud_count, SummarySpp[["mean"]],log="xy",slope=1,method="OLS")
+win.metafile("figs2/Accessory_Costs/scaled_ovule count.wmf", height=6, width=6)
+plot
+
+par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.1,.05)) 
+options(scipen = 5)
+
+mod2 <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+mod1 <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=mod2$groupsummary["Slope"][[1]])
+
+plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,200),ylab="scaled count",xlim=c(.01,100),cex=1.5)
+points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
+line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod1,3)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,1)
+#points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
+arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=1,length=.15)
+
+dev.off()
+
+summary(mod2)
+summary(mod1)
+
+mod1 <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+mod2 <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,200),ylab="scaled count",xlim=c(.01,100),cex=1.5)
+points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
+line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod1,3)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,1)
+#points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
+arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0)
+
+plot(prop_prepollen_costs~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),cex=1.5,pch=16,col=col.spp(species),log="x")
+mod <- sma(prop_prepollen_costs~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),log="x",method="SMA")
 summary(mod)
-line_function_log_xy(SummarySpp[["mean"]]$scaled_bud_count,mod,1)
-line_function_log_xy_zero(SummarySpp[["mean"]]$scaled_bud_count,mod,1)
 
-plot(scaled_bud_count ~ seedset, SummarySpp[["mean"]],log="y",pch=16,col=col.spp(species))
+plot(prop_prepollen_costs~ seedset, data=subset(SummarySpp[["mean"]]),cex=1.5,pch=16,col=col.spp(species),log="x")
+mod <- sma(prop_prepollen_costs~ seedset, data=subset(SummarySpp[["mean"]]),log="x",method="SMA")
+summary(mod)
+
+#mod <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+summary(mod1)
+plot(success_inv ~ prepollen_success_inv, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),xlim=c(10,100000),ylim=c(10,100000))
+mod <- sma(success_inv ~ prepollen_success_inv, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
+line_function_log_xy(SummarySpp[["mean"]]$prepollen_success_inv,mod,1)
+line_function_log_xy_zero(SummarySpp[["mean"]]$prepollen_success_inv,mod,1)
+
+SummaryInd$ovule_ratio <- SummaryInd$prepollen_costs/SummaryInd$embryo_endo_size
+
+SummarySpp[["mean"]]$pre_pollen_all_inv_scaled <- SummarySpp[["mean"]]$prepollen_all_inv /SummarySpp[["mean"]]$leaf_area
+
+plot(leaf_area~prepollen_all_inv,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
+mod <- sma(leaf_area~prepollen_all_inv,SummarySpp[["mean"]],log="xy",slope=1, method="SMA")
+summary(mod)
+
+plot(pre_pollen_all_inv_scaled~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
+mod <- sma(pre_pollen_all_inv_scaled~embryo_endo_size,SummarySpp[["mean"]],log="xy",slope=1, method="SMA")
+
+dev.off()
 
@@
 #relationship between plant weight and number of ovules initiated - bigger plants produce proportionally fewer buds
-mod <- sma(repro_all_count~total_weight,SummaryInd,method="OLS",log="xy",slope=1)
+mod <- sma(repro_all_count~total_weight,SummaryInd,method="SMA",log="xy",slope=1)
 summary(mod)
@@
 #there is no relationship between the proportion of energy going to seeds and the total energy for seedcosts
-mod <- sma(seed_costs~prop_seed_costs,SummarySpp[["mean"]],method="OLS",log="y")
+mod <- sma(seed_costs~prop_seed_costs,SummarySpp[["mean"]],method="SMA",log="y")
 summary(mod)
 
-#proportion energy invested in accessory tissues unrelated to seedsize
-mod <- sma(seed_size ~ prop_accessory_ee, data=subset(SummarySpp[["mean"]],species!="BAER"),method="OLS", log="y",slope.test=1)
+#RE per seed unrelated to seedsize
+mod <- sma(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(seed_size ~ prop_accessory_ee, SummarySpp[["mean"]],log="y",pch=16,col=col.spp(species))
+plot(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+#energy invested in accessory tissues unrelated to seedsize
+mod <- sma(accessory_per_seed_using_ee ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
+summary(mod)
+plot(accessory_per_seed_using_ee ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+#total seed costs unrelated to seedsize
+mod <- sma(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
+summary(mod)
+plot(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+#failure per seed unrelated to seedsize
+mod <- sma(failure_per_seed ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
+summary(mod)
+plot(failure_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(prop_prepollen_costs ~ seedset, data=subset(SummarySpp[["mean"]]),method="SMA", log="x",slope.test=1)
+summary(mod)
+plot(prop_prepollen_costs ~ seedset, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))
+
+mod <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+summary(mod)
+plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+summary(mod)
+plot(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(scaled_seed_count ~ provisioning_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+summary(mod)
+plot(scaled_seed_count ~ provisioning_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(scaled_seed_count ~ seed_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+summary(mod)
+plot(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(prepollen_all_per_seed ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
+summary(mod)
+plot(prepollen_failure_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.02,10000))
+points(prepollen_costs~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species))
 
 #more failure = lower seedset across species - in discussion
-mod <- sma(seedset ~ prop_failure, data=subset(SummarySpp[["mean"]],species!="BAER"),method="OLS", log="",slope.test=1)
+mod <- sma(seedset ~ prop_failure, data=subset(SummarySpp[["mean"]],species!="BAER"),method="SMA", log="",slope.test=1)
 summary(mod)
@@
 #seed size by propagule investment - all species
-mod <- sma(propagule_inv ~ embryo_endo_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
+mod <- sma(propagule_inv ~ embryo_endo_size, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
 summary(mod)
@@
 #seed size by propagule investment - without EPMI
-mod <- sma(propagule_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="OLS", log="xy",slope.test=1)
+mod <- sma(propagule_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="SMA", log="xy",slope.test=1)
 summary(mod)
@@
 #seed size by reproductive investment - all species
-mod <- sma(repro_inv ~ embryo_endo_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
+mod <- sma(repro_inv ~ embryo_endo_size, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
 summary(mod)
@@
 #seed size by reproductive investment - without EPMI
-mod <- sma(repro_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="OLS", log="xy",slope.test=1)
+mod <- sma(repro_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="SMA", log="xy",slope.test=1)
 summary(mod)
@@
 #seedset by pollen attraction
-mod <- sma(prop_prepollen_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="OLS")
+mod <- sma(prop_prepollen_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
 summary(mod)
@@
 #seed size by total weight - all species
-mod <- sma(total_weight_0 ~ embryo_endo_size, SummarySpp[["mean"]],method="OLS", log="xy",slope.test=1)
+mod <- sma(total_weight_0 ~ embryo_endo_size, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
 summary(mod)
 plot(total_weight_0 ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+
+#scaled ovule production vs prop pollen attraction  - all species
+mod <- sma(prop_prepollen_costs~scaled_ovule_count,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
+summary(mod)
+plot(prop_prepollen_costs ~ scaled_ovule_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
 results <- lines(fit$groupsummary)
@@
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope.test=1)
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=1)
 results <- lines(fit$groupsummary)
@@
 ```
+summary(slopes)
 
@@
 
-plot(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
-slopes <- sma(accessory_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+plot(repro_inv_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$repro_inv_per_seed,SummarySpp[["se"]]$accessory_per_seed)
+slopes <- sma(repro_inv_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seed_costs,SummarySpp[["se"]]$seed_costs)
-slopes <- sma(seed_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+slopes <- sma(seed_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
-slopes <- sma(prepollen_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+slopes <- sma(prepollen_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 plot(provisioning_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-slopes <- sma(provisioning_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+slopes <- sma(provisioning_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 plot(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all failure costs (mg/seed)",xlab="",cex=1.5)
-slopes <- sma(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="OLS", log="xy")
+slopes <- sma(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
-slopes <- sma(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+slopes <- sma(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_failure_per_seed,SummarySpp[["se"]]$prepollen_failure_per_seed)
-slopes <- sma(prepollen_failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+slopes <- sma(prepollen_failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
-slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="OLS")
+slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
 results <- fit$groupsummary
@@
 mtext("count, scaled to plant size",2,line=2.3)
-mod1 <- sma(scaled_seed_count~prop_prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_seed_count!=0),log="y",slope=-1,method="OLS")
-mod2 <- sma(scaled_bud_count~prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_bud_count!=0),log="xy",slope=3.23,method="OLS")
-mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
+mod1 <- sma(scaled_seed_count~prop_prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_seed_count!=0),log="y",slope=-1,method="SMA")
+mod2 <- sma(scaled_ovule_count~prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_ovule_count!=0),log="xy",slope=3.23,method="SMA")
+mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="SMA")
 
@@
 mtext("count, scaled to plant size",2,line=2.3)
-mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="OLS")
-mod2 <- sma(scaled_bud_count~embryo_endo_size,data=subset(SummaryInd,scaled_bud_count!=0),log="xy",slope=-1,method="OLS")
-mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="OLS")
+mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="SMA")
+mod2 <- sma(scaled_ovule_count~embryo_endo_size,data=subset(SummaryInd,scaled_ovule_count!=0),log="xy",slope=-1,method="SMA")
+mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="SMA")
 
@@
 plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.002,500),ylim=c(.004,.6),cex=1.5,xaxt="n",xlab="",ylab="")
-mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="OLS")
+mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="SMA")
 y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
@@
 extra.top.left.logxy("b",2,1.2)
+summary(mod)
 
@@
 y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
-mod <- sma(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
+mod <- sma(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
 #abline(mod$groupsummary["Int"][[1]],1,lty=2)
@@
 y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
-mod <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="OLS")
+mod <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
 line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
@@
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-fit <- sma(data[[yvar]] ~ data[[xvar]], method="OLS", log="xy",slope.test=1)
+fit <- sma(data[[yvar]] ~ data[[xvar]], method="SMA", log="xy",slope.test=1)
 temp <- as.data.frame(c(xvar, yvar,dplyr::select(fit$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Slope_test_p,n)))
@@
 plot(seedset~prop_failure,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),log="xy",pch=16,col=col.spp(species))
-mod <- sma(seed_size~total_weight_0,data=subset(SummarySpp[["mean"]]),log="xy",method="OLS")
+mod <- sma(seed_size~total_weight_0,data=subset(SummarySpp[["mean"]]),log="xy",method="SMA")
 summary(mod)
@@
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy",slope=1)
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope=1)
 results <- lines(fit$groupsummary)
@@
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], log="x",method="OLS")
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], log="x",method="SMA")
 results <- lines(fit$groupsummary)
@@
 points(scaled_repro_inv~seed_size,SummarySpp[["mean"]], cex=2, col=col.spp(species),pch=16)
-mod <-sma(scaled_repro_inv~seed_size,SummarySpp[["mean"]],log="xy",method="OLS")
+mod <-sma(scaled_repro_inv~seed_size,SummarySpp[["mean"]],log="xy",method="SMA")
 summary(mod)
@@
 points(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seed_count>0),col=col.spp(species),pch=16,cex=2)
-mod <- sma(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]]),method="OLS", log="xy")
+mod <- sma(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]]),method="SMA", log="xy")
 #words.top.right.logxy(mod)

### 2016-09-21 ms/Accessory/ms-supp.Rnw
Framework for supplementary materials document

\documentclass[10pt,twoside]{article}

\usepackage{suppmat}
\usepackage{listings}
\usepackage[T1]{fontenc} % Better underscores
\usepackage{longtable}

\usepackage[rgb,dvipsnames]{xcolor}
\definecolor{grey}{rgb}{0.5, 0.5, 0.5}

\newcommand{\smurl}[1]{\url{#1}}
\newcommand{\email}[1]{\href{mailto:#1}{\texttt{#1}}}

\title{Accessories dominate the costs of producing seed}
\runninghead{C\lowercase{osts of producing seed}}

\author{E. H. Wenk\textsuperscript{1,\textasteriskcentered}, K. Abramowicz\textsuperscript{2}, M. Westoby\textsuperscript{1}, D.S. Falster\textsuperscript{1} }
\affiliation{\textsuperscript{1} Biological Sciences, Macquarie University NSW 2109, Australia \\
\textsuperscript{2} Department of Mathematics and Mathematical Statistics, Ume{\aa} University, 90187 Ume{\aa}, Sweden \\
\textsuperscript{\textasteriskcentered} Correspondence author. E-mail: \email{ehwenk@gmail.com}
}

\usepackage[authoryear,sectionbib,sort]{natbib}
\bibliographystyle{amnat2}

\pdfminorversion=4 % tell pdflatex to generate PDF in version 1.4
% Needed for problem-free conversion on manuscript central (arrgh)
% http://timotheepoisot.fr/2013/06/24/manuscript-central-pdf-fix/

\titleprefix{Supporting Materials for:}

\date{}

<<preload, echo=FALSE>>=
library(xtable)
library(knitr)
opts_chunk$set(echo=FALSE, fig.pos = "!h", fig.align="center", comment = NA)

flowering_parts <- read.csv("Sup_Table_flowering_parts.csv",
  stringsAsFactors=FALSE, check.names=FALSE)

print_table_species <- function(species, data) {
  data <- data[data$species == species, -c(1)]
  print(xtable(data,
            hline.after=c(1),
            align='p{0.1cm}p{4cm}p{6cm}p{3cm}p{1cm}p{1cm}',
            label=sprintf("tab:parts_%s", species),
            caption=sprintf("Table of parts for %s.", species)),
      sanitize.text.function=I,
      , table.placement = "H"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
}

@

\begin{document}

\maketitle

\tableofcontents

\renewcommand{\thefigure}{S\arabic{figure}}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{secnumdepth}{0}

\clearpage

\section{A -- Methods for estimating Reproductive allocation}

All computations implemented in \textsc{r} \citep{R-2015}.

\subsection{Banksia ericifolia}

Details on parts for \emph{Banksia ericifolia} found in Table \ref{tab:parts_Banksia ericifolia}. See Fig \ref{fig:map Banksia ericifolia} for a plot.

<<echo=FALSE,results='asis'>>=
print_table_species("Banksia ericifolia", flowering_parts)
@

\begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
plot(BAER_GraphMaps$graph)
@
\caption{Map of parts for \emph{Banksia ericifolia}}
\label{fig:map Banksia ericifolia}
\end{figure}

\clearpage

\subsection{Conospermum ericifolium}

Details on parts for \emph{Conospermum ericifolium} found in Table \ref{tab:parts_Conospermum ericifolium}.  See Fig \ref{fig:map Conospermum ericifolium} for a plot.

<<echo=FALSE,results='asis'>>=
print_table_species("Conospermum ericifolium", flowering_parts)
@

\begin{figure}
\centering
<<echo=FALSE,results='asis'>>=
plot(BAER_GraphMaps$graph)
@
\caption{Map of parts for \emph{Conospermum ericifolium}}
\label{fig:map Conospermum ericifolium}
\end{figure}

\clearpage

\clearpage

\addcontentsline{toc}{section}{References}
\bibliography{references}

\end{document}

### 2016-10-05 scripts/Accessory_figs_20160905.Rmd
creating 3D plot of leaf replacement, new leaf, and reproductive investment

@@
 #points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
-arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=1,length=.15)
+arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0,length=.15)
 

### 2016-10-05 scripts/RA_figs_20160627.Rmd
creating 3D plot of leaf replacement, new leaf, and reproductive investment

@@
-#Figure 1 Different species have different RA values. But biggest shift in RA is with age
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
+###playing with variables to try and show meaningful RA plots despite negative leaf growth values
+``` {r}
 if (min(SummaryInd$growth_leaf) <= 0) {
@@
 
+SummaryInd$growth_leaf_fixed_max = SummaryInd$growth_leaf
+SummaryInd$RA_fixed_max = SummaryInd$RA_leaf_area
+for (i in 1:length(SummaryInd$individual)) {
+  if (SummaryInd$RA_leaf_area[i] < 0) {
+  SummaryInd$growth_leaf_fixed_max[i] = SummaryInd$repro_inv[i]*0.005
+  SummaryInd$RA_fixed_max[i] = 1.1 
+  }
+   if (SummaryInd$RA_leaf_area[i] > 1) {
+  SummaryInd$growth_leaf_fixed_max[i] = SummaryInd$repro_inv[i]*0.005
+  SummaryInd$RA_fixed_max[i] = 1.1
+  }
+}
+
+SummaryInd$leaf_replacement = SummaryInd$growth_leaf
+SummaryInd$leaf_new = SummaryInd$growth_leaf
+SummaryInd$leaf_new_nonzero = SummaryInd$growth_leaf
+for (i in 1:length(SummaryInd$individual)) {
+  if (SummaryInd$growth_leaf[i] < 0) {
+  SummaryInd$leaf_replacement[i] = SummaryInd$leaf_inv_gross[i]
+  SummaryInd$leaf_new_nonzero[i] =.1
+  SummaryInd$leaf_new[i] = 0
+  }
+   if (SummaryInd$growth_leaf[i] > 0) {
+  SummaryInd$leaf_replacement[i] = SummaryInd$leaf_shed[i]
+  SummaryInd$leaf_new[i] = SummaryInd$growth_leaf[i]
+  SummaryInd$leaf_new_nonzero[i] =SummaryInd$growth_leaf[i]
+  }
+}
+
+SummaryInd$repro_inv_nonzero = SummaryInd$repro_inv
+for (i in 1:length(SummaryInd$individual)) {
+  if (SummaryInd$repro_inv[i] < .0001) {
+    SummaryInd$repro_inv_nonzero[i] = .1
+  }
+}
+
+plot(leaf_replacement~leaf_new, subset(SummaryInd), log="xy", col=col.spp(species),pch=16)
+abline(0,1)
+
+plot(leaf_replacement~leaf_new, subset(SummaryInd), log="xy", col=col.age(age),pch=16)
+abline(0,1)
+
+scatterplot3d(log(SummaryInd$repro_inv_nonzero),log(SummaryInd$leaf_new_nonzero),log(SummaryInd$leaf_replacement),color=col.spp(SummaryInd$species),pch=16,type="h",lty.hplot=3)
+
+scatterplot3d(log(SummaryInd$leaf_replacement),log(SummaryInd$leaf_new),log(SummaryInd$repro_inv),color=col.spp(SummaryInd$species),pch=16,type="h", lty.hplot=3)
+
+scatterplot3d(log10(SummaryInd$leaf_replacement),log10(SummaryInd$leaf_new),log10(SummaryInd$repro_inv_nonzero),color=col.spp(SummaryInd$species),pch=16,grid=TRUE,type="h", lty.hplot=3,lwd=.2,xlim=c(-1,6),ylim=c(-1,6),zlim=c(-1,6))
+
+planes3d(0, x.coef = 1, y.coef = 1, lty = "dashed",)
+
+par(mfrow=c(1,1), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
+```
+
+#Figure 1 Different species have different RA values. But biggest shift in RA is with age
+```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
 #pdf("figs2/RA/Figure_1_leaf_vs_repro.pdf", height=4.3, width=8)
@@
 scatterplot3d(SummaryInd$leaf_shed,SummaryInd$leaf_inv_gross,SummaryInd$repro_inv,log="xyz",color=col.spp(SummaryInd$species),pch=16)
+
+ternary <- dplyr::select(SummaryInd,species,age,leaf_shed,growth_leaf,pack_disp_costs,seed_costs,embryo_endo_size)
+ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
+ternary$post_poll <- 100-ternary$per_poll
+ternary$per_seed <-100*ternary$embryo_endo_size/ternary$seed_costs
+ternary$per_disp <-100*ternary$pack_disp_costs/ternary$seed_costs
+
+mod_poll <- sma(per_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")
+mod_seed <- sma(per_seed~seed_costs,ternary,slope.test=0,method="OLS",log="x")
+mod_disp <- sma(per_disp~seed_costs,ternary,slope.test=0,method="OLS",log="x")
+mod_post_poll <- sma(post_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")
+
+costs_per_seed <- as.data.frame("costs for seed (%)")
+costs_per_seed <- cbind(costs_per_seed,dplyr::select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+
+costs_per_seed2 <- as.data.frame("costs for pre-pollination (%)")
+costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
+
+costs_per_seed2 <- as.data.frame("costs for dispersal (%)")
+costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
+names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
+costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
+
+write.csv(costs_per_seed, file="figs2/Accessory_Costs/Table00_in_text_costs_per_seed.csv",row.names=FALSE)
+
+win.metafile("figs2/Accessory_Costs/FigureXX_seedcost_components.wmf", height=6, width=6)
+plot
+
+plot(per_seed~seed_costs,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seed_costs")
+points(per_poll~seed_costs,ternary,col="red",pch=16,cex=2)
+points(per_disp~seed_costs,ternary,col="blue",pch=16,cex=2)
+
+abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
+abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
+abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
+legend("topright",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
+v <- sqrt(ternary$seed_costs/500)
+ternary$horz <- c(1.8,1.3,1.2,-0.3,0.6,0.6,0.5,-0.2,1.3,1.7,1.4,-0.2,-0.3,-0.3)
+ternary$vert <- c(v[1]*-1.7,v[2]*1.1,v[3]*1.2,v[4],v[5]*-2.3,v[6]*4.5,v[7],v[8]*1.6,v[9],v[10]*0.2,v[11],v[12],v[13],v[14])
+ternary = ternary[with(ternary, order(-seed_costs)), ]
+label <- 20
+
+dev.off()
+library(ggtern)
+win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
+plot
+
+par(mfrow=c(1,1), cex=1, omi=c(2,2,2,2), mai=c(2,2,2,2))
+
+ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
+      geom_point(size=sqrt(ternary$seed_costs/2),shape=20,color=col.spp(ternary$species)) +
+      theme_bw() + 
+      theme_showarrows() +
+      geom_text(label=ternary$species, color="black", hjust=ternary$horz, 
+                 vjust=ternary$vert,size=2) +
+      ggtitle("Seed cost components")+
+      labs(T="embryo+endosperm",L="pre-pollination",R="provisioning")+
+      Tarrowlab("embryo + endosperm weight (%)")+
+      Larrowlab("pre-pollination costs (%)")+
+      Rarrowlab("provisioning costs (%)")+
+      theme(plot.title = element_text(size=11,face="bold"))+
+      theme(tern.axis.title.T = element_text(size=9,face="plain"))+
+      theme(tern.axis.title.L = element_text(size=9,face="plain",hjust=0,vjust=1.7))+
+      theme(tern.axis.title.R = element_text(size=9,face="plain",hjust=1,vjust=1.7))+
+      theme(tern.axis.arrow.text = element_text(size=9,face="plain"))+
+      theme(tern.axis.arrow.start= 0.2)+ 
+      theme(tern.axis.arrow.finish=0.8)
+
 ```
 
-#Figure 1 - alternate rendition, not scaling leaf investment to be positive
+#Figure 1 - alternate rendition, not scaling leaf investment to be positive, reassigning "negative" leaf investment individuals to RA =1.1
 ```{r}
@@
 
-plot(repro_inv~jitter(growth_leaf_no_neg_values), subset(SummaryInd), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
+plot(repro_inv~(growth_leaf_fixed_max), subset(SummaryInd), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
      xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
@@
 
-plot(repro_inv~growth_leaf_no_neg_values, subset(SummaryInd), log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
+plot(repro_inv~growth_leaf_fixed_max, subset(SummaryInd), log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
      xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
@@
 
-data2 <- subset(SummaryInd,RA_leaf_area>-2&RA_leaf_area<3)
+#data2 <- subset(SummaryInd,RA_leaf_area>-2&RA_leaf_area<3)
+data2 <- subset(SummaryInd)
 data2 <- split(data2, data2$species)
@@
 for(spp in names(data)) {
-  plot(RA_leaf_area~age,data2[[spp]],col=col.age(data2[[spp]]$age),pch=16,xlab="",ylab="",log="x",xlim=c(1,40),ylim=c(-0.25,1.75),yaxt="n",xaxt="n")
+  plot(RA_fixed_max~age,data2[[spp]],col=col.age(data2[[spp]]$age),pch=16,xlab="",ylab="",log="x",xlim=c(1,40),ylim=c(-0.25,1.75),yaxt="n",xaxt="n")
   points(RA_leaf_area~age,data[[spp]],pch=151,col=col.age(data[[spp]]$age),cex=1.5)
@@
   extra.top.left.logx(labels.spp.full(spp),3)
-  extra.bottom.left.logx(data3[[spp]]$RA_type,1)
+  extra.bottom.left.logx(data3[[spp]]$RA_type,1,0.8)
 }

### 2016-10-10 ms/Accessory/ms-supp.Rnw
Option to turn off graphs

@@
   stringsAsFactors=FALSE, check.names=FALSE)
+flowering_parts$method <- gsub("_", " ", flowering_parts$method, fixed=TRUE)
 
@@
 
+plot_graph <- function(graph) {
+
+  #plot(graph)
+  plot(NA, type="n", xlim=c(0,1), ylim=c(0,1), ann=FALSE, axes=FALSE)
+}
 @
@@
 <<echo=FALSE,results='asis'>>=
-plot(BAER_GraphMaps$graph)
+plot_graph(BAER_GraphMaps$graph)
 @
@@
 <<echo=FALSE,results='asis'>>=
-plot(BAER_GraphMaps$graph)
+plot_graph(COER_GraphMaps$graph)
 @

### 2016-10-11 ms/Accessory/ms-supp.Rnw
adding other species to Supplementary Material

@@
 
+\subsection{Boronia ledifolia}
+
+Details on parts for \emph{Boronia ledifolia} found in Table \ref{tab:parts_Boronia ledifolia}. See Fig \ref{fig:map Boronia ledifolia} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Boronia ledifolia", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(BOLE_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Boronia ledifolia}}
+\label{fig:map Boronia ledifolia}
+\end{figure}
+
+\clearpage
+
 \subsection{Conospermum ericifolium}
@@
 
+\subsection{Epacris microphylla}
+
+Details on parts for \emph{Epacris microphylla} found in Table \ref{tab:parts_Epacris microphylla}. See Fig \ref{fig:map Epacris microphylla} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Epacris microphylla", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(EPMI_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Epacris microphylla}}
+\label{fig:map Epacris microphylla}
+\end{figure}
+
+\clearpage
+
+\subsection{Grevillea buxifolia}
+
+Details on parts for \emph{Grevillea buxifolia} found in Table \ref{tab:parts_Grevillea buxifolia}. See Fig \ref{fig:map Grevillea buxifolia} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Grevillea buxifolia", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(GRBU_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Grevillea buxifolia}}
+\label{fig:map Grevillea buxifolia}
+\end{figure}
+
+\clearpage
+
+\subsection{Grevillea speciosa}
+
+Details on parts for \emph{Grevillea speciosa} found in Table \ref{tab:parts_Grevillea speciosa}. See Fig \ref{fig:map Grevillea speciosa} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Grevillea speciosa", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(GRSP_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Grevillea speciosa}}
+\label{fig:map Grevillea speciosa}
+\end{figure}
+
+\clearpage
+
+\subsection{Hakea teretifolia}
+
+Details on parts for \emph{Hakea teretifolia} found in Table \ref{tab:parts_Hakea teretifolia}. See Fig \ref{fig:map Hakea teretifolia} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Hakea teretifolia", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(HATE_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Hakea teretifolia}}
+\label{fig:map Hakea teretifolia}
+\end{figure}
+
+\clearpage
+
+\subsection{Hemigenia purpurea}
+
+Details on parts for \emph{Hemigenia purpurea} found in Table \ref{tab:parts_Hemigenia purpurea}. See Fig \ref{fig:map Hemigenia purpurea} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Hemigenia purpurea", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(HEPU_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Hemigenia purpurea}}
+\label{fig:map Hemigenia purpurea}
+\end{figure}
+
+\clearpage
+
+\subsection{Leucopogon esquamatus}
+
+Details on parts for \emph{Leucopogon esquamatus} found in Table \ref{tab:parts_Leucopogon esquamatus}. See Fig \ref{fig:map Leucopogon esquamatus} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Leucopogon esquamatus", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(LEES_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Leucopogon esquamatus}}
+\label{fig:map Leucopogon esquamatus}
+\end{figure}
+
+\clearpage
+
+\subsection{Persoonia lanceolata}
+
+Details on parts for \emph{Persoonia lanceolata} found in Table \ref{tab:parts_Persoonia lanceolata}. See Fig \ref{fig:map Persoonia lanceolata} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Persoonia lanceolata", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(PELA_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Persoonia lanceolata}}
+\label{fig:map Persoonia lanceolata}
+\end{figure}
+
+\clearpage
+
+\subsection{Petrophile puchella}
+
+Details on parts for \emph{Petrophile puchella} found in Table \ref{tab:parts_Petrophile puchella}. See Fig \ref{fig:map Petrophile puchella} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Petrophile puchella", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(PEPU_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Petrophile puchella}}
+\label{fig:map Petrophile puchella}
+\end{figure}
+
+\clearpage
+
+\subsection{Phyllota phyllicoides}
+
+Details on parts for \emph{Phyllota phyllicoides} found in Table \ref{tab:parts_Phyllota phyllicoides}. See Fig \ref{fig:map Phyllota phyllicoides} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Phyllota phyllicoides", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(PHPH_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Phyllota phyllicoides}}
+\label{fig:map Phyllota phyllicoides}
+\end{figure}
+
+\clearpage
+
+\subsection{Pimelea linifolia}
+
+Details on parts for \emph{Pimelea linifolia} found in Table \ref{tab:parts_Pimelea linifolia}. See Fig \ref{fig:map Pimelea linifolia} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Pimelea linifolia", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(PILI_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Pimelea linifolia}}
+\label{fig:map Pimelea linifolia}
+\end{figure}
+
+\clearpage
+
+\subsection{Pultanaea tuberculata}
+
+Details on parts for \emph{Pultanaea tuberculata} found in Table \ref{tab:parts_Pultanaea tuberculata}. See Fig \ref{fig:map Pultanaea tuberculata} for a plot.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_species("Pultanaea tuberculata", flowering_parts)
+@
+
+  \begin{figure}
+\centering
+<<echo=FALSE,results='asis'>>=
+  plot_graph(PUTU_GraphMaps$graph)
+@
+  \caption{Map of parts for \emph{Pultanaea tuberculata}}
+\label{fig:map Pultanaea tuberculata}
+\end{figure}
+
+\clearpage
+
 \clearpage

### 2016-10-11 ms/Accessory/ms-supp.Rnw
Creating tables in xtable - both supplmentary material and main tables for ms

@@
   stringsAsFactors=FALSE, check.names=FALSE)
+
 flowering_parts$method <- gsub("_", " ", flowering_parts$method, fixed=TRUE)
@@
             hline.after=c(1),
-            align='p{0.1cm}p{4cm}p{6cm}p{3cm}p{1cm}p{1cm}',
+            align='p{0.1cm}p{4cm}p{6cm}p{2.5cm}p{1cm}p{1cm}',
             label=sprintf("tab:parts_%s", species),
@@
   plot(NA, type="n", xlim=c(0,1), ylim=c(0,1), ann=FALSE, axes=FALSE)
+  box()
 }
@@
 
-\maketitle
+%\maketitle
 
@@
 
-\subsection{Petrophile puchella}
+\subsection{Petrophile pulchella}
 
-Details on parts for \emph{Petrophile puchella} found in Table \ref{tab:parts_Petrophile puchella}. See Fig \ref{fig:map Petrophile puchella} for a plot.
+Details on parts for \emph{Petrophile pulchella} found in Table \ref{tab:parts_Petrophile pulchella}. See Fig \ref{fig:map Petrophile pulchella} for a plot.
 
 <<echo=FALSE,results='asis'>>=
-  print_table_species("Petrophile puchella", flowering_parts)
+  print_table_species("Petrophile pulchella", flowering_parts)
 @
@@
 @
-  \caption{Map of parts for \emph{Petrophile puchella}}
-\label{fig:map Petrophile puchella}
+  \caption{Map of parts for \emph{Petrophile pulchella}}
+\label{fig:map Petrophile pulchella}
 \end{figure}
@@
 
-\subsection{Phyllota phyllicoides}
+\subsection{Phyllota phylicoides}
 
-Details on parts for \emph{Phyllota phyllicoides} found in Table \ref{tab:parts_Phyllota phyllicoides}. See Fig \ref{fig:map Phyllota phyllicoides} for a plot.
+Details on parts for \emph{Phyllota phylicoides} found in Table \ref{tab:parts_Phyllota phylicoides}. See Fig \ref{fig:map Phyllota phylicoides} for a plot.
 
 <<echo=FALSE,results='asis'>>=
-  print_table_species("Phyllota phyllicoides", flowering_parts)
+  print_table_species("Phyllota phylicoides", flowering_parts)
 @
@@
 @
-  \caption{Map of parts for \emph{Phyllota phyllicoides}}
-\label{fig:map Phyllota phyllicoides}
+  \caption{Map of parts for \emph{Phyllota phylicoides}}
+\label{fig:map Phyllota phylicoides}
 \end{figure}
@@
 
-\subsection{Pultanaea tuberculata}
+\subsection{Pultenaea tuberculata}
 
-Details on parts for \emph{Pultanaea tuberculata} found in Table \ref{tab:parts_Pultanaea tuberculata}. See Fig \ref{fig:map Pultanaea tuberculata} for a plot.
+Details on parts for \emph{Pultenaea tuberculata} found in Table \ref{tab:parts_Pultenaea tuberculata}. See Fig \ref{fig:map Pultenaea tuberculata} for a plot.
 
 <<echo=FALSE,results='asis'>>=
-  print_table_species("Pultanaea tuberculata", flowering_parts)
+  print_table_species("Pultenaea tuberculata", flowering_parts)
 @
@@
 @
-  \caption{Map of parts for \emph{Pultanaea tuberculata}}
-\label{fig:map Pultanaea tuberculata}
+  \caption{Map of parts for \emph{Pultenaea tuberculata}}
+\label{fig:map Pultenaea tuberculata}
 \end{figure}
+
+\clearpage
+
+<<echo=FALSE,results='asis'>>=
+headers <- as.data.frame(matrix(vector(), 3, 3,
+                dimnames=list(c(), c("A","B","C"))),
+                stringsAsFactors=F)
+headers[1,] <- c("","Total reproductive investment","Total reproductive investment")
+headers[2,] <- c("","vs","vs")
+headers[3,] <- c("","propagule investment","flower investment")
+
+print(xtable(headers,
+             hline.after=c(-1),
+             align='p{0.1cm}p{4cm}|c|c'),
+        sanitize.text.function=I,
+        , table.placement = "H"
+        , caption.placement = "top"
+        , include.rownames = FALSE
+        , include.colnames = FALSE
+        , size = "small"
+        , floating = FALSE)             
+@
+
+<<echo=FALSE,results='asis'>>=
+TableSXX <- read.csv("Table_SXX_propagule_invest_vs_repro_inv.csv",
+                    stringsAsFactors=FALSE, check.names=FALSE)
+
+names(TableSXX) <- c("species","n","r$^2$","p", "n","r$^2$","p")
+TableSXX[,2] <- format(TableSXX[,2],digits=2,nsmall=2)
+TableSXX[,5] <- format(TableSXX[,5],digits=2,nsmall=2)
+TableSXX[,4] <- format_p(TableSXX[,4])
+TableSXX[,7] <- format_p(TableSXX[,7])
+
+TableSXX$species  <- paste("\\textit{",unique(TableSXX$species),"}", sep="")
+
+print(xtable(TableSXX,
+               hline.after=c(1),
+               align='p{0.1cm}p{4cm}|p{.94cm}p{1cm}p{1.5cm}|p{.75cm}p{1cm}p{1.5cm}',
+               caption="Intraspecific correlations between reproductive investment and (a) propagule investment and (b) flower investment"),
+               sanitize.text.function=I,
+        , table.placement = "H"
+        , caption.placement = "top"
+        , include.rownames = FALSE
+        , include.colnames = TRUE
+        , size = "small"
+        , floating = FALSE)
+@
+
+Table SXX.Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as "flower weight (mg) * bud count".
+
+\clearpage
+
+<<echo=FALSE,results='asis'>>=
+TableSXX <- read.csv("Table_SXX_propagule_invest_vs_repro_inv.csv",
+                    stringsAsFactors=FALSE, check.names=FALSE)
+
+names(TableSXX) <- c("species","n","r$^2$","p", "n","r$^2$","p")
+TableSXX[,2] <- format(TableSXX[,2],digits=2,nsmall=2)
+TableSXX[,5] <- format(TableSXX[,5],digits=2,nsmall=2)
+TableSXX[,4] <- format_p(TableSXX[,4])
+TableSXX[,7] <- format_p(TableSXX[,7])
+
+TableSXX$species  <- paste("\\textit{",unique(TableSXX$species),"}", sep="")
+
+print(xtable(TableSXX,
+               hline.after=c(1),
+               align='p{0.1cm}p{4cm}|p{.94cm}p{1cm}p{1.5cm}|p{.75cm}p{1cm}p{1.5cm}',
+               caption="Intraspecific correlations between reproductive investment and (a) propagule investment and (b) flower investment"),
+               sanitize.text.function=I,
+        , table.placement = "H"
+        , caption.placement = "top"
+        , include.rownames = FALSE
+        , include.colnames = TRUE
+        , size = "small"
+        , floating = FALSE)
+@
+
+Table SXX.Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as "flower weight (mg) * bud count".
+
+\clearpage
+
+<<echo=FALSE,results='asis'>>=
+Table02 <- read.csv("Table02_acc_cost_embryo_size_slopes.csv",
+                    stringsAsFactors=FALSE, check.names=FALSE)
+
+names(Table02) <- c("Variable", "r$^2$", "slope (95 CI)","p$_{slope<>1}$")
+Table02[,2] <- format(Table02[,2],digits=2,nsmall=2)
+Table02[,4] <- format(Table02[,4],digits=4,nsmall=4)
+
+print(xtable(Table02,
+               hline.after=c(1),
+               align='p{0.1cm}p{4cm}p{1cm}p{3cm}p{1cm}',
+               caption="Correlations with total reproductive investment"),
+               sanitize.text.function=I,
+        , table.placement = "H"
+        , caption.placement = "top"
+        , include.rownames = FALSE
+        , include.colnames = TRUE
+        , size = "small"
+        , floating = FALSE)
+@
+
+Table 2.
+Scaling of reproductive tissue costs with seed size.
+All variables were showed a strong correlation with seed size (p < 0.0001).
+Tables show properties of SMA line fits, between different variables and seed size.
+\clearpage
+
+<<echo=FALSE,results='asis'>>=
+Table03 <- read.csv("Table03_correlations_with_repro_inv.csv",
+                    stringsAsFactors=FALSE, check.names=FALSE)
+format_p <- function(p, digits = 4) {
+  x <- as.character(round(p, digits = digits))
+  pc <- 10^-digits
+  x[p < pc] <- paste("<", pc)
+  x
+}
+
+Table03$pval <- format_p(Table03$pval)
+Table03$variable <- c("Total plant weight (mg)","Propagule investment (mg)","Fruit investment (mg)","Flower investment (mg)",
+                      "Successful investment (mg)", "Successful pre-pollination investment (mg)","Provisioning investment (mg)",
+                      "Failed tissues (mg)")
+names(Table03) <- c("Variable", "n", "r$^2$", "p")
+print(xtable(Table03,
+               hline.after=c(1),
+               align='p{0.1cm}p{6.5cm}p{1cm}p{1cm}p{1.5cm}',
+               caption="Correlations with total reproductive investment",
+             digits = 2),
+               sanitize.text.function=I,
+        , table.placement = "H"
+        , caption.placement = "top"
+        , include.rownames = FALSE
+        , include.colnames = TRUE
+        , size = "small"
+        , floating = FALSE)
+@
+
+Table 3.
+Correlation of different estimates of reproductive investment (and total plant weight) against total reproductive investment (mg).
+Regressions are done across all individuals of all 14 study species for which both reproductive investment and the estimate variable are greater than zero.
+The total cost of failed tissues or simply the energy expenditure into flowers provides the best approximation of total reproductive investment.
+Flower investment is a composite variable calculated as flower weight (mg)*bud count.
+Successful investment is a composite variable calculated as seed costs (mg)*seed count.
 

### 2016-10-11 scripts/Accessory_figs_20160905.Rmd
Creating tables in xtable - both supplmentary material and main tables for ms

@@
 
-write.csv(acc_costs_spp_format, file="figs2/Accessory_Costs/Table01_AccCosts_by_Species.csv",row.names=FALSE)
+write.csv(acc_costs_spp_format, file="ms/Accessory/Table01_AccCosts_by_Species.csv",row.names=FALSE)
 ```
@@
 abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-words.bottom.left.logxy(mod)
 
@@
 
-acc_by_species$slope2 <- paste(format(acc_by_species$Slope,digits=3)," (",format(acc_by_species$Slope_lowCI,digits=3)," - ",format(acc_by_species$Slope_highCI,digits=3),")",sep="")
+acc_by_species$Slope <- format(acc_by_species$Slope,nsmall=2,digits=2)
+acc_by_species$Slope_lowCI <- format(acc_by_species$Slope_lowCI,nsmall=2,digits=2)
+acc_by_species$Slope_highCI <- format(acc_by_species$Slope_highCI,nsmall=2,digits=2)
+
+acc_by_species$slope2 <- paste(acc_by_species$Slope," (",acc_by_species$Slope_lowCI," - ",acc_by_species$Slope_highCI,")",sep="")
 
 acc_by_species$r2 <- format(acc_by_species$r2,digits=2)
-acc_by_species$pval <- format(acc_by_species$pval,digits=2)
-acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=3)
+acc_by_species$pval <- format_p(acc_by_species$pval)
+acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=2)
 acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
 
-write.csv(acc_slopes, file="figs2/Accessory_Costs/Table02_acc_cost_embryo_size_slopes.csv",row.names=FALSE)
+write.csv(acc_slopes, file="ms/Accessory/Table02_acc_cost_embryo_size_slopes.csv",row.names=FALSE)
 ```
@@
 acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
+acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
 
-write.csv(acc_slopes, file="figs2/Accessory_Costs/Table_S3_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
+write.csv(acc_slopes, file="ms/Accessory/Table_SXX_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
 ```
@@
 colnames(temp)[1]<- "xvar"
-results <- bind_rows(results, temp)
+results <- dplyr::bind_rows(results, temp)
   }
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table03_correlations_with_repro_inv.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/Table03_correlations_with_repro_inv.csv",row.names=FALSE)
 ```

### 2016-10-13 scripts/Flowering_parts_charts.Rmd
lots of work summarizing nutrient data
most of the way to calculating RA using N & P, but some mis-matches with tissue names

--- 2015-12-16 Flowering_parts_charts.Rmd
@@
 ``` {r}
-accessoryList <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryList.csv")
-accessoryListShort <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryListShort.csv")
-accessoryListShortest <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/accessoryListShortest.csv")
-tissue_energy <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/tissue_energy.csv")
-nectar <- read.csv("~/RA schedules - Kuringgai research/Reproductive_Allocation_Kuringgai/data/nectar.csv")
+accessoryList <- read.csv("~/Reproductive_Allocation_Kuringgai/data/accessoryList.csv")
+accessoryListShort <- read.csv("~/Reproductive_Allocation_Kuringgai/data/accessoryListShort.csv")
+accessoryListShortest <- read.csv("~/Reproductive_Allocation_Kuringgai/data/accessoryListShortest.csv")
+tissue_energy <- read.csv("~/Reproductive_Allocation_Kuringgai/data/tissue_energy.csv")
+nectar <- read.csv("~/Reproductive_Allocation_Kuringgai/data/nectar.csv")
 
@@
 View(SummaryInvest)
+names(Invest2)
 

### 2016-10-13 scripts/nutrient.Rmd
moving nutrient.Rmd file to scripts

nutrient <- read.csv("~/Reproductive_Allocation_Kuringgai/data/nutrient_data.csv")
soil <- read.csv("~/Reproductive_Allocation_Kuringgai/data/nutrient_soil.csv")
accessoryList <- read.csv("~/Reproductive_Allocation_Kuringgai/data/accessoryList.csv")

library(plyr)
library(dplyr)
library(tidyr)

pch.tissue <- function(x=NULL){
  ret <- c(wood_from_tip=16, wood_from_middle=10,wood_from_base=7,shed_sapwood=1,bark=15,shed_bark=0,leaves=17,senescent_leaves=2,seed=8,reproductive=4)
  names(ret) <- c("wood_from_tip","wood_from_middle","wood_from_base","shed_sapwood","bark","shed_bark","leaves","senescent_leaves","seed","reproductive")
  if(!is.null(x)) {
    ret <- ret[as.character(x)]
  }
  ret
}

pch.tissue2 <- function(x=NULL){
  ret <- c(sapwood=16, bark=15,leaves=17)
  names(ret) <- c("sapwood","bark","leaves")
  if(!is.null(x)) {
    ret <- ret[as.character(x)]
  }
  ret
}

nutrient <- nutrient %>%
  mutate(
    NP = N/P
  )

#soils data
```{r}
pdf("figs2/Nutrients/soil.pdf", height=6, width=6)
plot
plot(N~P,soil,col=col.age(age),pch=16,cex=replicate)
dev.off()
```

```{r}
nutrient_spp_age <- subset(nutrient,live_dead=="live"|live_dead=="dead")
mean_values <- function(nutrient_spp_age) {
  select(nutrient_spp_age,species,tissue,age,live_dead,K,P,N) %>%
  group_by(species,tissue,age,live_dead) %>%
  summarise_each(funs(mean),N,P,K)
}

nutrient_sum <- mean_values(nutrient_spp_age)

nutrient_sum_N <- select(nutrient_sum,species,tissue,age,live_dead,N)
nutrient_sum_N <- tidyr::spread(nutrient_sum_N,live_dead,N)
names(nutrient_sum_N) <- c("species","tissue","age","N_dead","N_live")

nutrient_sum_P <- select(nutrient_sum,species,tissue,age,live_dead,P)
nutrient_sum_P <- tidyr::spread(nutrient_sum_P,live_dead,P)
names(nutrient_sum_P) <- c("species","tissue","age","P_dead","P_live")

nutrient_sum_K <- select(nutrient_sum,species,tissue,age,live_dead,K)
nutrient_sum_K <- tidyr::spread(nutrient_sum_K,live_dead,K)
names(nutrient_sum_K) <- c("species","tissue","age","K_dead","K_live")

nutrient_sum_spp_age <- plyr::join(nutrient_sum_N, nutrient_sum_P, by = c("species","tissue","age"),type="full")
nutrient_sum_spp_age <- plyr::join(nutrient_sum_spp_age, nutrient_sum_K, by = c("species","tissue","age"),type="full")

nutrient_sum_spp_age <- nutrient_sum_spp_age %>%
  mutate(
    NUE = 1 - (N_dead/N_live),
    PUE = 1 - (P_dead/P_live),
    KUE = 1 - (K_dead/K_live)
  )
```

```{r}
nutrient_spp <- subset(nutrient,live_dead=="live"|live_dead=="dead")
mean_values <- function(nutrient_spp) {
  select(nutrient_spp_age,species,tissue,live_dead,K,P,N) %>%
  group_by(species,tissue,live_dead) %>%
  summarise_each(funs(mean),N,P,K)
}

nutrient_sum <- mean_values(nutrient_spp)

nutrient_sum_N <- select(nutrient_sum,species,tissue,live_dead,N)
nutrient_sum_N <- tidyr::spread(nutrient_sum_N,live_dead,N)
names(nutrient_sum_N) <- c("species","tissue","N_dead","N_live")

nutrient_sum_P <- select(nutrient_sum,species,tissue,live_dead,P)
nutrient_sum_P <- tidyr::spread(nutrient_sum_P,live_dead,P)
names(nutrient_sum_P) <- c("species","tissue","P_dead","P_live")

nutrient_sum_K <- select(nutrient_sum,species,tissue,live_dead,K)
nutrient_sum_K <- tidyr::spread(nutrient_sum_K,live_dead,K)
names(nutrient_sum_K) <- c("species","tissue","K_dead","K_live")

nutrient_sum_spp <- plyr::join(nutrient_sum_N, nutrient_sum_P, by = c("species","tissue"),type="full")
nutrient_sum_spp <- plyr::join(nutrient_sum_spp, nutrient_sum_K, by = c("species","tissue"),type="full")

nutrient_sum_spp <- nutrient_sum_spp %>%
  mutate(
    NUE = 1 - (N_dead/N_live),
    PUE = 1 - (P_dead/P_live),
    KUE = 1 - (K_dead/K_live)
  )
```

convert RA to nutrient values
```{r}
temp <- subset(nutrient_sum_spp,tissue=="leaves")
temp <- select(temp,species,N_dead,N_live,P_dead,P_live)
names(temp) <- c("species","N_dead_leaf","N_live_leaf","P_dead_leaf","P_live_leaf")

SummaryInd2 <- plyr::join(SummaryInd,temp, by="species")
SummaryInd2 <- SummaryInd2 %>% mutate(
  leaf_N_lost = leaf_shed*N_dead_leaf,
  leaf_P_lost = leaf_shed*P_dead_leaf,
  leaf_N_new = leaf_inv_gross*N_live_leaf,
  leaf_P_new = leaf_inv_gross*P_live_leaf,
  leaf_N_net = leaf_N_new - leaf_N_lost,
  leaf_P_net = leaf_P_new - leaf_P_lost
  )
```

Merging in reproduction data
``` {r}
InvestIndPart <- merge(InvestmentByPart,select(accessoryList,-sort), by=c("species","part"))

for(v in c("weight")) {
  i <- is.na(InvestIndPart[[v]])
  InvestIndPart[[v]][i] <- 0
}

SummaryInvest <- 
  InvestIndPart %>%
  group_by(parts_fewer_yet,individual) %>%
  summarise_each(funs(sum),weight)

SummaryInvest$species <- SummaryInvest$individual
SummaryInvest$species <- substr(SummaryInvest$species,1,nchar(SummaryInvest$species)-4)
names(SummaryInvest) <- c("tissue","individual","weight","species")

nutrient_subset <- select(nutrient_spp,species,tissue,N,P)

SummaryInvest <- merge(SummaryInvest,nutrient_subset, by=c("species","tissue"),all.x=TRUE)
names(SummaryInvest)

SummaryInvest$tissue_N <- SummaryInvest$weight*SummaryInvest$N
SummaryInvest$tissue_P <- SummaryInvest$weight*SummaryInvest$P

nutrientRepro <- 
  SummaryInvest %>%
  group_by(individual) %>%
  summarise_each(funs(sum),tissue_N,tissue_P)

SummaryInd2 <- plyr::join(SummaryInd2,nutrientRepro, by="individual")

SummaryInd2$RA_N <- SummaryInd2$tissue_N / (SummaryInd2$tissue_N + SummaryInd2$leaf_N_net)
SummaryInd2$RA_P <- SummaryInd2$tissue_P / (SummaryInd2$tissue_P + SummaryInd2$leaf_P_net)

  i <- which(is.infinite(SummaryInd2$RA_N))
  for(v in c("RA_N")) {
    SummaryInd2[[v]][i] <- NA
  }

```

xvar <- "age"
yvar3 <- "RA_N"
yvar2 <- "RA_P"
yvar <- "RA_leaf_area"

data <- subset(SummaryInd2,species!="PEPU")
data <- split(data, data$species)

par(mfrow=c(3,1), cex=1, omi=c(.8,.1,.6,.05), mai=c(.1,.8,.05,.05))

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",ylab=yvar,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="x",ylab=yvar2,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="x",xlab=xvar,ylab=yvar3,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
  mtext(labels.spp.full(spp),3, outer=TRUE,font=3)
  mtext("age (years)",outer=TRUE,1,line=1.5)
}

  if(spp=="BOLE"|spp=="COER"|spp=="GRSP"|spp=="HEPU") {
    rect(14,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
  }
  if(spp=="PILI") {
    rect(10,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
  }

plot(RA_N~age,subset(SummaryInd2,species=="BAER"),col=col.age(age),pch=16)

plot(leaf_N_lost ~ leaf_N_new,SummaryInd2,pch=16,col=col.spp(species),log="xy")
plot(leaf_N_lost ~ leaf_N_new,SummaryInd2,pch=16,col=col.age(age),log="xy")

abline(0,1)
plot(leaf_P_net ~ leaf_N_net,SummaryInd2,pch=16,col=col.spp(species),log="xy")

View(SummaryInd2)
#simple N vs P plot
```{r}
pdf("figs2/Nutrients/NvsP.pdf", height=11, width=8.5)
plot
par(mfrow=c(2,1), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.05,.05))
plot(P~N,data=subset(nutrient),col=col.spp(species),pch=pch.tissue(tissue_simple),log="xy")
legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

plot(P~N,data=subset(nutrient,tissue_simple=="reproductive"|tissue_simple=="seed"),col=col.spp(species),pch=16,log="xy",cex=0.75)
test <- subset(nutrient,tissue_simple=="reproductive"|tissue_simple=="seed")
text(test$P~test$N,labels=test$tissue_complete,cex=0.5,adj=-.2)
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")
dev.off()
```

#plotting live versus dead tissue
```{r}
pdf("figs2/Nutrients/live_vs_shed.pdf", height=11, width=8.5)
plot
par(mfrow=c(2,1), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.05,.05)) 
plot(P~N,data=subset(nutrient,tissue_complete=="leaves"),col=col.spp(species),pch=16,ylim=c(10,500),log="",xlim=c(.4,2.5))
points(P~N,data=subset(nutrient,tissue_complete=="senescent_leaves"),col=col.spp(species),pch=1,cex=1.5)
points(P~N,data=subset(nutrient,tissue_complete=="senescent_leaves"),col=col.spp(species),pch=1,cex=1)
text(1.05*par("usr")[1],0.95*par("usr")[4],"leaves versus shed leaves",adj=0)

plot(P~N,data=subset(nutrient,tissue_complete=="bark"),col=col.spp(species),pch=16,ylim=c(10,300),log="",xlim=c(.15,1.5))
points(P~N,data=subset(nutrient,tissue_complete=="shed_bark"),col=col.spp(species),pch=1,cex=1.5)
points(P~N,data=subset(nutrient,tissue_complete=="shed_bark"),col=col.spp(species),pch=1,cex=1)
text(1.05*par("usr")[1],0.95*par("usr")[4],"bark versus shed bark",adj=0)

plot(P~N,data=subset(nutrient,tissue_complete=="wood_from_tip"),col=col.spp(species),pch=16,ylim=c(1,300),log="",xlim=c(0,0.8),cex=1)
points(P~N,data=subset(nutrient,tissue_complete=="shed_sapwood"),col=col.spp(species),pch=1,cex=1.5)
points(P~N,data=subset(nutrient,tissue_complete=="shed_sapwood"),col=col.spp(species),pch=1,cex=1)
text(1.15*par("usr")[1],0.95*par("usr")[4],"sapwood versus shed sapwood",adj=0)

plot(P~N,data=subset(nutrient,tissue_complete=="wood_from_tip"),col=col.spp(species),pch=16,ylim=c(1,300),log="",xlim=c(0,0.8),cex=1)
points(P~N,data=subset(nutrient,tissue_complete=="wood_from_base"&age>3),col=col.spp(species),pch=1,cex=1.5)
points(P~N,data=subset(nutrient,tissue_complete=="wood_from_base"&age>3),col=col.spp(species),pch=1,cex=1)
text(1.05*par("usr")[1],0.95*par("usr")[4],"sapwood versus wood from base of plant for plants >3 years",adj=0)

plot(PUE~NUE,data=subset(nutrient_sum_spp_age),col=col.spp(species),pch=pch.tissue2(tissue),log="",xlim=c(-0.5,1),ylim=c(-0.5,1),xlab="NUE vs PUE by species*age")
rect(par("usr")[1],par("usr")[3],0,1.5,col="light gray",border=NA)
rect(par("usr")[1],par("usr")[3],1.5,0,col="light blue",border=NA)
rect(par("usr")[1],par("usr")[3],0,0,col="grey",border=NA)
points(PUE~NUE,data=subset(nutrient_sum_spp_age),col=col.spp(species),pch=pch.tissue2(tissue))
abline(0,1)
legend("topleft",legend=c("sapwood","bark","leaves"),pch=c(16,15,17),bty="n")
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

plot(PUE~NUE,data=subset(nutrient_sum_spp),col=col.spp(species),pch=pch.tissue2(tissue),log="",xlim=c(-0.5,1),ylim=c(-0.5,1),xlab="NUE vs PUE by species")
rect(par("usr")[1],par("usr")[3],0,1.5,col="light gray",border=NA)
rect(par("usr")[1],par("usr")[3],1.5,0,col="light blue",border=NA)
rect(par("usr")[1],par("usr")[3],0,0,col="grey",border=NA)
points(PUE~NUE,data=subset(nutrient_sum_spp),col=col.spp(species),pch=pch.tissue2(tissue))
abline(0,1)
legend("topleft",legend=c("sapwood","bark","leaves"),pch=c(16,15,17),bty="n")
legend("bottomright",legend=labels.spp(),col=col.spp(),pch=16, cex=.8,bty="n")

dev.off()
```

```{r}
pdf("figs2/Nutrients/age_by_species_NP.pdf", height=7.5, width=11)
plot
par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.05,.05)) 
for (i in c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU")) {
data <- subset(nutrient,species==i)
plot(P~N,data,col=col.age(age),pch=pch.tissue(tissue_simple),log="xy")
text(1,200,i)
data2 <- subset(data,tissue_simple=="reproductive"|tissue_simple=="seed")
text(P~N,data2,label=data2$tissue_complete,col="red",cex=0.7)
legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.8,bty="n")
legend("topleft",legend=c("sapwood","wood from mid","wood from base","shed sapwood","bark","shed bark","leaves","shed leaves", "seed", "other reproductive"),pch=c(16,10,7,1,15,0,17,2,8,4),bty="n")
}
dev.off()
```

#shed leaf N per year

### 2016-10-25 scripts/nutrient.Rmd
working up nutrient data

@@
+#starting commands
+```{r}
 nutrient <- read.csv("~/Reproductive_Allocation_Kuringgai/data/nutrient_data.csv")
@@
   ret <- c(wood_from_tip=16, wood_from_middle=10,wood_from_base=7,shed_sapwood=1,bark=15,shed_bark=0,leaves=17,senescent_leaves=2,seed=8,reproductive=4)
+
   names(ret) <- c("wood_from_tip","wood_from_middle","wood_from_base","shed_sapwood","bark","shed_bark","leaves","senescent_leaves","seed","reproductive")
@@
 
-nutrient <- nutrient %>%
-  mutate(
-    NP = N/P
-  )
-
-#soils data
-```{r}
-pdf("figs2/Nutrients/soil.pdf", height=6, width=6)
-plot
-plot(N~P,soil,col=col.age(age),pch=16,cex=replicate)
-dev.off()
+plot_abline <- function(add_lines) {
+  abline(log(1),1)
+  abline(log10(.1),1,col="light gray")
+  abline(log10(10),1,col="light gray")
+  abline(log10(.5),1,col="gray")
+  abline(log10(2),1,,col="gray")
+  abline(log10(.01),1,col="light blue")
+  abline(log10(100),1,col="light blue")
+}
 ```
 
+#SUMMARIZING AND MERGING NP DATA INTO SUMMARYIND
+
+#summarize nutrient data by species, age
 ```{r}
@@
 
+#summarize nutrient data by species
 ```{r}
@@
 
-convert RA to nutrient values
+#merge dataframe with species means for N,P,K content with SummaryInd
 ```{r}
 temp <- subset(nutrient_sum_spp,tissue=="leaves")
-temp <- select(temp,species,N_dead,N_live,P_dead,P_live)
-names(temp) <- c("species","N_dead_leaf","N_live_leaf","P_dead_leaf","P_live_leaf")
+temp <- select(temp,species,N_dead,N_live,P_dead,P_live,NUE,PUE)
+names(temp) <- c("species","dead_leaf_N","live_leaf_N","dead_leaf_P","live_leaf_P","NUE","PUE")
 
 SummaryInd2 <- plyr::join(SummaryInd,temp, by="species")
-SummaryInd2 <- SummaryInd2 %>% mutate(
-  leaf_N_lost = leaf_shed*N_dead_leaf,
-  leaf_P_lost = leaf_shed*P_dead_leaf,
-  leaf_N_new = leaf_inv_gross*N_live_leaf,
-  leaf_P_new = leaf_inv_gross*P_live_leaf,
-  leaf_N_net = leaf_N_new - leaf_N_lost,
-  leaf_P_net = leaf_P_new - leaf_P_lost
-  )
 ```
 
-Merging in reproduction data
+#merging in reproduction data
 ``` {r}
@@
   InvestIndPart %>%
-  group_by(parts_fewer_yet,individual) %>%
+  group_by(parts_to_match,individual) %>%
   summarise_each(funs(sum),weight)
@@
 SummaryInvest$species <- substr(SummaryInvest$species,1,nchar(SummaryInvest$species)-4)
-names(SummaryInvest) <- c("tissue","individual","weight","species")
+names(SummaryInvest) <- c("parts_to_match","individual","weight","species")
 
-nutrient_subset <- select(nutrient_spp,species,tissue,N,P)
+nutrient_subset <- select(nutrient_spp,species,parts_to_match,N,P)
 
-SummaryInvest <- merge(SummaryInvest,nutrient_subset, by=c("species","tissue"),all.x=TRUE)
+SummaryInvest <- merge(SummaryInvest,nutrient_subset, by=c("species","parts_to_match"),all.x=TRUE)
 names(SummaryInvest)
 
-SummaryInvest$tissue_N <- SummaryInvest$weight*SummaryInvest$N
-SummaryInvest$tissue_P <- SummaryInvest$weight*SummaryInvest$P
+SummaryInvest$repro_N <- SummaryInvest$weight*SummaryInvest$N
+SummaryInvest$repro_P <- SummaryInvest$weight*SummaryInvest$P
 
@@
   group_by(individual) %>%
-  summarise_each(funs(sum),tissue_N,tissue_P)
+  summarise_each(funs(sum),repro_N,repro_P)
 
 SummaryInd2 <- plyr::join(SummaryInd2,nutrientRepro, by="individual")
-
-SummaryInd2$RA_N <- SummaryInd2$tissue_N / (SummaryInd2$tissue_N + SummaryInd2$leaf_N_net)
-SummaryInd2$RA_P <- SummaryInd2$tissue_P / (SummaryInd2$tissue_P + SummaryInd2$leaf_P_net)
-
-  i <- which(is.infinite(SummaryInd2$RA_N))
-  for(v in c("RA_N")) {
-    SummaryInd2[[v]][i] <- NA
-  }
-
 ```
 
+#determine leaf N,P in various tissue pools
+```{r}
+SummaryInd2 <- SummaryInd2 %>% mutate(
+  leaf_N_lost = leaf_shed*dead_leaf_N,
+  leaf_P_lost = leaf_shed*dead_leaf_P,
+  leaf_N_resorbed = leaf_shed*(live_leaf_N-dead_leaf_N),
+  leaf_P_resorbed = leaf_shed*(live_leaf_P-dead_leaf_P),
+  leaf_N_new = leaf_inv_gross*live_leaf_N,
+  leaf_P_new = leaf_inv_gross*live_leaf_P,
+  leaf_N_net = leaf_N_new - leaf_N_resorbed,
+  leaf_P_net = leaf_P_new - leaf_P_resorbed,
+  leaf_N_for_RA = growth_leaf*live_leaf_N,
+  leaf_P_for_RA = growth_leaf*live_leaf_P,
+  NP_live_leaf = live_leaf_N/live_leaf_P,
+  NP_dead_leaf = dead_leaf_N/dead_leaf_P,
+  RA_N = repro_N / (repro_N + leaf_N_for_RA),
+  RA_P = repro_P / (repro_P + leaf_P_for_RA),
+  total_N_per_year = leaf_N_new + repro_N,
+  total_P_per_year = leaf_P_new + repro_P,
+  prop_recycled_N = leaf_N_resorbed / leaf_N_new,
+  prop_recycled_P = leaf_P_resorbed / leaf_P_new,
+  prop_required_N = leaf_N_resorbed / total_N_per_year,
+  prop_required_P = leaf_P_resorbed / total_P_per_year
+  )
+```
+
+#PLOTS
+
+#soils data
+```{r}
+pdf("figs2/Nutrients/soil.pdf", height=6, width=6)
+plot
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.6,.05), mai=c(.8,.8,.05,.05))
+plot(N~P,soil,col=col.age(age),pch=16,cex=replicate)
+dev.off()
+```
+
+#various plots using NP data in leaves, reproductive material
+```{r}
+pdf("figs2/Nutrients/plots_of_NP_use.pdf", height=7.5, width=11)
+plot
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.6,.05), mai=c(.8,.8,.05,.05))
+plot(leaf_N_net ~ repro_N,SummaryInd2, col=col.spp(species),pch=16,log="xy",xlim=c(1,10^7),ylim=c(1,10^7),xlab="",ylab="")
+mtext("N in reproductive material (mg)",1, outer=FALSE,line=2)
+mtext("new N from soil required for leaves (mg)",2, outer=FALSE,line=2)
+plot_abline(add_lines)
+
+plot(leaf_P_net ~ repro_P,SummaryInd2, col=col.spp(species),pch=16,log="xy",xlim=c(100,10^8),ylim=c(100,10^8),xlab="",ylab="")
+mtext("P in reproductive material (ppm)",1, outer=FALSE,line=2)
+mtext("new P from soil required for leaves (ppm)",2, outer=FALSE,line=2)
+plot_abline(add_lines)
+
+plot(total_N_per_year ~ leaf_N_resorbed,SummaryInd2, col=col.spp(species),pch=16,log="xy",xlim=c(1,10^7),ylim=c(1,10^7),xlab="",ylab="")
+mtext("N resorbed from shed leaves (mg)",1, outer=FALSE,line=2)
+mtext("total N used by plant for repro + all leaf growth (mg)",2, outer=FALSE,line=2)
+plot_abline(add_lines)
+
+plot(total_P_per_year ~ leaf_P_resorbed,SummaryInd2, col=col.spp(species),pch=16,log="xy",xlim=c(100,10^8),ylim=c(100,10^8),xlab="",ylab="")
+mtext("P resorbed from shed leaves (ppm)",1, outer=FALSE,line=2)
+mtext("total P used by plant for repro + all leaf growth (ppm)",2, outer=FALSE,line=2)
+plot_abline(add_lines)
+
+plot(prop_required_N ~ prop_required_P,SummaryInd2, col=col.age(age),pch=16,log="",xlim=c(-0.2,.9),ylim=c(-0.2,.9))
+abline(0,1)
+plot(prop_required_N ~ prop_required_P,SummaryInd2, col=col.spp(species),pch=16,log="",xlim=c(-0.2,.9),ylim=c(-0.2,.9))
+abline(0,1)
+
+plot(leaf_N_resorbed ~ leaf_N_net,subset(SummaryInd2,age>3), col=col.spp(species),pch=16,log="xy",xlim=c(1,10^7),ylim=c(1,10^7))
+plot_abline(add_lines)
+
+plot(leaf_P_resorbed ~ leaf_P_net,subset(SummaryInd2,age>3), col=col.spp(species),pch=16,log="xy",xlim=c(100,10^8),ylim=c(100,10^8))
+plot_abline(add_lines)
+
+plot(NUE~live_leaf_N,subset(SummaryInd2,LL_death<6), col=col.spp(species),pch=16,log="x",ylim=c(-.1,1))
+plot(PUE~live_leaf_P,subset(SummaryInd2,LL_death<6), col=col.spp(species),pch=16,log="x",ylim=c(-.1,1))
+dev.off()
+```
+
+#RA plots using NP data
+```{r}
+pdf("figs2/Nutrients/RA_using_NP.pdf", height=7.5, width=11)
+plot
 xvar <- "age"
@@
 for(spp in names(data)) {
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",ylab=yvar,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
-  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="x",ylab=yvar2,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
-  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="x",xlab=xvar,ylab=yvar3,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
-  mtext(labels.spp.full(spp),3, outer=TRUE,font=3)
-  mtext("age (years)",outer=TRUE,1,line=1.5)
-}
-
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",ylab=yvar,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
     if(spp=="BOLE"|spp=="COER"|spp=="GRSP"|spp=="HEPU") {
@@
   }
+  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="xy",ylab=yvar2,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
+      if(spp=="BOLE"|spp=="COER"|spp=="GRSP"|spp=="HEPU") {
+    rect(14,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
+    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
+  }
+  if(spp=="PILI") {
+    rect(10,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
+    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
+  }
+  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab=xvar,ylab=yvar3,cex=1,col=col.age(data[[spp]]$age),xlim=c(1,35))
+      if(spp=="BOLE"|spp=="COER"|spp=="GRSP"|spp=="HEPU") {
+    rect(14,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
+    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
+  }
+  if(spp=="PILI") {
+    rect(10,10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="light grey",density=NA)
+    rect(10^par("usr")[1],10^par("usr")[3],10^par("usr")[2],10^par("usr")[4],col="black",density=0)
+  }
+  mtext(labels.spp.full(spp),3, outer=TRUE,font=3)
+  mtext("age (years)",outer=TRUE,1,line=1.5)
+}
+dev.off()
+```
 
-plot(RA_N~age,subset(SummaryInd2,species=="BAER"),col=col.age(age),pch=16)
-
-plot(leaf_N_lost ~ leaf_N_new,SummaryInd2,pch=16,col=col.spp(species),log="xy")
-plot(leaf_N_lost ~ leaf_N_new,SummaryInd2,pch=16,col=col.age(age),log="xy")
-
-abline(0,1)
-plot(leaf_P_net ~ leaf_N_net,SummaryInd2,pch=16,col=col.spp(species),log="xy")
-
-View(SummaryInd2)
 #simple N vs P plot
@@
 
+#plotting NP data for each species, colored by age
 ```{r}
@@
 ```
-
-#shed leaf N per year

### 2016-10-25 scripts/RA_figs_20160627.Rmd
new RA plot showing how proportion of energy to different outcomes shift across life

@@
 ```
+  data <- data %>% mutate(
+    total_inv = repro_inv + growth_leaf + leaf_replacement + growth_stem,
+    prop_repro = repro_inv / total_inv,
+    prop_leaf_expand = (repro_inv + growth_leaf)/total_inv,
+    prop_leaf_replacement = (leaf_replacement+repro_inv + growth_leaf)/ total_inv,
+    prop_stem = total_inv/total_inv
+  )
 
-#Figure 1 Different species have different RA values. But biggest shift in RA is with age
+View(data)
+
+```{r}
+data <- dplyr::select(SummarySppAge[["mean"]],species,age,repro_inv,growth_leaf,leaf_replacement,growth_stem,leaf_shed)
+
+  for(v in c("repro_inv","growth_leaf","leaf_replacement","growth_stem","leaf_shed")) {
+    i <- is.na(data[[v]])
+    data[[v]][i] <- 0
+  }
+
+  for(v in c("growth_leaf")) {
+    i <- (data[[v]] < 0)
+    data[[v]][i] <- 0
+  }
+
+#data <- subset(data,species=="BOLE")
+data <- split(data, data$species)
+
+for(spp in names(data)) {
+
+  data[[spp]] <- data[[spp]] %>% mutate(
+    total_inv = repro_inv + growth_leaf + leaf_replacement + growth_stem,
+    prop_repro = repro_inv / total_inv,
+    prop_leaf_expand = (repro_inv + growth_leaf)/total_inv,
+    prop_leaf_replacement = (leaf_replacement+repro_inv + growth_leaf)/ total_inv,
+    prop_stem = total_inv/total_inv
+  )
+
+  plot(prop_repro~age,data[[spp]],pch=16,log="x",ylim=c(0.04,0.96),xlim=c(1.06*1.4,0.94*32),col="white")
+
+  if(spp=="PILI") {
+  polygon(x=c(1.4,7,7,1.4),y=c(1,1,0,0),col="burlywood4",density=NA)
+  polygon(x=c(1.4,2.4,5,7,7,1.4),y=c(data[[spp]]$prop_leaf_replacement[1],data[[spp]]$prop_leaf_replacement[2],data[[spp]]$prop_leaf_replacement[3],data[[spp]]$prop_leaf_replacement[4],
+                                           0,0),col="darkseagreen4",density=NA)
+  polygon(x=c(1.4,2.4,5,7,7,1.4),y=c(data[[spp]]$prop_leaf_expand[1],data[[spp]]$prop_leaf_expand[2],data[[spp]]$prop_leaf_expand[3],data[[spp]]$prop_leaf_expand[4],
+                                         0,0),col="darkseagreen2",density=NA)
+  polygon(x=c(1.4,2.4,5,7,7,1.4),y=c(data[[spp]]$prop_repro[1],data[[spp]]$prop_repro[2],data[[spp]]$prop_repro[3],data[[spp]]$prop_repro[4],
+                                         0,0),col="coral3",density=NA)
+  text(5,0.1,"reproductive")
+  text(1.4,0.18,"additional leaves",adj=0)
+  text(3,0.4,"replacement leaves",adj=0)
+  text(2,0.7,"additional stems",adj=0)
+  }
+
+  if(spp=="PHPH") {
+  polygon(x=c(2.4,32,32,2.4),y=c(1,1,0,0),col="burlywood4",density=NA)
+  polygon(x=c(2.4,5,7,9,32,32,2.4),y=c(data[[spp]]$prop_leaf_replacement[1],data[[spp]]$prop_leaf_replacement[2],data[[spp]]$prop_leaf_replacement[3],data[[spp]]$prop_leaf_replacement[4],
+                                           data[[spp]]$prop_leaf_replacement[5],0,0),col="darkseagreen4",density=NA)
+  polygon(x=c(2.4,5,7,9,32,32,2.4),y=c(data[[spp]]$prop_leaf_expand[1],data[[spp]]$prop_leaf_expand[2],data[[spp]]$prop_leaf_expand[3],data[[spp]]$prop_leaf_expand[4],
+                                         data[[spp]]$prop_leaf_expand[5],0,0),col="darkseagreen2",density=NA)
+  polygon(x=c(2.4,5,7,9,32,32,2.4),y=c(data[[spp]]$prop_repro[1],data[[spp]]$prop_repro[2],data[[spp]]$prop_repro[3],data[[spp]]$prop_repro[4],
+                                          data[[spp]]$prop_repro[5],0,0),col="coral3",density=NA)
+  text(20,data[[spp]]$prop_repro[5]*.7,"reproductive")
+  text(2.5,data[[spp]]$prop_leaf_expand[1]*.3,"additional leaves",adj=0)
+  text(5,data[[spp]]$prop_leaf_replacement[4]*.6,"replacement leaves",adj=0)
+  text(15,0.9,"additional stems",adj=0)
+    }
+
+ if(spp=="BOLE"|spp=="COER"|spp=="HEPU"|spp=="GRSP") {
+  polygon(x=c(1.4,9,9,1.4),y=c(1,1,0,0),col="burlywood4",density=NA) 
+  polygon(x=c(1.4,2.4,5,7,9,9,1.4),y=c(data[[spp]]$prop_leaf_replacement[1],data[[spp]]$prop_leaf_replacement[2],data[[spp]]$prop_leaf_replacement[3],data[[spp]]$prop_leaf_replacement[4],
+                                           data[[spp]]$prop_leaf_replacement[5],0,0),col="darkseagreen4",density=NA)
+  polygon(x=c(1.4,2.4,5,7,9,9,1.4),y=c(data[[spp]]$prop_leaf_expand[1],data[[spp]]$prop_leaf_expand[2],data[[spp]]$prop_leaf_expand[3],data[[spp]]$prop_leaf_expand[4],
+                                         data[[spp]]$prop_leaf_expand[5],0,0),col="darkseagreen2",density=NA)
+  polygon(x=c(1.4,2.4,5,7,9,9,1.4),y=c(data[[spp]]$prop_repro[1],data[[spp]]$prop_repro[2],data[[spp]]$prop_repro[3],data[[spp]]$prop_repro[4],
+                                          data[[spp]]$prop_repro[5],0,0),col="coral3",density=NA)
+  text(8,data[[spp]]$prop_repro[5]*.4,"reproductive",adj=1)
+  text(1.5,data[[spp]]$prop_leaf_expand[1]*.5,"additional leaves",adj=0)
+  text(4,data[[spp]]$prop_leaf_replacement[3]*.6,"replacement leaves",adj=0)
+  text(6,0.9,"additional stems",adj=1)
+  }
+
+  if(spp=="BAER"|spp=="EPMI"|spp=="GRBU"|spp=="HATE"|spp=="PELA"|spp=="PUTU"|spp=="LEES"|spp=="PEPU") {
+  polygon(x=c(1.4,32,32,1.4),y=c(1,1,0,0),col="burlywood4",density=NA)
+  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_leaf_replacement[1],data[[spp]]$prop_leaf_replacement[2],data[[spp]]$prop_leaf_replacement[3],data[[spp]]$prop_leaf_replacement[4],
+                                           data[[spp]]$prop_leaf_replacement[5],data[[spp]]$prop_leaf_replacement[6],0,0),col="darkseagreen4",density=NA)
+  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_leaf_expand[1],data[[spp]]$prop_leaf_expand[2],data[[spp]]$prop_leaf_expand[3],data[[spp]]$prop_leaf_expand[4],
+                                         data[[spp]]$prop_leaf_expand[5],data[[spp]]$prop_leaf_expand[6],0,0),col="darkseagreen2",density=NA)
+  polygon(x=c(1.4,2.4,5,7,9,32,32,1.4),y=c(data[[spp]]$prop_repro[1],data[[spp]]$prop_repro[2],data[[spp]]$prop_repro[3],data[[spp]]$prop_repro[4],
+                                          data[[spp]]$prop_repro[5],data[[spp]]$prop_repro[6],0,0),col="coral3",density=NA)
+  text(20,data[[spp]]$prop_repro[6]*.4,"reproductive")
+  text(1.5,data[[spp]]$prop_leaf_expand[1]*.3,"additional leaves",adj=0)
+  text(5,data[[spp]]$prop_leaf_replacement[4]*.6,"replacement leaves",adj=0)
+  text(15,0.9,"additional stems",adj=0)
+  }
+  extra.top.left.logx(labels.spp.full(spp),3,1)
+}
+```
+
+-#Figure 1 Different species have different RA values. But biggest shift in RA is with age
 ```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}

### 2016-10-25 scripts/Accessory_figs_20160905.Rmd
redoing Figure 1 and Figure 2 for Accessory Costs ms

@@
-win.metafile("figs2/Accessory_Costs/scaled_ovule count.wmf", height=6, width=6)
+```{r}
+pdf("figs2/Accessory_Costs/scaled_ovule count.pdf", height=6, width=6)
 plot
@@
 
-mod2 <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-mod1 <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=mod2$groupsummary["Slope"][[1]])
+mod2 <- sma(scaled_seed_count ~ seed_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+mod1 <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=mod2$groupsummary["Slope"][[1]],elev.test=mod2$coef[[1]][1,1])
 
-plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,200),ylab="scaled count",xlim=c(.01,100),cex=1.5)
-points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
+plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,500),ylab="scaled count",xlim=c(.01,5000),cex=1.5)
+points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
 line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod1,3)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,1)
-#points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
-arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0,length=.15)
+line_function_log_xy(SummarySpp[["mean"]]$seed_costs,mod2,1)
+#points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],pch=12,col=col.spp(species))
+#arrows(SummarySpp[["mean"]]$seed_costs,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0,length=.15)
 
 dev.off()
+```
 
-summary(mod2)
-summary(mod1)
+mod_seed <- sma(scaled_seed_count ~ seed_costs, data=subset(SummaryInd),method="SMA", log="xy",slope.test=-1)
+mod_ovule <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummaryInd),method="SMA", log="xy",slope.test=mod2$groupsummary["Slope"][[1]],elev.test=mod2$coef[[1]][1,1])
 
-mod1 <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-mod2 <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,200),ylab="scaled count",xlim=c(.01,100),cex=1.5)
-points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
-line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod1,3)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,1)
-#points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
-arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0)
+plot(scaled_ovule_count ~ prepollen_costs, SummaryInd,log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.0001,1000),ylab="scaled count",xlim=c(.001,10000),cex=1.5)
+points(scaled_seed_count ~ seed_costs, SummaryInd,cex=1.5,pch=16,col=col.spp(species))
 
-plot(prop_prepollen_costs~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),cex=1.5,pch=16,col=col.spp(species),log="x")
-mod <- sma(prop_prepollen_costs~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),log="x",method="SMA")
-summary(mod)
+line_function_log_xy(SummaryInd$seed_costs,mod_seed,1)
+line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod_ovule,3)
 
-plot(prop_prepollen_costs~ seedset, data=subset(SummarySpp[["mean"]]),cex=1.5,pch=16,col=col.spp(species),log="x")
-mod <- sma(prop_prepollen_costs~ seedset, data=subset(SummarySpp[["mean"]]),log="x",method="SMA")
-summary(mod)
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.1,.05)) 
+plot(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.05,10000))
+points(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],pch=1,col=col.spp(species))
+mod_repro_costs <- sma(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=1)
+mod_fixed_costs <- sma(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_repro_costs$coef[[1]][2,1])
+line_function_log_xy(SummarySpp[["mean"]]$repro_inv_per_seed,mod_repro_costs,3)
+line_function_log_xy(SummarySpp[["mean"]]$seed_costs,mod_fixed_costs,1)
 
-#mod <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-summary(mod1)
-plot(success_inv ~ prepollen_success_inv, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),xlim=c(10,100000),ylim=c(10,100000))
-mod <- sma(success_inv ~ prepollen_success_inv, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
-line_function_log_xy(SummarySpp[["mean"]]$prepollen_success_inv,mod,1)
-line_function_log_xy_zero(SummarySpp[["mean"]]$prepollen_success_inv,mod,1)
+summary(mod_repro_costs)
+summary(mod_fixed_costs)
 
-SummaryInd$ovule_ratio <- SummaryInd$prepollen_costs/SummaryInd$embryo_endo_size
+plot(prepollen_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.005,5000))
+points(prepollen_all_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],pch=1,col=col.spp(species))
+#points(prepollen_failure_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch="-",col=col.spp(species))
+mod_prepollen_all <- sma(prepollen_all_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_repro_costs$coef[[1]][2,1])
+mod_prepollen_costs <- sma(prepollen_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_repro_costs$coef[[1]][2,1])
+line_function_log_xy(SummarySpp[["mean"]]$prepollen_all_per_seed,mod_prepollen_all,3)
+line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod_prepollen_costs,1)
 
-SummarySpp[["mean"]]$pre_pollen_all_inv_scaled <- SummarySpp[["mean"]]$prepollen_all_inv /SummarySpp[["mean"]]$leaf_area
-
-plot(leaf_area~prepollen_all_inv,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
-mod <- sma(leaf_area~prepollen_all_inv,SummarySpp[["mean"]],log="xy",slope=1, method="SMA")
-summary(mod)
-
-plot(pre_pollen_all_inv_scaled~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
-mod <- sma(pre_pollen_all_inv_scaled~embryo_endo_size,SummarySpp[["mean"]],log="xy",slope=1, method="SMA")
-
-dev.off()
+summary(mod_prepollen_all)
+summary(mod_prepollen_costs)
 
@@
 
+plot(prop_prepollen_all~seedset,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x")
+
+plot(prop_prepollen_costs~seedset,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="")
+
+mod <- sma(prop_prepollen_all~embryo_endo_size,SummaryInd,log="x",method="SMA")
+summary(mod)
+
 #Table 1 showing accessory cost values for the species
@@
 abline(slopes$groupsummary["Int"][[1]],1,lty=2)
+summary(slopes)
+
+plot(prop_prepollen_costs_all_repro~ seedset,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)
 
@@
 
-plot(scaled_seed_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=16,log="y",col=col.spp(species))
-points(scaled_ovule_count~prop_prepollen_costs,SummarySpp[["mean"]],pch=21,col=col.spp(species))
-#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
-axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
-axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
-mtext("count, scaled to plant size",2,line=2.3)
-mod1 <- sma(scaled_seed_count~prop_prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_seed_count!=0),log="y",slope=-1,method="SMA")
-mod2 <- sma(scaled_ovule_count~prepollen_costs,data=subset(SummarySpp[["mean"]],scaled_ovule_count!=0),log="xy",slope=3.23,method="SMA")
-mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="SMA")
-
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod1,1)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,2)
-legend("topright",legend=c("seed count","initiated ovules count"),col=c("black","black"),pch=c(16,21),bty="n")
-
-summary(mod1)
-summary(mod2)
-extra.top.left.logxy("a",2,1.2)
-
 #Figure 2. Scaling of accessory costs versus weight of embryo + endosperm, by species
@@
 
-par(mfrow=c(2,2), cex=1, omi=c(1,.1,.05,.05), mai=c(.2,.8,.1,.05)) 
+par(mfrow=c(3,1), cex=1, omi=c(1,.1,.05,.05), mai=c(.2,.8,.1,.05)) 
 options(scipen = 5)
 
-plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,1000),yaxt="n",xaxt="n",ylab="")
-points(scaled_ovule_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
-#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
+plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,5000),yaxt="n",xaxt="n",ylab="")
+points(scaled_ovule_count~prepollen_costs,SummaryInd,pch=21,col=col.spp(species))
+
 axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
@@
 mtext("count, scaled to plant size",2,line=2.3)
-mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="SMA")
-mod2 <- sma(scaled_ovule_count~embryo_endo_size,data=subset(SummaryInd,scaled_ovule_count!=0),log="xy",slope=-1,method="SMA")
-mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="SMA")
 
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod1,1)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,2)
+mod_seed <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="SMA")
+mod_ovule <- sma(scaled_ovule_count~prepollen_costs,data=subset(SummaryInd,scaled_ovule_count!=0),log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
+
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_seed,1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_ovule,2)
 legend("topright",legend=c("seed count","initiated ovules count"),col=c("black","black"),pch=c(16,21),bty="n")
+extra.top.left.logxy("a",2,1.2)
 
-extra.top.left.logxy("a",2,1.2)
+summary(mod_seed)
+summary(mod_ovule)
 
@@
 extra.top.left.logxy("d",2,1.2)
+
+mtext(text="     seed size (mg)",side=1,line=1.5,outer=TRUE,adj=0.5)
+mtext(text="                     parental pessimist",line=3,side=1,adj=0,outer=TRUE,font=3)
+mtext(text="parental optimist    ",line=3,side=1,adj=1,outer=TRUE,font=3)
+
+dev.off()
+```
+
+#predictions
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure01_predictions.wmf", height=9, width=6)
+plot
+
+par(mfrow=c(3,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=2)
+segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
+axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
+axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
+mtext(text="count, scaled to leaf area",side=2,line=1.3,outer=FALSE,cex=0.8)
+mtext(text="costs (mg/seed)",side=1,line=1.3,outer=FALSE,cex=0.8)
+legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
+
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
+axis(1, at=c(0,1),labels=c(0,1),cex.axis=1)
+axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
+mtext(text="choosiness (ovule:seed)",side=2,line=1.3,outer=FALSE,cex=0.8)
+mtext(text="proportion reproductive costs to pollen-attraction costs for 1 ovule",side=1,line=1.3,outer=FALSE,cex=0.8)
+
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
+segments(x0=.15,x1=.9,y0=.15,y1=.9,lty=2)
+axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
+axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
+mtext(text="proportion total success costs",side=2,line=1.8,outer=FALSE,cex=0.8)
+mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
+legend("bottomleft",legend=c("pollen-attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
+
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
+segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=2)
+axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
+axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
+mtext(text="proportion all pollen-attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
+mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
+legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
+
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=2)
+segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=1)
+axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
+axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
+mtext(text="proportion all provisioning investment",side=2,line=1.8,outer=FALSE,cex=0.8)
+mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
+legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
+
+dev.off()
+```
+
+#outcomes - Figure 2
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure02_Oct24.wmf", height=9, width=6)
+plot
+
+par(mfrow=c(3,2), cex=1, omi=c(.1,.1,.05,.05), mai=c(.7,.8,.05,.05)) 
+options(scipen = 5)
+
+plot(scaled_seed_count~seed_costs,SummarySpp[["mean"]],pch=16,log="xy",col="#ca0020",xlim=c(.01,5000),ylim=c(5e-4,500),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)
+points(scaled_ovule_count~prepollen_costs,SummarySpp[["mean"]],pch=16,col="#0571b0",cex=1)
+
+axis(2, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8,las=2)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=0.8)
+mtext("costs to make a successful unit",1,line=1.8,cex=0.7)
+mtext("count, scaled to plant size",2,line=2.3,cex=0.7)
+
+mod_seed <- sma(scaled_seed_count~seed_costs,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
+mod_ovule <- sma(scaled_ovule_count~prepollen_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
+
+line_function_log_xy(SummarySpp[["mean"]]$seed_costs,mod_seed,1,col="#ca0020")
+line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod_ovule,1,col="#0571b0")
+legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by","pollen-attraction costs"),col=c("#ca0020","#0571b0","white"),pch=c(16,16,16),bty="n",cex=0.7)
+extra.top.left.logxy("a",2,1)
+
+plot(choosiness~prop_prepollen_costs_all_repro,SummarySpp[["mean"]],log="xy",col="#0571b0",pch=16,xlim=c(0.002,.5),ylim=c(3,800),xaxt="n",yaxt="n",cex=1,ylab="",xlab="")
+axis(2, at=c(10,100,1000), labels=c(10,100,1000),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,0.1), labels=c(0.01,0.1),cex.axis=0.8)
+mtext("prop reproductive investment to",1,line=1.7,cex=0.7)
+mtext("successful pollen-attraction costs",1,line=2.3,cex=0.7)
+mtext("choosiness (ovules:seed)",2,line=2.3,cex=0.7)
+
+mod_choosy <- sma(choosiness~prop_prepollen_costs_all_repro,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
+line_function_log_xy(SummarySpp[["mean"]]$prop_prepollen_costs_all_repro,mod_choosy,1,col="#0571b0")
+
+extra.top.left.logxy("b",2,1)
+
+plot(prop_prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col="#0571b0",
+     ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
+points(prop_postpollen_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,col="#ca0020")
+extra.top.left.logx("c",2,1)
+axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
+mtext("seed size (mg)",1,line=1.8,cex=0.7)
+mtext("prop successful investment",2,line=2.3,cex=0.7)
+legend("bottomleft",legend=c("pollen-attraction costs","provisioning costs"),col=c("#0571b0","#ca0020"),pch=c(16,16),bty="n",cex=0.7)
+
+mod_prop_prepollen_costs <- sma(prop_prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_prepollen_costs,1,col="#0571b0")
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_costs,1,col="#ca0020")
+
+plot(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col="#0571b0",ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
+points(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],pch=16,col="#ca0020")
+extra.top.left.logx("d",2,1)
+axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
+mtext("seed size (mg)",1,line=1.8,cex=0.7)
+mtext("prop total pollen-attraction investment",2,line=2.3,cex=0.7)
+legend("bottomleft",legend=c("successful ovules","aborted ovules"),col=c("#0571b0","#ca0020"),pch=c(16,16),bty="n",cex=0.7)
+
+mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_prepollen_failure <- sma(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_prepollen_success,1,col="#0571b0")
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_prepollen_failure,1,col="#ca0020")
+
+plot(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col="#0571b0",ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
+points(prop_postpollen_failure~embryo_endo_size,SummarySpp[["mean"]],pch=16,col="#ca0020")
+extra.top.left.logx("e",2,1)
+axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
+mtext("seed size (mg)",1,line=1.8,cex=0.7)
+mtext("prop total provisioning investment",2,line=2.3,cex=0.7)
+legend("bottomleft",legend=c("successful zygotes","aborted zygotes"),col=c("#0571b0","#ca0020"),pch=c(16,16),bty="n",cex=0.7)
+
+mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_success,1,col="#0571b0")
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_failure,1,col="#ca0020")
+
+plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="xy",col="#0571b0",xlim=c(.002,100),ylim=c(.01,20000),xlab="",ylab="",xaxt="n",yaxt="n")
+points(provisioning_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,col="#ca0020")
+extra.top.left.logxy("f",2,1)
+axis(2, at=c(0.01,1,100,10000), labels=c(0.01,1,100,10000),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
+mtext("seed size (mg)",1,line=1.8,cex=0.7)
+mtext("success cost (mg/seed)",2,line=2.3,cex=0.7)
+legend("bottomright",legend=c("pollen-attraction","provisioning"),col=c("#0571b0","#ca0020"),pch=c(16,16),bty="n",cex=0.7)
+
+mod_prepollen_costs <- sma(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
+mod_provisioning_costs <- sma(provisioning_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA",slope.test = mod_prepollen_costs$groupsummary$Slope_highCI)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_prepollen_costs,1,col="#0571b0")
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_provisioning_costs,1,col="#ca0020")
+
+dev.off()
+```
+
+#Table with above model results
+```{r}
+mod_prop_prepollen_costs <- sma(prop_prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_prepollen_failure <- sma(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+
+energy_prop <- dplyr::select(mod_prop_prepollen_costs$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+energy_prop$test[1] <- "Proportion prepollen costs"
+
+temp <- dplyr::select(mod_prop_prepollen_success$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+temp$test[1] <- "Proportion prepollen costs to success"
+energy_prop <- rbind(energy_prop,temp)
+
+temp <- dplyr::select(mod_prop_postpollen_success$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+temp$test[1] <- "Proportion postpollen costs to success"
+energy_prop <- rbind(energy_prop,temp)
+
+#temp <- dplyr::select(mod_prop_postpollen_costs$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+#temp$test[1] <- "Proportion postpollen costs"
+#energy_prop <- rbind(energy_prop,temp)
+
+#temp <- dplyr::select(mod_prop_prepollen_failure$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+#temp$test[1] <- "Proportion prepollen costs to failure"
+#energy_prop <- rbind(energy_prop,temp)
+
+#temp <- dplyr::select(mod_prop_postpollen_failure$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+#temp$test[1] <- "Proportion postpollen costs to failure"
+#energy_prop <- rbind(energy_prop,temp)
+
+```
+
+#Figure 2_NEW. Scaling of accessory costs versus weight of embryo + endosperm, by species
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure02_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
+plot
+
+par(mfrow=c(2,2), cex=1, omi=c(1,.1,.05,.05), mai=c(.2,.8,.1,.05)) 
+options(scipen = 5)
+
+plot((repro_all_count/seed_count)~prop_prepollen_costs_all_repro,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),ylab="",ylim=c(.8,500),yaxt="n",xlim=c(.0015,.5),xaxt="n")
+axis(2, at=c(1,10,100), labels=c(1,10,100),cex.axis=1)
+axis(1, at=c(0.001,0.005,0.01,0.05,0.1,0.5), labels=c(0.001,0.005,0.01,0.05,0.1,0.5),cex.axis=1)
+mtext("choosiness (ovules initiated per seed matured)",2,line=2.3)
+mtext("proportion reproductive investment for successful pollen-attraction costs",1,line=2.3)
+
+mod_choosy <- sma((repro_all_count/seed_count)~prop_prepollen_costs_all_repro,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
+
+line_function_log_xy(SummarySpp[["mean"]]$prop_prepollen_costs_all_repro,mod_choosy,1)
+summary(mod_choosy)
+
+plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.002,500),ylim=c(.004,.6),cex=1.5,xaxt="n",xlab="",ylab="")
+mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="SMA")
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+#text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
+mtext("seed set",2,line=2.3)
+extra.top.left.logxy("b",2,1.2)
+summary(mod)
+
+plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
+
+points(provisioning_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=21,cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)
+
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
+mtext("costs (mg/ovule)",2,line=2.3)
+
+mod_prepollen <- sma(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
+mod_provision <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_prepollen$groupsummary["Slope"][[1]])
+
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_prepollen,1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_provision,2)
+
+legend("topright",legend=c("pollen-attraction","provisioning"),col=c("black","black"),pch=c(16,21),bty="n")
+extra.top.left.logxy("c",2,1.2)
+
+plot(prop_prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+points(prop_prepollen_all~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
+axis(2, at=c(0,.5,1), labels=c(0,0.5,1.0),cex.axis=1)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
+extra.top.left.logx("d",2,1.2)
+
+mod_prop_prepollen_costs <- sma(prop_prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
+mod_prop_prepollen_all <- sma(prop_prepollen_all~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
+
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_prepollen_costs,1)
+
+summary(mod_prop_prepollen_costs)
+summary(mod_prop_prepollen_all)
+
+plot(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+points(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
+axis(2, at=c(0,.5,1), labels=c(0,0.5,1.0),cex.axis=1)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
+extra.top.left.logx("d",2,1.2)
+
+mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA")
+mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA")
+
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_success,1)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_prepollen_success,3)
+
+summary(mod_prop_postpollen_success)
+summary(mod_prop_prepollen_success)
 

### 2016-10-26 scripts/Accessory_figs_20160905.Rmd
small changes

@@
 
-plot(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col="#0571b0",ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
+plot(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col="#0571b0",ylim=c(-.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
 points(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],pch=16,col="#ca0020")
@@
 mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_prepollen_success_SMA <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA")
 mod_prop_prepollen_failure <- sma(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")

### 2016-10-26 R/Summaries.R

@@ -137,10 +137,22 @@ combine_by_individual <- function(IndividualsList, Growth_all, Accessory_counts_
     leaf_area_0_mature = leaf_area_0, #included, because when summarizing by species, this averages leaf area only for individuals that are reproducing
     seed_minus_embryo_endo = seed_size - embryo_endo_size,
     prepollen_costs = prepollen_partial_costs + pack_disp_early_costs, #all costs, ON A PER SEED BASIS, up to the point of pollination
+    prepollen_success_to_flower_inv = prepollen_success_inv, #redefining, such that prepollen_success_to_flower is all parts that DO reach open flower stage, and prepollen_success is below defined to just be flowers that progress to seeds
     pack_disp_costs = pack_disp_gross_costs + seed_minus_embryo_endo, #add in non-embryo-endo seed weight
     seed_costs = embryo_endo_size + pack_disp_costs + prepollen_costs,
     embryo_endo_costs = embryo_endo_size - seed_early_costs, #ON A PER SEED BASIS, cost of making a single propagule - now defined as an embryo + endosperm
-    prepollen_all_inv = prepollen_aborted_inv + prepollen_success_inv, #prepollen_success_inv is also flowers, so much bigger than investment in flowers that become seeds
+    aborted_seed_count = repro_all_count - seed_count - prepollen_all_count,
+    zygote_set = seed_count / (seed_count + aborted_fruit_count),
+    pollen_set = (seed_count + aborted_fruit_count) / flower_count,
+    prepollen_all_inv = prepollen_aborted_inv + prepollen_success_to_flower_inv, #prepollen_success_to_flower_inv is also flowers that don't progress, so much bigger than investment in flowers that become seeds
+    prepollen_success_inv = prepollen_costs*seed_count #prepollen_success_inv is redefined as investment to parts that develop into seeds
+  )
+    
+    
+
+    
+    
+  SummaryInd <- SummaryInd %>% mutate(  
     prepollen_failure_inv = prepollen_all_inv - (seed_count*prepollen_costs), #failure is all parts that don't progress to seeds; aborted is parts that don't reach flowering
     postpollen_all_inv = postpollen_aborted_inv + packaging_dispersal_inv + propagule_inv,
     postpollen_aborted_inv = postpollen_all_inv - (seed_count*pack_disp_costs) - (seed_count*embryo_endo_size), #so energy of empty seedpods becomes part of aborted
[…]

### 2016-11-01 scripts/Accessory_figs_20160905.Rmd
mainly updating some variable names, but also changes to Summaries to fix pre vs post pollination energy balancing.

--- 2016-10-11 scripts/Accessory_figs_20160905.Rmd
@@
 
-mod2 <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-mod1 <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=mod2$groupsummary["Slope"][[1]])
+mod2 <- sma(scaled_seed_count ~ seed_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+mod1 <- sma(scaled_ovule_count ~ pollen_attract_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=mod2$groupsummary["Slope"][[1]],elev.test=mod2$coef[[1]][1,1])
 
-plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,200),ylab="scaled count",xlim=c(.01,100),cex=1.5)
-points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
-line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod1,3)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,1)
-#points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
-arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0,length=.15)
+plot(scaled_ovule_count ~ pollen_attract_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,500),ylab="scaled count",xlim=c(.01,5000),cex=1.5)
+points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
+line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod1,3)
+line_function_log_xy(SummarySpp[["mean"]]$seed_costs,mod2,1)
+#points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],pch=12,col=col.spp(species))
+#arrows(SummarySpp[["mean"]]$seed_costs,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0,length=.15)
 
 dev.off()
+```
 
-summary(mod2)
-summary(mod1)
+mod_seed <- sma(scaled_seed_count ~ seed_costs, data=subset(SummaryInd),method="SMA", log="xy",slope.test=-1)
+mod_ovule <- sma(scaled_ovule_count ~ pollen_attract_costs, data=subset(SummaryInd),method="SMA", log="xy",slope.test=mod2$groupsummary["Slope"][[1]],elev.test=mod2$coef[[1]][1,1])
 
-mod1 <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-mod2 <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,200),ylab="scaled count",xlim=c(.01,100),cex=1.5)
-points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
-line_function_log_xy(SummarySpp[["mean"]]$prepollen_costs,mod1,3)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,1)
-#points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
-arrows(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0)
+plot(scaled_ovule_count ~ pollen_attract_costs, SummaryInd,log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.0001,1000),ylab="scaled count",xlim=c(.001,10000),cex=1.5)
+points(scaled_seed_count ~ seed_costs, SummaryInd,cex=1.5,pch=16,col=col.spp(species))
 
-plot(prop_prepollen_costs~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),cex=1.5,pch=16,col=col.spp(species),log="x")
-mod <- sma(prop_prepollen_costs~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),log="x",method="SMA")
-summary(mod)
+line_function_log_xy(SummaryInd$seed_costs,mod_seed,1)
+line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_ovule,3)
 
-plot(prop_prepollen_costs~ seedset, data=subset(SummarySpp[["mean"]]),cex=1.5,pch=16,col=col.spp(species),log="x")
-mod <- sma(prop_prepollen_costs~ seedset, data=subset(SummarySpp[["mean"]]),log="x",method="SMA")
-summary(mod)
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.1,.05)) 
+plot(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.05,10000))
+points(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],pch=1,col=col.spp(species))
+mod_repro_costs <- sma(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=1)
+mod_fixed_costs <- sma(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_repro_costs$coef[[1]][2,1])
+line_function_log_xy(SummarySpp[["mean"]]$repro_inv_per_seed,mod_repro_costs,3)
+line_function_log_xy(SummarySpp[["mean"]]$seed_costs,mod_fixed_costs,1)
 
-#mod <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-summary(mod1)
-plot(success_inv ~ prepollen_success_inv, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),xlim=c(10,100000),ylim=c(10,100000))
-mod <- sma(success_inv ~ prepollen_success_inv, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
-line_function_log_xy(SummarySpp[["mean"]]$prepollen_success_inv,mod,1)
-line_function_log_xy_zero(SummarySpp[["mean"]]$prepollen_success_inv,mod,1)
+summary(mod_repro_costs)
+summary(mod_fixed_costs)
 
-SummaryInd$ovule_ratio <- SummaryInd$prepollen_costs/SummaryInd$embryo_endo_size
+plot(pollen_attract_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.005,5000))
+points(prepollen_all_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],pch=1,col=col.spp(species))
+#points(prepollen_failure_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch="-",col=col.spp(species))
+mod_prepollen_all <- sma(prepollen_all_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_repro_costs$coef[[1]][2,1])
+mod_pollen_attract_costs <- sma(pollen_attract_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_repro_costs$coef[[1]][2,1])
+line_function_log_xy(SummarySpp[["mean"]]$prepollen_all_per_seed,mod_prepollen_all,3)
+line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_pollen_attract_costs,1)
 
-SummarySpp[["mean"]]$pre_pollen_all_inv_scaled <- SummarySpp[["mean"]]$prepollen_all_inv /SummarySpp[["mean"]]$leaf_area
-
-plot(leaf_area~prepollen_all_inv,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
-mod <- sma(leaf_area~prepollen_all_inv,SummarySpp[["mean"]],log="xy",slope=1, method="SMA")
-summary(mod)
-
-plot(pre_pollen_all_inv_scaled~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16)
-mod <- sma(pre_pollen_all_inv_scaled~embryo_endo_size,SummarySpp[["mean"]],log="xy",slope=1, method="SMA")
-
-dev.off()
+summary(mod_prepollen_all)
+summary(mod_pollen_attract_costs)
 
@@
 #relationship between plant weight and number of ovules initiated - bigger plants produce proportionally fewer buds
-mod <- sma(repro_all_count~total_weight,SummaryInd,method="SMA",log="xy",slope=1)
+mod <- sma(ovule_count~total_weight,SummaryInd,method="SMA",log="xy",slope=1)
 summary(mod)
@@
 #energy invested in accessory tissues unrelated to seedsize
-mod <- sma(accessory_per_seed_using_ee ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
+mod <- sma(accessory_costs_using_ee ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(accessory_per_seed_using_ee ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(accessory_costs_using_ee ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 
-mod <- sma(prop_prepollen_costs ~ seedset, data=subset(SummarySpp[["mean"]]),method="SMA", log="x",slope.test=1)
+mod <- sma(prop_pollen_attract_costs ~ seedset, data=subset(SummarySpp[["mean"]]),method="SMA", log="x",slope.test=1)
 summary(mod)
-plot(prop_prepollen_costs ~ seedset, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))
+plot(prop_pollen_attract_costs ~ seedset, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))
 
-mod <- sma(scaled_ovule_count ~ prepollen_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+mod <- sma(scaled_ovule_count ~ pollen_attract_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
 summary(mod)
-plot(scaled_ovule_count ~ prepollen_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(scaled_ovule_count ~ pollen_attract_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 summary(mod)
-plot(prepollen_failure_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.02,10000))
-points(prepollen_costs~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species))
+plot(prepollen_failure_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.02,10000))
+points(pollen_attract_costs~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species))
 
@@
 #seedset by pollen attraction
-mod <- sma(prop_prepollen_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
+mod <- sma(prop_pollen_attract_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
 summary(mod)
@@
 #scaled ovule production vs prop pollen attraction  - all species
-mod <- sma(prop_prepollen_costs~scaled_ovule_count,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
+mod <- sma(prop_pollen_attract_costs~scaled_ovule_count,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
 summary(mod)
-plot(prop_prepollen_costs ~ scaled_ovule_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(prop_pollen_attract_costs ~ scaled_ovule_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
-yvar <- "repro_all_count"
+yvar <- "ovule_count"
 xvar <- "repro_inv"
@@
 
-yvar <- "repro_all_count"
+yvar <- "ovule_count"
 xvar <- "leaf_area_0"
@@
 
+plot(prop_prepollen_all~seedset,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x")
+
+plot(prop_pollen_attract_costs~seedset,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="")
+
+mod <- sma(prop_prepollen_all~embryo_endo_size,SummaryInd,log="x",method="SMA")
+summary(mod)
+
 #Table 1 showing accessory cost values for the species
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,seedset,repro_inv_per_seed,prop_failure,prop_prepollen_vs_RE, prop_dispersal_vs_RE,prop_embryo_endo_vs_RE,seed_costs,prop_prepollen_costs,prop_postpollen_costs,embryo_endo_size,pack_disp_costs,prepollen_costs,failure_inv,repro_inv,seed_count)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,seedset,repro_inv_per_seed,prop_failure,prop_prepollen_vs_RE, prop_pack_disp_vs_RE,prop_embryo_endo_vs_RE,seed_costs,prop_pollen_attract_costs,prop_postpollen_costs,embryo_endo_size,pack_disp_costs,pollen_attract_costs,failure_inv,repro_inv,seed_count)
 acc_costs_spp$species <- labels.spp.full()
 acc_costs_spp_format <- acc_costs_spp
-for (i in c("embryo_endo_size","seedset","repro_inv_per_seed","prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","seed_costs","prop_prepollen_costs","prop_postpollen_costs")) {
+for (i in c("embryo_endo_size","seedset","repro_inv_per_seed","prop_failure","prop_prepollen_vs_RE","prop_pack_disp_vs_RE","prop_embryo_endo_vs_RE","seed_costs","prop_pollen_attract_costs","prop_postpollen_costs")) {
   acc_costs_spp_format[[i]] <- round(acc_costs_spp_format[[i]],digits=3)
@@
 
-for (i in c("prop_failure","prop_prepollen_vs_RE","prop_dispersal_vs_RE","prop_embryo_endo_vs_RE","prop_prepollen_costs","prop_postpollen_costs")) {
+for (i in c("prop_failure","prop_prepollen_vs_RE","prop_pack_disp_vs_RE","prop_embryo_endo_vs_RE","prop_pollen_attract_costs","prop_postpollen_costs")) {
   acc_costs_spp_format[[i]] <- round(100*acc_costs_spp_format[[i]],digits=1)
@@
 plot(repro_inv_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$repro_inv_per_seed,SummarySpp[["se"]]$accessory_per_seed)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$repro_inv_per_seed,SummarySpp[["se"]]$accessory_costs)
 slopes <- sma(repro_inv_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
@@
 abline(slopes$groupsummary["Int"][[1]],1,lty=2)
+summary(slopes)
+
+plot(prop_pollen_attract_costs_all_repro~ seedset,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)
 
@@
 
-plot(prepollen_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
-slopes <- sma(prepollen_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+plot(pollen_attract_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
+slopes <- sma(pollen_attract_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot(prepollen_failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_failure_per_seed,SummarySpp[["se"]]$prepollen_failure_per_seed)
-slopes <- sma(prepollen_failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+plot(prepollen_failure_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_failure_costs,SummarySpp[["se"]]$prepollen_failure_costs)
+slopes <- sma(prepollen_failure_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted during provisioning costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_aborted_per_seed,SummarySpp[["se"]]$postpollen_aborted_per_seed)
-slopes <- sma(postpollen_aborted_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+plot(postpollen_aborted_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted during provisioning costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_aborted_costs,SummarySpp[["se"]]$postpollen_aborted_costs)
+slopes <- sma(postpollen_aborted_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-par(mfrow=c(2,2), cex=1, omi=c(1,.1,.05,.05), mai=c(.2,.8,.1,.05)) 
+par(mfrow=c(3,1), cex=1, omi=c(1,.1,.05,.05), mai=c(.2,.8,.1,.05)) 
 options(scipen = 5)
 
-plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,1000),yaxt="n",xaxt="n",ylab="")
-points(scaled_ovule_count~embryo_endo_size,SummaryInd,pch=21,col=col.spp(species))
-#points(scaled_failure_count~embryo_endo_size,SummaryInd,pch=2,col=col.spp(species))
+plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,5000),yaxt="n",xaxt="n",ylab="")
+points(scaled_ovule_count~pollen_attract_costs,SummaryInd,pch=21,col=col.spp(species))
+
 axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
@@
 mtext("count, scaled to plant size",2,line=2.3)
-mod1 <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="SMA")
-mod2 <- sma(scaled_ovule_count~embryo_endo_size,data=subset(SummaryInd,scaled_ovule_count!=0),log="xy",slope=-1,method="SMA")
-mod3 <- sma(scaled_failure_count~embryo_endo_size,data=subset(SummaryInd,scaled_failure_count!=0),log="xy",slope=-1,method="SMA")
 
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod1,1)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod2,2)
+mod_seed <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="SMA")
+mod_ovule <- sma(scaled_ovule_count~pollen_attract_costs,data=subset(SummaryInd,scaled_ovule_count!=0),log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
+
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_seed,1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_ovule,2)
 legend("topright",legend=c("seed count","initiated ovules count"),col=c("black","black"),pch=c(16,21),bty="n")
+extra.top.left.logxy("a",2,1.2)
 
-extra.top.left.logxy("a",2,1.2)
+summary(mod_seed)
+summary(mod_ovule)
 
@@
 
-plot(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_costs,SummarySpp[["se"]]$prepollen_costs)
-mod <- sma(prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
+plot(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
+mod <- sma(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
 #abline(mod$groupsummary["Int"][[1]],1,lty=2)
@@
 plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$prepollen_costs)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$pollen_attract_costs)
 mod <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
@@
 extra.top.left.logxy("d",2,1.2)
+
+mtext(text="     seed size (mg)",side=1,line=1.5,outer=TRUE,adj=0.5)
+mtext(text="                     parental pessimist",line=3,side=1,adj=0,outer=TRUE,font=3)
+mtext(text="parental optimist    ",line=3,side=1,adj=1,outer=TRUE,font=3)
+
+dev.off()
+```
+
+#predictions
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure01_predictions.wmf", height=9, width=6)
+plot
+
+par(mfrow=c(3,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=2)
+segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
+axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
+axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
+mtext(text="count, scaled to leaf area",side=2,line=1.3,outer=FALSE,cex=0.8)
+mtext(text="costs (mg/seed)",side=1,line=1.3,outer=FALSE,cex=0.8)
+legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by pollen_attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
+
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
+axis(1, at=c(0,1),labels=c(0,1),cex.axis=1)
+axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
+mtext(text="choosiness (ovule:seed)",side=2,line=1.3,outer=FALSE,cex=0.8)
+mtext(text="proportion reproductive costs to pollen_attraction costs for 1 ovule",side=1,line=1.3,outer=FALSE,cex=0.8)
+
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
+segments(x0=.15,x1=.9,y0=.15,y1=.9,lty=2)
+axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
+axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
+mtext(text="proportion total success costs",side=2,line=1.8,outer=FALSE,cex=0.8)
+mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
+legend("bottomleft",legend=c("pollen_attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
+
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
+segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=2)
+axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
+axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
+mtext(text="proportion all pollen_attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
+mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
+legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
+
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=2)
+segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=1)
+axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
+axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
+mtext(text="proportion all provisioning investment",side=2,line=1.8,outer=FALSE,cex=0.8)
+mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
+legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
+
+dev.off()
+```
+
+#outcomes - Figure 2
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure02_Oct24.wmf", height=9, width=6)
+plot
+
+par(mfrow=c(3,2), cex=1, omi=c(.1,.1,.05,.05), mai=c(.7,.8,.05,.05)) 
+options(scipen = 5)
+
+#panel a
+plot(scaled_seed_count~seed_costs,SummarySpp[["mean"]],pch=16,log="xy",col=venetian_red,xlim=c(.01,5000),ylim=c(5e-4,500),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)
+points(scaled_ovule_count~pollen_attract_costs,SummarySpp[["mean"]],pch=16,col=cerulean,cex=1)
+
+axis(2, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8,las=2)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=0.8)
+mtext("costs to make a successful unit",1,line=1.8,cex=0.7)
+mtext("count, scaled to leaf area",2,line=2.3,cex=0.7)
+
+mod_seed <- sma(scaled_seed_count~seed_costs,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
+mod_ovule <- sma(scaled_ovule_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
+
+line_function_log_xy(SummarySpp[["mean"]]$seed_costs,mod_seed,1,col=venetian_red)
+line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_ovule,1,col=cerulean)
+legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by","pollen_attraction costs"),col=c(venetian_red,cerulean,"white"),pch=c(16,16,16),bty="n",cex=0.7)
+extra.top.left.logxy("a",2,1)
+
+#panel b
+#plot(choosiness~prop_pollen_attract_costs_all_repro,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(0.002,.5),ylim=c(3,800),xaxt="n",yaxt="n",cex=1,ylab="",xlab="")
+plot(choosiness~scaled_pollen_attract_costs,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(.002,.3),ylim=c(3,800),yaxt="n",cex=1,ylab="",xlab="",xaxt="n")
+axis(2, at=c(10,100,1000), labels=c(10,100,1000),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,0.1), labels=c(0.01,0.1),cex.axis=0.8)
+mtext("pollen-attractions costs, scaled to leaf area",1,line=1.7,cex=0.7)
+mtext("choosiness (ovules:seed)",2,line=2.3,cex=0.7)
+mod_choosy2 <- sma(choosiness~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",slope=-1,method="SMA")
+line_function_log_xy(SummarySpp[["mean"]]$scaled_pollen_attract_costs,mod_choosy2,1,col=cerulean)
+extra.top.left.logxy("b",2,1)
+
+#panel c - success proportions
+plot(prop_pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,
+     ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
+points(prop_postpollen_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,col=venetian_red)
+extra.top.left.logx("c",2,1)
+axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
+mtext("seed size (mg)",1,line=1.8,cex=0.7)
+mtext("prop. successful investment",2,line=2.3,cex=0.7)
+legend("bottomleft",legend=c("pollen_attraction costs","provisioning costs"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)
+
+mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_pollen_attract_costs,1,col=cerulean)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_costs,1,col=venetian_red)
+
+#panel d - pollen-attraction proportions
+plot(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
+points(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],pch=16,col=venetian_red)
+extra.top.left.logx("d",2,1)
+axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
+mtext("seed size (mg)",1,line=1.8,cex=0.7)
+mtext("prop. total pollen-attraction investment",2,line=2.3,cex=0.7)
+legend("bottomleft",legend=c("successful ovules","discarded ovules"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)
+
+mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_prepollen_failure <- sma(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_prepollen_success,1,col=cerulean)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_prepollen_failure,1,col=venetian_red)
+
+#panel e - provisioning proportions
+plot(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
+points(prop_postpollen_failure~embryo_endo_size,SummarySpp[["mean"]],pch=16,col=venetian_red)
+extra.top.left.logx("e",2,1)
+axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
+mtext("seed size (mg)",1,line=1.8,cex=0.7)
+mtext("prop. total provisioning investment",2,line=2.3,cex=0.7)
+legend("bottomleft",legend=c("successful zygotes","aborted zygotes"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)
+
+mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_success,1,col=cerulean)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_failure,1,col=venetian_red)
+
+#panel f - change in slope of "success costs"
+plot(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="xy",col=cerulean,xlim=c(.002,100),ylim=c(.01,20000),xlab="",ylab="",xaxt="n",yaxt="n")
+points(provisioning_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,col=venetian_red)
+extra.top.left.logxy("f",2,1)
+axis(2, at=c(0.01,1,100,10000), labels=c(0.01,1,100,10000),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
+mtext("seed size (mg)",1,line=1.8,cex=0.7)
+mtext("success cost (mg/seed)",2,line=2.3,cex=0.7)
+legend("bottomright",legend=c("pollen_attraction","provisioning"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)
+
+mod_pollen_attract_costs <- sma(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
+mod_provisioning_costs <- sma(provisioning_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA",slope.test = mod_pollen_attract_costs$groupsummary$Slope_highCI)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_pollen_attract_costs,1,col=cerulean)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_provisioning_costs,1,col=venetian_red)
+
+dev.off()
+```
+
+#Table with above model results
+```{r}
+mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_prepollen_success_SMA <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA")
+mod_prop_prepollen_failure <- sma(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+
+energy_prop <- dplyr::select(mod_prop_pollen_attract_costs$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+energy_prop$test[1] <- "Proportion sucess costs to prepollen"
+
+temp <- dplyr::select(mod_prop_prepollen_success$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+temp$test[1] <- "Proportion prepollen costs to success"
+energy_prop <- rbind(energy_prop,temp)
+
+temp <- dplyr::select(mod_prop_postpollen_success$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+temp$test[1] <- "Proportion postpollen costs to success"
+energy_prop <- rbind(energy_prop,temp)
+
+#temp <- dplyr::select(mod_prop_postpollen_costs$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+#temp$test[1] <- "Proportion postpollen costs"
+#energy_prop <- rbind(energy_prop,temp)
+
+#temp <- dplyr::select(mod_prop_prepollen_failure$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+#temp$test[1] <- "Proportion prepollen costs to failure"
+#energy_prop <- rbind(energy_prop,temp)
+
+#temp <- dplyr::select(mod_prop_postpollen_failure$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+#temp$test[1] <- "Proportion postpollen costs to failure"
+#energy_prop <- rbind(energy_prop,temp)
+
+```
+
+#Figure 2_NEW. Scaling of accessory costs versus weight of embryo + endosperm, by species
+```{r}
+win.metafile("figs2/Accessory_Costs/Figure02_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
+plot
+
+par(mfrow=c(2,2), cex=1, omi=c(1,.1,.05,.05), mai=c(.2,.8,.1,.05)) 
+options(scipen = 5)
+
+plot((ovule_count/seed_count)~prop_pollen_attract_costs_all_repro,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),ylab="",ylim=c(.8,500),yaxt="n",xlim=c(.0015,.5),xaxt="n")
+axis(2, at=c(1,10,100), labels=c(1,10,100),cex.axis=1)
+axis(1, at=c(0.001,0.005,0.01,0.05,0.1,0.5), labels=c(0.001,0.005,0.01,0.05,0.1,0.5),cex.axis=1)
+mtext("choosiness (ovules initiated per seed matured)",2,line=2.3)
+mtext("proportion reproductive investment for successful pollen_attraction costs",1,line=2.3)
+
+mod_choosy <- sma((ovule_count/seed_count)~prop_pollen_attract_costs_all_repro,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
+
+line_function_log_xy(SummarySpp[["mean"]]$prop_pollen_attract_costs_all_repro,mod_choosy,1)
+summary(mod_choosy)
+
+plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.002,500),ylim=c(.004,.6),cex=1.5,xaxt="n",xlab="",ylab="")
+mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="SMA")
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+#text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
+mtext("seed set",2,line=2.3)
+extra.top.left.logxy("b",2,1.2)
+summary(mod)
+
+plot(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
+
+points(provisioning_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=21,cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)
+
+axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
+mtext("costs (mg/ovule)",2,line=2.3)
+
+mod_prepollen <- sma(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
+mod_provision <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_prepollen$groupsummary["Slope"][[1]])
+
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_prepollen,1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_provision,2)
+
+legend("topright",legend=c("pollen_attraction","provisioning"),col=c("black","black"),pch=c(16,21),bty="n")
+extra.top.left.logxy("c",2,1.2)
+
+plot(prop_pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+points(prop_prepollen_all~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
+axis(2, at=c(0,.5,1), labels=c(0,0.5,1.0),cex.axis=1)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
+extra.top.left.logx("d",2,1.2)
+
+mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
+mod_prop_prepollen_all <- sma(prop_prepollen_all~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
+
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_pollen_attract_costs,1)
+
+summary(mod_prop_pollen_attract_costs)
+summary(mod_prop_prepollen_all)
+
+plot(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+points(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
+axis(2, at=c(0,.5,1), labels=c(0,0.5,1.0),cex.axis=1)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
+extra.top.left.logx("d",2,1.2)
+
+mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA")
+mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA")
+
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_success,1)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_prepollen_success,3)
+
+summary(mod_prop_postpollen_success)
+summary(mod_prop_prepollen_success)
 
@@
 xvar <- "repro_inv"
-yvar <- "accessory_per_seed"
+yvar <- "accessory_costs"
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 xvar <- "total_weight_0"
-yvar <- "accessory_per_seed"
+yvar <- "accessory_costs"
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 xvar <- "age"
-yvar <- "accessory_per_seed"
+yvar <- "accessory_costs"
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 
-xvar <- "repro_all_count"
+xvar <- "ovule_count"
 yvar <- "seed_count"
@@
 xvar <- "seed_count"
-yvar <- "accessory_per_seed"
+yvar <- "accessory_costs"
 data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 
-points(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seed_count>0),col="black",pch=16,cex=2.5)
-points(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seed_count>0),col=col.spp(species),pch=16,cex=2)
-mod <- sma(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]]),method="SMA", log="xy")
+points(accessory_costs~seed_count,data=subset(SummarySpp[["mean"]],accessory_costs>0&seed_count>0),col="black",pch=16,cex=2.5)
+points(accessory_costs~seed_count,data=subset(SummarySpp[["mean"]],accessory_costs>0&seed_count>0),col=col.spp(species),pch=16,cex=2)
+mod <- sma(accessory_costs~seed_count,data=subset(SummarySpp[["mean"]]),method="SMA", log="xy")
 #words.top.right.logxy(mod)

### 2016-11-01 R/Summaries.R

@@ -50,30 +50,30 @@ process_leaf_lifespan <- function(leafLifespan_raw, leavesPerLength) {
   for(v in c("shoot_leaf_count_start_length","shoot_leaf_count_start_count","lvs_end_length","lvs_end_count","shoot_leaf_count_growth_shoot_length","shoot_leaf_count_new_count","shoot_leaf_count_new_and_shed_count")) {
     i <- is.na(leafLifespan[[v]])
     leafLifespan[[v]][i] <- 0
-   }
-
+  }
+  
   #calculating leaf lifespan
   leafLifespan <- mutate(leafLifespan,
-    shoot_leaf_count_start = shoot_leaf_count_start_count + (shoot_leaf_count_start_length * count_per_length),
-    lvs_end = lvs_end_count + (lvs_end_length * count_per_length),
-    shoot_leaf_count_new = shoot_leaf_count_new_count + (shoot_leaf_count_growth_shoot_length * count_per_length),
-    LL_bd = (shoot_leaf_count_start)/(((shoot_leaf_count_start)-(lvs_end)) + (shoot_leaf_count_new)/2),
-    LL_death = (shoot_leaf_count_start)/((shoot_leaf_count_start)-(lvs_end)),
-    LL_birth = (shoot_leaf_count_start)/(shoot_leaf_count_new),
-    growth_shoot_diameter = (shoot_diameter_end - shoot_diameter_start),
-    growth_shoot_area = (3.14*((shoot_diameter_end/2)^2)) - (3.14*((shoot_diameter_start/2)^2)),
-    shoot_leaf_count = lvs_end + shoot_leaf_count_new
-    )
-
+                         shoot_leaf_count_start = shoot_leaf_count_start_count + (shoot_leaf_count_start_length * count_per_length),
+                         lvs_end = lvs_end_count + (lvs_end_length * count_per_length),
+                         shoot_leaf_count_new = shoot_leaf_count_new_count + (shoot_leaf_count_growth_shoot_length * count_per_length),
+                         LL_bd = (shoot_leaf_count_start)/(((shoot_leaf_count_start)-(lvs_end)) + (shoot_leaf_count_new)/2),
+                         LL_death = (shoot_leaf_count_start)/((shoot_leaf_count_start)-(lvs_end)),
+                         LL_birth = (shoot_leaf_count_start)/(shoot_leaf_count_new),
[…]

### 2016-11-01 R/figures.R

@@ -215,6 +215,8 @@ print_xtable <- function(data, file){
     file=file)
 }
 
+"cerulean" <- "#0571b0"
+"venetian_red" <- "#CA0020" 
 
 #plotting and stats
 #creating lists of information for plotting symbols, colors, labels

### 2016-11-10 scripts/RA_figs_20160627.Rmd
continued trying to fix problems with accounting

@@
 ```{r}
+pdf("figs2/RA/Figure_1_stacked_lines.pdf", height=11.5, width=8)
+plot
+par(mfrow=c(4,2), cex=1, omi=c(.1,0.1,.1,.1), mai=c(0.8,.8,.1,0.2))
+
 data <- dplyr::select(SummarySppAge[["mean"]],species,age,repro_inv,growth_leaf,leaf_replacement,growth_stem,leaf_shed)
@@
 
-#data <- subset(data,species=="BOLE")
 data <- split(data, data$species)
@@
 }
+
+dev.off()
 ```

### 2016-11-10 scripts/tests.Rmd
continued trying to fix problems with accounting

check <- SummaryInd
check$repro_inv2 <- check$packaging_dispersal_inv + check$postpollen_aborted_inv + check$prepollen_inv_aborted_preflowering + prepollen_inv_reach_flowering + check$propagule_inv

repro_check <- InvestmentByPart %>%
  group_by(individual) %>%
  summarise_each(funs(sum), weight)

library(dplyr)

check <- join(check,repro_check,by="individual")
plot(repro_inv~weight,check,col=col.spp(species),log="xy",pch=16)
check$diff <-check$repro_inv-check$weight

plot(diff~leaf_area_0,check,col=col.spp(species),log="x",pch=16)

check <- select(SummaryInd,individual,species, prepollen_inv_from_dispersal, seed_count,pack_disp_early_costs)
check$costs2 <- check$prepollen_inv_from_dispersal/check$seed_count
plot(costs2~pack_disp_early_costs,check,col=col.spp(species),pch=16,log="xy")
abline(0,1)

check <- subset(InvestmentByPart,species=="BAER")
unique(check$part)

part_check <- check %>%
  group_by(part) %>%
  summarise_each(funs(sum), weight)

View(part_check)

unique(part_check$part)

check <-subset(SummaryInd,species=="BAER")
check<-select(check,seed_count,individual)
names(SummaryInd)

SummaryInd$seed_count
```
check2 <- select(SummaryInd,individual,species,seed_count,seed_early_costs,prepollen_inv_from_propagule)
check2 <- subset(check2,seed_count>0)

check2$costs2 <- check2$prepollen_inv_from_propagule/check2$seed_count
plot(costs2~seed_early_costs,check2,col=col.spp(species),pch=16,log="xy")

check <- subset(InvestmentByPart,part=="seed"|part=="fruit_mature")

part_check <- check %>%
  group_by(part,individual) %>%
  summarise_each(funs(sum), weight,count)

part_check$unit_weight <-part_check$weight/part_check$count

check3 <- join(part_check,check2,by="individual")

```
names(check2)

check_COER <- subset(InvestmentByPart,species=="PUTU"&(part=="seed"|part=="")

part_check <- check_COER %>%
  group_by(individual) %>%
  summarise_each(funs(sum), weight,count)

check4 <- subset(SummaryInd,species=="COER"&seed_count>0)
check4 <- select(check4,individual,seed_count)

check <- subset(PartsSummary,species=="GRSP"&(part=="flower_stigma"|part=="finished_flower_stigma"))

plot(prepollen_inv_from_propagule_all ~ prepollen_prop_v2,SummaryInd,col=col.spp(species),pch=16,log="xy")
SummaryInd$prepollen_inv_from_propagule_all

```{r}
par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.1,.05)) 
repro3 <- InvestmentByPart %>%
    group_by(individual) %>%
    summarise_each(funs(sum), weight)

repro4 <- select(SummaryInd,individual,seed_count,repro_inv,species)
repro4 <- merge(repro4,repro3,by="individual")
plot(weight ~ repro_inv,repro4,col=col.spp(species),pch=16,log="xy")
abline(0,1)

repro5 <- subset(repro4,repro_inv!=weight)
plot(weight ~ repro_inv,repro5,col=col.spp(species),pch=16,log="xy")
```

plot(required_inv2 ~ required_inv,SummaryInd,col=col.spp(species),pch=16,log="xy")
abline(0,1)

plot(seed_costs ~ seed_costs2,SummaryInd,col=col.spp(species),pch=16,log="xy")
abline(0,1)

#works
SummaryInd$success <- SummaryInd$pollen_attract_costs*SummaryInd$seed_count
plot(prepollen_success_inv ~ success,SummaryInd,col=col.spp(species),pch=16,log="xy")
abline(0,1)

#works
SummaryInd$propagule <- SummaryInd$propagule_costs*SummaryInd$seed_count
plot(propagule_inv ~ propagule,SummaryInd,col=col.spp(species),pch=16,log="xy")
abline(0,1)

SummaryInd$propagule <- SummaryInd$propagule_costs*SummaryInd$seed_count
plot(propagule_inv ~ propagule,SummaryInd,col=col.spp(species),pch=16,log="xy")
abline(0,1)

part=="flower_petals"|part=="late_flower_petals"|

check <- subset(InvestmentByPart,species=="BOLE"&(part=="finished_flower"|part=="flower_petals"))
check

check <- subset(InvestmentByPart,species=="BAER"&(part=="seed"|part=="seed_pod"))
check2 <- subset(PartsSummary,part=="flower_stigma"|part=="finished_flower_stigma")
check1 <- subset(PartsSummary,part=="seed"|part=="fruit_mature")
check1 <- merge(check1,check2,by="species")
check1$ratio <- check1$weight.y/check1$weight.x
check1$complement <- 1 - check1$ratio
check1 <- check1[]

InvCat <- InvestmentCategories[["BOLE"]]
InvCat <- InvestmentCategories[["COER"]]
InvCat <- InvestmentCategories[["EPMI"]]
InvCat <- InvestmentCategories[["GRBU"]]
InvCat <- InvestmentCategories[["GRSP"]]
InvCat <- InvestmentCategories[["HATE"]]
InvCat <- InvestmentCategories[["HEPU"]]
InvCat <- InvestmentCategories[["LEES"]]
InvCat <- InvestmentCategories[["PELA"]]
InvCat <- InvestmentCategories[["PEPU"]]
InvCat <- InvestmentCategories[["PHPH"]]
InvCat <- InvestmentCategories[["PILI"]]
InvCat <- InvestmentCategories[["PUTU"]]

### 2016-11-15 scripts/tests.Rmd
code for file testing R issues

@@
 
-repro4 <- select(SummaryInd,individual,seed_count,repro_inv,species)
+SummaryInd$repro_new <- SummaryInd$prepollen2_all_inv + SummaryInd$postpollen2_all_inv
+repro4 <- select(SummaryInd,individual,seed_count,repro_inv,repro_new, species)
 repro4 <- merge(repro4,repro3,by="individual")
-plot(weight ~ repro_inv,repro4,col=col.spp(species),pch=16,log="xy")
+plot(weight ~ repro_new,repro4,col=col.spp(species),pch=16,log="xy")
 abline(0,1)
@@
 
+check2 <- subset(InvestmentByPart,species=="BOLE"&(part=="late_flower_petals"|part=="flower_petals"))
+
+repro3 <- check2 %>%
+    group_by(individual) %>%
+    summarise_each(funs(sum), count)
+
+check <- subset(SummaryInd,species=="BOLE")
+check <- select(check,individual, postpollen_count,prepollen_count_reach_flowering,seed_count)
+check3 <- merge(check,repro3,by="individual")
+
 InvCat <- InvestmentCategories[["BOLE"]]

### 2016-11-17 scripts/Accessory_figs_20160905.Rmd
small changes to files as working on Accessory Costs ms

@@
 
-mod2 <- sma(scaled_seed_count ~ seed_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+mod2 <- sma(scaled_seed_count ~ success_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
 mod1 <- sma(scaled_ovule_count ~ pollen_attract_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=mod2$groupsummary["Slope"][[1]],elev.test=mod2$coef[[1]][1,1])
@@
 plot(scaled_ovule_count ~ pollen_attract_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,500),ylab="scaled count",xlim=c(.01,5000),cex=1.5)
-points(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
+points(scaled_seed_count ~ success_costs, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
 line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod1,3)
-line_function_log_xy(SummarySpp[["mean"]]$seed_costs,mod2,1)
-#points(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],pch=12,col=col.spp(species))
-#arrows(SummarySpp[["mean"]]$seed_costs,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0,length=.15)
+line_function_log_xy(SummarySpp[["mean"]]$success_costs,mod2,1)
+#points(scaled_seed_count ~ embryo_endo_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
+#arrows(SummarySpp[["mean"]]$success_costs,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0,length=.15)
 
@@
 ```
-
-mod_seed <- sma(scaled_seed_count ~ seed_costs, data=subset(SummaryInd),method="SMA", log="xy",slope.test=-1)
-mod_ovule <- sma(scaled_ovule_count ~ pollen_attract_costs, data=subset(SummaryInd),method="SMA", log="xy",slope.test=mod2$groupsummary["Slope"][[1]],elev.test=mod2$coef[[1]][1,1])
-
-plot(scaled_ovule_count ~ pollen_attract_costs, SummaryInd,log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.0001,1000),ylab="scaled count",xlim=c(.001,10000),cex=1.5)
-points(scaled_seed_count ~ seed_costs, SummaryInd,cex=1.5,pch=16,col=col.spp(species))
-
-line_function_log_xy(SummaryInd$seed_costs,mod_seed,1)
-line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_ovule,3)
-
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.1,.05)) 
-plot(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.05,10000))
-points(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],pch=1,col=col.spp(species))
-mod_repro_costs <- sma(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=1)
-mod_fixed_costs <- sma(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_repro_costs$coef[[1]][2,1])
-line_function_log_xy(SummarySpp[["mean"]]$repro_inv_per_seed,mod_repro_costs,3)
-line_function_log_xy(SummarySpp[["mean"]]$seed_costs,mod_fixed_costs,1)
-
-summary(mod_repro_costs)
-summary(mod_fixed_costs)
-
-plot(pollen_attract_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.005,5000))
-points(prepollen_all_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],pch=1,col=col.spp(species))
-#points(prepollen_failure_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch="-",col=col.spp(species))
-mod_prepollen_all <- sma(prepollen_all_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_repro_costs$coef[[1]][2,1])
-mod_pollen_attract_costs <- sma(pollen_attract_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_repro_costs$coef[[1]][2,1])
-line_function_log_xy(SummarySpp[["mean"]]$prepollen_all_per_seed,mod_prepollen_all,3)
-line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_pollen_attract_costs,1)
-
-summary(mod_prepollen_all)
-summary(mod_pollen_attract_costs)
 
@@
 
-#there is no relationship between the proportion of energy going to seeds and the total energy for seedcosts
-mod <- sma(seed_costs~prop_seed_costs,SummarySpp[["mean"]],method="SMA",log="y")
+#RE per seed unrelated to seedsize
+mod <- sma(repro_costs ~ embryo_endo_costs, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
 summary(mod)
-
-#RE per seed unrelated to seedsize
-mod <- sma(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
-summary(mod)
-plot(repro_inv_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(repro_costs ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
 #energy invested in accessory tissues unrelated to seedsize
-mod <- sma(accessory_costs_using_ee ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
+mod <- sma(accessory_costs_using_ee ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(accessory_costs_using_ee ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(accessory_costs_using_ee ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
 #total seed costs unrelated to seedsize
-mod <- sma(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
+mod <- sma(success_costs ~ embryo_endo_costs, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(seed_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(success_costs ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
 #failure per seed unrelated to seedsize
-mod <- sma(failure_per_seed ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
+mod <- sma(failure_costs ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(failure_per_seed ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(failure_costs ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 
-mod <- sma(scaled_seed_count ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+mod <- sma(scaled_seed_count ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
 summary(mod)
-plot(scaled_seed_count ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(scaled_seed_count ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 
-mod <- sma(scaled_seed_count ~ seed_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
+mod <- sma(scaled_seed_count ~ success_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
 summary(mod)
-plot(scaled_seed_count ~ seed_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(scaled_seed_count ~ success_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
-mod <- sma(prepollen_all_per_seed ~ embryo_endo_size, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
+mod <- sma(prepollen_all_costs ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(prepollen_failure_costs ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.02,10000))
-points(pollen_attract_costs~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species))
+plot(prepollen_discarded_costs ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.02,10000))
+points(pollen_attract_costs~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species))
 
@@
 #seed size by propagule investment - all species
-mod <- sma(propagule_inv ~ embryo_endo_size, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
+mod <- sma(propagule_inv ~ embryo_endo_costs, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(propagule_inv_ee ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(propagule_inv_ee ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
 #seed size by propagule investment - without EPMI
-mod <- sma(propagule_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="SMA", log="xy",slope.test=1)
+mod <- sma(propagule_inv ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(propagule_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
+plot(propagule_inv ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
 
 #seed size by reproductive investment - all species
-mod <- sma(repro_inv ~ embryo_endo_size, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
+mod <- sma(repro_inv ~ embryo_endo_costs, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(repro_inv ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(repro_inv ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
 #seed size by reproductive investment - without EPMI
-mod <- sma(repro_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="SMA", log="xy",slope.test=1)
+mod <- sma(repro_inv ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(repro_inv ~ embryo_endo_size, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
+plot(repro_inv ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
 
@@
 #seed size by total weight - all species
-mod <- sma(total_weight_0 ~ embryo_endo_size, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
+mod <- sma(total_weight_0 ~ embryo_endo_costs, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(total_weight_0 ~ embryo_endo_size, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(total_weight_0 ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 
-plot(prop_prepollen_all~seedset,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x")
-
-plot(prop_pollen_attract_costs~seedset,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="")
-
-mod <- sma(prop_prepollen_all~embryo_endo_size,SummaryInd,log="x",method="SMA")
-summary(mod)
-
 #Table 1 showing accessory cost values for the species
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_size,seedset,repro_inv_per_seed,prop_failure,prop_prepollen_vs_RE, prop_pack_disp_vs_RE,prop_embryo_endo_vs_RE,seed_costs,prop_pollen_attract_costs,prop_postpollen_costs,embryo_endo_size,pack_disp_costs,pollen_attract_costs,failure_inv,repro_inv,seed_count)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_costs,seedset,repro_costs,prop_failure,prop_prepollen_vs_RE, prop_pack_disp_vs_RE,prop_embryo_endo_vs_RE,success_costs,prop_pollen_attract_costs,prop_postpollen_costs,embryo_endo_costs,packaging_dispersal_costs,pollen_attract_costs,failure_inv,repro_inv,seed_count)
 acc_costs_spp$species <- labels.spp.full()
 acc_costs_spp_format <- acc_costs_spp
-for (i in c("embryo_endo_size","seedset","repro_inv_per_seed","prop_failure","prop_prepollen_vs_RE","prop_pack_disp_vs_RE","prop_embryo_endo_vs_RE","seed_costs","prop_pollen_attract_costs","prop_postpollen_costs")) {
+for (i in c("embryo_endo_costs","seedset","repro_costs","prop_prepollen_discarded_vs_RE","prop_postpollen_discarded_vs_RE","prop_prepollen_vs_RE","prop_pack_disp_vs_RE","prop_embryo_endo_vs_RE","success_costs","prop_pollen_attract_costs","prop_postpollen_costs")) {
   acc_costs_spp_format[[i]] <- round(acc_costs_spp_format[[i]],digits=3)
@@
 
-plot(repro_inv_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$repro_inv_per_seed,SummarySpp[["se"]]$accessory_costs)
-slopes <- sma(repro_inv_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+plot(repro_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$repro_costs,SummarySpp[["se"]]$accessory_costs)
+slopes <- sma(repro_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot(seed_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="seed costs (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seed_costs,SummarySpp[["se"]]$seed_costs)
-slopes <- sma(seed_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+plot(success_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="seed costs (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$success_costs,SummarySpp[["se"]]$success_costs)
+slopes <- sma(success_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot(pollen_attract_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
-slopes <- sma(pollen_attract_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+plot(pollen_attract_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
+slopes <- sma(pollen_attract_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot(provisioning_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-slopes <- sma(provisioning_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+plot(provisioning_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
+slopes <- sma(provisioning_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
 abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)
 acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
@@
 
-plot(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all failure costs (mg/seed)",xlab="",cex=1.5)
-slopes <- sma(failure_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+plot(failure_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all failure costs (mg/seed)",xlab="",cex=1.5)
+slopes <- sma(failure_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
 abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$failure_per_seed,SummarySpp[["se"]]$failure_per_seed)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$failure_costs,SummarySpp[["se"]]$failure_costs)
 acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-plot(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_all_per_seed,SummarySpp[["se"]]$prepollen_all_per_seed)
-slopes <- sma(prepollen_all_per_seed ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+plot(prepollen_all_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prepollen_all_costs,SummarySpp[["se"]]$prepollen_all_costs)
+slopes <- sma(prepollen_all_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot(prepollen_failure_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$prepollen_failure_costs,SummarySpp[["se"]]$prepollen_failure_costs)
-slopes <- sma(prepollen_failure_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+plot(prepollen_discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prepollen_discarded_costs,SummarySpp[["se"]]$prepollen_discarded_costs)
+slopes <- sma(prepollen_discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot(postpollen_aborted_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted during provisioning costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_aborted_costs,SummarySpp[["se"]]$postpollen_aborted_costs)
-slopes <- sma(postpollen_aborted_costs ~ embryo_endo_size,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+plot(postpollen_aborted_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted during provisioning costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$postpollen_aborted_costs,SummarySpp[["se"]]$postpollen_aborted_costs)
+slopes <- sma(postpollen_aborted_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
@@
 
-plot((scaled_seed_count)~(embryo_endo_size),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,5000),yaxt="n",xaxt="n",ylab="")
+plot((scaled_seed_count)~(embryo_endo_costs),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,5000),yaxt="n",xaxt="n",ylab="")
 points(scaled_ovule_count~pollen_attract_costs,SummaryInd,pch=21,col=col.spp(species))
@@
 
-mod_seed <- sma(scaled_seed_count~embryo_endo_size,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="SMA")
+mod_seed <- sma(scaled_seed_count~embryo_endo_costs,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="SMA")
 mod_ovule <- sma(scaled_ovule_count~pollen_attract_costs,data=subset(SummaryInd,scaled_ovule_count!=0),log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
 
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_seed,1)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_ovule,2)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_seed,1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_ovule,2)
 legend("topright",legend=c("seed count","initiated ovules count"),col=c("black","black"),pch=c(16,21),bty="n")
@@
 
-plot(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.002,500),ylim=c(.004,.6),cex=1.5,xaxt="n",xlab="",ylab="")
-mod <- sma(seedset~embryo_endo_size,SummarySpp[["mean"]],log="xy", method="SMA")
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
+plot(seedset~embryo_endo_costs,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.002,500),ylim=c(.004,.6),cex=1.5,xaxt="n",xlab="",ylab="")
+mod <- sma(seedset~embryo_endo_costs,SummarySpp[["mean"]],log="xy", method="SMA")
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
 #text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
 axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
@@
 
-plot(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
-mod <- sma(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
+plot(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
+mod <- sma(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA")
 #abline(mod$groupsummary["Int"][[1]],1,lty=2)
@@
 mtext("pollen attraction costs (mg/seed)",2,line=2.3)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
-line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
+line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
 extra.top.left.logxy("c",2,1.2)
 
-plot(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$pollen_attract_costs)
-mod <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
-line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_size,mod,1)
+plot(postpollen_all_per_seed~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$pollen_attract_costs)
+mod <- sma(postpollen_all_per_seed~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA")
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
+line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
 axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
@@
 #panel a
-plot(scaled_seed_count~seed_costs,SummarySpp[["mean"]],pch=16,log="xy",col=venetian_red,xlim=c(.01,5000),ylim=c(5e-4,500),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)
+plot(scaled_seed_count~success_costs,SummarySpp[["mean"]],pch=16,log="xy",col=venetian_red,xlim=c(.01,5000),ylim=c(5e-4,500),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)
 points(scaled_ovule_count~pollen_attract_costs,SummarySpp[["mean"]],pch=16,col=cerulean,cex=1)
@@
 
-mod_seed <- sma(scaled_seed_count~seed_costs,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
+mod_seed <- sma(scaled_seed_count~success_costs,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
 mod_ovule <- sma(scaled_ovule_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
 
-line_function_log_xy(SummarySpp[["mean"]]$seed_costs,mod_seed,1,col=venetian_red)
+line_function_log_xy(SummarySpp[["mean"]]$success_costs,mod_seed,1,col=venetian_red)
 line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_ovule,1,col=cerulean)
@@
 mtext("choosiness (ovules:seed)",2,line=2.3,cex=0.7)
+mod_choosy <- sma(choosiness~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="SMA")
 mod_choosy2 <- sma(choosiness~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",slope=-1,method="SMA")
@@
 #panel c - success proportions
-plot(prop_pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,
+plot(prop_pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,
      ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
-points(prop_postpollen_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,col=venetian_red)
+points(prop_postpollen_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
 extra.top.left.logx("c",2,1)
@@
 
-mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
 
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_pollen_attract_costs,1,col=cerulean)
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_costs,1,col=venetian_red)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_pollen_attract_costs,1,col=cerulean)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_postpollen_costs,1,col=venetian_red)
 
 #panel d - pollen-attraction proportions
-plot(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
-points(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],pch=16,col=venetian_red)
+plot(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
+points(prop_prepollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
 extra.top.left.logx("d",2,1)
@@
 
-mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_prepollen_failure <- sma(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_prepollen_discarded <- sma(prop_prepollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
 
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_prepollen_success,1,col=cerulean)
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_prepollen_failure,1,col=venetian_red)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_prepollen_success,1,col=cerulean)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_prepollen_discarded,1,col=venetian_red)
 
 #panel e - provisioning proportions
-plot(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
-points(prop_postpollen_failure~embryo_endo_size,SummarySpp[["mean"]],pch=16,col=venetian_red)
+plot(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
+points(prop_postpollen_failure~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
 extra.top.left.logx("e",2,1)
@@
 
-mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
 
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_success,1,col=cerulean)
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_failure,1,col=venetian_red)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_postpollen_success,1,col=cerulean)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_postpollen_failure,1,col=venetian_red)
 
 #panel f - change in slope of "success costs"
-plot(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="xy",col=cerulean,xlim=c(.002,100),ylim=c(.01,20000),xlab="",ylab="",xaxt="n",yaxt="n")
-points(provisioning_costs~embryo_endo_size,SummarySpp[["mean"]],pch=16,col=venetian_red)
+plot(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="xy",col=cerulean,xlim=c(.002,100),ylim=c(.01,20000),xlab="",ylab="",xaxt="n",yaxt="n")
+points(provisioning_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
 extra.top.left.logxy("f",2,1)
@@
 
-mod_pollen_attract_costs <- sma(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
-mod_provisioning_costs <- sma(provisioning_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA",slope.test = mod_pollen_attract_costs$groupsummary$Slope_highCI)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_pollen_attract_costs,1,col=cerulean)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_provisioning_costs,1,col=venetian_red)
+mod_pollen_attract_costs <- sma(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA")
+mod_provisioning_costs <- sma(provisioning_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA",slope.test = mod_pollen_attract_costs$groupsummary$Slope_highCI)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_pollen_attract_costs,1,col=cerulean)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_provisioning_costs,1,col=venetian_red)
 
@@
 ```{r}
-mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_prepollen_success_SMA <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA")
-mod_prop_prepollen_failure <- sma(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_prepollen_success_SMA <- sma(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA")
+mod_prop_prepollen_discarded <- sma(prop_prepollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
 
@@
 
-#temp <- dplyr::select(mod_prop_prepollen_failure$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+#temp <- dplyr::select(mod_prop_prepollen_discarded$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
 #temp$test[1] <- "Proportion prepollen costs to failure"
@@
 
-plot(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
+plot(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
 
-points(provisioning_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=21,cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_size,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)
+points(provisioning_costs~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=21,cex=1.5)
+y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)
 
@@
 
-mod_prepollen <- sma(pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA")
-mod_provision <- sma(postpollen_all_per_seed~embryo_endo_size,SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_prepollen$groupsummary["Slope"][[1]])
+mod_prepollen <- sma(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA")
+mod_provision <- sma(postpollen_all_per_seed~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_prepollen$groupsummary["Slope"][[1]])
 
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_prepollen,1)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_size,mod_provision,2)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_prepollen,1)
+line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_provision,2)
 
@@
 
-plot(prop_pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-points(prop_prepollen_all~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
+plot(prop_pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+points(prop_prepollen_all~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
 axis(2, at=c(0,.5,1), labels=c(0,0.5,1.0),cex.axis=1)
@@
 
-mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
-mod_prop_prepollen_all <- sma(prop_prepollen_all~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
+mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
+mod_prop_prepollen_all <- sma(prop_prepollen_all~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
 
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_pollen_attract_costs,1)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_pollen_attract_costs,1)
 
@@
 
-plot(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-points(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
+plot(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+points(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
 axis(2, at=c(0,.5,1), labels=c(0,0.5,1.0),cex.axis=1)
@@
 
-mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA")
-mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA")
+mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA")
+mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA")
 
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_postpollen_success,1)
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_size,mod_prop_prepollen_success,3)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_postpollen_success,1)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_prepollen_success,3)
 
@@
 
-plot(seed_size~total_weight_0,SummaryInd,log="xy",pch=16,col=col.spp(species))
-plot(seed_size~total_weight_0,SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(propagule_costs~total_weight_0,SummaryInd,log="xy",pch=16,col=col.spp(species))
+plot(propagule_costs~total_weight_0,SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
 plot(seedset~prop_failure,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),log="xy",pch=16,col=col.spp(species))
-mod <- sma(seed_size~total_weight_0,data=subset(SummarySpp[["mean"]]),log="xy",method="SMA")
+mod <- sma(propagule_costs~total_weight_0,data=subset(SummarySpp[["mean"]]),log="xy",method="SMA")
 summary(mod)
@@
 ```{r}
-plot(scaled_repro_inv~seed_size,SummaryInd, col=col.spp(species),pch=16,log="xy")
-points(scaled_repro_inv~seed_size,SummarySpp[["mean"]], cex=2, col=col.spp(species),pch=16)
-mod <-sma(scaled_repro_inv~seed_size,SummarySpp[["mean"]],log="xy",method="SMA")
+plot(scaled_repro_inv~propagule_costs,SummaryInd, col=col.spp(species),pch=16,log="xy")
+points(scaled_repro_inv~propagule_costs,SummarySpp[["mean"]], cex=2, col=col.spp(species),pch=16)
+mod <-sma(scaled_repro_inv~propagule_costs,SummarySpp[["mean"]],log="xy",method="SMA")
 summary(mod)

### 2016-11-21 scripts/Accessory_figs_20160905.Rmd
work on Accessory Costs - all figures running again

@@
 ```{r}
-pdf("figs2/Accessory_Costs/scaled_ovule count.pdf", height=6, width=6)
+pdf("ms/Accessory_Costs/scaled_ovule count.pdf", height=6, width=6)
 plot
@@
 #average proportion energy going to failed tissues (among reproducing individuals)
-mean(subset(SummaryInd$prop_failure,SummaryInd$prop_failure>0))
+mean(subset(SummaryInd$prop_discarded,SummaryInd$prop_discarded>0))
 
 #average proportion of energy going to accessory costs (based on propagules, not seeds) (among individuals that produce seed)
-mean(subset(SummaryInd$prop_accessory_seed,SummaryInd$seed_count>0))
-mean(subset(SummaryInd$prop_accessory_ee,SummaryInd$seed_count>0))
-SummarySpp[["mean"]]$prop_accessory_seed
+mean(subset(SummaryInd$prop_accessory_using_propagule,SummaryInd$seed_count>0))
+mean(subset(SummaryInd$prop_accessory_using_embryo_endo,SummaryInd$seed_count>0))
+SummarySpp[["mean"]]$prop_accessory_using_propagule
 
-check <- dplyr::select(SummarySpp[["mean"]],species,prop_accessory_ee,prop_accessory_seed)
-check <- dplyr::arrange(check,prop_accessory_ee)
+check <- dplyr::select(SummarySpp[["mean"]],species,prop_accessory_using_embryo_endo,prop_accessory_using_propagule)
+check <- dplyr::arrange(check,prop_accessory_using_embryo_endo)
 
 #individual with lowest accessory costs
-check <- subset(SummaryInd,prop_propagule_ee>.1)
-check <- dplyr::select(check,individual,prop_propagule_ee)
-max(check$prop_propagule_ee)
+check <- subset(SummaryInd,prop_embryo_endo_vs_all_repro>.1)
+check <- dplyr::select(check,individual,prop_embryo_endo_vs_all_repro)
+max(check$prop_embryo_endo_vs_all_repro)
 
@@
 
-#failure per seed unrelated to seedsize
-mod <- sma(failure_costs ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
+#discarded per seed unrelated to seedsize
+mod <- sma(discarded_costs ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(failure_costs ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(discarded_costs ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
-mod <- sma(prop_pollen_attract_costs ~ seedset, data=subset(SummarySpp[["mean"]]),method="SMA", log="x",slope.test=1)
+mod <- sma(prop_pollen_attract_vs_all_repro ~ seedset, data=subset(SummarySpp[["mean"]]),method="SMA", log="x",slope.test=1)
 summary(mod)
-plot(prop_pollen_attract_costs ~ seedset, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))
+plot(prop_pollen_attract_vs_all_repro ~ seedset, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))
 
@@
 
-#more failure = lower seedset across species - in discussion
-mod <- sma(seedset ~ prop_failure, data=subset(SummarySpp[["mean"]],species!="BAER"),method="SMA", log="",slope.test=1)
+#more discarded = lower seedset across species - in discussion
+mod <- sma(seedset ~ prop_discarded, data=subset(SummarySpp[["mean"]],species!="BAER"),method="SMA", log="",slope.test=1)
 summary(mod)
-plot(seedset ~ prop_failure, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))
+plot(seedset ~ prop_discarded, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))
 
@@
 #seedset by pollen attraction
-mod <- sma(prop_pollen_attract_costs~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
+mod <- sma(prop_pollen_attract_vs_all_repro~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
 summary(mod)
@@
 #scaled ovule production vs prop pollen attraction  - all species
-mod <- sma(prop_pollen_attract_costs~scaled_ovule_count,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
+mod <- sma(prop_pollen_attract_vs_all_repro~scaled_ovule_count,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
 summary(mod)
-plot(prop_pollen_attract_costs ~ scaled_ovule_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(prop_pollen_attract_vs_all_repro ~ scaled_ovule_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 ```{r}
-acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_costs,seedset,repro_costs,prop_failure,prop_prepollen_vs_RE, prop_pack_disp_vs_RE,prop_embryo_endo_vs_RE,success_costs,prop_pollen_attract_costs,prop_postpollen_costs,embryo_endo_costs,packaging_dispersal_costs,pollen_attract_costs,failure_inv,repro_inv,seed_count)
+acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_costs, seedset, repro_costs, prop_prepollen_discarded_vs_all_repro,
+                               prop_postpollen_discarded_vs_all_repro, prop_pollen_attract_vs_all_repro, prop_pack_disp_vs_all_repro, 
+                               prop_embryo_endo_vs_all_repro, success_costs, prop_pollen_attract_vs_all_repro, prop_pollen_attract_vs_success, 
+                               prop_provisioning_vs_success, embryo_endo_costs, packaging_dispersal_costs, pollen_attract_costs, repro_inv,seed_count)
 acc_costs_spp$species <- labels.spp.full()
 acc_costs_spp_format <- acc_costs_spp
-for (i in c("embryo_endo_costs","seedset","repro_costs","prop_prepollen_discarded_vs_RE","prop_postpollen_discarded_vs_RE","prop_prepollen_vs_RE","prop_pack_disp_vs_RE","prop_embryo_endo_vs_RE","success_costs","prop_pollen_attract_costs","prop_postpollen_costs")) {
+for (i in c("embryo_endo_costs","seedset","repro_costs","prop_prepollen_discarded_vs_all_repro","prop_postpollen_discarded_vs_all_repro",
+            "prop_pollen_attract_vs_all_repro","prop_pack_disp_vs_all_repro","prop_embryo_endo_vs_all_repro","success_costs",
+            "prop_pollen_attract_vs_success", "prop_provisioning_vs_success","packaging_dispersal_costs","pollen_attract_costs", "repro_inv")) {
   acc_costs_spp_format[[i]] <- round(acc_costs_spp_format[[i]],digits=3)
@@
 
-for (i in c("prop_failure","prop_prepollen_vs_RE","prop_pack_disp_vs_RE","prop_embryo_endo_vs_RE","prop_pollen_attract_costs","prop_postpollen_costs")) {
-  acc_costs_spp_format[[i]] <- round(100*acc_costs_spp_format[[i]],digits=1)
+for (i in c("seed_count")) {
+  acc_costs_spp_format[[i]] <- round(acc_costs_spp_format[[i]],digits=1)
 }
+
+for (i in c("prop_prepollen_discarded_vs_all_repro","prop_postpollen_discarded_vs_all_repro","prop_pack_disp_vs_all_repro",
+            "prop_embryo_endo_vs_all_repro","prop_pollen_attract_vs_all_repro","prop_pollen_attract_vs_success", "prop_provisioning_vs_success")) {
+  acc_costs_spp_format[[i]] <- round(100*acc_costs_spp_format[[i]],digits=2)
+}
+
+acc_costs_spp_format <- acc_costs_spp_format[order(acc_costs_spp_format$embryo_endo_costs),]
 
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Table01_dots.wmf", height=3, width=.2)
+win.metafile("ms/Accessory/Table01_dots.wmf", height=3, width=.2)
 plot
@@
 par(mfrow=c(1,1), cex=1, omi=c(.01,.01,.01,.01), mai=c(.01,.01,.01,.01)) 
-dots <- dplyr::select(SummarySpp[["mean"]],species)
+dots <- dplyr::select(SummarySpp[["mean"]],species,embryo_endo_costs)
+dots <- dots[order(dots$embryo_endo_costs),] 
 dots$x <- c(1,1,1,1,1,1,1,1,1,1,1,1,1,1)
 dots$y <- c(28,26,24,22,20,18,16,14,12,10,8,6,4,2)
+
 plot(y~x,dots,cex=1.5,pch=16,xlab="",ylab="",xaxt="n",yaxt="n",col=col.spp(dots$species),bty="n",xlim=c(0.8,1.2),ylim=c(1.8,28.2))
@@
 
-plot(prop_pollen_attract_costs_all_repro~ seedset,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)
+plot(prop_pollen_attract_vs_all_repro_all_repro~ seedset,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)
 
@@
 
-plot(failure_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all failure costs (mg/seed)",xlab="",cex=1.5)
-slopes <- sma(failure_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+plot(discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all discarded costs (mg/seed)",xlab="",cex=1.5)
+slopes <- sma(discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
 abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
 abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$failure_costs,SummarySpp[["se"]]$failure_costs)
+y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$discarded_costs,SummarySpp[["se"]]$discarded_costs)
 acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
@@
 
-write.csv(acc_slopes, file="ms/Accessory/Table_SXX_propagule_invest_vs_repro_inv.csv",row.names=FALSE)
+write.csv(acc_slopes, file="ms/Accessory/Table_SXX_propagule_invest_vs_all_repropro_inv.csv",row.names=FALSE)
 ```
@@
 
-for (i in c("total_weight","failure_inv","success_inv","propagule_inv","packaging_dispersal_inv","prepollen_success_inv","fruit_inv","flower_inv")) {
+for (i in c("total_weight","propagule_inv","fruit_inv","flower_inv","flower_inv2","success_inv","prepollen_success_inv","pack_disp_success_inv","discarded_inv")) {
   for (j in c("repro_inv")) {
@@
 
-#Figure 2. Scaling of accessory costs versus weight of embryo + endosperm, by species
+#Figure 01. predictions
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure02_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
+win.metafile("ms/Accessory/Figure01b&c_predictions.wmf", height=3, width=6)
 plot
 
-par(mfrow=c(3,1), cex=1, omi=c(1,.1,.05,.05), mai=c(.2,.8,.1,.05)) 
-options(scipen = 5)
-
-plot((scaled_seed_count)~(embryo_endo_costs),SummaryInd,pch=16,log="xy",col=col.spp(species),xlim=c(.002,500),ylim=c(1e-4,5000),yaxt="n",xaxt="n",ylab="")
-points(scaled_ovule_count~pollen_attract_costs,SummaryInd,pch=21,col=col.spp(species))
-
-axis(2, at=c(0.0001,0.01,1,100), labels=c(0.0001,0.01,1,100),cex.axis=1)
-axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
-mtext("count, scaled to plant size",2,line=2.3)
-
-mod_seed <- sma(scaled_seed_count~embryo_endo_costs,data=subset(SummaryInd,scaled_seed_count!=0),log="xy",slope=-1,method="SMA")
-mod_ovule <- sma(scaled_ovule_count~pollen_attract_costs,data=subset(SummaryInd,scaled_ovule_count!=0),log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
-
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_seed,1)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_ovule,2)
-legend("topright",legend=c("seed count","initiated ovules count"),col=c("black","black"),pch=c(16,21),bty="n")
-extra.top.left.logxy("a",2,1.2)
-
-summary(mod_seed)
-summary(mod_ovule)
-
-plot(seedset~embryo_endo_costs,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.002,500),ylim=c(.004,.6),cex=1.5,xaxt="n",xlab="",ylab="")
-mod <- sma(seedset~embryo_endo_costs,SummarySpp[["mean"]],log="xy", method="SMA")
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
-#text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
-axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
-mtext("seed set",2,line=2.3)
-extra.top.left.logxy("b",2,1.2)
-summary(mod)
-
-plot(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
-mod <- sma(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA")
-#abline(mod$groupsummary["Int"][[1]],1,lty=2)
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
-mtext("pollen attraction costs (mg/seed)",2,line=2.3)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
-line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
-extra.top.left.logxy("c",2,1.2)
-
-plot(postpollen_all_per_seed~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$postpollen_all_per_seed,SummarySpp[["se"]]$pollen_attract_costs)
-mod <- sma(postpollen_all_per_seed~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA")
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
-line_function_log_xy_zero(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
-mtext("provisioning costs (mg/seed)",2,line=2.3)
-extra.top.left.logxy("d",2,1.2)
-
-mtext(text="     seed size (mg)",side=1,line=1.5,outer=TRUE,adj=0.5)
-mtext(text="                     parental pessimist",line=3,side=1,adj=0,outer=TRUE,font=3)
-mtext(text="parental optimist    ",line=3,side=1,adj=1,outer=TRUE,font=3)
-
-dev.off()
-```
-
-#predictions
-```{r}
-win.metafile("figs2/Accessory_Costs/Figure01_predictions.wmf", height=9, width=6)
-plot
-
-par(mfrow=c(3,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
+par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
 plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
@@
 axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
-mtext(text="count, scaled to leaf area",side=2,line=1.3,outer=FALSE,cex=0.8)
-mtext(text="costs (mg/seed)",side=1,line=1.3,outer=FALSE,cex=0.8)
-legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by pollen_attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
+mtext(text="count, scaled to plant size",side=2,line=1.1,outer=FALSE,cex=0.8)
+mtext(text="costs (mg/seed)",side=1,line=1.0,outer=FALSE,cex=0.8)
+legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
+extra.top.left("b",2,1)
 
@@
 segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
-axis(1, at=c(0,1),labels=c(0,1),cex.axis=1)
+axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
 axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
 mtext(text="choosiness (ovule:seed)",side=2,line=1.3,outer=FALSE,cex=0.8)
-mtext(text="proportion reproductive costs to pollen_attraction costs for 1 ovule",side=1,line=1.3,outer=FALSE,cex=0.8)
+mtext(text="pollen attraction costs,",side=1,line=1.1,outer=FALSE,cex=0.8)
+mtext(text="scaled to plant size",side=1,line=1.9,outer=FALSE,cex=0.8)
+extra.top.left("c",2,1)
+dev.off()
+
+win.metafile("ms/Accessory/Figure01def_predictions.wmf", height=6, width=6)
+plot
+
+par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05))
 
@@
 mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
-legend("bottomleft",legend=c("pollen_attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
+legend("bottomleft",legend=c("pollen-attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
+extra.top.left("d",2,1)
 
@@
 axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
-mtext(text="proportion all pollen_attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
+mtext(text="proportion all pollen-attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
 mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
 legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
+extra.top.left("e",2,1)
 
@@
 legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
+extra.top.left("f",2,1)
 
@@
 
-#outcomes - Figure 2
+#Figure 2
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure02_Oct24.wmf", height=9, width=6)
+win.metafile("ms/Accessory/Figure02.wmf", height=9, width=6)
 plot
@@
 plot(scaled_seed_count~success_costs,SummarySpp[["mean"]],pch=16,log="xy",col=venetian_red,xlim=c(.01,5000),ylim=c(5e-4,500),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)
-points(scaled_ovule_count~pollen_attract_costs,SummarySpp[["mean"]],pch=16,col=cerulean,cex=1)
+points(scaled_reach_flowering_count~pollen_attract_costs,SummarySpp[["mean"]],pch=16,col=cerulean,cex=1)
 
@@
 mod_seed <- sma(scaled_seed_count~success_costs,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
-mod_ovule <- sma(scaled_ovule_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
+mod_ovule2 <- sma(scaled_ovule_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
+mod_ovule <- sma(scaled_reach_flowering_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
 
@@
 line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_ovule,1,col=cerulean)
-legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by","pollen_attraction costs"),col=c(venetian_red,cerulean,"white"),pch=c(16,16,16),bty="n",cex=0.7)
+legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by","pollen-attraction costs"),col=c(venetian_red,cerulean,"white"),pch=c(16,16,16),bty="n",cex=0.7)
 extra.top.left.logxy("a",2,1)
@@
 #panel b
-#plot(choosiness~prop_pollen_attract_costs_all_repro,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(0.002,.5),ylim=c(3,800),xaxt="n",yaxt="n",cex=1,ylab="",xlab="")
-plot(choosiness~scaled_pollen_attract_costs,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(.002,.3),ylim=c(3,800),yaxt="n",cex=1,ylab="",xlab="",xaxt="n")
+#plot(choosiness~prop_pollen_attract_vs_all_repro_all_repro,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(0.002,.5),ylim=c(3,800),xaxt="n",yaxt="n",cex=1,ylab="",xlab="")
+plot(choosiness2~scaled_pollen_attract_costs,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(.002,.3),ylim=c(3,800),yaxt="n",cex=1,ylab="",xlab="",xaxt="n")
 axis(2, at=c(10,100,1000), labels=c(10,100,1000),cex.axis=0.8,las=2)
@@
 mtext("choosiness (ovules:seed)",2,line=2.3,cex=0.7)
-mod_choosy <- sma(choosiness~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="SMA")
-mod_choosy2 <- sma(choosiness~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",slope=-1,method="SMA")
+mod_choosy <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="SMA")
+mod_choosy2 <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",slope=-1,method="SMA")
 line_function_log_xy(SummarySpp[["mean"]]$scaled_pollen_attract_costs,mod_choosy2,1,col=cerulean)
@@
 #panel c - success proportions
-plot(prop_pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,
+plot(prop_pollen_attract_vs_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,
      ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
-points(prop_postpollen_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
+points(prop_provisioning_vs_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
+#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success-SummarySpp[["se"]]$prop_pollen_attract_vs_success,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success+SummarySpp[["se"]]$prop_pollen_attract_vs_success,code=3,angle=90, length=0.1,col=cerulean)
 extra.top.left.logx("c",2,1)
@@
 
-mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_pollen_attract_vs_success <- sma(prop_pollen_attract_vs_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_provisioning_vs_success <- sma(prop_provisioning_vs_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
 
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_pollen_attract_costs,1,col=cerulean)
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_postpollen_costs,1,col=venetian_red)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_pollen_attract_vs_success,1,col=cerulean)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_provisioning_vs_success,1,col=venetian_red)
 
@@
 points(prop_prepollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
+#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_success-SummarySpp[["se"]]$prop_prepollen_success,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_success+SummarySpp[["se"]]$prop_prepollen_success,code=3,angle=90, length=0.1,col=cerulean)
+#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded-SummarySpp[["se"]]$prop_prepollen_discarded,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded+SummarySpp[["se"]]$prop_prepollen_discarded,code=3,angle=90, length=0.1,col=venetian_red)
 extra.top.left.logx("d",2,1)
@@
 plot(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
-points(prop_postpollen_failure~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
+points(prop_postpollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
 extra.top.left.logx("e",2,1)
@@
 mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_discarded <- sma(prop_postpollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
 
 line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_postpollen_success,1,col=cerulean)
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_postpollen_failure,1,col=venetian_red)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_postpollen_discarded,1,col=venetian_red)
 
@@
 ```{r}
-mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_pollen_attract_vs_all_repro <- sma(prop_pollen_attract_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_provisioning_vs_success <- sma(prop_provisioning_vs_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
 mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
@@
 mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_postpollen_discarded <- sma(prop_postpollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
 
-energy_prop <- dplyr::select(mod_prop_pollen_attract_costs$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+energy_prop <- dplyr::select(mod_prop_pollen_attract_vs_all_repro$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
 energy_prop$test[1] <- "Proportion sucess costs to prepollen"
@@
 
-#temp <- dplyr::select(mod_prop_postpollen_costs$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+#temp <- dplyr::select(mod_prop_provisioning_vs_success$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
 #temp$test[1] <- "Proportion postpollen costs"
@@
 #temp <- dplyr::select(mod_prop_prepollen_discarded$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
-#temp$test[1] <- "Proportion prepollen costs to failure"
+#temp$test[1] <- "Proportion prepollen costs to discarded"
 #energy_prop <- rbind(energy_prop,temp)
 
-#temp <- dplyr::select(mod_prop_postpollen_failure$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
-#temp$test[1] <- "Proportion postpollen costs to failure"
+#temp <- dplyr::select(mod_prop_postpollen_discarded$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI)
+#temp$test[1] <- "Proportion postpollen costs to discarded"
 #energy_prop <- rbind(energy_prop,temp)
@@
 
-#Figure 2_NEW. Scaling of accessory costs versus weight of embryo + endosperm, by species
+#Figure 2 OLD. Scaling of accessory costs versus weight of embryo + endosperm, by species
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure02_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
+win.metafile("ms/Accessory_Costs/Figure02_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
 plot
@@
 
-plot((ovule_count/seed_count)~prop_pollen_attract_costs_all_repro,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),ylab="",ylim=c(.8,500),yaxt="n",xlim=c(.0015,.5),xaxt="n")
+plot((ovule_count/seed_count)~prop_pollen_attract_vs_all_repro_all_repro,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),ylab="",ylim=c(.8,500),yaxt="n",xlim=c(.0015,.5),xaxt="n")
 axis(2, at=c(1,10,100), labels=c(1,10,100),cex.axis=1)
@@
 
-mod_choosy <- sma((ovule_count/seed_count)~prop_pollen_attract_costs_all_repro,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
+mod_choosy <- sma((ovule_count/seed_count)~prop_pollen_attract_vs_all_repro_all_repro,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
 
-line_function_log_xy(SummarySpp[["mean"]]$prop_pollen_attract_costs_all_repro,mod_choosy,1)
+line_function_log_xy(SummarySpp[["mean"]]$prop_pollen_attract_vs_all_repro_all_repro,mod_choosy,1)
 summary(mod_choosy)
@@
 
-plot(prop_pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-points(prop_prepollen_all~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
+plot(prop_pollen_attract_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
+points(prop_prepollen_all_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
 axis(2, at=c(0,.5,1), labels=c(0,0.5,1.0),cex.axis=1)
@@
 
-mod_prop_pollen_attract_costs <- sma(prop_pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
-mod_prop_prepollen_all <- sma(prop_prepollen_all~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
+mod_prop_pollen_attract_vs_all_repro <- sma(prop_pollen_attract_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
+mod_prop_prepollen_all_vs_all_repro <- sma(prop_prepollen_all_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
 
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_pollen_attract_costs,1)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_pollen_attract_vs_all_repro,1)
 
-summary(mod_prop_pollen_attract_costs)
-summary(mod_prop_prepollen_all)
+summary(mod_prop_pollen_attract_vs_all_repro)
+summary(mod_prop_prepollen_all_vs_all_repro)
 
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure03_correlations_with_plant_weight.wmf", height=5, width=10)
+win.metafile("ms/Accessory/Figure03_correlations_with_plant_weight.wmf", height=5, width=10)
 plot
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/Figure_SXX_RE_RA_size_age_patterns.wmf", height=10, width=10)
+win.metafile("ms/Accessory/Figure_SXX_RE_RA_size_age_patterns.wmf", height=10, width=10)
 plot
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table05a_accessory_vs_RE.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/Table05a_accessory_vs_all_repro.csv",row.names=FALSE)
 
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)
 
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table05c_accessory_vs_age.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/Table05c_accessory_vs_age.csv",row.names=FALSE)
 dev.off()
@@
 
-#Table X.correlations between repro inv and flower inv by species (noted in Discussiong)
+#Table S1.correlations between repro inv and flower inv by species (noted in Discussiong)
 ```{r}
+yvar <- "repro_inv"
+xvar <- "embryo_endo_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+results <- fit$groupsummary
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=3)
+acc_slopes <- dplyr::select(results,group,n,r2,pval)
+
 yvar <- "repro_inv"
@@
 results$pval <- format(results$pval,digits=3)
-acc_slopes <- dplyr::select(results,group,n,r2,pval)
+acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
 
-write.csv(results, file="figs2/Accessory_Costs/Table06extra_flower_invest_vs_repro_inv.csv",row.names=FALSE)
+acc_slopes <- merge(acc_slopes,acc_slopes2,by="group")
+
+write.csv(acc_slopes, file="ms/Accessory/Table_S1_extra_flower_invest_vs_all_repro_inv.csv",row.names=FALSE)
 ```
@@
 
-for (i in c("total_weight","repro_inv","failure_inv","success_inv","propagule_inv","packaging_dispersal_inv","prepollen_success_inv","fruit_inv","flower_inv")) {
+for (i in c("total_weight","repro_inv","discarded_inv","success_inv","propagule_inv","packaging_dispersal_inv","prepollen_success_inv","fruit_inv","flower_inv")) {
   for (j in c("total_weight","leaf_area_0","diameter_0","repro_inv","propagule_inv")) {
@@
 
-write.csv(results, file="figs2/Accessory_Costs/Table07_EXTRA_correlations_with_repro_inv.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory_Costs/Table07_EXTRA_correlations_with_repro_inv.csv",row.names=FALSE)
 ```
@@
 
-plot(seedset~prop_failure,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),log="xy",pch=16,col=col.spp(species))
+plot(seedset~prop_discarded,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),log="xy",pch=16,col=col.spp(species))
 mod <- sma(propagule_costs~total_weight_0,data=subset(SummarySpp[["mean"]]),log="xy",method="SMA")
@@
 ```{r}
-Cairo("figs2/Accessory_Costs/FigureXX_seedcount_reprocount.svg", height=5, width=5,type="svg",pointsize=10,units="in")
-#win.metafile("figs2/Accessory_Costs/FigureXX_seedcount_reprocount.wmf", height=5, width=5)
+Cairo("ms/Accessory_Costs/FigureXX_seedcount_reprocount.svg", height=5, width=5,type="svg",pointsize=10,units="in")
+#win.metafile("ms/Accessory_Costs/FigureXX_seedcount_reprocount.wmf", height=5, width=5)
 
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/FigureXX_success_vs_failure.wmf", height=6, width=8)
+win.metafile("ms/Accessory_Costs/FigureXX_success_vs_discarded.wmf", height=6, width=8)
 plot
@@
 ```{r}
-win.metafile("figs2/Accessory_Costs/FigureXX_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
+win.metafile("ms/Accessory_Costs/FigureXX_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
 plot
@@
 
-write.csv(results, file="figs2/Accessory_Costs/TableXX_seedcount_vs_accessory.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory_Costs/TableXX_seedcount_vs_accessory.csv",row.names=FALSE)
 

### 2016-11-22 scripts/Accessory_figs_20160905.Rmd
work on accessory costs ms

@@
 #average proportion energy going to failed tissues (among reproducing individuals)
-mean(subset(SummaryInd$prop_discarded,SummaryInd$prop_discarded>0))
+1- mean(subset(SummaryInd$prop_success,SummaryInd$seed_count>0))
+mean(subset(SummaryInd$seedset,SummaryInd$seed_count>0))
 
 #average proportion of energy going to accessory costs (based on propagules, not seeds) (among individuals that produce seed)
-mean(subset(SummaryInd$prop_accessory_using_propagule,SummaryInd$seed_count>0))
-mean(subset(SummaryInd$prop_accessory_using_embryo_endo,SummaryInd$seed_count>0))
-SummarySpp[["mean"]]$prop_accessory_using_propagule
-
-check <- dplyr::select(SummarySpp[["mean"]],species,prop_accessory_using_embryo_endo,prop_accessory_using_propagule)
-check <- dplyr::arrange(check,prop_accessory_using_embryo_endo)
+mean(subset(SummaryInd$prop_accessory_vs_embryo_endo,SummaryInd$seed_count>0))
+mean(subset(SummaryInd$prop_accessory_vs_propagule,SummaryInd$seed_count>0))
+SummarySpp[["mean"]]$prop_accessory_vs_embryo_endo
+SummarySpp[["mean"]]$species
 
@@
 max(check$prop_embryo_endo_vs_all_repro)
+
+#r2 for relationship between propagule inv and repro inv across all individuals
+mod <- sma(propagule_inv~repro_inv,subset(SummaryInd,SummaryInd$seedset>0),log="xy",method="SMA")
+
+#individual with minimum accessory costs
+min(SummaryInd$prop_accessory_vs_embryo_endo)
+
+max(SummaryInd$prop_embryo_endo_vs_all_repro)
 
@@
 
-#total seed costs unrelated to seedsize
-mod <- sma(success_costs ~ embryo_endo_costs, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
+#total seed costs correlated with seedsize
+mod <- sma(success_costs ~ embryo_endo_costs, SummarySpp[["mean"]],method="SMA", log="xy")
 summary(mod)
@@
 
-#discarded per seed unrelated to seedsize
+#DISCUSSION: lower seedset = higher proportional investment in discarded tissues
+plot(seedset~prop_discarded_vs_all_repro,data=subset(SummarySpp[["mean"]]),log="",pch=16,col=col.spp(species))
+mod <- sma(seedset~prop_discarded_vs_all_repro,data=subset(SummarySpp[["mean"]],species!="BAER"),log="",method="SMA")
+summary(mod)
+
+#discarded costs correlated with seedsize
 mod <- sma(discarded_costs ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
@@
 
-mod <- sma(prop_pollen_attract_vs_all_repro ~ seedset, data=subset(SummarySpp[["mean"]]),method="SMA", log="x",slope.test=1)
-summary(mod)
-plot(prop_pollen_attract_vs_all_repro ~ seedset, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))
-
-mod <- sma(scaled_ovule_count ~ pollen_attract_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-summary(mod)
-plot(scaled_ovule_count ~ pollen_attract_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
-
-mod <- sma(scaled_seed_count ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-summary(mod)
-plot(scaled_seed_count ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
-
-mod <- sma(scaled_seed_count ~ provisioning_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-summary(mod)
-plot(scaled_seed_count ~ provisioning_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
-
-mod <- sma(scaled_seed_count ~ success_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-summary(mod)
-plot(scaled_seed_count ~ success_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
-
-mod <- sma(prepollen_all_costs ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
-summary(mod)
-plot(prepollen_discarded_costs ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species),ylim=c(.02,10000))
-points(pollen_attract_costs~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species))
-
-#more discarded = lower seedset across species - in discussion
-mod <- sma(seedset ~ prop_discarded, data=subset(SummarySpp[["mean"]],species!="BAER"),method="SMA", log="",slope.test=1)
-summary(mod)
-plot(seedset ~ prop_discarded, SummarySpp[["mean"]],log="",pch=16,col=col.spp(species))
-
 #seed size by propagule investment - all species
@@
 summary(mod)
-plot(propagule_inv_ee ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(propagule_inv ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 
-#seed size by reproductive investment - all species
+#DISCUSSION SECTION ON ESTIMATING REPRODUCTIVE EFFORT: seed size by reproductive investment - all species
 mod <- sma(repro_inv ~ embryo_endo_costs, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
@@
 
-#seed size by reproductive investment - without EPMI
+#DISCUSSION SECTION ON ESTIMATING REPRODUCTIVE EFFORT: seed size by reproductive investment - without EPMI
 mod <- sma(repro_inv ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]],species!="EPMI"),method="SMA", log="xy",slope.test=1)
@@
 
-#seedset by pollen attraction
-mod <- sma(prop_pollen_attract_vs_all_repro~seedset,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
-summary(mod)
-
-#seed size by total weight - all species
+#DISCUSSION SECTION ON ESTIMATING REPRODUCTIVE EFFORT: seed size by total weight - all species
 mod <- sma(total_weight_0 ~ embryo_endo_costs, SummarySpp[["mean"]],method="SMA", log="xy",slope.test=1)
@@
 plot(total_weight_0 ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
-
-#scaled ovule production vs prop pollen attraction  - all species
-mod <- sma(prop_pollen_attract_vs_all_repro~scaled_ovule_count,data=subset(SummarySpp[["mean"]]),log="x",slope=1,method="SMA")
-summary(mod)
-plot(prop_pollen_attract_vs_all_repro ~ scaled_ovule_count, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=1)
-results <- lines(fit$groupsummary)
-plot(fit,xlab=xvar,ylab=yvar,pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,30000))
-results
-
-yvar <- "propagule_inv"
-xvar <- "leaf_area_0_mature"
-data <- subset(SummarySppAge[["mean"]],SummarySppAge[["mean"]][[xvar]]>0&SummarySppAge[["mean"]][[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
 results <- lines(fit$groupsummary)
@@
 
-for (i in c("total_weight","propagule_inv","fruit_inv","flower_inv","flower_inv2","success_inv","prepollen_success_inv","pack_disp_success_inv","discarded_inv")) {
+for (i in c("total_weight","embryo_endo_inv","propagule_inv","fruit_inv","flower_inv","flower_inv2","success_inv","prepollen_success_inv","pack_disp_success_inv","discarded_inv")) {
   for (j in c("repro_inv")) {
@@
 
-mod_pollen_attract_costs <- sma(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA")
-mod_provisioning_costs <- sma(provisioning_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA",slope.test = mod_pollen_attract_costs$groupsummary$Slope_highCI)
+mod_repro_costs <- sma(repro_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA")
+mod_pollen_attract_costs <- sma(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA",slope.test = mod_repro_costs$groupsummary$Slope_lowCI)
+mod_provisioning_costs <- sma(provisioning_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA",slope.test = mod_repro_costs$groupsummary$Slope)
+
 line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_pollen_attract_costs,1,col=cerulean)
@@
 abline(0,1)
-mod <- sma(propagule_inv~repro_inv,data=subset(SummaryInd,propagule_inv>0),log="xy",method="OLS")
+mod <- sma(embryo_endo_inv~repro_inv,data=subset(SummaryInd,propagule_inv>0),log="xy",method="OLS")
 mtext(text="total propagule investment (mg)",side=1,line=2.2,outer=FALSE)
@@
 
-plot(seedset~prop_discarded,data=subset(SummarySpp[["mean"]],species!="BAER"&species!="PEPU"),log="xy",pch=16,col=col.spp(species))
-mod <- sma(propagule_costs~total_weight_0,data=subset(SummarySpp[["mean"]]),log="xy",method="SMA")
-summary(mod)
 ```

### 2016-11-24 scripts/Accessory_figs_20160905.Rmd
work on accessory costs

@@
-```{r}
-pdf("ms/Accessory_Costs/scaled_ovule count.pdf", height=6, width=6)
-plot
+plot(seedset~scaled_provisioning_costs,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)
 
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.05,.05), mai=c(.8,.8,.1,.05)) 
-options(scipen = 5)
+mod_ovule <- sma(choosiness~prop_pollen_attract_vs_success,data=SummarySpp[["mean"]],log="xy",method="SMA")
 
-mod2 <- sma(scaled_seed_count ~ success_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=-1)
-mod1 <- sma(scaled_ovule_count ~ pollen_attract_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=mod2$groupsummary["Slope"][[1]],elev.test=mod2$coef[[1]][1,1])
+axis(2, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8,las=2)
+axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=0.8)
+mtext("costs to make a successful unit",1,line=1.8,cex=0.7)
+mtext("count, scaled to leaf area",2,line=2.3,cex=0.7)
 
-plot(scaled_ovule_count ~ pollen_attract_costs, SummarySpp[["mean"]],log="xy",pch=1,col=col.spp(species),xlab="cost to make a unit: dashed =ovule; solid=seed",ylim=c(.001,500),ylab="scaled count",xlim=c(.01,5000),cex=1.5)
-points(scaled_seed_count ~ success_costs, SummarySpp[["mean"]],cex=1.5,pch=16,col=col.spp(species))
-line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod1,3)
-line_function_log_xy(SummarySpp[["mean"]]$success_costs,mod2,1)
-#points(scaled_seed_count ~ embryo_endo_costs, SummarySpp[["mean"]],pch=12,col=col.spp(species))
-#arrows(SummarySpp[["mean"]]$success_costs,SummarySpp[["mean"]]$scaled_seed_count,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["mean"]]$scaled_ovule_count,col=col.spp(SummarySpp[["mean"]]$species),code=0,length=.15)
-
-dev.off()
-```
+mod_x <- sma(accessory_inv~embryo_endo_inv,data=SummarySpp[["mean"]],log="xy",method="SMA")
+mod_x <- sma(accessory_costs~embryo_endo_costs,data=SummarySpp[["mean"]],log="xy",method="SMA")
+plot(zygote_set~embryo_endo_costs,SummaryInd,pch=16,log="x",col=col.spp(species),cex=1)
 
@@
 
-#discarded costs correlated with seedsize
-mod <- sma(discarded_costs ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
+#RESULTS - seed set vs seed size
+mod <- sma(seedset ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]]),method="SMA", log="xy",slope.test=1)
 summary(mod)
-plot(discarded_costs ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
+plot(seedset ~ embryo_endo_costs, SummarySpp[["mean"]],log="xy",pch=16,col=col.spp(species))
 
@@
 plot(propagule_inv ~ embryo_endo_costs, data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(repro_inv ~ embryo_endo_inv, SummaryInd,method="SMA", log="xy",slope.test=1)
+summary(mod)
+plot(repro_inv ~ embryo_endo_inv, SummaryInd,log="xy",pch=16,col=col.spp(species))
+
+mod <- sma(repro_inv ~ flower_inv, SummaryInd,method="SMA", log="xy",slope.test=1)
+summary(mod)
+plot(repro_inv ~ flower_inv, SummaryInd,log="xy",pch=16,col=col.spp(species))
 
@@
 ```{r}
+mod_propagule_inv_all <- sma(repro_inv~propagule_inv,data=SummaryInd,log="xy",method="SMA")
+mod_propagule_inv_all
+
+mod_flower_inv_all <- sma(repro_inv~flower_inv,data=SummaryInd,log="xy",method="SMA")
+mod_flower_inv_all
+
 yvar <- "repro_inv"
@@
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=mod_propagule_inv_all$groupsummary["Slope"][[1]],elev.test=mod_propagule_inv_all$coef[[1]][1,1])
 results <- fit$groupsummary
@@
 
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
 results <- fit$groupsummary
@@
 mtext(text="costs (mg/seed)",side=1,line=1.0,outer=FALSE,cex=0.8)
-legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
+legend("bottomleft",legend=c("seed count by reproductive costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
 extra.top.left("b",2,1)
@@
 #panel a
-plot(scaled_seed_count~success_costs,SummarySpp[["mean"]],pch=16,log="xy",col=venetian_red,xlim=c(.01,5000),ylim=c(5e-4,500),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)
+plot(scaled_seed_count~repro_costs,SummarySpp[["mean"]],pch=16,log="xy",col=venetian_red,xlim=c(.01,5000),ylim=c(5e-4,500),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)
 points(scaled_reach_flowering_count~pollen_attract_costs,SummarySpp[["mean"]],pch=16,col=cerulean,cex=1)
@@
 
-mod_seed <- sma(scaled_seed_count~success_costs,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
+mod_seed <- sma(scaled_seed_count~repro_costs,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
 mod_ovule2 <- sma(scaled_ovule_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
@@
 
-line_function_log_xy(SummarySpp[["mean"]]$success_costs,mod_seed,1,col=venetian_red)
+line_function_log_xy(SummarySpp[["mean"]]$repro_costs,mod_seed,1,col=venetian_red)
 line_function_log_xy(SummarySpp[["mean"]]$pollen_attract_costs,mod_ovule,1,col=cerulean)
-legend("bottomleft",legend=c("seed count by success costs","initiated ovules count by","pollen-attraction costs"),col=c(venetian_red,cerulean,"white"),pch=c(16,16,16),bty="n",cex=0.7)
+legend("bottomleft",legend=c("seed count by reproductive costs","mature ovules count by","pollen-attraction costs"),col=c(venetian_red,cerulean,"white"),pch=c(16,16,16),bty="n",cex=0.7)
 extra.top.left.logxy("a",2,1)
@@
 results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(1,300000),xlim=c(1,300000), xlab="",ylab="",lty=results$linetype,pch=16)
+plot(fit,col=col.spp(fit$groupsummary$group),log="xy",ylim=c(.3,300000),xlim=c(.3,300000), xlab="",ylab="",lty=results$linetype,pch=16)
 abline(0,1)
 mod <- sma(embryo_endo_inv~repro_inv,data=subset(SummaryInd,propagule_inv>0),log="xy",method="OLS")
-mtext(text="total propagule investment (mg)",side=1,line=2.2,outer=FALSE)
+mtext(text="total embryo and endosperm investment (mg)",side=1,line=2.2,outer=FALSE)
 mtext(text="total reproductive investment (mg)",side=2,line=2,outer=TRUE)
@@
 results <- lines(fit$groupsummary)
-plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(1,300000),xlim=c(1,300000),yaxt="n")
+plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(.3,300000),xlim=c(.3,300000),yaxt="n")
 axis(2, at=c(1,100,10000),labels=c("","",""))

### 2016-11-24 R/Summaries.R

@@ -138,6 +138,7 @@ combine_by_individual <- function(IndividualsList, Growth_all, ReproductiveCosts
     pack_disp_success_inv = pack_disp_success_inv + (seed_coat_costs*seed_count),
     repro_costs = divide_zero(repro_inv,seed_count),
     accessory_costs = repro_costs - embryo_endo_costs,
+    accessory_inv = repro_inv - embryo_endo_inv,
     accessory_costs_using_seedweight = repro_costs - propagule_costs,
     provisioning_costs = packaging_dispersal_costs + embryo_endo_costs,
     flower_inv = pollen_attract_costs*ovule_count, #a proxy measure showing good way to estimate total repro inv; doesn't have exact meaning since "repro all count" includes aborted buds 
@@ -172,6 +173,7 @@ combine_by_individual <- function(IndividualsList, Growth_all, ReproductiveCosts
     scaled_reach_flowering_count = divide_zero(prepollen_count_reach_flowering,leaf_area_0),
     scaled_repro_inv = divide_zero(repro_inv,leaf_area_0),
     scaled_pollen_attract_costs = divide_zero(pollen_attract_costs,leaf_area_0),
+    scaled_provisioning_costs = divide_zero(provisioning_costs,leaf_area_0),
     discarded_to_ovule_ratio = 1 - seedset
   )
   
@@ -197,10 +199,10 @@ combine_by_individual <- function(IndividualsList, Growth_all, ReproductiveCosts
              "leaf_shed","leaf_inv_gross","growth_leaf_neg","RA_leaf_area","leaf_area_midyear","leaf_area_0_mature","reproducing","seed_coat_costs",
              "pollen_attract_costs","packaging_dispersal_costs","success_costs","embryo_endo_costs","repro_costs","accessory_costs","prop_postpollen_all_vs_all_repro",
              "accessory_costs_using_seedweight","provisioning_costs","prepollen_all_inv","prepollen_success_inv","prepollen_discarded_inv","postpollen_all_inv",
-             "postpollen_aborted_inv","flower_inv","fruit_inv","success_inv","embryo_endo_inv","prepollen_all_costs","discarded_inv","choosiness2",
-             "prepollen_discarded_costs","postpollen_aborted_costs","postpollen_all_costs","prop_success","prop_propagule_vs_all_repro",
[…]

### 2016-11-24 scripts/nutrient.Rmd
starting to think about nutrient concentrations in stems

@@
 
+#looking at sequential discs from stems
+```{r}
+wood_discs_base <- nutrient %>%
+    subset(tissue_complete %in% c("wood_from_base"))%>%
+    select(individual_rep1,species,P) 
+names(wood_discs_base) <- c("individual","species","P_base")
+
+wood_discs_middle <- nutrient %>%
+    subset(tissue_complete %in% c("wood_from_middle"))%>%
+    select(individual_rep1,P) 
+names(wood_discs_middle) <- c("individual","P_mid")
+
+wood_discs_tip <- nutrient %>%
+    subset(tissue_complete %in% c("wood_from_tip"))%>%
+    select(individual_rep1,P) 
+names(wood_discs_tip) <- c("individual","P_tip")
+
+wood_discs <- merge(wood_discs_base, wood_discs_middle, by="individual")
+wood_discs <- merge(wood_discs, wood_discs_tip, by="individual")
+
+```
+unique(nutrient$tissue_complete)
+
 #PLOTS

### 2016-11-29 scripts/Accessory_figs_20160905.Rmd
work on accessory costs ms

@@
 par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05))
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
+segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=2)
+axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
+axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
+mtext(text="proportion all pollen-attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
+mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
+legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
+extra.top.left("d",2,1)
+
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=2)
+segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=1)
+axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
+axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
+mtext(text="proportion all provisioning investment",side=2,line=1.8,outer=FALSE,cex=0.8)
+mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
+legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
+extra.top.left("e",2,1)
 
@@
 legend("bottomleft",legend=c("pollen-attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
-extra.top.left("d",2,1)
-
-plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
-segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
-segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=2)
-axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
-axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
-mtext(text="proportion all pollen-attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
-mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
-legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
-extra.top.left("e",2,1)
-
-plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
-segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=2)
-segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=1)
-axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
-axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
-mtext(text="proportion all provisioning investment",side=2,line=1.8,outer=FALSE,cex=0.8)
-mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
-legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
 extra.top.left("f",2,1)
@@
 #panel c - success proportions
-plot(prop_pollen_attract_vs_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,
-     ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
-points(prop_provisioning_vs_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
-#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success-SummarySpp[["se"]]$prop_pollen_attract_vs_success,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success+SummarySpp[["se"]]$prop_pollen_attract_vs_success,code=3,angle=90, length=0.1,col=cerulean)
-extra.top.left.logx("c",2,1)
-axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
-mtext("seed size (mg)",1,line=1.8,cex=0.7)
-mtext("prop. successful investment",2,line=2.3,cex=0.7)
-legend("bottomleft",legend=c("pollen_attraction costs","provisioning costs"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)
-
-mod_prop_pollen_attract_vs_success <- sma(prop_pollen_attract_vs_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
-mod_prop_provisioning_vs_success <- sma(prop_provisioning_vs_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
-
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_pollen_attract_vs_success,1,col=cerulean)
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_provisioning_vs_success,1,col=venetian_red)
-
-#panel d - pollen-attraction proportions
 plot(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
@@
 #arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded-SummarySpp[["se"]]$prop_prepollen_discarded,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded+SummarySpp[["se"]]$prop_prepollen_discarded,code=3,angle=90, length=0.1,col=venetian_red)
-extra.top.left.logx("d",2,1)
+extra.top.left.logx("c",2,1)
 axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
@@
 
-#panel e - provisioning proportions
+#panel d - pollen-attraction proportions
 plot(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
 points(prop_postpollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
-extra.top.left.logx("e",2,1)
+extra.top.left.logx("d",2,1)
 axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
@@
 
+#panel e - provisioning proportions
+plot(prop_pollen_attract_vs_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="x",col=cerulean,
+     ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
+points(prop_provisioning_vs_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
+#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success-SummarySpp[["se"]]$prop_pollen_attract_vs_success,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success+SummarySpp[["se"]]$prop_pollen_attract_vs_success,code=3,angle=90, length=0.1,col=cerulean)
+extra.top.left.logx("e",2,1)
+axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
+mtext("seed size (mg)",1,line=1.8,cex=0.7)
+mtext("prop. successful investment",2,line=2.3,cex=0.7)
+legend("bottomleft",legend=c("pollen attraction costs","provisioning costs"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)
+
+mod_prop_pollen_attract_vs_success <- sma(prop_pollen_attract_vs_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+mod_prop_provisioning_vs_success <- sma(prop_provisioning_vs_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="OLS")
+
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_pollen_attract_vs_success,1,col=cerulean)
+line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_provisioning_vs_success,1,col=venetian_red)
+
 #panel f - change in slope of "success costs"
-plot(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="xy",col=cerulean,xlim=c(.002,100),ylim=c(.01,20000),xlab="",ylab="",xaxt="n",yaxt="n")
+plot(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,log="xy",col=cerulean,xlim=c(.01,100),ylim=c(.01,20000),xlab="",ylab="",xaxt="n",yaxt="n")
 points(provisioning_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
@@
 mtext("success cost (mg/seed)",2,line=2.3,cex=0.7)
-legend("bottomright",legend=c("pollen_attraction","provisioning"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)
+legend("bottomright",legend=c("pollen attraction","provisioning"),col=c(cerulean,venetian_red),pch=c(16,16),bty="n",cex=0.7)
 
@@
 mtext("choosiness (ovules initiated per seed matured)",2,line=2.3)
-mtext("proportion reproductive investment for successful pollen_attraction costs",1,line=2.3)
+mtext("proportion reproductive investment for successful pollen attraction costs",1,line=2.3)
 
@@
 
-legend("topright",legend=c("pollen_attraction","provisioning"),col=c("black","black"),pch=c(16,21),bty="n")
+legend("topright",legend=c("pollen attraction","provisioning"),col=c("black","black"),pch=c(16,21),bty="n")
 extra.top.left.logxy("c",2,1.2)

### 2016-11-29 scripts/nutrient.Rmd
trying to bring in data on stem diameter with and without bark - equation to take mean of diameters is not working

@@
 
+use <- subset(nutrient,nutrient$with_bark_diam_mm!="")
+
+for (i in 1:length(use$individual_rep1)) {
+  if (use$with_bark_diam_mm[i]=="") {
+    use$with_bark_diam <- 3
+    use$with_bark_diam <- mean(as.numeric(unlist(strsplit(as.character(use$with_bark_diam_mm), split = ";"))))
+  } else {
+    nutrient$with_bark_diam <- 4
+  }
+}
+
+subset(nutrient$with_bark_diam_mm,nutrient$with_bark_diam_mm!="")
 #looking at sequential discs from stems
@@
 ```
-unique(nutrient$tissue_complete)
+names(nutrient)
 

### 2016-11-30 scripts/RA_figs_201601129.Rmd
work on RA figures

--- 2016-11-10 scripts/RA_figs_20160627.Rmd
@@
-###playing with variables to try and show meaningful RA plots despite negative leaf growth values
+#new variables
 ``` {r}
-if (min(SummaryInd$growth_leaf) <= 0) {
-  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf - SummaryInd$growth_leaf_min + 1
-} else {
-  SummaryInd$growth_leaf_positive = SummaryInd$growth_leaf
-}
-
-SummaryInd$repro_inv_log <- 0
-for (i in 1:length(SummaryInd$individual)) {
-  if (SummaryInd$repro_inv[i] > 0) {
-    SummaryInd$repro_inv_log[i] <- log10(SummaryInd$repro_inv[i])
-  }else{
-    SummaryInd$repro_inv_log[i] <- 0  
-  }
-}
-
-SummaryInd$leaf_inv_log <- 0
-for (i in 1:length(SummaryInd$individual)) {
-  if (SummaryInd$growth_leaf[i] > 0) {
-    SummaryInd$leaf_inv_log[i] <- log10(SummaryInd$growth_leaf[i])
-  }else{
-    SummaryInd$leaf_inv_log[i] <- -(log10(-SummaryInd$growth_leaf[i]))  
-  }
-}
-
-SummaryInd$leaf_repro_inv_log <- 0
-for (i in 1:length(SummaryInd$individual)) {
-  if (SummaryInd$leaf_repro_inv[i] > 0) {
-    SummaryInd$leaf_repro_inv_log[i] <- log10(SummaryInd$leaf_repro_inv[i])
-  }else{
-    SummaryInd$leaf_repro_inv_log[i] <- -(log10(-SummaryInd$leaf_repro_inv[i]))  
-  }
-}
-
-SummaryInd$growth_leaf_no_neg_values = SummaryInd$growth_leaf
-for (i in 1:length(SummaryInd$individual)) {
-  if (SummaryInd$growth_leaf_no_neg_values[i] < 0) {
-  SummaryInd$growth_leaf_no_neg_values[i] = SummaryInd$repro_inv[i]*.01
-  }
-}
-
 SummaryInd$growth_leaf_fixed_max = SummaryInd$growth_leaf
@@
 
-SummaryInd$leaf_replacement = SummaryInd$growth_leaf
-SummaryInd$leaf_new = SummaryInd$growth_leaf
-SummaryInd$leaf_new_nonzero = SummaryInd$growth_leaf
+SummaryInd$leaf_inv_log <- 0
 for (i in 1:length(SummaryInd$individual)) {
-  if (SummaryInd$growth_leaf[i] < 0) {
-  SummaryInd$leaf_replacement[i] = SummaryInd$leaf_inv_gross[i]
-  SummaryInd$leaf_new_nonzero[i] =.1
-  SummaryInd$leaf_new[i] = 0
-  }
   if (SummaryInd$growth_leaf[i] > 0) {
-  SummaryInd$leaf_replacement[i] = SummaryInd$leaf_shed[i]
-  SummaryInd$leaf_new[i] = SummaryInd$growth_leaf[i]
-  SummaryInd$leaf_new_nonzero[i] =SummaryInd$growth_leaf[i]
+    SummaryInd$leaf_inv_log[i] <- log10(SummaryInd$growth_leaf[i])
+  }else{
+    SummaryInd$leaf_inv_log[i] <- -(log10(-SummaryInd$growth_leaf[i]))  
   }
@@
 
-SummaryInd$repro_inv_nonzero = SummaryInd$repro_inv
+SummaryInd$repro_inv_log <- 0
 for (i in 1:length(SummaryInd$individual)) {
-  if (SummaryInd$repro_inv[i] < .0001) {
-    SummaryInd$repro_inv_nonzero[i] = .1
+  if (SummaryInd$repro_inv[i] > 0) {
+    SummaryInd$repro_inv_log[i] <- log10(SummaryInd$repro_inv[i])
+  }else{
+    SummaryInd$repro_inv_log[i] <- 0  
   }
@@
 
-plot(leaf_replacement~leaf_new, subset(SummaryInd), log="xy", col=col.spp(species),pch=16)
-abline(0,1)
+SummaryInd$leaf_repro_inv_log <- 0
+for (i in 1:length(SummaryInd$individual)) {
+  if (SummaryInd$leaf_repro_inv[i] > 0) {
+    SummaryInd$leaf_repro_inv_log[i] <- log10(SummaryInd$leaf_repro_inv[i])
+  }else{
+    SummaryInd$leaf_repro_inv_log[i] <- -(log10(-SummaryInd$leaf_repro_inv[i]))  
+  }
+}
 
-plot(leaf_replacement~leaf_new, subset(SummaryInd), log="xy", col=col.age(age),pch=16)
-abline(0,1)
+```
+#Figure 2 - RA schedules for species, including indication of schedule-type
+```{r}
+win.metafile("ms/RA/Figure_2_RA_schedules.wmf", height=11, width=8)
+plot
+#pdf("figs2/RA/Figure_2_RA_schedules.pdf", height=11, width=8)
+par(mfcol=c(5,3), cex=1, omi=c(.7,.7,.1,.1), mai=c(0.15,.15,0.05,0.05))
 
-scatterplot3d(log(SummaryInd$repro_inv_nonzero),log(SummaryInd$leaf_new_nonzero),log(SummaryInd$leaf_replacement),color=col.spp(SummaryInd$species),pch=16,type="h",lty.hplot=3)
+yvar <- "leaf_inv_log"
+xvar <- "total_weight_0"
 
-scatterplot3d(log(SummaryInd$leaf_replacement),log(SummaryInd$leaf_new),log(SummaryInd$repro_inv),color=col.spp(SummaryInd$species),pch=16,type="h", lty.hplot=3)
+data <- subset(SummarySppAge[["mean"]])
+data <- split(data, data$species)
 
-scatterplot3d(log10(SummaryInd$leaf_replacement),log10(SummaryInd$leaf_new),log10(SummaryInd$repro_inv_nonzero),color=col.spp(SummaryInd$species),pch=16,grid=TRUE,type="h", lty.hplot=3,lwd=.2,xlim=c(-1,6),ylim=c(-1,6),zlim=c(-1,6))
+#data2 <- subset(SummaryInd,RA_leaf_area>-2&RA_leaf_area<3)
+data2 <- subset(SummaryInd)
+data2 <- split(data2, data2$species)
 
-planes3d(0, x.coef = 1, y.coef = 1, lty = "dashed",)
+curves <- as.data.frame(c("determinate: gradual","determinate: gradual","indeterminate: asymptotic","indeterminate: asymptotic","determinate: bang-bang","determinate: bang-bang","indeterminate: gradual","determinate: bang-bang","determinate: gradual","determinate: gradual","indeterminate: declining","determinate: gradual","determinate: bang-bang","determinate: gradual"))
 
-par(mfrow=c(1,1), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
+curves <- cbind(curves, SummarySpp[["mean"]]$species)
+names(curves) <- c("RA_type","species")
+
+data3 <- curves
+data3 <- split(data3, data3$species)
+
+for(spp in names(data)) {
+  plot(RA_fixed_max~age,data2[[spp]],col=col.age(data2[[spp]]$age),pch=16,xlab="",ylab="",log="x",xlim=c(1,40),ylim=c(-0.25,1.75),yaxt="n",xaxt="n")
+  points(RA_leaf_area~age,data[[spp]],pch=151,col=col.age(data[[spp]]$age),cex=1.5)
+   if(spp=="BOLE"|spp=="COER") {
+    rect(14,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
+    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
+  }
+    if(spp=="GRSP"|spp=="HEPU") {
+    rect(20,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
+    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
+  }
+  if(spp=="PILI") {
+    rect(10,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
+    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
+  }
+  abline(0,0)
+  abline(1,0,lty=3)
+  axis(1, at=c(1,2,5,10,20,30), labels=c("","","","","",""),cex.axis=.8,las=1,tck=-.03) 
+  axis(2, at=c(-0,0.5,1,1.5), labels=c("","","",""),cex.axis=.8,las=1,tck=-.03)
+
+  if(spp=="GRBU"|spp=="PELA"|spp=="PUTU"){
+    axis(1, at=c(1,2,5,10,20,30), labels=c(1,2,5,10,20,30),cex.axis=.8,las=1) 
+      } else{}
+  if(spp=="BAER"|spp=="BOLE"|spp=="COER"|spp=="EPMI"|spp=="GRBU"){
+    axis(2, at=c(-0,0.5,1,1.5), labels=c(-0,0.5,1,1.5),cex.axis=.8,las=1)
+  } else{}
+  extra.top.left.logx(labels.spp.full(spp),3,1)
+  extra.bottom.left.logx(data3[[spp]]$RA_type,1,0.8)
+}
+
+mtext("RA", 2, outer=TRUE,cex=1,line=2)
+mtext("age",1, outer=TRUE,cex=1,line=1.8)
+
+dev.off()
 ```
-  data <- data %>% mutate(
-    total_inv = repro_inv + growth_leaf + leaf_replacement + growth_stem,
-    prop_repro = repro_inv / total_inv,
-    prop_leaf_expand = (repro_inv + growth_leaf)/total_inv,
-    prop_leaf_replacement = (leaf_replacement+repro_inv + growth_leaf)/ total_inv,
-    prop_stem = total_inv/total_inv
-  )
 
-View(data)
+#Figure 3, Table 1 - comparing max RA to various functional traits and life history traits
+```{r}
+RA_test <- as.data.frame(c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU"))
+names(RA_test) <- c("species")
+RA_test$min_age <- c(8,6,6,8,8,6,8,6,8,8,6,8,4,8)
+test <- SummaryInd
+test <- dplyr::left_join(SummaryInd, RA_test, by = "species")
+test <- subset(test,age>min_age)
+test2 <- test %>% 
+          group_by(species) %>% 
+          summarise_each(funs(mean), maxH,RA_leaf_area)
+names(test2) <- c("species","maxH","maxRA_leaf_area")
+test2$mature <- c(7,1.4,2.4,2.4,5,2.4,7,1.4,2.4,9,7,2.4,1.4,2.4)
+test2$lifespan <- c(40,9,12,40,30,20,40,20,40,40,40,30,7,30)
 
+Table_01 <- as.data.frame(select(SummarySpp[["mean"]],species,RA_leaf_area,embryo_endo_costs,LMA,wood_density,growth_shoot_length,seed_count,scaled_seed_count))
+Table_01 <- dplyr::right_join(Table_01,test2,by="species")
+Table_01$lifetime_RA <- Table_01$lifespan*Table_01$RA_leaf_area
+plot(Table_01$lifetime_RA~embryo_endo_costs,Table_01,col=col.spp(species),pch=16,log="x")
+
+win.metafile("ms/RA/Figure_3_maxRA_correlates.wmf", height=11, width=8)
+plot
+par(mfcol=c(3,2), cex=1, omi=c(.1,.7,.1,.1), mai=c(.8,.3,.1,0.2))
+
+plot(maxRA_leaf_area~lifespan,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
+mtext("lifespan (years)",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
+mod <- lm(log10(lifespan)~maxRA_leaf_area,Table_01)
+extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)),1,1)
+mtext("maximum RA",2,outer=TRUE,line=1)
+
+plot(maxRA_leaf_area~mature,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
+mtext("age at maturity (years)",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
+mod <- lm(mature~log10(maxRA_leaf_area),Table_01)
+extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)),1,1)
+
+plot(maxRA_leaf_area~embryo_endo_costs,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n",xlim=c(.005,30),xaxt="n")
+mtext("embryo + endosperm weight (mg)",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
+axis(1, at=c(.01,.1,1,10), labels=c(.01,.1,1,10),las=1)
+mod <- lm(log10(embryo_endo_costs)~maxRA_leaf_area,Table_01)
+extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)),1,1)
+legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
+
+plot(maxRA_leaf_area~maxH,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
+mtext("maximum height (mm)",1,outer=FALSE,line=2)
+mod <- lm(log10(maxH)~maxRA_leaf_area,Table_01)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
+extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)),1,1)
+
+plot(maxRA_leaf_area~LMA,Table_01,col=col.spp(species),pch=16,cex=1.5,xlab="",yaxt="n")
+mtext("LMA",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
+mod <- lm(LMA~RA_leaf_area,Table_01)
+extra.bottom.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
+
+plot(maxRA_leaf_area~wood_density,Table_01,col=col.spp(species),pch=16,cex=1.5,xlab="",yaxt="n")
+mtext("wood density",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
+mod <- lm(wood_density~maxRA_leaf_area,Table_01)
+extra.top.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)),1,1)
+dev.off()
+
+write.csv(Table_01, file="ms/RA/Table01_maxRA_correlates.csv",row.names=FALSE)
+```
+
+#Figure 4a - reproductive vs leaf investment across plant weights
+#Shows clearly how there is a crossover in leaf vs reproductive investment for all species, but magnitude of effect is very different
 ```{r}
-pdf("figs2/RA/Figure_1_stacked_lines.pdf", height=11.5, width=8)
+win.metafile("ms/RA/Figure_4a_investment.wmf", height=11, width=8)
 plot
-par(mfrow=c(4,2), cex=1, omi=c(.1,0.1,.1,.1), mai=c(0.8,.8,.1,0.2))
+#pdf("figs2/RA/Figure_4a_investment.pdf", height=11, width=8)
+par(mfcol=c(5,3), cex=1, omi=c(.3,.7,.1,.1), mai=c(0.5,.15,0.05,0.05))
+
+yvar <- "leaf_inv_log"
+xvar <- "total_weight_0"
+
+data <- subset(SummaryInd)
+data <- split(data, data$species)
+
+data2 <- subset(SummaryInd,RA_leaf_area>-2&RA_leaf_area<3)
+data2 <- split(data2, data2$species)
+
+for(spp in names(data)) {
+
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=.8,ylim=c(-4,6),
+                    col=col.age(data[[spp]]$age),cex.main=0.9, yaxt="n")
+
+  points(repro_inv_log~total_weight_0,data[[spp]],pch=1,cex=1.2,col=col.age(data[[spp]]$age))
+  points(leaf_repro_inv_log~total_weight_0,data[[spp]],pch=151,cex=1,col=col.age(data[[spp]]$age))
+  extra.top.left.logx(labels.spp.full(spp),3,1)
+  #arrows(data[[spp]]$total_weight_0,data[[spp]]$leaf_inv_log,data[[spp]]$total_weight_0,data[[spp]]$repro_inv_log,lwd=1,length=.08,
+  #col=col.age(data[[spp]]$age))
+  abline(0,0)
+  axis(2, at=c(-4,-2,0,2,4), labels=c("","","","",""),cex.axis=.8,las=1,tck=-.03)
+
+  if(spp=="BAER"|spp=="BOLE"|spp=="COER"|spp=="EPMI"|spp=="GRBU"){
+    axis(2, at=c(-4,-2,0,2,4), labels=c(-10000,-100,0,100,10000),cex.axis=.8,las=1)
+      } else {}
+}
+
+mtext("investment (mg)", 2, outer=TRUE,cex=1,line=2.5)
+mtext("plant weight (mg)",1,outer=TRUE,cex=1,line=-.3)
+
+dev.off()
+```
+
+data <- as.data.frame(select(SummarySppAge[["mean"]],species,age, repro_inv,growth_leaf,leaf_replacement,growth_stem,diameter))
+for(v in c("repro_inv","growth_leaf","leaf_replacement","growth_stem")) {
+    i <- is.na(data[[v]])
+    data[[v]][i] <- 0
+  }
+
+  for(v in c("growth_leaf")) {
+    i <- (data[[v]] < 0)
+    data[[v]][i] <- 0
+  }
+
+data$lifetime_repro_inv <- data$repro_inv
+data$lifetime_growth_leaf <- data$growth_leaf
+
+for (i in 1:length(data$diameter)) {
+  if (data$age[i] == 2.4) {
+  data$lifetime_repro_inv[i] <- data$lifetime_repro_inv[i]*2.6
+  data$lifetime_growth_leaf[i] <- data$lifetime_growth_leaf[i]*2.6
+  }
+}
+
+for (i in 1:length(data$diameter)) {
+  if (data$age[i] == 5) {
+  data$lifetime_repro_inv[i] <- data$lifetime_repro_inv[i]*2
+  data$lifetime_growth_leaf[i] <- data$lifetime_growth_leaf[i]*2
+  }
+}
+
+for (i in 1:length(data$diameter)) {
+  if (data$age[i] == 7) {
+  data$lifetime_repro_inv[i] <- data$lifetime_repro_inv[i]*2
+  data$lifetime_growth_leaf[i] <- data$lifetime_growth_leaf[i]*2
+  }
+}
+
+for (i in 1:length(data$diameter)) {
+  if (data$age[i] == 9) {
+  data$lifetime_repro_inv[i] <- data$lifetime_repro_inv[i]*5
+  data$lifetime_growth_leaf[i] <- data$lifetime_growth_leaf[i]*5
+  }
+}
+
+for (i in 1:length(data$diameter)) {
+  if (data$age[i] == 32) {
+  data$lifetime_repro_inv[i] <- data$lifetime_repro_inv[i]*18
+  data$lifetime_growth_leaf[i] <- data$lifetime_growth_leaf[i]*18
+  }
+}
+
+lifetime <- data %>%
+            group_by(species) %>% 
+            summarise(repro = sum(lifetime_repro_inv))
+
+lifetime2 <- data %>%
+            group_by(species) %>% 
+            summarise(leaf_growth = sum(lifetime_growth_leaf))
+
+lifetime <- merge(lifetime,lifetime2,by="species")
+
+lifetime$RA <- lifetime$repro / (lifetime$repro + lifetime$leaf_growth)            
+plot(RA~leaf_growth,lifetime,pch=16,col=col.spp(species),log="x")
+
+#stacked lines
+```{r}
+#pdf("figs2/RA/Figure_1_stacked_lines.pdf", height=11.5, width=8)
+#plot
+par(mfrow=c(7,4), cex=1, omi=c(.1,0.1,.1,.1), mai=c(0.8,.8,.1,0.2))
 
@@
     prop_leaf_replacement = (leaf_replacement+repro_inv + growth_leaf)/ total_inv,
-    prop_stem = total_inv/total_inv
+    prop_stem = total_inv/total_inv,
+    stack1 = repro_inv,
+    stack2 = repro_inv+growth_leaf,
+    stack3= leaf_replacement+repro_inv + growth_leaf,
+    stack4 = total_inv
   )
@@
   extra.top.left.logx(labels.spp.full(spp),3,1)
+
+  plot(stack4~age,data[[spp]],col="white",log="x")
+  if(spp=="BOLE"|spp=="COER"|spp=="HEPU"|spp=="GRSP") {
+  polygon(x=c(1.4,2.4,7,9,9,1.4),y=c(data[[spp]]$stack4[1],data[[spp]]$stack4[2],data[[spp]]$stack4[4],
+                                           data[[spp]]$stack4[5],0.1,0.1),col="burlywood4",density=NA) 
+  polygon(x=c(1.4,2.4,7,9,9,1.4),y=c(data[[spp]]$stack3[1],data[[spp]]$stack3[2],data[[spp]]$stack3[4],
+                                           data[[spp]]$stack3[5],0.1,0.1),col="darkseagreen4",density=NA)
+  polygon(x=c(1.4,2.4,7,9,9,1.4),y=c(data[[spp]]$stack2[1],data[[spp]]$stack2[2],data[[spp]]$stack2[4],
+                                         data[[spp]]$stack2[5],0.1,0.1),col="darkseagreen2",density=NA)
+  polygon(x=c(1.4,2.4,7,9,9,1.4),y=c(data[[spp]]$stack1[1],data[[spp]]$stack1[2],data[[spp]]$stack1[4],
+                                          data[[spp]]$stack1[5],0.1,0.1),col="coral3",density=NA)
+  text(8,data[[spp]]$prop_repro[5]*.4,"reproductive",adj=1)
+  text(1.5,data[[spp]]$prop_leaf_expand[1]*.5,"additional leaves",adj=0)
+  text(4,data[[spp]]$prop_leaf_replacement[3]*.6,"replacement leaves",adj=0)
+  text(6,0.9,"additional stems",adj=1)
   }
 
-dev.off()
-```
-
--#Figure 1 Different species have different RA values. But biggest shift in RA is with age
-```{r, echo=FALSE,message=FALSE,fig.width=14, fig.height=7.5}
-#pdf("figs2/RA/Figure_1_leaf_vs_repro.pdf", height=4.3, width=8)
-win.metafile("figs2/RA/Figure_1_leaf_vs_repro.wmf", height=4.3, width=8)
-plot
-par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2)) 
-plot(repro_inv~growth_leaf_positive, subset(SummaryInd,growth_leaf_positive>1), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
-     xlab="",ylab="",yaxt="n",xaxt="n",cex=0.8)
-axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
-axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
-legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
-abline(0,1)
-text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
-abline(log10(3),1)
-text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
-abline(log10(9),1)
-text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
-abline(log10(19),1)
-text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
-abline(log10(.111),1)
-text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
-abline(log10(.010101),1)
-text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
-mtext("reproductive investment (mg)",2,line=1,outer=TRUE)
-
-plot(repro_inv~growth_leaf_positive, subset(SummaryInd,growth_leaf_positive>1), log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
-     xlab="",ylab="",yaxt="n",xaxt="n",cex=0.8)
-axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
-axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
-legend("bottomright",legend=labels.age(),col=col.age(),pch=16, cex=.6,bty="n")
-abline(0,1)
-text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
-abline(log10(3),1)
-text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
-abline(log10(9),1)
-text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
-abline(log10(19),1)
-text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
-abline(log10(.111),1)
-text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
-abline(log10(.010101),1)
-text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
-mtext("leaf investment, scaled to be positive (mg)",1,line=2,outer=TRUE)
-dev.off()
-```
-
-#Figure 1 - shed leaves, gross leaf production
-```{r}
-pdf("figs2/RA/Figure_0_gross_leaf_inv.pdf", height=4.3, width=8)
-plot
-par(mfrow=c(1,2), cex=1, omi=c(.1,0.1,.1,.1), mai=c(0.8,.8,.1,0.2)) 
-plot(leaf_shed ~ leaf_inv_gross,SummaryInd,log="xy",pch=16, col=col.spp(species),xlim=c(1,10^7),ylim=c(1,10^7))
-abline(0,1)
-plot(leaf_shed ~ leaf_inv_gross,SummaryInd,log="xy",pch=16, col=col.age(age),xlim=c(1,10^7),ylim=c(1,10^7))
-
-abline(0,1)
-
-dev.off()
-
-scatterplot3d(SummaryInd$leaf_shed,SummaryInd$leaf_inv_gross,SummaryInd$repro_inv,log="xyz",color=col.spp(SummaryInd$species),pch=16)
-
-ternary <- dplyr::select(SummaryInd,species,age,leaf_shed,growth_leaf,pack_disp_costs,seed_costs,embryo_endo_size)
-ternary$per_poll <-100*ternary$prepollen_costs/ternary$seed_costs
-ternary$post_poll <- 100-ternary$per_poll
-ternary$per_seed <-100*ternary$embryo_endo_size/ternary$seed_costs
-ternary$per_disp <-100*ternary$pack_disp_costs/ternary$seed_costs
-
-mod_poll <- sma(per_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")
-mod_seed <- sma(per_seed~seed_costs,ternary,slope.test=0,method="OLS",log="x")
-mod_disp <- sma(per_disp~seed_costs,ternary,slope.test=0,method="OLS",log="x")
-mod_post_poll <- sma(post_poll~seed_costs,ternary,slope.test=0,method="OLS",log="x")
-
-costs_per_seed <- as.data.frame("costs for seed (%)")
-costs_per_seed <- cbind(costs_per_seed,dplyr::select(mod_seed$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-
-costs_per_seed2 <- as.data.frame("costs for pre-pollination (%)")
-costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_poll$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
-
-costs_per_seed2 <- as.data.frame("costs for dispersal (%)")
-costs_per_seed2 <- cbind(costs_per_seed2,dplyr::select(mod_disp$groupsummary,r2,pval,Int,Slope,Slope_lowCI,Slope_highCI,Slope_test,Slope_test_p))
-names(costs_per_seed2) <- c("investment category (mg)","r squared","p value","intercept","slope","slope_lowCI","slope_highCI","slope test","slope test p")
-costs_per_seed <- rbind(costs_per_seed,costs_per_seed2)
-
-write.csv(costs_per_seed, file="figs2/Accessory_Costs/Table00_in_text_costs_per_seed.csv",row.names=FALSE)
-
-win.metafile("figs2/Accessory_Costs/FigureXX_seedcost_components.wmf", height=6, width=6)
-plot
-
-plot(per_seed~seed_costs,ternary,col="black",log="x",pch=21,cex=2,ylim=c(0,75),ylab="prop of seed_costs")
-points(per_poll~seed_costs,ternary,col="red",pch=16,cex=2)
-points(per_disp~seed_costs,ternary,col="blue",pch=16,cex=2)
-
-abline(mod_poll$groupsummary["Int"][[1]],mod_poll$groupsummary["Slope"][[1]],col="red",lwd=2)
-abline(mod_seed$groupsummary["Int"][[1]],mod_seed$groupsummary["Slope"][[1]],col="black",lty=2,lwd=2)
-abline(mod_disp$groupsummary["Int"][[1]],mod_disp$groupsummary["Slope"][[1]],col="blue",lwd=2)
-legend("topright",legend=c("seed","prepollen","pack&disp"),col=c("black","red","blue"),pch=16, cex=1.1,bty="n")
-v <- sqrt(ternary$seed_costs/500)
-ternary$horz <- c(1.8,1.3,1.2,-0.3,0.6,0.6,0.5,-0.2,1.3,1.7,1.4,-0.2,-0.3,-0.3)
-ternary$vert <- c(v[1]*-1.7,v[2]*1.1,v[3]*1.2,v[4],v[5]*-2.3,v[6]*4.5,v[7],v[8]*1.6,v[9],v[10]*0.2,v[11],v[12],v[13],v[14])
-ternary = ternary[with(ternary, order(-seed_costs)), ]
-label <- 20
-
-dev.off()
-library(ggtern)
-win.metafile("figs2/Accessory_Costs/Figure03_ternary_diagram_seed_costs.wmf", height=5, width=5)
-plot
-
-par(mfrow=c(1,1), cex=1, omi=c(2,2,2,2), mai=c(2,2,2,2))
-
-ggtern(data=ternary,aes(y=per_seed,x=per_poll,z=per_disp)) +
-      geom_point(size=sqrt(ternary$seed_costs/2),shape=20,color=col.spp(ternary$species)) +
-      theme_bw() + 
-      theme_showarrows() +
-      geom_text(label=ternary$species, color="black", hjust=ternary$horz, 
-                 vjust=ternary$vert,size=2) +
-      ggtitle("Seed cost components")+
-      labs(T="embryo+endosperm",L="pre-pollination",R="provisioning")+
-      Tarrowlab("embryo + endosperm weight (%)")+
-      Larrowlab("pre-pollination costs (%)")+
-      Rarrowlab("provisioning costs (%)")+
-      theme(plot.title = element_text(size=11,face="bold"))+
-      theme(tern.axis.title.T = element_text(size=9,face="plain"))+
-      theme(tern.axis.title.L = element_text(size=9,face="plain",hjust=0,vjust=1.7))+
-      theme(tern.axis.title.R = element_text(size=9,face="plain",hjust=1,vjust=1.7))+
-      theme(tern.axis.arrow.text = element_text(size=9,face="plain"))+
-      theme(tern.axis.arrow.start= 0.2)+ 
-      theme(tern.axis.arrow.finish=0.8)
-
-```
-
-#Figure 1 - alternate rendition, not scaling leaf investment to be positive, reassigning "negative" leaf investment individuals to RA =1.1
-```{r}
-pdf("figs2/RA/Figure_1_alt_leaf_vs_repro.pdf", height=4.3, width=8)
-plot
-
-par(mfrow=c(1,2), cex=1, omi=c(1.1,0.8,.1,.1), mai=c(0.3,.4,.1,0.2))
-
-plot(repro_inv~(growth_leaf_fixed_max), subset(SummaryInd), log="xy", col=col.spp(species),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
-     xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
-axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
-axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
-#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
-abline(0,1)
-text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
-abline(log10(3),1)
-text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
-abline(log10(9),1)
-text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
-abline(log10(19),1)
-text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
-abline(log10(.111),1)
-text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
-abline(log10(.010101),1)
-text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
-mtext("reproductive investment (mg)",2,line=1,outer=TRUE)
-
-plot(repro_inv~growth_leaf_fixed_max, subset(SummaryInd), log="xy", col=col.age(age),pch=16,xlim=c(1,1000000),ylim=c(1,1000000),
-     xlab="",ylab="",cex=0.8,xaxt="n",yaxt="n")
-axis(1, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
-axis(2, at=c(1,100,10000,1000000), labels=c(1,100,10000,"1000000"),cex.axis=0.9)
-#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
-abline(0,1)
-text(10^5.6,10^5.8,srt=45,"RA = 0.5",cex=.6)
-abline(log10(3),1)
-text(10^5.13,10^5.8,srt=45,"RA = 0.75",cex=.6)
-abline(log10(9),1)
-text(10^4.67,10^5.8,srt=45,"RA = 0.9",cex=.6)
-abline(log10(19),1)
-text(10^4.33,10^5.8,srt=45,"RA = 0.95",cex=.6)
-abline(log10(.111),1)
-text(10^5.6,10^4.85,srt=45,"RA = 0.1",cex=.6)
-abline(log10(.010101),1)
-text(10^5.6,10^3.8,srt=45,"RA = 0.01",cex=.6)
-
-mtext("leaf investment (mg)",1,line=2,outer=TRUE)
-dev.off()
-```
-
-#Figure 2 - RA schedules for species, including indication of schedule-type
-```{r}
-win.metafile("figs2/RA/Figure_2_RA_schedules.wmf", height=11, width=8)
-plot
-#pdf("figs2/RA/Figure_2_RA_schedules.pdf", height=11, width=8)
-par(mfcol=c(5,3), cex=1, omi=c(.7,.7,.1,.1), mai=c(0.15,.15,0.05,0.05))
-
-yvar <- "leaf_inv_log"
-xvar <- "total_weight_0"
-
-data <- subset(SummarySppAge[["mean"]])
-data <- split(data, data$species)
-
-#data2 <- subset(SummaryInd,RA_leaf_area>-2&RA_leaf_area<3)
-data2 <- subset(SummaryInd)
-data2 <- split(data2, data2$species)
-
-curves <- as.data.frame(c("determinate: gradual","determinate: gradual","indeterminate: asymptotic","indeterminate: asymptotic","determinate: bang-bang","determinate: bang-bang","indeterminate: gradual","determinate: bang-bang","determinate: gradual","determinate: gradual","indeterminate: declining","determinate: gradual","determinate: bang-bang","determinate: gradual"))
-
-curves <- cbind(curves, SummarySpp[["mean"]]$species)
-names(curves) <- c("RA_type","species")
-
-data3 <- curves
-data3 <- split(data3, data3$species)
-
-for(spp in names(data)) {
-  plot(RA_fixed_max~age,data2[[spp]],col=col.age(data2[[spp]]$age),pch=16,xlab="",ylab="",log="x",xlim=c(1,40),ylim=c(-0.25,1.75),yaxt="n",xaxt="n")
-  points(RA_leaf_area~age,data[[spp]],pch=151,col=col.age(data[[spp]]$age),cex=1.5)
-   if(spp=="BOLE"|spp=="COER") {
-    rect(14,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
-    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
-  }
-    if(spp=="GRSP"|spp=="HEPU") {
-    rect(20,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
-    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
-  }
-  if(spp=="PILI") {
-    rect(10,par("usr")[3],10^par("usr")[2],par("usr")[4],col="light grey",density=NA)
-    rect(10^par("usr")[1],par("usr")[3],10^par("usr")[2],par("usr")[4],col="black",density=0)
-  }
-  abline(0,0)
-  abline(1,0,lty=3)
-  axis(1, at=c(1,2,5,10,20,30), labels=c("","","","","",""),cex.axis=.8,las=1,tck=-.03) 
-  axis(2, at=c(-0,0.5,1,1.5), labels=c("","","",""),cex.axis=.8,las=1,tck=-.03)
-
-  if(spp=="GRBU"|spp=="PELA"|spp=="PUTU"){
-    axis(1, at=c(1,2,5,10,20,30), labels=c(1,2,5,10,20,30),cex.axis=.8,las=1) 
-      } else{}
-  if(spp=="BAER"|spp=="BOLE"|spp=="COER"|spp=="EPMI"|spp=="GRBU"){
-    axis(2, at=c(-0,0.5,1,1.5), labels=c(-0,0.5,1,1.5),cex.axis=.8,las=1)
-  } else{}
-  extra.top.left.logx(labels.spp.full(spp),3)
-  extra.bottom.left.logx(data3[[spp]]$RA_type,1,0.8)
 }
 
-mtext("RA", 2, outer=TRUE,cex=1,line=2)
-mtext("age",1, outer=TRUE,cex=1,line=1.8)
-
-dev.off()
-```
-
-#Figure 3, Table 1 - comparing max RA to various functional traits and life history traits
-```{r}
-RA_test <- as.data.frame(c("BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","LEES","PELA","PEPU","PHPH","PILI","PUTU"))
-names(RA_test) <- c("species")
-RA_test$min_age <- c(8,6,6,8,8,6,8,6,8,8,6,8,4,8)
-test <- SummaryInd
-test <- dplyr::left_join(SummaryInd, RA_test, by = "species")
-test <- subset(test,age>min_age)
-test2 <- test %>% 
-          group_by(species) %>% 
-          summarise_each(funs(mean), maxH,RA_leaf_area)
-names(test2) <- c("species","maxH","maxRA_leaf_area")
-test2$mature <- c(7,1.4,2.4,2.4,5,2.4,7,1.4,2.4,9,7,2.4,1.4,2.4)
-test2$lifespan <- c(40,9,12,40,30,20,40,20,40,40,40,30,7,30)
-
-Table_01 <- as.data.frame(select(SummarySpp[["mean"]],species,RA_leaf_area,embryo_endo_size,LMA,wood_density,growth_shoot_length,seed_count))
-Table_01 <- dplyr::right_join(Table_01,test2,by="species")
-Table_01$RA_per_year <- Table_01$RA_leaf_area/Table_01$lifespan
-
-win.metafile("figs2/RA/Figure_3_maxRA_correlates.wmf", height=11, width=8)
-plot
-par(mfcol=c(3,2), cex=1, omi=c(.1,.7,.1,.1), mai=c(.8,.3,.1,0.2))
-
-plot(maxRA_leaf_area~lifespan,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
-mtext("lifespan (years)",1,outer=FALSE,line=2)
-axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
-mod <- lm(log10(lifespan)~maxRA_leaf_area,Table_01)
-extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
-mtext("maximum RA",2,outer=TRUE,line=1)
-
-plot(maxRA_leaf_area~mature,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
-mtext("age at maturity (years)",1,outer=FALSE,line=2)
-axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
-mod <- lm(mature~log10(maxRA_leaf_area),Table_01)
-extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
-
-plot(maxRA_leaf_area~embryo_endo_size,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n",xlim=c(.005,30),xaxt="n")
-mtext("embryo + endosperm weight (mg)",1,outer=FALSE,line=2)
-axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
-axis(1, at=c(.01,.1,1,10), labels=c(.01,.1,1,10),las=1)
-mod <- lm(log10(embryo_endo_size)~maxRA_leaf_area,Table_01)
-extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
-legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
-
-plot(maxRA_leaf_area~maxH,Table_01,col=col.spp(species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
-mtext("maximum height (mm)",1,outer=FALSE,line=2)
-mod <- lm(log10(maxH)~maxRA_leaf_area,Table_01)
-axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
-extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
-
-plot(maxRA_leaf_area~LMA,Table_01,col=col.spp(species),pch=16,cex=1.5,xlab="",yaxt="n")
-mtext("LMA",1,outer=FALSE,line=2)
-axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
-mod <- lm(LMA~RA_leaf_area,Table_01)
-extra.bottom.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
-
-plot(maxRA_leaf_area~wood_density,Table_01,col=col.spp(species),pch=16,cex=1.5,xlab="",yaxt="n")
-mtext("wood density",1,outer=FALSE,line=2)
-axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
-mod <- lm(wood_density~maxRA_leaf_area,Table_01)
-extra.top.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
-dev.off()
-
-write.csv(Table_01, file="figs2/RA/Table01_maxRA_correlates.csv",row.names=FALSE)
-
-plot(RA_per_year ~ maxRA_leaf_area,Table_01,col=col.spp(species),pch=16,cex=2,log="y")
-mod <- lm(maxRA_leaf_area~log10(RA_per_year),Table_01)
-summary(mod)
-
-plot(seed_count ~ maxRA_leaf_area,Table_01,col=col.spp(species),pch=16,cex=2,log="y")
-```
-
-#Figure 4a - reproductive vs leaf investment across plant weights
-#Shows clearly how there is a crossover in leaf vs reproductive investment for all species, but magnitude of effect is very different
-```{r}
-win.metafile("figs2/RA/Figure_4a_investment.wmf", height=11, width=8)
-plot
-#pdf("figs2/RA/Figure_4a_investment.pdf", height=11, width=8)
-par(mfcol=c(5,3), cex=1, omi=c(.3,.7,.1,.1), mai=c(0.5,.15,0.05,0.05))
-
-yvar <- "leaf_inv_log"
-xvar <- "total_weight_0"
-
-data <- subset(SummaryInd)
-data <- split(data, data$species)
-
-data2 <- subset(SummaryInd,RA_leaf_area>-2&RA_leaf_area<3)
-data2 <- split(data2, data2$species)
-
-for(spp in names(data)) {
-
-  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="x",xlab="",ylab="",cex=.8,ylim=c(-4,6),
-                    col=col.age(data[[spp]]$age),cex.main=0.9, yaxt="n")
-
-  points(repro_inv_log~total_weight_0,data[[spp]],pch=1,cex=1.2,col=col.age(data[[spp]]$age))
-  points(leaf_repro_inv_log~total_weight_0,data[[spp]],pch=151,cex=1,col=col.age(data[[spp]]$age))
-  extra.top.left.logx(labels.spp.full(spp),3)
-  #arrows(data[[spp]]$total_weight_0,data[[spp]]$leaf_inv_log,data[[spp]]$total_weight_0,data[[spp]]$repro_inv_log,lwd=1,length=.08,
-  #col=col.age(data[[spp]]$age))
-  abline(0,0)
-  axis(2, at=c(-4,-2,0,2,4), labels=c("","","","",""),cex.axis=.8,las=1,tck=-.03)
-
-  if(spp=="BAER"|spp=="BOLE"|spp=="COER"|spp=="EPMI"|spp=="GRBU"){
-    axis(2, at=c(-4,-2,0,2,4), labels=c(-10000,-100,0,100,10000),cex.axis=.8,las=1)
-      } else {}
-}
-
-mtext("investment (mg)", 2, outer=TRUE,cex=1,line=2.5)
-mtext("plant weight (mg)",1,outer=TRUE,cex=1,line=-.3)
-
-dev.off()
+#dev.off()
 ```
@@
 ```{r}
-win.metafile("figs2/RA/Figure_4b_leaf_area_vs_age.wmf", height=11, width=8)
+win.metafile("ms/RA/Figure_4b_leaf_area_vs_age.wmf", height=11, width=8)
 plot
@@
   points(leaf_area~age,data2[[spp]],cex=1.5,col=col.age(data2[[spp]]$age),pch=151)
-  extra.top.left.logxy(labels.spp.full(spp),3)
+  extra.top.left.logxy(labels.spp.full(spp),3,1)
    if(spp=="BOLE"|spp=="COER") {

### 2016-11-30 R/Summaries.R

@@ -255,7 +255,7 @@ get_species_values <- function(SummaryInd, groups) {
     SummaryInd %>%
     group_by_(.dots=dots) %>%
     summarise_each(f, height, growth_inv, total_weight, total_weight_0,total_inv, RA, RA_leaf_area, diameter, stem_area,
-      leaf_weight, stem_weight, growth_stem_diameter, growth_stem_area, growth_leaf, leaf_shed,
+      leaf_weight, stem_weight, growth_stem_diameter, growth_stem_area, growth_leaf, leaf_shed,leaf_weight_0,stem_weight_0,repro_inv,
       growth_stem, diameter, diameter_0,LMA, wood_density,leaf_area,leaf_area_0,leaf_area_midyear,leaf_replacement,growth_leaf_neg)
   })
   names(out[[1]]) <- fs
@@ -281,7 +281,7 @@ get_species_values <- function(SummaryInd, groups) {
     SummaryInd %>%
     filter(repro_inv > 0) %>%
     group_by_(.dots=dots) %>%
-    summarise_each(f,repro_inv,ovule_count,leaf_area_0_mature)
+    summarise_each(f,ovule_count,leaf_area_0_mature)
   })
   names(out[[4]]) <- fs
 

### 2016-12-01 scripts/RA_figs_201601129.Rmd
working through RA figs

@@
+traits <- as.data.frame(select(SummarySpp[["mean"]],species,RA_leaf_area,RA_max_1,RA_vs_all_leaf,embryo_endo_costs,LMA,wood_density,growth_shoot_length,seed_count,lifespan,maturity,asymptotic_RA))
+traits$maxH <- SummarySpp[["max"]]$height
+
+temp <- subset(SummarySppAge[["mean"]], age >= asymptotic_RA)
+temp <- temp %>%
+        group_by(species) %>%
+        summarise_each(funs(mean), RA_leaf_area,RA_max_1,RA_vs_all_leaf)
+names(temp) <- c("species","RA_leaf_area_max","RA_max_1_max","RA_vs_all_leaf_max")
+
+traits <- merge(traits,temp,by="species")
+
+#win.metafile("figs2/RA/Figure_3_maxRA_correlates.wmf", height=11, width=8)
+#plot
+par(mfcol=c(3,2), cex=1, omi=c(.1,.7,.1,.1), mai=c(.8,.3,.1,0.2))
+
+i <- traits$RA_leaf_area_max
+i <- traits$RA_max_1_max
+i <- traits$RA_vs_all_leaf_max
+for (i in c(traits$RA_leaf_area_max,traits$RA_max_1_max,traits$RA_vs_all_leaf_max)) {
+
+plot(i~traits$lifespan,col=col.spp(traits$species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
+mtext("lifespan (years)",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
+# <- lm(log10(lifespan)~i,traits)
+#extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
+mtext("maximum RA",2,outer=TRUE,line=1)
+
+plot(i~traits$maturity,col=col.spp(traits$species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
+mtext("age at maturity (years)",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
+#mod <- lm(mature~log10(i),traits)
+#extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
+
+plot(i~traits$embryo_endo_costs,col=col.spp(traits$species),pch=16,cex=1.5,log="x",xlab="",yaxt="n",xlim=c(.005,30),xaxt="n")
+mtext("embryo + endosperm weight (mg)",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
+axis(1, at=c(.01,.1,1,10), labels=c(.01,.1,1,10),las=1)
+#mod <- lm(log10(embryo_endo_size)~i,traits)
+#extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
+#legend("topleft",legend=labels.spp(),col=col.spp(),pch=16, cex=.6,bty="n")
+
+plot(i~traits$maxH,col=col.spp(traits$species),pch=16,cex=1.5,log="x",xlab="",yaxt="n")
+mtext("maximum height (mm)",1,outer=FALSE,line=2)
+#mod <- lm(log10(maxH)~i,traits)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
+#extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
+
+plot(i~traits$LMA,col=col.spp(traits$species),pch=16,cex=1.5,xlab="",yaxt="n",log="x")
+mtext("LMA",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
+#mod <- lm(LMA~RA_leaf_area,traits)
+#extra.bottom.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
+
+plot(i~wood_density,traits,col=col.spp(traits$species),pch=16,cex=1.5,xlab="",yaxt="n")
+mtext("wood density",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c("","","","","",""),cex.axis=.8,las=1)
+#mod <- lm(wood_density~i,traits)
+#extra.top.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
+#dev.off()
+}
+
+write.csv(traits, file="figs2/RA/Table01_maxRA_correlates.csv",row.names=FALSE)
+
+plot(RA_per_year ~ i,traits,col=col.spp(species),pch=16,cex=2,log="y")
+mod <- lm(i~log10(RA_per_year),traits)
+summary(mod)
+
+plot(seed_count ~ i,traits,col=col.spp(species),pch=16,cex=2,log="y")
+
 #new variables

### 2016-12-01 R/Summaries.R

@@ -195,6 +195,8 @@ combine_by_individual <- function(IndividualsList, Growth_all, ReproductiveCosts
      prop_repro = repro_inv/gross_inv,
      prop_leaf_expand = (repro_inv + growth_leaf_pos)/gross_inv,
      prop_leaf_replacement = (leaf_replacement + repro_inv + growth_leaf_pos)/gross_inv,
+     RA_vs_all_leaf = repro_inv / (leaf_replacement + growth_leaf_pos + repro_inv),
+     RA_seed = embryo_endo_inv / total_inv
      prop_stem = 1
    )
   
@@ -214,7 +216,7 @@ combine_by_individual <- function(IndividualsList, Growth_all, ReproductiveCosts
              "prop_pack_disp_vs_success","prop_pollen_attract_vs_all_repro","prop_pack_disp_vs_all_repro","prop_embryo_endo_vs_all_repro","prop_postpollen_success","discarded_costs",
              "prop_postpollen_discarded","prop_prepollen_success","prop_prepollen_discarded","scaled_discarded_count","scaled_reach_flowering_count",
              "scaled_seed_count","scaled_ovule_count","scaled_repro_inv","discarded_to_ovule_ratio","leaf_replacement","scaled_pollen_attract_costs",
-             "RA_max_1","gross_inv","prop_repro","prop_leaf_expand","prop_leaf_replacement","prop_stem")) {
+             "RA_max_1","gross_inv","prop_repro","prop_leaf_expand","prop_leaf_replacement","prop_stem","RA_vs_all_leaf","RA_seed")) {
     i <- is.na(SummaryInd[[v]])
     SummaryInd[[v]][i] <- 0
     i <- is.infinite(SummaryInd[[v]])
@@ -266,7 +268,7 @@ get_species_values <- function(SummaryInd, groups) {
     summarise_each(f, height, growth_inv, total_weight, total_weight_0,total_inv, RA, RA_leaf_area, stem_area,growth_leaf_pos,
       leaf_weight, stem_weight, growth_stem_diameter, growth_stem_area, growth_leaf, leaf_shed,leaf_weight_0,stem_weight_0,repro_inv,
       growth_stem, diameter, diameter_0,LMA, wood_density,leaf_area,leaf_area_0,leaf_area_midyear,leaf_replacement,growth_leaf_neg,
[…]

### 2016-12-01 RA_figs.R

@@ -1,7 +1,7 @@
 # pdf('ms/RA/Figure_1_stacked_lines.pdf', height=11.5, width=8) plot
 
 data <- select(SummarySppAge[["mean"]], species, age, repro_inv, growth_leaf, leaf_replacement,leaf_area_0,leaf_weight_0,
-  growth_stem, leaf_shed,prop_stem,prop_leaf_replacement,prop_leaf_expand,prop_repro,RA_max_1,lifespan,height)
+  growth_stem, leaf_shed,prop_stem,prop_leaf_replacement,prop_leaf_expand,prop_repro,RA_max_1,lifespan,height, RA_vs_all_leaf)
 
 
 par(mfrow = c(7,4), cex = 1, oma = c(5, 5, 1, 1), mar = c(0, 3, 2, 1))
@@ -31,13 +31,25 @@ for (i in seq_along(all_species)) {
     mtext("Standing leaf biomass (mg)", 2, line=2.5, outer=FALSE)
   }
   
-  #reproductive investment
-  plot(NA,xaxt="n",xlim = c(1.4, 32), ylim=c(1,(max(data_sp$repro_inv)*1.1)),log="x",xaxs = "i", yaxs = "i", xaxt="n", ylab="n")
-  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$repro_inv, 0, 0), col = "coral3", density = NA)
+  # #reproductive investment
+  # plot(NA,xaxt="n",xlim = c(1.4, 32), ylim=c(1,(max(data_sp$repro_inv)*1.1)),log="x",xaxs = "i", yaxs = "i", xaxt="n", ylab="n")
+  # polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$repro_inv, 0, 0), col = "coral3", density = NA)
+  # axis(1, labels = (i %in% c(7,14)))
+  # 
+  # if (i %in% c(4,11)) {
+  #   mtext("reproductive investment (mg)", 2, line=2.5, outer=FALSE)
+  # }
+  
+  #RA leaf area, all leaf
+  plot(NA, log = "x", ylim = c(0, 1),  xlim = c(1.4, 32), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
+  box()
   axis(1, labels = (i %in% c(7,14)))
- 
+  axis(2, at = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = TRUE, las=1)
[…]

### 2016-12-12 RA_figs.Rmd
work on RA manuscript

# pdf('ms/RA/Figure_1_stacked_lines.pdf', height=11.5, width=8) plot

data <- select(SummarySppAge[["mean"]], species, age, repro_inv, growth_leaf, leaf_replacement,leaf_area_0,leaf_weight_0,total_inv,prop_surplus,
  growth_stem, leaf_shed,prop_stem,prop_leaf_replacement,prop_leaf_expand,prop_repro,RA_max_1,lifespan,height, RA_vs_all_leaf,
  LL_death,height_0,total_weight_0,all_leaf_inv)
data$leaf_shed2 <- data$leaf_weight_0 / data$LL_death
data_ind <- select(SummaryInd,species,individual,age, LL_death,height_0,leaf_shed,leaf_weight_0,
                   growth_leaf_pos,repro_inv,total_weight_0,all_leaf_inv,total_inv,surplus_energy)

```{r}
par(mfrow = c(7,4), cex = 1, oma = c(5, 5, 1, 1), mar = c(0, 3, 2, 1))

all_species <- unique(data$species)

for (i in seq_along(all_species)) {

  # Todo: this should be calculated at individual level before taking means by species
  data_sp <- filter(data, species == all_species[i])
  data_sp_ind <- filter(data_ind, species == all_species[i])
  data_sp_no5 <- subset(data_sp,age!=5)
  m <- max(data_sp$age)
  n <- length(data_sp$age)
  curves <- as.data.frame(c("determinate: gradual","determinate: gradual","indeterminate: asymptotic","indeterminate: asymptotic",
                            "determinate: bang-bang","determinate: bang-bang","indeterminate: gradual","determinate: bang-bang",
                            "determinate: gradual","determinate: gradual","indeterminate: declining","determinate: gradual",
                            "determinate: bang-bang","determinate: gradual"))

  #height
  plot(NA,log = "x", ylim=c(1,(max(data_sp$height_0)*1.1)), xlim = c(1.2, 37), xaxs = "i", yaxs = "i", xaxt="n", ylab="n")
  box()
  axis(1, labels = (i %in% c(7,14)))
  points(x = data_sp$age, y = data_sp$height_0, col = "darkseagreen4", lwd=2,type="l")
  points(x = data_sp_ind$age, y = data_sp_ind$height_0, col = "black")

  if (i %in% c(4,11)) {
    mtext("Height (mm)", 2, line=2, outer=FALSE)
  }

  #leaf area
  plot(NA, log = "x", xlim = c(1.4, 32), ylim=c(1,(max(data_sp$leaf_weight_0)*1.1)),xaxs = "i", yaxs = "i", xaxt="n", ylab="n")
  box()
  axis(1, labels = (i %in% c(7,14)))
  points(x = data_sp$age, y = data_sp$leaf_weight_0, col = "darkseagreen4", lwd=2,type="l")
  points(x = data_sp_ind$age, y = data_sp_ind$leaf_weight_0, col = "black")
  #points(x = data_sp_ind$age, y = data_sp_ind$leaf_weight_0, col = "black",cex=0.5,pch=16)
  #points(x = data_sp$age, y = data_sp$leaf_shed2, col = "darkseagreen4", lwd=2,type="l")
  #points(x = data_sp_ind$age, y = data_sp_ind$leaf_shed, col = "darkseagreen4")
  #points(x = data_sp$age, y = data_sp$growth_leaf, col = "darkseagreen2", lwd=2,type="l")
  mtext(labels.spp.full(all_species[i]), 3, 0)

  if (i %in% c(4,11)) {
    mtext("Standing leaf biomass (mg)", 2, line=2.5, outer=FALSE)
  }

  plot(NA, log = "x", xlim = c(1.4, 32), ylim=c(1,(max(data_sp$total_inv)*0.7)),xaxs = "i", yaxs = "i", xaxt="n", ylab="n")
  box()
  axis(1, labels = (i %in% c(7,14)))
  points(x = data_sp$age, y = data_sp$repro_inv, col = "coral3", lwd=2,type="l")
  #points(x = data_sp_ind$age, y = data_sp_ind$leaf_weight_0, col = "black",cex=0.5,pch=16)
  points(x = data_sp$age, y = data_sp$leaf_shed2, col = "darkseagreen4", lwd=2,type="l")
  #points(x = data_sp_ind$age, y = data_sp_ind$leaf_shed, col = "darkseagreen4")
  points(x = data_sp$age, y = data_sp$growth_leaf, col = "darkseagreen2", lwd=2,type="l")
  mtext(labels.spp.full(all_species[i]), 3, 0)

  if (i %in% c(4,11)) {
    mtext("Yearly investment (mg)", 2, line=2.5, outer=FALSE)
  }

  plot(NA, log = "xy", xlim = c((min(data_sp_ind$total_weight_0)*0.9),(max(data_sp_ind$total_weight_0)*1.1)), ylim=c(1,(max(data_sp_ind$total_inv)*0.7)),xaxs = "i", yaxs = "i", xaxt="n", ylab="n")
  box()
  axis(1, labels = (i %in% c(7,14)))
  points(x = data_sp_ind$total_weight_0, y = data_sp_ind$all_leaf_inv, col = "darkseagreen4", lwd=2,type="p",pch=1,cex=1.4)
  points(x = data_sp_ind$total_weight_0, y = data_sp_ind$repro_inv, col = "coral3", lwd=2,type="p",pch=1,cex=1.4)
  points(x = data_sp_ind$total_weight_0, y = data_sp_ind$growth_leaf_pos, col = "darkseagreen2", lwd=2,type="p",pch=1,cex=1.4)
  mtext(labels.spp.full(all_species[i]), 3, 0)

  if (i %in% c(4,11)) {
    mtext("Yearly investment (mg)", 2, line=2.5, outer=FALSE)
  }

  # #reproductive investment
  # plot(NA,xaxt="n",xlim = c(1.4, 32), ylim=c(1,(max(data_sp$repro_inv)*1.1)),log="x",xaxs = "i", yaxs = "i", xaxt="n", ylab="n")
  # polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$repro_inv, 0, 0), col = "coral3", density = NA)
  # axis(1, labels = (i %in% c(7,14)))
  # 
  # if (i %in% c(4,11)) {
  #   mtext("reproductive investment (mg)", 2, line=2.5, outer=FALSE)
  # }

  # #leaf lifespan
  # plot(NA,log = "x", ylim = c(0, 6),  xlim = c(1.2, 37), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
  # box()
  # axis(1, labels = (i %in% c(7,14)))
  # axis(2, at = c(0,2,4,6), labels = TRUE, las=1)
  # points(x = data_sp$age, y = data_sp$LL_death, col = "darkseagreen4", lwd=2,type="l")
  # points(x = data_sp_ind$age, y = data_sp_ind$LL_death, col = "black")
  # 
  # if (i %in% c(4,11)) {
  #   mtext("Leaf lifespan (yrs), based on leaf death", 2, line=2, outer=FALSE)
  # }
}
```

```{r}
#FIGURE 2
par(mfrow = c(7,3), cex = 1, oma = c(5, 5, 1, 1), mar = c(0, 3, 2, 1))

all_species <- unique(data$species)

for (i in seq_along(all_species)) {

  data_sp <- filter(data, species == all_species[i])
  m <- max(data_sp$age)
  n <- length(data_sp$age)

  #RA leaf area, max 1
  plot(NA, log = "x", ylim = c(0, 1),  xlim = c(1.4, 32), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
  box()
  axis(1, labels = (i %in% c(7,14)))
  axis(2, at = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = c(0,"","","","",1), las=1)
  polygon(x = c(1,m,m,1), y = c(1,1, 0, 0), col = "darkseagreen2", density = NA)
  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$RA_max_1, 0, 0), col = "coral3", density = NA)

  if (i %in% c(4,11)) {
    mtext("Proportional allocation to reproduction vs leaf growth", 2, line=2, outer=FALSE)
  }

  #RA leaf area, all leaf
  plot(NA, log = "x", ylim = c(0, 1),  xlim = c(1.4, 32), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
  box()
  axis(1, labels = (i %in% c(7,14)))
  axis(2, at = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = c(0,"","","","",1), las=1)
  polygon(x = c(1,m,m,1), y = c(1,1, 0, 0), col = "darkseagreen4", density = NA)
  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_surplus, 0, 0), col = "darkseagreen2", density = NA)
  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$RA_vs_all_leaf, 0, 0), col = "coral3", density = NA)
  mtext(labels.spp.full(all_species[i]), 3, 0)

  if (i %in% c(4,11)) {
    mtext("Proportional allocation to reproduction vs leaf growth + REPLACEMENT", 2, line=2, outer=FALSE)
  }

  #proportion different energy
  plot(NA, log = "x", ylim = c(0, 1),  xlim = c(1.4, 32), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
  box()
  axis(1, labels = (i %in% c(7,14)))
  axis(2, at = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = c(0,"","","","",1), las=1)

  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_stem, 0, 0), col = "burlywood4", density = NA)
  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_leaf_replacement, 0, 0), col = "darkseagreen4", density = NA)
  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_leaf_expand, 0, 0), col = "darkseagreen2", density = NA)
  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_repro, 0, 0), col = "coral3", density = NA)

  if (i %in% c(4,11)) {
    mtext("Proportional allocation to all energy sinks", 2, line=2, outer=FALSE)
  }
}
```

```{r}
#FIGURE 3
par(mfrow = c(7,4), cex = 1, oma = c(5, 5, 1, 1), mar = c(0, 3, 2, 1))

all_species <- unique(data$species)

for (i in seq_along(all_species)) {

  data_sp <- filter(data, species == all_species[i])
  data_sp_ind <- filter(data_ind, species == all_species[i])
  data_sp_no5 <- subset(data_sp,age!=5)
  m <- max(data_sp$age)
  n <- length(data_sp$age)

#panel 1
  plot(NA, log = "xy", xlim = c(1,(max(data_sp_ind$all_leaf_inv)*1.1)),  ylim = c(1,(max(data_sp_ind$repro_inv)*1.1)), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
  box()
  points(x = data_sp_ind$all_leaf_inv, y = data_sp_ind$repro_inv, col = "darkseagreen4", lwd=2,type="p",pch=1,cex=1.4)

#panel 2
  plot(NA, log = "xy", xlim = c(1,(max(data_sp_ind$growth_leaf_pos)*1.1)),  ylim = c(1,(max(data_sp_ind$repro_inv)*1.1)), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
  box()
  points(x = data_sp_ind$growth_leaf_pos, y = data_sp_ind$repro_inv, col = "darkseagreen4", lwd=2,type="p",pch=1,cex=1.4)

}
```

### 2016-12-12 R/Summaries.R

@@ -120,7 +120,7 @@ combine_by_individual <- function(IndividualsList, Growth_all, ReproductiveCosts
     shoot_growth_leaf_area = shoot_leaf_count_new*leaf_size,
     shoot_leaf_area_0 = shoot_leaf_area - shoot_growth_leaf_area,
     prop_shoot_growth_leaf_area = shoot_growth_leaf_area / shoot_leaf_area_0,
-    leaf_shed = leaf_weight_0 * LL_death,
+    leaf_shed = leaf_weight_0 / LL_death,
     leaf_inv_gross = leaf_shed + growth_leaf,
     growth_leaf_neg = growth_leaf,
     RA_leaf_area = repro_inv / (repro_inv + growth_leaf),
@@ -190,15 +190,20 @@ combine_by_individual <- function(IndividualsList, Growth_all, ReproductiveCosts
   
    SummaryInd <- SummaryInd %>% mutate(
      leaf_replacement = leaf_shed + growth_leaf_neg,
-     RA_max_1 = repro_inv / (growth_leaf_pos + repro_inv),
+     surplus_inv = repro_inv + growth_leaf_pos,
+     all_leaf_inv = leaf_replacement + growth_leaf_pos,
+     all_leaf_and_repro_inv = repro_inv + leaf_replacement + growth_leaf_pos,
+     RA_max_1 = repro_inv / surplus_inv,
      gross_inv = repro_inv + growth_leaf_pos + leaf_replacement + growth_stem,
      prop_repro = repro_inv/gross_inv,
-     prop_leaf_expand = (repro_inv + growth_leaf_pos)/gross_inv,
-     prop_leaf_replacement = (leaf_replacement + repro_inv + growth_leaf_pos)/gross_inv,
-     RA_vs_all_leaf = repro_inv / (leaf_replacement + growth_leaf_pos + repro_inv),
-     RA_seed = embryo_endo_inv / total_inv
-     prop_stem = 1
-   )
+     prop_leaf_expand = surplus_inv /gross_inv,
+     prop_leaf_replacement = all_leaf_and_repro_inv/gross_inv,
+     prop_surplus = surplus_inv / all_leaf_and_repro_inv,
+     RA_vs_all_leaf = repro_inv / all_leaf_and_repro_inv,
+     RA_seed = embryo_endo_inv / total_inv,
+     prop_stem = 1,
+     prop_leaf_replacement_vs_all_leaf = leaf_replacement / all_leaf_inv
+    )
   
[…]

### 2016-12-13 old/Accessory_figs_2016.Rmd
moving old accessory costs figures

#Figure 1. Correlations of various reproductive investment categories against plant weight
```{r}
win.metafile("figs2/Accessory_Costs/Figure01_correlations_with_plant_weight.wmf", height=9, width=13)
plot

par(mfrow=c(2,3), cex=1, omi=c(1,0.1,.1,0.05), mai=c(.2,.55,.1,0.1))
options(scipen = 2)

library(smatr)
xvar <- "total_weight_0"
yvar <- "repro_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",lty=results$linetype,xaxt="n",pch=20)
mod <- lm(log10(total_weight_0)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0))
words.top.left.logxy(mod)
mtext(text="total reproductive investment (mg)",side=2,line=2.3,outer=FALSE)

xvar <- "total_weight_0"
yvar <- "fruit_weight"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",lty=results$linetype,xaxt="n",yaxt="n",pch=20)
mod <- lm(log10(total_weight_0)~log10(fruit_weight),data=subset(SummaryInd,fruit_weight>0))
words.top.left.logxy(mod)
mtext(text="investment in fruit (mg)",side=2,line=0.6,outer=FALSE)

xvar <- "total_weight_0"
yvar <- "propagule_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",lty=results$linetype,xaxt="n",yaxt="n",pch=20)
mod <- lm(log10(total_weight_0)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0))
words.top.left.logxy(mod)
mtext(text="investment in propagules (mg)",side=2,line=0.6,outer=FALSE)
mtext(text="total plant weight (mg)",side=1,line=1.5,outer=TRUE)

xvar <- "total_weight_0"
yvar <- "prepollen_all_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=20,log="xy",xlim=c(10,10000000),ylim=c(1,1000000),xlab="",ylab="",lty=results$linetype)
mod <- lm(log10(total_weight_0)~log10(prepollen_all_inv),data=subset(SummaryInd,prepollen_all_inv>0))
words.top.left.logxy(mod)
mtext(text="investment in prepollination tissues (mg)",side=2,line=2.3,outer=FALSE)

xvar <- "total_weight_0"
yvar <- "repro_all_count"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit, pch=20, col = col.spp(fit$groupsummary$group),lty=results$linetype,xlim=c(10,10000000),ylim=c(1,1000000),xlab="total weight (mg)",ylab="repro all count",yaxt="n")
mtext(text="count of all reproductive units",side=2,line=0.6,outer=FALSE)

xvar <- "total_weight_0"
yvar <- "seed_count"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit, pch=20, col = col.spp(fit$groupsummary$group),lty=results$linetype,xlim=c(10,10000000),ylim=c(1,1000000),xlab="total weight (mg)",ylab="repro all count",yaxt="n")
mtext(text="seed count",side=2,line=0.6,outer=FALSE)
mtext(text="total plant weight (mg)",side=1,line=1.5,outer=TRUE)

dev.off()
```

#In other words, for many species, seed counts do not provide an accurate estimate of reproductive investment
```{r}
win.metafile("figs2/Accessory_Costs/Figure02_correlations_with_repro_inv.wmf", height=6, width=13)
plot

par(mfrow=c(1,3), cex=1, omi=c(1,0.4,.1,0.05), mai=c(.2,.4,.1,0.1))
options(scipen = 2)

yvar <- "repro_inv"
xvar <- "repro_all_count"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,xlab="",ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,ylim=c(2,300000))
mtext(text="propagule investment (mg)",side=1,line=2,outer=FALSE)
mtext(text="reproductive investment (mg)",side=2,line=1,outer=TRUE)
legend_with_r2(results,"bottomright")

write.csv(results, file="figs2/Accessory_Costs/Table01a_seed_count_vs_repro_inv.csv",row.names=FALSE)

yvar <- "repro_inv"
xvar <- "propagule_inv"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- fit$groupsummary
plot(fit,xlab=xvar,ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,yaxt="n",ylim=c(2,300000))
mtext(text="count of buds initiated",side=1,line=2,outer=FALSE)
legend_with_r2(results,"bottomright")

write.csv(results, file="figs2/Accessory_Costs/Table01b_repro_all_count_vs_repro_inv.csv",row.names=FALSE)

yvar <- "repro_inv"
xvar <- "diameter"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- fit$groupsummary
plot(fit,xlab=xvar,ylab="",pch=16, col=col.spp(fit$groupsummary$group),lty=results$linetype,yaxt="n",ylim=c(2,300000))
mtext(text="stem diameter (mm)",side=1,line=2,outer=FALSE)
legend_with_r2(results,"bottomright")

write.csv(results, file="figs2/Accessory_Costs/Table01c_diameter_vs_repro_inv.csv",row.names=FALSE)
dev.off()
```

#Appendix Fig 1. Correlations with leaf investment  
* if you change conditions to "growth_leaf>50" to remove those old individuals that are no longer replacing leaves, the correlations become ~2x as strong
```{r}
win.metafile("figs2/Accessory_Costs/Appendix01_correlations_with_leaf_investment.wmf", height=9, width=9)
plot

par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.1), mai=c(1.1,1,.3,0.1))
plot(propagule_inv~growth_leaf,data=subset(SummaryInd,propagule_inv>0&growth_leaf>0),col=col.spp(species),pch=16,log="xy")
mod <- lm(log10(growth_leaf)~log10(propagule_inv),data=subset(SummaryInd,propagule_inv>0&growth_leaf>0))
words.top.left.logxy(mod)

plot(fruit_weight~growth_leaf,data=subset(SummaryInd,fruit_weight>0&growth_leaf>0),col=col.spp(species),pch=16,log="xy")
mod <- lm(log10(growth_leaf)~log10(fruit_weight),data=subset(SummaryInd,fruit_weight>0&growth_leaf>0))
words.top.left.logxy(mod)

plot(repro_inv~growth_leaf,data=subset(SummaryInd,repro_inv>0&growth_leaf>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
mod <- lm(log10(growth_leaf)~log10(repro_inv),data=subset(SummaryInd,repro_inv>0&growth_leaf>0))
words.top.left.logxy(mod)

plot(prepollen_all_inv~growth_leaf,data=subset(SummaryInd,prepollen_all_inv>0&growth_leaf>0),col=col.spp(species),pch=16,log="xy",xlim=c(10,10000000),ylim=c(1,1000000))
mod <- lm(log10(growth_leaf)~log10(prepollen_all_inv),data=subset(SummaryInd,prepollen_all_inv>0&growth_leaf>0))
words.top.left.logxy(mod)

dev.off()
```

#Table showing accessory cost values for the species
```{r}
acc_costs_spp <- dplyr::select(SummarySpp[["mean"]],species,seed_size,seed_to_ovule_ratio,accessory_per_seed,total_accessory_Lord,prepollencosts,b_div_p,c_div_p,dispersalcosts_increment,dispersalcosts_increment2,prop_accessory_nonzero)
acc_costs_spp$species <- labels.spp.full()
acc_costs_spp <- format(acc_costs_spp, digit=2)

write.csv(acc_costs_spp, file="figs2/Accessory_Costs/Table02_AccCosts_by_Species.csv",row.names=FALSE)
```

#Figure 2 and Table 3. Scaling of accessory costs versus seed size, by species
```{r}
win.metafile("figs2/Accessory_Costs/Figure02_acc_cost_seed_size_4panel.wmf", height=8, width=12)
plot

par(mfrow=c(2,3), cex=1, omi=c(.5,.1,.1,.1), mai=c(.1,1,.3,.1)) 
options(scipen = 5)

plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",xaxt="n",cex=1.5)
mod <- lm(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
words.top.left.logxy(mod)
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$accessory_per_seed,SummarySpp[["se"]]$accessory_per_seed)
slopes <- sma(log10(accessory_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],slope.test=1))
abline(slopes$coef[[1]][1,1],slopes$coef[[1]][2,1])
abline(slopes$coef[[1]][1,1],1,col="red")
acc_by_species <- slopes$coef[[1]]
# 
# plot(b_div_p ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all pre-pollination accessory costs (mg/seed)",xlab="",xaxt="n",cex=1.5)
# mod <- lm(log10(b_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0))
# words.top.left.logxy(mod)
# y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$b_div_p,SummarySpp[["se"]]$b_div_p)
# slopes <- sma(log10(b_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],slope.test=1,groupsummary=TRUE))
# abline(slopes$coef[[1]][1,1],slopes$coef[[1]][2,1])
# abline(slopes$coef[[1]][1,1],1,col="red")
# acc_by_species <- dplyr::bind_rows(acc_by_species, slopes$coef[[1]])

plot(prepollencosts ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(prepollencosts) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
extra.topleft.logxy("slope <1, so bigger seeded species have lower fixed costs of making pre-pollination parts")
slopes <- sma(log10(prepollencosts) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
abline(slopes$coef[[1]][1,1],slopes$coef[[1]][2,1])
abline(slopes$coef[[1]][1,1],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, slopes$coef[[1]])

plot(prepollen_failure_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen failure costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(prepollen_failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]))
words.bottom.right.logxy(mod)
extra.topleft.logxy("the per seed costs of failure scale isometrically with seed size")
slopes <- sma(log10(prepollen_failure_per_seed) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
abline(slopes$coef[[1]][1,1],slopes$coef[[1]][2,1])
abline(slopes$coef[[1]][1,1],1,col="red")
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$prepollen_failure_per_seed,SummarySpp[["se"]]$prepollen_failure_per_seed)
acc_by_species <- dplyr::bind_rows(acc_by_species, slopes$coef[[1]])

plot(c_div_p ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted fruit accessory costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
mod <- lm(log10(c_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],accessory_per_seed>0&species!="COER"&species!="BAER"))
words.top.left.logxy(mod)
y.error.bars(SummarySpp[["mean"]]$seed_size,SummarySpp[["mean"]]$c_div_p,SummarySpp[["se"]]$c_div_p)
slopes <- sma(log10(c_div_p) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),slope.test=1)
abline(slopes$coef[[1]][1,1],slopes$coef[[1]][2,1])
abline(slopes$coef[[1]][1,1],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, slopes$coef[[1]])

plot(dispersalcosts_increment ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
mod <- lm(log10(dispersalcosts_increment) ~ log10(seed_size),data=subset(SummarySpp[["mean"]],species!="LEES"))
words.top.left.logxy(mod)
slopes <- sma(log10(dispersalcosts_increment) ~ log10(seed_size),data=subset(SummarySpp[["mean"]]),slope.test=1)
abline(slopes$coef[[1]][1,1],slopes$coef[[1]][2,1])
abline(slopes$coef[[1]][1,1],1,col="red")
acc_by_species <- dplyr::bind_rows(acc_by_species, slopes$coef[[1]])

acc_by_species$names = c("intercept","slope","intercept","slope","intercept","slope","intercept","slope","intercept","slope")
acc_by_species$variable = c("acc cost","acc cost","prepollen_success","prepollen_success","prepollen_failure","prepollen_failure","c div p","c div p","dispersal","dispersal")

write.csv(acc_by_species, file="figs2/Accessory_Costs/Table03_acc_by_species.csv",row.names=FALSE)

mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)

dev.off()
```

```{r}
win.metafile("figs2/Accessory_Costs/Figure_seedset_vs_seedsize.wmf", height=5, width=5)
plot

par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5)) 
plot(seedset~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=2)
mod <- lm(log10(seed_size)~log10(seedset),data=subset(SummarySpp[["mean"]]))
#abline(mod$coefficients[1],mod$coefficients[2])
words.top.left.logxy(mod)

dev.off()
```

#Table 4 and Figure 3.Per seed accessory costs are lower in individuals with higher seed count. 
###This effect is true across species, since larger-seeded species produce fewer seeds and have higher per seed accessory costs and true within species, since absolute accessory investment is a function of plant size not seedset
```{r}
win.metafile("figs2/Accessory_Costs/Figure_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
plot

par(mfrow=c(1,1), cex=1, omi=c(1,1,.1,.1), mai=c(1,1,.5,.5))

xvar <- "seed_count"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)

points(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seed_count>0),col="black",pch=16,cex=2.5)
points(accessory_per_seed~seed_count,data=subset(SummarySpp[["mean"]],accessory_per_seed>0&seed_count>0),col=col.spp(species),pch=16,cex=2)
mod <- lm(log10(accessory_per_seed)~log10(seed_count),data=subset(SummarySpp[["mean"]]))
words.top.right.logxy(mod)
legend_with_r2(results,"bottomleft")

results
write.csv(results, file="figs2/Accessory_Costs/Table04a_seedcount_vs_accessory.csv",row.names=FALSE)

dev.off()
```

#Table 4 extra - showing propagule investment instead of seed_count. Could also replace with seedset
```{r}
win.metafile("figs2/Accessory_Costs/Figure_acc_cost_by_seedset.wmf", height=9, width=9)
plot

par(mfrow=c(2,2), cex=1, omi=c(.5,.1,.1,.1), mai=c(.1,1,.3,.1))

xvar <- "seedset"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="total accessory costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000),xaxt="n")
legend_with_r2(results,"bottomleft")

write.csv(results, file="figs2/Accessory_Costs/Table04b_seedset_vs_accessory.csv",row.names=FALSE)

xvar <- "seedset"
yvar <- "b_div_p"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab="b div p = pre-pollination costs (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000),xaxt="n")
legend_with_r2(results,"bottomleft")

write.csv(results, file="figs2/Accessory_Costs/Table06a_b_div_p_vs_seedset.csv",row.names=FALSE)

xvar <- "seedset"
yvar <- "c_div_p"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy") 
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab="c div p = aborted post pollination (mg/seed)",lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000))
legend_with_r2(results,"bottomleft")

write.csv(results, file="figs2/Accessory_Costs/Table06b_c_div_p_vs_seedset.csv",row.names=FALSE)

xvar <- "seedset"
yvar <- "packaging_dispersal_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(results$group),pch=16,xlab="",ylab=yvar,lty=results$linetype,xlim=c(.0005,.5),ylim=c(.01,200000))
legend_with_r2(results,"bottomleft")
mtext(text="seedset",side=1,line=1.5,outer=TRUE)

dev.off()
```

```{r}
xvar <- "seedset"
yvar <- "packaging_dispersal_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)

results <- select(results,group,r2)
names(results) <- c("species","r2")

results$ovules_per_fruit <- c(60,4,1,1,2,2,2,4,1,40,2,20,2)
max_seedset <- select(SummarySpp[["max"]],species,seedset) 
min_seedset <- select(SummarySpp[["min"]],species,seedset) 
results <- merge(results, max_seedset, by=c("species"), all=TRUE)
results <- merge(results, min_seedset, by=c("species"), all=TRUE)
names(results)=c("species","r2","ovules_per_fruit","max_seedset","min_seedset")

win.metafile("figs2/Accessory_Costs/Table07_dispcosts_vs_ovules.wmf", height=6, width=6)
plot

par(mfrow=c(1,1), cex=1, omi=c(.4,.4,.1,.1), mai=c(.8,.8,.2,.2)) 
plot(ovules_per_fruit~r2,data=subset(results,species!="PELA"),log="y",col=col.spp(species),pch=16,cex=2,xlab="ovules per fruit",ylab="strength of correlation between dispersal costs and seedset")
mod <- lm(r2~log10(ovules_per_fruit),data=subset(results,species!="PELA"))
words.bottom.right.logy(mod)
dev.off()

write.csv(results, file="figs2/Accessory_Costs/Table06c_dispersal_vs_seedset.csv",row.names=FALSE)
```

#Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
##Not a single species shows a reduction in per seed accessory costs with increased plant size.Indeed, EPMI has higher pre-pollination accessory costs    (slope = 0.38, r2=0.19, p=0.019) and accessory costs due to aborted fruit and seeds (slope = 0.83, r2=0.268, p=0.019) in larger individuals, as larger individuals of this species have lower seedset (slope = -0.31, r2=0.198, p=0.018). GRSP also has a nearly significant decline in seedset in larger individuals (slope = -0.78, r2=0.298, p=0.067).
```{r}
win.metafile("figs2/Accessory_Costs/Figure_RE_RA_size_age_patterns.wmf", height=8, width=8)
plot

par(mfrow=c(2,2), cex=1, omi=c(.1,0.4,.1,0.05), mai=c(.6,.3,.1,0.1))
options(scipen = 2)

xvar <- "repro_inv"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
legend_with_r2(results,"bottomright")

write.csv(results, file="figs2/Accessory_Costs/Table05a_accessory_vs_RE.csv",row.names=FALSE)

xvar <- "RA"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0&SummaryInd$age>2)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
mtext(text="RA",side=1,line=2,outer=FALSE)
legend_with_r2(results,"topleft")

write.csv(results, file="figs2/Accessory_Costs/Table05b_accessory_vs_RA.csv",row.names=FALSE)

xvar <- "total_weight_0"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
legend_with_r2(results,"bottomright")

write.csv(results, file="figs2/Accessory_Costs/Table05c_accessory_vs_total_weight.csv",row.names=FALSE)

xvar <- "age"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
mtext(text="age (years)",side=1,line=2,outer=FALSE)
mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
legend_with_r2(results,"topleft")

write.csv(results, file="figs2/Accessory_Costs/Table05d_accessory_vs_age.csv",row.names=FALSE)
dev.off()
```

#Considering the individual components of accessory costs vs. seedset - since seedset best predictor of accessory costs

#For each species the accessory cost components that cause shifts in total accessory costs is different and reflects both which components are largest and whichvary most with some factor - seedset, age, etc.
```{r}
xvar1 <- "packaging_dispersal_per_seed"
xvar2 <- "b_div_p"
xvar3 <- "c_div_p"
yvar <- "accessory_per_seed"
data <- subset(SummaryInd,SummaryInd[[xvar1]]>0&SummaryInd[[xvar2]]>0&SummaryInd[[xvar3]]>0)
data <- split(data, data$species)

mod <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar1]]))+(log10(x[[xvar2]]))+(log10(x[[xvar3]]))))

species_coef <- as.data.frame(c("intercept","packaging&dispersal","b_div_p","c_div_p"))

species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[1]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[2]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[3]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[4]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[5]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[6]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[7]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[8]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[9]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[10]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[11]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[12]]$coefficients))
species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[13]]$coefficients))
#species_coef <- dplyr::bind_cols(species_coef, as.data.frame(mod[[14]]$coefficients))
names(species_coef) <- c("effect","BAER","BOLE","COER","EPMI","GRBU","GRSP","HATE","HEPU","PELA","PEPU","PHPH","PILI","PUTU")

write.csv(species_coef, file="figs2/Accessory_Costs/Table08_breaking_down_accessory_costs_spp.csv",row.names=FALSE)
```

#looking at how the slopes of the relationship between accessory investment and propagule investment shift across species 
##slopes only statistically different from 1 in 2 species
##intercepts quite variable - means that the "baseline" accessory investment, before you get any propagules varies
```{r}
par(mfrow=c(1,1), cex=1, omi=c(.2,.2,.1,.1), mai=c(1,1,.1,.1)) 
plot(propagule_inv~accessory_inv,data=subset(SummaryInd,accessory_inv>0&propagule_inv>0),col=col.spp(species),pch=16,log="xy",xlab="total accessory investment (mg)",ylab="total propagule investment (mg)")
slope_check <- sma(log10(propagule_inv)~ log10(accessory_inv),data=subset(SummaryInd,propagule_inv>0))
summary(slope_check)

data <- select(SummaryInd,species,propagule_inv,accessory_inv)
data <- subset(data,propagule_inv>0)
data <- split(data, data$species)

for(i in 1:14) {
slope_check <- sma(log10(propagule_inv)~ log10(accessory_inv),data[[i]],slope.test=1)
summary(slope_check)
}

xvar <- "accessory_inv"
yvar <- "propagule_inv"

data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab=xvar,ylab=yvar,lty=results$linetype)
```

```{r}
win.metafile("figs2/Accessory_Costs/Figure_success_vs_failure.wmf", height=6, width=8)
plot

par(mfrow=c(1,2), cex=1, omi=c(.8,.1,.1,.1), mai=c(.1,.8,.1,.1))

xvar <- "repro_inv"
yvar <- "prop_propagule"

data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,lty=results$linetype,ylim=c(.001,1),xlab="",ylab="prop repro energy to propagules")
abline(-0.30103,0,lwd=2)
abline(-1,0,lwd=2)

xvar <- "repro_inv"
yvar <- "percent_for_success"

data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
results <- lines(fit$groupsummary)
plot(fit,col=col.spp(fit$groupsummary$group),pch=16,lty=results$linetype,ylim=c(.001,1),xlab="",ylab="prop repro energy to success")
abline(-0.30103,0,lwd=2)
abline(-1,0,lwd=2)
mtext(text="reproductive investment (mg)",side=1,line=2,outer=TRUE)

dev.off()
```

#species with bigger seeds, lower seedset spend less per flower. Here taking the percent of the cost to make a single flower that goes into pre-pollination parts
```{r}
win.metafile("figs2/Accessory_Costs/Figure_costs_to_make_1_seed.wmf", height=4, width=12)
plot

par(mfrow=c(1,3), cex=1, omi=c(.8,0.1,.1,0.05), mai=c(.1,.8,.1,0.1))

plot(seedcosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="all costs to make 1 seed (mg) = seedcosts")
mod <- lm(log10(seed_size)~log10(seedcosts),data=subset(SummarySpp[["mean"]]))
extra.topleft.logxy("total accessory costs required to produce 1 seed are lower for smaller seeded species")
words.bottom.left.logxy(mod)

plot(percent_prepollencosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for prepollination")
extra.topleft.logxy("species with big seeds have low costs of producing a single flower")
mod <- lm(log10(seed_size)~log10(percent_prepollencosts),data=subset(SummarySpp[["mean"]]))
words.bottom.left.logxy(mod)

plot(percent_dispersalcosts~seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5,xlab="",ylab="prop seedcosts for dispersal")
extra.topleft.logxy("species with big seeds have high packaging and dispersal costs")
mod <- lm(log10(seed_size)~log10(percent_dispersalcosts),data=subset(SummarySpp[["mean"]],percent_dispersalcosts>0))
words.bottom.left.logxy(mod)
mtext(text="seed size (mg)",side=1,line=2,outer=TRUE)

dev.off()
```

### 2016-12-13 scripts/starting_commands.R

@@ -9,7 +9,6 @@ PartsSummary <- readRDS("export/PartsSummary_all.rds")
 
 library(digest)
 library(Rcpp)
-library(cmnormt)
 library(reshape2)
 library(tibble)
 library(smatr)

### 2016-12-13 Analaysis-RA.Rmd
Restructure materials for MS into folders
ignore generated figures
keep current version in single directory

--- 2016-12-12 RA_figs.Rmd
@@
 # pdf('ms/RA/Figure_1_stacked_lines.pdf', height=11.5, width=8) plot
+
+SummarySppAge[["mean"]]$leaf_shed_mean <- SummaryInd %>%
+        group_by(species,age) %>%
+        summarise(mean(leaf_shed_mean))
+
+SummarySppAge[["mean"]]$leaf_replacement_mean <- SummaryInd %>%
+        group_by(species,age) %>%
+        summarise(mean(leaf_replacement_mean))
 
@@
   growth_stem, leaf_shed,prop_stem,prop_leaf_replacement,prop_leaf_expand,prop_repro,RA_max_1,lifespan,height, RA_vs_all_leaf,
-  LL_death,height_0,total_weight_0,all_leaf_inv)
+  LL_death,height_0,total_weight_0,all_leaf_inv,surplus_inv,all_leaf_and_repro_inv,propagule_inv,ovule_count,success_inv)
 data$leaf_shed2 <- data$leaf_weight_0 / data$LL_death
-data_ind <- select(SummaryInd,species,individual,age, LL_death,height_0,leaf_shed,leaf_weight_0,
-                   growth_leaf_pos,repro_inv,total_weight_0,all_leaf_inv,total_inv,surplus_energy)
+data_ind <- select(SummaryInd,species,individual,age, LL_death,height_0,leaf_shed,leaf_weight_0,propagule_inv,ovule_count,
+                   growth_leaf_pos,repro_inv,total_weight_0,all_leaf_inv,total_inv,surplus_inv,all_leaf_and_repro_inv,age,success_inv)
 
@@
   axis(1, labels = (i %in% c(7,14)))
-  points(x = data_sp_ind$total_weight_0, y = data_sp_ind$all_leaf_inv, col = "darkseagreen4", lwd=2,type="p",pch=1,cex=1.4)
-  points(x = data_sp_ind$total_weight_0, y = data_sp_ind$repro_inv, col = "coral3", lwd=2,type="p",pch=1,cex=1.4)
-  points(x = data_sp_ind$total_weight_0, y = data_sp_ind$growth_leaf_pos, col = "darkseagreen2", lwd=2,type="p",pch=1,cex=1.4)
+  points(x = data_sp_ind$leaf_weight_0, y = data_sp_ind$all_leaf_inv, col = "darkseagreen4", lwd=2,type="p",pch=1,cex=1.4)
+  points(x = data_sp_ind$leaf_weight_0, y = data_sp_ind$repro_inv, col = "coral3", lwd=2,type="p",pch=1,cex=1.4)
+  points(x = data_sp_ind$leaf_weight_0, y = data_sp_ind$growth_leaf_pos, col = "darkseagreen2", lwd=2,type="p",pch=1,cex=1.4)
   mtext(labels.spp.full(all_species[i]), 3, 0)
@@
 #FIGURE 2
-par(mfrow = c(7,3), cex = 1, oma = c(5, 5, 1, 1), mar = c(0, 3, 2, 1))
+par(mfrow = c(7,4), cex = 1, oma = c(5, 5, 1, 1), mar = c(0, 3, 2, 1))
 
@@
   #proportion different energy
-  plot(NA, log = "x", ylim = c(0, 1),  xlim = c(1.4, 32), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
-  box()
-  axis(1, labels = (i %in% c(7,14)))
-  axis(2, at = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = c(0,"","","","",1), las=1)
-
-  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_stem, 0, 0), col = "burlywood4", density = NA)
-  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_leaf_replacement, 0, 0), col = "darkseagreen4", density = NA)
-  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_leaf_expand, 0, 0), col = "darkseagreen2", density = NA)
-  polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_repro, 0, 0), col = "coral3", density = NA)
-
-  if (i %in% c(4,11)) {
-    mtext("Proportional allocation to all energy sinks", 2, line=2, outer=FALSE)
-  }
+  # plot(NA, log = "x", ylim = c(0, 1),  xlim = c(1.4, 32), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
+  # box()
+  # axis(1, labels = (i %in% c(7,14)))
+  # axis(2, at = c(0, 0.2, 0.4, 0.6, 0.8, 1), labels = c(0,"","","","",1), las=1)
+  # 
+  # 
+  # polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_stem, 0, 0), col = "burlywood4", density = NA)
+  # polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_leaf_replacement, 0, 0), col = "darkseagreen4", density = NA)
+  # polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_leaf_expand, 0, 0), col = "darkseagreen2", density = NA)
+  # polygon(x = data_sp$age[c(1:n, n, 1)], y = c(data_sp$prop_repro, 0, 0), col = "coral3", density = NA)
+  # 
+  # if (i %in% c(4,11)) {
+  #   mtext("Proportional allocation to all energy sinks", 2, line=2, outer=FALSE)
+  # }
 }
@@
 #panel 1
-  plot(NA, log = "xy", xlim = c(1,(max(data_sp_ind$all_leaf_inv)*1.1)),  ylim = c(1,(max(data_sp_ind$repro_inv)*1.1)), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
-  box()
-  points(x = data_sp_ind$all_leaf_inv, y = data_sp_ind$repro_inv, col = "darkseagreen4", lwd=2,type="p",pch=1,cex=1.4)
+ plot(repro_inv ~ leaf_weight_0,data_sp_ind,log="xy",pch=16,xaxt="n")
+ points(repro_inv ~ growth_leaf_pos,data_sp_ind,log="xy",pch=16,xaxt="n",col="darkseagreen4")
+ points(repro_inv ~ all_leaf_inv,data_sp_ind,log="xy",pch=16,xaxt="n",col="darkseagreen2")
+ abline(0,1)
+ mtext(labels.spp.full(all_species[i]), 3, 0)
+
+ plot(ovule_count ~ leaf_weight_0,data_sp_ind,log="xy",pch=16,xaxt="n",col=col.age(age))
+ #points(leaf_weight_0 ~ ovule_count,data_sp_ind,log="xy",pch=1,xaxt="n",col=col.age(age))
+ #points(surplus_inv ~ leaf_weight_0,data_sp_ind,log="xy",pch=14,xaxt="n",col=col.age(age))
+ #points(repro_inv ~ growth_leaf_pos,data_sp_ind,log="xy",pch=16,xaxt="n",col="darkseagreen4")
+ #points(repro_inv ~ all_leaf_inv,data_sp_ind,log="xy",pch=16,xaxt="n",col="darkseagreen2")
+ abline(0,1)
+ mtext(labels.spp.full(all_species[i]), 3, 0)
 
 #panel 2
-  plot(NA, log = "xy", xlim = c(1,(max(data_sp_ind$growth_leaf_pos)*1.1)),  ylim = c(1,(max(data_sp_ind$repro_inv)*1.1)), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
-  box()
-  points(x = data_sp_ind$growth_leaf_pos, y = data_sp_ind$repro_inv, col = "darkseagreen4", lwd=2,type="p",pch=1,cex=1.4)
+ #  plot(all_leaf_and_repro_inv ~ leaf_weight_0,data_sp_ind,log="xy",pch=16,xaxt="n")
+ # points(surplus_inv ~ total_weight_0,data_sp_ind,log="xy",pch=16,xaxt="n",col="darkseagreen2")
+ # abline(0,1)
+ # mtext(labels.spp.full(all_species[i]), 3, 0)
 
@@
 ```
+
+```{r}
+yvar <- "repro_inv"
+xvar <- "leaf_weight_0"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=1)
+results <- fit$groupsummary
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=3)
+acc_slopes <- dplyr::select(results,group,n,r2,pval)
+names(acc_slopes) <- c("species","n_leaf_weight","r2_leaf_weight","p_leaf_weight")
+
+yvar <- "repro_inv"
+xvar <- "growth_leaf_pos"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=1)
+results <- fit$groupsummary
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=3)
+acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
+names(acc_slopes2) <- c("species","n_growth_leaf","r2_growth_leaf","p_growth_leaf")
+acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
+
+yvar <- "repro_inv"
+xvar <- "all_leaf_inv"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=1)
+results <- fit$groupsummary
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=3)
+acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
+names(acc_slopes2) <- c("species","n_all_leaf_inv","r2_all_leaf_inv","p_all_leaf_inv")
+acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
+
+acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+
+write.csv(acc_slopes, file="ms/RA/Table_XX_best_predictor_repro_inv.csv",row.names=FALSE)
+```
+
+```{r}
+yvar <- "surplus_inv"
+xvar <- "leaf_weight_0"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=1)
+results <- fit$groupsummary
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=3)
+acc_slopes <- dplyr::select(results,group,n,r2,pval)
+names(acc_slopes) <- c("species","n_lsurplus","r2_surplus","p_surplus")
+
+yvar <- "all_leaf_and_repro_inv"
+xvar <- "leaf_weight_0"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=1)
+results <- fit$groupsummary
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=3)
+acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
+names(acc_slopes2) <- c("species","n_leaf_and_repro","r2_leaf_and_repro","p_leaf_and_repro")
+acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
+
+yvar <- "all_leaf_inv"
+xvar <- "leaf_weight_0"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=1)
+results <- fit$groupsummary
+results$r2 <- format(results$r2,digits=2)
+results$pval <- format(results$pval,digits=3)
+acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
+names(acc_slopes2) <- c("species","n_all_leaf_inv","r2_all_leaf_inv","p_all_leaf_inv")
+acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
+
+acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+
+write.csv(acc_slopes, file="ms/RA/Table_XX_best_predictor_leaf_weight.csv",row.names=FALSE)
+```
+
+yvar <- "ovule_count"
+xvar <- "leaf_weight_0"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=1)
+results <- fit$groupsummary
+results

### 2016-12-13 Analysis-accessory.Rmd
Restructure materials for MS into folders
ignore generated figures
keep current version in single directory

--- 2016-11-29 scripts/Accessory_figs_20160905.Rmd
@@
-plot(seedset~scaled_provisioning_costs,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),yaxt="n",xaxt="n",ylab="",xlab="",cex=1)
+```{r}
+library(digest)
+library(Rcpp)
+library(reshape2)
+library(tibble)
+library(smatr)
+library(broom)
+library(dplyr)
+library(stats)
+library(scales)
+library(colorspace)
 
-mod_ovule <- sma(choosiness~prop_pollen_attract_vs_success,data=SummarySpp[["mean"]],log="xy",method="SMA")
+remake::make("export")
 
-axis(2, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8,las=2)
-axis(1, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=0.8)
-mtext("costs to make a successful unit",1,line=1.8,cex=0.7)
-mtext("count, scaled to leaf area",2,line=2.3,cex=0.7)
+SummaryInd <- readRDS("export/SummaryInd.rds")
+SummarySpp <- readRDS("export/SummarySpp.rds")
+SummarySppAge <- readRDS("export/SummarySppAge.rds")
+HarvestData <- readRDS("export/HarvestData.rds")
+InvestmentByPart <- readRDS("export/Investment_FD_all.rds")
+PartsSummary <- readRDS("export/PartsSummary_all.rds")
 
-mod_x <- sma(accessory_inv~embryo_endo_inv,data=SummarySpp[["mean"]],log="xy",method="SMA")
-mod_x <- sma(accessory_costs~embryo_endo_costs,data=SummarySpp[["mean"]],log="xy",method="SMA")
-plot(zygote_set~embryo_endo_costs,SummaryInd,pch=16,log="x",col=col.spp(species),cex=1)
+source("R/figures.R")
+```
 
@@
 
-write.csv(acc_costs_spp_format, file="ms/Accessory/Table01_AccCosts_by_Species.csv",row.names=FALSE)
+write.csv(acc_costs_spp_format, file="ms/Accessory/output/Table01_AccCosts_by_Species.csv",row.names=FALSE)
 ```
@@
 ```{r}
-win.metafile("ms/Accessory/Table01_dots.wmf", height=3, width=.2)
-plot
+png("ms/Accessory/output/Table01_dots.png", height=3, width=.2, units="in", res=300)
 
@@
 plot(y~x,dots,cex=1.5,pch=16,xlab="",ylab="",xaxt="n",yaxt="n",col=col.spp(dots$species),bty="n",xlim=c(0.8,1.2),ylim=c(1.8,28.2))
-
 dev.off()
 ```
-summary(slopes)
 
@@
 
-write.csv(acc_slopes, file="ms/Accessory/Table02_acc_cost_embryo_size_slopes.csv",row.names=FALSE)
-```
-
-#Table Supplementary.correlations between repro inv and propagule inv by species
-```{r}
-mod_propagule_inv_all <- sma(repro_inv~propagule_inv,data=SummaryInd,log="xy",method="SMA")
-mod_propagule_inv_all
-
-mod_flower_inv_all <- sma(repro_inv~flower_inv,data=SummaryInd,log="xy",method="SMA")
-mod_flower_inv_all
-
-yvar <- "repro_inv"
-xvar <- "propagule_inv"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=mod_propagule_inv_all$groupsummary["Slope"][[1]],elev.test=mod_propagule_inv_all$coef[[1]][1,1])
-results <- fit$groupsummary
-results$r2 <- format(results$r2,digits=2)
-results$pval <- format(results$pval,digits=3)
-acc_slopes <- dplyr::select(results,group,n,r2,pval)
-names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule")
-
-yvar <- "repro_inv"
-xvar <- "flower_inv"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
-results <- fit$groupsummary
-results$r2 <- format(results$r2,digits=2)
-results$pval <- format(results$pval,digits=3)
-acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
-names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
-acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
-acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-
-write.csv(acc_slopes, file="ms/Accessory/Table_SXX_propagule_invest_vs_all_repropro_inv.csv",row.names=FALSE)
+write.csv(acc_slopes, file="ms/Accessory/output/Table02_acc_cost_embryo_size_slopes.csv",row.names=FALSE)
 ```
@@
 
-write.csv(results, file="ms/Accessory/Table03_correlations_with_repro_inv.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/output/Table03_correlations_with_repro_inv.csv",row.names=FALSE)
 ```
@@
 ```{r}
-win.metafile("ms/Accessory/Figure01b&c_predictions.wmf", height=3, width=6)
-plot
-
+png("ms/Accessory/output/Figure01b&c_predictions.png", height=3, width=6, units="in", res=300)
 par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
@@
 
-win.metafile("ms/Accessory/Figure01def_predictions.wmf", height=6, width=6)
-plot
+png("ms/Accessory/output/Figure01def_predictions.png", height=6, width=6, units="in", res=300)
 
@@
 ```{r}
-win.metafile("ms/Accessory/Figure02.wmf", height=9, width=6)
-plot
+png("ms/Accessory/output/Figure02.png", height=9, width=6, units="in", res=300)
 
@@
 
-#Figure 2 OLD. Scaling of accessory costs versus weight of embryo + endosperm, by species
-```{r}
-win.metafile("ms/Accessory_Costs/Figure02_embryo_size_acc_cost_correlations.wmf", height=9, width=10)
-plot
-
-par(mfrow=c(2,2), cex=1, omi=c(1,.1,.05,.05), mai=c(.2,.8,.1,.05)) 
-options(scipen = 5)
-
-plot((ovule_count/seed_count)~prop_pollen_attract_vs_all_repro_all_repro,SummarySpp[["mean"]],pch=16,log="xy",col=col.spp(species),ylab="",ylim=c(.8,500),yaxt="n",xlim=c(.0015,.5),xaxt="n")
-axis(2, at=c(1,10,100), labels=c(1,10,100),cex.axis=1)
-axis(1, at=c(0.001,0.005,0.01,0.05,0.1,0.5), labels=c(0.001,0.005,0.01,0.05,0.1,0.5),cex.axis=1)
-mtext("choosiness (ovules initiated per seed matured)",2,line=2.3)
-mtext("proportion reproductive investment for successful pollen attraction costs",1,line=2.3)
-
-mod_choosy <- sma((ovule_count/seed_count)~prop_pollen_attract_vs_all_repro_all_repro,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
-
-line_function_log_xy(SummarySpp[["mean"]]$prop_pollen_attract_vs_all_repro_all_repro,mod_choosy,1)
-summary(mod_choosy)
-
-plot(seedset~embryo_endo_costs,SummarySpp[["mean"]],log="xy",col=col.spp(species),pch=16, xlim=c(.002,500),ylim=c(.004,.6),cex=1.5,xaxt="n",xlab="",ylab="")
-mod <- sma(seedset~embryo_endo_costs,SummarySpp[["mean"]],log="xy", method="SMA")
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$seedset,SummarySpp[["se"]]$seedset)
-#text((10^(0.99*(par("usr")[2]-par("usr")[1])+par("usr")[1])),(10^(0.97*(par("usr")[4]-par("usr")[3])+par("usr")[3])),paste("r2 = ",round(sma_sum(mod)[1],2)),adj=1)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod,1)
-axis(1, at=c(0.01,1,100), labels=c("","",""),cex.axis=1)
-mtext("seed set",2,line=2.3)
-extra.top.left.logxy("b",2,1.2)
-summary(mod)
-
-plot(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="xy", yaxt="n",xaxt="n", ylim=c(.02,5000), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
-
-points(provisioning_costs~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=21,cex=1.5)
-y.error.bars.2(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)
-
-axis(2, at=c(0.1,10,1000), labels=c(0.1,10,1000),cex.axis=1)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
-mtext("costs (mg/ovule)",2,line=2.3)
-
-mod_prepollen <- sma(pollen_attract_costs~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA")
-mod_provision <- sma(postpollen_all_per_seed~embryo_endo_costs,SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_prepollen$groupsummary["Slope"][[1]])
-
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_prepollen,1)
-line_function_log_xy(SummarySpp[["mean"]]$embryo_endo_costs,mod_provision,2)
-
-legend("topright",legend=c("pollen attraction","provisioning"),col=c("black","black"),pch=c(16,21),bty="n")
-extra.top.left.logxy("c",2,1.2)
-
-plot(prop_pollen_attract_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-points(prop_prepollen_all_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
-axis(2, at=c(0,.5,1), labels=c(0,0.5,1.0),cex.axis=1)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
-extra.top.left.logx("d",2,1.2)
-
-mod_prop_pollen_attract_vs_all_repro <- sma(prop_pollen_attract_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
-mod_prop_prepollen_all_vs_all_repro <- sma(prop_prepollen_all_vs_all_repro~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA",slope.test=0)
-
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_pollen_attract_vs_all_repro,1)
-
-summary(mod_prop_pollen_attract_vs_all_repro)
-summary(mod_prop_prepollen_all_vs_all_repro)
-
-plot(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=16,log="x", yaxt="n",xaxt="n", ylim=c(0,1), xlim=c(.002,500), ylab="",xlab="",cex=1.5)
-points(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],col=col.spp(species),pch=1,cex=1.5)
-axis(2, at=c(0,.5,1), labels=c(0,0.5,1.0),cex.axis=1)
-axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=1)
-extra.top.left.logx("d",2,1.2)
-
-mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA")
-mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_costs,SummarySpp[["mean"]],log="x",method="SMA")
-
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_postpollen_success,1)
-line_function_log_x(SummarySpp[["mean"]]$embryo_endo_costs,mod_prop_prepollen_success,3)
-
-summary(mod_prop_postpollen_success)
-summary(mod_prop_prepollen_success)
-
-mtext(text="     seed size (mg)",side=1,line=1.5,outer=TRUE,adj=0.5)
-mtext(text="                     parental pessimist",line=3,side=1,adj=0,outer=TRUE,font=3)
-mtext(text="parental optimist    ",line=3,side=1,adj=1,outer=TRUE,font=3)
-
-dev.off()
-```
-
 #Figure 3. Correlations of various reproductive investment categories against plant weight
 ```{r}
-win.metafile("ms/Accessory/Figure03_correlations_with_plant_weight.wmf", height=5, width=10)
-plot
+png("ms/Accessory/output/Figure03_correlations_with_plant_weight.png", height=5, width=10, units="in", res=300)
 
@@
 ```{r}
-win.metafile("ms/Accessory/Figure_SXX_RE_RA_size_age_patterns.wmf", height=10, width=10)
-plot
+png("ms/Accessory/output/Figure_SXX_RE_RA_size_age_patterns.png", height=10, width=10, units="in", res=300)
 
@@
 
-write.csv(results, file="ms/Accessory/Table05a_accessory_vs_all_repro.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/output/Table05a_accessory_vs_all_repro.csv",row.names=FALSE)
 
@@
 
-write.csv(results, file="ms/Accessory/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/output/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)
 
@@
 
-write.csv(results, file="ms/Accessory/Table05c_accessory_vs_age.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/output/Table05c_accessory_vs_age.csv",row.names=FALSE)
 dev.off()
@@
 
-write.csv(acc_slopes, file="ms/Accessory/Table_S1_extra_flower_invest_vs_all_repro_inv.csv",row.names=FALSE)
+write.csv(acc_slopes, file="ms/Accessory/output/Table_S1_extra_flower_invest_vs_all_repro_inv.csv",row.names=FALSE)
 ```
@@
 
-write.csv(results, file="ms/Accessory_Costs/Table07_EXTRA_correlations_with_repro_inv.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/output/output/Table07_EXTRA_correlations_with_repro_inv.csv",row.names=FALSE)
 ```
@@
 
-```{r}
-Cairo("ms/Accessory_Costs/FigureXX_seedcount_reprocount.svg", height=5, width=5,type="svg",pointsize=10,units="in")
-#win.metafile("ms/Accessory_Costs/FigureXX_seedcount_reprocount.wmf", height=5, width=5)
-
-plot
-
-par(mfrow=c(1,1), cex=1, omi=c(.1,.1,.1,0.05), mai=c(.8,.8,.1,0.1))
-options(scipen = 2)
-
-xvar <- "ovule_count"
-yvar <- "seed_count"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope=1)
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="buds initiated (count)",ylab="seed count",lty=results$linetype,xlim=c(0.9,20000),ylim=c(0.9,20000))
-
-dplyr::select(results,group,n,r2,pval,Slope,Slope_test_p)
-abline(0,1,lwd=2)
-abline(-2,1,lwd=2)
-
-legend_with_r2(results,"topleft")
-
-dev.off()
-```
-
 #Although very little energy goes into propagules (or embryos) a notable amount of energy is required for successful seeds to form
 ```{r}
-win.metafile("ms/Accessory_Costs/FigureXX_success_vs_discarded.wmf", height=6, width=8)
-plot
+png("ms/Accessory/output/FigureXX_success_vs_discarded.png", height=6, width=8, units="in", res=300)
 
@@
 ```{r}
-win.metafile("ms/Accessory_Costs/FigureXX_EXTRA_acc_cost_by_seed_count.wmf", height=5, width=5)
-plot
+png("ms/Accessory/output/FigureXX_EXTRA_acc_cost_by_seed_count.png", height=5, width=5, units="in", res=300)
 
@@
 
-write.csv(results, file="ms/Accessory_Costs/TableXX_seedcount_vs_accessory.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/output/TableXX_seedcount_vs_accessory.csv",row.names=FALSE)
 

### 2016-12-13 ms/Accessory/Wenk-Accessory-SI.Rnw
Restructure materials for MS into folders
ignore generated figures
keep current version in single directory

--- 2016-10-11 ms/Accessory/ms-supp.Rnw
@@
 
-flowering_parts <- read.csv("Sup_Table_flowering_parts.csv",
-  stringsAsFactors=FALSE, check.names=FALSE)
+flowering_parts <- read.csv("Sup_Table_flowering_parts.csv", stringsAsFactors=FALSE, check.names=FALSE)
 
@@
 
-  #plot(graph)
-  plot(NA, type="n", xlim=c(0,1), ylim=c(0,1), ann=FALSE, axes=FALSE)
-  box()
+  plot(graph)
+  #plot(NA, type="n", xlim=c(0,1), ylim=c(0,1), ann=FALSE, axes=FALSE); box()
 }
@@
 
-<<echo=FALSE,results='asis'>>=
-TableSXX <- read.csv("Table_SXX_propagule_invest_vs_repro_inv.csv",
-                    stringsAsFactors=FALSE, check.names=FALSE)
+<<echo=FALSE, results='asis', warning=FALSE>>=
+
+make_table_propagule_invest_vs_all_repropro_inv <- function(SummaryInd) {
+  mod_propagule_inv_all <- sma(repro_inv~propagule_inv,data=SummaryInd,log="xy",method="SMA")
+  mod_flower_inv_all <- sma(repro_inv~flower_inv,data=SummaryInd,log="xy",method="SMA")
+
+  yvar <- "repro_inv"
+  xvar <- "propagule_inv"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=mod_propagule_inv_all$groupsummary["Slope"][[1]],elev.test=mod_propagule_inv_all$coef[[1]][1,1])
+  results <- fit$groupsummary
+  acc_slopes <- dplyr::select(results,group,n,r2,pval)
+  names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule")
+
+  yvar <- "repro_inv"
+  xvar <- "flower_inv"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
+  results <- fit$groupsummary
+  acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
+  names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
+  acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
+  acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  acc_slopes
+}
+
+TableSXX <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)
 
@@
 TableSXX[,2] <- format(TableSXX[,2],digits=2,nsmall=2)
+TableSXX[,3] <- format(TableSXX[,3],digits=2,nsmall=2)
+TableSXX[,6] <- format(TableSXX[,6],digits=2,nsmall=2)
 TableSXX[,5] <- format(TableSXX[,5],digits=2,nsmall=2)
@@
 
-<<echo=FALSE,results='asis'>>=
-TableSXX <- read.csv("Table_SXX_propagule_invest_vs_repro_inv.csv",
-                    stringsAsFactors=FALSE, check.names=FALSE)
-
-names(TableSXX) <- c("species","n","r$^2$","p", "n","r$^2$","p")
-TableSXX[,2] <- format(TableSXX[,2],digits=2,nsmall=2)
-TableSXX[,5] <- format(TableSXX[,5],digits=2,nsmall=2)
-TableSXX[,4] <- format_p(TableSXX[,4])
-TableSXX[,7] <- format_p(TableSXX[,7])
-
-TableSXX$species  <- paste("\\textit{",unique(TableSXX$species),"}", sep="")
-
-print(xtable(TableSXX,
-               hline.after=c(1),
-               align='p{0.1cm}p{4cm}|p{.94cm}p{1cm}p{1.5cm}|p{.75cm}p{1cm}p{1.5cm}',
-               caption="Intraspecific correlations between reproductive investment and (a) propagule investment and (b) flower investment"),
-               sanitize.text.function=I,
-        , table.placement = "H"
-        , caption.placement = "top"
-        , include.rownames = FALSE
-        , include.colnames = TRUE
-        , size = "small"
-        , floating = FALSE)
-@
-
-Table SXX.Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as "flower weight (mg) * bud count".
-
-\clearpage
-
-<<echo=FALSE,results='asis'>>=
-Table02 <- read.csv("Table02_acc_cost_embryo_size_slopes.csv",
-                    stringsAsFactors=FALSE, check.names=FALSE)
-
-names(Table02) <- c("Variable", "r$^2$", "slope (95 CI)","p$_{slope<>1}$")
-Table02[,2] <- format(Table02[,2],digits=2,nsmall=2)
-Table02[,4] <- format(Table02[,4],digits=4,nsmall=4)
-
-print(xtable(Table02,
-               hline.after=c(1),
-               align='p{0.1cm}p{4cm}p{1cm}p{3cm}p{1cm}',
-               caption="Correlations with total reproductive investment"),
-               sanitize.text.function=I,
-        , table.placement = "H"
-        , caption.placement = "top"
-        , include.rownames = FALSE
-        , include.colnames = TRUE
-        , size = "small"
-        , floating = FALSE)
-@
-
-Table 2.
-Scaling of reproductive tissue costs with seed size.
-All variables were showed a strong correlation with seed size (p < 0.0001).
-Tables show properties of SMA line fits, between different variables and seed size.
-\clearpage
-
-<<echo=FALSE,results='asis'>>=
-Table03 <- read.csv("Table03_correlations_with_repro_inv.csv",
-                    stringsAsFactors=FALSE, check.names=FALSE)
-format_p <- function(p, digits = 4) {
-  x <- as.character(round(p, digits = digits))
-  pc <- 10^-digits
-  x[p < pc] <- paste("<", pc)
-  x
-}
-
-Table03$pval <- format_p(Table03$pval)
-Table03$variable <- c("Total plant weight (mg)","Propagule investment (mg)","Fruit investment (mg)","Flower investment (mg)",
-                      "Successful investment (mg)", "Successful pre-pollination investment (mg)","Provisioning investment (mg)",
-                      "Failed tissues (mg)")
-names(Table03) <- c("Variable", "n", "r$^2$", "p")
-print(xtable(Table03,
-               hline.after=c(1),
-               align='p{0.1cm}p{6.5cm}p{1cm}p{1cm}p{1.5cm}',
-               caption="Correlations with total reproductive investment",
-             digits = 2),
-               sanitize.text.function=I,
-        , table.placement = "H"
-        , caption.placement = "top"
-        , include.rownames = FALSE
-        , include.colnames = TRUE
-        , size = "small"
-        , floating = FALSE)
-@
-
-Table 3.
-Correlation of different estimates of reproductive investment (and total plant weight) against total reproductive investment (mg).
-Regressions are done across all individuals of all 14 study species for which both reproductive investment and the estimate variable are greater than zero.
-The total cost of failed tissues or simply the energy expenditure into flowers provides the best approximation of total reproductive investment.
-Flower investment is a composite variable calculated as flower weight (mg)*bud count.
-Successful investment is a composite variable calculated as seed costs (mg)*seed count.
-
-\clearpage
-
-\clearpage
-
 \addcontentsline{toc}{section}{References}

### 2016-12-13 scripts/Accessory_figs_2015_12.Rmd
Restructure materials for MS into folders
ignore generated figures
keep current version in single directory

--- 2015-12-23 Accessory_figs_2015_12.Rmd
@@
 
-plot(total_accessory_Lord ~ seed_size,data=subset(SummarySppAge[["mean"]]),col=col.age(age),pch=16,log="xy", ylab="total per seed accessory costs")
-mod <- lm(log(total_accessory_Lord) ~ log(seed_size)*age,data=subset(SummaryInd,total_accessory_Lord>0))
+plot(total_accessory_Lord ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="total per seed accessory costs")
+mod <- lm(log(total_accessory_Lord) ~ log(seed_size),data=subset(SummarySpp[["mean"]],total_accessory_Lord>0))
+words.bottom.right.logxy(mod)
+summary(mod)
+
+plot(accessory_per_seed ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="total per seed accessory costs")
+mod <- lm(log(total_accessory_Lord) ~ log(seed_size),data=subset(SummarySpp[["mean"]],total_accessory_Lord>0))
 words.bottom.right.logxy(mod)
@@
 ```{r}
-plot(b_div_p ~ seed_size,data=subset(SummarySppAge[["mean"]]),col=col.age(age),pch=16,log="xy", ylab="per seed cost to procur pollen")
+plot(b_div_p ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy", ylab="per seed cost to procur pollen")
 mod <- lm(log(b_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,b_div_p>0))
@@
 summary(mod)
-slopes <- sma(log(b_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,b_div_p>0),slope.test=1)
+slopes <- sma(log(b_div_p) ~ log(seed_size),data=subset(SummaryInd,b_div_p>0),slope.test=1)
 summary(slopes)
 
-plot(c_div_p ~ seed_size,data=subset(SummarySppAge[["mean"]],c_div_p>0.00001),col=col.age(age),pch=16,log="xy", ylab="per seed cost of aborted fruits and seeds")
+plot(c_div_p ~ seed_size,data=subset(SummaryInd,c_div_p>0.00001),col=col.age(age),pch=16,log="xy", ylab="per seed cost of aborted fruits and seeds")
 mod <- lm(log(c_div_p) ~ log(seed_size)*age,data=subset(SummaryInd,c_div_p>0.00001))
@@
 
-plot(total_accessory_Lord  ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+plot(total_accessory_Lord  ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy")
 mod <- lm(log(total_accessory_Lord) ~ log(seed_size)*age,data=subset(SummaryInd,total_accessory_Lord>0))
 words.bottom.right.logxy(mod)
+summary(mod)
 slopes <- sma(log(total_accessory_Lord) ~ log(seed_size),data=subset(SummaryInd,total_accessory_Lord>0),slope.test=1)
 summary(slopes)
-
+slopes2 <- as.matrix(coef(slopes))
+abline(log(slopes2[1]),slopes2[2])
 #calculation of total accessory investment divided by seed count (accessory_per_seed) very closely correlated with accessory costs per seed using the equations in Lord
@@
 plot(seed_to_ovule_ratio ~ seed_size,data=subset(SummaryInd),col=col.spp(species),pch=16,log="xy")
+
+plot(seedset ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy")
 mod <- lm(log(seed_size) ~ log(seed_to_ovule_ratio),data=subset(SummaryInd,seed_to_ovule_ratio>0))
@@
 plot(accessory_per_seed~seed_size,data=subset(SummaryInd),log="xy",col=col.spp(species), pch=16)
+
+par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
+plot(total_accessory_Lord ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylab="total per seed accessory costs")
+abline(0,1)
+mod <- lm(log(total_accessory_Lord) ~ log(seed_size),data=subset(SummarySpp[["mean"]],total_accessory_Lord>0))
+words.bottom.right.logxy(mod)
+summary(mod)
+
+plot(c_div_p ~ seed_size,data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER"),col=col.spp(species),pch=16,log="xy")
+abline(0,1)
+mod <- lm(log(c_div_p) ~ log(seed_size),data=subset(SummarySpp[["mean"]],species!="COER"&species!="BAER",total_accessory_Lord>0))
+words.bottom.right.logxy(mod)
+
+plot(b_div_p ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy")
+abline(1.1,1)
+mod <- lm(log(b_div_p) ~ log(seed_size),data=subset(SummarySpp[["mean"]],total_accessory_Lord>0))
+words.bottom.right.logxy(mod)
+
+plot(dispersalcosts_increment ~ seed_size,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy")
+abline(0,1)
+mod <- lm(log(dispersalcosts_increment) ~ log(seed_size),data=subset(SummarySpp[["mean"]],dispersalcosts_increment>0))
+words.bottom.right.logxy(mod)
+
+```{r}
+par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
+xvar <- "total_accessory_Lord"
+yvar <- "RA"
+
+data <- subset(SummaryInd,total_accessory_Lord>0&RA>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1, 
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+```
+
+```{r}
+par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
+xvar <- "total_accessory_Lord"
+yvar <- "repro_inv"
+
+data <- subset(SummaryInd,total_accessory_Lord>0&RA>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1, 
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+```
+
+```{r}
+par(mfrow=c(4,4), cex=1, omi=c(.1,.1,.1,.1), mai=c(.5,.5,.5,.5)) 
+xvar <- "b_div_p"
+yvar <- "repro_inv"
+
+data <- subset(SummaryInd,b_div_p>0&RA>0&age>2)
+data <- split(data, data$species)
+lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  (log(x[[xvar]]))))
+results <- summarise_all_fits(lmfits)
+
+results$r.squared <- round(results$r.squared,digits=3)
+results$p.value <- round(results$p.value,digits=3)
+results$a <- round(results$a,digits=2)
+results$b <- round(results$b,digits=2)
+results
+
+for(spp in names(data)) {
+  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="xy",xlab="",ylab="",cex=1, 
+                    main=spp,col=col.age(data[[spp]]$age))
+}
+```
+
+#seedset lower in plants with bigger seeds, except at oldest site, when large seeded species doing relatively better and relationship flat
+```{r}
+par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
+plot(seedset ~ seed_size,data=subset(SummarySppAge[["mean"]],age==32),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ log(seedset),data=subset(SummarySppAge[["mean"]],age==32))
+words.bottom.left.logxy(mod)
+
+plot(seedset ~ seed_size,data=subset(SummarySppAge[["mean"]],age==9),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ log(seedset),data=subset(SummarySppAge[["mean"]],age==9))
+words.bottom.left.logxy(mod)
+
+plot(seedset ~ seed_size,data=subset(SummarySppAge[["mean"]],age==7),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ log(seedset),data=subset(SummarySppAge[["mean"]],age==7))
+words.bottom.left.logxy(mod)
+
+plot(seedset ~ seed_size,data=subset(SummarySppAge[["mean"]],age==5),col=col.spp(species),pch=16,log="xy")
+mod <- lm(log(seed_size) ~ log(seedset),data=subset(SummarySppAge[["mean"]],age==5&seedset>0))
+words.bottom.left.logxy(mod)
+```
+
+```{r}
+par(mfrow=c(2,2), cex=1, omi=c(.4,0.3,.3,0.3), mai=c(1.1,1,.3,0.3))
+plot(b_div_p ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy")
+abline(0,1)
+plot(c_div_p ~ seed_size,data=subset(SummaryInd,species!="COER"),col=col.age(age),pch=16,log="xy")
+abline(0,1)
+plot(dispersalcosts_increment ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy")
+abline(0,1)
+plot(total_accessory_Lord ~ seed_size,data=subset(SummaryInd),col=col.age(age),pch=16,log="xy")
+```

### 2016-12-13 Analysis-accessory.Rmd
Deleting commented/old code

@@
 mod_seed <- sma(scaled_seed_count~repro_costs,data=SummarySpp[["mean"]],log="xy",slope=-1,method="SMA")
-mod_ovule2 <- sma(scaled_ovule_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
 mod_ovule <- sma(scaled_reach_flowering_count~pollen_attract_costs,data=SummarySpp[["mean"]],log="xy",method="SMA",slope.test=mod_seed$groupsummary["Slope"][[1]],elev.test=mod_seed$coef[[1]][1,1])
@@
 #panel b
-#plot(choosiness~prop_pollen_attract_vs_all_repro_all_repro,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(0.002,.5),ylim=c(3,800),xaxt="n",yaxt="n",cex=1,ylab="",xlab="")
 plot(choosiness2~scaled_pollen_attract_costs,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(.002,.3),ylim=c(3,800),yaxt="n",cex=1,ylab="",xlab="",xaxt="n")
@@
 mtext("choosiness (ovules:seed)",2,line=2.3,cex=0.7)
-mod_choosy <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="SMA")
+#mod_choosy <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="SMA")
 mod_choosy2 <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",slope=-1,method="SMA")
@@
 points(prop_prepollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
-#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_success-SummarySpp[["se"]]$prop_prepollen_success,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_success+SummarySpp[["se"]]$prop_prepollen_success,code=3,angle=90, length=0.1,col=cerulean)
-#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded-SummarySpp[["se"]]$prop_prepollen_discarded,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded+SummarySpp[["se"]]$prop_prepollen_discarded,code=3,angle=90, length=0.1,col=venetian_red)
 extra.top.left.logx("c",2,1)
@@
 points(prop_provisioning_vs_success~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
-#arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success-SummarySpp[["se"]]$prop_pollen_attract_vs_success,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success+SummarySpp[["se"]]$prop_pollen_attract_vs_success,code=3,angle=90, length=0.1,col=cerulean)
 extra.top.left.logx("e",2,1)
@@
 
-dev.off()
-```
-
-#Supplementary Table. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
-```{r}
-png("ms/Accessory/output/Figure_SXX_RE_RA_size_age_patterns.png", height=10, width=10, units="in", res=300)
-
-par(mfrow=c(2,2), cex=1, omi=c(.1,.4,.1,.05), mai=c(.6,.3,.1,.1))
-options(scipen = 2)
-
-xvar <- "repro_inv"
-yvar <- "accessory_costs"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
-mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
-legend_with_r2(results,"bottomright")
-
-write.csv(results, file="ms/Accessory/output/Table05a_accessory_vs_all_repro.csv",row.names=FALSE)
-
-xvar <- "total_weight_0"
-yvar <- "accessory_costs"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
-mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
-legend_with_r2(results,"bottomright")
-
-write.csv(results, file="ms/Accessory/output/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)
-
-xvar <- "age"
-yvar <- "accessory_costs"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
-mtext(text="age (years)",side=1,line=2,outer=FALSE)
-mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
-legend_with_r2(results,"topleft")
-
-write.csv(results, file="ms/Accessory/output/Table05c_accessory_vs_age.csv",row.names=FALSE)
 dev.off()

### 2016-12-13 Analysis-accessory.Rmd
separating out supplementary material figures

--- 2016-12-13 Analysis-accessory.Rmd
@@
 
-#Supplementary Table. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
-```{r}
-png("ms/Accessory/output/Figure_SXX_RE_RA_size_age_patterns.png", height=10, width=10, units="in", res=300)
-
-par(mfrow=c(2,2), cex=1, omi=c(.1,.4,.1,.05), mai=c(.6,.3,.1,.1))
-options(scipen = 2)
-
-xvar <- "repro_inv"
-yvar <- "accessory_costs"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
-mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
-legend_with_r2(results,"bottomright")
-
-write.csv(results, file="ms/Accessory/output/Table05a_accessory_vs_all_repro.csv",row.names=FALSE)
-
-xvar <- "total_weight_0"
-yvar <- "accessory_costs"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
-mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
-legend_with_r2(results,"bottomright")
-
-write.csv(results, file="ms/Accessory/output/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)
-
-xvar <- "age"
-yvar <- "accessory_costs"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
-mtext(text="age (years)",side=1,line=2,outer=FALSE)
-mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
-legend_with_r2(results,"topleft")
-
-write.csv(results, file="ms/Accessory/output/Table05c_accessory_vs_age.csv",row.names=FALSE)
-dev.off()
-```
-
 #Table S1.correlations between repro inv and flower inv by species (noted in Discussiong)

### 2016-12-13 ms/Accessory/Wenk-Accessory-SI.Rnw
separating out supplementary material figures

@@
 
+\clearpage
+
+<<echo=FALSE,results='asis'>>=
+headers <- as.data.frame(matrix(vector(), 3,4,
+                dimnames=list(c(), c("A","B","C","D"))),
+                stringsAsFactors=F)
+headers[1,] <- c("","Proportion","Proportion","Proportion")
+headers[2,] <- c("","pollen-attraction","provisioning","success")
+headers[3,] <- c("","investment to","investment to","investment to")
+
+print(xtable(headers,
+             hline.after=c(-1),
+             align='p{0.1cm}p{11.5cm}|p{3cm}|p{3cm}|p{3cm}'),
+        sanitize.text.function=I,
+        , table.placement = "H"
+        , caption.placement = "top"
+        , include.rownames = FALSE
+        , include.colnames = FALSE
+        , size = "small"
+        , floating = FALSE)             
+@
+
+<<echo=FALSE, results='asis', warning=FALSE>>=
+
+make_table_species_values_for_allocation_seedsize_table <- function(file) {
+  data <- select(file,species,embryo_endo_costs, scaled_seed_count,scaled_ovule_count,
+                 scaled_pollen_attract_costs,choosiness2,prop_prepollen_success, prop_prepollen_discarded,
+                 prop_postpollen_success,prop_postpollen_discarded, prop_pollen_attract_vs_success,prop_provisioning_vs_success)
+  data$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  data
+}
+
+TableS2 <- make_table_species_values_for_allocation_seedsize_table(SummarySpp[["mean"]])
+
+names(TableS2) <- c("species","embryo and endosperm costs","scaled seed count","scaled ovule count","scaled pollen-attraction costs","choosiness","to success","to discarded","to success","to discarded","to pollen-attraction","to provisioning")
+
+for (i in 2:12) {
+TableS2[,i] <- format(TableS2[,i],digits=3,nsmall=2)
+}
+
+TableS2$species  <- paste("\\textit{",unique(TableS2$species),"}", sep="")
+
+print(xtable(TableS2,
+               hline.after=c(1),
+               align='p{0.1cm}p{4cm}|p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}',
+               caption="Species values for data plotted in Figure 2",
+               sanitize.text.function=I,
+        , table.placement = "H"
+        , caption.placement = "top"
+        , include.rownames = FALSE
+        , include.colnames = TRUE
+        , size = "small"
+        , floating = FALSE))
+@
+Table S2. Species values for data plotted in Figure 2, shifts in reproductive tissue allocation with seed size.
+
 <<echo=FALSE,results='asis'>>=
@@
 
-TableSXX <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)
+TableS3 <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)
 
-names(TableSXX) <- c("species","n","r$^2$","p", "n","r$^2$","p")
-TableSXX[,2] <- format(TableSXX[,2],digits=2,nsmall=2)
-TableSXX[,3] <- format(TableSXX[,3],digits=2,nsmall=2)
-TableSXX[,6] <- format(TableSXX[,6],digits=2,nsmall=2)
-TableSXX[,5] <- format(TableSXX[,5],digits=2,nsmall=2)
-TableSXX[,4] <- format_p(TableSXX[,4])
-TableSXX[,7] <- format_p(TableSXX[,7])
+names(TableS3) <- c("species","n","r$^2$","p", "n","r$^2$","p")
+TableS3[,2] <- format(TableS3[,2],digits=2,nsmall=2)
+TableS3[,3] <- format(TableS3[,3],digits=2,nsmall=2)
+TableS3[,6] <- format(TableS3[,6],digits=2,nsmall=2)
+TableS3[,5] <- format(TableS3[,5],digits=2,nsmall=2)
+TableS3[,4] <- format_p(TableS3[,4])
+TableS3[,7] <- format_p(TableS3[,7])
 
-TableSXX$species  <- paste("\\textit{",unique(TableSXX$species),"}", sep="")
+TableS3$species  <- paste("\\textit{",unique(TableS3$species),"}", sep="")
 
-print(xtable(TableSXX,
+print(xtable(TableS3,
                hline.after=c(1),
@@
 
-Table SXX.Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as "flower weight (mg) * bud count".
+Table S3.Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as "flower weight (mg) * bud count".
 
+\clearpage
+#Supplementary Table. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
+```{r}
+xvar <- "repro_inv"
+yvar <- "accessory_costs"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
+mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
+legend_with_r2(results,"bottomright")
+
+xvar <- "total_weight_0"
+yvar <- "accessory_costs"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
+mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
+legend_with_r2(results,"bottomright")
+
+xvar <- "age"
+yvar <- "accessory_costs"
+data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+results <- lines(fit$groupsummary)
+plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
+mtext(text="age (years)",side=1,line=2,outer=FALSE)
+mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
+legend_with_r2(results,"topleft")
+```
+
+Table S4. Shifts in accessory costs with shifts in age, plant size, or reproductive effort. 
 \clearpage

### 2016-12-15 ms/Accessory/Wenk-Accessory-SI.Rnw
SI: add title, fix table headers

@@
 
+% Enable new column type -- centered with fixed
+% Following http://texblog.org/2008/05/07/fwd-equal-cell-width-right-and-centre-aligned-content/
+\usepackage{array}
+\newcolumntype{x}[1]{%
+>{\raggedleft}p{#1}}%
+
 \newcommand{\smurl}[1]{\url{#1}}
@@
 
-\title{Accessories dominate the costs of producing seed}
-\runninghead{C\lowercase{osts of producing seed}}
+\title{Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species}
+\runninghead{S\lowercase{hifts in allocation among reproductive tissues}}
 
@@
 
-\pdfminorversion=4 % tell pdflatex to generate PDF in version 1.4
+\pdfminorversion=4
+% tell pdflatex to generate PDF in version 1.4
 % Needed for problem-free conversion on manuscript central (arrgh)
@@
 
-%\maketitle
+\maketitle
 
@@
 
-\section{A -- Methods for estimating Reproductive allocation}
+\section{A -- Methods for estimating reproductive allocation}
 
@@
 
-\clearpage
-
 <<echo=FALSE,results='asis'>>=
@@
 
-<<echo=FALSE, results='asis', warning=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 
@@
   acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
-  acc_slopes$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  acc_slopes$species <-  paste("\\textit{",species,"}", sep="")
+  names(acc_slopes) <- c("species","n","r$^2$","p", "n","r$^2$","p")
   acc_slopes
@@
 
-names(TableS3) <- c("species","n","r$^2$","p", "n","r$^2$","p")
-TableS3[,2] <- format(TableS3[,2],digits=2,nsmall=2)
-TableS3[,3] <- format(TableS3[,3],digits=2,nsmall=2)
-TableS3[,6] <- format(TableS3[,6],digits=2,nsmall=2)
-TableS3[,5] <- format(TableS3[,5],digits=2,nsmall=2)
-TableS3[,4] <- format_p(TableS3[,4])
-TableS3[,7] <- format_p(TableS3[,7])
-
-TableS3$species  <- paste("\\textit{",unique(TableS3$species),"}", sep="")
-
-print(xtable(TableS3,
-               hline.after=c(1),
-               align='p{0.1cm}p{4cm}|p{.94cm}p{1cm}p{1.5cm}|p{.75cm}p{1cm}p{1.5cm}',
-               caption="Intraspecific correlations between reproductive investment and (a) propagule investment and (b) flower investment"),
-               sanitize.text.function=I,
-        , table.placement = "H"
-        , caption.placement = "top"
-        , include.rownames = FALSE
-        , include.colnames = TRUE
-        , size = "small"
-        , floating = FALSE)
+for(i in c(2,3,5,6)){
+  TableS3[,i] <- format(TableS3[,i],digits=2,nsmall=2)
+}
+for(i in c(4,7)){
+  TableS3[,i] <- format_p(TableS3[,i])
+}
 @
 
-Table S3.Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as "flower weight (mg) * bud count".
-
-\clearpage
-#Supplementary Table. Higher RE, RA, plant size do not lead to lower accessory costs; age shows mixed results
-```{r}
-xvar <- "repro_inv"
-yvar <- "accessory_costs"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
-mtext(text="reproductive investment (mg) (RE)",side=1,line=2,outer=FALSE)
-legend_with_r2(results,"bottomright")
-
-xvar <- "total_weight_0"
-yvar <- "accessory_costs"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab=yvar,lty=results$linetype)
-mtext(text="total plant size (mg)",side=1,line=2,outer=FALSE)
-legend_with_r2(results,"bottomright")
-
-xvar <- "age"
-yvar <- "accessory_costs"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-results <- lines(fit$groupsummary)
-plot(fit,col=col.spp(fit$groupsummary$group),pch=16,xlab="",ylab="",lty=results$linetype)
-mtext(text="age (years)",side=1,line=2,outer=FALSE)
-mtext(text="per seed accessory costs (mg/seed)",side=2,line=1,outer=TRUE)
-legend_with_r2(results,"topleft")
-```
+\begin{table}[H]
+\centering
+\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight (mg) $\times$ bud count'}
+\label{tab:propagule_invest_vs_repro}
+\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
+\hline
+& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
+& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
+<<echo=FALSE, results='asis', warning=FALSE>>=
+print(xtable(TableS3)
+        , sanitize.text.function=I
+        , include.rownames = FALSE
+        , include.colnames = TRUE,
+        only.contents=TRUE)
+@
+\end{tabular}
+\end{table}
 
@@
 
-\addcontentsline{toc}{section}{References}
+\addcontentsline{toc}{section}{B -- References}
 \bibliography{references}

### 2016-12-15 Analaysis-RA.Rmd
Renaming of files in Summary workflow; add starting commands for each analysis

@@
+```{r}
+# library(digest)
+# library(Rcpp)
+# library(reshape2)
+# library(tibble)
+library(smatr)
+library(broom)
+library(dplyr)
+# library(stats)
+# library(scales)
+# library(colorspace)
+
+remake::make("export")
+
+SummaryCombine <- readRDS("export/SummaryCombine.rds")
+SummarySpp <- readRDS("export/SummarySpp.rds")
+SummarySppAge <- readRDS("export/SummarySppAge.rds")
+
+HarvestData <- readRDS("export/HarvestData.rds")
+InvestmentByPart <- readRDS("export/Investment_FD_all.rds")
+PartsSummary <- readRDS("export/PartsSummary_all.rds")
+
+source("R/figures.R")
+```
+
 # pdf('ms/RA/Figure_1_stacked_lines.pdf', height=11.5, width=8) plot
 
-SummarySppAge[["mean"]]$leaf_shed_mean <- SummaryInd %>%
+SummarySppAge[["mean"]]$leaf_shed_mean <- SummaryCombine %>%
         group_by(species,age) %>%
@@
 
-SummarySppAge[["mean"]]$leaf_replacement_mean <- SummaryInd %>%
+SummarySppAge[["mean"]]$leaf_replacement_mean <- SummaryCombine %>%
         group_by(species,age) %>%
@@
 data$leaf_shed2 <- data$leaf_weight_0 / data$LL_death
-data_ind <- select(SummaryInd,species,individual,age, LL_death,height_0,leaf_shed,leaf_weight_0,propagule_inv,ovule_count,
+data_ind <- select(SummaryCombine,species,individual,age, LL_death,height_0,leaf_shed,leaf_weight_0,propagule_inv,ovule_count,
                    growth_leaf_pos,repro_inv,total_weight_0,all_leaf_inv,total_inv,surplus_inv,all_leaf_and_repro_inv,age,success_inv)
@@
 xvar <- "leaf_weight_0"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+data <- subset(SummaryCombine,SummaryCombine[[xvar]]>0&SummaryCombine[[yvar]]>0)
 
@@
 xvar <- "growth_leaf_pos"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+data <- subset(SummaryCombine,SummaryCombine[[xvar]]>0&SummaryCombine[[yvar]]>0)
 
@@
 xvar <- "all_leaf_inv"
-data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+data <- subset(SummaryCombine,SummaryCombine[[xvar]]>0&SummaryCombine[[yvar]]>0)
 

### 2016-12-15 Analysis-accessory.Rmd
Renaming of files in Summary workflow; add starting commands for each analysis

--- 2016-12-13 Analysis-accessory.Rmd
@@
 ```{r}
-library(digest)
-library(Rcpp)
-library(reshape2)
-library(tibble)
+# library(digest)
+# library(Rcpp)
+# library(reshape2)
+# library(tibble)
 library(smatr)
@@
 library(dplyr)
-library(stats)
-library(scales)
-library(colorspace)
+# library(stats)
+# library(scales)
+# library(colorspace)
 
@@
 SummarySppAge <- readRDS("export/SummarySppAge.rds")
-HarvestData <- readRDS("export/HarvestData.rds")
-InvestmentByPart <- readRDS("export/Investment_FD_all.rds")
-PartsSummary <- readRDS("export/PartsSummary_all.rds")
 

### 2016-12-15 Analaysis-RA.Rmd
Change "leaf lifespan" to "Leaf loss"
- proportion of leaf loss is what we actually want and estimates are
meaningful whereas estimates of leaf lifespan are less reliable
when shoots are growing rapidly
- also removed a bunch of variables no longer used

@@
 source("R/figures.R")
-```
-
-# pdf('ms/RA/Figure_1_stacked_lines.pdf', height=11.5, width=8) plot
-
-SummarySppAge[["mean"]]$leaf_shed_mean <- SummaryCombine %>%
-        group_by(species,age) %>%
-        summarise(mean(leaf_shed_mean))
-
-SummarySppAge[["mean"]]$leaf_replacement_mean <- SummaryCombine %>%
-        group_by(species,age) %>%
-        summarise(mean(leaf_replacement_mean))
 
@@
   growth_stem, leaf_shed,prop_stem,prop_leaf_replacement,prop_leaf_expand,prop_repro,RA_max_1,lifespan,height, RA_vs_all_leaf,
-  LL_death,height_0,total_weight_0,all_leaf_inv,surplus_inv,all_leaf_and_repro_inv,propagule_inv,ovule_count,success_inv)
-data$leaf_shed2 <- data$leaf_weight_0 / data$LL_death
-data_ind <- select(SummaryCombine,species,individual,age, LL_death,height_0,leaf_shed,leaf_weight_0,propagule_inv,ovule_count,
+  prop_leaf_loss,height_0,total_weight_0,all_leaf_inv,surplus_inv,all_leaf_and_repro_inv,propagule_inv,ovule_count,success_inv)
+
+data_ind <- select(SummaryCombine,species,individual,age, prop_leaf_loss,height_0,leaf_shed,leaf_weight_0,propagule_inv,ovule_count,
                    growth_leaf_pos,repro_inv,total_weight_0,all_leaf_inv,total_inv,surplus_inv,all_leaf_and_repro_inv,age,success_inv)
 
+```
+
 ```{r}
+
+# pdf('ms/RA/Figure_1_stacked_lines.pdf', height=11.5, width=8) plot
 par(mfrow = c(7,4), cex = 1, oma = c(5, 5, 1, 1), mar = c(0, 3, 2, 1))
@@
   #leaf area
-  plot(NA, log = "x", xlim = c(1.4, 32), ylim=c(1,(max(data_sp$leaf_weight_0)*1.1)),xaxs = "i", yaxs = "i", xaxt="n", ylab="n")
+  plot(NA, log = "x", xlim = c(1.4, 32), ylim=c(0,1),xaxs = "i", yaxs = "i", xaxt="n", ylab="n")
   box()
   axis(1, labels = (i %in% c(7,14)))
-  points(x = data_sp$age, y = data_sp$leaf_weight_0, col = "darkseagreen4", lwd=2,type="l")
-  points(x = data_sp_ind$age, y = data_sp_ind$leaf_weight_0, col = "black")
+  points(x = data_sp$age, y = data_sp$prop_leaf_loss, col = "darkseagreen4", lwd=2,type="l")
+  points(x = data_sp_ind$age, y = data_sp_ind$prop_leaf_loss, col = "black")
   #points(x = data_sp_ind$age, y = data_sp_ind$leaf_weight_0, col = "black",cex=0.5,pch=16)
-  #points(x = data_sp$age, y = data_sp$leaf_shed2, col = "darkseagreen4", lwd=2,type="l")
   #points(x = data_sp_ind$age, y = data_sp_ind$leaf_shed, col = "darkseagreen4")
@@
   #points(x = data_sp_ind$age, y = data_sp_ind$leaf_weight_0, col = "black",cex=0.5,pch=16)
-  points(x = data_sp$age, y = data_sp$leaf_shed2, col = "darkseagreen4", lwd=2,type="l")
-  #points(x = data_sp_ind$age, y = data_sp_ind$leaf_shed, col = "darkseagreen4")
+  points(x = data_sp_ind$age, y = data_sp_ind$leaf_shed, col = "darkseagreen4")
   points(x = data_sp$age, y = data_sp$growth_leaf, col = "darkseagreen2", lwd=2,type="l")
@@
   # #leaf lifespan
-  # plot(NA,log = "x", ylim = c(0, 6),  xlim = c(1.2, 37), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
+  # plot(NA,log = "x", ylim = c(0, 1),  xlim = c(1.2, 37), xaxs = "i", yaxs = "i", axes= FALSE, ann=FALSE)
   # box()
@@
   # axis(2, at = c(0,2,4,6), labels = TRUE, las=1)
-  # points(x = data_sp$age, y = data_sp$LL_death, col = "darkseagreen4", lwd=2,type="l")
-  # points(x = data_sp_ind$age, y = data_sp_ind$LL_death, col = "black")
+  # points(x = data_sp$age, y = data_sp$prop_leaf_loss, col = "darkseagreen4", lwd=2,type="l")
+  # points(x = data_sp_ind$age, y = data_sp_ind$prop_leaf_loss, col = "black")
   # 

### 2016-12-15 ms/Accessory/Wenk-Accessory-SI.Rnw
SI: dotpoints on what is needed
- also import text from old documents

@@
 
-\section{A -- Methods for estimating reproductive allocation}
+\section{Additional results}
+
+\section{Details on data from main text}
+
+Describe contents of csv files attached
+
+\section{Overview of methods for estimating reproductive allocation}
 
 All computations implemented in \textsc{r} \citep{R-2015}.
+
+List of files
+
+- brief summary here? Detailed list of contents below in section below. Or move up here?
+
+What is measured by individual and species
+
+- for parts default is at species unless actual piece was collected
+- various techniques used to estimate weights, eg. by legnth, volume, count -- specified in tables.
+
+Census
+
+- measurements indicating Counts of parts on each individual\\
+- use species level conversions to get number of parts by individual * census\\
+- algorithm which estimates demography of numbers of parts, with respect to map of progression\\
+- convert numbers into weights (BAER\_Investment -- > 4 dataframes in a list, but only FD (= final development of parts) is used, others for error checking)\\
+- group into different categories (BAER\_reproductive costs -- by function `ReproductiveCosts')\\
+  - investment: weight (mg)\\
+  - count (number)\\
+  - costs (mg/successful seed)\\
+  - reference back to groups in paper and in accessoryParts.yml\\
+- at individual level, calculate various proportions and metrics, after combining growth, reproduction, traits ( in `combine\_by\_individual')\\
+
+Investment categories
+
+- process stuff in file `accessoryParts.yml'
+
+\section{Details about input files (Old text to adapt)}
+
+2013\_Kuringgai\_harvest
+Allometric data for plants harvested in autumn 2013, including weights and diameters of each harvested segment.
+Briefly, this dataset includes data on 14 dominant species that are all obligate seeders following a fire.
+For each species, data were collected from 7 replicate individuals at each of 6 sites, or the subset of those sites on which a given species occurred.
+The sites represent a chronosequence created by a patchy fire history in the area; all species germinate within a year of a fire, allowing fire history to be used as a proxy for age.
+When the plants were harvested, they were divided into multiple segments along the stem leader.
+The diameter was measured at each cut in autumn 2012, when the plants were tagged, and in autumn 2013, at harvest.
+For each segment, the dry weights of the leaves and stems were determined separately.
+
+2013\_Kuringgai\_harvest-meta
+Brief descriptions of each data column in the file 2013\_Kuringgai\_harvest, including units.
+
+flower\_parts
+Harvested and weighed flower parts, including collections from tagged individuals (once mature or at time of harvest) and from other individuals in the population (to estimate weight of specific plant parts).
+All plant parts included in a species' "plant map" have weights in this spreadsheet – or, in rare cases, entries are instead plants parts whose weight is used to calculate the weight of a plant part included in a "plant map".
+(A "plant map" shows the developmental trajectory of a flower or inflorescence from bud to seed for each species, indicating the flow or carbon as well as discarded parts.) If plant parts are collected from a tagged individual, this spreadsheet also indicates in which census periods this specific weight, rather than a species average, should be used for calculating that individual's reproductive investment.
+Plant parts all have counts and weights, while the subset of plant parts whose size varies, also have columns indicating height and diameter dimensions; the weight of the plant part at a specific size is then determined by either a regression or volume calculation.
+For a few plant parts, census data measure the length of stem or cone covered with flowers; for these situations, the segment length collected is also recorded, such that the number of flowers per unit length can be calculated.
+
+Flower\_parts-meta
+Brief descriptions of each data column in the file flower\_parts, including units.
+
+Flowering\_cat\_lookup\_table
+This file contains a matrix of plant parts (rows) by species (columns).
+For each cell that is used on a given species plant map, the meaning of the values in the spreadsheet titled "reproduction" are indicated in this spreadsheet.
+Possible method are (1) count, indicating that the numbers represent simple counts; (2) count\_by\_length, indicating that the length of stem or cone covered with buds, flowers or fruit is measured; (3) regress\_by\_dim, indicating that the dimensions of the flowering part are measured and must be converted to a dry mass using a regression equation; and (4) volume, indicating that the height and diameter of the flowering part are given and must be converted to a dry mass using the calculated volume of the flowering part multiplied by the average density of the flowering part.
+
+flowering\_categories\_descriptions
+This files contains a matrix of plant parts (rows) by species (columns).
+For each cell that is used on a given species plant map, a description of the botanical parts included in the "flower part" is given as well as the flowering stage at which the flower part is harvested, if it is not obvious.
+
+LMA
+This file contains data on leaf area and leaf weight for each of the 14 species at each of the 6 sites.
+For each species by site combination, leaves were collected from 4-5 individuals (occasionally fewer).
+A pooled sample was then scanned for leaf area and weighed dry.
+Three leaf ages were collected for each species; for species where leaf lifespan is short, only two leaf cohorts could be collected.
+For juvenile individuals, where leaf size and shape changes rapidly with each new flush of leaves, it was noted additional descriptions of the leaves were made.
+
+LMA\_metadata
+Brief descriptions of each data column in the file LMA\_metadata, including units.
+
+MultiplierTable
+Lookup table indicating, for each species by flower part combination, if the investment per part is for a single (1) or multiple propagules, defined as either a mature fruit or a seed, depending on what is the dispersal unit for each species.
+Within a single column, i.e.
+within a single species developmental trajectory, numbers will change if the "count" used to access reproduction changes at a given developmental stage.
+For instance, with BOLE (Boronia ledifolia), counts are made by flowers up through the finished flower stage, but then fruit are the unit counted and each flower forms 4 fruit.
+
+Reproduction
+The reproduction spreadsheet provides both verbal and numeric descriptions of reproduction at each census between April-June 2012, when the plants were first tagged, until April-June 2013, when the plants were harvested.
+There is a separate row of data for each individual, at each of the 18 censuses.
+In addition, at each census, there is a row indicating plant parts that are pre-existing on the plant versus new.
+Flower (or fruit) parts are considered pre-existing if the predecessor of that flower part, as described on that species "plant map" existed in a previous census period.
+Some plant maps may have multiple parallel diagrams describing how flower parts develop.
+In that case, a flower part must have a predecessor on that specific diagram to be considered "pre-existing".
+Each of the many plant parts are listed as column headers.
+At each census, both new and further developed but pre-existing flower parts are recorded.
+Plant parts that are unchanged in developmental stage between successive censuses are not recorded.
+Neither are plant parts that disappear between successive censuses.
+Instead, pre-existing plant parts are recorded if they have progressed to a "more mature" flowering/fruiting stage, as defined by that species "plant map".
+As an example, if at one census there were 50 PHPH (Phyllota phylicoides) buds recorded and at the next stage, 30 PHPH flowers, 30 of the 50 buds progressed from being buds to being flowers, while the remaining 20 buds were either shed or are still buds.
+The numbers entered in the cell correspond to either counts, lengths, or dimensions, depending on the method indicated in the file titled "Flowering\_cat\_lookup\_table".
+
+Seed multiplier
+Table indicating if final investment is in units of a single seed (1) or multiple seeds.
+For species where the final propagule contains multiple seeds, a multiplier is included so that total investment in seeds/fruits (i.e.
+propagules) can be scaled to a single seed.
+
+Sites
+Tables of sites used in study.
+Includes site names used in other spreadsheets, date of fire, fire year, as defined by NSW fire layers (which would be the best indicator of germination date), and UTM coordinates for each site.
+
+Species\_names
+Table of species included in study. Includes 4-letter code names used in other spreadsheets, scientific names, family names, and common names.
+
+wood\_density
+Data on wood density for each species.
+Wood samples were collected from sufficiently large plants to ensure replicable displacement values.
+Bark and pith were both removed from the samples before determining volume.
+Multiple methods were tested, with numbers most consistent using the "tweezer" method.
+Using this method, samples were held with tweezers and just submerged.
+Using this method, the balance stabilized rapidly and repeatedly.
+These measurements were all made using the Mettler balance.
+Of the measurements made using the "pipette\_suspension" method, where a section of wood was submerged inside a suspended pipette, only those made on the Sartorius balance are believable.
+
+wood\_density\_meta
+Brief descriptions of each data column in the file wood\_density\_meta, including units.
+
+\section{Details on calculations by species}
+
+Species differ from one another in
+
+\begin{enumerate}
+\item Something
+\item Something else
+\end{enumerate}
+
+For each species provide
+
+\begin{enumerate}
+\item Something
+\item Something else
+\end{enumerate}
 
@@
 
-\addcontentsline{toc}{section}{B -- References}
+\addcontentsline{toc}{section}{References}
 \bibliography{references}

### 2016-12-15 ms/Accessory/Wenk-Accessory-SI.Rnw
Example printing data from _meta.csv files

@@
       sanitize.text.function=I,
-      , table.placement = "H"
+      , table.placement = "h"
+      , caption.placement = "top"
+      , include.rownames = FALSE
+      , include.colnames = TRUE
+      , size = "small"
+      , tabular.environment = 'longtable'
+      , floating = FALSE)
+}
+
+print_table_metadata <- function(path) {
+
+  data <-  read.csv(path, stringsAsFactors=FALSE, check.names=FALSE)
+  file <- gsub("_", "\\_", basename(path), fixed = TRUE)
+  print(xtable(data,
+            hline.after=c(1),
+            label=sprintf("tab:file_", file),
+            caption=
+              sprintf("Variables within the file `%s`. These definitions are defined within the file `%s` in the folder `data`.",
+              gsub("\\_meta", "", file, fixed = TRUE), file)),
+      , table.placement = "h"
       , caption.placement = "top"
@@
 
-2013\_Kuringgai\_harvest
+\subsection{Harvest}
+
 Allometric data for plants harvested in autumn 2013, including weights and diameters of each harvested segment.
@@
 For each segment, the dry weights of the leaves and stems were determined separately.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/harvest_meta.csv")
+@
 
@@
 
-Flower\_parts-meta
+\subsection{Flower\_parts}
 Brief descriptions of each data column in the file flower\_parts, including units.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/flowerParts_meta.csv")
+@
 

### 2016-12-20 scripts/nutrient.Rmd
adding plots to nutrient analysis showing shifts in bulk stem N & P with shifts in stem diameter. Added temporary diameter column to data - need to instead take mean in R

@@
 ```
+
+```{r}
+stem_segments <- nutrient %>%
+    subset(tissue_complete %in% c("wood_from_base","wood_from_middle","wood_from_tip"))%>%
+    select(species,age,P,N,diameter_temp,tissue_complete) 
+stem_segments$diameter <- as.numeric(stem_segments$diameter)
+stem_segments$area <- ((stem_segments$diameter/2)^2)*3.14159
+
+all_species <- unique(stem_segments$species)
+
+pdf("ms/Nutrient/output/stem segment by diameter.pdf", height=11, width=8)
+plot
+
+par(mfrow = c(4,2), cex = 1, omi=c(.1,.1,.6,.05), mai=c(1,1,.05,.05))
+
+for (i in seq_along(all_species)) {
+
+data_sp <- filter(stem_segments, species == all_species[i])
+plot(P~area,data=data_sp,log="x",col=col.age(data_sp$age),pch=pch.tissue(data_sp$tissue_complete),xlab="",ylab="")
+mod <- sma(P~area,data=data_sp,log="x")
+mtext("stem area (mm^2)",1,line=1.7,cex=0.7)
+mtext("P concentration",2,line=2.3,cex=0.7)
+mtext(labels.spp.full(all_species[i]), 3, 0)
+plot(N~area,data=data_sp,log="x",col=col.age(data_sp$age),pch=pch.tissue(data_sp$tissue_complete),xlab="",ylab="")
+mtext("stem area (mm^2)",1,line=1.7,cex=0.7)
+mtext("N concentration",2,line=2.3,cex=0.7)
+
+  if (i %in% c(1,5,9,13)) {
+   legend("bottomleft",legend=c("sapwood","wood from mid","wood from base"),pch=c(16,10,7),bty="n",cex=0.8)
+   legend("topright",legend=labels.age(),col=col.age(),pch=16, bty="n",cex=0.8)
+  }
+
+}
+
+dev.off()
+```
+
+plot(P~diameter,stem_segments,log="xy",col=col.spp(species),pch=16)
+
+stem_segments$diameter <- as.numeric(stem_segments$diameter)
 

### 2016-12-20 Analysis-accessory.Rmd
Edits to Accessory Figs manuscript, including reworking Figure 1 and accompanying text and work on discussion.
Some work on Tables for Supp Material

@@
 ```{r}
-png("ms/Accessory/output/Figure01b&c_predictions.png", height=3, width=6, units="in", res=300)
-par(mfrow=c(1,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05)) 
+png("ms/Accessory/output/Figure01b&c&d_predictions.png", height=3.6, width=9, units="in", res=300)
+par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.6,.05))
 plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
-segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=2)
+segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=1)
+axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
+axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
+mtext(text="b.  Trade-off 1:",side=3,outer=FALSE,adj=0,line=1.6)
+mtext(text="Seed count-reproductive costs",side=3,outer=FALSE,adj=0,line=0.7)
+mtext(text="seed count,",side=2,line=1.3,outer=FALSE,cex=0.8)
+mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
+mtext(text="reproductive costs",side=1,line=0.3,outer=FALSE,cex=0.8)
+mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
+#extra.top.left("b",2,1)
+
+plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
 segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
@@
 axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
-mtext(text="count, scaled to plant size",side=2,line=1.1,outer=FALSE,cex=0.8)
-mtext(text="costs (mg/seed)",side=1,line=1.0,outer=FALSE,cex=0.8)
-legend("bottomleft",legend=c("seed count by reproductive costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
-extra.top.left("b",2,1)
+mtext(text="c.  Trade-off 2.",side=3,outer=FALSE,adj=0,line=1.6)
+mtext(text="Ovule count-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
+mtext(text="mature ovules count,",side=2,line=1.3,outer=FALSE,cex=0.8)
+mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
+mtext(text="pollen attraction costs",side=1,line=0.3,outer=FALSE,cex=0.8)
+mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
+#extra.top.left("c",2,1)
 
@@
 axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
-mtext(text="choosiness (ovule:seed)",side=2,line=1.3,outer=FALSE,cex=0.8)
-mtext(text="pollen attraction costs,",side=1,line=1.1,outer=FALSE,cex=0.8)
-mtext(text="scaled to plant size",side=1,line=1.9,outer=FALSE,cex=0.8)
-extra.top.left("c",2,1)
+mtext(text="d.  Trade-off 3.",side=3,outer=FALSE,adj=0,line=1.6)
+mtext(text="Choosiness-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
+mtext(text="choosiness",side=2,line=1.3,outer=FALSE,cex=0.8)
+mtext(text="(ovule:seed)",side=2,line=0.4,outer=FALSE,cex=0.8)
+mtext(text="pollen attraction costs,",side=1,line=0.3,outer=FALSE,cex=0.8)
+mtext(text="scaled to plant size",side=1,line=1.2,outer=FALSE,cex=0.8)
+mtext(text="(mg/seed)",side=1,line=2.1,outer=FALSE,cex=0.8)
+#extra.top.left("d",2,1)
 dev.off()
 
-png("ms/Accessory/output/Figure01def_predictions.png", height=6, width=6, units="in", res=300)
-
-par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05))
-plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
-segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
-segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=2)
-axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
-axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
-mtext(text="proportion all pollen-attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
-mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
-legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
-extra.top.left("d",2,1)
-
-plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
-segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=2)
-segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=1)
-axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
-axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
-mtext(text="proportion all provisioning investment",side=2,line=1.8,outer=FALSE,cex=0.8)
-mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
-legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
-extra.top.left("e",2,1)
-
-plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
-segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
-segments(x0=.15,x1=.9,y0=.15,y1=.9,lty=2)
-axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
-axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
-mtext(text="proportion total success costs",side=2,line=1.8,outer=FALSE,cex=0.8)
-mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
-legend("bottomleft",legend=c("pollen-attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
-extra.top.left("f",2,1)
-
-dev.off()
+# png("ms/Accessory/output/Figure01def_predictions.png", height=6, width=6, units="in", res=300)
+# 
+# par(mfrow=c(2,2), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.1,.05))
+# plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+# segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
+# segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=2)
+# axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
+# axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
+# mtext(text="proportion all pollen-attraction investment",side=2,line=1.8,outer=FALSE,cex=0.8)
+# mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
+# legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
+# extra.top.left("d",2,1)
+# 
+# plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+# segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=2)
+# segments(x0=.15,x1=.85,y0=.15,y1=.85,lty=1)
+# axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
+# axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
+# mtext(text="proportion all provisioning investment",side=2,line=1.8,outer=FALSE,cex=0.8)
+# mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
+# legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
+# extra.top.left("e",2,1)
+# 
+# plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
+# segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
+# segments(x0=.15,x1=.9,y0=.15,y1=.9,lty=2)
+# axis(2, at=c(0,1),labels=c(0,1),cex.axis=1,las=2)
+# axis(1, at=c(0,1),labels=c("smaller","larger"),cex.axis=1)
+# mtext(text="proportion total success costs",side=2,line=1.8,outer=FALSE,cex=0.8)
+# mtext(text="seed size (mg)",side=1,line=1.3,outer=FALSE,cex=0.8)
+# legend("bottomleft",legend=c("pollen-attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
+# extra.top.left("f",2,1)
+# 
+# dev.off()
 ```
@@
 extra.top.left.logxy("a",2,1)
+
+plot(choosiness2~prop_pollen_attract_vs_all_repro,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(.002,.3),ylim=c(3,800),yaxt="n",cex=1,ylab="",xlab="",xaxt="n")
+axis(2, at=c(10,100,1000), labels=c(10,100,1000),cex.axis=0.8,las=2)
+axis(1, at=c(0.01,0.1), labels=c(0.01,0.1),cex.axis=0.8)
+mtext("pollen-attractions costs, scaled to leaf area",1,line=1.7,cex=0.7)
+mtext("choosiness (ovules:seed)",2,line=2.3,cex=0.7)
+#mod_choosy <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="SMA")
+mod_choosy2 <- sma(choosiness2~prop_pollen_attract_vs_all_repro,data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",slope=-1,method="SMA")
 

### 2016-12-20 scripts/Accessory_figs_20160905.Rmd
Edits to Accessory Figs manuscript, including reworking Figure 1 and accompanying text and work on discussion.
Some work on Tables for Supp Material

@@
 ```{r}
-win.metafile("ms/Accessory/Figure_SXX_RE_RA_size_age_patterns.wmf", height=10, width=10)
-plot
-
-par(mfrow=c(2,2), cex=1, omi=c(.1,.4,.1,.05), mai=c(.6,.3,.1,.1))
-options(scipen = 2)
-
 xvar <- "repro_inv"
@@
 
-write.csv(results, file="ms/Accessory/Table05a_accessory_vs_all_repro.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/output/TableS3a_accessory_vs_all_repro.csv",row.names=FALSE)
 
@@
 
-write.csv(results, file="ms/Accessory/Table05b_accessory_vs_total_weight.csv",row.names=FALSE)
+write.csv(results, file="ms/Accessory/output/TableS3b_accessory_vs_total_weight.csv",row.names=FALSE)
 
@@
 
-write.csv(results, file="ms/Accessory/Table05c_accessory_vs_age.csv",row.names=FALSE)
-dev.off()
+write.csv(results, file="ms/Accessory/output/TableS3c_accessory_vs_age.csv",row.names=FALSE)
 ```

### 2017-02-08 ms/Accessory/Wenk-Accessory-SI.Rnw
misc small changes
work on supplementary material for Accessory ms. Added metadata files for several data files, worked on figures for SuppMaterial.

@@
 \begin{document}
+\SweaveOpts{concordance=TRUE}
 
@@
 
-List of files
+List of data files.
 
-- brief summary here? Detailed list of contents below in section below. Or move up here?
+The following files contain the empirical data used in the analyses:
+
+accessory_parts.yml
+flowerCategories.csv and flowerCategories_meta.csv
+flowerParts.csv and flowerParts_meta.csv
+individuals.csv and individuals_meta.csv
+MultiplierTable.csv
+reproduction.csv and reproduction_meta.csv
+seedMultiplier.csv
+
+The following files contain supplmentary data about the species and sites:
+seedsize.csv and seedsize_meta.csv
+sites.csv and sites_meta.csv
+species.csv
 
@@
 
-- for parts default is at species unless actual piece was collected
-- various techniques used to estimate weights, eg. by legnth, volume, count -- specified in tables.
+- for flower parts, the default is at the species level unless the actual piece was collected; Plant parts that were collected on an individual is recorded in the file flowerParts
+- all reproductive output is measured at the individual
 
@@
 
-Investment categories
+\section{Investment categories}
 
-- process stuff in file `accessoryParts.yml'
+accessoryParts.yml
+This file contains, for each species, lists of reproductive tissues that fall into various tissue categories=.
+These categories are then used to calculate the reproductive investment in the key reproductive tissue categories, (1) pollen-attraction tissues aborted prior to provisioning; (2) pollen-attraction tissues associated with flowers that form mature seeds; (3) provisioning tissues aborted prior to the formation of a mature seed; (4) packaging and dispersal tissues associated with a mature seed; (5) the mature seed itself.
+Dividing reproductive investment into these categories requires, for each tissue type, knowing the count of parts that reach the key stages (pollinator-ready, onset of provisioning, mature seed) and the mass of parts at each stage.
 
-\section{Details about input files (Old text to adapt)}
-
-\subsection{Harvest}
-
-Allometric data for plants harvested in autumn 2013, including weights and diameters of each harvested segment.
-Briefly, this dataset includes data on 14 dominant species that are all obligate seeders following a fire.
-For each species, data were collected from 7 replicate individuals at each of 6 sites, or the subset of those sites on which a given species occurred.
-The sites represent a chronosequence created by a patchy fire history in the area; all species germinate within a year of a fire, allowing fire history to be used as a proxy for age.
-When the plants were harvested, they were divided into multiple segments along the stem leader.
-The diameter was measured at each cut in autumn 2012, when the plants were tagged, and in autumn 2013, at harvest.
-For each segment, the dry weights of the leaves and stems were determined separately.
+\subsection{accessoryParts\_metadata}
+Brief descriptions of each reproductive parts category in the file accessoryParts.
 
 <<echo=FALSE,results='asis'>>=
-  print_table_metadata("../../data/harvest_meta.csv")
+  print_table_metadata("../../data/accessoryParts_meta.csv")
 @
 
-2013\_Kuringgai\_harvest-meta
-Brief descriptions of each data column in the file 2013\_Kuringgai\_harvest, including units.
+\section{Details about input files}
+floweringCategories
+This file contains a matrix of plant parts (rows) by species (columns).
+For each cell that is used on a given species plant map, the meaning of the values in the spreadsheet titled "reproduction" are indicated in this spreadsheet.
+Possible method are (1) count, indicating that the numbers represent simple counts; (2) count\_by\_length, indicating that the length of stem or cone covered with buds, flowers or fruit is measured; (3) regress\_by\_dim, indicating that the dimensions of the flowering part are measured and must be converted to a dry mass using a regression equation; and (4) volume, indicating that the height and diameter of the flowering part are given and must be converted to a dry mass using the calculated volume of the flowering part multiplied by the average density of the flowering part.
 
-flower\_parts
+floweringCategories\_metadata
+This files contains a matrix of plant parts (rows) by species (columns).
+For each cell that is used on a given species plant map, a description of the botanical parts included in the "flower part" is given as well as the flowering stage at which the flower part is harvested, if it is not obvious.
+
+flowerParts
 Harvested and weighed flower parts, including collections from tagged individuals (once mature or at time of harvest) and from other individuals in the population (to estimate weight of specific plant parts).
@@
 
-\subsection{Flower\_parts}
-Brief descriptions of each data column in the file flower\_parts, including units.
+\subsection{flowerParts\_metadata}
+Brief descriptions of each data column in the file flowerParts, including units.
 
@@
 
-Flowering\_cat\_lookup\_table
-This file contains a matrix of plant parts (rows) by species (columns).
-For each cell that is used on a given species plant map, the meaning of the values in the spreadsheet titled "reproduction" are indicated in this spreadsheet.
-Possible method are (1) count, indicating that the numbers represent simple counts; (2) count\_by\_length, indicating that the length of stem or cone covered with buds, flowers or fruit is measured; (3) regress\_by\_dim, indicating that the dimensions of the flowering part are measured and must be converted to a dry mass using a regression equation; and (4) volume, indicating that the height and diameter of the flowering part are given and must be converted to a dry mass using the calculated volume of the flowering part multiplied by the average density of the flowering part.
+Individuals
+This file contains a list of all plants harvested at the 7 Kuring'gai fieldsites.
+For each individual it includes basic information about each individual - tag number, age, site, whether the plant was alive at the time of harvest, and information on which calculations use this individual's data.
+The data itself is contained in other files.
 
-flowering\_categories\_descriptions
-This files contains a matrix of plant parts (rows) by species (columns).
-For each cell that is used on a given species plant map, a description of the botanical parts included in the "flower part" is given as well as the flowering stage at which the flower part is harvested, if it is not obvious.
+\subsection{Individuals\_metadata}
+Brief descriptions of each data column in the file Individuals, including units.
 
-LMA
-This file contains data on leaf area and leaf weight for each of the 14 species at each of the 6 sites.
-For each species by site combination, leaves were collected from 4-5 individuals (occasionally fewer).
-A pooled sample was then scanned for leaf area and weighed dry.
-Three leaf ages were collected for each species; for species where leaf lifespan is short, only two leaf cohorts could be collected.
-For juvenile individuals, where leaf size and shape changes rapidly with each new flush of leaves, it was noted additional descriptions of the leaves were made.
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/Individuals_meta.csv")
+@
 
-LMA\_metadata
-Brief descriptions of each data column in the file LMA\_metadata, including units.
-
-MultiplierTable
+multiplierTable
 Lookup table indicating, for each species by flower part combination, if the investment per part is for a single (1) or multiple propagules, defined as either a mature fruit or a seed, depending on what is the dispersal unit for each species.
@@
 
-Reproduction
-The reproduction spreadsheet provides both verbal and numeric descriptions of reproduction at each census between April-June 2012, when the plants were first tagged, until April-June 2013, when the plants were harvested.
+reproduction
+The reproduction spreadsheet provides both verbal and numeric descriptions of reproduction at each census between April-June 2012 (or June 2013 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were first tagged, until April-June 2013 (or June 2014 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were harvested.
 There is a separate row of data for each individual, at each of the 18 censuses.
@@
 In that case, a flower part must have a predecessor on that specific diagram to be considered "pre-existing".
+
 Each of the many plant parts are listed as column headers.
@@
 As an example, if at one census there were 50 PHPH (Phyllota phylicoides) buds recorded and at the next stage, 30 PHPH flowers, 30 of the 50 buds progressed from being buds to being flowers, while the remaining 20 buds were either shed or are still buds.
-The numbers entered in the cell correspond to either counts, lengths, or dimensions, depending on the method indicated in the file titled "Flowering\_cat\_lookup\_table".
+The numbers entered in the cell correspond to either counts, lengths, or dimensions, depending on the method indicated in the file titled "floweringCategories".
 
-Seed multiplier
-Table indicating if final investment is in units of a single seed (1) or multiple seeds.
-For species where the final propagule contains multiple seeds, a multiplier is included so that total investment in seeds/fruits (i.e.
-propagules) can be scaled to a single seed.
+\subsection{reproduction\_metadata}
+Brief descriptions of the first set of data columns in the file reproduction.
 
-Sites
-Tables of sites used in study.
-Includes site names used in other spreadsheets, date of fire, fire year, as defined by NSW fire layers (which would be the best indicator of germination date), and UTM coordinates for each site.
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/reproduction_meta.csv")
+@
 
-Species\_names
+seedsize
+
+\subsection{seedsize\_metadata}
+Brief descriptions of the first set of data columns in the file seedsize, including units.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/seedsize_meta.csv")
+@
+
+sites
+Tables of sites used in study. Includes site names used in other spreadsheets, date of fire, fire year, as defined by NSW fire layers, and UTM coordinates for each site.
+
+\subsection{sites\_metadata}
+Brief descriptions of the first set of data columns in the file sites
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/sites_meta.csv")
+@
+
+species
 Table of species included in study. Includes 4-letter code names used in other spreadsheets, scientific names, family names, and common names.
-
-wood\_density
-Data on wood density for each species.
-Wood samples were collected from sufficiently large plants to ensure replicable displacement values.
-Bark and pith were both removed from the samples before determining volume.
-Multiple methods were tested, with numbers most consistent using the "tweezer" method.
-Using this method, samples were held with tweezers and just submerged.
-Using this method, the balance stabilized rapidly and repeatedly.
-These measurements were all made using the Mettler balance.
-Of the measurements made using the "pipette\_suspension" method, where a section of wood was submerged inside a suspended pipette, only those made on the Sartorius balance are believable.
-
-wood\_density\_meta
-Brief descriptions of each data column in the file wood\_density\_meta, including units.
 
@@
 
-Species differ from one another in
+Each species uses notably different algorithms to determine reproductive tissue investment, as each species forms different reproductive tissues and different methods are practical for recording each species' reproductive investment in the field.
+For some reproductive parts a simple count is pracical, while for species with a large number of buds (or flowers or fruit) that are regularly spaced along branches, the length of stem covered in buds is a better measure.
+For species that form cones, the cones can be notably different in size and each cone's dimensions must be recorded.
 
@@
 
-For each species provide
+For each species we established a list of different reproductive tissue parts and mapped how these parts developed through time.
+As the reproductive cycle progresses, tissue parts were repeatedly split into two (or more) parts.
+For instance, a bud, once open, divides into being petals + stamens, a sepal, and a stigma.
+As a pollinated stigma develops into a fruit, it will be further divided into seed, seed pod, and potentially additional parts.
+This is shown in the map for each species.
+
+The accompanying table for each species provides a list of plant parts, a description of exactly what tissues are included in each plant part and at what developmental stage, the method whereby the count and mass of the plant parts is measured, and the number of ovules in each unit of plant part.
 
@@
 
-<<echo=FALSE,results='asis'>>=
-headers <- as.data.frame(matrix(vector(), 3,4,
-                dimnames=list(c(), c("A","B","C","D"))),
-                stringsAsFactors=F)
-headers[1,] <- c("","Proportion","Proportion","Proportion")
-headers[2,] <- c("","pollen-attraction","provisioning","success")
-headers[3,] <- c("","investment to","investment to","investment to")
-
-print(xtable(headers,
-             hline.after=c(-1),
-             align='p{0.1cm}p{11.5cm}|p{3cm}|p{3cm}|p{3cm}'),
-        sanitize.text.function=I,
-        , table.placement = "H"
-        , caption.placement = "top"
-        , include.rownames = FALSE
-        , include.colnames = FALSE
-        , size = "small"
-        , floating = FALSE)             
-@
-
 <<echo=FALSE, results='asis', warning=FALSE>>=
@@
   data <- select(file,species,embryo_endo_costs, scaled_seed_count,scaled_ovule_count,
-                 scaled_pollen_attract_costs,choosiness2,prop_prepollen_success, prop_prepollen_discarded,
+                 scaled_pollen_attract_costs,choosiness,prop_prepollen_success, prop_prepollen_discarded,
                  prop_postpollen_success,prop_postpollen_discarded, prop_pollen_attract_vs_success,prop_provisioning_vs_success)
@@
 
-TableS2 <- make_table_species_values_for_allocation_seedsize_table(SummarySpp[["mean"]])
+TableS15 <- make_table_species_values_for_allocation_seedsize_table(SummarySpp[["mean"]])
 
-names(TableS2) <- c("species","embryo and endosperm costs","scaled seed count","scaled ovule count","scaled pollen-attraction costs","choosiness","to success","to discarded","to success","to discarded","to pollen-attraction","to provisioning")
+names(TableS15) <- c("species","embryo and endosperm costs","scaled seed count","scaled ovule count","scaled pollen-attraction costs","choosiness","to success","to discarded","to success","to discarded","to pollen-attraction","to provisioning")
 
 for (i in 2:12) {
-TableS2[,i] <- format(TableS2[,i],digits=3,nsmall=2)
+TableS15[,i] <- format(TableS15[,i],digits=3,nsmall=2)
 }
 
-TableS2$species  <- paste("\\textit{",unique(TableS2$species),"}", sep="")
+TableS15$species  <- paste("\\textit{",unique(TableS15$species),"}", sep="")
+@
 
-print(xtable(TableS2,
-               hline.after=c(1),
-               align='p{0.1cm}p{4cm}|p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}',
-               caption="Species values for data plotted in Figure 2",
-               sanitize.text.function=I,
-        , table.placement = "H"
-        , caption.placement = "top"
+\begin{table}[H]
+\centering
+\caption{Species values for data plotted in Figure 2, shifts in reproductive tissue allocation with seed size.}
+\label{tab:species}
+\begin{tabular}{p{0.1cm}p{4cm}|p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
+\hline
+& \multicolumn{8}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
+& \multicolumn{8}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
+& \multicolumn{8}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
+<<echo=FALSE, results='asis', warning=FALSE>>=
+print(xtable(TableS15)
+        , sanitize.text.function=I
         , include.rownames = FALSE
-        , include.colnames = TRUE
-        , size = "small"
-        , floating = FALSE))
+        , include.colnames = TRUE,
+        only.contents=TRUE)
 @
-Table S2. Species values for data plotted in Figure 2, shifts in reproductive tissue allocation with seed size.
+\end{tabular}
+\end{table}
 
-<<echo=FALSE,results='asis'>>=
-headers <- as.data.frame(matrix(vector(), 3, 3,
-                dimnames=list(c(), c("A","B","C"))),
-                stringsAsFactors=F)
-headers[1,] <- c("","Total reproductive investment","Total reproductive investment")
-headers[2,] <- c("","vs","vs")
-headers[3,] <- c("","propagule investment","flower investment")
+\clearpage
+<<echo=FALSE, results='asis', warning=FALSE>>=
+make_table_RA_shifts_with_age <- function() {
+  xvar <- "repro_inv"
+  yvar <- "accessory_per_seed"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-print(xtable(headers,
-             hline.after=c(-1),
-             align='p{0.1cm}p{4cm}|c|c'),
-        sanitize.text.function=I,
-        , table.placement = "H"
-        , caption.placement = "top"
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+  accessory_vs_RE <- lines(fit$groupsummary)
+  accessory_vs_RE <- dplyr::select(accessory_vs_RE,group,n,r2,pval)
+
+  xvar <- "total_weight_0"
+  yvar <- "accessory_per_seed"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+  accessory_vs_size <- lines(fit$groupsummary)
+  accessory_vs_size <- dplyr::select(accessory_vs_size,group,n,r2,pval)
+
+  xvar <- "age"
+  yvar <- "accessory_per_seed"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+  accessory_vs_age <- lines(fit$groupsummary)
+  accessory_vs_age <- dplyr::select(accessory_vs_age,group,n,r2,pval)
+
+  TableS16 <- merge(accessory_vs_RE,accessory_vs_size,by="group")
+  TableS16 <- merge(TableS16,accessory_vs_age,by="group")
+
+  names(TableS16) <- c("species","n","r$^2$","p","n","r$^2$","p","n","r$^2$","p")
+
+  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  TableS16$species <-  paste("\\textit{",species,"}", sep="")
+
+  TableS16
+}
+
+TableS16 <- make_table_RA_shifts_with_age()
+
+for(i in c(2,3,5,6,8,9)){
+  TableS16[,i] <- format(TableS16[,i],digits=2,nsmall=2)
+}
+for(i in c(4,7,10)){
+  TableS16[,i] <- format_p(TableS16[,i])
+}
+
+TableS16$species  <- paste("\\textit{",unique(TableS16$species),"}", sep="")
+@
+
+\begin{table}[H]
+\centering
+\caption{Shifts in accessory costs with shifts in age, plant size, or reproductive effort.}
+\label{tab:propagule_invest_vs_repro}
+\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
+\hline
+& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
+& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c}{vs. plant mass (mg)}& \multicolumn{3}{c}{vs. age} \\
+<<echo=FALSE, results='asis', warning=FALSE>>=
+print(xtable(TableS17)
+        , sanitize.text.function=I
         , include.rownames = FALSE
-        , include.colnames = FALSE
-        , size = "small"
-        , floating = FALSE)             
+        , include.colnames = TRUE,
+        only.contents=TRUE)
 @
+\end{tabular}
+\end{table}
+
+\clearpage
+
+% lines that previously created tableS16 - will delete once new version working
+% print(xtable(TableS2,
+%                hline.after=c(1),
+%                align='p{0.1cm}p{4cm}|p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}',
+%                caption="Species values for data plotted in Figure 2",
+%                sanitize.text.function=I,
+%         , table.placement = "H"
+%         , caption.placement = "top"
+%         , include.rownames = FALSE
+%         , include.colnames = TRUE
+%         , size = "small"
+%         , floating = FALSE))
 
@@
   acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
+  names(acc_slopes) <- c("species","n","r$^2$","p", "n","r$^2$","p")
   species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
   acc_slopes$species <-  paste("\\textit{",species,"}", sep="")
-  names(acc_slopes) <- c("species","n","r$^2$","p", "n","r$^2$","p")
+
   acc_slopes
@@
 
-TableS3 <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)
+TableS17 <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)
 
 for(i in c(2,3,5,6)){
-  TableS3[,i] <- format(TableS3[,i],digits=2,nsmall=2)
+  TableS17[,i] <- format(TableS17[,i],digits=2,nsmall=2)
 }
 for(i in c(4,7)){
-  TableS3[,i] <- format_p(TableS3[,i])
+  TableS17[,i] <- format_p(TableS17[,i])
 }
@@
 <<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS3)
+print(xtable(TableS16)
         , sanitize.text.function=I
@@
 
-Table S4. Shifts in accessory costs with shifts in age, plant size, or reproductive effort. 
+\clearpage
+
+<<echo=FALSE, results='asis', warning=FALSE>>=
+make_table_buds_vs_size <- function() {
+  xvar <- "total_weight_0"
+  yvar <- "ovule_count"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+  TableS18 <- lines(fit$groupsummary)
+  TableS18 <- dplyr::select(TableS18,group,n,r2,pval)
+
+  names(TableS18) <- c("species","n","r$^2$","p")
+
+  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  TableS18$species <-  paste("\\textit{",species,"}", sep="")
+
+  TableS18
+}
+
+TableS18 <- make_table_buds_vs_size()
+
+for(i in c(2,3)){
+  TableS18[,i] <- format(TableS18[,i],digits=2,nsmall=2)
+}
+for(i in c(4)){
+  TableS18[,i] <- format_p(TableS18[,i])
+}
+
+TableS18$species  <- paste("\\textit{",unique(TableS18$species),"}", sep="")
+@
+
+\begin{table}[H]
+\centering
+\caption{Count of buds initiated is well predicted by plant size}
+\label{tab:propagule_invest_vs_repro}
+\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}}
+\hline
+<<echo=FALSE, results='asis', warning=FALSE>>=
+print(xtable(TableS17)
+        , sanitize.text.function=I
+        , include.rownames = FALSE
+        , include.colnames = TRUE,
+        only.contents=TRUE)
+@
+\end{tabular}
+\end{table}
+
 \clearpage

### 2017-02-08 ms/Accessory/Wenk-RA-SI_NOT_FOR_ACCESSORY.Rnw
work on supplementary material for Accessory ms. Added metadata files for several data files, worked on figures for SuppMaterial.

\subsection{Harvest}

Allometric data for plants harvested in autumn 2013, including weights and diameters of each harvested segment. Briefly, this dataset includes data on 14 dominant species that are all obligate seeders following a fire. For each species, data were collected from 7 replicate individuals at each of 6 sites, or the subset of those sites on which a given species occurred. The sites represent a chronosequence created by a patchy fire history in the area; all species germinate within a year of a fire, allowing fire history to be used as a proxy for age. When the plants were harvested, they were divided into multiple segments along the stem leader. The diameter was measured at each cut in autumn 2012, when the plants were tagged, and in autumn 2013, at harvest.  For each segment, the dry weights of the leaves and stems were determined separately.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/harvest_meta.csv")
@

  2013\_Kuringgai\_harvest-meta
Brief descriptions of each data column in the file 2013\_Kuringgai\_harvest, including units.

LMA
This file contains data on leaf area and leaf weight for each of the 14 species at each of the 6 sites. For each species by site combination, leaves were collected from 4-5 individuals (occasionally fewer). A pooled sample was then scanned for leaf area and weighed dry. Three leaf ages were collected for each species; for species where leaf lifespan is short, only two leaf cohorts could be collected. For juvenile individuals, where leaf size and shape changes rapidly with each new flush of leaves, it was noted additional descriptions of the leaves were made.

\subsection{LMA\_metadata}
Brief descriptions of each data column in the file LMA, including units.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/LMA_meta.csv")
@

woodDensity
Data on wood density for each species. Wood samples were collected from sufficiently large plants to ensure replicable displacement values. Bark and pith were both removed from the samples before determining volume. Multiple methods were tested, with numbers most consistent using the "tweezer" method. Using this method, samples were held with tweezers and just submerged. Using this method, the balance stabilized rapidly and repeatedly. These measurements were all made using the Mettler balance. Of the measurements made using the "pipette\_suspension" method, where a section of wood was submerged inside a suspended pipette, only those made on the Sartorius balance are believable.

\subsection{woodDensity\_meta}
Brief descriptions of each data column in the file woodDensity\_meta, including units.

<<echo=FALSE,results='asis'>>=
  print_table_metadata("../../data/woodDensity_meta.csv")
@

### 2017-02-14 Analysis-accessory.Rmd
work on supplementary material for Accessory ms. Added metadata files for several data files, worked on figures for SuppMaterial.
work on Accessory manuscript - Supplementary Information should currently compile. Tables should be final (other than sequence). Small amount more worked needed in descriptions at beginning.
next version of manuscript complete except very end of Intro

@@
 
+#DISCUSSION - slope of seed size vs repro costs not different from values reported in Lord; i.e. testing slope against the 1.1 she had.
+
+slopes <- sma(repro_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1.1173,method="SMA", log="xy")
+
+checking_slope <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
+
 yvar <- "ovule_count"
@@
 results
+
 ```
@@
 
-plot(repro_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), xlim=c(.02,10000), ylab="total per seed accessory costs (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$repro_costs,SummarySpp[["se"]]$accessory_costs)
+#repro costs
 slopes <- sma(repro_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-summary(slopes)
-
-plot(prop_pollen_attract_vs_all_repro_all_repro~ seedset,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy",cex=1.5)
 
@@
 
-plot(success_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="seed costs (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$success_costs,SummarySpp[["se"]]$success_costs)
+#accessory costs
+slopes <- sma(accessory_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+#success costs
 slopes <- sma(success_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
+
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+#pollen attraction costs
+slopes <- sma(pollen_attract_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+#provisioning costs
+slopes <- sma(provisioning_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+#discarded costs
+slopes <- sma(discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+#discarded prepollen costs
+slopes <- sma(prepollen_discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+#discarded postpollen costs
+slopes <- sma(postpollen_aborted_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+
 acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-plot(pollen_attract_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="prepollen success costs (mg/seed)",xlab="",cex=1.5)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$pollen_attract_costs,SummarySpp[["se"]]$pollen_attract_costs)
-slopes <- sma(pollen_attract_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-plot(provisioning_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="dispersal & packaging accessory costs (mg/seed)",xlab="",cex=1.5)
-slopes <- sma(provisioning_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$provisioning_costs,SummarySpp[["se"]]$provisioning_costs)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-mtext(text="seed size (mg)",side=1,line=1.5,outer=TRUE)
-
-plot(discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all discarded costs (mg/seed)",xlab="",cex=1.5)
-slopes <- sma(discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$discarded_costs,SummarySpp[["se"]]$discarded_costs)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-plot(prepollen_all_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="all pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prepollen_all_costs,SummarySpp[["se"]]$prepollen_all_costs)
-slopes <- sma(prepollen_all_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-plot(prepollen_discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted pre-pollination costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prepollen_discarded_costs,SummarySpp[["se"]]$prepollen_discarded_costs)
-slopes <- sma(prepollen_discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-plot(postpollen_aborted_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),col=col.spp(species),pch=16,log="xy", ylim=c(.02,10000), ylab="aborted during provisioning costs (mg/seed)",xlab="",cex=1.5,xaxt="n")
-y.error.bars(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$postpollen_aborted_costs,SummarySpp[["se"]]$postpollen_aborted_costs)
-slopes <- sma(postpollen_aborted_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-abline(slopes$groupsummary["Int"][[1]],slopes$groupsummary["Slope"][[1]])
-abline(slopes$groupsummary["Int"][[1]],1,lty=2)
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-acc_by_species$variable = c("total accessory costs","seed costs","pollen attraction costs","provisioning costs", "failed tissues costs","all pre-pollen costs per seed","failed pre-pollination costs","failed provisioning costs")
+acc_by_species$variable = c("total reproductive costs","total accessory costs","seed costs","pollen attraction costs","provisioning costs", "failed tissues costs","failed pre-pollination costs","failed provisioning costs")
 
@@
 axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
-mtext(text="b.  Trade-off 1:",side=3,outer=FALSE,adj=0,line=1.6)
+mtext(text="Trade-off 1:",side=3,outer=FALSE,adj=0,line=1.6)
 mtext(text="Seed count-reproductive costs",side=3,outer=FALSE,adj=0,line=0.7)
@@
 axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
-mtext(text="c.  Trade-off 2.",side=3,outer=FALSE,adj=0,line=1.6)
+mtext(text="Trade-off 2.",side=3,outer=FALSE,adj=0,line=1.6)
 mtext(text="Ovule count-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
@@
 axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
-mtext(text="d.  Trade-off 3.",side=3,outer=FALSE,adj=0,line=1.6)
+mtext(text="Trade-off 3.",side=3,outer=FALSE,adj=0,line=1.6)
 mtext(text="Choosiness-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
@@
 
+names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule","n_flower","r2_flower","p_flower")
+
 write.csv(acc_slopes, file="ms/Accessory/output/Table_S1_extra_flower_invest_vs_all_repro_inv.csv",row.names=FALSE)

### 2017-02-14 ms/Accessory/Wenk-Accessory-SI.Rnw
work on Accessory manuscript - Supplementary Information should currently compile. Tables should be final (other than sequence). Small amount more worked needed in descriptions at beginning.
next version of manuscript complete except very end of Intro

@@
   xvar <- "repro_inv"
-  yvar <- "accessory_per_seed"
+  yvar <- "accessory_costs"
   data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
   xvar <- "total_weight_0"
-  yvar <- "accessory_per_seed"
+  yvar <- "accessory_costs"
   data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
   xvar <- "age"
-  yvar <- "accessory_per_seed"
+  yvar <- "accessory_costs"
   data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
@@
 
-TableS16$species  <- paste("\\textit{",unique(TableS16$species),"}", sep="")
 @
@@
 <<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS17)
+print(xtable(TableS16)
         , sanitize.text.function=I
@@
 <<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS16)
+print(xtable(TableS17)
         , sanitize.text.function=I
@@
 <<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS17)
+print(xtable(TableS18)
+        , sanitize.text.function=I
+        , include.rownames = FALSE
+        , include.colnames = TRUE,
+        only.contents=TRUE)
+@
+\end{tabular}
+\end{table}
+
+<<echo=FALSE, results='asis', warning=FALSE>>=
+make_table_Table2_using_propagule <- function() {
+slopes <- sma(repro_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
+
+slopes <- sma(accessory_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(success_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(pollen_attract_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(provisioning_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(prepollen_discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(postpollen_aborted_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+acc_by_species$variable = c("total reproductive costs","total accessory costs","seed costs","pollen attraction costs","provisioning costs", "failed tissues costs","failed pre-pollination costs","failed provisioning costs")
+
+acc_by_species$Slope <- format(acc_by_species$Slope,nsmall=2,digits=2)
+acc_by_species$Slope_lowCI <- format(acc_by_species$Slope_lowCI,nsmall=2,digits=2)
+acc_by_species$Slope_highCI <- format(acc_by_species$Slope_highCI,nsmall=2,digits=2)
+
+acc_by_species$slope2 <- paste(acc_by_species$Slope," (",acc_by_species$Slope_lowCI," - ",acc_by_species$Slope_highCI,")",sep="")
+
+acc_by_species$r2 <- format(acc_by_species$r2,digits=2)
+acc_by_species$pval <- format_p(acc_by_species$pval)
+acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=2)
+acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
+}
+TableS19 <- make_table_Table2_using_propagule()
+@
+\begin{table}[H]
+\centering
+\caption{Scaling of reproductive tissue costs with total propagule size}
+\label{tab:propagule_invest_vs_repro}
+\begin{tabular}{p{4cm}|x{.94cm}x{3cm}x{1.5cm}}
+\hline
+<<echo=FALSE, results='asis', warning=FALSE>>=
+print(xtable(TableS19)
         , sanitize.text.function=I

### 2017-02-14 ms/Accessory/Wenk-Accessory-SI.Rnw
few more changes to Supplementary Information file

@@
 
+All computations implemented in \textsc{r} \citep{R-2015}.
+
+<<echo=FALSE, results='asis', warning=FALSE>>=
+
+make_table_species_values_for_allocation_seedsize_table <- function(file) {
+  data <- select(file,species,embryo_endo_costs, scaled_seed_count,scaled_ovule_count,
+                 scaled_pollen_attract_costs,choosiness,prop_prepollen_success, prop_prepollen_discarded,
+                 prop_postpollen_success,prop_postpollen_discarded, prop_pollen_attract_vs_success,prop_provisioning_vs_success)
+  data$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  data
+}
+
+TableS15 <- make_table_species_values_for_allocation_seedsize_table(SummarySpp[["mean"]])
+
+names(TableS15) <- c("species","embryo and endosperm costs","scaled seed count","scaled ovule count","scaled pollen-attraction costs","choosiness","to success","to discarded","to success","to discarded","to pollen-attraction","to provisioning")
+
+for (i in 2:12) {
+TableS15[,i] <- format(TableS15[,i],digits=3,nsmall=2)
+}
+
+TableS15$species  <- paste("\\textit{",unique(TableS15$species),"}", sep="")
+@
+
+\begin{table}[H]
+\centering
+\caption{Species values for data plotted in Figure 2, shifts in reproductive tissue allocation with seed size.}
+\label{tab:species}
+\begin{tabular}{p{0.1cm}p{4cm}|p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
+\hline
+& \multicolumn{8}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
+& \multicolumn{8}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
+& \multicolumn{8}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
+<<echo=FALSE, results='asis', warning=FALSE>>=
+print(xtable(TableS15)
+        , sanitize.text.function=I
+        , include.rownames = FALSE
+        , include.colnames = TRUE,
+        only.contents=TRUE)
+@
+\end{tabular}
+\end{table}
+
+\clearpage
+<<echo=FALSE, results='asis', warning=FALSE>>=
+make_table_RA_shifts_with_age <- function() {
+  xvar <- "repro_inv"
+  yvar <- "accessory_costs"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+  accessory_vs_RE <- lines(fit$groupsummary)
+  accessory_vs_RE <- dplyr::select(accessory_vs_RE,group,n,r2,pval)
+
+  xvar <- "total_weight_0"
+  yvar <- "accessory_costs"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+  accessory_vs_size <- lines(fit$groupsummary)
+  accessory_vs_size <- dplyr::select(accessory_vs_size,group,n,r2,pval)
+
+  xvar <- "age"
+  yvar <- "accessory_costs"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
+  accessory_vs_age <- lines(fit$groupsummary)
+  accessory_vs_age <- dplyr::select(accessory_vs_age,group,n,r2,pval)
+
+  TableS16 <- merge(accessory_vs_RE,accessory_vs_size,by="group")
+  TableS16 <- merge(TableS16,accessory_vs_age,by="group")
+
+  names(TableS16) <- c("species","n","r$^2$","p","n","r$^2$","p","n","r$^2$","p")
+
+  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  TableS16$species <-  paste("\\textit{",species,"}", sep="")
+
+  TableS16
+}
+
+TableS16 <- make_table_RA_shifts_with_age()
+
+for(i in c(2,3,5,6,8,9)){
+  TableS16[,i] <- format(TableS16[,i],digits=2,nsmall=2)
+}
+for(i in c(4,7,10)){
+  TableS16[,i] <- format_p(TableS16[,i])
+}
+
+@
+
+\begin{table}[H]
+\centering
+\caption{Shifts in accessory costs with shifts in age, plant size, or reproductive effort.}
+\label{tab:propagule_invest_vs_repro}
+\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
+\hline
+& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
+& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c}{vs. plant mass (mg)}& \multicolumn{3}{c}{vs. age} \\
+<<echo=FALSE, results='asis', warning=FALSE>>=
+print(xtable(TableS16)
+        , sanitize.text.function=I
+        , include.rownames = FALSE
+        , include.colnames = TRUE,
+        only.contents=TRUE)
+@
+\end{tabular}
+\end{table}
+
+\clearpage
+
+% lines that previously created tableS16 - will delete once new version working
+% print(xtable(TableS2,
+%                hline.after=c(1),
+%                align='p{0.1cm}p{4cm}|p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}',
+%                caption="Species values for data plotted in Figure 2",
+%                sanitize.text.function=I,
+%         , table.placement = "H"
+%         , caption.placement = "top"
+%         , include.rownames = FALSE
+%         , include.colnames = TRUE
+%         , size = "small"
+%         , floating = FALSE))
+
+<<echo=FALSE, warning=FALSE>>=
+
+make_table_propagule_invest_vs_all_repropro_inv <- function(SummaryInd) {
+  mod_propagule_inv_all <- sma(repro_inv~propagule_inv,data=SummaryInd,log="xy",method="SMA")
+  mod_flower_inv_all <- sma(repro_inv~flower_inv,data=SummaryInd,log="xy",method="SMA")
+
+  yvar <- "repro_inv"
+  xvar <- "propagule_inv"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=mod_propagule_inv_all$groupsummary["Slope"][[1]],elev.test=mod_propagule_inv_all$coef[[1]][1,1])
+  results <- fit$groupsummary
+  acc_slopes <- dplyr::select(results,group,n,r2,pval)
+  names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule")
+
+  yvar <- "repro_inv"
+  xvar <- "flower_inv"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
+  results <- fit$groupsummary
+  acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
+  names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
+  acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
+  names(acc_slopes) <- c("species","n","r$^2$","p", "n","r$^2$","p")
+  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  acc_slopes$species <-  paste("\\textit{",species,"}", sep="")
+
+  acc_slopes
+}
+
+TableS17 <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)
+
+for(i in c(2,3,5,6)){
+  TableS17[,i] <- format(TableS17[,i],digits=2,nsmall=2)
+}
+for(i in c(4,7)){
+  TableS17[,i] <- format_p(TableS17[,i])
+}
+@
+
+\begin{table}[H]
+\centering
+\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight (mg) $\times$ bud count'}
+\label{tab:propagule_invest_vs_repro}
+\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
+\hline
+& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
+& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
+<<echo=FALSE, results='asis', warning=FALSE>>=
+print(xtable(TableS17)
+        , sanitize.text.function=I
+        , include.rownames = FALSE
+        , include.colnames = TRUE,
+        only.contents=TRUE)
+@
+\end{tabular}
+\end{table}
+
+\clearpage
+
+<<echo=FALSE, results='asis', warning=FALSE>>=
+make_table_Table2_using_propagule <- function() {
+slopes <- sma(repro_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
+
+slopes <- sma(accessory_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(success_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(pollen_attract_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(provisioning_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(prepollen_discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+slopes <- sma(postpollen_aborted_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+
+acc_by_species$variable = c("total reproductive costs","total accessory costs","seed costs","pollen attraction costs","provisioning costs", "failed tissues costs","failed pre-pollination costs","failed provisioning costs")
+
+acc_by_species$Slope <- format(acc_by_species$Slope,nsmall=2,digits=2)
+acc_by_species$Slope_lowCI <- format(acc_by_species$Slope_lowCI,nsmall=2,digits=2)
+acc_by_species$Slope_highCI <- format(acc_by_species$Slope_highCI,nsmall=2,digits=2)
+
+acc_by_species$slope2 <- paste(acc_by_species$Slope," (",acc_by_species$Slope_lowCI," - ",acc_by_species$Slope_highCI,")",sep="")
+
+acc_by_species$r2 <- format(acc_by_species$r2,digits=2)
+acc_by_species$pval <- format_p(acc_by_species$pval)
+acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=2)
+acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
+}
+TableS19 <- make_table_Table2_using_propagule()
+@
+\begin{table}[H]
+\centering
+\caption{Scaling of reproductive tissue costs with total propagule size}
+\label{tab:propagule_invest_vs_repro}
+\begin{tabular}{p{4cm}|x{.94cm}x{3cm}x{1.5cm}}
+\hline
+<<echo=FALSE, results='asis', warning=FALSE>>=
+print(xtable(TableS19)
+        , sanitize.text.function=I
+        , include.rownames = FALSE
+        , include.colnames = TRUE,
+        only.contents=TRUE)
+@
+\end{tabular}
+\end{table}
+
+\clearpage
+
+<<echo=FALSE, results='asis', warning=FALSE>>=
+make_table_buds_vs_size <- function() {
+  xvar <- "total_weight_0"
+  yvar <- "ovule_count"
+  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+
+  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
+  TableS18 <- lines(fit$groupsummary)
+  TableS18 <- dplyr::select(TableS18,group,n,r2,pval)
+
+  names(TableS18) <- c("species","n","r$^2$","p")
+
+  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  TableS18$species <-  paste("\\textit{",species,"}", sep="")
+
+  TableS18
+}
+
+TableS18 <- make_table_buds_vs_size()
+
+for(i in c(2,3)){
+  TableS18[,i] <- format(TableS18[,i],digits=2,nsmall=2)
+}
+for(i in c(4)){
+  TableS18[,i] <- format_p(TableS18[,i])
+}
+
+TableS18$species  <- paste("\\textit{",unique(TableS18$species),"}", sep="")
+@
+
+\begin{table}[H]
+\centering
+\caption{Count of buds initiated is well predicted by plant size}
+\label{tab:propagule_invest_vs_repro}
+\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}}
+\hline
+<<echo=FALSE, results='asis', warning=FALSE>>=
+print(xtable(TableS18)
+        , sanitize.text.function=I
+        , include.rownames = FALSE
+        , include.colnames = TRUE,
+        only.contents=TRUE)
+@
+\end{tabular}
+\end{table}
+
+\clearpage
+
 \section{Details on data from main text}
 
-Describe contents of csv files attached
+\section{Investment categories}
 
-\section{Overview of methods for estimating reproductive allocation}
+accessoryParts.yml
+This file contains, for each species, lists of reproductive tissues that fall into various tissue categories=.
+These categories are then used to calculate the reproductive investment in the key reproductive tissue categories, (1) pollen-attraction tissues aborted prior to provisioning; (2) pollen-attraction tissues associated with flowers that form mature seeds; (3) provisioning tissues aborted prior to the formation of a mature seed; (4) packaging and dispersal tissues associated with a mature seed; (5) the mature seed itself.
+Dividing reproductive investment into these categories requires, for each tissue type, knowing the count of parts that reach the key stages (pollinator-ready, onset of provisioning, mature seed) and the mass of parts at each stage.
 
-All computations implemented in \textsc{r} \citep{R-2015}.
+\subsection{accessoryParts\_metadata}
+Brief descriptions of each reproductive parts category in the file accessoryParts.
 
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/accessoryParts_meta.csv")
+@
+
+\subsection{investment categories by species}
+List for each species of reproductive tissue types included in each of the investment categories
+<<echo=FALSE,results='asis'>>=
+  @@@("../../data/accessoryParts.yml")
+@
+
+\section{Details about input files}
 List of data files.
@@
 
-What is measured by individual and species
-
-- for flower parts, the default is at the species level unless the actual piece was collected; Plant parts that were collected on an individual is recorded in the file flowerParts
-- all reproductive output is measured at the individual
-
-Census
-
-- measurements indicating Counts of parts on each individual\\
-- use species level conversions to get number of parts by individual * census\\
-- algorithm which estimates demography of numbers of parts, with respect to map of progression\\
-- convert numbers into weights (BAER\_Investment -- > 4 dataframes in a list, but only FD (= final development of parts) is used, others for error checking)\\
-- group into different categories (BAER\_reproductive costs -- by function `ReproductiveCosts')\\
-  - investment: weight (mg)\\
-  - count (number)\\
-  - costs (mg/successful seed)\\
-  - reference back to groups in paper and in accessoryParts.yml\\
-- at individual level, calculate various proportions and metrics, after combining growth, reproduction, traits ( in `combine\_by\_individual')\\
-
-\section{Investment categories}
-
-accessoryParts.yml
-This file contains, for each species, lists of reproductive tissues that fall into various tissue categories=.
-These categories are then used to calculate the reproductive investment in the key reproductive tissue categories, (1) pollen-attraction tissues aborted prior to provisioning; (2) pollen-attraction tissues associated with flowers that form mature seeds; (3) provisioning tissues aborted prior to the formation of a mature seed; (4) packaging and dispersal tissues associated with a mature seed; (5) the mature seed itself.
-Dividing reproductive investment into these categories requires, for each tissue type, knowing the count of parts that reach the key stages (pollinator-ready, onset of provisioning, mature seed) and the mass of parts at each stage.
-
-\subsection{accessoryParts\_metadata}
-Brief descriptions of each reproductive parts category in the file accessoryParts.
-
-<<echo=FALSE,results='asis'>>=
-  print_table_metadata("../../data/accessoryParts_meta.csv")
-@
-
-\section{Details about input files}
 floweringCategories
@@
 
+\section{Overview of methods for estimating reproductive allocation}
+
+\subsection{Overview of plant maps}
+
+For each species we established a list of different reproductive tissue parts and mapped how these parts developed through time.
+As the reproductive cycle progresses, tissue parts were repeatedly split into two (or more) parts.
+For instance, a bud, once open, divides into being petals + stamens, a sepal, and a stigma.
+As a pollinated stigma develops into a fruit, it will be further divided into seed, seed pod, and potentially additional parts.
+Along the developmental trajectory, various reproductive tissues are designated as reaching their final development stage, the point in the reproductive cycle where they no longer increase in mass.
+For some tissues, such as petals, final development is reached long before a mature seed forms, while other tissues, such as the seed and seedpod do not reach final development until the end of the developmental trajectory.
+
+Each species reproductive tissue development initiates with a bud or inflorescence bud, which increases in size and is divided into multiple tissue types several times during development.
+The central development axis terminates with the formation of a mature seed, while side branches end in fully developed tissues (such as petals, calyx, pedicel) and aborted tissues (aborted seeds, aborted fruit) at the point where they cease to increase in mass.
+The developmental flowchart for each species is shown in the maps in the next section.
+
+The accompanying table for each species provides a list of plant parts, a description of exactly what tissues are included in each plant part and at what developmental stage, the method whereby the count and mass of the plant parts is measured, and the number of ovules in each unit of plant part.
+
+\subsection{How the census is completed for each part}
+
+The count of each reproductive tissue type was determined for each individual at each census time.
+For some reproductive parts a simple count is practical, while for species with a large number of buds (or flowers or fruit) that are regularly spaced along branches, the length of stem covered in buds is a better measure.
+For species that form cones, the cones can be notably different in size and each cone's dimensions must be recorded throughout development.
+
+- measurements indicating Counts of parts on each individual\\
+- use species level conversions to get number of parts by individual * census\\
+- algorithm which estimates demography of numbers of parts, with respect to map of progression\\
+- convert numbers into weights (BAER\_Investment -- > 4 dataframes in a list, but only FD (= final development of parts) is used, others for error checking)\\
+- group into different categories (BAER\_reproductive costs -- by function `ReproductiveCosts')\\
+  - investment: weight (mg)\\
+  - count (number)\\
+  - costs (mg/successful seed)\\
+  - reference back to groups in paper and in accessoryParts.yml\\
+- at individual level, calculate various proportions and metrics, after combining growth, reproduction, traits ( in `combine\_by\_individual')\\
+
+\subsection{How parts weights are determined}
+
+For all plant parts, a sample of the representative part was collected on other individuals in the population to obtain a mean tissue mass.
+For plant parts that vary considerably in size, such as cones, the mass of parts of different sizes was measured and a regression of mass per length or mass per volume was established.
+The data file flowerCategories indicates, for each reproductive tissue type, for each species, what method was used to determine the mass of the plant part.
+
+For some individuals, actual reproductive parts were collected.
+This includes any reproductive parts of the plants at the time of harvest, including both current reproductive tissues and previously mature woody fruits still attached to the branches.
+In additional some seeds were collected once mature, but before they were dispersed.
+Whenever actual reproductive parts were collected from an individual, the unit mass of these structures was used instead of the population mean.
+
+\subsection{R scripts used to calculate reproductive investment}
+
 \section{Details on calculations by species}
@@
 Each species uses notably different algorithms to determine reproductive tissue investment, as each species forms different reproductive tissues and different methods are practical for recording each species' reproductive investment in the field.
-For some reproductive parts a simple count is pracical, while for species with a large number of buds (or flowers or fruit) that are regularly spaced along branches, the length of stem covered in buds is a better measure.
-For species that form cones, the cones can be notably different in size and each cone's dimensions must be recorded.
 
@@
 \end{enumerate}
-
-For each species we established a list of different reproductive tissue parts and mapped how these parts developed through time.
-As the reproductive cycle progresses, tissue parts were repeatedly split into two (or more) parts.
-For instance, a bud, once open, divides into being petals + stamens, a sepal, and a stigma.
-As a pollinated stigma develops into a fruit, it will be further divided into seed, seed pod, and potentially additional parts.
-This is shown in the map for each species.
-
-The accompanying table for each species provides a list of plant parts, a description of exactly what tissues are included in each plant part and at what developmental stage, the method whereby the count and mass of the plant parts is measured, and the number of ovules in each unit of plant part.
 
@@
 
-<<echo=FALSE, results='asis', warning=FALSE>>=
-
-make_table_species_values_for_allocation_seedsize_table <- function(file) {
-  data <- select(file,species,embryo_endo_costs, scaled_seed_count,scaled_ovule_count,
-                 scaled_pollen_attract_costs,choosiness,prop_prepollen_success, prop_prepollen_discarded,
-                 prop_postpollen_success,prop_postpollen_discarded, prop_pollen_attract_vs_success,prop_provisioning_vs_success)
-  data$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  data
-}
-
-TableS15 <- make_table_species_values_for_allocation_seedsize_table(SummarySpp[["mean"]])
-
-names(TableS15) <- c("species","embryo and endosperm costs","scaled seed count","scaled ovule count","scaled pollen-attraction costs","choosiness","to success","to discarded","to success","to discarded","to pollen-attraction","to provisioning")
-
-for (i in 2:12) {
-TableS15[,i] <- format(TableS15[,i],digits=3,nsmall=2)
-}
-
-TableS15$species  <- paste("\\textit{",unique(TableS15$species),"}", sep="")
-@
-
-\begin{table}[H]
-\centering
-\caption{Species values for data plotted in Figure 2, shifts in reproductive tissue allocation with seed size.}
-\label{tab:species}
-\begin{tabular}{p{0.1cm}p{4cm}|p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
-\hline
-& \multicolumn{8}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
-& \multicolumn{8}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
-& \multicolumn{8}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
-<<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS15)
-        , sanitize.text.function=I
-        , include.rownames = FALSE
-        , include.colnames = TRUE,
-        only.contents=TRUE)
-@
-\end{tabular}
-\end{table}
-
-\clearpage
-<<echo=FALSE, results='asis', warning=FALSE>>=
-make_table_RA_shifts_with_age <- function() {
-  xvar <- "repro_inv"
-  yvar <- "accessory_costs"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_RE <- lines(fit$groupsummary)
-  accessory_vs_RE <- dplyr::select(accessory_vs_RE,group,n,r2,pval)
-
-  xvar <- "total_weight_0"
-  yvar <- "accessory_costs"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_size <- lines(fit$groupsummary)
-  accessory_vs_size <- dplyr::select(accessory_vs_size,group,n,r2,pval)
-
-  xvar <- "age"
-  yvar <- "accessory_costs"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_age <- lines(fit$groupsummary)
-  accessory_vs_age <- dplyr::select(accessory_vs_age,group,n,r2,pval)
-
-  TableS16 <- merge(accessory_vs_RE,accessory_vs_size,by="group")
-  TableS16 <- merge(TableS16,accessory_vs_age,by="group")
-
-  names(TableS16) <- c("species","n","r$^2$","p","n","r$^2$","p","n","r$^2$","p")
-
-  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  TableS16$species <-  paste("\\textit{",species,"}", sep="")
-
-  TableS16
-}
-
-TableS16 <- make_table_RA_shifts_with_age()
-
-for(i in c(2,3,5,6,8,9)){
-  TableS16[,i] <- format(TableS16[,i],digits=2,nsmall=2)
-}
-for(i in c(4,7,10)){
-  TableS16[,i] <- format_p(TableS16[,i])
-}
-
-@
-
-\begin{table}[H]
-\centering
-\caption{Shifts in accessory costs with shifts in age, plant size, or reproductive effort.}
-\label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
-\hline
-& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
-& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c}{vs. plant mass (mg)}& \multicolumn{3}{c}{vs. age} \\
-<<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS16)
-        , sanitize.text.function=I
-        , include.rownames = FALSE
-        , include.colnames = TRUE,
-        only.contents=TRUE)
-@
-\end{tabular}
-\end{table}
-
-\clearpage
-
-% lines that previously created tableS16 - will delete once new version working
-% print(xtable(TableS2,
-%                hline.after=c(1),
-%                align='p{0.1cm}p{4cm}|p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}',
-%                caption="Species values for data plotted in Figure 2",
-%                sanitize.text.function=I,
-%         , table.placement = "H"
-%         , caption.placement = "top"
-%         , include.rownames = FALSE
-%         , include.colnames = TRUE
-%         , size = "small"
-%         , floating = FALSE))
-
-<<echo=FALSE, warning=FALSE>>=
-
-make_table_propagule_invest_vs_all_repropro_inv <- function(SummaryInd) {
-  mod_propagule_inv_all <- sma(repro_inv~propagule_inv,data=SummaryInd,log="xy",method="SMA")
-  mod_flower_inv_all <- sma(repro_inv~flower_inv,data=SummaryInd,log="xy",method="SMA")
-
-  yvar <- "repro_inv"
-  xvar <- "propagule_inv"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=mod_propagule_inv_all$groupsummary["Slope"][[1]],elev.test=mod_propagule_inv_all$coef[[1]][1,1])
-  results <- fit$groupsummary
-  acc_slopes <- dplyr::select(results,group,n,r2,pval)
-  names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule")
-
-  yvar <- "repro_inv"
-  xvar <- "flower_inv"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
-  results <- fit$groupsummary
-  acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
-  names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
-  acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
-  names(acc_slopes) <- c("species","n","r$^2$","p", "n","r$^2$","p")
-  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  acc_slopes$species <-  paste("\\textit{",species,"}", sep="")
-
-  acc_slopes
-}
-
-TableS17 <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)
-
-for(i in c(2,3,5,6)){
-  TableS17[,i] <- format(TableS17[,i],digits=2,nsmall=2)
-}
-for(i in c(4,7)){
-  TableS17[,i] <- format_p(TableS17[,i])
-}
-@
-
-\begin{table}[H]
-\centering
-\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight (mg) $\times$ bud count'}
-\label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
-\hline
-& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
-& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
-<<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS17)
-        , sanitize.text.function=I
-        , include.rownames = FALSE
-        , include.colnames = TRUE,
-        only.contents=TRUE)
-@
-\end{tabular}
-\end{table}
-
-\clearpage
-
-<<echo=FALSE, results='asis', warning=FALSE>>=
-make_table_buds_vs_size <- function() {
-  xvar <- "total_weight_0"
-  yvar <- "ovule_count"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-  TableS18 <- lines(fit$groupsummary)
-  TableS18 <- dplyr::select(TableS18,group,n,r2,pval)
-
-  names(TableS18) <- c("species","n","r$^2$","p")
-
-  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  TableS18$species <-  paste("\\textit{",species,"}", sep="")
-
-  TableS18
-}
-
-TableS18 <- make_table_buds_vs_size()
-
-for(i in c(2,3)){
-  TableS18[,i] <- format(TableS18[,i],digits=2,nsmall=2)
-}
-for(i in c(4)){
-  TableS18[,i] <- format_p(TableS18[,i])
-}
-
-TableS18$species  <- paste("\\textit{",unique(TableS18$species),"}", sep="")
-@
-
-\begin{table}[H]
-\centering
-\caption{Count of buds initiated is well predicted by plant size}
-\label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}}
-\hline
-<<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS18)
-        , sanitize.text.function=I
-        , include.rownames = FALSE
-        , include.colnames = TRUE,
-        only.contents=TRUE)
-@
-\end{tabular}
-\end{table}
-
-<<echo=FALSE, results='asis', warning=FALSE>>=
-make_table_Table2_using_propagule <- function() {
-slopes <- sma(repro_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
-
-slopes <- sma(accessory_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(success_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(pollen_attract_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(provisioning_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(prepollen_discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(postpollen_aborted_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-acc_by_species$variable = c("total reproductive costs","total accessory costs","seed costs","pollen attraction costs","provisioning costs", "failed tissues costs","failed pre-pollination costs","failed provisioning costs")
-
-acc_by_species$Slope <- format(acc_by_species$Slope,nsmall=2,digits=2)
-acc_by_species$Slope_lowCI <- format(acc_by_species$Slope_lowCI,nsmall=2,digits=2)
-acc_by_species$Slope_highCI <- format(acc_by_species$Slope_highCI,nsmall=2,digits=2)
-
-acc_by_species$slope2 <- paste(acc_by_species$Slope," (",acc_by_species$Slope_lowCI," - ",acc_by_species$Slope_highCI,")",sep="")
-
-acc_by_species$r2 <- format(acc_by_species$r2,digits=2)
-acc_by_species$pval <- format_p(acc_by_species$pval)
-acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=2)
-acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
-}
-TableS19 <- make_table_Table2_using_propagule()
-@
-\begin{table}[H]
-\centering
-\caption{Scaling of reproductive tissue costs with total propagule size}
-\label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.94cm}x{3cm}x{1.5cm}}
-\hline
-<<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS19)
-        , sanitize.text.function=I
-        , include.rownames = FALSE
-        , include.colnames = TRUE,
-        only.contents=TRUE)
-@
-\end{tabular}
-\end{table}
-
-\clearpage
-
 \addcontentsline{toc}{section}{References}

### 2017-02-14 ms/Accessory/Wenk-Accessory-SI.Rnw
Fix errors in building suppmat

@@
 \begin{document}
-\SweaveOpts{concordance=TRUE}
 
@@
   fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_RE <- lines(fit$groupsummary)
-  accessory_vs_RE <- dplyr::select(accessory_vs_RE,group,n,r2,pval)
+  accessory_vs_RE <- dplyr::select(fit$groupsummary,group,n,r2,pval)
 
@@
   fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_size <- lines(fit$groupsummary)
-  accessory_vs_size <- dplyr::select(accessory_vs_size,group,n,r2,pval)
+  accessory_vs_size <- dplyr::select(fit$groupsummary,group,n,r2,pval)
 
@@
   fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_age <- lines(fit$groupsummary)
-  accessory_vs_age <- dplyr::select(accessory_vs_age,group,n,r2,pval)
+  accessory_vs_age <- dplyr::select(fit$groupsummary,group,n,r2,pval)
 
@@
 \label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.94cm}x{3cm}x{1.5cm}}
+\begin{tabular}{p{4cm}|x{.94cm}x{3cm}p{1.5cm}}
 \hline
@@
 print(xtable(TableS19)
-        , sanitize.text.function=I
+        # , sanitize.text.function=I
         , include.rownames = FALSE
@@
   fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-  TableS18 <- lines(fit$groupsummary)
-  TableS18 <- dplyr::select(TableS18,group,n,r2,pval)
+  TableS18 <- dplyr::select(fit$groupsummary,group,n,r2,pval)
 
@@
 \label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}}
+\begin{tabular}{p{4cm}|x{.94cm}x{1cm}p{1.5cm}}
 \hline
@@
 <<echo=FALSE,results='asis'>>=
-  @@@("../../data/accessoryParts.yml")
+  ###("../../data/accessoryParts.yml")
 @
@@
 
-accessory_parts.yml
-flowerCategories.csv and flowerCategories_meta.csv
-flowerParts.csv and flowerParts_meta.csv
-individuals.csv and individuals_meta.csv
+accessory\_parts.yml
+flowerCategories.csv and flowerCategories\_meta.csv
+flowerParts.csv and flowerParts\_meta.csv
+individuals.csv and individuals\_meta.csv
 MultiplierTable.csv
-reproduction.csv and reproduction_meta.csv
+reproduction.csv and reproduction\_meta.csv
 seedMultiplier.csv
@@
 The following files contain supplmentary data about the species and sites:
-seedsize.csv and seedsize_meta.csv
-sites.csv and sites_meta.csv
+seedsize.csv and seedsize\_meta.csv
+sites.csv and sites\_meta.csv
 species.csv

### 2017-02-14 Analysis-accessory.Rmd
adding table with summary of numbers from Figure 2

@@
 mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
-#extra.top.left("b",2,1)
 
@@
 mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
-#extra.top.left("c",2,1)
 
@@
 mtext(text="(mg/seed)",side=1,line=2.1,outer=FALSE,cex=0.8)
-#extra.top.left("d",2,1)
+
 dev.off()
@@
 extra.top.left.logxy("a",2,1)
-
-plot(choosiness2~prop_pollen_attract_vs_all_repro,SummarySpp[["mean"]],log="xy",col=cerulean,pch=16,xlim=c(.002,.3),ylim=c(3,800),yaxt="n",cex=1,ylab="",xlab="",xaxt="n")
-axis(2, at=c(10,100,1000), labels=c(10,100,1000),cex.axis=0.8,las=2)
-axis(1, at=c(0.01,0.1), labels=c(0.01,0.1),cex.axis=0.8)
-mtext("pollen-attractions costs, scaled to leaf area",1,line=1.7,cex=0.7)
-mtext("choosiness (ovules:seed)",2,line=2.3,cex=0.7)
-#mod_choosy <- sma(choosiness2~scaled_pollen_attract_costs,data=subset(SummarySpp[["mean"]]),log="xy",slope=-1,method="SMA")
-mod_choosy2 <- sma(choosiness2~prop_pollen_attract_vs_all_repro,data=subset(SummarySpp[["mean"]],species!="EPMI"),log="xy",slope=-1,method="SMA")
 
@@
 dev.off()
+
+Figure2_summary <- dplyr::select(mod_seed$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI)
+
+Figure2_summary <- dplyr::bind_rows(Figure2_summary,
+  dplyr::select(mod_ovule$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI))
+
+Figure2_summary <- dplyr::bind_rows(Figure2_summary,
+  dplyr::select(mod_choosy2$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI))
+
+Figure2_summary <- dplyr::bind_rows(Figure2_summary,
+  dplyr::select(mod_prop_prepollen_success$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI))
+
+Figure2_summary <- dplyr::bind_rows(Figure2_summary,
+  dplyr::select(mod_prop_postpollen_success$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI))
+
+Figure2_summary <- dplyr::bind_rows(Figure2_summary,
+  dplyr::select(mod_prop_pollen_attract_vs_success$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI))
+
+Figure2_summary$names <- c("seed count by reproductive costs","mature ovule count by pollen attraction costs","choosiness by pollen-attraction costs","prop of pollen attraction to success by seed size","prop of provisioning to success by seed size","prop of successful investment to pollen attraction by seed size")
+
 ```

### 2017-02-15 ms/Accessory/Wenk-Accessory-SI.Rnw
Additional edits to Supplementary Material after checking pdf. I've also added sections on the various R scripts.
One of the main edits still needed is how to wrap text in tables - to avoid tables falling off page.

@@
 \label{tab:species}
-\begin{tabular}{p{0.1cm}p{4cm}|p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
+\begin{tabular}{p{4cm}|p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
 \hline
-& \multicolumn{8}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
-& \multicolumn{8}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
-& \multicolumn{8}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
+& \multicolumn{7}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
+& \multicolumn{7}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
+& \multicolumn{7}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
 <<echo=FALSE, results='asis', warning=FALSE>>=
@@
 \label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
+\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.25cm}|x{.75cm}x{1cm}p{1.25cm}|x{.75cm}x{1cm}p{1.25cm}}
 \hline
-& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
-& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c}{vs. plant mass (mg)}& \multicolumn{3}{c}{vs. age} \\
+& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c|}{Accessory costs}& \multicolumn{3}{c|}{Accessory costs} \\
+& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c|}{vs. plant mass (mg)}& \multicolumn{3}{c|}{vs. age} \\
 <<echo=FALSE, results='asis', warning=FALSE>>=
@@
 \clearpage
-
-% lines that previously created tableS16 - will delete once new version working
-% print(xtable(TableS2,
-%                hline.after=c(1),
-%                align='p{0.1cm}p{4cm}|p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}|p{1.5cm}p{1.5cm}',
-%                caption="Species values for data plotted in Figure 2",
-%                sanitize.text.function=I,
-%         , table.placement = "H"
-%         , caption.placement = "top"
-%         , include.rownames = FALSE
-%         , include.colnames = TRUE
-%         , size = "small"
-%         , floating = FALSE))
 
@@
 \label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.94cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
+\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
 \hline
@@
 
-acc_by_species$variable = c("total reproductive costs","total accessory costs","seed costs","pollen attraction costs","provisioning costs", "failed tissues costs","failed pre-pollination costs","failed provisioning costs")
+acc_by_species$variable = c("total reproductive","total accessory","seed","pollen attraction","provisioning", "failed tissue","failed pre-pollination","failed provisioning")
 
@@
 TableS19 <- make_table_Table2_using_propagule()
+names(TableS19) <- c("costs","r$^2$","slope (95% CI)","p (slope test)")
 @
@@
 \label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.94cm}x{3cm}p{1.5cm}}
+\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{1.5cm}}
 \hline
@@
 \label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.94cm}x{1cm}p{1.5cm}}
+\begin{tabular}{p{4cm}|x{.75cm}x{1cm}p{1.25cm}}
 \hline
@@
 
-accessoryParts.yml
-This file contains, for each species, lists of reproductive tissues that fall into various tissue categories=.
+The file accessoryParts.yml contains, for each species, lists of reproductive tissues that fall into various tissue categories=.
 These categories are then used to calculate the reproductive investment in the key reproductive tissue categories, (1) pollen-attraction tissues aborted prior to provisioning; (2) pollen-attraction tissues associated with flowers that form mature seeds; (3) provisioning tissues aborted prior to the formation of a mature seed; (4) packaging and dispersal tissues associated with a mature seed; (5) the mature seed itself.
@@
 
-\subsection{investment categories by species}
+\subsection{investment categories by species in accessoryParts.yml}
 List for each species of reproductive tissue types included in each of the investment categories
@@
 
-accessory\_parts.yml
-flowerCategories.csv and flowerCategories\_meta.csv
-flowerParts.csv and flowerParts\_meta.csv
-individuals.csv and individuals\_meta.csv
-MultiplierTable.csv
-reproduction.csv and reproduction\_meta.csv
-seedMultiplier.csv
+\begin{enumerate}
+\item accessory\_parts.yml
+\item flowerCategories.csv and flowerCategories\_meta.csv
+\item flowerParts.csv and flowerParts\_meta.csv
+\item individuals.csv and individuals\_meta.csv
+\item MultiplierTable.csv
+\item reproduction.csv and reproduction\_meta.csv
+\item seedMultiplier.csv
+\end{enumerate}
 
 The following files contain supplmentary data about the species and sites:
-seedsize.csv and seedsize\_meta.csv
-sites.csv and sites\_meta.csv
-species.csv
 
-floweringCategories
+\begin{enumerate}
+\item seedsize.csv and seedsize\_meta.csv
+\item sites.csv and sites\_meta.csv
+\item species.csv
+\end{enumerate}
+
+\subsection{floweringCategories}
 This file contains a matrix of plant parts (rows) by species (columns).
@@
 
-floweringCategories\_metadata
+\subsection{floweringCategories\_metadata}
 This files contains a matrix of plant parts (rows) by species (columns).
@@
 
-flowerParts
+\subsection{flowerParts}
 Harvested and weighed flower parts, including collections from tagged individuals (once mature or at time of harvest) and from other individuals in the population (to estimate weight of specific plant parts).
@@
 
-Individuals
+\subsection{Individuals}
 This file contains a list of all plants harvested at the 7 Kuring'gai fieldsites.
@@
 
-multiplierTable
+\subsection{multiplierTable}
 Lookup table indicating, for each species by flower part combination, if the investment per part is for a single (1) or multiple propagules, defined as either a mature fruit or a seed, depending on what is the dispersal unit for each species.
@@
 
-reproduction
+\subsection{reproduction}
 The reproduction spreadsheet provides both verbal and numeric descriptions of reproduction at each census between April-June 2012 (or June 2013 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were first tagged, until April-June 2013 (or June 2014 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were harvested.
@@
 
-seedsize
+\subsection{seedsize}
+A collection of species level information, including seed size and embryo-endosperm weight.
+This file also includes data on the number of ovules per ovary, lifespan, age at maturity, and approximate age at which RA asymptotes.
 
@@
 
-sites
+\subsection{sites}
 Tables of sites used in study. Includes site names used in other spreadsheets, date of fire, fire year, as defined by NSW fire layers, and UTM coordinates for each site.
@@
 
-species
+\subsection{species}
 Table of species included in study. Includes 4-letter code names used in other spreadsheets, scientific names, family names, and common names.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/species.csv")
+@
 
@@
 For each species we established a list of different reproductive tissue parts and mapped how these parts developed through time.
-As the reproductive cycle progresses, tissue parts were repeatedly split into two (or more) parts.
-For instance, a bud, once open, divides into being petals + stamens, a sepal, and a stigma.
+
+Each species reproductive tissue development initiates with a bud or inflorescence bud, which increases in size and is divided into multiple tissue types several times during development.For instance, a bud, once open, divides into being petals + stamens, a sepal, and a stigma.
 As a pollinated stigma develops into a fruit, it will be further divided into seed, seed pod, and potentially additional parts.
-Along the developmental trajectory, various reproductive tissues are designated as reaching their final development stage, the point in the reproductive cycle where they no longer increase in mass.
-For some tissues, such as petals, final development is reached long before a mature seed forms, while other tissues, such as the seed and seedpod do not reach final development until the end of the developmental trajectory.
-
-Each species reproductive tissue development initiates with a bud or inflorescence bud, which increases in size and is divided into multiple tissue types several times during development.
 The central development axis terminates with the formation of a mature seed, while side branches end in fully developed tissues (such as petals, calyx, pedicel) and aborted tissues (aborted seeds, aborted fruit) at the point where they cease to increase in mass.
@@
 For some reproductive parts a simple count is practical, while for species with a large number of buds (or flowers or fruit) that are regularly spaced along branches, the length of stem covered in buds is a better measure.
-For species that form cones, the cones can be notably different in size and each cone's dimensions must be recorded throughout development.
-
-- measurements indicating Counts of parts on each individual\\
-- use species level conversions to get number of parts by individual * census\\
-- algorithm which estimates demography of numbers of parts, with respect to map of progression\\
-- convert numbers into weights (BAER\_Investment -- > 4 dataframes in a list, but only FD (= final development of parts) is used, others for error checking)\\
-- group into different categories (BAER\_reproductive costs -- by function `ReproductiveCosts')\\
-  - investment: weight (mg)\\
-  - count (number)\\
-  - costs (mg/successful seed)\\
-  - reference back to groups in paper and in accessoryParts.yml\\
-- at individual level, calculate various proportions and metrics, after combining growth, reproduction, traits ( in `combine\_by\_individual')\\
+These lengths were converted into counts through a species value of "flowers per length".
+For species that form cones, the cones can be notably different in size and each cone's dimensions was recorded throughout development.
+The counts of flowers (or other reproductive tissues) were then converted to a count of ovules using the values in the file multiplierTable.
 
@@
 
-\subsection{R scripts used to calculate reproductive investment}
+\section{R scripts used to calculate reproductive investment}
+
+\subsection{preprocess.R}
+
+Includes functions filterBySpecies, which subsets by species, and filterForAllocation, indicating which individuals to use for allocation calculations.
+
+Uses data files: data/individuals.csv
+Output: IndividualsList (by species)
+
+\subsection{OrderedListOfParts.R}
+
+Script defining lists of reproductive parts for each species.
+
+Uses data files: None
+Output: PartsList (by species)
+
+\subsection{FlowerParts.R}
+
+Script to calculate the weights of all reproductive tissues for each individual, including special calculations for:
+
+\begin{enumerate}
+\item determine weights based on dimensions where applicable
+\item individual based weights where applicable
+\end{enumerate}
+
+Uses data files and data frames: data/flowerParts.csv, PartsList (by species)
+Output: PartsSummary (by species)
+
+\subsection{GraphRepresentation.R}
+
+Script describing defining the plant maps for each species.
+
+Uses data files and data frames: PartsSummary (by species), data/MultiplierTable.csv
+Output: GraphMaps (by species)
+
+\subsection{Investment.R}
+
+Script that combines each species plant map (GraphMaps), weights of flower parts (PartsSummary), and the census data (Reproduction) to calculate the actual investment in reproductive parts.
+
+A key part of the calculation is the algorithm which estimates demography of numbers of parts, with respect to map of progression.
+That is, if, in census x, a large bud exists, it is assumed that it has developped from a medium sized bud (the previous stage) in census x-1.
+If in census x-1 no medium buds exists, the large bud is assumed to have developped from a small bud (two stages back).
+This process continues back along the plant map developmental trajectory until a plausible predecessor is located in the previous census period.
+After this process is complete, any parts from census x-1 for which a subsequent developmental stage is not identified as designated as having reached their final developmental stage at census x-1 (i.e.
+they aborted).
+
+For plant parts, such as petals, that as a final development stage, no success is sought.
+
+There are four dataframes within Investment, but only FD (FinalDevelopment) is used. The others were generated for error checking.
+
+Uses data files and data frames: data/reproduction.csv (and Reproduction), data/floweringCategories.csv (and FloweringCategories), data/multiplierTable.csv (and MultiplierTable), GraphMaps (by species), PartsSummary (by species)
+Output: Investment (by species)
+
+\subsection{ReproductionTissues.R}
+
+This script takes the investment data and breaks it down into specific reproductive cost categories based on the data in accessoryParts.yml
+
+Uses data files and data frames: IndividualsList (by species), data/accessoryParts.yml(and InvestmentCategories), Investment (by species),  PartsSummary (by species)
+Output: ReproductiveCosts (by species)
 
@@
 Each species uses notably different algorithms to determine reproductive tissue investment, as each species forms different reproductive tissues and different methods are practical for recording each species' reproductive investment in the field.
-
-\begin{enumerate}
-\item Something
-\item Something else
-\end{enumerate}
-
-\begin{enumerate}
-\item Something
-\item Something else
-\end{enumerate}
 

### 2017-02-21 ms/Accessory/Wenk-Accessory-SI.Rnw
last few changes to accessory files, including: - adding UTM coordinates to sites - creating visual plant maps (currently in powerpoint. I'll soon convert those to file format that can be embedded into latex file) - few more details for main SI file

@@
 
-The file accessoryParts.yml contains, for each species, lists of reproductive tissues that fall into various tissue categories=.
+The file accessoryParts.yml contains, for each species, lists of reproductive tissues that fall into various tissue categories.
 These categories are then used to calculate the reproductive investment in the key reproductive tissue categories, (1) pollen-attraction tissues aborted prior to provisioning; (2) pollen-attraction tissues associated with flowers that form mature seeds; (3) provisioning tissues aborted prior to the formation of a mature seed; (4) packaging and dispersal tissues associated with a mature seed; (5) the mature seed itself.
@@
 
-Script to calculate the weights of all reproductive tissues for each individual, including special calculations for:
+Script to calculate the unit weights of all reproductive tissues for each individual, including special calculations for:
 
@@
 Script describing defining the plant maps for each species.
+Each plant map begins with a bud (or the appropriate starting point for reproductive tissue development for a specific species) and depicts graphically how the tissue develops through the plant's reproductive cycle to a seed or mature fruit.
+During the reproductive cycle, there will be branches off the central tissue axis (development from bud to seed).
+Some of these lead to aborted tissue types (colored red in the graph maps below) and others lead to tissues that reach their final development stage and are then shed by a plant (e.g.
+petals, calyx, seed pod; colored green in the graph maps below).
+For some species, there are mutiple axes of development.
+For instance, cones and flowers on a cone have separate axes, because the number of flowers on a cone is inconsistent across individuals.
+A few species have aborted plant parts that are listed as a separate axis.
+In these cases, the aborted unit weighs less than a bud and therefore cannot be shown as ever having reached the stage of a bud.
 

### 2017-02-24 ms/Accessory/Wenk-Accessory-SI.Rnw
remove SeaveOpts line (self-inserts whenever I push button "compile PDF in RStudio)
started adding in pdfs of plant maps. All the others are in the same folder, but didn't add them in until I'm sure syntax is correct.

@@
   plot_graph(BAER_GraphMaps$graph)
+  ###\includegraphics{"../../ms/Accessory/output/BAER.pdf"}
 @
@@
   plot_graph(BOLE_GraphMaps$graph)
+  ###\includegraphics{"../../ms/Accessory/output/BOLE.pdf"}
 @

### 2017-03-03 Analaysis-RA.Rmd
continued work on RA manuscript introduction

@@
 
-data <- select(SummarySppAge[["mean"]], species, age, repro_inv, growth_leaf, leaf_replacement,leaf_area_0,leaf_weight_0,total_inv,prop_surplus,
+data <- select(SummarySppAge[["mean"]], species, age, repro_inv, growth_leaf, leaf_replacement,leaf_area_0,leaf_weight_0,total_inv,prop_surplus,seed_count,
   growth_stem, leaf_shed,prop_stem,prop_leaf_replacement,prop_leaf_expand,prop_repro,RA_max_1,lifespan,height, RA_vs_all_leaf,
@@
 data_ind <- select(SummaryCombine,species,individual,age, prop_leaf_loss,height_0,leaf_shed,leaf_weight_0,propagule_inv,ovule_count,
-                   growth_leaf_pos,repro_inv,total_weight_0,all_leaf_inv,total_inv,surplus_inv,all_leaf_and_repro_inv,age,success_inv)
+                   growth_leaf_pos,repro_inv,total_weight_0,all_leaf_inv,total_inv,surplus_inv,all_leaf_and_repro_inv,age,success_inv,
+                   seed_count)
 

### 2017-05-05 Analysis-accessory.Rmd
small changes to accessory analysis from long ago

@@
 ```{r}
-png("ms/Accessory/output/Figure01b&c&d_predictions.png", height=3.6, width=9, units="in", res=300)
-par(mfrow=c(1,3), cex=1, omi=c(.1,.1,.05,.2), mai=c(.8,.8,.6,.05))
+png("ms/Accessory/output/Figure01b_predictions.png", height=2.5, width=7.3, units="in", res=300)
+
+windowsFonts(
+  Myriad=windowsFont("Myriad Pro")
+)
+
+par(mfrow=c(1,3), cex=1, omi=c(.1,.35,.05,.05), mai=c(.7,.5,.05,.15))
 plot(0,0,ylim=c(0,1),yaxt="n",xaxt="n",xlim=c(0,1),col="white",xlab="",ylab="")
 segments(x0=.2,x1=.9,y0=.9,y1=.2,lty=1)
-axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
-axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
-mtext(text="Trade-off 1:",side=3,outer=FALSE,adj=0,line=1.6)
-mtext(text="Seed count-reproductive costs",side=3,outer=FALSE,adj=0,line=0.7)
-mtext(text="seed count,",side=2,line=1.3,outer=FALSE,cex=0.8)
-mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
-mtext(text="reproductive costs",side=1,line=0.3,outer=FALSE,cex=0.8)
-mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
+#axis(3, at=c(0,1),labels=c("lower","higher"),family="Myriad",cex.axis=0.875)
+#axis(2, at=c(0,1),labels=c("lower","higher"),family="Myriad",cex.axis=0.875,las=2)
+#mtext(text="Trade-off 1:",side=3,outer=FALSE,adj=0,line=1.6)
+#mtext(text="Seed count-reproductive costs",side=3,outer=FALSE,adj=0,line=0.7)
+mtext(text="seed count,",side=2,line=1.3,outer=FALSE,family="Myriad",cex=0.875)
+mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,family="Myriad",cex=0.875)
+mtext(text="reproductive costs",side=1,line=0.3,outer=FALSE,family="Myriad",cex=0.875)
+mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,family="Myriad",cex=0.875)
 
@@
 segments(x0=.1,x1=.8,y0=.8,y1=.1,lty=1)
-axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
-axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
-mtext(text="Trade-off 2.",side=3,outer=FALSE,adj=0,line=1.6)
-mtext(text="Ovule count-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
-mtext(text="mature ovules count,",side=2,line=1.3,outer=FALSE,cex=0.8)
-mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,cex=0.8)
-mtext(text="pollen attraction costs",side=1,line=0.3,outer=FALSE,cex=0.8)
-mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,cex=0.8)
+#axis(3, at=c(0,1),labels=c("lower","higher"),family="Myriad",cex.axis=0.875)
+#axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
+#mtext(text="Trade-off 2.",side=3,outer=FALSE,adj=0,line=1.6)
+#mtext(text="Ovule count-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
+mtext(text="mature ovules count,",side=2,line=1.3,outer=FALSE,family="Myriad",cex=0.875)
+mtext(text="scaled to plant size",side=2,line=0.4,outer=FALSE,family="Myriad",cex=0.875)
+mtext(text="pollen attraction costs",side=1,line=0.3,outer=FALSE,family="Myriad",cex=0.875)
+mtext(text="(mg/seed)",side=1,line=1.2,outer=FALSE,family="Myriad",cex=0.875)
 
@@
 segments(x0=.1,x1=.9,y0=.9,y1=.1,lty=1)
-axis(1, at=c(0,1),labels=c("lower","higher"),cex.axis=1)
-axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
-mtext(text="Trade-off 3.",side=3,outer=FALSE,adj=0,line=1.6)
-mtext(text="Choosiness-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
-mtext(text="choosiness",side=2,line=1.3,outer=FALSE,cex=0.8)
-mtext(text="(ovule:seed)",side=2,line=0.4,outer=FALSE,cex=0.8)
-mtext(text="pollen attraction costs,",side=1,line=0.3,outer=FALSE,cex=0.8)
-mtext(text="scaled to plant size",side=1,line=1.2,outer=FALSE,cex=0.8)
-mtext(text="(mg/seed)",side=1,line=2.1,outer=FALSE,cex=0.8)
+#axis(3, at=c(0,1),labels=c("lower","higher"),family="Myriad",cex.axis=0.875)
+#axis(2, at=c(0,1),labels=c("lower","higher"),cex.axis=1,las=2)
+#mtext(text="Trade-off 3.",side=3,outer=FALSE,adj=0,line=1.6)
+#mtext(text="Choosiness-pollen attraction costs",side=3,outer=FALSE,adj=0,line=0.7)
+mtext(text="choosiness",side=2,line=1.3,outer=FALSE,family="Myriad",cex=0.875)
+mtext(text="(ovule:seed)",side=2,line=0.4,outer=FALSE,family="Myriad",cex=0.875)
+mtext(text="pollen attraction costs,",side=1,line=0.3,family="Myriad",cex=0.875)
+mtext(text="scaled to plant size",side=1,line=1.2,family="Myriad",cex=0.875)
+mtext(text="(mg/seed)",side=1,line=2.1,outer=FALSE,family="Myriad",cex=0.875)
 
@@
 
+mod_seed$groupsummary$r2
+mod_ovule$groupsummary$r2
+
 #panel b
@@
 extra.top.left.logxy("b",2,1)
+
+mod_choosy2$groupsummary$r2
 

### 2017-05-05 ms/Accessory/Wenk-Accessory-SI.Rnw
Substantial reworking of Supp Matt for Accessories paper
- extract plant map images form power powerpoint
- fix table widths
- reorder materials, section headers etc

--- 2017-02-21 ms/Accessory/Wenk-Accessory-SI.Rnw
@@
 \usepackage{longtable}
+\usepackage{graphicx}
 
@@
 % http://timotheepoisot.fr/2013/06/24/manuscript-central-pdf-fix/
+
+% allow some pages to be landscape
+\usepackage{lscape}
 
@@
 
-print_table_metadata <- function(path) {
+print_table_metadata <- function(path, align = NULL) {
 
@@
   file <- gsub("_", "\\_", basename(path), fixed = TRUE)
+
+  label <- sprintf("tab:%s_meta", strsplit(basename(path), "_")[[1]][1])
+
   print(xtable(data,
+            align=align,
             hline.after=c(1),
-            label=sprintf("tab:file_", file),
+            label= label,
             caption=
-              sprintf("Variables within the file `%s`. These definitions are defined within the file `%s` in the folder `data`.",
-              gsub("\\_meta", "", file, fixed = TRUE), file)),
+              sprintf("Details on variables within the file \\texttt{%s}.",
+              gsub("\\_meta", "", file, fixed = TRUE))),
       , table.placement = "h"
@@
 
+\begingroup
+\let\cleardoublepage\relax
+\let\clearpage\relax
 \tableofcontents
+\endgroup
 
@@
 
-\clearpage
-
-\section{Additional results}
-
-All computations implemented in \textsc{r} \citep{R-2015}.
+\section{Additional results supporting main text}
 
@@
 
-names(TableS15) <- c("species","embryo and endosperm costs","scaled seed count","scaled ovule count","scaled pollen-attraction costs","choosiness","to success","to discarded","to success","to discarded","to pollen-attraction","to provisioning")
+names(TableS15) <- c("species","embryo and endosperm costs","scaled seed count","scaled ovule count","scaled pollen-attraction costs","choosiness","success","discarded","success","discarded","pollen-attraction","provisioning")
 
@@
 \centering
-\caption{Species values for data plotted in Figure 2, shifts in reproductive tissue allocation with seed size.}
+\caption{Species values for data plotted in Figure 2: shifts in reproductive tissue allocation with seed size.}
 \label{tab:species}
@@
 & \multicolumn{7}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
+
+% \begin{tabular}{p{3cm}|p{1cm}p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
+% \hline
+% &&&& \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
+% &&&& \multicolumn{2}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
+% &&&& \multicolumn{2}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
+
 <<echo=FALSE, results='asis', warning=FALSE>>=
@@
 \end{tabular}
+
+{\color{red}
+\begin{itemize}
+  \item Started reworking table headers but have no idea what they're meant to be.
+  \item Decrease decimal places?
+  \item Swing page to landscape?
+  \item Add units?
+\end{itemize}
+}
+
 \end{table}
@@
 <<echo=FALSE, results='asis', warning=FALSE>>=
-make_table_RA_shifts_with_age <- function() {
+make_table_RA_shifts_with_age <- function(SummaryInd) {
   xvar <- "repro_inv"
@@
 
-TableS16 <- make_table_RA_shifts_with_age()
+TableS16 <- make_table_RA_shifts_with_age(SummaryInd)
 
 for(i in c(2,3,5,6,8,9)){
-  TableS16[,i] <- format(TableS16[,i],digits=2,nsmall=2)
+  TableS16[,i] <- format_r2(TableS16[,i])
 }
@@
 }
-
 @
@@
 \centering
-\caption{Shifts in accessory costs with shifts in age, plant size, or reproductive effort.}
-\label{tab:propagule_invest_vs_repro}
+\caption{Testing for shifts in accessory costs with in age, plant size, or reproductive effort.}
+\label{tab:access_vs_age}
 \begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.25cm}|x{.75cm}x{1cm}p{1.25cm}|x{.75cm}x{1cm}p{1.25cm}}
 \hline
-& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c|}{Accessory costs}& \multicolumn{3}{c|}{Accessory costs} \\
-& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c|}{vs. plant mass (mg)}& \multicolumn{3}{c|}{vs. age} \\
+& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c|}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
+& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c|}{vs. plant mass}& \multicolumn{3}{c}{vs. age} \\
 <<echo=FALSE, results='asis', warning=FALSE>>=
@@
 for(i in c(2,3,5,6)){
-  TableS17[,i] <- format(TableS17[,i],digits=2,nsmall=2)
+  TableS17[,i] <- format_r2(TableS17[,i])
 }
@@
 \centering
-\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight (mg) $\times$ bud count'}
+\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight $\times$ bud count'.}
 \label{tab:propagule_invest_vs_repro}
@@
 
-acc_by_species$Slope <- format(acc_by_species$Slope,nsmall=2,digits=2)
-acc_by_species$Slope_lowCI <- format(acc_by_species$Slope_lowCI,nsmall=2,digits=2)
-acc_by_species$Slope_highCI <- format(acc_by_species$Slope_highCI,nsmall=2,digits=2)
+acc_by_species$Slope <- format_r2(acc_by_species$Slope)
+acc_by_species$Slope_lowCI <- format_r2(acc_by_species$Slope_lowCI)
+acc_by_species$Slope_highCI <- format_r2(acc_by_species$Slope_highCI)
 
@@
 
-acc_by_species$r2 <- format(acc_by_species$r2,digits=2)
+acc_by_species$r2 <- format_r2(acc_by_species$r2)
 acc_by_species$pval <- format_p(acc_by_species$pval)
-acc_by_species$Slope_test_p <- format(acc_by_species$Slope_test_p,digits=2)
+acc_by_species$Slope_test_p <- format_p(acc_by_species$Slope_test_p)
 acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
@@
 TableS19 <- make_table_Table2_using_propagule()
-names(TableS19) <- c("costs","r$^2$","slope (95% CI)","p (slope test)")
+names(TableS19) <- c("costs","r$^2$","slope (95$\\%$ CI)","p (slope test)")
 @
@@
 \centering
-\caption{Scaling of reproductive tissue costs with total propagule size}
-\label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{1.5cm}}
+\caption{Scaling of reproductive tissue costs with total propagule size.}
+\label{tab:repro_tissues_vs_prop_size}
+\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{3cm}}
 \hline
@@
 print(xtable(TableS19)
-        # , sanitize.text.function=I
+         , sanitize.text.function=I
         , include.rownames = FALSE
@@
 for(i in c(2,3)){
-  TableS18[,i] <- format(TableS18[,i],digits=2,nsmall=2)
+  TableS18[,i] <- format_r2(TableS18[,i])
 }
@@
 \centering
-\caption{Count of buds initiated is well predicted by plant size}
-\label{tab:propagule_invest_vs_repro}
+\caption{Count of buds initiated is well predicted by plant size.}
+\label{tab:bud_count_vs_size}
 \begin{tabular}{p{4cm}|x{.75cm}x{1cm}p{1.25cm}}
@@
 
-\section{Details on data from main text}
-
-\section{Investment categories}
-
-The file accessoryParts.yml contains, for each species, lists of reproductive tissues that fall into various tissue categories.
-These categories are then used to calculate the reproductive investment in the key reproductive tissue categories, (1) pollen-attraction tissues aborted prior to provisioning; (2) pollen-attraction tissues associated with flowers that form mature seeds; (3) provisioning tissues aborted prior to the formation of a mature seed; (4) packaging and dispersal tissues associated with a mature seed; (5) the mature seed itself.
-Dividing reproductive investment into these categories requires, for each tissue type, knowing the count of parts that reach the key stages (pollinator-ready, onset of provisioning, mature seed) and the mass of parts at each stage.
-
-\subsection{accessoryParts\_metadata}
-Brief descriptions of each reproductive parts category in the file accessoryParts.
-
-<<echo=FALSE,results='asis'>>=
-  print_table_metadata("../../data/accessoryParts_meta.csv")
-@
-
-\subsection{investment categories by species in accessoryParts.yml}
-List for each species of reproductive tissue types included in each of the investment categories
-<<echo=FALSE,results='asis'>>=
-  ###("../../data/accessoryParts.yml")
-@
-
-\section{Details about input files}
-List of data files.
-
-The following files contain the empirical data used in the analyses:
-
-\begin{enumerate}
-\item accessory\_parts.yml
-\item flowerCategories.csv and flowerCategories\_meta.csv
-\item flowerParts.csv and flowerParts\_meta.csv
-\item individuals.csv and individuals\_meta.csv
-\item MultiplierTable.csv
-\item reproduction.csv and reproduction\_meta.csv
-\item seedMultiplier.csv
-\end{enumerate}
-
-The following files contain supplmentary data about the species and sites:
-
-\begin{enumerate}
-\item seedsize.csv and seedsize\_meta.csv
-\item sites.csv and sites\_meta.csv
-\item species.csv
-\end{enumerate}
-
-\subsection{floweringCategories}
-This file contains a matrix of plant parts (rows) by species (columns).
-For each cell that is used on a given species plant map, the meaning of the values in the spreadsheet titled "reproduction" are indicated in this spreadsheet.
-Possible method are (1) count, indicating that the numbers represent simple counts; (2) count\_by\_length, indicating that the length of stem or cone covered with buds, flowers or fruit is measured; (3) regress\_by\_dim, indicating that the dimensions of the flowering part are measured and must be converted to a dry mass using a regression equation; and (4) volume, indicating that the height and diameter of the flowering part are given and must be converted to a dry mass using the calculated volume of the flowering part multiplied by the average density of the flowering part.
-
-\subsection{floweringCategories\_metadata}
-This files contains a matrix of plant parts (rows) by species (columns).
-For each cell that is used on a given species plant map, a description of the botanical parts included in the "flower part" is given as well as the flowering stage at which the flower part is harvested, if it is not obvious.
-
-\subsection{flowerParts}
-Harvested and weighed flower parts, including collections from tagged individuals (once mature or at time of harvest) and from other individuals in the population (to estimate weight of specific plant parts).
-All plant parts included in a species' "plant map" have weights in this spreadsheet – or, in rare cases, entries are instead plants parts whose weight is used to calculate the weight of a plant part included in a "plant map".
-(A "plant map" shows the developmental trajectory of a flower or inflorescence from bud to seed for each species, indicating the flow or carbon as well as discarded parts.) If plant parts are collected from a tagged individual, this spreadsheet also indicates in which census periods this specific weight, rather than a species average, should be used for calculating that individual's reproductive investment.
-Plant parts all have counts and weights, while the subset of plant parts whose size varies, also have columns indicating height and diameter dimensions; the weight of the plant part at a specific size is then determined by either a regression or volume calculation.
-For a few plant parts, census data measure the length of stem or cone covered with flowers; for these situations, the segment length collected is also recorded, such that the number of flowers per unit length can be calculated.
-
-\subsection{flowerParts\_metadata}
-Brief descriptions of each data column in the file flowerParts, including units.
-
-<<echo=FALSE,results='asis'>>=
-  print_table_metadata("../../data/flowerParts_meta.csv")
-@
-
-\subsection{Individuals}
-This file contains a list of all plants harvested at the 7 Kuring'gai fieldsites.
-For each individual it includes basic information about each individual - tag number, age, site, whether the plant was alive at the time of harvest, and information on which calculations use this individual's data.
-The data itself is contained in other files.
-
-\subsection{Individuals\_metadata}
-Brief descriptions of each data column in the file Individuals, including units.
-
-<<echo=FALSE,results='asis'>>=
-  print_table_metadata("../../data/Individuals_meta.csv")
-@
-
-\subsection{multiplierTable}
-Lookup table indicating, for each species by flower part combination, if the investment per part is for a single (1) or multiple propagules, defined as either a mature fruit or a seed, depending on what is the dispersal unit for each species.
-Within a single column, i.e.
-within a single species developmental trajectory, numbers will change if the "count" used to access reproduction changes at a given developmental stage.
-For instance, with BOLE (Boronia ledifolia), counts are made by flowers up through the finished flower stage, but then fruit are the unit counted and each flower forms 4 fruit.
-
-\subsection{reproduction}
-The reproduction spreadsheet provides both verbal and numeric descriptions of reproduction at each census between April-June 2012 (or June 2013 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were first tagged, until April-June 2013 (or June 2014 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were harvested.
-There is a separate row of data for each individual, at each of the 18 censuses.
-In addition, at each census, there is a row indicating plant parts that are pre-existing on the plant versus new.
-Flower (or fruit) parts are considered pre-existing if the predecessor of that flower part, as described on that species "plant map" existed in a previous census period.
-Some plant maps may have multiple parallel diagrams describing how flower parts develop.
-In that case, a flower part must have a predecessor on that specific diagram to be considered "pre-existing".
-
-Each of the many plant parts are listed as column headers.
-At each census, both new and further developed but pre-existing flower parts are recorded.
-Plant parts that are unchanged in developmental stage between successive censuses are not recorded.
-Neither are plant parts that disappear between successive censuses.
-Instead, pre-existing plant parts are recorded if they have progressed to a "more mature" flowering/fruiting stage, as defined by that species "plant map".
-As an example, if at one census there were 50 PHPH (Phyllota phylicoides) buds recorded and at the next stage, 30 PHPH flowers, 30 of the 50 buds progressed from being buds to being flowers, while the remaining 20 buds were either shed or are still buds.
-The numbers entered in the cell correspond to either counts, lengths, or dimensions, depending on the method indicated in the file titled "floweringCategories".
-
-\subsection{reproduction\_metadata}
-Brief descriptions of the first set of data columns in the file reproduction.
-
-<<echo=FALSE,results='asis'>>=
-  print_table_metadata("../../data/reproduction_meta.csv")
-@
-
-\subsection{seedsize}
-A collection of species level information, including seed size and embryo-endosperm weight.
-This file also includes data on the number of ovules per ovary, lifespan, age at maturity, and approximate age at which RA asymptotes.
-
-\subsection{seedsize\_metadata}
-Brief descriptions of the first set of data columns in the file seedsize, including units.
-
-<<echo=FALSE,results='asis'>>=
-  print_table_metadata("../../data/seedsize_meta.csv")
-@
-
-\subsection{sites}
-Tables of sites used in study. Includes site names used in other spreadsheets, date of fire, fire year, as defined by NSW fire layers, and UTM coordinates for each site.
-
-\subsection{sites\_metadata}
-Brief descriptions of the first set of data columns in the file sites
-
-<<echo=FALSE,results='asis'>>=
-  print_table_metadata("../../data/sites_meta.csv")
-@
-
-\subsection{species}
-Table of species included in study. Includes 4-letter code names used in other spreadsheets, scientific names, family names, and common names.
-
-<<echo=FALSE,results='asis'>>=
-  print_table_metadata("../../data/species.csv")
-@
-
-\section{Overview of methods for estimating reproductive allocation}
-
-\subsection{Overview of plant maps}
+\section{Additional details on methods and details about input files}
 
@@
 
+Tables
 The accompanying table for each species provides a list of plant parts, a description of exactly what tissues are included in each plant part and at what developmental stage, the method whereby the count and mass of the plant parts is measured, and the number of ovules in each unit of plant part.
@@
 For species that form cones, the cones can be notably different in size and each cone's dimensions was recorded throughout development.
-The counts of flowers (or other reproductive tissues) were then converted to a count of ovules using the values in the file multiplierTable.
+The counts of flowers (or other reproductive tissues) were then converted to a count of ovules using the values in the file \texttt{multiplierTable.csv} (details below).
 
@@
 
-\section{R scripts used to calculate reproductive investment}
+\subsection{Details on calculations by species}
 
-\subsection{preprocess.R}
+Each species uses notably different algorithms to determine reproductive tissue investment, as each species forms different reproductive tissues and different methods are practical for recording each species' reproductive investment in the field.
+
+\subsubsection{Banksia ericifolia}
+
+Details on parts for \emph{Banksia ericifolia} found in Table \ref{tab:parts_Banksia ericifolia}. See Fig \ref{fig:map Banksia ericifolia} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/BAER.png}
+\caption{Map of parts for \emph{Banksia ericifolia}}
+\label{fig:map Banksia ericifolia}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Banksia ericifolia", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Boronia ledifolia}
+
+Details on parts for \emph{Boronia ledifolia} found in Table \ref{tab:parts_Boronia ledifolia}. See Fig \ref{fig:map Boronia ledifolia} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/BOLE.png}
+\caption{Map of parts for \emph{Boronia ledifolia}}
+\label{fig:map Boronia ledifolia}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Boronia ledifolia", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Conospermum ericifolium}
+
+Details on parts for \emph{Conospermum ericifolium} found in Table \ref{tab:parts_Conospermum ericifolium}.  See Fig \ref{fig:map Conospermum ericifolium} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/COER.png}
+\caption{Map of parts for \emph{Conospermum ericifolium}}
+\label{fig:map Conospermum ericifolium}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Conospermum ericifolium", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Epacris microphylla}
+
+Details on parts for \emph{Epacris microphylla} found in Table \ref{tab:parts_Epacris microphylla}. See Fig \ref{fig:map Epacris microphylla} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/EPMI.png}
+\caption{Map of parts for \emph{Epacris microphylla}}
+\label{fig:map Epacris microphylla}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Epacris microphylla", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Grevillea buxifolia}
+
+Details on parts for \emph{Grevillea buxifolia} found in Table \ref{tab:parts_Grevillea buxifolia}. See Fig \ref{fig:map Grevillea buxifolia} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/GRBU.png}
+\caption{Map of parts for \emph{Grevillea buxifolia}}
+\label{fig:map Grevillea buxifolia}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Grevillea buxifolia", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Grevillea speciosa}
+
+Details on parts for \emph{Grevillea speciosa} found in Table \ref{tab:parts_Grevillea speciosa}. See Fig \ref{fig:map Grevillea speciosa} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/GRSP.png}
+\caption{Map of parts for \emph{Grevillea speciosa}}
+\label{fig:map Grevillea speciosa}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Grevillea speciosa", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Hakea teretifolia}
+
+Details on parts for \emph{Hakea teretifolia} found in Table \ref{tab:parts_Hakea teretifolia}. See Fig \ref{fig:map Hakea teretifolia} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/HATE.png}
+\caption{Map of parts for \emph{Hakea teretifolia}}
+\label{fig:map Hakea teretifolia}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Hakea teretifolia", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Hemigenia purpurea}
+
+Details on parts for \emph{Hemigenia purpurea} found in Table \ref{tab:parts_Hemigenia purpurea}. See Fig \ref{fig:map Hemigenia purpurea} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/HEPU.png}
+\caption{Map of parts for \emph{Hemigenia purpurea}}
+\label{fig:map Hemigenia purpurea}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Hemigenia purpurea", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Leucopogon esquamatus}
+
+Details on parts for \emph{Leucopogon esquamatus} found in Table \ref{tab:parts_Leucopogon esquamatus}. See Fig \ref{fig:map Leucopogon esquamatus} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/LEES.png}
+\caption{Map of parts for \emph{Leucopogon esquamatus}}
+\label{fig:map Leucopogon esquamatus}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Leucopogon esquamatus", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Persoonia lanceolata}
+
+Details on parts for \emph{Persoonia lanceolata} found in Table \ref{tab:parts_Persoonia lanceolata}. See Fig \ref{fig:map Persoonia lanceolata} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/PELA.png}
+\caption{Map of parts for \emph{Persoonia lanceolata}}
+\label{fig:map Persoonia lanceolata}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Persoonia lanceolata", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Petrophile pulchella}
+
+Details on parts for \emph{Petrophile pulchella} found in Table \ref{tab:parts_Petrophile pulchella}. See Fig \ref{fig:map Petrophile pulchella} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/PEPU.png}
+\caption{Map of parts for \emph{Petrophile pulchella}}
+\label{fig:map Petrophile pulchella}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Petrophile pulchella", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Phyllota phylicoides}
+
+Details on parts for \emph{Phyllota phylicoides} found in Table \ref{tab:parts_Phyllota phylicoides}. See Fig \ref{fig:map Phyllota phylicoides} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/PHPH.png}
+\caption{Map of parts for \emph{Phyllota phylicoides}}
+\label{fig:map Phyllota phylicoides}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Phyllota phylicoides", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Pimelea linifolia}
+
+Details on parts for \emph{Pimelea linifolia} found in Table \ref{tab:parts_Pimelea linifolia}. See Fig \ref{fig:map Pimelea linifolia} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/PILI.png}
+\caption{Map of parts for \emph{Pimelea linifolia}}
+\label{fig:map Pimelea linifolia}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Pimelea linifolia", flowering_parts)
+@
+
+\clearpage
+
+\subsubsection{Pultenaea tuberculata}
+
+Details on parts for \emph{Pultenaea tuberculata} found in Table \ref{tab:parts_Pultenaea tuberculata}. See Fig \ref{fig:map Pultenaea tuberculata} for a plot.
+
+\begin{figure}
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/PUTU.png}
+\caption{Map of parts for \emph{Pultenaea tuberculata}}
+\label{fig:map Pultenaea tuberculata}
+\end{figure}
+
+<<echo=FALSE,results='asis'>>=
+print_table_species("Pultenaea tuberculata", flowering_parts)
+@
+
+\clearpage
+
+\subsection{Structure of data files}
+
+The following files contain the empirical data used in the analyses:
+
+\begin{enumerate}
+\item \texttt{accessory\_parts.yml}
+\item \texttt{flowerCategories.csv}
+\item \texttt{flowerParts.csv}
+\item \texttt{individuals.csv}
+\item \texttt{MultiplierTable.csv}
+\item \texttt{reproduction.csv}
+\item \texttt{seedMultiplier.csv}
+\end{enumerate}
+The following files contain supplementary data about the species and sites:
+\begin{enumerate}
+\item \texttt{seedsize.csv}
+\item \texttt{sites.csv}
+\item \texttt{species.csv}
+\end{enumerate}
+
+\subsubsection{Accessory Parts}
+
+The file \texttt{accessoryParts.yml} contains, for each species, lists of reproductive tissues that fall into various tissue categories.
+These categories are then used to calculate the reproductive investment in the key reproductive tissue categories, (1) pollen-attraction tissues aborted prior to provisioning; (2) pollen-attraction tissues associated with flowers that form mature seeds; (3) provisioning tissues aborted prior to the formation of a mature seed; (4) packaging and dispersal tissues associated with a mature seed; (5) the mature seed itself.
+Dividing reproductive investment into these categories requires, for each tissue type, knowing the count of parts that reach the key stages (pollinator-ready, onset of provisioning, mature seed) and the mass of parts at each stage.
+Table \ref{tab:accessoryParts_meta} provides descriptions of each reproductive part category in the file \texttt{accessoryParts.yml}.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/accessoryParts_meta.csv", align = 'p{0.1cm}p{6cm}p{10cm}')
+@
+
+\subsubsection{Flowering Categories}
+
+The file \texttt{flowerCategories.csv} contains a matrix of plant parts (rows) by species (columns).
+For each cell that is used on a given species plant map, the meaning of the values in the spreadsheet titled "reproduction" are indicated in this spreadsheet.
+Possible method are (1) count, indicating that the numbers represent simple counts; (2) count\_by\_length, indicating that the length of stem or cone covered with buds, flowers or fruit is measured; (3) regress\_by\_dim, indicating that the dimensions of the flowering part are measured and must be converted to a dry mass using a regression equation; and (4) volume, indicating that the height and diameter of the flowering part are given and must be converted to a dry mass using the calculated volume of the flowering part multiplied by the average density of the flowering part.
+
+The file \texttt{floweringCategories\_meta} contains a matrix of plant parts (rows) by species (columns).
+For each cell that is used on a given species plant map, a description of the botanical parts included in the "flower part" is given as well as the flowering stage at which the flower part is harvested, if it is not obvious.
+
+\subsubsection{Flower Parts}
+The file \texttt{flowerParts.csv} contains records for harvested and weighed flower parts, including collections from tagged individuals (once mature or at time of harvest) and from other individuals in the population (to estimate weight of specific plant parts).
+Table \ref{tab:flowerParts_meta} gives a brief descriptions of each column in the file.
+
+All plant parts included in a species' "plant map" have weights in this spreadsheet – or, in rare cases, entries are instead plants parts whose weight is used to calculate the weight of a plant part included in a "plant map".
+(A "plant map" shows the developmental trajectory of a flower or inflorescence from bud to seed for each species, indicating the flow or carbon as well as discarded parts.) If plant parts are collected from a tagged individual, this spreadsheet also indicates in which census periods this specific weight, rather than a species average, should be used for calculating that individual's reproductive investment.
+Plant parts all have counts and weights, while the subset of plant parts whose size varies, also have columns indicating height and diameter dimensions; the weight of the plant part at a specific size is then determined by either a regression or volume calculation.
+For a few plant parts, census data measure the length of stem or cone covered with flowers; for these situations, the segment length collected is also recorded, such that the number of flowers per unit length can be calculated.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/flowerParts_meta.csv", align = 'p{0.1cm}p{4cm}p{2cm}p{10cm}')
+@
+
+\subsubsection{Individuals}
+This file \texttt{individuals.csv} contains a list of all plants harvested at the 7 Kuring'gai field sites.
+For each individual it includes basic information about each individual - tag number, age, site, whether the plant was alive at the time of harvest, and information on which calculations use this individual's data.
+The data itself is contained in other files.
+Table \ref{Individuals_meta} gives a brief description of each data column in the file.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/Individuals_meta.csv", align = 'p{0.1cm}p{6cm}p{10cm}')
+@
+
+\subsubsection{Multiplier Table}
+The file \texttt{MultiplierTable.csv} is a lookup table indicating, for each species by flower part combination, if the investment per part is for a single (1) or multiple propagules, defined as either a mature fruit or a seed, depending on what is the dispersal unit for each species.
+Within a single column, i.e.
+within a single species developmental trajectory, numbers will change if the "count" used to access reproduction changes at a given developmental stage.
+For instance, with BOLE (\emph{Boronia ledifolia}), counts are made by flowers up through the finished flower stage, but then fruit are the unit counted and each flower forms 4 fruit.
+
+\subsubsection{Reproduction}
+
+The file \texttt{reproduction.csv} provides both verbal and numeric descriptions of reproduction at each census between April-June 2012 (or June 2013 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were first tagged, until April-June 2013 (or June 2014 for Wilunga2013 and the second set of individuals tagged at Waratah2011), when the plants were harvested.
+Table \ref{tab:reproduction_meta} gives a brief description of the columns in the file.
+There is a separate row of data for each individual, at each of the 18 censuses.
+In addition, at each census, there is a row indicating plant parts that are pre-existing on the plant versus new.
+Flower (or fruit) parts are considered pre-existing if the predecessor of that flower part, as described on that species "plant map" existed in a previous census period.
+Some plant maps may have multiple parallel diagrams describing how flower parts develop.
+In that case, a flower part must have a predecessor on that specific diagram to be considered "pre-existing".
+
+Each of the many plant parts are listed as column headers.
+At each census, both new and further developed but pre-existing flower parts are recorded.
+Plant parts that are unchanged in developmental stage between successive censuses are not recorded.
+Neither are plant parts that disappear between successive censuses.
+Instead, pre-existing plant parts are recorded if they have progressed to a "more mature" flowering/fruiting stage, as defined by that species "plant map".
+As an example, if at one census there were 50 PHPH (\emph{Phyllota phylicoides}) buds recorded and at the next stage, 30 PHPH flowers, 30 of the 50 buds progressed from being buds to being flowers, while the remaining 20 buds were either shed or are still buds.
+The numbers entered in the cell correspond to either counts, lengths, or dimensions, depending on the method indicated in the file titled "floweringCategories".
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/reproduction_meta.csv", align = 'p{0.1cm}p{6cm}p{10cm}')
+@
+
+\subsubsection{Seed size}
+The file \texttt{seedsize.csv} includes a collection of species level information, including seed size and embryo-endosperm weight.
+This file also includes data on the number of ovules per ovary, lifespan, age at maturity, and approximate age at which RA asymptotes.
+Table \ref{tab:seedsize_meta} gives a brief description of the data columns in the file.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/seedsize_meta.csv", align = 'p{0.1cm}p{4cm}p{10cm}p{2cm}')
+@
+
+\subsubsection{Sites}
+The file \texttt{sites.csv} lists details of sites used in study.
+Includes site names used in other spreadsheets, date of fire, fire year, as defined by NSW fire layers, and UTM coordinates for each site.
+Table \ref{tab:sites_meta} gives a brief description of the data columns in the file.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/sites_meta.csv", align = 'p{0.1cm}p{6cm}p{10cm}')
+@
+
+\subsubsection{Species}
+The file \texttt{species.csv} lists species included in study.
+Includes 4-letter code names used in other spreadsheets, scientific names, family names, and common names.
+Table \ref{tab:species} gives a brief description of the data columns in the file.
+
+<<echo=FALSE,results='asis'>>=
+  print_table_metadata("../../data/species.csv")
+@
+
+\subsection{Code calculating reproductive investment}
+
+\subsubsection{preprocess.R}
 
@@
 
-\subsection{OrderedListOfParts.R}
+\subsubsection{OrderedListOfParts.R}
 
@@
 
-\subsection{FlowerParts.R}
+\subsubsection{FlowerParts.R}
 
@@
 
-\subsection{GraphRepresentation.R}
+\subsubsection{GraphRepresentation.R}
 
@@
 
-\subsection{Investment.R}
+\subsubsection{Investment.R}
 
@@
 
-\subsection{ReproductionTissues.R}
+\subsubsection{ReproductionTissues.R}
 
@@
 
-\section{Details on calculations by species}
-
-Each species uses notably different algorithms to determine reproductive tissue investment, as each species forms different reproductive tissues and different methods are practical for recording each species' reproductive investment in the field.
-
-\subsection{Banksia ericifolia}
-
-Details on parts for \emph{Banksia ericifolia} found in Table \ref{tab:parts_Banksia ericifolia}. See Fig \ref{fig:map Banksia ericifolia} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Banksia ericifolia", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-plot_graph(BAER_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Banksia ericifolia}}
-\label{fig:map Banksia ericifolia}
-\end{figure}
-
-\clearpage
-
-\subsection{Boronia ledifolia}
-
-Details on parts for \emph{Boronia ledifolia} found in Table \ref{tab:parts_Boronia ledifolia}. See Fig \ref{fig:map Boronia ledifolia} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Boronia ledifolia", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(BOLE_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Boronia ledifolia}}
-\label{fig:map Boronia ledifolia}
-\end{figure}
-
-\clearpage
-
-\subsection{Conospermum ericifolium}
-
-Details on parts for \emph{Conospermum ericifolium} found in Table \ref{tab:parts_Conospermum ericifolium}.  See Fig \ref{fig:map Conospermum ericifolium} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Conospermum ericifolium", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(COER_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Conospermum ericifolium}}
-\label{fig:map Conospermum ericifolium}
-\end{figure}
-
-\clearpage
-
-\subsection{Epacris microphylla}
-
-Details on parts for \emph{Epacris microphylla} found in Table \ref{tab:parts_Epacris microphylla}. See Fig \ref{fig:map Epacris microphylla} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Epacris microphylla", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(EPMI_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Epacris microphylla}}
-\label{fig:map Epacris microphylla}
-\end{figure}
-
-\clearpage
-
-\subsection{Grevillea buxifolia}
-
-Details on parts for \emph{Grevillea buxifolia} found in Table \ref{tab:parts_Grevillea buxifolia}. See Fig \ref{fig:map Grevillea buxifolia} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Grevillea buxifolia", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(GRBU_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Grevillea buxifolia}}
-\label{fig:map Grevillea buxifolia}
-\end{figure}
-
-\clearpage
-
-\subsection{Grevillea speciosa}
-
-Details on parts for \emph{Grevillea speciosa} found in Table \ref{tab:parts_Grevillea speciosa}. See Fig \ref{fig:map Grevillea speciosa} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Grevillea speciosa", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(GRSP_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Grevillea speciosa}}
-\label{fig:map Grevillea speciosa}
-\end{figure}
-
-\clearpage
-
-\subsection{Hakea teretifolia}
-
-Details on parts for \emph{Hakea teretifolia} found in Table \ref{tab:parts_Hakea teretifolia}. See Fig \ref{fig:map Hakea teretifolia} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Hakea teretifolia", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(HATE_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Hakea teretifolia}}
-\label{fig:map Hakea teretifolia}
-\end{figure}
-
-\clearpage
-
-\subsection{Hemigenia purpurea}
-
-Details on parts for \emph{Hemigenia purpurea} found in Table \ref{tab:parts_Hemigenia purpurea}. See Fig \ref{fig:map Hemigenia purpurea} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Hemigenia purpurea", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(HEPU_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Hemigenia purpurea}}
-\label{fig:map Hemigenia purpurea}
-\end{figure}
-
-\clearpage
-
-\subsection{Leucopogon esquamatus}
-
-Details on parts for \emph{Leucopogon esquamatus} found in Table \ref{tab:parts_Leucopogon esquamatus}. See Fig \ref{fig:map Leucopogon esquamatus} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Leucopogon esquamatus", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(LEES_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Leucopogon esquamatus}}
-\label{fig:map Leucopogon esquamatus}
-\end{figure}
-
-\clearpage
-
-\subsection{Persoonia lanceolata}
-
-Details on parts for \emph{Persoonia lanceolata} found in Table \ref{tab:parts_Persoonia lanceolata}. See Fig \ref{fig:map Persoonia lanceolata} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Persoonia lanceolata", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(PELA_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Persoonia lanceolata}}
-\label{fig:map Persoonia lanceolata}
-\end{figure}
-
-\clearpage
-
-\subsection{Petrophile pulchella}
-
-Details on parts for \emph{Petrophile pulchella} found in Table \ref{tab:parts_Petrophile pulchella}. See Fig \ref{fig:map Petrophile pulchella} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Petrophile pulchella", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(PEPU_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Petrophile pulchella}}
-\label{fig:map Petrophile pulchella}
-\end{figure}
-
-\clearpage
-
-\subsection{Phyllota phylicoides}
-
-Details on parts for \emph{Phyllota phylicoides} found in Table \ref{tab:parts_Phyllota phylicoides}. See Fig \ref{fig:map Phyllota phylicoides} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Phyllota phylicoides", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(PHPH_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Phyllota phylicoides}}
-\label{fig:map Phyllota phylicoides}
-\end{figure}
-
-\clearpage
-
-\subsection{Pimelea linifolia}
-
-Details on parts for \emph{Pimelea linifolia} found in Table \ref{tab:parts_Pimelea linifolia}. See Fig \ref{fig:map Pimelea linifolia} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Pimelea linifolia", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(PILI_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Pimelea linifolia}}
-\label{fig:map Pimelea linifolia}
-\end{figure}
-
-\clearpage
-
-\subsection{Pultenaea tuberculata}
-
-Details on parts for \emph{Pultenaea tuberculata} found in Table \ref{tab:parts_Pultenaea tuberculata}. See Fig \ref{fig:map Pultenaea tuberculata} for a plot.
-
-<<echo=FALSE,results='asis'>>=
-print_table_species("Pultenaea tuberculata", flowering_parts)
-@
-
-\begin{figure}
-\centering
-<<echo=FALSE,results='asis'>>=
-  plot_graph(PUTU_GraphMaps$graph)
-@
-\caption{Map of parts for \emph{Pultenaea tuberculata}}
-\label{fig:map Pultenaea tuberculata}
-\end{figure}
-
-\clearpage
-
-\addcontentsline{toc}{section}{References}
-\bibliography{references}
-
 \end{document}

### 2017-05-05 ms/Accessory/Wenk-Accessory-SI.Rnw
-small changes to accessory manuscript files
-typos fixed in metadata files

@@
 make_table_species_values_for_allocation_seedsize_table <- function(file) {
-  data <- select(file,species,embryo_endo_costs, scaled_seed_count,scaled_ovule_count,
+  data <- select(file,species,scaled_seed_count,scaled_ovule_count,
                  scaled_pollen_attract_costs,choosiness,prop_prepollen_success, prop_prepollen_discarded,
@@
 
-names(TableS15) <- c("species","embryo and endosperm costs","scaled seed count","scaled ovule count","scaled pollen-attraction costs","choosiness","success","discarded","success","discarded","pollen-attraction","provisioning")
+names(TableS15) <- c("species","seed count scaled to leaf area","ovule count scaled to leaf area","pollen-attraction costs scaled to leaf area","choosiness (1/seedset)","success","discarded","success","discarded","pollen-attraction","provisioning")
 
@@
 \centering
-\caption{Species values for data plotted in Figure 2: shifts in reproductive tissue allocation with seed size.}
+\caption{Species values for data plotted in Figure 2: shifts in reproductive tissue allocation with seed size.
+Data for reproductive costs (Figure 2, panel a), Seed-size, pollen-attraction costs, and provisioning costs (Figure 2, panel f) are presented in Table 1 in the main text and are not included here.}
 \label{tab:species}
-\begin{tabular}{p{4cm}|p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
+\begin{tabular}{p{4cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
 \hline
-& \multicolumn{7}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
-& \multicolumn{7}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
-& \multicolumn{7}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
+& \multicolumn{4}{c|}{} & \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
+& \multicolumn{4}{c|}{} & \multicolumn{2}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
+& \multicolumn{4}{c|}{} & \multicolumn{2}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
 
@@
 @
+\hline
+& \multicolumn{1}{c|}{Figure reference} & \multicolumn{3}{c|}{Fig 2, panel a} & \multicolumn{2}{c|}{Fig 2, panel b} & \multicolumn{2}{c}{Fig 2, panel c} & \multicolumn{2}{c}{Fig 2, panel d} & \multicolumn{2}{c}{Fig 2, panel e} \\
+
 \end{tabular}
@@
 \centering
-\caption{Testing for shifts in accessory costs with in age, plant size, or reproductive effort.}
+\caption{Testing for shifts in accessory costs with in age, plant size, or reproductive effort.
+Shifts in accessory costs with these variables is suggested as one possible explanation of increasing reproductive investment in larger, older plants, but such a trend did not exist in these data.}
 \label{tab:access_vs_age}
@@
 \centering
-\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight $\times$ bud count'.}
+\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight $\times$ bud count'.
+Due to the high proportion of aborted flowers, flower investment was a better proxy of reproductive investment than was propagule investment.
+This was true both across species (Figure 3, Table 3 in the main text) and within species, as is shown here.}
 \label{tab:propagule_invest_vs_repro}
@@
 \centering
-\caption{Scaling of reproductive tissue costs with total propagule size.}
+\caption{Scaling of reproductive tissue costs with total propagule size.
+In this manuscript all "seed size" calculations use embryo and endosperm size, not propagule size.
+Most previous research has used propagule size as a measure of "seed size" and noted isometric relationships between various tissue costs and "seed size".
+Using embryo and endosperm size, these relationship did not exist for this data set, but are present if "seed size" includes the entire propagule.}
 \label{tab:repro_tissues_vs_prop_size}
@@
 print(xtable(TableS19)
-         , sanitize.text.function=I
-        , include.rownames = FALSE
-        , include.colnames = TRUE,
-        only.contents=TRUE)
-@
-\end{tabular}
-\end{table}
-
-\clearpage
-
-<<echo=FALSE, results='asis', warning=FALSE>>=
-make_table_buds_vs_size <- function() {
-  xvar <- "total_weight_0"
-  yvar <- "ovule_count"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")
-  TableS18 <- dplyr::select(fit$groupsummary,group,n,r2,pval)
-
-  names(TableS18) <- c("species","n","r$^2$","p")
-
-  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  TableS18$species <-  paste("\\textit{",species,"}", sep="")
-
-  TableS18
-}
-
-TableS18 <- make_table_buds_vs_size()
-
-for(i in c(2,3)){
-  TableS18[,i] <- format_r2(TableS18[,i])
-}
-for(i in c(4)){
-  TableS18[,i] <- format_p(TableS18[,i])
-}
-
-TableS18$species  <- paste("\\textit{",unique(TableS18$species),"}", sep="")
-@
-
-\begin{table}[H]
-\centering
-\caption{Count of buds initiated is well predicted by plant size.}
-\label{tab:bud_count_vs_size}
-\begin{tabular}{p{4cm}|x{.75cm}x{1cm}p{1.25cm}}
-\hline
-<<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS18)
          , sanitize.text.function=I

### 2017-05-05 ms/Accessory/Wenk-Accessory-SI.Rnw
more small changes

@@
 within a single species developmental trajectory, numbers will change if the "count" used to access reproduction changes at a given developmental stage.
-For instance, with BOLE (\emph{Boronia ledifolia}), counts are made by flowers up through the finished flower stage, but then fruit are the unit counted and each flower forms 4 fruit.
+For instance, with BOLE (\emph{Boronia ledifolia}), counts are made by flowers up through the finished flower stage, but then fruits are the unit counted for not all 4 fruits develop within each flower.
 

### 2017-05-16 ms/Accessory/Wenk-Accessory-SI.Rnw
Completing supplementary information

@@
 
-% allow some pages to be landscape
-\usepackage{lscape}
-
 \titleprefix{Supporting Materials for:}
@@
 flowering_parts <- read.csv("Sup_Table_flowering_parts.csv", stringsAsFactors=FALSE, check.names=FALSE)
-
-flowering_parts$method <- gsub("_", " ", flowering_parts$method, fixed=TRUE)
+flowering_parts$Method <- clean_headers(flowering_parts$Method)
+flowering_parts$Part <- firstup(flowering_parts$Part)
+flowering_parts$Description <- firstup(flowering_parts$Description)
 
 print_table_species <- function(species, data) {
-  data <- data[data$species == species, -c(1)]
+  data <- data[data$Species == species, -c(1)]
   print(xtable(data,
             hline.after=c(1),
-            align='p{0.1cm}p{4cm}p{6cm}p{2.5cm}p{1cm}p{1cm}',
-            label=sprintf("tab:parts_%s", species),
-            caption=sprintf("Table of parts for %s.", species)),
+            align='p{0.1cm}p{4.5cm}p{6cm}p{2cm}p{1cm}p{1cm}',
+            label=sprintf("tab:parts_%s", gsub(" ", "_", species)),
+            caption=sprintf("Table of parts for \\emph{%s}.", species)),
       sanitize.text.function=I,
@@
             caption=
-              sprintf("Details on variables within the file \\texttt{%s}.",
-              gsub("\\_meta", "", file, fixed = TRUE))),
+              sprintf("Description of variables within the file \\texttt{data/%s}. These definitions can also be found within the file \\texttt{data/%s}.",
+              gsub("\\_meta", "", file, fixed = TRUE), file)),
       , table.placement = "h"
@@
 }
-
-plot_graph <- function(graph) {
-
-  plot(graph)
-  #plot(NA, type="n", xlim=c(0,1), ylim=c(0,1), ann=FALSE, axes=FALSE); box()
-}
 @
@@
 
-names(TableS15) <- c("species","seed count scaled to leaf area","ovule count scaled to leaf area","pollen-attraction costs scaled to leaf area","choosiness (1/seedset)","success","discarded","success","discarded","pollen-attraction","provisioning")
+names(TableS15) <- c("species","seed count","ovule count","pollen-attraction costs","choosi- ness","success","discarded","success","discarded","pollen-attraction","provi- sioning")
 
-for (i in 2:12) {
-TableS15[,i] <- format(TableS15[,i],digits=3,nsmall=2)
+for (i in 2:11) {
+TableS15[,i] <- format(TableS15[,i],digits=3, nsmall=0)
 }
@@
 
-\begin{table}[H]
+\begin{table}[h]
 \centering
 \caption{Species values for data plotted in Figure 2: shifts in reproductive tissue allocation with seed size.
+Counts and costs are per unit leaf area of the plant.
+The bottom line indicates the corresponding figure of the main text where the data are presented.
 Data for reproductive costs (Figure 2, panel a), Seed-size, pollen-attraction costs, and provisioning costs (Figure 2, panel f) are presented in Table 1 in the main text and are not included here.}
 \label{tab:species}
-\begin{tabular}{p{4cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
+{\footnotesize
+\begin{tabular}{p{3cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1.5cm}p{1cm}}
 \hline
-& \multicolumn{4}{c|}{} & \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
-& \multicolumn{4}{c|}{} & \multicolumn{2}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
-& \multicolumn{4}{c|}{} & \multicolumn{2}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
-
-% \begin{tabular}{p{3cm}|p{1cm}p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1.5cm}p{1cm}|p{1cm}p{1.5cm}|p{1.5cm}p{1.5cm}}
-% \hline
-% &&&& \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c}{Proportion}& \multicolumn{2}{c}{Proportion} \\
-% &&&& \multicolumn{2}{c|}{pollen-attraction} & \multicolumn{2}{c}{provisioning}& \multicolumn{2}{c}{success} \\
-% &&&& \multicolumn{2}{c|}{investment to} & \multicolumn{2}{c}{investment to}& \multicolumn{2}{c}{investment to} \\
-
+& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c|}{Proportion}& \multicolumn{2}{c}{Proportion} \\
+& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{pollen-attraction} & \multicolumn{2}{c|}{provisioning}& \multicolumn{2}{c}{success} \\
+& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{investment to} & \multicolumn{2}{c|}{investment to}& \multicolumn{2}{c}{investment to} \\
 <<echo=FALSE, results='asis', warning=FALSE>>=
@@
         only.contents=TRUE)
+cat("Figure reference & \\multicolumn{2}{c|}{Fig.
+2, panel a} & \\multicolumn{2}{c|}{Fig.
+2, panel b} & \\multicolumn{2}{c|}{Fig.
+2, panel c} & \\multicolumn{2}{c|}{Fig.
+2, panel d}  & \\multicolumn{2}{c}{Fig.
+2, panel e}\\\\
+\\hline")
 @
-\hline
-& \multicolumn{1}{c|}{Figure reference} & \multicolumn{3}{c|}{Fig 2, panel a} & \multicolumn{2}{c|}{Fig 2, panel b} & \multicolumn{2}{c}{Fig 2, panel c} & \multicolumn{2}{c}{Fig 2, panel d} & \multicolumn{2}{c}{Fig 2, panel e} \\
-
 \end{tabular}
-
-{\color{red}
-\begin{itemize}
-  \item Started reworking table headers but have no idea what they're meant to be.
-  \item Decrease decimal places?
-  \item Swing page to landscape?
-  \item Add units?
-\end{itemize}
 }
-
 \end{table}
@@
 
-  names(TableS16) <- c("species","n","r$^2$","p","n","r$^2$","p","n","r$^2$","p")
+  names(TableS16) <- c("Species","n","r$^2$","p","n","r$^2$","p","n","r$^2$","p")
 
-  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  TableS16$species <-  paste("\\textit{",species,"}", sep="")
+  Species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  TableS16$Species <-  paste("\\textit{",Species,"}", sep="")
 
@@
   acc_slopes <- dplyr::select(results,group,n,r2,pval)
-  names(acc_slopes) <- c("species","n_propagule","r2_propagule","p_propagule")
+  names(acc_slopes) <- c("Species","n_propagule","r2_propagule","p_propagule")
 
@@
   acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
-  names(acc_slopes2) <- c("species","n_flower","r2_flower","p_flower")
-  acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="species")
-  names(acc_slopes) <- c("species","n","r$^2$","p", "n","r$^2$","p")
-  species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  acc_slopes$species <-  paste("\\textit{",species,"}", sep="")
+  names(acc_slopes2) <- c("Species","n_flower","r2_flower","p_flower")
+  acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="Species")
+  names(acc_slopes) <- c("Species","n","r$^2$","p", "n","r$^2$","p")
+  Species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
+  acc_slopes$Species <-  paste("\\textit{",Species,"}", sep="")
 
@@
 TableS19 <- make_table_Table2_using_propagule()
-names(TableS19) <- c("costs","r$^2$","slope (95$\\%$ CI)","p (slope test)")
+names(TableS19) <- c("Costs","r$^2$","Slope (95$\\%$ CI)","p (slope test)")
+TableS19$Costs <- firstup(TableS19$Costs)
+
 @
@@
 
-\section{Additional details on methods and details about input files}
+\section{Additional details on methods}
+
+\subsection{Methods for calculating investment in reproductive tissues}
+
+We collected data for 14 species (Table \ref{tab:species}) at 7 sites (Tables \ref{tab:sites}). Individuals were selected as described in the main text.
+
+<<echo=FALSE,results='asis'>>=
+  data <-  read.csv("../../data/species.csv", stringsAsFactors=FALSE, check.names=FALSE)
+  data$Common_name <- firstup(data$Common_name)
+  names(data) <-  clean_headers(names(data))
+
+  print(xtable(data,
+            align= 'p{1cm}p{5cm}p{3cm}p{3cm}p{2cm}p{3cm}',
+            hline.after=c(1),
+            label= "tab:species",
+            caption="Details on study species."),
+      , table.placement = "h"
+      , caption.placement = "top"
+      , include.rownames = FALSE
+      , include.colnames = TRUE
+      , size = "small"
+      , tabular.environment = 'longtable'
+      , floating = FALSE)
+
+  data <-  read.csv("../../data/sites.csv", stringsAsFactors=FALSE, check.names=FALSE)
+  data <- data[order(data$age_at_harvest),]
+  names(data) <-  clean_headers(names(data))
+
+  print(xtable(data,
+            align= 'p{0.1cm}p{2cm}p{1cm}p{1cm}p{1cm}p{1.4cm}p{1.4cm}p{7cm}',
+            hline.after=c(1),
+            label= "tab:sites",
+            caption="Details on study sites."),
+      , table.placement = "h"
+      , caption.placement = "top"
+      , include.rownames = FALSE
+      , include.colnames = TRUE
+      , size = "small"
+      , tabular.environment = 'longtable'
+      , floating = FALSE)
+@
 
 For each species we established a list of different reproductive tissue parts and mapped how these parts developed through time.
+Each species reproductive tissue development initiates with a bud or inflorescence bud, which increases in size and is divided into multiple tissue types several times during development.
+For instance, a bud, once open, divides into being petals + stamens, a sepal, and a stigma.
+As a pollinated stigma develops into a fruit, it will be further divided into seed, seed pod, and potentially additional parts.
+The central development axis terminates with the formation of a mature seed, while side axes end in fully developed tissues (such as petals, calyx, pedicel) and aborted tissues (aborted seeds, aborted fruit) at the point where they cease to increase in mass.
 
-Each species reproductive tissue development initiates with a bud or inflorescence bud, which increases in size and is divided into multiple tissue types several times during development.For instance, a bud, once open, divides into being petals + stamens, a sepal, and a stigma.
-As a pollinated stigma develops into a fruit, it will be further divided into seed, seed pod, and potentially additional parts.
-The central development axis terminates with the formation of a mature seed, while side branches end in fully developed tissues (such as petals, calyx, pedicel) and aborted tissues (aborted seeds, aborted fruit) at the point where they cease to increase in mass.
-The developmental flowchart for each species is shown in the maps in the next section.
+While all species developed reproductive tissues from buds to seeds, species showed different developmental pathways in the precise reproductive tissues used.
+We therefore created a developmental flowchart for each species, as shown below in following sections in Figs.
+\ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}).
+Tables \ref{tab:parts_Banksia_ericifolia}-Table \ref{tab:parts_Pultenaea_tuberculata} then provide, for each species, a list of plant parts, a description of exactly what tissues are included in each plant part and at what developmental stage, the method whereby the count and mass of the plant parts is measured, and the number of ovules in each unit of plant part.
 
-Tables
-The accompanying table for each species provides a list of plant parts, a description of exactly what tissues are included in each plant part and at what developmental stage, the method whereby the count and mass of the plant parts is measured, and the number of ovules in each unit of plant part.
-
-\subsection{How the census is completed for each part}
+\subsubsection{How the census is completed for each part}
 
@@
 For some reproductive parts a simple count is practical, while for species with a large number of buds (or flowers or fruit) that are regularly spaced along branches, the length of stem covered in buds is a better measure.
-These lengths were converted into counts through a species value of "flowers per length".
+These lengths were converted into counts through a species-level estimate of "flowers per length".
 For species that form cones, the cones can be notably different in size and each cone's dimensions was recorded throughout development.
-The counts of flowers (or other reproductive tissues) were then converted to a count of ovules using the values in the file \texttt{multiplierTable.csv} (details below).
+The counts of flowers (or other reproductive tissues) were then converted to a count of ovules using the values in the variable \texttt{Multiplier per factor}.
+Tables \ref{tab:parts_Banksia_ericifolia}-Table \ref{tab:parts_Pultenaea_tuberculata} indicate for each species and plant part, the method used to estimate the mass of parts.
 
-\subsection{How parts weights are determined}
+\subsubsection{How parts weights are determined}
 
-For all plant parts, a sample of the representative part was collected on other individuals in the population to obtain a mean tissue mass.
-For plant parts that vary considerably in size, such as cones, the mass of parts of different sizes was measured and a regression of mass per length or mass per volume was established.
-The data file flowerCategories indicates, for each reproductive tissue type, for each species, what method was used to determine the mass of the plant part.
-
+For all plant parts, a sample of the representative part was collected from other individuals growing nearby the sample population.
+We then estimated an average mass of that tissue part for each species.
+For plant parts that vary considerably in size, such as cones, the mass of parts of different sizes were measured and a regression of mass per length or mass per volume was established.
 For some individuals, actual reproductive parts were collected.
 This includes any reproductive parts of the plants at the time of harvest, including both current reproductive tissues and previously mature woody fruits still attached to the branches.
-In additional some seeds were collected once mature, but before they were dispersed.
+In addition, some seeds were collected once mature, but before they were dispersed.
 Whenever actual reproductive parts were collected from an individual, the unit mass of these structures was used instead of the population mean.
+
+\subsubsection{How investment in each part is estimated}
+
+Our goal was to estimate the amount of mass each plant invests in different tissues within a given time period from field census data recording the numbers of each part type at successive census dates for a given plant.
+To achieve this we apply an accounting algorithm to estimate the number of units that have progressed from one category to another in the interval between censuses.
+The algorithm works as follows:
+
+\begin{itemize}
+\item At each census, we compare the number of each part with possible numbers of predecessors from the prior census.
+Predecessors are those parts that lie at the same or younger age in the plant maps.
+\item For a each part in turn, we try to identify the most obvious predecessor, being the one with minimal amount of progression needed to satisfy successive censuses.
+The predecessor is removed from the list of possible predecessors and the process sis repeated until all parts have predecessors.
+\item After finding a predecessor, the investment needed to progress  is calculated.
+The investment is defined as the difference between the element mass at the time of census and that of it's predecessor.
+\end{itemize}
+
+As an example, if, in census $t$, a large bud exists, it is assumed that it has developped from a medium sized bud (the previous stage) in census $t$-1.
+If in census $t$-1 no medium buds exists, the large bud is assumed to have developped from a small bud (two stages back).
+This process continues back along the plant map developmental trajectory until a plausible predecessor is located in the previous census period.
+After this process is complete, any parts from census $t$-1 for which a subsequent developmental stage is not identified as designated as having reached their final developmental stage at census $t$-1 (i.e.
+they aborted).
+For plant parts, such as petals, that as a final development stage, no success is sought.
 
@@
 
-Each species uses notably different algorithms to determine reproductive tissue investment, as each species forms different reproductive tissues and different methods are practical for recording each species' reproductive investment in the field.
+The algorithm for estimating reproductive investment is adjusted for each species according to the specific developmental pathway it uses to produce seeds.
+Below, for each species we provide a graphic illustration of the pathway used (Figs.
+\ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}), and tables detailing specific about each part (Tables \ref{tab:parts_Banksia_ericifolia}-Table \ref{tab:parts_Pultenaea_tuberculata}).
+Figure \ref{fig:map_key} provides a key on the colouring in Figs.
+\ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}).
 
-\subsubsection{Banksia ericifolia}
+Each plant map begins with a bud (or the appropriate starting point for reproductive tissue development for a specific species) and depicts graphically how the tissue develops through the plant's reproductive cycle to a seed or mature fruit.
+During the reproductive cycle, there will be branches off the central tissue axis (development from bud to seed).
+Some of these lead to aborted tissue types (colored red in the graph maps below) and others lead to tissues that reach their final development stage and are then shed by a plant (e.g.
+petals, calyx, seed pod; colored green in the graph maps below).
+For some species, there are multiple axes of development.
+For instance, cones and flowers on a cone have separate axes, because the number of flowers on a cone is inconsistent across individuals.
+A few species have aborted plant parts that are listed as a separate axis.
+In these cases, the aborted unit weighs less than a bud and therefore cannot be shown as ever having reached the stage of a bud.
 
-Details on parts for \emph{Banksia ericifolia} found in Table \ref{tab:parts_Banksia ericifolia}. See Fig \ref{fig:map Banksia ericifolia} for a plot.
+\begin{figure}[h]
+\centering
+\includegraphics[width=\linewidth]{../plant_maps/crop/key.png}
+\caption{Key describing use of colour in Figs. \ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}.}
+\label{fig:map_key}
+\end{figure}
+\clearpage
 
-\begin{figure}
+\subsubsection{\emph{Banksia ericifolia}}
+
+Fig.
+\ref{fig:map_Banksia_ericifolia} indicates the developmental pathway for reproductive tissues in the species \emph{Banksia ericifolia}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Banksia_ericifolia}.
+
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/BAER.png}
-\caption{Map of parts for \emph{Banksia ericifolia}}
-\label{fig:map Banksia ericifolia}
+\caption{Map of parts for \emph{Banksia ericifolia}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Banksia_ericifolia}
 \end{figure}
 
+\clearpage
 <<echo=FALSE,results='asis'>>=
@@
 
-\subsubsection{Boronia ledifolia}
+\subsubsection{\emph{Boronia ledifolia}}
 
-Details on parts for \emph{Boronia ledifolia} found in Table \ref{tab:parts_Boronia ledifolia}. See Fig \ref{fig:map Boronia ledifolia} for a plot.
+Fig.
+\ref{fig:map_Boronia_ledifolia} indicates the developmental pathway for reproductive tissues in the species \emph{Boronia ledifolia}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Boronia_ledifolia}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/BOLE.png}
-\caption{Map of parts for \emph{Boronia ledifolia}}
-\label{fig:map Boronia ledifolia}
+\caption{Map of parts for \emph{Boronia ledifolia}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Boronia_ledifolia}
 \end{figure}
 
+\clearpage
 <<echo=FALSE,results='asis'>>=
@@
 
-\subsubsection{Conospermum ericifolium}
+\subsubsection{\emph{Conospermum ericifolium}}
 
-Details on parts for \emph{Conospermum ericifolium} found in Table \ref{tab:parts_Conospermum ericifolium}.  See Fig \ref{fig:map Conospermum ericifolium} for a plot.
+Fig.
+\ref{fig:map_Conospermum_ericifolium} indicates the developmental pathway for reproductive tissues in the species \emph{Conospermum ericifolium}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Conospermum_ericifolium}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/COER.png}
-\caption{Map of parts for \emph{Conospermum ericifolium}}
-\label{fig:map Conospermum ericifolium}
+\caption{Map of parts for \emph{Conospermum ericifolium}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Conospermum_ericifolium}
 \end{figure}
 
+\clearpage
 <<echo=FALSE,results='asis'>>=
@@
 
-\subsubsection{Epacris microphylla}
+\subsubsection{\emph{Epacris microphylla}}
 
-Details on parts for \emph{Epacris microphylla} found in Table \ref{tab:parts_Epacris microphylla}. See Fig \ref{fig:map Epacris microphylla} for a plot.
+Fig.
+\ref{fig:map_Epacris_microphylla} indicates the developmental pathway for reproductive tissues in the species \emph{Epacris microphylla}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Epacris_microphylla}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/EPMI.png}
-\caption{Map of parts for \emph{Epacris microphylla}}
-\label{fig:map Epacris microphylla}
+\caption{Map of parts for \emph{Epacris microphylla}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Epacris_microphylla}
 \end{figure}
 
+\clearpage
 <<echo=FALSE,results='asis'>>=
@@
 
-\subsubsection{Grevillea buxifolia}
+\subsubsection{\emph{Grevillea buxifolia}}
 
-Details on parts for \emph{Grevillea buxifolia} found in Table \ref{tab:parts_Grevillea buxifolia}. See Fig \ref{fig:map Grevillea buxifolia} for a plot.
+Fig.
+\ref{fig:map_Grevillea_buxifolia} indicates the developmental pathway for reproductive tissues in the species \emph{Grevillea buxifolia}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Grevillea_buxifolia}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/GRBU.png}
-\caption{Map of parts for \emph{Grevillea buxifolia}}
-\label{fig:map Grevillea buxifolia}
+\caption{Map of parts for \emph{Grevillea buxifolia}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Grevillea_buxifolia}
 \end{figure}
+
+\clearpage
 
@@
 
-\subsubsection{Grevillea speciosa}
+\subsubsection{\emph{Grevillea speciosa}}
 
-Details on parts for \emph{Grevillea speciosa} found in Table \ref{tab:parts_Grevillea speciosa}. See Fig \ref{fig:map Grevillea speciosa} for a plot.
+Fig.
+\ref{fig:map_Grevillea_speciosa} indicates the developmental pathway for reproductive tissues in the species \emph{Grevillea speciosa}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Grevillea_speciosa}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/GRSP.png}
-\caption{Map of parts for \emph{Grevillea speciosa}}
-\label{fig:map Grevillea speciosa}
+\caption{Map of parts for \emph{Grevillea speciosa}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Grevillea_speciosa}
 \end{figure}
 
+\clearpage
 <<echo=FALSE,results='asis'>>=
@@
 
-\subsubsection{Hakea teretifolia}
+\subsubsection{\emph{Hakea teretifolia}}
 
-Details on parts for \emph{Hakea teretifolia} found in Table \ref{tab:parts_Hakea teretifolia}. See Fig \ref{fig:map Hakea teretifolia} for a plot.
+Fig.
+\ref{fig:map_Hakea_teretifolia} indicates the developmental pathway for reproductive tissues in the species \emph{Hakea teretifolia}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Hakea_teretifolia}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/HATE.png}
-\caption{Map of parts for \emph{Hakea teretifolia}}
-\label{fig:map Hakea teretifolia}
+\caption{Map of parts for \emph{Hakea teretifolia}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Hakea_teretifolia}
 \end{figure}
+
+\clearpage
 
@@
 
-\subsubsection{Hemigenia purpurea}
+\subsubsection{\emph{Hemigenia purpurea}}
 
-Details on parts for \emph{Hemigenia purpurea} found in Table \ref{tab:parts_Hemigenia purpurea}. See Fig \ref{fig:map Hemigenia purpurea} for a plot.
+Fig.
+\ref{fig:map_Hemigenia_purpurea} indicates the developmental pathway for reproductive tissues in the species \emph{Hemigenia purpurea}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Hemigenia_purpurea}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/HEPU.png}
-\caption{Map of parts for \emph{Hemigenia purpurea}}
-\label{fig:map Hemigenia purpurea}
+\caption{Map of parts for \emph{Hemigenia purpurea}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Hemigenia_purpurea}
 \end{figure}
 
+\clearpage
 <<echo=FALSE,results='asis'>>=
@@
 
-\subsubsection{Leucopogon esquamatus}
+\subsubsection{\emph{Leucopogon esquamatus}}
 
-Details on parts for \emph{Leucopogon esquamatus} found in Table \ref{tab:parts_Leucopogon esquamatus}. See Fig \ref{fig:map Leucopogon esquamatus} for a plot.
+Fig.
+\ref{fig:map_Leucopogon_esquamatus} indicates the developmental pathway for reproductive tissues in the species \emph{Leucopogon esquamatus}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Leucopogon_esquamatus}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/LEES.png}
-\caption{Map of parts for \emph{Leucopogon esquamatus}}
-\label{fig:map Leucopogon esquamatus}
+\caption{Map of parts for \emph{Leucopogon esquamatus}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Leucopogon_esquamatus}
 \end{figure}
 
+\clearpage
 <<echo=FALSE,results='asis'>>=
@@
 
-\subsubsection{Persoonia lanceolata}
+\subsubsection{\emph{Persoonia lanceolata}}
 
-Details on parts for \emph{Persoonia lanceolata} found in Table \ref{tab:parts_Persoonia lanceolata}. See Fig \ref{fig:map Persoonia lanceolata} for a plot.
+Fig.
+\ref{fig:map_Persoonia_lanceolata} indicates the developmental pathway for reproductive tissues in the species \emph{Persoonia lanceolata}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Persoonia_lanceolata}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/PELA.png}
-\caption{Map of parts for \emph{Persoonia lanceolata}}
-\label{fig:map Persoonia lanceolata}
+\caption{Map of parts for \emph{Persoonia lanceolata}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Persoonia_lanceolata}
 \end{figure}
+
+\clearpage
 
@@
 
-\subsubsection{Petrophile pulchella}
+\subsubsection{\emph{Petrophile pulchella}}
 
-Details on parts for \emph{Petrophile pulchella} found in Table \ref{tab:parts_Petrophile pulchella}. See Fig \ref{fig:map Petrophile pulchella} for a plot.
+Fig.
+\ref{fig:map_Petrophile_pulchella} indicates the developmental pathway for reproductive tissues in the species \emph{Petrophile pulchella}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Petrophile_pulchella}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/PEPU.png}
-\caption{Map of parts for \emph{Petrophile pulchella}}
-\label{fig:map Petrophile pulchella}
+\caption{Map of parts for \emph{Petrophile pulchella}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Petrophile_pulchella}
 \end{figure}
+
+\clearpage
 
@@
 
-\subsubsection{Phyllota phylicoides}
+\subsubsection{\emph{Phyllota phylicoides}}
 
-Details on parts for \emph{Phyllota phylicoides} found in Table \ref{tab:parts_Phyllota phylicoides}. See Fig \ref{fig:map Phyllota phylicoides} for a plot.
+Fig.
+\ref{fig:map_Phyllota_phylicoides} indicates the developmental pathway for reproductive tissues in the species \emph{Phyllota phylicoides}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Phyllota_phylicoides}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/PHPH.png}
-\caption{Map of parts for \emph{Phyllota phylicoides}}
-\label{fig:map Phyllota phylicoides}
+\caption{Map of parts for \emph{Phyllota phylicoides}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Phyllota_phylicoides}
 \end{figure}
+
+\clearpage
 
@@
 
-\subsubsection{Pimelea linifolia}
+\subsubsection{\emph{Pimelea linifolia}}
 
-Details on parts for \emph{Pimelea linifolia} found in Table \ref{tab:parts_Pimelea linifolia}. See Fig \ref{fig:map Pimelea linifolia} for a plot.
+Fig.
+\ref{fig:map_Pimelea_linifolia} indicates the developmental pathway for reproductive tissues in the species \emph{Pimelea linifolia}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Pimelea_linifolia}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/PILI.png}
-\caption{Map of parts for \emph{Pimelea linifolia}}
-\label{fig:map Pimelea linifolia}
+\caption{Map of parts for \emph{Pimelea linifolia}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Pimelea_linifolia}
 \end{figure}
+
+\clearpage
 
@@
 
-\subsubsection{Pultenaea tuberculata}
+\subsubsection{\emph{Pultenaea tuberculata}}
 
-Details on parts for \emph{Pultenaea tuberculata} found in Table \ref{tab:parts_Pultenaea tuberculata}. See Fig \ref{fig:map Pultenaea tuberculata} for a plot.
+Fig.
+\ref{fig:map_Pultenaea_tuberculata} indicates the developmental pathway for reproductive tissues in the species \emph{Pultenaea tuberculata}.
+Arrows indicate the direction of progression.
+The numbers of each part shown in the diagram were recorded in successive censuses.
+Further details on each part type are given in Table \ref{tab:parts_Pultenaea_tuberculata}.
 
-\begin{figure}
+\begin{figure}[h]
 \centering
 \includegraphics[width=\linewidth]{../plant_maps/crop/PUTU.png}
-\caption{Map of parts for \emph{Pultenaea tuberculata}}
-\label{fig:map Pultenaea tuberculata}
+\caption{Map of parts for \emph{Pultenaea tuberculata}. Colours indicate different categories, as described in Fig. \ref{fig:map_key}.}
+\label{fig:map_Pultenaea_tuberculata}
 \end{figure}
+
+\clearpage
 
@@
 
-The following files contain the empirical data used in the analyses:
+The following files contain the empirical data used in the analyses decsribed above and in the main:
 
@@
 \end{enumerate}
+
+Below we describe in more detail the contents of each file.
 
@@
 <<echo=FALSE,results='asis'>>=
-  print_table_metadata("../../data/species.csv")
+  print_table_metadata("../../data/species_meta.csv", align = 'p{0.1cm}p{6cm}p{10cm}')
 @
 
+\clearpage
 \subsection{Code calculating reproductive investment}
 
-\subsubsection{preprocess.R}
+Code reproducing the results described in this paper is available at \\ \href{https://github.com/traitecoevo/reproductive_allocation_kuringai}{github.com/traitecoevo/reproductive\_allocation\_kuringai}.
+Further instructions on running the code are available at that address.
+Here we simply provide a brief overview of the content.
+The folder \texttt{R} contains functions implementing the methods described above and in the main text as follows.
 
-Includes functions filterBySpecies, which subsets by species, and filterForAllocation, indicating which individuals to use for allocation calculations.
+\subsubsection{\texttt{FlowerParts.R}}
 
-Uses data files: data/individuals.csv
-Output: IndividualsList (by species)
+Defines functions that calculates the unit weights of all reproductive tissues for each individual, including special calculations for determining,
+where applicable: i)  weights based on dimensions; and ii) individual based weights.
 
-\subsubsection{OrderedListOfParts.R}
+\subsubsection{\texttt{GraphRepresentation.R}}
 
-Script defining lists of reproductive parts for each species.
+Defines the plant maps for each species, as shown in Figs. \ref{fig:map_Banksia ericifolia}-Table \ref{fig:map_Pultenaea tuberculata}. Also defines the list of reproductive parts for each species.
 
-Uses data files: None
-Output: PartsList (by species)
+\subsubsection{\texttt{Growth.R}}
 
-\subsubsection{FlowerParts.R}
+Defines functions that estimate growth rates of the plant (not used in this analysis).
 
-Script to calculate the unit weights of all reproductive tissues for each individual, including special calculations for:
+\subsubsection{\texttt{Investment.R}}
 
-\begin{enumerate}
-\item determine weights based on dimensions where applicable
-\item individual based weights where applicable
-\end{enumerate}
+Functions that combine, for each species, the map of parts (\texttt{GraphMaps}), weights of flower parts (\texttt{PartsSummary}), and the census data (\texttt{Reproduction}) to calculate the actual investment in reproductive parts.
+The output is a list with four dataframes, but only one (\texttt{FD} (= Final Development)) is used.
+The others were generated for error checking.
 
-Uses data files and data frames: data/flowerParts.csv, PartsList (by species)
-Output: PartsSummary (by species)
+\subsubsection{\texttt{ReproductionTissues.R}}
 
-\subsubsection{GraphRepresentation.R}
+Defines functions that take the investment data and breaks it down into specific reproductive cost categories based on the data in \texttt{accessoryParts.yml}
 
-Script describing defining the plant maps for each species.
-Each plant map begins with a bud (or the appropriate starting point for reproductive tissue development for a specific species) and depicts graphically how the tissue develops through the plant's reproductive cycle to a seed or mature fruit.
-During the reproductive cycle, there will be branches off the central tissue axis (development from bud to seed).
-Some of these lead to aborted tissue types (colored red in the graph maps below) and others lead to tissues that reach their final development stage and are then shed by a plant (e.g.
-petals, calyx, seed pod; colored green in the graph maps below).
-For some species, there are mutiple axes of development.
-For instance, cones and flowers on a cone have separate axes, because the number of flowers on a cone is inconsistent across individuals.
-A few species have aborted plant parts that are listed as a separate axis.
-In these cases, the aborted unit weighs less than a bud and therefore cannot be shown as ever having reached the stage of a bud.
+\subsubsection{\texttt{Species.R}}
 
-Uses data files and data frames: PartsSummary (by species), data/MultiplierTable.csv
-Output: GraphMaps (by species)
+Defines functions that apply the methods for all species in the study.
 
-\subsubsection{Investment.R}
+\subsubsection{\texttt{Summaries.R}}
 
-Script that combines each species plant map (GraphMaps), weights of flower parts (PartsSummary), and the census data (Reproduction) to calculate the actual investment in reproductive parts.
+Defines functions that summarise and combined the different components.
 
-A key part of the calculation is the algorithm which estimates demography of numbers of parts, with respect to map of progression.
-That is, if, in census x, a large bud exists, it is assumed that it has developped from a medium sized bud (the previous stage) in census x-1.
-If in census x-1 no medium buds exists, the large bud is assumed to have developped from a small bud (two stages back).
-This process continues back along the plant map developmental trajectory until a plausible predecessor is located in the previous census period.
-After this process is complete, any parts from census x-1 for which a subsequent developmental stage is not identified as designated as having reached their final developmental stage at census x-1 (i.e.
-they aborted).
+\subsubsection{\texttt{WeightCalculations.R}}
 
-For plant parts, such as petals, that as a final development stage, no success is sought.
-
-There are four dataframes within Investment, but only FD (FinalDevelopment) is used. The others were generated for error checking.
-
-Uses data files and data frames: data/reproduction.csv (and Reproduction), data/floweringCategories.csv (and FloweringCategories), data/multiplierTable.csv (and MultiplierTable), GraphMaps (by species), PartsSummary (by species)
-Output: Investment (by species)
-
-\subsubsection{ReproductionTissues.R}
-
-This script takes the investment data and breaks it down into specific reproductive cost categories based on the data in accessoryParts.yml
-
-Uses data files and data frames: IndividualsList (by species), data/accessoryParts.yml(and InvestmentCategories), Investment (by species),  PartsSummary (by species)
-Output: ReproductiveCosts (by species)
+Functions that estimate, for each part, the weights invested in reproductive allocation.
 

### 2017-05-22 ms/Accessory/Wenk-Accessory-SI.Rnw
Better readme, links, Clean analysis script

@@
 
-Code reproducing the results described in this paper is available at \\ \href{https://github.com/traitecoevo/reproductive_allocation_kuringai}{github.com/traitecoevo/reproductive\_allocation\_kuringai}.
+Code reproducing the results described in this paper is available at \\ \href{https://github.com/traitecoevo/reproductive_allocation_kuringgai}{github.com/traitecoevo/reproductive\_allocation\_kuringgai}.
 Further instructions on running the code are available at that address.

### 2017-05-22 Analysis-accessory.R

@@ -1,5 +1,3 @@
-
-
 library(smatr)
 library(broom)
 library(dplyr)

### 2017-05-22 ms/Accessory/Wenk-Accessory-SI.Rnw
Final edits, cover letter, abstract

@@
 
-For each species we established a list of different reproductive tissue parts and mapped how these parts developed through time.
-Each species reproductive tissue development initiates with a bud or inflorescence bud, which increases in size and is divided into multiple tissue types several times during development.
+For each species, we established a list of different reproductive tissue parts and mapped how these parts developed through time.
+In all species, reproductive tissue development initiates with a bud or inflorescence bud, which increases in size and is divided into multiple tissue types several times during development.
 For instance, a bud, once open, divides into being petals + stamens, a sepal, and a stigma.
@@
 
-While all species developed reproductive tissues from buds to seeds, species showed different developmental pathways in the precise reproductive tissues used.
+While all species developed reproductive tissues from buds to seeds, species showed different developmental pathways due to the precise reproductive tissues used.
 We therefore created a developmental flowchart for each species, as shown below in following sections in Figs.
@@
 they aborted).
-For plant parts, such as petals, that as a final development stage, no success is sought.
+For plant parts, such as petals, that is a final development stage, no success is sought.
 
@@
 For each cell that is used on a given species plant map, a description of the botanical parts included in the "flower part" is given as well as the flowering stage at which the flower part is harvested, if it is not obvious.
+This is the information presented in Tables \ref{tab:parts_Banksia_ericifolia}-Table \ref{tab:parts_Pultenaea_tuberculata}, above.
 
@@
 
-All plant parts included in a species' "plant map" have weights in this spreadsheet – or, in rare cases, entries are instead plants parts whose weight is used to calculate the weight of a plant part included in a "plant map".
+All plant parts included in a species' "plant map" have weights in this spreadsheet -- or, in rare cases, entries are instead plants parts whose weight is used to calculate the weight of a plant part included in a "plant map".
 (A "plant map" shows the developmental trajectory of a flower or inflorescence from bud to seed for each species, indicating the flow or carbon as well as discarded parts.) If plant parts are collected from a tagged individual, this spreadsheet also indicates in which census periods this specific weight, rather than a species average, should be used for calculating that individual's reproductive investment.
@@
 The data itself is contained in other files.
-Table \ref{Individuals_meta} gives a brief description of each data column in the file.
+Table \ref{tab:Individuals_meta} gives a brief description of each data column in the file.
 
@@
 For instance, with BOLE (\emph{Boronia ledifolia}), counts are made by flowers up through the finished flower stage, but then fruits are the unit counted for not all 4 fruits develop within each flower.
+This is the information presented in Tables \ref{tab:parts_Banksia_ericifolia}-Table \ref{tab:parts_Pultenaea_tuberculata}, above.
 
@@
 Table \ref{tab:sites_meta} gives a brief description of the data columns in the file.
+Tables \ref{tab:sites} displays the data in this file.
 
@@
 
-Defines the plant maps for each species, as shown in Figs. \ref{fig:map_Banksia ericifolia}-Table \ref{fig:map_Pultenaea tuberculata}. Also defines the list of reproductive parts for each species.
+Defines the plant maps and the list of reproductive parts for each specie, as shown in Figs.
+\ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata} and Tables \ref{tab:parts_Banksia_ericifolia}-Table \ref{tab:parts_Pultenaea_tuberculata}.
 

### 2017-05-30 Analaysis-RA.Rmd
work on ESA talk fixing Summaries to remove individuals without leaf turnover data before taking site means

@@
 ```{r}
-
-# pdf('ms/RA/Figure_1_stacked_lines.pdf', height=11.5, width=8) plot
+#pdf('ms/RA/Figure_1_stacked_lines.pdf', height=11.5, width=8) 
+plot
 par(mfrow = c(7,4), cex = 1, oma = c(5, 5, 1, 1), mar = c(0, 3, 2, 1))
@@
   # Todo: this should be calculated at individual level before taking means by species
-  data_sp <- filter(data, species == all_species[i])
-  data_sp_ind <- filter(data_ind, species == all_species[i])
+  data_sp <- filter(data, species == all_species[1])
+  data_sp_ind <- filter(data_ind, species == all_species[1])
   data_sp_no5 <- subset(data_sp,age!=5)

### 2017-05-30 R/Summaries.R

@@ -65,7 +65,7 @@ process_leaf_loss <- function(data_raw, leavesPerLength) {
     shoot_leaf_count = lvs_end + shoot_leaf_count_new) %>%
   select(species, age, individual, shoot_length_start, growth_shoot_length,
     shoot_leaf_count_new_and_shed_count, shoot_leaf_count_start, prop_leaf_loss,
-    shoot_leaf_count_new, shoot_leaf_count)
+    shoot_leaf_count_new, shoot_leaf_count,lvs_end,lvs_end_count,lvs_end_length,count_per_length)
 }
 
 # Calculate average wood density by species
@@ -202,9 +202,15 @@ combine_by_individual <- function(IndividualsList, Growth_all, ReproductiveCosts
       prop_leaf_replacement = divide_zero(all_leaf_and_repro_inv, gross_inv),
       prop_surplus = divide_zero(surplus_inv, all_leaf_and_repro_inv),
       RA_vs_all_leaf = divide_zero(repro_inv, all_leaf_and_repro_inv),
-      RA_seed = divide_zero(embryo_endo_inv, total_inv),
+      RA_seed = divide_zero(embryo_endo_inv, gross_inv),
       prop_stem = 1,
-      prop_leaf_replacement_vs_all_leaf = divide_zero(leaf_replacement, all_leaf_inv))
+      leaf_shed_prop_surplus = 1-(divide_zero(leaf_shed,all_leaf_and_repro_inv)),
+      repro_prop_surplus = divide_zero(repro_inv,all_leaf_and_repro_inv), 
+      leaf_replacement_prop_surplus = divide_zero(leaf_replacement,all_leaf_and_repro_inv), 
+      repro_and_leaf_growth_prop_surplus = divide_zero((growth_leaf_pos+repro_inv),all_leaf_and_repro_inv), 
+      seed_prop_surplus = divide_zero(embryo_endo_inv, all_leaf_and_repro_inv),
+      prop_leaf_replacement_vs_all_leaf = divide_zero(leaf_replacement, all_leaf_inv)
+      )
 
   # Where these ratios are infinite we are setting them to zero. It represents
   # cases where no successful seeds were produced
@@ -215,7 +221,14 @@ combine_by_individual <- function(IndividualsList, Growth_all, ReproductiveCosts
     i <- is.infinite(SummaryInd[[v]])
     SummaryInd[[v]][i] <- 0
   }
+  
+  for (v in c("leaf_shed_prop_surplus")) {
[…]

### 2017-05-30 scripts/ESA_talk.R

@@ -1,0 +1,490 @@
+
+win.metafile("ms/RA/maxRA_LMA_correlation.wmf", height=4, width=4)
+plot
+par(mfcol=c(1,1), cex=1, omi=c(.1,.7,.1,.1), mai=c(.8,.3,.1,0.2)) 
+i <- traits$RA_leaf_area_max
+plot(i~traits$LMA,col="blue",pch=16,cex=1.5,xlab="",yaxt="n",log="x")
+mtext("LMA",1,outer=FALSE,line=3)
+mtext("maximum RA",2,outer=FALSE,line=3)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(.4,.6,.8,1,1.2,1.4),cex.axis=.8,las=1)
+#mod <- lm(LMA~RA_leaf_area,traits)
+#extra.bottom.left(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
+dev.off()
+
+
+
+###################
+
+win.metafile("ms/RA/life_history_correlations.wmf", height=4, width=12)
+plot
+par(mfcol=c(1,3), cex=1, omi=c(.1,.7,.1,.1), mai=c(.8,.3,.1,0.2)) 
+i <- traits$RA_leaf_area_max
+
+plot(i~traits$lifespan,pch=16,cex=1.5,log="x",xlab="",yaxt="n")
+mtext("lifespan (years)",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
+# <- lm(log10(lifespan)~i,traits)
+#extra.bottom.left.logx(paste("r2=",round(glance(mod)[1],2),"; p-value:",round(glance(mod)[5],4)))
+mtext("maximum RA",2,outer=TRUE,line=1)
+
+plot(i~traits$maturity,pch=16,cex=1.5,log="x",xlab="",yaxt="n")
+mtext("age at maturity (years)",1,outer=FALSE,line=2)
+axis(2, at=c(.4,.6,.8,1,1.2,1.4), labels=c(0.4,0.6,0.8,1.0,1.2,1.4),cex.axis=.9,las=1)
+#mod <- lm(mature~log10(i),traits)
[…]

### 2017-06-28 scripts/Accessory_figs_20160905.Rmd
Start revising Accessory costs MS

@@
 legend("bottomleft",legend=c("seed count by reproductive costs","initiated ovules count by pollen-attraction costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
-extra.top.left("b",2,1)
+extra.top.left("b")
 
@@
 mtext(text="scaled to plant size",side=1,line=1.9,outer=FALSE,cex=0.8)
-extra.top.left("c",2,1)
+extra.top.left("c")
 dev.off()
@@
 legend("bottomleft",legend=c("become seeds","are aborted before provisioning"),title="into ovules that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
-extra.top.left("d",2,1)
+extra.top.left("d")
 
@@
 legend("bottomleft",legend=c("become seeds","are aborted"),title="into zygotes that:",col=c("black","black"),pch=c(16,21),bty="n",cex=0.5,xjust=0)
-extra.top.left("e",2,1)
+extra.top.left("e")
 
@@
 legend("bottomleft",legend=c("pollen-attraction costs","provisioning costs"),col=c("black","black"),pch=c(16,21),bty="n",cex=0.5)
-extra.top.left("f",2,1)
+extra.top.left("f")
 
@@
 legend("bottomleft",legend=c("seed count by reproductive costs","mature ovules count by","pollen-attraction costs"),col=c(venetian_red,cerulean,"white"),pch=c(16,16,16),bty="n",cex=0.7)
-extra.top.left.logxy("a",2,1)
+extra.top.left.logxy("a")
 
@@
 line_function_log_xy(SummarySpp[["mean"]]$scaled_pollen_attract_costs,mod_choosy2,1,col=cerulean)
-extra.top.left.logxy("b",2,1)
+extra.top.left.logxy("b")
 
@@
 #arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded-SummarySpp[["se"]]$prop_prepollen_discarded,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_prepollen_discarded+SummarySpp[["se"]]$prop_prepollen_discarded,code=3,angle=90, length=0.1,col=venetian_red)
-extra.top.left.logx("c",2,1)
+extra.top.left.logx("c")
 axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
@@
 points(prop_postpollen_discarded~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
-extra.top.left.logx("d",2,1)
+extra.top.left.logx("d")
 axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
@@
 #arrows(SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success-SummarySpp[["se"]]$prop_pollen_attract_vs_success,SummarySpp[["mean"]]$embryo_endo_costs,SummarySpp[["mean"]]$prop_pollen_attract_vs_success+SummarySpp[["se"]]$prop_pollen_attract_vs_success,code=3,angle=90, length=0.1,col=cerulean)
-extra.top.left.logx("e",2,1)
+extra.top.left.logx("e")
 axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
@@
 points(provisioning_costs~embryo_endo_costs,SummarySpp[["mean"]],pch=16,col=venetian_red)
-extra.top.left.logxy("f",2,1)
+extra.top.left.logxy("f")
 axis(2, at=c(0.01,1,100,10000), labels=c(0.01,1,100,10000),cex.axis=0.8,las=2)

### 2017-06-28 R/figures.R

@@ -76,41 +76,16 @@ labels.spp.genus <- function(x = NULL) {
 }
 
 col.age <- function(x = NULL) {
-  
+
   ret <- c("red", "orchid1", "gold1", "darkolivegreen3", "cyan2", "dodgerblue3",
-           "purple")
+    "purple")
   names(ret) <- c("0.1", "1.4", "2.4", "5", "7", "9", "32")
-  
+
   if (!is.null(x)) {
     ret <- ret[as.character(x)]
   }
   ret
 }
-
-col.age2 <- function(x = NULL) {
-  
-  ret <- c("darkslategray1", "darkslategray2", "darkslategray3", "darkslategray4", "darkslategray", "gray33",
-           "black")
-  names(ret) <- c("0.1", "1.4", "2.4", "5", "7", "9", "32")
-  
-  if (!is.null(x)) {
-    ret <- ret[as.character(x)]
-  }
-  ret
-}
-
-col.age.leaf <- function(x = NULL) {
-  
-  ret <- c("darkseagreen1", "darkseagreen1", "darkseagreen2", "darkseagreen3", "darkseagreen4", "gray33",
-           "black")
-  names(ret) <- c("0.1", "1.4", "2.4", "5", "7", "9", "32")
-  
-  if (!is.null(x)) {
-    ret <- ret[as.character(x)]
-  }
-  ret
-}
-
 
 labels.age <- function(x = NULL) {
   names(col.age(x))
@@ -157,6 +132,14 @@ format_p <- function(p, digits = 3) {
   x
 }
 
+format_p2 <- function(p, digits = 3) {
+  x <- as.character(round(p, digits = digits))
+  pc <- 10^-digits
+  x[p < pc] <- paste("<", pc)
+  x[p >= pc] <- paste("=", x[p >= pc])
+  x
+}
+
 format_r2 <- function(x) {
   format(round(x, 2), nsmall = 2)
 }
@@ -176,6 +159,36 @@ print_xtable <- function(data, file) {
 
 # plotting and stats creating lists of information for plotting symbols,
 # colors, labels
+
+
+add_axis_log10 <- function(side=1, labels=TRUE, las=1, ...){
+  at <- -20:20
+  if(labels)
+    lab <- do.call(expression, lapply(at, function(i) bquote(10^.(i))))
+  else
+    lab=""
+  axis(side, at = 10^at, labels = lab, las=las,...)
+}
+
[…]

### 2017-09-08 ms/RA/Wenk-RA-SI.Rnw
Update figures and MS for analysis on RA

--- 2017-05-22 ms/Accessory/Wenk-Accessory-SI.Rnw
@@
 
+\usepackage{float}
 \usepackage{suppmat}
@@
 
-\author{E. H. Wenk\textsuperscript{1,\textasteriskcentered}, K. Abramowicz\textsuperscript{2}, M. Westoby\textsuperscript{1}, D.S. Falster\textsuperscript{1} }
-\affiliation{\textsuperscript{1} Biological Sciences, Macquarie University NSW 2109, Australia \\
-\textsuperscript{2} Department of Mathematics and Mathematical Statistics, Ume{\aa} University, 90187 Ume{\aa}, Sweden \\
-\textsuperscript{\textasteriskcentered} Correspondence author. E-mail: \email{ehwenk@gmail.com}
-}
+\author[a,*]{E.H. Wenk}
+\author[b]{K. Abramowicz}
+\author[a]{M. Westoby}
+\author[c]{D.S. Falster}
 
-\usepackage[authoryear,sectionbib,sort]{natbib}
-\bibliographystyle{amnat2}
+\affil[a]{Department of Biological Sciences, Macquarie University NSW 2109, Australia}
+\affil[b]{Department of Mathematics and Mathematical Statistics, Ume{\aa} University, 90187 Ume{\aa}, Sweden}
+\affil[c]{Evolution and Ecology Research Centre, University of New South Wales, Australia}
+
+%\textsuperscript{\textasteriskcentered} Correspondence author. E-mail: \email{ehwenk@gmail.com}
 
@@
 
-flowering_parts <- read.csv("Sup_Table_flowering_parts.csv", stringsAsFactors=FALSE, check.names=FALSE)
+flowering_parts <- read.csv("../Accessory/Sup_Table_flowering_parts.csv", stringsAsFactors=FALSE, check.names=FALSE)
 flowering_parts$Method <- clean_headers(flowering_parts$Method)
@@
 \maketitle
-
-\begingroup
-\let\cleardoublepage\relax
-\let\clearpage\relax
-\tableofcontents
-\endgroup
 

### 2017-12-06 ms/Accessory/Wenk-Accessory-SI.Rnw
Changes to Accessory paper
Updating figures for RA and adding SuppMatt
- added lat & lon to site file by converting from UTM coordinates (closes #31)
- added maps of filed sites
- reformatted suppmat style (it broke)

@@
 
-print_table_species <- function(species, data) {
-  data <- data[data$Species == species, -c(1)]
-  print(xtable(data,
-            hline.after=c(1),
-            align='p{0.1cm}p{4.5cm}p{6cm}p{2cm}p{1cm}p{1cm}',
-            label=sprintf("tab:parts_%s", gsub(" ", "_", species)),
-            caption=sprintf("Table of parts for \\emph{%s}.", species)),
-      sanitize.text.function=I,
-      , table.placement = "h"
-      , caption.placement = "top"
-      , include.rownames = FALSE
-      , include.colnames = TRUE
-      , size = "small"
-      , tabular.environment = 'longtable'
-      , floating = FALSE)
-}
-
-print_table_metadata <- function(path, align = NULL) {
-
-  data <-  read.csv(path, stringsAsFactors=FALSE, check.names=FALSE)
-  file <- gsub("_", "\\_", basename(path), fixed = TRUE)
-
-  label <- sprintf("tab:%s_meta", strsplit(basename(path), "_")[[1]][1])
-
-  print(xtable(data,
-            align=align,
-            hline.after=c(1),
-            label= label,
-            caption=
-              sprintf("Description of variables within the file \\texttt{data/%s}. These definitions can also be found within the file \\texttt{data/%s}.",
-              gsub("\\_meta", "", file, fixed = TRUE), file)),
-      , table.placement = "h"
-      , caption.placement = "top"
-      , include.rownames = FALSE
-      , include.colnames = TRUE
-      , size = "small"
-      , tabular.environment = 'longtable'
-      , floating = FALSE)
-}
 @
@@
 
-\begin{table}[H]
+\begin{table}[h]
 \centering
@@
 @
-\begin{table}[H]
+\begin{table}[h]
 \centering
@@
 
-We collected data for 14 species (Table \ref{tab:species}) at 7 sites (Tables \ref{tab:sites}). Individuals were selected as described in the main text.
+We collected data for 14 species (Table \ref{tab:species}) at 7 sites (Tables \ref{tab:sites}, Fig. \ref{fig:map}). Individuals were selected as described in the main text.
 
 <<echo=FALSE,results='asis'>>=
+
 data <-  read.csv("../../data/species.csv", stringsAsFactors=FALSE, check.names=FALSE)
 data$Common_name <- firstup(data$Common_name)
+i <- data$Previous_names != ""
+data$Species_name[i] <- sprintf("%s (previously %s)", data$Species_name[i],data$Previous_names[i])
+data <- dplyr::select(data,-Previous_names)
+
 names(data) <-  clean_headers(names(data))
@@
 print(xtable(data,
-            align= 'p{1cm}p{5cm}p{3cm}p{3cm}p{2cm}p{3cm}',
+          align= 'p{1cm}p{5cm}p{3cm}p{5cm}p{2cm}',
           hline.after=c(1),
@@
 print(xtable(data,
-            align= 'p{0.1cm}p{2cm}p{1cm}p{1cm}p{1cm}p{1.4cm}p{1.4cm}p{7cm}',
+          align= 'p{0.1cm}p{2cm}p{1cm}p{1cm}p{1cm}p{1.2cm}p{1.2cm}p{1.2cm}p{1.2cm}p{5cm}',
           hline.after=c(1),
+          digits=c(0,0,0,2,0,0,0,4,4,0),
           label= "tab:sites",
@@
 @
+
+\begin{figure}[h]
+\centering
+\includegraphics[height=10cm]{../map.pdf}
+\caption{Map of study locations.}
+\label{fig:map}
+\end{figure}
 

### 2017-12-06 ms/RA/Wenk-RA-SI.Rnw
Updating figures for RA and adding SuppMatt
- added lat & lon to site file by converting from UTM coordinates (closes #31)
- added maps of filed sites
- reformatted suppmat style (it broke)

--- 2017-05-22 ms/Accessory/Wenk-Accessory-SI.Rnw
@@
 
-\title{Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species}
-\runninghead{S\lowercase{hifts in allocation among reproductive tissues}}
+\title{Investment in reproduction by 14 iteroparous perennials and its coordination with other life-history and functional traits}
+\runninghead{I\lowercase{nvestment in reproduction}}
 
-\author{E. H. Wenk\textsuperscript{1,\textasteriskcentered}, K. Abramowicz\textsuperscript{2}, M. Westoby\textsuperscript{1}, D.S. Falster\textsuperscript{1} }
-\affiliation{\textsuperscript{1} Biological Sciences, Macquarie University NSW 2109, Australia \\
+\author{E. H. Wenk\textsuperscript{1,\textasteriskcentered}, K. Abramowicz\textsuperscript{2}, M. Westoby\textsuperscript{1}, D.S. Falster\textsuperscript{3} }
+\affiliation{
+\textsuperscript{1} Biological Sciences, Macquarie University NSW 2109, Australia \\
 \textsuperscript{2} Department of Mathematics and Mathematical Statistics, Ume{\aa} University, 90187 Ume{\aa}, Sweden \\
+\textsuperscript{3} Evolution and Ecology Research Centre, University of New South Wales, Sydney NSW 2052, Australia \\
 \textsuperscript{\textasteriskcentered} Correspondence author. E-mail: \email{ehwenk@gmail.com}
 }
-
-\usepackage[authoryear,sectionbib,sort]{natbib}
-\bibliographystyle{amnat2}
 
@@
 
-<<echo=FALSE, results='asis', warning=FALSE>>=
-
-make_table_species_values_for_allocation_seedsize_table <- function(file) {
-  data <- select(file,species,scaled_seed_count,scaled_ovule_count,
-                 scaled_pollen_attract_costs,choosiness,prop_prepollen_success, prop_prepollen_discarded,
-                 prop_postpollen_success,prop_postpollen_discarded, prop_pollen_attract_vs_success,prop_provisioning_vs_success)
-  data$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  data
-}
-
-TableS15 <- make_table_species_values_for_allocation_seedsize_table(SummarySpp[["mean"]])
-
-names(TableS15) <- c("species","seed count","ovule count","pollen-attraction costs","choosi- ness","success","discarded","success","discarded","pollen-attraction","provi- sioning")
-
-for (i in 2:11) {
-TableS15[,i] <- format(TableS15[,i],digits=3, nsmall=0)
-}
-
-TableS15$species  <- paste("\\textit{",unique(TableS15$species),"}", sep="")
-@
-
-\begin{table}[h]
+\begin{figure}[h]
 \centering
-\caption{Species values for data plotted in Figure 2: shifts in reproductive tissue allocation with seed size.
-Counts and costs are per unit leaf area of the plant.
-The bottom line indicates the corresponding figure of the main text where the data are presented.
-Data for reproductive costs (Figure 2, panel a), Seed-size, pollen-attraction costs, and provisioning costs (Figure 2, panel f) are presented in Table 1 in the main text and are not included here.}
-\label{tab:species}
-{\footnotesize
-\begin{tabular}{p{3cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1.5cm}p{1cm}}
-\hline
-& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c|}{Proportion}& \multicolumn{2}{c}{Proportion} \\
-& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{pollen-attraction} & \multicolumn{2}{c|}{provisioning}& \multicolumn{2}{c}{success} \\
-& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{investment to} & \multicolumn{2}{c|}{investment to}& \multicolumn{2}{c}{investment to} \\
-<<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS15)
-        , sanitize.text.function=I
-        , include.rownames = FALSE
-        , include.colnames = TRUE,
-        only.contents=TRUE)
-cat("Figure reference & \\multicolumn{2}{c|}{Fig.
-2, panel a} & \\multicolumn{2}{c|}{Fig.
-2, panel b} & \\multicolumn{2}{c|}{Fig.
-2, panel c} & \\multicolumn{2}{c|}{Fig.
-2, panel d}  & \\multicolumn{2}{c}{Fig.
-2, panel e}\\\\
-\\hline")
-@
-\end{tabular}
-}
-\end{table}
-
-\clearpage
-<<echo=FALSE, results='asis', warning=FALSE>>=
-make_table_RA_shifts_with_age <- function(SummaryInd) {
-  xvar <- "repro_inv"
-  yvar <- "accessory_costs"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_RE <- dplyr::select(fit$groupsummary,group,n,r2,pval)
-
-  xvar <- "total_weight_0"
-  yvar <- "accessory_costs"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_size <- dplyr::select(fit$groupsummary,group,n,r2,pval)
-
-  xvar <- "age"
-  yvar <- "accessory_costs"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_age <- dplyr::select(fit$groupsummary,group,n,r2,pval)
-
-  TableS16 <- merge(accessory_vs_RE,accessory_vs_size,by="group")
-  TableS16 <- merge(TableS16,accessory_vs_age,by="group")
-
-  names(TableS16) <- c("Species","n","r$^2$","p","n","r$^2$","p","n","r$^2$","p")
-
-  Species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  TableS16$Species <-  paste("\\textit{",Species,"}", sep="")
-
-  TableS16
-}
-
-TableS16 <- make_table_RA_shifts_with_age(SummaryInd)
-
-for(i in c(2,3,5,6,8,9)){
-  TableS16[,i] <- format_r2(TableS16[,i])
-}
-for(i in c(4,7,10)){
-  TableS16[,i] <- format_p(TableS16[,i])
-}
-@
-
-\begin{table}[H]
-\centering
-\caption{Testing for shifts in accessory costs with in age, plant size, or reproductive effort.
-Shifts in accessory costs with these variables is suggested as one possible explanation of increasing reproductive investment in larger, older plants, but such a trend did not exist in these data.}
-\label{tab:access_vs_age}
-\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.25cm}|x{.75cm}x{1cm}p{1.25cm}|x{.75cm}x{1cm}p{1.25cm}}
-\hline
-& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c|}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
-& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c|}{vs. plant mass}& \multicolumn{3}{c}{vs. age} \\
-<<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS16)
-        , sanitize.text.function=I
-        , include.rownames = FALSE
-        , include.colnames = TRUE,
-        only.contents=TRUE)
-@
-\end{tabular}
-\end{table}
-
+\includegraphics[width=\linewidth]{figures/height.pdf}
+\caption{Plots of plant height against estimated site age for the 14 study species.
+Species are sorted from top to bottom based on their Age at maturation (Table 1).
+The points indicate data points for the individual plants assessed, with colours indicating site age.
+Fitted lines are generalised additive models, with r$^2$ value indicating the amount of variance explained.}
+\label{fig:height}
+\end{figure}
 \clearpage
 
-<<echo=FALSE, warning=FALSE>>=
-
-make_table_propagule_invest_vs_all_repropro_inv <- function(SummaryInd) {
-  mod_propagule_inv_all <- sma(repro_inv~propagule_inv,data=SummaryInd,log="xy",method="SMA")
-  mod_flower_inv_all <- sma(repro_inv~flower_inv,data=SummaryInd,log="xy",method="SMA")
-
-  yvar <- "repro_inv"
-  xvar <- "propagule_inv"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=mod_propagule_inv_all$groupsummary["Slope"][[1]],elev.test=mod_propagule_inv_all$coef[[1]][1,1])
-  results <- fit$groupsummary
-  acc_slopes <- dplyr::select(results,group,n,r2,pval)
-  names(acc_slopes) <- c("Species","n_propagule","r2_propagule","p_propagule")
-
-  yvar <- "repro_inv"
-  xvar <- "flower_inv"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
-
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
-  results <- fit$groupsummary
-  acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
-  names(acc_slopes2) <- c("Species","n_flower","r2_flower","p_flower")
-  acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="Species")
-  names(acc_slopes) <- c("Species","n","r$^2$","p", "n","r$^2$","p")
-  Species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  acc_slopes$Species <-  paste("\\textit{",Species,"}", sep="")
-
-  acc_slopes
-}
-
-TableS17 <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)
-
-for(i in c(2,3,5,6)){
-  TableS17[,i] <- format_r2(TableS17[,i])
-}
-for(i in c(4,7)){
-  TableS17[,i] <- format_p(TableS17[,i])
-}
-@
-
-\begin{table}[H]
+\begin{figure}[h]
 \centering
-\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight $\times$ bud count'.
-Due to the high proportion of aborted flowers, flower investment was a better proxy of reproductive investment than was propagule investment.
-This was true both across species (Figure 3, Table 3 in the main text) and within species, as is shown here.}
-\label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
-\hline
-& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
-& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
-<<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS17)
-        , sanitize.text.function=I
-        , include.rownames = FALSE
-        , include.colnames = TRUE,
-        only.contents=TRUE)
-@
-\end{tabular}
-\end{table}
-
+\includegraphics[height=20cm]{figures/RA_demo_all.pdf}
+\caption{As in Fig. 3 but showing data for all 14 study species.}
+\label{fig:RA_all}
+\end{figure}
 \clearpage
 
-<<echo=FALSE, results='asis', warning=FALSE>>=
-make_table_Table2_using_propagule <- function() {
-slopes <- sma(repro_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
-
-slopes <- sma(accessory_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(success_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(pollen_attract_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(provisioning_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(prepollen_discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(postpollen_aborted_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-acc_by_species$variable = c("total reproductive","total accessory","seed","pollen attraction","provisioning", "failed tissue","failed pre-pollination","failed provisioning")
-
-acc_by_species$Slope <- format_r2(acc_by_species$Slope)
-acc_by_species$Slope_lowCI <- format_r2(acc_by_species$Slope_lowCI)
-acc_by_species$Slope_highCI <- format_r2(acc_by_species$Slope_highCI)
-
-acc_by_species$slope2 <- paste(acc_by_species$Slope," (",acc_by_species$Slope_lowCI," - ",acc_by_species$Slope_highCI,")",sep="")
-
-acc_by_species$r2 <- format_r2(acc_by_species$r2)
-acc_by_species$pval <- format_p(acc_by_species$pval)
-acc_by_species$Slope_test_p <- format_p(acc_by_species$Slope_test_p)
-acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
-}
-TableS19 <- make_table_Table2_using_propagule()
-names(TableS19) <- c("Costs","r$^2$","Slope (95$\\%$ CI)","p (slope test)")
-TableS19$Costs <- firstup(TableS19$Costs)
-
-@
-\begin{table}[H]
+\begin{figure}[h]
 \centering
-\caption{Scaling of reproductive tissue costs with total propagule size.
-In this manuscript all "seed size" calculations use embryo and endosperm size, not propagule size.
-Most previous research has used propagule size as a measure of "seed size" and noted isometric relationships between various tissue costs and "seed size".
-Using embryo and endosperm size, these relationship did not exist for this data set, but are present if "seed size" includes the entire propagule.}
-\label{tab:repro_tissues_vs_prop_size}
-\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{3cm}}
-\hline
-<<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS19)
-         , sanitize.text.function=I
-        , include.rownames = FALSE
-        , include.colnames = TRUE,
-        only.contents=TRUE)
-@
-\end{tabular}
-\end{table}
-
+\includegraphics[width=0.75\linewidth]{figures/leaf_loss.pdf}
+\caption{Relationship between a species leaf mass per area and it's rate of annual leaf turnover.}
+\label{fig:leaf_loss}
+\end{figure}
 \clearpage
@@
 
-\subsection{Methods for calculating investment in reproductive tissues}
+\subsection{Species and sites}
 
-We collected data for 14 species (Table \ref{tab:species}) at 7 sites (Tables \ref{tab:sites}). Individuals were selected as described in the main text.
+We collected data for 14 species (Table \ref{tab:species}) at 7 sites (Tables \ref{tab:sites}, Fig. \ref{fig:map}). Individuals were selected as described in the main text.
 
 <<echo=FALSE,results='asis'>>=
+
 data <-  read.csv("../../data/species.csv", stringsAsFactors=FALSE, check.names=FALSE)
 data$Common_name <- firstup(data$Common_name)
+i <- data$Previous_names != ""
+data$Species_name[i] <- sprintf("%s (previously %s)", data$Species_name[i],data$Previous_names[i])
+data <- dplyr::select(data,-Previous_names)
+
 names(data) <-  clean_headers(names(data))
@@
 @
+
+\begin{figure}[h]
+\centering
+\includegraphics[height=10cm]{../map.pdf}
+\caption{Map of study locations.}
+\label{fig:map}
+\end{figure}
+
+\clearpage
+\subsection{Methods for calculating investment in reproductive tissues and growth}
 
@@
 
+\subsubsection{Estimating leaf and stem growth}
+
+XXXXX
+
+\clearpage
+
 \subsection{Details on calculations by species}
@@
 
+Also shown below  in Figs.
+\ref{fig:growth_Banksia_ericifolia}, \ref{fig:growth_Boronia_ledifolia},...., \ref{fig:growth_Pultenaea_tuberculata} are the relationships used to estimate growth in leaf and stem mass for each species.
+
 \begin{figure}[h]
@@
 
+Fig. \ref{fig:growth_Banksia_ericifolia} shows the relationships used to estimate growth in leaf and stem mass for this species.
+
 \begin{figure}[h]
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/BAER.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Banksia ericifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Banksia_ericifolia}
+\end{figure}
+
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Boronia_ledifolia}.
+
+Fig. \ref{fig:growth_Boronia_ledifolia} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/BOLE.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Boronia ledifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Boronia_ledifolia}
+\end{figure}
+
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Conospermum_ericifolium}.
+
+Fig. \ref{fig:growth_Conospermum_ericifolium} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/COER.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Conospermum ericifolium}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Conospermum_ericifolium}
+\end{figure}
+
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Epacris_microphylla}.
+
+Fig. \ref{fig:growth_Epacris_microphylla} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/EPMI.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Epacris microphylla}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Epacris_microphylla}
+\end{figure}
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Grevillea_buxifolia}.
+
+Fig. \ref{fig:growth_Grevillea_buxifolia} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/GRBU.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Grevillea buxifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Grevillea_buxifolia}
+\end{figure}
+
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Grevillea_speciosa}.
+
+Fig. \ref{fig:growth_Grevillea_speciosa} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/GRSP.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Grevillea speciosa}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Grevillea_speciosa}
+\end{figure}
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Hakea_teretifolia}.
+
+Fig. \ref{fig:growth_Hakea_teretifolia} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/HATE.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Hakea teretifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Hakea_teretifolia}
+\end{figure}
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Hemigenia_purpurea}.
+
+Fig. \ref{fig:growth_Hemigenia_purpurea} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/HEPU.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Hemigenia purpurea}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Hemigenia_purpurea}
+\end{figure}
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Leucopogon_esquamatus}.
+
+Fig. \ref{fig:growth_Leucopogon_esquamatus} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/LEES.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Leucopogon esquamatus}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Leucopogon_esquamatus}
+\end{figure}
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Persoonia_lanceolata}.
+
+Fig. \ref{fig:growth_Persoonia_lanceolata} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/PELA.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Persoonia lanceolata}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Persoonia_lanceolata}
+\end{figure}
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Petrophile_pulchella}.
+
+Fig. \ref{fig:growth_Petrophile_pulchella} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/PEPU.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Petrophile pulchella}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Petrophile_pulchella}
+\end{figure}
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Phyllota_phylicoides}.
+
+Fig. \ref{fig:growth_Phyllota_phylicoides} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/PHPH.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Phyllota phylicoides}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Phyllota_phylicoides}
+\end{figure}
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Pimelea_linifolia}.
+
+Fig. \ref{fig:growth_Pimelea_linifolia} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/PILI.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Pimelea linifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Pimelea_linifolia}
+\end{figure}
 \clearpage
@@
 Further details on each part type are given in Table \ref{tab:parts_Pultenaea_tuberculata}.
+
+Fig. \ref{fig:growth_Pultenaea_tuberculata} shows the relationships used to estimate growth in leaf and stem mass for this species.
 
@@
 
+\begin{figure}[h]
+\centering
+\includegraphics[width=0.6\linewidth]{../growth_plots/PUTU.pdf}
+\caption{Estimating growth in leaf and stem mass for \emph{Pultenaea tuberculata}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
+estimated growth trajectory for each individual across an entire year.}
+\label{fig:growth_Pultenaea_tuberculata}
+\end{figure}
 \clearpage
@@
 
-Defines functions that estimate growth rates of the plant (not used in this analysis).
+Defines functions that estimate growth rates of the plant.
 

### 2017-12-06 R/Growth.R

@@ -147,15 +147,21 @@ growth_calculations <- function(thisSpecies, HarvestData, IndividualsList) {
     data.frame()
   }
 
-  path <- "output/growth_plots"
+  path <- "ms/growth_plots"
   dir.create(path, FALSE, TRUE)
-  pdf(sprintf("%s/%s.pdf", path, thisSpecies), width = 10, height = 3)
+  pdf(sprintf("%s/%s.pdf", path, thisSpecies), width = 4, height = 8)
   on.exit(dev.off())
 
   suppressWarnings({
-    par(mfrow = c(1, 4), cex = 1, oma = c(1, 1, 2, 1), mar = c(4, 4, 0, 1))
+    par(mfrow = c(2, 1), cex = 1, oma = c(3, 1, 2, 1), mar = c(4, 4, 0, 1))
     plot(stem_weight ~ diameter, data = HarvestData_basal_2, pch = 16, log = "xy",
-      col = col.age(age))
+      col = col.age(age), axes = FALSE, ann=FALSE)
+    mtext("Stem diameter (mm)", side = 1, line = 2)
+    mtext("Stem weight (g)", side = 2, line = 3)
+    box()
+    axis(1)
+    add_axis_log10(2)
+
     dia.r <- seq_log_range(c(0.05, 50), 50)
     points(dia.r, y_hat(fit.s, dia.r), type = "l")
     out %>% group_by(individual) %>% do(add_line(., "diameter", "stem_weight_est"))
@@ -163,27 +169,18 @@ growth_calculations <- function(thisSpecies, HarvestData, IndividualsList) {
       "_"), "", individual), cex = 0.2)
 
     plot(leaf_weight ~ age, data = HarvestData_basal_2, pch = 16, log = "xy",
-      col = col.age(age), xlim = c(0.05,32))
+      col = col.age(age), xlim = c(0.05,32), axes = FALSE, ann=FALSE)
     age.r <- seq_log_range(c(0.08, 35), 50)
     points(age.r, y_hat(fit.l, age.r), type = "l")
     out %>% group_by(individual) %>% do(add_line(., "age", "leaf_weight_est"))
-    mtext(thisSpecies, line = 1, outer = TRUE)
     text(leaf_weight ~ age, data = HarvestData_basal_2, labels = gsub(paste0(thisSpecies,
       "_"), "", individual), cex = 0.2)
 
-
[…]

### 2017-12-10 ms/RA/Wenk-RA-SI.Rnw
more details on leaf-stem growth for Supp Matt

@@
 \item For a each part in turn, we try to identify the most obvious predecessor, being the one with minimal amount of progression needed to satisfy successive censuses.
-The predecessor is removed from the list of possible predecessors and the process sis repeated until all parts have predecessors.
+The predecessor is removed from the list of possible predecessors and the process is repeated until all parts have predecessors.
 \item After finding a predecessor, the investment needed to progress  is calculated.
@@
 
-As an example, if, in census $t$, a large bud exists, it is assumed that it has developped from a medium sized bud (the previous stage) in census $t$-1.
-If in census $t$-1 no medium buds exists, the large bud is assumed to have developped from a small bud (two stages back).
+As an example, if, in census $t$, a large bud exists, it is assumed that it has developed from a medium sized bud (the previous stage) in census $t$-1.
+If in census $t$-1 no medium buds exists, the large bud is assumed to have developed from a small bud (two stages back).
 This process continues back along the plant map developmental trajectory until a plausible predecessor is located in the previous census period.
@@
 
-XXXXX
+We estimated the net amount of leaf and stem growth across the study period from point estimates of the weight of each tissue at the beginning and end of the study.
+Destructive harvests were taken at the end of the study and so leaf and stem weights at that point were calculated exactly (within measurement error).
+To estimate leaf growth across the study period we fitted a generalised additive model (GAM), a semi-parametric modelling approach that makes no assumption about the shape of the relationships, with site age as a predictor.
+We allowed four degrees of freedom, which resulted in biologically realistic relationships.
+Both X and Y variables were log transformed.
+These relationships were fitted across all individuals within each species, i.e.
+from multiple site ages.
+To maintain individual-level variation around the fitted line, we used the fitted lines to estimate the ratio of leaf mass at the end and beginning of the study, and then applied this ratio to the observed endpoint, i.e.
+\begin{equation}\label{eq:biomass}
+y_i(t_1) = y_i(t_2) \frac{\hat{y}(t_1)}{\hat{y}(t_2)}
+\end{equation}
+where $y_i(t)$ is true biomass of individual $i$ at time $t$ and $\hat{y}(t)$ is the estimated biomass of an average individual in the species at time $t$.
+
+A similar technique was used estimate stem growth, but using stem diameter instead of age as the predictor and using a linear regression instead of a GAM.
+
+Plots of the fitted relationships for both leaf mass and stem mass for each species are included below (Figs. \ref{fig:growth_Banksia_ericifolia}, \ref{fig:growth_Pultenaea_tuberculata}).
 
@@
 Below, for each species we provide a graphic illustration of the pathway used (Figs.
-\ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}), and tables detailing specific about each part (Tables \ref{tab:parts_Banksia_ericifolia}-Table \ref{tab:parts_Pultenaea_tuberculata}).
+\ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}), and tables detailing specific about each part (Tables \ref{tab:parts_Banksia_ericifolia}-\ref{tab:parts_Pultenaea_tuberculata}).
 Figure \ref{fig:map_key} provides a key on the colouring in Figs.
@@
 
-Also shown below  in Figs.
-\ref{fig:growth_Banksia_ericifolia}, \ref{fig:growth_Boronia_ledifolia},...., \ref{fig:growth_Pultenaea_tuberculata} are the relationships used to estimate growth in leaf and stem mass for each species.
+Also shown below are the relationships used to estimate growth in leaf and stem mass for each species (Figs. \ref{fig:growth_Banksia_ericifolia}-\ref{fig:growth_Pultenaea_tuberculata}).
 
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Banksia ericifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Banksia_ericifolia}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Boronia ledifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Boronia_ledifolia}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Conospermum ericifolium}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Conospermum_ericifolium}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Epacris microphylla}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Epacris_microphylla}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Grevillea buxifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Grevillea_buxifolia}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Grevillea speciosa}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Grevillea_speciosa}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Hakea teretifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Hakea_teretifolia}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Hemigenia purpurea}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Hemigenia_purpurea}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Leucopogon esquamatus}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Leucopogon_esquamatus}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Persoonia lanceolata}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Persoonia_lanceolata}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Petrophile pulchella}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Petrophile_pulchella}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Phyllota phylicoides}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Phyllota_phylicoides}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Pimelea linifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Pimelea_linifolia}
@@
 \caption{Estimating growth in leaf and stem mass for \emph{Pultenaea tuberculata}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
-estimated growth trajectory for each individual across an entire year.}
+estimated growth trajectory for each individual across an entire year, calculated from eq. \ref{eq:biomass}.}
 \label{fig:growth_Pultenaea_tuberculata}

### 2017-12-11 ms/Accessory/Wenk-Accessory-SI.Rnw
Minor edits to SuppMatt

@@
 
-data <-  read.csv("../../data/sites.csv", stringsAsFactors=FALSE, check.names=FALSE)
+data <-  read.csv("../../data/sites.csv", stringsAsFactors=FALSE, check.names=FALSE) %>% 
+  filter(site != "Bobbin2010")
+
 data <- data[order(data$age_at_harvest),]
@@
 For some individuals, actual reproductive parts were collected.
-This includes any reproductive parts of the plants at the time of harvest, including both current reproductive tissues and previously mature woody fruits still attached to the branches.
+This includes any reproductive parts of the plants at the time of harvest.
 In addition, some seeds were collected once mature, but before they were dispersed.
@@
 
-Our goal was to estimate the amount of mass each plant invests in different tissues within a given time period from field census data recording the numbers of each part type at successive census dates for a given plant.
+Our goal was to estimate the amount of mass each plant invests in different tissues within each census period from field data recording the numbers of each part type at successive census dates for a given plant.
 To achieve this we apply an accounting algorithm to estimate the number of units that have progressed from one category to another in the interval between censuses.

### 2017-12-11 ms/RA/Wenk-RA-SI.Rnw
Minor edits to SuppMatt

@@
 
-\title{Investment in reproduction by 14 iteroparous perennials and its coordination with other life-history and functional traits}
+\title{Investment in reproduction for 14 iteroparous perennials is large and associated with other life-history and functional traits}
 \runninghead{I\lowercase{nvestment in reproduction}}
@@
 \includegraphics[width=0.75\linewidth]{figures/leaf_loss.pdf}
-\caption{Relationship between a species leaf mass per area and it's rate of annual leaf turnover.}
+\caption{Relationship between a species' leaf mass per area and annual rate of leaf turnover.}
 \label{fig:leaf_loss}
@@
 
-data <-  read.csv("../../data/sites.csv", stringsAsFactors=FALSE, check.names=FALSE)
+data <-  read.csv("../../data/sites.csv", stringsAsFactors=FALSE, check.names=FALSE) %>% 
+  filter(site != "Bobbin2010")
 data <- data[order(data$age_at_harvest),]
@@
 Predecessors are those parts that lie at the same or younger age in the plant maps.
-\item For a each part in turn, we try to identify the most obvious predecessor, being the one with minimal amount of progression needed to satisfy successive censuses.
+\item For a each part in turn, we try to identify the most obvious predecessor, as the one with minimal amount of progression needed to satisfy successive censuses.
 The predecessor is removed from the list of possible predecessors and the process is repeated until all parts have predecessors.

### 2017-12-11 R/ms-SuppMatt.R

@@ -48,11 +48,12 @@ figure_site_map <- function(file) {
   basemap <- get_map('Kuringai National Park', zoom = 12, maptype = "hybrid")
 
   # Load site data 
-  data <-  read.csv(file, stringsAsFactors=FALSE, check.names=FALSE)
+  data <-  read.csv(file, stringsAsFactors=FALSE, check.names=FALSE) %>% 
+    filter(site != "Bobbin2010")
 
   ## Add nudges to data
-  nudge_x <- c(-0.002, 0.03, -0.002, -0.002, 0.035, 0.035, -0.002)
-  nudge_y <- c(0.002, 0, -0.002, 0.001, -0.003, 0, 0.003)
+  nudge_x <- c(-0.002, 0.03, -0.002, -0.002, 0.035, -0.002)
+  nudge_y <- c(0.002, 0, -0.002, 0.001, -0.003, 0.003)
 
 
   ggmap(basemap) + 

### 2018-02-05 ms/RA/Wenk-RA-SI.Rnw
Small fixes to supplementary materials. Finished proofreading now.

@@
 While all species developed reproductive tissues from buds to seeds, species showed different developmental pathways due to the precise reproductive tissues used.
-We therefore created a developmental flowchart for each species, as shown below in following sections in Figs.
+We therefore created a developmental flowchart for each species, as shown below in Figs.
 \ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}).
@@
 Predecessors are those parts that lie at the same or younger age in the plant maps.
-\item For a each part in turn, we try to identify the most obvious predecessor, as the one with minimal amount of progression needed to satisfy successive censuses.
+\item For each part in turn, we try to identify the most obvious predecessor, as the one with minimal amount of progression needed between successive censuses.
 The predecessor is removed from the list of possible predecessors and the process is repeated until all parts have predecessors.
 \item After finding a predecessor, the investment needed to progress  is calculated.
-The investment is defined as the difference between the element mass at the time of census and that of it's predecessor.
+The investment is defined as the difference between the element mass at the time of census and that of its predecessor.
 \end{itemize}
@@
 This process continues back along the plant map developmental trajectory until a plausible predecessor is located in the previous census period.
-After this process is complete, any parts from census $t$-1 for which a subsequent developmental stage is not identified as designated as having reached their final developmental stage at census $t$-1 (i.e.
+After this process is complete, any parts from census $t$-1 for which a subsequent developmental stage is not identified are designated as having reached their final developmental stage at census $t$-1 (i.e.
 they aborted).
@@
 
-Plots of the fitted relationships for both leaf mass and stem mass for each species are included below (Figs. \ref{fig:growth_Banksia_ericifolia}, \ref{fig:growth_Pultenaea_tuberculata}).
+Plots of the fitted relationships for both leaf mass and stem mass for each species are included below (Figs. \ref{fig:growth_Banksia_ericifolia}- \ref{fig:growth_Pultenaea_tuberculata}).
 
@@
 Below, for each species we provide a graphic illustration of the pathway used (Figs.
-\ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}), and tables detailing specific about each part (Tables \ref{tab:parts_Banksia_ericifolia}-\ref{tab:parts_Pultenaea_tuberculata}).
+\ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}), and tables detailing specifics about each part (Tables \ref{tab:parts_Banksia_ericifolia}-\ref{tab:parts_Pultenaea_tuberculata}).
 Figure \ref{fig:map_key} provides a key on the colouring in Figs.
@@
 Within a single column, i.e.
-within a single species developmental trajectory, numbers will change if the "count" used to access reproduction changes at a given developmental stage.
+within a single species developmental trajectory, numbers will change if the reproductive part being "counted" during censuses changes between developmental stages.
 For instance, with BOLE (\emph{Boronia ledifolia}), counts are made by flowers up through the finished flower stage, but then fruits are the unit counted for not all 4 fruits develop within each flower.

### 2018-06-05 ms/Accessory/Wenk-Accessory-SI.Rnw
Updates to SI and figures fro Accessories paper.

@@
 library(knitr)
-opts_chunk$set(echo=FALSE, fig.pos = "!h", fig.align="center", comment = NA)
+opts_chunk$set(echo=FALSE, fig.pos = "!h", fig.align="center", comment = NA, warning = FALSE)
 
@@
 
-<<echo=FALSE, results='asis', warning=FALSE>>=
+<<echo=FALSE, warning=FALSE>>=
 
-make_table_species_values_for_allocation_seedsize_table <- function(file) {
-  data <- select(file,species,scaled_seed_count,scaled_ovule_count,
-                 scaled_pollen_attract_costs,choosiness,prop_prepollen_success, prop_prepollen_discarded,
-                 prop_postpollen_success,prop_postpollen_discarded, prop_pollen_attract_vs_success,prop_provisioning_vs_success)
-  data$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  data
+make_table_figure3_main_text <- function(SummarySpp) {
+  acc_costs_spp <- dplyr::select(SummarySpp[["mean"]], species, 
+                               seedset, embryo_endo_costs, prop_pollen_attract_vs_success, 
+                               prop_prepollen_success, prop_postpollen_success)
+
+  acc_costs_spp$species <-  paste("\\textit{",labels.spp.full(),"}", sep="")
+  for (i in c("seedset", "embryo_endo_costs", "prop_pollen_attract_vs_success", 
+                               "prop_prepollen_success", "prop_postpollen_success")) {
+    acc_costs_spp[[i]] <- round(acc_costs_spp[[i]], digits = 3)
+
   }
 
-TableS15 <- make_table_species_values_for_allocation_seedsize_table(SummarySpp[["mean"]])
+  names(acc_costs_spp) <- c("Species","ratio seeds to ovules","seed size",
+                                  "prop. of successful inv. to pollen attraction tissues",
+                                  "prop. of pollen attraction tissues to successful inv.",
+                                  "prop. of provisioning tissues to successful inv.")
 
-names(TableS15) <- c("species","seed count","ovule count","pollen-attraction costs","choosi- ness","success","discarded","success","discarded","pollen-attraction","provi- sioning")
-
-for (i in 2:11) {
-TableS15[,i] <- format(TableS15[,i],digits=3, nsmall=0)
+  acc_costs_spp
 }
 
-TableS15$species  <- paste("\\textit{",unique(TableS15$species),"}", sep="")
+TableS1 <- make_table_figure3_main_text(SummarySpp)
 @
@@
 \centering
-\caption{Species values for data plotted in Figure 2: shifts in reproductive tissue allocation with seed size.
-Counts and costs are per unit leaf area of the plant.
-The bottom line indicates the corresponding figure of the main text where the data are presented.
-Data for reproductive costs (Figure 2, panel a), Seed-size, pollen-attraction costs, and provisioning costs (Figure 2, panel f) are presented in Table 1 in the main text and are not included here.}
-\label{tab:species}
-{\footnotesize
-\begin{tabular}{p{3cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1.5cm}p{1cm}}
+\caption{NEED TITLE - showing values in Figure Table 3 in the main text}
+\label{tab:fig_3_table}
+\begin{tabular}{p{4cm}p{2cm}p{2cm}p{2cm}p{2cm}p{2cm}}
 \hline
-& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c|}{Proportion}& \multicolumn{2}{c}{Proportion} \\
-& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{pollen-attraction} & \multicolumn{2}{c|}{provisioning}& \multicolumn{2}{c}{success} \\
-& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{investment to} & \multicolumn{2}{c|}{investment to}& \multicolumn{2}{c}{investment to} \\
 <<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS15)
+print(xtable(TableS1)
         , sanitize.text.function=I
@@
         only.contents=TRUE)
-cat("Figure reference & \\multicolumn{2}{c|}{Fig.
-2, panel a} & \\multicolumn{2}{c|}{Fig.
-2, panel b} & \\multicolumn{2}{c|}{Fig.
-2, panel c} & \\multicolumn{2}{c|}{Fig.
-2, panel d}  & \\multicolumn{2}{c}{Fig.
-2, panel e}\\\\
-\\hline")
 @
 \end{tabular}
-}
 \end{table}
@@
 \clearpage
+
 <<echo=FALSE, results='asis', warning=FALSE>>=
-make_table_RA_shifts_with_age <- function(SummaryInd) {
-  xvar <- "repro_inv"
-  yvar <- "accessory_costs"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+make_table_Table2_using_seed <- function() {
+slopes <- sma(repro_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
 
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_RE <- dplyr::select(fit$groupsummary,group,n,r2,pval)
+slopes <- sma(accessory_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-  xvar <- "total_weight_0"
-  yvar <- "accessory_costs"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+slopes <- sma(success_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_size <- dplyr::select(fit$groupsummary,group,n,r2,pval)
+slopes <- sma(pollen_attract_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-  xvar <- "age"
-  yvar <- "accessory_costs"
-  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
+slopes <- sma(provisioning_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
-  accessory_vs_age <- dplyr::select(fit$groupsummary,group,n,r2,pval)
+slopes <- sma(discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-  TableS16 <- merge(accessory_vs_RE,accessory_vs_size,by="group")
-  TableS16 <- merge(TableS16,accessory_vs_age,by="group")
+slopes <- sma(prepollen_discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+acc_by_species <- dplyr::bind_rows(acc_by_species,
+  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-  names(TableS16) <- c("Species","n","r$^2$","p","n","r$^2$","p","n","r$^2$","p")
+slopes <- sma(postpollen_aborted_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
+acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
 
-  Species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
-  TableS16$Species <-  paste("\\textit{",Species,"}", sep="")
+acc_by_species$variable = c("total reproductive","total accessory","seed","pollen attraction","provisioning", "failed tissue","failed pre-pollination","failed provisioning")
 
-  TableS16
+acc_by_species$Slope <- format_r2(acc_by_species$Slope)
+acc_by_species$Slope_lowCI <- format_r2(acc_by_species$Slope_lowCI)
+acc_by_species$Slope_highCI <- format_r2(acc_by_species$Slope_highCI)
+
+acc_by_species$slope2 <- paste(acc_by_species$Slope," (",acc_by_species$Slope_lowCI," - ",acc_by_species$Slope_highCI,")",sep="")
+
+acc_by_species$r2 <- format_r2(acc_by_species$r2)
+acc_by_species$pval <- format_p(acc_by_species$pval)
+acc_by_species$Slope_test_p <- format_p(acc_by_species$Slope_test_p)
+acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
 }
+TableS19 <- make_table_Table2_using_seed()
+names(TableS19) <- c("Costs","r$^2$","Slope (95$\\%$ CI)","p (slope test)")
+TableS19$Costs <- firstup(TableS19$Costs)
 
-TableS16 <- make_table_RA_shifts_with_age(SummaryInd)
-
-for(i in c(2,3,5,6,8,9)){
-  TableS16[,i] <- format_r2(TableS16[,i])
-}
-for(i in c(4,7,10)){
-  TableS16[,i] <- format_p(TableS16[,i])
-}
 @
-
 \begin{table}[h]
 \centering
-\caption{Testing for shifts in accessory costs with in age, plant size, or reproductive effort.
-Shifts in accessory costs with these variables is suggested as one possible explanation of increasing reproductive investment in larger, older plants, but such a trend did not exist in these data.}
-\label{tab:access_vs_age}
-\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.25cm}|x{.75cm}x{1cm}p{1.25cm}|x{.75cm}x{1cm}p{1.25cm}}
+\caption{Scaling of reproductive tissue costs with total seed size.
+In this manuscript all "seed size" calculations use embryo and endosperm size, not propagule size.
+Most previous research has used propagule size as a measure of "seed size" and noted isometric relationships between various tissue costs and "seed size".
+Using embryo and endosperm size, these relationship did not exist for this data set, but are present if "seed size" includes the entire propagule.}
+\label{tab:repro_tissues_vs_prop_size}
+\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{3cm}}
 \hline
-& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c|}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
-& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c|}{vs. plant mass}& \multicolumn{3}{c}{vs. age} \\
 <<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS16)
+print(xtable(TableS19)
          , sanitize.text.function=I
@@
 make_table_propagule_invest_vs_all_repropro_inv <- function(SummaryInd) {
-  mod_propagule_inv_all <- sma(repro_inv~propagule_inv,data=SummaryInd,log="xy",method="SMA")
-  mod_flower_inv_all <- sma(repro_inv~flower_inv,data=SummaryInd,log="xy",method="SMA")
 
@@
 
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=mod_propagule_inv_all$groupsummary["Slope"][[1]],elev.test=mod_propagule_inv_all$coef[[1]][1,1])
-  results <- fit$groupsummary
-  acc_slopes <- dplyr::select(results,group,n,r2,pval)
-  names(acc_slopes) <- c("Species","n_propagule","r2_propagule","p_propagule")
+  acc_slopes <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")$groupsummary %>%
+                select(group,n,r2,pval, Int, Slope)
+  names(acc_slopes) <- c("Species","n_propagule","r2_propagule","p_propagule", "int_propagule","slope_propagule")
 
@@
 
-  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
-  results <- fit$groupsummary
-  acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
-  names(acc_slopes2) <- c("Species","n_flower","r2_flower","p_flower")
+  acc_slopes2 <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy")$groupsummary %>%
+                select(group,r2,pval, Int, Slope)
+  names(acc_slopes2) <- c("Species","r2_flower","p_flower", "int_flower","slope_flower")
+
   acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="Species")
-  names(acc_slopes) <- c("Species","n","r$^2$","p", "n","r$^2$","p")
+  names(acc_slopes) <- c("Species","n","r$^2$","p","int.", "slope","r$^2$","p","int.", "slope")
   Species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
@@
 \label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
+\begin{tabular}{p{4cm}|x{.75cm}|x{1cm}x{1.5cm}x{1cm}x{1cm}|x{1cm}x{1.5cm}x{1cm}p{1cm}}
 \hline
-& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
-& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
+& & \multicolumn{4}{c|}{Total reproductive investment} & \multicolumn{4}{c}{Total reproductive investment} \\
+& & \multicolumn{4}{c|}{vs. propagule investment} & \multicolumn{4}{c}{vs. flower investment} \\
 <<echo=FALSE, results='asis', warning=FALSE>>=
 print(xtable(TableS17)
-        , sanitize.text.function=I
-        , include.rownames = FALSE
-        , include.colnames = TRUE,
-        only.contents=TRUE)
-@
-\end{tabular}
-\end{table}
-
-\clearpage
-
-<<echo=FALSE, results='asis', warning=FALSE>>=
-make_table_Table2_using_propagule <- function() {
-slopes <- sma(repro_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
-
-slopes <- sma(accessory_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(success_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(pollen_attract_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(provisioning_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(prepollen_discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(postpollen_aborted_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-acc_by_species$variable = c("total reproductive","total accessory","seed","pollen attraction","provisioning", "failed tissue","failed pre-pollination","failed provisioning")
-
-acc_by_species$Slope <- format_r2(acc_by_species$Slope)
-acc_by_species$Slope_lowCI <- format_r2(acc_by_species$Slope_lowCI)
-acc_by_species$Slope_highCI <- format_r2(acc_by_species$Slope_highCI)
-
-acc_by_species$slope2 <- paste(acc_by_species$Slope," (",acc_by_species$Slope_lowCI," - ",acc_by_species$Slope_highCI,")",sep="")
-
-acc_by_species$r2 <- format_r2(acc_by_species$r2)
-acc_by_species$pval <- format_p(acc_by_species$pval)
-acc_by_species$Slope_test_p <- format_p(acc_by_species$Slope_test_p)
-acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
-}
-TableS19 <- make_table_Table2_using_propagule()
-names(TableS19) <- c("Costs","r$^2$","Slope (95$\\%$ CI)","p (slope test)")
-TableS19$Costs <- firstup(TableS19$Costs)
-
-@
-\begin{table}[h]
-\centering
-\caption{Scaling of reproductive tissue costs with total propagule size.
-In this manuscript all "seed size" calculations use embryo and endosperm size, not propagule size.
-Most previous research has used propagule size as a measure of "seed size" and noted isometric relationships between various tissue costs and "seed size".
-Using embryo and endosperm size, these relationship did not exist for this data set, but are present if "seed size" includes the entire propagule.}
-\label{tab:repro_tissues_vs_prop_size}
-\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{3cm}}
-\hline
-<<echo=FALSE, results='asis', warning=FALSE>>=
-print(xtable(TableS19)
         , sanitize.text.function=I
@@
 \ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}).
-Tables \ref{tab:parts_Banksia_ericifolia}-Table \ref{tab:parts_Pultenaea_tuberculata} then provide, for each species, a list of plant parts, a description of exactly what tissues are included in each plant part and at what developmental stage, the method whereby the count and mass of the plant parts is measured, and the number of ovules in each unit of plant part.
+Tables \ref{tab:parts_Banksia_ericifolia}-\ref{tab:parts_Pultenaea_tuberculata} then provide, for each species, a list of plant parts, a description of exactly what tissues are included in each plant part and at what developmental stage, the method whereby the count and mass of the plant parts is measured, and the number of ovules in each unit of plant part.
 
@@
 The counts of flowers (or other reproductive tissues) were then converted to a count of ovules using the values in the variable \texttt{Multiplier per factor}.
-Tables \ref{tab:parts_Banksia_ericifolia}-Table \ref{tab:parts_Pultenaea_tuberculata} indicate for each species and plant part, the method used to estimate the mass of parts.
+Tables \ref{tab:parts_Banksia_ericifolia}-\ref{tab:parts_Pultenaea_tuberculata} indicate for each species and plant part, the method used to estimate the mass of parts.
 

### 2018-06-05 R/ms-accessory.R

@@ -25,15 +25,16 @@ figure_accessory_bar <- function(SummarySpp) {
 
 figure_accessory_v_seed_size <- function(SummarySpp) {
 
+  
   data <- SummarySpp[["mean"]]
-
+  
   par(mfrow = c(3, 2), oma = c(2, 1, 1, 0), mar = c(5, 5, 2,2))
-
+  
   XLIM <- c(0.008, 50)
   x.pred <- seq_log_range(range(data$embryo_endo_costs), 50)
   x.pred2 <- seq_log_range(range(data$seedset), 50)
-
-
+  
+  
   y.pred <- function(out, x) {
     predict(out, list(embryo_endo_costs = x),type="response")
   }
@@ -41,99 +42,101 @@ figure_accessory_v_seed_size <- function(SummarySpp) {
   y.pred2 <- function(out, x) {
     predict(out, list(prop_prepollen_success = x),type="response")
   }
-
+  
   y.pred3 <- function(out, x) {
     predict(out, list(seedset = x),type="response")
   }
-
+  
   legend_text <- function(out) {
     sprintf("R2 = %s, p %s", format_r2(R2_glm(out)), format_p2(coef(summary(out))[,4][2]))
   }
-
-  px <- -0.25
-  py  <- 1.15
-
+  
+  px <- -0.05
+  py  <- 1.2
+  
   # panel - choosiness; lower seedset species invest lower proportion of success costs in pollen attraction tissues
   plot(prop_pollen_attract_vs_success ~ seedset, data, log = "x",
        col = venetian_red, pch = 16, xlim = c(1E-3, 1), ylim = c(0, 1),
        cex = 1, ylab = "", xlab = "", xaxt = "n", yaxt = "n")
-  extra.top.left.logx("A", px = px, py = py, font=2)
-  extra.top.left.logx("Division within successfully-matured units", px = px +0.05, py =py)
+  extra.top.left.logx("A", px = px-.1, py = py-.06, font=2,cex=1.3)
+  extra.top.left.logx("Division within successfully-matured units", px = px -.02, py =py-.06,cex=1.3)
   add_axis_proprtion(2, las=1)
   add_axis_log10(1)
-
-  mtext("Prop. to pollen-attraction", 2, line = 3)
-  mtext("Ratio of seeds:ovules", 1, line = 3)
+  
+  mtext("Prop. to pollen attraction", 2, line = 3)
+  mtext("Ratio of seeds:ovules", 1, line = 2.8)
   
[…]

### 2018-06-05 ms/Accessory/Wenk-Accessory-SI.Rnw
Further updates to SI and figures

@@
                                "prop_prepollen_success", "prop_postpollen_success")) {
-    acc_costs_spp[[i]] <- round(acc_costs_spp[[i]], digits = 3)
+    acc_costs_spp[[i]] <- round(acc_costs_spp[[i]], digits = 4)
 
@@
 
-  names(acc_costs_spp) <- c("Species","ratio seeds to ovules","seed size",
-                                  "prop. of successful inv. to pollen attraction tissues",
-                                  "prop. of pollen attraction tissues to successful inv.",
-                                  "prop. of provisioning tissues to successful inv.")
+  names(acc_costs_spp) <- c("Species","Ratio seeds to ovules","seed size",
+                                  "Prop. of successful inv. to pollen attraction tissues",
+                                  "Prop. of pollen attraction tissues to successful inv.",
+                                  "Prop. of provisioning tissues to successful inv.")
 
@@
 \centering
-\caption{NEED TITLE - showing values in Figure Table 3 in the main text}
+\caption{Values plotted in Figure 3 in the main text, showing the linkage across species between maternal optimism and seed size.}
 \label{tab:fig_3_table}
@@
 make_table_Table2_using_seed <- function() {
-slopes <- sma(repro_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)
 
-slopes <- sma(accessory_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
+  f <- function(yvar, xvar, data) {
+      sma(data[[yvar]] ~ data[[xvar]],method="SMA", log="xy")$groupsummary %>% 
+      mutate(x = xvar, y=yvar) %>%
+      select(x, y, everything()) %>%
+      mutate(
+       int =  paste(format_r2(Int)," (",format_r2(Int_lowCI)," - ",format_r2(Int_highCI),")",sep=""),
+       slope = paste(format_r2(Slope)," (",format_r2(Slope_lowCI)," - ",format_r2(Slope_highCI),")",sep=""),
+       r2 = format_r2(r2),
+       pval = format_p(pval),
+       slope_test = format_p(Slope_test_p)
+    )
+  }
 
-slopes <- sma(success_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(pollen_attract_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(provisioning_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(prepollen_discarded_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species,
-  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-slopes <- sma(postpollen_aborted_costs ~ embryo_endo_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
-acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))
-
-acc_by_species$variable = c("total reproductive","total accessory","seed","pollen attraction","provisioning", "failed tissue","failed pre-pollination","failed provisioning")
-
-acc_by_species$Slope <- format_r2(acc_by_species$Slope)
-acc_by_species$Slope_lowCI <- format_r2(acc_by_species$Slope_lowCI)
-acc_by_species$Slope_highCI <- format_r2(acc_by_species$Slope_highCI)
-
-acc_by_species$slope2 <- paste(acc_by_species$Slope," (",acc_by_species$Slope_lowCI," - ",acc_by_species$Slope_highCI,")",sep="")
-
-acc_by_species$r2 <- format_r2(acc_by_species$r2)
-acc_by_species$pval <- format_p(acc_by_species$pval)
-acc_by_species$Slope_test_p <- format_p(acc_by_species$Slope_test_p)
-acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
+  dplyr::bind_rows(
+    f("repro_costs", "embryo_endo_costs", SummarySpp[["mean"]]),
+    f("accessory_costs", "embryo_endo_costs", SummarySpp[["mean"]]),
+    f("success_costs", "embryo_endo_costs", SummarySpp[["mean"]]),
+    f("pollen_attract_costs", "embryo_endo_costs", SummarySpp[["mean"]]),
+    f("provisioning_costs", "embryo_endo_costs", SummarySpp[["mean"]]),
+    f("discarded_costs", "embryo_endo_costs", SummarySpp[["mean"]]),
+    f("prepollen_discarded_costs", "embryo_endo_costs", SummarySpp[["mean"]]),
+    f("postpollen_aborted_costs", "embryo_endo_costs", SummarySpp[["mean"]])
+  ) %>%
+  mutate(
+    variable = c("total reproductive","total accessory","seed","pollen attraction","provisioning", "failed tissue","failed pre-pollination","failed provisioning")) %>%
+  select(variable, n, r2, int, slope)
 }
 TableS19 <- make_table_Table2_using_seed()
-names(TableS19) <- c("Costs","r$^2$","Slope (95$\\%$ CI)","p (slope test)")
+names(TableS19) <- c("Costs","n","r$^2$","Int (95$\\%$ CI)", "Slope (95$\\%$ CI)")
 TableS19$Costs <- firstup(TableS19$Costs)
@@
 \centering
-\caption{Scaling of reproductive tissue costs with total seed size.
-In this manuscript all "seed size" calculations use embryo and endosperm size, not propagule size.
-Most previous research has used propagule size as a measure of "seed size" and noted isometric relationships between various tissue costs and "seed size".
-Using embryo and endosperm size, these relationship did not exist for this data set, but are present if "seed size" includes the entire propagule.}
+\caption{
+Scaling of reproductive tissue costs with seed size.
+Each data point is a species average value.
+Costs are all calculated as mg carbon investment per mature seed.
+All variables showed a strong correlation with seed size (p < 0.0001).
+The table shows properties of SMA line fits, between different variables and seed size.
+All variables are log-scaled.
+}
 \label{tab:repro_tissues_vs_prop_size}
-\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{3cm}}
+\begin{tabular}{p{5cm}|x{.75cm}x{.75cm}x{3.5cm}p{3cm}}
 \hline
@@
   xvar <- "propagule_inv"
+
   data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)
 
-  acc_slopes <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")$groupsummary %>%
-                select(group,n,r2,pval, Int, Slope)
-  names(acc_slopes) <- c("Species","n_propagule","r2_propagule","p_propagule", "int_propagule","slope_propagule")
+  acc_slopes <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS", log="xy")$groupsummary %>%
+        mutate(
+          int =  paste(format_r2(Int)," (",format_r2(Int_lowCI)," - ",format_r2(Int_highCI),")",sep=""),
+          slope = paste(format_r2(Slope)," (",format_r2(Slope_lowCI)," - ",format_r2(Slope_highCI),")",sep=""),
+          r2 = format_r2(r2),
+          pval = format_p(pval)) %>%
+      select(group,n,r2, int, slope)
+  names(acc_slopes) <- c("Species","n_propagule","r2_propagule","int_propagule","slope_propagule")
 
@@
 
-  acc_slopes2 <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy")$groupsummary %>%
-                select(group,r2,pval, Int, Slope)
-  names(acc_slopes2) <- c("Species","r2_flower","p_flower", "int_flower","slope_flower")
+  acc_slopes2 <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="OLS",  log="xy")$groupsummary %>%
+        mutate(
+          int =  paste(format_r2(Int)," (",format_r2(Int_lowCI)," - ",format_r2(Int_highCI),")",sep=""),
+          slope = paste(format_r2(Slope)," (",format_r2(Slope_lowCI)," - ",format_r2(Slope_highCI),")",sep=""),
+          r2 = format_r2(r2),
+          pval = format_p(pval)) %>%
+      select(group,r2, int, slope)
+  names(acc_slopes2) <- c("Species","r2_flower","int_flower","slope_flower")
 
   acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="Species")
-  names(acc_slopes) <- c("Species","n","r$^2$","p","int.", "slope","r$^2$","p","int.", "slope")
+  names(acc_slopes) <- c("Species","n","r$^2$","intercept", "slope","r$^2$","intercept", "slope")
   Species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
   acc_slopes$Species <-  paste("\\textit{",Species,"}", sep="")
+  acc_slopes$n <- as.character(round(acc_slopes$n, 0))
 
@@
 
-for(i in c(2,3,5,6)){
-  TableS17[,i] <- format_r2(TableS17[,i])
-}
-for(i in c(4,7)){
-  TableS17[,i] <- format_p(TableS17[,i])
-}
 @
@@
 \centering
-\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight $\times$ bud count'.
+\caption{Details on linear models fitted across individuals within each species to predict total reproductive investment from (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight $\times$ bud count'.
 Due to the high proportion of aborted flowers, flower investment was a better proxy of reproductive investment than was propagule investment.
-This was true both across species (Figure 3, Table 3 in the main text) and within species, as is shown here.}
+This was true both across species (Figure 4, Table 2 in the main text) and within species, as is shown here.}
 \label{tab:propagule_invest_vs_repro}
-\begin{tabular}{p{4cm}|x{.75cm}|x{1cm}x{1.5cm}x{1cm}x{1cm}|x{1cm}x{1.5cm}x{1cm}p{1cm}}
+\begin{tabular}{p{2.5cm}|x{.75cm}|x{0.75cm}x{2.75cm}x{2.75cm}|x{0.75cm}x{2.75cm}p{2.75cm}}
 \hline
-& & \multicolumn{4}{c|}{Total reproductive investment} & \multicolumn{4}{c}{Total reproductive investment} \\
-& & \multicolumn{4}{c|}{vs. propagule investment} & \multicolumn{4}{c}{vs. flower investment} \\
+& & \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
+& & \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
 <<echo=FALSE, results='asis', warning=FALSE>>=
@@
 Below, for each species we provide a graphic illustration of the pathway used (Figs.
-\ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}), and tables detailing specific about each part (Tables \ref{tab:parts_Banksia_ericifolia}-Table \ref{tab:parts_Pultenaea_tuberculata}).
+\ref{fig:map_Banksia_ericifolia}-\ref{fig:map_Pultenaea_tuberculata}), and tables detailing specifics about each part (Tables \ref{tab:parts_Banksia_ericifolia}-\ref{tab:parts_Pultenaea_tuberculata}).
 Figure \ref{fig:map_key} provides a key on the colouring in Figs.
